### 2016-12-14 _region_.tex
testing

\message{ !name(paper.tex)}\documentclass[12pt]{report}

% This first part of the file is called the PREAMBLE. It includes
% customizations and command definitions. The preamble is everything
% between \documentclass and \begin{document}.

\usepackage[margin=1in]{geometry} % set the margins to 1in on all sides
\usepackage{graphicx} % to include figures
\usepackage{amsmath} % great math stuff
\usepackage{amsfonts} % for blackboard bold, etc
\usepackage{amsthm} % better theorem environments

% various theorems, numbered by section

\newtheorem{thm}{Theorem} \newtheorem{claim}{Claim}
\newtheorem{remark}{Remark} \newtheorem{definition}{Definition}
\newtheorem{lem}[thm]{Lemma} \newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary} \newtheorem{conj}[thm]{Conjecture}

\DeclareMathOperator{\id}{id}

\newcommand{\bd}[1]{\mathbf{#1}} % for bolding symbols
\newcommand{\RR}{\mathbb{R}} % for Real numbers
\newcommand{\ZZ}{\mathbb{Z}} % for Integers
\newcommand{\MB}{\mathbb{B}_{\matsym}} % for Integers
\newcommand{\SB}{\mathbb{B}_{\sym}} % for Integers
\newcommand{\col}[1]{\begin{matrix} #1 \end{matrix} \right]}
\newcommand{\comb}[2]{\binom{#1^2 + #2^2}{#1+#2}}
\newcommand{\stab}{\text{\textbf{Stab}}}
\newcommand{\setstab}{\text{\textbf{SetStab}}}
\newcommand{\matstab}{\text{\textbf{MatStab}}}
\newcommand{\inv}{\text{\textbf{inv}}}
\newcommand{\aut}{\text{\textbf{Aut}}}
\newcommand{\kernal}{\text{\textbf{ker}}}
\newcommand{\alt}{\text{\textbf{Alt}}}
\newcommand{\sym}{\text{\textbf{Sym}}}
\newcommand{\rank}{\text{\textbf{rk}}}
\newcommand{\orb}{\text{\textbf{Orb}}}
\newcommand{\SP}{\text{\textbf{SP}}}
\newcommand{\maj}{\text{\textbf{Maj}}}
\newcommand{\dom}{\text{\textbf{Dom}}}
\newcommand{\child}{\text{child}}
\newcommand{\countgate}{\text{count}}

\newcommand{\Alpha}{A}
\newcommand{\matsym}{\text{\textbf{MatSym}}}
\begin{document}

\message{ !name(paper.tex) !offset(540) }
\section{Translating to Formulas of FPC}
Let $C = (C_n)_{n \in \mathbb{N}}$ be a P-uniform family of polynomial-size
symmetric $(\SB, \MB, \tau)$ circuits, and where $\MB$ is the rank basis.

It remains to show that there is a formula $Q$ when interpreted in the structure
$\mathcal{A}^\leq \uplus \langle [n], \leq \rangle$. Since $C$ is p-uniform, by
the Immerman-Vardi theorem and Lemma \ref{}, we have an FP interpretation
defining a rigid symmetric circuit equivalent to $C_n$ (also called $C_n$) over
the number sort of $\mathcal{A}^\leq$, where $\Phi = (\phi_G,\phi_W,
\phi_\Omega, (\phi_s)_{s \in \SB \uplus \{rank\} \uplus \tau \uplus \{0,1\}},
(\phi_{\and_R})_{R \in \tau}, \phi_L)$, where:
\begin{itemize}
\item $\phi_G(\bar{x})$ holds iff $x$ encodes a gate
\item $\phi_W(\bar{x},\bar{y})$ holds iff $\bar{x}$ and $\bar{y}$ encode gates
  and if $g_{\bar{x}}$ and $g_{\bar{y}}$ are these two encoded gates
  respectively then $W(g_{\bar{x}}, g_{\bar{y}})$.
\item $\phi_{\Omega}(\bar{x},\bar{y})$
\item For all $s \in \SB \uplus \{rank\} \uplus \tau \uplus \{0,1\}$ we have
  that $\phi_s (\bar{x})$ holds iff $\bar{x}$ encodes a gate with a labelling
  corresponding to $s$.
\item For all $R \in \tau$ we have $\phi_{\and_R}(\bar{x}, \bar{y})$ holds iff
\item $\phi_L(\bar{x}, \bar{y}, u, v)$ holds iff $L(g_{\bar{x}})(u,v) =
  g_{\bar{y}}$.
\end{itemize}

Moreover, note that for any such circuit we could check if a given gate $g$ is a
rank gate, and check $\Sigma(g)$ in polynomial time. Thus, using the
Immerman-Vardi Theorem, we can define a formula $\text{CHAR}$ such that $\langle
[n], \leq\rangle \models \text{CHAR}[g,p,u]$ iff $\langle [n], \leq\rangle
\models \phi_G[g] \land \phi_{rank}[g]$ and the rank gate $g$ (as per the
interpretation) is over characteristic $p$ and has threshold $u$.

Similarly, using Lemma \ref{} and using the Immerman-Vardi theorem, we can
construct a formula $\text{SUPP}$ such $\langle [n], \leq \rangle \models
\text{SUPP}[g,u]$ iff $\langle [n], \leq \rangle \models \phi_G[g]$ and $u$ is
in $sp(g)$. This formula can be used as in \cite{} to inductively define
$\text{SUPP}_i(g,u)$ for each $i \in [n]$ which holds iff $u$ is the $i$th
element of the support of $g$.

Define the $\text{AGREE}$ and $\theta_s$ formulas for all $s \in \SB \uplus \tau
\uplus \{0,1\}$ as in \cite{}.

Now we define the formula
\begin{align*}
  theta_{rank}(\mu, \bar{x}) := \bigwedge_{1 \leq i < j \leq k} x_i
  \neq x_j \wedge \forall \bar{y} \( \[\rk (x \leq \phi_{mr}, y \leq
  \phi_{mc}, \pi \leq r) \theta^' \]\),
  \end{\align*}

      \begin{align*}
        \theta(a,b):= \exists \nu \(W(\nu, \mu) \and \agree (\mu,\nu, \bar{x}, \bar{y}) \and \phi_L (\mu, \nu, a, b) \and V(\nu, y)\) 
      \end{align*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\message{ !name(paper.tex) !offset(683) }

\end{document}

### 2016-12-14 paper.tex
testing

\documentclass[12pt]{report}

% This first part of the file is called the PREAMBLE. It includes
% customizations and command definitions. The preamble is everything
% between \documentclass and \begin{document}.

\usepackage[margin=1in]{geometry} % set the margins to 1in on all sides
\usepackage{graphicx} % to include figures
\usepackage{amsmath} % great math stuff
\usepackage{amsfonts} % for blackboard bold, etc
\usepackage{amsthm} % better theorem environments

% various theorems, numbered by section

\newtheorem{thm}{Theorem} \newtheorem{claim}{Claim}
\newtheorem{remark}{Remark} \newtheorem{definition}{Definition}
\newtheorem{lem}[thm]{Lemma} \newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary} \newtheorem{conj}[thm]{Conjecture}

\DeclareMathOperator{\id}{id}

\newcommand{\bd}[1]{\mathbf{#1}} % for bolding symbols
\newcommand{\RR}{\mathbb{R}} % for Real numbers
\newcommand{\ZZ}{\mathbb{Z}} % for Integers
\newcommand{\MB}{\mathbb{B}_{\matsym}} % for Integers
\newcommand{\SB}{\mathbb{B}_{\sym}} % for Integers
\newcommand{\col}[1]{\begin{matrix} #1 \end{matrix} \right]}
\newcommand{\comb}[2]{\binom{#1^2 + #2^2}{#1+#2}}
\newcommand{\stab}{\text{\textbf{Stab}}}
\newcommand{\setstab}{\text{\textbf{SetStab}}}
\newcommand{\matstab}{\text{\textbf{MatStab}}}
\newcommand{\inv}{\text{\textbf{inv}}}
\newcommand{\aut}{\text{\textbf{Aut}}}
\newcommand{\kernal}{\text{\textbf{ker}}}
\newcommand{\alt}{\text{\textbf{Alt}}}
\newcommand{\sym}{\text{\textbf{Sym}}}
\newcommand{\rank}{\text{\textbf{rk}}}
\newcommand{\orb}{\text{\textbf{Orb}}}
\newcommand{\SP}{\text{\textbf{SP}}}
\newcommand{\maj}{\text{\textbf{Maj}}}
\newcommand{\dom}{\text{\textbf{Dom}}}
\newcommand{\child}{\text{child}}
\newcommand{\countgate}{\text{count}}
\newcommand{\agree}{\text{AGREE}}
\newcommand{\supp}{\text{SUPP}}
\newcommand{\rankparam}{\text{PARAM}}

\newcommand{\Alpha}{A}
\newcommand{\matsym}{\text{\textbf{MatSym}}}
\begin{document}

\nocite{*}

\title{Circuits}

\author{Gregory Wilsenach \\ 
Computer Laboratory \\
University of Cambridge}

\maketitle

\tableofcontents

\chapter{Introduction}

\chapter{Background}

\chapter{Symmetric Circuits}

\chapter{Extending Symmetric Circuits}

\chapter{Matrix-Symmetric Circuits}

The symmetric circuits of Anderson and Dawar \cite{} have been shown to express
$FPC$.

In this section we develop a notion of a matrix-symmetric circuit, an extension
of the symmetric circuit defined by Anderson and Dawar \cite{}. This is my
latest version of the support and circuit capturing result.

\section{}

\section{Circuits and Symmetry}
\begin{definition}
  Let $A$ and $B$ be sets, say that a function $f: \{ 0,1 \}^{A \times B}
  \rightarrow \{ 0,1 \}$ is matrix-symmetric if for any $\omega: A \times B
  \rightarrow \{0, 1\}$ and $(\alpha, \beta) \in \sym_A \times \sym_B$ we have
  $f((\alpha, \beta)\cdot \omega) = f (\omega)$.
  \\
  A function $f: \{0,1\}^* \rightarrow \{0,1\}$ is matrix-symmetric iff for any
  two finite sets $A$, $B$ we have that that $f|_{A \times B}$ is
  matrix-symmetric (where $f|_{A \times B}$ is the restriction of the function
  $f$ to inputs sequences of size $\vert A \times B \vert$ and where elements of
  the input sequence are labelled by elements of $A \times B$).
\end{definition}

\section{The Support Theorem}

Without a loss of generality we assume that $A$ and $B$ are always initial
segments of the natural numbers.

% Let $C$ be a circuit over some Boolean basis. For each gate $g \in C$ we
% associate a relation $\omega_g$ (or just $\omega$ when the context makes it
% clear). We say a gate is symmetric if that relation

% So far we have defined a circuit over a Boolean basis where the circuit
% elements all compute symmetric functions. The definition of an induced
% automorphism only makes. As such, we begin by augmenting the definition of a
% circuit and automorphism.

\begin{definition}[Circuits on Structures]
  For $\mathbb{B}_{\sym}$ a basis of Boolean symmetric functions,
  $\mathbb{B}_{\matsym}$ a basis of Boolean matrix-symmetric functions and
  $\tau$ a set of relation symbols, we define a $(\mathbb{B}_\sym,
  \mathbb{B}_\sym, \tau)$-circuit $C_n$ computing a $q$-ary query $Q$ is a
  structure $\langle G, W, \Omega, \Sigma, \Lambda, L\rangle$.
  \begin{itemize}
  \item $G$ is called the set of gates of $C_n$ and $\vert C_n \vert := \vert G
    \vert$.
  \item $W \subseteq G \times G$, where $W$ is called the wires of the circuit.
    $(G,W)$ must be a directed acyclic graph. For $g \in G$ we $H_g := \{ h \in
    C_n : W(h,g)\}$ be the set of children of $g$.
  \item $\Omega$ is an injective function from $[n]^q$ to $G$. The gates in the
    image of $\Omega$ are called the output gates. When $q = 0$, $\Omega$ is a
    constant function mapping to a single output gate.
  \item $\Sigma$ is a function from $G$ to $\mathbb{B}_\sym \uplus
    \mathbb{B}_\matstab \uplus \tau \uplus \{0,1\} $ which maps input gates to
    $\tau \uplus \{0,1\}$ and where $\Sigma^{-1} (0) \leq 1$ $\Sigma^{-1} (1)
    \leq 1$ and the internal gates get mapped into $\mathbb{B}_\sym \uplus
    \mathbb{B}_\matstab$. Gates mapped to $\tau$ are called relational gates and
    gates mapped to 1 or 0 are called constant gates.
  \item $\Lambda$ is a sequence of injective functions $(\Lambda_R)_{R \in
      \tau}$ where for each $R \in \tau$, $\Lambda_R$ maps each relational gate
    $g$ with $R = \Sigma (g)$ to the tuple $\Lambda_R (g) \in [n]^r$, where $r$
    is the arity of the symbol $R$. When no ambiguity arises we write $\Lambda
    (g)$ for $\Lambda_R (g)$.
  \item $L$ is the set of labelings of $C_n$. Let $g \in G$ be an internal gate
    and $H$ be the children of $g$. Then let $S$ be a set where $\{0,1\}^S =
    \dom(\Sigma (g))$. Then $L$ is a function that assigns to $g$ an onto
    function $\omega_g:S \rightarrow H$. We call this the matrix labelling of
    $g$.
  \end{itemize}
\end{definition}

% \begin{definition}
%   let $C = \langle G, W, \Omega, \Sigma, \Lambda, L\rangle$ be a
%   $(\mathbb{B}_\sym, \mathbb{B}_\sym, \tau)$-circuit, then take $g_1,g_2 \in
%   G$ such that $\Sigma (g_1) \Sigma(g_2) \in \mathbb{B}_\matsym$.

\begin{definition}
  Let $\omega_1: A \times B \rightarrow H$ and $\omega_2: A' \times B'
  \rightarrow H'$ define the equivalence relation $\sim$ as $\omega_1 \sim
  \omega_2$ iff $\omega_1$ and $\omega_2$ have the same domain and co-domain and
  there exists $(\alpha, \beta) \in \sym_A \times \sym_B$ and for all $(a,b) \in
  A \times B$ we have $\omega_1 = \omega_2 \circ (\alpha, \beta)$.
\end{definition}

% \begin{definition}
%   Let $\omega_1: A \rightarrow H$ and $omega_2:A' \rightarrow H'$. Define the
%   equivalence relation $\sim$ as $\omega_1 \sim \omega_2$ iff $\omega_1$ and
%   $\omega_2$ have the same domain and co-domain, and
% \end{definition}

\begin{definition}[Automorphism]
  let $C = \langle G, W, \Omega, \Sigma, \Lambda, L\rangle$ be a
  $(\mathbb{B}_\sym, \mathbb{B}_\sym, \tau)$-circuit computing at $q$-ary query
  on structures of size $n$. Let $\sigma \in \sym_n$ and $\pi: G \rightarrow G$
  be a bijection such that
  \begin{itemize}
  \item for all gates $g, h \in G$, $W(g,h)$ iff $W(\pi g, \pi h)$,
  \item for all output tuples $x \in [n]^q$, $\pi \Omega (x) = \Omega (\sigma
    x)$,
  \item for all gates $g \in G$, $\Sigma (g) = \Sigma (\pi g)$, and
  \item for each relational gate $g \in G$, $\sigma \Lambda (g) = \Lambda (\pi
    g)$
  \item for each internal gate $g$ if $\Sigma (g) \in \mathbb(B)_\matsym$. Then
    we have that $L(\pi g) \sim \pi \circ L(g)$.
  \end{itemize}
\end{definition}

\begin{remark}
  I also need a new notion of robustness here in order to collapse gates that
  have the same children and equivalent labelings are properly regarded as being
  the same gate.
\end{remark}
% \begin{definition}
%   Let $C$ be a circuit, $g$ be a gate in $C$, $H$ be $g$'s set of children and
%   let $\omega: A \times B \rightarrow H$ be a surjection, where $A$ and $B$
%   are sets and $g$ takes $\vert A \vert \cdot \vert B \vert$ inputs. Call such
%   an $\omega$ a matrix labeling for $g$.
% \end{definition}

% \begin{definition}
%   Let $C$ be a circuit and $g_1$ and $g_2$ be gates in $C$. Let $\sigma \in
%   \sym_n$ be a permutation such
% \end{definition}

\begin{definition}
  Let $\omega$ be a matrix labeling for $g$. Define the matrix stabilizer for
  $\omega$, denoted by $\matstab(\omega)$, to be the set of all $\sigma \in
  \sym_n$ such that $\sigma H = H$ and there exists $(\alpha, \beta) \in \sym_A
  \times \sym_B$ such that for all $(i,j) \in A \times B$ we have that $\omega
  (\alpha i, \beta j) = \sigma \omega (i,j)$.
\end{definition}

\begin{definition}
  Let $g$ be a gate with matrix labeling $\omega$, $h,h' \in H$ and $\sigma \in
  \sym_n$. We say that a pair $(h, h')$ is compatible with $(\sigma, \omega)$ if
  $\sigma h, \sigma h' \in H$ and there exists $(\gamma_1, \gamma_2),
  (\gamma_1', \gamma_2') \in \sym_A \times \sym_B$ s.t.
  \begin{align*}
    &(\gamma_1, \gamma_2) \cdot \omega^{-1} (h) = \omega^{-1}(\sigma h), \text{ and} \\ 
    &(\gamma_1', \gamma_2') \cdot \omega^{-1} (h') = \omega^{-1}(\sigma h'),
  \end{align*}
  and for all $(i,j) \in \omega^{-1}(h)$, $(i',j') \in \omega^{-1}(h')$ we have
  that
  \begin{align*}
    &i =i' \implies \gamma_1(i) = \gamma_1'(i'), \text{ and} \\
    &j =j' \implies \gamma_2(j) = \gamma_2'(j').
  \end{align*}

\end{definition}

\begin{lem}
  Let $g$ be a gate, $\omega$ be a matrix labeling of $g$, $\sigma \in \sym_n$.
  Then $\sigma \in \matstab(\omega)$ iff for all $h,h' \in H$ we have that
  $(h,h')$ is compatible with $(\sigma, \omega)$.
\end{lem}

\begin{proof}
  $`\Rightarrow'$: We have that $\sigma \in \matstab(\omega)$ and so there
  exists $(\alpha, \beta) \in \sym_A \times \sym_B$ such that for all $(i,j) \in
  A \times B$ we have $\sigma \omega (i,j) = \omega (\alpha i, \beta j)$. From
  compatibility we have that $h,h' \in H$ Let $h, h' \in H$ . Let $(\gamma_1,
  \gamma_2) := (\gamma_1', \gamma_2') := (\alpha, \beta)$. This assignment is
  sufficient to prove the direction.

  $`\Leftarrow'$: Suppose for all $h,h' \in H$ we have $(\gamma_1, \gamma_2),
  (\gamma_1, \gamma_2') \in \sym_A \times \sym_B$ satisfying the above
  requirements. Notice that for a given $i \in A$ and any $j, j' \in B$, let $h
  = \omega(i,j)$ and $h' = \omega(i,j')$, then we have that $\gamma_1 (i) =
  \gamma_1'(i)$. It follows that we can define a $\alpha \in \sym_A$ by
  $\alpha(i) = \gamma_1 (i)$. Similarly we can define $\beta \in \sym_B$ by
  $\beta (j) = \gamma_2 (j)$.

\end{proof}

\begin{definition}
  Let $g$ be a gate with matrix labeling $\omega$. Let $(\sigma, h, h') \in
  \sym([n]) \times H^2$. Say that $(\sigma, h, h')$ is useful if $(h,h')$ is
  incompatible with $(\sigma, \omega)$.

  Say that two distinct pairs $(\sigma_1, h_1, h_1'), (\sigma_2, h_2, h_2') \in
  \sym([n]) \times H^2$ are mutually independent if
  \begin{itemize}
  \item $\sigma_2 h_1 = h_1$,
  \item $\sigma_2 \sigma_1 h_1 = \sigma_1 h_1$,
  \item $\sigma_2 h_1' = h_1'$,
  \item $\sigma_2 \sigma_1 h_1' = \sigma h_1'$,
  \end{itemize}
  We say that a set $S \subseteq \sym([n]) \times H^2$ is useful if each pair in
  it is useful. We say that S is independent if each pair of distinct pairs in
  $S$ are mutually independent.
\end{definition}

We denote the usual equivalence relation on $\sym_n$ from the (right) cosets of
$\matstab(\omega)$ by $\sim_\omega$.

\begin{lem}
  Let $\sigma_1, \sigma_1 \in \sym_n$ and suppose $\sigma_1 \sim_\omega
  \sigma_2$ then for any $(h,h') \in H^2$ we have that $(h,h')$ is compatible
  with $(\sigma_1, \omega)$ iff $(h,h')$ is compatible with $(\sigma_2,
  \omega)$.
\end{lem}

\begin{proof}
  Suppose we have that $\sigma_1 \sim_\omega \sigma_2$. And additionally
  supposed $(h, h')$ compatible with $(\sigma_1, \omega)$.

  It follows there exists $(\alpha, \beta) \in \sym_A \times \sym_B$ such that
  $\sigma_1 \omega (i,j) = \sigma_2\omega (\alpha i, \beta j)$, and we have
  $(\gamma_1, \gamma_2), (\gamma_1', \gamma_2') \in \sym_A \times \sym_B$
  satisfying the requirements of compatibility. We note that $(\alpha, \beta)
  \cdot \omega^{-1}(\sigma_1 h) = \omega^{-1}(\sigma_2 h)$. Thus by composition
  we have that $(\alpha \gamma_1, \beta \gamma_2) \cdot \omega^{-1}(h) =
  \omega^{-1}(\sigma_2 h)$ and $(\alpha \gamma_1', \beta \gamma_2') \cdot
  \omega^{-1}(h') = \omega^{-1}(\sigma_2 h')$, and clearly the remaining
  requirement for compatibility follows from the bijectivity of $\alpha$ and
  $\beta$. The result follows. The other direction of the implication follows
  from symmetry.
\end{proof}

\begin{claim}
  \label{claim:useful-independant-set}
  Let $g$ be a rank gate with labeling $\omega$ and child set $H$. Let $S$ be a
  useful and independent. We then have that $\vert \sym_n: \matstab(\omega)
  \vert \leq 2^{\vert S \vert}$.
\end{claim}

\begin{proof}
  Let $R \subseteq S$ and define $\sigma_R = \Pi_{(\sigma, h, h') \in R} \sigma$
  (with some arbitrary order assumed on $S$). Let $R$ and $Q$ be distinct
  subsets of $S$ and WLOG let $\vert R \vert \geq \vert Q \vert$. We want to
  show that we don't have $\sigma_R \omega \sim_\omega \sigma_Q \omega$. Pick
  any $(\sigma, h, h') \in R/Q \neq \emptyset$. Given that $\sigma_R h = \sigma
  h$ and $\sigma_R h' = \sigma h'$ it is easy to see that the usefulness of
  $(\sigma, h,h')$ implies the incompatibility of $(h,h')$ with with $(\omega,
  \sigma_R)$. Moreover, the fact that $\sigma_Q h = h$ and $\sigma_Q h' = h'$
  makes it easy to see $(h,h')$ is compatible with $(\omega, \sigma_Q)$. From
  the above lemma we may conclude that that we do not have $\sigma_R \sim_\omega
  \sigma_Q$, and the result follows.
\end{proof}

The following two lemmas proved by Anderson and Dawar \cite{} are both of use in
proving the following theorem.

\begin{lem}
  \label{lem:big-or-small}
  For any $\epsilon$ and $n$ such that $0 < \epsilon < 1$ and $\log n \geq
  \frac{4}{\epsilon}$, if $\mathcal{P}$ is a partition of $[n]$ with $k$ parts,
  $s = [\sym_n : \setstab (\mathcal{P})]$ and $n \leq s leq 2^{n^{1-\epsilon}}$,
  then $\min \{k, n-k\} \leq \frac{8}{\epsilon} \frac{\log s}{\log n}$.
\end{lem}

\begin{lem}
  \label{lem:small-means-support}
  For any $\epsilon$ and $n$ such that $0 < \epsilon < 1$ and $\log n \geq
  \frac{8}{\epsilon^2}$, if $\mathcal{P}$ is a partition of $[n]$ with $\vert
  \mathcal{P} \vert \leq \frac{n}{2}$, $s:= [\sym_n : \setstab (\mathcal{P})]$
  and $n \leq s \leq 2^{n^{1-\epsilon}}$, then $\mathcal{P}$ contains a part $P$
  with at least $n - \frac{33}{\epsilon} \cdot \frac{\log s} {\log n}$.
\end{lem}

If $g$ is a symmetric gate (i.e. the usual gates in a circuit) we note that
$\orb(g) = [\sym_n : \stab (g)]$ by the orbit-stabilizer theorem.

If $g$ is a matrix-symmetric gate then $\orb(g) = [\sym_n:\matstab (\omega)]$,
where $\omega$ is the matrix labelling associated with $g$.

\begin{thm}
  For any $\epsilon$ and $n$ such that $\frac{2}{3} \leq \epsilon \leq 1$ and $n
  \geq \frac{128}{\epsilon^2}$, if $C$ is a symmetric, rigid circuit on
  structures of size $n$ and $s := \max_{g \in C} \vert \orb (g)\vert \leq
  2^{n^{1-\epsilon}}$, then, $SP(C) \leq \frac{33}{\epsilon}\frac{log s}{log
    n}$.
\end{thm}

\begin{proof}
  It is easy to see that if $g$ is a gate in $C$ then $\stab (g) \subseteq
  \setstab(\SP(g))$, and so $s \geq \orb(g) = [\sym_n : \stab(g)] \geq [\sym_n :
  setstab(\SP(g))]$. Thus if $\vert \SP(g) \vert \leq frac{n}{2}$, then from
  Lemma \ref{lem:small-means-support}, we have $\| SP (g) \| \leq
  \frac{33}{\epsilon} \cdot \frac{\log s} {\log n}$. The result thus follows
  from showing that for each $g$ in $C$ we have that $\vert \SP (g) \vert \leq
  \frac{n}{2}$.

  % Include some detail here for constant and relational gates
  The cases where $g$ is a constant or relational gate are easy to handle.

  We now consider the case for internal gates. Let $g$ be the topologically
  first internal gate with $\vert \SP(g) \vert > \frac{n}{2}$. If $g$ is not a
  matrix-symmetric gate then the result follows from the argument presented by
  Anderson and Dawar \cite{}. Suppose $g$ is a matrix-symmetric gate, and
  suppose $g$ has a labelling $\omega$. We now argue that this leads to a
  contradiction.

  Let $k' := \lceil \frac{8 \log s}{\epsilon \log n} \rceil$. From the
  assumptions on $s, n$ and $\epsilon$ we have that $k' \leq
  \frac{1}{4}n^{1-\epsilon} < \frac{n}{2}$. Lemma \ref{lem:big-or-small} implies
  that $n - \vert \SP(g) \vert \leq k'$

  From Claim \ref{claim:useful-independant-set} it remains to show that we can
  construct a sufficiently large useful and independent set of gate-automorphism
  pairs $S$. Divide $[n]$ into $\lfloor \frac{n}{k' + 2} \rfloor$ disjoint sets
  $S_i$ of size $k' + 2$ and ignore the elements left over. It follows that for
  each $i$ there is a permutation $\sigma_i$ which fixes $[n] / S_i$ pointwise
  but moves $g$. Suppose there was no such $\sigma_i$ it follows that every
  every permutation that fixes $[n]/S_i$ pointwise fixes $g$. Thus the partition
  of all the singletons in $[n]/S_i$ and $S_i$ is a supporting partition. As
  $\SP(g)$ is the coarsest partition it follows that $\vert \SP(g) \vert \leq n
  - (k'+2) + 1 = n - k' - 1$, which contradicts the inequality $n - \vert \SP(g)
  \vert \leq k'$.

  Since $g$ is moved by each $\sigma_i$ and $C$ is rigid it follows that we
  don't have $\sigma_i \notin \matstab(\omega)$. Thus there exists $(h_i, h_i')$
  that is inconsistent with $(\sigma_i, \omega)$, and so the triple $(\sigma_i,
  h_i, h_i')$ is useful.

  Let $\SP (h)^*$ be the union of all parts of $\SP(h)$ except for the largest
  part. Let $Q_i = \SP(h_i)^* \cup \SP(\sigma_i h_i)^* \cup \SP (h_i')^* \cup
  \SP (\sigma_i h_i')^*$. Then note that if $\sigma_j$ fixes $Q_i$ then by
  construction, we have that $\sigma_j \in \stab_n(\SP(h_i)) \cap
  \stab_n(\SP(\sigma_i h_i)) \cap \stab_n(\SP(h_i')) \cap \stab_n(\SP(\sigma_i
  h_i'))$

  Define a graph $K$ with vertices given by the sets $S_i$ and an edge from
  $S_i$ to $S_j$ (with $i \neq j$) if $Q_i \cap S_j \neq \emptyset$. It follows
  then that if there is no edge between $S_i$ and $S_j$ then $(\sigma_i, h_i,
  h_i')$ and $(\sigma_j, h_j, h_j')$ are mutually independent. It remains to
  argue that $K$ has a large independent set. This is possible as the out-degree
  of $S_i$ in $K$ is bounded by
  \begin{align*}
    \vert Q_i \vert \leq \|SP(h_i) \| + \|SP(\sigma_i h_i) \| + \|SP(h_i') \| + \|SP(\sigma_i h_i') \leq 4 \cdot \frac{33\log s}{\epsilon \log n}
  \end{align*}.

  This follows as the sets $S_i$ are disjoint and we may apply Lemma
  \ref{lem:small-means-support} to each of the child gates. It follows that the
  average total degree (in + out degree) of $K$ is at most $2 \cdot \vert Q_i
  \vert \leq 34 \cdot k'$. Now greedily select a maximal independent set in $K$
  by repeatedly selecting $S_i$ with the lowest total degree and eliminating it
  and its neighbours. This action does not affect the bound on the average total
  degree of $K$ and hence determines an independent set $I$ in $K$ of size at
  least
  \begin{align*}
    \frac{\lfloor \frac{n}{k' + 2} \rfloor}{34k' + 1} \geq \frac{n - (k'+2)}{34k'+1k'+2} \geq \frac{n\frac{7}{16}}{34k'^2 + 69k' +2} \geq \frac{n}{(16k')^2}.
  \end{align*}

  Take $S = \{(\sigma, h, h') : S_i \in I \}$. Then from the above argument we
  have that $S$ is useful and independent.

  Moreover, from Claim \ref{claim:useful-independant-set}, we have that $s \geq
  \vert \orb(g) \vert \geq 2^{\vert S \vert} \geq 2^{\frac{n}{(16k')^2}}$ then
  $n^{1-\epsilon} \geq \log s \geq n \cdot (\frac{128}{\epsilon}\frac{\log
    s}{\log n})^{-2} > n \cdot (n^{1-\epsilon})^{-2} = n^{2\epsilon -1} \geq
  n^{1-\epsilon}$. This is a contradiction.
\end{proof}

\section{Rigid Circuits}

\begin{definition}
  We say that a circuit $C$ has bijective labels if for each gate $g$ in $C$,
  $L(g)$ is a bijection.
\end{definition}

\begin{lem}
  \label{lem:bij_labels}
  There is an algorithm that runs in polynomial time that takes in a circuit $C$
  and outputs a circuit with unique gates $C'$. Moreover, if $C$ was symmetric
  then $C'$ is symmetric. If $C$ is rigid then $C'$ is rigid.
\end{lem}

\begin{proof}
  Let $S = 2*\vert C \vert$. Recurse through the gates of $C$ topologically and
  let $h$ be the next gate topologically. If for all $g \in W(h, \cdot)$ we have
  that $L\vert (g)^{-1}(h) \vert = 1$ continue on to the next gate. If not add
  in a tower of $S$ $\and$ gates such that $h \rightarrow \and^h_1 \rightarrow
  \ldots \rightarrow \and^h_S$ (i.e. we have a tower of $\and$ gates with $h$ as
  input to $\and^h_1$ and the output of each $\and^h_i$ connected to the input
  of each $\and^h_{i+1}$ for each $1 \leq i < S$). Now for each $g \in W(h,
  \cdot)$, if $L(g)^{-1}(h) = \{ s_0, \ldots, s_{r}\}$, for each $1 \leq i \leq
  r$ add in the wires $W(\and^h_i, g)$ and set $L(g)(s_{i}) = \and^h_i$. Now
  continue on to the next gate topologically and run the above algorithm.

  % First, notice that for a given gate $h$ and $k \in \mathbb{N}$, we can
  % define
  % a sub-circuit $h^k = 1 \and \cdots, 1 \and h$ (or rather a $k$-height tower
  % of
  % $k$ binary $\and$ gates with $h$ at the top and all other inputs set to
  % $1$).
  % We call $h$ the top of the sub-circuit $h^k$ and the bottom $and$ gate (the
  % output of the sub-circuit) the bottom gate. We may think of this as a
  % $k$-height copy of the gate $h$, in the sense that it has the same output as
  % $h$ and similar orbits. We now use different copies to distinguish gates
  % that
  % otherwise have the same labelling.

  % Let $h$ be the next gate topologically. Then let $r$ be maximal such that
  % $W(h,g)$ and $\omega_g^{-1}(h) = \{ s^g_1, s^g_2, \ldots, s^g_r \}$. Then
  % let
  % $k$ be the height of the highest tower with $h$ at the top and with it's
  % bottom connected to a gate in $W(h, \cdot)$. Then create a single
  % $k+r-1$-height tower by adding in the appropriate number of binary $\and$
  % gates below $h$.

  % For each $g \in W(h, \cdot)$ and for each $\omega_g^{-1}(h) = \{s^g_1,
  % s^g_2,\ldots , s^g_{r_g}\}$, set $L'(g)(s^g_1) = h$ each child starting with
  % the $and$-gate child to $h$ add in a wire from from the $i$th gate in the
  % tower to $g$ and set $L'(g)(s^g_{i+1}) = \and_i$, where $\and_i$ is the
  % $i$th
  % $\and$ gate in the tower starting with the $\and$ gate in the tower child to
  % $h$. There are enough gates in the tower as $r_g \leq r$.

  We call this updated circuit $C'$.

  Firstly, note that after running the above algorithm for each $g$ the
  labelling of $g$ will be a bijection. Moreover, it's easy to see that the
  output of each gate remains unchanged, and as such the output of the circuit
  is unchanged.

  Secondly, notice that the size of $C'$ is at most $2*\vert C \vert^2$, and
  note that the above algorithm runs in polynomial time.

  Now suppose that $C$ is symmetric. Let $\sigma$ be a permutation on the input
  universe and $\pi_C$ the induced automorphism on $C$. We now define $\pi$, the
  induced automorphism on $C'$. For each gate $g$ in $C'$, if $g$ is in $C$ then
  set $\pi(g) := pi_C(g)$. If $g$ is not in $C$ then $g$ must be some
  $\and^h_i$, for some $h$ in $C$. Then set $\pi(\and^h_i) :=
  \and^{\pi_C(h)}_i$. It is easy to see that $\pi$ is an automorphism, and $\pi$
  extends $\sigma$.

  Suppose that $C$ is rigid. It is easy to see that $C'$ will be rigid as well.

\end{proof}

% If $h$ is a binary $\and$ gate, then we say that $h$ has height $k+1$ if it
% has a $k$-height tower of binary $and$ gates connected above it, with a
% non-$\and$ gate $p$ connected to the final binary $\and$ gate, and all other
% inputs connected to $1$. We then say that $h$ is the base of a tower of height
% $k$ and type $p$.

% Then for each $h \in W_g$, if $h$ is not a binary $\and$ gate, the let $k$ be
% the largest integer such that there a gate $h' \in W(h, \cdot)$ which is the
% base of a tower of height $k$ and type $h$. it's output directly connected to
% one of the gates in $W(h^k, \cdot)$ (with k = 0 corresponding to just $h$).
% Then each $i \in \{1, \ldots , \vert \omega^{-1}(h)\vert\}$ add into the
% circuit $h^{k+i}$ and wire it to $g$. Notice that this step requires adding
% $\vert \omega^{-1}(h) \vert -1$ gates to the circuit. For some assumed
% ordering $\dom(\omega)$, let $\{s_0, \cdot, s_m\} = \omega^{-1}(h)$. Define
% $L'(g)(s_i) = h^{k+i}$. Now continue on to the next gate topologically where
% $L(g)$ is not a bijection, and execute the same process

\begin{lem}
  There is an algorithm that runs in polynomial time that takes in a circuit $C$
  and outputs a circuit $C'$ such that $C'$ is rigid and has bijective labels.
  Moreover, if $C$ was symmetric it follows that $C'$ will be symmetric.
\end{lem}

\begin{proof}
  First run the algorithm from Lemma \ref{lem:bij_labels} on $C$, and call the
  output circuit $C$.

  Recurse through the gates of $C$ topologically. For each internal gate $g$,
  for all $g'$ in $C$ such that $g \neq g'$, $W(\cdot, g) = W(\cdot, g')$, $W(g,
  \cdot) = W(g', \cdot)$, $\Sigma(g) = \Sigma(g')$, $L(g) \sim L(g')$ and
  $\Omega^{-1}(g) = \Omega^{-1}(g')$, delete $g'$ and for all $s \in L^{-1}(g')$
  set $L(s) := g$.

  Now re-run the algorithm from Lemma \ref{lem:bij_labels} on $C$ and output the
  result.
\end{proof}

  \begin{lem}
    Let $C = \langle G, W, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\SB, \MB,
    \tau)-circuit$ on structures of size $n$. There is a deterministic algorithm
    which runs in Poly($\vert C \vert$) and outputs a rigid $(\SB, \MB, \tau)
    circuit$ $C'$ such that $G' = G$ and for any $g \in G$, and any input
    $\tau$-structure $\mathcal{A}$ and any bijection $\gamma$ from $A$ to $[n]$,
    $C[\gamma \mathcal{A}](g) = C'[\gamma \mathcal{A}](g)$ and if $C$ is
    symmetric then so is $C'$.
  \end{lem}

  \begin{proof}

  \end{proof}

  \section{Computing Supports}
  \begin{lem}
    Let $C$ be a rigid $(\SB, MB, \tau)$-circuit on structures of size $n$ and
    $\sigma \in \sym_n$. There is a deterministic algorithm which runs in time
    Poly($\vert C \vert$) and outputs for each gate $g$ its image under the
    automorphism $\pi$ induced by $\sigma$, if it exists.
  \end{lem}
  \begin{proof}
    The proof proceeds by recursively going through the circuit and building the
    mapping $\pi$ induced by $\sigma$.

    Suppose $g$ is a constant gate, then $\pi g := g$. Suppose $g$ is a
    relational gate, then there is at most one gate $g'$ such that $\Sigma (g) =
    \Sigma (g')$ and $\sigma\Lambda (g') = \Lambda (g)$. If such a $g'$ exists
    assign $\pi g := g'$, else terminate with failure.

    If $g$ is an symmetric internal gate then (from rigidity) there is at most
    one gate $g'$ such that $\Sigma (g) = \Sigma(g')$ and $W_{g'} = \pi W_g$.
    Assign $\pi g := g'$ if such a gate exists, or else terminate with failure.

    If $g$ is a matrix-symmetric internal gate then consider the set of gates
    $g'$ such that $g'$ has children $\pi W_g$ and $\Sigma(g) = \Sigma(g')$, and
    let $A \times B = \dom (Sigma(g))$. If no such gate $g'$ exists, terminate
    with failure. Define $\sigma_{\pi, g'}:A \times B \rightarrow A \times B$ by
    $\sigma_{\pi, g'} = \omega^{-1}_{g'} \pi \omega_{g}$. Then clearly
    $\omega_{g'} \sigma_{\pi, g'} = \pi \omega_{g}$, and it's easy to show that
    $\pi \omega_g \sim \omega_{g'}$ iff $\sigma_{\pi,g'} \in \sym_A \times
    \sym_B$. But this just involves checking that $\sigma$ acts as a bijection
    on $A$ and $B$ separately and, given that $\vert A \vert$ and $\vert B
    \vert$ are both bounded by $\vert C \vert$, the algorithm which just
    iterates through $A$ and $B$ is sufficient. If for every $g'$ it is found
    that $\pi_{\sigma,g'}$ is not in $\sym_A \times \sym_B$ then terminate with
    failure. If there is a $g'$ for which $\pi_{\sigma, g'} \in \sym_A \times
    \sym_B$ then it is unique by rigidity and so set $\pi g := g'$.

    If $g$ is an output gate, then check that for all tuples in $[n]^{q}$ we
    have that $\pi \Omega (x) = \Omega (\sigma (x))$, and terminate with failure
    if the condition is not met.

    If the algorithm has not terminated with failure, output the automorphism.

    The algorithm clearly runs in Poly($\vert C \vert$)
  \end{proof}

  \section{Evaluating Symmetric Circuits}
  We need to extend two Lemmas in this section.

\begin{lem}
  Let $g$ be a matrix-symmetric gate in $C_n$ with children $H$. Let $\alpha \in
  U^{\underbar{\sp(g)}}$, and suppose $\gamma_1, \gamma_2: U \rightarrow [n]$
  with $\gamma^{-1}_1 \sim \alpha$ and $\alpha \sim \gamma^{-1}_2$. Let $A
  \times B = \dom (L(g))$.

  For an input structure $\mathcal{A}$, let $L^0_\gamma: A \times B \rightarrow
  \{0,1\}$, where $L^0_\gamma (a,b):= C[\gamma \mathcal{A}] (L(g)(a,b))$.

  Then $L^0_{\gamma_1} \sim L^0_{\gamma_2}$.
\end{lem}

\begin{proof}
  We have that there exists a unique $\pi \in \sym_n$ such that $\pi \gamma_1 =
  \gamma_2$. Moreover, since $\gamma^{-1}_1$ and $\gamma^{-1}_2$ are both
  consistent with $\alpha$, it follows that $\pi$ must fix $\sp(g)$. Thus $L(g)
  \sim \pi L(g)$, and so there exists $(\sigma, \lambda)$ such that $\pi L(g) =
  L(g) (\sigma, \lambda)$.

  We then have that,
  \begin{align*}
    L^0_{\gamma_1} (a,b) &= C_n[\gamma_1 \mathcal{A}](L(g)(a,b))\\
                         & = C_n[\pi gamma_1 \mathcal{A}][\pi L(g)(a,b)] \\
                         & = C_n[gamma_2 \mathcal{A}][L(g)((\sigma, \lambda)(a,b))]\\
                         & = L^0_{\gamma_2} ((\sigma, \lambda) (a,b)),
  \end{align*}
  and it follows that $L^0_{\gamma_1} \sim L^0_{\gamma_2}$.

\end{proof}

\begin{lem}
  Let $g$ be a matrix symmetric gate in $C_n$ with children $H$. Let $\alpha \in
  U^{\underbar{\sp(g)}}$ and $\gamma: U \rightrrow [n]$ such that
  $gamma^{-1}\sim \alpha$. Let $A \times B = \dom (L(g))$ and define
  $L^{EV}_\alpha: A \times B \rightarrow \{0,1\}$ by
  \begin{align*}
    L^{EV}_\alpha (a,b):=
    \begin{cases*}
      1 & if $A_h \cap \EV_h \neq \emptyset$ 0 & otherwise
    \end{cases*},
  \end{align*}
  where for $h \in W_g, A_h:= \{\beta \in U^{\underline{\sp(h)}} \vert \alpha
  \sim \beta\}$. Then $L^0_\gamma = L^{EV}_\alpha$ and $\alpha \in \EV(g)$ iff
  $\rk^u_p(L^0_\gamma)$
\end{lem}
\begin{proof}

\end{proof}

\begin{lem}
  Let $g$ be a matrix-symmetric gate in $C_n$ with children $W_g$. $Let \alpha
  \in U^{\underbar{\sp(g)}}$ and let $\gamma: U \rightarrow [n]$ such that
  $\gamma^{-1} \sim \alpha$. Let $A \times B = \dom (L(g))$, and let
  $f:\{0,1\}^{A \times B} \rightarrow \{0,1\}$ be the matrix-symmetric function
  associated with $g$. Define $L^{EV}_\alpha: A \times B \rightarrow \{0,1\}$ by
  \begin{align*}
    L^{EV}_\alpha (a,b):=
    \begin{cases*}
      1 & if $A_h \cap \EV_h \neq \emptyset$ 0 & otherwise
    \end{cases*},
  \end{align*}
  where for $h \in W_g, A_h:= \{\beta \in U^{\underline{\sp(h)}} \vert \alpha
  \sim \beta\}$. Then $\alpha \in \EV_g$ iff $f(L^\EV_\alpha)$.
\end{lem}
\begin{proof}
  First note that if $\alpha \in U^{\underbar{\sp{g}}}$ then $\alpha \in \EV_g$
  iff we have that $C_n[\gamma \mathcal{A}](g)= f (L^0_\gamma) = 1$. Notice that
  from Lemma \ref{} that this holds for any particular $\gamma$ iff it holds for
  all such $\gamma$.

  We now show that $L^\EV_\alpha = L^0_\gamma$, and so complete the proof.

  Suppose for $(a,b) \in A \times B$ we have that $L^\EV_\alpha(a,b) = 1$. Let
  $h:= L(g)(a,b)$. It follows that $A_h \cap \EV_h \neq \emptyset$, i.e there
  exits $\beta \in \sp(h)$ such that $\beta \sim \alpha$ and there exists
  $\gamma_h \in \Gamma(h)$ such that $\gamma^{-1}_h \sim \beta$. It follows from
  transitivity and Lemma \ref{} that $\gamma_h \sim \alpha$ and so
  $L^0_\alpha(a,b) = C_n[\gamma \mathcal{A}](h) = C_n[\gamma_h \mathcal{A}](h) =
  1$.

  Now suppose that $L^0_\gamma (a,b) = 1$
\end{proof}

\section{Translating to Formulas of FPC}
Let $\mathcal{C} = (C_n)_{n \in \mathbb{N}}$ be a P-uniform family of
polynomial-size symmetric $(\SB, \MB, \tau)$ circuits, and where $\MB$ is the
rank basis. It remains to show that there is a formula $Q$ in the vocabulary
$\tau \uplus \{\leq\}$ such that for any $n$ and $\tau$-structure $\mathcal{A}$
with a universe $U$ of carnality $n$, the $q$-ary query defined by $C_n$ on the
input $\mathcal{A}$ is defined by the formula $Q$ when interpreted in the
structure $\mathcal{A}^\leq = \mathcal{A} \uplus \langle [n], \leq \rangle$.

Since $\mathcal{C}$ is $P$-uniform, and from Lemmas \ref{} and \ref{} and the
Immerman-Vardi theorem, we have an FP interpretation defining a rigid symmetric
circuit with bijective labels equivalent to $C_n$ (which we also call $C_n$)
over the the number sort of $\mathcal{A}^\leq$, where $\Phi = (\phi_G,\phi_W,
\phi_\Omega, (\phi_s)_{s \in \SB \uplus \{rank\} \uplus \tau \uplus \{0,1\}},
(\phi_{\and_R})_{R \in \tau}, \phi_L)$. We note that $Phi$ is a $t$-width
interpretation over the universe $[n]$. So if $\mu, \nu, \nu_1, \ldots \in
[n]^t$, the formulas are defined such that:

\begin{itemize}
\item $\phi_G(\mu)$ holds iff $\mu$ encodes a gate
\item $\phi_W(\nu,\mu)$ holds iff $\nu$ and $\mu$ encode gates and if $g_{\nu}$
  and $g_{\mu}$ are these two encoded gates respectively then $W(g_{\nu},
  g_{\mu})$.
\item $\phi_{\Omega}(\nu_1, \ldots, \nu_q, \mu)$ holds iff $\nu_1, \ldots, nu_q$
  each encode numbers less than or equal to $[n]$ and $\Omega(\nu_1, \ldots,
  \nu_q) = g_\mu$.
\item For all $s \in \SB \uplus \{rank\} \uplus \tau \uplus \{0,1\}$ we have
  that $\phi_s (\mu)$ holds iff $\mu$ encodes a gate such that $\Sigma(g_\mu) =
  s$ (or, in the case that $s = \rank$, we require that $\Sigma(g_\mu)$ is a
  rank symbol.)
\item For all $R \in \tau$ with arity $r$ we have that $\phi_{\and_R}(\nu_1,
  \ldots, \nu_r, \mu)$ holds iff $\nu_1 , \ldots , \nu_r$ encodes numbers less
  than or equal to $[n]$, $\mu$ encodes a gate such that $\Sigma(g_\mu) = R$ and
  $\Lambda_R(g_\mu) = (\nu_1, \ldots, \nu_r)$.
\item $\phi_L(\nu, \mu, \nu_1, nu_2)$ holds iff $\nu$ and $\mu$ encode gates and
  $\nu_1, \nu_2$ encode numbers, and $L(g_{\mu})(\nu_1,\nu_2) = g_\nu$. If
  $\dom(L (g_\mu)) = [a] \times [b]$, then the encoding of $[a]$ and $[b]$ are
  initial segments under the lithographically induced order. Moreover, the
  encodings of $[a]$ and $[b]$ preserve the order relation.
\end{itemize}

From now on we use $\mu$ and $\nu$ to stand for $t$-length sequences encoding
gates, and use $\nu_1, \ldots$ for sequences that encode numbers. We use $g_\mu$
and $g_\nu$ for the gates encoded by these sequence, while simply identifying
the sequence $\nu_i$ with the number it encodes.

Using the Immerman-Vardi Theorem, we can define an FP($\leq$) formula
$\rankpara$ such that $\langle [n], \leq\rangle \models \rankpara[g,p,u]$ iff
$\langle [n], \leq\rangle \models \phi_G[g] \land \phi_{\rank}[g]$ and the rank
gate $g$ (as per the interpretation) computes the rank over characteristic $p$
and has threshold $u$.

We can define FP($\leq$) formulas $\max_A$ and $\max_B$ such that $\langle [n],
\leq \rangle \models \max_A[g, \nu_1]$ iff $\nu_1$ encodes $a$, where
$\dom(L(g)) = [a]\times [b]$. Similarly, $\langle [n], \leq \rangle \models
\max_B[g, \nu_1]$ iff $\nu_1$ encodes $b$ where $\dom(L(g)) = [a] \times [b]$.

Again using Lemma \ref{} and the Immerman-Vardi theorem, we can construct a
formula $\supp$ such $\langle [n], \leq \rangle \models \supp[g,u]$ iff $\langle
[n], \leq \rangle \models \phi_G[g]$ and $u$ is in $sp(g)$. This formula can be
used as in \cite{} to inductively define $\supp_i(g,u)$ for each $i \in [n]$
which holds iff $u$ is the $i$th element of the support of $g$.

Define the $\agree$ and $\theta_s$ formulas for all $s \in \SB \uplus \tau
\uplus \{0,1\}$ as in \cite{}.

Now we define the formula
\begin{align*}
  \theta_{\rank}:= (\mu, \bar{x}) := \bigwedge_{1 \leq i < j \leq k} x_i
  \neq x_j \wedge \forall \bar{y} ( [ \rank (x \leq \phi_{mr}, y \leq
  \phi_{mc}, \pi \leq r). \theta^{'} ] ),
\end{align*}
\begin{align*}
  \theta^{'}(a,b):= \exists \nu (W(\nu, \mu) \wedge \agree (\mu,\nu, \bar{x}, \bar{y}) \wedge \phi_L (\mu, \nu, a, b) \wedge V(\nu, y))
\end{align*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{October 27th: Counting Gates Simulate Symmetric Gates}

In this chapter we prove that symmetric circuits with majority gates are at
least as powerful as symmetric circuits over any other Boolean basis consisting
of symmetric functions.

Recall the following that $\mathbb{B} = \{ \neg , \wedge , \lor \}$ and
$\mathbb{B}_\maj = \{ \maj \} \cup \mathbb{B}$.

Let $F: \{0,1\}^* \rightarrow \{0,1\}$ be a symmetric Boolean function. Since
$F$ is symmetric we note that for a fixed size input the output of $F$ is
entirely determined by the number of 1's in its input. Then let
$c_{F}:\mathbb{N} \rightarrow 2^{\mathbb{N}}$ define a function where $c_{F}(n)$
is the set of all $m \leq n$ such that for all $\vec{x} \in \{ 0,1 \}^n$ with
$m$ 1's we have $F (\vec{x}) = 1$. Clearly a symmetric Boolean function $F$ is
entirely determined by $c_{F}$.

\begin{prop}
  \label{prop:fuctions-maj}
  There is a polynomial $p(k)$ such that for any symmetric function $F$ and a
  given $k \in \mathbb{N}$ there is a circuit $C_k$ on $k$ inputs over the basis
  $\mathbb{B}_\maj$ which is symmetric, constant depth and with width bounded by
  $p(k)$.
\end{prop}

\begin{proof}
  We define the circuit $C_k$ for inputs $\vec{x} = ( x_1, \ldots, x_k )$.

  For $a \in \mathbb{N}$ we define a get $\countgate_a$ by
  \begin{align*}
    &\countgate_a = \maj (x_1, \ldots, x_k, \underbrace {0, \ldots, 0}_{2a -
      k}) \land \neg \maj (x_1, \ldots , x_k, \underbrace{0, \ldots,  0}_{2a - k + 2})\text{ if $a \geq \frac{k}{2}$,} \\
    &\countgate_a = \maj (x_1, \ldots, x_k, \underbrace {1, \ldots, 1}_{x -
      2a}) \land \neg \maj (x_1, \ldots , x_k, \underbrace{1, \ldots,
      1}_{k - 2a -2}) \text{ if $a < \frac{k}{2}$. }
  \end{align*}

  Then let $g = \bigvee_{a \in c_{F_i}(k)}\countgate_a$ and let $C_{k}$ be the
  circuit with input gates labeled by $\vec{x}$ and output gate $g$.

  t is easy to see that $C_k$ is constant depth and it's width is a polynomial
  in $k$. We have that in each layer of $C_{g'}$ each gate is connected to all
  gates in the previous layer, and as such the circuit is symmetric.
\end{proof}

The above proposition has a straight forward application to circuit
characterizations.

\begin{prop}
  Let $F = \{F_i : i \in I \}$ be a family of symmetric Boolean functions where
  $F_i: \{0,1\}^* \rightarrow \{ 0,1 \}$.

  Let $(C_n)_{n \in \mathbb{N}}$ be family of symmetric circuits over the
  Boolean basis $\mathbb{B} \cup F$, where $C_n$ is a circuit on structures of
  size $n$, and the size of each circuit in the family is bounded by some
  function $f(n)$. Then there exists a polynomial $q(n)$ and a family of
  symmetric circuits $(C_n')_{n \in \mathbb{N}}$ over $\mathbb{B}_\maj$, where
  $C_n'$ is a circuit on structures of size $n$ and $\vert C_n' \vert \leq
  q(f(n))$.
\end{prop}

\begin{proof}
  From $C_n$ we construct $C_n'$ in the obvious way. For each gate $g \in C_n$
  of type $F_i$ we have a symmetric circuit $C_g$ from Proposition
  \ref{prop:function-maj} that computes the same function as $g$. Then let
  $C_n'$ be $C_n$ but with each gate $g$ replaced by $C_g$. It is easy to see
  that $C_n'$ is symmetric. We also have that each gate $g$ must have at most
  $f(n)$ inputs, and the size of $C_g$ is bounded by $p(f(n))$. Thus the size of
  $C_n'$ is bounded by $f(n)p(f(n))$.
\end{proof}

\chapter{October 29th: Symmetric Circuits and CPT}

We already have that that the set of queries decidable by symmetric
circuits (respectively with counting) is exactly the set of queries
expressible in Fixed-Point Logic. We know that the CFI query is not
expressible in FPC, and so there is no symmetric circuit that can
compute the query.

In our attempts to find a circuit characterisation of CPT, we might try and weaken the requirement of symmetry in our notion of symmetric circuits in order to express the CFI query (and perhaps the whole of CPT). One approach would be to weaken the requirement of having small orbits, to rather only having small orbits with respect to our particular input structure. We formalise this notion below.

\begin{definition}
Let $C$ be a circuit on structures of size $n$. Let $g$ be a gate in $C$ and let $X$ be a set of input strings closed under the action of the symmetric group. The $inv_X = \{ \sigma \in \sym_n : \forall x \in X g \circ H (x) = g \circ H (\sigma x)$.
\end{definition}
\begin{definition}
  Let $(C_n)_{n \in \mathbb{N}}$ be a family of circuits. For any
  finite structure $\mathcal{A}$ let $X_{\mathcal{A}}$ be the set of
  all string encodings of $\mathcal{A}$. We say a circuit family has
  small isomorphism orbits if there is a polynomial $p(n)$ such that
  for any sufficiently large $n$, finite structure $\mathcal{A}$ of
  cardinality $n$ and any $g \in C_n$ we have
  $\vert S_n : \inv_{X_{\mathcal{A}}}(g) \vert \leq p(n)$.
\end{definition}

\begin{thm}
  \label{thm:simple_group}
  Let $n \in \mathbb{N}$, $n \geq 5$. Let $r \in \mathbb{N}$ such that
  $r \leq n/2$. Suppose that $G$ is a subgroup of $\sym(n)$, then
  there is a constant $k \in mathbb{N}$ such that for all $n \geq k$
  if $\vert \sym(n):G \vert \leq {{n}\choose {r}}$ then there exists
  $X \subseteq [n]$ with $\vert X \vert \leq r$ and such that
  $\alt([n] \setminus X) \leq G$.
\end{thm}

The following result shows that even this weakened definition fails to
capture CPT.
\begin{thm}
  There is no family of circuits with small isomorphism orbits that
  expresses the CFI query.
\end{thm}
\begin{proof}
  Let $(G_n)_{n \in \mathbb{N}}$ be a family of ordered graphs such that each $G_n$ has
  odd and even CFI graphs $\mathfrak{G}$ and $\tilde{\mathfrak{G}}$ respectively, each of
  cardinality $n$. Furthermore, suppose the CFI query for $(G_n)$ is not expressible in
  FPC (the existence of such a family is guaranteed by
  \cite{}). Suppose there exists a family of circuits $(C_n)_{n \in \mathbb{N}}$ with
  small isomorphism orbits that decides the CFI query for $(G_n)$.
  Then we have that $C_n(\mathfrak{G}) = 1$ and
  $C_n(\tilde{\mathfrak{G}}) = 0$, and for any $g \in C_n$

  \begin{align*}
    \vert S_n : \inv_{X_{\mathcal{G}}}(g) \vert &\leq p(n),\\
    \vert S_n : \inv_{X_{\tilde{\mathcal{G}}}}(g) \vert &\leq p(n)
  \end{align*}.
  Let $k$ be such that $p(n) \leq n^k$ for all sufficiently large $n$. Then we have that $p(n) \leq n^k \leq {{n}\choose{k+1}}$ for all sufficiently large $n$, and (again, taking $n$ large enough) we have that $k \leq n/2$. Taking $n$ larger than the constant in Theorem \ref{thm:simple_group} it follows that there exists an $X_1, X_2 \subseteq [n]$ such that $\vert X_1 \vert, \vert X_2 \vert \leq k$ and $\alt ([n] \setminus X_1) \subseteq  \inv_{X_{\mathfrak{G}}}(g)$, $\alt ([n] \setminus X_2) \subseteq  \inv_{X_{\tilde{\mathfrak{G}}}}(g)$. It follows that
  \begin{align*}
    \alt ([n] \setminus (X_1 \cup X_2)) &\subseteq \alt ([n] \setminus X_1) \cap \alt ([n] \setminus X_2)\\
                                        &\subseteq \inv_{X_{\mathfrak{G}}}(g) \cap \inv_{X_{\tilde{\mathfrak{G}}}}(g) \\
                                        &\subseteq \inv_{X_{\mathfrak{G} \cup \tilde{\mathfrak{G}}}}(g) =  \inv_{CFI(G)}(g),
  \end{align*}
  where $CFI(G)$ is set of all encodings of all CFI graphs of $G_n$.

  We then have that
  \begin{align*}
    \vert S_n : \inv_{CFI(G)}(g) \vert \leq \vert S_n : \alt ([n] \setminus (X_1 \cup X_2)) \leq  \frac{n!}{(n-2k)!/2} \leq n^{2k+1},
  \end{align*}
  with the last inequality following for large enough $n$. We thus
  have from Theorem \ref{} that there is a symmetric circuit $D_n$
  that decides the CFI problem for $G_n$, and hence a family $(D_n)$
  that decides the CFI problem for the family of graphs $(G_n)$. From
  the theorem of Dawar et al. \cite{}, it follows that there is as
  formula of FPC that decides the CFI query for $(G_n)$ contradicting
  our assumption.
\end{proof}
\end{document}

### 2017-04-10 paper.tex
Things have been updated
Last Changes

@@
 \newcommand{\rankparam}{\text{PARAM}}
+\newcommand{\consp}{\text{sp}}
+\newcommand{\row}{\text{row}}
+\newcommand{\column}{\text{col}}
+\newcommand{\rowsp}{\text{r}}
+\newcommand{\colsp}{\text{c}}
+\newcommand{\EV}{\text{EV}}
+\newcommand{\spstab}[1]{\stab (\consp (#1))}
 
@@
 latest version of the support and circuit capturing result.
-
-\section{}
 
@@
   Let $g$ be a matrix-symmetric gate in $C_n$ with children $H$. Let $\alpha \in
-  U^{\underbar{\sp(g)}}$, and suppose $\gamma_1, \gamma_2: U \rightarrow [n]$
+  U^{\underbar{\consp(g)}}$, and suppose $\gamma_1, \gamma_2: U \rightarrow [n]$
   with $\gamma^{-1}_1 \sim \alpha$ and $\alpha \sim \gamma^{-1}_2$. Let $A
@@
 
-\begin{lem}
-  Let $g$ be a matrix symmetric gate in $C_n$ with children $H$. Let $\alpha \in
-  U^{\underbar{\sp(g)}}$ and $\gamma: U \rightrrow [n]$ such that
-  $gamma^{-1}\sim \alpha$. Let $A \times B = \dom (L(g))$ and define
-  $L^{EV}_\alpha: A \times B \rightarrow \{0,1\}$ by
-  \begin{align*}
-    L^{EV}_\alpha (a,b):=
-    \begin{cases*}
-      1 & if $A_h \cap \EV_h \neq \emptyset$ 0 & otherwise
-    \end{cases*},
-  \end{align*}
-  where for $h \in W_g, A_h:= \{\beta \in U^{\underline{\sp(h)}} \vert \alpha
-  \sim \beta\}$. Then $L^0_\gamma = L^{EV}_\alpha$ and $\alpha \in \EV(g)$ iff
-  $\rk^u_p(L^0_\gamma)$
-\end{lem}
-\begin{proof}
-
-\end{proof}
-
-\begin{lem}
-  Let $g$ be a matrix-symmetric gate in $C_n$ with children $W_g$. $Let \alpha
-  \in U^{\underbar{\sp(g)}}$ and let $\gamma: U \rightarrow [n]$ such that
-  $\gamma^{-1} \sim \alpha$. Let $A \times B = \dom (L(g))$, and let
-  $f:\{0,1\}^{A \times B} \rightarrow \{0,1\}$ be the matrix-symmetric function
-  associated with $g$. Define $L^{EV}_\alpha: A \times B \rightarrow \{0,1\}$ by
-  \begin{align*}
-    L^{EV}_\alpha (a,b):=
-    \begin{cases*}
-      1 & if $A_h \cap \EV_h \neq \emptyset$ 0 & otherwise
-    \end{cases*},
-  \end{align*}
-  where for $h \in W_g, A_h:= \{\beta \in U^{\underline{\sp(h)}} \vert \alpha
-  \sim \beta\}$. Then $\alpha \in \EV_g$ iff $f(L^\EV_\alpha)$.
-\end{lem}
-\begin{proof}
-  First note that if $\alpha \in U^{\underbar{\sp{g}}}$ then $\alpha \in \EV_g$
-  iff we have that $C_n[\gamma \mathcal{A}](g)= f (L^0_\gamma) = 1$. Notice that
-  from Lemma \ref{} that this holds for any particular $\gamma$ iff it holds for
-  all such $\gamma$.
-
-  We now show that $L^\EV_\alpha = L^0_\gamma$, and so complete the proof.
-
-  Suppose for $(a,b) \in A \times B$ we have that $L^\EV_\alpha(a,b) = 1$. Let
-  $h:= L(g)(a,b)$. It follows that $A_h \cap \EV_h \neq \emptyset$, i.e there
-  exits $\beta \in \sp(h)$ such that $\beta \sim \alpha$ and there exists
-  $\gamma_h \in \Gamma(h)$ such that $\gamma^{-1}_h \sim \beta$. It follows from
-  transitivity and Lemma \ref{} that $\gamma_h \sim \alpha$ and so
-  $L^0_\alpha(a,b) = C_n[\gamma \mathcal{A}](h) = C_n[\gamma_h \mathcal{A}](h) =
-  1$.
-
-  Now suppose that $L^0_\gamma (a,b) = 1$
-\end{proof}
+% \begin{lem}
+%   Let $g$ be a matrix symmetric gate in $C_n$ with children $H$. Let $\alpha \in
+%   U^{\underbar{\consp(g)}}$ and $\gamma: U \rightarrow [n]$ such that
+%   $gamma^{-1}\sim \alpha$. Let $A \times B = \dom (L(g))$ and define
+%   $L^{EV}_\alpha: A \times B \rightarrow \{0,1\}$ by
+  % \begin{align*}
+  %   L^{EV}_\alpha (a,b):=
+    % \begin{cases*}
+    %   1 & if $A_h \cap \EV_h \neq \emptyset$ 0 & otherwise
+   % \end{cases*},
+%  \end{align*}
+%  where for $h \in W_g, A_h:= \{\beta \in U^{\underline{\sp(h)}} \vert \alpha
+%  \sim \beta\}$. Then $L^0_\gamma = L^{EV}_\alpha$ and $\alpha \in \EV(g)$ iff
+%  $\rk^u_p(L^0_\gamma)$
+%\end{lem}
+%\begin{proof}
+%  
+%\end{proof}
+
+% \begin{lem}
+%   Let $g$ be a matrix-symmetric gate in $C_n$ with children $W_g$. $Let \alpha
+%   \in U^{\underbar{\consp(g)}}$ and let $\gamma: U \rightarrow [n]$ such that
+%   $\gamma^{-1} \sim \alpha$. Let $A \times B = \dom (L(g))$, and let
+%   $f:\{0,1\}^{A \times B} \rightarrow \{0,1\}$ be the matrix-symmetric function
+%   associated with $g$. Define $L^{EV}_\alpha: A \times B \rightarrow \{0,1\}$ by
+  % \begin{align*}
+  %   L^{EV}_\alpha (a,b):=
+%     \begin{cases*}
+%       1 & if $A_h \cap \EV_h \neq \emptyset$ 0 & otherwise
+%     \end{cases*},
+%   \end{align*}
+%   where for $h \in W_g, A_h:= \{\beta \in U^{\underline{\sp(h)}} \vert \alpha
+%   \sim \beta\}$. Then $\alpha \in \EV_g$ iff $f(L^\EV_\alpha)$.
+% \end{lem}
+% \begin{proof}
+%   First note that if $\alpha \in U^{\underbar{\sp{g}}}$ then $\alpha \in \EV_g$
+%   iff we have that $C_n[\gamma \mathcal{A}](g)= f (L^0_\gamma) = 1$. Notice that
+%   from Lemma \ref{} that this holds for any particular $\gamma$ iff it holds for
+%   all such $\gamma$.
+
+%   We now show that $L^\EV_\alpha = L^0_\gamma$, and so complete the proof.
+
+%   Suppose for $(a,b) \in A \times B$ we have that $L^\EV_\alpha(a,b) = 1$. Let
+%   $h:= L(g)(a,b)$. It follows that $A_h \cap \EV_h \neq \emptyset$, i.e there
+%   exits $\beta \in \sp(h)$ such that $\beta \sim \alpha$ and there exists
+%   $\gamma_h \in \Gamma(h)$ such that $\gamma^{-1}_h \sim \beta$. It follows from
+%   transitivity and Lemma \ref{} that $\gamma_h \sim \alpha$ and so
+%   $L^0_\alpha(a,b) = C_n[\gamma \mathcal{A}](h) = C_n[\gamma_h \mathcal{A}](h) =
+%   1$.
+
+%   Now suppose that $L^0_\gamma (a,b) = 1$
+% \end{proof}
 
@@
 Using the Immerman-Vardi Theorem, we can define an FP($\leq$) formula
-$\rankpara$ such that $\langle [n], \leq\rangle \models \rankpara[g,p,u]$ iff
+$\rankparam$ such that $\langle [n], \leq\rangle \models \rankparam,a[g,p,u]$ iff
 $\langle [n], \leq\rangle \models \phi_G[g] \land \phi_{\rank}[g]$ and the rank
@@
 \end{align*}
+
+\pagebreak
+
+\section{Computing the Rank of a Labelling in FPR}
+
+In this section I discuss how to determine the rank a matrix labelling at some
+gate $g$. This is a rough copy written for the purpose of discussion. In this
+section we fix some circuit $C_n$ and some rank gate $g$ in $C_n$, with matrix
+labelling $\omega$.
+
+\begin{definition}
+  Let $h \in H$, then $S \subseteq [n]$ is a row support iff $\forall \sigma \in
+  \stab (\consp(g))$ whenever $\forall i \in S, \sigma i = i$ then $\row (\sigma
+  h) = \row (h)$.
+  \\~\\
+  Similarly we can define the notion of a column support.
+  \\~\\
+  Let $r_h$ be the canonical row support and $c_h$ be the canonical column
+  support.
+\end{definition}
+
+\begin{remark}
+  Let $\sigma \in \spstab{g}$, then we know that $\sigma$ induces an action on
+  the rows and columns such that the result is a row column permutation. We may
+  associate with $\sigma$ a pair $(\sigma_r, \sigma_c) \in \sym_A \times
+  \sym_B$, where $\sigma_r (i) = \row (\sigma h)$, for some $h \in H$, $\row (h
+  = i)$ and similarly $\sigma_c (j) = \column (\sigma h)$, for some $h \in H$,
+  $\column (h) = j$. The definition of a permutation on a circuit, and the
+  stability group for $g$ gives us that such permutations must exist.
+\end{remark}
+
+The following lemma asserts a few basic facts about the (canonical) row and
+column supports.
+
+\begin{lem}
+  Let $h \in H$, then $r_h \subset \consp(h)$, $c_h \subset \consp(h)$ and $c_r
+  \cup r_h = \consp(h)$.
+\end{lem}
+
+We introduce here some useful notation.
+
+\begin{definition}
+  Let $S^r_h = \{ \sigma \in \stab (\consp(g)) : \sigma \vec{r_h} = \vec{r_h}
+  \}$ and $G^r_h = \{ \sigma \in \stab(\consp(g)) : \row(\sigma h) = \row(h)\}$.
+  Let $S^c_h = \{ \sigma \in \stab (\consp(g)) : \sigma \vec{c_h} = \vec{c_h}
+  \}$ and $G^c_h = \{ \sigma \in \stab(\consp(g)) : \column(\sigma h) =
+  \column(h)\}$.
+\end{definition}
+
+Clearly, by definition of a row and column support, $S^r_h \subseteq G^r_h$ and
+$S^c_h \subseteq G^c_h$.
+\\~\\
+In this section some simplifying assumptions are made.
+
+\begin{remark}
+  In this section I assume for the moment that:
+  \begin{itemize}
+  \item $\consp (g) = \{\}$,
+  \item $S^r_h = G^r_h$ and $S^c_h = G^c_h$, and
+  \item $\forall h,h' \in H$ we have $\vert r_h \vert = \vert r_{h'} \vert$ and
+    $\vert c_h \vert = \vert c_{h'} \vert$.
+  \end{itemize}
+\end{remark}
+
+Let $k_r = \vert r_h \vert$ and $k_c = \vert c_h \vert$. In the following we let
+$\vec{x} \in U^{k_r}$ and $\vec{y} \in U^{k_c}$. These vectors are thought of as
+generic assignments to the row and column supports of some element $h \in H$. Of
+course, the structure of the row and column supports of a particular $h \in H$
+does matter, and two assignments may be valid or invalid depending on that
+stricture. We now consider ways of `choosing' a particular element of $H$ that
+has the `correct' structure for such a pair.
+\\~\\
+Then let for $h \in H$, let $\vec{x}_h: r_h \rightarrow U$ be defined by
+$\vec{x}_h(i) = \vec{x}(\vec{r_h}^{-1}(i))$. Similarly, let $\vec{y}_h: c_h
+\rightarrow U$ be defined by $\vec{y}_h(i) = \vec{y}(\vec{c_h}^{-1}(i))$. We can
+think of the functions $(h, \vec{x}) \mapsto \vec{x}_h$ and $(h, \vec{y})
+\mapsto \vec{y}_h$ as taking these respective tuples and assigning them to the
+row and column supports of $h$.
+
+\begin{lem}
+  For each pair $(\vec{x}, \vec{y})$ there is an $h \in H$ such that $\vec{x}_h
+  \sim \vec{y}_h$.
+\end{lem}
+
+Let us then define a function $\mu : U^{k_r} \times U^{k_c} \rightarrow H$,
+where $\mu(\vec{x}, \vec{y})$ is the minimal $h \in H$ (in the order of the
+structure) such that $\vec{x}_h \sim \vec{y}_h$. The above lemma tells us that
+this function is indeed well-defined (in particular, it's total).
+
+We note that if $\vec{x}_h \sim \vec{y}_h$ it follows that we can define
+$(\vec{x}, \vec{y})$ an assignment to the support of $h$.
+
+We then define the matrix $M(\vec{x}, \vec{y}) := (\vec{x}, \vec{y}) \in
+\EV_{\mu(\vec{x}, \vec{y})}$.
+
+We now define what it means for two matrices to be row-column equivalent.
+
+\begin{definition}
+  Let $M_1$ and $M_2$ be matrices over some field, with row and column indexes
+  given by $(A_1, B_1)$ and $(A_2, B_2)$, respectively. We say that $M_1$ and
+  $M_2$ are row-column equivalent iff there exists bijections $\alpha: A_1
+  \rightarrow A_2$ and $\beta: B_1 \rightarrow B_2$ such that for all $(a,b) \in
+  A_1 \times B_1$ we have that $M_1(a,b) = M_2 (\alpha (a), \beta (b))$. If
+  $M_1$ and $M_2$ are row-column equivalent we say that $M_1 \sim M_2$.
+\end{definition}
+
+Suppose $\alpha_g \in U^{\sp(g)}$ an injection and fix a bijection $\gamma: U
+\rightarrow [n]$ such that $\alpha_g \sim \gamma^{-1}$. We can then define
+$L^\gamma: A \times B \rightarrow \{0,1\}$ by $L^\gamma(a,b) = C[\gamma
+\mathcal{A}](\omega (a,b))$.
+\\~\\
+We note that, in fact, it is the choice of the assignment to the support of $g$,
+i.e. $\alpha_g$, that really matters in the sense that for any two global
+assignments that agree on the support of $g$ will produce row-column equivalent
+matrices. The following lemma formalises this observation.
+
+\begin{lem}
+  Let $g$ be a matrix-symmetric gate in $C_n$ with children $H$ and matrix
+  labelling $L(g)$. Let $\alpha_g \in U^{\consp(g)}$, and suppose $\gamma_1,
+  \gamma_2: U \rightarrow [n]$ with $\gamma^{-1}_1 \sim \alpha$ and $\alpha \sim
+  \gamma^{-1}_2$. Let $A \times B = \dom (L(g))$.
+
+  For an input structure $\mathcal{A}$, let $L^\gamma: A \times B \rightarrow
+  \{0,1\}$, where $L^{\gamma_2} (a,b):= C[\gamma \mathcal{A}] (L(g)(a,b))$.
+
+  Then $L^{\gamma_1} \sim L^{\gamma_2}$.
+\end{lem}
+\begin{proof}
+  We have that there exists a unique $\pi \in \sym_n$ such that $\pi \gamma_1 =
+  \gamma_2$. Moreover, since $\gamma^{-1}_1$ and $\gamma^{-1}_2$ are both
+  consistent with $\alpha$, it follows that $\pi$ must fix $\sp(g)$. Thus $L(g)
+  \sim \pi L(g)$, and so there exists $(\sigma, \lambda)$ such that $\pi L(g) =
+  L(g) \cdot (\sigma, \lambda)$.
+
+  We then have that,
+  \begin{align*}
+    L^{\gamma_1} (a,b) &= C_n[\gamma_1 \mathcal{A}](L(g)(a,b))\\
+                       & = C_n[\pi \gamma_1 \mathcal{A}][\pi L(g)(a,b)] \\
+                       & = C_n[\gamma_2 \mathcal{A}][L(g)((\sigma, \lambda)(a,b))]\\
+                       & = L^{\gamma_2} ((\sigma, \lambda) (a,b)),
+  \end{align*}
+  and it follows that $L^{\gamma_1} \sim L^{\gamma_2}$.
+\end{proof}
+
+\begin{lem}
+  Let $h_1, h_2 \in H$ and $\sigma_1, \sigma_2 \in \spstab{g}$. Suppose
+  $\sigma_1 \vec{r_{h_1}} = \sigma_2 \vec{r_{h_2}}$. Then $\row (\sigma_1 h_1) =
+  \row (\sigma_2 h_2)$.
+\end{lem}
+\begin{proof}
+  There exists $\sigma \in \spstab{g}$ such that $\sigma \vec{r_{h_1}} =
+  \vec{r_{h_2}}$, and so $\sigma_1 \vec{r_{h_1}} = \sigma_2 \sigma
+  \vec{r_{h_1}}$, and thus $(\sigma_2 \sigma)^{-1} \sigma_1 \vec{r_{h_1}} =
+  \vec{r_{h_1}}$. It follows that $(\sigma_2 \sigma)^{-1} \sigma_1 \in S^r_{h_1}
+  \subseteq G^r_{h_1}$, and so $\row ((\sigma_2 \sigma)^{-1} \sigma_1 h_1) =
+  \row (h_1)$. Thus $((\sigma_2)_r \sigma_r)^{-1} (\sigma_1)_r \row (h_1) = \row
+  (h_1)$.
+
+  It follows that $\row (\sigma_1 h ) = (\sigma_1)_r \row (h_1) = (\sigma_2)_r
+  \sigma_r\row (h_1) = (\sigma_2)_r \row (\sigma h_1) = (\sigma_2)_r \row (h_2)
+  = \row (\sigma_2 h_2)$.
+
+  % Uses assumption (-check-)
+
+\end{proof}
+
+\begin{claim}
+  For $h \in H$ and $\sigma \in \stab(\consp (g))$, we have that
+  $\vec{r}_{\sigma h_1} = \sigma \vec{r}_{h_1}$.
+\end{claim}
+\begin{proof}
+  Proof needed, proof strategy in book
+\end{proof}
+
+\begin{lem}
+  Let $h_1, h_2 \in H$ and $\sigma_1, \sigma_2 \in \stab (\consp(g))$ such that
+  $\sigma_1 \vec{r}_{h_1} = \sigma_2 \vec{r}_{h_2}$ and there exists $\sigma \in
+  \stab(\consp (g))$ such that $\row (\sigma h_1) = \row (\sigma h_2)$, then
+  $\row (\sigma_1 h_1) = \row (\sigma_2 h_2)$.
+\end{lem}
+\begin{proof}
+  proof in book
+  % So $\row (\sigma h_1) = \row (h_2)$, and so $\sigma \vec{r} = \vec{r}_{\sigma h_1} =
+  % \vec{r}_{h_2}$.
+\end{proof}
+
+Let $\Pi^\gamma_{(\vec{x}), \vec{y}}(\mu(\vec{x}, \vec{y}))$ be the action on
+$\mu (\vec{x}, \vec{y})$ defined the action on the support given by
+$\Pi^\gamma_{(\vec{x}, \vec{y})}(\vec{\sp(h)}) = \gamma ((\vec{x}, \vec{y})$.
+
+\begin{claim}
+  Let $\vec{y}, \vec{y}' \in U^{k_r}$ and $\vec{x}, \vec{x} \in U^{k_c }$ then
+  \begin{align*}
+    \row (\Pi^\gamma_{(\vec{x}, \vec{y})}(\mu(\vec{x}, \vec{y}))) = \row (\Pi^\gamma_{(\vec{x}, \vec{y}')}(\mu(\vec{x}, \vec{y}'),
+  \end{align*}
+  and
+  \begin{align*}
+    \column(\Pi^\gamma_{(\vec{x}, \vec{y})}(\mu(\vec{x}, \vec{y}))) = \column
+    (\Pi^\gamma_{(\vec{x}', \vec{y})}(\mu(\vec{x}', \vec{y}).
+  \end{align*}
+\end{claim}
+\begin{proof}
+  proof in book
+\end{proof}
+
+We let $\alpha: U^{k_r} \rightarrow A$, $\beta: U^{k_c} \rightarrow B$ be
+defined by $\alpha (\vec{x}) = \row (\Pi^\gamma_{(\vec{x}, \vec{y})} (\mu
+(\vec{x}, \vec{y})$ for some $\vec{y} \in U^{k_c}$. Similarly we can define
+$\beta (\vec{y})$.
+
+The above claim tells us that this definition is well defined.
+
+\begin{claim} 
+  Both $\alpha$ and $\beta$ are bijections.
+\end{claim}
+\begin{proof}
+ proof in book 
+\end{proof}
+
+\begin{thm}
+  $L$ is row-column equivalent to $M$.
+\end{thm}
+\begin{proof}[proof of above theorem]
+  \begin{align*}
+    M(\vec{x}, \vec{y}) &\iff (\vec{x}, \vec{y}) \in \EV_{\mu({\vec{x}, \vec{y}})} \\  
+                        &\iff C_n [\gamma \mathcal{A}] (\Pi^\gamma_{(\vec{x}, \vec{y})} (\mu (\vec{x}, \vec{y}))) \\
+                        &\iff C_n [\gamma \mathcal{A}] (\omega (\alpha (\vec{x}), \beta (\vec{y}))) \\
+                        &\iff L^\gamma (\alpha (\vec{x}), \beta (\vec{y}))
+  \end{align*}
+  The above calculation, combined with the fact that $\alpha$ and $\beta$ are
+  bijections, proves the result.
+\end{proof}
 
@@
 \end{proof}
+
 \end{document}

### 2017-07-18 paper.tex
asdfasdf

--- 2016-12-14 paper.tex
@@
 \usepackage{amsthm} % better theorem environments
+\usepackage{xspace}
 
@@
 
-\newtheorem{thm}{Theorem} \newtheorem{claim}{Claim}
-\newtheorem{remark}{Remark} \newtheorem{definition}{Definition}
+\newtheorem{thm}{Theorem} \newtheorem{claim}[thm]{Claim}
+\newtheorem{remark}[thm]{Remark} \newtheorem{definition}[thm]{Definition}
 \newtheorem{lem}[thm]{Lemma} \newtheorem{prop}[thm]{Proposition}
@@
 \DeclareMathOperator{\id}{id}
+
+\newcommand{\reals}{\mathbb{R}}
+\newcommand{\nats}{\mathbb{N}}
+
+\newcommand{\logic}[1]{\text{\upshape #1}\xspace}
+\newcommand{\FPC}{\logic{FPC}}
+\newcommand{\FO}{\logic{FO}}
+\newcommand{\FP}{\logic{FP}}
+\newcommand{\FPR}{\logic{FPrk}}
+\newcommand{\CPTC}{\logic{$\tilde{\text C}$PT(Card)}}
+
+\newcommand{\PT}{\ensuremath{\mathrm{P}}\xspace}
 
@@
 \newcommand{\sym}{\text{\textbf{Sym}}}
+\newcommand{\std}{\text{\textbf{std}}}
 \newcommand{\rank}{\text{\textbf{rk}}}
@@
 \newcommand{\SP}{\text{\textbf{SP}}}
-\newcommand{\maj}{\text{\textbf{Maj}}}
+\newcommand{\SPs}{\text{\textbf{SPs}}}
+\newcommand{\maj}{\text{\textbf{maj}}}
 \newcommand{\dom}{\text{\textbf{Dom}}}
+\newcommand{\img}{\text{\textbf{Img}}}
 \newcommand{\child}{\text{child}}
@@
 \newcommand{\rankparam}{\text{PARAM}}
+\newcommand{\consp}{\text{sp}}
+\newcommand{\consps}{\text{sps}}
+\newcommand{\row}{\text{row}}
+\newcommand{\column}{\text{col}}
+\newcommand{\rowsp}{\text{r}}
+\newcommand{\colsp}{\text{c}}
+\newcommand{\EV}{\text{EV}}
+\newcommand{\type}{\text{type}}
+\newcommand{\types}{\text{types}}
+\newcommand{\spstab}[1]{\stab (\consp (#1))}
 
@@
 
-\nocite{*}
-
-\title{Circuits}
-
-\author{Gregory Wilsenach \\ 
+\title{Symmetric Circuits for Rank Gates}
+
+\author{Anuj Dawar and Gregory Wilsenach \\ 
 Computer Laboratory \\
@@
 
+A finite relational structure, such as a graph, can be represented as a binary
+string in a standard way (for instance, by enumerating its adjacency matrix).
+When we speak of the computational complexity of properties of graphs, we assume
+such an encoding in order to present the structure as input to a machine or
+circuit or other appropriate computational model. The properties of structures
+we are interested in studying are invariant under isomorphisms. This requirement
+translates into an invariance condition on sets of strings---say that a language
+$L \subseteq \{0,1\}^\star$ is a \emph{graph property} if, whenever $x \in L$
+for a string $x$ representing a graph $G$, we have $y\in L$ for any string $y$
+obtained from $x$ by re-ordering the vertices of $G$. The central open question
+in descriptive complexity---whether there is a logical characterisation of the
+polynomial-time decidable properties of finite relational structures--- can then
+be understood as the question of characterizing those languages $L$ that are in
+$\PT$ and are graph properties.
+
+Anderson and Dawar~\cite{AndersonD17} study this question through the lens of circuit
+complexity, by considering \emph{symmetric circuits}. These are circuits that
+necessarily accept graph properties, with this fact explicitly witnessed by
+automorphisms of the circuit. To be precise, we can think of a property of
+(directed) graphs on $n$ vertices as being given by a Boolean function $f:
+\{0,1\}^{n^2} \rightarrow \{0,1\}$ which takes as input the $n^2$ potential
+edges and outputs $1$ if the property is satisfied by the graph given on the
+input. The function $f$ is \emph{graph-symmetric} in the sense that any permutation of
+its inputs induced by a permutation of the $n$ vertices leaves $f$ unchanged
+(note this is not the same thing as requiring that $f$ is invariant under all
+permutations of its inputs). A symmetric circuit is a circuit computing a
+Boolean function of $n^2$ inputs where each permutation of $[n]$ can be extended
+to an automorphism of the circuit. Such a circuit necessarily computes an
+invariant function.
+
+The results of~\cite{AndersonD17} show a tight relationship between the decdability of
+a graph property by means of a polynomial-size family of symmetric circuits and
+its definability in extensions of fixed-point logic. In particular, they show
+that a property is definable in fixed-point logic with counting ($\FPC$) if, and
+only if, it is decidable by a polynomially-uniform family of symmetric circuits
+using Boolean and majority gates (or, equivalently, threshold gates). Without
+the symmetry restriction, polynomial-size families of circuits have the same
+computational power whether we restrict ourselves to Boolean gates only or allow
+richer bases such as threshold gates. One consequence of the results
+in~\cite{AD14} is that, with the requirement of symmetry, these different bases
+do yield different expressive power, suggesting some lack of robustness to the
+model. One of the results in the present paper shows that the model with
+majority circuits is robust in the sense that it is able to simulate, by means
+of symmetric circuits, any symmetric circuit composed of gates computing Boolean
+functions that are themselves symmetric (in the sense that they are invariant
+under \emph{all} permutations of their inputs. Thus, any property decidable by a
+polynomially-uniform family of such circuits is definable in $\FPC$.
+
+This motivates the study of symmetric circuit families that involve gates which
+themselves may compute non-symmetric functions. In particular, motivated by the
+study of rank logic~\cite{DGHL09,GP15}, we consider gates that are
+\emph{matrix-symmetric}. These are gates computing a Boolean function $f:
+\{0,1\}^{A \times B} \rightarrow \{0,1\}$ which is invariant under arbitrary
+permutations of $A$ and $B$. A typical example is the function computing the
+rank of an $A \times B$ $0$-$1$ matrix. We show that the support theorem of
+Anderson and Dawar can be shown to hold, even in the presence of
+matrix-symmetric gates. This allows us to show that definability in the logic
+fixed-point with rank ($\FPR$) is the same as decidability by
+polynomially-uniform families of symmetric circuits with rank gates.
+
+% Another extension of $\FPC$ that has received much attention in the descriptive
+% complexity literature is the class $\CPTC$ of \emph{choiceless polynomial time
+%   with counting}. The work of~\cite{AD14} leaves open the question of obtaining
+% a circuit characterization of this class and it was suggested there that this
+% would require a relaxation of the notion of symmetry used in defining symmetric
+% circuits. In particular, while $\CPTC$ is based on a machine model designed to
+% preserve symmetry by forbidding choices, the polynomial time and space
+% restrictions apply int he context of the symmetries fo a \emph{single input
+%   structure}. In this paper, we consider a relaxation of the notion of symmetric
+% circuit intended to capture exactly this intuition. However, we are able to show
+% that this does not yield a characterization of $\CPTC$. In particular, we show
+% that no family in this class of relaxed symmetric circuits can distinguish odd
+% from even Cai-F\"urer-Immerman graphs, something we know is do-able in
+% $\CPTC$~\cite{DRR08}.
+
 \chapter{Background}
+In this section we present basic background on logics, first-order structures,
+and symmetric circuits.
+
+\section{Logic and Structures}
+A \emph{relational vocabulary} (usually denoted by $\tau$) is a finite sequence
+of relation symbols $R_1, \ldots, R_k$, such that for all $i \in [k]$, $R_i$ has
+arity of $r_i \in \nats$.
+
+A $\tau$-structure $\mathcal{A}$ is a tuple $\langle U, R^{\mathcal{A}}_1 ,
+\ldots , R^{\mathcal{A}}_k \rangle$, where $U$ is a set and called the
+\emph{universe} of $\mathcal{A}$ and for all $i \in [k]$ the relations
+$R^{\mathcal{A}}_i \subseteq U^{r_i}$. The elements of $U$ are called the
+elements of $\mathcal{A}$. A \emph{multi-sorted} structure is one whose universe
+is a disjoint union, where each set in the union is called a \emph{sort}. The
+size of a structure is the cardinality of its universe.
+
+All structures in this paper are finite.
+
+\section{First Order, Fixed-Point, Counting}
+
+Let $\FO(\tau)$ denote \emph{first order logic} with respect to the vocabulary
+$\tau$. \emph{Fixed-Point Logic} is the extension of $\FO(\tau)$ with an
+inflationary fixed-point operator (see \cite{} for details). For logic
+$\mathcal{L}$, a formula $\phi \in \mathcal{L}(\tau)$, $x$ a $k$-length tuple of
+variables, $\mathcal{A}$ a (finite) structure, and $a \in U^k$, we have that
+$\phi (x)$ denotes that the variables in $x$ are free in $\phi$ and we write
+$\mathcal{A} \models_{\mathcal{L}} \phi[a]$ iff the the formula $\phi$ is true
+in $\mathcal{A}$ with respect to $\mathcal{L}$ with the variables $x$ assigned
+to $a$. The context usually makes the logic obvious, and in that case we usually
+drop the subscript.
+
+We also recall the definition of \emph{fixed-point logic with counting} $\FPC$,
+an extension $\FP$ with counting quantifiers. For a structure $\mathcal{A}$,
+Formulas of this logic are evaluated over a structure $\mathcal{A}$ by extending
+that structure to $\mathcal{A}^\leq$, a two sorted extension of $\mathcal{A}$ by
+an ordered number sort $\{1, \ldots, \vert U\vert \}$. Variables are taken to be
+either point variables, ranging over $U$ or number variables ranging over
+$[\vert U \vert]$. The counting quantifiers are of the form $\#_x$, where $x$ is
+either a point or number variable and for $\phi(x) \in \FPC(\tau)$, $\#_x
+\phi(x)$ is a term denoting the element of the number sort corresponding to
+$\vert \{a \in \mathcal{A} | \mathcal{A} \models \phi[a]\}\vert$. Note
+additionally that $k$-tuples of number variables can be used to encode numbers
+in $\FPC$ of size up to $\vert U\vert^k$. For more details on $\FPC$ please see
+\cite{}.
+
+\section{Rank Logic}
+This still needs to be filled in
+
+\section{Symmetric Circuits}
+This still needs to be filled in
 
 \chapter{Symmetric Circuits}
-
-\chapter{Extending Symmetric Circuits}
-
-\chapter{Matrix-Symmetric Circuits}
-
-The symmetric circuits of Anderson and Dawar \cite{} have been shown to express
-$FPC$.
-
-In this section we develop a notion of a matrix-symmetric circuit, an extension
-of the symmetric circuit defined by Anderson and Dawar \cite{}. This is my
-latest version of the support and circuit capturing result.
-
-\section{}
-
-\section{Circuits and Symmetry}
+In this section we discuss symmetric circuits, their limitations and extensions
+of this model.
+
+\section{Symmetric Circuits and Limitations}
+Symmetric circuits, as developed by Anderson and Dawar, are, importantly defined
+over (complete) Boolean basis consisting of symmetric functions. The following
+result shows that once a majority gate has been included in this basis any
+symmetric function can be computed using polynomial-size symmetric circuits, and
+as such no additional symmetric function added to the Basis improves the power
+of the model.
+
+Recall from Anderson and Dawar \cite{AndersonD17} we have that $\mathbb{B}_{\std} = \{
+\neg , \wedge , \lor \}$ and $\mathbb{B}_\maj = \{ \maj \} \cup \mathbb{B}$.
+
+Let $F: \{0,1\}^* \rightarrow \{0,1\}$ be a symmetric Boolean function. Since
+$F$ is symmetric we note that for a fixed size input the output of $F$ is
+entirely determined by the number of 1's in its input. Then let
+$c_{F}:\mathbb{N} \rightarrow 2^{\mathbb{N}}$ define a function where $c_{F}(n)$
+is the set of all $m \leq n$ such that for all $\vec{x} \in \{ 0,1 \}^n$ with
+$m$ 1's we have $F (\vec{x}) = 1$. Clearly any symmetric Boolean function $F$ is
+entirely determined by $c_{F}$.
+
+\begin{prop}
+  \label{prop:fuctions-maj}
+  There is a polynomial $p(k)$ such that for any symmetric function $F$ and a
+  given $k \in \mathbb{N}$ there is a circuit $C_k$ on $k$ inputs over the basis
+  $\mathbb{B}_\maj$ which is symmetric, constant depth and with width bounded by
+  $p(k)$.
+\end{prop}
+
+\begin{proof}
+  We define the circuit $C_k$ for inputs $\vec{x} = ( x_1, \ldots, x_k )$.
+
+  For $a \in \mathbb{N}$ we define a get $\countgate_a$ by
+  \begin{align*}
+    &\countgate_a = \maj (x_1, \ldots, x_k, \underbrace {0, \ldots, 0}_{2a -
+      k}) \land \neg \maj (x_1, \ldots , x_k, \underbrace{0, \ldots,  0}_{2a - k + 2})\text{ if $a \geq \frac{k}{2}$,} \\
+    &\countgate_a = \maj (x_1, \ldots, x_k, \underbrace {1, \ldots, 1}_{x -
+      2a}) \land \neg \maj (x_1, \ldots , x_k, \underbrace{1, \ldots,
+      1}_{k - 2a -2}) \text{ if $a < \frac{k}{2}$. }
+  \end{align*}
+
+  Then let $g = \bigvee_{a \in c_{F_i}(k)}\countgate_a$ and let $C_{k}$ be the
+  circuit with input gates labeled by $\vec{x}$ and output gate $g$.
+
+  t is easy to see that $C_k$ is constant depth and it's width is a polynomial
+  in $k$. We have that in each layer of $C_{g'}$ each gate is connected to all
+  gates in the previous layer, and as such the circuit is symmetric.
+\end{proof}
+
+The above proposition has a straight forward application to circuit
+characterisations.
+
+\begin{thm}
+  Let $F = \{F_i : i \in I \}$ be a family of symmetric Boolean functions where
+  $F_i: \{0,1\}^* \rightarrow \{ 0,1 \}$.
+
+  Let $(C_n)_{n \in \mathbb{N}}$ be family of symmetric circuits over the
+  Boolean basis $\mathbb{B} \cup F$, where $C_n$ is a circuit on structures of
+  size $n$, and the size of each circuit in the family is bounded by some
+  function $f(n)$. Then there exists a polynomial $q(n)$ and a family of
+  symmetric circuits $(C_n')_{n \in \mathbb{N}}$ over $\mathbb{B}_\maj$, where
+  $C_n'$ is a circuit on structures of size $n$ and $\vert C_n' \vert \leq
+  q(f(n))$.
+\end{thm}
+
+\begin{proof}
+  From $C_n$ we construct $C_n'$ in the obvious way. For each gate $g \in C_n$
+  of type $F_i$ we have a symmetric circuit $C_g$ from Proposition
+  \ref{prop:function-maj} that computes the same function as $g$. Then let
+  $C_n'$ be $C_n$ but with each gate $g$ replaced by $C_g$. It is easy to see
+  that $C_n'$ is symmetric. We also have that each gate $g$ must have at most
+  $f(n)$ inputs, and the size of $C_g$ is bounded by $p(f(n))$. Thus the size of
+  $C_n'$ is bounded by $f(n)p(f(n))$.
+\end{proof}
+
+\section{G-Symmetric Functions}
+In order to extend the notion of a circuit by extending the basis we need to
+consider functions that are not symmetric in the full sense of the term but have
+some weakened notion of symmetry.
+
 \begin{definition}
-  Let $A$ and $B$ be sets, say that a function $f: \{ 0,1 \}^{A \times B}
-  \rightarrow \{ 0,1 \}$ is matrix-symmetric if for any $\omega: A \times B
-  \rightarrow \{0, 1\}$ and $(\alpha, \beta) \in \sym_A \times \sym_B$ we have
-  $f((\alpha, \beta)\cdot \omega) = f (\omega)$.
-  \\
-  A function $f: \{0,1\}^* \rightarrow \{0,1\}$ is matrix-symmetric iff for any
-  two finite sets $A$, $B$ we have that that $f|_{A \times B}$ is
-  matrix-symmetric (where $f|_{A \times B}$ is the restriction of the function
-  $f$ to inputs sequences of size $\vert A \times B \vert$ and where elements of
-  the input sequence are labelled by elements of $A \times B$).
-\end{definition}
-
-\section{The Support Theorem}
-
-Without a loss of generality we assume that $A$ and $B$ are always initial
-segments of the natural numbers.
-
-% Let $C$ be a circuit over some Boolean basis. For each gate $g \in C$ we
-% associate a relation $\omega_g$ (or just $\omega$ when the context makes it
-% clear). We say a gate is symmetric if that relation
-
-% So far we have defined a circuit over a Boolean basis where the circuit
-% elements all compute symmetric functions. The definition of an induced
-% automorphism only makes. As such, we begin by augmenting the definition of a
-% circuit and automorphism.
+  Let $f: \{0,1\}^X \rightarrow \{0,1\}$ be a function. Let $G \subseteq \sym_X$
+  be a subgroup. We say that $f$ is \emph{$G$-symmetric} if for all $\sigma \in
+  G$, $x \in X$, $f(\sigma x) = f(x)$.
+\end{definition}
+
+We can also introduce similar notions in the case of a two dimensional Boolean
+string.
+
+\begin{definition}
+  Let $f: \{0,1\}^{A \times B} \rightarrow \{0,1\}$ be a function. Let $G
+  \subseteq \sym_{A \times B}$ be a subgroup. We say that $f$ is
+  \emph{matrix-symmetric} if it is $\sym_A \times \sym_B$-symmetric and we say
+  that $f$ is \emph{graph-symmetric} if $A = B$ and it is $\sym_A$-symmetric
+  (with $\sym_A$ acting on both $A$ and $B$).
+\end{definition}
+
+So if we think of $f: \{0,1\}^{A \times B} \rightarrow \{0,1\}$ as representing
+a matrix, then matrix-symmetry corresponds to the property of the function being
+invariant under row-column permutations. If, instead, we have that $A = B$ and
+we then think of $f$ as encoding the adjacency matrix of a graph, then
+graph-symmetry corresponds to the function being constant on isomorphism
+classes.
+
+Importantly, many natural functions of interest are matrix symmetric. For
+example, the function that computes the rank of the matrix over $\mathbb{F}_2$.
+or a thresholded rank function, for example the rank of the matrix over
+$\mathbb{F}_p$ being larger then $r$, for some particular $(p, r) \in
+\mathbb{N}$.
+
+\section{Symmetric Circuits with Matrix-Symmetric Gates}
+
+In this section we develop the corresponding notion of a symmetric circuit, ones
+which allow for the inclusion of matrix-symmetric gates. In particular, these
+circuits are defined using two sets of Boolean functions. The first, denoted by
+$\mathbb{B}_\sym$, is taken to be the symmetric Boolean basis (either
+$\mathbb{B}_\std$ or $\mathbb{B}_\maj$). The second, denoted by
+$\mathbb{B}_\matsym$ is taken to be the matrix-symmetric basis, consisting of a
+collection of matrix-symmetric functions.
 
@@
   \begin{itemize}
+    \setlength\itemsep{0mm}
   \item $G$ is called the set of gates of $C_n$ and $\vert C_n \vert := \vert G
@@
     (g)$ for $\Lambda_R (g)$.
-  \item $L$ is the set of labelings of $C_n$. Let $g \in G$ be an internal gate
-    and $H$ be the children of $g$. Then let $S$ be a set where $\{0,1\}^S =
-    \dom(\Sigma (g))$. Then $L$ is a function that assigns to $g$ an onto
-    function $\omega_g:S \rightarrow H$. We call this the matrix labelling of
-    $g$.
+  \item $L$ assigns labels to the gates (and their inputs) in $C_n$. Let $g \in
+    G$ be an internal gate and $H$ be the gates input to $g$. Then $L(g) : A
+    \times B \rightarrow H$, where $L(g)$ must be surjective and $A, B \subseteq
+    [n]$. We call this the \emph{matrix labelling} of $g$.
   \end{itemize}
@@
 
-% \begin{definition}
-%   let $C = \langle G, W, \Omega, \Sigma, \Lambda, L\rangle$ be a
-%   $(\mathbb{B}_\sym, \mathbb{B}_\sym, \tau)$-circuit, then take $g_1,g_2 \in
-%   G$ such that $\Sigma (g_1) \Sigma(g_2) \in \mathbb{B}_\matsym$.
-
-\begin{definition}
-  Let $\omega_1: A \times B \rightarrow H$ and $\omega_2: A' \times B'
-  \rightarrow H'$ define the equivalence relation $\sim$ as $\omega_1 \sim
-  \omega_2$ iff $\omega_1$ and $\omega_2$ have the same domain and co-domain and
-  there exists $(\alpha, \beta) \in \sym_A \times \sym_B$ and for all $(a,b) \in
-  A \times B$ we have $\omega_1 = \omega_2 \circ (\alpha, \beta)$.
-\end{definition}
-
-% \begin{definition}
-%   Let $\omega_1: A \rightarrow H$ and $omega_2:A' \rightarrow H'$. Define the
-%   equivalence relation $\sim$ as $\omega_1 \sim \omega_2$ iff $\omega_1$ and
-%   $\omega_2$ have the same domain and co-domain, and
-% \end{definition}
+Note the additional requirement that each gate have an associated labelling in
+order to facilitate the evaluation of the gate.
+
+Given some finite $\tau$-structure $\mathcal{A}$ of size $n$ and some bijection
+$\gamma: U \rightarrow [n]$, the evaluation of some $(\mathbb{B}_\sym,
+\mathbb{B}_\sym, \tau)$-circuit) circuit $C$ proceeds by recursively evaluating
+gates. Here the evaluation of the gate $g$ is denoted by $C[\gamma
+\mathcal{A}](g)$. If $g$ is anything but a matrix-symmetric gate, then the
+evaluation is as per the symmetric circuits of Anderson and Dawar \cite{}. If
+$g$ is matrix-symmetric then the evaluation is given by applying the Boolean
+operation $\Sigma(g)$ to the matrix $L^{\gamma}:\dom(L(g)) \rightarrow \{0,1\}$
+defined by $L^{\gamma}(i,j) = C[\gamma \mathcal{A}](L(g)(i,j))$.
+
+\begin{definition}[Invariant Circuit\cite{AndersonD17}]
+  Let $C_n$ be a $(\mathbb{B}_\sym, \mathbb{B}_\sym, \tau)$-circuit, computing
+  some $q$-ary query. We say $C_n$ is \emph{invariant} if for every
+  $\tau$-structure $\mathcal{A}$ of size $n$, $a \in \mathcal{A}^q$, and
+  bijections $\gamma_1, \gamma_2: U \rightarrow [n]$ we have that $C[\gamma_1
+  \mathcal{A}](\Omega (\gamma_1 a)) = C[\gamma_2 \mathcal{A}](\Omega (\gamma_2
+  a))$.
+\end{definition}
 
@@
   let $C = \langle G, W, \Omega, \Sigma, \Lambda, L\rangle$ be a
-  $(\mathbb{B}_\sym, \mathbb{B}_\sym, \tau)$-circuit computing at $q$-ary query
-  on structures of size $n$. Let $\sigma \in \sym_n$ and $\pi: G \rightarrow G$
-  be a bijection such that
+  $(\mathbb{B}_\sym, \mathbb{B}_\matsym, \tau)$-circuit computing at $q$-ary
+  query on structures of size $n$. Let $\sigma \in \sym_n$ and $\pi: G
+  \rightarrow G$ be a bijection such that
   \begin{itemize}
+    \setlength\itemsep{0mm}
   \item for all gates $g, h \in G$, $W(g,h)$ iff $W(\pi g, \pi h)$,
@@
     x)$,
-  \item for all gates $g \in G$, $\Sigma (g) = \Sigma (\pi g)$, and
+  \item for all gates $g \in G$, $\Sigma (g) = \Sigma (\pi g)$,
   \item for each relational gate $g \in G$, $\sigma \Lambda (g) = \Lambda (\pi
-    g)$
-  \item for each internal gate $g$ if $\Sigma (g) \in \mathbb(B)_\matsym$. Then
-    we have that $L(\pi g) \sim \pi \circ L(g)$.
+    g)$, and
+  \item for each internal gate $g$ if $\Sigma (g) \in \mathbb(B)_\matsym$ then
+    we have that $L(\pi g) \sim \pi \cdot L(g)$.
   \end{itemize}
+
+  We call $\pi$ an \emph{automorphism} of $C$, and we say that $\sigma$
+  \emph{induces the automorphism} $\pi$. The group of automorphisms of $C$ is
+  called $\aut_n (C)$.
+\end{definition}
+
+\begin{definition}[Symmetric\cite{AndersonD17}]
+  A circuit $C$ on structures of size $n$ is called \emph{symmetric} if every
+  $\sigma \in \sym_n$ induces an automorphism on $C$.
+\end{definition}
+
+It follows for any symmetric circuit $C_n$ there is a mapping from $\sym_n$ to
+$\aut_n(C)$, from $ \sigma$ to the induced automorphism. This homomorphism is
+injective so long as a single element of $[n]$ appears in the in the label of
+some input gate of $C$ (as then all elements appear by
+symmetry)\cite{AndersonD17}. In this paper we always assume that there is always
+one such element as otherwise all inputs are constant, and so the circuit just
+computes a constant function. In order to assure this homomorphism is surjective
+Anderson and Dawar \cite{AndersonD17} introduce the notion of a \emph{rigid}
+circuit.
+
+\begin{definition}[Rigidity]
+  Let C be a $(\mathbb{B}_\sym, \mathbb{B}_\sym, \tau)$-circuit, where $C =
+  \langle G, W, \Omega, \Sigma, \Lambda, L\rangle$. Say that $C$ is rigid if
+  there are no internal gates $g, g' \in G$ such that $\Sigma(g) = \Sigma (g')$,
+  $\Omega^{-1}(g) = \Omega^{-1}(g')$, and for every $g'' \in G$, $W(g'', g')$
+  and $W(g,g'')$ iff $W(g', g'')$.
+\end{definition}
+
+Another property which simplifies our analysis is the property of having
+\emph{bijective labels}.
+
+\begin{definition}
+  We say that a circuit $C$ has bijective labels if for each gate $g$ in $C$,
+  $L(g)$ is a bijection.
+\end{definition}
+
+We prove in a later section that a circuit may be transformed in polynomial time
+into an equivalent circuit that is both rigid and has bijective labelings. Hence
+we may assume these two properties without a loss of generality.
+
+With the assumption of rigidity in place, we abuse notation for permutations and
+let $\sigma \in \sym_n$ also denote the induced automorphism.
+
+We finally want to define symmetric circuits with rank gates.
+
+\begin{definition}
+  Let $\mathbb{B}_{\matsym}$ consist of functions of the form $f_{p,r}:
+  \{0,1\}^{A \times B} \rightarrow \{0,1\}$ for $A, B$ initial segments of
+  $\mathbb{N}$ and $f, p \in \mathbb{N}$, with $p$ prime, and such that for
+  $f_{p,r}(M) = 1$ iff the matrix $M: A \times B \rightarrow \{0,1\}$ has rank
+  at least $r$ over the field $\mathbb{F}_p$. A \emph{symmetric circuit with
+    rank gates} is a $(\mathbb{B}_\maj, \mathbb{B}_\matsym, \tau)$-circuit, for some
+  vocabulary $\tau$.
+\end{definition}
+
+The natural restriction to consider on families of circuits is uniformity.
+
+\begin{definition}
+  Let $(C_n)_{n \in \mathbb{N}}$ be a family of Boolean circuits. We say that
+  $(C_n)_{n \in \mathbb{N}}$ is \emph{$P$-uniform} if the mapping $n \mapsto C_n$ is
+  computable in polynomial time.
+\end{definition}
+
+We are now ready to state what will be the main theorem of this paper.
+
+\begin{thm}[Main Theorem]
+ A graph property is decidable by a $P$-uniform family of symmetric circuits
+ with rank gates if, and only if, it is definable by an FPR sentence.
+\end{thm}
+
+% \section{Circuits to FPR}
+
+% In this section I discuss how to determine the rank a matrix labelling at some
+% gate $g$. This is a rough copy written for the purpose of discussion. In this
+% section we fix some circuit $C_n$ and some rank gate $g$ in $C_n$ with a set
+% of children $H$ and matrix labelling $L: [a] \times [b] \rightarrow H$ (which
+% we assume WLOG is a bijection).
+
+\chapter{Symmetry and Support}
+In order to analyse families of symmetric circuits we will need to develop some
+theory for analysing symmetries. In this section we define the terms needed
+(e.g. the notion of a support) and prove basic results. We then prove the first
+important theorem in this paper, the support theorem, using these tools. It is
+worth noting that we prove the support theorem for arbitrary symmetric circuits
+with matrix-symmetric gates, not just for rank gates.
+
+\section{Supports and Supporting Partitions}
+In this section we formally define a support and the related notion of a
+supporting partition.
+
+\begin{definition}
+  Let $G$ be a subgroup of $\sym_n$ and let $S \subseteq [n]$. Then $S$ is a
+  \emph{support} for $G$ if $\stab(S) \subset G$.
+\end{definition}
+
+\begin{definition}
+  Let $G$ be a subgroup of $\sym_n$ and $\mathcal{P}$ be a partition of $[n]$.
+  Then $\mathcal{P}$ is a \emph{supporting partition} for $G$ if
+  $\stab(\mathcal{P}) \subseteq [n]$.
+\end{definition}
+
+Notice that if $\mathcal{P}$ is a supporting partition for $G$ and $P \in
+\mathcal{P}$ then $\stab([n] \setminus P) \subseteq \stab(\mathcal{P}) \subset
+G$, i.e. $[n] \setminus P$ is a support for $G$.
+
+These supporting partitions admits a natural partial order in terms of
+coarseness. If $\mathcal{P}, \mathcal{P}'$ we say that $\mathcal{P}'$ is as
+course as $\mathcal{P}$ (denoted by $\mathcal{P}' \supseteq \mathcal{P}$) if for
+all $x \in \mathcal{P}$ there exists $y \in \mathcal{P}'$ such that $x \subseteq
+y$ \cite{AndersonD17}.
+
+Anderson and Dawar \cite{AndersonD17} show that for any permutation group $G
+\subseteq \sym_n$ a unique coarsest partition can always be found. We call this
+partition the \emph{canonical supporting partition}, and denote it by $\SP (G)$.
+This canonical supporting partition, along with the above observation about
+supports, will allow us to construct for each group a canonical support.
+
+\begin{definition}
+  Let $G$ be a subgroup of $\sym_n$. Let $\| SP(G) \| = \min \{\vert [n]
+  \setminus P \vert : P \in SP(G) \}$. We say that $G$ has small support if $\|
+  SP(G) \| < \frac{n}{2}$.
+\end{definition}
+
+\begin{definition}
+  Let $G$ be a subgroup of $\sym_n$ such that $G$ has small support. Let
+  $\consp(G) = [n] \setminus P$, where $P$ is the maximal element of $\SP(G)$.
+  We call $\consp(G)$ the canonical support of $G$.
 \end{definition}
@@
 \begin{remark}
-  I also need a new notion of robustness here in order to collapse gates that
-  have the same children and equivalent labelings are properly regarded as being
-  the same gate.
+  Include a remark about the importance of asserting the size consideration. Use
+  the alternating group as an example.
 \end{remark}
+
+We state the following two results from Anderson and Dawar \cite{AndersonD17}.
+
+\begin{lem}
+  \label{lem:SP_conjugation}
+  Let $G \leq \sym_n$ and $\sigma \in \sym_n$ then $\sigma \SP (G) = \SP(\sigma
+  G \sigma^{-1})$.
+\end{lem}
+
+\begin{lem}
+  For any $G \leq \sym_n$ we have that $\stab (\SP (G)) \subseteq G
+  \setstab(\SP(G))$.
+\end{lem}
+
+\section{Group Action on Supports}
+In this paper, distinct the case of Anderson and Dawar \cite{AndersonD17}, we
+will need to develop theory and terminology for dealing with group actions (and
+supports) on more than just gates in the circuit. In particular, we use this
+theory for understanding the actions on the rows and columns of a labelling of a
+gate.
+
+\begin{definition}
+  Let $G$ be a subgroup of $\sym_n$ and $X$ be a set on which a left group
+  action of $G$ on $X$ is defined. We denote the canonical supporting partition
+  of $x\in X$ by $\SP (x) = \SP (\stab(x))$. We say that $x \in X$ has small
+  support if $\stab(x)$ has small support. We say that $X$ has small supports if
+  all $x \in X$, $x$ have small support.
+
+  If $x \in X$ has small support, we denote the \emph{canonical support} of $x$
+  by $\consp(x) = \consp (stab(x))$.
+\end{definition}
+
+\begin{definition}
+  Let $G$ be a group and $X$ be a set on which a left group action of $G$ on $X$
+  is defined. Then $\stab_G (x) = \{\pi \in G : \pi x = x\}$ and $\orb_G (x) =
+  \{\pi x : \pi \in G\}$. In the event that the context makes the group obvious
+  we omit the subscript.
+\end{definition}
+
+\begin{lem}
+  \label{lem:stab_conjugation}
+  Let $G$ be a subgroup of $\sym_n$, $X$ be a set on which a left group action
+  of $G$ on $X$ is defined and $\sigma \in G$. Then for any $x \in X$ it follows
+  that $\sigma \stab (x) \sigma^{-1} = \stab(\sigma x)$.
+\end{lem}
+
+\begin{proof}
+  Let $\pi \in \stab(x)$, then $\sigma \pi \sigma^{-1}(\sigma x) = \sigma \pi
+  (x) = \sigma (x)$, and so $\sigma \pi \sigma^{-1} \in \stab(\sigma x)$. Let
+  $\pi \in \stab(\sigma (x))$ then $\pi \sigma (x) = \sigma (x)$ and so
+  $\sigma^{-1} \pi \sigma (x) = x$. It follows that $\sigma^{-1} \pi \sigma \in
+  \stab(x)$ and so $\pi = \sigma (\sigma^{-1} \pi \sigma) \sigma ^{-1} \in
+  \sigma \stab(x) \sigma^{-1}$.
+\end{proof}
+
+\begin{lem}
+  \label{lem:support_mapping}
+  Let $G $ be a subgroup of $\sym_n$, $X$ be a set on which a left group action
+  of $G$ on $X$ is defined and $\sigma \in G$. Then for any $x \in X$ it follows
+  that $\sigma \SP (x) = \SP (\sigma x)$ and, if $x$ has small support, $\sigma
+  \consp (x) = \consp (\sigma x)$.
+\end{lem}
+\begin{proof}
+  From Lemma \ref{lem:SP_conjugation} and Lemma \ref{lem:stab_conjugation} have
+  that $\sigma \SP (x) = \SP(\sigma \stab(h) \sigma^{-1}) = \SP (\stab(\sigma
+  x)) = \SP (\sigma x)$. Thus proving the first part of the statement.
+
+  From the fact that $\| \SP(x) \| < \frac{n}{2}$ it follows there exists a
+  unique $P_1 \in \SP(x)$ such that $\vert P_1 \vert > \frac{n}{2}$ and
+  $\consp(x) = [n] \setminus P_1$. But then $\sigma \consp (x) = \sigma([n]
+  \setminus P_1) = [n] \setminus (\sigma P_1)$. We note that $\sigma P_1 \in
+  \sigma \SP (x) = \SP(\sigma x)$ and $\vert \sigma P_1 \vert > \frac{n}{2}$.
+  Thus $\sigma P_1$ is the unique largest partition in $\SP(\sigma x)$, and so
+  $\consp(\sigma x) = [n]\setminus (\sigma P_1) = \sigma (consp(x))$. Thus
+  proving the second part of the statement.
+\end{proof}
+
+\begin{lem}
+  Let $G$ be a subgroup of $\sym_n$, $X$ be a set on which a left group action
+  of $G$ on $X$ is defined. Then for any $x \in X$ with small support, and
+  $\sigma, \sigma' \in G$ such that $\sigma (vec{\consp}(x)) = \sigma'
+  (\vec{\consp}((x))$ we have that $\sigma (x) = \sigma'(x)$.
+\end{lem}
+\begin{proof}
+  We have that $(\sigma')^{-1}\sigma(\vec{\consp}(x)) = \vec{\consp}(x)$ and so
+  $(\sigma')^{-1} \sigma (x) = x$ and thus $\sigma (x) = \sigma' (x)$.
+\end{proof}
+
+% \begin{lem}
+%   Let $G \leq \sym_n$, $X$ be a set on which a left group action of $G$ on $X$
+%   is defined and $\sigma \in G$. Then if $y \in \orb_{G} (x)$ and $\consp (x)
+%   = \consp (y)$ then $x = y$.
+% \end{lem}
+
+% \begin{proof}
+%   Let $\sigma \in G$ be such that $\sigma x = y$. Then $\consp(x) = \consp (y)
+%   = \consp (\sigma x) = \sigma \consp (x)$. Thus $\sigma (\sp (x))$
+% \end{proof}
+
 % \begin{definition}
-%   Let $C$ be a circuit, $g$ be a gate in $C$, $H$ be $g$'s set of children and
-%   let $\omega: A \times B \rightarrow H$ be a surjection, where $A$ and $B$
-%   are sets and $g$ takes $\vert A \vert \cdot \vert B \vert$ inputs. Call such
-%   an $\omega$ a matrix labeling for $g$.
+%   Let $h \in H$. Let $\stab_r(h)$ be a subgroup of $\stab(\consp(g))$
+%   consisting of exactly those permutations $\sigma$ such that $\row (\sigma h)
+%   = \row (h)$. Let $\stab_c(h)$ be a subgroup of $\stab(\consp(g))$ consisting
+%   of exactly those permutations $\sigma$ such that $\column (\sigma h) =
+%   \column(h)$.
 % \end{definition}
@@
 % \begin{definition}
-%   Let $C$ be a circuit and $g_1$ and $g_2$ be gates in $C$. Let $\sigma \in
-%   \sym_n$ be a permutation such
+%   A set $S \subseteq [n]$ is called a row-support for $h$ if $S$ is a support
+%   for $\stab_r(h)$. A set $S \subseteq [n]$ is called a column-support for $h$
+%   iff $S$ is a support for $\stab_c(h)$.
 % \end{definition}
+
+% \begin{definition}
+%   A partition $\mathcal{P}_r$ is called a row-supporting partition iff
+%   $\mathcal{P}_r$ is a support for $\stab_r(h)$. A partition $\mathcal{P}_c$
+%   is called a column-supporting partition iff $\mathcal{P}_c$ is a support for
+%   $\stab_c(h)$.
+% \end{definition}
+
+% \begin{definition}
+%   Let $\SP^r(h)$ denote the conical supporting partition and $r_h$ the
+%   canonical support of $\stab_r(h)$. Similarly, let $\SP^c(h)$ denote the
+%   conical supporting partition and $c_h$ the canonical support of
+%   $\stab_c(h)$.
+% \end{definition}
+
+% \begin{definition}
+%   Let $G \subseteq \sym_n$ be a subgroup. Then let $\SPs(G)$ be the set of all
+%   supporting partitions of $G$ and $\consps(G)$ be the set of all supports of
+%   $G$.
+% \end{definition}
+
+% We now prove a few important lemmas on supports.
+
+% \begin{lem}
+%   Let $A, B \leq \sym_n$ then $\SP(A \cap B) \subseteq \SP (A) $.
+% \end{lem}
+% \begin{proof}
+%   Let $\mathcal{P}$ be a supporting partition of $A \cap B$. Then
+%   $\mathcal{P}$ is a supporting partition of $A$. Since $\SP(A)$ is coarser
+%   than all such partitions the result follows.
+% \end{proof}
+
+% \begin{lem}
+%   Let $h \in H$, then $\SP(\stab(h)) \subseteq \SP (\stab (\row (h)))$ and
+%   $\SP (\stab(h)) \subseteq \SP (\stab (\column(h)))$.
+% \end{lem}
+% \begin{proof}
+%   It can be shown that $\stab (h)$
+% \end{proof}
+
+% The following lemma will be used to prove the relationship between the support
+% of a gate and the supports of its row and columns.
+% % Use this lemma + a support type theorem in order to get the result.
+% \begin{lem}
+%   Let $G \leq \sym_n$, $X_1$ and $X_2$ be sets on which left group actions of
+%   $G$ on $X_1$ and $X_2$ are defined. Let $x_1 \in X_1$ and $x_2 \in X_2$ and
+%   suppose $\vert \consp(x_1) \vert < \frac{n}{2}$ and $ \vert \consp(x_2)
+%   \vert < \frac{n}{2}$. Then if $\SP(\stab(x_1)) \subseteq \SP (\stab(x_2))$
+%   then $\consp (x_2) \subseteq \consp (x_1)$.
+% \end{lem}
+% \begin{proof}
+%   Since $\vert \consp(x_1) \vert = \| \SP (\stab(x_1)) \| < \frac{n}{2}$ it
+%   follows that there a unique maximal $P_1 \in \SP (\stab(x_1))$ such that
+%   $\vert P_1 \vert > \frac{n}{2}$. Similarly there is a unique maximal $P_2
+%   \in \SP (\stab(x_2))$. Moreover, from the fact that $\SP (\stab(x_2))$ is
+%   coarser than $\SP (\stab(x_1))$, it follows that there exists $P \in
+%   \SP(\stab(x_2))$ such that $P_1 \subseteq P$. From the fact that
+%   $\frac{n}{2} < \vert P_1 \vert \leq \vert P \vert$ and $P_2$ is the only
+%   part such that $\frac{n}{2} < \vert P_2 \vert$, it follows that $P_1
+%   \subseteq P = P_2$ and so $\consp(x_2) = [n] - P_2 \subseteq [n] - P_1 =
+%   \consp(x_1)$.
+% \end{proof}
+
+\section{Support Theorems}
+In this section we develop an analogous theorem to the support theorem of
+Anderson and Dawar \cite{AndersonD17}.
+%
+%\begin{lem}[Support Lemma]
+%  For any $\epsilon$ and $n$ such that $\frac{2}{3} \leq \epsilon \leq 1$ and
+%  $n \geq \frac{128}{\epsilon^2}$, if $C$ is a symmetric, rigid circuit on
+%  structures of size $n$ and $s := \max_{g \in C} \vert \orb (g)\vert \leq
+%  2^{n^{1-\epsilon}}$, then, for all $g \in C$, $\vert \SP (g) \vert \leq
+%  \frac{n}{2}$.
+% \end{lem}
+
+% \begin{thm}[Support Theorem]
+%   For any $\epsilon$ and $n$ such that $\frac{2}{3} \leq \epsilon \leq 1$ and
+%   $n \geq \frac{128}{\epsilon^2}$, if $C$ is a symmetric, rigid circuit on
+%   structures of size $n$ and $s := \max_{g \in C} \vert \orb (g)\vert \leq
+%   2^{n^{1-\epsilon}}$, then, $SP(C) \leq \frac{33}{\epsilon}\frac{\log s}{\log
+%   n}$.
+% \end{thm}
+
+% \begin{lem}
+%   For any $\epsilon$ and $n$ such that $\frac{2}{3} \leq \epsilon \leq 1$ and
+%   $n \geq \frac{128}{\epsilon^2}$, if $C$ is a symmetric, rigid circuit on
+%   structures of size $n$ and $s := \max_{g \in C} \vert \orb (g)\vert \leq
+%   2^{n^{1-\epsilon}}$, then, for all $g \in C$, we have for all $(i,j) \in
+%   \dom (L_g)$ that $\consp(i) \subseteq \consp (L_g(i,j))$ and $\consp(j)
+%   \subseteq \consp(L_g (i,j)))$.
+% \end{lem}
+
+% \begin{lem}
+%   Let $\mathcal{P}_1$ and $\mathcal{P}_2$ be partitions of $[n]$ such that
+%   $\mathcal{P}_1 = A \cup S_1$ and $\mathcal{P}_2 = B \cup S_2$, and
+%   \begin{enumerate}
+%   \item for all $X \in A$ and $Y \in B$ we have that $X \cap Y = \emptyset$,
+%     and
+%   \item for all $x \in S_1 \cup S_2$, x is a singleton.
+%   \end{enumerate}
+%   It follows that $\varepsilon(\mathcal{P}_1, \mathcal{P}_2) = A \cup B \cup
+%   S$, where $S$ is a set of singletons.
+% \end{lem}
+% \begin{proof}
+% \end{proof}
+
+% \begin{lem}
+%   Let $G_1$ and $G_2$ be subgroups of $\sym_n$. Then $\SP^S(G_1) = \SP^S(G_2)$
+%   iff $\consp^S(G_1) = \consp^S(G_2)$.
+% \end{lem}
+% \begin{proof}
+
+% \end{proof}
+
+% \begin{lem}
+%   Let $G_1$ and $G_2$ be subgroups of $\sym_n$. Then $\consp^S(G_1) =
+%   \consp^S(G_2)$ implies that $\consp (G_1) = \consp (G_2)$.
+% \end{lem}
+% \begin{proof}
+% \end{proof}
+
+% The following lemma asserts a few basic facts about the canonical row and
+% column supports.
+
+% \begin{lem}
+%   Let $h \in H$, then $r_h \subset \consp(h)$, $c_h \subset \consp(h)$ and
+%   $c_r \cup r_h = \consp(h)$.
+% \end{lem}
 
@@
   Say that two distinct pairs $(\sigma_1, h_1, h_1'), (\sigma_2, h_2, h_2') \in
-  \sym([n]) \times H^2$ are mutually independent if
+  \sym_n\times H^2$ are mutually independent if
   \begin{itemize}
+    \setlength\itemsep{0mm}
   \item $\sigma_2 h_1 = h_1$,
@@
   \end{itemize}
-  We say that a set $S \subseteq \sym([n]) \times H^2$ is useful if each pair in
+  We say that a set $S \subseteq \sym_n \times H^2$ is useful if each pair in
   it is useful. We say that S is independent if each pair of distinct pairs in
@@
 
-The following two lemmas proved by Anderson and Dawar \cite{} are both of use in
-proving the following theorem.
+The following two lemmas proved by Anderson and Dawar \cite{AndersonD17} are
+both of use in proving the following theorem.
 
@@
   matrix-symmetric gate then the result follows from the argument presented by
-  Anderson and Dawar \cite{}. Suppose $g$ is a matrix-symmetric gate, and
+  Anderson and Dawar \cite{AndersonD17}. Suppose $g$ is a matrix-symmetric gate, and
   suppose $g$ has a labelling $\omega$. We now argue that this leads to a
@@
 
-\section{Rigid Circuits}
+\chapter{Translating Circuits into Formulas}
+In this section we develop the theory for defining a formula of FPR from a
+family of $P$-uniform family of symmetric circuits with rank gates. We first
+show prove results on the generality of rigid circuits and circuits with
+bijective labelings. Second, we prove that there are polynomial time algorithms
+for determining canonical supports of gates. Third, we develop a FPR definable
+way of evaluating a rank gate in the circuit. Finally, we complete the result by
+explicitly defining an FPR formula corresponding to a given family of symmetric
+circuits with rank gates.
+
+We note that most of these results are for the more general case of symmetric
+circuits with matrix-symmetric gates.
+
+\section{Rigid Circuits and Labelings}
 
@@
 
-% If $h$ is a binary $\and$ gate, then we say that $h$ has height $k+1$ if it
-% has a $k$-height tower of binary $and$ gates connected above it, with a
-% non-$\and$ gate $p$ connected to the final binary $\and$ gate, and all other
-% inputs connected to $1$. We then say that $h$ is the base of a tower of height
-% $k$ and type $p$.
-
-% Then for each $h \in W_g$, if $h$ is not a binary $\and$ gate, the let $k$ be
-% the largest integer such that there a gate $h' \in W(h, \cdot)$ which is the
-% base of a tower of height $k$ and type $h$. it's output directly connected to
-% one of the gates in $W(h^k, \cdot)$ (with k = 0 corresponding to just $h$).
-% Then each $i \in \{1, \ldots , \vert \omega^{-1}(h)\vert\}$ add into the
-% circuit $h^{k+i}$ and wire it to $g$. Notice that this step requires adding
-% $\vert \omega^{-1}(h) \vert -1$ gates to the circuit. For some assumed
-% ordering $\dom(\omega)$, let $\{s_0, \cdot, s_m\} = \omega^{-1}(h)$. Define
-% $L'(g)(s_i) = h^{k+i}$. Now continue on to the next gate topologically where
-% $L(g)$ is not a bijection, and execute the same process
-
 \begin{lem}
@@
   \section{Computing Supports}
+
  \begin{lem}
@@
    $\pi \omega_g \sim \omega_{g'}$ iff $\sigma_{\pi,g'} \in \sym_A \times
-    \sym_B$. But this just involves checking that $\sigma$ acts as a bijection
-    on $A$ and $B$ separately and, given that $\vert A \vert$ and $\vert B
-    \vert$ are both bounded by $\vert C \vert$, the algorithm which just
-    iterates through $A$ and $B$ is sufficient. If for every $g'$ it is found
-    that $\pi_{\sigma,g'}$ is not in $\sym_A \times \sym_B$ then terminate with
+   \sym_B$. But this just involves checking that $\sigma$ acts as a bijection on
+   $A$ and $B$ separately and, given that $\vert A \vert$ and $\vert B \vert$
+   are both bounded by $\vert C \vert$, the algorithm which just iterates
+   through $A$ and $B$ is sufficient. If for every $g'$ it is found that
+   $\pi_{\sigma,g'}$ is not in $\sym_A \times \sym_B$ then terminate with
    failure. If there is a $g'$ for which $\pi_{\sigma, g'} \in \sym_A \times
@@
 
-    If $g$ is an output gate, then check that for all tuples in $[n]^{q}$ we
-    have that $\pi \Omega (x) = \Omega (\sigma (x))$, and terminate with failure
-    if the condition is not met.
+   If $g$ is an output gate, then check that for all tuples in $[n]^{q}$ we have
+   that $\pi \Omega (x) = \Omega (\sigma (x))$, and terminate with failure if
+   the condition is not met.
 
@@
 
-  \section{Evaluating Symmetric Circuits}
-  We need to extend two Lemmas in this section.
-
-\begin{lem}
-  Let $g$ be a matrix-symmetric gate in $C_n$ with children $H$. Let $\alpha \in
-  U^{\underbar{\sp(g)}}$, and suppose $\gamma_1, \gamma_2: U \rightarrow [n]$
-  with $\gamma^{-1}_1 \sim \alpha$ and $\alpha \sim \gamma^{-1}_2$. Let $A
-  \times B = \dom (L(g))$.
-
-  For an input structure $\mathcal{A}$, let $L^0_\gamma: A \times B \rightarrow
-  \{0,1\}$, where $L^0_\gamma (a,b):= C[\gamma \mathcal{A}] (L(g)(a,b))$.
-
-  Then $L^0_{\gamma_1} \sim L^0_{\gamma_2}$.
+\section {Evaluating Circuits}
+Let $\mathcal{C} = (C_n)_{n \in \mathbb{N}}$ be a family of polynomial-size
+rigid symmetric circuits with matrix-symmetric gates. that compute a $q$-ary
+query. Let $n_0$ the constant in the hypothesis of the Support Theorem.
+
+Let $\mathcal{A}$ be a structure of size $n$ over the universe $U$, and let $g$
+be a matrix-symmetric gate in $C_n$. In this section we develop the theory which
+will allow us to evaluate this gate in FPR and (using results from Anderson and
+Dawar \cite{}) recursively evaluate the circuit.
+
+We recall that in order to evaluate the gate $g$ we need to consider a bijection
+$\gamma: U \rightarrow [n]$, with the evaluation of $g$ given by $C_n[\gamma
+\mathcal{A}](g)$. We first show that the evaluation of $g$ depends only on which
+elements of $U$ are mapped to $\consp(g)$.
+
+\begin{definition}
+  Let $f: X \rightarrow Y$ and $g : X' \rightarrow Y'$. We say that $f$ is
+  \emph{compatible} with $g$, or $f \sim g$, if for all $a \in S_1 \cap S_2$,
+  $f(a) = g(a)$ and for all $a \in S_1 \setminus S_2$ and $b \in S_2 \setminus
+  S_1$, $f(a) \neq g(b)$.
+\end{definition}
+
+\begin{definition}
+  Let $f: A \times B \rightarrow H$ and $p: A' \times B' \rightarrow H$. We say
+  that $f$ and $p$ are \emph{row-column equivalent} if there exist bijections
+  $\alpha: A \rightarrow A'$ and $\beta: B \rightarrow B'$ such that for all
+  $(a, b) \in A \times B$, $f(a,b)g(\alpha(a), \beta(b))$. In this case we write
+  $f \sim p$.
+\end{definition}
+
+For a given bijection $\gamma: U \rightarrow [n]$ we can define a matrix
+$L^{\gamma} : \dom (g) \rightarrow \{0,1\}$ by $L^{\gamma} (a,b) := C[\gamma
+\mathcal{A}](L(g)(a,b))$. In the following Lemma we show that the the matrix
+symmetry of the gate $g$ ensures that for any two bijections $\gamma_1,
+\gamma_2$, if they agree on the support of $g$ then $L^{\gamma_1}_g$ is
+row-column equivalent to $L^{\gamma_2}_g$. This implies that the evaluation of
+$g$ depends only on the assignment to its support.
+
+\begin{lem}
+  Let $g$ be a matrix-symmetric gate in $C_n$ with children $H$. Let $\eta:
+  \consp(g) \rightarrow U$ be an injection, and suppose $\gamma_1, \gamma_2: U
+  \rightarrow [n]$ with $\gamma^{-1}_1 \sim \eta$ and $\eta \sim \gamma^{-1}_2$.
+  Let $A \times B = \dom (L(g))$. Then $L^{\gamma_1}$ and $L^{\gamma_2}$ are
+  row-column equivalent.
 \end{lem}
@@
   \gamma_2$. Moreover, since $\gamma^{-1}_1$ and $\gamma^{-1}_2$ are both
-  consistent with $\alpha$, it follows that $\pi$ must fix $\sp(g)$. Thus $L(g)
-  \sim \pi L(g)$, and so there exists $(\sigma, \lambda)$ such that $\pi L(g) =
-  L(g) (\sigma, \lambda)$.
+  consistent with $\alpha$, it follows that $\pi$ must fix $\consp(g)$. Thus
+  $L(g) \sim \pi \cdot L(g)$, and so there exists $(\sigma, \lambda)$ such that
+  $\pi L(g) = L(g) (\sigma, \lambda)$.
 
@@
   \begin{align*}
-    L^0_{\gamma_1} (a,b) &= C_n[\gamma_1 \mathcal{A}](L(g)(a,b))\\
-                         & = C_n[\pi gamma_1 \mathcal{A}][\pi L(g)(a,b)] \\
-                         & = C_n[gamma_2 \mathcal{A}][L(g)((\sigma, \lambda)(a,b))]\\
-                         & = L^0_{\gamma_2} ((\sigma, \lambda) (a,b)),
+    L^{\gamma_1} (a,b) &= C_n[\gamma_1 \mathcal{A}](L(g)(a,b))\\
+                       & = C_n[\pi \gamma_1 \mathcal{A}][\pi L(g)(a,b)] \\
+                       & = C_n[\gamma_2 \mathcal{A}][L(g)((\sigma, \lambda)(a,b))]\\
+                       & = L^{\gamma_2} ((\sigma, \lambda) (a,b)),
   \end{align*}
-  and it follows that $L^0_{\gamma_1} \sim L^0_{\gamma_2}$.
-
-\end{proof}
-
-\begin{lem}
-  Let $g$ be a matrix symmetric gate in $C_n$ with children $H$. Let $\alpha \in
-  U^{\underbar{\sp(g)}}$ and $\gamma: U \rightrrow [n]$ such that
-  $gamma^{-1}\sim \alpha$. Let $A \times B = \dom (L(g))$ and define
-  $L^{EV}_\alpha: A \times B \rightarrow \{0,1\}$ by
+  and it follows that $L^{\gamma_1} \sim L^{\gamma_2}$.
+\end{proof}
+
+For each gate we define the set of all assignments to support of that gate which
+cause the evaluate to true: $\EV_g := \{ \alpha: U^{\underline{\consp(g)}} :
+\exists \gamma \in U^{\underline{[n]}} C_n [\gamma \mathcal{A}](g) = 1 \wedge
+\alpha \sim \gamma^{-1}\}$. We now construct $\EV_g$ using $\EV_h$ for each $h
+\in H_g$. In doing so we entirely characterise exactly which bijections $\gamma:
+U \rightarrow [n]$ cause $g$ to evaluate to true.
+
+% \begin{remark}
+%   Let $\sigma \in \spstab{g}$, then we know that there exists $(\sigma_r,
+%   \sigma_c) \in \sym_A \times \sym_B$ and $\sigma_r (i) = \row (\sigma h)$,
+%   for any $h \in H$ such that $\row (h) = i$ and similarly $\sigma_c (j) =
+%   \column (\sigma h)$, for any $h \in H$ such that $\column (h) = j$.
+% \end{remark}
+
+We introduce here some useful notation.
+
+\begin{definition}
+  Let $S^r_h = \{ \sigma \in \stab (\consp(g)) : \sigma \vec{r_h} = \vec{r_h}
+  \}$ and $G^r_h = \{ \sigma \in \stab(\consp(g)) : \row(\sigma h) = \row(h)\}$.
+  Let $S^c_h = \{ \sigma \in \stab (\consp(g)) : \sigma \vec{c_h} = \vec{c_h}
+  \}$ and $G^c_h = \{ \sigma \in \stab(\consp(g)) : \column(\sigma h) =
+  \column(h)\}$.
+\end{definition}
+
+Clearly, by definition of a row and column support, $S^r_h \subseteq G^r_h$ and
+$S^c_h \subseteq G^c_h$.
+
+% \begin{remark}
+%   In this section I assume for the moment that:
+%   \begin{itemize}
+%   \item $\consp (g) = \{\}$,
+%   \item $S^r_h = G^r_h$ and $S^c_h = G^c_h$,
+%   \item $\forall h,h' \in H$ we have $\vert r_h \vert = \vert r_{h'} \vert$
+%     and $\vert c_h \vert = \vert c_{h'} \vert$,
+%   \item For all $i,i' \in A$ $\exists \sigma \in \stab(\consp (g))$ such that
+%     $\sigma_r i = i'$. Similarly for all $j, j' \in B$ $\sigma \exists \in
+%     \spstab{g}$ such that $\sigma_c j = j'$.
+%   \item $\forall h \in H$, $\orb (h) = H$
+%   \end{itemize}
+% \end{remark}
+
+% Let $k_r = \vert r_h \vert$ and $k_c = \vert c_h \vert$. Let $\mathcal{G}_r =
+% \{\sigma_r : \sigma \in \spstab{g}\}$ and $\mathcal{G}_c = \{sigma_c : \sigma
+% \in \spstab{g}\}$.
+
+% \begin{definition}
+%   Let $\mathcal{G} \leq \sym_n$ and $x$ be an element of a set on which an
+%   action of $\sym_n$ is defined. Then $\orb_{\mathcal{G}}(x) = \{x^\pi: \pi
+%   \in \mathcal{G}\}$.
+
+%   For $i \in [a]$ let $\orb_r(i) = \orb_{\mathcal{G}_r}(i)$ and for $j \in
+%   [b]$ let $\orb_c (j) = \orb_{\mathcal{G}_c}(j)$.
+% \end{definition}
+
+% \begin{definition}
+%   Let $A, B \subseteq [n]$ and let $t = (t_1, t_2, t_3) \in \mathbb{N}^3$. We
+%   say that $(A,B)$ has \emph{type} $t$ if $\vert A \vert = t_1$, $\vert B
+%   \vert = t_2$ and $\vert A \cap B \vert = t_{3}$. We say that $\type (A,B) =
+%   t$.
+% \end{definition}
+
+For the sake of brevity, for sets $Z,X,Y$, where $f : Z \rightarrow X$ and $p :
+Z \rightarrow Y$ are injections, let $f_p = f \cdot p^{-1}$.
+
+\begin{definition}
+  Let $\vec{x}, \vec{y} : Z \rightarrow X$ and $\vec{r}, \vec{c}: Z \rightarrow
+  Y$ be injections. If $\vec{x} \cdot \vec{r}^{-1} \sim \vec{y} \cdot
+  \vec{c}^{-1}$ we say that $(\vec{x}, \vec{y})$ and $(\vec{r} \vec{c})$ have
+  the same \emph{type}.
+\end{definition}
+
+We note that if we have $f : X \rightarrow Y$ and $p: X' \rightarrow Y'$ and $f
+\sim p$ then define $(f \vert p): X \cup X' \rightarrow Y \cup Y'$ by
+
 \begin{align*}
-    L^{EV}_\alpha (a,b):=
-    \begin{cases*}
-      1 & if $A_h \cap \EV_h \neq \emptyset$ 0 & otherwise
-    \end{cases*},
+  (f \vert p) (x) =
+  \begin{cases}
+    f (x) & x \in X \\
+    p (x) & x \in Y.
+  \end{cases}
 \end{align*}
-  where for $h \in W_g, A_h:= \{\beta \in U^{\underline{\sp(h)}} \vert \alpha
-  \sim \beta\}$. Then $L^0_\gamma = L^{EV}_\alpha$ and $\alpha \in \EV(g)$ iff
-  $\rk^u_p(L^0_\gamma)$
-\end{lem}
-\begin{proof}
-
-\end{proof}
-
-\begin{lem}
-  Let $g$ be a matrix-symmetric gate in $C_n$ with children $W_g$. $Let \alpha
-  \in U^{\underbar{\sp(g)}}$ and let $\gamma: U \rightarrow [n]$ such that
-  $\gamma^{-1} \sim \alpha$. Let $A \times B = \dom (L(g))$, and let
-  $f:\{0,1\}^{A \times B} \rightarrow \{0,1\}$ be the matrix-symmetric function
-  associated with $g$. Define $L^{EV}_\alpha: A \times B \rightarrow \{0,1\}$ by
+
+The compatibility of these two functions ensures that this function is well
+defined.
+
+% \begin{claim}
+%   Let $A_1,B_1, A_2, B_2 \subseteq [n]$. Then $(A_1, B_1)$ and $(A_2, B_2)$
+%   have the same type iff $\exists \pi \in \sym_n$ such that $A_1 = A^\pi_2$
+%   and $B_1 = B^\pi_2$.
+% \end{claim}
+
+% \begin{definition}
+%   Let $f: A \rightarrow S$ and $g: B \rightarrow S$ be injections, with $A$
+%   and $B$ being finite sets. Then $(f,g)$ has \emph{type} $t= (t_1 , t_2, t_3)
+%   \in \mathbb{N}^3$ if $\vert A \vert = t_1$ and $\vert B \vert = t_2$ $\vert
+%   \{i \in A \cap B : f(i) = g(i)\} \vert = t_3$. We say that $\type (f,g) =
+%   t$.
+% \end{definition}
+
+% \begin{definition}
+%   Let $h \in H$ the \emph{type} of $h$ is the type of $(r_h, c_h)$. We denote
+%   the type of $h$ by $\type (h)$.
+% \end{definition}
+
+We now fix an injection $\eta : \consp(g) \rightarrow U$ and describe an
+approach for determining if $\eta \in EV_g$.
+
+Let $X$ be a set on which the left group action on $\sym_n$ is defined and $s
+\in X$. We denote $\vec{x}$ then $A_s = \{\vec{x} \in U^{\underline{[\vert
+    \sp(s) \vert ]}} : \eta \sim \vec{x} \cdot \vec{\consp}(s)^{-1} \}$, where
+$\vec{\consp}(s): [\vert \consp(s) \vert] \rightarrow \consp(s)$ maps $i \in
+[\vert \consp(s) \vert]$ to the $i$th element of $\consp(s)$. For $\vec{x} \in
+A_s$, we use $\vec{x}_s$ from here forward to denote $\vec{x} \cdot
+\vec{\consp(s)^{-1}}$.
+
+% Let $L(g)(i,j) = h \in H$, $\vec{x} \in A_i$ and $\vec{y} \in A_j$. Let
+% $\vec{r} \in ^{\underline{\consp(i)}}$ and $\vec{c}
+% \in\consp{j}^{\underline(\consp(j))}$. Suppose $(\vec{r}, \vec{c})$ has the
+% type of $(\vec{x}, \vec{y})$. Then we can define $(\vec{x}\vert \vec{y}):
+% \consp(i) \cup \consp(j) \rightarrow U$ by
+% \begin{align*}
+%   (\vec{x}_{\vec{r}} \vert \vec{y}_{\vec{c}}) (z) =
+%   \begin{cases}
+%     \vec{x} (\vec{r}^{-1}(z)) \text{ if } z \in \consp(i) \\
+%     \vec{y} (\vec{r}^{-1}(z)) \text{ if } z \in \consp(j). \\
+%   \end{cases}
+% \end{align*}
+
+This mapping allows us to combine two assignments into a single assignment. This
+will be useful when combining the row and column supports of a gate.
+
+% \begin{claim}
+%   Let $f: A \rightarrow S$ and $g B \rightarrow S$ be injections. Then $(f,g)$
+%   has the same type as $(A,B)$. It follows that if $h \in H$, and $(i,j) =
+%   L^{-1}(h)$,with $f \in A^r_i$ and $ g \in A^c_j$ then $h$ has the same type
+%   as $(f,g)$.
+% \end{claim}
+
+% For $(i,j) \in [a] \times [b]$ let $H_{i,j} = \{L(p,q): (p,q) \in \orb_r(i)
+% \times \orb_c(j)]\}$.
+
+% \begin{claim}
+%   For all $(i', j') \in \orb_r(i) \times \orb_c(j)$ and $\sigma \in
+%   \spstab{g}$, $(\sigma_r i', \sigma_cj') \in \orb_r(i) \times \orb_c(j)$.
+% \end{claim}
+
+% \begin{claim}
+%   For all $(i,j) \in [a] \times [b]$, $H_{i,j}$ is a union of orbits.
+% \end{claim}
+
+% \begin{lem}
+%   Let $(i,j) \in [a] \times [b]$. If $h, h' \in H_{i,j}$ and $h, h'$ are the
+%   same type then $h' \in \orb(h)$.
+% \end{lem}
+
+We now define a matrix that we later be shown to be definable in FPR. We then
+show that this matrix is row-column equivalent to $L^{\gamma}$, for any
+bijection $\gamma: U \rightarrow [n]$, and hence allowing us to determine the
+rank of the matrix input to $g$ in FPR.
+
+Let $R^{\min} = \{\min (\orb(\row(h))) : h \in H\}$ and $C^{\min} = \{ \min
+(\orb (\column(h))) : h \in H\}$ and let
 \begin{align*}
-    L^{EV}_\alpha (a,b):=
-    \begin{cases*}
-      1 & if $A_h \cap \EV_h \neq \emptyset$ 0 & otherwise
-    \end{cases*},
+  I = \{(i, \vec{x}): i \in R^{\min}, \vec{x} \in A_i\},
 \end{align*}
-  where for $h \in W_g, A_h:= \{\beta \in U^{\underline{\sp(h)}} \vert \alpha
-  \sim \beta\}$. Then $\alpha \in \EV_g$ iff $f(L^\EV_\alpha)$.
-\end{lem}
-\begin{proof}
-  First note that if $\alpha \in U^{\underbar{\sp{g}}}$ then $\alpha \in \EV_g$
-  iff we have that $C_n[\gamma \mathcal{A}](g)= f (L^0_\gamma) = 1$. Notice that
-  from Lemma \ref{} that this holds for any particular $\gamma$ iff it holds for
-  all such $\gamma$.
-
-  We now show that $L^\EV_\alpha = L^0_\gamma$, and so complete the proof.
-
-  Suppose for $(a,b) \in A \times B$ we have that $L^\EV_\alpha(a,b) = 1$. Let
-  $h:= L(g)(a,b)$. It follows that $A_h \cap \EV_h \neq \emptyset$, i.e there
-  exits $\beta \in \sp(h)$ such that $\beta \sim \alpha$ and there exists
-  $\gamma_h \in \Gamma(h)$ such that $\gamma^{-1}_h \sim \beta$. It follows from
-  transitivity and Lemma \ref{} that $\gamma_h \sim \alpha$ and so
-  $L^0_\alpha(a,b) = C_n[\gamma \mathcal{A}](h) = C_n[\gamma_h \mathcal{A}](h) =
-  1$.
-
-  Now suppose that $L^0_\gamma (a,b) = 1$
-\end{proof}
-
-\section{Translating to Formulas of FPC}
-Let $\mathcal{C} = (C_n)_{n \in \mathbb{N}}$ be a P-uniform family of
-polynomial-size symmetric $(\SB, \MB, \tau)$ circuits, and where $\MB$ is the
-rank basis. It remains to show that there is a formula $Q$ in the vocabulary
-$\tau \uplus \{\leq\}$ such that for any $n$ and $\tau$-structure $\mathcal{A}$
-with a universe $U$ of carnality $n$, the $q$-ary query defined by $C_n$ on the
-input $\mathcal{A}$ is defined by the formula $Q$ when interpreted in the
-structure $\mathcal{A}^\leq = \mathcal{A} \uplus \langle [n], \leq \rangle$.
-
-Since $\mathcal{C}$ is $P$-uniform, and from Lemmas \ref{} and \ref{} and the
-Immerman-Vardi theorem, we have an FP interpretation defining a rigid symmetric
-circuit with bijective labels equivalent to $C_n$ (which we also call $C_n$)
-over the the number sort of $\mathcal{A}^\leq$, where $\Phi = (\phi_G,\phi_W,
-\phi_\Omega, (\phi_s)_{s \in \SB \uplus \{rank\} \uplus \tau \uplus \{0,1\}},
-(\phi_{\and_R})_{R \in \tau}, \phi_L)$. We note that $Phi$ is a $t$-width
-interpretation over the universe $[n]$. So if $\mu, \nu, \nu_1, \ldots \in
-[n]^t$, the formulas are defined such that:
-
-\begin{itemize}
-\item $\phi_G(\mu)$ holds iff $\mu$ encodes a gate
-\item $\phi_W(\nu,\mu)$ holds iff $\nu$ and $\mu$ encode gates and if $g_{\nu}$
-  and $g_{\mu}$ are these two encoded gates respectively then $W(g_{\nu},
-  g_{\mu})$.
-\item $\phi_{\Omega}(\nu_1, \ldots, \nu_q, \mu)$ holds iff $\nu_1, \ldots, nu_q$
-  each encode numbers less than or equal to $[n]$ and $\Omega(\nu_1, \ldots,
-  \nu_q) = g_\mu$.
-\item For all $s \in \SB \uplus \{rank\} \uplus \tau \uplus \{0,1\}$ we have
-  that $\phi_s (\mu)$ holds iff $\mu$ encodes a gate such that $\Sigma(g_\mu) =
-  s$ (or, in the case that $s = \rank$, we require that $\Sigma(g_\mu)$ is a
-  rank symbol.)
-\item For all $R \in \tau$ with arity $r$ we have that $\phi_{\and_R}(\nu_1,
-  \ldots, \nu_r, \mu)$ holds iff $\nu_1 , \ldots , \nu_r$ encodes numbers less
-  than or equal to $[n]$, $\mu$ encodes a gate such that $\Sigma(g_\mu) = R$ and
-  $\Lambda_R(g_\mu) = (\nu_1, \ldots, \nu_r)$.
-\item $\phi_L(\nu, \mu, \nu_1, nu_2)$ holds iff $\nu$ and $\mu$ encode gates and
-  $\nu_1, \nu_2$ encode numbers, and $L(g_{\mu})(\nu_1,\nu_2) = g_\nu$. If
-  $\dom(L (g_\mu)) = [a] \times [b]$, then the encoding of $[a]$ and $[b]$ are
-  initial segments under the lithographically induced order. Moreover, the
-  encodings of $[a]$ and $[b]$ preserve the order relation.
-\end{itemize}
-
-From now on we use $\mu$ and $\nu$ to stand for $t$-length sequences encoding
-gates, and use $\nu_1, \ldots$ for sequences that encode numbers. We use $g_\mu$
-and $g_\nu$ for the gates encoded by these sequence, while simply identifying
-the sequence $\nu_i$ with the number it encodes.
-
-Using the Immerman-Vardi Theorem, we can define an FP($\leq$) formula
-$\rankpara$ such that $\langle [n], \leq\rangle \models \rankpara[g,p,u]$ iff
-$\langle [n], \leq\rangle \models \phi_G[g] \land \phi_{\rank}[g]$ and the rank
-gate $g$ (as per the interpretation) computes the rank over characteristic $p$
-and has threshold $u$.
-
-We can define FP($\leq$) formulas $\max_A$ and $\max_B$ such that $\langle [n],
-\leq \rangle \models \max_A[g, \nu_1]$ iff $\nu_1$ encodes $a$, where
-$\dom(L(g)) = [a]\times [b]$. Similarly, $\langle [n], \leq \rangle \models
-\max_B[g, \nu_1]$ iff $\nu_1$ encodes $b$ where $\dom(L(g)) = [a] \times [b]$.
-
-Again using Lemma \ref{} and the Immerman-Vardi theorem, we can construct a
-formula $\supp$ such $\langle [n], \leq \rangle \models \supp[g,u]$ iff $\langle
-[n], \leq \rangle \models \phi_G[g]$ and $u$ is in $sp(g)$. This formula can be
-used as in \cite{} to inductively define $\supp_i(g,u)$ for each $i \in [n]$
-which holds iff $u$ is the $i$th element of the support of $g$.
-
-Define the $\agree$ and $\theta_s$ formulas for all $s \in \SB \uplus \tau
-\uplus \{0,1\}$ as in \cite{}.
-
-Now we define the formula
+and
 \begin{align*}
-  \theta_{\rank}:= (\mu, \bar{x}) := \bigwedge_{1 \leq i < j \leq k} x_i
-  \neq x_j \wedge \forall \bar{y} ( [ \rank (x \leq \phi_{mr}, y \leq
-  \phi_{mc}, \pi \leq r). \theta^{'} ] ),
+  J = \{(j, \vec{y}): j \in C^{\min}, \vec{y} \in A_j \}.
 \end{align*}
+
+% \begin{align*}
+%   M ((i, \vec{x}), (j, \vec{y})) := \bigvee_{t \in \types} ((\vec{x},
+%   \vec{y}) \text{ has type } t) \land (\vec{x} | \vec{y}) \in \EV_{\mu_{i,j}(t)}.
+% \end{align*}
+
+Let $(i, \vec{x}) \in I$ and $(j, \vec{y}) \in J$.
+
+Let $u_1 , \ldots , u_{2k}$ be the first $2k$ elements of $[n] \setminus
+\consp(g)$ in the natural order on the structure. Then let
+\[r = \eta^{-1} (\img(\vec{x}) \cap \eta (\consp(g))) \cup
+  \{u_{\vec{x}^{-1}(a)}: a \in \img(x) \setminus \eta (\consp (g))\} \] and
+\[s = \eta^{-1} (y \cap \eta (\consp(g))) \cup (x \cap y) \cup \{ u_{k +
+    \vec{x}^{-1}(a)} : a \in y \setminus (x \cup \eta (\consp (g))) \}). \]
+Define
+\[
+  \vec{r} (a) =
+  \begin{cases}
+    \eta^{-1} (\vec{x} (a)) & a \in \vec{x}^{-1} (x \cap \eta (\consp(g))) \\
+    u_{a} & a \in \vec{x}^{-1} (x \setminus \eta(\consp(g)),
+  \end{cases}
+\]
+and
+\[
+  \vec{c} (a) =
+  \begin{cases}
+    \eta^{-1} (\vec{y} (a)) & a \in \vec{y}^{-1}(y \cap \eta (\consp (g))) \\
+    \vec{r} (a) & a \in \vec{y}^{-1} (x \cap y \setminus \eta (\consp (g))) \\
+    u_{k+a} & \text{otherwise}.
+  \end{cases}
+\]
+
+\begin{lem}
+  \label{lem:permutation_row-column}
+  There exists $\sigma_1, \sigma_2 \in \spstab{g}$ such that $\sigma_1 \cdot
+  \vec{\consp(i)} = \vec{r}$ and $\sigma_2 \cdot \vec{\consp(j)} = \vec{c}$.
+\end{lem}
+\begin{proof}
+  To be added from the book
+\end{proof}
+
+Let $h = L(g)(\sigma_1(i), \sigma_2 (j))$. Then we can define the matrix $M : I
+\times J \rightarrow \{0,1\}$ by
+
 \begin{align*}
-  \theta^{'}(a,b):= \exists \nu (W(\nu, \mu) \wedge \agree (\mu,\nu, \bar{x}, \bar{y}) \wedge \phi_L (\mu, \nu, a, b) \wedge V(\nu, y))
+  M((i , \vec{x}), (j, \vec{y})) := (\vec{x}_{\vec{r}} \vert \vec{y}_{\vec{c}}) \in EV_h.
 \end{align*}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\chapter{October 27th: Counting Gates Simulate Symmetric Gates}
-
-In this chapter we prove that symmetric circuits with majority gates are at
-least as powerful as symmetric circuits over any other Boolean basis consisting
-of symmetric functions.
-
-Recall the following that $\mathbb{B} = \{ \neg , \wedge , \lor \}$ and
-$\mathbb{B}_\maj = \{ \maj \} \cup \mathbb{B}$.
-
-Let $F: \{0,1\}^* \rightarrow \{0,1\}$ be a symmetric Boolean function. Since
-$F$ is symmetric we note that for a fixed size input the output of $F$ is
-entirely determined by the number of 1's in its input. Then let
-$c_{F}:\mathbb{N} \rightarrow 2^{\mathbb{N}}$ define a function where $c_{F}(n)$
-is the set of all $m \leq n$ such that for all $\vec{x} \in \{ 0,1 \}^n$ with
-$m$ 1's we have $F (\vec{x}) = 1$. Clearly a symmetric Boolean function $F$ is
-entirely determined by $c_{F}$.
-
-\begin{prop}
-  \label{prop:fuctions-maj}
-  There is a polynomial $p(k)$ such that for any symmetric function $F$ and a
-  given $k \in \mathbb{N}$ there is a circuit $C_k$ on $k$ inputs over the basis
-  $\mathbb{B}_\maj$ which is symmetric, constant depth and with width bounded by
-  $p(k)$.
-\end{prop}
-
-\begin{proof}
-  We define the circuit $C_k$ for inputs $\vec{x} = ( x_1, \ldots, x_k )$.
-
-  For $a \in \mathbb{N}$ we define a get $\countgate_a$ by
+It remains to show that $M \sim L^{\gamma}$ for some (and so all) bijections
+$\gamma: U \rightarrow [n]$.
+% \begin{definition}
+%   Let $M_1$ and $M_2$ be matrices over some field, with row and column indexes
+%   given by $(A_1, B_1)$ and $(A_2, B_2)$, respectively. We say that $M_1$ and
+%   $M_2$ are row-column equivalent iff there exists bijections $\alpha: A_1
+%   \rightarrow A_2$ and $\beta: B_1 \rightarrow B_2$ such that for all $(a,b)
+%   \in A_1 \times B_1$ we have that $M_1(a,b) = M_2 (\alpha (a), \beta (b))$.
+%   If $M_1$ and $M_2$ are row-column equivalent we say that $M_1 \sim M_2$.
+% \end{definition}
+
+% Fix $\gamma: U \rightarrow [n]$ such that $\gamma^{-1} \sim \eta$. We define
+% $L^\gamma: A \times B \rightarrow \{0,1\}$ by $L^\gamma(a,b) = C[\gamma
+% \mathcal{A}](L (a,b))$.
+% \\~\\
+% We note that, in fact, it is the choice of the assignment to the support of
+% $g$, i.e. $\eta$, that really matters in the sense that for any two global
+% assignments that agree on the support of $g$ will produce row-column
+% equivalent matrices. The following lemma formalises this observation.
+
+% \begin{lem}
+%   Let $g$ be a matrix-symmetric gate in $C_n$ with children $H$ and matrix
+%   labelling $L(g)$. Let $\eta \in U^{\consp(g)}$, and suppose $\gamma_1,
+%   \gamma_2: U \rightarrow [n]$ with $\gamma^{-1}_1 \sim \alpha$ and $
+%   \gamma^{-1}_2 \sim \alpha$. Let $A \times B = \dom (L(g))$.
+
+%   Then for an input structure $\mathcal{A}$, $L^{\gamma_1} \sim L^{\gamma_2}$.
+% \end{lem}
+% \begin{proof}
+%   We have that there exists a unique $\pi \in \sym_n$ such that $\pi \gamma_1
+%   = \gamma_2$. Moreover, since $\gamma^{-1}_1$ and $\gamma^{-1}_2$ are both
+%   consistent with $\eta$, it follows that $\pi$ must fix $\consp(g)$. Thus
+%   $L(g) \sim \pi L(g)$, and so there exists $(\alpha, \beta)$ such that $\pi
+%   L(g) = L(g) \cdot (\alpha, \beta)$.
+
+%   We then have that,
+%   \begin{align*}
+%     L^{\gamma_1} (a,b) &= C_n[\gamma_1 \mathcal{A}](L(g)(a,b))\\
+%                        & = C_n[\pi \gamma_1 \mathcal{A}][\pi L(g)(a,b)] \\
+%                        & = C_n[\gamma_2 \mathcal{A}][L(g)((\alpha, \beta)(a,b))]\\
+%                        & = L^{\gamma_2} ((\alpha, \beta) (a,b)),
+%   \end{align*}
+%   and it follows that $L^{\gamma_1} \sim L^{\gamma_2}$.
+% \end{proof}
+
+\begin{claim}
+  Let $\sigma \in \spstab{g}$, $\eta \in U^{\underline{\consp(g)}}$, $\gamma: U
+  \rightarrow [n]$ a bijection such that $\gamma^{-1} \sim \eta$. Then
+  $\gamma^{-1} \cdot \sigma \sim \eta$.
+\end{claim}
+\begin{proof}
+  Suppose $a \in \consp(g)$, then $\sigma (a) = a$ and so $\gamma^{-1} (\sigma
+  (a)) = \gamma^{-1} (a) = \eta (a)$.
+\end{proof}
+
+% \begin{claim}
+%   For $h \in H$ and $\sigma \in \stab(\consp (g))$, we have that
+%   $\vec{r}_{\sigma h_1} = \sigma \vec{r}_{h_1}$.
+% \end{claim}
+% \begin{proof}
+%   Proof in book
+% \end{proof}
+
+The following result shows that the action on the support of an object
+determines the action on that object.
+
+\begin{lem}
+  \label{lem:support_determine_action}
+  Let $\sigma, \sigma' \in \spstab{g}$, $a$ be an object on which on the action
+  of these two permutations is defined, and $\consp(a) \subset [n]$ be a support
+  of $a$. Then if $\sigma (\vec{\consp}(a)) = \sigma' (\vec{\consp}(a))$ then
+  $\sigma (a) = \sigma' (a)$.
+\end{lem}
+\begin{proof}
+  From $\sigma (\vec{\consp(a)}) = \sigma' (\vec{\consp(a)})$, it follows that
+  $\pi = (\sigma')^{-1} \sigma$ fixes $\vec{\consp}(a)$. Thus $\sigma (a) =
+  \sigma' (\pi (a)) = \sigma' (a)$.
+\end{proof}
+
+% \begin{lem}
+%   \label{lem:map_same_support_same_row}
+%   Let $\sigma, \sigma' \in \spstab{g}$ and suppose for some $i \in [a]$ we
+%   have that $\sigma (\vec{r}_i) = \sigma (\vec{r}_i)$. It follows that
+%   $\sigma_r (i) = \sigma'_r (i)$.
+% \end{lem}
+% \begin{proof}
+%   Let $pi = (\sigma^{-1} \sigma')_r \in G^r_i$. Then $ (\sigma^{-1} \sigma')_r
+%   (i) = \sigma^{-1}_r \sigma'_r (i) = i$, and so $\sigma_r (i) = \sigma'_r
+%   (i)$.
+% \end{proof}
+
+% Let $X$ be a set on which the left group action on which the left group action
+% of $\sym_n$ is defined and let $a \in X$. Let $\vec{x} \in A_i$ and $f \in
+% U^{\underline{[\vert \consp{a} \vert]}}$. Then $\Pi^{\gamma}_{\vec{x}_f} (a)$
+% is the action on $a$ defined by $\Pi^{\gamma}_{\vec{x}_f} (z) =
+% \gamma(\vec{x_f}(z))$, for all $z \in \consp (a)$. Lemma
+% \ref{lem:support_determine_action} tells us that this action is well defined.
+
+% Let $(i, j) \in A \times B$, let $\vec{x} \in A^r_i$ and $\vec{y} \in A^c_j$.
+% Define permutations $\Pi^{\gamma}_{\vec{x}}$ and $\Pi^{{\gamma},c}_{\vec{y}}$
+% such that $\Pi^{\gamma,r}_{\vec{x}}(\vec{r}_i) = \gamma (\vec{x})$ and
+% $\Pi^{\gamma,c}_{\vec{y}}(\vec{c}_j) = \gamma (\vec{y})$. From Lemma
+% \ref{lem:support_determine_action} we have that the choice of $\vec{x}$ and
+% $\vec{y}$ uniquely determine the mappings $\Pi^{\gamma,r}_{\vec{x}}(i)$ and
+% $\Pi^{\gamma,c}_{\vec{y}}(j)$
+
+Let $\alpha^{\gamma}: I \rightarrow A$ and $\beta^{\gamma}: J \rightarrow B$ be
+defined by $\alpha^{\gamma} (i, \vec{x}) = \Pi^{\gamma}_{\vec{x}_{i}}(i)$ and
+$\beta^{\gamma} (j, \vec{y}) = \Pi^{\gamma}_{\vec{y}_{j}}(j)$.
+
+We now show that $\alpha^{\gamma}$ and $\beta^{\gamma}$ act as witnesses to the
+row-column of equivalence of $M$ and $L^{\gamma}$. The following lemma proves
+surjectivity.
+
+\begin{lem} 
+  For any bijection $\gamma : U \rightarrow [n]$ both $\alpha^{\delta}$ and
+  $\beta^{\delta}$ are surjective.
+\end{lem}
+\begin{proof}
+  We show that $\alpha$ is surjective, with the same result for $\beta$
+  following similarly. Let $q \in A$ and let $i = \min (\orb (q))$. Then there
+  exists $\sigma \in \spstab{g}$ such that $\sigma i = q$. Let $\vec{x} =
+  \gamma^{-1} (\sigma(\vec{\consp}(i)))$. Notice that for $a \in \consp(i)$ we
+  have that $\vec{x}_i(a) = \gamma^{-1} (\sigma (a))$, and since $\gamma^{-1}
+  \cdot \sigma \sim \eta$, it follows that $\vec{x} \in A_i$.
+
+  For $a \in \consp(i)$ we have $\Pi^{\gamma}_{\vec{x}_i} (a) = \gamma
+  (\vec{x}_i(a)) = \gamma \cdot \gamma^{-1} \sigma (a) = \sigma (a)$. From Lemma
+  \ref{lem:support_determine_action} it follows that $\alpha(i, \vec{x}) = q$.
+\end{proof}
+
+The following lemma allows us to factor through permutations.
+\begin{lem}
+  \label{lem:alpha_and_gamma}
+  Let $(i,\vec{x}) \in I$ and $(j, \vec{y}) \in J$. Let $\gamma: U \rightarrow
+  [n]$ be a bijection such that $\gamma^{-1} \sim \eta$ and $\pi \in spstab{g}$.
+  Then $\pi \alpha^{\gamma}(i, \vec{x}) = \alpha^{\pi \gamma}(i, \vec{x})$ and
+  $\pi \beta^{\gamma}(j, \vec{y}) = \beta^{\pi \gamma}(j, \vec{y})$.
+\end{lem}
+\begin{proof}
+  We have that $\pi \alpha^{\gamma}(i, \vec{x}) = \pi
+  \Pi^{\gamma}_{\vec{x}_i}(i)$ and $(\pi
+  \Pi^{\gamma}_{\vec{x}_{i}}(\vec{\consp}(i)) = \pi \cdot \gamma (\vec{x}) =
+  \Pi^{\pi \gamma}_{\vec{x}_i}(\vec{\consp}(i))$. Since
+  $\Pi^{\gamma}_{\vec{x}_i}$ and $\Pi^{\pi \gamma}_{\vec{x}_i}$ are in
+  $\spstab{g}$, it follows from Lemma \ref{lem:support_determine_action}, that
+  $\pi \alpha^{\gamma}(i, \vec{x}) = \pi \Pi^{\gamma}_{\vec{x}_i} (i) = \Pi^{\pi
+    \gamma}_{\vec{x}_i}(i) = \alpha^{\pi \gamma}(i, \vec{x})$. Similarly, $\pi
+  \beta^{\gamma}(j, \vec{y}) = \beta^{\pi \gamma} (j, \vec{y})$.
+\end{proof}
+
+\begin{lem}
+  \label{lem:alpha_ind_gamma}
+  Let $(i,\vec{x}) \in I$ and $(j, \vec{y}) \in J$. Let $\gamma_1, \gamma_2: U
+  \rightarrow [n]$ be bijections such that $\gamma^{-1}_1 \sim \eta$ and
+  $\gamma^{-1}_2 \sim \eta$. Let $\mathcal{A}$ be a structure. Then
+  $C_n[\gamma_1 \mathcal{A}] (L(\alpha^{\gamma_1}(i, \vec{x}),
+  \beta^{\gamma_1}(j, \vec{y}))) = C_n[\gamma_2 \mathcal{A}]
+  (L(\alpha^{\gamma_2}(i, \vec{x}), \beta^{\gamma_2}(j, \vec{y})))$.
+\end{lem}
+\begin{proof}
+  We note that there exists $\pi \in \sym_n$ such that $\gamma_1 = \pi
+  \gamma_2$. Moreover, since $\gamma^{-1}_1$ and $\gamma^{-1}_2$ are both
+  consistent with $\eta$, it follows that $\pi \in \spstab{g}$. We then have
+  that
   \begin{align*}
-    &\countgate_a = \maj (x_1, \ldots, x_k, \underbrace {0, \ldots, 0}_{2a -
-      k}) \land \neg \maj (x_1, \ldots , x_k, \underbrace{0, \ldots,  0}_{2a - k + 2})\text{ if $a \geq \frac{k}{2}$,} \\
-    &\countgate_a = \maj (x_1, \ldots, x_k, \underbrace {1, \ldots, 1}_{x -
-      2a}) \land \neg \maj (x_1, \ldots , x_k, \underbrace{1, \ldots,
-      1}_{k - 2a -2}) \text{ if $a < \frac{k}{2}$. }
+    C_n[\gamma_1 \mathcal{A}](L(\alpha^{\gamma_1}(i, \vec{x}), \beta^{\gamma_1}(j,
+    \vec{y})) &= C_n[\pi \gamma_1 \mathcal{A}](\pi L(\alpha^{\gamma_1}(i, \vec{x}),
+                \beta^{\gamma_1}(j, \vec{y})) \\
+              &= C_n[\pi \gamma_1 \mathcal{A}](L(\pi
+                \alpha^{\gamma_1}(i, \vec{x}), \pi \beta^{\gamma_1}(j, \vec{y}))\\
+              &= C_n[\pi
+                \gamma_1 \mathcal{A}](L(\alpha^{\pi \gamma_1}(i, \vec{x}), \pi \beta^{\pi
+                \gamma_1}(j, \vec{y})\\
+              &= C_n[\gamma_2 \mathcal] (L(\alpha^{\gamma_2}(i,
+                \vec{x}), \beta^{\gamma_2}(j, \vec{y})))\\
+  \end{align*}The third equality follows from Lemma \ref{lem:alpha_and_gamma}.
+\end{proof}
+
+\begin{lem}
+  \label{lem:defining_h_from_IJ}
+  Let $(i, \vec{x}) \in I$ and $j, \vec{y} \in J$. Let $\vec{r}$ and $\vec{c}$
+  be described as above. Let $\sigma_1$ and $\sigma_2$ be as from Lemma
+  \ref{lem:permutation_row-colum}. Let $h = L(g) (\sigma_1 (i), \sigma_2 (j))$.
+  Then $\alpha^{\gamma'} (i, \vec{x}) = \row (h)$ and $\beta^{\gamma'}
+  (i,\vec{y}) = \column(h)$.
+\end{lem}
+\begin{proof}
+  $\alpha^{\gamma'}(i, \vec{x}) = \Pi^{\gamma'}_{\vec{x}_i} (i)$. It is
+  sufficient to show that for all $a \in sp(g)$, $\Pi^{\gamma}_{\vec{x}_i} (a) =
+  \sigma_1 (a)$. Note that $\Pi^{\gamma'}_{\vec{x}_i} (a) =
+  (\Pi^{\gamma}_{(\vec{x}_{\vec{r}} \vert \vec{y}_{\vec{c}})})^{-1} \gamma
+  (\vec{x}_i (a))$, and if $b = \sigma_1 (a)$ we have that $\gamma (\vec{x}_i
+  (a)) = \gamma (\vec{x} (\vec{\consp}(i)^{-1} (a))) = \gamma (\vec{x}
+  (\vec{\consp}(i)^{-1} (\sigma^{-1}_1 b))) = \gamma (\vec{x} ((\sigma_1 \cdot
+  \vec{\consp}(i))^{-1} (b))) = \gamma (\vec{x} (\vec{r}^{-1}(b))) =
+  \Pi^{\gamma}_{(\vec{x}_{\vec{r}} \vert \vec{y}_{\vec{c}})}(b)$. So
+  $\Pi^{\gamma'}_{\vec{x}} (a) = b = \sigma_1 (a)$. Similarly for
+  $\beta^{\gamma'}$.
+\end{proof}
+
+\begin{thm}
+  Let $\delta: U \rightarrow [n]$, $M$ is row-column equivalent to $L^{\gamma}$.
+  This equivalence is witnessed by $\alpha^{\gamma}$ and $\beta^{\gamma}$.
+\end{thm}
+\begin{proof}
+  We have that $\alpha^{\gamma}$ and $\beta^{\gamma}$ are surjective. Let
+  $\gamma' = (\Pi^{\gamma}_{(\vec{x}_{\vec{r}} \vert \vec{y}_{\vec{c}})})^{-1}
+  \gamma$.
+
+  \begin{align*}
+    M((i, \vec{x}), (j, \vec{y}))
+    &= (\vec{x}_{\vec{r}} \vert \vec{y}_{\vec{c}}) \in \EV_h \\
+    &= C_n[\gamma \mathcal{A}] (\Pi^{\gamma}_{(\vec{x}_{\vec{r}} \vert \vec{y}_{\vec{c}})} (h)) \\
+    &= C_n[\gamma' \mathcal{A}] (h) \\
+    &= C_n[\gamma' \mathcal{A}](L(\row(h), \column (h)))\\
+    &= C_n[\gamma' \mathcal{A}](L(\alpha^{\gamma'}(i, \vec{x}), \beta^{\gamma'}(j, \vec{y})))\\
+    &= C_n[\gamma \mathcal{A}](L(\alpha^{\gamma}(i, \vec{x}), \beta^{\gamma}(j, \vec{y}))y)\\
+    &= L^{\gamma}(\alpha^{\gamma}(i, \vec{x}), \beta^{\gamma}(j, \vec{y}))
   \end{align*}
-
-  Then let $g = \bigvee_{a \in c_{F_i}(k)}\countgate_a$ and let $C_{k}$ be the
-  circuit with input gates labeled by $\vec{x}$ and output gate $g$.
-
-  t is easy to see that $C_k$ is constant depth and it's width is a polynomial
-  in $k$. We have that in each layer of $C_{g'}$ each gate is connected to all
-  gates in the previous layer, and as such the circuit is symmetric.
-\end{proof}
-
-The above proposition has a straight forward application to circuit
-characterizations.
-
-\begin{prop}
-  Let $F = \{F_i : i \in I \}$ be a family of symmetric Boolean functions where
-  $F_i: \{0,1\}^* \rightarrow \{ 0,1 \}$.
-
-  Let $(C_n)_{n \in \mathbb{N}}$ be family of symmetric circuits over the
-  Boolean basis $\mathbb{B} \cup F$, where $C_n$ is a circuit on structures of
-  size $n$, and the size of each circuit in the family is bounded by some
-  function $f(n)$. Then there exists a polynomial $q(n)$ and a family of
-  symmetric circuits $(C_n')_{n \in \mathbb{N}}$ over $\mathbb{B}_\maj$, where
-  $C_n'$ is a circuit on structures of size $n$ and $\vert C_n' \vert \leq
-  q(f(n))$.
-\end{prop}
-
-\begin{proof}
-  From $C_n$ we construct $C_n'$ in the obvious way. For each gate $g \in C_n$
-  of type $F_i$ we have a symmetric circuit $C_g$ from Proposition
-  \ref{prop:function-maj} that computes the same function as $g$. Then let
-  $C_n'$ be $C_n$ but with each gate $g$ replaced by $C_g$. It is easy to see
-  that $C_n'$ is symmetric. We also have that each gate $g$ must have at most
-  $f(n)$ inputs, and the size of $C_g$ is bounded by $p(f(n))$. Thus the size of
-  $C_n'$ is bounded by $f(n)p(f(n))$.
-\end{proof}
-
-\chapter{October 29th: Symmetric Circuits and CPT}
-
-We already have that that the set of queries decidable by symmetric
-circuits (respectively with counting) is exactly the set of queries
-expressible in Fixed-Point Logic. We know that the CFI query is not
-expressible in FPC, and so there is no symmetric circuit that can
-compute the query.
-
-In our attempts to find a circuit characterisation of CPT, we might try and weaken the requirement of symmetry in our notion of symmetric circuits in order to express the CFI query (and perhaps the whole of CPT).
-One approach would be to weaken the requirement of having small orbits, to rather only having small orbits with respect to our particular input structure.
-We formalise this notion below.
-
-\begin{definition}
-Let $C$ be a circuit on structures of size $n$.
-Let $g$ be a gate in $C$ and let $X$ be a set of input strings closed under the action of the symmetric group.
-The $inv_X = \{ \sigma \in \sym_n : \forall x \in X g \circ H (x) = g \circ H (\sigma x)$.
-\end{definition}
-\begin{definition}
-  Let $(C_n)_{n \in \mathbb{N}}$ be a family of circuits. For any
-  finite structure $\mathcal{A}$ let $X_{\mathcal{A}}$ be the set of
-  all string encodings of $\mathcal{A}$. We say a circuit family has
-  small isomorphism orbits if there is a polynomial $p(n)$ such that
-  for any sufficiently large $n$, finite structure $\mathcal{A}$ of
-  cardinality $n$ and any $g \in C_n$ we have
-  $\vert S_n : \inv_{X_{\mathcal{A}}}(g) \vert \leq p(n)$.
-\end{definition}
-
-\begin{thm}
-  \label{thm:simple_group}
-  Let $n \in \mathbb{N}$, $n \geq 5$. Let $r \in \mathbb{N}$ such that
-  $r \leq n/2$. Suppose that $G$ is a subgroup of $\sym(n)$, then
-  there is a constant $k \in mathbb{N}$ such that for all $n \geq k$
-  if $\vert \sym(n):G \vert \leq {{n}\choose {r}}$ then there exists
-  $X \subseteq [n]$ with $\vert X \vert \leq r$ and such that
-  $\alt([n] \setminus X) \leq G$.
-\end{thm}
-
-The following result shows that even this weakened definition fails to
-capture CPT.
-\begin{thm}
-  There is no family of circuits with small isomorphism orbits that
-  expresses the CFI query.
-\end{thm}
-\begin{proof}
-  Let $(G_n)_{n \in \mathbb{N}}$ be a family of ordered graphs such that each $G_n$ has
-  odd and even CFI graphs $\mathfrak{G}$ and $\tilde{\mathfrak{G}}$ respectively, each of
-  cardinality $n$. Furthermore, suppose the CFI query for $(G_n)$ is not expressible in
-  FPC (the existence of such a family is guaranteed by
-  \cite{}). Suppose there exists a family of circuits $(C_n)_{n \in \mathbb{N}}$ with
-  small isomorphism orbits that decides the CFI query for $(G_n)$.
-  Then we have that $C_n(\mathfrak{G}) = 1$ and
-  $C_n(\tilde{\mathfrak{G}}) = 0$, and for any $g \in C_n$
-
-  \begin{align*}
-    \vert S_n : \inv_{X_{\mathcal{G}}}(g) \vert &\leq p(n),\\
-    \vert S_n : \inv_{X_{\tilde{\mathcal{G}}}}(g) \vert &\leq p(n)
-  \end{align*}.
-  Let $k$ be such that $p(n) \leq n^k$ for all sufficiently large $n$.
-Then we have that $p(n) \leq n^k \leq {{n}\choose{k+1}}$ for all sufficiently large $n$, and (again, taking $n$ large enough) we have that $k \leq n/2$.
-Taking $n$ larger than the constant in Theorem \ref{thm:simple_group} it follows that there exists an $X_1, X_2 \subseteq [n]$ such that $\vert X_1 \vert, \vert X_2 \vert \leq k$ and $\alt ([n] \setminus X_1) \subseteq  \inv_{X_{\mathfrak{G}}}(g)$, $\alt ([n] \setminus X_2) \subseteq  \inv_{X_{\tilde{\mathfrak{G}}}}(g)$.
-It follows that
-  \begin{align*}
-    \alt ([n] \setminus (X_1 \cup X_2)) &\subseteq \alt ([n] \setminus X_1) \cap \alt ([n] \setminus X_2)\\
-                                        &\subseteq \inv_{X_{\mathfrak{G}}}(g) \cap \inv_{X_{\tilde{\mathfrak{G}}}}(g) \\
-                                        &\subseteq \inv_{X_{\mathfrak{G} \cup \tilde{\mathfrak{G}}}}(g) =  \inv_{CFI(G)}(g),
-  \end{align*}
-  where $CFI(G)$ is set of all encodings of all CFI graphs of $G_n$.
-
-  We then have that
-  \begin{align*}
-    \vert S_n : \inv_{CFI(G)}(g) \vert \leq \vert S_n : \alt ([n] \setminus (X_1 \cup X_2)) \leq  \frac{n!}{(n-2k)!/2} \leq n^{2k+1},
-  \end{align*}
-  with the last inequality following for large enough $n$. We thus
-  have from Theorem \ref{} that there is a symmetric circuit $D_n$
-  that decides the CFI problem for $G_n$, and hence a family $(D_n)$
-  that decides the CFI problem for the family of graphs $(G_n)$. From
-  the theorem of Dawar et al. \cite{}, it follows that there is as
-  formula of FPC that decides the CFI query for $(G_n)$ contradicting
-  our assumption.
-\end{proof}
+  The second equality follows from Lemma \ref{}. The fifth equality follows from
+  Lemma \ref{lem:defining_h_from_IJ}. The sixth equality follows from Lemma
+  \ref{lem:alpha_ind_gamma}.
+
+\end{proof}
+
+\section{FPR Formulas}
+
+% \begin{lem}
+%   Let $(i, \vec{x}) \in I$ and $(j, \vec{y}) \in J$. Let $h \in H$ such that
+%   $\row (h) \in \orb_r (i)$, $\column (h) \in \orb_c(j)$, and $\type(h) =
+%   \type(\vec{x}, \vec{y})$. Let $\gamma: U \rightarrow [n]$ be a bijection and
+%   $\mathcal{A}$ a structure. Then $C_n[\gamma
+%   \mathcal{A}](\Pi^{\gamma}_{\vec{x} \vert \vec{y}} (h)) = C_n[\gamma
+%   \mathcal{A}](L(\alpha^{\gamma}(i, \vec{x}), \beta^{\gamma}(j, \vec{y})))$.
+% \end{lem}
+% \begin{proof}
+%   Let $\gamma' = (\Pi^{\gamma}_{\vec{x} \vert \vec{y}})^{-1} \gamma$. First we
+%   show that $h = L(\alpha^{\gamma'}(i, \vec{x}), \beta^{\gamma'}(j,
+%   \vec{y}))$. Notice that $\Pi^{\gamma'}_{\vec{x}}(\vec{r}_i) =
+%   \gamma'(\vec{x}) = (\Pi^{\gamma}_{\vec{x} \vert \vec{y}})^{-1} \gamma
+%   (\vec{x}) = \vec{r}_h$. But $\row(h) \in \orb_r(i)$ and so there exists
+%   $\vec{x}' \in A^r_i$ such that $\Pi^{\gamma'}_{vec{x}'}(i) = \row{h}$ From
+%   Lemma \ref{lem:support_determine_action} it follows that $\row (h) =
+%   \Pi^{\gamma'}_{\vec{x}}(i) = \alpha^{\gamma'}(i, \vec{x})$. Similarly, we
+%   can show that $\column(h) = \beta^{\gamma'}(j, \vec{y})$. It follows that $h
+%   = L(\alpha^{\gamma'}(i, \vec{x}), \beta^{\gamma'}(j, \vec{y}))$, and so
+%   \begin{align*}
+%     C_n[\gamma \mathcal{A}](\Pi^{\gamma}_{\vec{x}
+%     \vert \vec{y}} (h))
+%     &= C_n[\gamma' \mathcal{A}](h)\\
+%     &= C_n[\gamma' \mathcal{A}](L(\alpha^{\gamma'}(i, \vec{x}), \beta^{\gamma'}(j, \vec{y})))\\
+%     &= C_n[\gamma \mathcal{A}](L(\alpha^{\gamma}(i, \vec{x}), \beta^{\gamma}(j, \vec{y}))).
+%   \end{align*}
+%   The final equality follows from Lemma \ref{lem:alpha_ind_gamma}.
+% \end{proof}
+
+% \chapter{New Stuff}
+% Let $x,y \subset U$ such that $\vert x \vert = \vert y \vert = k \in
+% \mathbb{N}$. Let $\vec{x}: [k] \rightarrow x$ and $\vec{y}: [k] \rightarrow y$
+% be bijections.
+
+% We need to define $r, c \subset [n]$ such that $\vert r \vert = \vert c \vert
+% = k$ and there exists bijections $\vec {r}: [k] \rightarrow r$ and $\vec{c}:
+% [k] \rightarrow c$.
+
+% Let $u_1 , \ldots , u_{2k}$ be the first $2k$ elements of $[n] \setminus
+% \SP(g)$ in order. Then let
+% \[r = \eta^{-1} (x \cap \eta (\SP(g))) \cup \{u_{\vec{x}^{-1}(a)}: a \in x
+%   \setminus \alpha (\SP (g))\} \] and
+% \[s = \eta^{-1} (y \cap \eta (\SP(g))) \cup (x \cap y) \cup \{ u_{k +
+%   \vec{x}^{-1}(a)} : a \in y \setminus (x \cup \alpha (\SP (g))) \}). \]
+% Define
+% \[
+%   \vec{r} (a) =
+%   \begin{cases}
+%     \eta^{-1} (\vec{x} (a)) & a \in \vec{x}^{-1} (x \cap \eta (\SP(g))) \\
+%     u_{a} & a \in \vec{x}^{-1} (x \setminus \eta(\SP(g)),
+%   \end{cases}
+% \]
+% and
+
+% \[
+%   \vec{c} (a) =
+%   \begin{cases}
+%     \eta^{-1} (\vec{y} (a)) & a \in \vec{y}^{-1}(y \cap \eta (\SP (g))) \\
+%     \vec{r} (a) & a \in \vec{y}^{-1} (x \cap y \setminus \eta (\SP (g))) \\
+%     u_{k+a} & \text{otherwise}.
+%   \end{cases}
+% \]
+
+% \begin{lem}
+%   $x_r \sim \eta$ and $x_c \sim \eta$
+% \end{lem}
+
+% \begin{lem}
+%   $\SP(g) \cap \SP(i) = \SP(g) \cap r$ and $\SP (g) \cap SP (j) = \SP (g) \cap
+%   c$.
+% \end{lem}
+
+% Let $(\vec{x}, \vec{y})_{\vec{r}, \vec{c}}: r \cup c \rightarrow U$ be defined
+% by
+% \[
+%   (\vec{x}, \vec{y})_{\vec{r}, \vec{c}}(a) =
+%   \begin{cases}
+%     \vec{x}(\vec{r}^{-1}(a)) & a \in r \\
+%     \vec{y}(\vec{c}^{-1}(a)) & a \in c
+%   \end{cases}
+% \]
+
+% This function is well defined.
+
+% % \begin{lem}
+% %   Let $r, c \subset U$ and let $r_1, r_2 : [k_1] \rightarrow r$ and $c_1, c_2 :
+% %   [k_2] \rightarrow c$ then $\type(\vec{r}_1, \vec{c}_1) = \type (\vec{r}_2 ,
+% %   \vec{c}_2)$.
+% % \end{lem}
+
+% \begin{lem}
+%   $(\vec{x}_{\vec{r}} \vert \vec{y}_{\vec{y}}) \sim \eta$
+% \end{lem}
+
+% \begin{lem}
+%   There exists $\sigma_1, \sigma_2 \in \spstab{g}$ such that $\sigma_1 \cdot
+%   \vec{\consp(i)} = \vec{r}$ and $\sigma_2 \cdot \vec{\consp(j)} = \vec{c}$.
+% \end{lem}
+
+% \begin{lem}
+%   Let $(i, \vec{x}) \in I$ and $j, \vec{y} \in J$. Let $\vec{r}$ and $\vec{c}$
+%   be described as above. Let $\sigma_1$ and $\sigma_2$ be as from Lemma
+%   \ref{}. Let $h = L(g) (\sigma_1 (i), \sigma_2 (j))$. Then $\alpha^{\gamma'}
+%   (i, \vec{x}) = \row (h)$ and $\beta^{\gamma'} (i,\vec{y}) = \column(h)$.
+% \end{lem}
+% \begin{proof}
+%   $\alpha^{\gamma'}(i, \vec{x}) = \Pi^{\gamma'}_{\vec{x}} (i)$. It is
+%   sufficient to show that for all $a \in sp(g)$, $\Pi^{\gamma}_{\vec{x}} (a) =
+%   \sigma_1 (a)$. Note that $\Pi^{\gamma'}_{\vec{x}_i} (a) =
+%   (\Pi^{\gamma}_{(\vec{x}, \vec{y})_{\vec{r}, \vec{c}}})^{-1} \gamma
+%   (\vec{x}_i (a))$, and if $b = \sigma_1 (a)$ we have that $\gamma (\vec{x}_i
+%   (a)) = \gamma (\vec{x} (\vec{\consp}(i)^{-1} (a))) = \gamma (\vec{x}
+%   (\vec{\consp}(i)^{-1} (\sigma^{-1}_1 b))) = \gamma (\vec{x} ((\sigma_1 \cdot
+%   \vec{\consp}(i))^{-1} (b))) = \gamma (\vec{x} (\vec{r}^{-1}(b))) =
+%   \Pi^{\gamma}_{(\vec{x}, \vec{y})_{\vec{r}, \vec{c}}}(b)$. So
+%   $\Pi^{\gamma'}_{\vec{x}} (a) = b = \sigma_1 (a)$. Similarly for
+%   $\beta^{\gamma'}$.
+% \end{proof}
+
+% \begin{lem}
+%   Let $(i, \vec{x}) \in I$ and $(j, \vec{y}) \in J$. There exists $h \in H$
+%   such that $h$ has type $(\vec{x}, \vec{y})$ and for any bijection $\gamma: U
+%   \rightarrow [n]$ and structure $\mathcal{A}$ then $C_n[\gamma \mathcal{A}]
+%   (\Pi^{\gamma}_{(\vec{x} \vert \vec{y})_{h}}) = C_n [\gamma
+%   \mathcal{A}](L(\alpha^{\gamma}(i, \vec{x}), \beta^{\gamma}(j, \vec{y})))$.
+% \end{lem}
+
+% \begin{lem}
+%   Let $h \in H$ and $\vec{z} \in A_h$ and $\Pi^{\delta}_h$ be a permutation
+%   such that $\Pi^{\delta}_{\vec{z}}(a) = \delta(\vec{z}(a))$ for all $a \in
+%   \sp(h)$. Then $C_n[\gamma \mathcal{A}](\Pi^{delta}_{\vec{z}} (h))$ iff
+%   $\vec{z} \in \EV_h$.
+% \end{lem}
+
+% \begin{thm}
+%   The matrix $M$ is equivalent to $L$.
+% \end{thm}
+
+\chapter{Concluding Remarks}
+\bibliographystyle{plain} \bibliography{references}
 \end{document}

### 2017-07-26 sections/background.tex
26/07/2017

--- 2016-12-14 paper.tex
@@
-\documentclass[12pt]{report}
+\documentclass[../paper.tex]{subfiles}
 
-% This first part of the file is called the PREAMBLE. It includes
-% customizations and command definitions. The preamble is everything
-% between \documentclass and \begin{document}.
+\begin{document}
+In this section we present basic background on logics, first-order structures,
+and symmetric circuits.
 
-\usepackage[margin=1in]{geometry} % set the margins to 1in on all sides
-\usepackage{graphicx} % to include figures
-\usepackage{amsmath} % great math stuff
-\usepackage{amsfonts} % for blackboard bold, etc
-\usepackage{amsthm} % better theorem environments
+\subsection{Logic and Structures}
+A \emph{relational vocabulary} (usually denoted by $\tau$) is a finite sequence
+of relation symbols $R_1, \ldots, R_k$, such that for all $i \in [k]$, $R_i$ has
+arity of $r_i \in \nats$.
 
-% various theorems, numbered by section
+A $\tau$-structure $\mathcal{A}$ is a tuple $\langle U, R^{\mathcal{A}}_1 ,
+\ldots , R^{\mathcal{A}}_k \rangle$, where $U$ is a set and called the
+\emph{universe} of $\mathcal{A}$ and for all $i \in [k]$ the relations
+$R^{\mathcal{A}}_i \subseteq U^{r_i}$. The elements of $U$ are called the
+elements of $\mathcal{A}$. A \emph{multi-sorted} structure is one whose universe
+is a disjoint union, where each set in the union is called a \emph{sort}. The
+size of a structure is the cardinality of its universe.
 
-\newtheorem{thm}{Theorem} \newtheorem{claim}{Claim}
-\newtheorem{remark}{Remark} \newtheorem{definition}{Definition}
-\newtheorem{lem}[thm]{Lemma} \newtheorem{prop}[thm]{Proposition}
-\newtheorem{cor}[thm]{Corollary} \newtheorem{conj}[thm]{Conjecture}
+All structures in this paper are finite.
 
-\DeclareMathOperator{\id}{id}
+\subsection{First Order, Fixed-Point, Counting}
 
-\newcommand{\bd}[1]{\mathbf{#1}} % for bolding symbols
-\newcommand{\RR}{\mathbb{R}} % for Real numbers
-\newcommand{\ZZ}{\mathbb{Z}} % for Integers
-\newcommand{\MB}{\mathbb{B}_{\matsym}} % for Integers
-\newcommand{\SB}{\mathbb{B}_{\sym}} % for Integers
-\newcommand{\col}[1]{\begin{matrix} #1 \end{matrix} \right]}
-\newcommand{\comb}[2]{\binom{#1^2 + #2^2}{#1+#2}}
-\newcommand{\stab}{\text{\textbf{Stab}}}
-\newcommand{\setstab}{\text{\textbf{SetStab}}}
-\newcommand{\matstab}{\text{\textbf{MatStab}}}
-\newcommand{\inv}{\text{\textbf{inv}}}
-\newcommand{\aut}{\text{\textbf{Aut}}}
-\newcommand{\kernal}{\text{\textbf{ker}}}
-\newcommand{\alt}{\text{\textbf{Alt}}}
-\newcommand{\sym}{\text{\textbf{Sym}}}
-\newcommand{\rank}{\text{\textbf{rk}}}
-\newcommand{\orb}{\text{\textbf{Orb}}}
-\newcommand{\SP}{\text{\textbf{SP}}}
-\newcommand{\maj}{\text{\textbf{Maj}}}
-\newcommand{\dom}{\text{\textbf{Dom}}}
-\newcommand{\child}{\text{child}}
-\newcommand{\countgate}{\text{count}}
-\newcommand{\agree}{\text{AGREE}}
-\newcommand{\supp}{\text{SUPP}}
-\newcommand{\rankparam}{\text{PARAM}}
+Let $\FO(\tau)$ denote \emph{first order logic} with respect to the vocabulary
+$\tau$. \emph{Fixed-Point Logic} is the extension of $\FO(\tau)$ with an
+inflationary fixed-point operator (see \cite{} for details). For logic
+$\mathcal{L}$, a formula $\phi \in \mathcal{L}(\tau)$, $x$ a $k$-length tuple of
+variables, $\mathcal{A}$ a (finite) structure, and $a \in U^k$, we have that
+$\phi (x)$ denotes that the variables in $x$ are free in $\phi$ and we write
+$\mathcal{A} \models_{\mathcal{L}} \phi[a]$ iff the the formula $\phi$ is true
+in $\mathcal{A}$ with respect to $\mathcal{L}$ with the variables $x$ assigned
+to $a$. The context usually makes the logic obvious, and in that case we usually
+drop the subscript.
 
-\newcommand{\Alpha}{A}
-\newcommand{\matsym}{\text{\textbf{MatSym}}}
-\begin{document}
+We also recall the definition of \emph{fixed-point logic with counting} $\FPC$,
+an extension $\FP$ with counting quantifiers. For a structure $\mathcal{A}$,
+Formulas of this logic are evaluated over a structure $\mathcal{A}$ by extending
+that structure to $\mathcal{A}^\leq$, a two sorted extension of $\mathcal{A}$ by
+an ordered number sort $\{1, \ldots, \vert U\vert \}$. Variables are taken to be
+either point variables, ranging over $U$ or number variables ranging over
+$[\vert U \vert]$. The counting quantifiers are of the form $\#_x$, where $x$ is
+either a point or number variable and for $\phi(x) \in \FPC(\tau)$, $\#_x
+\phi(x)$ is a term denoting the element of the number sort corresponding to
+$\vert \{a \in \mathcal{A} | \mathcal{A} \models \phi[a]\}\vert$. Note
+additionally that $k$-tuples of number variables can be used to encode numbers
+in $\FPC$ of size up to $\vert U\vert^k$. For more details on $\FPC$ please see
+\cite{}.
 
-\nocite{*}
+\subsection{Rank Logic}
+In this paper we use the definition of $\FPR$ given by Grad\"{e}l and Pakusa
+\cite{}, an strictly more expressive extension of the rank logic introduced by
+Dawar et. al. cite{}. We briefly define this logic here. For more detail please
+see \cite{}. $\FPR$ is an extension of $\FPC$ with rank operators, which we now
+define.
 
-\title{Circuits}
+Let $\phi (\vec{x}, \vec {\nu} \leq \vec{t}, \vec{y}\vec{\mu} \leq \vec{s})$ be
+a numeric term, where $\vec{x}$ and $\vec{y}$ are tuples of variables ranging
+over the universe of the structure, $\vec{\nu}$ and $\vec{\mu}$ are tuples of
+variables ranging over the number type, and $\vec{s}$ and $\vec{t}$ are tuples
+of closed numeric terms that bound the range of $\vec{\nu}$ and $\vec{\mu}$
+respectively. Then let $\mathcal{A}$ be a structure and let
+$\mathbb{N}^{\leq\vec{t}} := \{\vec{n} \in \mathbb{N}^{\vert \vec{v} \vert}: n_i
+\leq t^{\mathcal{A}}_i\}$, and let $\mathbb{N}^{\leq \vec{s}}$ be defined
+similarly. Let $I:= A^{\vert \vec{x} \vert} \times \mathbb{N}^{\leq \vec{t}}$
+and $J := A^{\vert \vec{y} \vert} \times \mathbb{N}^{\leq \vec{s}}$ Then let
+$M^{\mathcal{A}}_\phi : I \times J \rightarrow \mathbb{N}$ be defined by
+$M^{\mathcal{A}}_\phi (\vec{a}\vec{n}, \vec{b}\vec{m}):=
+\phi^{\mathcal{A}}(\vec{a}\vec{n},\vec{b}\vec{m})$.
 
-\author{Gregory Wilsenach \\ 
-Computer Laboratory \\
-University of Cambridge}
+The rank operator is then defined as $[rk (\vec{x}, \vec {\nu} \leq \vec{t},
+\vec{y}\vec{\mu} \leq \vec{s}, \pi \leq r). \phi]$, where $\pi$ is a variable
+ranging over the number sort and $r$ is a closed numeric term that bounds $\pi$.
+The value of the rank term for a structure $\mathcal{A}$ and an assignment $\pi
+\mapsto p$, where $p$ is prime, is given by the rank of $M^{\mathcal{A}}_\phi$
+mod $p$, as understood as a matrix over $\mathbb{F}_p$.
 
-\maketitle
-
-\tableofcontents
-
-\chapter{Introduction}
-
-\chapter{Background}
-
-\chapter{Symmetric Circuits}
-
-\chapter{Extending Symmetric Circuits}
-
-\chapter{Matrix-Symmetric Circuits}
-
-The symmetric circuits of Anderson and Dawar \cite{} have been shown to express
-$FPC$.
-
-In this section we develop a notion of a matrix-symmetric circuit, an extension
-of the symmetric circuit defined by Anderson and Dawar \cite{}. This is my
-latest version of the support and circuit capturing result.
-
-\section{}
-
-\section{Circuits and Symmetry}
-\begin{definition}
-  Let $A$ and $B$ be sets, say that a function $f: \{ 0,1 \}^{A \times B}
-  \rightarrow \{ 0,1 \}$ is matrix-symmetric if for any $\omega: A \times B
-  \rightarrow \{0, 1\}$ and $(\alpha, \beta) \in \sym_A \times \sym_B$ we have
-  $f((\alpha, \beta)\cdot \omega) = f (\omega)$.
-  \\
-  A function $f: \{0,1\}^* \rightarrow \{0,1\}$ is matrix-symmetric iff for any
-  two finite sets $A$, $B$ we have that that $f|_{A \times B}$ is
-  matrix-symmetric (where $f|_{A \times B}$ is the restriction of the function
-  $f$ to inputs sequences of size $\vert A \times B \vert$ and where elements of
-  the input sequence are labelled by elements of $A \times B$).
-\end{definition}
-
-\section{The Support Theorem}
-
-Without a loss of generality we assume that $A$ and $B$ are always initial
-segments of the natural numbers.
-
-% Let $C$ be a circuit over some Boolean basis. For each gate $g \in C$ we
-% associate a relation $\omega_g$ (or just $\omega$ when the context makes it
-% clear). We say a gate is symmetric if that relation
-
-% So far we have defined a circuit over a Boolean basis where the circuit
-% elements all compute symmetric functions. The definition of an induced
-% automorphism only makes. As such, we begin by augmenting the definition of a
-% circuit and automorphism.
-
-\begin{definition}[Circuits on Structures]
-  For $\mathbb{B}_{\sym}$ a basis of Boolean symmetric functions,
-  $\mathbb{B}_{\matsym}$ a basis of Boolean matrix-symmetric functions and
-  $\tau$ a set of relation symbols, we define a $(\mathbb{B}_\sym,
-  \mathbb{B}_\sym, \tau)$-circuit $C_n$ computing a $q$-ary query $Q$ is a
-  structure $\langle G, W, \Omega, \Sigma, \Lambda, L\rangle$.
-  \begin{itemize}
-  \item $G$ is called the set of gates of $C_n$ and $\vert C_n \vert := \vert G
-    \vert$.
-  \item $W \subseteq G \times G$, where $W$ is called the wires of the circuit.
-    $(G,W)$ must be a directed acyclic graph. For $g \in G$ we $H_g := \{ h \in
-    C_n : W(h,g)\}$ be the set of children of $g$.
-  \item $\Omega$ is an injective function from $[n]^q$ to $G$. The gates in the
-    image of $\Omega$ are called the output gates. When $q = 0$, $\Omega$ is a
-    constant function mapping to a single output gate.
-  \item $\Sigma$ is a function from $G$ to $\mathbb{B}_\sym \uplus
-    \mathbb{B}_\matstab \uplus \tau \uplus \{0,1\} $ which maps input gates to
-    $\tau \uplus \{0,1\}$ and where $\Sigma^{-1} (0) \leq 1$ $\Sigma^{-1} (1)
-    \leq 1$ and the internal gates get mapped into $\mathbb{B}_\sym \uplus
-    \mathbb{B}_\matstab$. Gates mapped to $\tau$ are called relational gates and
-    gates mapped to 1 or 0 are called constant gates.
-  \item $\Lambda$ is a sequence of injective functions $(\Lambda_R)_{R \in
-      \tau}$ where for each $R \in \tau$, $\Lambda_R$ maps each relational gate
-    $g$ with $R = \Sigma (g)$ to the tuple $\Lambda_R (g) \in [n]^r$, where $r$
-    is the arity of the symbol $R$. When no ambiguity arises we write $\Lambda
-    (g)$ for $\Lambda_R (g)$.
-  \item $L$ is the set of labelings of $C_n$. Let $g \in G$ be an internal gate
-    and $H$ be the children of $g$. Then let $S$ be a set where $\{0,1\}^S =
-    \dom(\Sigma (g))$. Then $L$ is a function that assigns to $g$ an onto
-    function $\omega_g:S \rightarrow H$. We call this the matrix labelling of
-    $g$.
-  \end{itemize}
-\end{definition}
-
-% \begin{definition}
-%   let $C = \langle G, W, \Omega, \Sigma, \Lambda, L\rangle$ be a
-%   $(\mathbb{B}_\sym, \mathbb{B}_\sym, \tau)$-circuit, then take $g_1,g_2 \in
-%   G$ such that $\Sigma (g_1) \Sigma(g_2) \in \mathbb{B}_\matsym$.
-
-\begin{definition}
-  Let $\omega_1: A \times B \rightarrow H$ and $\omega_2: A' \times B'
-  \rightarrow H'$ define the equivalence relation $\sim$ as $\omega_1 \sim
-  \omega_2$ iff $\omega_1$ and $\omega_2$ have the same domain and co-domain and
-  there exists $(\alpha, \beta) \in \sym_A \times \sym_B$ and for all $(a,b) \in
-  A \times B$ we have $\omega_1 = \omega_2 \circ (\alpha, \beta)$.
-\end{definition}
-
-% \begin{definition}
-%   Let $\omega_1: A \rightarrow H$ and $omega_2:A' \rightarrow H'$. Define the
-%   equivalence relation $\sim$ as $\omega_1 \sim \omega_2$ iff $\omega_1$ and
-%   $\omega_2$ have the same domain and co-domain, and
-% \end{definition}
-
-\begin{definition}[Automorphism]
-  let $C = \langle G, W, \Omega, \Sigma, \Lambda, L\rangle$ be a
-  $(\mathbb{B}_\sym, \mathbb{B}_\sym, \tau)$-circuit computing at $q$-ary query
-  on structures of size $n$. Let $\sigma \in \sym_n$ and $\pi: G \rightarrow G$
-  be a bijection such that
-  \begin{itemize}
-  \item for all gates $g, h \in G$, $W(g,h)$ iff $W(\pi g, \pi h)$,
-  \item for all output tuples $x \in [n]^q$, $\pi \Omega (x) = \Omega (\sigma
-    x)$,
-  \item for all gates $g \in G$, $\Sigma (g) = \Sigma (\pi g)$, and
-  \item for each relational gate $g \in G$, $\sigma \Lambda (g) = \Lambda (\pi
-    g)$
-  \item for each internal gate $g$ if $\Sigma (g) \in \mathbb(B)_\matsym$. Then
-    we have that $L(\pi g) \sim \pi \circ L(g)$.
-  \end{itemize}
-\end{definition}
-
-\begin{remark}
-  I also need a new notion of robustness here in order to collapse gates that
-  have the same children and equivalent labelings are properly regarded as being
-  the same gate.
-\end{remark}
-% \begin{definition}
-%   Let $C$ be a circuit, $g$ be a gate in $C$, $H$ be $g$'s set of children and
-%   let $\omega: A \times B \rightarrow H$ be a surjection, where $A$ and $B$
-%   are sets and $g$ takes $\vert A \vert \cdot \vert B \vert$ inputs. Call such
-%   an $\omega$ a matrix labeling for $g$.
-% \end{definition}
-
-% \begin{definition}
-%   Let $C$ be a circuit and $g_1$ and $g_2$ be gates in $C$. Let $\sigma \in
-%   \sym_n$ be a permutation such
-% \end{definition}
-
-\begin{definition}
-  Let $\omega$ be a matrix labeling for $g$. Define the matrix stabilizer for
-  $\omega$, denoted by $\matstab(\omega)$, to be the set of all $\sigma \in
-  \sym_n$ such that $\sigma H = H$ and there exists $(\alpha, \beta) \in \sym_A
-  \times \sym_B$ such that for all $(i,j) \in A \times B$ we have that $\omega
-  (\alpha i, \beta j) = \sigma \omega (i,j)$.
-\end{definition}
-
-\begin{definition}
-  Let $g$ be a gate with matrix labeling $\omega$, $h,h' \in H$ and $\sigma \in
-  \sym_n$. We say that a pair $(h, h')$ is compatible with $(\sigma, \omega)$ if
-  $\sigma h, \sigma h' \in H$ and there exists $(\gamma_1, \gamma_2),
-  (\gamma_1', \gamma_2') \in \sym_A \times \sym_B$ s.t.
-  \begin{align*}
-    &(\gamma_1, \gamma_2) \cdot \omega^{-1} (h) = \omega^{-1}(\sigma h), \text{ and} \\ 
-    &(\gamma_1', \gamma_2') \cdot \omega^{-1} (h') = \omega^{-1}(\sigma h'),
-  \end{align*}
-  and for all $(i,j) \in \omega^{-1}(h)$, $(i',j') \in \omega^{-1}(h')$ we have
-  that
-  \begin{align*}
-    &i =i' \implies \gamma_1(i) = \gamma_1'(i'), \text{ and} \\
-    &j =j' \implies \gamma_2(j) = \gamma_2'(j').
-  \end{align*}
-
-\end{definition}
-
-\begin{lem}
-  Let $g$ be a gate, $\omega$ be a matrix labeling of $g$, $\sigma \in \sym_n$.
-  Then $\sigma \in \matstab(\omega)$ iff for all $h,h' \in H$ we have that
-  $(h,h')$ is compatible with $(\sigma, \omega)$.
-\end{lem}
-
-\begin{proof}
-  $`\Rightarrow'$: We have that $\sigma \in \matstab(\omega)$ and so there
-  exists $(\alpha, \beta) \in \sym_A \times \sym_B$ such that for all $(i,j) \in
-  A \times B$ we have $\sigma \omega (i,j) = \omega (\alpha i, \beta j)$. From
-  compatibility we have that $h,h' \in H$ Let $h, h' \in H$ . Let $(\gamma_1,
-  \gamma_2) := (\gamma_1', \gamma_2') := (\alpha, \beta)$. This assignment is
-  sufficient to prove the direction.
-
-  $`\Leftarrow'$: Suppose for all $h,h' \in H$ we have $(\gamma_1, \gamma_2),
-  (\gamma_1, \gamma_2') \in \sym_A \times \sym_B$ satisfying the above
-  requirements. Notice that for a given $i \in A$ and any $j, j' \in B$, let $h
-  = \omega(i,j)$ and $h' = \omega(i,j')$, then we have that $\gamma_1 (i) =
-  \gamma_1'(i)$. It follows that we can define a $\alpha \in \sym_A$ by
-  $\alpha(i) = \gamma_1 (i)$. Similarly we can define $\beta \in \sym_B$ by
-  $\beta (j) = \gamma_2 (j)$.
-
-\end{proof}
-
-\begin{definition}
-  Let $g$ be a gate with matrix labeling $\omega$. Let $(\sigma, h, h') \in
-  \sym([n]) \times H^2$. Say that $(\sigma, h, h')$ is useful if $(h,h')$ is
-  incompatible with $(\sigma, \omega)$.
-
-  Say that two distinct pairs $(\sigma_1, h_1, h_1'), (\sigma_2, h_2, h_2') \in
-  \sym([n]) \times H^2$ are mutually independent if
-  \begin{itemize}
-  \item $\sigma_2 h_1 = h_1$,
-  \item $\sigma_2 \sigma_1 h_1 = \sigma_1 h_1$,
-  \item $\sigma_2 h_1' = h_1'$,
-  \item $\sigma_2 \sigma_1 h_1' = \sigma h_1'$,
-  \end{itemize}
-  We say that a set $S \subseteq \sym([n]) \times H^2$ is useful if each pair in
-  it is useful. We say that S is independent if each pair of distinct pairs in
-  $S$ are mutually independent.
-\end{definition}
-
-We denote the usual equivalence relation on $\sym_n$ from the (right) cosets of
-$\matstab(\omega)$ by $\sim_\omega$.
-
-\begin{lem}
-  Let $\sigma_1, \sigma_1 \in \sym_n$ and suppose $\sigma_1 \sim_\omega
-  \sigma_2$ then for any $(h,h') \in H^2$ we have that $(h,h')$ is compatible
-  with $(\sigma_1, \omega)$ iff $(h,h')$ is compatible with $(\sigma_2,
-  \omega)$.
-\end{lem}
-
-\begin{proof}
-  Suppose we have that $\sigma_1 \sim_\omega \sigma_2$. And additionally
-  supposed $(h, h')$ compatible with $(\sigma_1, \omega)$.
-
-  It follows there exists $(\alpha, \beta) \in \sym_A \times \sym_B$ such that
-  $\sigma_1 \omega (i,j) = \sigma_2\omega (\alpha i, \beta j)$, and we have
-  $(\gamma_1, \gamma_2), (\gamma_1', \gamma_2') \in \sym_A \times \sym_B$
-  satisfying the requirements of compatibility. We note that $(\alpha, \beta)
-  \cdot \omega^{-1}(\sigma_1 h) = \omega^{-1}(\sigma_2 h)$. Thus by composition
-  we have that $(\alpha \gamma_1, \beta \gamma_2) \cdot \omega^{-1}(h) =
-  \omega^{-1}(\sigma_2 h)$ and $(\alpha \gamma_1', \beta \gamma_2') \cdot
-  \omega^{-1}(h') = \omega^{-1}(\sigma_2 h')$, and clearly the remaining
-  requirement for compatibility follows from the bijectivity of $\alpha$ and
-  $\beta$. The result follows. The other direction of the implication follows
-  from symmetry.
-\end{proof}
-
-\begin{claim}
-  \label{claim:useful-independant-set}
-  Let $g$ be a rank gate with labeling $\omega$ and child set $H$. Let $S$ be a
-  useful and independent. We then have that $\vert \sym_n: \matstab(\omega)
-  \vert \leq 2^{\vert S \vert}$.
-\end{claim}
-
-\begin{proof}
-  Let $R \subseteq S$ and define $\sigma_R = \Pi_{(\sigma, h, h') \in R} \sigma$
-  (with some arbitrary order assumed on $S$). Let $R$ and $Q$ be distinct
-  subsets of $S$ and WLOG let $\vert R \vert \geq \vert Q \vert$. We want to
-  show that we don't have $\sigma_R \omega \sim_\omega \sigma_Q \omega$. Pick
-  any $(\sigma, h, h') \in R/Q \neq \emptyset$. Given that $\sigma_R h = \sigma
-  h$ and $\sigma_R h' = \sigma h'$ it is easy to see that the usefulness of
-  $(\sigma, h,h')$ implies the incompatibility of $(h,h')$ with with $(\omega,
-  \sigma_R)$. Moreover, the fact that $\sigma_Q h = h$ and $\sigma_Q h' = h'$
-  makes it easy to see $(h,h')$ is compatible with $(\omega, \sigma_Q)$. From
-  the above lemma we may conclude that that we do not have $\sigma_R \sim_\omega
-  \sigma_Q$, and the result follows.
-\end{proof}
-
-The following two lemmas proved by Anderson and Dawar \cite{} are both of use in
-proving the following theorem.
-
-\begin{lem}
-  \label{lem:big-or-small}
-  For any $\epsilon$ and $n$ such that $0 < \epsilon < 1$ and $\log n \geq
-  \frac{4}{\epsilon}$, if $\mathcal{P}$ is a partition of $[n]$ with $k$ parts,
-  $s = [\sym_n : \setstab (\mathcal{P})]$ and $n \leq s leq 2^{n^{1-\epsilon}}$,
-  then $\min \{k, n-k\} \leq \frac{8}{\epsilon} \frac{\log s}{\log n}$.
-\end{lem}
-
-\begin{lem}
-  \label{lem:small-means-support}
-  For any $\epsilon$ and $n$ such that $0 < \epsilon < 1$ and $\log n \geq
-  \frac{8}{\epsilon^2}$, if $\mathcal{P}$ is a partition of $[n]$ with $\vert
-  \mathcal{P} \vert \leq \frac{n}{2}$, $s:= [\sym_n : \setstab (\mathcal{P})]$
-  and $n \leq s \leq 2^{n^{1-\epsilon}}$, then $\mathcal{P}$ contains a part $P$
-  with at least $n - \frac{33}{\epsilon} \cdot \frac{\log s} {\log n}$.
-\end{lem}
-
-If $g$ is a symmetric gate (i.e. the usual gates in a circuit) we note that
-$\orb(g) = [\sym_n : \stab (g)]$ by the orbit-stabilizer theorem.
-
-If $g$ is a matrix-symmetric gate then $\orb(g) = [\sym_n:\matstab (\omega)]$,
-where $\omega$ is the matrix labelling associated with $g$.
-
-\begin{thm}
-  For any $\epsilon$ and $n$ such that $\frac{2}{3} \leq \epsilon \leq 1$ and $n
-  \geq \frac{128}{\epsilon^2}$, if $C$ is a symmetric, rigid circuit on
-  structures of size $n$ and $s := \max_{g \in C} \vert \orb (g)\vert \leq
-  2^{n^{1-\epsilon}}$, then, $SP(C) \leq \frac{33}{\epsilon}\frac{log s}{log
-    n}$.
-\end{thm}
-
-\begin{proof}
-  It is easy to see that if $g$ is a gate in $C$ then $\stab (g) \subseteq
-  \setstab(\SP(g))$, and so $s \geq \orb(g) = [\sym_n : \stab(g)] \geq [\sym_n :
-  setstab(\SP(g))]$. Thus if $\vert \SP(g) \vert \leq frac{n}{2}$, then from
-  Lemma \ref{lem:small-means-support}, we have $\| SP (g) \| \leq
-  \frac{33}{\epsilon} \cdot \frac{\log s} {\log n}$. The result thus follows
-  from showing that for each $g$ in $C$ we have that $\vert \SP (g) \vert \leq
-  \frac{n}{2}$.
-
-  % Include some detail here for constant and relational gates
-  The cases where $g$ is a constant or relational gate are easy to handle.
-
-  We now consider the case for internal gates. Let $g$ be the topologically
-  first internal gate with $\vert \SP(g) \vert > \frac{n}{2}$. If $g$ is not a
-  matrix-symmetric gate then the result follows from the argument presented by
-  Anderson and Dawar \cite{}. Suppose $g$ is a matrix-symmetric gate, and
-  suppose $g$ has a labelling $\omega$. We now argue that this leads to a
-  contradiction.
-
-  Let $k' := \lceil \frac{8 \log s}{\epsilon \log n} \rceil$. From the
-  assumptions on $s, n$ and $\epsilon$ we have that $k' \leq
-  \frac{1}{4}n^{1-\epsilon} < \frac{n}{2}$. Lemma \ref{lem:big-or-small} implies
-  that $n - \vert \SP(g) \vert \leq k'$
-
-  From Claim \ref{claim:useful-independant-set} it remains to show that we can
-  construct a sufficiently large useful and independent set of gate-automorphism
-  pairs $S$. Divide $[n]$ into $\lfloor \frac{n}{k' + 2} \rfloor$ disjoint sets
-  $S_i$ of size $k' + 2$ and ignore the elements left over. It follows that for
-  each $i$ there is a permutation $\sigma_i$ which fixes $[n] / S_i$ pointwise
-  but moves $g$. Suppose there was no such $\sigma_i$ it follows that every
-  every permutation that fixes $[n]/S_i$ pointwise fixes $g$. Thus the partition
-  of all the singletons in $[n]/S_i$ and $S_i$ is a supporting partition. As
-  $\SP(g)$ is the coarsest partition it follows that $\vert \SP(g) \vert \leq n
-  - (k'+2) + 1 = n - k' - 1$, which contradicts the inequality $n - \vert \SP(g)
-  \vert \leq k'$.
-
-  Since $g$ is moved by each $\sigma_i$ and $C$ is rigid it follows that we
-  don't have $\sigma_i \notin \matstab(\omega)$. Thus there exists $(h_i, h_i')$
-  that is inconsistent with $(\sigma_i, \omega)$, and so the triple $(\sigma_i,
-  h_i, h_i')$ is useful.
-
-  Let $\SP (h)^*$ be the union of all parts of $\SP(h)$ except for the largest
-  part. Let $Q_i = \SP(h_i)^* \cup \SP(\sigma_i h_i)^* \cup \SP (h_i')^* \cup
-  \SP (\sigma_i h_i')^*$. Then note that if $\sigma_j$ fixes $Q_i$ then by
-  construction, we have that $\sigma_j \in \stab_n(\SP(h_i)) \cap
-  \stab_n(\SP(\sigma_i h_i)) \cap \stab_n(\SP(h_i')) \cap \stab_n(\SP(\sigma_i
-  h_i'))$
-
-  Define a graph $K$ with vertices given by the sets $S_i$ and an edge from
-  $S_i$ to $S_j$ (with $i \neq j$) if $Q_i \cap S_j \neq \emptyset$. It follows
-  then that if there is no edge between $S_i$ and $S_j$ then $(\sigma_i, h_i,
-  h_i')$ and $(\sigma_j, h_j, h_j')$ are mutually independent. It remains to
-  argue that $K$ has a large independent set. This is possible as the out-degree
-  of $S_i$ in $K$ is bounded by
-  \begin{align*}
-    \vert Q_i \vert \leq \|SP(h_i) \| + \|SP(\sigma_i h_i) \| + \|SP(h_i') \| + \|SP(\sigma_i h_i') \leq 4 \cdot \frac{33\log s}{\epsilon \log n}
-  \end{align*}.
-
-  This follows as the sets $S_i$ are disjoint and we may apply Lemma
-  \ref{lem:small-means-support} to each of the child gates. It follows that the
-  average total degree (in + out degree) of $K$ is at most $2 \cdot \vert Q_i
-  \vert \leq 34 \cdot k'$. Now greedily select a maximal independent set in $K$
-  by repeatedly selecting $S_i$ with the lowest total degree and eliminating it
-  and its neighbours. This action does not affect the bound on the average total
-  degree of $K$ and hence determines an independent set $I$ in $K$ of size at
-  least
-  \begin{align*}
-    \frac{\lfloor \frac{n}{k' + 2} \rfloor}{34k' + 1} \geq \frac{n - (k'+2)}{34k'+1k'+2} \geq \frac{n\frac{7}{16}}{34k'^2 + 69k' +2} \geq \frac{n}{(16k')^2}.
-  \end{align*}
-
-  Take $S = \{(\sigma, h, h') : S_i \in I \}$. Then from the above argument we
-  have that $S$ is useful and independent.
-
-  Moreover, from Claim \ref{claim:useful-independant-set}, we have that $s \geq
-  \vert \orb(g) \vert \geq 2^{\vert S \vert} \geq 2^{\frac{n}{(16k')^2}}$ then
-  $n^{1-\epsilon} \geq \log s \geq n \cdot (\frac{128}{\epsilon}\frac{\log
-    s}{\log n})^{-2} > n \cdot (n^{1-\epsilon})^{-2} = n^{2\epsilon -1} \geq
-  n^{1-\epsilon}$. This is a contradiction.
-\end{proof}
-
-\section{Rigid Circuits}
-
-\begin{definition}
-  We say that a circuit $C$ has bijective labels if for each gate $g$ in $C$,
-  $L(g)$ is a bijection.
-\end{definition}
-
-\begin{lem}
-  \label{lem:bij_labels}
-  There is an algorithm that runs in polynomial time that takes in a circuit $C$
-  and outputs a circuit with unique gates $C'$. Moreover, if $C$ was symmetric
-  then $C'$ is symmetric. If $C$ is rigid then $C'$ is rigid.
-\end{lem}
-
-\begin{proof}
-  Let $S = 2*\vert C \vert$. Recurse through the gates of $C$ topologically and
-  let $h$ be the next gate topologically. If for all $g \in W(h, \cdot)$ we have
-  that $L\vert (g)^{-1}(h) \vert = 1$ continue on to the next gate. If not add
-  in a tower of $S$ $\and$ gates such that $h \rightarrow \and^h_1 \rightarrow
-  \ldots \rightarrow \and^h_S$ (i.e. we have a tower of $\and$ gates with $h$ as
-  input to $\and^h_1$ and the output of each $\and^h_i$ connected to the input
-  of each $\and^h_{i+1}$ for each $1 \leq i < S$). Now for each $g \in W(h,
-  \cdot)$, if $L(g)^{-1}(h) = \{ s_0, \ldots, s_{r}\}$, for each $1 \leq i \leq
-  r$ add in the wires $W(\and^h_i, g)$ and set $L(g)(s_{i}) = \and^h_i$. Now
-  continue on to the next gate topologically and run the above algorithm.
-
-  % First, notice that for a given gate $h$ and $k \in \mathbb{N}$, we can
-  % define
-  % a sub-circuit $h^k = 1 \and \cdots, 1 \and h$ (or rather a $k$-height tower
-  % of
-  % $k$ binary $\and$ gates with $h$ at the top and all other inputs set to
-  % $1$).
-  % We call $h$ the top of the sub-circuit $h^k$ and the bottom $and$ gate (the
-  % output of the sub-circuit) the bottom gate. We may think of this as a
-  % $k$-height copy of the gate $h$, in the sense that it has the same output as
-  % $h$ and similar orbits. We now use different copies to distinguish gates
-  % that
-  % otherwise have the same labelling.
-
-  % Let $h$ be the next gate topologically. Then let $r$ be maximal such that
-  % $W(h,g)$ and $\omega_g^{-1}(h) = \{ s^g_1, s^g_2, \ldots, s^g_r \}$. Then
-  % let
-  % $k$ be the height of the highest tower with $h$ at the top and with it's
-  % bottom connected to a gate in $W(h, \cdot)$. Then create a single
-  % $k+r-1$-height tower by adding in the appropriate number of binary $\and$
-  % gates below $h$.
-
-  % For each $g \in W(h, \cdot)$ and for each $\omega_g^{-1}(h) = \{s^g_1,
-  % s^g_2,\ldots , s^g_{r_g}\}$, set $L'(g)(s^g_1) = h$ each child starting with
-  % the $and$-gate child to $h$ add in a wire from from the $i$th gate in the
-  % tower to $g$ and set $L'(g)(s^g_{i+1}) = \and_i$, where $\and_i$ is the
-  % $i$th
-  % $\and$ gate in the tower starting with the $\and$ gate in the tower child to
-  % $h$. There are enough gates in the tower as $r_g \leq r$.
-
-  We call this updated circuit $C'$.
-
-  Firstly, note that after running the above algorithm for each $g$ the
-  labelling of $g$ will be a bijection. Moreover, it's easy to see that the
-  output of each gate remains unchanged, and as such the output of the circuit
-  is unchanged.
-
-  Secondly, notice that the size of $C'$ is at most $2*\vert C \vert^2$, and
-  note that the above algorithm runs in polynomial time.
-
-  Now suppose that $C$ is symmetric. Let $\sigma$ be a permutation on the input
-  universe and $\pi_C$ the induced automorphism on $C$. We now define $\pi$, the
-  induced automorphism on $C'$. For each gate $g$ in $C'$, if $g$ is in $C$ then
-  set $\pi(g) := pi_C(g)$. If $g$ is not in $C$ then $g$ must be some
-  $\and^h_i$, for some $h$ in $C$. Then set $\pi(\and^h_i) :=
-  \and^{\pi_C(h)}_i$. It is easy to see that $\pi$ is an automorphism, and $\pi$
-  extends $\sigma$.
-
-  Suppose that $C$ is rigid. It is easy to see that $C'$ will be rigid as well.
-
-\end{proof}
-
-% If $h$ is a binary $\and$ gate, then we say that $h$ has height $k+1$ if it
-% has a $k$-height tower of binary $and$ gates connected above it, with a
-% non-$\and$ gate $p$ connected to the final binary $\and$ gate, and all other
-% inputs connected to $1$. We then say that $h$ is the base of a tower of height
-% $k$ and type $p$.
-
-% Then for each $h \in W_g$, if $h$ is not a binary $\and$ gate, the let $k$ be
-% the largest integer such that there a gate $h' \in W(h, \cdot)$ which is the
-% base of a tower of height $k$ and type $h$. it's output directly connected to
-% one of the gates in $W(h^k, \cdot)$ (with k = 0 corresponding to just $h$).
-% Then each $i \in \{1, \ldots , \vert \omega^{-1}(h)\vert\}$ add into the
-% circuit $h^{k+i}$ and wire it to $g$. Notice that this step requires adding
-% $\vert \omega^{-1}(h) \vert -1$ gates to the circuit. For some assumed
-% ordering $\dom(\omega)$, let $\{s_0, \cdot, s_m\} = \omega^{-1}(h)$. Define
-% $L'(g)(s_i) = h^{k+i}$. Now continue on to the next gate topologically where
-% $L(g)$ is not a bijection, and execute the same process
-
-\begin{lem}
-  There is an algorithm that runs in polynomial time that takes in a circuit $C$
-  and outputs a circuit $C'$ such that $C'$ is rigid and has bijective labels.
-  Moreover, if $C$ was symmetric it follows that $C'$ will be symmetric.
-\end{lem}
-
-\begin{proof}
-  First run the algorithm from Lemma \ref{lem:bij_labels} on $C$, and call the
-  output circuit $C$.
-
-  Recurse through the gates of $C$ topologically. For each internal gate $g$,
-  for all $g'$ in $C$ such that $g \neq g'$, $W(\cdot, g) = W(\cdot, g')$, $W(g,
-  \cdot) = W(g', \cdot)$, $\Sigma(g) = \Sigma(g')$, $L(g) \sim L(g')$ and
-  $\Omega^{-1}(g) = \Omega^{-1}(g')$, delete $g'$ and for all $s \in L^{-1}(g')$
-  set $L(s) := g$.
-
-  Now re-run the algorithm from Lemma \ref{lem:bij_labels} on $C$ and output the
-  result.
-\end{proof}
-
-  \begin{lem}
-    Let $C = \langle G, W, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\SB, \MB,
-    \tau)-circuit$ on structures of size $n$. There is a deterministic algorithm
-    which runs in Poly($\vert C \vert$) and outputs a rigid $(\SB, \MB, \tau)
-    circuit$ $C'$ such that $G' = G$ and for any $g \in G$, and any input
-    $\tau$-structure $\mathcal{A}$ and any bijection $\gamma$ from $A$ to $[n]$,
-    $C[\gamma \mathcal{A}](g) = C'[\gamma \mathcal{A}](g)$ and if $C$ is
-    symmetric then so is $C'$.
-  \end{lem}
-
-  \begin{proof}
-
-  \end{proof}
-
-  \section{Computing Supports}
-  \begin{lem}
-    Let $C$ be a rigid $(\SB, MB, \tau)$-circuit on structures of size $n$ and
-    $\sigma \in \sym_n$. There is a deterministic algorithm which runs in time
-    Poly($\vert C \vert$) and outputs for each gate $g$ its image under the
-    automorphism $\pi$ induced by $\sigma$, if it exists.
-  \end{lem}
-  \begin{proof}
-    The proof proceeds by recursively going through the circuit and building the
-    mapping $\pi$ induced by $\sigma$.
-
-    Suppose $g$ is a constant gate, then $\pi g := g$. Suppose $g$ is a
-    relational gate, then there is at most one gate $g'$ such that $\Sigma (g) =
-    \Sigma (g')$ and $\sigma\Lambda (g') = \Lambda (g)$. If such a $g'$ exists
-    assign $\pi g := g'$, else terminate with failure.
-
-    If $g$ is an symmetric internal gate then (from rigidity) there is at most
-    one gate $g'$ such that $\Sigma (g) = \Sigma(g')$ and $W_{g'} = \pi W_g$.
-    Assign $\pi g := g'$ if such a gate exists, or else terminate with failure.
-
-    If $g$ is a matrix-symmetric internal gate then consider the set of gates
-    $g'$ such that $g'$ has children $\pi W_g$ and $\Sigma(g) = \Sigma(g')$, and
-    let $A \times B = \dom (Sigma(g))$. If no such gate $g'$ exists, terminate
-    with failure. Define $\sigma_{\pi, g'}:A \times B \rightarrow A \times B$ by
-    $\sigma_{\pi, g'} = \omega^{-1}_{g'} \pi \omega_{g}$. Then clearly
-    $\omega_{g'} \sigma_{\pi, g'} = \pi \omega_{g}$, and it's easy to show that
-    $\pi \omega_g \sim \omega_{g'}$ iff $\sigma_{\pi,g'} \in \sym_A \times
-    \sym_B$. But this just involves checking that $\sigma$ acts as a bijection
-    on $A$ and $B$ separately and, given that $\vert A \vert$ and $\vert B
-    \vert$ are both bounded by $\vert C \vert$, the algorithm which just
-    iterates through $A$ and $B$ is sufficient. If for every $g'$ it is found
-    that $\pi_{\sigma,g'}$ is not in $\sym_A \times \sym_B$ then terminate with
-    failure. If there is a $g'$ for which $\pi_{\sigma, g'} \in \sym_A \times
-    \sym_B$ then it is unique by rigidity and so set $\pi g := g'$.
-
-    If $g$ is an output gate, then check that for all tuples in $[n]^{q}$ we
-    have that $\pi \Omega (x) = \Omega (\sigma (x))$, and terminate with failure
-    if the condition is not met.
-
-    If the algorithm has not terminated with failure, output the automorphism.
-
-    The algorithm clearly runs in Poly($\vert C \vert$)
-  \end{proof}
-
-  \section{Evaluating Symmetric Circuits}
-  We need to extend two Lemmas in this section.
-
-\begin{lem}
-  Let $g$ be a matrix-symmetric gate in $C_n$ with children $H$. Let $\alpha \in
-  U^{\underbar{\sp(g)}}$, and suppose $\gamma_1, \gamma_2: U \rightarrow [n]$
-  with $\gamma^{-1}_1 \sim \alpha$ and $\alpha \sim \gamma^{-1}_2$. Let $A
-  \times B = \dom (L(g))$.
-
-  For an input structure $\mathcal{A}$, let $L^0_\gamma: A \times B \rightarrow
-  \{0,1\}$, where $L^0_\gamma (a,b):= C[\gamma \mathcal{A}] (L(g)(a,b))$.
-
-  Then $L^0_{\gamma_1} \sim L^0_{\gamma_2}$.
-\end{lem}
-
-\begin{proof}
-  We have that there exists a unique $\pi \in \sym_n$ such that $\pi \gamma_1 =
-  \gamma_2$. Moreover, since $\gamma^{-1}_1$ and $\gamma^{-1}_2$ are both
-  consistent with $\alpha$, it follows that $\pi$ must fix $\sp(g)$. Thus $L(g)
-  \sim \pi L(g)$, and so there exists $(\sigma, \lambda)$ such that $\pi L(g) =
-  L(g) (\sigma, \lambda)$.
-
-  We then have that,
-  \begin{align*}
-    L^0_{\gamma_1} (a,b) &= C_n[\gamma_1 \mathcal{A}](L(g)(a,b))\\
-                         & = C_n[\pi gamma_1 \mathcal{A}][\pi L(g)(a,b)] \\
-                         & = C_n[gamma_2 \mathcal{A}][L(g)((\sigma, \lambda)(a,b))]\\
-                         & = L^0_{\gamma_2} ((\sigma, \lambda) (a,b)),
-  \end{align*}
-  and it follows that $L^0_{\gamma_1} \sim L^0_{\gamma_2}$.
-
-\end{proof}
-
-\begin{lem}
-  Let $g$ be a matrix symmetric gate in $C_n$ with children $H$. Let $\alpha \in
-  U^{\underbar{\sp(g)}}$ and $\gamma: U \rightrrow [n]$ such that
-  $gamma^{-1}\sim \alpha$. Let $A \times B = \dom (L(g))$ and define
-  $L^{EV}_\alpha: A \times B \rightarrow \{0,1\}$ by
-  \begin{align*}
-    L^{EV}_\alpha (a,b):=
-    \begin{cases*}
-      1 & if $A_h \cap \EV_h \neq \emptyset$ 0 & otherwise
-    \end{cases*},
-  \end{align*}
-  where for $h \in W_g, A_h:= \{\beta \in U^{\underline{\sp(h)}} \vert \alpha
-  \sim \beta\}$. Then $L^0_\gamma = L^{EV}_\alpha$ and $\alpha \in \EV(g)$ iff
-  $\rk^u_p(L^0_\gamma)$
-\end{lem}
-\begin{proof}
-
-\end{proof}
-
-\begin{lem}
-  Let $g$ be a matrix-symmetric gate in $C_n$ with children $W_g$. $Let \alpha
-  \in U^{\underbar{\sp(g)}}$ and let $\gamma: U \rightarrow [n]$ such that
-  $\gamma^{-1} \sim \alpha$. Let $A \times B = \dom (L(g))$, and let
-  $f:\{0,1\}^{A \times B} \rightarrow \{0,1\}$ be the matrix-symmetric function
-  associated with $g$. Define $L^{EV}_\alpha: A \times B \rightarrow \{0,1\}$ by
-  \begin{align*}
-    L^{EV}_\alpha (a,b):=
-    \begin{cases*}
-      1 & if $A_h \cap \EV_h \neq \emptyset$ 0 & otherwise
-    \end{cases*},
-  \end{align*}
-  where for $h \in W_g, A_h:= \{\beta \in U^{\underline{\sp(h)}} \vert \alpha
-  \sim \beta\}$. Then $\alpha \in \EV_g$ iff $f(L^\EV_\alpha)$.
-\end{lem}
-\begin{proof}
-  First note that if $\alpha \in U^{\underbar{\sp{g}}}$ then $\alpha \in \EV_g$
-  iff we have that $C_n[\gamma \mathcal{A}](g)= f (L^0_\gamma) = 1$. Notice that
-  from Lemma \ref{} that this holds for any particular $\gamma$ iff it holds for
-  all such $\gamma$.
-
-  We now show that $L^\EV_\alpha = L^0_\gamma$, and so complete the proof.
-
-  Suppose for $(a,b) \in A \times B$ we have that $L^\EV_\alpha(a,b) = 1$. Let
-  $h:= L(g)(a,b)$. It follows that $A_h \cap \EV_h \neq \emptyset$, i.e there
-  exits $\beta \in \sp(h)$ such that $\beta \sim \alpha$ and there exists
-  $\gamma_h \in \Gamma(h)$ such that $\gamma^{-1}_h \sim \beta$. It follows from
-  transitivity and Lemma \ref{} that $\gamma_h \sim \alpha$ and so
-  $L^0_\alpha(a,b) = C_n[\gamma \mathcal{A}](h) = C_n[\gamma_h \mathcal{A}](h) =
-  1$.
-
-  Now suppose that $L^0_\gamma (a,b) = 1$
-\end{proof}
-
-\section{Translating to Formulas of FPC}
-Let $\mathcal{C} = (C_n)_{n \in \mathbb{N}}$ be a P-uniform family of
-polynomial-size symmetric $(\SB, \MB, \tau)$ circuits, and where $\MB$ is the
-rank basis. It remains to show that there is a formula $Q$ in the vocabulary
-$\tau \uplus \{\leq\}$ such that for any $n$ and $\tau$-structure $\mathcal{A}$
-with a universe $U$ of carnality $n$, the $q$-ary query defined by $C_n$ on the
-input $\mathcal{A}$ is defined by the formula $Q$ when interpreted in the
-structure $\mathcal{A}^\leq = \mathcal{A} \uplus \langle [n], \leq \rangle$.
-
-Since $\mathcal{C}$ is $P$-uniform, and from Lemmas \ref{} and \ref{} and the
-Immerman-Vardi theorem, we have an FP interpretation defining a rigid symmetric
-circuit with bijective labels equivalent to $C_n$ (which we also call $C_n$)
-over the the number sort of $\mathcal{A}^\leq$, where $\Phi = (\phi_G,\phi_W,
-\phi_\Omega, (\phi_s)_{s \in \SB \uplus \{rank\} \uplus \tau \uplus \{0,1\}},
-(\phi_{\and_R})_{R \in \tau}, \phi_L)$. We note that $Phi$ is a $t$-width
-interpretation over the universe $[n]$. So if $\mu, \nu, \nu_1, \ldots \in
-[n]^t$, the formulas are defined such that:
-
-\begin{itemize}
-\item $\phi_G(\mu)$ holds iff $\mu$ encodes a gate
-\item $\phi_W(\nu,\mu)$ holds iff $\nu$ and $\mu$ encode gates and if $g_{\nu}$
-  and $g_{\mu}$ are these two encoded gates respectively then $W(g_{\nu},
-  g_{\mu})$.
-\item $\phi_{\Omega}(\nu_1, \ldots, \nu_q, \mu)$ holds iff $\nu_1, \ldots, nu_q$
-  each encode numbers less than or equal to $[n]$ and $\Omega(\nu_1, \ldots,
-  \nu_q) = g_\mu$.
-\item For all $s \in \SB \uplus \{rank\} \uplus \tau \uplus \{0,1\}$ we have
-  that $\phi_s (\mu)$ holds iff $\mu$ encodes a gate such that $\Sigma(g_\mu) =
-  s$ (or, in the case that $s = \rank$, we require that $\Sigma(g_\mu)$ is a
-  rank symbol.)
-\item For all $R \in \tau$ with arity $r$ we have that $\phi_{\and_R}(\nu_1,
-  \ldots, \nu_r, \mu)$ holds iff $\nu_1 , \ldots , \nu_r$ encodes numbers less
-  than or equal to $[n]$, $\mu$ encodes a gate such that $\Sigma(g_\mu) = R$ and
-  $\Lambda_R(g_\mu) = (\nu_1, \ldots, \nu_r)$.
-\item $\phi_L(\nu, \mu, \nu_1, nu_2)$ holds iff $\nu$ and $\mu$ encode gates and
-  $\nu_1, \nu_2$ encode numbers, and $L(g_{\mu})(\nu_1,\nu_2) = g_\nu$. If
-  $\dom(L (g_\mu)) = [a] \times [b]$, then the encoding of $[a]$ and $[b]$ are
-  initial segments under the lithographically induced order. Moreover, the
-  encodings of $[a]$ and $[b]$ preserve the order relation.
-\end{itemize}
-
-From now on we use $\mu$ and $\nu$ to stand for $t$-length sequences encoding
-gates, and use $\nu_1, \ldots$ for sequences that encode numbers. We use $g_\mu$
-and $g_\nu$ for the gates encoded by these sequence, while simply identifying
-the sequence $\nu_i$ with the number it encodes.
-
-Using the Immerman-Vardi Theorem, we can define an FP($\leq$) formula
-$\rankpara$ such that $\langle [n], \leq\rangle \models \rankpara[g,p,u]$ iff
-$\langle [n], \leq\rangle \models \phi_G[g] \land \phi_{\rank}[g]$ and the rank
-gate $g$ (as per the interpretation) computes the rank over characteristic $p$
-and has threshold $u$.
-
-We can define FP($\leq$) formulas $\max_A$ and $\max_B$ such that $\langle [n],
-\leq \rangle \models \max_A[g, \nu_1]$ iff $\nu_1$ encodes $a$, where
-$\dom(L(g)) = [a]\times [b]$. Similarly, $\langle [n], \leq \rangle \models
-\max_B[g, \nu_1]$ iff $\nu_1$ encodes $b$ where $\dom(L(g)) = [a] \times [b]$.
-
-Again using Lemma \ref{} and the Immerman-Vardi theorem, we can construct a
-formula $\supp$ such $\langle [n], \leq \rangle \models \supp[g,u]$ iff $\langle
-[n], \leq \rangle \models \phi_G[g]$ and $u$ is in $sp(g)$. This formula can be
-used as in \cite{} to inductively define $\supp_i(g,u)$ for each $i \in [n]$
-which holds iff $u$ is the $i$th element of the support of $g$.
-
-Define the $\agree$ and $\theta_s$ formulas for all $s \in \SB \uplus \tau
-\uplus \{0,1\}$ as in \cite{}.
-
-Now we define the formula
-\begin{align*}
-  \theta_{\rank}:= (\mu, \bar{x}) := \bigwedge_{1 \leq i < j \leq k} x_i
-  \neq x_j \wedge \forall \bar{y} ( [ \rank (x \leq \phi_{mr}, y \leq
-  \phi_{mc}, \pi \leq r). \theta^{'} ] ),
-\end{align*}
-\begin{align*}
-  \theta^{'}(a,b):= \exists \nu (W(\nu, \mu) \wedge \agree (\mu,\nu, \bar{x}, \bar{y}) \wedge \phi_L (\mu, \nu, a, b) \wedge V(\nu, y))
-\end{align*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\chapter{October 27th: Counting Gates Simulate Symmetric Gates}
-
-In this chapter we prove that symmetric circuits with majority gates are at
-least as powerful as symmetric circuits over any other Boolean basis consisting
-of symmetric functions.
-
-Recall the following that $\mathbb{B} = \{ \neg , \wedge , \lor \}$ and
-$\mathbb{B}_\maj = \{ \maj \} \cup \mathbb{B}$.
-
-Let $F: \{0,1\}^* \rightarrow \{0,1\}$ be a symmetric Boolean function. Since
-$F$ is symmetric we note that for a fixed size input the output of $F$ is
-entirely determined by the number of 1's in its input. Then let
-$c_{F}:\mathbb{N} \rightarrow 2^{\mathbb{N}}$ define a function where $c_{F}(n)$
-is the set of all $m \leq n$ such that for all $\vec{x} \in \{ 0,1 \}^n$ with
-$m$ 1's we have $F (\vec{x}) = 1$. Clearly a symmetric Boolean function $F$ is
-entirely determined by $c_{F}$.
-
-\begin{prop}
-  \label{prop:fuctions-maj}
-  There is a polynomial $p(k)$ such that for any symmetric function $F$ and a
-  given $k \in \mathbb{N}$ there is a circuit $C_k$ on $k$ inputs over the basis
-  $\mathbb{B}_\maj$ which is symmetric, constant depth and with width bounded by
-  $p(k)$.
-\end{prop}
-
-\begin{proof}
-  We define the circuit $C_k$ for inputs $\vec{x} = ( x_1, \ldots, x_k )$.
-
-  For $a \in \mathbb{N}$ we define a get $\countgate_a$ by
-  \begin{align*}
-    &\countgate_a = \maj (x_1, \ldots, x_k, \underbrace {0, \ldots, 0}_{2a -
-      k}) \land \neg \maj (x_1, \ldots , x_k, \underbrace{0, \ldots,  0}_{2a - k + 2})\text{ if $a \geq \frac{k}{2}$,} \\
-    &\countgate_a = \maj (x_1, \ldots, x_k, \underbrace {1, \ldots, 1}_{x -
-      2a}) \land \neg \maj (x_1, \ldots , x_k, \underbrace{1, \ldots,
-      1}_{k - 2a -2}) \text{ if $a < \frac{k}{2}$. }
-  \end{align*}
-
-  Then let $g = \bigvee_{a \in c_{F_i}(k)}\countgate_a$ and let $C_{k}$ be the
-  circuit with input gates labeled by $\vec{x}$ and output gate $g$.
-
-  t is easy to see that $C_k$ is constant depth and it's width is a polynomial
-  in $k$. We have that in each layer of $C_{g'}$ each gate is connected to all
-  gates in the previous layer, and as such the circuit is symmetric.
-\end{proof}
-
-The above proposition has a straight forward application to circuit
-characterizations.
-
-\begin{prop}
-  Let $F = \{F_i : i \in I \}$ be a family of symmetric Boolean functions where
-  $F_i: \{0,1\}^* \rightarrow \{ 0,1 \}$.
-
-  Let $(C_n)_{n \in \mathbb{N}}$ be family of symmetric circuits over the
-  Boolean basis $\mathbb{B} \cup F$, where $C_n$ is a circuit on structures of
-  size $n$, and the size of each circuit in the family is bounded by some
-  function $f(n)$. Then there exists a polynomial $q(n)$ and a family of
-  symmetric circuits $(C_n')_{n \in \mathbb{N}}$ over $\mathbb{B}_\maj$, where
-  $C_n'$ is a circuit on structures of size $n$ and $\vert C_n' \vert \leq
-  q(f(n))$.
-\end{prop}
-
-\begin{proof}
-  From $C_n$ we construct $C_n'$ in the obvious way. For each gate $g \in C_n$
-  of type $F_i$ we have a symmetric circuit $C_g$ from Proposition
-  \ref{prop:function-maj} that computes the same function as $g$. Then let
-  $C_n'$ be $C_n$ but with each gate $g$ replaced by $C_g$. It is easy to see
-  that $C_n'$ is symmetric. We also have that each gate $g$ must have at most
-  $f(n)$ inputs, and the size of $C_g$ is bounded by $p(f(n))$. Thus the size of
-  $C_n'$ is bounded by $f(n)p(f(n))$.
-\end{proof}
-
-\chapter{October 29th: Symmetric Circuits and CPT}
-
-We already have that that the set of queries decidable by symmetric
-circuits (respectively with counting) is exactly the set of queries
-expressible in Fixed-Point Logic. We know that the CFI query is not
-expressible in FPC, and so there is no symmetric circuit that can
-compute the query.
-
-In our attempts to find a circuit characterisation of CPT, we might try and weaken the requirement of symmetry in our notion of symmetric circuits in order to express the CFI query (and perhaps the whole of CPT).
-One approach would be to weaken the requirement of having small orbits, to rather only having small orbits with respect to our particular input structure.
-We formalise this notion below.
-
-\begin{definition}
-Let $C$ be a circuit on structures of size $n$.
-Let $g$ be a gate in $C$ and let $X$ be a set of input strings closed under the action of the symmetric group.
-The $inv_X = \{ \sigma \in \sym_n : \forall x \in X g \circ H (x) = g \circ H (\sigma x)$.
-\end{definition}
-\begin{definition}
-  Let $(C_n)_{n \in \mathbb{N}}$ be a family of circuits. For any
-  finite structure $\mathcal{A}$ let $X_{\mathcal{A}}$ be the set of
-  all string encodings of $\mathcal{A}$. We say a circuit family has
-  small isomorphism orbits if there is a polynomial $p(n)$ such that
-  for any sufficiently large $n$, finite structure $\mathcal{A}$ of
-  cardinality $n$ and any $g \in C_n$ we have
-  $\vert S_n : \inv_{X_{\mathcal{A}}}(g) \vert \leq p(n)$.
-\end{definition}
-
-\begin{thm}
-  \label{thm:simple_group}
-  Let $n \in \mathbb{N}$, $n \geq 5$. Let $r \in \mathbb{N}$ such that
-  $r \leq n/2$. Suppose that $G$ is a subgroup of $\sym(n)$, then
-  there is a constant $k \in mathbb{N}$ such that for all $n \geq k$
-  if $\vert \sym(n):G \vert \leq {{n}\choose {r}}$ then there exists
-  $X \subseteq [n]$ with $\vert X \vert \leq r$ and such that
-  $\alt([n] \setminus X) \leq G$.
-\end{thm}
-
-The following result shows that even this weakened definition fails to
-capture CPT.
-\begin{thm}
-  There is no family of circuits with small isomorphism orbits that
-  expresses the CFI query.
-\end{thm}
-\begin{proof}
-  Let $(G_n)_{n \in \mathbb{N}}$ be a family of ordered graphs such that each $G_n$ has
-  odd and even CFI graphs $\mathfrak{G}$ and $\tilde{\mathfrak{G}}$ respectively, each of
-  cardinality $n$. Furthermore, suppose the CFI query for $(G_n)$ is not expressible in
-  FPC (the existence of such a family is guaranteed by
-  \cite{}). Suppose there exists a family of circuits $(C_n)_{n \in \mathbb{N}}$ with
-  small isomorphism orbits that decides the CFI query for $(G_n)$.
-  Then we have that $C_n(\mathfrak{G}) = 1$ and
-  $C_n(\tilde{\mathfrak{G}}) = 0$, and for any $g \in C_n$
-
-  \begin{align*}
-    \vert S_n : \inv_{X_{\mathcal{G}}}(g) \vert &\leq p(n),\\
-    \vert S_n : \inv_{X_{\tilde{\mathcal{G}}}}(g) \vert &\leq p(n)
-  \end{align*}.
-  Let $k$ be such that $p(n) \leq n^k$ for all sufficiently large $n$.
-Then we have that $p(n) \leq n^k \leq {{n}\choose{k+1}}$ for all sufficiently large $n$, and (again, taking $n$ large enough) we have that $k \leq n/2$.
-Taking $n$ larger than the constant in Theorem \ref{thm:simple_group} it follows that there exists an $X_1, X_2 \subseteq [n]$ such that $\vert X_1 \vert, \vert X_2 \vert \leq k$ and $\alt ([n] \setminus X_1) \subseteq  \inv_{X_{\mathfrak{G}}}(g)$, $\alt ([n] \setminus X_2) \subseteq  \inv_{X_{\tilde{\mathfrak{G}}}}(g)$.
-It follows that
-  \begin{align*}
-    \alt ([n] \setminus (X_1 \cup X_2)) &\subseteq \alt ([n] \setminus X_1) \cap \alt ([n] \setminus X_2)\\
-                                        &\subseteq \inv_{X_{\mathfrak{G}}}(g) \cap \inv_{X_{\tilde{\mathfrak{G}}}}(g) \\
-                                        &\subseteq \inv_{X_{\mathfrak{G} \cup \tilde{\mathfrak{G}}}}(g) =  \inv_{CFI(G)}(g),
-  \end{align*}
-  where $CFI(G)$ is set of all encodings of all CFI graphs of $G_n$.
-
-  We then have that
-  \begin{align*}
-    \vert S_n : \inv_{CFI(G)}(g) \vert \leq \vert S_n : \alt ([n] \setminus (X_1 \cup X_2)) \leq  \frac{n!}{(n-2k)!/2} \leq n^{2k+1},
-  \end{align*}
-  with the last inequality following for large enough $n$. We thus
-  have from Theorem \ref{} that there is a symmetric circuit $D_n$
-  that decides the CFI problem for $G_n$, and hence a family $(D_n)$
-  that decides the CFI problem for the family of graphs $(G_n)$. From
-  the theorem of Dawar et al. \cite{}, it follows that there is as
-  formula of FPC that decides the CFI query for $(G_n)$ contradicting
-  our assumption.
-\end{proof}
+\subsection{Symmetric Circuits}
+This still needs to be filled in
 \end{document}

### 2017-07-26 sections/conclusion.tex
26/07/2017

--- 2017-07-26 sections/background.tex
@@
 \documentclass[../paper.tex]{subfiles}
-
 \begin{document}
-In this section we present basic background on logics, first-order structures,
-and symmetric circuits.
-
-\subsection{Logic and Structures}
-A \emph{relational vocabulary} (usually denoted by $\tau$) is a finite sequence
-of relation symbols $R_1, \ldots, R_k$, such that for all $i \in [k]$, $R_i$ has
-arity of $r_i \in \nats$.
-
-A $\tau$-structure $\mathcal{A}$ is a tuple $\langle U, R^{\mathcal{A}}_1 ,
-\ldots , R^{\mathcal{A}}_k \rangle$, where $U$ is a set and called the
-\emph{universe} of $\mathcal{A}$ and for all $i \in [k]$ the relations
-$R^{\mathcal{A}}_i \subseteq U^{r_i}$. The elements of $U$ are called the
-elements of $\mathcal{A}$. A \emph{multi-sorted} structure is one whose universe
-is a disjoint union, where each set in the union is called a \emph{sort}. The
-size of a structure is the cardinality of its universe.
-
-All structures in this paper are finite.
-
-\subsection{First Order, Fixed-Point, Counting}
-
-Let $\FO(\tau)$ denote \emph{first order logic} with respect to the vocabulary
-$\tau$. \emph{Fixed-Point Logic} is the extension of $\FO(\tau)$ with an
-inflationary fixed-point operator (see \cite{} for details). For logic
-$\mathcal{L}$, a formula $\phi \in \mathcal{L}(\tau)$, $x$ a $k$-length tuple of
-variables, $\mathcal{A}$ a (finite) structure, and $a \in U^k$, we have that
-$\phi (x)$ denotes that the variables in $x$ are free in $\phi$ and we write
-$\mathcal{A} \models_{\mathcal{L}} \phi[a]$ iff the the formula $\phi$ is true
-in $\mathcal{A}$ with respect to $\mathcal{L}$ with the variables $x$ assigned
-to $a$. The context usually makes the logic obvious, and in that case we usually
-drop the subscript.
-
-We also recall the definition of \emph{fixed-point logic with counting} $\FPC$,
-an extension $\FP$ with counting quantifiers. For a structure $\mathcal{A}$,
-Formulas of this logic are evaluated over a structure $\mathcal{A}$ by extending
-that structure to $\mathcal{A}^\leq$, a two sorted extension of $\mathcal{A}$ by
-an ordered number sort $\{1, \ldots, \vert U\vert \}$. Variables are taken to be
-either point variables, ranging over $U$ or number variables ranging over
-$[\vert U \vert]$. The counting quantifiers are of the form $\#_x$, where $x$ is
-either a point or number variable and for $\phi(x) \in \FPC(\tau)$, $\#_x
-\phi(x)$ is a term denoting the element of the number sort corresponding to
-$\vert \{a \in \mathcal{A} | \mathcal{A} \models \phi[a]\}\vert$. Note
-additionally that $k$-tuples of number variables can be used to encode numbers
-in $\FPC$ of size up to $\vert U\vert^k$. For more details on $\FPC$ please see
-\cite{}.
-
-\subsection{Rank Logic}
-In this paper we use the definition of $\FPR$ given by Grad\"{e}l and Pakusa
-\cite{}, an strictly more expressive extension of the rank logic introduced by
-Dawar et. al. cite{}. We briefly define this logic here. For more detail please
-see \cite{}. $\FPR$ is an extension of $\FPC$ with rank operators, which we now
-define.
-
-Let $\phi (\vec{x}, \vec {\nu} \leq \vec{t}, \vec{y}\vec{\mu} \leq \vec{s})$ be
-a numeric term, where $\vec{x}$ and $\vec{y}$ are tuples of variables ranging
-over the universe of the structure, $\vec{\nu}$ and $\vec{\mu}$ are tuples of
-variables ranging over the number type, and $\vec{s}$ and $\vec{t}$ are tuples
-of closed numeric terms that bound the range of $\vec{\nu}$ and $\vec{\mu}$
-respectively. Then let $\mathcal{A}$ be a structure and let
-$\mathbb{N}^{\leq\vec{t}} := \{\vec{n} \in \mathbb{N}^{\vert \vec{v} \vert}: n_i
-\leq t^{\mathcal{A}}_i\}$, and let $\mathbb{N}^{\leq \vec{s}}$ be defined
-similarly. Let $I:= A^{\vert \vec{x} \vert} \times \mathbb{N}^{\leq \vec{t}}$
-and $J := A^{\vert \vec{y} \vert} \times \mathbb{N}^{\leq \vec{s}}$ Then let
-$M^{\mathcal{A}}_\phi : I \times J \rightarrow \mathbb{N}$ be defined by
-$M^{\mathcal{A}}_\phi (\vec{a}\vec{n}, \vec{b}\vec{m}):=
-\phi^{\mathcal{A}}(\vec{a}\vec{n},\vec{b}\vec{m})$.
-
-The rank operator is then defined as $[rk (\vec{x}, \vec {\nu} \leq \vec{t},
-\vec{y}\vec{\mu} \leq \vec{s}, \pi \leq r). \phi]$, where $\pi$ is a variable
-ranging over the number sort and $r$ is a closed numeric term that bounds $\pi$.
-The value of the rank term for a structure $\mathcal{A}$ and an assignment $\pi
-\mapsto p$, where $p$ is prime, is given by the rank of $M^{\mathcal{A}}_\phi$
-mod $p$, as understood as a matrix over $\mathbb{F}_p$.
-
-\subsection{Symmetric Circuits}
-This still needs to be filled in
 \end{document}

### 2017-07-26 sections/introduction.tex
26/07/2017

--- 2016-12-14 paper.tex
@@
-\documentclass[12pt]{report}
+\documentclass[../paper.tex]{subfiles}
+\begin{document}
+A finite relational structure, such as a graph, can be represented as a binary
+string in a standard way (for instance, by enumerating its adjacency matrix).
+When we speak of the computational complexity of properties of graphs, we assume
+such an encoding in order to present the structure as input to a machine or
+circuit or other appropriate computational model. The properties of structures
+we are interested in studying are invariant under isomorphisms. This requirement
+translates into an invariance condition on sets of strings---say that a language
+$L \subseteq \{0,1\}^\star$ is a \emph{graph property} if, whenever $x \in L$
+for a string $x$ representing a graph $G$, we have $y\in L$ for any string $y$
+obtained from $x$ by re-ordering the vertices of $G$. The central open question
+in descriptive complexity---whether there is a logical characterisation of the
+polynomial-time decidable properties of finite relational structures--- can then
+be understood as the question of characterizing those languages $L$ that are in
+$\PT$ and are graph properties.
 
-% This first part of the file is called the PREAMBLE. It includes
-% customizations and command definitions. The preamble is everything
-% between \documentclass and \begin{document}.
+Anderson and Dawar~\cite{AndersonD17} study this question through the lens of
+circuit complexity, by considering \emph{symmetric circuits}. These are circuits
+that necessarily accept graph properties, with this fact explicitly witnessed by
+automorphisms of the circuit. To be precise, we can think of a property of
+(directed) graphs on $n$ vertices as being given by a Boolean function $f:
+\{0,1\}^{n^2} \rightarrow \{0,1\}$ which takes as input the $n^2$ potential
+edges and outputs $1$ if the property is satisfied by the graph given on the
+input. The function $f$ is \emph{graph-symmetric} in the sense that any
+permutation of its inputs induced by a permutation of the $n$ vertices leaves
+$f$ unchanged (note this is not the same thing as requiring that $f$ is
+invariant under all permutations of its inputs). A symmetric circuit is a
+circuit computing a Boolean function of $n^2$ inputs where each permutation of
+$[n]$ can be extended to an automorphism of the circuit. Such a circuit
+necessarily computes an invariant function.
 
-\usepackage[margin=1in]{geometry} % set the margins to 1in on all sides
-\usepackage{graphicx} % to include figures
-\usepackage{amsmath} % great math stuff
-\usepackage{amsfonts} % for blackboard bold, etc
-\usepackage{amsthm} % better theorem environments
+The results of~\cite{AndersonD17} show a tight relationship between the
+decdability of a graph property by means of a polynomial-size family of
+symmetric circuits and its definability in extensions of fixed-point logic. In
+particular, they show that a property is definable in fixed-point logic with
+counting ($\FPC$) if, and only if, it is decidable by a polynomially-uniform
+family of symmetric circuits using Boolean and majority gates (or, equivalently,
+threshold gates). Without the symmetry restriction, polynomial-size families of
+circuits have the same computational power whether we restrict ourselves to
+Boolean gates only or allow richer bases such as threshold gates. One
+consequence of the results in~\cite{AD14} is that, with the requirement of
+symmetry, these different bases do yield different expressive power, suggesting
+some lack of robustness to the model. One of the results in the present paper
+shows that the model with majority circuits is robust in the sense that it is
+able to simulate, by means of symmetric circuits, any symmetric circuit composed
+of gates computing Boolean functions that are themselves symmetric (in the sense
+that they are invariant under \emph{all} permutations of their inputs. Thus, any
+property decidable by a polynomially-uniform family of such circuits is
+definable in $\FPC$.
 
-% various theorems, numbered by section
+This motivates the study of symmetric circuit families that involve gates which
+themselves may compute non-symmetric functions. In particular, motivated by the
+study of rank logic~\cite{DGHL09,GP15}, we consider gates that are
+\emph{matrix-symmetric}. These are gates computing a Boolean function $f:
+\{0,1\}^{A \times B} \rightarrow \{0,1\}$ which is invariant under arbitrary
+permutations of $A$ and $B$. A typical example is the function computing the
+rank of an $A \times B$ $0$-$1$ matrix. We show that the support theorem of
+Anderson and Dawar can be shown to hold, even in the presence of
+matrix-symmetric gates. This allows us to show that definability in the logic
+fixed-point with rank ($\FPR$) is the same as decidability by
+polynomially-uniform families of symmetric circuits with rank gates.
+% Another extension of $\FPC$ that has received much attention in the
+% descriptive complexity literature is the class $\CPTC$ of \emph{choiceless
+% polynomial time with counting}. The work of~\cite{AD14} leaves open the
+% question of obtaining a circuit characterization of this class and it was
+% suggested there that this would require a relaxation of the notion of symmetry
+% used in defining symmetric circuits. In particular, while $\CPTC$ is based on
+% a machine model designed to preserve symmetry by forbidding choices, the
+% polynomial time and space restrictions apply int he context of the symmetries
+% fo a \emph{single input structure}. In this paper, we consider a relaxation of
+% the notion of symmetric circuit intended to capture exactly this intuition.
+% However, we are able to show that this does not yield a characterization of
+% $\CPTC$. In particular, we show that no family in this class of relaxed
+% symmetric circuits can distinguish odd from even Cai-F\"urer-Immerman graphs,
+% something we know is do-able in $\CPTC$~\cite{DRR08}.
 
-\newtheorem{thm}{Theorem} \newtheorem{claim}{Claim}
-\newtheorem{remark}{Remark} \newtheorem{definition}{Definition}
-\newtheorem{lem}[thm]{Lemma} \newtheorem{prop}[thm]{Proposition}
-\newtheorem{cor}[thm]{Corollary} \newtheorem{conj}[thm]{Conjecture}
-
-\DeclareMathOperator{\id}{id}
-
-\newcommand{\bd}[1]{\mathbf{#1}} % for bolding symbols
-\newcommand{\RR}{\mathbb{R}} % for Real numbers
-\newcommand{\ZZ}{\mathbb{Z}} % for Integers
-\newcommand{\MB}{\mathbb{B}_{\matsym}} % for Integers
-\newcommand{\SB}{\mathbb{B}_{\sym}} % for Integers
-\newcommand{\col}[1]{\begin{matrix} #1 \end{matrix} \right]}
-\newcommand{\comb}[2]{\binom{#1^2 + #2^2}{#1+#2}}
-\newcommand{\stab}{\text{\textbf{Stab}}}
-\newcommand{\setstab}{\text{\textbf{SetStab}}}
-\newcommand{\matstab}{\text{\textbf{MatStab}}}
-\newcommand{\inv}{\text{\textbf{inv}}}
-\newcommand{\aut}{\text{\textbf{Aut}}}
-\newcommand{\kernal}{\text{\textbf{ker}}}
-\newcommand{\alt}{\text{\textbf{Alt}}}
-\newcommand{\sym}{\text{\textbf{Sym}}}
-\newcommand{\rank}{\text{\textbf{rk}}}
-\newcommand{\orb}{\text{\textbf{Orb}}}
-\newcommand{\SP}{\text{\textbf{SP}}}
-\newcommand{\maj}{\text{\textbf{Maj}}}
-\newcommand{\dom}{\text{\textbf{Dom}}}
-\newcommand{\child}{\text{child}}
-\newcommand{\countgate}{\text{count}}
-\newcommand{\agree}{\text{AGREE}}
-\newcommand{\supp}{\text{SUPP}}
-\newcommand{\rankparam}{\text{PARAM}}
-
-\newcommand{\Alpha}{A}
-\newcommand{\matsym}{\text{\textbf{MatSym}}}
-\begin{document}
-
-\nocite{*}
-
-\title{Circuits}
-
-\author{Gregory Wilsenach \\ 
-Computer Laboratory \\
-University of Cambridge}
-
-\maketitle
-
-\tableofcontents
-
-\chapter{Introduction}
-
-\chapter{Background}
-
-\chapter{Symmetric Circuits}
-
-\chapter{Extending Symmetric Circuits}
-
-\chapter{Matrix-Symmetric Circuits}
-
-The symmetric circuits of Anderson and Dawar \cite{} have been shown to express
-$FPC$.
-
-In this section we develop a notion of a matrix-symmetric circuit, an extension
-of the symmetric circuit defined by Anderson and Dawar \cite{}. This is my
-latest version of the support and circuit capturing result.
-
-\section{}
-
-\section{Circuits and Symmetry}
-\begin{definition}
-  Let $A$ and $B$ be sets, say that a function $f: \{ 0,1 \}^{A \times B}
-  \rightarrow \{ 0,1 \}$ is matrix-symmetric if for any $\omega: A \times B
-  \rightarrow \{0, 1\}$ and $(\alpha, \beta) \in \sym_A \times \sym_B$ we have
-  $f((\alpha, \beta)\cdot \omega) = f (\omega)$.
-  \\
-  A function $f: \{0,1\}^* \rightarrow \{0,1\}$ is matrix-symmetric iff for any
-  two finite sets $A$, $B$ we have that that $f|_{A \times B}$ is
-  matrix-symmetric (where $f|_{A \times B}$ is the restriction of the function
-  $f$ to inputs sequences of size $\vert A \times B \vert$ and where elements of
-  the input sequence are labelled by elements of $A \times B$).
-\end{definition}
-
-\section{The Support Theorem}
-
-Without a loss of generality we assume that $A$ and $B$ are always initial
-segments of the natural numbers.
-
-% Let $C$ be a circuit over some Boolean basis. For each gate $g \in C$ we
-% associate a relation $\omega_g$ (or just $\omega$ when the context makes it
-% clear). We say a gate is symmetric if that relation
-
-% So far we have defined a circuit over a Boolean basis where the circuit
-% elements all compute symmetric functions. The definition of an induced
-% automorphism only makes. As such, we begin by augmenting the definition of a
-% circuit and automorphism.
-
-\begin{definition}[Circuits on Structures]
-  For $\mathbb{B}_{\sym}$ a basis of Boolean symmetric functions,
-  $\mathbb{B}_{\matsym}$ a basis of Boolean matrix-symmetric functions and
-  $\tau$ a set of relation symbols, we define a $(\mathbb{B}_\sym,
-  \mathbb{B}_\sym, \tau)$-circuit $C_n$ computing a $q$-ary query $Q$ is a
-  structure $\langle G, W, \Omega, \Sigma, \Lambda, L\rangle$.
-  \begin{itemize}
-  \item $G$ is called the set of gates of $C_n$ and $\vert C_n \vert := \vert G
-    \vert$.
-  \item $W \subseteq G \times G$, where $W$ is called the wires of the circuit.
-    $(G,W)$ must be a directed acyclic graph. For $g \in G$ we $H_g := \{ h \in
-    C_n : W(h,g)\}$ be the set of children of $g$.
-  \item $\Omega$ is an injective function from $[n]^q$ to $G$. The gates in the
-    image of $\Omega$ are called the output gates. When $q = 0$, $\Omega$ is a
-    constant function mapping to a single output gate.
-  \item $\Sigma$ is a function from $G$ to $\mathbb{B}_\sym \uplus
-    \mathbb{B}_\matstab \uplus \tau \uplus \{0,1\} $ which maps input gates to
-    $\tau \uplus \{0,1\}$ and where $\Sigma^{-1} (0) \leq 1$ $\Sigma^{-1} (1)
-    \leq 1$ and the internal gates get mapped into $\mathbb{B}_\sym \uplus
-    \mathbb{B}_\matstab$. Gates mapped to $\tau$ are called relational gates and
-    gates mapped to 1 or 0 are called constant gates.
-  \item $\Lambda$ is a sequence of injective functions $(\Lambda_R)_{R \in
-      \tau}$ where for each $R \in \tau$, $\Lambda_R$ maps each relational gate
-    $g$ with $R = \Sigma (g)$ to the tuple $\Lambda_R (g) \in [n]^r$, where $r$
-    is the arity of the symbol $R$. When no ambiguity arises we write $\Lambda
-    (g)$ for $\Lambda_R (g)$.
-  \item $L$ is the set of labelings of $C_n$. Let $g \in G$ be an internal gate
-    and $H$ be the children of $g$. Then let $S$ be a set where $\{0,1\}^S =
-    \dom(\Sigma (g))$. Then $L$ is a function that assigns to $g$ an onto
-    function $\omega_g:S \rightarrow H$. We call this the matrix labelling of
-    $g$.
-  \end{itemize}
-\end{definition}
-
-% \begin{definition}
-%   let $C = \langle G, W, \Omega, \Sigma, \Lambda, L\rangle$ be a
-%   $(\mathbb{B}_\sym, \mathbb{B}_\sym, \tau)$-circuit, then take $g_1,g_2 \in
-%   G$ such that $\Sigma (g_1) \Sigma(g_2) \in \mathbb{B}_\matsym$.
-
-\begin{definition}
-  Let $\omega_1: A \times B \rightarrow H$ and $\omega_2: A' \times B'
-  \rightarrow H'$ define the equivalence relation $\sim$ as $\omega_1 \sim
-  \omega_2$ iff $\omega_1$ and $\omega_2$ have the same domain and co-domain and
-  there exists $(\alpha, \beta) \in \sym_A \times \sym_B$ and for all $(a,b) \in
-  A \times B$ we have $\omega_1 = \omega_2 \circ (\alpha, \beta)$.
-\end{definition}
-
-% \begin{definition}
-%   Let $\omega_1: A \rightarrow H$ and $omega_2:A' \rightarrow H'$. Define the
-%   equivalence relation $\sim$ as $\omega_1 \sim \omega_2$ iff $\omega_1$ and
-%   $\omega_2$ have the same domain and co-domain, and
-% \end{definition}
-
-\begin{definition}[Automorphism]
-  let $C = \langle G, W, \Omega, \Sigma, \Lambda, L\rangle$ be a
-  $(\mathbb{B}_\sym, \mathbb{B}_\sym, \tau)$-circuit computing at $q$-ary query
-  on structures of size $n$. Let $\sigma \in \sym_n$ and $\pi: G \rightarrow G$
-  be a bijection such that
-  \begin{itemize}
-  \item for all gates $g, h \in G$, $W(g,h)$ iff $W(\pi g, \pi h)$,
-  \item for all output tuples $x \in [n]^q$, $\pi \Omega (x) = \Omega (\sigma
-    x)$,
-  \item for all gates $g \in G$, $\Sigma (g) = \Sigma (\pi g)$, and
-  \item for each relational gate $g \in G$, $\sigma \Lambda (g) = \Lambda (\pi
-    g)$
-  \item for each internal gate $g$ if $\Sigma (g) \in \mathbb(B)_\matsym$. Then
-    we have that $L(\pi g) \sim \pi \circ L(g)$.
-  \end{itemize}
-\end{definition}
-
-\begin{remark}
-  I also need a new notion of robustness here in order to collapse gates that
-  have the same children and equivalent labelings are properly regarded as being
-  the same gate.
-\end{remark}
-% \begin{definition}
-%   Let $C$ be a circuit, $g$ be a gate in $C$, $H$ be $g$'s set of children and
-%   let $\omega: A \times B \rightarrow H$ be a surjection, where $A$ and $B$
-%   are sets and $g$ takes $\vert A \vert \cdot \vert B \vert$ inputs. Call such
-%   an $\omega$ a matrix labeling for $g$.
-% \end{definition}
-
-% \begin{definition}
-%   Let $C$ be a circuit and $g_1$ and $g_2$ be gates in $C$. Let $\sigma \in
-%   \sym_n$ be a permutation such
-% \end{definition}
-
-\begin{definition}
-  Let $\omega$ be a matrix labeling for $g$. Define the matrix stabilizer for
-  $\omega$, denoted by $\matstab(\omega)$, to be the set of all $\sigma \in
-  \sym_n$ such that $\sigma H = H$ and there exists $(\alpha, \beta) \in \sym_A
-  \times \sym_B$ such that for all $(i,j) \in A \times B$ we have that $\omega
-  (\alpha i, \beta j) = \sigma \omega (i,j)$.
-\end{definition}
-
-\begin{definition}
-  Let $g$ be a gate with matrix labeling $\omega$, $h,h' \in H$ and $\sigma \in
-  \sym_n$. We say that a pair $(h, h')$ is compatible with $(\sigma, \omega)$ if
-  $\sigma h, \sigma h' \in H$ and there exists $(\gamma_1, \gamma_2),
-  (\gamma_1', \gamma_2') \in \sym_A \times \sym_B$ s.t.
-  \begin{align*}
-    &(\gamma_1, \gamma_2) \cdot \omega^{-1} (h) = \omega^{-1}(\sigma h), \text{ and} \\ 
-    &(\gamma_1', \gamma_2') \cdot \omega^{-1} (h') = \omega^{-1}(\sigma h'),
-  \end{align*}
-  and for all $(i,j) \in \omega^{-1}(h)$, $(i',j') \in \omega^{-1}(h')$ we have
-  that
-  \begin{align*}
-    &i =i' \implies \gamma_1(i) = \gamma_1'(i'), \text{ and} \\
-    &j =j' \implies \gamma_2(j) = \gamma_2'(j').
-  \end{align*}
-
-\end{definition}
-
-\begin{lem}
-  Let $g$ be a gate, $\omega$ be a matrix labeling of $g$, $\sigma \in \sym_n$.
-  Then $\sigma \in \matstab(\omega)$ iff for all $h,h' \in H$ we have that
-  $(h,h')$ is compatible with $(\sigma, \omega)$.
-\end{lem}
-
-\begin{proof}
-  $`\Rightarrow'$: We have that $\sigma \in \matstab(\omega)$ and so there
-  exists $(\alpha, \beta) \in \sym_A \times \sym_B$ such that for all $(i,j) \in
-  A \times B$ we have $\sigma \omega (i,j) = \omega (\alpha i, \beta j)$. From
-  compatibility we have that $h,h' \in H$ Let $h, h' \in H$ . Let $(\gamma_1,
-  \gamma_2) := (\gamma_1', \gamma_2') := (\alpha, \beta)$. This assignment is
-  sufficient to prove the direction.
-
-  $`\Leftarrow'$: Suppose for all $h,h' \in H$ we have $(\gamma_1, \gamma_2),
-  (\gamma_1, \gamma_2') \in \sym_A \times \sym_B$ satisfying the above
-  requirements. Notice that for a given $i \in A$ and any $j, j' \in B$, let $h
-  = \omega(i,j)$ and $h' = \omega(i,j')$, then we have that $\gamma_1 (i) =
-  \gamma_1'(i)$. It follows that we can define a $\alpha \in \sym_A$ by
-  $\alpha(i) = \gamma_1 (i)$. Similarly we can define $\beta \in \sym_B$ by
-  $\beta (j) = \gamma_2 (j)$.
-
-\end{proof}
-
-\begin{definition}
-  Let $g$ be a gate with matrix labeling $\omega$. Let $(\sigma, h, h') \in
-  \sym([n]) \times H^2$. Say that $(\sigma, h, h')$ is useful if $(h,h')$ is
-  incompatible with $(\sigma, \omega)$.
-
-  Say that two distinct pairs $(\sigma_1, h_1, h_1'), (\sigma_2, h_2, h_2') \in
-  \sym([n]) \times H^2$ are mutually independent if
-  \begin{itemize}
-  \item $\sigma_2 h_1 = h_1$,
-  \item $\sigma_2 \sigma_1 h_1 = \sigma_1 h_1$,
-  \item $\sigma_2 h_1' = h_1'$,
-  \item $\sigma_2 \sigma_1 h_1' = \sigma h_1'$,
-  \end{itemize}
-  We say that a set $S \subseteq \sym([n]) \times H^2$ is useful if each pair in
-  it is useful. We say that S is independent if each pair of distinct pairs in
-  $S$ are mutually independent.
-\end{definition}
-
-We denote the usual equivalence relation on $\sym_n$ from the (right) cosets of
-$\matstab(\omega)$ by $\sim_\omega$.
-
-\begin{lem}
-  Let $\sigma_1, \sigma_1 \in \sym_n$ and suppose $\sigma_1 \sim_\omega
-  \sigma_2$ then for any $(h,h') \in H^2$ we have that $(h,h')$ is compatible
-  with $(\sigma_1, \omega)$ iff $(h,h')$ is compatible with $(\sigma_2,
-  \omega)$.
-\end{lem}
-
-\begin{proof}
-  Suppose we have that $\sigma_1 \sim_\omega \sigma_2$. And additionally
-  supposed $(h, h')$ compatible with $(\sigma_1, \omega)$.
-
-  It follows there exists $(\alpha, \beta) \in \sym_A \times \sym_B$ such that
-  $\sigma_1 \omega (i,j) = \sigma_2\omega (\alpha i, \beta j)$, and we have
-  $(\gamma_1, \gamma_2), (\gamma_1', \gamma_2') \in \sym_A \times \sym_B$
-  satisfying the requirements of compatibility. We note that $(\alpha, \beta)
-  \cdot \omega^{-1}(\sigma_1 h) = \omega^{-1}(\sigma_2 h)$. Thus by composition
-  we have that $(\alpha \gamma_1, \beta \gamma_2) \cdot \omega^{-1}(h) =
-  \omega^{-1}(\sigma_2 h)$ and $(\alpha \gamma_1', \beta \gamma_2') \cdot
-  \omega^{-1}(h') = \omega^{-1}(\sigma_2 h')$, and clearly the remaining
-  requirement for compatibility follows from the bijectivity of $\alpha$ and
-  $\beta$. The result follows. The other direction of the implication follows
-  from symmetry.
-\end{proof}
-
-\begin{claim}
-  \label{claim:useful-independant-set}
-  Let $g$ be a rank gate with labeling $\omega$ and child set $H$. Let $S$ be a
-  useful and independent. We then have that $\vert \sym_n: \matstab(\omega)
-  \vert \leq 2^{\vert S \vert}$.
-\end{claim}
-
-\begin{proof}
-  Let $R \subseteq S$ and define $\sigma_R = \Pi_{(\sigma, h, h') \in R} \sigma$
-  (with some arbitrary order assumed on $S$). Let $R$ and $Q$ be distinct
-  subsets of $S$ and WLOG let $\vert R \vert \geq \vert Q \vert$. We want to
-  show that we don't have $\sigma_R \omega \sim_\omega \sigma_Q \omega$. Pick
-  any $(\sigma, h, h') \in R/Q \neq \emptyset$. Given that $\sigma_R h = \sigma
-  h$ and $\sigma_R h' = \sigma h'$ it is easy to see that the usefulness of
-  $(\sigma, h,h')$ implies the incompatibility of $(h,h')$ with with $(\omega,
-  \sigma_R)$. Moreover, the fact that $\sigma_Q h = h$ and $\sigma_Q h' = h'$
-  makes it easy to see $(h,h')$ is compatible with $(\omega, \sigma_Q)$. From
-  the above lemma we may conclude that that we do not have $\sigma_R \sim_\omega
-  \sigma_Q$, and the result follows.
-\end{proof}
-
-The following two lemmas proved by Anderson and Dawar \cite{} are both of use in
-proving the following theorem.
-
-\begin{lem}
-  \label{lem:big-or-small}
-  For any $\epsilon$ and $n$ such that $0 < \epsilon < 1$ and $\log n \geq
-  \frac{4}{\epsilon}$, if $\mathcal{P}$ is a partition of $[n]$ with $k$ parts,
-  $s = [\sym_n : \setstab (\mathcal{P})]$ and $n \leq s leq 2^{n^{1-\epsilon}}$,
-  then $\min \{k, n-k\} \leq \frac{8}{\epsilon} \frac{\log s}{\log n}$.
-\end{lem}
-
-\begin{lem}
-  \label{lem:small-means-support}
-  For any $\epsilon$ and $n$ such that $0 < \epsilon < 1$ and $\log n \geq
-  \frac{8}{\epsilon^2}$, if $\mathcal{P}$ is a partition of $[n]$ with $\vert
-  \mathcal{P} \vert \leq \frac{n}{2}$, $s:= [\sym_n : \setstab (\mathcal{P})]$
-  and $n \leq s \leq 2^{n^{1-\epsilon}}$, then $\mathcal{P}$ contains a part $P$
-  with at least $n - \frac{33}{\epsilon} \cdot \frac{\log s} {\log n}$.
-\end{lem}
-
-If $g$ is a symmetric gate (i.e. the usual gates in a circuit) we note that
-$\orb(g) = [\sym_n : \stab (g)]$ by the orbit-stabilizer theorem.
-
-If $g$ is a matrix-symmetric gate then $\orb(g) = [\sym_n:\matstab (\omega)]$,
-where $\omega$ is the matrix labelling associated with $g$.
-
-\begin{thm}
-  For any $\epsilon$ and $n$ such that $\frac{2}{3} \leq \epsilon \leq 1$ and $n
-  \geq \frac{128}{\epsilon^2}$, if $C$ is a symmetric, rigid circuit on
-  structures of size $n$ and $s := \max_{g \in C} \vert \orb (g)\vert \leq
-  2^{n^{1-\epsilon}}$, then, $SP(C) \leq \frac{33}{\epsilon}\frac{log s}{log
-    n}$.
-\end{thm}
-
-\begin{proof}
-  It is easy to see that if $g$ is a gate in $C$ then $\stab (g) \subseteq
-  \setstab(\SP(g))$, and so $s \geq \orb(g) = [\sym_n : \stab(g)] \geq [\sym_n :
-  setstab(\SP(g))]$. Thus if $\vert \SP(g) \vert \leq frac{n}{2}$, then from
-  Lemma \ref{lem:small-means-support}, we have $\| SP (g) \| \leq
-  \frac{33}{\epsilon} \cdot \frac{\log s} {\log n}$. The result thus follows
-  from showing that for each $g$ in $C$ we have that $\vert \SP (g) \vert \leq
-  \frac{n}{2}$.
-
-  % Include some detail here for constant and relational gates
-  The cases where $g$ is a constant or relational gate are easy to handle.
-
-  We now consider the case for internal gates. Let $g$ be the topologically
-  first internal gate with $\vert \SP(g) \vert > \frac{n}{2}$. If $g$ is not a
-  matrix-symmetric gate then the result follows from the argument presented by
-  Anderson and Dawar \cite{}. Suppose $g$ is a matrix-symmetric gate, and
-  suppose $g$ has a labelling $\omega$. We now argue that this leads to a
-  contradiction.
-
-  Let $k' := \lceil \frac{8 \log s}{\epsilon \log n} \rceil$. From the
-  assumptions on $s, n$ and $\epsilon$ we have that $k' \leq
-  \frac{1}{4}n^{1-\epsilon} < \frac{n}{2}$. Lemma \ref{lem:big-or-small} implies
-  that $n - \vert \SP(g) \vert \leq k'$
-
-  From Claim \ref{claim:useful-independant-set} it remains to show that we can
-  construct a sufficiently large useful and independent set of gate-automorphism
-  pairs $S$. Divide $[n]$ into $\lfloor \frac{n}{k' + 2} \rfloor$ disjoint sets
-  $S_i$ of size $k' + 2$ and ignore the elements left over. It follows that for
-  each $i$ there is a permutation $\sigma_i$ which fixes $[n] / S_i$ pointwise
-  but moves $g$. Suppose there was no such $\sigma_i$ it follows that every
-  every permutation that fixes $[n]/S_i$ pointwise fixes $g$. Thus the partition
-  of all the singletons in $[n]/S_i$ and $S_i$ is a supporting partition. As
-  $\SP(g)$ is the coarsest partition it follows that $\vert \SP(g) \vert \leq n
-  - (k'+2) + 1 = n - k' - 1$, which contradicts the inequality $n - \vert \SP(g)
-  \vert \leq k'$.
-
-  Since $g$ is moved by each $\sigma_i$ and $C$ is rigid it follows that we
-  don't have $\sigma_i \notin \matstab(\omega)$. Thus there exists $(h_i, h_i')$
-  that is inconsistent with $(\sigma_i, \omega)$, and so the triple $(\sigma_i,
-  h_i, h_i')$ is useful.
-
-  Let $\SP (h)^*$ be the union of all parts of $\SP(h)$ except for the largest
-  part. Let $Q_i = \SP(h_i)^* \cup \SP(\sigma_i h_i)^* \cup \SP (h_i')^* \cup
-  \SP (\sigma_i h_i')^*$. Then note that if $\sigma_j$ fixes $Q_i$ then by
-  construction, we have that $\sigma_j \in \stab_n(\SP(h_i)) \cap
-  \stab_n(\SP(\sigma_i h_i)) \cap \stab_n(\SP(h_i')) \cap \stab_n(\SP(\sigma_i
-  h_i'))$
-
-  Define a graph $K$ with vertices given by the sets $S_i$ and an edge from
-  $S_i$ to $S_j$ (with $i \neq j$) if $Q_i \cap S_j \neq \emptyset$. It follows
-  then that if there is no edge between $S_i$ and $S_j$ then $(\sigma_i, h_i,
-  h_i')$ and $(\sigma_j, h_j, h_j')$ are mutually independent. It remains to
-  argue that $K$ has a large independent set. This is possible as the out-degree
-  of $S_i$ in $K$ is bounded by
-  \begin{align*}
-    \vert Q_i \vert \leq \|SP(h_i) \| + \|SP(\sigma_i h_i) \| + \|SP(h_i') \| + \|SP(\sigma_i h_i') \leq 4 \cdot \frac{33\log s}{\epsilon \log n}
-  \end{align*}.
-
-  This follows as the sets $S_i$ are disjoint and we may apply Lemma
-  \ref{lem:small-means-support} to each of the child gates. It follows that the
-  average total degree (in + out degree) of $K$ is at most $2 \cdot \vert Q_i
-  \vert \leq 34 \cdot k'$. Now greedily select a maximal independent set in $K$
-  by repeatedly selecting $S_i$ with the lowest total degree and eliminating it
-  and its neighbours. This action does not affect the bound on the average total
-  degree of $K$ and hence determines an independent set $I$ in $K$ of size at
-  least
-  \begin{align*}
-    \frac{\lfloor \frac{n}{k' + 2} \rfloor}{34k' + 1} \geq \frac{n - (k'+2)}{34k'+1k'+2} \geq \frac{n\frac{7}{16}}{34k'^2 + 69k' +2} \geq \frac{n}{(16k')^2}.
-  \end{align*}
-
-  Take $S = \{(\sigma, h, h') : S_i \in I \}$. Then from the above argument we
-  have that $S$ is useful and independent.
-
-  Moreover, from Claim \ref{claim:useful-independant-set}, we have that $s \geq
-  \vert \orb(g) \vert \geq 2^{\vert S \vert} \geq 2^{\frac{n}{(16k')^2}}$ then
-  $n^{1-\epsilon} \geq \log s \geq n \cdot (\frac{128}{\epsilon}\frac{\log
-    s}{\log n})^{-2} > n \cdot (n^{1-\epsilon})^{-2} = n^{2\epsilon -1} \geq
-  n^{1-\epsilon}$. This is a contradiction.
-\end{proof}
-
-\section{Rigid Circuits}
-
-\begin{definition}
-  We say that a circuit $C$ has bijective labels if for each gate $g$ in $C$,
-  $L(g)$ is a bijection.
-\end{definition}
-
-\begin{lem}
-  \label{lem:bij_labels}
-  There is an algorithm that runs in polynomial time that takes in a circuit $C$
-  and outputs a circuit with unique gates $C'$. Moreover, if $C$ was symmetric
-  then $C'$ is symmetric. If $C$ is rigid then $C'$ is rigid.
-\end{lem}
-
-\begin{proof}
-  Let $S = 2*\vert C \vert$. Recurse through the gates of $C$ topologically and
-  let $h$ be the next gate topologically. If for all $g \in W(h, \cdot)$ we have
-  that $L\vert (g)^{-1}(h) \vert = 1$ continue on to the next gate. If not add
-  in a tower of $S$ $\and$ gates such that $h \rightarrow \and^h_1 \rightarrow
-  \ldots \rightarrow \and^h_S$ (i.e. we have a tower of $\and$ gates with $h$ as
-  input to $\and^h_1$ and the output of each $\and^h_i$ connected to the input
-  of each $\and^h_{i+1}$ for each $1 \leq i < S$). Now for each $g \in W(h,
-  \cdot)$, if $L(g)^{-1}(h) = \{ s_0, \ldots, s_{r}\}$, for each $1 \leq i \leq
-  r$ add in the wires $W(\and^h_i, g)$ and set $L(g)(s_{i}) = \and^h_i$. Now
-  continue on to the next gate topologically and run the above algorithm.
-
-  % First, notice that for a given gate $h$ and $k \in \mathbb{N}$, we can
-  % define
-  % a sub-circuit $h^k = 1 \and \cdots, 1 \and h$ (or rather a $k$-height tower
-  % of
-  % $k$ binary $\and$ gates with $h$ at the top and all other inputs set to
-  % $1$).
-  % We call $h$ the top of the sub-circuit $h^k$ and the bottom $and$ gate (the
-  % output of the sub-circuit) the bottom gate. We may think of this as a
-  % $k$-height copy of the gate $h$, in the sense that it has the same output as
-  % $h$ and similar orbits. We now use different copies to distinguish gates
-  % that
-  % otherwise have the same labelling.
-
-  % Let $h$ be the next gate topologically. Then let $r$ be maximal such that
-  % $W(h,g)$ and $\omega_g^{-1}(h) = \{ s^g_1, s^g_2, \ldots, s^g_r \}$. Then
-  % let
-  % $k$ be the height of the highest tower with $h$ at the top and with it's
-  % bottom connected to a gate in $W(h, \cdot)$. Then create a single
-  % $k+r-1$-height tower by adding in the appropriate number of binary $\and$
-  % gates below $h$.
-
-  % For each $g \in W(h, \cdot)$ and for each $\omega_g^{-1}(h) = \{s^g_1,
-  % s^g_2,\ldots , s^g_{r_g}\}$, set $L'(g)(s^g_1) = h$ each child starting with
-  % the $and$-gate child to $h$ add in a wire from from the $i$th gate in the
-  % tower to $g$ and set $L'(g)(s^g_{i+1}) = \and_i$, where $\and_i$ is the
-  % $i$th
-  % $\and$ gate in the tower starting with the $\and$ gate in the tower child to
-  % $h$. There are enough gates in the tower as $r_g \leq r$.
-
-  We call this updated circuit $C'$.
-
-  Firstly, note that after running the above algorithm for each $g$ the
-  labelling of $g$ will be a bijection. Moreover, it's easy to see that the
-  output of each gate remains unchanged, and as such the output of the circuit
-  is unchanged.
-
-  Secondly, notice that the size of $C'$ is at most $2*\vert C \vert^2$, and
-  note that the above algorithm runs in polynomial time.
-
-  Now suppose that $C$ is symmetric. Let $\sigma$ be a permutation on the input
-  universe and $\pi_C$ the induced automorphism on $C$. We now define $\pi$, the
-  induced automorphism on $C'$. For each gate $g$ in $C'$, if $g$ is in $C$ then
-  set $\pi(g) := pi_C(g)$. If $g$ is not in $C$ then $g$ must be some
-  $\and^h_i$, for some $h$ in $C$. Then set $\pi(\and^h_i) :=
-  \and^{\pi_C(h)}_i$. It is easy to see that $\pi$ is an automorphism, and $\pi$
-  extends $\sigma$.
-
-  Suppose that $C$ is rigid. It is easy to see that $C'$ will be rigid as well.
-
-\end{proof}
-
-% If $h$ is a binary $\and$ gate, then we say that $h$ has height $k+1$ if it
-% has a $k$-height tower of binary $and$ gates connected above it, with a
-% non-$\and$ gate $p$ connected to the final binary $\and$ gate, and all other
-% inputs connected to $1$. We then say that $h$ is the base of a tower of height
-% $k$ and type $p$.
-
-% Then for each $h \in W_g$, if $h$ is not a binary $\and$ gate, the let $k$ be
-% the largest integer such that there a gate $h' \in W(h, \cdot)$ which is the
-% base of a tower of height $k$ and type $h$. it's output directly connected to
-% one of the gates in $W(h^k, \cdot)$ (with k = 0 corresponding to just $h$).
-% Then each $i \in \{1, \ldots , \vert \omega^{-1}(h)\vert\}$ add into the
-% circuit $h^{k+i}$ and wire it to $g$. Notice that this step requires adding
-% $\vert \omega^{-1}(h) \vert -1$ gates to the circuit. For some assumed
-% ordering $\dom(\omega)$, let $\{s_0, \cdot, s_m\} = \omega^{-1}(h)$. Define
-% $L'(g)(s_i) = h^{k+i}$. Now continue on to the next gate topologically where
-% $L(g)$ is not a bijection, and execute the same process
-
-\begin{lem}
-  There is an algorithm that runs in polynomial time that takes in a circuit $C$
-  and outputs a circuit $C'$ such that $C'$ is rigid and has bijective labels.
-  Moreover, if $C$ was symmetric it follows that $C'$ will be symmetric.
-\end{lem}
-
-\begin{proof}
-  First run the algorithm from Lemma \ref{lem:bij_labels} on $C$, and call the
-  output circuit $C$.
-
-  Recurse through the gates of $C$ topologically. For each internal gate $g$,
-  for all $g'$ in $C$ such that $g \neq g'$, $W(\cdot, g) = W(\cdot, g')$, $W(g,
-  \cdot) = W(g', \cdot)$, $\Sigma(g) = \Sigma(g')$, $L(g) \sim L(g')$ and
-  $\Omega^{-1}(g) = \Omega^{-1}(g')$, delete $g'$ and for all $s \in L^{-1}(g')$
-  set $L(s) := g$.
-
-  Now re-run the algorithm from Lemma \ref{lem:bij_labels} on $C$ and output the
-  result.
-\end{proof}
-
-  \begin{lem}
-    Let $C = \langle G, W, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\SB, \MB,
-    \tau)-circuit$ on structures of size $n$. There is a deterministic algorithm
-    which runs in Poly($\vert C \vert$) and outputs a rigid $(\SB, \MB, \tau)
-    circuit$ $C'$ such that $G' = G$ and for any $g \in G$, and any input
-    $\tau$-structure $\mathcal{A}$ and any bijection $\gamma$ from $A$ to $[n]$,
-    $C[\gamma \mathcal{A}](g) = C'[\gamma \mathcal{A}](g)$ and if $C$ is
-    symmetric then so is $C'$.
-  \end{lem}
-
-  \begin{proof}
-
-  \end{proof}
-
-  \section{Computing Supports}
-  \begin{lem}
-    Let $C$ be a rigid $(\SB, MB, \tau)$-circuit on structures of size $n$ and
-    $\sigma \in \sym_n$. There is a deterministic algorithm which runs in time
-    Poly($\vert C \vert$) and outputs for each gate $g$ its image under the
-    automorphism $\pi$ induced by $\sigma$, if it exists.
-  \end{lem}
-  \begin{proof}
-    The proof proceeds by recursively going through the circuit and building the
-    mapping $\pi$ induced by $\sigma$.
-
-    Suppose $g$ is a constant gate, then $\pi g := g$. Suppose $g$ is a
-    relational gate, then there is at most one gate $g'$ such that $\Sigma (g) =
-    \Sigma (g')$ and $\sigma\Lambda (g') = \Lambda (g)$. If such a $g'$ exists
-    assign $\pi g := g'$, else terminate with failure.
-
-    If $g$ is an symmetric internal gate then (from rigidity) there is at most
-    one gate $g'$ such that $\Sigma (g) = \Sigma(g')$ and $W_{g'} = \pi W_g$.
-    Assign $\pi g := g'$ if such a gate exists, or else terminate with failure.
-
-    If $g$ is a matrix-symmetric internal gate then consider the set of gates
-    $g'$ such that $g'$ has children $\pi W_g$ and $\Sigma(g) = \Sigma(g')$, and
-    let $A \times B = \dom (Sigma(g))$. If no such gate $g'$ exists, terminate
-    with failure. Define $\sigma_{\pi, g'}:A \times B \rightarrow A \times B$ by
-    $\sigma_{\pi, g'} = \omega^{-1}_{g'} \pi \omega_{g}$. Then clearly
-    $\omega_{g'} \sigma_{\pi, g'} = \pi \omega_{g}$, and it's easy to show that
-    $\pi \omega_g \sim \omega_{g'}$ iff $\sigma_{\pi,g'} \in \sym_A \times
-    \sym_B$. But this just involves checking that $\sigma$ acts as a bijection
-    on $A$ and $B$ separately and, given that $\vert A \vert$ and $\vert B
-    \vert$ are both bounded by $\vert C \vert$, the algorithm which just
-    iterates through $A$ and $B$ is sufficient. If for every $g'$ it is found
-    that $\pi_{\sigma,g'}$ is not in $\sym_A \times \sym_B$ then terminate with
-    failure. If there is a $g'$ for which $\pi_{\sigma, g'} \in \sym_A \times
-    \sym_B$ then it is unique by rigidity and so set $\pi g := g'$.
-
-    If $g$ is an output gate, then check that for all tuples in $[n]^{q}$ we
-    have that $\pi \Omega (x) = \Omega (\sigma (x))$, and terminate with failure
-    if the condition is not met.
-
-    If the algorithm has not terminated with failure, output the automorphism.
-
-    The algorithm clearly runs in Poly($\vert C \vert$)
-  \end{proof}
-
-  \section{Evaluating Symmetric Circuits}
-  We need to extend two Lemmas in this section.
-
-\begin{lem}
-  Let $g$ be a matrix-symmetric gate in $C_n$ with children $H$. Let $\alpha \in
-  U^{\underbar{\sp(g)}}$, and suppose $\gamma_1, \gamma_2: U \rightarrow [n]$
-  with $\gamma^{-1}_1 \sim \alpha$ and $\alpha \sim \gamma^{-1}_2$. Let $A
-  \times B = \dom (L(g))$.
-
-  For an input structure $\mathcal{A}$, let $L^0_\gamma: A \times B \rightarrow
-  \{0,1\}$, where $L^0_\gamma (a,b):= C[\gamma \mathcal{A}] (L(g)(a,b))$.
-
-  Then $L^0_{\gamma_1} \sim L^0_{\gamma_2}$.
-\end{lem}
-
-\begin{proof}
-  We have that there exists a unique $\pi \in \sym_n$ such that $\pi \gamma_1 =
-  \gamma_2$. Moreover, since $\gamma^{-1}_1$ and $\gamma^{-1}_2$ are both
-  consistent with $\alpha$, it follows that $\pi$ must fix $\sp(g)$. Thus $L(g)
-  \sim \pi L(g)$, and so there exists $(\sigma, \lambda)$ such that $\pi L(g) =
-  L(g) (\sigma, \lambda)$.
-
-  We then have that,
-  \begin{align*}
-    L^0_{\gamma_1} (a,b) &= C_n[\gamma_1 \mathcal{A}](L(g)(a,b))\\
-                         & = C_n[\pi gamma_1 \mathcal{A}][\pi L(g)(a,b)] \\
-                         & = C_n[gamma_2 \mathcal{A}][L(g)((\sigma, \lambda)(a,b))]\\
-                         & = L^0_{\gamma_2} ((\sigma, \lambda) (a,b)),
-  \end{align*}
-  and it follows that $L^0_{\gamma_1} \sim L^0_{\gamma_2}$.
-
-\end{proof}
-
-\begin{lem}
-  Let $g$ be a matrix symmetric gate in $C_n$ with children $H$. Let $\alpha \in
-  U^{\underbar{\sp(g)}}$ and $\gamma: U \rightrrow [n]$ such that
-  $gamma^{-1}\sim \alpha$. Let $A \times B = \dom (L(g))$ and define
-  $L^{EV}_\alpha: A \times B \rightarrow \{0,1\}$ by
-  \begin{align*}
-    L^{EV}_\alpha (a,b):=
-    \begin{cases*}
-      1 & if $A_h \cap \EV_h \neq \emptyset$ 0 & otherwise
-    \end{cases*},
-  \end{align*}
-  where for $h \in W_g, A_h:= \{\beta \in U^{\underline{\sp(h)}} \vert \alpha
-  \sim \beta\}$. Then $L^0_\gamma = L^{EV}_\alpha$ and $\alpha \in \EV(g)$ iff
-  $\rk^u_p(L^0_\gamma)$
-\end{lem}
-\begin{proof}
-
-\end{proof}
-
-\begin{lem}
-  Let $g$ be a matrix-symmetric gate in $C_n$ with children $W_g$. $Let \alpha
-  \in U^{\underbar{\sp(g)}}$ and let $\gamma: U \rightarrow [n]$ such that
-  $\gamma^{-1} \sim \alpha$. Let $A \times B = \dom (L(g))$, and let
-  $f:\{0,1\}^{A \times B} \rightarrow \{0,1\}$ be the matrix-symmetric function
-  associated with $g$. Define $L^{EV}_\alpha: A \times B \rightarrow \{0,1\}$ by
-  \begin{align*}
-    L^{EV}_\alpha (a,b):=
-    \begin{cases*}
-      1 & if $A_h \cap \EV_h \neq \emptyset$ 0 & otherwise
-    \end{cases*},
-  \end{align*}
-  where for $h \in W_g, A_h:= \{\beta \in U^{\underline{\sp(h)}} \vert \alpha
-  \sim \beta\}$. Then $\alpha \in \EV_g$ iff $f(L^\EV_\alpha)$.
-\end{lem}
-\begin{proof}
-  First note that if $\alpha \in U^{\underbar{\sp{g}}}$ then $\alpha \in \EV_g$
-  iff we have that $C_n[\gamma \mathcal{A}](g)= f (L^0_\gamma) = 1$. Notice that
-  from Lemma \ref{} that this holds for any particular $\gamma$ iff it holds for
-  all such $\gamma$.
-
-  We now show that $L^\EV_\alpha = L^0_\gamma$, and so complete the proof.
-
-  Suppose for $(a,b) \in A \times B$ we have that $L^\EV_\alpha(a,b) = 1$. Let
-  $h:= L(g)(a,b)$. It follows that $A_h \cap \EV_h \neq \emptyset$, i.e there
-  exits $\beta \in \sp(h)$ such that $\beta \sim \alpha$ and there exists
-  $\gamma_h \in \Gamma(h)$ such that $\gamma^{-1}_h \sim \beta$. It follows from
-  transitivity and Lemma \ref{} that $\gamma_h \sim \alpha$ and so
-  $L^0_\alpha(a,b) = C_n[\gamma \mathcal{A}](h) = C_n[\gamma_h \mathcal{A}](h) =
-  1$.
-
-  Now suppose that $L^0_\gamma (a,b) = 1$
-\end{proof}
-
-\section{Translating to Formulas of FPC}
-Let $\mathcal{C} = (C_n)_{n \in \mathbb{N}}$ be a P-uniform family of
-polynomial-size symmetric $(\SB, \MB, \tau)$ circuits, and where $\MB$ is the
-rank basis. It remains to show that there is a formula $Q$ in the vocabulary
-$\tau \uplus \{\leq\}$ such that for any $n$ and $\tau$-structure $\mathcal{A}$
-with a universe $U$ of carnality $n$, the $q$-ary query defined by $C_n$ on the
-input $\mathcal{A}$ is defined by the formula $Q$ when interpreted in the
-structure $\mathcal{A}^\leq = \mathcal{A} \uplus \langle [n], \leq \rangle$.
-
-Since $\mathcal{C}$ is $P$-uniform, and from Lemmas \ref{} and \ref{} and the
-Immerman-Vardi theorem, we have an FP interpretation defining a rigid symmetric
-circuit with bijective labels equivalent to $C_n$ (which we also call $C_n$)
-over the the number sort of $\mathcal{A}^\leq$, where $\Phi = (\phi_G,\phi_W,
-\phi_\Omega, (\phi_s)_{s \in \SB \uplus \{rank\} \uplus \tau \uplus \{0,1\}},
-(\phi_{\and_R})_{R \in \tau}, \phi_L)$. We note that $Phi$ is a $t$-width
-interpretation over the universe $[n]$. So if $\mu, \nu, \nu_1, \ldots \in
-[n]^t$, the formulas are defined such that:
-
-\begin{itemize}
-\item $\phi_G(\mu)$ holds iff $\mu$ encodes a gate
-\item $\phi_W(\nu,\mu)$ holds iff $\nu$ and $\mu$ encode gates and if $g_{\nu}$
-  and $g_{\mu}$ are these two encoded gates respectively then $W(g_{\nu},
-  g_{\mu})$.
-\item $\phi_{\Omega}(\nu_1, \ldots, \nu_q, \mu)$ holds iff $\nu_1, \ldots, nu_q$
-  each encode numbers less than or equal to $[n]$ and $\Omega(\nu_1, \ldots,
-  \nu_q) = g_\mu$.
-\item For all $s \in \SB \uplus \{rank\} \uplus \tau \uplus \{0,1\}$ we have
-  that $\phi_s (\mu)$ holds iff $\mu$ encodes a gate such that $\Sigma(g_\mu) =
-  s$ (or, in the case that $s = \rank$, we require that $\Sigma(g_\mu)$ is a
-  rank symbol.)
-\item For all $R \in \tau$ with arity $r$ we have that $\phi_{\and_R}(\nu_1,
-  \ldots, \nu_r, \mu)$ holds iff $\nu_1 , \ldots , \nu_r$ encodes numbers less
-  than or equal to $[n]$, $\mu$ encodes a gate such that $\Sigma(g_\mu) = R$ and
-  $\Lambda_R(g_\mu) = (\nu_1, \ldots, \nu_r)$.
-\item $\phi_L(\nu, \mu, \nu_1, nu_2)$ holds iff $\nu$ and $\mu$ encode gates and
-  $\nu_1, \nu_2$ encode numbers, and $L(g_{\mu})(\nu_1,\nu_2) = g_\nu$. If
-  $\dom(L (g_\mu)) = [a] \times [b]$, then the encoding of $[a]$ and $[b]$ are
-  initial segments under the lithographically induced order. Moreover, the
-  encodings of $[a]$ and $[b]$ preserve the order relation.
-\end{itemize}
-
-From now on we use $\mu$ and $\nu$ to stand for $t$-length sequences encoding
-gates, and use $\nu_1, \ldots$ for sequences that encode numbers. We use $g_\mu$
-and $g_\nu$ for the gates encoded by these sequence, while simply identifying
-the sequence $\nu_i$ with the number it encodes.
-
-Using the Immerman-Vardi Theorem, we can define an FP($\leq$) formula
-$\rankpara$ such that $\langle [n], \leq\rangle \models \rankpara[g,p,u]$ iff
-$\langle [n], \leq\rangle \models \phi_G[g] \land \phi_{\rank}[g]$ and the rank
-gate $g$ (as per the interpretation) computes the rank over characteristic $p$
-and has threshold $u$.
-
-We can define FP($\leq$) formulas $\max_A$ and $\max_B$ such that $\langle [n],
-\leq \rangle \models \max_A[g, \nu_1]$ iff $\nu_1$ encodes $a$, where
-$\dom(L(g)) = [a]\times [b]$. Similarly, $\langle [n], \leq \rangle \models
-\max_B[g, \nu_1]$ iff $\nu_1$ encodes $b$ where $\dom(L(g)) = [a] \times [b]$.
-
-Again using Lemma \ref{} and the Immerman-Vardi theorem, we can construct a
-formula $\supp$ such $\langle [n], \leq \rangle \models \supp[g,u]$ iff $\langle
-[n], \leq \rangle \models \phi_G[g]$ and $u$ is in $sp(g)$. This formula can be
-used as in \cite{} to inductively define $\supp_i(g,u)$ for each $i \in [n]$
-which holds iff $u$ is the $i$th element of the support of $g$.
-
-Define the $\agree$ and $\theta_s$ formulas for all $s \in \SB \uplus \tau
-\uplus \{0,1\}$ as in \cite{}.
-
-Now we define the formula
-\begin{align*}
-  \theta_{\rank}:= (\mu, \bar{x}) := \bigwedge_{1 \leq i < j \leq k} x_i
-  \neq x_j \wedge \forall \bar{y} ( [ \rank (x \leq \phi_{mr}, y \leq
-  \phi_{mc}, \pi \leq r). \theta^{'} ] ),
-\end{align*}
-\begin{align*}
-  \theta^{'}(a,b):= \exists \nu (W(\nu, \mu) \wedge \agree (\mu,\nu, \bar{x}, \bar{y}) \wedge \phi_L (\mu, \nu, a, b) \wedge V(\nu, y))
-\end{align*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\chapter{October 27th: Counting Gates Simulate Symmetric Gates}
-
-In this chapter we prove that symmetric circuits with majority gates are at
-least as powerful as symmetric circuits over any other Boolean basis consisting
-of symmetric functions.
-
-Recall the following that $\mathbb{B} = \{ \neg , \wedge , \lor \}$ and
-$\mathbb{B}_\maj = \{ \maj \} \cup \mathbb{B}$.
-
-Let $F: \{0,1\}^* \rightarrow \{0,1\}$ be a symmetric Boolean function. Since
-$F$ is symmetric we note that for a fixed size input the output of $F$ is
-entirely determined by the number of 1's in its input. Then let
-$c_{F}:\mathbb{N} \rightarrow 2^{\mathbb{N}}$ define a function where $c_{F}(n)$
-is the set of all $m \leq n$ such that for all $\vec{x} \in \{ 0,1 \}^n$ with
-$m$ 1's we have $F (\vec{x}) = 1$. Clearly a symmetric Boolean function $F$ is
-entirely determined by $c_{F}$.
-
-\begin{prop}
-  \label{prop:fuctions-maj}
-  There is a polynomial $p(k)$ such that for any symmetric function $F$ and a
-  given $k \in \mathbb{N}$ there is a circuit $C_k$ on $k$ inputs over the basis
-  $\mathbb{B}_\maj$ which is symmetric, constant depth and with width bounded by
-  $p(k)$.
-\end{prop}
-
-\begin{proof}
-  We define the circuit $C_k$ for inputs $\vec{x} = ( x_1, \ldots, x_k )$.
-
-  For $a \in \mathbb{N}$ we define a get $\countgate_a$ by
-  \begin{align*}
-    &\countgate_a = \maj (x_1, \ldots, x_k, \underbrace {0, \ldots, 0}_{2a -
-      k}) \land \neg \maj (x_1, \ldots , x_k, \underbrace{0, \ldots,  0}_{2a - k + 2})\text{ if $a \geq \frac{k}{2}$,} \\
-    &\countgate_a = \maj (x_1, \ldots, x_k, \underbrace {1, \ldots, 1}_{x -
-      2a}) \land \neg \maj (x_1, \ldots , x_k, \underbrace{1, \ldots,
-      1}_{k - 2a -2}) \text{ if $a < \frac{k}{2}$. }
-  \end{align*}
-
-  Then let $g = \bigvee_{a \in c_{F_i}(k)}\countgate_a$ and let $C_{k}$ be the
-  circuit with input gates labeled by $\vec{x}$ and output gate $g$.
-
-  t is easy to see that $C_k$ is constant depth and it's width is a polynomial
-  in $k$. We have that in each layer of $C_{g'}$ each gate is connected to all
-  gates in the previous layer, and as such the circuit is symmetric.
-\end{proof}
-
-The above proposition has a straight forward application to circuit
-characterizations.
-
-\begin{prop}
-  Let $F = \{F_i : i \in I \}$ be a family of symmetric Boolean functions where
-  $F_i: \{0,1\}^* \rightarrow \{ 0,1 \}$.
-
-  Let $(C_n)_{n \in \mathbb{N}}$ be family of symmetric circuits over the
-  Boolean basis $\mathbb{B} \cup F$, where $C_n$ is a circuit on structures of
-  size $n$, and the size of each circuit in the family is bounded by some
-  function $f(n)$. Then there exists a polynomial $q(n)$ and a family of
-  symmetric circuits $(C_n')_{n \in \mathbb{N}}$ over $\mathbb{B}_\maj$, where
-  $C_n'$ is a circuit on structures of size $n$ and $\vert C_n' \vert \leq
-  q(f(n))$.
-\end{prop}
-
-\begin{proof}
-  From $C_n$ we construct $C_n'$ in the obvious way. For each gate $g \in C_n$
-  of type $F_i$ we have a symmetric circuit $C_g$ from Proposition
-  \ref{prop:function-maj} that computes the same function as $g$. Then let
-  $C_n'$ be $C_n$ but with each gate $g$ replaced by $C_g$. It is easy to see
-  that $C_n'$ is symmetric. We also have that each gate $g$ must have at most
-  $f(n)$ inputs, and the size of $C_g$ is bounded by $p(f(n))$. Thus the size of
-  $C_n'$ is bounded by $f(n)p(f(n))$.
-\end{proof}
-
-\chapter{October 29th: Symmetric Circuits and CPT}
-
-We already have that that the set of queries decidable by symmetric
-circuits (respectively with counting) is exactly the set of queries
-expressible in Fixed-Point Logic. We know that the CFI query is not
-expressible in FPC, and so there is no symmetric circuit that can
-compute the query.
-
-In our attempts to find a circuit characterisation of CPT, we might try and weaken the requirement of symmetry in our notion of symmetric circuits in order to express the CFI query (and perhaps the whole of CPT).
-One approach would be to weaken the requirement of having small orbits, to rather only having small orbits with respect to our particular input structure.
-We formalise this notion below.
-
-\begin{definition}
-Let $C$ be a circuit on structures of size $n$.
-Let $g$ be a gate in $C$ and let $X$ be a set of input strings closed under the action of the symmetric group.
-The $inv_X = \{ \sigma \in \sym_n : \forall x \in X g \circ H (x) = g \circ H (\sigma x)$.
-\end{definition}
-\begin{definition}
-  Let $(C_n)_{n \in \mathbb{N}}$ be a family of circuits. For any
-  finite structure $\mathcal{A}$ let $X_{\mathcal{A}}$ be the set of
-  all string encodings of $\mathcal{A}$. We say a circuit family has
-  small isomorphism orbits if there is a polynomial $p(n)$ such that
-  for any sufficiently large $n$, finite structure $\mathcal{A}$ of
-  cardinality $n$ and any $g \in C_n$ we have
-  $\vert S_n : \inv_{X_{\mathcal{A}}}(g) \vert \leq p(n)$.
-\end{definition}
-
-\begin{thm}
-  \label{thm:simple_group}
-  Let $n \in \mathbb{N}$, $n \geq 5$. Let $r \in \mathbb{N}$ such that
-  $r \leq n/2$. Suppose that $G$ is a subgroup of $\sym(n)$, then
-  there is a constant $k \in mathbb{N}$ such that for all $n \geq k$
-  if $\vert \sym(n):G \vert \leq {{n}\choose {r}}$ then there exists
-  $X \subseteq [n]$ with $\vert X \vert \leq r$ and such that
-  $\alt([n] \setminus X) \leq G$.
-\end{thm}
-
-The following result shows that even this weakened definition fails to
-capture CPT.
-\begin{thm}
-  There is no family of circuits with small isomorphism orbits that
-  expresses the CFI query.
-\end{thm}
-\begin{proof}
-  Let $(G_n)_{n \in \mathbb{N}}$ be a family of ordered graphs such that each $G_n$ has
-  odd and even CFI graphs $\mathfrak{G}$ and $\tilde{\mathfrak{G}}$ respectively, each of
-  cardinality $n$. Furthermore, suppose the CFI query for $(G_n)$ is not expressible in
-  FPC (the existence of such a family is guaranteed by
-  \cite{}). Suppose there exists a family of circuits $(C_n)_{n \in \mathbb{N}}$ with
-  small isomorphism orbits that decides the CFI query for $(G_n)$.
-  Then we have that $C_n(\mathfrak{G}) = 1$ and
-  $C_n(\tilde{\mathfrak{G}}) = 0$, and for any $g \in C_n$
-
-  \begin{align*}
-    \vert S_n : \inv_{X_{\mathcal{G}}}(g) \vert &\leq p(n),\\
-    \vert S_n : \inv_{X_{\tilde{\mathcal{G}}}}(g) \vert &\leq p(n)
-  \end{align*}.
-  Let $k$ be such that $p(n) \leq n^k$ for all sufficiently large $n$.
-Then we have that $p(n) \leq n^k \leq {{n}\choose{k+1}}$ for all sufficiently large $n$, and (again, taking $n$ large enough) we have that $k \leq n/2$.
-Taking $n$ larger than the constant in Theorem \ref{thm:simple_group} it follows that there exists an $X_1, X_2 \subseteq [n]$ such that $\vert X_1 \vert, \vert X_2 \vert \leq k$ and $\alt ([n] \setminus X_1) \subseteq  \inv_{X_{\mathfrak{G}}}(g)$, $\alt ([n] \setminus X_2) \subseteq  \inv_{X_{\tilde{\mathfrak{G}}}}(g)$.
-It follows that
-  \begin{align*}
-    \alt ([n] \setminus (X_1 \cup X_2)) &\subseteq \alt ([n] \setminus X_1) \cap \alt ([n] \setminus X_2)\\
-                                        &\subseteq \inv_{X_{\mathfrak{G}}}(g) \cap \inv_{X_{\tilde{\mathfrak{G}}}}(g) \\
-                                        &\subseteq \inv_{X_{\mathfrak{G} \cup \tilde{\mathfrak{G}}}}(g) =  \inv_{CFI(G)}(g),
-  \end{align*}
-  where $CFI(G)$ is set of all encodings of all CFI graphs of $G_n$.
-
-  We then have that
-  \begin{align*}
-    \vert S_n : \inv_{CFI(G)}(g) \vert \leq \vert S_n : \alt ([n] \setminus (X_1 \cup X_2)) \leq  \frac{n!}{(n-2k)!/2} \leq n^{2k+1},
-  \end{align*}
-  with the last inequality following for large enough $n$. We thus
-  have from Theorem \ref{} that there is a symmetric circuit $D_n$
-  that decides the CFI problem for $G_n$, and hence a family $(D_n)$
-  that decides the CFI problem for the family of graphs $(G_n)$. From
-  the theorem of Dawar et al. \cite{}, it follows that there is as
-  formula of FPC that decides the CFI query for $(G_n)$ contradicting
-  our assumption.
-\end{proof}
 \end{document}

### 2017-07-26 sections/symmetric-circuits.25-07-2017.tex
26/07/2017

--- 2016-12-14 paper.tex
@@
-\documentclass[12pt]{report}
+\documentclass[../paper.tex]{subfiles}
 
-% This first part of the file is called the PREAMBLE. It includes
-% customizations and command definitions. The preamble is everything
-% between \documentclass and \begin{document}.
+\begin{document}
+Symmetric circuits, as developed by Anderson and Dawar, are, importantly defined
+over (complete) Boolean basis consisting of symmetric functions. The following
+result shows that once a majority gate has been included in this basis any
+symmetric function can be computed using polynomial-size symmetric circuits, and
+as such no additional symmetric function added to the Basis improves the power
+of the model.
 
-\usepackage[margin=1in]{geometry} % set the margins to 1in on all sides
-\usepackage{graphicx} % to include figures
-\usepackage{amsmath} % great math stuff
-\usepackage{amsfonts} % for blackboard bold, etc
-\usepackage{amsthm} % better theorem environments
-
-% various theorems, numbered by section
-
-\newtheorem{thm}{Theorem} \newtheorem{claim}{Claim}
-\newtheorem{remark}{Remark} \newtheorem{definition}{Definition}
-\newtheorem{lem}[thm]{Lemma} \newtheorem{prop}[thm]{Proposition}
-\newtheorem{cor}[thm]{Corollary} \newtheorem{conj}[thm]{Conjecture}
-
-\DeclareMathOperator{\id}{id}
-
-\newcommand{\bd}[1]{\mathbf{#1}} % for bolding symbols
-\newcommand{\RR}{\mathbb{R}} % for Real numbers
-\newcommand{\ZZ}{\mathbb{Z}} % for Integers
-\newcommand{\MB}{\mathbb{B}_{\matsym}} % for Integers
-\newcommand{\SB}{\mathbb{B}_{\sym}} % for Integers
-\newcommand{\col}[1]{\begin{matrix} #1 \end{matrix} \right]}
-\newcommand{\comb}[2]{\binom{#1^2 + #2^2}{#1+#2}}
-\newcommand{\stab}{\text{\textbf{Stab}}}
-\newcommand{\setstab}{\text{\textbf{SetStab}}}
-\newcommand{\matstab}{\text{\textbf{MatStab}}}
-\newcommand{\inv}{\text{\textbf{inv}}}
-\newcommand{\aut}{\text{\textbf{Aut}}}
-\newcommand{\kernal}{\text{\textbf{ker}}}
-\newcommand{\alt}{\text{\textbf{Alt}}}
-\newcommand{\sym}{\text{\textbf{Sym}}}
-\newcommand{\rank}{\text{\textbf{rk}}}
-\newcommand{\orb}{\text{\textbf{Orb}}}
-\newcommand{\SP}{\text{\textbf{SP}}}
-\newcommand{\maj}{\text{\textbf{Maj}}}
-\newcommand{\dom}{\text{\textbf{Dom}}}
-\newcommand{\child}{\text{child}}
-\newcommand{\countgate}{\text{count}}
-\newcommand{\agree}{\text{AGREE}}
-\newcommand{\supp}{\text{SUPP}}
-\newcommand{\rankparam}{\text{PARAM}}
-
-\newcommand{\Alpha}{A}
-\newcommand{\matsym}{\text{\textbf{MatSym}}}
-\begin{document}
-
-\nocite{*}
-
-\title{Circuits}
-
-\author{Gregory Wilsenach \\ 
-Computer Laboratory \\
-University of Cambridge}
-
-\maketitle
-
-\tableofcontents
-
-\chapter{Introduction}
-
-\chapter{Background}
-
-\chapter{Symmetric Circuits}
-
-\chapter{Extending Symmetric Circuits}
-
-\chapter{Matrix-Symmetric Circuits}
-
-The symmetric circuits of Anderson and Dawar \cite{} have been shown to express
-$FPC$.
-
-In this section we develop a notion of a matrix-symmetric circuit, an extension
-of the symmetric circuit defined by Anderson and Dawar \cite{}. This is my
-latest version of the support and circuit capturing result.
-
-\section{}
-
-\section{Circuits and Symmetry}
-\begin{definition}
-  Let $A$ and $B$ be sets, say that a function $f: \{ 0,1 \}^{A \times B}
-  \rightarrow \{ 0,1 \}$ is matrix-symmetric if for any $\omega: A \times B
-  \rightarrow \{0, 1\}$ and $(\alpha, \beta) \in \sym_A \times \sym_B$ we have
-  $f((\alpha, \beta)\cdot \omega) = f (\omega)$.
-  \\
-  A function $f: \{0,1\}^* \rightarrow \{0,1\}$ is matrix-symmetric iff for any
-  two finite sets $A$, $B$ we have that that $f|_{A \times B}$ is
-  matrix-symmetric (where $f|_{A \times B}$ is the restriction of the function
-  $f$ to inputs sequences of size $\vert A \times B \vert$ and where elements of
-  the input sequence are labelled by elements of $A \times B$).
-\end{definition}
-
-\section{The Support Theorem}
-
-Without a loss of generality we assume that $A$ and $B$ are always initial
-segments of the natural numbers.
-
-% Let $C$ be a circuit over some Boolean basis. For each gate $g \in C$ we
-% associate a relation $\omega_g$ (or just $\omega$ when the context makes it
-% clear). We say a gate is symmetric if that relation
-
-% So far we have defined a circuit over a Boolean basis where the circuit
-% elements all compute symmetric functions. The definition of an induced
-% automorphism only makes. As such, we begin by augmenting the definition of a
-% circuit and automorphism.
-
-\begin{definition}[Circuits on Structures]
-  For $\mathbb{B}_{\sym}$ a basis of Boolean symmetric functions,
-  $\mathbb{B}_{\matsym}$ a basis of Boolean matrix-symmetric functions and
-  $\tau$ a set of relation symbols, we define a $(\mathbb{B}_\sym,
-  \mathbb{B}_\sym, \tau)$-circuit $C_n$ computing a $q$-ary query $Q$ is a
-  structure $\langle G, W, \Omega, \Sigma, \Lambda, L\rangle$.
-  \begin{itemize}
-  \item $G$ is called the set of gates of $C_n$ and $\vert C_n \vert := \vert G
-    \vert$.
-  \item $W \subseteq G \times G$, where $W$ is called the wires of the circuit.
-    $(G,W)$ must be a directed acyclic graph. For $g \in G$ we $H_g := \{ h \in
-    C_n : W(h,g)\}$ be the set of children of $g$.
-  \item $\Omega$ is an injective function from $[n]^q$ to $G$. The gates in the
-    image of $\Omega$ are called the output gates. When $q = 0$, $\Omega$ is a
-    constant function mapping to a single output gate.
-  \item $\Sigma$ is a function from $G$ to $\mathbb{B}_\sym \uplus
-    \mathbb{B}_\matstab \uplus \tau \uplus \{0,1\} $ which maps input gates to
-    $\tau \uplus \{0,1\}$ and where $\Sigma^{-1} (0) \leq 1$ $\Sigma^{-1} (1)
-    \leq 1$ and the internal gates get mapped into $\mathbb{B}_\sym \uplus
-    \mathbb{B}_\matstab$. Gates mapped to $\tau$ are called relational gates and
-    gates mapped to 1 or 0 are called constant gates.
-  \item $\Lambda$ is a sequence of injective functions $(\Lambda_R)_{R \in
-      \tau}$ where for each $R \in \tau$, $\Lambda_R$ maps each relational gate
-    $g$ with $R = \Sigma (g)$ to the tuple $\Lambda_R (g) \in [n]^r$, where $r$
-    is the arity of the symbol $R$. When no ambiguity arises we write $\Lambda
-    (g)$ for $\Lambda_R (g)$.
-  \item $L$ is the set of labelings of $C_n$. Let $g \in G$ be an internal gate
-    and $H$ be the children of $g$. Then let $S$ be a set where $\{0,1\}^S =
-    \dom(\Sigma (g))$. Then $L$ is a function that assigns to $g$ an onto
-    function $\omega_g:S \rightarrow H$. We call this the matrix labelling of
-    $g$.
-  \end{itemize}
-\end{definition}
-
-% \begin{definition}
-%   let $C = \langle G, W, \Omega, \Sigma, \Lambda, L\rangle$ be a
-%   $(\mathbb{B}_\sym, \mathbb{B}_\sym, \tau)$-circuit, then take $g_1,g_2 \in
-%   G$ such that $\Sigma (g_1) \Sigma(g_2) \in \mathbb{B}_\matsym$.
-
-\begin{definition}
-  Let $\omega_1: A \times B \rightarrow H$ and $\omega_2: A' \times B'
-  \rightarrow H'$ define the equivalence relation $\sim$ as $\omega_1 \sim
-  \omega_2$ iff $\omega_1$ and $\omega_2$ have the same domain and co-domain and
-  there exists $(\alpha, \beta) \in \sym_A \times \sym_B$ and for all $(a,b) \in
-  A \times B$ we have $\omega_1 = \omega_2 \circ (\alpha, \beta)$.
-\end{definition}
-
-% \begin{definition}
-%   Let $\omega_1: A \rightarrow H$ and $omega_2:A' \rightarrow H'$. Define the
-%   equivalence relation $\sim$ as $\omega_1 \sim \omega_2$ iff $\omega_1$ and
-%   $\omega_2$ have the same domain and co-domain, and
-% \end{definition}
-
-\begin{definition}[Automorphism]
-  let $C = \langle G, W, \Omega, \Sigma, \Lambda, L\rangle$ be a
-  $(\mathbb{B}_\sym, \mathbb{B}_\sym, \tau)$-circuit computing at $q$-ary query
-  on structures of size $n$. Let $\sigma \in \sym_n$ and $\pi: G \rightarrow G$
-  be a bijection such that
-  \begin{itemize}
-  \item for all gates $g, h \in G$, $W(g,h)$ iff $W(\pi g, \pi h)$,
-  \item for all output tuples $x \in [n]^q$, $\pi \Omega (x) = \Omega (\sigma
-    x)$,
-  \item for all gates $g \in G$, $\Sigma (g) = \Sigma (\pi g)$, and
-  \item for each relational gate $g \in G$, $\sigma \Lambda (g) = \Lambda (\pi
-    g)$
-  \item for each internal gate $g$ if $\Sigma (g) \in \mathbb(B)_\matsym$. Then
-    we have that $L(\pi g) \sim \pi \circ L(g)$.
-  \end{itemize}
-\end{definition}
-
-\begin{remark}
-  I also need a new notion of robustness here in order to collapse gates that
-  have the same children and equivalent labelings are properly regarded as being
-  the same gate.
-\end{remark}
-% \begin{definition}
-%   Let $C$ be a circuit, $g$ be a gate in $C$, $H$ be $g$'s set of children and
-%   let $\omega: A \times B \rightarrow H$ be a surjection, where $A$ and $B$
-%   are sets and $g$ takes $\vert A \vert \cdot \vert B \vert$ inputs. Call such
-%   an $\omega$ a matrix labeling for $g$.
-% \end{definition}
-
-% \begin{definition}
-%   Let $C$ be a circuit and $g_1$ and $g_2$ be gates in $C$. Let $\sigma \in
-%   \sym_n$ be a permutation such
-% \end{definition}
-
-\begin{definition}
-  Let $\omega$ be a matrix labeling for $g$. Define the matrix stabilizer for
-  $\omega$, denoted by $\matstab(\omega)$, to be the set of all $\sigma \in
-  \sym_n$ such that $\sigma H = H$ and there exists $(\alpha, \beta) \in \sym_A
-  \times \sym_B$ such that for all $(i,j) \in A \times B$ we have that $\omega
-  (\alpha i, \beta j) = \sigma \omega (i,j)$.
-\end{definition}
-
-\begin{definition}
-  Let $g$ be a gate with matrix labeling $\omega$, $h,h' \in H$ and $\sigma \in
-  \sym_n$. We say that a pair $(h, h')$ is compatible with $(\sigma, \omega)$ if
-  $\sigma h, \sigma h' \in H$ and there exists $(\gamma_1, \gamma_2),
-  (\gamma_1', \gamma_2') \in \sym_A \times \sym_B$ s.t.
-  \begin{align*}
-    &(\gamma_1, \gamma_2) \cdot \omega^{-1} (h) = \omega^{-1}(\sigma h), \text{ and} \\ 
-    &(\gamma_1', \gamma_2') \cdot \omega^{-1} (h') = \omega^{-1}(\sigma h'),
-  \end{align*}
-  and for all $(i,j) \in \omega^{-1}(h)$, $(i',j') \in \omega^{-1}(h')$ we have
-  that
-  \begin{align*}
-    &i =i' \implies \gamma_1(i) = \gamma_1'(i'), \text{ and} \\
-    &j =j' \implies \gamma_2(j) = \gamma_2'(j').
-  \end{align*}
-
-\end{definition}
-
-\begin{lem}
-  Let $g$ be a gate, $\omega$ be a matrix labeling of $g$, $\sigma \in \sym_n$.
-  Then $\sigma \in \matstab(\omega)$ iff for all $h,h' \in H$ we have that
-  $(h,h')$ is compatible with $(\sigma, \omega)$.
-\end{lem}
-
-\begin{proof}
-  $`\Rightarrow'$: We have that $\sigma \in \matstab(\omega)$ and so there
-  exists $(\alpha, \beta) \in \sym_A \times \sym_B$ such that for all $(i,j) \in
-  A \times B$ we have $\sigma \omega (i,j) = \omega (\alpha i, \beta j)$. From
-  compatibility we have that $h,h' \in H$ Let $h, h' \in H$ . Let $(\gamma_1,
-  \gamma_2) := (\gamma_1', \gamma_2') := (\alpha, \beta)$. This assignment is
-  sufficient to prove the direction.
-
-  $`\Leftarrow'$: Suppose for all $h,h' \in H$ we have $(\gamma_1, \gamma_2),
-  (\gamma_1, \gamma_2') \in \sym_A \times \sym_B$ satisfying the above
-  requirements. Notice that for a given $i \in A$ and any $j, j' \in B$, let $h
-  = \omega(i,j)$ and $h' = \omega(i,j')$, then we have that $\gamma_1 (i) =
-  \gamma_1'(i)$. It follows that we can define a $\alpha \in \sym_A$ by
-  $\alpha(i) = \gamma_1 (i)$. Similarly we can define $\beta \in \sym_B$ by
-  $\beta (j) = \gamma_2 (j)$.
-
-\end{proof}
-
-\begin{definition}
-  Let $g$ be a gate with matrix labeling $\omega$. Let $(\sigma, h, h') \in
-  \sym([n]) \times H^2$. Say that $(\sigma, h, h')$ is useful if $(h,h')$ is
-  incompatible with $(\sigma, \omega)$.
-
-  Say that two distinct pairs $(\sigma_1, h_1, h_1'), (\sigma_2, h_2, h_2') \in
-  \sym([n]) \times H^2$ are mutually independent if
-  \begin{itemize}
-  \item $\sigma_2 h_1 = h_1$,
-  \item $\sigma_2 \sigma_1 h_1 = \sigma_1 h_1$,
-  \item $\sigma_2 h_1' = h_1'$,
-  \item $\sigma_2 \sigma_1 h_1' = \sigma h_1'$,
-  \end{itemize}
-  We say that a set $S \subseteq \sym([n]) \times H^2$ is useful if each pair in
-  it is useful. We say that S is independent if each pair of distinct pairs in
-  $S$ are mutually independent.
-\end{definition}
-
-We denote the usual equivalence relation on $\sym_n$ from the (right) cosets of
-$\matstab(\omega)$ by $\sim_\omega$.
-
-\begin{lem}
-  Let $\sigma_1, \sigma_1 \in \sym_n$ and suppose $\sigma_1 \sim_\omega
-  \sigma_2$ then for any $(h,h') \in H^2$ we have that $(h,h')$ is compatible
-  with $(\sigma_1, \omega)$ iff $(h,h')$ is compatible with $(\sigma_2,
-  \omega)$.
-\end{lem}
-
-\begin{proof}
-  Suppose we have that $\sigma_1 \sim_\omega \sigma_2$. And additionally
-  supposed $(h, h')$ compatible with $(\sigma_1, \omega)$.
-
-  It follows there exists $(\alpha, \beta) \in \sym_A \times \sym_B$ such that
-  $\sigma_1 \omega (i,j) = \sigma_2\omega (\alpha i, \beta j)$, and we have
-  $(\gamma_1, \gamma_2), (\gamma_1', \gamma_2') \in \sym_A \times \sym_B$
-  satisfying the requirements of compatibility. We note that $(\alpha, \beta)
-  \cdot \omega^{-1}(\sigma_1 h) = \omega^{-1}(\sigma_2 h)$. Thus by composition
-  we have that $(\alpha \gamma_1, \beta \gamma_2) \cdot \omega^{-1}(h) =
-  \omega^{-1}(\sigma_2 h)$ and $(\alpha \gamma_1', \beta \gamma_2') \cdot
-  \omega^{-1}(h') = \omega^{-1}(\sigma_2 h')$, and clearly the remaining
-  requirement for compatibility follows from the bijectivity of $\alpha$ and
-  $\beta$. The result follows. The other direction of the implication follows
-  from symmetry.
-\end{proof}
-
-\begin{claim}
-  \label{claim:useful-independant-set}
-  Let $g$ be a rank gate with labeling $\omega$ and child set $H$. Let $S$ be a
-  useful and independent. We then have that $\vert \sym_n: \matstab(\omega)
-  \vert \leq 2^{\vert S \vert}$.
-\end{claim}
-
-\begin{proof}
-  Let $R \subseteq S$ and define $\sigma_R = \Pi_{(\sigma, h, h') \in R} \sigma$
-  (with some arbitrary order assumed on $S$). Let $R$ and $Q$ be distinct
-  subsets of $S$ and WLOG let $\vert R \vert \geq \vert Q \vert$. We want to
-  show that we don't have $\sigma_R \omega \sim_\omega \sigma_Q \omega$. Pick
-  any $(\sigma, h, h') \in R/Q \neq \emptyset$. Given that $\sigma_R h = \sigma
-  h$ and $\sigma_R h' = \sigma h'$ it is easy to see that the usefulness of
-  $(\sigma, h,h')$ implies the incompatibility of $(h,h')$ with with $(\omega,
-  \sigma_R)$. Moreover, the fact that $\sigma_Q h = h$ and $\sigma_Q h' = h'$
-  makes it easy to see $(h,h')$ is compatible with $(\omega, \sigma_Q)$. From
-  the above lemma we may conclude that that we do not have $\sigma_R \sim_\omega
-  \sigma_Q$, and the result follows.
-\end{proof}
-
-The following two lemmas proved by Anderson and Dawar \cite{} are both of use in
-proving the following theorem.
-
-\begin{lem}
-  \label{lem:big-or-small}
-  For any $\epsilon$ and $n$ such that $0 < \epsilon < 1$ and $\log n \geq
-  \frac{4}{\epsilon}$, if $\mathcal{P}$ is a partition of $[n]$ with $k$ parts,
-  $s = [\sym_n : \setstab (\mathcal{P})]$ and $n \leq s leq 2^{n^{1-\epsilon}}$,
-  then $\min \{k, n-k\} \leq \frac{8}{\epsilon} \frac{\log s}{\log n}$.
-\end{lem}
-
-\begin{lem}
-  \label{lem:small-means-support}
-  For any $\epsilon$ and $n$ such that $0 < \epsilon < 1$ and $\log n \geq
-  \frac{8}{\epsilon^2}$, if $\mathcal{P}$ is a partition of $[n]$ with $\vert
-  \mathcal{P} \vert \leq \frac{n}{2}$, $s:= [\sym_n : \setstab (\mathcal{P})]$
-  and $n \leq s \leq 2^{n^{1-\epsilon}}$, then $\mathcal{P}$ contains a part $P$
-  with at least $n - \frac{33}{\epsilon} \cdot \frac{\log s} {\log n}$.
-\end{lem}
-
-If $g$ is a symmetric gate (i.e. the usual gates in a circuit) we note that
-$\orb(g) = [\sym_n : \stab (g)]$ by the orbit-stabilizer theorem.
-
-If $g$ is a matrix-symmetric gate then $\orb(g) = [\sym_n:\matstab (\omega)]$,
-where $\omega$ is the matrix labelling associated with $g$.
-
-\begin{thm}
-  For any $\epsilon$ and $n$ such that $\frac{2}{3} \leq \epsilon \leq 1$ and $n
-  \geq \frac{128}{\epsilon^2}$, if $C$ is a symmetric, rigid circuit on
-  structures of size $n$ and $s := \max_{g \in C} \vert \orb (g)\vert \leq
-  2^{n^{1-\epsilon}}$, then, $SP(C) \leq \frac{33}{\epsilon}\frac{log s}{log
-    n}$.
-\end{thm}
-
-\begin{proof}
-  It is easy to see that if $g$ is a gate in $C$ then $\stab (g) \subseteq
-  \setstab(\SP(g))$, and so $s \geq \orb(g) = [\sym_n : \stab(g)] \geq [\sym_n :
-  setstab(\SP(g))]$. Thus if $\vert \SP(g) \vert \leq frac{n}{2}$, then from
-  Lemma \ref{lem:small-means-support}, we have $\| SP (g) \| \leq
-  \frac{33}{\epsilon} \cdot \frac{\log s} {\log n}$. The result thus follows
-  from showing that for each $g$ in $C$ we have that $\vert \SP (g) \vert \leq
-  \frac{n}{2}$.
-
-  % Include some detail here for constant and relational gates
-  The cases where $g$ is a constant or relational gate are easy to handle.
-
-  We now consider the case for internal gates. Let $g$ be the topologically
-  first internal gate with $\vert \SP(g) \vert > \frac{n}{2}$. If $g$ is not a
-  matrix-symmetric gate then the result follows from the argument presented by
-  Anderson and Dawar \cite{}. Suppose $g$ is a matrix-symmetric gate, and
-  suppose $g$ has a labelling $\omega$. We now argue that this leads to a
-  contradiction.
-
-  Let $k' := \lceil \frac{8 \log s}{\epsilon \log n} \rceil$. From the
-  assumptions on $s, n$ and $\epsilon$ we have that $k' \leq
-  \frac{1}{4}n^{1-\epsilon} < \frac{n}{2}$. Lemma \ref{lem:big-or-small} implies
-  that $n - \vert \SP(g) \vert \leq k'$
-
-  From Claim \ref{claim:useful-independant-set} it remains to show that we can
-  construct a sufficiently large useful and independent set of gate-automorphism
-  pairs $S$. Divide $[n]$ into $\lfloor \frac{n}{k' + 2} \rfloor$ disjoint sets
-  $S_i$ of size $k' + 2$ and ignore the elements left over. It follows that for
-  each $i$ there is a permutation $\sigma_i$ which fixes $[n] / S_i$ pointwise
-  but moves $g$. Suppose there was no such $\sigma_i$ it follows that every
-  every permutation that fixes $[n]/S_i$ pointwise fixes $g$. Thus the partition
-  of all the singletons in $[n]/S_i$ and $S_i$ is a supporting partition. As
-  $\SP(g)$ is the coarsest partition it follows that $\vert \SP(g) \vert \leq n
-  - (k'+2) + 1 = n - k' - 1$, which contradicts the inequality $n - \vert \SP(g)
-  \vert \leq k'$.
-
-  Since $g$ is moved by each $\sigma_i$ and $C$ is rigid it follows that we
-  don't have $\sigma_i \notin \matstab(\omega)$. Thus there exists $(h_i, h_i')$
-  that is inconsistent with $(\sigma_i, \omega)$, and so the triple $(\sigma_i,
-  h_i, h_i')$ is useful.
-
-  Let $\SP (h)^*$ be the union of all parts of $\SP(h)$ except for the largest
-  part. Let $Q_i = \SP(h_i)^* \cup \SP(\sigma_i h_i)^* \cup \SP (h_i')^* \cup
-  \SP (\sigma_i h_i')^*$. Then note that if $\sigma_j$ fixes $Q_i$ then by
-  construction, we have that $\sigma_j \in \stab_n(\SP(h_i)) \cap
-  \stab_n(\SP(\sigma_i h_i)) \cap \stab_n(\SP(h_i')) \cap \stab_n(\SP(\sigma_i
-  h_i'))$
-
-  Define a graph $K$ with vertices given by the sets $S_i$ and an edge from
-  $S_i$ to $S_j$ (with $i \neq j$) if $Q_i \cap S_j \neq \emptyset$. It follows
-  then that if there is no edge between $S_i$ and $S_j$ then $(\sigma_i, h_i,
-  h_i')$ and $(\sigma_j, h_j, h_j')$ are mutually independent. It remains to
-  argue that $K$ has a large independent set. This is possible as the out-degree
-  of $S_i$ in $K$ is bounded by
-  \begin{align*}
-    \vert Q_i \vert \leq \|SP(h_i) \| + \|SP(\sigma_i h_i) \| + \|SP(h_i') \| + \|SP(\sigma_i h_i') \leq 4 \cdot \frac{33\log s}{\epsilon \log n}
-  \end{align*}.
-
-  This follows as the sets $S_i$ are disjoint and we may apply Lemma
-  \ref{lem:small-means-support} to each of the child gates. It follows that the
-  average total degree (in + out degree) of $K$ is at most $2 \cdot \vert Q_i
-  \vert \leq 34 \cdot k'$. Now greedily select a maximal independent set in $K$
-  by repeatedly selecting $S_i$ with the lowest total degree and eliminating it
-  and its neighbours. This action does not affect the bound on the average total
-  degree of $K$ and hence determines an independent set $I$ in $K$ of size at
-  least
-  \begin{align*}
-    \frac{\lfloor \frac{n}{k' + 2} \rfloor}{34k' + 1} \geq \frac{n - (k'+2)}{34k'+1k'+2} \geq \frac{n\frac{7}{16}}{34k'^2 + 69k' +2} \geq \frac{n}{(16k')^2}.
-  \end{align*}
-
-  Take $S = \{(\sigma, h, h') : S_i \in I \}$. Then from the above argument we
-  have that $S$ is useful and independent.
-
-  Moreover, from Claim \ref{claim:useful-independant-set}, we have that $s \geq
-  \vert \orb(g) \vert \geq 2^{\vert S \vert} \geq 2^{\frac{n}{(16k')^2}}$ then
-  $n^{1-\epsilon} \geq \log s \geq n \cdot (\frac{128}{\epsilon}\frac{\log
-    s}{\log n})^{-2} > n \cdot (n^{1-\epsilon})^{-2} = n^{2\epsilon -1} \geq
-  n^{1-\epsilon}$. This is a contradiction.
-\end{proof}
-
-\section{Rigid Circuits}
-
-\begin{definition}
-  We say that a circuit $C$ has bijective labels if for each gate $g$ in $C$,
-  $L(g)$ is a bijection.
-\end{definition}
-
-\begin{lem}
-  \label{lem:bij_labels}
-  There is an algorithm that runs in polynomial time that takes in a circuit $C$
-  and outputs a circuit with unique gates $C'$. Moreover, if $C$ was symmetric
-  then $C'$ is symmetric. If $C$ is rigid then $C'$ is rigid.
-\end{lem}
-
-\begin{proof}
-  Let $S = 2*\vert C \vert$. Recurse through the gates of $C$ topologically and
-  let $h$ be the next gate topologically. If for all $g \in W(h, \cdot)$ we have
-  that $L\vert (g)^{-1}(h) \vert = 1$ continue on to the next gate. If not add
-  in a tower of $S$ $\and$ gates such that $h \rightarrow \and^h_1 \rightarrow
-  \ldots \rightarrow \and^h_S$ (i.e. we have a tower of $\and$ gates with $h$ as
-  input to $\and^h_1$ and the output of each $\and^h_i$ connected to the input
-  of each $\and^h_{i+1}$ for each $1 \leq i < S$). Now for each $g \in W(h,
-  \cdot)$, if $L(g)^{-1}(h) = \{ s_0, \ldots, s_{r}\}$, for each $1 \leq i \leq
-  r$ add in the wires $W(\and^h_i, g)$ and set $L(g)(s_{i}) = \and^h_i$. Now
-  continue on to the next gate topologically and run the above algorithm.
-
-  % First, notice that for a given gate $h$ and $k \in \mathbb{N}$, we can
-  % define
-  % a sub-circuit $h^k = 1 \and \cdots, 1 \and h$ (or rather a $k$-height tower
-  % of
-  % $k$ binary $\and$ gates with $h$ at the top and all other inputs set to
-  % $1$).
-  % We call $h$ the top of the sub-circuit $h^k$ and the bottom $and$ gate (the
-  % output of the sub-circuit) the bottom gate. We may think of this as a
-  % $k$-height copy of the gate $h$, in the sense that it has the same output as
-  % $h$ and similar orbits. We now use different copies to distinguish gates
-  % that
-  % otherwise have the same labelling.
-
-  % Let $h$ be the next gate topologically. Then let $r$ be maximal such that
-  % $W(h,g)$ and $\omega_g^{-1}(h) = \{ s^g_1, s^g_2, \ldots, s^g_r \}$. Then
-  % let
-  % $k$ be the height of the highest tower with $h$ at the top and with it's
-  % bottom connected to a gate in $W(h, \cdot)$. Then create a single
-  % $k+r-1$-height tower by adding in the appropriate number of binary $\and$
-  % gates below $h$.
-
-  % For each $g \in W(h, \cdot)$ and for each $\omega_g^{-1}(h) = \{s^g_1,
-  % s^g_2,\ldots , s^g_{r_g}\}$, set $L'(g)(s^g_1) = h$ each child starting with
-  % the $and$-gate child to $h$ add in a wire from from the $i$th gate in the
-  % tower to $g$ and set $L'(g)(s^g_{i+1}) = \and_i$, where $\and_i$ is the
-  % $i$th
-  % $\and$ gate in the tower starting with the $\and$ gate in the tower child to
-  % $h$. There are enough gates in the tower as $r_g \leq r$.
-
-  We call this updated circuit $C'$.
-
-  Firstly, note that after running the above algorithm for each $g$ the
-  labelling of $g$ will be a bijection. Moreover, it's easy to see that the
-  output of each gate remains unchanged, and as such the output of the circuit
-  is unchanged.
-
-  Secondly, notice that the size of $C'$ is at most $2*\vert C \vert^2$, and
-  note that the above algorithm runs in polynomial time.
-
-  Now suppose that $C$ is symmetric. Let $\sigma$ be a permutation on the input
-  universe and $\pi_C$ the induced automorphism on $C$. We now define $\pi$, the
-  induced automorphism on $C'$. For each gate $g$ in $C'$, if $g$ is in $C$ then
-  set $\pi(g) := pi_C(g)$. If $g$ is not in $C$ then $g$ must be some
-  $\and^h_i$, for some $h$ in $C$. Then set $\pi(\and^h_i) :=
-  \and^{\pi_C(h)}_i$. It is easy to see that $\pi$ is an automorphism, and $\pi$
-  extends $\sigma$.
-
-  Suppose that $C$ is rigid. It is easy to see that $C'$ will be rigid as well.
-
-\end{proof}
-
-% If $h$ is a binary $\and$ gate, then we say that $h$ has height $k+1$ if it
-% has a $k$-height tower of binary $and$ gates connected above it, with a
-% non-$\and$ gate $p$ connected to the final binary $\and$ gate, and all other
-% inputs connected to $1$. We then say that $h$ is the base of a tower of height
-% $k$ and type $p$.
-
-% Then for each $h \in W_g$, if $h$ is not a binary $\and$ gate, the let $k$ be
-% the largest integer such that there a gate $h' \in W(h, \cdot)$ which is the
-% base of a tower of height $k$ and type $h$. it's output directly connected to
-% one of the gates in $W(h^k, \cdot)$ (with k = 0 corresponding to just $h$).
-% Then each $i \in \{1, \ldots , \vert \omega^{-1}(h)\vert\}$ add into the
-% circuit $h^{k+i}$ and wire it to $g$. Notice that this step requires adding
-% $\vert \omega^{-1}(h) \vert -1$ gates to the circuit. For some assumed
-% ordering $\dom(\omega)$, let $\{s_0, \cdot, s_m\} = \omega^{-1}(h)$. Define
-% $L'(g)(s_i) = h^{k+i}$. Now continue on to the next gate topologically where
-% $L(g)$ is not a bijection, and execute the same process
-
-\begin{lem}
-  There is an algorithm that runs in polynomial time that takes in a circuit $C$
-  and outputs a circuit $C'$ such that $C'$ is rigid and has bijective labels.
-  Moreover, if $C$ was symmetric it follows that $C'$ will be symmetric.
-\end{lem}
-
-\begin{proof}
-  First run the algorithm from Lemma \ref{lem:bij_labels} on $C$, and call the
-  output circuit $C$.
-
-  Recurse through the gates of $C$ topologically. For each internal gate $g$,
-  for all $g'$ in $C$ such that $g \neq g'$, $W(\cdot, g) = W(\cdot, g')$, $W(g,
-  \cdot) = W(g', \cdot)$, $\Sigma(g) = \Sigma(g')$, $L(g) \sim L(g')$ and
-  $\Omega^{-1}(g) = \Omega^{-1}(g')$, delete $g'$ and for all $s \in L^{-1}(g')$
-  set $L(s) := g$.
-
-  Now re-run the algorithm from Lemma \ref{lem:bij_labels} on $C$ and output the
-  result.
-\end{proof}
-
-  \begin{lem}
-    Let $C = \langle G, W, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\SB, \MB,
-    \tau)-circuit$ on structures of size $n$. There is a deterministic algorithm
-    which runs in Poly($\vert C \vert$) and outputs a rigid $(\SB, \MB, \tau)
-    circuit$ $C'$ such that $G' = G$ and for any $g \in G$, and any input
-    $\tau$-structure $\mathcal{A}$ and any bijection $\gamma$ from $A$ to $[n]$,
-    $C[\gamma \mathcal{A}](g) = C'[\gamma \mathcal{A}](g)$ and if $C$ is
-    symmetric then so is $C'$.
-  \end{lem}
-
-  \begin{proof}
-
-  \end{proof}
-
-  \section{Computing Supports}
-  \begin{lem}
-    Let $C$ be a rigid $(\SB, MB, \tau)$-circuit on structures of size $n$ and
-    $\sigma \in \sym_n$. There is a deterministic algorithm which runs in time
-    Poly($\vert C \vert$) and outputs for each gate $g$ its image under the
-    automorphism $\pi$ induced by $\sigma$, if it exists.
-  \end{lem}
-  \begin{proof}
-    The proof proceeds by recursively going through the circuit and building the
-    mapping $\pi$ induced by $\sigma$.
-
-    Suppose $g$ is a constant gate, then $\pi g := g$. Suppose $g$ is a
-    relational gate, then there is at most one gate $g'$ such that $\Sigma (g) =
-    \Sigma (g')$ and $\sigma\Lambda (g') = \Lambda (g)$. If such a $g'$ exists
-    assign $\pi g := g'$, else terminate with failure.
-
-    If $g$ is an symmetric internal gate then (from rigidity) there is at most
-    one gate $g'$ such that $\Sigma (g) = \Sigma(g')$ and $W_{g'} = \pi W_g$.
-    Assign $\pi g := g'$ if such a gate exists, or else terminate with failure.
-
-    If $g$ is a matrix-symmetric internal gate then consider the set of gates
-    $g'$ such that $g'$ has children $\pi W_g$ and $\Sigma(g) = \Sigma(g')$, and
-    let $A \times B = \dom (Sigma(g))$. If no such gate $g'$ exists, terminate
-    with failure. Define $\sigma_{\pi, g'}:A \times B \rightarrow A \times B$ by
-    $\sigma_{\pi, g'} = \omega^{-1}_{g'} \pi \omega_{g}$. Then clearly
-    $\omega_{g'} \sigma_{\pi, g'} = \pi \omega_{g}$, and it's easy to show that
-    $\pi \omega_g \sim \omega_{g'}$ iff $\sigma_{\pi,g'} \in \sym_A \times
-    \sym_B$. But this just involves checking that $\sigma$ acts as a bijection
-    on $A$ and $B$ separately and, given that $\vert A \vert$ and $\vert B
-    \vert$ are both bounded by $\vert C \vert$, the algorithm which just
-    iterates through $A$ and $B$ is sufficient. If for every $g'$ it is found
-    that $\pi_{\sigma,g'}$ is not in $\sym_A \times \sym_B$ then terminate with
-    failure. If there is a $g'$ for which $\pi_{\sigma, g'} \in \sym_A \times
-    \sym_B$ then it is unique by rigidity and so set $\pi g := g'$.
-
-    If $g$ is an output gate, then check that for all tuples in $[n]^{q}$ we
-    have that $\pi \Omega (x) = \Omega (\sigma (x))$, and terminate with failure
-    if the condition is not met.
-
-    If the algorithm has not terminated with failure, output the automorphism.
-
-    The algorithm clearly runs in Poly($\vert C \vert$)
-  \end{proof}
-
-  \section{Evaluating Symmetric Circuits}
-  We need to extend two Lemmas in this section.
-
-\begin{lem}
-  Let $g$ be a matrix-symmetric gate in $C_n$ with children $H$. Let $\alpha \in
-  U^{\underbar{\sp(g)}}$, and suppose $\gamma_1, \gamma_2: U \rightarrow [n]$
-  with $\gamma^{-1}_1 \sim \alpha$ and $\alpha \sim \gamma^{-1}_2$. Let $A
-  \times B = \dom (L(g))$.
-
-  For an input structure $\mathcal{A}$, let $L^0_\gamma: A \times B \rightarrow
-  \{0,1\}$, where $L^0_\gamma (a,b):= C[\gamma \mathcal{A}] (L(g)(a,b))$.
-
-  Then $L^0_{\gamma_1} \sim L^0_{\gamma_2}$.
-\end{lem}
-
-\begin{proof}
-  We have that there exists a unique $\pi \in \sym_n$ such that $\pi \gamma_1 =
-  \gamma_2$. Moreover, since $\gamma^{-1}_1$ and $\gamma^{-1}_2$ are both
-  consistent with $\alpha$, it follows that $\pi$ must fix $\sp(g)$. Thus $L(g)
-  \sim \pi L(g)$, and so there exists $(\sigma, \lambda)$ such that $\pi L(g) =
-  L(g) (\sigma, \lambda)$.
-
-  We then have that,
-  \begin{align*}
-    L^0_{\gamma_1} (a,b) &= C_n[\gamma_1 \mathcal{A}](L(g)(a,b))\\
-                         & = C_n[\pi gamma_1 \mathcal{A}][\pi L(g)(a,b)] \\
-                         & = C_n[gamma_2 \mathcal{A}][L(g)((\sigma, \lambda)(a,b))]\\
-                         & = L^0_{\gamma_2} ((\sigma, \lambda) (a,b)),
-  \end{align*}
-  and it follows that $L^0_{\gamma_1} \sim L^0_{\gamma_2}$.
-
-\end{proof}
-
-\begin{lem}
-  Let $g$ be a matrix symmetric gate in $C_n$ with children $H$. Let $\alpha \in
-  U^{\underbar{\sp(g)}}$ and $\gamma: U \rightrrow [n]$ such that
-  $gamma^{-1}\sim \alpha$. Let $A \times B = \dom (L(g))$ and define
-  $L^{EV}_\alpha: A \times B \rightarrow \{0,1\}$ by
-  \begin{align*}
-    L^{EV}_\alpha (a,b):=
-    \begin{cases*}
-      1 & if $A_h \cap \EV_h \neq \emptyset$ 0 & otherwise
-    \end{cases*},
-  \end{align*}
-  where for $h \in W_g, A_h:= \{\beta \in U^{\underline{\sp(h)}} \vert \alpha
-  \sim \beta\}$. Then $L^0_\gamma = L^{EV}_\alpha$ and $\alpha \in \EV(g)$ iff
-  $\rk^u_p(L^0_\gamma)$
-\end{lem}
-\begin{proof}
-
-\end{proof}
-
-\begin{lem}
-  Let $g$ be a matrix-symmetric gate in $C_n$ with children $W_g$. $Let \alpha
-  \in U^{\underbar{\sp(g)}}$ and let $\gamma: U \rightarrow [n]$ such that
-  $\gamma^{-1} \sim \alpha$. Let $A \times B = \dom (L(g))$, and let
-  $f:\{0,1\}^{A \times B} \rightarrow \{0,1\}$ be the matrix-symmetric function
-  associated with $g$. Define $L^{EV}_\alpha: A \times B \rightarrow \{0,1\}$ by
-  \begin{align*}
-    L^{EV}_\alpha (a,b):=
-    \begin{cases*}
-      1 & if $A_h \cap \EV_h \neq \emptyset$ 0 & otherwise
-    \end{cases*},
-  \end{align*}
-  where for $h \in W_g, A_h:= \{\beta \in U^{\underline{\sp(h)}} \vert \alpha
-  \sim \beta\}$. Then $\alpha \in \EV_g$ iff $f(L^\EV_\alpha)$.
-\end{lem}
-\begin{proof}
-  First note that if $\alpha \in U^{\underbar{\sp{g}}}$ then $\alpha \in \EV_g$
-  iff we have that $C_n[\gamma \mathcal{A}](g)= f (L^0_\gamma) = 1$. Notice that
-  from Lemma \ref{} that this holds for any particular $\gamma$ iff it holds for
-  all such $\gamma$.
-
-  We now show that $L^\EV_\alpha = L^0_\gamma$, and so complete the proof.
-
-  Suppose for $(a,b) \in A \times B$ we have that $L^\EV_\alpha(a,b) = 1$. Let
-  $h:= L(g)(a,b)$. It follows that $A_h \cap \EV_h \neq \emptyset$, i.e there
-  exits $\beta \in \sp(h)$ such that $\beta \sim \alpha$ and there exists
-  $\gamma_h \in \Gamma(h)$ such that $\gamma^{-1}_h \sim \beta$. It follows from
-  transitivity and Lemma \ref{} that $\gamma_h \sim \alpha$ and so
-  $L^0_\alpha(a,b) = C_n[\gamma \mathcal{A}](h) = C_n[\gamma_h \mathcal{A}](h) =
-  1$.
-
-  Now suppose that $L^0_\gamma (a,b) = 1$
-\end{proof}
-
-\section{Translating to Formulas of FPC}
-Let $\mathcal{C} = (C_n)_{n \in \mathbb{N}}$ be a P-uniform family of
-polynomial-size symmetric $(\SB, \MB, \tau)$ circuits, and where $\MB$ is the
-rank basis. It remains to show that there is a formula $Q$ in the vocabulary
-$\tau \uplus \{\leq\}$ such that for any $n$ and $\tau$-structure $\mathcal{A}$
-with a universe $U$ of carnality $n$, the $q$-ary query defined by $C_n$ on the
-input $\mathcal{A}$ is defined by the formula $Q$ when interpreted in the
-structure $\mathcal{A}^\leq = \mathcal{A} \uplus \langle [n], \leq \rangle$.
-
-Since $\mathcal{C}$ is $P$-uniform, and from Lemmas \ref{} and \ref{} and the
-Immerman-Vardi theorem, we have an FP interpretation defining a rigid symmetric
-circuit with bijective labels equivalent to $C_n$ (which we also call $C_n$)
-over the the number sort of $\mathcal{A}^\leq$, where $\Phi = (\phi_G,\phi_W,
-\phi_\Omega, (\phi_s)_{s \in \SB \uplus \{rank\} \uplus \tau \uplus \{0,1\}},
-(\phi_{\and_R})_{R \in \tau}, \phi_L)$. We note that $Phi$ is a $t$-width
-interpretation over the universe $[n]$. So if $\mu, \nu, \nu_1, \ldots \in
-[n]^t$, the formulas are defined such that:
-
-\begin{itemize}
-\item $\phi_G(\mu)$ holds iff $\mu$ encodes a gate
-\item $\phi_W(\nu,\mu)$ holds iff $\nu$ and $\mu$ encode gates and if $g_{\nu}$
-  and $g_{\mu}$ are these two encoded gates respectively then $W(g_{\nu},
-  g_{\mu})$.
-\item $\phi_{\Omega}(\nu_1, \ldots, \nu_q, \mu)$ holds iff $\nu_1, \ldots, nu_q$
-  each encode numbers less than or equal to $[n]$ and $\Omega(\nu_1, \ldots,
-  \nu_q) = g_\mu$.
-\item For all $s \in \SB \uplus \{rank\} \uplus \tau \uplus \{0,1\}$ we have
-  that $\phi_s (\mu)$ holds iff $\mu$ encodes a gate such that $\Sigma(g_\mu) =
-  s$ (or, in the case that $s = \rank$, we require that $\Sigma(g_\mu)$ is a
-  rank symbol.)
-\item For all $R \in \tau$ with arity $r$ we have that $\phi_{\and_R}(\nu_1,
-  \ldots, \nu_r, \mu)$ holds iff $\nu_1 , \ldots , \nu_r$ encodes numbers less
-  than or equal to $[n]$, $\mu$ encodes a gate such that $\Sigma(g_\mu) = R$ and
-  $\Lambda_R(g_\mu) = (\nu_1, \ldots, \nu_r)$.
-\item $\phi_L(\nu, \mu, \nu_1, nu_2)$ holds iff $\nu$ and $\mu$ encode gates and
-  $\nu_1, \nu_2$ encode numbers, and $L(g_{\mu})(\nu_1,\nu_2) = g_\nu$. If
-  $\dom(L (g_\mu)) = [a] \times [b]$, then the encoding of $[a]$ and $[b]$ are
-  initial segments under the lithographically induced order. Moreover, the
-  encodings of $[a]$ and $[b]$ preserve the order relation.
-\end{itemize}
-
-From now on we use $\mu$ and $\nu$ to stand for $t$-length sequences encoding
-gates, and use $\nu_1, \ldots$ for sequences that encode numbers. We use $g_\mu$
-and $g_\nu$ for the gates encoded by these sequence, while simply identifying
-the sequence $\nu_i$ with the number it encodes.
-
-Using the Immerman-Vardi Theorem, we can define an FP($\leq$) formula
-$\rankpara$ such that $\langle [n], \leq\rangle \models \rankpara[g,p,u]$ iff
-$\langle [n], \leq\rangle \models \phi_G[g] \land \phi_{\rank}[g]$ and the rank
-gate $g$ (as per the interpretation) computes the rank over characteristic $p$
-and has threshold $u$.
-
-We can define FP($\leq$) formulas $\max_A$ and $\max_B$ such that $\langle [n],
-\leq \rangle \models \max_A[g, \nu_1]$ iff $\nu_1$ encodes $a$, where
-$\dom(L(g)) = [a]\times [b]$. Similarly, $\langle [n], \leq \rangle \models
-\max_B[g, \nu_1]$ iff $\nu_1$ encodes $b$ where $\dom(L(g)) = [a] \times [b]$.
-
-Again using Lemma \ref{} and the Immerman-Vardi theorem, we can construct a
-formula $\supp$ such $\langle [n], \leq \rangle \models \supp[g,u]$ iff $\langle
-[n], \leq \rangle \models \phi_G[g]$ and $u$ is in $sp(g)$. This formula can be
-used as in \cite{} to inductively define $\supp_i(g,u)$ for each $i \in [n]$
-which holds iff $u$ is the $i$th element of the support of $g$.
-
-Define the $\agree$ and $\theta_s$ formulas for all $s \in \SB \uplus \tau
-\uplus \{0,1\}$ as in \cite{}.
-
-Now we define the formula
-\begin{align*}
-  \theta_{\rank}:= (\mu, \bar{x}) := \bigwedge_{1 \leq i < j \leq k} x_i
-  \neq x_j \wedge \forall \bar{y} ( [ \rank (x \leq \phi_{mr}, y \leq
-  \phi_{mc}, \pi \leq r). \theta^{'} ] ),
-\end{align*}
-\begin{align*}
-  \theta^{'}(a,b):= \exists \nu (W(\nu, \mu) \wedge \agree (\mu,\nu, \bar{x}, \bar{y}) \wedge \phi_L (\mu, \nu, a, b) \wedge V(\nu, y))
-\end{align*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\chapter{October 27th: Counting Gates Simulate Symmetric Gates}
-
-In this chapter we prove that symmetric circuits with majority gates are at
-least as powerful as symmetric circuits over any other Boolean basis consisting
-of symmetric functions.
-
-Recall the following that $\mathbb{B} = \{ \neg , \wedge , \lor \}$ and
-$\mathbb{B}_\maj = \{ \maj \} \cup \mathbb{B}$.
+Recall from Anderson and Dawar \cite{AndersonD17} we have that $\mathbb{B}_{\std} = \{
+\neg , \wedge , \lor \}$ and $\mathbb{B}_\maj = \{ \maj \} \cup \mathbb{B}$.
 
@@
 is the set of all $m \leq n$ such that for all $\vec{x} \in \{ 0,1 \}^n$ with
-$m$ 1's we have $F (\vec{x}) = 1$. Clearly a symmetric Boolean function $F$ is
+$m$ 1's we have $F (\vec{x}) = 1$. Clearly any symmetric Boolean function $F$ is
 entirely determined by $c_{F}$.
@@
 The above proposition has a straight forward application to circuit
-characterizations.
+characterisations.
 
-\begin{prop}
+\begin{thm}
   Let $F = \{F_i : i \in I \}$ be a family of symmetric Boolean functions where
@@
   q(f(n))$.
-\end{prop}
+\end{thm}
 
@@
 
-\chapter{October 29th: Symmetric Circuits and CPT}
-
-We already have that that the set of queries decidable by symmetric
-circuits (respectively with counting) is exactly the set of queries
-expressible in Fixed-Point Logic. We know that the CFI query is not
-expressible in FPC, and so there is no symmetric circuit that can
-compute the query.
-
-In our attempts to find a circuit characterisation of CPT, we might try and weaken the requirement of symmetry in our notion of symmetric circuits in order to express the CFI query (and perhaps the whole of CPT).
-One approach would be to weaken the requirement of having small orbits, to rather only having small orbits with respect to our particular input structure.
-We formalise this notion below.
+\subsection{G-Symmetric Functions}
+In order to extend the notion of a circuit by extending the basis we need to
+consider functions that are not symmetric in the full sense of the term but have
+some weakened notion of symmetry.
 
 \begin{definition}
-Let $C$ be a circuit on structures of size $n$.
-Let $g$ be a gate in $C$ and let $X$ be a set of input strings closed under the action of the symmetric group.
-The $inv_X = \{ \sigma \in \sym_n : \forall x \in X g \circ H (x) = g \circ H (\sigma x)$.
-\end{definition}
-\begin{definition}
-  Let $(C_n)_{n \in \mathbb{N}}$ be a family of circuits. For any
-  finite structure $\mathcal{A}$ let $X_{\mathcal{A}}$ be the set of
-  all string encodings of $\mathcal{A}$. We say a circuit family has
-  small isomorphism orbits if there is a polynomial $p(n)$ such that
-  for any sufficiently large $n$, finite structure $\mathcal{A}$ of
-  cardinality $n$ and any $g \in C_n$ we have
-  $\vert S_n : \inv_{X_{\mathcal{A}}}(g) \vert \leq p(n)$.
+  Let $f: \{0,1\}^X \rightarrow \{0,1\}$ be a function. Let $G \subseteq \sym_X$
+  be a subgroup. We say that $f$ is \emph{$G$-symmetric} if for all $\sigma \in
+  G$, $x \in X$, $f(\sigma x) = f(x)$.
 \end{definition}
 
-\begin{thm}
-  \label{thm:simple_group}
-  Let $n \in \mathbb{N}$, $n \geq 5$. Let $r \in \mathbb{N}$ such that
-  $r \leq n/2$. Suppose that $G$ is a subgroup of $\sym(n)$, then
-  there is a constant $k \in mathbb{N}$ such that for all $n \geq k$
-  if $\vert \sym(n):G \vert \leq {{n}\choose {r}}$ then there exists
-  $X \subseteq [n]$ with $\vert X \vert \leq r$ and such that
-  $\alt([n] \setminus X) \leq G$.
+We can also introduce similar notions in the case of a two dimensional Boolean
+string.
+
+\begin{definition}
+  Let $f: \{0,1\}^{A \times B} \rightarrow \{0,1\}$ be a function. Let $G
+  \subseteq \sym_{A \times B}$ be a subgroup. We say that $f$ is
+  \emph{matrix-symmetric} if it is $\sym_A \times \sym_B$-symmetric and we say
+  that $f$ is \emph{graph-symmetric} if $A = B$ and it is $\sym_A$-symmetric
+  (with $\sym_A$ acting on both $A$ and $B$).
+\end{definition}
+
+So if we think of $f: \{0,1\}^{A \times B} \rightarrow \{0,1\}$ as representing
+a matrix, then matrix-symmetry corresponds to the property of the function being
+invariant under row-column permutations. If, instead, we have that $A = B$ and
+we then think of $f$ as encoding the adjacency matrix of a graph, then
+graph-symmetry corresponds to the function being constant on isomorphism
+classes.
+
+Importantly, many natural functions of interest are matrix symmetric. For
+example, the function that computes the rank of the matrix over $\mathbb{F}_2$.
+or a thresholded rank function, for example the rank of the matrix over
+$\mathbb{F}_p$ being larger then $r$, for some particular $(p, r) \in
+\mathbb{N}$.
+
+In this section we develop the corresponding notion of a symmetric circuit, ones
+which allow for the inclusion of matrix-symmetric gates. In particular, these
+circuits are defined using two sets of Boolean functions. The first, denoted by
+$\mathbb{B}_\sym$, is taken to be the symmetric Boolean basis (either
+$\mathbb{B}_\std$ or $\mathbb{B}_\maj$). The second, denoted by
+$\mathbb{B}_\matsym$ is taken to be the matrix-symmetric basis, consisting of a
+collection of matrix-symmetric functions.
+
+\begin{definition}[Circuits on Structures]
+  For $\mathbb{B}_{\sym}$ a basis of Boolean symmetric functions,
+  $\mathbb{B}_{\matsym}$ a basis of Boolean matrix-symmetric functions and
+  $\tau$ a set of relation symbols, we define a $(\mathbb{B}_\sym,
+  \mathbb{B}_\sym, \tau)$-circuit $C_n$ computing a $q$-ary query $Q$ is a
+  structure $\langle G, W, \Omega, \Sigma, \Lambda, L\rangle$.
+  \begin{itemize}
+    \setlength\itemsep{0mm}
+  \item $G$ is called the set of gates of $C_n$ and $\vert C_n \vert := \vert G
+    \vert$.
+  \item $W \subseteq G \times G$, where $W$ is called the wires of the circuit.
+    $(G,W)$ must be a directed acyclic graph. For $g \in G$ we $H_g := \{ h \in
+    C_n : W(h,g)\}$ be the set of children of $g$.
+  \item $\Omega$ is an injective function from $[n]^q$ to $G$. The gates in the
+    image of $\Omega$ are called the output gates. When $q = 0$, $\Omega$ is a
+    constant function mapping to a single output gate.
+  \item $\Sigma$ is a function from $G$ to $\mathbb{B}_\sym \uplus
+    \mathbb{B}_\matstab \uplus \tau \uplus \{0,1\} $ which maps input gates to
+    $\tau \uplus \{0,1\}$ and where $\Sigma^{-1} (0) \leq 1$ $\Sigma^{-1} (1)
+    \leq 1$ and the internal gates get mapped into $\mathbb{B}_\sym \uplus
+    \mathbb{B}_\matstab$. Gates mapped to $\tau$ are called relational gates and
+    gates mapped to 1 or 0 are called constant gates.
+  \item $\Lambda$ is a sequence of injective functions $(\Lambda_R)_{R \in
+      \tau}$ where for each $R \in \tau$, $\Lambda_R$ maps each relational gate
+    $g$ with $R = \Sigma (g)$ to the tuple $\Lambda_R (g) \in [n]^r$, where $r$
+    is the arity of the symbol $R$. When no ambiguity arises we write $\Lambda
+    (g)$ for $\Lambda_R (g)$.
+  \item $L$ assigns labels to the gates (and their inputs) in $C_n$. Let $g \in
+    G$ be an internal gate and $H$ be the gates input to $g$. Then $L(g) : A
+    \times B \rightarrow H$, where $L(g)$ must be surjective and $A, B \subseteq
+    [n]$. We call this the \emph{matrix labelling} of $g$.
+  \end{itemize}
+\end{definition}
+
+Note the additional requirement that each gate have an associated labelling in
+order to facilitate the evaluation of the gate.
+
+Given some finite $\tau$-structure $\mathcal{A}$ of size $n$ and some bijection
+$\gamma: U \rightarrow [n]$, the evaluation of some $(\mathbb{B}_\sym,
+\mathbb{B}_\sym, \tau)$-circuit) circuit $C$ proceeds by recursively evaluating
+gates. Here the evaluation of the gate $g$ is denoted by $C[\gamma
+\mathcal{A}](g)$. If $g$ is anything but a matrix-symmetric gate, then the
+evaluation is as per the symmetric circuits of Anderson and Dawar \cite{}. If
+$g$ is matrix-symmetric then the evaluation is given by applying the Boolean
+operation $\Sigma(g)$ to the matrix $L^{\gamma}:\dom(L(g)) \rightarrow \{0,1\}$
+defined by $L^{\gamma}(i,j) = C[\gamma \mathcal{A}](L(g)(i,j))$.
+
+\begin{definition}[Invariant Circuit\cite{AndersonD17}]
+  Let $C_n$ be a $(\mathbb{B}_\sym, \mathbb{B}_\sym, \tau)$-circuit, computing
+  some $q$-ary query. We say $C_n$ is \emph{invariant} if for every
+  $\tau$-structure $\mathcal{A}$ of size $n$, $a \in \mathcal{A}^q$, and
+  bijections $\gamma_1, \gamma_2: U \rightarrow [n]$ we have that $C[\gamma_1
+  \mathcal{A}](\Omega (\gamma_1 a)) = C[\gamma_2 \mathcal{A}](\Omega (\gamma_2
+  a))$.
+\end{definition}
+
+\begin{definition}[Automorphism]
+  let $C = \langle G, W, \Omega, \Sigma, \Lambda, L\rangle$ be a
+  $(\mathbb{B}_\sym, \mathbb{B}_\matsym, \tau)$-circuit computing at $q$-ary
+  query on structures of size $n$. Let $\sigma \in \sym_n$ and $\pi: G
+  \rightarrow G$ be a bijection such that
+  \begin{itemize}
+    \setlength\itemsep{0mm}
+  \item for all gates $g, h \in G$, $W(g,h)$ iff $W(\pi g, \pi h)$,
+  \item for all output tuples $x \in [n]^q$, $\pi \Omega (x) = \Omega (\sigma
+    x)$,
+  \item for all gates $g \in G$, $\Sigma (g) = \Sigma (\pi g)$,
+  \item for each relational gate $g \in G$, $\sigma \Lambda (g) = \Lambda (\pi
+    g)$, and
+  \item for each internal gate $g$ if $\Sigma (g) \in \mathbb(B)_\matsym$ then
+    we have that $L(\pi g) \sim \pi \cdot L(g)$.
+  \end{itemize}
+
+  We call $\pi$ an \emph{automorphism} of $C$, and we say that $\sigma$
+  \emph{induces the automorphism} $\pi$. The group of automorphisms of $C$ is
+  called $\aut_n (C)$.
+\end{definition}
+
+\begin{definition}[Symmetric\cite{AndersonD17}]
+  A circuit $C$ on structures of size $n$ is called \emph{symmetric} if every
+  $\sigma \in \sym_n$ induces an automorphism on $C$.
+\end{definition}
+
+It follows for any symmetric circuit $C_n$ there is a mapping from $\sym_n$ to
+$\aut_n(C)$, from $ \sigma$ to the induced automorphism. This homomorphism is
+injective so long as a single element of $[n]$ appears in the in the label of
+some input gate of $C$ (as then all elements appear by
+symmetry)\cite{AndersonD17}. In this paper we always assume that there is always
+one such element as otherwise all inputs are constant, and so the circuit just
+computes a constant function. In order to assure this homomorphism is surjective
+Anderson and Dawar \cite{AndersonD17} introduce the notion of a \emph{rigid}
+circuit.
+
+\begin{definition}[Rigidity]
+  Let C be a $(\mathbb{B}_\sym, \mathbb{B}_\sym, \tau)$-circuit, where $C =
+  \langle G, W, \Omega, \Sigma, \Lambda, L\rangle$. Say that $C$ is rigid if
+  there are no internal gates $g, g' \in G$ such that $\Sigma(g) = \Sigma (g')$,
+  $\Omega^{-1}(g) = \Omega^{-1}(g')$, and for every $g'' \in G$, $W(g'', g')$
+  and $W(g,g'')$ iff $W(g', g'')$.
+\end{definition}
+
+Another property which simplifies our analysis is the property of having
+\emph{bijective labels}.
+
+\begin{definition}
+  We say that a circuit $C$ has bijective labels if for each gate $g$ in $C$,
+  $L(g)$ is a bijection.
+\end{definition}
+
+We prove in a later section that a circuit may be transformed in polynomial time
+into an equivalent circuit that is both rigid and has bijective labelings. Hence
+we may assume these two properties without a loss of generality.
+
+With the assumption of rigidity in place, we abuse notation for permutations and
+let $\sigma \in \sym_n$ also denote the induced automorphism.
+
+We finally want to define symmetric circuits with rank gates.
+
+\begin{definition}
+  Let $\mathbb{B}_{\matsym}$ consist of functions of the form $f_{p,r}:
+  \{0,1\}^{A \times B} \rightarrow \{0,1\}$ for $A, B$ initial segments of
+  $\mathbb{N}$ and $f, p \in \mathbb{N}$, with $p$ prime, and such that for
+  $f_{p,r}(M) = 1$ iff the matrix $M: A \times B \rightarrow \{0,1\}$ has rank
+  at least $r$ over the field $\mathbb{F}_p$. A \emph{symmetric circuit with
+    rank gates} is a $(\mathbb{B}_\maj, \mathbb{B}_\matsym, \tau)$-circuit, for some
+  vocabulary $\tau$.
+\end{definition}
+
+The natural restriction to consider on families of circuits is uniformity.
+
+\begin{definition}
+  Let $(C_n)_{n \in \mathbb{N}}$ be a family of Boolean circuits. We say that
+  $(C_n)_{n \in \mathbb{N}}$ is \emph{$P$-uniform} if the mapping $n \mapsto C_n$ is
+  computable in polynomial time.
+\end{definition}
+
+We are now ready to state what will be the main theorem of this paper.
+
+\begin{thm}[Main Theorem]
+ A graph property is decidable by a $P$-uniform family of symmetric circuits
+ with rank gates if, and only if, it is definable by an FPR sentence.
 \end{thm}
 
-The following result shows that even this weakened definition fails to
-capture CPT.
-\begin{thm}
-  There is no family of circuits with small isomorphism orbits that
-  expresses the CFI query.
-\end{thm}
-\begin{proof}
-  Let $(G_n)_{n \in \mathbb{N}}$ be a family of ordered graphs such that each $G_n$ has
-  odd and even CFI graphs $\mathfrak{G}$ and $\tilde{\mathfrak{G}}$ respectively, each of
-  cardinality $n$. Furthermore, suppose the CFI query for $(G_n)$ is not expressible in
-  FPC (the existence of such a family is guaranteed by
-  \cite{}). Suppose there exists a family of circuits $(C_n)_{n \in \mathbb{N}}$ with
-  small isomorphism orbits that decides the CFI query for $(G_n)$.
-  Then we have that $C_n(\mathfrak{G}) = 1$ and
-  $C_n(\tilde{\mathfrak{G}}) = 0$, and for any $g \in C_n$
+% \section{Circuits to FPR}
 
-  \begin{align*}
-    \vert S_n : \inv_{X_{\mathcal{G}}}(g) \vert &\leq p(n),\\
-    \vert S_n : \inv_{X_{\tilde{\mathcal{G}}}}(g) \vert &\leq p(n)
-  \end{align*}.
-  Let $k$ be such that $p(n) \leq n^k$ for all sufficiently large $n$.
-Then we have that $p(n) \leq n^k \leq {{n}\choose{k+1}}$ for all sufficiently large $n$, and (again, taking $n$ large enough) we have that $k \leq n/2$.
-Taking $n$ larger than the constant in Theorem \ref{thm:simple_group} it follows that there exists an $X_1, X_2 \subseteq [n]$ such that $\vert X_1 \vert, \vert X_2 \vert \leq k$ and $\alt ([n] \setminus X_1) \subseteq  \inv_{X_{\mathfrak{G}}}(g)$, $\alt ([n] \setminus X_2) \subseteq  \inv_{X_{\tilde{\mathfrak{G}}}}(g)$.
-It follows that
-  \begin{align*}
-    \alt ([n] \setminus (X_1 \cup X_2)) &\subseteq \alt ([n] \setminus X_1) \cap \alt ([n] \setminus X_2)\\
-                                        &\subseteq \inv_{X_{\mathfrak{G}}}(g) \cap \inv_{X_{\tilde{\mathfrak{G}}}}(g) \\
-                                        &\subseteq \inv_{X_{\mathfrak{G} \cup \tilde{\mathfrak{G}}}}(g) =  \inv_{CFI(G)}(g),
-  \end{align*}
-  where $CFI(G)$ is set of all encodings of all CFI graphs of $G_n$.
-
-  We then have that
-  \begin{align*}
-    \vert S_n : \inv_{CFI(G)}(g) \vert \leq \vert S_n : \alt ([n] \setminus (X_1 \cup X_2)) \leq  \frac{n!}{(n-2k)!/2} \leq n^{2k+1},
-  \end{align*}
-  with the last inequality following for large enough $n$. We thus
-  have from Theorem \ref{} that there is a symmetric circuit $D_n$
-  that decides the CFI problem for $G_n$, and hence a family $(D_n)$
-  that decides the CFI problem for the family of graphs $(G_n)$. From
-  the theorem of Dawar et al. \cite{}, it follows that there is as
-  formula of FPC that decides the CFI query for $(G_n)$ contradicting
-  our assumption.
-\end{proof}
+% In this section I discuss how to determine the rank a matrix labelling at some
+% gate $g$. This is a rough copy written for the purpose of discussion. In this
+% section we fix some circuit $C_n$ and some rank gate $g$ in $C_n$ with a set
+% of children $H$ and matrix labelling $L: [a] \times [b] \rightarrow H$ (which
+% we assume WLOG is a bijection).
 \end{document}

### 2017-07-26 sections/symmetric-circuits.tex
26/07/2017

\documentclass[../paper.tex]{subfiles}
%\usepackage{../mymacros}
\begin{document}
% Note: include circuits in background
Circuits are a well-studied model in complexity theory and, more recently, they
have been studied in the context of finite model theory. Circuits in the
literature () are usually defined as DAG's, with each vertex labelled by some
element of a basis. While not explicitly stated, a consequence of this
definition is that, when evaluating a gate, the Boolean function labelling this
gate should not depend on any ordering or labelling of its input. In other
words, it must be a symmetric function.

Motivated by the desire to study circuits with gates that compute rank, a
function which is not symmetric, we develop a general framework for studying
functions whose output depends on the structure of the input. This structure
also allows us to define and explore appropriate symmetries on the function.

With the necessary structure on the input of each Boolean function explicitly given, we then
develop a circuit model which incorporates this structure, and so allows for
circuits to be defined over Basis of functions that are not symmetric.

Finally, we prove that no family of Basis of symmetric functions can improve on
the expressive power of the circuit model of Anderson and Dawar \cite{AndersonD17}.
Together with the main theorem of this paper this implies that the more general
circuit models that are defined over basis of functions which are not symmetric
(with respect to the whole symmetric group) are strictly more powerful.

% consider the problem of explicitly labelling the input of the function both so
% that the semantics of the function can be reasonably defined and so as to
% ensure that appropriate symmetry conditions on the function can be enforced.

% labelled by functions that are not symmetric, we need to think explicitly
% about how the input is to be labelled and how that structure should be
% mirrored in the circuit definition. In particular, we should like to consider
% functions which invariant under some action and so choose labellings which
% appropriately reflect the required symmetry conditions of the function.

% In this section we first discuss how to structure the input to a Boolean
% function appropriately and how symmetries on that input structure induce
% useful symmetries on the function.

\subsection{$\tau$-Symmetric Functions}
% note: include many-sorted signature in background
Let $\tau = (R, S, \nu)$ be a many-sorted, relational signature. Suppose some
ordering on the set of relations and sorts, so $R = \{R_1 \ldots, R_t\}$ and $S
= \{s_1, \ldots s_p\}$, and let $\nu(R_i) = (a^i_1, \ldots , a^i_{\arty(R_i)})$,
where $a^i_q \in S$ for all $q \in [\arty(R_i)]$. For each $s \in S$ let $A_{s}$
be a non-empty set, and let $A = A_{s_1} \times \ldots \times A_{s_p}$. Let
\[
  X^{\tau}_A:= A_{a^1_1} \times \ldots \times A_{a^1_{\arty(R_1)}} \times \ldots
  \times A_{a^t_1} \times A_{a^t_{\arty(R_t)}}.
\]

Let $G \leq \sym_{A_{s_1}} \times \ldots \times \sym_{A_{s_p}}$. There is a
natural action of $G$ on $X$. It is easy to see that if $\mathcal{C}_A$ is the
category with objects given by $\tau$-structures over $A$ and morphisms by the
action of $G$, and $\mathcal{C}_X$ is the category of subsets of $X^{\tau}_A$
with morphisms similarly given by the action of $G$, then these two categories
are equivalent. More informally, the subsets of $X^{\tau}_A$ encode the
$\tau$-structures over $A$. This relationship is bijective and the action of $G$
factors through this bijection.

\begin{remark}
  Is the categorical language unnecessary? It seemed the quickest way of saying
  what I wanted to say formally.
\end{remark}

\begin{remark}
  In the above section (and just below) we talk about the action of
  $\sym_{A_{s_1}} \times \ldots \times \sym_{A_{s_p}}$ on elements of $X^\tau_A$
  and structured functions. In the proof of the support theorem, when defining a
  definable matrix for converting circuits into formulas, and later on in this
  section, it is useful to speak more generally and instead look at bijections
  from $A_1, \ldots A_{s_p}$ to $B_1, \ldots, B_{s_p}$, thus allowing us to map
  between $X^\tau_A$ and $X^\tau_B$ and so between the associated structured
  functions. I've added this in later on in the section, but I still need to
  incorporate it into the original definition (it's a more general notion in a
  sense, and so I think it should be incorporated). I'll wait for feedback
  before doing this as I'm not sure this formulation will survive.
\end{remark}

Note that there is also a natural action on functions of the form $\vec{i}:
X^{\tau}_A \rightarrow \{0,1\}$ given by $\sigma \cdot \vec{i}(x) =
\vec{i}(\sigma x)$.

We now introduce a few useful notions of symmetry. We call a function of the
form $F:\{0,1\}^{X^{\tau}_A} \rightarrow \{0,1\}$ a \emph{$(\tau, A)$-structured
  function}, with $\tau$ called the \emph{signature of $F$} and $A$ \emph{the
  universe of $F$}. Call $F$ a \emph{structured function} if it is a $(\tau,
A)$-structured function for some appropriate $\tau$ and $A$.

We say a $(\tau, A)$-function is \emph{$(\tau, G)$-symmetric} if for all
$\vec{i} \in \{0,1\}^{X^\tau_A}$ and $\sigma \in G$, $f(\sigma \cdot \vec{i}) =
f(\vec{i})$. We say $F$ is \emph{$\tau$-symmetric} if it is $(\tau,
\sym_{A_{s_1}} \times \ldots \times \sym_{A_{s_p}})$-symmetric. Let $\tau = (S,
R, \nu)$, with $\vert S \vert \leq 2$, $R = {R'}$ and $\nu (R') = (s_1, s_2)$
(with $s_1$ and $s_2$ being the first and last elements of S in the ordering
respectively); if $F$ is $\tau$-symmetric we say $F$ is \emph{matrix-symmetric}.
If $\tau$ is single-sorted we call $F$ \emph{simple} and if it consists of a
single unary relation, we call $F$ \emph{unary}. We say $F$ is
\emph{graph-symmetric} if $F$ is simple and matrix-symmetric.

\begin{lem}
  Let $X^\tau_A$ be defined as above and let $F: \{0,1\}^{X^{\tau}_A}
  \rightarrow \{0,1\}$, then $F$ is a symmetric function (in the sense of
  Anderson and Dawar \cite{AndersonD17}) if and only if $F$ is a simple and
  unary.
\end{lem}

We briefly introduce notions of equivalence useful for comparing functions.
\begin{definition}
  Let $\tau = (R, S, \nu)$ be a many-sorted signature and let $A = A_1 \times
  \ldots A_s$ and $B = B_1 \times \ldots \times B_s$ be a product of non-empty
  sets. A \emph{sorted bijection} between $A$ and $B$ is a function bijections
  $f: A \rightarrow B$ such that $f (A_i) = B_i$ for all $i \in S$. There is an
  obvious action of $f$ that maps $X^\tau_A$ to $X^\tau_B$ and
  $\{0,1\}^{X^\tau_A}$ to $\{0,1\}^{X^\tau_B}$.

  Let $L: X^\tau_A \rightarrow H$ and $L': X^\tau_B \rightarrow H$ be two
  functions for some finite set $H$. We say that $L \sim L'$, or \emph{$L$ is
    equivalent to $L'$}, if there is a sorted bijection $f: A \rightarrow B$
  such that for all $x \in X^\tau_A$, $L(x) = L'(f (x))$.

  Let $F$ be a $(\tau, A)$-structured function and $G$ be a $(\tau,
  B)$-structured function. Then we say that $F \sim G$, or \emph{$F$ is
    equivalent to $G$}, if there is a sorted bijection $f: A rightarrow B$ such
  that for all $\vec{i} \in \{0,1\}^{X^\tau_A}$, $F (\vec{i}) = G(f(\vec{i}))$.
\end{definition}

\begin{remark}
  There is an obvious connection between $\tau$-symmetric functions and
  generalised quantifiers (or closed classes of structures). Should I include
  details about this connection? I also feel a lot of dirtiness might be
  avoidable if we instead recast everything in terms of generalised quantifiers.
  For one, generalised quantifiers give a natural way of defining a Boolean
  function for each input universe.
\end{remark}

\subsection{Symmetric Circuits}
Having developed the notion of a function that accepts input structured in
accordance with some vocabulary, we now develop a circuit model which
incorporates this structure on the inputs of a gate. We use this general
framework to define the notion of a matrix-symmetric circuit, a circuit with
gates labelled by matrix-symmetric Boolean functions, and finally we develop the
notion of a matrix-symmetric circuit with rank.

% Importantly, many natural functions of interest are matrix symmetric. For
% example, the function that computes the rank of the matrix over
% $\mathbb{F}_2$. or a thresholded rank function, for example the rank of the
% matrix over $\mathbb{F}_p$ being larger then $r$, for some particular $(p, r)
% \in \mathbb{N}$.

\begin{definition}[Circuits on Structures]
  Let $\mathbb{B}$ be a basis of structured functions and $\tau$ a set of
  relation symbols, we define a \emph{$(\mathbb{B}, \tau)$-circuit} $C_n$
  computing a $q$-ary query $Q$ is a structure $\langle G, W, \Omega, \Sigma,
  \Lambda, L\rangle$.
  \begin{itemize}
    \setlength\itemsep{0mm}
  \item $G$ is called the set of gates of $C_n$ and $\vert C_n \vert := \vert G
    \vert$.
  \item $W \subseteq G \times G$, where $W$ is called the wires of the circuit.
    $(G,W)$ must be a directed acyclic graph. For $g \in G$ we $H_g := \{ h \in
    G: W(h,g)\}$ be the set of children of $g$.
  \item $\Omega$ is an injective function from $[n]^q$ to $G$. The gates in the
    image of $\Omega$ are called the output gates. When $q = 0$, $\Omega$ is a
    constant function mapping to a single output gate.
  \item $\Sigma$ is a function from $G$ to $\mathbb{B} \uplus \tau \uplus
    \{0,1\} $ which maps input gates to $\tau \uplus \{0,1\}$ and where $\vert
    \Sigma^{-1} (0) \vert \leq 1$ $\vert \Sigma^{-1} (1) \vert \leq 1$ and the
    internal gates get mapped into $\mathbb{B}$. Gates mapped to $\tau$ are
    called relational gates and gates mapped to 1 or 0 are called constant
    gates.
  \item $\Lambda$ is a sequence of injective functions $(\Lambda_R)_{R \in
      \tau}$ where for each $R \in \tau$, $\Lambda_R$ maps each relational gate
    $g$ with $R = \Sigma (g)$ to the tuple $\Lambda_R (g) \in [n]^r$, where $r$
    is the arity of the symbol $R$. When no ambiguity arises we write $\Lambda
    (g)$ for $\Lambda_R (g)$.
  \item $L$ to each gate a labelling on its children. Let $\tau_g$ and $A_g$ be
    such that $\Sigma(g)$ is a $(\tau_g, A_g)$-structured function. Then $L(g)$
    is a surjection from $X^{\tau_g}_{A_g}$ to $H_g$. We call $L(g)$ the
    \emph{structure-labelling} of $g$.
  \end{itemize}
\end{definition}

Given some finite $\tau$-structure $\mathcal{A}$ of size $n$ and some bijection
$\gamma: U \rightarrow [n]$ and let $\gamma \mathcal{A}$ be the structure formed
by mapping the universe of $\mathcal{A}$ in accordance with $\gamma$. The
evaluation of some $(\mathbb{B}, \tau)$-circuit $C$ proceeds by recursively
evaluating gates. The evaluation of the gate $g$ using $\gamma$ with input
$\mathcal{A}$ is denoted by $C[\gamma \mathcal{A}](g)$. The evaluation of a gate
$g$ is given as follows.
\begin{enumerate}
  \setlength\itemsep{0mm}
\item If $g$ is a constant gate then it evaluates to the bit given by
  $\Sigma(g)$.
\item If $g$ is a relational gate then $g$ evaluates to true iff $\gamma
  \mathcal{A} \models \Sigma(g)(\Lambda (g))$.
\item If $g$ is an internal gate labelled by a $(\tau_g, A_g)$-structured
  function $\Sigma(g)$, let $L^{\gamma}_g: X^{\tau_g}_{A_g} \rightarrow \{0,1\}$
  be defined by $L^{\gamma}_g(x) = C[\gamma \mathcal{A}](L(g)(x))$. Then $g$
  evaluates to true iff $\Sigma(g) (L^{\gamma}_g)$.
\end{enumerate}
$C$ defines the $q$-ary query $Q \subseteq \mathcal{A}^q$ where $a \in Q$ iff
$C[\gamma \mathcal{A}](\Omega (\gamma a)) = 1$.

The following definition is an important circuit property introduced by Anderson
and Dawar \cite{AndersonD17}. We introduce it for the sake of comparison.

\begin{definition}[Invariant Circuit]
  Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit, computing some $q$-ary query. We
  say $C_n$ is \emph{invariant} if for every $\tau$-structure $\mathcal{A}$ of
  size $n$, $a \in \mathcal{A}^q$, and bijections $\gamma_1, \gamma_2: U
  \rightarrow [n]$ we have that $C[\gamma_1 \mathcal{A}](\Omega (\gamma_1 a)) =
  C[\gamma_2 \mathcal{A}](\Omega (\gamma_2 a))$.
\end{definition}

This property ensures that a circuit (or a family of circuits) is invariant
under isomorphism. In other words, the circuit (or family of circuits) decides a
graph property. The following lemma allows us to recast this notion in terms of
the language developed in this paper.

\begin{definition}
  Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit computing a Boolean query. We have
  that $C_n$ computes a $(\tau, [n])$-structured function $F$. We say $C_n$ is
  $\tau$-symmetric if $F$ is $\tau$-symmetric.
\end{definition}

\begin{lem}
  Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit. $C_n$ is $\tau$-symmetric iff
  $C_n$ is invariant.
\end{lem}

The following definition gives us a way of saying that two structured functions
with the same signature are equivalent up to a choice of their universe.

\begin{definition}[Automorphism]
  let $C = \langle G, W, \Omega, \Sigma, \Lambda, L\rangle$ be a
  $(\mathbb{B},\tau)$-circuit computing at $q$-ary query on structures of size
  $n$. Let $\sigma \in \sym_n$ and $\pi: G \rightarrow G$ be a bijection such
  that
  \begin{itemize}
    \setlength\itemsep{0mm}
  \item for all gates $g, h \in G$, $W(g,h)$ iff $W(\pi g, \pi h)$,
  \item for all output tuples $x \in [n]^q$, $\pi \Omega (x) = \Omega (\sigma
    x)$,
  \item for all gates $g \in G$, let $\Sigma (g) \sim \Sigma (\pi g)$,
  \item for each relational gate $g \in G$, $\sigma \Lambda (g) = \Lambda (\pi
    g)$, and
  \item for each internal gate $g$ if $\Sigma (g) \in \mathbb(B)$ then we have
    that $L(\pi g) \sim \pi \cdot L(g)$.
  \end{itemize}

  We call $\pi$ an \emph{automorphism} of $C$, and we say that $\sigma$
  \emph{induces the automorphism} $\pi$. The group of automorphisms of $C$ is
  called $\aut_n (C)$.
\end{definition}

\begin{definition}[Symmetry]
  A circuit $C$ on structures of size $n$ is called \emph{symmetric} if every
  $\sigma \in \sym_n$ induces an automorphism on $C$.
\end{definition}

It follows for any symmetric circuit $C_n$ there is a homomorphism $h$ that maps
$\sym_n$ to $\aut_n(C)$. This homomorphism is injective so long as a single
element of $[n]$ appears in the in the label of some input gate of $C$ (as then
all elements appear by symmetry)\cite{AndersonD17}. In this paper we always
assume that there is at least one such element, as otherwise all inputs are
constant, and so the circuit just computes a constant function. In order to
assure this homomorphism is surjective Anderson and Dawar \cite{AndersonD17}
introduce the notion of a \emph{rigid} circuit.

\begin{definition}[Rigidity]
  Let C be a $(\mathbb{B}, \tau)$-circuit, where $C = \langle G, W, \Omega,
  \Sigma, \Lambda, L\rangle$. Say that $C$ is rigid if there are no distinct
  internal gates $g, g' \in G$ such that $\Sigma(g) \sim \Sigma (g')$,
  $\Omega^{-1}(g) = \Omega^{-1}(g')$, $H_g = H_{g'}$ and $L(g) \sim L'(g)$.
\end{definition}

Another property which simplifies our analysis is the property of having
\emph{bijective labels}.

\begin{definition}
  We say that a circuit $C$ has \emph{bijective labels} if for each gate $g$ in
  $C$, $L(g)$ is a bijection.
\end{definition}

We prove in a later section that a circuit may be transformed in polynomial time
into an equivalent circuit that is both rigid and has bijective labelings. Hence
we may assume these two properties without a loss of generality.

With the assumption of rigidity in place, we abuse notation for permutations and
let $\sigma \in \sym_n$ also denote the induced automorphism.

We finally want to define a circuits that allow for gates labelled by
matrix-symmetric functions.
\begin{definition}
  Let $\mathbb{B}$ be a basis containing all simple unary structured functions
  that compute $\land$, $\lor$, $\neg$ and $\maj$ and such that all elements of
  this basis are either matrix-symmetric or simple unary. We call a
  $(\mathbb{B}, \tau)$-circuit a \emph{matrix-symmetric circuit}.
\end{definition}

We define a circuit that has gates that compute rank.
\begin{definition}
  Let the $(\mathbb{B}, \tau)$-circuit $C$ be a matrix-symmetric circuit. Let
  $\mathbb{B}_m$ be the subset of $\mathbb{B}$ consisting of all those functions
  that are matrix-symmetric but not symmetric. For any non-empty sets $A_1, A_2$
  and $r, p \in \mathbb{N}$, where $p$ prime define a $F_{p,r}: \{0,1\}^{A_1
    \times A_2} \rightarrow \{0,1\}$ such that $f_{p,r}(M) = 1$ iff the matrix
  $M: A_1 \times B_1 \rightarrow \{0,1\}$ has rank at least $r$ over the field
  $\mathbb{F}_p$. We call such a function a \emph{bounded-rank function}. If
  $\mathbb{B}_m$ is equal to the set of all such bounded-rank functions, then we
  call $C$ a \emph{symmetric circuit with rank gates}.
\end{definition}

% The natural restriction to consider on families of circuits is uniformity.

% \begin{definition}
%   Let $(C_n)_{n \in \mathbb{N}}$ be a family of Boolean circuits. We say that
%   $(C_n)_{n \in \mathbb{N}}$ is \emph{$P$-uniform} if the mapping $n \mapsto
%   C_n$ is computable in polynomial time.
% \end{definition}

We are now ready to state what will be the main theorem of this paper.
\begin{thm}[Main Theorem]
  A graph property is decidable by a $P$-uniform family of symmetric circuits
  with rank gates if, and only if, it is definable by an FPR sentence.
\end{thm}

\subsection{Limitations of Symmetric Bases}
When looking at symmetric circuits with matrix symmetric functions, it is
natural to ask if this extension to matrix-symmetric functions is really
necessary. In this section we show that Symmetric circuits, as developed by
Anderson and Dawar, defined over the usual basis with majority gates can compute
any symmetric function over polynomial size circuits. As such no additional
symmetric function added to the Basis improves the power of the model.

Recall from Anderson and Dawar \cite{AndersonD17} we have that
$\mathbb{B}_{\std} = \{ \neg , \wedge , \lor \}$ and $\mathbb{B}_\maj = \{ \maj
\} \cup \mathbb{B}$.

Let $F: \{0,1\}^* \rightarrow \{0,1\}$ be a symmetric Boolean function. Since
$F$ is symmetric we note that for a fixed size input the output of $F$ is
entirely determined by the number of 1's in its input. Then let
$c_{F}:\mathbb{N} \rightarrow 2^{\mathbb{N}}$ define a function where $c_{F}(n)$
is the set of all $m \leq n$ such that for all $\vec{x} \in \{ 0,1 \}^n$ with
$m$ 1's we have $F (\vec{x}) = 1$. Clearly any symmetric Boolean function $F$ is
entirely determined by $c_{F}$.

\begin{prop}
  \label{prop:fuctions-maj}
  There is a polynomial $p(k)$ such that for any symmetric function $F$ and a
  given $k \in \mathbb{N}$ there is a circuit $C_k$ on $k$ inputs over the basis
  $\mathbb{B}_\maj$ which is symmetric, constant depth and with width bounded by
  $p(k)$.
\end{prop}

\begin{proof}
  We define the circuit $C_k$ for inputs $\vec{x} = ( x_1, \ldots, x_k )$.

  For $a \in \mathbb{N}$ we define a gate $\countgate_a$ by
  \begin{align*}
    \countgate_a = \begin{cases} \maj (x_1, \ldots, x_k, \underbrace {0, \ldots,
        0}_{2a - k}) \land \neg \maj (x_1, \ldots , x_k, \underbrace{0, \ldots,
        0}_{2a - k + 2}) &  a \geq \frac{k}{2} \\
      \maj (x_1, \ldots, x_k, \underbrace {1, \ldots, 1}_{x - 2a}) \land \neg
      \maj (x_1, \ldots , x_k, \underbrace{1, \ldots, 1}_{k - 2a -2}) & a <
      \frac{k}{2}.
    \end{cases}
  \end{align*}
  Then let $g = \bigvee_{a \in c_{F_i}(k)}\countgate_a$ and let $C_{k}$ be the
  circuit with input gates labeled by $\vec{x}$ and output gate $g$.

  t is easy to see that $C_k$ is constant depth and it's width is a polynomial
  in $k$. We have that in each layer of $C_{g'}$ each gate is connected to all
  gates in the previous layer, and as such the circuit is symmetric.
\end{proof}

The above proposition has a straight forward application to circuit
characterisations.

\begin{thm}
  Let $F = \{F_i : i \in I \}$ be a family of symmetric Boolean functions where
  $F_i: \{0,1\}^* \rightarrow \{ 0,1 \}$.

  Let $(C_n)_{n \in \mathbb{N}}$ be family of symmetric circuits over the
  Boolean basis $\mathbb{B} \cup F$, where $C_n$ is a circuit on structures of
  size $n$, and the size of each circuit in the family is bounded by some
  function $f(n)$. Then there exists a polynomial $q(n)$ and a family of
  symmetric circuits $(C_n')_{n \in \mathbb{N}}$ over $\mathbb{B}_\maj$, where
  $C_n'$ is a circuit on structures of size $n$ and $\vert C_n' \vert \leq
  q(f(n))$.
\end{thm}

\begin{proof}
  From $C_n$ we construct $C_n'$ in the obvious way. For each gate $g \in C_n$
  of type $F_i$ we have a symmetric circuit $C_g$ from Proposition
  \ref{prop:function-maj} that computes the same function as $g$. Then let
  $C_n'$ be $C_n$ but with each gate $g$ replaced by $C_g$. It is easy to see
  that $C_n'$ is symmetric. We also have that each gate $g$ must have at most
  $f(n)$ inputs, and the size of $C_g$ is bounded by $p(f(n))$. Thus the size of
  $C_n'$ is bounded by $f(n)p(f(n))$.
\end{proof}

This result, combined with the main result of this paper, gives us that
symmetric circuits with rank are a strictly more powerful model than any circuit
model defined over a basis of symmetric functions.

% \section{Circuits to FPR}

% In this section I discuss how to determine the rank a matrix labelling at some
% gate $g$. This is a rough copy written for the purpose of discussion. In this
% section we fix some circuit $C_n$ and some rank gate $g$ in $C_n$ with a set
% of children $H$ and matrix labelling $L: [a] \times [b] \rightarrow H$ (which
% we assume WLOG is a bijection).
\end{document}

### 2017-07-26 paper.tex
26/07/2017

--- 2016-12-14 paper.tex
@@
-\documentclass[12pt]{report}
+\documentclass[12pt]{article}
 
-% This first part of the file is called the PREAMBLE. It includes
-% customizations and command definitions. The preamble is everything
-% between \documentclass and \begin{document}.
+% This first part of the file is called the PREAMBLE. It includes customizations
+% and command definitions. The preamble is everything between \documentclass
+% and \begin{document}.
 
@@
 \usepackage{amsthm} % better theorem environments
+\usepackage{xspace}
+\usepackage{subfiles}%allow for subfiles
+\usepackage{blindtext}
+\usepackage{mymacros}
 
-% various theorems, numbered by section
-
-\newtheorem{thm}{Theorem} \newtheorem{claim}{Claim}
-\newtheorem{remark}{Remark} \newtheorem{definition}{Definition}
-\newtheorem{lem}[thm]{Lemma} \newtheorem{prop}[thm]{Proposition}
-\newtheorem{cor}[thm]{Corollary} \newtheorem{conj}[thm]{Conjecture}
+\newtheorem{thm}{Theorem}
+\newtheorem{claim}[thm]{Claim}
+\newtheorem{remark}[thm]{Remark}
+\newtheorem{definition}[thm]{Definition}
+\newtheorem{lem}[thm]{Lemma}
+\newtheorem{prop}[thm]{Proposition}
+\newtheorem{cor}[thm]{Corollary}
+\newtheorem{conj}[thm]{Conjecture}
 
@@
 
-\newcommand{\bd}[1]{\mathbf{#1}} % for bolding symbols
-\newcommand{\RR}{\mathbb{R}} % for Real numbers
-\newcommand{\ZZ}{\mathbb{Z}} % for Integers
-\newcommand{\MB}{\mathbb{B}_{\matsym}} % for Integers
-\newcommand{\SB}{\mathbb{B}_{\sym}} % for Integers
-\newcommand{\col}[1]{\begin{matrix} #1 \end{matrix} \right]}
-\newcommand{\comb}[2]{\binom{#1^2 + #2^2}{#1+#2}}
-\newcommand{\stab}{\text{\textbf{Stab}}}
-\newcommand{\setstab}{\text{\textbf{SetStab}}}
-\newcommand{\matstab}{\text{\textbf{MatStab}}}
-\newcommand{\inv}{\text{\textbf{inv}}}
-\newcommand{\aut}{\text{\textbf{Aut}}}
-\newcommand{\kernal}{\text{\textbf{ker}}}
-\newcommand{\alt}{\text{\textbf{Alt}}}
-\newcommand{\sym}{\text{\textbf{Sym}}}
-\newcommand{\rank}{\text{\textbf{rk}}}
-\newcommand{\orb}{\text{\textbf{Orb}}}
-\newcommand{\SP}{\text{\textbf{SP}}}
-\newcommand{\maj}{\text{\textbf{Maj}}}
-\newcommand{\dom}{\text{\textbf{Dom}}}
-\newcommand{\child}{\text{child}}
-\newcommand{\countgate}{\text{count}}
-\newcommand{\agree}{\text{AGREE}}
-\newcommand{\supp}{\text{SUPP}}
-\newcommand{\rankparam}{\text{PARAM}}
-
-\newcommand{\Alpha}{A}
-\newcommand{\matsym}{\text{\textbf{MatSym}}}
 \begin{document}
 
-\nocite{*}
+\title{Symmetric Circuits for Rank Gates}
 
-\title{Circuits}
-
-\author{Gregory Wilsenach \\ 
+\author{Anuj Dawar and Gregory Wilsenach \\ 
 Computer Laboratory \\
@@
 \tableofcontents
+\newpage
 
-\chapter{Introduction}
+\section{Introduction}
+\subfile{sections/introduction}
+\newpage
 
-\chapter{Background}
+\section{Background}
+\subfile{sections/background}
+\newpage
 
-\chapter{Symmetric Circuits}
+\section{Symmetric Circuits}
+\subfile{sections/symmetric-circuits}
+\newpage
 
-\chapter{Extending Symmetric Circuits}
+\section{Symmetry and Support}
+\subfile{sections/symmetry-and-support}
+\newpage
 
-\chapter{Matrix-Symmetric Circuits}
+\section{Translating Circuits into Formulas}
+\subfile{sections/translating-circuits-into-formulas}
+\newpage
 
-The symmetric circuits of Anderson and Dawar \cite{} have been shown to express
-$FPC$.
+\section{Concluding Remarks}
+\subfile{sections/conclusion}
+\newpage
 
-In this section we develop a notion of a matrix-symmetric circuit, an extension
-of the symmetric circuit defined by Anderson and Dawar \cite{}. This is my
-latest version of the support and circuit capturing result.
-
-\section{}
-
-\section{Circuits and Symmetry}
-\begin{definition}
-  Let $A$ and $B$ be sets, say that a function $f: \{ 0,1 \}^{A \times B}
-  \rightarrow \{ 0,1 \}$ is matrix-symmetric if for any $\omega: A \times B
-  \rightarrow \{0, 1\}$ and $(\alpha, \beta) \in \sym_A \times \sym_B$ we have
-  $f((\alpha, \beta)\cdot \omega) = f (\omega)$.
-  \\
-  A function $f: \{0,1\}^* \rightarrow \{0,1\}$ is matrix-symmetric iff for any
-  two finite sets $A$, $B$ we have that that $f|_{A \times B}$ is
-  matrix-symmetric (where $f|_{A \times B}$ is the restriction of the function
-  $f$ to inputs sequences of size $\vert A \times B \vert$ and where elements of
-  the input sequence are labelled by elements of $A \times B$).
-\end{definition}
-
-\section{The Support Theorem}
-
-Without a loss of generality we assume that $A$ and $B$ are always initial
-segments of the natural numbers.
-
-% Let $C$ be a circuit over some Boolean basis. For each gate $g \in C$ we
-% associate a relation $\omega_g$ (or just $\omega$ when the context makes it
-% clear). We say a gate is symmetric if that relation
-
-% So far we have defined a circuit over a Boolean basis where the circuit
-% elements all compute symmetric functions. The definition of an induced
-% automorphism only makes. As such, we begin by augmenting the definition of a
-% circuit and automorphism.
-
-\begin{definition}[Circuits on Structures]
-  For $\mathbb{B}_{\sym}$ a basis of Boolean symmetric functions,
-  $\mathbb{B}_{\matsym}$ a basis of Boolean matrix-symmetric functions and
-  $\tau$ a set of relation symbols, we define a $(\mathbb{B}_\sym,
-  \mathbb{B}_\sym, \tau)$-circuit $C_n$ computing a $q$-ary query $Q$ is a
-  structure $\langle G, W, \Omega, \Sigma, \Lambda, L\rangle$.
-  \begin{itemize}
-  \item $G$ is called the set of gates of $C_n$ and $\vert C_n \vert := \vert G
-    \vert$.
-  \item $W \subseteq G \times G$, where $W$ is called the wires of the circuit.
-    $(G,W)$ must be a directed acyclic graph. For $g \in G$ we $H_g := \{ h \in
-    C_n : W(h,g)\}$ be the set of children of $g$.
-  \item $\Omega$ is an injective function from $[n]^q$ to $G$. The gates in the
-    image of $\Omega$ are called the output gates. When $q = 0$, $\Omega$ is a
-    constant function mapping to a single output gate.
-  \item $\Sigma$ is a function from $G$ to $\mathbb{B}_\sym \uplus
-    \mathbb{B}_\matstab \uplus \tau \uplus \{0,1\} $ which maps input gates to
-    $\tau \uplus \{0,1\}$ and where $\Sigma^{-1} (0) \leq 1$ $\Sigma^{-1} (1)
-    \leq 1$ and the internal gates get mapped into $\mathbb{B}_\sym \uplus
-    \mathbb{B}_\matstab$. Gates mapped to $\tau$ are called relational gates and
-    gates mapped to 1 or 0 are called constant gates.
-  \item $\Lambda$ is a sequence of injective functions $(\Lambda_R)_{R \in
-      \tau}$ where for each $R \in \tau$, $\Lambda_R$ maps each relational gate
-    $g$ with $R = \Sigma (g)$ to the tuple $\Lambda_R (g) \in [n]^r$, where $r$
-    is the arity of the symbol $R$. When no ambiguity arises we write $\Lambda
-    (g)$ for $\Lambda_R (g)$.
-  \item $L$ is the set of labelings of $C_n$. Let $g \in G$ be an internal gate
-    and $H$ be the children of $g$. Then let $S$ be a set where $\{0,1\}^S =
-    \dom(\Sigma (g))$. Then $L$ is a function that assigns to $g$ an onto
-    function $\omega_g:S \rightarrow H$. We call this the matrix labelling of
-    $g$.
-  \end{itemize}
-\end{definition}
-
-% \begin{definition}
-%   let $C = \langle G, W, \Omega, \Sigma, \Lambda, L\rangle$ be a
-%   $(\mathbb{B}_\sym, \mathbb{B}_\sym, \tau)$-circuit, then take $g_1,g_2 \in
-%   G$ such that $\Sigma (g_1) \Sigma(g_2) \in \mathbb{B}_\matsym$.
-
-\begin{definition}
-  Let $\omega_1: A \times B \rightarrow H$ and $\omega_2: A' \times B'
-  \rightarrow H'$ define the equivalence relation $\sim$ as $\omega_1 \sim
-  \omega_2$ iff $\omega_1$ and $\omega_2$ have the same domain and co-domain and
-  there exists $(\alpha, \beta) \in \sym_A \times \sym_B$ and for all $(a,b) \in
-  A \times B$ we have $\omega_1 = \omega_2 \circ (\alpha, \beta)$.
-\end{definition}
-
-% \begin{definition}
-%   Let $\omega_1: A \rightarrow H$ and $omega_2:A' \rightarrow H'$. Define the
-%   equivalence relation $\sim$ as $\omega_1 \sim \omega_2$ iff $\omega_1$ and
-%   $\omega_2$ have the same domain and co-domain, and
-% \end{definition}
-
-\begin{definition}[Automorphism]
-  let $C = \langle G, W, \Omega, \Sigma, \Lambda, L\rangle$ be a
-  $(\mathbb{B}_\sym, \mathbb{B}_\sym, \tau)$-circuit computing at $q$-ary query
-  on structures of size $n$. Let $\sigma \in \sym_n$ and $\pi: G \rightarrow G$
-  be a bijection such that
-  \begin{itemize}
-  \item for all gates $g, h \in G$, $W(g,h)$ iff $W(\pi g, \pi h)$,
-  \item for all output tuples $x \in [n]^q$, $\pi \Omega (x) = \Omega (\sigma
-    x)$,
-  \item for all gates $g \in G$, $\Sigma (g) = \Sigma (\pi g)$, and
-  \item for each relational gate $g \in G$, $\sigma \Lambda (g) = \Lambda (\pi
-    g)$
-  \item for each internal gate $g$ if $\Sigma (g) \in \mathbb(B)_\matsym$. Then
-    we have that $L(\pi g) \sim \pi \circ L(g)$.
-  \end{itemize}
-\end{definition}
-
-\begin{remark}
-  I also need a new notion of robustness here in order to collapse gates that
-  have the same children and equivalent labelings are properly regarded as being
-  the same gate.
-\end{remark}
-% \begin{definition}
-%   Let $C$ be a circuit, $g$ be a gate in $C$, $H$ be $g$'s set of children and
-%   let $\omega: A \times B \rightarrow H$ be a surjection, where $A$ and $B$
-%   are sets and $g$ takes $\vert A \vert \cdot \vert B \vert$ inputs. Call such
-%   an $\omega$ a matrix labeling for $g$.
-% \end{definition}
-
-% \begin{definition}
-%   Let $C$ be a circuit and $g_1$ and $g_2$ be gates in $C$. Let $\sigma \in
-%   \sym_n$ be a permutation such
-% \end{definition}
-
-\begin{definition}
-  Let $\omega$ be a matrix labeling for $g$. Define the matrix stabilizer for
-  $\omega$, denoted by $\matstab(\omega)$, to be the set of all $\sigma \in
-  \sym_n$ such that $\sigma H = H$ and there exists $(\alpha, \beta) \in \sym_A
-  \times \sym_B$ such that for all $(i,j) \in A \times B$ we have that $\omega
-  (\alpha i, \beta j) = \sigma \omega (i,j)$.
-\end{definition}
-
-\begin{definition}
-  Let $g$ be a gate with matrix labeling $\omega$, $h,h' \in H$ and $\sigma \in
-  \sym_n$. We say that a pair $(h, h')$ is compatible with $(\sigma, \omega)$ if
-  $\sigma h, \sigma h' \in H$ and there exists $(\gamma_1, \gamma_2),
-  (\gamma_1', \gamma_2') \in \sym_A \times \sym_B$ s.t.
-  \begin{align*}
-    &(\gamma_1, \gamma_2) \cdot \omega^{-1} (h) = \omega^{-1}(\sigma h), \text{ and} \\ 
-    &(\gamma_1', \gamma_2') \cdot \omega^{-1} (h') = \omega^{-1}(\sigma h'),
-  \end{align*}
-  and for all $(i,j) \in \omega^{-1}(h)$, $(i',j') \in \omega^{-1}(h')$ we have
-  that
-  \begin{align*}
-    &i =i' \implies \gamma_1(i) = \gamma_1'(i'), \text{ and} \\
-    &j =j' \implies \gamma_2(j) = \gamma_2'(j').
-  \end{align*}
-
-\end{definition}
-
-\begin{lem}
-  Let $g$ be a gate, $\omega$ be a matrix labeling of $g$, $\sigma \in \sym_n$.
-  Then $\sigma \in \matstab(\omega)$ iff for all $h,h' \in H$ we have that
-  $(h,h')$ is compatible with $(\sigma, \omega)$.
-\end{lem}
-
-\begin{proof}
-  $`\Rightarrow'$: We have that $\sigma \in \matstab(\omega)$ and so there
-  exists $(\alpha, \beta) \in \sym_A \times \sym_B$ such that for all $(i,j) \in
-  A \times B$ we have $\sigma \omega (i,j) = \omega (\alpha i, \beta j)$. From
-  compatibility we have that $h,h' \in H$ Let $h, h' \in H$ . Let $(\gamma_1,
-  \gamma_2) := (\gamma_1', \gamma_2') := (\alpha, \beta)$. This assignment is
-  sufficient to prove the direction.
-
-  $`\Leftarrow'$: Suppose for all $h,h' \in H$ we have $(\gamma_1, \gamma_2),
-  (\gamma_1, \gamma_2') \in \sym_A \times \sym_B$ satisfying the above
-  requirements. Notice that for a given $i \in A$ and any $j, j' \in B$, let $h
-  = \omega(i,j)$ and $h' = \omega(i,j')$, then we have that $\gamma_1 (i) =
-  \gamma_1'(i)$. It follows that we can define a $\alpha \in \sym_A$ by
-  $\alpha(i) = \gamma_1 (i)$. Similarly we can define $\beta \in \sym_B$ by
-  $\beta (j) = \gamma_2 (j)$.
-
-\end{proof}
-
-\begin{definition}
-  Let $g$ be a gate with matrix labeling $\omega$. Let $(\sigma, h, h') \in
-  \sym([n]) \times H^2$. Say that $(\sigma, h, h')$ is useful if $(h,h')$ is
-  incompatible with $(\sigma, \omega)$.
-
-  Say that two distinct pairs $(\sigma_1, h_1, h_1'), (\sigma_2, h_2, h_2') \in
-  \sym([n]) \times H^2$ are mutually independent if
-  \begin{itemize}
-  \item $\sigma_2 h_1 = h_1$,
-  \item $\sigma_2 \sigma_1 h_1 = \sigma_1 h_1$,
-  \item $\sigma_2 h_1' = h_1'$,
-  \item $\sigma_2 \sigma_1 h_1' = \sigma h_1'$,
-  \end{itemize}
-  We say that a set $S \subseteq \sym([n]) \times H^2$ is useful if each pair in
-  it is useful. We say that S is independent if each pair of distinct pairs in
-  $S$ are mutually independent.
-\end{definition}
-
-We denote the usual equivalence relation on $\sym_n$ from the (right) cosets of
-$\matstab(\omega)$ by $\sim_\omega$.
-
-\begin{lem}
-  Let $\sigma_1, \sigma_1 \in \sym_n$ and suppose $\sigma_1 \sim_\omega
-  \sigma_2$ then for any $(h,h') \in H^2$ we have that $(h,h')$ is compatible
-  with $(\sigma_1, \omega)$ iff $(h,h')$ is compatible with $(\sigma_2,
-  \omega)$.
-\end{lem}
-
-\begin{proof}
-  Suppose we have that $\sigma_1 \sim_\omega \sigma_2$. And additionally
-  supposed $(h, h')$ compatible with $(\sigma_1, \omega)$.
-
-  It follows there exists $(\alpha, \beta) \in \sym_A \times \sym_B$ such that
-  $\sigma_1 \omega (i,j) = \sigma_2\omega (\alpha i, \beta j)$, and we have
-  $(\gamma_1, \gamma_2), (\gamma_1', \gamma_2') \in \sym_A \times \sym_B$
-  satisfying the requirements of compatibility. We note that $(\alpha, \beta)
-  \cdot \omega^{-1}(\sigma_1 h) = \omega^{-1}(\sigma_2 h)$. Thus by composition
-  we have that $(\alpha \gamma_1, \beta \gamma_2) \cdot \omega^{-1}(h) =
-  \omega^{-1}(\sigma_2 h)$ and $(\alpha \gamma_1', \beta \gamma_2') \cdot
-  \omega^{-1}(h') = \omega^{-1}(\sigma_2 h')$, and clearly the remaining
-  requirement for compatibility follows from the bijectivity of $\alpha$ and
-  $\beta$. The result follows. The other direction of the implication follows
-  from symmetry.
-\end{proof}
-
-\begin{claim}
-  \label{claim:useful-independant-set}
-  Let $g$ be a rank gate with labeling $\omega$ and child set $H$. Let $S$ be a
-  useful and independent. We then have that $\vert \sym_n: \matstab(\omega)
-  \vert \leq 2^{\vert S \vert}$.
-\end{claim}
-
-\begin{proof}
-  Let $R \subseteq S$ and define $\sigma_R = \Pi_{(\sigma, h, h') \in R} \sigma$
-  (with some arbitrary order assumed on $S$). Let $R$ and $Q$ be distinct
-  subsets of $S$ and WLOG let $\vert R \vert \geq \vert Q \vert$. We want to
-  show that we don't have $\sigma_R \omega \sim_\omega \sigma_Q \omega$. Pick
-  any $(\sigma, h, h') \in R/Q \neq \emptyset$. Given that $\sigma_R h = \sigma
-  h$ and $\sigma_R h' = \sigma h'$ it is easy to see that the usefulness of
-  $(\sigma, h,h')$ implies the incompatibility of $(h,h')$ with with $(\omega,
-  \sigma_R)$. Moreover, the fact that $\sigma_Q h = h$ and $\sigma_Q h' = h'$
-  makes it easy to see $(h,h')$ is compatible with $(\omega, \sigma_Q)$. From
-  the above lemma we may conclude that that we do not have $\sigma_R \sim_\omega
-  \sigma_Q$, and the result follows.
-\end{proof}
-
-The following two lemmas proved by Anderson and Dawar \cite{} are both of use in
-proving the following theorem.
-
-\begin{lem}
-  \label{lem:big-or-small}
-  For any $\epsilon$ and $n$ such that $0 < \epsilon < 1$ and $\log n \geq
-  \frac{4}{\epsilon}$, if $\mathcal{P}$ is a partition of $[n]$ with $k$ parts,
-  $s = [\sym_n : \setstab (\mathcal{P})]$ and $n \leq s leq 2^{n^{1-\epsilon}}$,
-  then $\min \{k, n-k\} \leq \frac{8}{\epsilon} \frac{\log s}{\log n}$.
-\end{lem}
-
-\begin{lem}
-  \label{lem:small-means-support}
-  For any $\epsilon$ and $n$ such that $0 < \epsilon < 1$ and $\log n \geq
-  \frac{8}{\epsilon^2}$, if $\mathcal{P}$ is a partition of $[n]$ with $\vert
-  \mathcal{P} \vert \leq \frac{n}{2}$, $s:= [\sym_n : \setstab (\mathcal{P})]$
-  and $n \leq s \leq 2^{n^{1-\epsilon}}$, then $\mathcal{P}$ contains a part $P$
-  with at least $n - \frac{33}{\epsilon} \cdot \frac{\log s} {\log n}$.
-\end{lem}
-
-If $g$ is a symmetric gate (i.e. the usual gates in a circuit) we note that
-$\orb(g) = [\sym_n : \stab (g)]$ by the orbit-stabilizer theorem.
-
-If $g$ is a matrix-symmetric gate then $\orb(g) = [\sym_n:\matstab (\omega)]$,
-where $\omega$ is the matrix labelling associated with $g$.
-
-\begin{thm}
-  For any $\epsilon$ and $n$ such that $\frac{2}{3} \leq \epsilon \leq 1$ and $n
-  \geq \frac{128}{\epsilon^2}$, if $C$ is a symmetric, rigid circuit on
-  structures of size $n$ and $s := \max_{g \in C} \vert \orb (g)\vert \leq
-  2^{n^{1-\epsilon}}$, then, $SP(C) \leq \frac{33}{\epsilon}\frac{log s}{log
-    n}$.
-\end{thm}
-
-\begin{proof}
-  It is easy to see that if $g$ is a gate in $C$ then $\stab (g) \subseteq
-  \setstab(\SP(g))$, and so $s \geq \orb(g) = [\sym_n : \stab(g)] \geq [\sym_n :
-  setstab(\SP(g))]$. Thus if $\vert \SP(g) \vert \leq frac{n}{2}$, then from
-  Lemma \ref{lem:small-means-support}, we have $\| SP (g) \| \leq
-  \frac{33}{\epsilon} \cdot \frac{\log s} {\log n}$. The result thus follows
-  from showing that for each $g$ in $C$ we have that $\vert \SP (g) \vert \leq
-  \frac{n}{2}$.
-
-  % Include some detail here for constant and relational gates
-  The cases where $g$ is a constant or relational gate are easy to handle.
-
-  We now consider the case for internal gates. Let $g$ be the topologically
-  first internal gate with $\vert \SP(g) \vert > \frac{n}{2}$. If $g$ is not a
-  matrix-symmetric gate then the result follows from the argument presented by
-  Anderson and Dawar \cite{}. Suppose $g$ is a matrix-symmetric gate, and
-  suppose $g$ has a labelling $\omega$. We now argue that this leads to a
-  contradiction.
-
-  Let $k' := \lceil \frac{8 \log s}{\epsilon \log n} \rceil$. From the
-  assumptions on $s, n$ and $\epsilon$ we have that $k' \leq
-  \frac{1}{4}n^{1-\epsilon} < \frac{n}{2}$. Lemma \ref{lem:big-or-small} implies
-  that $n - \vert \SP(g) \vert \leq k'$
-
-  From Claim \ref{claim:useful-independant-set} it remains to show that we can
-  construct a sufficiently large useful and independent set of gate-automorphism
-  pairs $S$. Divide $[n]$ into $\lfloor \frac{n}{k' + 2} \rfloor$ disjoint sets
-  $S_i$ of size $k' + 2$ and ignore the elements left over. It follows that for
-  each $i$ there is a permutation $\sigma_i$ which fixes $[n] / S_i$ pointwise
-  but moves $g$. Suppose there was no such $\sigma_i$ it follows that every
-  every permutation that fixes $[n]/S_i$ pointwise fixes $g$. Thus the partition
-  of all the singletons in $[n]/S_i$ and $S_i$ is a supporting partition. As
-  $\SP(g)$ is the coarsest partition it follows that $\vert \SP(g) \vert \leq n
-  - (k'+2) + 1 = n - k' - 1$, which contradicts the inequality $n - \vert \SP(g)
-  \vert \leq k'$.
-
-  Since $g$ is moved by each $\sigma_i$ and $C$ is rigid it follows that we
-  don't have $\sigma_i \notin \matstab(\omega)$. Thus there exists $(h_i, h_i')$
-  that is inconsistent with $(\sigma_i, \omega)$, and so the triple $(\sigma_i,
-  h_i, h_i')$ is useful.
-
-  Let $\SP (h)^*$ be the union of all parts of $\SP(h)$ except for the largest
-  part. Let $Q_i = \SP(h_i)^* \cup \SP(\sigma_i h_i)^* \cup \SP (h_i')^* \cup
-  \SP (\sigma_i h_i')^*$. Then note that if $\sigma_j$ fixes $Q_i$ then by
-  construction, we have that $\sigma_j \in \stab_n(\SP(h_i)) \cap
-  \stab_n(\SP(\sigma_i h_i)) \cap \stab_n(\SP(h_i')) \cap \stab_n(\SP(\sigma_i
-  h_i'))$
-
-  Define a graph $K$ with vertices given by the sets $S_i$ and an edge from
-  $S_i$ to $S_j$ (with $i \neq j$) if $Q_i \cap S_j \neq \emptyset$. It follows
-  then that if there is no edge between $S_i$ and $S_j$ then $(\sigma_i, h_i,
-  h_i')$ and $(\sigma_j, h_j, h_j')$ are mutually independent. It remains to
-  argue that $K$ has a large independent set. This is possible as the out-degree
-  of $S_i$ in $K$ is bounded by
-  \begin{align*}
-    \vert Q_i \vert \leq \|SP(h_i) \| + \|SP(\sigma_i h_i) \| + \|SP(h_i') \| + \|SP(\sigma_i h_i') \leq 4 \cdot \frac{33\log s}{\epsilon \log n}
-  \end{align*}.
-
-  This follows as the sets $S_i$ are disjoint and we may apply Lemma
-  \ref{lem:small-means-support} to each of the child gates. It follows that the
-  average total degree (in + out degree) of $K$ is at most $2 \cdot \vert Q_i
-  \vert \leq 34 \cdot k'$. Now greedily select a maximal independent set in $K$
-  by repeatedly selecting $S_i$ with the lowest total degree and eliminating it
-  and its neighbours. This action does not affect the bound on the average total
-  degree of $K$ and hence determines an independent set $I$ in $K$ of size at
-  least
-  \begin{align*}
-    \frac{\lfloor \frac{n}{k' + 2} \rfloor}{34k' + 1} \geq \frac{n - (k'+2)}{34k'+1k'+2} \geq \frac{n\frac{7}{16}}{34k'^2 + 69k' +2} \geq \frac{n}{(16k')^2}.
-  \end{align*}
-
-  Take $S = \{(\sigma, h, h') : S_i \in I \}$. Then from the above argument we
-  have that $S$ is useful and independent.
-
-  Moreover, from Claim \ref{claim:useful-independant-set}, we have that $s \geq
-  \vert \orb(g) \vert \geq 2^{\vert S \vert} \geq 2^{\frac{n}{(16k')^2}}$ then
-  $n^{1-\epsilon} \geq \log s \geq n \cdot (\frac{128}{\epsilon}\frac{\log
-    s}{\log n})^{-2} > n \cdot (n^{1-\epsilon})^{-2} = n^{2\epsilon -1} \geq
-  n^{1-\epsilon}$. This is a contradiction.
-\end{proof}
-
-\section{Rigid Circuits}
-
-\begin{definition}
-  We say that a circuit $C$ has bijective labels if for each gate $g$ in $C$,
-  $L(g)$ is a bijection.
-\end{definition}
-
-\begin{lem}
-  \label{lem:bij_labels}
-  There is an algorithm that runs in polynomial time that takes in a circuit $C$
-  and outputs a circuit with unique gates $C'$. Moreover, if $C$ was symmetric
-  then $C'$ is symmetric. If $C$ is rigid then $C'$ is rigid.
-\end{lem}
-
-\begin{proof}
-  Let $S = 2*\vert C \vert$. Recurse through the gates of $C$ topologically and
-  let $h$ be the next gate topologically. If for all $g \in W(h, \cdot)$ we have
-  that $L\vert (g)^{-1}(h) \vert = 1$ continue on to the next gate. If not add
-  in a tower of $S$ $\and$ gates such that $h \rightarrow \and^h_1 \rightarrow
-  \ldots \rightarrow \and^h_S$ (i.e. we have a tower of $\and$ gates with $h$ as
-  input to $\and^h_1$ and the output of each $\and^h_i$ connected to the input
-  of each $\and^h_{i+1}$ for each $1 \leq i < S$). Now for each $g \in W(h,
-  \cdot)$, if $L(g)^{-1}(h) = \{ s_0, \ldots, s_{r}\}$, for each $1 \leq i \leq
-  r$ add in the wires $W(\and^h_i, g)$ and set $L(g)(s_{i}) = \and^h_i$. Now
-  continue on to the next gate topologically and run the above algorithm.
-
-  % First, notice that for a given gate $h$ and $k \in \mathbb{N}$, we can
-  % define
-  % a sub-circuit $h^k = 1 \and \cdots, 1 \and h$ (or rather a $k$-height tower
-  % of
-  % $k$ binary $\and$ gates with $h$ at the top and all other inputs set to
-  % $1$).
-  % We call $h$ the top of the sub-circuit $h^k$ and the bottom $and$ gate (the
-  % output of the sub-circuit) the bottom gate. We may think of this as a
-  % $k$-height copy of the gate $h$, in the sense that it has the same output as
-  % $h$ and similar orbits. We now use different copies to distinguish gates
-  % that
-  % otherwise have the same labelling.
-
-  % Let $h$ be the next gate topologically. Then let $r$ be maximal such that
-  % $W(h,g)$ and $\omega_g^{-1}(h) = \{ s^g_1, s^g_2, \ldots, s^g_r \}$. Then
-  % let
-  % $k$ be the height of the highest tower with $h$ at the top and with it's
-  % bottom connected to a gate in $W(h, \cdot)$. Then create a single
-  % $k+r-1$-height tower by adding in the appropriate number of binary $\and$
-  % gates below $h$.
-
-  % For each $g \in W(h, \cdot)$ and for each $\omega_g^{-1}(h) = \{s^g_1,
-  % s^g_2,\ldots , s^g_{r_g}\}$, set $L'(g)(s^g_1) = h$ each child starting with
-  % the $and$-gate child to $h$ add in a wire from from the $i$th gate in the
-  % tower to $g$ and set $L'(g)(s^g_{i+1}) = \and_i$, where $\and_i$ is the
-  % $i$th
-  % $\and$ gate in the tower starting with the $\and$ gate in the tower child to
-  % $h$. There are enough gates in the tower as $r_g \leq r$.
-
-  We call this updated circuit $C'$.
-
-  Firstly, note that after running the above algorithm for each $g$ the
-  labelling of $g$ will be a bijection. Moreover, it's easy to see that the
-  output of each gate remains unchanged, and as such the output of the circuit
-  is unchanged.
-
-  Secondly, notice that the size of $C'$ is at most $2*\vert C \vert^2$, and
-  note that the above algorithm runs in polynomial time.
-
-  Now suppose that $C$ is symmetric. Let $\sigma$ be a permutation on the input
-  universe and $\pi_C$ the induced automorphism on $C$. We now define $\pi$, the
-  induced automorphism on $C'$. For each gate $g$ in $C'$, if $g$ is in $C$ then
-  set $\pi(g) := pi_C(g)$. If $g$ is not in $C$ then $g$ must be some
-  $\and^h_i$, for some $h$ in $C$. Then set $\pi(\and^h_i) :=
-  \and^{\pi_C(h)}_i$. It is easy to see that $\pi$ is an automorphism, and $\pi$
-  extends $\sigma$.
-
-  Suppose that $C$ is rigid. It is easy to see that $C'$ will be rigid as well.
-
-\end{proof}
-
-% If $h$ is a binary $\and$ gate, then we say that $h$ has height $k+1$ if it
-% has a $k$-height tower of binary $and$ gates connected above it, with a
-% non-$\and$ gate $p$ connected to the final binary $\and$ gate, and all other
-% inputs connected to $1$. We then say that $h$ is the base of a tower of height
-% $k$ and type $p$.
-
-% Then for each $h \in W_g$, if $h$ is not a binary $\and$ gate, the let $k$ be
-% the largest integer such that there a gate $h' \in W(h, \cdot)$ which is the
-% base of a tower of height $k$ and type $h$. it's output directly connected to
-% one of the gates in $W(h^k, \cdot)$ (with k = 0 corresponding to just $h$).
-% Then each $i \in \{1, \ldots , \vert \omega^{-1}(h)\vert\}$ add into the
-% circuit $h^{k+i}$ and wire it to $g$. Notice that this step requires adding
-% $\vert \omega^{-1}(h) \vert -1$ gates to the circuit. For some assumed
-% ordering $\dom(\omega)$, let $\{s_0, \cdot, s_m\} = \omega^{-1}(h)$. Define
-% $L'(g)(s_i) = h^{k+i}$. Now continue on to the next gate topologically where
-% $L(g)$ is not a bijection, and execute the same process
-
-\begin{lem}
-  There is an algorithm that runs in polynomial time that takes in a circuit $C$
-  and outputs a circuit $C'$ such that $C'$ is rigid and has bijective labels.
-  Moreover, if $C$ was symmetric it follows that $C'$ will be symmetric.
-\end{lem}
-
-\begin{proof}
-  First run the algorithm from Lemma \ref{lem:bij_labels} on $C$, and call the
-  output circuit $C$.
-
-  Recurse through the gates of $C$ topologically. For each internal gate $g$,
-  for all $g'$ in $C$ such that $g \neq g'$, $W(\cdot, g) = W(\cdot, g')$, $W(g,
-  \cdot) = W(g', \cdot)$, $\Sigma(g) = \Sigma(g')$, $L(g) \sim L(g')$ and
-  $\Omega^{-1}(g) = \Omega^{-1}(g')$, delete $g'$ and for all $s \in L^{-1}(g')$
-  set $L(s) := g$.
-
-  Now re-run the algorithm from Lemma \ref{lem:bij_labels} on $C$ and output the
-  result.
-\end{proof}
-
-  \begin{lem}
-    Let $C = \langle G, W, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\SB, \MB,
-    \tau)-circuit$ on structures of size $n$. There is a deterministic algorithm
-    which runs in Poly($\vert C \vert$) and outputs a rigid $(\SB, \MB, \tau)
-    circuit$ $C'$ such that $G' = G$ and for any $g \in G$, and any input
-    $\tau$-structure $\mathcal{A}$ and any bijection $\gamma$ from $A$ to $[n]$,
-    $C[\gamma \mathcal{A}](g) = C'[\gamma \mathcal{A}](g)$ and if $C$ is
-    symmetric then so is $C'$.
-  \end{lem}
-
-  \begin{proof}
-
-  \end{proof}
-
-  \section{Computing Supports}
-  \begin{lem}
-    Let $C$ be a rigid $(\SB, MB, \tau)$-circuit on structures of size $n$ and
-    $\sigma \in \sym_n$. There is a deterministic algorithm which runs in time
-    Poly($\vert C \vert$) and outputs for each gate $g$ its image under the
-    automorphism $\pi$ induced by $\sigma$, if it exists.
-  \end{lem}
-  \begin{proof}
-    The proof proceeds by recursively going through the circuit and building the
-    mapping $\pi$ induced by $\sigma$.
-
-    Suppose $g$ is a constant gate, then $\pi g := g$. Suppose $g$ is a
-    relational gate, then there is at most one gate $g'$ such that $\Sigma (g) =
-    \Sigma (g')$ and $\sigma\Lambda (g') = \Lambda (g)$. If such a $g'$ exists
-    assign $\pi g := g'$, else terminate with failure.
-
-    If $g$ is an symmetric internal gate then (from rigidity) there is at most
-    one gate $g'$ such that $\Sigma (g) = \Sigma(g')$ and $W_{g'} = \pi W_g$.
-    Assign $\pi g := g'$ if such a gate exists, or else terminate with failure.
-
-    If $g$ is a matrix-symmetric internal gate then consider the set of gates
-    $g'$ such that $g'$ has children $\pi W_g$ and $\Sigma(g) = \Sigma(g')$, and
-    let $A \times B = \dom (Sigma(g))$. If no such gate $g'$ exists, terminate
-    with failure. Define $\sigma_{\pi, g'}:A \times B \rightarrow A \times B$ by
-    $\sigma_{\pi, g'} = \omega^{-1}_{g'} \pi \omega_{g}$. Then clearly
-    $\omega_{g'} \sigma_{\pi, g'} = \pi \omega_{g}$, and it's easy to show that
-    $\pi \omega_g \sim \omega_{g'}$ iff $\sigma_{\pi,g'} \in \sym_A \times
-    \sym_B$. But this just involves checking that $\sigma$ acts as a bijection
-    on $A$ and $B$ separately and, given that $\vert A \vert$ and $\vert B
-    \vert$ are both bounded by $\vert C \vert$, the algorithm which just
-    iterates through $A$ and $B$ is sufficient. If for every $g'$ it is found
-    that $\pi_{\sigma,g'}$ is not in $\sym_A \times \sym_B$ then terminate with
-    failure. If there is a $g'$ for which $\pi_{\sigma, g'} \in \sym_A \times
-    \sym_B$ then it is unique by rigidity and so set $\pi g := g'$.
-
-    If $g$ is an output gate, then check that for all tuples in $[n]^{q}$ we
-    have that $\pi \Omega (x) = \Omega (\sigma (x))$, and terminate with failure
-    if the condition is not met.
-
-    If the algorithm has not terminated with failure, output the automorphism.
-
-    The algorithm clearly runs in Poly($\vert C \vert$)
-  \end{proof}
-
-  \section{Evaluating Symmetric Circuits}
-  We need to extend two Lemmas in this section.
-
-\begin{lem}
-  Let $g$ be a matrix-symmetric gate in $C_n$ with children $H$. Let $\alpha \in
-  U^{\underbar{\sp(g)}}$, and suppose $\gamma_1, \gamma_2: U \rightarrow [n]$
-  with $\gamma^{-1}_1 \sim \alpha$ and $\alpha \sim \gamma^{-1}_2$. Let $A
-  \times B = \dom (L(g))$.
-
-  For an input structure $\mathcal{A}$, let $L^0_\gamma: A \times B \rightarrow
-  \{0,1\}$, where $L^0_\gamma (a,b):= C[\gamma \mathcal{A}] (L(g)(a,b))$.
-
-  Then $L^0_{\gamma_1} \sim L^0_{\gamma_2}$.
-\end{lem}
-
-\begin{proof}
-  We have that there exists a unique $\pi \in \sym_n$ such that $\pi \gamma_1 =
-  \gamma_2$. Moreover, since $\gamma^{-1}_1$ and $\gamma^{-1}_2$ are both
-  consistent with $\alpha$, it follows that $\pi$ must fix $\sp(g)$. Thus $L(g)
-  \sim \pi L(g)$, and so there exists $(\sigma, \lambda)$ such that $\pi L(g) =
-  L(g) (\sigma, \lambda)$.
-
-  We then have that,
-  \begin{align*}
-    L^0_{\gamma_1} (a,b) &= C_n[\gamma_1 \mathcal{A}](L(g)(a,b))\\
-                         & = C_n[\pi gamma_1 \mathcal{A}][\pi L(g)(a,b)] \\
-                         & = C_n[gamma_2 \mathcal{A}][L(g)((\sigma, \lambda)(a,b))]\\
-                         & = L^0_{\gamma_2} ((\sigma, \lambda) (a,b)),
-  \end{align*}
-  and it follows that $L^0_{\gamma_1} \sim L^0_{\gamma_2}$.
-
-\end{proof}
-
-\begin{lem}
-  Let $g$ be a matrix symmetric gate in $C_n$ with children $H$. Let $\alpha \in
-  U^{\underbar{\sp(g)}}$ and $\gamma: U \rightrrow [n]$ such that
-  $gamma^{-1}\sim \alpha$. Let $A \times B = \dom (L(g))$ and define
-  $L^{EV}_\alpha: A \times B \rightarrow \{0,1\}$ by
-  \begin{align*}
-    L^{EV}_\alpha (a,b):=
-    \begin{cases*}
-      1 & if $A_h \cap \EV_h \neq \emptyset$ 0 & otherwise
-    \end{cases*},
-  \end{align*}
-  where for $h \in W_g, A_h:= \{\beta \in U^{\underline{\sp(h)}} \vert \alpha
-  \sim \beta\}$. Then $L^0_\gamma = L^{EV}_\alpha$ and $\alpha \in \EV(g)$ iff
-  $\rk^u_p(L^0_\gamma)$
-\end{lem}
-\begin{proof}
-
-\end{proof}
-
-\begin{lem}
-  Let $g$ be a matrix-symmetric gate in $C_n$ with children $W_g$. $Let \alpha
-  \in U^{\underbar{\sp(g)}}$ and let $\gamma: U \rightarrow [n]$ such that
-  $\gamma^{-1} \sim \alpha$. Let $A \times B = \dom (L(g))$, and let
-  $f:\{0,1\}^{A \times B} \rightarrow \{0,1\}$ be the matrix-symmetric function
-  associated with $g$. Define $L^{EV}_\alpha: A \times B \rightarrow \{0,1\}$ by
-  \begin{align*}
-    L^{EV}_\alpha (a,b):=
-    \begin{cases*}
-      1 & if $A_h \cap \EV_h \neq \emptyset$ 0 & otherwise
-    \end{cases*},
-  \end{align*}
-  where for $h \in W_g, A_h:= \{\beta \in U^{\underline{\sp(h)}} \vert \alpha
-  \sim \beta\}$. Then $\alpha \in \EV_g$ iff $f(L^\EV_\alpha)$.
-\end{lem}
-\begin{proof}
-  First note that if $\alpha \in U^{\underbar{\sp{g}}}$ then $\alpha \in \EV_g$
-  iff we have that $C_n[\gamma \mathcal{A}](g)= f (L^0_\gamma) = 1$. Notice that
-  from Lemma \ref{} that this holds for any particular $\gamma$ iff it holds for
-  all such $\gamma$.
-
-  We now show that $L^\EV_\alpha = L^0_\gamma$, and so complete the proof.
-
-  Suppose for $(a,b) \in A \times B$ we have that $L^\EV_\alpha(a,b) = 1$. Let
-  $h:= L(g)(a,b)$. It follows that $A_h \cap \EV_h \neq \emptyset$, i.e there
-  exits $\beta \in \sp(h)$ such that $\beta \sim \alpha$ and there exists
-  $\gamma_h \in \Gamma(h)$ such that $\gamma^{-1}_h \sim \beta$. It follows from
-  transitivity and Lemma \ref{} that $\gamma_h \sim \alpha$ and so
-  $L^0_\alpha(a,b) = C_n[\gamma \mathcal{A}](h) = C_n[\gamma_h \mathcal{A}](h) =
-  1$.
-
-  Now suppose that $L^0_\gamma (a,b) = 1$
-\end{proof}
-
-\section{Translating to Formulas of FPC}
-Let $\mathcal{C} = (C_n)_{n \in \mathbb{N}}$ be a P-uniform family of
-polynomial-size symmetric $(\SB, \MB, \tau)$ circuits, and where $\MB$ is the
-rank basis. It remains to show that there is a formula $Q$ in the vocabulary
-$\tau \uplus \{\leq\}$ such that for any $n$ and $\tau$-structure $\mathcal{A}$
-with a universe $U$ of carnality $n$, the $q$-ary query defined by $C_n$ on the
-input $\mathcal{A}$ is defined by the formula $Q$ when interpreted in the
-structure $\mathcal{A}^\leq = \mathcal{A} \uplus \langle [n], \leq \rangle$.
-
-Since $\mathcal{C}$ is $P$-uniform, and from Lemmas \ref{} and \ref{} and the
-Immerman-Vardi theorem, we have an FP interpretation defining a rigid symmetric
-circuit with bijective labels equivalent to $C_n$ (which we also call $C_n$)
-over the the number sort of $\mathcal{A}^\leq$, where $\Phi = (\phi_G,\phi_W,
-\phi_\Omega, (\phi_s)_{s \in \SB \uplus \{rank\} \uplus \tau \uplus \{0,1\}},
-(\phi_{\and_R})_{R \in \tau}, \phi_L)$. We note that $Phi$ is a $t$-width
-interpretation over the universe $[n]$. So if $\mu, \nu, \nu_1, \ldots \in
-[n]^t$, the formulas are defined such that:
-
-\begin{itemize}
-\item $\phi_G(\mu)$ holds iff $\mu$ encodes a gate
-\item $\phi_W(\nu,\mu)$ holds iff $\nu$ and $\mu$ encode gates and if $g_{\nu}$
-  and $g_{\mu}$ are these two encoded gates respectively then $W(g_{\nu},
-  g_{\mu})$.
-\item $\phi_{\Omega}(\nu_1, \ldots, \nu_q, \mu)$ holds iff $\nu_1, \ldots, nu_q$
-  each encode numbers less than or equal to $[n]$ and $\Omega(\nu_1, \ldots,
-  \nu_q) = g_\mu$.
-\item For all $s \in \SB \uplus \{rank\} \uplus \tau \uplus \{0,1\}$ we have
-  that $\phi_s (\mu)$ holds iff $\mu$ encodes a gate such that $\Sigma(g_\mu) =
-  s$ (or, in the case that $s = \rank$, we require that $\Sigma(g_\mu)$ is a
-  rank symbol.)
-\item For all $R \in \tau$ with arity $r$ we have that $\phi_{\and_R}(\nu_1,
-  \ldots, \nu_r, \mu)$ holds iff $\nu_1 , \ldots , \nu_r$ encodes numbers less
-  than or equal to $[n]$, $\mu$ encodes a gate such that $\Sigma(g_\mu) = R$ and
-  $\Lambda_R(g_\mu) = (\nu_1, \ldots, \nu_r)$.
-\item $\phi_L(\nu, \mu, \nu_1, nu_2)$ holds iff $\nu$ and $\mu$ encode gates and
-  $\nu_1, \nu_2$ encode numbers, and $L(g_{\mu})(\nu_1,\nu_2) = g_\nu$. If
-  $\dom(L (g_\mu)) = [a] \times [b]$, then the encoding of $[a]$ and $[b]$ are
-  initial segments under the lithographically induced order. Moreover, the
-  encodings of $[a]$ and $[b]$ preserve the order relation.
-\end{itemize}
-
-From now on we use $\mu$ and $\nu$ to stand for $t$-length sequences encoding
-gates, and use $\nu_1, \ldots$ for sequences that encode numbers. We use $g_\mu$
-and $g_\nu$ for the gates encoded by these sequence, while simply identifying
-the sequence $\nu_i$ with the number it encodes.
-
-Using the Immerman-Vardi Theorem, we can define an FP($\leq$) formula
-$\rankpara$ such that $\langle [n], \leq\rangle \models \rankpara[g,p,u]$ iff
-$\langle [n], \leq\rangle \models \phi_G[g] \land \phi_{\rank}[g]$ and the rank
-gate $g$ (as per the interpretation) computes the rank over characteristic $p$
-and has threshold $u$.
-
-We can define FP($\leq$) formulas $\max_A$ and $\max_B$ such that $\langle [n],
-\leq \rangle \models \max_A[g, \nu_1]$ iff $\nu_1$ encodes $a$, where
-$\dom(L(g)) = [a]\times [b]$. Similarly, $\langle [n], \leq \rangle \models
-\max_B[g, \nu_1]$ iff $\nu_1$ encodes $b$ where $\dom(L(g)) = [a] \times [b]$.
-
-Again using Lemma \ref{} and the Immerman-Vardi theorem, we can construct a
-formula $\supp$ such $\langle [n], \leq \rangle \models \supp[g,u]$ iff $\langle
-[n], \leq \rangle \models \phi_G[g]$ and $u$ is in $sp(g)$. This formula can be
-used as in \cite{} to inductively define $\supp_i(g,u)$ for each $i \in [n]$
-which holds iff $u$ is the $i$th element of the support of $g$.
-
-Define the $\agree$ and $\theta_s$ formulas for all $s \in \SB \uplus \tau
-\uplus \{0,1\}$ as in \cite{}.
-
-Now we define the formula
-\begin{align*}
-  \theta_{\rank}:= (\mu, \bar{x}) := \bigwedge_{1 \leq i < j \leq k} x_i
-  \neq x_j \wedge \forall \bar{y} ( [ \rank (x \leq \phi_{mr}, y \leq
-  \phi_{mc}, \pi \leq r). \theta^{'} ] ),
-\end{align*}
-\begin{align*}
-  \theta^{'}(a,b):= \exists \nu (W(\nu, \mu) \wedge \agree (\mu,\nu, \bar{x}, \bar{y}) \wedge \phi_L (\mu, \nu, a, b) \wedge V(\nu, y))
-\end{align*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\chapter{October 27th: Counting Gates Simulate Symmetric Gates}
-
-In this chapter we prove that symmetric circuits with majority gates are at
-least as powerful as symmetric circuits over any other Boolean basis consisting
-of symmetric functions.
-
-Recall the following that $\mathbb{B} = \{ \neg , \wedge , \lor \}$ and
-$\mathbb{B}_\maj = \{ \maj \} \cup \mathbb{B}$.
-
-Let $F: \{0,1\}^* \rightarrow \{0,1\}$ be a symmetric Boolean function. Since
-$F$ is symmetric we note that for a fixed size input the output of $F$ is
-entirely determined by the number of 1's in its input. Then let
-$c_{F}:\mathbb{N} \rightarrow 2^{\mathbb{N}}$ define a function where $c_{F}(n)$
-is the set of all $m \leq n$ such that for all $\vec{x} \in \{ 0,1 \}^n$ with
-$m$ 1's we have $F (\vec{x}) = 1$. Clearly a symmetric Boolean function $F$ is
-entirely determined by $c_{F}$.
-
-\begin{prop}
-  \label{prop:fuctions-maj}
-  There is a polynomial $p(k)$ such that for any symmetric function $F$ and a
-  given $k \in \mathbb{N}$ there is a circuit $C_k$ on $k$ inputs over the basis
-  $\mathbb{B}_\maj$ which is symmetric, constant depth and with width bounded by
-  $p(k)$.
-\end{prop}
-
-\begin{proof}
-  We define the circuit $C_k$ for inputs $\vec{x} = ( x_1, \ldots, x_k )$.
-
-  For $a \in \mathbb{N}$ we define a get $\countgate_a$ by
-  \begin{align*}
-    &\countgate_a = \maj (x_1, \ldots, x_k, \underbrace {0, \ldots, 0}_{2a -
-      k}) \land \neg \maj (x_1, \ldots , x_k, \underbrace{0, \ldots,  0}_{2a - k + 2})\text{ if $a \geq \frac{k}{2}$,} \\
-    &\countgate_a = \maj (x_1, \ldots, x_k, \underbrace {1, \ldots, 1}_{x -
-      2a}) \land \neg \maj (x_1, \ldots , x_k, \underbrace{1, \ldots,
-      1}_{k - 2a -2}) \text{ if $a < \frac{k}{2}$. }
-  \end{align*}
-
-  Then let $g = \bigvee_{a \in c_{F_i}(k)}\countgate_a$ and let $C_{k}$ be the
-  circuit with input gates labeled by $\vec{x}$ and output gate $g$.
-
-  t is easy to see that $C_k$ is constant depth and it's width is a polynomial
-  in $k$. We have that in each layer of $C_{g'}$ each gate is connected to all
-  gates in the previous layer, and as such the circuit is symmetric.
-\end{proof}
-
-The above proposition has a straight forward application to circuit
-characterizations.
-
-\begin{prop}
-  Let $F = \{F_i : i \in I \}$ be a family of symmetric Boolean functions where
-  $F_i: \{0,1\}^* \rightarrow \{ 0,1 \}$.
-
-  Let $(C_n)_{n \in \mathbb{N}}$ be family of symmetric circuits over the
-  Boolean basis $\mathbb{B} \cup F$, where $C_n$ is a circuit on structures of
-  size $n$, and the size of each circuit in the family is bounded by some
-  function $f(n)$. Then there exists a polynomial $q(n)$ and a family of
-  symmetric circuits $(C_n')_{n \in \mathbb{N}}$ over $\mathbb{B}_\maj$, where
-  $C_n'$ is a circuit on structures of size $n$ and $\vert C_n' \vert \leq
-  q(f(n))$.
-\end{prop}
-
-\begin{proof}
-  From $C_n$ we construct $C_n'$ in the obvious way. For each gate $g \in C_n$
-  of type $F_i$ we have a symmetric circuit $C_g$ from Proposition
-  \ref{prop:function-maj} that computes the same function as $g$. Then let
-  $C_n'$ be $C_n$ but with each gate $g$ replaced by $C_g$. It is easy to see
-  that $C_n'$ is symmetric. We also have that each gate $g$ must have at most
-  $f(n)$ inputs, and the size of $C_g$ is bounded by $p(f(n))$. Thus the size of
-  $C_n'$ is bounded by $f(n)p(f(n))$.
-\end{proof}
-
-\chapter{October 29th: Symmetric Circuits and CPT}
-
-We already have that that the set of queries decidable by symmetric
-circuits (respectively with counting) is exactly the set of queries
-expressible in Fixed-Point Logic. We know that the CFI query is not
-expressible in FPC, and so there is no symmetric circuit that can
-compute the query.
-
-In our attempts to find a circuit characterisation of CPT, we might try and weaken the requirement of symmetry in our notion of symmetric circuits in order to express the CFI query (and perhaps the whole of CPT).
-One approach would be to weaken the requirement of having small orbits, to rather only having small orbits with respect to our particular input structure.
-We formalise this notion below.
-
-\begin{definition}
-Let $C$ be a circuit on structures of size $n$.
-Let $g$ be a gate in $C$ and let $X$ be a set of input strings closed under the action of the symmetric group.
-The $inv_X = \{ \sigma \in \sym_n : \forall x \in X g \circ H (x) = g \circ H (\sigma x)$.
-\end{definition}
-\begin{definition}
-  Let $(C_n)_{n \in \mathbb{N}}$ be a family of circuits. For any
-  finite structure $\mathcal{A}$ let $X_{\mathcal{A}}$ be the set of
-  all string encodings of $\mathcal{A}$. We say a circuit family has
-  small isomorphism orbits if there is a polynomial $p(n)$ such that
-  for any sufficiently large $n$, finite structure $\mathcal{A}$ of
-  cardinality $n$ and any $g \in C_n$ we have
-  $\vert S_n : \inv_{X_{\mathcal{A}}}(g) \vert \leq p(n)$.
-\end{definition}
-
-\begin{thm}
-  \label{thm:simple_group}
-  Let $n \in \mathbb{N}$, $n \geq 5$. Let $r \in \mathbb{N}$ such that
-  $r \leq n/2$. Suppose that $G$ is a subgroup of $\sym(n)$, then
-  there is a constant $k \in mathbb{N}$ such that for all $n \geq k$
-  if $\vert \sym(n):G \vert \leq {{n}\choose {r}}$ then there exists
-  $X \subseteq [n]$ with $\vert X \vert \leq r$ and such that
-  $\alt([n] \setminus X) \leq G$.
-\end{thm}
-
-The following result shows that even this weakened definition fails to
-capture CPT.
-\begin{thm}
-  There is no family of circuits with small isomorphism orbits that
-  expresses the CFI query.
-\end{thm}
-\begin{proof}
-  Let $(G_n)_{n \in \mathbb{N}}$ be a family of ordered graphs such that each $G_n$ has
-  odd and even CFI graphs $\mathfrak{G}$ and $\tilde{\mathfrak{G}}$ respectively, each of
-  cardinality $n$. Furthermore, suppose the CFI query for $(G_n)$ is not expressible in
-  FPC (the existence of such a family is guaranteed by
-  \cite{}). Suppose there exists a family of circuits $(C_n)_{n \in \mathbb{N}}$ with
-  small isomorphism orbits that decides the CFI query for $(G_n)$.
-  Then we have that $C_n(\mathfrak{G}) = 1$ and
-  $C_n(\tilde{\mathfrak{G}}) = 0$, and for any $g \in C_n$
-
-  \begin{align*}
-    \vert S_n : \inv_{X_{\mathcal{G}}}(g) \vert &\leq p(n),\\
-    \vert S_n : \inv_{X_{\tilde{\mathcal{G}}}}(g) \vert &\leq p(n)
-  \end{align*}.
-  Let $k$ be such that $p(n) \leq n^k$ for all sufficiently large $n$.
-Then we have that $p(n) \leq n^k \leq {{n}\choose{k+1}}$ for all sufficiently large $n$, and (again, taking $n$ large enough) we have that $k \leq n/2$.
-Taking $n$ larger than the constant in Theorem \ref{thm:simple_group} it follows that there exists an $X_1, X_2 \subseteq [n]$ such that $\vert X_1 \vert, \vert X_2 \vert \leq k$ and $\alt ([n] \setminus X_1) \subseteq  \inv_{X_{\mathfrak{G}}}(g)$, $\alt ([n] \setminus X_2) \subseteq  \inv_{X_{\tilde{\mathfrak{G}}}}(g)$.
-It follows that
-  \begin{align*}
-    \alt ([n] \setminus (X_1 \cup X_2)) &\subseteq \alt ([n] \setminus X_1) \cap \alt ([n] \setminus X_2)\\
-                                        &\subseteq \inv_{X_{\mathfrak{G}}}(g) \cap \inv_{X_{\tilde{\mathfrak{G}}}}(g) \\
-                                        &\subseteq \inv_{X_{\mathfrak{G} \cup \tilde{\mathfrak{G}}}}(g) =  \inv_{CFI(G)}(g),
-  \end{align*}
-  where $CFI(G)$ is set of all encodings of all CFI graphs of $G_n$.
-
-  We then have that
-  \begin{align*}
-    \vert S_n : \inv_{CFI(G)}(g) \vert \leq \vert S_n : \alt ([n] \setminus (X_1 \cup X_2)) \leq  \frac{n!}{(n-2k)!/2} \leq n^{2k+1},
-  \end{align*}
-  with the last inequality following for large enough $n$. We thus
-  have from Theorem \ref{} that there is a symmetric circuit $D_n$
-  that decides the CFI problem for $G_n$, and hence a family $(D_n)$
-  that decides the CFI problem for the family of graphs $(G_n)$. From
-  the theorem of Dawar et al. \cite{}, it follows that there is as
-  formula of FPC that decides the CFI query for $(G_n)$ contradicting
-  our assumption.
-\end{proof}
+\bibliographystyle{plain} \bibliography{references}
 \end{document}

### 2017-07-26 sections/introduction.tex
26/07/2017

@@
 \begin{document}
-A finite relational structure, such as a graph, can be represented as a binary
-string in a standard way (for instance, by enumerating its adjacency matrix).
-When we speak of the computational complexity of properties of graphs, we assume
-such an encoding in order to present the structure as input to a machine or
-circuit or other appropriate computational model. The properties of structures
-we are interested in studying are invariant under isomorphisms. This requirement
-translates into an invariance condition on sets of strings---say that a language
-$L \subseteq \{0,1\}^\star$ is a \emph{graph property} if, whenever $x \in L$
-for a string $x$ representing a graph $G$, we have $y\in L$ for any string $y$
-obtained from $x$ by re-ordering the vertices of $G$. The central open question
-in descriptive complexity---whether there is a logical characterisation of the
-polynomial-time decidable properties of finite relational structures--- can then
-be understood as the question of characterizing those languages $L$ that are in
-$\PT$ and are graph properties.
+% A finite relational structure, such as a graph, can be represented as a binary
+% string in a standard way (for instance, by enumerating its adjacency matrix).
+% When we speak of the computational complexity of properties of graphs, we assume
+% such an encoding in order to present the structure as input to a machine or
+% circuit or other appropriate computational model. The properties of structures
+% we are interested in studying are invariant under isomorphisms. This requirement
+% translates into an invariance condition on sets of strings---say that a language
+% $L \subseteq \{0,1\}^\star$ is a \emph{graph property} if, whenever $x \in L$
+% for a string $x$ representing a graph $G$, we have $y\in L$ for any string $y$
+% obtained from $x$ by re-ordering the vertices of $G$. The central open question
+% in descriptive complexity---whether there is a logical characterisation of the
+% polynomial-time decidable properties of finite relational structures--- can then
+% be understood as the question of characterizing those languages $L$ that are in
+% $\PT$ and are graph properties.
 
-Anderson and Dawar~\cite{AndersonD17} study this question through the lens of
-circuit complexity, by considering \emph{symmetric circuits}. These are circuits
-that necessarily accept graph properties, with this fact explicitly witnessed by
-automorphisms of the circuit. To be precise, we can think of a property of
-(directed) graphs on $n$ vertices as being given by a Boolean function $f:
-\{0,1\}^{n^2} \rightarrow \{0,1\}$ which takes as input the $n^2$ potential
-edges and outputs $1$ if the property is satisfied by the graph given on the
-input. The function $f$ is \emph{graph-symmetric} in the sense that any
-permutation of its inputs induced by a permutation of the $n$ vertices leaves
-$f$ unchanged (note this is not the same thing as requiring that $f$ is
-invariant under all permutations of its inputs). A symmetric circuit is a
-circuit computing a Boolean function of $n^2$ inputs where each permutation of
-$[n]$ can be extended to an automorphism of the circuit. Such a circuit
-necessarily computes an invariant function.
+% Anderson and Dawar~\cite{AndersonD17} study this question through the lens of
+% circuit complexity, by considering \emph{symmetric circuits}. These are circuits
+% that necessarily accept graph properties, with this fact explicitly witnessed by
+% automorphisms of the circuit. To be precise, we can think of a property of
+% (directed) graphs on $n$ vertices as being given by a Boolean function $f:
+% \{0,1\}^{n^2} \rightarrow \{0,1\}$ which takes as input the $n^2$ potential
+% edges and outputs $1$ if the property is satisfied by the graph given on the
+% input. The function $f$ is \emph{graph-symmetric} in the sense that any
+% permutation of its inputs induced by a permutation of the $n$ vertices leaves
+% $f$ unchanged (note this is not the same thing as requiring that $f$ is
+% invariant under all permutations of its inputs). A symmetric circuit is a
+% circuit computing a Boolean function of $n^2$ inputs where each permutation of
+% $[n]$ can be extended to an automorphism of the circuit. Such a circuit
+% necessarily computes an invariant function.
 
-The results of~\cite{AndersonD17} show a tight relationship between the
-decdability of a graph property by means of a polynomial-size family of
-symmetric circuits and its definability in extensions of fixed-point logic. In
-particular, they show that a property is definable in fixed-point logic with
-counting ($\FPC$) if, and only if, it is decidable by a polynomially-uniform
-family of symmetric circuits using Boolean and majority gates (or, equivalently,
-threshold gates). Without the symmetry restriction, polynomial-size families of
-circuits have the same computational power whether we restrict ourselves to
-Boolean gates only or allow richer bases such as threshold gates. One
-consequence of the results in~\cite{AD14} is that, with the requirement of
-symmetry, these different bases do yield different expressive power, suggesting
-some lack of robustness to the model. One of the results in the present paper
-shows that the model with majority circuits is robust in the sense that it is
-able to simulate, by means of symmetric circuits, any symmetric circuit composed
-of gates computing Boolean functions that are themselves symmetric (in the sense
-that they are invariant under \emph{all} permutations of their inputs. Thus, any
-property decidable by a polynomially-uniform family of such circuits is
-definable in $\FPC$.
+% The results of~\cite{AndersonD17} show a tight relationship between the
+% decdability of a graph property by means of a polynomial-size family of
+% symmetric circuits and its definability in extensions of fixed-point logic. In
+% particular, they show that a property is definable in fixed-point logic with
+% counting ($\FPC$) if, and only if, it is decidable by a polynomially-uniform
+% family of symmetric circuits using Boolean and majority gates (or, equivalently,
+% threshold gates). Without the symmetry restriction, polynomial-size families of
+% circuits have the same computational power whether we restrict ourselves to
+% Boolean gates only or allow richer bases such as threshold gates. One
+% consequence of the results in~\cite{AD14} is that, with the requirement of
+% symmetry, these different bases do yield different expressive power, suggesting
+% some lack of robustness to the model. One of the results in the present paper
+% shows that the model with majority circuits is robust in the sense that it is
+% able to simulate, by means of symmetric circuits, any symmetric circuit composed
+% of gates computing Boolean functions that are themselves symmetric (in the sense
+% that they are invariant under \emph{all} permutations of their inputs. Thus, any
+% property decidable by a polynomially-uniform family of such circuits is
+% definable in $\FPC$.
 
-This motivates the study of symmetric circuit families that involve gates which
-themselves may compute non-symmetric functions. In particular, motivated by the
-study of rank logic~\cite{DGHL09,GP15}, we consider gates that are
-\emph{matrix-symmetric}. These are gates computing a Boolean function $f:
-\{0,1\}^{A \times B} \rightarrow \{0,1\}$ which is invariant under arbitrary
-permutations of $A$ and $B$. A typical example is the function computing the
-rank of an $A \times B$ $0$-$1$ matrix. We show that the support theorem of
-Anderson and Dawar can be shown to hold, even in the presence of
-matrix-symmetric gates. This allows us to show that definability in the logic
-fixed-point with rank ($\FPR$) is the same as decidability by
-polynomially-uniform families of symmetric circuits with rank gates.
-% Another extension of $\FPC$ that has received much attention in the
-% descriptive complexity literature is the class $\CPTC$ of \emph{choiceless
-% polynomial time with counting}. The work of~\cite{AD14} leaves open the
-% question of obtaining a circuit characterization of this class and it was
-% suggested there that this would require a relaxation of the notion of symmetry
-% used in defining symmetric circuits. In particular, while $\CPTC$ is based on
-% a machine model designed to preserve symmetry by forbidding choices, the
-% polynomial time and space restrictions apply int he context of the symmetries
-% fo a \emph{single input structure}. In this paper, we consider a relaxation of
-% the notion of symmetric circuit intended to capture exactly this intuition.
-% However, we are able to show that this does not yield a characterization of
-% $\CPTC$. In particular, we show that no family in this class of relaxed
-% symmetric circuits can distinguish odd from even Cai-F\"urer-Immerman graphs,
-% something we know is do-able in $\CPTC$~\cite{DRR08}.
+% This motivates the study of symmetric circuit families that involve gates which
+% themselves may compute non-symmetric functions. In particular, motivated by the
+% study of rank logic~\cite{DGHL09,GP15}, we consider gates that are
+% \emph{matrix-symmetric}. These are gates computing a Boolean function $f:
+% \{0,1\}^{A \times B} \rightarrow \{0,1\}$ which is invariant under arbitrary
+% permutations of $A$ and $B$. A typical example is the function computing the
+% rank of an $A \times B$ $0$-$1$ matrix. We show that the support theorem of
+% Anderson and Dawar can be shown to hold, even in the presence of
+% matrix-symmetric gates. This allows us to show that definability in the logic
+% fixed-point with rank ($\FPR$) is the same as decidability by
+% polynomially-uniform families of symmetric circuits with rank gates.
+% % Another extension of $\FPC$ that has received much attention in the
+% % descriptive complexity literature is the class $\CPTC$ of \emph{choiceless
+% % polynomial time with counting}. The work of~\cite{AD14} leaves open the
+% % question of obtaining a circuit characterization of this class and it was
+% % suggested there that this would require a relaxation of the notion of symmetry
+% % used in defining symmetric circuits. In particular, while $\CPTC$ is based on
+% % a machine model designed to preserve symmetry by forbidding choices, the
+% % polynomial time and space restrictions apply int he context of the symmetries
+% % fo a \emph{single input structure}. In this paper, we consider a relaxation of
+% % the notion of symmetric circuit intended to capture exactly this intuition.
+% % However, we are able to show that this does not yield a characterization of
+% % $\CPTC$. In particular, we show that no family in this class of relaxed
+% % symmetric circuits can distinguish odd from even Cai-F\"urer-Immerman graphs,
+% % something we know is do-able in $\CPTC$~\cite{DRR08}.
 

### 2017-08-03 sections/background.tex
Updated first four sections.

@@
 A \emph{relational vocabulary} (usually denoted by $\tau$) is a finite sequence
-of relation symbols $R_1, \ldots, R_k$, such that for all $i \in [k]$, $R_i$ has
-arity of $r_i \in \nats$.
+of relation symbols $(R_1, \ldots, R_k)$, such that for all $i \in [k]$, $R_i$
+has arity of $r_i \in \nats$. All vocabularies discussed in this paper are
+relational vocabularies. A \emph{many-sorted vocabulary} is a tuple of the form
+$(R, S, \nu)$, where $R$ is a relational vocabulary, $S$ is a finite sequence of
+\emph{sort} symbols $(s_1, \ldots s_p)$, and $\nu$ is a function that assigns to
+each $R_i \in R$ a tuple $\nu(R_i) := (s^i_1, \ldots, s^i_{r_i})$, where for
+each $j \in [r_i]$, $s^i_j \in S$. We call $\nu$ the \emph{\type function} and
+$\nu(R_i)$ the \emph(type) of $R_i$.
 
-A $\tau$-structure $\mathcal{A}$ is a tuple $\langle U, R^{\mathcal{A}}_1 ,
-\ldots , R^{\mathcal{A}}_k \rangle$, where $U$ is a set and called the
-\emph{universe} of $\mathcal{A}$ and for all $i \in [k]$ the relations
-$R^{\mathcal{A}}_i \subseteq U^{r_i}$. The elements of $U$ are called the
-elements of $\mathcal{A}$. A \emph{multi-sorted} structure is one whose universe
-is a disjoint union, where each set in the union is called a \emph{sort}. The
-size of a structure is the cardinality of its universe.
+Let $\tau$ be a many-sorted vocabulary. A \emph{$\tau$-structure} $\mathcal{A}$
+is a tuple $(U , R^{\mathcal{A}}_1 , \ldots , R^{\mathcal{A}}_k )$, where $U$,
+the \emph{universe} of $\mathcal{A}$, is a disjoint union of non-empty sets
+$U_{s_j}$, one for each sort symbol $s_j \in S$. For each $i \in [k]$, where
+$\nu(R_i) = (s^i_1 , \ldots , s^i_{r_i})$, $R^{\mathcal{A}}_i \subseteq
+U_{s^i_1} \times \ldots \times U_{s^i_{r_i}}$. The elements of $U$ are called
+the elements of $\mathcal{A}$. If $tau$ is a relational vocabulary, a
+$\tau$-structure is a structure over $(\tau, S, \nu)$, where $S$ is a singleton
+and $\nu$ is the only allowable type function. The size of a structure
+$\mathcal{A}$, denoted by $\vert \mathcal{A} \vert$, is the cardinality of its
+universe. The sorted-size of a structure is a vector $\vec{n} := (n_{s_1},
+\ldots , n_{s_p}) \in \mathbb{N}^{S}$ such that $\vert U_{s} \vert = n_{s}$ for
+all $s \in S$. If $a \in U_{s_j}$ for some sort $s_j \in S$, we say that $a$ has
+sort $s_j$. We often use $A$ to denote the universe of a structure
+$\mathcal{A}$. All structures in this paper are finite unless stated otherwise.
 
-All structures in this paper are finite.
+\begin{definition}
+  Let $S = \{s_1, \ldots , s_p\}$ be a set of sort symbols and $A = A_{s_1}
+  \sqcup \ldots \sqcup A_{s_p}$ and $B = B_{s_1}\dotcup \ldots \dotcup
+  B_{s_p}$ be disjoint unions of non-empty sets. A \emph{sorted bijection}
+  between $A$ and $B$ is a bijection $f: A \rightarrow B$ such that $f (A_s) =
+  B_s$ for all $s \in S$.
+\end{definition}
 
-\subsection{First Order, Fixed-Point, Counting}
+If $\tau = (R, S, \nu)$ is a single-sorted vocabulary then we abuse notation and
+identify $\tau$ with $R$.
 
+\subsection{First Order, Fixed-Point and Counting}
 Let $\FO(\tau)$ denote \emph{first order logic} with respect to the vocabulary
@@
 inflationary fixed-point operator (see \cite{} for details). For logic
-$\mathcal{L}$, a formula $\phi \in \mathcal{L}(\tau)$, $x$ a $k$-length tuple of
-variables, $\mathcal{A}$ a (finite) structure, and $a \in U^k$, we have that
-$\phi (x)$ denotes that the variables in $x$ are free in $\phi$ and we write
-$\mathcal{A} \models_{\mathcal{L}} \phi[a]$ iff the the formula $\phi$ is true
-in $\mathcal{A}$ with respect to $\mathcal{L}$ with the variables $x$ assigned
-to $a$. The context usually makes the logic obvious, and in that case we usually
-drop the subscript.
+$\mathcal{L}$, a formula $\phi \in \mathcal{L}(\tau)$, $x$ a $k$-tuple of
+variables, $\mathcal{A}$ a (finite) structure, and $a \in U^k$, we write the
+formulas $phi (x)$ to denote that the free variables of $\phi$ are among and we
+write $\mathcal{A} \models_{\mathcal{L}} \phi[a]$ iff the the formula $\phi$ is
+true in $\mathcal{A}$ with respect to $\mathcal{L}$ with the variables $x$
+assigned to $a$. The context often makes the logic obvious, and in that case we
+usually omit the subscript.
 
 We also recall the definition of \emph{fixed-point logic with counting} $\FPC$,
-an extension $\FP$ with counting quantifiers. For a structure $\mathcal{A}$,
-Formulas of this logic are evaluated over a structure $\mathcal{A}$ by extending
-that structure to $\mathcal{A}^\leq$, a two sorted extension of $\mathcal{A}$ by
-an ordered number sort $\{1, \ldots, \vert U\vert \}$. Variables are taken to be
-either point variables, ranging over $U$ or number variables ranging over
-$[\vert U \vert]$. The counting quantifiers are of the form $\#_x$, where $x$ is
-either a point or number variable and for $\phi(x) \in \FPC(\tau)$, $\#_x
-\phi(x)$ is a term denoting the element of the number sort corresponding to
-$\vert \{a \in \mathcal{A} | \mathcal{A} \models \phi[a]\}\vert$. Note
-additionally that $k$-tuples of number variables can be used to encode numbers
-in $\FPC$ of size up to $\vert U\vert^k$. For more details on $\FPC$ please see
-\cite{}.
+an extension $\FP$ with counting terms (see \cite{grohe2017descriptive} for
+details). Variables and terms in $\FPC$ must be of one of two sorts, vertex or
+numeric, where vertex variables are assigned to elements of the universe the
+structure and numeric variables to the elements of $\mathbb{N}$. All atomic
+formula as in $\FP$ are formulas of $\FPC$ (using only vertex sort variables).
+Let $\phi(x)$ be a formula of $\FPC$ with free variables $x$, then $\# x \phi$
+is a numeric, with the term's semantics being the number of elements satisfying
+$\phi$. All numeric variables as well as the symbols 0 and 1 are numeric terms
+with the expected semantics. If $\mu_1 and \mu_2$ are numeric terms, then $\mu_1
++ \mu_2$ and $\mu_1 * \mu_2$ are numeric terms with the expected semantics.
+Moreover, if $\mu_1$ and $\mu_2$ are numeric terms, then $\mu_1 < \mu_2$ and
+$\mu_1 = \mu_2$ are formulas with the expected semantics. If $\vec{x}$ is a
+$k$-tuple of numeric variables and $\vec{\mu}$ is a $k$-tuple of closed numeric
+term (i.e. ones without any free variables) then $\exists \vec{x} \leq \vec{\mu}
+\phi(\vec{x})$ and $\forall \vec{x} \leq \vec{mu} \phi(\vec{x})$ are formulas.
+In the existential case, for a $\tau$-structure $\mathcal{A}$, we say
+$\mathcal{A} \models \exists \vec{x} \leq \vec{\mu} \phi(\vec{x})$ iff there
+exists $\vec{n} \in [\mu^{\mathcal{A}}_1] \times \ldots \times
+[\mu^{\mathcal{A}}_2]$, such that $phi^{\mathcal{A}}$ holds for the assignment
+$\vec{x} \mapsto \vec{n}$. The semantics of the universal case follows
+similarly. The application of the fixed-point operator (but now with the
+relation variables possibly being of mixed type), and Boolean connectives
+similarly define formulas as in $\FP$. The semantics of these formulas is also
+similarly defined.
+
+% Let $\FO(\tau)$ denote \emph{first order logic} with respect to the vocabulary
+% $\tau$. \emph{Fixed-Point Logic} is the extension of $\FO(\tau)$ with an
+% inflationary fixed-point operator (see \cite{} for details). For logic
+% $\mathcal{L}$, a formula $\phi \in \mathcal{L}(\tau)$, $x$ a $k$-length tuple
+% of variables, $\mathcal{A}$ a (finite) structure, and $a \in U^k$, we have
+% that $\phi (x)$ denotes that the variables in $x$ are free in $\phi$ and we
+% write $\mathcal{A} \models_{\mathcal{L}} \phi[a]$ iff the the formula $\phi$
+% is true in $\mathcal{A}$ with respect to $\mathcal{L}$ with the variables $x$
+% assigned to $a$. The context usually makes the logic obvious, and in that case
+% we usually drop the subscript.
+
+% We also recall the definition of \emph{fixed-point logic with counting}
+% $\FPC$, an extension $\FP$ with counting quantifiers. For a structure
+% $\mathcal{A}$, Formulas of this logic are evaluated over a structure
+% $\mathcal{A}$ by extending that structure to $\mathcal{A}^\leq$, a two sorted
+% extension of $\mathcal{A}$ by an ordered number sort $\{1, \ldots, \vert
+% U\vert \}$. Variables are taken to be either point variables, ranging over $U$
+% or number variables ranging over $[\vert U \vert]$. The counting quantifiers
+% are of the form $\#_x$, where $x$ is either a point or number variable and for
+% $\phi(x) \in \FPC(\tau)$, $\#_x \phi(x)$ is a term denoting the element of the
+% number sort corresponding to $\vert \{a \in \mathcal{A} | \mathcal{A} \models
+% \phi[a]\}\vert$. Note additionally that $k$-tuples of number variables can be
+% used to encode numbers in $\FPC$ of size up to $\vert U\vert^k$. For more
+% details on $\FPC$ please see \cite{}.
 
@@
 In this paper we use the definition of $\FPR$ given by Grad\"{e}l and Pakusa
-\cite{}, an strictly more expressive extension of the rank logic introduced by
-Dawar et. al. cite{}. We briefly define this logic here. For more detail please
-see \cite{}. $\FPR$ is an extension of $\FPC$ with rank operators, which we now
-define.
+\cite{Gradel2015}, an strictly more expressive extension of the rank logic
+introduced by Dawar et. al. cite{Dawar09logicswith}. We briefly define this
+logic here. For more detail please see \cite{Gradel2015}. $\FPR$ is an extension
+of $\FPC$ with rank operators, which we now define.
 
@@
 over the universe of the structure, $\vec{\nu}$ and $\vec{\mu}$ are tuples of
-variables ranging over the number type, and $\vec{s}$ and $\vec{t}$ are tuples
-of closed numeric terms that bound the range of $\vec{\nu}$ and $\vec{\mu}$
-respectively. Then let $\mathcal{A}$ be a structure and let
-$\mathbb{N}^{\leq\vec{t}} := \{\vec{n} \in \mathbb{N}^{\vert \vec{v} \vert}: n_i
-\leq t^{\mathcal{A}}_i\}$, and let $\mathbb{N}^{\leq \vec{s}}$ be defined
-similarly. Let $I:= A^{\vert \vec{x} \vert} \times \mathbb{N}^{\leq \vec{t}}$
-and $J := A^{\vert \vec{y} \vert} \times \mathbb{N}^{\leq \vec{s}}$ Then let
-$M^{\mathcal{A}}_\phi : I \times J \rightarrow \mathbb{N}$ be defined by
-$M^{\mathcal{A}}_\phi (\vec{a}\vec{n}, \vec{b}\vec{m}):=
-\phi^{\mathcal{A}}(\vec{a}\vec{n},\vec{b}\vec{m})$.
+numeric variables , and $\vec{s}$ and $\vec{t}$ are tuples of closed numeric
+terms that bound the range of $\vec{\nu}$ and $\vec{\mu}$ respectively. Then let
+$\mathcal{A}$ be a structure and let $\mathbb{N}^{\leq\vec{t}} := \{\vec{n} \in
+\mathbb{N}^{\vert \vec{v} \vert}: n_i \leq t^{\mathcal{A}}_i\}$, and let
+$\mathbb{N}^{\leq \vec{s}}$ be defined similarly. Let $I:= A^{\vert \vec{x}
+  \vert} \times \mathbb{N}^{\leq \vec{t}}$ and $J := A^{\vert \vec{y} \vert}
+\times \mathbb{N}^{\leq \vec{s}}$ Then let $M^{\mathcal{A}}_\phi : I \times J
+\rightarrow \mathbb{N}$ be defined by $M^{\mathcal{A}}_\phi (\vec{a}\vec{n},
+\vec{b}\vec{m}):= \phi^{\mathcal{A}}(\vec{a}\vec{n},\vec{b}\vec{m})$.
 
 The rank operator is then defined as $[rk (\vec{x}, \vec {\nu} \leq \vec{t},
-\vec{y}\vec{\mu} \leq \vec{s}, \pi \leq r). \phi]$, where $\pi$ is a variable
-ranging over the number sort and $r$ is a closed numeric term that bounds $\pi$.
-The value of the rank term for a structure $\mathcal{A}$ and an assignment $\pi
-\mapsto p$, where $p$ is prime, is given by the rank of $M^{\mathcal{A}}_\phi$
-mod $p$, as understood as a matrix over $\mathbb{F}_p$.
+\vec{y}\vec{\mu} \leq \vec{s}, \pi \leq r). \phi]$, where $\pi$ is a numeric
+variable and $r$ is a closed numeric term that bounds $\pi$. The value of the
+rank term for a structure $\mathcal{A}$ and an assignment $\pi \mapsto p$, where
+$p$ is prime, is given by the rank  of $M^{\mathcal{A}}_\phi$ mod $p$, where the
+matrix is understood to have entries in $\mathbb{F}_p$.
+
+\subsection{Circuits}
+A \emph{Boolean circuit} $C$ defined over some basis $\mathbb{B}$ is a directed
+acyclic graph (DAG) with designated input gates $x_1, \ldots, x_n$, each with
+in-degree $0$, internal gates labelled by elements of $\mathbb{B}$, and a single
+designated output gate with out-degree 0. A Boolean basis consists either of a
+set of Boolean functions or a set of symbols which implicitly define a family of
+Boolean functions.
+
+Let $C$ be a circuit with input gates $x_1, \ldots, x_n$ and output gate $g_o$.
+The evaluation of $C$ for an input $\vec{x}\in \{0,1\}^n$ proceeds inductively
+from the assignment of $\vec{x}$ to the input gates. with the internal and
+output gates evaluated in accordance with the element of the basis labelling
+that gate. We denote the evaluation of a gate $g$ in by $C[\vec{x}](g)$, with
+the out of the circuit then given by $C[\vec{x}](g_o)$. In this way $C$ computes
+a Boolean function of the form $f:\{0,1\}^n \rightarrow \{0,1\}$. It is easy to
+see that for any complete Basis and any Boolean function there is a circuit over
+that basis that computes the function.
+
+% It is worth noting that the input to a gate is an unstructured set, and as
+% such it is implicitly required that the label associated with that gate define
+% a \emph{symmetric function} (a function whose output depends on the number of
+% 1's in its input).
+
+There are many natural properties of a circuit.The \emph{size} of a circuit $C$,
+denoted by $\vert C \vert$ is the number of gates in the circuit. The
+\emph{depth} of a circuit is the length of the longest path from an input gate
+to the output gate. The \emph{width} of a circuit is the maximum size of a set
+of gates all the same distance from the input gates.
+
+We say a family of circuits $(C_n)_{\mathbb{N}}$ \emph{decides} a language $L
+\{0,1\}^{*} \rightarrow \{0,1\}$ if $C_n$ computes the same function as $L$
+restricted to inputs of size $n$. It is common to ask about the class of
+languages that a can be decided by circuit families with certain restrictions.
+The following restriction is of importance in this paper.
+
+Two Boolean bases often considered in this paper are $\mathbb{B}_{\std} = \{
+\neg , \wedge , \lor \}$ and $\mathbb{B}_\maj = \{ \maj \} \cup \mathbb{B}$,
+where $\neg, \wedge and \lor$ are the usual logical connectives and $\maj$ is
+the majority gate, where for a Boolean sequence $\vec{x}$, $\maj(\vec{x}) = 1$
+iff the number of $1$'s in $\vec{x}$ is greater than or equal to
+$\frac{\vert\vec{x}\vert}{2}$.
+
+\begin{definition}
+  Let $(C_n)_{n \in \mathbb{N}}$ be a family of Boolean circuits. We say that
+  $(C_n)_{n \in \mathbb{N}}$ is \emph{$\PT$-uniform} if the mapping $n \mapsto
+  C_n$ is polynomial-time computable in $n$.
+\end{definition}
+
+Let $C$ be a circuit with the sets of gates $G$ and edge relation $W$. Let $g
+\in G$, we denote the \emph{children} or \emph{input gates} of $g$ by the set
+$H_g := \{h \in G : W(h,g)\}$.
 
 \subsection{Symmetric Circuits}
-This still needs to be filled in
+A circuit for structures, as given by Anderson and Dawar, is defined for a fixed
+relational vocabulary $\tau$, a Boolean basis of $\mathbb{B}$ \emph{symmetric
+  functions} (function's whose output depends only on the number of 1's in the
+input) and some fixed universe of size $n$. The input gates are taken to be the
+formal graph of the relational symbols over the universe $[n]$, i.e. gates
+labelled by $R(\vec{x})$ where $\vec{x} \in [n]^{\arty(R)}$. The input to the
+circuit is a finite $\tau$-structure $\mathcal{A}$ of cardinality $n$.
+
+Evaluation of the circuit proceeds by first choosing a bijection $\gamma$ from
+the universe of $\mathcal{A}$ to $[n]$ and then, for each input gate, using the
+interpretation of the relevant relational symbol in $\mathcal{A}$ and the
+bijection $\gamma$ to evaluate the gate. Recursing through the circuit and
+evaluating the internal gates using the given semantics for the symbols in the
+Boolean basis allows each gate in the circuit to be evaluated.
+
+A circuit is \emph{invariant} if its output does not depend on the choice of
+$\gamma$. A \emph{symmetric} circuit is a circuit such that every permutation on
+the universe $[n]$, each of which induces a permutation on the input gates,
+extends to an automorphism of the circuit. A symmetric circuit is necessarily
+invariant.
+
+It is important to note that the word `symmetric' is used in two different ways
+here. When applied to a circuit the above definition is used, but when applied
+to a Boolean function it denotes a function whose output depends only on the
+number of 1's in its input.
+
+The main result of~\cite{AndersonD17} is the following characterisation theorem.
+
+\begin{thm}
+  For any relational vocabulary $\tau$, a property of finite $\tau$-structures
+  is decided by a P-uniform family of symmetric circuits with majority gates if,
+  and only if, it is expressible in FPC.
+\end{thm}
+
 \end{document}

### 2017-08-03 sections/symmetric-circuits.tex
Updated first four sections.

@@
 % Note: include circuits in background
-Circuits are a well-studied model in complexity theory and, more recently, they
-have been studied in the context of finite model theory. Circuits in the
-literature () are usually defined as DAG's, with each vertex labelled by some
-element of a basis. While not explicitly stated, a consequence of this
-definition is that, when evaluating a gate, the Boolean function labelling this
-gate should not depend on any ordering or labelling of its input. In other
-words, it must be a symmetric function.
+Circuits are a well-studied model in complexity theory, and more recently they
+have been studied in the context of finite model theory. However, there are some
+subtleties in the definition and evaluation of circuits which must be considered
+carefully and have important implications for the notion of a symmetric circuit
+studied in this paper. Let $C$ be a Boolean circuit $g$ be an internal gate
+labelled by some function $f_g: \{0,1\}^{A} \rightarrow \{0,1\}$, for some index
+set $A$ with $\vert A \vert = \vert H_g \vert$. Formally, evaluating $g$
+requires a (usually bijective) indexing function $f_i: A \mapsto H_g$, which
+organises the inputs of $g$ into an appropriate sequence. The evaluation of $g$
+is then given by $C[\vec{x}](g) = f_g (a \mapsto C[\vec{x}](f_i(a)))$. As such
+the evaluation of a gate in a circuit may depend on how the inputs to the gate
+are indexed.
 
-Motivated by the desire to study circuits with gates that compute rank, a
-function which is not symmetric, we develop a general framework for studying
-functions whose output depends on the structure of the input. This structure
-also allows us to define and explore appropriate symmetries on the function.
+In most contexts in complexity theory, circuits may be taken to be implicitly
+ordered objects and so this indexing function can be defined as taking the $i$th
+element of $A$ to the $i$th element of $H_g$. However, in general this renders
+the evaluation of a circuit for a given input a property both of the circuit and
+an arbitrary order. In order to address this problem this problem many authors
+only define circuits over Boolean bases of symmetric functions (e.g. the
+standard basis or the majority basis). In this case the evaluation of a gate is
+independent of the choice of indexing function.
 
-With the necessary structure on the input of each Boolean function explicitly given, we then
-develop a circuit model which incorporates this structure, and so allows for
-circuits to be defined over Basis of functions that are not symmetric.
+However, in this paper we require gates labelled by Boolean rank functions, i.e.
+a function that takes in a Boolean sequence indexed by `row' and `column' sets,
+outputs 1 iff that matrix, when interpreted as having entries in $\mathbb{F}_p$,
+has rank at least $r$. These rank functions clearly depend on how the input
+sequence is labelled, and so are not symmetric. However, it is worth noting that
+while such rank functions may be symmetric, they are symmetric in the weaker
+sense of being constant under permutations on the rows and columns of the input
+matrix.
 
-Finally, we prove that no family of Basis of symmetric functions can improve on
-the expressive power of the circuit model of Anderson and Dawar \cite{AndersonD17}.
-Together with the main theorem of this paper this implies that the more general
-circuit models that are defined over basis of functions which are not symmetric
-(with respect to the whole symmetric group) are strictly more powerful.
+Motivated by the desire to study circuits with gates that compute rank, We
+develop a general framework for circuits that allows gates to be labelled by
+Boolean functions of the form $F: \{0,1\}^{X} \rightarrow \{0, 1\}$, where the
+labelling $X$ is the universe of a many-sorted structure over some vocabulary
+$\tau$. The Moreover, we generalise the notion of a circuit for structures (see
+Anderson and Dawar \cite{AndersonD17}), incorporate an appropriate labelling for
+the inputs of each gate and allowing for a Boolean basis including non-symmetric
+functions. Furthermore, the vocabulary $\tau$ will allow us to impose natural
+symmetry conditions on $F$, and so allowing us to develop a useful notion of a
+symmetric circuit.
+
+We also prove that no family symmetric functions defined over a basis of
+symmetric functions can improve on the expressive power of the circuit model of
+Anderson and Dawar \cite{AndersonD17}. Together with the main theorem of this
+paper this implies that these more general symmetric circuits are strictly more
+powerful.
 
@@
 
-\subsection{$\tau$-Symmetric Functions}
-% note: include many-sorted signature in background
-Let $\tau = (R, S, \nu)$ be a many-sorted, relational signature. Suppose some
-ordering on the set of relations and sorts, so $R = \{R_1 \ldots, R_t\}$ and $S
-= \{s_1, \ldots s_p\}$, and let $\nu(R_i) = (a^i_1, \ldots , a^i_{\arty(R_i)})$,
-where $a^i_q \in S$ for all $q \in [\arty(R_i)]$. For each $s \in S$ let $A_{s}$
-be a non-empty set, and let $A = A_{s_1} \times \ldots \times A_{s_p}$. Let
+\subsection{Structured Functions and Symmetry}
+Let $\tau = (R, S, \nu)$ be a many-sorted, relational signature, with $R = \{R_1
+\ldots, R_t\}$ and $S = [s]$ for some $s \in \nats$, and $\nu(R_i) = (a^i_1,
+\ldots , a^i_{r_i)})$, where $r_i = \arty(R_i)$ and $a^i_q \in S$ for all $q \in
+[r_i]$. For each $s \in S$ let $A_s$ be a non-empty set, and let $A := A_{1}
+\sqcup \ldots \sqcup A_{s} = \{(a,s) : a \in A_s\}$. Let
 \[
-  X^{\tau}_A:= A_{a^1_1} \times \ldots \times A_{a^1_{\arty(R_1)}} \times \ldots
-  \times A_{a^t_1} \times A_{a^t_{\arty(R_t)}}.
-\]
+  \ind (A, \tau) := A_{a^1_1} \times \ldots \times A_{a^1_{r_1}} \times \ldots
+  \times A_{a^t_1} \times A_{a^t_{r_t}},
+\]. We call $\ind (A, \tau)$ the \emph{index defined by} $(A, \tau)$.
 
-Let $G \leq \sym_{A_{s_1}} \times \ldots \times \sym_{A_{s_p}}$. There is a
-natural action of $G$ on $X$. It is easy to see that if $\mathcal{C}_A$ is the
-category with objects given by $\tau$-structures over $A$ and morphisms by the
-action of $G$, and $\mathcal{C}_X$ is the category of subsets of $X^{\tau}_A$
-with morphisms similarly given by the action of $G$, then these two categories
-are equivalent. More informally, the subsets of $X^{\tau}_A$ encode the
-$\tau$-structures over $A$. This relationship is bijective and the action of $G$
-factors through this bijection.
+% It is worth noting that there is a natural bijection $P$ that maps
+% $\tau$-structures with universe $A$ to subsets of $\Ind(A, \tau)$, taking each
+% $\tau$-structure $\mathcal{A}$ to the set $\{(\vec{X}_1, \ldots , \vec{X}_t) :
+% \exists i \in [t] \(\vec{X_i} \in R^{\mathcal{A}}_i \) \}$.
 
-\begin{remark}
-  Is the categorical language unnecessary? It seemed the quickest way of saying
-  what I wanted to say formally.
-\end{remark}
+For the remainder of the section let $X := \ind (A, \tau)$. Let $G \leq
+\sym_{X}$, there is a natural action of $G$ on $X$. There is also a natural
+action of $\sym_{A_1} \times \ldots \times \sym_{A_s}$ on $X$ and a subgroup
+$G'$ of $\sym_X$ corresponding to the same action. We identify these two groups.
 
-\begin{remark}
-  In the above section (and just below) we talk about the action of
-  $\sym_{A_{s_1}} \times \ldots \times \sym_{A_{s_p}}$ on elements of $X^\tau_A$
-  and structured functions. In the proof of the support theorem, when defining a
-  definable matrix for converting circuits into formulas, and later on in this
-  section, it is useful to speak more generally and instead look at bijections
-  from $A_1, \ldots A_{s_p}$ to $B_1, \ldots, B_{s_p}$, thus allowing us to map
-  between $X^\tau_A$ and $X^\tau_B$ and so between the associated structured
-  functions. I've added this in later on in the section, but I still need to
-  incorporate it into the original definition (it's a more general notion in a
-  sense, and so I think it should be incorporated). I'll wait for feedback
-  before doing this as I'm not sure this formulation will survive.
-\end{remark}
+Furthermore, we can defined an action of $G$ on functions of the form $f: X
+\rightarrow H$, for any set $H$, given by $\sigma \cdot f(x) = f(\sigma \cdot
+x)$ for all $x \in X$. If $H = \{0,1\}$ we say that $f$ is a \emph{binary
+  sequence indexed by $X$}. If $H$ is surjective, we say that \emph{$f$ indexes
+  $H$ by $X$} or \emph{$f$ indexes $H$ by $(A,\tau)$}.
 
-Note that there is also a natural action on functions of the form $\vec{i}:
-X^{\tau}_A \rightarrow \{0,1\}$ given by $\sigma \cdot \vec{i}(x) =
-\vec{i}(\sigma x)$.
+We develop a notion of equivalence from this action. Say that two functions $f,
+g : X \rightarrow H$ are \emph{$G$-equivalent} iff there exists $\sigma \in G$
+such that $f(x) = f(\sigma \cdot x)$ for all $x \in X$. We say $f$ and $g$ are
+\emph{sort-equivalent} if they are $\sym_{A_1} \times \ldots
+\sym_{A_p}$-equivalent.
 
-We now introduce a few useful notions of symmetry. We call a function of the
-form $F:\{0,1\}^{X^{\tau}_A} \rightarrow \{0,1\}$ a \emph{$(\tau, A)$-structured
-  function}, with $\tau$ called the \emph{signature of $F$} and $A$ \emph{the
-  universe of $F$}. Call $F$ a \emph{structured function} if it is a $(\tau,
-A)$-structured function for some appropriate $\tau$ and $A$.
+We call a function of the form $F:\{0,1\}^{X} \rightarrow \{0,1\}$ a
+\emph{$(\tau, A)$-structured function}. We call $(\tau, A)$ the \emph{type} of
+$F$, $\tau$ the \emph{signature of $F$} and $A$ \emph{the universe of $F$}. We
+also use $\ind(F)$ to abbreviate $\ind (\type (F))$.Call $F$ a \emph{structured
+  function} if it is a $(\tau, A)$-structured function for some appropriate
+$\tau$ and $A$.
 
-We say a $(\tau, A)$-function is \emph{$(\tau, G)$-symmetric} if for all
-$\vec{i} \in \{0,1\}^{X^\tau_A}$ and $\sigma \in G$, $f(\sigma \cdot \vec{i}) =
-f(\vec{i})$. We say $F$ is \emph{$\tau$-symmetric} if it is $(\tau,
-\sym_{A_{s_1}} \times \ldots \times \sym_{A_{s_p}})$-symmetric. Let $\tau = (S,
-R, \nu)$, with $\vert S \vert \leq 2$, $R = {R'}$ and $\nu (R') = (s_1, s_2)$
-(with $s_1$ and $s_2$ being the first and last elements of S in the ordering
-respectively); if $F$ is $\tau$-symmetric we say $F$ is \emph{matrix-symmetric}.
-If $\tau$ is single-sorted we call $F$ \emph{simple} and if it consists of a
-single unary relation, we call $F$ \emph{unary}. We say $F$ is
-\emph{graph-symmetric} if $F$ is simple and matrix-symmetric.
+% It is easy to see that if $\mathcal{C}_A$ is the category with objects given
+% by $\tau$-structures over $A$ and morphisms by the action of $G$, and
+% $\mathcal{C}_X$ is the category of subsets of $X^{\tau}_A$ with morphisms
+% similarly given by the action of $G$, then these two categories are
+% equivalent. More informally, the subsets of $X^{\tau}_A$ encode the
+% $\tau$-structures over $A$. This relationship is bijective and the action of
+% $G$ factors through this bijection.
+
+% \begin{remark}
+%   Is the categorical language unnecessary? It seemed the quickest way of
+%   saying what I wanted to say formally.
+% \end{remark}
+
+% \begin{remark}
+%   In the above section (and just below) we talk about the action of
+%   $\sym_{A_{s_1}} \times \ldots \times \sym_{A_{s_p}}$ on elements of
+%   $X^\tau_A$ and structured functions. In the proof of the support theorem,
+%   when defining a definable matrix for converting circuits into formulas, and
+%   later on in this section, it is useful to speak more generally and instead
+%   look at bijections from $A_1, \ldots A_{s_p}$ to $B_1, \ldots, B_{s_p}$,
+%   thus allowing us to map between $X^\tau_A$ and $X^\tau_B$ and so between the
+%   associated structured functions. I've added this in later on in the section,
+%   but I still need to incorporate it into the original definition (it's a more
+%   general notion in a sense, and so I think it should be incorporated). I'll
+%   wait for feedback before doing this as I'm not sure this formulation will
+%   survive.
+% \end{remark}
+
+These structured functions give us a general framework for indexing the input to
+functions. Moreover, the structure on these index sets allows us to develop a
+natural notion of symmetry particular to the indexing used by the function. Let
+$F$ be a $(\tau, A)$-structured function. We say $F$ is \emph{$G$-invariant} if
+for all $G$-equivalent $\vec{x},\vec{y} \in \{0,1\}^{X}$, $F(\vec{x}) =
+F(\vec{y})$. We say $F$ is \emph{sort-invariant} if it is $(\tau, \sym_{A_{1}}
+\times \ldots \times \sym_{A_{s}})$-invariant. If $\tau = (\{R\}, [2], \nu)$,
+with $\nu (R) = (1, 2)$ and $F$ is sort-invariant then we say $F$ is
+\emph{matrix-invariant}.
+
+% Let $F$ be a $(\tau, A)$-structured function with $\tau = (\{R\}, \{1\},
+% \nu)$, where $R$ is a binary relation. Let $G \leq \sym_A$ such that for any
+% $v, w \in A$ We say $F$ is \emph{graph-symmetric} if $F$ is $(\tau, A)$simple
+% and matrix-symmetric.
+
+% If $\tau$ is single-sorted we call $F$ \emph{simple} and if it consists of a
+% single unary relation, we call $F$ \emph{unary-relational}.
+We have developed this more general notion of symmetry for Boolean functions
+that naturally takes into account the structure on the input sequence. The
+following lemma shows that symmetry is just the requirement that the function be
+invariant under permutations of its input, irrespective of structure.
 
 \begin{lem}
-  Let $X^\tau_A$ be defined as above and let $F: \{0,1\}^{X^{\tau}_A}
-  \rightarrow \{0,1\}$, then $F$ is a symmetric function (in the sense of
-  Anderson and Dawar \cite{AndersonD17}) if and only if $F$ is a simple and
-  unary.
+  Let $F$ be a $(\tau, A)$-structured function. $F$ is a symmetric function if
+  and only if $F$ is $\sym_A$-invariant.
 \end{lem}
 
-We briefly introduce notions of equivalence useful for comparing functions.
-\begin{definition}
-  Let $\tau = (R, S, \nu)$ be a many-sorted signature and let $A = A_1 \times
-  \ldots A_s$ and $B = B_1 \times \ldots \times B_s$ be a product of non-empty
-  sets. A \emph{sorted bijection} between $A$ and $B$ is a function bijections
-  $f: A \rightarrow B$ such that $f (A_i) = B_i$ for all $i \in S$. There is an
-  obvious action of $f$ that maps $X^\tau_A$ to $X^\tau_B$ and
-  $\{0,1\}^{X^\tau_A}$ to $\{0,1\}^{X^\tau_B}$.
+% We briefly introduce notions of equivalence useful for comparing functions.
+% \begin{definition}
+%   Let $\tau = (R, S, \nu)$ be a many-sorted signature and let $A = A_1 \times
+%   \ldots A_s$ and $B = B_1 \times \ldots \times B_s$ be a product of non-empty
+%   sets. A \emph{sorted bijection} between $A$ and $B$ is a function bijections
+%   $f: A \rightarrow B$ such that $f (A_i) = B_i$ for all $i \in S$. There is
+%   an obvious action of $f$ that maps $X^\tau_A$ to $X^\tau_B$ and
+%   $\{0,1\}^{X^\tau_A}$ to $\{0,1\}^{X^\tau_B}$.
 
-  Let $L: X^\tau_A \rightarrow H$ and $L': X^\tau_B \rightarrow H$ be two
-  functions for some finite set $H$. We say that $L \sim L'$, or \emph{$L$ is
-    equivalent to $L'$}, if there is a sorted bijection $f: A \rightarrow B$
-  such that for all $x \in X^\tau_A$, $L(x) = L'(f (x))$.
+%   Let $L: X^\tau_A \rightarrow H$ and $L': X^\tau_B \rightarrow H$ be two
+%   functions for some finite set $H$. We say that $L \sim L'$, or \emph{$L$ is
+%   equivalent to $L'$}, if there is a sorted bijection $f: A \rightarrow B$
+%   such that for all $x \in X^\tau_A$, $L(x) = L'(f (x))$.
 
-  Let $F$ be a $(\tau, A)$-structured function and $G$ be a $(\tau,
-  B)$-structured function. Then we say that $F \sim G$, or \emph{$F$ is
-    equivalent to $G$}, if there is a sorted bijection $f: A rightarrow B$ such
-  that for all $\vec{i} \in \{0,1\}^{X^\tau_A}$, $F (\vec{i}) = G(f(\vec{i}))$.
-\end{definition}
+%   Let $F$ be a $(\tau, A)$-structured function and $G$ be a $(\tau,
+%   B)$-structured function. Then we say that $F \sim G$, or \emph{$F$ is
+%   equivalent to $G$}, if there is a sorted bijection $f: A rightarrow B$ such
+%   that for all $\vec{i} \in \{0,1\}^{X^\tau_A}$, $F (\vec{i}) =
+%   G(f(\vec{i}))$.
+% \end{definition}
 
-\begin{remark}
-  There is an obvious connection between $\tau$-symmetric functions and
-  generalised quantifiers (or closed classes of structures). Should I include
-  details about this connection? I also feel a lot of dirtiness might be
-  avoidable if we instead recast everything in terms of generalised quantifiers.
-  For one, generalised quantifiers give a natural way of defining a Boolean
-  function for each input universe.
-\end{remark}
+% \begin{remark}
+%   There is an obvious connection between $\tau$-symmetric functions and
+%   generalised quantifiers (or closed classes of structures). Should I include
+%   details about this connection? I also feel a lot of dirtiness might be
+%   avoidable if we instead recast everything in terms of generalised
+%   quantifiers. For one, generalised quantifiers give a natural way of defining
+%   a Boolean function for each input universe.
+% \end{remark}
 
@@
 \begin{definition}[Circuits on Structures]
-  Let $\mathbb{B}$ be a basis of structured functions and $\tau$ a set of
-  relation symbols, we define a \emph{$(\mathbb{B}, \tau)$-circuit} $C_n$
-  computing a $q$-ary query $Q$ is a structure $\langle G, W, \Omega, \Sigma,
+  Let $\mathbb{B}$ be a basis of structured functions and $\tau := (R, \{s_1,
+  \ldots, s_p\}, \nu)$ be a many-sorted vocabulary and let $\vec{n} := (n_{s_1},
+  \ldots , n_{s_p}) \in \mathbb{N}^{S}$, we define a \emph{$(\mathbb{B},
+    \tau)$-circuit} $C_{\vec{n}}$ computing a $q$-ary query $Q$ of type
+  $(s^Q_{1}, \ldots , s^Q_{q})$ is a structure $\langle G, W, \Omega, \Sigma,
   \Lambda, L\rangle$.
@@
     \setlength\itemsep{0mm}
-  \item $G$ is called the set of gates of $C_n$ and $\vert C_n \vert := \vert G
-    \vert$.
+  \item $G$ is called the set of gates of $C_{\vec{n}}$ and $\vert C_{\vec{n}}
+    \vert := \vert G \vert$.
   \item $W \subseteq G \times G$, where $W$ is called the wires of the circuit.
@@
     G: W(h,g)\}$ be the set of children of $g$.
-  \item $\Omega$ is an injective function from $[n]^q$ to $G$. The gates in the
-    image of $\Omega$ are called the output gates. When $q = 0$, $\Omega$ is a
-    constant function mapping to a single output gate.
+  \item $\Omega$ is an injective function from $[n_{i_1}] \times \ldots \times
+    [n_{i_q}]$ to $G$. The gates in the image of $\Omega$ are called the output
+    gates. When $q = 0$, $\Omega$ is a constant function mapping to a single
+    output gate.
   \item $\Sigma$ is a function from $G$ to $\mathbb{B} \uplus \tau \uplus
@@
     \Sigma^{-1} (0) \vert \leq 1$ $\vert \Sigma^{-1} (1) \vert \leq 1$ and the
-    internal gates get mapped into $\mathbb{B}$. Gates mapped to $\tau$ are
-    called relational gates and gates mapped to 1 or 0 are called constant
-    gates.
-  \item $\Lambda$ is a sequence of injective functions $(\Lambda_R)_{R \in
-      \tau}$ where for each $R \in \tau$, $\Lambda_R$ maps each relational gate
-    $g$ with $R = \Sigma (g)$ to the tuple $\Lambda_R (g) \in [n]^r$, where $r$
-    is the arity of the symbol $R$. When no ambiguity arises we write $\Lambda
-    (g)$ for $\Lambda_R (g)$.
-  \item $L$ to each gate a labelling on its children. Let $\tau_g$ and $A_g$ be
-    such that $\Sigma(g)$ is a $(\tau_g, A_g)$-structured function. Then $L(g)$
-    is a surjection from $X^{\tau_g}_{A_g}$ to $H_g$. We call $L(g)$ the
-    \emph{structure-labelling} of $g$.
+    internal gates get mapped into $\mathbb{B}$. Gates mapped to $R$ are called
+    relational gates and gates mapped to 1 or 0 are called constant gates.
+  \item $\Lambda$ is a sequence of injective functions $(\Lambda_{R'})_{R' \in
+      R}$ where for each $R' \in R$ with arity $r$ and type $(s^{R'}_{1},
+    \ldots, s^{R'}_{r})$, $\Lambda_{R'}$ maps each relational gate $g$ with $R'
+    = \Sigma (g)$ to the tuple $\Lambda_{R'} (g) \in [n_{s^{R'}_1}] \times
+    \ldots \times [n_{S^{R'}_r}]$. When no ambiguity arises we write $\Lambda
+    (g)$ for $\Lambda_{R'} (g)$.
+  \item $L$ maps to each internal gate a labelling on its children. Let $g$ be
+    an internal gate. We have that $L(g)$ is a surjection from $\ind (\Sigma (g))$
+    to $H_g$. We call $L(g)$ the \emph{child-labelling} for $g$.
   \end{itemize}
@@
 
-Given some finite $\tau$-structure $\mathcal{A}$ of size $n$ and some bijection
-$\gamma: U \rightarrow [n]$ and let $\gamma \mathcal{A}$ be the structure formed
-by mapping the universe of $\mathcal{A}$ in accordance with $\gamma$. The
-evaluation of some $(\mathbb{B}, \tau)$-circuit $C$ proceeds by recursively
+We write $C_{\vec{n}}$ to emphasise that the circuit accepts input structures
+with sorted-size $\vec{n}$. If $\tau$ is single-sorted vocabulary then we write
+$C_n$ to emphasise that $C_n$ accepts input structures of size $n$. For a gate
+$g \in C_{\vec{n}}$ we abuse notation and define the \emph{type} of $g$, denoted
+by $\type (g)$, to be type of $\Sigma(g)$, and the \emph{index} of $g$, denoted by
+$\ind(g)$, to be the the index for $\Sigma(g)$.
+
+Let $\tau = (\{s_1, \ldots, s_p\}, \{R_1, \ldots , R_t\}, \nu)$. Let
+$\mathcal{A}$ be a many-sorted $\tau$-structure with sorts $U_1, \ldots, U_p$
+and sort-size $\vec{n}$, and let $\gamma: U \rightarrow [n_{s_1}] \sqcup \ldots
+\sqcup [n_{s_p}]$ be a sorted bijection. Let $\gamma \mathcal{A}$ be the
+structure formed by mapping the universe of $\mathcal{A}$ in accordance with
+$\gamma$. The evaluation of some $(\mathbb{B}, \tau)$-circuit $C$ computing a
+q-ary query $Q$ of type $(s^Q_{1}, \ldots , s^Q_{q})$ proceeds by recursively
 evaluating gates. The evaluation of the gate $g$ using $\gamma$ with input
@@
 \item If $g$ is an internal gate labelled by a $(\tau_g, A_g)$-structured
-  function $\Sigma(g)$, let $L^{\gamma}_g: X^{\tau_g}_{A_g} \rightarrow \{0,1\}$
-  be defined by $L^{\gamma}_g(x) = C[\gamma \mathcal{A}](L(g)(x))$. Then $g$
+  function $\Sigma(g)$, let $L^{\gamma}_g: \ind(F) \rightarrow \{0,1\}$ be
+  defined by $L^{\gamma}_g(x) = C[\gamma \mathcal{A}](L(g)(x))$. Then $g$
   evaluates to true iff $\Sigma(g) (L^{\gamma}_g)$.
 \end{enumerate}
-$C$ defines the $q$-ary query $Q \subseteq \mathcal{A}^q$ where $a \in Q$ iff
-$C[\gamma \mathcal{A}](\Omega (\gamma a)) = 1$.
+$C$ defines the $q$-ary query $Q \subseteq U_{s^Q_1} \times \ldots \times
+U_{s^Q_q}$ where $\vec{a} \in Q$ iff $C[\gamma \mathcal{A}](\Omega (\gamma
+\vec{a})) = 1$.
 
@@
 \begin{definition}[Invariant Circuit]
-  Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit, computing some $q$-ary query. We
-  say $C_n$ is \emph{invariant} if for every $\tau$-structure $\mathcal{A}$ of
-  size $n$, $a \in \mathcal{A}^q$, and bijections $\gamma_1, \gamma_2: U
-  \rightarrow [n]$ we have that $C[\gamma_1 \mathcal{A}](\Omega (\gamma_1 a)) =
-  C[\gamma_2 \mathcal{A}](\Omega (\gamma_2 a))$.
+  Let $C_{\vec{n}}$ be a $(\mathbb{B}, \tau)$-circuit, computing some $q$-ary
+  query of type $(s^Q_1, \ldots , s^Q_q)$. We say $C_{\vec{n}}$ is
+  \emph{invariant} if for every $\tau$-structure $\mathcal{A}$ of size
+  $\vec{n}$, $\vec{a} \in U_{i_1} \times \ldots \times U_{i_q}$, and sorted
+  bijections $\gamma_1, \gamma_2: U \rightarrow [n_{s_p}] \sqcup\ldots \sqcup
+  [n_{s_p}]$ we have that $C[\gamma_1 \mathcal{A}](\Omega (\gamma_1 \vec{a})) =
+  C[\gamma_2 \mathcal{A}](\Omega (\gamma_2 \vec{a}))$.
 \end{definition}
 
-This property ensures that a circuit (or a family of circuits) is invariant
-under isomorphism. In other words, the circuit (or family of circuits) decides a
-graph property. The following lemma allows us to recast this notion in terms of
-the language developed in this paper.
-
-\begin{definition}
-  Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit computing a Boolean query. We have
-  that $C_n$ computes a $(\tau, [n])$-structured function $F$. We say $C_n$ is
-  $\tau$-symmetric if $F$ is $\tau$-symmetric.
-\end{definition}
+This property ensures that the function computed by a circuit (or a family of
+circuits) is invariant under isomorphisms on the input structure. In other
+words, the circuit (or family of circuits) decides a property of the structure.
+The following lemma allows us to recast this notion in terms of the language
+developed in this paper.
 
 \begin{lem}
-  Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit. $C_n$ is $\tau$-symmetric iff
-  $C_n$ is invariant.
+  Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit. We have that the function
+  computed by $C_n$ is $\tau$-symmetric iff $C_n$ is invariant.
 \end{lem}
 
-The following definition gives us a way of saying that two structured functions
-with the same signature are equivalent up to a choice of their universe.
+For the sake of simplicity, from now on we assume the that all circuits take in
+structures over a single-sorted vocabulary.
 
@@
   let $C = \langle G, W, \Omega, \Sigma, \Lambda, L\rangle$ be a
-  $(\mathbb{B},\tau)$-circuit computing at $q$-ary query on structures of size
-  $n$. Let $\sigma \in \sym_n$ and $\pi: G \rightarrow G$ be a bijection such
-  that
+  $(\mathbb{B},\tau)$-circuit computing a $q$-ary query on structures of size
+  $n$, and where $\mathbb{B}$ is a bases of sort-symmetric functions. Let
+  $\sigma \in \sym_n$ and $\pi: G \rightarrow G$ be a bijection such that
   \begin{itemize}
@@
     x)$,
-  \item for all gates $g \in G$, let $\Sigma (g) \sim \Sigma (\pi g)$,
+  \item for all gates $g \in G$, let $\Sigma (g) = \Sigma (\pi g)$,
   \item for each relational gate $g \in G$, $\sigma \Lambda (g) = \Lambda (\pi
     g)$, and
-  \item for each internal gate $g$ if $\Sigma (g) \in \mathbb(B)$ then we have
-    that $L(\pi g) \sim \pi \cdot L(g)$.
+  \item for each internal gate $g$ then we have that $L(\pi g)$ and $ \pi \cdot
+    L(g)$ are sort-equivalent.
   \end{itemize}
-
   We call $\pi$ an \emph{automorphism} of $C$, and we say that $\sigma$
@@
 \begin{definition}[Rigidity]
-  Let C be a $(\mathbb{B}, \tau)$-circuit, where $C = \langle G, W, \Omega,
-  \Sigma, \Lambda, L\rangle$. Say that $C$ is rigid if there are no distinct
-  internal gates $g, g' \in G$ such that $\Sigma(g) \sim \Sigma (g')$,
-  $\Omega^{-1}(g) = \Omega^{-1}(g')$, $H_g = H_{g'}$ and $L(g) \sim L'(g)$.
+  Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit, where $C_n = \langle G, W,
+  \Omega, \Sigma, \Lambda, L\rangle$. Say that $C_n$ is \emph{rigid} if there
+  are no distinct internal gates $g, g' \in G$ such that $\Sigma(g) = \Sigma
+  (g')$, $\Omega^{-1}(g) = \Omega^{-1}(g')$, $H_g = H_{g'}$ and $L(g')$ and
+  $L(g)$ are sort-equivalent.
 \end{definition}
@@
 matrix-symmetric functions.
+
 \begin{definition}
-  Let $\mathbb{B}$ be a basis containing all simple unary structured functions
+  Let $\mathbb{B}$ be a basis containing the single-sorted structured functions
   that compute $\land$, $\lor$, $\neg$ and $\maj$ and such that all elements of
   this basis are either matrix-symmetric or simple unary. We call a
-  $(\mathbb{B}, \tau)$-circuit a \emph{matrix-symmetric circuit}.
+  $(\mathbb{B}, \tau)$-circuit a \emph{symmetric matrix-circuit}.
 \end{definition}
@@
   Let the $(\mathbb{B}, \tau)$-circuit $C$ be a matrix-symmetric circuit. Let
-  $\mathbb{B}_m$ be the subset of $\mathbb{B}$ consisting of all those functions
-  that are matrix-symmetric but not symmetric. For any non-empty sets $A_1, A_2$
-  and $r, p \in \mathbb{N}$, where $p$ prime define a $F_{p,r}: \{0,1\}^{A_1
-    \times A_2} \rightarrow \{0,1\}$ such that $f_{p,r}(M) = 1$ iff the matrix
-  $M: A_1 \times B_1 \rightarrow \{0,1\}$ has rank at least $r$ over the field
-  $\mathbb{F}_p$. We call such a function a \emph{bounded-rank function}. If
-  $\mathbb{B}_m$ is equal to the set of all such bounded-rank functions, then we
-  call $C$ a \emph{symmetric circuit with rank gates}.
+  $\mathbb{B}_m \subseteq \mathbb{B}$ consist of all matrix-symmetric functions
+  that are not symmetric. For any non-empty sets $A_1, A_2$ and $r, p \in
+  \mathbb{N}$, where $p$ prime define a $F_{p,r}: \{0,1\}^{A_1 \times A_2}
+  \rightarrow \{0,1\}$ such that $f_{p,r}(M) = 1$ iff the matrix $M: A_1 \times
+  B_1 \rightarrow \{0,1\}$ has rank at least $r$ over the field $\mathbb{F}_p$.
+  We call such a function a \emph{bounded-rank function}. If $\mathbb{B}_m$ is
+  equal to the set of all such bounded-rank functions, then we call $C$ a
+  \emph{symmetric rank-circuit}.
 \end{definition}
@@
   A graph property is decidable by a $P$-uniform family of symmetric circuits
-  with rank gates if, and only if, it is definable by an FPR sentence.
+  with rank gates if, and only if, it is definable by an $\FPR$ sentence.
 \end{thm}
@@
 $\mathbb{B}_{\std} = \{ \neg , \wedge , \lor \}$ and $\mathbb{B}_\maj = \{ \maj
-\} \cup \mathbb{B}$.
+\} \cup \mathbb{B}_{\std}$.
 
-Let $F: \{0,1\}^* \rightarrow \{0,1\}$ be a symmetric Boolean function. Since
-$F$ is symmetric we note that for a fixed size input the output of $F$ is
-entirely determined by the number of 1's in its input. Then let
+Let $F = (F_n: \{0,1\}^n \rightarrow \{0,1\})_{n \in \mathbb{N}}$ be a family of
+symmetric Boolean functions. Recall that for any $n \in \mathbb{N}$, the output
+of $F_n$ is entirely determined by the number of 1's in its input. Then let
 $c_{F}:\mathbb{N} \rightarrow 2^{\mathbb{N}}$ define a function where $c_{F}(n)$
 is the set of all $m \leq n$ such that for all $\vec{x} \in \{ 0,1 \}^n$ with
-$m$ 1's we have $F (\vec{x}) = 1$. Clearly any symmetric Boolean function $F$ is
-entirely determined by $c_{F}$.
+$m$ 1's we have $F_n (\vec{x}) = 1$. Clearly any symmetric Boolean function
+$F_n$ is entirely determined by $c_{F}(n)$, and so $F$ is entirely determined by
+$C_F$.
 
@@
   \label{prop:fuctions-maj}
-  There is a polynomial $p(k)$ such that for any symmetric function $F$ and a
-  given $k \in \mathbb{N}$ there is a circuit $C_k$ on $k$ inputs over the basis
-  $\mathbb{B}_\maj$ which is symmetric, constant depth and with width bounded by
-  $p(k)$.
+  Let $F = (F_n: \{0,1\}^n \rightarrow \{0,1\})_{n \in \mathbb{N}}$ be a family
+  of symmetric functions. There exists a family of Boolean circuits $(C_n)_{n
+    \in \mathbb{N}}$ defined over $\mathbb{B}_\maj$ computing $F$. Moreover,
+  $(C_n)_{n \in \nats}$ has depth at most $5$ and width at most $2n+2$ and size
+  at most $8n + 3$.
 \end{prop}
@@
 \begin{proof}
-  We define the circuit $C_k$ for inputs $\vec{x} = ( x_1, \ldots, x_k )$.
+  We define the circuit $C_n$ with $n$ input gates denoted by $x_1, \ldots, x_k$
+  by successively adding gates. For $a \in \mathbb{N}$ we add an `and' gate
+  $\countgate_a$, and a number of `majority' and `not' gates, wiring them up as
+  follows:
+\[
+  \countgate_a = \begin{cases} \land ( \maj  ( x_1, \ldots, x_n, \underbrace {0, \ldots,
+        0}_{2a - n} ), \neg ( \maj (x_1, \ldots , x_n, \underbrace{0, \ldots,
+        0}_{2a - n + 2} ) )) &  a \geq \frac{n}{2} \\
+     \land ( \maj ( x_1, \ldots, x_n, \underbrace {1, \ldots, 1}_{n -
+           2a} ),  \neg (
+      \maj ( x_1, \ldots , x_n, \underbrace{1, \ldots, 1}_{n - 2a -2}
+      ) )) & a <
+      \frac{n}{2}.
+    \end{cases}
+  \]
 
-  For $a \in \mathbb{N}$ we define a gate $\countgate_a$ by
-  \begin{align*}
-    \countgate_a = \begin{cases} \maj (x_1, \ldots, x_k, \underbrace {0, \ldots,
-        0}_{2a - k}) \land \neg \maj (x_1, \ldots , x_k, \underbrace{0, \ldots,
-        0}_{2a - k + 2}) &  a \geq \frac{k}{2} \\
-      \maj (x_1, \ldots, x_k, \underbrace {1, \ldots, 1}_{x - 2a}) \land \neg
-      \maj (x_1, \ldots , x_k, \underbrace{1, \ldots, 1}_{k - 2a -2}) & a <
-      \frac{k}{2}.
-    \end{cases}
-  \end{align*}
-  Then let $g = \bigvee_{a \in c_{F_i}(k)}\countgate_a$ and let $C_{k}$ be the
-  circuit with input gates labeled by $\vec{x}$ and output gate $g$.
+  Clearly $\vert c_F(n) \vert \leq n$, for each $a \in c_F(n)$ we have added
+  four gates, so thus far the circuit's width is at most $2n + 2$ (2 extra for
+  the possible inclusion of constant gates) and depth at most $4$. Now add to
+  $C_n$ a `or' gate $g$ and connect the output of $\countgate_a$ to the input of
+  $g$ for each $a \in c_F(n)$. Mark $g$ as the output gate for $C_n$.
 
-  t is easy to see that $C_k$ is constant depth and it's width is a polynomial
-  in $k$. We have that in each layer of $C_{g'}$ each gate is connected to all
-  gates in the previous layer, and as such the circuit is symmetric.
+  It is easy to see that $C_n$ has depth at most $5$, width at most by $2n + 2$
+  and size at most $1 + 4(2n) + 2 = 8n+3$. We have that in each layer of $C_{g'}$
+  each gate is connected to all gates in the previous layer, and as such the
+  circuit is symmetric.
 \end{proof}
@@
 \begin{thm}
-  Let $F = \{F_i : i \in I \}$ be a family of symmetric Boolean functions where
-  $F_i: \{0,1\}^* \rightarrow \{ 0,1 \}$.
+  Let $\mathcal{F} = \{F_i : i \in I \}$, where $F_i$ is a family of symmetric
+  Boolean functions.
 
   Let $(C_n)_{n \in \mathbb{N}}$ be family of symmetric circuits over the
-  Boolean basis $\mathbb{B} \cup F$, where $C_n$ is a circuit on structures of
-  size $n$, and the size of each circuit in the family is bounded by some
-  function $f(n)$. Then there exists a polynomial $q(n)$ and a family of
+  Boolean basis $\mathbb{B}_{\std} \cup (\bigcup_{i \in I} F_i)$, where $C_n$ is
+  a circuit on structures of size $n$, and the size of each circuit in the
+  family is bounded by some function $f(n)$. Then there exists a family of
   symmetric circuits $(C_n')_{n \in \mathbb{N}}$ over $\mathbb{B}_\maj$, where
   $C_n'$ is a circuit on structures of size $n$ and $\vert C_n' \vert \leq
-  q(f(n))$.
+  (8f(n) + 3) f(n))$.
 \end{thm}
@@
 \begin{proof}
-  From $C_n$ we construct $C_n'$ in the obvious way. For each gate $g \in C_n$
-  of type $F_i$ we have a symmetric circuit $C_g$ from Proposition
-  \ref{prop:function-maj} that computes the same function as $g$. Then let
-  $C_n'$ be $C_n$ but with each gate $g$ replaced by $C_g$. It is easy to see
-  that $C_n'$ is symmetric. We also have that each gate $g$ must have at most
-  $f(n)$ inputs, and the size of $C_g$ is bounded by $p(f(n))$. Thus the size of
-  $C_n'$ is bounded by $f(n)p(f(n))$.
+  From $C_n$ we construct $C_n'$ as follows. For each gate $g \in C_n$ of
+  labelled by a member of $F_i$ we have a symmetric circuit $C_g$ from
+  Proposition \ref{prop:function-maj} that computes the same function as $g$.
+  Then let $C_n'$ be $C_n$ but with each gate $g$ replaced by $C_g$. It is easy
+  to see that $C_n'$ is symmetric. We also have that each gate $g$ must have at
+  most $f(n)$ inputs, and so the size of $C_g$ is bounded by $8f(n) + 3$. Thus
+  the size of $C_n'$ is bounded by $(8f(n)+3) f(n)$.
 \end{proof}
 
-This result, combined with the main result of this paper, gives us that
-symmetric circuits with rank are a strictly more powerful model than any circuit
-model defined over a basis of symmetric functions.
+This result gives us that for any family of circuits over an arbitrary basis of
+symmetric functions we can can construct another circuit family computing the
+same function over the majority basis without a blowup in size. As such, we know
+that we cannot extend the power of the symmetric circuits studied by Anderson
+and Dawar \cite{AndersonD17} by simply considering alternative bases of
+symmetric functions. This result, combined with the main result of this paper,
+gives us that symmetric circuits with rank are a strictly more powerful model
+than any circuit model defined over a basis of symmetric functions.
 
-% \section{Circuits to FPR}
-
-% In this section I discuss how to determine the rank a matrix labelling at some
-% gate $g$. This is a rough copy written for the purpose of discussion. In this
-% section we fix some circuit $C_n$ and some rank gate $g$ in $C_n$ with a set
-% of children $H$ and matrix labelling $L: [a] \times [b] \rightarrow H$ (which
-% we assume WLOG is a bijection).
 \end{document}

### 2017-08-21 sections/symmetric-circuits.tex
I have realised that my generalisation of symmetry is flawed and will need an overhaul. However, I want to keep a copy so I'm updating git.
This version is the told one where we are just speaking of $\mathcal{D}$-invarient functions.

@@
 % Note: include circuits in background
-Circuits are a well-studied model in complexity theory, and more recently they
-have been studied in the context of finite model theory. However, there are some
-subtleties in the definition and evaluation of circuits which must be considered
-carefully and have important implications for the notion of a symmetric circuit
-studied in this paper. Let $C$ be a Boolean circuit $g$ be an internal gate
-labelled by some function $f_g: \{0,1\}^{A} \rightarrow \{0,1\}$, for some index
-set $A$ with $\vert A \vert = \vert H_g \vert$. Formally, evaluating $g$
-requires a (usually bijective) indexing function $f_i: A \mapsto H_g$, which
-organises the inputs of $g$ into an appropriate sequence. The evaluation of $g$
-is then given by $C[\vec{x}](g) = f_g (a \mapsto C[\vec{x}](f_i(a)))$. As such
-the evaluation of a gate in a circuit may depend on how the inputs to the gate
-are indexed.
+Boolean circuits have long been as an alternative model from which to study
+algorithmic complexity. A circuit is evaluated for some ordered binary input
+sequence by recursively evaluating each gate in the circuit, starting from the
+input gates. Suppose then we are evaluating some gate $g$ in a circuit $C$. The
+procedure involves taking the input string formed by evaluating all gates input
+to $g$ and applying the Boolean function that labels $g$ to that string. But
+this process assumes an externally-imposed ordering on the gates input to $g$;
+an assumption common in most parts of complexity theory, where the encoding of
+structures for computation induces such orderings, but not in finite model
+theory.
 
-In most contexts in complexity theory, circuits may be taken to be implicitly
-ordered objects and so this indexing function can be defined as taking the $i$th
-element of $A$ to the $i$th element of $H_g$. However, in general this renders
-the evaluation of a circuit for a given input a property both of the circuit and
-an arbitrary order. In order to address this problem this problem many authors
-only define circuits over Boolean bases of symmetric functions (e.g. the
-standard basis or the majority basis). In this case the evaluation of a gate is
-independent of the choice of indexing function.
+Circuit models have also been studied in finite model theory as a means for
+characterising the expressive power of logics. In particular, research has
+focused on symmetric circuits defined over bases of symmetric Boolean functions
+(see \cite{}). The fact that the basis consist of only symmetric functions is a
+crucial requirement, ensuring that the evaluation of a gate does not depend on
+the order.
 
-However, in this paper we require gates labelled by Boolean rank functions, i.e.
-a function that takes in a Boolean sequence indexed by `row' and `column' sets,
-outputs 1 iff that matrix, when interpreted as having entries in $\mathbb{F}_p$,
-has rank at least $r$. These rank functions clearly depend on how the input
-sequence is labelled, and so are not symmetric. However, it is worth noting that
-while such rank functions may be symmetric, they are symmetric in the weaker
-sense of being constant under permutations on the rows and columns of the input
-matrix.
+In this section we extend the circuit model so as to allow us to define
+symmetric circuits over a broader basis of functions. We introduce the notion of
+a structured function , i.e. a Boolean function whose input is indexed in
+accordance with some many-sorted structure. This allows us to characterise many
+natural symmetry properties of structured functions in terms of equally natural
+symmetry properties of many-sorted structures. We use this to derive a general
+symmetry conditions on structured functions and a symmetric circuit model whose
+basis elements are symmetric structured functions.
 
-Motivated by the desire to study circuits with gates that compute rank, We
-develop a general framework for circuits that allows gates to be labelled by
-Boolean functions of the form $F: \{0,1\}^{X} \rightarrow \{0, 1\}$, where the
-labelling $X$ is the universe of a many-sorted structure over some vocabulary
-$\tau$. The Moreover, we generalise the notion of a circuit for structures (see
-Anderson and Dawar \cite{AndersonD17}), incorporate an appropriate labelling for
-the inputs of each gate and allowing for a Boolean basis including non-symmetric
-functions. Furthermore, the vocabulary $\tau$ will allow us to impose natural
-symmetry conditions on $F$, and so allowing us to develop a useful notion of a
-symmetric circuit.
+% We incorporate this labelling in the circuit model by including for each gate
+% $g$ labelled by a structured function $$an indexing on its children that
+% matches the index for the function that labels $g$. We allow these circuits to
+% be defined over bases of structured functions with this more general symmetry
+% condition
 
-We also prove that no family symmetric functions defined over a basis of
-symmetric functions can improve on the expressive power of the circuit model of
-Anderson and Dawar \cite{AndersonD17}. Together with the main theorem of this
-paper this implies that these more general symmetric circuits are strictly more
-powerful.
+% In order then to include a gate computing rank in our symmetric circuit model
+% we need to rec We are interested in circuit with gates that can compute rank
+% and so, since rank is not a symmetric function, we develop a symmetric circuit
+% model capable of incorporating non-symmetric functions in its basis. Moreover,
+% we note that
+
+% In particular, we are interested in Boolean functions that compute rank, i.e.
+% functions that take in a binary matrix and compute the rank of that matrix
+% over some prime field and compare the result with some threshold. But clearly
+% this rank function is not symmetric. Furthermore, its evaluation depends on
+% how the input set is labelled to form a matrix.
+
+% In this section we develop the
+
+% allowing us to develop natural symmetry conditions on the functions in terms
+% of symmetry conditions on the structure. This indexing allows us to generalise
+% the notion of a symmetric function by relativising the symmetry condition in
+% accord with the structure on the input string. Incorporating this indexing
+% into the circuit and
+
+% ore recently, they have played a role in finite model theory, with many
+% authors (e.g. ) studying circuit models that take in some representation of a
+% finite algebraic structure and which obey certain natural symmetry conditions.
+% However, there are some subtleties in the definition and evaluation of
+% circuits which must be considered carefully and have important implications
+% for the notion of a symmetric circuit studied in this paper. Let $C$ be a
+% Boolean circuit $g$ be an internal gate labelled by some function $f_g:
+% \{0,1\}^{A} \rightarrow \{0,1\}$, for some index set $A$ with $\vert A \vert =
+% \vert H_g \vert$. Formally, evaluating $g$ requires a (usually bijective)
+% indexing function $f_i: A \mapsto H_g$, which organises the inputs of $g$ into
+% an appropriate sequence. The evaluation of $g$ is then given by $C[\vec{x}](g)
+% = f_g (a \mapsto C[\vec{x}](f_i(a)))$. As such the evaluation of a gate in a
+% circuit may depend on how the inputs to the gate are indexed.
+
+% In most contexts in complexity theory, circuits may be taken to be implicitly
+% ordered objects and so this indexing function can be defined as taking the
+% $i$th element of $A$ to the $i$th element of $H_g$. However, in general this
+% renders the evaluation of a circuit for a given input a property both of the
+% circuit and an arbitrary order. In order to address this problem this problem
+% many authors only define circuits over Boolean bases of symmetric functions
+% (e.g. the standard basis or the majority basis). In this case the evaluation
+% of a gate is independent of the choice of indexing function.
+
+% However, in this paper we require gates labelled by Boolean rank functions,
+% i.e. a function that takes in a Boolean sequence indexed by `row' and `column'
+% sets, outputs 1 iff that matrix, when interpreted as having entries in
+% $\mathbb{F}_p$, has rank at least $r$. These rank functions clearly depend on
+% how the input sequence is labelled, and so are not symmetric. However, it is
+% worth noting that while such rank functions may be symmetric, they are
+% symmetric in the weaker sense of being constant under permutations on the rows
+% and columns of the input matrix.
+
+% Motivated by the desire to study circuits with gates that compute rank, We
+% develop a general framework for circuits that allows gates to be labelled by
+% Boolean functions of the form $F: \{0,1\}^{X} \rightarrow \{0, 1\}$, where the
+% labelling $X$ is the universe of a many-sorted structure over some vocabulary
+% $\tau$. The Moreover, we generalise the notion of a circuit for structures
+% (see Anderson and Dawar \cite{AndersonD17}), incorporate an appropriate
+% labelling for the inputs of each gate and allowing for a Boolean basis
+% including non-symmetric functions. Furthermore, the vocabulary $\tau$ will
+% allow us to impose natural symmetry conditions on $F$, and so allowing us to
+% develop a useful notion of a symmetric circuit.
+
+% We also prove that no family symmetric functions defined over a basis of
+% symmetric functions can improve on the expressive power of the circuit model
+% of Anderson and Dawar \cite{AndersonD17}. Together with the main theorem of
+% this paper this implies that these more general symmetric circuits are
+% strictly more powerful
 
@@
 \subsection{Structured Functions and Symmetry}
+Before we begin this section let us review Boolean circuits and a few useful
+symmetry conditions placed on these circuits. Let $X$ be a finite set and $F:
+\{0,1\}^{X} \rightarrow \{0,1\}$ be a Boolean function. We call $X$ the
+\emph{index} of $F$, and denote it by $\ind(F)$. It is often the case that the
+index $X$ is in some sense structured, but let us first consider the case where
+$X$ is an unstructured set. In this case the only natural symmetry condition to
+consider is where $F$ is invariant under the action of $\sym_n$, i.e. $F$ is a
+symmetric function. Suppose instead $X$ consists of all two element subsets of
+the set $V$. Here we can think of $X$ as representing all potential edges in a
+graph, and $\vec{x} \in \{0,1\}^X$ as defining a graph. It is natural then to
+consider the case where $F$ determines a property of the graph, i.e. where $F$
+is invariant under the action of $\sym_V$ on the input (i.e renaming of the
+vertices). We call such a function \emph{graph-invariant}. Suppose that $X := A
+\times B$ for two non-empty sets $A$ and $B$. Here we can think of $\vec{x} \in
+\{0,1\}^X$ as an (unordered) matrix, and we can consider the case where $F$ is
+invariant under the action of $\sym_A \times \sym_B$. In this case we say $F$ is
+\emph{matrix-invariant}. Notice that in each of these cases the symmetry
+condition of interest on the function was related to the structure of the index
+set.
+
+In the rest of this subsection we develop the notion of structured function, a
+Boolean function whose input is structured in accord with some structure and
+whose natural symmetry conditions follow from similar conditions on the
+structure.
+
+% $X:= {n}\choose{2}$, for some $n$, we can think of $F$ as taking in some $n$
+% vertex graph, and we should like $F$ to respect permutations on the graph. In
+% this case we insist that $F$ is a \emph{graph symmetric} function, for all $$
+% where we can think of $F$ as taking in a graph with $n$ vertices, where $X:=
+% {n}\choose{2}$ as indexing a graph with $n$ vertices
+
+% The set $X$ is often used just to provide an ordering, and so $F$ just takes
+% in a binary $\vert X \vert$-tuple. While in general the order of the input
+% sequence matters, it is common to consider the case where $F$ is a
+% \emph{symmetric} Boolean function, i.e. for all $\sigma \in \sym_{X}$,
+% $\vec{x} \in \{0,1\}^{X}$, $F(\vec{x}\cdot \sigma) = \vec{x}$. In this case
+% the output of the function is independent of the ordering on the input tuple.
+% Indeed, many natural Boolean functions (e.g. `and', `or', `not', `majority',
+% etc.) are symmetric functions. One of the benefits of considering symmetric
+% functions
+
 Let $\tau = (R, S, \nu)$ be a many-sorted, relational signature, with $R = \{R_1
@@
 \ldots , a^i_{r_i)})$, where $r_i = \arty(R_i)$ and $a^i_q \in S$ for all $q \in
-[r_i]$. For each $s \in S$ let $A_s$ be a non-empty set, and let $A := A_{1}
-\sqcup \ldots \sqcup A_{s} = \{(a,s) : a \in A_s\}$. Let
-\[
-  \ind (A, \tau) := A_{a^1_1} \times \ldots \times A_{a^1_{r_1}} \times \ldots
-  \times A_{a^t_1} \times A_{a^t_{r_t}},
-\]. We call $\ind (A, \tau)$ the \emph{index defined by} $(A, \tau)$.
+[r_i]$. Let $\mathcal{D}$ be a $\tau$-structure, with the universe $D = D_1
+\uplus \ldots \uplus D_s = \{(i,d) : d \in D_i\}$.
 
-% It is worth noting that there is a natural bijection $P$ that maps
-% $\tau$-structures with universe $A$ to subsets of $\Ind(A, \tau)$, taking each
-% $\tau$-structure $\mathcal{A}$ to the set $\{(\vec{X}_1, \ldots , \vec{X}_t) :
-% \exists i \in [t] \(\vec{X_i} \in R^{\mathcal{A}}_i \) \}$.
+Let the \emph{index-domain} of $\mathcal{D}$ be $\rdom {\mathcal{D}} = \{(i, j)
+:= i \in [r_j], R_j \text{ a relation in $\tau$} \}$. Let the \emph{index
+  defined by} $\mathcal{D}$ be the set of all functions $f: \rdom(\mathcal{D})
+\rightarrow D$ such that for all $R_j \in R$ and $i \in [r_j]$, $f(i, j) \in
+A_{a^{j}_i}$. We abuse notation and denote the index defined by
+$\ind(\mathcal{D})$. We note that, since the set of relation symbols and sort
+symbols are ordered, we can also think of each $f \in \ind(\mathcal{D})$ as a
+tuple in $D_{a^1_1} \times \ldots \times D_{a^1_{r_1}} \times \ldots \times
+D_{a^t_1} \times D_{a^t_{r_t}}$. We will use these tuples in order to index the
+inputs to a Boolean function.
 
-For the remainder of the section let $X := \ind (A, \tau)$. Let $G \leq
-\sym_{X}$, there is a natural action of $G$ on $X$. There is also a natural
-action of $\sym_{A_1} \times \ldots \times \sym_{A_s}$ on $X$ and a subgroup
-$G'$ of $\sym_X$ corresponding to the same action. We identify these two groups.
-
-Furthermore, we can defined an action of $G$ on functions of the form $f: X
-\rightarrow H$, for any set $H$, given by $\sigma \cdot f(x) = f(\sigma \cdot
-x)$ for all $x \in X$. If $H = \{0,1\}$ we say that $f$ is a \emph{binary
-  sequence indexed by $X$}. If $H$ is surjective, we say that \emph{$f$ indexes
-  $H$ by $X$} or \emph{$f$ indexes $H$ by $(A,\tau)$}.
+For the remainder of the section fix a $\tau$-structure $\mathcal{D}$ and let $X
+:= \ind (\mathcal{D})$. Let $G \leq \sym_{X}$. We note that there is a natural
+action of $G$ on $X$. Furthermore, we can define an action of $G$ on functions
+of the form $f: X \rightarrow H$, for any set $H$, given by $\sigma \cdot f(x) =
+f(\sigma \cdot x)$ for all $x \in X$. If $H = \{0,1\}$ we say that $f$ is a
+\emph{binary sequence indexed by $X$}. If $H$ is surjective, we say that
+\emph{$f$ indexes $H$ by $X$} or \emph{$f$ indexes $H$ by $\mathcal{D}$}. We
+note that $\aut(\mathcal{D})$ and $\iso(\mathcal{D})$ can be identified with
+subgroups of $\sym_X$.
 
@@
 such that $f(x) = f(\sigma \cdot x)$ for all $x \in X$. We say $f$ and $g$ are
-\emph{sort-equivalent} if they are $\sym_{A_1} \times \ldots
-\sym_{A_p}$-equivalent.
+\emph{isomorphism-equivalent} if they are $\iso(\mathcal{D}$-equivalent. We say
+that $f$ and $g$ are \emph{automorphism-equivalent} if they are $
+\aut(\mathcal{D})$-equivalent. We say that $f$ and $g$ are
+\emph{sort-equivalent} in the special case where every relation in $\mathcal{D}$
+contains all possible tuples and $f$ and $g$ are automorphism-equivalent.
 
 We call a function of the form $F:\{0,1\}^{X} \rightarrow \{0,1\}$ a
-\emph{$(\tau, A)$-structured function}. We call $(\tau, A)$ the \emph{type} of
-$F$, $\tau$ the \emph{signature of $F$} and $A$ \emph{the universe of $F$}. We
-also use $\ind(F)$ to abbreviate $\ind (\type (F))$.Call $F$ a \emph{structured
-  function} if it is a $(\tau, A)$-structured function for some appropriate
-$\tau$ and $A$.
+\emph{$\mathcal{D}$-structured function}. We note that $\ind(F) =
+\ind(\mathcal{D})$, justifying our above choice of notation. We also say
+\emph{the vocabulary of $F$} and \emph{the universe of $F$} to refer to the
+vocabulary and universe of $\mathcal{D}$.
 
@@
 These structured functions give us a general framework for indexing the input to
-functions. Moreover, the structure on these index sets allows us to develop a
-natural notion of symmetry particular to the indexing used by the function. Let
-$F$ be a $(\tau, A)$-structured function. We say $F$ is \emph{$G$-invariant} if
-for all $G$-equivalent $\vec{x},\vec{y} \in \{0,1\}^{X}$, $F(\vec{x}) =
-F(\vec{y})$. We say $F$ is \emph{sort-invariant} if it is $(\tau, \sym_{A_{1}}
-\times \ldots \times \sym_{A_{s}})$-invariant. If $\tau = (\{R\}, [2], \nu)$,
-with $\nu (R) = (1, 2)$ and $F$ is sort-invariant then we say $F$ is
-\emph{matrix-invariant}.
+functions while also providing us with a natural set of groups from which to
+develop symmetry conditions for Boolean functions. We now introduce some of
+these conditions. Let $F$ be a $\mathcal{D}$-structured function. We say $F$ is
+\emph{$G$-invariant} if it constant on $G$-equivalent input vectors, i.e. for
+all $G$-equivalent $\vec{x},\vec{y} \in \{0,1\}^{X}$, $F(\vec{x}) = F(\vec{y})$.
+Similarly, we say $F$ is \emph{automorphism-invariant} if it is constant on
+automorphism-equivalent input vectors and \emph{isomorphism-invariant} if it is
+constant on isomorphism-equivalent input vectors. If all the relations in
+$\mathcal{D}$ contain all possible tuples, and $F$ is automorphism-invariant,
+then we say that $F$ is \emph{sort-invariant}. If the vocabulary of $F$ has two
+sorts $s_1, s_2$ and one binary relation $R$ with type $(s_1, s_2)$ and $F$ is
+sort-invariant, then we say $F$ is \emph{matrix-invariant}.
+
+Notice that if $\tau$ is the empty vocabulary and $\mathcal{D}$ is a
+$\tau$-structure, i.e. $\mathcal{D}$ is a pure set, then any
+$\mathcal{D}$-structured function $F$ is automorphism-invariant (or
+isomorphism-invariant) if, and only if, $F$ is symmetric. Also, if $\mathcal{D}$
+is a graph, then $F$ is isomorphism invariant if, and only if, $F$ is
+graph-invariant (except with a slight alteration, here $F$ takes in the edge
+relation rather than a binary string indexed by two element sets of vertices).
+Similarly, $F$ is matrix invariant (as a structured function) if, and only if,
+it is matrix-invariant in the sense defined right at the beginning of this
+subsection. In each of these cases choosing an appropriate structure leads to an
+appropriate index and an appropriate notion of symmetry. In this way structured
+functions generalise the notion of a symmetric function and allow us to capture
+a broad range of structure-specific symmetry conditions in a single definition.
+In the next section we will show how to define a circuit and a symmetric circuit
+using bases of structured functions.
 
@@
 % single unary relation, we call $F$ \emph{unary-relational}.
-We have developed this more general notion of symmetry for Boolean functions
-that naturally takes into account the structure on the input sequence. The
-following lemma shows that symmetry is just the requirement that the function be
-invariant under permutations of its input, irrespective of structure.
-
-\begin{lem}
-  Let $F$ be a $(\tau, A)$-structured function. $F$ is a symmetric function if
-  and only if $F$ is $\sym_A$-invariant.
-\end{lem}
 
@@
 \subsection{Symmetric Circuits}
-Having developed the notion of a function that accepts input structured in
-accordance with some vocabulary, we now develop a circuit model which
-incorporates this structure on the inputs of a gate. We use this general
-framework to define the notion of a matrix-symmetric circuit, a circuit with
-gates labelled by matrix-symmetric Boolean functions, and finally we develop the
-notion of a matrix-symmetric circuit with rank.
+We define a circuit over a basis of structured functions that are not
+necessarily symmetric. As such, the circuit must include for each gate $g$ an
+index on its children corresponding to the index of the function labelling $g$.
+
+% Having developed the notion of a function that accepts input structured in
+% accordance with some vocabulary, we now develop a circuit model which
+% incorporates this structure on the inputs of a gate. We use this general
+% framework to define the notion of a matrix-symmetric circuit, a circuit with
+% gates labelled by matrix-symmetric Boolean functions, and finally we develop
+% the notion of a matrix-symmetric circuit with rank.
 
@@
 \begin{definition}[Circuits on Structures]
-  Let $\mathbb{B}$ be a basis of structured functions and $\tau := (R, \{s_1,
-  \ldots, s_p\}, \nu)$ be a many-sorted vocabulary and let $\vec{n} := (n_{s_1},
-  \ldots , n_{s_p}) \in \mathbb{N}^{S}$, we define a \emph{$(\mathbb{B},
-    \tau)$-circuit} $C_{\vec{n}}$ computing a $q$-ary query $Q$ of type
-  $(s^Q_{1}, \ldots , s^Q_{q})$ is a structure $\langle G, W, \Omega, \Sigma,
-  \Lambda, L\rangle$.
+  Let $\mathbb{B}$ be a basis and $\tau$ be a relational vocabulary, we define a
+  \emph{$(\mathbb{B}, \tau)$-circuit} $C_n$ computing a $q$-ary query $Q$ as a
+  structure $\langle G, \Omega, \Sigma, \Lambda, L \rangle$.
   \begin{itemize}
     \setlength\itemsep{0mm}
-  \item $G$ is called the set of gates of $C_{\vec{n}}$ and $\vert C_{\vec{n}}
-    \vert := \vert G \vert$.
-  \item $W \subseteq G \times G$, where $W$ is called the wires of the circuit.
-    $(G,W)$ must be a directed acyclic graph. For $g \in G$ we $H_g := \{ h \in
-    G: W(h,g)\}$ be the set of children of $g$.
-  \item $\Omega$ is an injective function from $[n_{i_1}] \times \ldots \times
-    [n_{i_q}]$ to $G$. The gates in the image of $\Omega$ are called the output
-    gates. When $q = 0$, $\Omega$ is a constant function mapping to a single
-    output gate.
+  \item $G$ is called the set of gates of $C_n$ and $\vert C_n \vert := \vert G
+    \vert$.
+  \item $\Omega$ is an injective function from $[n]^q$ to $G$. The gates in the
+    image of $\Omega$ are called the output gates. When $q = 0$, $\Omega$ is a
+    constant function mapping to a single output gate.
   \item $\Sigma$ is a function from $G$ to $\mathbb{B} \uplus \tau \uplus
-    \{0,1\} $ which maps input gates to $\tau \uplus \{0,1\}$ and where $\vert
-    \Sigma^{-1} (0) \vert \leq 1$ $\vert \Sigma^{-1} (1) \vert \leq 1$ and the
-    internal gates get mapped into $\mathbb{B}$. Gates mapped to $R$ are called
-    relational gates and gates mapped to 1 or 0 are called constant gates.
-  \item $\Lambda$ is a sequence of injective functions $(\Lambda_{R'})_{R' \in
-      R}$ where for each $R' \in R$ with arity $r$ and type $(s^{R'}_{1},
-    \ldots, s^{R'}_{r})$, $\Lambda_{R'}$ maps each relational gate $g$ with $R'
-    = \Sigma (g)$ to the tuple $\Lambda_{R'} (g) \in [n_{s^{R'}_1}] \times
-    \ldots \times [n_{S^{R'}_r}]$. When no ambiguity arises we write $\Lambda
-    (g)$ for $\Lambda_{R'} (g)$.
-  \item $L$ maps to each internal gate a labelling on its children. Let $g$ be
-    an internal gate. We have that $L(g)$ is a surjection from $\ind (\Sigma (g))$
-    to $H_g$. We call $L(g)$ the \emph{child-labelling} for $g$.
+    \{0,1\} $ such that $\vert \Sigma^{-1} (0) \vert \leq 1$ $\vert \Sigma^{-1}
+    (1) \vert \leq 1$. Those gates mapped to $\tau \uplus \{0,1\}$ are called
+    input gates, with those mapped to $\tau$ called relational gates and those
+    mapped $\{0,1\}$ called constant gates. Those gates mapped to $\mathbb{B}$
+    are called internal gates.
+  \item $\Lambda$ is a sequence of injective functions $(\Lambda_{R_i})_{R_i \in
+      R}$ such that $\Lambda_{R_i}$ maps each relational gate $g$ with $R_i =
+    \Sigma (g)$ to the tuple $\Lambda_{R_i} (g) \in [n]^{r}$. When no ambiguity
+    arises we write $\Lambda (g)$ for $\Lambda_{R_i} (g)$.
+  \item $L$ associates with each internal gate $g$ a function $L(g):
+    \dom(\Sigma(g)) \rightarrow G$ such that if we define a relation $W
+    \subseteq G^{2}$ by $W(h_1,h_2)$ iff $h_2$ is an internal gate and $h_1$ is
+    in the image of $L(h_2)$, then $(G, W)$ is a directed acyclic graph.
   \end{itemize}
@@
 
-We write $C_{\vec{n}}$ to emphasise that the circuit accepts input structures
-with sorted-size $\vec{n}$. If $\tau$ is single-sorted vocabulary then we write
-$C_n$ to emphasise that $C_n$ accepts input structures of size $n$. For a gate
-$g \in C_{\vec{n}}$ we abuse notation and define the \emph{type} of $g$, denoted
-by $\type (g)$, to be type of $\Sigma(g)$, and the \emph{index} of $g$, denoted by
-$\ind(g)$, to be the the index for $\Sigma(g)$.
+% \begin{definition}[Circuits on Structures]
+%   Let $\mathbb{B}$ be a basis of structured functions and $\tau := (R, \{s_1,
+%   \ldots, s_p\}, \nu)$ be a many-sorted vocabulary and let $\vec{n} :=
+%   (n_{s_1}, \ldots , n_{s_p}) \in \mathbb{N}^{S}$, we define a
+%   \emph{$(\mathbb{B}, \tau)$-circuit} $C_{\vec{n}}$ computing a $q$-ary query
+%   $Q$ of type $(s^Q_{1}, \ldots , s^Q_{q})$ is a structure $\langle G, W,
+%   \Omega, \Sigma, \Lambda, L\rangle$.
+%   \begin{itemize}
+%     \setlength\itemsep{0mm}
+%   \item $G$ is called the set of gates of $C_{\vec{n}}$ and $\vert C_{\vec{n}}
+%     \vert := \vert G \vert$.
+%   \item $W \subseteq G \times G$, where $W$ is called the wires of the
+%     circuit. $(G,W)$ must be a directed acyclic graph. For $g \in G$ we $H_g
+%     := \{ h \in G: W(h,g)\}$ be the set of children of $g$.
+%   \item $\Omega$ is an injective function from $[n_{i_1}] \times \ldots \times
+%     [n_{i_q}]$ to $G$. The gates in the image of $\Omega$ are called the
+%     output gates. When $q = 0$, $\Omega$ is a constant function mapping to a
+%     single output gate.
+%   \item $\Sigma$ is a function from $G$ to $\mathbb{B} \uplus \tau \uplus
+%     \{0,1\} $ which maps input gates to $\tau \uplus \{0,1\}$ and where $\vert
+%     \Sigma^{-1} (0) \vert \leq 1$ $\vert \Sigma^{-1} (1) \vert \leq 1$ and the
+%     internal gates get mapped into $\mathbb{B}$. Gates mapped to $R$ are
+%     called relational gates and gates mapped to 1 or 0 are called constant
+%     gates.
+%   \item $\Lambda$ is a sequence of injective functions $(\Lambda_{R'})_{R' \in
+%     R}$ where for each $R' \in R$ with arity $r$ and type $(s^{R'}_{1},
+%     \ldots, s^{R'}_{r})$, $\Lambda_{R'}$ maps each relational gate $g$ with
+%     $R' = \Sigma (g)$ to the tuple $\Lambda_{R'} (g) \in [n_{s^{R'}_1}] \times
+%     \ldots \times [n_{S^{R'}_r}]$. When no ambiguity arises we write $\Lambda
+%     (g)$ for $\Lambda_{R'} (g)$.
+%   \item $L$ maps to each internal gate a labelling on its children. Let $g$ be
+%     an internal gate. We have that $L(g)$ is a surjection from $\ind (\Sigma
+%     (g))$ to $H_g$. We call $L(g)$ the \emph{child-labelling} for $g$.
+%   \end{itemize}
+% \end{definition}
 
-Let $\tau = (\{s_1, \ldots, s_p\}, \{R_1, \ldots , R_t\}, \nu)$. Let
-$\mathcal{A}$ be a many-sorted $\tau$-structure with sorts $U_1, \ldots, U_p$
-and sort-size $\vec{n}$, and let $\gamma: U \rightarrow [n_{s_1}] \sqcup \ldots
-\sqcup [n_{s_p}]$ be a sorted bijection. Let $\gamma \mathcal{A}$ be the
-structure formed by mapping the universe of $\mathcal{A}$ in accordance with
+Let $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
+\tau)$-circuit. The $n$ here denotes that $C_n$ accepts structures of size $n$.
+For a gate $g \in C_n$, we define the \emph{index} of $g$, denoted by $\ind(g)$,
+as $\ind(\Sigma(g))$ and we let $H_g$ denote the set of all gates in the image
+of $L(g)$.
+
+For any two sets $X, Y$ we let $X^{\underline{Y}}$ denote the set of all
+injective functions from $Y$ to $X$.
+
+Let $\tau = (R_1, \ldots , R_t)$, $\mathcal{A}$ be a $\tau$-structure of size
+$n$, and $\gamma: \in [n]^{\underline{U}}$. Let $\gamma \mathcal{A}$ be the
+structure formed by mapping U, the universe of $\mathcal{A}$, in accordance with
 $\gamma$. The evaluation of some $(\mathbb{B}, \tau)$-circuit $C$ computing a
-q-ary query $Q$ of type $(s^Q_{1}, \ldots , s^Q_{q})$ proceeds by recursively
-evaluating gates. The evaluation of the gate $g$ using $\gamma$ with input
-$\mathcal{A}$ is denoted by $C[\gamma \mathcal{A}](g)$. The evaluation of a gate
-$g$ is given as follows.
+q-ary query $Q$ proceeds by recursively evaluating the gates in the circuit. The
+evaluation of the gate $g$ using $\gamma$ with input $\mathcal{A}$ is denoted by
+$C[\gamma \mathcal{A}](g)$, and is given as follows
 \begin{enumerate}
@@
   \mathcal{A} \models \Sigma(g)(\Lambda (g))$.
-\item If $g$ is an internal gate labelled by a $(\tau_g, A_g)$-structured
-  function $\Sigma(g)$, let $L^{\gamma}_g: \ind(F) \rightarrow \{0,1\}$ be
-  defined by $L^{\gamma}_g(x) = C[\gamma \mathcal{A}](L(g)(x))$. Then $g$
-  evaluates to true iff $\Sigma(g) (L^{\gamma}_g)$.
+\item If $g$ is an internal gate such that $\Sigma (g)$ is a
+  $\mathcal{D}$-structured function, let $L^{\gamma}_g: \ind(g) \rightarrow
+  \{0,1\}$ be defined by $L^{\gamma}_g(x) = C[\gamma \mathcal{A}](L(g)(x))$, for
+  all $x \in \ind(g)$. Then $g$ evaluates to true iff $\Sigma(g) (L^{\gamma}_g)
+  = 1$.
 \end{enumerate}
-$C$ defines the $q$-ary query $Q \subseteq U_{s^Q_1} \times \ldots \times
-U_{s^Q_q}$ where $\vec{a} \in Q$ iff $C[\gamma \mathcal{A}](\Omega (\gamma
-\vec{a})) = 1$.
+We say that $C_n$ defines the $q$-ary query $Q \subseteq U^q$ where $\vec{a} \in
+Q$ iff $C_n[\gamma \mathcal{A}](\Omega (\gamma \vec{a})) = 1$.
 
-The following definition is an important circuit property introduced by Anderson
-and Dawar \cite{AndersonD17}. We introduce it for the sake of comparison.
+% The circuit $C_n$ The following definition is an important circuit property
+% introduced by Anderson and Dawar \cite{AndersonD17}. We introduce it for the
+% sake of comparison.
+
+The following circuit condition is from Anderson and Dawar \cite{AndersonD17}.
 
 \begin{definition}[Invariant Circuit]
-  Let $C_{\vec{n}}$ be a $(\mathbb{B}, \tau)$-circuit, computing some $q$-ary
-  query of type $(s^Q_1, \ldots , s^Q_q)$. We say $C_{\vec{n}}$ is
-  \emph{invariant} if for every $\tau$-structure $\mathcal{A}$ of size
-  $\vec{n}$, $\vec{a} \in U_{i_1} \times \ldots \times U_{i_q}$, and sorted
-  bijections $\gamma_1, \gamma_2: U \rightarrow [n_{s_p}] \sqcup\ldots \sqcup
-  [n_{s_p}]$ we have that $C[\gamma_1 \mathcal{A}](\Omega (\gamma_1 \vec{a})) =
-  C[\gamma_2 \mathcal{A}](\Omega (\gamma_2 \vec{a}))$.
+  Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit, computing some $q$-ary query. We
+  say $C_n$ is \emph{invariant} if for every $\tau$-structure $\mathcal{A}$ of
+  size $n$, $\vec{a} \in U^{q}$, and $\gamma_1, \gamma_2: [n]^{\underline{U}}$
+  we have that $C[\gamma_1 \mathcal{A}](\Omega (\gamma_1 \vec{a})) = C[\gamma_2
+  \mathcal{A}](\Omega (\gamma_2 \vec{a}))$.
 \end{definition}
-
-This property ensures that the function computed by a circuit (or a family of
-circuits) is invariant under isomorphisms on the input structure. In other
-words, the circuit (or family of circuits) decides a property of the structure.
-The following lemma allows us to recast this notion in terms of the language
-developed in this paper.
+In general, the evaluation of a circuit depends on the presentation of the
+structure (i.e. on the chosen bijection $\gamma$). If family of $(\mathcal{B},
+\tau)$-circuits $\mathcal{C}$ is invariant it follows that the query computed is
+a $q$-query on $\tau$-structures. It follows that if $q = 0$ then $\mathcal{C}$
+computes a property of $\tau$-structures. The following lemma allows us to
+recast this notion in terms of the language developed in this paper.
 
 \begin{lem}
-  Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit. We have that the function
-  computed by $C_n$ is $\tau$-symmetric iff $C_n$ is invariant.
+  Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit. The function computed by $C_n$ is
+  isomorphism-invariant iff $C_n$ is invariant.
 \end{lem}
@@
 \begin{definition}[Automorphism]
-  let $C = \langle G, W, \Omega, \Sigma, \Lambda, L\rangle$ be a
+  let $C = \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a
   $(\mathbb{B},\tau)$-circuit computing a $q$-ary query on structures of size
@@
   We call $\pi$ an \emph{automorphism} of $C$, and we say that $\sigma$
-  \emph{induces the automorphism} $\pi$. The group of automorphisms of $C$ is
+  \emph{extends to the automorphism} $\pi$. The group of automorphisms of $C$ is
   called $\aut_n (C)$.
@@
   \[
-  \countgate_a = \begin{cases} \land ( \maj  ( x_1, \ldots, x_n, \underbrace {0, \ldots,
-        0}_{2a - n} ), \neg ( \maj (x_1, \ldots , x_n, \underbrace{0, \ldots,
+    \countgate_a = \begin{cases} \land ( \maj ( x_1, \ldots, x_n, \underbrace
+      {0, \ldots, 0}_{2a - n} ), \neg ( \maj (x_1, \ldots , x_n, \underbrace{0,
+        \ldots,
         0}_{2a - n + 2} ) )) &  a \geq \frac{n}{2} \\
-     \land ( \maj ( x_1, \ldots, x_n, \underbrace {1, \ldots, 1}_{n -
-           2a} ),  \neg (
-      \maj ( x_1, \ldots , x_n, \underbrace{1, \ldots, 1}_{n - 2a -2}
-      ) )) & a <
-      \frac{n}{2}.
+      \land ( \maj ( x_1, \ldots, x_n, \underbrace {1, \ldots, 1}_{n - 2a} ),
+      \neg ( \maj ( x_1, \ldots , x_n, \underbrace{1, \ldots, 1}_{n - 2a -2} )
+      )) & a < \frac{n}{2}.
     \end{cases}
@@
   It is easy to see that $C_n$ has depth at most $5$, width at most by $2n + 2$
-  and size at most $1 + 4(2n) + 2 = 8n+3$. We have that in each layer of $C_{g'}$
-  each gate is connected to all gates in the previous layer, and as such the
-  circuit is symmetric.
+  and size at most $1 + 4(2n) + 2 = 8n+3$. We have that in each layer of
+  $C_{g'}$ each gate is connected to all gates in the previous layer, and as
+  such the circuit is symmetric.
 \end{proof}

### 2017-11-13 sections/background.tex
13-Nov-2017

@@
   Let $S = \{s_1, \ldots , s_p\}$ be a set of sort symbols and $A = A_{s_1}
-  \sqcup \ldots \sqcup A_{s_p}$ and $B = B_{s_1}\dotcup \ldots \dotcup
+  \uplus \ldots \uplus A_{s_p}$ and $B = B_{s_1}\uplus \ldots \uplus
   B_{s_p}$ be disjoint unions of non-empty sets. A \emph{sorted bijection}
@@
 
+\subsection{Basic Notation}
+
+Let $f : X \rightarrow Y$ be a function and $\sim$ be an equivalence relation on Y.
+We define $f/{\sim} : X \rightarrow Y/{\sim}$ by $f(x) = [f(x)]_{\sim}$.
+We call this the quotient of the function by $\sim$.
+For any two sets $X, Y$ we let $X^{\underline{Y}}$ denote the set of all injective functions from $Y$ to $X$.
+
 \end{document}

### 2017-11-13 sections/introduction.tex
13-Nov-2017

--- 2017-07-26 sections/introduction.tex
@@
 \begin{document}
-A finite relational structure, such as a graph, can be represented as a binary
-string in a standard way (for instance, by enumerating its adjacency matrix).
-When we speak of the computational complexity of properties of graphs, we assume
-such an encoding in order to present the structure as input to a machine or
-circuit or other appropriate computational model. The properties of structures
-we are interested in studying are invariant under isomorphisms. This requirement
-translates into an invariance condition on sets of strings---say that a language
-$L \subseteq \{0,1\}^\star$ is a \emph{graph property} if, whenever $x \in L$
-for a string $x$ representing a graph $G$, we have $y\in L$ for any string $y$
-obtained from $x$ by re-ordering the vertices of $G$. The central open question
-in descriptive complexity---whether there is a logical characterisation of the
-polynomial-time decidable properties of finite relational structures--- can then
-be understood as the question of characterizing those languages $L$ that are in
-$\PT$ and are graph properties.
+When we study algorithmic complexity we often study complexity classes defined
+in terms of some restricted class of machines. Circuit complexity, where one
+makes use of similarly restricted families of Boolean circuits rather than
+machines, has long served as an alternative approach. These circuits models have
+a natural attraction for researchers, as their simpler structure seems to make
+them more amendable to analysis and their connections with machine models
+provides an alternative avenue for better understanding fundamental problems in
+complexity theory, including the $\PT$ vs $\NP$ problem.
 
-Anderson and Dawar~\cite{AndersonD17} study this question through the lens of
-circuit complexity, by considering \emph{symmetric circuits}. These are circuits
-that necessarily accept graph properties, with this fact explicitly witnessed by
-automorphisms of the circuit. To be precise, we can think of a property of
-(directed) graphs on $n$ vertices as being given by a Boolean function $f:
-\{0,1\}^{n^2} \rightarrow \{0,1\}$ which takes as input the $n^2$ potential
-edges and outputs $1$ if the property is satisfied by the graph given on the
-input. The function $f$ is \emph{graph-symmetric} in the sense that any
-permutation of its inputs induced by a permutation of the $n$ vertices leaves
-$f$ unchanged (note this is not the same thing as requiring that $f$ is
-invariant under all permutations of its inputs). A symmetric circuit is a
-circuit computing a Boolean function of $n^2$ inputs where each permutation of
-$[n]$ can be extended to an automorphism of the circuit. Such a circuit
-necessarily computes an invariant function.
+Descriptive complexity instead concerns the characterisation of complexity
+classes in terms of logics. The central open question in the field -- whether
+there is a logical characterisation of the polynomial-time decidable properties
+of finite relational structures -- essentially asks if there is a logic the
+sentences of which describe all (and only) polynomial-time decidable
+isomorphism-closed classes of graphs (i.e. every \emph{graph property} in
+$\PT$). As in the algorithmic complexity case, the use of circuits in
+descriptive complexity has proved useful, with Otto \cite{Otto1997} and
+Denenberg et al.~\cite{DENENBERG1986216} developing circuit-based
+characterisations for logics. These characterisation are given in terms of
+\emph{symmetric circuits}, circuits that take in finite structures over some
+universe and where permutations of the universe of the input structure are
+reflected by automorphisms of the circuit.
 
-The results of~\cite{AndersonD17} show a tight relationship between the
-decdability of a graph property by means of a polynomial-size family of
-symmetric circuits and its definability in extensions of fixed-point logic. In
-particular, they show that a property is definable in fixed-point logic with
-counting ($\FPC$) if, and only if, it is decidable by a polynomially-uniform
-family of symmetric circuits using Boolean and majority gates (or, equivalently,
-threshold gates). Without the symmetry restriction, polynomial-size families of
-circuits have the same computational power whether we restrict ourselves to
-Boolean gates only or allow richer bases such as threshold gates. One
-consequence of the results in~\cite{AD14} is that, with the requirement of
-symmetry, these different bases do yield different expressive power, suggesting
-some lack of robustness to the model. One of the results in the present paper
-shows that the model with majority circuits is robust in the sense that it is
-able to simulate, by means of symmetric circuits, any symmetric circuit composed
-of gates computing Boolean functions that are themselves symmetric (in the sense
-that they are invariant under \emph{all} permutations of their inputs. Thus, any
-property decidable by a polynomially-uniform family of such circuits is
-definable in $\FPC$.
+% In this way symmetric circuits provide a natural class from which to develop
+% circuit characterisations for logics, taking in abstract structures and
+% ensuring that isomorphism (permutations) on the input structure are reflected
+% in the circuit structure, which consequently implies that the function
+% computed by the circuit is \emph{invariant} (i.e. computes a graph property)
+% makes symmetric circuits a natural class from which to develop circuit
+% characterisations of logics.
 
-This motivates the study of symmetric circuit families that involve gates which
-themselves may compute non-symmetric functions. In particular, motivated by the
-study of rank logic~\cite{DGHL09,GP15}, we consider gates that are
-\emph{matrix-symmetric}. These are gates computing a Boolean function $f:
-\{0,1\}^{A \times B} \rightarrow \{0,1\}$ which is invariant under arbitrary
-permutations of $A$ and $B$. A typical example is the function computing the
-rank of an $A \times B$ $0$-$1$ matrix. We show that the support theorem of
-Anderson and Dawar can be shown to hold, even in the presence of
-matrix-symmetric gates. This allows us to show that definability in the logic
-fixed-point with rank ($\FPR$) is the same as decidability by
-polynomially-uniform families of symmetric circuits with rank gates.
-% Another extension of $\FPC$ that has received much attention in the
-% descriptive complexity literature is the class $\CPTC$ of \emph{choiceless
-% polynomial time with counting}. The work of~\cite{AD14} leaves open the
-% question of obtaining a circuit characterization of this class and it was
-% suggested there that this would require a relaxation of the notion of symmetry
-% used in defining symmetric circuits. In particular, while $\CPTC$ is based on
-% a machine model designed to preserve symmetry by forbidding choices, the
-% polynomial time and space restrictions apply int he context of the symmetries
-% fo a \emph{single input structure}. In this paper, we consider a relaxation of
-% the notion of symmetric circuit intended to capture exactly this intuition.
-% However, we are able to show that this does not yield a characterization of
-% $\CPTC$. In particular, we show that no family in this class of relaxed
-% symmetric circuits can distinguish odd from even Cai-F\"urer-Immerman graphs,
-% something we know is do-able in $\CPTC$~\cite{DRR08}.
+Anderson and Dawar \cite{AndersonD17} developed a similar
+circuit-characterisation for $\FPC$, proving that families of P-uniform families
+of symmetric circuits defined over a complete Boolean basis with majority gates
+completely characterises \emph{fixed-point logic with counting} ($\FPC$).
 
+While it is known that $\FPC$ does not capture $\PT$ \cite{Cau1992}, $\FPC$ does
+capture $\PT$ over many classes of structures \cite{Grohe2010} and many natural
+$\PT$ problems are expressible in $\FPC$ (e.g.\ Maximum Matching
+\cite{Anderson2013}). While $\FPC$ is thus an important logic of interest for
+its own sake, it also plays a role as a logic from which other important logics
+of study are defined. The particular logic of interest in this paper is
+\emph{fixed-point logic with rank} ($\FPR$), introduced by Dawar et
+al.~\cite{Dawar09logicswith}, and is defined as an extension of $\FPC$ that
+includes operators that can define the rank of a definable matrix over a fixed
+finite field. This extension was prompted by the work of Atserias et
+al.~\cite{Atserias20091666}, who had shown that that some of the most difficult
+to express problems in $\PT$ (that are not expressible in $\FPC$) were reducible
+to the general problem of solving systems of linear equations over prime fields.
+Indeed, problems of this sort have remained the primary source of
+difficult-to-express problems in descriptive complexity, motivating the modern
+study of $\FPR$.
+
+It is worth noting the logic defined by Dawar et al.\cite{} defines for each
+prime a separate operator that computes the rank of the matrix over that prime.
+It was shown by Gr\"{a}del and Pakusa \cite{GradelP15a} that this logic does not
+capture $\PT$. Instead, they present a strictly more expressive alternative rank
+logic which includes only a single rank operator that takes in both the matrix
+and a specific prime over which to compute the rank as input. In this paper when
+we refer to $\FPR$ we are referring to this more expressive version of
+Gra\"{a}del and Pakusa.
+
+In this paper we develop a circuit characterisation of $\FPR$ in terms of
+symmetric circuits that have gates that compute rank. Concretely, a circuit
+$C_n$ for structures of size $n$ is a directed acyclic graph (DAG) whose
+internal gates are marked by elements of some basis. This basis consists of
+operations or, more concretely, Boolean functions such that a gate $g$ in $C_n$
+with $k$ input gates is labelled by a function $f: \{0,1\}^A \rightarrow
+\{0,1\}$, where $\vert A \vert = k$. When evaluating the circuit, $g$ is
+computed by evaluating $f$ with the input given by the binary string formed by
+evaluating the gates input to $g$, implicitly mapping $A$ to the input gates of
+$g$. However, the output of $f$ in general depends on the order (or structure)
+of the binary string taken as input, and as such the evaluation of $g$ depends
+on which gates are assigned to each element of $A$.
+
+This point is often ignored in circuit complexity by ensuring that functions in
+the Boolean basis are \emph{symmetric}, i.e. depend only on the number of 1's in
+it's input, rendering the particular assignment from $A$ to the input gates
+irrelevant. This is the approach taken by Anderson and Dawar \cite{AndersonD17}.
+However, functions that compute an operation like rank, i.e. a function that
+takes in a matrix with Boolean entries and outputs 1 iff that matrix, when
+interpreted in $\mathbb{F}_p$, has rank at least $r$, certainly depend on how
+the input is formed into a matrix, and as such is not a symmetric function.
+
+We introduce the notion of a \emph{structured function}, which allows us to both
+index inputs appropriately and introduce appropriate generalisations of symmetry
+depending on the structure of the input. Each such function $F$ is uses a many-sorted
+structure, with some signature $\tau_F$, in order to index the input. This
+definition allows us to generalise the notion of symmetry to a particular
+labelling, and so introduce the notion of a \emph{$\tau$-symmetric functions}.
+
+We also introduce a generalised symmetric circuit allows, which allows for
+$\tau$-symmetric functions in the Boolean basis, not just symmetric ones. The
+circuit also provides a function $L$ that maps to each internal gate $g$ to a
+labelling on its input corresponding the labelling on the input of the Boolean
+function that labels this gate.
+
+\begin{remark}
+  I'm not sure how much detail to go into here, this could be a major
+  digression.
+\end{remark}
+
+% That is, eacFor example, if we should like The circuit $C_n$ associates with
+% each internal gate $g$ a structure $\dom (g)$, and each gate input a sequence of
+% elements from each sort $\dom(g)$ in accordance with the sorts of the
+
+% of definition includes an additional function which assosiates for each gate $g$
+% a
+
+% require that the Basis over which the circuit is defined are symemtric.. We
+% begin by generalising the notion of a symmetric circuit. A symmetric circuit, as
+% presented in \cite{AndersonD17}, and in many parts of complexity theory,
+% supposes that the in Boolean function that labels in the gate is
+% \emph{symmetric} that labels a particular gate We first generalise the notion of
+% a symmetric circuit so as to allow for gate
+
+% In this general notion of a symmetric circuit, a Boolean basis consists not just
+% of a set of Boolean functions, but a set of \emph{structured functions} -- a
+% function indexed A symmetric $\tau$-circuits is defined for some universe size
+% $n$ and Boolean basis $\mathbb{B}$ of Boolean functions. Each Boolean function
+% in $\mathbb{B}$ is a \emph{structured Boolean function} in the sense that
+
+% In this abstract we review the work of Anderson and Dawar on symmetric
+% circuits, and extend their analysis by broadening the basis of functions they
+% consider to include so-called `matrix-symmetric' functions. This class of
+% functions includes important non-symmetric functions, e.g.\ the rank of a
+% matrix, and this allows us to study symmetric circuits with gates that compute
+% rank. Our main result is a circuit characterisation for FPR. In particular, we
+% show that P-uniform families of symmetric circuits with rank gates
+% characterise FPR. This requires a significant advance on the methods
+% of~\cite{AndersonD17}.
 \end{document}

### 2017-11-13 sections/symmetric-circuits.tex
13-Nov-2017

@@
 % Note: include circuits in background
-Boolean circuits have long been as an alternative model from which to study
-algorithmic complexity. A circuit is evaluated for some ordered binary input
-sequence by recursively evaluating each gate in the circuit, starting from the
-input gates. Suppose then we are evaluating some gate $g$ in a circuit $C$. The
-procedure involves taking the input string formed by evaluating all gates input
-to $g$ and applying the Boolean function that labels $g$ to that string. But
-this process assumes an externally-imposed ordering on the gates input to $g$;
-an assumption common in most parts of complexity theory, where the encoding of
-structures for computation induces such orderings, but not in finite model
-theory.
 
-Circuit models have also been studied in finite model theory as a means for
-characterising the expressive power of logics. In particular, research has
-focused on symmetric circuits defined over bases of symmetric Boolean functions
-(see \cite{}). The fact that the basis consist of only symmetric functions is a
-crucial requirement, ensuring that the evaluation of a gate does not depend on
-the order.
+%AD: re-wrote the introductory paragraphs to be a bit more substantive.
 
-In this section we extend the circuit model so as to allow us to define
-symmetric circuits over a broader basis of functions. We introduce the notion of
-a structured function , i.e. a Boolean function whose input is indexed in
-accordance with some many-sorted structure. This allows us to characterise many
-natural symmetry properties of structured functions in terms of equally natural
-symmetry properties of many-sorted structures. We use this to derive a general
-symmetry conditions on structured functions and a symmetric circuit model whose
-basis elements are symmetric structured functions.
+A Boolean circuit $C$ computing a function from $\{0,1\}^n$ to
+$\{0,1\}$ is usually described as a directed acyclic graph, with each
+gate $g$ that has $m$ incoming edges labelled with a Boolean function
+$f_g : \{0,1\}^m \rightarrow \{0,1\}$ from a basis $\mathbb{B}$ and
+exactly $n$ input gates of $C$ are labelled by variables.  If the
+function $f_g$ can be arbitrary, then the circuit $C$ must impose an
+order on the gates that provide the inputs to $g$.  When we say that
+$C$ is a directed acyclic graph, without further ordering the nodes,
+we implicitly assume that the functions in the basis $\mathbb{B}$ are
+\emph{symmetric}.  That is to say $f_g$ is invariant under all
+permutations of its $m$ inputs.  This unstated assumption is pervasive
+in circuit complexity.  In particular, the standard Boolean basis of
+AND, OR and NOT gates as well as bases with majority or threshold
+gates only contain symmetric functions.
+
+We are interested in Boolean circuits that compute queries on
+structures, such as graphs.  In the case of (undirected, loop-free)
+graphs on $n$ vertices, such a circuit might compute a function from
+$\{0,1\}^{n \choose 2}$ to $\{0,1\}$.  In this case, the function
+computed by the circuit is not necessarily invariant under all
+permutations of the inputs, but it is invariant under all permutations
+of the $n \choose 2$ inputs induced by permutations of $[n]$.
+We are especially concerned with \emph{symmetric} circuits, that is
+those where the permutations of $[n]$ extend to automorphisms of the
+circuit.  Note that this use of the word ``symmetric'' is distinct to
+that its use when applied to Boolean functions.  For such circuits, Anderson and Dawar~\cite{AndersonD17}
+consider $\PT$-uniform circuits in the standard Boolean basis as
+well one with majority gates.  It is a consequence of their results
+that the latter are strictly more powerful than the former.  In
+particular, they are shown to be equivalent
+to the logic $\FPC$.  In contrast, we show, in this section, that adding any
+further symmetric functions to the basis does not allow us to extend
+the power of $\PT$-uniform symmetric circuits beyond that of $\FPC$.
+
+As our aim is a circuit characterisation of $\FPR$, whose expressive
+power is strictly greater than that of $\FPC$, we need to
+consider gates corresponding to non-symmetric Boolean functions.  In
+particular, we consider \emph{rank} gates whose inputs are a matrix
+and whose result is invariant under row and column permutations.  To
+lead up to this, we first develop a general framework of structured
+Boolean functions.  These are functions whose inputs naturally encode
+$\tau$-structures and where the output is invariant under the natural
+symmetries of such structures.  The\emph{matrix-invariant} functions
+are a natural partiruclar case.   We therefore define symmetric circuits in a
+general form where gates can be labelled by \emph{isomorphism-invariant} structured
+functions.
+
+Ultimately, our aim is replicate the results Anderson and
+Dawar~\cite{AndersonD17} in this more general setting.  A difficulty
+we face is that the proof methods in that paper heavily rely on the
+assumption that the Boolean functions computed by individual gates are
+symmetric functions.  We address this difficulty in the next section.
+
+% Boolean circuits have long acted as an alternative model from which to study
+% algorithmic complexity. A circuit is evaluated for some input binary sequence by
+% recursively evaluating each gate in the circuit, starting from the input gates.
+% Suppose then we in the process of evaluating the circuit $C$ and are at the
+% stage of evaluating the gate $g$. We take the input sequence formed from the
+% evaluations of the gates input to $g$ and applying the element of the basis that
+% labels $g$ to that sequence. It follows that in order to evaluate $g$ we need to
+% suppose some order on the evaluations of the input gates. In many cases this
+% order is simply induced by an assumed order on the whole of the circuit; an
+% assumption common in most parts of complexity theory, where the encoding of
+% structures for computation induces such orders, but problematic in finite model
+% theory.
+
+% Circuit models have also been studied in finite model theory, often as a means
+% for characterising the expressive power of logics. In particular, research has
+% focused on symmetric circuits defined over bases of symmetric Boolean functions
+% (see \cite{}). The fact that the basis consist of only symmetric functions is a
+% crucial requirement, ensuring that the evaluation of a gate does not depend on
+% an external order. However, in this paper we will need to consider circuits with
+% gates that compute rank, a function that is not symmetric.
+
+% In this section we extend this circuit model so as to allow for the inclusion of
+% non-symmetric functions in the basis. We allow each gate $g$ to index its input
+% gate in accordance with the basis element labeling $g$. We introduce the notion
+% of a \emph{structured function}, a Boolean function whose input is indexed in
+% accordance with a many-sorted vocabulary $\tau$. The input vector to a
+% structured function can then be thought of as encoding a $\tau$-structure. In
+% particular, we consider structured functions that compute properties of
+% $\tau$-structures, which we call \emph{isomorphism-invariant} structured
+% functions. We then define what it means for a circuit over a basis of
+% isomorphism-invariant structured functions to be symmetric. This generalises the
+% notion of a symmetric circuit. We also show that there are limitations on the
+% power of symmetric circuits over bases of symmetric functions, justifying the
+% importance of this generalisation.
 
@@
 \subsection{Structured Functions and Symmetry}
-Before we begin this section let us review Boolean circuits and a few useful
-symmetry conditions placed on these circuits. Let $X$ be a finite set and $F:
-\{0,1\}^{X} \rightarrow \{0,1\}$ be a Boolean function. We call $X$ the
-\emph{index} of $F$, and denote it by $\ind(F)$. It is often the case that the
-index $X$ is in some sense structured, but let us first consider the case where
-$X$ is an unstructured set. In this case the only natural symmetry condition to
-consider is where $F$ is invariant under the action of $\sym_n$, i.e. $F$ is a
-symmetric function. Suppose instead $X$ consists of all two element subsets of
-the set $V$. Here we can think of $X$ as representing all potential edges in a
-graph, and $\vec{x} \in \{0,1\}^X$ as defining a graph. It is natural then to
-consider the case where $F$ determines a property of the graph, i.e. where $F$
-is invariant under the action of $\sym_V$ on the input (i.e renaming of the
-vertices). We call such a function \emph{graph-invariant}. Suppose that $X := A
-\times B$ for two non-empty sets $A$ and $B$. Here we can think of $\vec{x} \in
-\{0,1\}^X$ as an (unordered) matrix, and we can consider the case where $F$ is
-invariant under the action of $\sym_A \times \sym_B$. In this case we say $F$ is
-\emph{matrix-invariant}. Notice that in each of these cases the symmetry
-condition of interest on the function was related to the structure of the index
-set.
+Let $X$ be a finite set and $F: \{0,1\}^{X} \rightarrow \{0,1\}$. We call $X$
+the \emph{index} of $F$, and denote it by $\ind(F)$. We are often interested in
+classes of functions characterised by certain symmetry conditions. Perhaps the
+simplest example is the class of symmetric functions, i.e.\ those functions
+invariant under the action of the symmetric group on their index. However, in
+many cases this symmetry condition may be too strong, or otherwise
+inappropriate. For example, suppose $X$ consists of all two element subsets of
+some set $V$. We may think of $X$ as containing all potential edges in a graph,
+and the input sequence $ \vec{x} \in \{0,1\}^X$ as encoding a graph. In this
+case we might require instead that $F$ be invariant under the action of $\sym_V$
+on $\vec{x}$. This condition guarantees that $F$ determines a graph property,
+and we call such a function \emph{graph-invariant}. Another example of interest,
+especially in this paper, is the case where $X := A \times B$, where $A$ and $B$
+are non-empty sets, and we think of $\vec{x} \in \{0,1\}^X$ as encoding an
+(unordered) matrix. It is natural then to consider the case where $F$ is
+invariant under the action of $\sym_A \times \sym_B$, and we say such a function
+is \emph{matrix-invariant}. In this subsection we develop a general framework
+for dealing with functions that take in structures.
 
-In the rest of this subsection we develop the notion of structured function, a
-Boolean function whose input is structured in accord with some structure and
-whose natural symmetry conditions follow from similar conditions on the
-structure.
+%AD - rewrote the paragraph to reduce the use of subscripts and superscripts.
+Let $\tau = (R, S, \nu)$ be a many-sorted signature.
+% with $R = \{R_1 \ldots,
+% R_t\}$, $S = \{s_1, \ldots , s_p\}$, and $\nu(R_i) = (a^i_1, \ldots ,
+% a^i_{r_i)})$, where $r_i = \arty(R_i)$ and $a^i_q \in S$ for all $q \in
+% [r_i]$.
+Let $D := \biguplus_{s \in S} D_{s} = \{(s,d) : d \in D_s\}$, be a
+disjoint union of non-empty sets, indexed by $S$, i.e.\ $D$ is
+potentially the universe of a $\tau$-structure. We call $D$ a \emph{$\tau$-sorted set}.
+For each $P \in R$, let $P^D$ denote the trivial relation over the
+many-sorted universe $D$, i.e.\ $P^D := D_{a_1} \times \ldots \times
+D_{a_{r}}$, where $\nu(P) = (a_1, \ldots , a_{r)})$.   Let the \emph{index defined by the pair $(\tau, D)$} be
+the set $\biguplus_{P\in R} P^{D}$.  We use this set to index the input to a Boolean
+function, as such we abuse notation and denote the index defined by
+$(\tau, D)$ by $\ind(\tau, D)$. We call $\tau$ the vocabulary and $D$ the universe of $\ind(\tau, D)$.
 
-% $X:= {n}\choose{2}$, for some $n$, we can think of $F$ as taking in some $n$
-% vertex graph, and we should like $F$ to respect permutations on the graph. In
-% this case we insist that $F$ is a \emph{graph symmetric} function, for all $$
-% where we can think of $F$ as taking in a graph with $n$ vertices, where $X:=
-% {n}\choose{2}$ as indexing a graph with $n$ vertices
+For the remainder of this subsection we fix a vocabulary $\tau$ and a
+many-sorted set $D=\biguplus_{s \in S} D_{s}$
+and let $X := \ind (\tau, D)$. Let $G \leq \sym_{X}$, and let
+$\sortsym(D) := \prod_{s \in S} \sym_{D_{s}}$.  We call the elements of $\sortsym(D)$ \emph{sorted permutations}. Note that
+$\sortsym(D)$ can be identified with a subgroup of $\sym_X$. There is an
+obvious action of $G$ on $X$.  We can extend this to an action on the set of functions
+of the form $f: X \rightarrow X$, for any set $H$, defined by $\sigma \cdot f(x)
+= f(\sigma \cdot x)$ for all $x \in X$, $\sigma \in G$.
 
-% The set $X$ is often used just to provide an ordering, and so $F$ just takes
-% in a binary $\vert X \vert$-tuple. While in general the order of the input
-% sequence matters, it is common to consider the case where $F$ is a
-% \emph{symmetric} Boolean function, i.e. for all $\sigma \in \sym_{X}$,
-% $\vec{x} \in \{0,1\}^{X}$, $F(\vec{x}\cdot \sigma) = \vec{x}$. In this case
-% the output of the function is independent of the ordering on the input tuple.
-% Indeed, many natural Boolean functions (e.g. `and', `or', `not', `majority',
-% etc.) are symmetric functions. One of the benefits of considering symmetric
-% functions
-
-Let $\tau = (R, S, \nu)$ be a many-sorted, relational signature, with $R = \{R_1
-\ldots, R_t\}$ and $S = [s]$ for some $s \in \nats$, and $\nu(R_i) = (a^i_1,
-\ldots , a^i_{r_i)})$, where $r_i = \arty(R_i)$ and $a^i_q \in S$ for all $q \in
-[r_i]$. Let $\mathcal{D}$ be a $\tau$-structure, with the universe $D = D_1
-\uplus \ldots \uplus D_s = \{(i,d) : d \in D_i\}$.
-
-Let the \emph{index-domain} of $\mathcal{D}$ be $\rdom {\mathcal{D}} = \{(i, j)
-:= i \in [r_j], R_j \text{ a relation in $\tau$} \}$. Let the \emph{index
-  defined by} $\mathcal{D}$ be the set of all functions $f: \rdom(\mathcal{D})
-\rightarrow D$ such that for all $R_j \in R$ and $i \in [r_j]$, $f(i, j) \in
-A_{a^{j}_i}$. We abuse notation and denote the index defined by
-$\ind(\mathcal{D})$. We note that, since the set of relation symbols and sort
-symbols are ordered, we can also think of each $f \in \ind(\mathcal{D})$ as a
-tuple in $D_{a^1_1} \times \ldots \times D_{a^1_{r_1}} \times \ldots \times
-D_{a^t_1} \times D_{a^t_{r_t}}$. We will use these tuples in order to index the
-inputs to a Boolean function.
-
-For the remainder of the section fix a $\tau$-structure $\mathcal{D}$ and let $X
-:= \ind (\mathcal{D})$. Let $G \leq \sym_{X}$. We note that there is a natural
-action of $G$ on $X$. Furthermore, we can define an action of $G$ on functions
-of the form $f: X \rightarrow H$, for any set $H$, given by $\sigma \cdot f(x) =
-f(\sigma \cdot x)$ for all $x \in X$. If $H = \{0,1\}$ we say that $f$ is a
-\emph{binary sequence indexed by $X$}. If $H$ is surjective, we say that
-\emph{$f$ indexes $H$ by $X$} or \emph{$f$ indexes $H$ by $\mathcal{D}$}. We
-note that $\aut(\mathcal{D})$ and $\iso(\mathcal{D})$ can be identified with
-subgroups of $\sym_X$.
-
-We develop a notion of equivalence from this action. Say that two functions $f,
-g : X \rightarrow H$ are \emph{$G$-equivalent} iff there exists $\sigma \in G$
-such that $f(x) = f(\sigma \cdot x)$ for all $x \in X$. We say $f$ and $g$ are
-\emph{isomorphism-equivalent} if they are $\iso(\mathcal{D}$-equivalent. We say
-that $f$ and $g$ are \emph{automorphism-equivalent} if they are $
-\aut(\mathcal{D})$-equivalent. We say that $f$ and $g$ are
-\emph{sort-equivalent} in the special case where every relation in $\mathcal{D}$
-contains all possible tuples and $f$ and $g$ are automorphism-equivalent.
+% If $H$ is surjective, we say that \emph{$f$ indexes $H$ by $X$} or \emph{$f$
+% indexes $H$ by $\mathcal{D}$}.
+We say that two functions $f, g : X \rightarrow H$ are \emph{$G$-equivalent} if
+there exists $\sigma \in G$ such that $f = \sigma \cdot g$. We say $f$ and $g$
+are \emph{isomorphism-equivalent} if they are $\sortsym(D)$-equivalent.
+We are interested in the case where $H = \{0,1\}$, i.e.\ $f : X
+\rightarrow \{0,1\}$.
+In this case $f$ defines for each relation $R^D_i$ a subset of that relation, and thus determines a $\tau$-structure over the universe $D$.
+We note that two functions $f, g: X \rightarrow
+\{0,1\}$ are isomorphism-equivalent if, and only if, the two $\tau$-structures
+they determine are isomorphic.
 
 We call a function of the form $F:\{0,1\}^{X} \rightarrow \{0,1\}$ a
-\emph{$\mathcal{D}$-structured function}. We note that $\ind(F) =
-\ind(\mathcal{D})$, justifying our above choice of notation. We also say
-\emph{the vocabulary of $F$} and \emph{the universe of $F$} to refer to the
-vocabulary and universe of $\mathcal{D}$.
+\emph{$(\tau, D)$-structured function}, or just a \emph{structured function}
+when there is no need to emphasise the particular vocabulary.  We note that
+$\ind(F) = \ind(\tau, D)$, justifying our choice of notation.  We let
+\emph{the vocabulary of $F$} and \emph{the universe of $F$} denote
+$\tau$ and $D$ respectively.
 
@@
 
-These structured functions give us a general framework for indexing the input to
-functions while also providing us with a natural set of groups from which to
-develop symmetry conditions for Boolean functions. We now introduce some of
-these conditions. Let $F$ be a $\mathcal{D}$-structured function. We say $F$ is
-\emph{$G$-invariant} if it constant on $G$-equivalent input vectors, i.e. for
-all $G$-equivalent $\vec{x},\vec{y} \in \{0,1\}^{X}$, $F(\vec{x}) = F(\vec{y})$.
-Similarly, we say $F$ is \emph{automorphism-invariant} if it is constant on
-automorphism-equivalent input vectors and \emph{isomorphism-invariant} if it is
-constant on isomorphism-equivalent input vectors. If all the relations in
-$\mathcal{D}$ contain all possible tuples, and $F$ is automorphism-invariant,
-then we say that $F$ is \emph{sort-invariant}. If the vocabulary of $F$ has two
-sorts $s_1, s_2$ and one binary relation $R$ with type $(s_1, s_2)$ and $F$ is
-sort-invariant, then we say $F$ is \emph{matrix-invariant}.
+Structured functions give us a general framework for indexing the input sequence to a Boolean function and associating with that function an appropriate symmetry condition. Let $F$ be a
+$(\tau, D)$-structured function. We say $F$ is \emph{$G$-invariant} if it is
+constant on $G$-equivalent input vectors, i.e.\ for all $G$-equivalent $\vec{x},
+\vec{y} \in \{0,1\}^{X}$, $F(\vec{x}) = F(\vec{y})$. We say $F$ is
+\emph{isomorphism-invariant} if it is $\sortsym (D)$-invariant. Note that
+a structured function with vocabulary $\tau$ is isomorphism-invariant if, and
+only if, it decides a property of $\tau$-structures.
 
-Notice that if $\tau$ is the empty vocabulary and $\mathcal{D}$ is a
-$\tau$-structure, i.e. $\mathcal{D}$ is a pure set, then any
-$\mathcal{D}$-structured function $F$ is automorphism-invariant (or
-isomorphism-invariant) if, and only if, $F$ is symmetric. Also, if $\mathcal{D}$
-is a graph, then $F$ is isomorphism invariant if, and only if, $F$ is
-graph-invariant (except with a slight alteration, here $F$ takes in the edge
-relation rather than a binary string indexed by two element sets of vertices).
-Similarly, $F$ is matrix invariant (as a structured function) if, and only if,
-it is matrix-invariant in the sense defined right at the beginning of this
-subsection. In each of these cases choosing an appropriate structure leads to an
-appropriate index and an appropriate notion of symmetry. In this way structured
-functions generalise the notion of a symmetric function and allow us to capture
-a broad range of structure-specific symmetry conditions in a single definition.
-In the next section we will show how to define a circuit and a symmetric circuit
-using bases of structured functions.
+At the beginning of this subsection we defined three Boolean functions with
+differently indexed inputs and corresponding symmetry conditions. We now look at
+how these functions might be thought of as structured functions, and how the
+symmetry conditions we discussed are naturally reproduced. Suppose $\tau$ is
+single-sorted and consists of a single unary relation. Then any structured
+function $F$ with vocabulary $\tau$ is isomorphism-invariant if, and only if, it
+is symmetric. If instead the vocabulary of $F$ is the graph vocabulary, then $F$
+is isomorphism-invariant if, and only if, $F$ decides a property of directed
+graphs. Lastly, if the vocabulary of $F$ has just two sorts $(s_1, s_2)$ and one
+binary relation with type $(s_1, s_2)$, then $F$ is isomorphism-invariant if,
+and only if, it is matrix-invariant.
+
+In each case a natural choice of the structure indexes the input to the
+structured function appropriately and produces the appropriate symmetry
+condition. It is worth mentioning that the graph-invariant case is not strictly
+reproduced above, as the structured functions are rather defined over directed
+graphs.
+
+From the above observations, we may think of symmetric functions as
+isomorphism-invariant structured functions over the single-sorted vocabulary with
+a single unary relation. We can similarly think of matrix-invariant functions as
+isomorphism-invariant structured functions over the appropriate vocabulary. More
+formally, if the vocabulary of $F$ consists of $p$ sort symbols $s_1, \ldots ,
+s_p$ and only one relation symbol with type $(s_1, \ldots, s_p)$ and $F$ is
+isomorphism-invariant, then we say $F$ is \emph{sort-invariant}. If $p = 2$ and
+$F$ is sort-invariant then we say that $F$ is \emph{matrix-invariant}.
+
+In keeping with convention for Boolean functions, and for introducing simplicity
+without a loss of generality, we assume that the universe of any structured
+function is always a disjoint union of initial segments of the natural
+numbers, i.e.\ if $F$ is structured function with universe $D_{s_1} \uplus \ldots
+\uplus D_{s_p}$, then for all $s \in \{s_1 , \ldots , s_p\}$ there exists $d_s \in \mathbb{N}$ such
+that $D_{s} = [d_s]$. We also assume that every $(\tau, D)$-structured function has the property that every $a \in D$ appears in at least one element of $\ind(\tau, D)$.
 
@@
 \subsection{Symmetric Circuits}
-We define a circuit over a basis of structured functions that are not
-necessarily symmetric. As such, the circuit must include for each gate $g$ an
-index on its children corresponding to the index of the function labelling $g$.
+% We define a circuit over a basis of structured functions that are not
+% necessarily symmetric. As such, the circuit must include for each gate $g$ an
+% index on its children corresponding to the index of the function labelling
+% $g$.
+In this section we extend the circuit definitions of Anderson and Dawar
+\cite{AndersonD17}, introducing a circuit for structures that incorporates an
+indexing for each gate in accordance with the Boolean function labelling that
+gate. This allows us to define (and evaluate) circuits with gates labelled by
+non-symmetric functions.
 
@@
 
+We now define a \emph{$(\mathbb{B}, \tau)$-circuit} . This is a circuit that
+computes a function on structures in the relational vocabulary $\tau$ and where
+the gates are labelled by elements of the basis $\mathbb{B}$. Each element of
+the basis is a $(\tau,D)$-structured function for some $\tau$ and $D$. Note
+that, in the interests of keeping our definitions from getting excessively
+complicated, we do not consider circuits computing functions over multi-sorted
+vocabularies.
 \begin{definition}[Circuits on Structures]
@@
   \item $\Sigma$ is a function from $G$ to $\mathbb{B} \uplus \tau \uplus
-    \{0,1\} $ such that $\vert \Sigma^{-1} (0) \vert \leq 1$ $\vert \Sigma^{-1}
-    (1) \vert \leq 1$. Those gates mapped to $\tau \uplus \{0,1\}$ are called
-    input gates, with those mapped to $\tau$ called relational gates and those
-    mapped $\{0,1\}$ called constant gates. Those gates mapped to $\mathbb{B}$
-    are called internal gates.
+    \{0,1\} $ such that $\vert \Sigma^{-1} (0) \vert \leq 1$ and $\vert
+    \Sigma^{-1} (1) \vert \leq 1$. Those gates mapped to $\tau \uplus \{0,1\}$
+    are called input gates, with those mapped to $\tau$ called relational gates
+    and those mapped $\{0,1\}$ called constant gates. Those gates mapped to
+    $\mathbb{B}$ are called internal gates.
   \item $\Lambda$ is a sequence of injective functions $(\Lambda_{R_i})_{R_i \in
-      R}$ such that $\Lambda_{R_i}$ maps each relational gate $g$ with $R_i =
-    \Sigma (g)$ to the tuple $\Lambda_{R_i} (g) \in [n]^{r}$. When no ambiguity
+      R}$ such that $\Lambda_{R_i}$ maps each relational gate $g$ with $\Sigma
+    (g) = R_i$ to the tuple $\Lambda_{R_i} (g) \in [n]^{r}$. When no ambiguity
     arises we write $\Lambda (g)$ for $\Lambda_{R_i} (g)$.
   \item $L$ associates with each internal gate $g$ a function $L(g):
-    \dom(\Sigma(g)) \rightarrow G$ such that if we define a relation $W
+    \ind(\Sigma(g)) \rightarrow G$ such that if we define a relation $W
     \subseteq G^{2}$ by $W(h_1,h_2)$ iff $h_2$ is an internal gate and $h_1$ is
@@
 as $\ind(\Sigma(g))$ and we let $H_g$ denote the set of all gates in the image
-of $L(g)$.
+of $L(g)$. We also refer to the vocabulary and universe of $g$ to abbreviate
+referring to the vocabulary and universe of $\Sigma(g)$.
 
-For any two sets $X, Y$ we let $X^{\underline{Y}}$ denote the set of all
-injective functions from $Y$ to $X$.
+% It is worth noting that in general computing the syntactic equivalence
+% relation in polynomial time may not be possible. In fact, given two bipartite
+% graphs it is possible to construct (in time polynomial in the size of the
+% graphs) a circuit with gates labelled by matrix-symmetric functions such that
+% two specified gates are syntacticly equivalent if,and only if, the two
+% bipartite graphs are isomorphic. Since there is a polynomial time reduction
+% from the graph isomorphism problem to the graph isomorphism problem on
+% bipartite graphs, it follows that there is a polynomial time reduction from
+% the graph isomorphism to the problem of computing syntactic equivalence. We
+% formalise this result in the following proposition, and give the explicit
+% construction referenced.
 
-Let $\tau = (R_1, \ldots , R_t)$, $\mathcal{A}$ be a $\tau$-structure of size
-$n$, and $\gamma: \in [n]^{\underline{U}}$. Let $\gamma \mathcal{A}$ be the
-structure formed by mapping U, the universe of $\mathcal{A}$, in accordance with
-$\gamma$. The evaluation of some $(\mathbb{B}, \tau)$-circuit $C$ computing a
-q-ary query $Q$ proceeds by recursively evaluating the gates in the circuit. The
-evaluation of the gate $g$ using $\gamma$ with input $\mathcal{A}$ is denoted by
-$C[\gamma \mathcal{A}](g)$, and is given as follows
+% \begin{prop}
+%   There is a a polynomial time reduction from Graph Isomorphism to the problem
+%   of deciding if two specified gates in a matrix-circuit are syntacticly
+%   equivalent.
+% \end{prop}
+% \begin{proof}
+% \end{proof}
+
+% In contrast, in the restricted case where the gates of the circuit are
+% labelled only by symmetric Boolean functions then the syntactic equivalence
+% relation can be computed in polynomial time.
+
+% \begin{prop}
+%   Let $C_n$ be a circuit with symmetric gates. Then the problem of syntactic
+%   equivalence relation on the gates of $C_n$ can be computed in polynomial
+%   time.
+% \end{prop}
+% \begin{proof}
+% \end{proof}
+
+Let $\tau$ be a relational vocabulary, % = (R_1, \ldots , R_t)$
+$\mathcal{A}$ a $\tau$-structure over an $n$-element universe $U$ and $\gamma
+\in [n]^{\underline{U}}$.
+% AD - need to define the notation [n]^{\underline{U}} in the background section
+% -- DONE
+
+Let $\gamma \mathcal{A}$ be the structure on universe $[n]$ formed by mapping
+$U$ in accordance with $\gamma$. The evaluation of a $(\mathbb{B},
+\tau)$-circuit $C_n$ computing a $q$-ary query $Q$ proceeds by recursively
+evaluating the gates in the circuit. The evaluation of the gate $g$ for the
+bijection $\gamma$ and input $\mathcal{A}$ is denoted by $C[\gamma
+\mathcal{A}](g)$, and is given as follows:
 \begin{enumerate}
@@
   \mathcal{A} \models \Sigma(g)(\Lambda (g))$.
-\item If $g$ is an internal gate such that $\Sigma (g)$ is a
-  $\mathcal{D}$-structured function, let $L^{\gamma}_g: \ind(g) \rightarrow
-  \{0,1\}$ be defined by $L^{\gamma}_g(x) = C[\gamma \mathcal{A}](L(g)(x))$, for
-  all $x \in \ind(g)$. Then $g$ evaluates to true iff $\Sigma(g) (L^{\gamma}_g)
-  = 1$.
+\item If $g$ is an internal gate such that $\Sigma (g)$ let $L^{\gamma}_g:
+  \ind(g) \rightarrow \{0,1\}$ be defined by $L^{\gamma}_g(x) = C[\gamma
+  \mathcal{A}](L(g)(x))$, for all $x \in \ind(g)$. Then $g$ evaluates to true
+  iff $\Sigma(g) (L^{\gamma}_g) = 1$.
 \end{enumerate}
-We say that $C_n$ defines the $q$-ary query $Q \subseteq U^q$ where $\vec{a} \in
-Q$ iff $C_n[\gamma \mathcal{A}](\Omega (\gamma \vec{a})) = 1$.
+We say that $C_n$ defines the $q$-ary query $Q \subseteq U^q$ under $\gamma$
+where $\vec{a} \in Q$ iff $C_n[\gamma \mathcal{A}](\Omega (\gamma \vec{a})) =
+1$.
 
@@
 \end{definition}
-In general, the evaluation of a circuit depends on the presentation of the
-structure (i.e. on the chosen bijection $\gamma$). If family of $(\mathcal{B},
-\tau)$-circuits $\mathcal{C}$ is invariant it follows that the query computed is
-a $q$-query on $\tau$-structures. It follows that if $q = 0$ then $\mathcal{C}$
-computes a property of $\tau$-structures. The following lemma allows us to
-recast this notion in terms of the language developed in this paper.
+
+In other words $C_n$ is invariant if the evaluation of the circuit on any
+$n$-element structure $\mathcal{A}$ does not depend on the particular map
+$\gamma$ that takes the universe of the structure to $[n]$. In general, the
+evaluation of a circuit depends on the presentation of the structure (i.e.\ the
+bijection $\gamma$). If a family of $(\mathcal{B}, \tau)$-circuits $\mathcal{C}$
+is invariant it follows that the query computed is a $q$-query on
+$\tau$-structures. Thus if $q = 0$ then $\mathcal{C}$ computes a property of
+$\tau$-structures. The following lemma allows us to recast this notion in terms
+of the language developed in this paper.
 
@@
   Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit. The function computed by $C_n$ is
-  isomorphism-invariant iff $C_n$ is invariant.
+  $\tau$-invariant iff $C_n$ is an invariant circuit.
 \end{lem}
+% AD - does this require a few lines of proof? To be added
 
-For the sake of simplicity, from now on we assume the that all circuits take in
-structures over a single-sorted vocabulary.
+% \begin{definition}[Automorphism]
+%   let $C = \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a
+%   $(\mathbb{B},\tau)$-circuit computing a $q$-ary query on structures of size
+%   $n$, and where $\mathbb{B}$ is a basis of isomorphism-invariant structured
+%   functions. Let $\sigma \in \sym_n$ and $\pi: G \rightarrow G$ be a bijection
+%   such that
+%   \begin{itemize}
+%     \setlength\itemsep{0mm}
+%   \item for all output tuples $x \in [n]^q$, $\pi \Omega (x) = \Omega (\sigma
+%     x)$,
+%   \item for all gates $g \in G$, let $\Sigma (g) = \Sigma (\pi g)$,
+%   \item for each relational gate $g \in G$, $\sigma \Lambda (g) = \Lambda (\pi
+%     g)$, and
+%   \item For each pair of gates $g, h \in G$ $W(h,g)$ iff $W(\pi h, \pi g)$ and
+%     for each internal gate $g$ we have that $L(\pi g)$ and $ \pi \cdot L(g)$
+%     are isomorphism-equivalent.
+%   \end{itemize}
+%   We call $\pi$ an \emph{automorphism} of $C$, and we say that $\sigma$
+%   \emph{extends to an automorphism} $\pi$. The group of automorphisms of $C$
+%   is called $\aut (C)$.
+% \end{definition}
 
@@
   $(\mathbb{B},\tau)$-circuit computing a $q$-ary query on structures of size
-  $n$, and where $\mathbb{B}$ is a bases of sort-symmetric functions. Let
-  $\sigma \in \sym_n$ and $\pi: G \rightarrow G$ be a bijection such that
+  $n$, and where $\mathbb{B}$ is a basis of isomorphism-invariant structured
+  functions. Let $\sigma \in \sym_n$ and $\pi: G \rightarrow G$ be a bijection
+  such that
   \begin{itemize}
     \setlength\itemsep{0mm}
-  \item for all gates $g, h \in G$, $W(g,h)$ iff $W(\pi g, \pi h)$,
   \item for all output tuples $x \in [n]^q$, $\pi \Omega (x) = \Omega (\sigma
@@
     g)$, and
-  \item for each internal gate $g$ then we have that $L(\pi g)$ and $ \pi \cdot
-    L(g)$ are sort-equivalent.
+  \item For each pair of gates $g, h \in G$ $W(h,g)$ if and only if $W(\pi h,
+    \pi g)$ and for each internal gate $g$ we have that $L(\pi g)$ and $ \pi
+    \cdot L(g)$ are isomorphism-equivalent.
   \end{itemize}
   We call $\pi$ an \emph{automorphism} of $C$, and we say that $\sigma$
-  \emph{extends to the automorphism} $\pi$. The group of automorphisms of $C$ is
-  called $\aut_n (C)$.
+  \emph{extends to an automorphism} $\pi$. The group of automorphisms of $C$ is
+  called $\aut (C)$.
 \end{definition}
@@
   A circuit $C$ on structures of size $n$ is called \emph{symmetric} if every
-  $\sigma \in \sym_n$ induces an automorphism on $C$.
+  $\sigma \in \sym_n$ extends to an automorphism on $C$.
 \end{definition}
 
-It follows for any symmetric circuit $C_n$ there is a homomorphism $h$ that maps
-$\sym_n$ to $\aut_n(C)$. This homomorphism is injective so long as a single
-element of $[n]$ appears in the in the label of some input gate of $C$ (as then
-all elements appear by symmetry)\cite{AndersonD17}. In this paper we always
-assume that there is at least one such element, as otherwise all inputs are
-constant, and so the circuit just computes a constant function. In order to
-assure this homomorphism is surjective Anderson and Dawar \cite{AndersonD17}
-introduce the notion of a \emph{rigid} circuit.
+It follows that for any symmetric circuit $C_n$ there is a homomorphism $h$ that
+maps $\sym_n$ to $\aut(C)$, taking any $\sigma \in \sym_n$ to an automorphism
+that extends it. Such a homomorphism is injective so long as some element of
+$[n]$ appears in a label of some input gate of $C$ (as then all elements appear
+by symmetry)~\cite{AndersonD17} and therefore no two distinct elements of
+$\sym_n$ agree on all input gates. In this paper we always assume that this is
+the case, as otherwise all inputs are constant, and so the circuit just computes
+a constant function. In order to develop a great many technical tools needed in
+this paper we should like to be able to, without a loss of generality, assume
+that that this homomorphism is in fact an isomorphism as well. In order to do so
+we make use of the rigidity condition.
 
-\begin{definition}[Rigidity]
-  Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit, where $C_n = \langle G, W,
-  \Omega, \Sigma, \Lambda, L\rangle$. Say that $C_n$ is \emph{rigid} if there
-  are no distinct internal gates $g, g' \in G$ such that $\Sigma(g) = \Sigma
-  (g')$, $\Omega^{-1}(g) = \Omega^{-1}(g')$, $H_g = H_{g'}$ and $L(g')$ and
-  $L(g)$ are sort-equivalent.
+We define rigidity in terms of an equivalence relation on the gates of a
+circuit. This recursively defined equivalence relation holds between two gates
+if the circuit underneath these two gates are in some sense the same. Before we
+define this relation we need to introduce some notation.
+
+% When analysing circuits we are often interested in identifying families of
+% gates that We are interested not just in the case where the labelling function
+% $L(g)$ is an injection but when there are no two gates in its image that are
+% in some broader sense the same. Of course we cannot efficiently decide if two
+% gates in a circuit compute the same function (unless SAT is in $\P$). We may,
+% however, consider a weaker relation on gates -- a syntactic condition which
+% encodes the idea that the circuits underneath two gates are in some sense the
+% same. We define this notion formally below. Before we do we define what it
+% means for two functions to be isomorphism-equivalent up to an equivalence
+% relation.
+
+% We will often be interested in the case where two functions are
+% isomorphism-equivalent up to syntactic equivalence. We define this notion (for
+% an arbitrary equivalence relation) below.
+
+\begin{definition}
+  Let $\tau$ be a many-sorted vocabulary and $D$ be a $\tau$-sorted set. Let X
+  be a set and $\sim$ be an equivalence relation defined on $X$. Let $Y, Z
+  \subset X$. We say two functions $f : \ind(\tau,D) \rightarrow X$ and $g :
+  \ind(\tau, D) \rightarrow Y$ are \emph{isomorphism-equivalent up to $\sim$} if
+  $Y/{\sim} = X/{\sim}$ and $f/{\sim}$ is isomorphism-equivalent to $g/{\sim}$.
 \end{definition}
 
-Another property which simplifies our analysis is the property of having
-\emph{bijective labels}.
+\begin{definition}
+  Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit such that $C_n = \langle G, W,
+  \Omega, \Sigma, \Lambda, L\rangle$. We recursively define the equivalence
+  relation \emph{syntactic equivalence}, which we denote using the symbol
+  `$\equiv$', on $G$ as follows. We say $g \equiv h$ if (i) $\Sigma(g) =
+  \Sigma(h)$, (ii) if $g$ and $h$ are constant gates then they are equal, (iii)
+  if $g$ and $h$ are relational gates then $\Lambda(g) = \Lambda(h)$, (iv) if
+  $g$ and $h$ are internal gates then the functions $L(g)$ and $L(h)$ are
+  isomorphism-equivalent up to syntactic equivalence, and (v) if $g$ and $h$ are
+  output gates then $\Omega^{-1}(g) = \Omega^{-1}(h)$.
+\end{definition}
+
+We have already required that for each gate $g$ in a circuit must have an
+injective labelling function. The following condition ensures that $L(g)/{\sim}$
+is also an injection.
 
 \begin{definition}
-  We say that a circuit $C$ has \emph{bijective labels} if for each gate $g$ in
-  $C$, $L(g)$ is a bijection.
+  Let $C_n$ be a circuit and $g$ be a gate in $C_n$. We say $g$ has \emph{unique
+    labels} if $\vert H_g \vert = \vert H_g \setminus \equiv \vert $. We say
+  that the circuit $C_n$ has \emph{unique labels} if every gate in $C_n$ has
+  unique labels.
 \end{definition}
 
-We prove in a later section that a circuit may be transformed in polynomial time
-into an equivalent circuit that is both rigid and has bijective labelings. Hence
-we may assume these two properties without a loss of generality.
-
-With the assumption of rigidity in place, we abuse notation for permutations and
-let $\sigma \in \sym_n$ also denote the induced automorphism.
-
-We finally want to define a circuits that allow for gates labelled by
-matrix-symmetric functions.
+We are also ready to define what it means for a circuit to be rigid.
 
 \begin{definition}
-  Let $\mathbb{B}$ be a basis containing the single-sorted structured functions
-  that compute $\land$, $\lor$, $\neg$ and $\maj$ and such that all elements of
-  this basis are either matrix-symmetric or simple unary. We call a
-  $(\mathbb{B}, \tau)$-circuit a \emph{symmetric matrix-circuit}.
+  We say that a circuit $C_n$ is \emph{rigid} if every equivalence class of
+  gates under the syntactic equivalence relation is a singleton.
 \end{definition}
 
-We define a circuit that has gates that compute rank.
+We prove in Proposition~\ref{} that there is a polynomial time algorithm that
+takes in a symmetric circuit with unique labels and outputs an equivalent rigid
+circuit. It is worth noting that the requirement that the circuit have unique
+labels is very important (see Section \ref{} for a detailed discussion of this
+point). Since we are interested in $P$-uniform families of circuits, this result
+allows us to assume the rigidity of a circuit without a loss of generality.
+Moreover, as we will show in Proposition \ref{}, if a circuit is rigid then
+every $\sigma \in \sym_n$ has exactly one an extension to an automorphism of
+$C_n$, and so the above defined homomorphism mapping $\sym_n$ to $\aut(C_n)$ is
+an isomorphism. Since we may assume rigidity without a loss of generality this
+property may also be assumed without a loss of generality. As such we abuse
+notation and let $\sigma \in \sym_n$ also denote the induced automorphism of the
+circuit.
+
+% \begin{definition}[Rigidity]
+%   Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit, where $C_n = \langle G, W,
+%   \Omega, \Sigma, \Lambda, L\rangle$. Say that $C_n$ is \emph{rigid} if there
+%   are no distinct internal gates $g, g' \in G$ such that $\Sigma(g) = \Sigma
+%   (g')$, $\Omega^{-1}(g) = \Omega^{-1}(g')$, $H_g = H_{g'}$, and $L(g')$ and
+%   $L(g)$ are isomorphism-equivalent.
+% \end{definition}
+
+Let $\MB$ be the set of all structured functions that are symmetric or
+matrix-invariant. Let $r, p \in \nats$, with $p$ prime, and let $D_1$ and $D_2$
+be initial segments of the natural numbers. Then there is a matrix-invariant
+structured function $F^{\rank}_{p,r}: \{0,1\}^{D_1 \times D_2}$, with universe
+$D_1 \uplus D_2$, such that $F^{\rank}_{p,r}(M) = 1$ if, and only if, the matrix
+$M \in \{0,1\}^{D_1 \times D_2}$ has rank at most $r$ when its entries are
+understood as elements of the finite field $\mathbb{F}_p$. Let
+$\mathbb{B}_\rank$ be the union of the set of all such functions with
+$\mathbb{B}_{\maj}$.
+
 \begin{definition}
-  Let the $(\mathbb{B}, \tau)$-circuit $C$ be a matrix-symmetric circuit. Let
-  $\mathbb{B}_m \subseteq \mathbb{B}$ consist of all matrix-symmetric functions
-  that are not symmetric. For any non-empty sets $A_1, A_2$ and $r, p \in
-  \mathbb{N}$, where $p$ prime define a $F_{p,r}: \{0,1\}^{A_1 \times A_2}
-  \rightarrow \{0,1\}$ such that $f_{p,r}(M) = 1$ iff the matrix $M: A_1 \times
-  B_1 \rightarrow \{0,1\}$ has rank at least $r$ over the field $\mathbb{F}_p$.
-  We call such a function a \emph{bounded-rank function}. If $\mathbb{B}_m$ is
-  equal to the set of all such bounded-rank functions, then we call $C$ a
-  \emph{symmetric rank-circuit}.
+  Let $\mathbb{B} \subseteq \MB$. We call a symmetric $(\mathbb{B},
+  \tau)$-circuit with unique labels a \emph{symmetric matrix-circuit}.
+\end{definition}
+
+\begin{definition}
+  Let $\mathbb{B} \subseteq \MB$. We call a symmetric $(\mathbb{B}_\rank,
+  \tau)$-circuit with unique labels a \emph{symmetric rank-circuit}.
 \end{definition}
@@
 % \end{definition}
+We are now ready to state the main theorem of this paper.
 
-We are now ready to state what will be the main theorem of this paper.
 \begin{thm}[Main Theorem]
-  A graph property is decidable by a $P$-uniform family of symmetric circuits
-  with rank gates if, and only if, it is definable by an $\FPR$ sentence.
+  A graph property is decidable by a $P$-uniform family of symmetric
+  rank-circuits if, and only if, it is definable by an $\FPR$ sentence.
 \end{thm}
 
+% Anderson and Dawar use the above proposition (or, rather, an analogous
+% relation) in order to
+
+% an automorphism of a circuit $C_n$ from the elements to $\aut(C_n)$. In the
+% following sections this fact
+
+% It is worth noting that in general computing the syntactic equivalence
+% relation in polynomial time may not be possible. In fact, given two bipartite
+% graphs it is possible to construct (in time polynomial in the size of the
+% graphs) a circuit with gates labelled by matrix-symmetric functions such that
+% two specified gates are syntacticly equivalent if,and only if, the two
+% bipartite graphs are isomorphic. Since there is a polynomial time reduction
+% from the graph isomorphism problem to the graph isomorphism problem on
+% bipartite graphs, it follows that there is a polynomial time reduction from
+% the graph isomorphism to the problem of computing syntactic equivalence. We
+% formalise this result in the following proposition, and give the explicit
+% construction referenced.
+
 \subsection{Limitations of Symmetric Bases}
-When looking at symmetric circuits with matrix symmetric functions, it is
-natural to ask if this extension to matrix-symmetric functions is really
-necessary. In this section we show that Symmetric circuits, as developed by
-Anderson and Dawar, defined over the usual basis with majority gates can compute
-any symmetric function over polynomial size circuits. As such no additional
-symmetric function added to the Basis improves the power of the model.
+In this section we show that any family of symmetric circuits over an arbitrary
+basis of symmetric functions can be transformed in polynomial time into a family of
+symmetric circuits that decide the same language but are defined over the basis
+$\mathbb{B}_\maj$.  In other words, it makes no difference to the
+expressive power of such circuits whether we include \emph{all}
+symmetric functions in the basis or just $\mathbb{B}_\maj$.
+It follows that in order to construct $P$-uniform families of
+symmetric circuits that define queires not in $\FPC$, we need to
+consider bases with non-symmetric functions.
 
-Recall from Anderson and Dawar \cite{AndersonD17} we have that
-$\mathbb{B}_{\std} = \{ \neg , \wedge , \lor \}$ and $\mathbb{B}_\maj = \{ \maj
-\} \cup \mathbb{B}_{\std}$.
+% Recall from Anderson and Dawar \cite{AndersonD17} we have that
+% $\mathbb{B}_{\std} = \{ \neg , \wedge , \lor \}$ and $\mathbb{B}_\maj = \{
+% \maj \} \cup \mathbb{B}_{\std}$.
 
-Let $F = (F_n: \{0,1\}^n \rightarrow \{0,1\})_{n \in \mathbb{N}}$ be a family of
-symmetric Boolean functions. Recall that for any $n \in \mathbb{N}$, the output
-of $F_n$ is entirely determined by the number of 1's in its input. Then let
-$c_{F}:\mathbb{N} \rightarrow 2^{\mathbb{N}}$ define a function where $c_{F}(n)$
-is the set of all $m \leq n$ such that for all $\vec{x} \in \{ 0,1 \}^n$ with
-$m$ 1's we have $F_n (\vec{x}) = 1$. Clearly any symmetric Boolean function
-$F_n$ is entirely determined by $c_{F}(n)$, and so $F$ is entirely determined by
-$C_F$.
+Let $F : \{0,1\}^n\rightarrow \{0,1\}$ be a symmetric Boolean function. Recall
+that the output of $F$ is entirely determined by the number of $1$s in its
+input. Let $c_{F} \subseteq [n]$ be the set of all $m \leq n$ such that for
+all $\vec{x} \in \{ 0,1 \}^n$ with $m$ $1$s we have $F (\vec{x}) = 1$. Clearly
+any symmetric function $F$ is entirely determined by $c_{F}$. As such, $F$
+may be encoded by a tuple $f \in \{0,1\}^{n}$, where $f (i) = 1 $ iff $i
+\in c_{F}$. We assume this encoding below.
 
@@
   \label{prop:fuctions-maj}
-  Let $F = (F_n: \{0,1\}^n \rightarrow \{0,1\})_{n \in \mathbb{N}}$ be a family
-  of symmetric functions. There exists a family of Boolean circuits $(C_n)_{n
-    \in \mathbb{N}}$ defined over $\mathbb{B}_\maj$ computing $F$. Moreover,
-  $(C_n)_{n \in \nats}$ has depth at most $5$ and width at most $2n+2$ and size
-  at most $8n + 3$.
+  There is a deterministic algorithm that outputs for each symmetric function
+  $F: \{0,1\}^n \rightarrow \{0,1\}$ (encoded as a binary $n$-tuple as above) a symmetric circuit $C$ defined over
+  the basis $\mathbb{B}_\maj$ that computes $F$. Moreover, this function is
+  computable in time polynomial in $n$ and the circuit $C$ has depth at most
+  $5$, width at most $2n+2$ and size at most $5n + 3$.
 \end{prop}
@@
 \begin{proof}
-  We define the circuit $C_n$ with $n$ input gates denoted by $x_1, \ldots, x_k$
-  by successively adding gates. For $a \in \mathbb{N}$ we add an `and' gate
-  $\countgate_a$, and a number of `majority' and `not' gates, wiring them up as
-  follows:
+  We have $c_{F}$ from the input. We now define $C$. We define the set of
+  gates and wires of $C$ layer by layer as follows. The first layer consists
+  of just the $n$ input gates labelled by the variables $x_1, \ldots , x_n$. The
+  second layer consists of two `majority' gates for each $a \in c_{F}$, which
+  we denote by $\maj_a$ and $\maj^{\neg}_a$. For each $a \in c_{F}$ there is
+  one wire from each of $x_1, \ldots , x_n$ to $\maj_a$ and $\maj^{\neg}_a$. For
+  all $a \geq \frac{n}{2}$, there are $2a - n$ wires from $0$ to $\maj_a$ and
+  $2a - n + 2$ wires from $0$ to $\maj^{\neg}_a$. For all $a < \frac{n}{2}$
+  there are $n - 2a$ wires from $1$ to $\maj_a$ and $n - 2a - 2$ wires from $1$
+  to $maj^{\neg}_a$. The third layer consists of one `not' gate for each $a \in
+  c_{F}$, which we denote by $\neg_a$. For each $a \in c_{F}$ there is a
+  wire from $\maj^\neg_a$ to $\neg_a$. The fourth layer consists of one `and'
+  gate for each $a \in c_{F}$, which we denote by $\countgate_a$. For each $a
+  \in c_{F}$ there is a wire from each of $\maj_a$ and $\neg_a$ to
+  $\countgate_a$. The fifth layer consists of just a single `or' gate,
+  designated as the output gate, and for each $a \in c_{F}$ there is a wire
+  from $\countgate_a$ to the output gate.
+
+  We summarise the circuit up to the fourth layer as follows:
   \[
@@
   \]
+  We note that for an input vector $\vec{x}$, $count_a$ evaluates to 1 if, and
+  only if, the number of 1's in $\vec{x}$ equals $a$. Thus we have that $C$
+  evaluates to 1 if, and only if, there exists $a \in c_{F}$ such that the
+  number of $1$'s in $\vec{x}$ equals $a$ if, and only if, $F (\vec{x}) = 1$.
+  Moreover, it is easy to see that $C$ is symmetric and the algorithm defined
+  runs in time polynomial in $n$.
+%AD - perhaps include a brief argument for why C is symmetric?
 
-  Clearly $\vert c_F(n) \vert \leq n$, for each $a \in c_F(n)$ we have added
-  four gates, so thus far the circuit's width is at most $2n + 2$ (2 extra for
-  the possible inclusion of constant gates) and depth at most $4$. Now add to
-  $C_n$ a `or' gate $g$ and connect the output of $\countgate_a$ to the input of
-  $g$ for each $a \in c_F(n)$. Mark $g$ as the output gate for $C_n$.
-
-  It is easy to see that $C_n$ has depth at most $5$, width at most by $2n + 2$
-  and size at most $1 + 4(2n) + 2 = 8n+3$. We have that in each layer of
-  $C_{g'}$ each gate is connected to all gates in the previous layer, and as
-  such the circuit is symmetric.
+  Furthermore, notice that the first layer contains $n$ gates and the second
+  layer contains at most $2 \vert c_{F} \vert \leq 2n$ gates. The third and
+  fourth layer each contain at most $n$ gates. As such $C$ has size at most $n
+  + 2n + 2n + 1 + 2 = 5n +3$ (the additional 2 is for the constant gates). The
+  width of $C$ is at most $2n + 2$, and the depth is at most $5$.
 \end{proof}
 
-The above proposition has a straight forward application to circuit
-characterisations.
-
 \begin{thm}
-  Let $\mathcal{F} = \{F_i : i \in I \}$, where $F_i$ is a family of symmetric
-  Boolean functions.
-
-  Let $(C_n)_{n \in \mathbb{N}}$ be family of symmetric circuits over the
-  Boolean basis $\mathbb{B}_{\std} \cup (\bigcup_{i \in I} F_i)$, where $C_n$ is
-  a circuit on structures of size $n$, and the size of each circuit in the
-  family is bounded by some function $f(n)$. Then there exists a family of
-  symmetric circuits $(C_n')_{n \in \mathbb{N}}$ over $\mathbb{B}_\maj$, where
-  $C_n'$ is a circuit on structures of size $n$ and $\vert C_n' \vert \leq
-  (8f(n) + 3) f(n))$.
+  Let $\mathbb{B}$ be a basis of symmetric functions and let $(C_n)_{n \in
+    \mathbb{N}}$ be a family of symmetric circuits defined over the basis $\mathbb{B}$. Then there exists a family
+  of symmetric circuits $(C_n')_{n \in \mathbb{N}}$ defined over
+  $\mathbb{B}_\maj$ that decides the same language. Moreover, the map $C_n
+  \mapsto C_n'$ is polynomial-time computable and for each $n \in \nats$, $\vert
+  C_n' \vert \leq (5 \cdot \vert C_n \vert + 3) \cdot \vert C_n \vert$.
 \end{thm}
@@
 \begin{proof}
-  From $C_n$ we construct $C_n'$ as follows. For each gate $g \in C_n$ of
-  labelled by a member of $F_i$ we have a symmetric circuit $C_g$ from
-  Proposition \ref{prop:function-maj} that computes the same function as $g$.
-  Then let $C_n'$ be $C_n$ but with each gate $g$ replaced by $C_g$. It is easy
-  to see that $C_n'$ is symmetric. We also have that each gate $g$ must have at
-  most $f(n)$ inputs, and so the size of $C_g$ is bounded by $8f(n) + 3$. Thus
-  the size of $C_n'$ is bounded by $(8f(n)+3) f(n)$.
+  From $C_n$ we construct $C_n'$ as follows. For each gate $g \in C_n$ 
+  labelled by a member of $\mathbb{B}$ we have a symmetric circuit $C_g$ from
+  Proposition~\ref{prop:function-maj} that computes the same function as $g$.
+  Then let $C_n'$ be as $C_n$ but with each gate $g \in C_n$ replaced by $C_g$.
+  It is easy to see that $C_n'$ is symmetric. We also have that each gate $g$
+  must have at most $\vert C_n \vert$ inputs, and so the size of $C_g$ is
+  bounded by $5 \vert C_n \vert + 3$. Thus the size of $C_n'$ is bounded by
+  $(5f(n)+3) f(n)$. This algorithm clearly runs in polynomial-time.
 \end{proof}
@@
 This result gives us that for any family of circuits over an arbitrary basis of
-symmetric functions we can can construct another circuit family computing the
-same function over the majority basis without a blowup in size. As such, we know
-that we cannot extend the power of the symmetric circuits studied by Anderson
-and Dawar \cite{AndersonD17} by simply considering alternative bases of
-symmetric functions. This result, combined with the main result of this paper,
-gives us that symmetric circuits with rank are a strictly more powerful model
-than any circuit model defined over a basis of symmetric functions.
-
+symmetric functions we can construct another symmetric circuit family
+computing the same function over the majority basis without a blowup in size.
+Moreover, we also have that if the first family was uniform the second family
+will be as well. As such, we cannot extend the power of the $P$-uniform
+symmetric circuits families studied by Anderson and Dawar \cite{AndersonD17} by
+simply considering alternative bases of symmetric functions, thus motivating the
+generalisation developed in the previous subsection to non-symmetric functions.
 \end{document}

### 2017-11-13 sections/translating-formulas-to-cicuits.tex
13-Nov-2017

\documentclass[../paper.tex]{subfiles}
\begin{document}

\subsection{Circuit Manipulation}
In this section and the next we develop a number of results that reference
$P$-uniform families of circuits. In order to prove these results we often need
to define polynomial-time algorithms for generating or manipulating circuits. In
this subsection we define a number of algorithms that perform commonly invoked
operations on circuits.

We often include quotes around the names of these algorithm in order to avoid
any confusion. We assume a reasonable encoding of the circuit.

The algorithm \emph{merge} takes a circuit and an appropriate set of gates and
produces a new circuit by combining those gates into a single gate.

\begin{definition}
  The algorithm \emph{merge} takes as input a circuit $C = \langle G, \Omega,
  \Sigma , \Lambda, L \rangle$ and a set of syntactically equivalent gates $H =
  \{h_1, \ldots , h_p\}$ and outputs a new circuit $C' = \langle G', \Omega',
  \Sigma', \Lambda', L' \rangle$, where
  \begin{itemize}
    \setlength\itemsep{0mm}
  \item $G' = G \setminus \{h_2, \ldots, h_q\}$,
  \item $\Omega' = \Omega$,
  \item $\Sigma' = \restr{\Sigma}{G'}$,
  \item $\Lambda' = \Lambda$, and
  \item For all $g \in G'$ and $\vec{a} \in Ind(g)$ if $L(g) (\vec{a}) \in H$
    then $L'(g)(\vec{a}) = h_1$ and if $L(g)(\vec{a}) \notin H$ then
    $L'(g)(\vec{a}) = L(g)(\vec{a})$.
  \end{itemize}
\end{definition}

It can be shown that `merge' can be implemented so as to run in time polynomial
in the size of the input circuit. We note that if the input circuit to `merge'
is symmetric (resp. has unique labels) then the output circuit will also be
symmetric (resp. have unique labels). The input and output circuits compute the
same function.

% Moreover, if we run merge on a circuit $C$ and a set $H$ then if $C$ has
% unique labels and $H$ has the property that there is no gate $g$ in $C$ such
% that two elements of $H$ are in $H_g$ then if $C$ has unique labels then so
% does $C'$. Moreover, if $C$ is symmetric then so is $C'$.

The algorithm \emph{separate-labels} takes a circuit and outputs an equivalent
circuit such that every symmetric-gate has unique labels.

\begin{definition}
  The algorithm \emph{separate-labels} takes as input a $(\mathbb{B},
  \tau)$-circuit $C := \langle G, \Omega, \Sigma , \Lambda, L \rangle$ and
  outputs circuit $C' = \langle G', \Omega', \Sigma', \Lambda', L' \rangle$. We
  now describe how these values are derived. We have that $\Omega' = \Omega'$
  and $\Lambda' = \Lambda$. We start with $G' = G$, $\Sigma' = \Sigma$ and $L' =
  L$ and updates their definitions iteratively according to the following
  procedure.

  Let $k$ denote a variable initialised to $1$. Let $S$ be the set of all gates
  of height $k$ that are symmetric-gates. For each $h_1 \in \bigcup_{g \in
    S}H_g$ let $g \in S$ be the first gate (using the order of the circuit
  derived from its encoding) such that $\vert L(g)^{-1}(h_1) \vert$ is maximal.
  Let $\{a_1, \ldots, a_p\} := L(g)^{-1}(h_1)$ (again, making use of the order).
  We add to $G'$ the gates $\{h_2, \ldots, h_p\}$ and for each $i \in \{2,
  \ldots, p\}$ we set $\Sigma'(h_i)$ such that $h_i$ is a $\land$ gate with a
  single output and $L'(h_i)$ such that $h_i$ takes only $h_{i-1}$ as an input.
  For each $g' \in S$ such that $h_1 \in H_g$ let $\{ b_1, \ldots, b_q \} :=
  L(g)^{-1}(h_1)$. For each $i \in [q]$ let $L'(g')(b_i) = h_i$. Iterate $k$ and
  repeat this procedure until $k$ exceeds the depth of the circuit.
\end{definition}

It can be shown that `separate-labels' can be implemented so as to run in time
polynomial in the size of the input circuit. We note that both the input and
output circuits compute the same function. Moreover, if all of the non-symmetric
gates in the input circuit have unique labels then the output circuit will have
unique labels. If the input circuit is symmetric and has the property that every
non-symmetric gate in the circuit has unique labels then the output circuit is
symmetric.

% Notice that for a given circuit $C$ and a symmetric-gate $g$ in $C$, running
% `merge' on each equivalence class of syntactically equivalent gates input to
% $g$ and then running `separate-labels' on the resultant circuit produces
% circuit $C'$ computing the same function as $C$ but the gate $g$ in $C$ has
% unique labels.

The algorithm \emph{insert} takes as input two circuits and creates a new
circuit formed by inserting the gates of the first circuit into the second
circuit.

\begin{definition}
  The algorithm \emph{insert} takes as input a $(\mathbb{B}_1, \tau_1)$-circuit
  $C^1 := \langle G_1, \Omega_1, \Sigma_1 , \Lambda_1, L_1 \rangle$ and a
  $(\mathbb{B}_2, \tau_2)$-circuit $C^2 := \langle G_2, \Omega_2, \Sigma_2 ,
  \Lambda_2, L_2 \rangle$ and outputs a $(\mathbb{B}_1 \cup \mathbb{B}_2, \tau_1
  \uplus \tau_2)$-circuit $C = \langle G, \Omega, \Sigma , \Lambda, L \rangle$
  such that
  \begin{itemize}
    \setlength\itemsep{0mm}
  \item $G = G_1 \uplus G_2$,
  \item $\Omega = \Omega_2$,
  \item $\Sigma = \Sigma_1 \uplus \Sigma_2$,
  \item $\Lambda = \Lambda_1 \uplus \Lambda_2$, and
  \item $L = L_1 \uplus L_2$.
  \end{itemize}
\end{definition}

It can be shown that `insert' can be implemented so as to run in time polynomial
in the size of the input circuit. If the input circuits are symmetric then the
output circuit will be symmetric.

The operation \emph{replace} removes a gate from a circuit and replaces it with
another gate.

\begin{definition}
  Formally, \emph{replace} is an algorithm that takes as input a circuit $C =
  \langle G, \Omega, \Sigma, \Lambda, L\rangle$ and a pair of gates $(g_1, g_2)$
  in $C$ and outputs a circuit $C' = \langle G', \Omega', \Sigma', \Lambda', L'
  \rangle$ such that
  \begin{itemize}
    \setlength\itemsep{0mm}
  \item $G' = G \setminus \{g_1\}$,
  \item $\Omega'$ is an function from the domain of $\Omega$ to $G'$ such that
    for each $\vec{a} \in \dom(Omega)$ if $\Omega(\vec{a}) = g_1$ then
    $\Omega'(\vec{a}) = g_2$ and if then $\Omega'(\vec{a}) = \Omega(\vec{a})$.
  \item $\Sigma' = \restr{\Sigma}{G'}$
  \item $\Lambda' = \restr{\Lambda}{G'}$
  \item For each $g \in G'$ and each $\vec{a} \in \ind(g)$ if $L(g)(\vec{a}) =
    g_1$ then $L'(g)(\vec{a}) = g_2$ and if not then $L'(g)(\vec{a}) =
    L(g)(\vec{a})$.
  \end{itemize}
\end{definition}

It can be shown that `replace' can be implemented so as to run in time
polynomial in the size of the input circuit.

The algorithm \emph{tag} takes in a circuit, a gate in that circuit, a relation
symbol and a tuple and outputs a circuit computing but with an additional
gadget, constructed using the gates labelled by the given relation symbol and
tuple, marking the designated gate. The idea is that marking a gate can be used
as a step to ensure unique labels in a circuit.

\begin{definition}
  The algorithm \emph{tag} takes in a $(\mathbb{B}, \tau)$-circuit $C_n :=
  \langle G, \Omega, \Sigma, \Lambda, L \rangle$, a relation symbol $R \in
  \tau$, a gate $g \in G$ and a tuple $\vec{a} \in [n]^k$ for some $k$ and
  outputs the circuit $C_n' = \langle G', \Omega', \Sigma', \Lambda', L'\rangle$
  defined by the following algorithm. Let $G' = G \uplus \{\land_g, \land_{g'},
  \land_1, \ldots , \land_k\}$, $\Omega' = \Omega$, and $\Lambda' = \Lambda$.
  Define $L'$ and $\Sigma'$ as follows. For each $g \in G$ $\Sigma'(g) =
  \Sigma(g)$. For each $g \in \{\land_0, \land_1, \ldots , \land_k \}$,
  $\Sigma(g)$ is an $\AND$-gate that takes in two inputs. $\Sigma(\land_g)$ is
  an $\AND$-gate that takes in a single input. Set $g$ to be the lone input to
  $\land_g$. Set the two inputs to $\land_0$ to be $\land_g$ and $\land_1$. For
  each $i \in [k-1]$ set the inputs of $\land_i$ to be $\land_{i+1}$ and the
  gate $g_i \in G'$ such that $\Sigma(g_i) = R$ and $\Lambda^{-1}(g_i) =
  \vec{a}_i$, where $\vec{a}_i$ is the $k$-tuple $(\vec{a}(i), \ldots,
  \vec{a}(i))$. Set the inputs of $\land_k$ to be the constant gate $1$ and the
  gate $g_k$ such that $\Sigma(g) = R$ and $\Lambda^{-1}(g_k) = \vec{a}_k$.

  For each gate $h \in G \setminus \{g\}$ and $\vec{b} \in \ind(h)$, if
  $L(h)(\vec{b}) = g$ then let $L'(h)(\vec{b}) = \land_0$, otherwise let
  $L'(h)(\vec{b}) = L(h)(\vec{b})$.

\end{definition}

It can be shown that `tag' can be implemented so as to run in time polynomial in
the size of the input. The input and output circuits compute the same function.
Moreover, if the input circuit had unique labels then the output circuit will
have unique labels. In the event that the input relation symbol is obvious from
the context we omit it when invoking this algorithm.

The algorithm \emph{glue-circuits} takes in a designated circuit and another set
of appropriate circuits and forms a new circuit by replacing the relational
gates of the designated circuit with the output gates of the circuits in the
given set.

\begin{definition}
  The algorithm \emph{glue-circuits} takes as input a set of relation symbols
  $\tau_R := \{R_1, \ldots, R_t\}$ and $t+1$ circuits $\{C^0, \ldots, C^{t}\}$,
  where $C^0 = \langle G_0, \Omega_0, \Sigma_0, \Lambda_0, L_0 \rangle$ is a
  $(\mathbb{B}, \tau)$-circuit with $\tau_R \subseteq \tau$ and for each $i \in
  [t]$, $C^i = \langle G_i, \Omega_i, \Sigma_i, \Lambda_i, L_i \rangle$ is a
  $(\mathbb{B}_i, \tau_i)$-circuit computing a query of arity $\arty(R_i)$. The
  algorithm outputs, for a given input, a circuit $C = \langle G, \Omega,
  \Sigma, \Lambda, L\rangle$ constructed as follows. Let $C^0' := C^0$. For each
  $i \in [t]$ fix a relation symbol $V_i \in \tau_i \setminnus \tau_R$. For each
  $i \in [t]$ construct the circuit $C^{i}' = \langle G_i', \Omega_i',
  \Sigma_i', \Lambda_i', L_i' \rangle $ by `inserting' $C^i$ into $C^{i-1}'$,
  and call the resultant circuit $D^{i-1}'$. For each relational gate $g$ in
  $D^{i-1}$ labelled by the symbol $R_i$, `replace' $g$ with the gate
  $\Omega_{i}(\Lambda_{i-1}'(g))$ in $D^{i-1}$ and `tag' the gate
  $\Omega_i(\Lambda_{i-1}'(g))$ in $D^{i-1}$ using the tuple $\Lambda_{i-1}'(g)$
  and the relation symbol $V_i$. Output the circuit $C := C^t'$.
\end{definition}

It can be shown that `glue-circuits' can be implemented so as to run in time
polynomial in the combined size of the input circuits. Moreover, if the input
circuits are all symmetric (resp. have unique labels) then the output circuit
will be symmetric (resp. have unique labels). We sometimes refer to `gluing'
$(C^1, \ldots, C^t)$ into $C^0$ along $(R_1 , \ldots , R_t)$ when invoking
`glue-circuit' on the input $(C^0, \ldots , C^t)$ and $\tau_R = \{R_1, \ldots ,
R_t\}$.

\subsection{Unique Labels and Rigidity}
In contrast with the work of Anderson and Dawar~\cite{}, the circuit families we
use to establish our main result are additionally required to have unique
labels. In this subsection we briefly discuss this inclusion, and present
results suggesting its importance.

It is important to note that our analysis of circuits depends crucially on the
fact that a circuit may be transformed (in polynomial time) into an equivalent
circuit with the property that each element of $\sym_n$ induces a unique
automorphism on the circuit $C_n$. This fact ensures a canonical action of
$\sym_n$ on the circuit $C_n$ and is a crucial requirement for defining needed
theoretical tools, such as supports, and computing various facts about the
circuit in polynomial time, such as the coarsest supporting partition or the
orbit of a gate.

Anderson and Dawar~\cite{AndersonD17} define a condition analogous to the one
define above and prove that it's a sufficient condition for establishing the
uniqueness of the induced automorphism on the circuit and that a circuit can be
transformed into an equivalent rigid circuit in polynomial time.

Although the rigidity condition we present in this paper is similarly defined,
the existence of a polynomial-time computable transformation of a circuit into
an equivalent rigid circuit is not as straight forward. Indeed, it is possible
to show that the problem of determining if a given $(\mathbb{B}, \tau)$-circuit
is rigid is as least as hard as the graph isomorphism problem. This is a direct
consequence of the following result.

\begin{prop}
  There is a a polynomial time reduction from the graph isomorphism problem to
  the problem of deciding if a specified gate in a matrix-circuit is syntacticly
  equivalent to any other gate in the circuit.
  \label{prop:syntactic-graph-iso}
\end{prop}
\begin{proof}
\end{proof}

Another obvious consequence of this result is that if the syntactic equivalence
relation for an input $(\mathbb{B}, \tau)$-circuit can be computed in polynomial
time then the graph isomorphism problem is in $\PT$. It is worth noting that if
we restrict the input to a class of circuits defined over symmetric bases then
we can decide the syntactic equivalence relation in polynomial time.

\begin{prop}
  Let $C_n$ be a circuit with symmetric gates. There is an algorithm that takes
  in such a circuit, runs in time polynomial in the size of the circuit, and
  outputs the syntactic equivalence relation on the gates of $C_n$.
  \label{prop:symmetric-syntactic}
\end{prop}
\begin{proof}
\end{proof}

Moreover, it turns out that being able to compute the syntactic equivalence
relation in polynomial time for some class of circuits $\mathcal{C}$ implies
that the existence of a polynomial-time algorithm for converting circuits in $C$
into equivalent rigid circuit.

\begin{prop}
  Let $\mathcal{C}$ be a set of circuits. Suppose the syntactic equivalence
  relation can be computed in polynomial time for circuits in $\mathcal{C}$. It
  follows that there is an algorithm that runs in polynomial time that takes in
  a circuit $C \in \mathcal{C}$ and outputs a rigid circuit $C'$ such that if
  $C$ is symmetric then $C'$ is symmetric.
  \label{prop:syntactic-equivilence-rigid}
\end{prop}
\begin{proof}
\end{proof}

The following result gives us that the unique labels condition is sufficient.

\begin{prop}
  There is an algorithm that takes in a $(\mathbb{B}, \tau)$-circuit with unique
  labels and outputs the syntactic equivalence relation on its gates. This
  algorithm runs in polynomial time.
  \label{prop:unique-labels-syntactic-equiv}
\end{prop}
\begin{proof}
\end{proof}

Putting together Propositions \ref{prop:symmetric-syntactic},
\ref{prop:syntactic-equivilence-rigid}, and
\ref{prop:unique-labels-syntactic-equiv}, we have that there is a
polynomial-time algorithm that takes as input a circuit with unique labels and
outputs an equivalent rigid circuit. In fact, there is an equivalence of sorts
between the unique labels condition and the rigidity condition.

\begin{prop}
  Let $\mathcal{C}$ be a family of circuits. There is an algorithm that runs in
  polynomial-time and takes in a circuit $C \in \mathcal{C}$ and outputs a rigid
  circuit $C'$ such that if $C$ is symmetric then $C'$ is symmetric if, and only
  if, there is an algorithm that runs in polynomial-time and takes in a circuit
  $C \in \mathcal{C}$ and outputs a circuit $C'$ with unique labels such that if
  $C$ is symmetric then $C'$ is symmetric.
\end{prop}

It follows then that for the symmetric circuits defined over bases of symmetric
functions discussed by Anderson and Dawar~\cite{} we may assume the circuits are
rigid and/or have unique labels without a loss of generality. For the more
general circuit discussed in this paper we cannot make such an assumption as
deciding rigidity is harder then graph isomorphism. However, if we restrict
ourselves to families of circuits with unique labels then again we may assume
rigidity without a loss of generality.

Of course, this restriction to circuits with unique labels is only useful if we
can show that formulas in rank logic can be translated into $P$-uniform families
circuits with unique labels. In the next subsection we prove that this is indeed
the case.

\subsection{Translating FPR to Symmetric Matrix Circuits}
Anderson and Dawar~\cite{} define (or reference) a translation of formulas of
$\FPC$ into equivalent $P$-uniform families of symmetric majority-circuits. More
formally, they show that for $\theta(\vec{x}) \in \FPC[\tau]$ there exists a
$P$-uniform family of symmetric majority-circuits $(C_n)_{n \in \nats}$ such
that the query computed by $(C_n)_{n \in \nats}$ is equal to the query defined
by $\theta (\vec{x})$. In this subsection we develop a similar translation from
formulas of $\FPR$ into $P$-uniform families of symmetric matrix-circuits.

% From Lemma \cite{} we may assume, without a loss of generality, that $(C_n)_{n
% \in nats}$ is a family of rigid circuits (and hence has unique labels).

We are now ready to prove the main theorem of this section.

\begin{thm}
  For any relational vocabulary $\tau$ and each $\theta(\vec{x}) \in \FPR[\tau]$
  there is an algorithm that takes as input a natural number $n$ and outputs a
  symmetric matrix-circuit $C_n$ with unique labels. This algorithm runs in time
  polynomial in $n$ and the family of circuits produced by this algorithm
  $(C_n)_{n \in \nats}$ computes the same query as the one defined by
  $\theta(\vec{x})$.
\end{thm}

\begin{proof}
  We say a formula $\psi(\vec{x}) \in \FPR[tau]$ is
  \emph{matrix-circuit-translatable} if there is a $P$-uniform family of
  symmetric matrix-circuits with unique labels that compute the same query as
  $\psi(\vec{x})$. If a formula $\psi(\vec{x}) \in \FPR[tau]$ is
  matrix-circuit-translatable we let $(C^\psi_n)_{n \in \nats}$ denote the
  corresponding $P$-uniform family of symmetric matrix-circuits with unique
  labels.

  We prove that $\theta(\vec{x}) \in \FPR[\tau]$ is matrix-circuit-translatable
  by structural induction. That is, we first prove that if every sub-formula of
  $\theta(\vec{x})$ is circuit-translatable then $\theta(\vec{x})$ is
  circuit-translatable and, second, we note that every atomic formula in
  $\FPR[\tau]$ is circuit-translatable. We have already that formulas of
  $\FPC[\tau]$ are circuit translatable (Anderson and Dawar~\cite{AndersonD17}),
  and in fact we may assume, without a loss of generality, that this translation
  yields a family of rigid circuits.

  % It is sufficient to prove that if $\theta(\vec{x})$ has the property that
  % all
  % of its subformulas have are matrix-circuit-translatable then there is an
  % algorithm that takes in a natural number $n$ and outputs a symmetric
  % matrix-circuit $C^\theta_n$ with unique labels that is equivalent to
  % $\theta(\vec{x})$ on structures of size $n$.

  Suppose $\phi_1, \phi_2 \in \FPR[\tau]$ are matrix-circuit-translatable and
  $\theta (\vec{x}) = \phi_1(\vec{x}) \land \phi_2(\vec{x})$. Let $R_{\phi_1}$
  and $R_{\phi_2}$ be two $\vert \vec{x} \vert$-ary relation symbols not in
  $\tau$. Let $\theta' (\vec{x}) := R_{\phi_1}(\vec{x}) \land
  R_{\phi_2}(\vec{x})$. This is a formula of $\FPC$, and so we may efficiently
  compute $C^{\theta'}_n$ using the construction in \cite{AndersonD17}. From the
  inductive hypothesis, for each $i \in \{1,2\}$ we may also efficiently compute
  the circuit $C^{\phi_i}_n = \langle G_i, \Omega_i, \Sigma_i Lambda_i, L_i
  \rangle$. We construct $C^{\theta}_n$ by `gluing' $C^{\phi_1}$ and
  $C^{\phi_2}$ into $C^{\theta'}_n$ along $R_1$ and $R_2$

  % We construct the circuit $C'_n = \langle G', \Omega', \Sigma',
  % \Lambda', L' \rangle$ by `inserting' $C^{\phi_1}_n$ and $C^{\phi_2}_n$ into
  % $C^{\theta'}_n$. We now construct $C^{\theta}_n$ from $C'_n$ as follows:
  % \begin{itemize}
  % \item For each $i \in \{1,2\}$ and each relational gate $g$ in $C_n$ such
  %   that $\Sigma'(g) = R_{\phi_i}$ `replace' $g$ with
  %   $\Omega_i(\Lambda_i(g))$,
  % \item then, for each syntactic equivalence class $H \subseteq
  %   \range(\Omega_1) \uplus \range(Omega_2)$, `merge' $H$, and finally
  % \item run `separate-labels' on the circuit.
  % \end{itemize}

  We note that, since $C^{\phi_1}_n$, $C^{\phi_2}_n$ and $C^{\theta'}_n$ have
  unique labels, the only gates that might not have unique labels in
  $C^{\theta}_n$ are those whose input gates include gates in the range of
  $\Omega_1$ or $\Omega_2$. However, all such gates are symmetric and steps (2)
  and (3) above guarantee that these gates have unique labels. Finally, we note
  that this algorithm can implemented such that the computation of
  $C^{\theta}_n$ from $n$ runs in time polynomial in $n$.

  Analogous algorithms can be used to prove that other formulas are
  circuit-translatable. Indeed, for circuit-translatable $\phi, \phi_1, \phi_2
  \in \FPR[\tau]$ an analogous algorithm allows us to prove that
  $\phi_1(\vec{x}) \lor \phi_2(\vec{x})$, $\neg \phi(\vec{x})$, $\forall y. \phi
  (\vec{x}, y)$, $\exists y. \phi (\vec{x}, y)$ are all circuit-translatable.

  Suppose $\theta(\vec{x}) = [\lfp_{V, \vec{y}} \phi(\vec{y}, V)](\vec{x})$ for
  some circuit-translatable formula $\phi(\vec{x}, \vec{y}) \in FPR[\tau \uplus
  \{V\}]$ and $k$-ary relation symbol $V$. We now describe an algorithm that
  takes in a natural number $n$ and outputs $C^{\theta}_n$. We have that we may
  efficiently compute $C^{\phi}_n$. For each $i \in [n^k]$ we construct a
  circuit $C^i = \langle G^i, \Omega^i, \Sigma^i, \Lambda^i, L \rangle $ as
  follows. Let $C^1$ be $C^{\phi}_n$ but with all relational gates labelled by
  the symbol $V$ replaced with a $0$. For each $i>1$ we construct $C^{i}$ by
  `gluing' $C^{i-1}$ into $C^\phi_n$, producing $C^i$. Set $C^{\theta}_n :=
  C^{n^k}$. Since $C^1$ and $C^\phi_n$ are symmetric and have unique labels, by
  induction for each $i > 1$ $C^i$ is symmetric and has unique labels. It
  follows that $C^{\theta}_n$ is symmetric and has unique labels. Moreover,
  since the least-fixed-point operator must converge in at most $n^k$ steps,
  this algorithm runs in time polynomial in $n$ and the family
  $(C^{\theta}_n)_{n \in \nats}$ computes the same query as $\theta(\vec{x})$.

  We have from \cite{} that a formula containing number terms may be converted
  into an equivalent family of formulas containing counting quantifiers. More
  formally if $\theta (\vec{x})$ contains number terms then there exists an
  algorithm that takes as input a natural number $n$ and outputs a formula
  $\theta_n(\vec{x}) \in C$ with counting quantifiers and no number terms which
  is equivalent to $\theta(\vec{x})$ for structures of size $n$ and does not
  contain any number terms. Moreover, this algorithm runs in time polynomial in
  $n$.

  Thus to handle the number-term case it is sufficient to show that if
  $\phi(\vec{x}) \in \FPR[\tau]$ is circuit-translatable then $\theta(\vec{x})
  := C^{k}y. \phi(\vec{x}, y)$ is circuit translatable. Again, an analogous
  construction as for the $\AND$-gate case described in detail above is
  sufficient.

  We have from \cite{} that a formula containing rank operator may be converted
  into an equivalent family of formulas containing rank quantifiers. In other
  words for a given formula $\theta(\vec{x}) \in \FPR[\tau]$ containing rank
  operators there exists an algorithm that takes as input a natural number $n$
  and outputs a formula $\theta_n(\vec{x})$ with rank quantifiers and no rank
  operators. It is thus sufficient to prove that if $\phi(\vec{z}, \vec{y},
  \vec{x})$ is circuit-translatable, $p$ is prime and $r$ is a natural number
  then $\theta(\vec{x}) = \rank^{\leq r}_p \vec{z} \vec{y}. \phi(\vec{z},
  \vec{y}, \vec{x})$ is circuit-translatable. We define an algorithm that takes
  as input a natural number $n$ outputs the required circuit $C^{\theta}_n$.

  We may efficiently compute the $(\mathbb{B}_{\rank}, \tau)$-circuit
  $C^{\phi}_n = \langle G^{\phi}, \Omega^{\phi}, \Sigma^{\phi}, \Lambda^{\phi},
  L^{\phi} \rangle$. Let $k:= \vert \vec{x} \vert$, $k_1 : = \vert \vec{z}
  \vert$ and $k_2 := \vert \vec{y} \vert$. We now define a $(\mathbb{B}_{\rank},
  \{ R \})$-circuit $C':= \langle G', \Omega', \Sigma', \Lambda', L'\rangle$,
  where $R$ is a $(k_1 + k_2 +k)$-arity relation symbol. Let $G_1' :=
  \{g_{\rank, \vec{c}} : \vec{c} \in [n]^k\}$ and $G_2' : = \{ g_{R, \vec{a},
    \vec{b}, \vec{c}} : \vec{a} \in [n]^{k_1}, \vec{b} \in [n]^{k_2}, \vec{c}
  \in [n]^{k}\}$.

  \begin{itemize}
    \setlength\itemsep{0mm}
  \item Let $G' := G_1' \uplus G_2'$,
  \item $\Omega'$ be an injection from $[n]^k$ to $G'$ defined by
    $\Omega'(\vec{c}) = g_{\rank, \vec{c}}$,

  \item $\Sigma' (g) := rk^r_p$ if $g \in G_1'$ and $\Sigma'(g) = R$ if $g \in
    G_2'$,
  \item For each $(\vec{a}, \vec{b}, \vec{c}) \in [n]^{k_1 +k_2 + k}$ let
    $\Lambda' (\vec{a}, \vec{b}, \vec{c}) := g_{R, \vec{a}, \vec{b}, \vec{c}}$,
    and

  \item For each gate $g_{\rank, \vec{a}} \in G_1'$ let $L(g_{\rank, \vec{a}}):
    [n]^{k_1} \times [n]^{k_2} \rightarrow G'$ be defined by $L(g_{\rank,
      \vec{c}})(\vec{a}, \vec{b}) := g_{R, \vec{a}, \vec{b}, \vec{c}}$ for each
    $\vec{a} \in [n]^{k_1}$ and $\vec{b} \in [n]^{k_2}$.

    \end{itemize}
    Let $C^{\theta}_n$ be the result of `gluing' $C^{\phi}_n$ into $C'$.

    It is easy to see that both $C'$ and $C^{\phi}_n$ are symmetric
    rank-circuits with unique labels. Thus $C^{\theta}_n$ is a symmetric
    rank-circuit with unique labels. The construction of $C'$, and hence
    $C^{\theta}_n$, can be implemented so as to run in time polynomial in $n$.
    The construction ensures that the circuit family $(C^{\theta}_n)_{n \in
      \nats}$ computes the same query as the one defined by $\theta(\vec{x})$.

    It remains only to note that any atomic formula of $\FPR[\tau]$ is trivially
    circuit-translatable. The result thus follows.
  \end{proof}

  % such that for any structure $\mathcal{A}$ of size $n$ and an assignment $$
  % to the tuple of variables $\vec{x}$

  % is symmetric and has unique labels.

  % an equality between two numerical terms or an application of the
  % least-fixed-point operator,

  % it follows from Lemma \ref{}, that the syntactic equivalence relation on
  % $G_1 \uplus G_2$ can be efficiently computed.

  % Note that the construction guarantees that $C^{\theta}_n$ is symmetric.
  % Moreover, since the only gates in $C^{\theta}_n$ are either output gates
  % or gates

  % Suppose $\theta(\vec{x})$ is of the form $\phi_1(\vec{x}) \land
  % \phi_2(\vec{x})$, $\phi_1(\vec{x})\lor \phi_2(\vec{x})$, $\neg
  % \phi(\vec{x})$, $\thr_k(y).\phi(\vec{x}, y)$, $\forall y. \phi (\vec{x},
  % y)$, $\exists y. \phi (\vec{x}, y)$, an equality between two numerical
  % terms or an application of the least-fixed-point operator, and each of
  % these sub-formulas is $(\mathbb{B}, \tau)$-circuit-translatable} then
  % $\theta(\vec{x})$ is $(\mathbb{B}, \tau)$-circuit-translatable}. This
  % follows from the following construction. Let $n \in \nats$. We take derive
  % the formula $\theta'(\vec{x})$ from $\theta(\vec{x})$ by replacing each
  % sub-formula $\phi(\vec{z})$ with the formula $R_\phi(\vec{z})$ (adding in
  % some new relational symbol $R_\phi$). We may then translate
  % $\theta'(\vec{x})$ into a $P$-uniform family of symmetric circuits with
  % threshold and unique labels $(C^{\theta'}_n)_{n \in \nats}$. For each $n$
  % we then replace the relational gates in $C^{\theta'}_n$ labelled by
  % $R_\phi$ with the circuit $C^{\phi}_n$ (that is, we add in the entire
  % circuit $C^\phi_n$ and replace each relational gate $g$ labelled by
  % $R_\phi$ such that $\vec{a}:= \Lambda(\vec{a})$ with with the output gates
  % of $C^{\phi}_n$ such that if $g$ is a relational gate computing
  % $R_\phi(\vec{a})$ then $g$ is replaced by the gate $\Omega^{-1}(\vec{a})$
  % in $C^{\phi}_n$). We call this new circuit $C^\theta_n$. It is easy to see
  % that this circuit is symmetric. To see that it has unique labels, notice
  % that we need only check

  % , if $L;$ $L'(g) := L(g)$ for all $g \in G' \cap G$ and for all $g \in H$
  % $L'(H) := L(g)$ if $g \in H$

  % \begin{lem}
  %   We say a
  % \end{lem}

  % We should like to argue that for any $\theta(\vec{x}) \in \FPR[\tau]$ if
  % every sub-formula of $\theta(\vec{x})$ is $(\mathbb_{\mat}, \tau)$-circuit
  % translatable then $\theta(\vec{x})$ is $(\mathbb_{\mat}, \tau)$-circuit
  % translatable. The existence of the desired translation then follows by
  % induction on the structure of the formula.

  % It is easy to see that if $\theta(\vec{x})$ is of the form $\phi_1(\vec{x})
  % \land \phi_2(\vec{x})$, $\phi_1(\vec{x})\lor \phi_2(\vec{x})$, $\neg
  % \phi(\vec{x})$, $\thr_k(y).\phi(\vec{x}, y)$, $\forall y. \phi (\vec{x},
  % y)$, $\exists y. \phi (\vec{x}, y)$, an equality between two numerical terms
  % or an application of the least-fixed-point operator, and each of these
  % sub-formulas is $(\mathbb{B}, \tau)$-circuit-translatable} then
  % $\theta(\vec{x})$ is $(\mathbb{B}, \tau)$-circuit-translatable}. This
  % follows from the following construction. Let $n \in \nats$. We take derive
  % the formula $\theta'(\vec{x})$ from $\theta(\vec{x})$ by replacing each
  % sub-formula $\phi(\vec{z})$ with the formula $R_\phi(\vec{z})$ (adding in
  % some new relational symbol $R_\phi$). We may then translate
  % $\theta'(\vec{x})$ into a $P$-uniform family of symmetric circuits with
  % threshold and unique labels $(C^{\theta'}_n)_{n \in \nats}$. For each $n$ we
  % then replace the relational gates in $C^{\theta'}_n$ labelled by $R_\phi$
  % with the circuit $C^{\phi}_n$ (that is, we add in the entire circuit
  % $C^\phi_n$ and replace each relational gate $g$ labelled by $R_\phi$ such
  % that $\vec{a}:= \Lambda(\vec{a})$ with with the output gates of $C^{\phi}_n$
  % such that if $g$ is a relational gate computing $R_\phi(\vec{a})$ then $g$
  % is replaced by the gate $\Omega^{-1}(\vec{a})$ in $C^{\phi}_n$). We call
  % this new circuit $C^\theta_n$. It is easy to see that this circuit is
  % symmetric. To see that it has unique labels, notice that we need only check

  % We solve this problem completely for one case and argue that the other cases
  % follow similarly. Suppose $\theta (\vec{x}) = \phi_1(\vec{x}) \land
  % \phi_2(\vec{x})$. We now describe an algorithm that takes in $n\in \nats$
  % and outputs a formula $C^\theta_n$ with the required properties. We first
  % introduce two relation symbols $R_{\phi_1}$ and $R_{\phi_2}$ not in $\tau$
  % and with arity $\vert\vec{x}\vert$. We define $\theta' (\vec{x}) =
  % R_{\phi_1}(\vec{x}) \land R_{\phi_2}(\vec{x})$ and compute the associated
  % symmetric threshold circuit with unique labels $C^{\theta'}_n$. Similarly,
  % for each $i\ \in \{1,2\}$ we may compute the symmetric $(\mathbb{B},
  % \tau)$-circuit with unique labels corresponding to $\phi_i$ that takes in
  % inputs of size $n$, $C^{\phi_i}_n = \langle G_i, \Omega_i, \Sigma_i
  % Lambda_i, L_i \rangle$ algorithms given by the inductive hypothesis. We then
  % construct $C^{\theta}_n$ by inserting into $C^{\theta'}_n$ the circuits
  % $C^{\phi_1}_n$ and $C^{\phi_2}_n$ (that is, taking a disjoint union of the
  % sets of gates and the functions that define each circuit -- with the
  % exception of $\Omega$ which is specified by $C^{\theta'}_n$ alone). Then for
  % all $i \in \{1,2\}$ and each relational gate $g$ in $C^{\theta}_n$ such that
  % $\Sigma(g) = R_{\phi_i}$ we replace $g$ with $\Omega_i(\Lambda_i(g))$. Since
  % $C^{\phi_1}_n$ and $C^{\phi_2}_n$ have unique labels, it follows from Lemma
  % \ref{} that we can efficiently decide if any two gates $g_1, g_2 \in G_1
  % \uplus G_2$ are syntactical equivalent. For each pair of gates $g_1, g_2$ in
  % the range of $\Omega_1 \uplus \Omega_2$ we check if $g_1 \equiv g_2$, and if
  % so we merge them.

  % The resultant circuit $C^{\theta}_n$ is clearly a symmetric $(\mathbb{B},
  % \tau)-circuit$-circuit. Moreover, it is easy to see that if all pairs of
  % gates in the range of $\Omega_1 \uplus Omega_2$ are not syntactical
  % equivalent $g$ is a gate such that $h_1, h_2 \in H_g$ are syntactically
  % equivalent then . it has unique labels (as the only point where two input
  % gates could be equivalent

  % we can from Lemma \ref{} that we can efficiently decide if two any two gates
  % from the union of these circuits are syntactical equivalent. If any of their
  % output gates are syntactically equivalent, merge these gates. This new
  % circuit has disjoint

  % we replace the relational gate $g$ in $C^{\theta'}_n$ such that $\Sigma(g) =
  % R_\phi$ and $\Lambda(g) = \vec{a}$ with the circuit $C^\phi_n$ $\vec{a}$, an
  % $\arty(R_\pi)$ each relational gate $R_\phi(\vec{a})$ in the circuit
  % $C^{\theta'}_n$

  % It remains to show that for any $k \in \nats$ and formula $\phi \in
  % \FPR[\tau]$ such that $\phi$ formula of the form $\theta (\vec{z}): = [rk
  % (\vec{x}, \vec {\nu} \leq \vec{t}, \vec{y}\vec{\mu} \leq \vec{s}, \pi \leq
  % r). \phi(\vec{x}, \vec{nu}, \vec{y}, \vec(mu), \vec{s}, \vec{z})] \leq k$
  % there is an equivalent $P$-uniform family of symmetric rank-circuits with
  % unique labels $(C_n)_{n \in \nats}$ that compute the same query as $\theta$.

  % \begin{lem}
  %   Let $\tau$ be a relational vocabulary and let $\phi(\vec{x})$ be a formula
  %   of $\FPR[\tau]$. There is an algorithm that takes as input a natural
  %   number $n$ and outputs a formula $\phi_n$ such that $\phi_n$ contains no
  %   rank operators or counting terms and for any $\tau$-structure
  %   $\mathcal{A}$ of size $n$ and $\vert \vec{x} \vert$-tuple of elements
  %   $\vec{a}$ from the universe of $\mathcal{A}$, $\mathcal{A}\models
  %   \phi[\vec{a}]$ if, and only if, $\mathcal{A}\models \phi_n[\vec{a}]$.
  %   Moreover, this algorithm runs in time polynomial in $n$.
  % \end{lem}

  % \begin{thm}
  %   Let $\tau$ be a relational vocabulary and let $\phi$ be a formula of
  %   $\FPR[\tau]$. There is an algorithm that takes as input a natural number
  %   $n$ and outputs a symmetric matrix-circuit $C_n$. This algorithm runs in
  %   time polynomial in $n$. Moreover, the query computed by the circuit family
  %   $(C_n)_{n \in \nats}$ and the query defined by the formula $\phi$ are
  %   equal.
  % \end{thm}
  % \begin{proof}
  %   We describe a transformation inductively on the structure of the formula.
  %   This procedure can then be implemented algorithmically using recursion.

  %   If $\phi(\vec{a})$ is an atomic formula

  % \end{proof}

  % We define this transformation by recursion on the structure of the formula
  % and note that and note that such a transformation can be implemented so as
  % to run in time polynomial in $n$.

  % Let $\phi$ be a formula

  % \begin{thm}
  %   Formulas of $\FPR$ can be translated into symmetric matrix-circuits
  % \end{thm}
  % \begin{proof}
  %   The idea here is to do exactly the same thing as for FPC formulas except
  %   when we arrive at a rank quantifier we `tag' each formula with
  % \end{proof}
 \end{document}

### 2017-11-16 sections/translating-formulas-to-cicuits.tex
13-Nov-2017
16 Nov

@@
 
-The algorithm \emph{merge} takes a circuit and an appropriate set of gates and
-produces a new circuit by combining those gates into a single gate.
+We first define the operation $\op{merge}$ that takes in a circuit and a set of
+syntactically equivalent gates and produces a new circuit by combining those
+gates into a single gate.
 
 \begin{definition}
-  The algorithm \emph{merge} takes as input a circuit $C = \langle G, \Omega,
-  \Sigma , \Lambda, L \rangle$ and a set of syntactically equivalent gates $H =
-  \{h_1, \ldots , h_p\}$ and outputs a new circuit $C' = \langle G', \Omega',
-  \Sigma', \Lambda', L' \rangle$, where
+  The operation $\op{merge}(C, H)$ takes as input a circuit $C = \langle G,
+  \Omega, \Sigma , \Lambda, L \rangle$ and a set of syntactically equivalent
+  gates $H = \{h_1, \ldots , h_p\}$ and outputs the circuit $C' = \langle G',
+  \Omega', \Sigma', \Lambda', L' \rangle$, where
   \begin{itemize}
@@
 
-It can be shown that `merge' can be implemented so as to run in time polynomial
-in the size of the input circuit. We note that if the input circuit to `merge'
-is symmetric (resp. has unique labels) then the output circuit will also be
-symmetric (resp. have unique labels). The input and output circuits compute the
-same function.
+It can be shown that $\op{merge}$ can be computed by an algorithm running in
+time polynomial in the size of the input circuit. We note that the input and
+output circuits compute the same function. Moreover, if the input circuit is
+symmetric (resp. has unique labels) then the output circuit will also be
+symmetric (resp. have unique labels).
+
+The the operation $\op{merge-all}$ simply applies $\op{merge}$ to the syntactic
+equivalence classes of some input set of gates.
+
+\begin{definition}
+  The operation $\op{merge-all}(C, H)$ takes as input an ordered circuit $C$ and
+  a set of gates $H$ with unique labels and outputs another circuit $C'$. Let
+  $H_1, \ldots, H_p$ be the equivalence classes of $H$ linearly ordered using
+  the order on the circuit but such that for all $i, j \in [p]$ if $i \leq j$
+  then the height of the gates in $H_i$ is less than or equal to the height of
+  the gates in $H_j$. Let $C'$ be the result of successively executing
+  $\op{merge}$ on each partition.
+\end{definition}
+
+For an input tuple $(C, H)$ it follows from Lemma \cite{} that the syntactic
+equivalence relation on $H$ can be computed in time polynomial in the size of
+$C$. Thus it can be shown that the operation $\op{merge-all}$ can be computed in
+time polynomial in the size of the input circuit. As in the case of
+$\op{merge}$, the operation $\op{merge-all}$ preserves symmetry, unique labels
+and the ensures that the input and output circuits compute the same function. If
+$C$ is an ordered circuit and $H$ is a set of gates with unique labels, then if
+$g$ is a gate in both $C$ and $C' := \op{merge-all}(C, H)$, then if all of the input
+gates of $g$ in $C$ are in $H$ then no two distinct input gates of $g$ in $C'$
+are syntactically equivalent (but $g$ does not have unique labels in $C'$ as
+$L'(g)$ may not be injective).
 
@@
 
-The algorithm \emph{separate-labels} takes a circuit and outputs an equivalent
-circuit such that every symmetric-gate has unique labels.
+The operation $\op{make-injective}$ takes in a circuit and a symmetric gate and
+outputs an equivalent circuit but such that the selected gate now has injective
+labels.
 
 \begin{definition}
-  The algorithm \emph{separate-labels} takes as input a $(\mathbb{B},
-  \tau)$-circuit $C := \langle G, \Omega, \Sigma , \Lambda, L \rangle$ and
-  outputs circuit $C' = \langle G', \Omega', \Sigma', \Lambda', L' \rangle$. We
-  now describe how these values are derived. We have that $\Omega' = \Omega'$
-  and $\Lambda' = \Lambda$. We start with $G' = G$, $\Sigma' = \Sigma$ and $L' =
-  L$ and updates their definitions iteratively according to the following
-  procedure.
-
-  Let $k$ denote a variable initialised to $1$. Let $S$ be the set of all gates
-  of height $k$ that are symmetric-gates. For each $h_1 \in \bigcup_{g \in
-    S}H_g$ let $g \in S$ be the first gate (using the order of the circuit
-  derived from its encoding) such that $\vert L(g)^{-1}(h_1) \vert$ is maximal.
-  Let $\{a_1, \ldots, a_p\} := L(g)^{-1}(h_1)$ (again, making use of the order).
-  We add to $G'$ the gates $\{h_2, \ldots, h_p\}$ and for each $i \in \{2,
-  \ldots, p\}$ we set $\Sigma'(h_i)$ such that $h_i$ is a $\land$ gate with a
-  single output and $L'(h_i)$ such that $h_i$ takes only $h_{i-1}$ as an input.
-  For each $g' \in S$ such that $h_1 \in H_g$ let $\{ b_1, \ldots, b_q \} :=
-  L(g)^{-1}(h_1)$. For each $i \in [q]$ let $L'(g')(b_i) = h_i$. Iterate $k$ and
-  repeat this procedure until $k$ exceeds the depth of the circuit.
+  The operation $\op{make-injective}(C, h)$ takes as input an ordered
+  $(\mathbb{B}, \tau)$-circuit $C := \langle G, \Omega, \Sigma , \Lambda, L
+  \rangle$ and a gate $h \in G$ and outputs the circuit $C' := \langle G',
+  \Omega', \Sigma', \Lambda', L' \rangle$. Let $c = \max \{\vert
+  L(g)^{-1}(h)\vert : g \in W(h, \cdot)\}$. If $c = 1$ then $C' := C$. If $c >
+  1$ then $C'$ is defined such that
+  \begin{itemize}
+    \setlength\itemsep{0mm}
+  \item $G' = G \uplus \{h_2, \ldots, h_{c-1}\}$,
+  \item $\Omega' = \Omega$,
+  \item For each $g \in G$ let $\Sigma' (g) = \Sigma(g)$, otherwise let
+    $\Sigma'(g)$ be a single-input $\AND$-gate.
+  \item $\Lambda'= \Lambda$
+  \item For each $g \in G'$ if $g \in G \setminus W(h, \cdot)$ then $L'(g) =
+    L(g)$. If $g \in W(h, \cdot)$ let $\{\vec{a}_1, \ldots, \vec{a}_k\} :=
+    L(g)^{-1}(h)$ and for each $\vec{a} \in \ind(g)$ if $L(g)(\vec{a}) \neq h$
+    then $L'(g)(\vec{a}) = L(g)(\vec{a})$ and if $\vec{a} = \vec{a_i} \in
+    L(g)^{-1}(h)$ then let $L'(g)(\vec{a}) = h_i$.
+  \end{itemize}
 \end{definition}
 
-It can be shown that `separate-labels' can be implemented so as to run in time
-polynomial in the size of the input circuit. We note that both the input and
-output circuits compute the same function. Moreover, if all of the non-symmetric
-gates in the input circuit have unique labels then the output circuit will have
-unique labels. If the input circuit is symmetric and has the property that every
-non-symmetric gate in the circuit has unique labels then the output circuit is
-symmetric.
+It can be shown that $\op{make-injective}$ can be computed by an algorithm
+running in time polynomial in the size of the input circuit. Moreover, the input
+and output circuits of this operation compute the same function.
+
+% Furthermore, $\op{make-injective}(C, h) = C'$ and there exists a symmetric
+% gate $g \in C$ such that $\vert L(g)^{-1}(h) \vert > 1$ then the number of
+% non-injective symmetric gates in $C'$ is strictly less than the number of
+% non-injective symmetric gates in $C'$.
+
+The operation $\op{make-injective-all}$ takes in a circuit and outputs an
+equivalent circuit such that every symmetric-gate in that circuit has injective
+labels.
+
+\begin{definition}
+  The operation $\op{make-injective-all}(C)$ takes as input an ordered
+  $(\mathbb{B}, \tau)$-circuit $C := \langle G, \Omega, \Sigma , \Lambda, L
+  \rangle$ and outputs the circuit $C' := \langle G', \Omega', \Sigma',
+  \Lambda', L' \rangle$ defined as follows. Let $F(C*) = \op{make-injective}(C*,
+  h)$, where $h$ is the first gate in $C*$ such that there exists a gate $g$ in
+  $C*$ where $\vert L*(g)^{-1}(h)\vert > 1$. Let $(C^0, C^1, \ldots)$ be a
+  sequence of circuits where $C^0 := C$ and for $i > 1$, $C^i = F(C^{i-1})$. It
+  can be shown that this sequence converges after at most $\vert C \vert$ many
+  steps. Let $C'$ be this limit.
+\end{definition}
+
+Since $\op{make-injective}$ can be computed in polynomial time, and the number
+of iterations required in order to reach is a fixed-point in the definition of
+$\op{make-injective-all}$ is bounded by the size of the input circuit, it
+follows that $\op{make-injective-all}$ can be computed in time polynomial in the
+size of the input circuit. Moreover, $\op{make-injective-all}$ preserves
+symmetry, rigidity and unique labels. Moreover, the input and output circuits
+compute the same function.
+
+% $ $g$ in $C$ such that $W(h,g)$, let $g_{h_1}$ be the first gate in the
+% circuit such that for all $g' \in S_j$, $\vert L(g_{h_1})^{-1}(h_1) \vert \geq
+% L(g')^{-1}(h_1)$
+
+% We define $C'$ as follows. Let $F$ be a function that takes in an ordered
+% circuit $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ and outputs a
+% circuit $C* := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ defined as
+% follows. If for all $g \in G$, $L(g)$ is an injection then $F(C) = C$ and if
+% not then $F(C)$ is defined as follows.
+
+% Let $j \in [\depth(C)]$, and let ${G_0}' = G$, ${\Sigma_0}' = \Sigma$ and
+% ${L}_0' = L$.
+
+% Let $S_j$ be the set of all gates of height $j$ that are symmetric-gates. For
+% each $h_1 \in \bigcup_{g \in S_j} H_g$ let $g_{h_1} \in S_j$ be the first gate
+% in the circuit such that for all $g' \in S_j$, $\vert L(g_{h_1})^{-1}(h_1)
+% \vert \geq L(g')^{-1}(h_1)$. Let $(a_1, \ldots, a_p) := L(g_{h_1})^{-1}(h_1)$
+% (ordered according the to order on the circuit). We add to $G'$ the gates
+% $\{h_2, \ldots, h_p\}$ and for each $i \in \{2, \ldots, p\}$ we set
+% $\Sigma'(h_i)$ such that $h_i$ is a $\land$ gate with a single output and
+% $L'(h_i)$ such that $h_i$ takes only $h_{i-1}$ as an input. For each $g' \in
+% S$ such that $h_1 \in H_g$ let $\{ b_1, \ldots, b_q \} := L(g)^{-1}(h_1)$. For
+% each $i \in [q]$ let $L'(g')(b_i) = h_i$. Iterate $k$ and repeat this
+% procedure until $k$ exceeds the depth of the circuit.
+
+% \begin{definition}
+%   The operation \emph{separate-labels} takes as input an ordered $(\mathbb{B},
+%   \tau)$-circuit $C := \langle G, \Omega, \Sigma , \Lambda, L \rangle$ and
+%   outputs the circuit $C' = \langle G', \Omega', \Sigma', \Lambda', L'
+%   \rangle$. We define $C'$ as follows. Let $j \in [\depth(C)]$, and let
+%   ${G_0}' = G$, ${\Sigma_0}' = \Sigma$ and ${L}_0' = L$. Let $S_j$ be the set
+%   of all gates of height $j$ that are symmetric-gates. For each $h_1 \in
+%   \bigcup_{g \in S_j} H_g$ let $g_{h_1} \in S_j$ be the first gate in the
+%   circuit such that for all $g' \in S_j$, $\vert L(g_{h_1})^{-1}(h_1) \vert
+%   \geq L(g')^{-1}(h_1)$. Let $(a_1, \ldots, a_p) := L(g_{h_1})^{-1}(h_1)$
+%   (ordered according the to order on the circuit). We add to $G'$ the gates
+%   $\{h_2, \ldots, h_p\}$ and for each $i \in \{2, \ldots, p\}$ we set
+%   $\Sigma'(h_i)$ such that $h_i$ is a $\land$ gate with a single output and
+%   $L'(h_i)$ such that $h_i$ takes only $h_{i-1}$ as an input. For each $g' \in
+%   S$ such that $h_1 \in H_g$ let $\{ b_1, \ldots, b_q \} := L(g)^{-1}(h_1)$.
+%   For each $i \in [q]$ let $L'(g')(b_i) = h_i$. Iterate $k$ and repeat this
+%   procedure until $k$ exceeds the depth of the circuit.
+% \end{definition}
 
@@
 
-The algorithm \emph{insert} takes as input two circuits and creates a new
-circuit formed by inserting the gates of the first circuit into the second
-circuit.
+The operation $\op{insert}$ takes as input two circuits and outputs a circuit
+formed by inserting the gates of the first circuit into the second circuit.
 
 \begin{definition}
-  The algorithm \emph{insert} takes as input a $(\mathbb{B}_1, \tau_1)$-circuit
-  $C^1 := \langle G_1, \Omega_1, \Sigma_1 , \Lambda_1, L_1 \rangle$ and a
-  $(\mathbb{B}_2, \tau_2)$-circuit $C^2 := \langle G_2, \Omega_2, \Sigma_2 ,
-  \Lambda_2, L_2 \rangle$ and outputs a $(\mathbb{B}_1 \cup \mathbb{B}_2, \tau_1
-  \uplus \tau_2)$-circuit $C = \langle G, \Omega, \Sigma , \Lambda, L \rangle$
-  such that
+  The operation $\op{insert}(C^1, C^2)$ takes as input a $(\mathbb{B}_1,
+  \tau_1)$-circuit $C^1 := \langle G_1, \Omega_1, \Sigma_1 , \Lambda_1, L_1
+  \rangle$ and a $(\mathbb{B}_2, \tau_2)$-circuit $C^2 := \langle G_2, \Omega_2,
+  \Sigma_2 , \Lambda_2, L_2 \rangle$ and outputs a $(\mathbb{B}_1 \cup
+  \mathbb{B}_2, \tau_1 \uplus \tau_2)$-circuit $C = \langle G, \Omega, \Sigma ,
+  \Lambda, L \rangle$ where
   \begin{itemize}
@@
 
-It can be shown that `insert' can be implemented so as to run in time polynomial
-in the size of the input circuit. If the input circuits are symmetric then the
-output circuit will be symmetric.
+It can be shown that $\op{insert}$ can be be computed in polynomial time. If the
+input circuits are symmetric then the output circuit will be symmetric.
 
-The operation \emph{replace} removes a gate from a circuit and replaces it with
+The operation $\op{replace}$ removes a gate from a circuit and replaces it with
 another gate.
@@
 \begin{definition}
-  Formally, \emph{replace} is an algorithm that takes as input a circuit $C =
+  The operation $\op{replace}(C, g_1, g_2)$ takes as input a circuit $C =
   \langle G, \Omega, \Sigma, \Lambda, L\rangle$ and a pair of gates $(g_1, g_2)$
@@
 
-It can be shown that `replace' can be implemented so as to run in time
+It can be shown that the operation $\op{replace}$ can be computed in time
 polynomial in the size of the input circuit.
 
-The algorithm \emph{tag} takes in a circuit, a gate in that circuit, a relation
-symbol and a tuple and outputs a circuit computing but with an additional
-gadget, constructed using the gates labelled by the given relation symbol and
-tuple, marking the designated gate. The idea is that marking a gate can be used
-as a step to ensure unique labels in a circuit.
+The operation $\op{tag}$ takes in a circuit, a gate in that circuit, a relation
+symbol and a tuple and outputs a circuit computing the same function but with an
+additional gadget, constructed using the gates labelled by the given relation
+symbol and tuple, marking the designated gate. The idea is that marking a gate
+can be used as a step to ensure unique labels in a circuit.
 
 \begin{definition}
-  The algorithm \emph{tag} takes in a $(\mathbb{B}, \tau)$-circuit $C_n :=
-  \langle G, \Omega, \Sigma, \Lambda, L \rangle$, a relation symbol $R \in
-  \tau$, a gate $g \in G$ and a tuple $\vec{a} \in [n]^k$ for some $k$ and
-  outputs the circuit $C_n' = \langle G', \Omega', \Sigma', \Lambda', L'\rangle$
-  defined by the following algorithm. Let $G' = G \uplus \{\land_g, \land_{g'},
-  \land_1, \ldots , \land_k\}$, $\Omega' = \Omega$, and $\Lambda' = \Lambda$.
-  Define $L'$ and $\Sigma'$ as follows. For each $g \in G$ $\Sigma'(g) =
-  \Sigma(g)$. For each $g \in \{\land_0, \land_1, \ldots , \land_k \}$,
-  $\Sigma(g)$ is an $\AND$-gate that takes in two inputs. $\Sigma(\land_g)$ is
-  an $\AND$-gate that takes in a single input. Set $g$ to be the lone input to
-  $\land_g$. Set the two inputs to $\land_0$ to be $\land_g$ and $\land_1$. For
-  each $i \in [k-1]$ set the inputs of $\land_i$ to be $\land_{i+1}$ and the
+  The operation $\op{tag}(C, R, g, \vec{a})$ takes in a $(\mathbb{B},
+  \tau)$-circuit $C_n := \langle G, \Omega, \Sigma, \Lambda, L \rangle$, a
+  relation symbol $R \in \tau$, a gate $g \in G$ and a tuple $\vec{a} \in [n]^k$
+  for some $k$ and outputs the circuit $C_n' = \langle G', \Omega', \Sigma',
+  \Lambda', L'\rangle$ defined by the following algorithm. Let $G' = G \uplus
+  \{\land_g, \land_{g'}, \land_1, \ldots , \land_k\}$, $\Omega' = \Omega$, and
+  $\Lambda' = \Lambda$. Define $L'$ and $\Sigma'$ as follows. For each $g \in G$
+  $\Sigma'(g) = \Sigma(g)$. For each $g \in \{\land_0, \land_1, \ldots , \land_k
+  \}$, $\Sigma(g)$ is an $\AND$-gate that takes in two inputs. $\Sigma(\land_g)$
+  is an $\AND$-gate that takes in a single input. Set $g$ to be the lone input
+  to $\land_g$. Set the two inputs to $\land_0$ to be $\land_g$ and $\land_1$.
+  For each $i \in [k-1]$ set the inputs of $\land_i$ to be $\land_{i+1}$ and the
   gate $g_i \in G'$ such that $\Sigma(g_i) = R$ and $\Lambda^{-1}(g_i) =
@@
 
-It can be shown that `tag' can be implemented so as to run in time polynomial in
-the size of the input. The input and output circuits compute the same function.
-Moreover, if the input circuit had unique labels then the output circuit will
-have unique labels. In the event that the input relation symbol is obvious from
-the context we omit it when invoking this algorithm.
+% \begin{definition}
+%   The algorithm \emph{tag} takes in a $(\mathbb{B}, \tau)$-circuit $C_n :=
+%   \langle G, \Omega, \Sigma, \Lambda, L \rangle$, a relation symbol $R \in
+%   \tau$, a gate $g \in G$ and a tuple $\vec{a} \in [n]^k$ for some $k$ and
+%   outputs the circuit $C_n' = \langle G', \Omega', \Sigma', \Lambda',
+%   L'\rangle$ defined by the following algorithm. Let $G' = G \uplus \{\land_g,
+%   \land_{g'}, \land_1, \ldots , \land_k\}$, $\Omega' = \Omega$, and $\Lambda'
+%   = \Lambda$. Define $L'$ and $\Sigma'$ as follows. For each $g \in G$
+%   $\Sigma'(g) = \Sigma(g)$. For each $g \in \{\land_0, \land_1, \ldots ,
+%   \land_k \}$, $\Sigma(g)$ is an $\AND$-gate that takes in two inputs.
+%   $\Sigma(\land_g)$ is an $\AND$-gate that takes in a single input. Set $g$ to
+%   be the lone input to $\land_g$. Set the two inputs to $\land_0$ to be
+%   $\land_g$ and $\land_1$. For each $i \in [k-1]$ set the inputs of $\land_i$
+%   to be $\land_{i+1}$ and the gate $g_i \in G'$ such that $\Sigma(g_i) = R$
+%   and $\Lambda^{-1}(g_i) = \vec{a}_i$, where $\vec{a}_i$ is the $k$-tuple
+%   $(\vec{a}(i), \ldots, \vec{a}(i))$. Set the inputs of $\land_k$ to be the
+%   constant gate $1$ and the gate $g_k$ such that $\Sigma(g) = R$ and
+%   $\Lambda^{-1}(g_k) = \vec{a}_k$.
 
-The algorithm \emph{glue-circuits} takes in a designated circuit and another set
-of appropriate circuits and forms a new circuit by replacing the relational
-gates of the designated circuit with the output gates of the circuits in the
-given set.
+%   For each gate $h \in G \setminus \{g\}$ and $\vec{b} \in \ind(h)$, if
+%   $L(h)(\vec{b}) = g$ then let $L'(h)(\vec{b}) = \land_0$, otherwise let
+%   $L'(h)(\vec{b}) = L(h)(\vec{b})$.
+
+% \end{definition}
+
+It can be shown that $\op{concatenate}$ can be implemented so as to run in time
+polynomial in the size of the input. The input and output circuits compute the
+same function. Moreover, if the input circuit had unique labels then the output
+circuit will have unique labels. In the event that the input relation symbol is
+obvious from the context we omit it when invoking this algorithm.
+
+The operation $\op{concatenate}$ takes in a circuit and a set of appropriate
+circuits and forms a new circuit by replacing the relational gates of the
+designated circuit with the output gates of the circuits in the given set of
+circuits.
 
 \begin{definition}
-  The algorithm \emph{glue-circuits} takes as input a set of relation symbols
-  $\tau_R := \{R_1, \ldots, R_t\}$ and $t+1$ circuits $\{C^0, \ldots, C^{t}\}$,
-  where $C^0 = \langle G_0, \Omega_0, \Sigma_0, \Lambda_0, L_0 \rangle$ is a
-  $(\mathbb{B}, \tau)$-circuit with $\tau_R \subseteq \tau$ and for each $i \in
-  [t]$, $C^i = \langle G_i, \Omega_i, \Sigma_i, \Lambda_i, L_i \rangle$ is a
-  $(\mathbb{B}_i, \tau_i)$-circuit computing a query of arity $\arty(R_i)$. The
-  algorithm outputs, for a given input, a circuit $C = \langle G, \Omega,
-  \Sigma, \Lambda, L\rangle$ constructed as follows. Let $C^0' := C^0$. For each
-  $i \in [t]$ fix a relation symbol $V_i \in \tau_i \setminnus \tau_R$. For each
-  $i \in [t]$ construct the circuit $C^{i}' = \langle G_i', \Omega_i',
-  \Sigma_i', \Lambda_i', L_i' \rangle $ by `inserting' $C^i$ into $C^{i-1}'$,
-  and call the resultant circuit $D^{i-1}'$. For each relational gate $g$ in
-  $D^{i-1}$ labelled by the symbol $R_i$, `replace' $g$ with the gate
-  $\Omega_{i}(\Lambda_{i-1}'(g))$ in $D^{i-1}$ and `tag' the gate
-  $\Omega_i(\Lambda_{i-1}'(g))$ in $D^{i-1}$ using the tuple $\Lambda_{i-1}'(g)$
-  and the relation symbol $V_i$. Output the circuit $C := C^t'$.
+  The operation $\op{concatenate}(C, \mathcal{C}, \tau_R, R)$, where $C :=
+  \langle G, \Omega, \Sigma, \Lambda, L \rangle$ is a $(\mathbb{B},
+  \tau)$-circuit, $\tau_R := (R_1, \ldots, R_t)$ is a sequence of relation
+  symbols such that $\tau_R \subseteq \tau$, $\mathcal{C} := ( C^1, \ldots,
+  C^t)$ is a finite sequence of circuits, where for each $i \in [t]$, $C^i =
+  \langle G_i, \Omega_i, \Sigma_i, \Lambda_i, L_i \rangle$ is a $(\mathbb{B}_i,
+  \tau_i)$-circuit such that $\tau_i \not\subset \tau_R$ and $C^i$ computes a
+  query of arity $\arty(R_i)$, and $R$ is a relation symbol in $(\tau \setminus
+  \tau_R) \cup (\bigcup_{1 \leq i \leq t}\tau_i))$. The operation outputs a
+  circuit $C' = \langle G', \Omega', \Sigma', \Lambda', L' \rangle$ defined from
+  the input as follows. Note that all circuits take in structures of size $n$.
+
+  Let ${C^0}' := \langle G^0, \Omega^0, \Sigma^0, \Lambda^0, L^0 \rangle := C$.
+  For each $i \in [t]$ fix a relation symbol $V_i \in \tau_i \setminus \tau_R$.
+  For each $i \in [t]$ construct the circuit ${C^{i}}' = \langle G_i',
+  \Omega_i', \Sigma_i', \Lambda_i', L_i' \rangle $ by $\op{inserting}$ $C^i$
+  into ${C^{i-1}}'$, and call the resultant circuit ${D^{i-1}}'$. For each
+  relational gate $g$ in $D^{i-1}$ labelled by the symbol $R_i$, $\op{replace}$
+  $g$ with the gate $\Omega_{i}(\Lambda_{i-1}'(g))$ in $D^{i-1}$ and $\op{tag}$
+  the gate $\Omega_i(\Lambda_{i-1}'(g))$ in $D^{i-1}$ using the tuple
+  $\Lambda_{i-1}'(g)$ and the relation symbol $R$. Output the circuit $C' :=
+  {C^t}'$.
 \end{definition}
 
-It can be shown that `glue-circuits' can be implemented so as to run in time
-polynomial in the combined size of the input circuits. Moreover, if the input
-circuits are all symmetric (resp. have unique labels) then the output circuit
-will be symmetric (resp. have unique labels). We sometimes refer to `gluing'
-$(C^1, \ldots, C^t)$ into $C^0$ along $(R_1 , \ldots , R_t)$ when invoking
+% \begin{definition}
+%   The operation $\op{concatenate-circuits}(C, \mathcal{C}, \tau_R) = C'$,
+%   where $C := \langle G, \Omega, \Sigma, \Lambda_0, L_0 \rangle$ is a
+%   $(\mathbb{B}, \tau)$-circuit, $\mathcal{C}$ is a finite set of circuits
+%   takes as input a set of relation symbols $\tau_R := \{R_1, \ldots, R_t\}$
+%   and $t+1$ circuits $\{C^0, \ldots, C^{t}\}$, where $C^0 = \langle G_0,
+%   \Omega_0, \Sigma_0, \Lambda_0, L_0 \rangle$ is a $(\mathbb{B},
+%   \tau)$-circuit with $\tau_R \subseteq \tau$ and for each $i \in [t]$, $C^i =
+%   \langle G_i, \Omega_i, \Sigma_i, \Lambda_i, L_i \rangle$ is a
+%   $(\mathbb{B}_i, \tau_i)$-circuit computing a query of arity $\arty(R_i)$.
+%   The algorithm outputs, for a given input, a circuit $C = \langle G, \Omega,
+%   \Sigma, \Lambda, L\rangle$ constructed as follows. Let ${C^0}' := C^0$. For
+%   each $i \in [t]$ fix a relation symbol $V_i \in \tau_i \setminus \tau_R$.
+%   For each $i \in [t]$ construct the circuit ${C^{i}}' = \langle G_i',
+%   \Omega_i', \Sigma_i', \Lambda_i', L_i' \rangle $ by `inserting' $C^i$ into
+%   ${C^{i-1}}'$, and call the resultant circuit ${D^{i-1}}'$. For each
+%   relational gate $g$ in $D^{i-1}$ labelled by the symbol $R_i$, `replace' $g$
+%   with the gate $\Omega_{i}(\Lambda_{i-1}'(g))$ in $D^{i-1}$ and `tag' the
+%   gate $\Omega_i(\Lambda_{i-1}'(g))$ in $D^{i-1}$ using the tuple
+%   $\Lambda_{i-1}'(g)$ and the relation symbol $V_i$. Output the circuit $C :=
+%   {C^t}'$.
+% \end{definition}
+
+It can be shown that $\op(concatenate)$ can be computed in time polynomial in
+the combined size of the input circuits. Moreover, if the input circuits are all
+symmetric (resp. have unique labels) then the output circuit will be symmetric
+(resp. have unique labels). We sometimes refer to $\op(concatenate)$ $(C^1,
+\ldots, C^t)$ into $C^0$ along $(R_1 , \ldots , R_t)$ when invoking
 `glue-circuit' on the input $(C^0, \ldots , C^t)$ and $\tau_R = \{R_1, \ldots ,
@@
 \begin{prop}
-  There is an algorithm that takes in a $(\mathbb{B}, \tau)$-circuit with unique
-  labels and outputs the syntactic equivalence relation on its gates. This
-  algorithm runs in polynomial time.
+  Let $C_n := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
+  \tau)$-circuit with unique labels. There is a deterministic algorithm that
+  takes in such a circuit and outputs the syntactic equivalence relation on $G$.
+  Moreover, this algorithm runs in time polynomial in the size of the circuit.
   \label{prop:unique-labels-syntactic-equiv}
@@
 \begin{proof}
+  We proceed to define a relation $\sim$ by induction on height (i.e. distance
+  from an input gate). This relation will be the syntactic equivalence relation
+  on $G$. It is easy to check the conditions for syntactic equivalence for gates
+  of height 0 as all such gates are input gates and so are either constant gates
+  or relational gates. Suppose $g$ and $h$ are gates of height greater than
+  zero. We only need to check conditions (i), (iv) and (v) of syntactic
+  equivalence. It is easy to check (i) and (v). If either condition is false
+  then $g$ and $h$ are not syntacticly equivalent. So suppose $g$ and $h$ are
+  two internal gates such that $\Sigma (g) = \Sigma(h)$ and if they are both
+  output gates then $\Omega^{-1}(g) = \Omega^{-1}(h)$. It remains to check if
+  $L(g)/{\sim}$ and $L(h)/{\sim}$ are isomorphism equivalent. First check if
+  $H_h /{\sim} = H_g /{\sim}$. If not, $g$ and $h$ are not syntactically
+  equivalent. So suppose $H_h /{\sim} = H_g /{\sim}$. We know that $C_n$ has
+  unique labels, and so $L(g)/{\sim}$ and $L(h)/{\sim}$ are injections so are
+  isomorphism equivalent if, and only if, $L(g)^{-1}L(h)$ acts like an
+  isomorphism. This can be checked by first checking that the function induces a
+  sorted permutation on the universe of $g$ (which can be done by iterating over
+  the index of $g$). This is sufficient as $L(g)(L(g)^{-1}L(h)) = L(h)$.
+
+  It is easy to see that, given a reasonable binary encoding of a circuit, the
+  above procedure can be implemented so as to run in polynomial time, and that
+  the relation $\sim$ is the syntactic equivalence relation on $C_n$.
 \end{proof}
+
+% \begin{prop}
+%   There is an algorithm that takes in a $(\mathbb{B}, \tau)$-circuit $C$ with
+%   unique labels and outputs the syntactic equivalence relation on its gates.
+%   This algorithm runs in time polynomial in the size of $C$.
+%   \label{prop:unique-labels-syntactic-equiv}
+% \end{prop}
+% \begin{proof}
+%   We build of the relation by induction. Let $g$
+% \end{proof}
 
@@
 \subsection{Translating FPR to Symmetric Matrix Circuits}
-Anderson and Dawar~\cite{} define (or reference) a translation of formulas of
-$\FPC$ into equivalent $P$-uniform families of symmetric majority-circuits. More
-formally, they show that for $\theta(\vec{x}) \in \FPC[\tau]$ there exists a
-$P$-uniform family of symmetric majority-circuits $(C_n)_{n \in \nats}$ such
-that the query computed by $(C_n)_{n \in \nats}$ is equal to the query defined
-by $\theta (\vec{x})$. In this subsection we develop a similar translation from
-formulas of $\FPR$ into $P$-uniform families of symmetric matrix-circuits.
+Anderson and Dawar~\cite{} define a translation from formulas of $\FPC$ into
+equivalent $P$-uniform families of symmetric majority-circuits. More formally,
+they show that for $\theta(\vec{x}) \in \FPC[\tau]$ there exists a $P$-uniform
+family of symmetric majority-circuits $(C_n)_{n \in \nats}$ such that the query
+computed by $(C_n)_{n \in \nats}$ is equal to the query defined by $\theta
+(\vec{x})$. In this subsection we develop a similar translation from formulas of
+$\FPR$ into $P$-uniform families of symmetric matrix-circuits.
 
@@
 
-  Suppose $\phi_1, \phi_2 \in \FPR[\tau]$ are matrix-circuit-translatable and
-  $\theta (\vec{x}) = \phi_1(\vec{x}) \land \phi_2(\vec{x})$. Let $R_{\phi_1}$
-  and $R_{\phi_2}$ be two $\vert \vec{x} \vert$-ary relation symbols not in
-  $\tau$. Let $\theta' (\vec{x}) := R_{\phi_1}(\vec{x}) \land
-  R_{\phi_2}(\vec{x})$. This is a formula of $\FPC$, and so we may efficiently
-  compute $C^{\theta'}_n$ using the construction in \cite{AndersonD17}. From the
-  inductive hypothesis, for each $i \in \{1,2\}$ we may also efficiently compute
-  the circuit $C^{\phi_i}_n = \langle G_i, \Omega_i, \Sigma_i Lambda_i, L_i
-  \rangle$. We construct $C^{\theta}_n$ by `gluing' $C^{\phi_1}$ and
-  $C^{\phi_2}$ into $C^{\theta'}_n$ along $R_1$ and $R_2$
+  We first consider the case where $\theta(\vec{x})$ is a conjunction of
+  matrix-circuit-translatable formulas. Suppose $\phi_1, \phi_2 \in \FPR[\tau]$
+  are matrix-circuit-translatable and $\theta (\vec{x}) = \phi_1(\vec{x}) \land
+  \phi_2(\vec{x})$. Let $R_{\phi_1}$ and $R_{\phi_2}$ be two $\vert \vec{x}
+  \vert$-ary relation symbols not in $\tau$. Let $\theta' (\vec{x}) :=
+  R_{\phi_1}(\vec{x}) \land R_{\phi_2}(\vec{x})$. Let $n \in \nats$. Since
+  $\theta'(\vec{x})$ is a formula of $\FPC$, we may efficiently compute
+  $C^{\theta'}_n$ using the construction in \cite{AndersonD17}. From the
+  inductive hypothesis, for each $i \in \{1,2\}$ we may efficiently compute the
+  circuit $C^{\phi_i}_n = \langle G_i, \Omega_i, \Sigma_i Lambda_i, L_i
+  \rangle$. Let $R \in \tau$ and let $D^{\theta}_n :=
+  \op{compose}(C^{\theta'}_n, (C^{\phi_1}_n, C^{\phi_2}_n), (R_1, R_2), R)$. Let
+  $H$ consist of all non-output gates in $D^{\theta}_n$. From the inductive
+  hypothesis all gates in $H$ have unique labels. Let $C^{\theta}_n :=
+  \op{make-injective-all}(\op{merge-all}(D^{\theta}_n, H))$.
+
+  Notice that $D^{\theta}_n$ computes the same relation as defined by
+  $\theta(\vec{x})$ for structures of size $n$. Moreover, since the remaining
+  two operations preserve the function computed, it follows $C^{\theta}_n$
+  computes the same relation as defined by $\theta(\vec{x})$ for structures of
+  size $n$. Furthermore, since $C^{\phi_1}_n$, $C^{\phi_2}_n$ and $C^{theta'}_n$
+  are symmetric so is $C^{\theta}_n$. Lastly, notice that all non-output gates
+  in $D^{\theta}_n$ have unique labels. After the $\op{merge-all}$ and
+  $\op{make-injective-all}$ operation the output gates have unique labels, and thus
+  $C^{\theta}_n$ has unique labels. This construction takes in a natural number
+  $n$ and produces the required circuit $C^{\theta}_n$. This construction can be
+  computed by an algorithm in time polynomial in $n$. Thus $\theta(\vec{x})$ is
+  matrix-circuit-translatable.
 
   % We construct the circuit $C'_n = \langle G', \Omega', \Sigma',
-  % \Lambda', L' \rangle$ by `inserting' $C^{\phi_1}_n$ and $C^{\phi_2}_n$ into
+  % \Lambda', L' \rangle$ by `inserting' $C^{\phi_1}_n$ and $C^{\phi_2}_n$
+  % into
   % $C^{\theta'}_n$. We now construct $C^{\theta}_n$ from $C'_n$ as follows:
@@
 
-  We note that, since $C^{\phi_1}_n$, $C^{\phi_2}_n$ and $C^{\theta'}_n$ have
-  unique labels, the only gates that might not have unique labels in
-  $C^{\theta}_n$ are those whose input gates include gates in the range of
-  $\Omega_1$ or $\Omega_2$. However, all such gates are symmetric and steps (2)
-  and (3) above guarantee that these gates have unique labels. Finally, we note
-  that this algorithm can implemented such that the computation of
-  $C^{\theta}_n$ from $n$ runs in time polynomial in $n$.
+  % We note that, since $C^{\phi_1}_n$, $C^{\phi_2}_n$ and $C^{\theta'}_n$ have
+  % unique labels, the only gates that might not have unique labels in
+  % $C^{\theta}_n$ are those whose input gates include gates in the range of
+  % $\Omega_1$ or $\Omega_2$. However, all such gates are symmetric and steps
+  % (2)
+  % and (3) above guarantee that these gates have unique labels. Finally, we
+  % note
+  % that this algorithm can implemented such that the computation of
+  % $C^{\theta}_n$ from $n$ runs in time polynomial in $n$.
 
-  Analogous algorithms can be used to prove that other formulas are
-  circuit-translatable. Indeed, for circuit-translatable $\phi, \phi_1, \phi_2
-  \in \FPR[\tau]$ an analogous algorithm allows us to prove that
-  $\phi_1(\vec{x}) \lor \phi_2(\vec{x})$, $\neg \phi(\vec{x})$, $\forall y. \phi
-  (\vec{x}, y)$, $\exists y. \phi (\vec{x}, y)$ are all circuit-translatable.
+  The approach used above for resolving the conjunctive case can be thought of
+  as having three steps. First, replacing each sub-formula with a relation
+  symbol, resulting in a formula of $\FPC$. Second, using the algorithms from
+  the inductive hypothesis' on sub-formulas, producing appropriate families of
+  circuits computing each sub-formula, and the known circuit-translation for
+  formulas of $\FPC$, in order to to produce an appropriate family of circuits
+  computing the operation on these sub-formulas. Third, using the concatenation
+  operation to combine these circuit families and two final operations in order
+  to ensure the family has the required properties.
+
+  This same approach can be used for to handle many other cases. For
+  matrix-circuit-translatable $\phi, \phi_1, \phi_2 \in \FPR[\tau]$ similar
+  constructions can be used to prove that if $\theta(\vec{x}) \in FPR[\tau]$ is
+  equal to $\phi_1(\vec{x}) \lor \phi_2(\vec{x})$, $\neg \phi(\vec{x})$,
+  $\forall y. \phi (\vec{x}, y)$ or $\exists y. \phi (\vec{x}, y)$ then
+  $\theta(\vec{x})$ is matrix-circuit-translatable.
 
   Suppose $\theta(\vec{x}) = [\lfp_{V, \vec{y}} \phi(\vec{y}, V)](\vec{x})$ for
-  some circuit-translatable formula $\phi(\vec{x}, \vec{y}) \in FPR[\tau \uplus
-  \{V\}]$ and $k$-ary relation symbol $V$. We now describe an algorithm that
-  takes in a natural number $n$ and outputs $C^{\theta}_n$. We have that we may
-  efficiently compute $C^{\phi}_n$. For each $i \in [n^k]$ we construct a
+  some matrix-circuit-translatable formula $\phi(\vec{x}, \vec{y}) \in FPR[\tau
+  \uplus \{V\}]$ and $k$-ary relation symbol $V$. We now describe an algorithm
+  that takes in a natural number $n$ and outputs $C^{\theta}_n$. We have that we
+  may efficiently compute $C^{\phi}_n$. For each $i \in [n^k]$ we construct a
   circuit $C^i = \langle G^i, \Omega^i, \Sigma^i, \Lambda^i, L \rangle $ as
@@
 
-  We have from \cite{} that a formula containing number terms may be converted
-  into an equivalent family of formulas containing counting quantifiers. More
-  formally if $\theta (\vec{x})$ contains number terms then there exists an
-  algorithm that takes as input a natural number $n$ and outputs a formula
-  $\theta_n(\vec{x}) \in C$ with counting quantifiers and no number terms which
-  is equivalent to $\theta(\vec{x})$ for structures of size $n$ and does not
-  contain any number terms. Moreover, this algorithm runs in time polynomial in
-  $n$.
+  The result in \cite{} establishes that for every formula $\theta(\vec{x})$
+  containing number-terms there is a $P$-uniform family of formulas
+  $(\theta_n(\vec{x}))_{n \in \nats}$ containing counting quantifiers and no
+  number-terms, and such that for all $n \in \nats$, $\theta(\vec{x})$ and
+  $\theta_n(\vec{x})$ are equivalent on structures of size $n$.
 
-  Thus to handle the number-term case it is sufficient to show that if
-  $\phi(\vec{x}) \in \FPR[\tau]$ is circuit-translatable then $\theta(\vec{x})
-  := C^{k}y. \phi(\vec{x}, y)$ is circuit translatable. Again, an analogous
-  construction as for the $\AND$-gate case described in detail above is
-  sufficient.
+  % gives for each $\theta (\vec{x}) \in FPC[\tau]$ a $P$-uniform family of
+  % formulas $(\theta_n)_{n \in \nats}$ such that $\theta_n(\vec{x})$ is in the
+  % extension of fixed-point logic with counting quantifiers and is equivalent
+  % to
+  % $\theta(\vec{x})$ on structures of size $n$. Similarly, it can be shown that
+  % for $\theta (\vec{x}) \in FPR[\tau]$ there exists an algorithm that takes as
+  % input a natural number $n$ and outputs a formula $\theta_n(\vec{x})$ with
+  % counting quantifiers and no number terms which is equivalent to
+  % $\theta(\vec{x})$ for structures of size $n$ and does not contain any number
+  % terms. Moreover, this algorithm runs in time polynomial in $n$.
 
-  We have from \cite{} that a formula containing rank operator may be converted
-  into an equivalent family of formulas containing rank quantifiers. In other
-  words for a given formula $\theta(\vec{x}) \in \FPR[\tau]$ containing rank
-  operators there exists an algorithm that takes as input a natural number $n$
-  and outputs a formula $\theta_n(\vec{x})$ with rank quantifiers and no rank
-  operators. It is thus sufficient to prove that if $\phi(\vec{z}, \vec{y},
-  \vec{x})$ is circuit-translatable, $p$ is prime and $r$ is a natural number
-  then $\theta(\vec{x}) = \rank^{\leq r}_p \vec{z} \vec{y}. \phi(\vec{z},
-  \vec{y}, \vec{x})$ is circuit-translatable. We define an algorithm that takes
-  as input a natural number $n$ outputs the required circuit $C^{\theta}_n$.
+  Thus, in order to handle the number-term case, it is sufficient to show that
+  if $\phi(\vec{x}) \in \FPR[\tau]$ is circuit-translatable then
+  $\theta(\vec{x}) := C^{k}y. \phi(\vec{x}, y)$ is matrix-circuit-translatable.
+  A similar construction as for the universal and existential quantifier gives
+  the required algorithm.
 
-  We may efficiently compute the $(\mathbb{B}_{\rank}, \tau)$-circuit
-  $C^{\phi}_n = \langle G^{\phi}, \Omega^{\phi}, \Sigma^{\phi}, \Lambda^{\phi},
-  L^{\phi} \rangle$. Let $k:= \vert \vec{x} \vert$, $k_1 : = \vert \vec{z}
-  \vert$ and $k_2 := \vert \vec{y} \vert$. We now define a $(\mathbb{B}_{\rank},
-  \{ R \})$-circuit $C':= \langle G', \Omega', \Sigma', \Lambda', L'\rangle$,
-  where $R$ is a $(k_1 + k_2 +k)$-arity relation symbol. Let $G_1' :=
-  \{g_{\rank, \vec{c}} : \vec{c} \in [n]^k\}$ and $G_2' : = \{ g_{R, \vec{a},
-    \vec{b}, \vec{c}} : \vec{a} \in [n]^{k_1}, \vec{b} \in [n]^{k_2}, \vec{c}
-  \in [n]^{k}\}$.
+  The result in \cite{} establishes that for every formula $\theta(\vec{x}) \in
+  \FPR[\tau]$ containing rank operators, there exists an algorithm that takes as
+  input a natural number $n$ and outputs a formula $\theta_n(\vec{x})$ with rank
+  quantifiers and no rank operators such that $\theta(\vec{x})$ and
+  $\theta_n(\vec{x})$ are equivalent on structures of size $n$. It is thus
+  sufficient to prove that, for matrix-circuit-translatable $\phi(\vec{z},
+  \vec{y}, \vec{x}) \in \FPR[\tau]$ is, a prime $p$, and a natural number $r$,
+  $\theta(\vec{x}) := \rank^{\leq r}_p \vec{z} \vec{y}. \phi(\vec{z}, \vec{y},
+  \vec{x})$ is circuit-translatable. We define an algorithm that takes as input
+  a natural number $n$ outputs the required circuit $C^{\theta}_n$.
+
+  From the inductive hypothesis we may efficiently compute $C^{\phi}_n = \langle
+  G^{\phi}, \Omega^{\phi}, \Sigma^{\phi}, \Lambda^{\phi}, L^{\phi} \rangle$. Let
+  $k:= \vert \vec{x} \vert$, $k_1 : = \vert \vec{z} \vert$ and $k_2 := \vert
+  \vec{y} \vert$. Let $R_\phi$ be a $(k_1 + k_2 + k)$-ary relation symbol not in
+  $\tau$. Let $\theta'(\vec{x}) = \rank^{\leq r}_r := \vec{z}, \vec{y}. \phi
+  (\vec{z}, \vec{y}, \vec{x})$. We now define a $(\mathbb{B}_{\rank}, \{
+  R_{\phi} \})$-circuit $C^{\theta'}_n:= \langle G^{\theta'}, \Omega^{\theta'},
+  \Sigma^{\theta'}, \Lambda^{\theta'}, L^{\theta'}\rangle$ as follows. Let $G_1
+  := \{g_{\rank, \vec{c}} : \vec{c} \in [n]^k\}$ and $G_2 : = \{ g_{R_{\phi},
+    \vec{a}, \vec{b}, \vec{c}} : \vec{a} \in [n]^{k_1}, \vec{b} \in [n]^{k_2},
+  \vec{c} \in [n]^{k}\}$.
 
@@
     \setlength\itemsep{0mm}
-  \item Let $G' := G_1' \uplus G_2'$,
-  \item $\Omega'$ be an injection from $[n]^k$ to $G'$ defined by
-    $\Omega'(\vec{c}) = g_{\rank, \vec{c}}$,
+  \item Let $G^{\theta'} := G_1 \uplus G_2$,
+  \item $\Omega^{\theta'}$ be an injection from $[n]^k$ to $G'$ defined by
+    $\Omega^{\theta'}(\vec{c}) = g_{\rank, \vec{c}}$,
 
-  \item $\Sigma' (g) := rk^r_p$ if $g \in G_1'$ and $\Sigma'(g) = R$ if $g \in
-    G_2'$,
+  \item $\Sigma^{\theta'} (g) := rk^r_p$ if $g \in G_1$ and $\Sigma^{\theta'}(g)
+    = R_\phi$ if $g \in G_2$,
   \item For each $(\vec{a}, \vec{b}, \vec{c}) \in [n]^{k_1 +k_2 + k}$ let
-    $\Lambda' (\vec{a}, \vec{b}, \vec{c}) := g_{R, \vec{a}, \vec{b}, \vec{c}}$,
-    and
+    $\Lambda^{\theta'} (\vec{a}, \vec{b}, \vec{c}) := g_{R_{\phi}, \vec{a},
+      \vec{b}, \vec{c}}$, and
 
-  \item For each gate $g_{\rank, \vec{a}} \in G_1'$ let $L(g_{\rank, \vec{a}}):
-    [n]^{k_1} \times [n]^{k_2} \rightarrow G'$ be defined by $L(g_{\rank,
-      \vec{c}})(\vec{a}, \vec{b}) := g_{R, \vec{a}, \vec{b}, \vec{c}}$ for each
-    $\vec{a} \in [n]^{k_1}$ and $\vec{b} \in [n]^{k_2}$.
+  \item For each gate $g_{\rank, \vec{a}} \in G_1$ let $L(g_{\rank, \vec{a}}):
+    [n]^{k_1} \times [n]^{k_2} \rightarrow G^{\theta'}$ be defined by
+    $L(g_{\rank, \vec{c}})(\vec{a}, \vec{b}) := g_{R_\phi, \vec{a}, \vec{b},
+      \vec{c}}$ for each $\vec{a} \in [n]^{k_1}$ and $\vec{b} \in [n]^{k_2}$.
+  \end{itemize}
 
-    \end{itemize}
-    Let $C^{\theta}_n$ be the result of `gluing' $C^{\phi}_n$ into $C'$.
+  It is easy to see that both $C^{\theta'}_n$ (and $C^{\phi}_n$) are symmetric
+  rank-circuits with unique labels. Let $R$ be a relation symbol in $\tau$. Let
+  $D^{\theta}_n := \op{compose}(C^{\theta'}_n, (C^{\phi}_n), (R_\phi), R)$. Let
+  $H$ consist of all non-output gates in $D^{\theta}_n$. From the inductive
+  hypothesis all gates in $H$ have unique labels. Let $C^{\theta}_n :=
+  \op{make-injective-all}(\op{merge-all}(D^{\theta}_n, H))$.
 
-    It is easy to see that both $C'$ and $C^{\phi}_n$ are symmetric
-    rank-circuits with unique labels. Thus $C^{\theta}_n$ is a symmetric
-    rank-circuit with unique labels. The construction of $C'$, and hence
-    $C^{\theta}_n$, can be implemented so as to run in time polynomial in $n$.
-    The construction ensures that the circuit family $(C^{\theta}_n)_{n \in
-      \nats}$ computes the same query as the one defined by $\theta(\vec{x})$.
+  Since $C^{\theta'}_n$ and $C^{\phi}_n$ are symmetric and have unique labels it
+  follows that $D^{\theta}_n$ is a symmetric rank-circuit with unique labels. It
+  can be shown that the construction of $C^{\theta}_n$ given the number $n$ can
+  be implemented as an algorithm running in time polynomial in $n$. The
+  construction ensures that the circuit family $(C^{\theta}_n)_{n \in \nats}$
+  computes the same query as the one defined by $\theta(\vec{x})$.
 
@@
 
-  % such that for any structure $\mathcal{A}$ of size $n$ and an assignment $$
-  % to the tuple of variables $\vec{x}$
+% \langle G', \Omega', \Sigma', \Lambda', L'\rangle$, where $R$ is a $(k_1 + k_2
+% +k)$-arity relation symbol. Let $G_1' := \{g_{\rank, \vec{c}} : \vec{c} \in
+% [n]^k\}$ and $G_2' : = \{ g_{R, \vec{a}, \vec{b}, \vec{c}} : \vec{a} \in
+% [n]^{k_1}, \vec{b} \in [n]^{k_2}, \vec{c} \in [n]^{k}\}$.
+
+% \begin{itemize}
+%   \setlength\itemsep{0mm}
+% \item Let $G' := G_1' \uplus G_2'$,
+% \item $\Omega'$ be an injection from $[n]^k$ to $G'$ defined by
+%   $\Omega'(\vec{c}) = g_{\rank, \vec{c}}$,
+
+% \item $\Sigma' (g) := rk^r_p$ if $g \in G_1'$ and $\Sigma'(g) = R$ if $g \in
+%   G_2'$,
+% \item For each $(\vec{a}, \vec{b}, \vec{c}) \in [n]^{k_1 +k_2 + k}$ let
+%   $\Lambda' (\vec{a}, \vec{b}, \vec{c}) := g_{R, \vec{a}, \vec{b},
+%   \vec{c}}$,
+%   and
+
+% \item For each gate $g_{\rank, \vec{a}} \in G_1'$ let $L(g_{\rank, \vec{a}}):
+%   [n]^{k_1} \times [n]^{k_2} \rightarrow G'$ be defined by $L(g_{\rank,
+%   \vec{c}})(\vec{a}, \vec{b}) := g_{R, \vec{a}, \vec{b}, \vec{c}}$ for each
+%   $\vec{a} \in [n]^{k_1}$ and $\vec{b} \in [n]^{k_2}$.
+
+% \end{itemize}
+% Let $C^{\theta}_n$ be the result of `gluing' $C^{\phi}_n$ into $C'$.
+
+% It is easy to see that both $C'$ and $C^{\phi}_n$ are symmetric rank-circuits
+% with unique labels. Thus $C^{\theta}_n$ is a symmetric rank-circuit with
+% unique labels. The construction of $C'$, and hence $C^{\theta}_n$, can be
+% implemented so as to run in time polynomial in $n$. The construction ensures
+% that the circuit family $(C^{\theta}_n)_{n \in \nats}$ computes the same query
+% as the one defined by $\theta(\vec{x})$.
+
+% It remains only to note that any atomic formula of $\FPR[\tau]$ is trivially
+% circuit-translatable. The result thus follows.
+% \end{proof}
+
+% such that for any structure $\mathcal{A}$ of size $n$ and an assignment $$ to
+% the tuple of variables $\vec{x}$
 
@@
 
-  % it follows from Lemma \ref{}, that the syntactic equivalence relation on
-  % $G_1 \uplus G_2$ can be efficiently computed.
+% it follows from Lemma \ref{}, that the syntactic equivalence relation on $G_1
+% \uplus G_2$ can be efficiently computed.
 
 % Note that the construction guarantees that $C^{\theta}_n$ is symmetric.
-  % Moreover, since the only gates in $C^{\theta}_n$ are either output gates
-  % or gates
+% Moreover, since the only gates in $C^{\theta}_n$ are either output gates or
+% gates
 
 % Suppose $\theta(\vec{x})$ is of the form $\phi_1(\vec{x}) \land
-  % \phi_2(\vec{x})$, $\phi_1(\vec{x})\lor \phi_2(\vec{x})$, $\neg
-  % \phi(\vec{x})$, $\thr_k(y).\phi(\vec{x}, y)$, $\forall y. \phi (\vec{x},
-  % y)$, $\exists y. \phi (\vec{x}, y)$, an equality between two numerical
-  % terms or an application of the least-fixed-point operator, and each of
-  % these sub-formulas is $(\mathbb{B}, \tau)$-circuit-translatable} then
-  % $\theta(\vec{x})$ is $(\mathbb{B}, \tau)$-circuit-translatable}. This
-  % follows from the following construction. Let $n \in \nats$. We take derive
-  % the formula $\theta'(\vec{x})$ from $\theta(\vec{x})$ by replacing each
-  % sub-formula $\phi(\vec{z})$ with the formula $R_\phi(\vec{z})$ (adding in
-  % some new relational symbol $R_\phi$). We may then translate
-  % $\theta'(\vec{x})$ into a $P$-uniform family of symmetric circuits with
-  % threshold and unique labels $(C^{\theta'}_n)_{n \in \nats}$. For each $n$
-  % we then replace the relational gates in $C^{\theta'}_n$ labelled by
-  % $R_\phi$ with the circuit $C^{\phi}_n$ (that is, we add in the entire
-  % circuit $C^\phi_n$ and replace each relational gate $g$ labelled by
-  % $R_\phi$ such that $\vec{a}:= \Lambda(\vec{a})$ with with the output gates
-  % of $C^{\phi}_n$ such that if $g$ is a relational gate computing
-  % $R_\phi(\vec{a})$ then $g$ is replaced by the gate $\Omega^{-1}(\vec{a})$
-  % in $C^{\phi}_n$). We call this new circuit $C^\theta_n$. It is easy to see
-  % that this circuit is symmetric. To see that it has unique labels, notice
-  % that we need only check
+% \phi_2(\vec{x})$, $\phi_1(\vec{x})\lor \phi_2(\vec{x})$, $\neg \phi(\vec{x})$,
+% $\thr_k(y).\phi(\vec{x}, y)$, $\forall y. \phi (\vec{x}, y)$, $\exists y. \phi
+% (\vec{x}, y)$, an equality between two numerical terms or an application of
+% the least-fixed-point operator, and each of these sub-formulas is
+% $(\mathbb{B}, \tau)$-circuit-translatable} then $\theta(\vec{x})$ is
+% $(\mathbb{B}, \tau)$-circuit-translatable}. This follows from the following
+% construction. Let $n \in \nats$. We take derive the formula $\theta'(\vec{x})$
+% from $\theta(\vec{x})$ by replacing each sub-formula $\phi(\vec{z})$ with the
+% formula $R_\phi(\vec{z})$ (adding in some new relational symbol $R_\phi$). We
+% may then translate $\theta'(\vec{x})$ into a $P$-uniform family of symmetric
+% circuits with threshold and unique labels $(C^{\theta'}_n)_{n \in \nats}$. For
+% each $n$ we then replace the relational gates in $C^{\theta'}_n$ labelled by
+% $R_\phi$ with the circuit $C^{\phi}_n$ (that is, we add in the entire circuit
+% $C^\phi_n$ and replace each relational gate $g$ labelled by $R_\phi$ such that
+% $\vec{a}:= \Lambda(\vec{a})$ with with the output gates of $C^{\phi}_n$ such
+% that if $g$ is a relational gate computing $R_\phi(\vec{a})$ then $g$ is
+% replaced by the gate $\Omega^{-1}(\vec{a})$ in $C^{\phi}_n$). We call this new
+% circuit $C^\theta_n$. It is easy to see that this circuit is symmetric. To see
+% that it has unique labels, notice that we need only check
 
@@
 
-  % We should like to argue that for any $\theta(\vec{x}) \in \FPR[\tau]$ if
-  % every sub-formula of $\theta(\vec{x})$ is $(\mathbb_{\mat}, \tau)$-circuit
+% We should like to argue that for any $\theta(\vec{x}) \in \FPR[\tau]$ if every
+% sub-formula of $\theta(\vec{x})$ is $(\mathbb_{\mat}, \tau)$-circuit
 % translatable then $\theta(\vec{x})$ is $(\mathbb_{\mat}, \tau)$-circuit
@@
 % \land \phi_2(\vec{x})$, $\phi_1(\vec{x})\lor \phi_2(\vec{x})$, $\neg
-  % \phi(\vec{x})$, $\thr_k(y).\phi(\vec{x}, y)$, $\forall y. \phi (\vec{x},
-  % y)$, $\exists y. \phi (\vec{x}, y)$, an equality between two numerical terms
-  % or an application of the least-fixed-point operator, and each of these
-  % sub-formulas is $(\mathbb{B}, \tau)$-circuit-translatable} then
-  % $\theta(\vec{x})$ is $(\mathbb{B}, \tau)$-circuit-translatable}. This
-  % follows from the following construction. Let $n \in \nats$. We take derive
-  % the formula $\theta'(\vec{x})$ from $\theta(\vec{x})$ by replacing each
-  % sub-formula $\phi(\vec{z})$ with the formula $R_\phi(\vec{z})$ (adding in
-  % some new relational symbol $R_\phi$). We may then translate
-  % $\theta'(\vec{x})$ into a $P$-uniform family of symmetric circuits with
-  % threshold and unique labels $(C^{\theta'}_n)_{n \in \nats}$. For each $n$ we
-  % then replace the relational gates in $C^{\theta'}_n$ labelled by $R_\phi$
-  % with the circuit $C^{\phi}_n$ (that is, we add in the entire circuit
-  % $C^\phi_n$ and replace each relational gate $g$ labelled by $R_\phi$ such
-  % that $\vec{a}:= \Lambda(\vec{a})$ with with the output gates of $C^{\phi}_n$
-  % such that if $g$ is a relational gate computing $R_\phi(\vec{a})$ then $g$
-  % is replaced by the gate $\Omega^{-1}(\vec{a})$ in $C^{\phi}_n$). We call
-  % this new circuit $C^\theta_n$. It is easy to see that this circuit is
-  % symmetric. To see that it has unique labels, notice that we need only check
+% \phi(\vec{x})$, $\thr_k(y).\phi(\vec{x}, y)$, $\forall y. \phi (\vec{x}, y)$,
+% $\exists y. \phi (\vec{x}, y)$, an equality between two numerical terms or an
+% application of the least-fixed-point operator, and each of these sub-formulas
+% is $(\mathbb{B}, \tau)$-circuit-translatable} then $\theta(\vec{x})$ is
+% $(\mathbb{B}, \tau)$-circuit-translatable}. This follows from the following
+% construction. Let $n \in \nats$. We take derive the formula $\theta'(\vec{x})$
+% from $\theta(\vec{x})$ by replacing each sub-formula $\phi(\vec{z})$ with the
+% formula $R_\phi(\vec{z})$ (adding in some new relational symbol $R_\phi$). We
+% may then translate $\theta'(\vec{x})$ into a $P$-uniform family of symmetric
+% circuits with threshold and unique labels $(C^{\theta'}_n)_{n \in \nats}$. For
+% each $n$ we then replace the relational gates in $C^{\theta'}_n$ labelled by
+% $R_\phi$ with the circuit $C^{\phi}_n$ (that is, we add in the entire circuit
+% $C^\phi_n$ and replace each relational gate $g$ labelled by $R_\phi$ such that
+% $\vec{a}:= \Lambda(\vec{a})$ with with the output gates of $C^{\phi}_n$ such
+% that if $g$ is a relational gate computing $R_\phi(\vec{a})$ then $g$ is
+% replaced by the gate $\Omega^{-1}(\vec{a})$ in $C^{\phi}_n$). We call this new
+% circuit $C^\theta_n$. It is easy to see that this circuit is symmetric. To see
+% that it has unique labels, notice that we need only check
 
@@
 % follow similarly. Suppose $\theta (\vec{x}) = \phi_1(\vec{x}) \land
-  % \phi_2(\vec{x})$. We now describe an algorithm that takes in $n\in \nats$
-  % and outputs a formula $C^\theta_n$ with the required properties. We first
-  % introduce two relation symbols $R_{\phi_1}$ and $R_{\phi_2}$ not in $\tau$
-  % and with arity $\vert\vec{x}\vert$. We define $\theta' (\vec{x}) =
+% \phi_2(\vec{x})$. We now describe an algorithm that takes in $n\in \nats$ and
+% outputs a formula $C^\theta_n$ with the required properties. We first
+% introduce two relation symbols $R_{\phi_1}$ and $R_{\phi_2}$ not in $\tau$ and
+% with arity $\vert\vec{x}\vert$. We define $\theta' (\vec{x}) =
 % R_{\phi_1}(\vec{x}) \land R_{\phi_2}(\vec{x})$ and compute the associated
-  % symmetric threshold circuit with unique labels $C^{\theta'}_n$. Similarly,
-  % for each $i\ \in \{1,2\}$ we may compute the symmetric $(\mathbb{B},
+% symmetric threshold circuit with unique labels $C^{\theta'}_n$. Similarly, for
+% each $i\ \in \{1,2\}$ we may compute the symmetric $(\mathbb{B},
 % \tau)$-circuit with unique labels corresponding to $\phi_i$ that takes in
-  % inputs of size $n$, $C^{\phi_i}_n = \langle G_i, \Omega_i, \Sigma_i
-  % Lambda_i, L_i \rangle$ algorithms given by the inductive hypothesis. We then
-  % construct $C^{\theta}_n$ by inserting into $C^{\theta'}_n$ the circuits
-  % $C^{\phi_1}_n$ and $C^{\phi_2}_n$ (that is, taking a disjoint union of the
-  % sets of gates and the functions that define each circuit -- with the
-  % exception of $\Omega$ which is specified by $C^{\theta'}_n$ alone). Then for
-  % all $i \in \{1,2\}$ and each relational gate $g$ in $C^{\theta}_n$ such that
-  % $\Sigma(g) = R_{\phi_i}$ we replace $g$ with $\Omega_i(\Lambda_i(g))$. Since
-  % $C^{\phi_1}_n$ and $C^{\phi_2}_n$ have unique labels, it follows from Lemma
-  % \ref{} that we can efficiently decide if any two gates $g_1, g_2 \in G_1
-  % \uplus G_2$ are syntactical equivalent. For each pair of gates $g_1, g_2$ in
-  % the range of $\Omega_1 \uplus \Omega_2$ we check if $g_1 \equiv g_2$, and if
-  % so we merge them.
+% inputs of size $n$, $C^{\phi_i}_n = \langle G_i, \Omega_i, \Sigma_i Lambda_i,
+% L_i \rangle$ algorithms given by the inductive hypothesis. We then construct
+% $C^{\theta}_n$ by inserting into $C^{\theta'}_n$ the circuits $C^{\phi_1}_n$
+% and $C^{\phi_2}_n$ (that is, taking a disjoint union of the sets of gates and
+% the functions that define each circuit -- with the exception of $\Omega$ which
+% is specified by $C^{\theta'}_n$ alone). Then for all $i \in \{1,2\}$ and each
+% relational gate $g$ in $C^{\theta}_n$ such that $\Sigma(g) = R_{\phi_i}$ we
+% replace $g$ with $\Omega_i(\Lambda_i(g))$. Since $C^{\phi_1}_n$ and
+% $C^{\phi_2}_n$ have unique labels, it follows from Lemma \ref{} that we can
+% efficiently decide if any two gates $g_1, g_2 \in G_1 \uplus G_2$ are
+% syntactical equivalent. For each pair of gates $g_1, g_2$ in the range of
+% $\Omega_1 \uplus \Omega_2$ we check if $g_1 \equiv g_2$, and if so we merge
+% them.
 
 % The resultant circuit $C^{\theta}_n$ is clearly a symmetric $(\mathbb{B},
-  % \tau)-circuit$-circuit. Moreover, it is easy to see that if all pairs of
-  % gates in the range of $\Omega_1 \uplus Omega_2$ are not syntactical
-  % equivalent $g$ is a gate such that $h_1, h_2 \in H_g$ are syntactically
-  % equivalent then . it has unique labels (as the only point where two input
-  % gates could be equivalent
+% \tau)-circuit$-circuit. Moreover, it is easy to see that if all pairs of gates
+% in the range of $\Omega_1 \uplus Omega_2$ are not syntactical equivalent $g$
+% is a gate such that $h_1, h_2 \in H_g$ are syntactically equivalent then . it
+% has unique labels (as the only point where two input gates could be equivalent
 
@@
 % from the union of these circuits are syntactical equivalent. If any of their
-  % output gates are syntactically equivalent, merge these gates. This new
-  % circuit has disjoint
+% output gates are syntactically equivalent, merge these gates. This new circuit
+% has disjoint
 
@@
 % \FPR[\tau]$ such that $\phi$ formula of the form $\theta (\vec{z}): = [rk
-  % (\vec{x}, \vec {\nu} \leq \vec{t}, \vec{y}\vec{\mu} \leq \vec{s}, \pi \leq
-  % r). \phi(\vec{x}, \vec{nu}, \vec{y}, \vec(mu), \vec{s}, \vec{z})] \leq k$
-  % there is an equivalent $P$-uniform family of symmetric rank-circuits with
-  % unique labels $(C_n)_{n \in \nats}$ that compute the same query as $\theta$.
+% (\vec{x}, \vec {\nu} \leq \vec{t}, \vec{y}\vec{\mu} \leq \vec{s}, \pi \leq r).
+% \phi(\vec{x}, \vec{nu}, \vec{y}, \vec(mu), \vec{s}, \vec{z})] \leq k$ there is
+% an equivalent $P$-uniform family of symmetric rank-circuits with unique labels
+% $(C_n)_{n \in \nats}$ that compute the same query as $\theta$.
 
@@
 
-  % We define this transformation by recursion on the structure of the formula
-  % and note that and note that such a transformation can be implemented so as
-  % to run in time polynomial in $n$.
+% We define this transformation by recursion on the structure of the formula and
+% note that and note that such a transformation can be implemented so as to run
+% in time polynomial in $n$.
 

### 2017-11-28 sections/symmetric-circuits.tex
28 Nov 2017

@@
 
-%AD: re-wrote the introductory paragraphs to be a bit more substantive.
+% AD: re-wrote the introductory paragraphs to be a bit more substantive.
 
-A Boolean circuit $C$ computing a function from $\{0,1\}^n$ to
-$\{0,1\}$ is usually described as a directed acyclic graph, with each
-gate $g$ that has $m$ incoming edges labelled with a Boolean function
-$f_g : \{0,1\}^m \rightarrow \{0,1\}$ from a basis $\mathbb{B}$ and
-exactly $n$ input gates of $C$ are labelled by variables.  If the
-function $f_g$ can be arbitrary, then the circuit $C$ must impose an
-order on the gates that provide the inputs to $g$.  When we say that
-$C$ is a directed acyclic graph, without further ordering the nodes,
-we implicitly assume that the functions in the basis $\mathbb{B}$ are
-\emph{symmetric}.  That is to say $f_g$ is invariant under all
-permutations of its $m$ inputs.  This unstated assumption is pervasive
-in circuit complexity.  In particular, the standard Boolean basis of
-AND, OR and NOT gates as well as bases with majority or threshold
-gates only contain symmetric functions.
+A Boolean circuit $C$ computing a function from $\{0,1\}^n$ to $\{0,1\}$ is
+usually described as a directed acyclic graph, with each gate $g$ that has $m$
+incoming edges labelled with a Boolean function $f_g : \{0,1\}^m \rightarrow
+\{0,1\}$ from a basis $\mathbb{B}$ and exactly $n$ input gates of $C$ are
+labelled by variables. If the function $f_g$ can be arbitrary, then the circuit
+$C$ must impose an order on the gates that provide the inputs to $g$. When we
+say that $C$ is a directed acyclic graph, without further ordering the nodes, we
+implicitly assume that the functions in the basis $\mathbb{B}$ are
+\emph{symmetric}. That is to say $f_g$ is invariant under all permutations of
+its $m$ inputs. This unstated assumption is pervasive in circuit complexity. In
+particular, the standard Boolean basis of AND, OR and NOT gates as well as bases
+with majority or threshold gates only contain symmetric functions.
 
-We are interested in Boolean circuits that compute queries on
-structures, such as graphs.  In the case of (undirected, loop-free)
-graphs on $n$ vertices, such a circuit might compute a function from
-$\{0,1\}^{n \choose 2}$ to $\{0,1\}$.  In this case, the function
-computed by the circuit is not necessarily invariant under all
-permutations of the inputs, but it is invariant under all permutations
-of the $n \choose 2$ inputs induced by permutations of $[n]$.
-We are especially concerned with \emph{symmetric} circuits, that is
-those where the permutations of $[n]$ extend to automorphisms of the
-circuit.  Note that this use of the word ``symmetric'' is distinct to
-that its use when applied to Boolean functions.  For such circuits, Anderson and Dawar~\cite{AndersonD17}
-consider $\PT$-uniform circuits in the standard Boolean basis as
-well one with majority gates.  It is a consequence of their results
-that the latter are strictly more powerful than the former.  In
-particular, they are shown to be equivalent
-to the logic $\FPC$.  In contrast, we show, in this section, that adding any
-further symmetric functions to the basis does not allow us to extend
-the power of $\PT$-uniform symmetric circuits beyond that of $\FPC$.
+We are interested in Boolean circuits that compute queries on structures, such
+as graphs. In the case of (undirected, loop-free) graphs on $n$ vertices, such a
+circuit might compute a function from $\{0,1\}^{n \choose 2}$ to $\{0,1\}$. In
+this case, the function computed by the circuit is not necessarily invariant
+under all permutations of the inputs, but it is invariant under all permutations
+of the $n \choose 2$ inputs induced by permutations of $[n]$. We are especially
+concerned with \emph{symmetric} circuits, that is those where the permutations
+of $[n]$ extend to automorphisms of the circuit. Note that this use of the word
+``symmetric'' is distinct to that its use when applied to Boolean functions. For
+such circuits, Anderson and Dawar~\cite{AndersonD17} consider $\PT$-uniform
+circuits in the standard Boolean basis as well one with majority gates. It is a
+consequence of their results that the latter are strictly more powerful than the
+former. In particular, they are shown to be equivalent to the logic $\FPC$. In
+contrast, we show, in this section, that adding any further symmetric functions
+to the basis does not allow us to extend the power of $\PT$-uniform symmetric
+circuits beyond that of $\FPC$.
 
-As our aim is a circuit characterisation of $\FPR$, whose expressive
-power is strictly greater than that of $\FPC$, we need to
-consider gates corresponding to non-symmetric Boolean functions.  In
-particular, we consider \emph{rank} gates whose inputs are a matrix
-and whose result is invariant under row and column permutations.  To
-lead up to this, we first develop a general framework of structured
-Boolean functions.  These are functions whose inputs naturally encode
-$\tau$-structures and where the output is invariant under the natural
-symmetries of such structures.  The\emph{matrix-invariant} functions
-are a natural partiruclar case.   We therefore define symmetric circuits in a
-general form where gates can be labelled by \emph{isomorphism-invariant} structured
-functions.
+As our aim is a circuit characterisation of $\FPR$, whose expressive power is
+strictly greater than that of $\FPC$, we need to consider gates corresponding to
+non-symmetric Boolean functions. In particular, we consider \emph{rank} gates
+whose inputs are a matrix and whose result is invariant under row and column
+permutations. To lead up to this, we first develop a general framework of
+structured Boolean functions. These are functions whose inputs naturally encode
+$\tau$-structures and where the output is invariant under the natural symmetries
+of such structures. The\emph{matrix-invariant} functions are a natural
+partiruclar case. We therefore define symmetric circuits in a general form where
+gates can be labelled by \emph{isomorphism-invariant} structured functions.
 
 Ultimately, our aim is replicate the results Anderson and
-Dawar~\cite{AndersonD17} in this more general setting.  A difficulty
-we face is that the proof methods in that paper heavily rely on the
-assumption that the Boolean functions computed by individual gates are
-symmetric functions.  We address this difficulty in the next section.
+Dawar~\cite{AndersonD17} in this more general setting. A difficulty we face is
+that the proof methods in that paper heavily rely on the assumption that the
+Boolean functions computed by individual gates are symmetric functions. We
+address this difficulty in the next section.
 
 % Boolean circuits have long acted as an alternative model from which to study
-% algorithmic complexity. A circuit is evaluated for some input binary sequence by
-% recursively evaluating each gate in the circuit, starting from the input gates.
-% Suppose then we in the process of evaluating the circuit $C$ and are at the
-% stage of evaluating the gate $g$. We take the input sequence formed from the
-% evaluations of the gates input to $g$ and applying the element of the basis that
-% labels $g$ to that sequence. It follows that in order to evaluate $g$ we need to
-% suppose some order on the evaluations of the input gates. In many cases this
-% order is simply induced by an assumed order on the whole of the circuit; an
-% assumption common in most parts of complexity theory, where the encoding of
-% structures for computation induces such orders, but problematic in finite model
-% theory.
+% algorithmic complexity. A circuit is evaluated for some input binary sequence
+% by recursively evaluating each gate in the circuit, starting from the input
+% gates. Suppose then we in the process of evaluating the circuit $C$ and are at
+% the stage of evaluating the gate $g$. We take the input sequence formed from
+% the evaluations of the gates input to $g$ and applying the element of the
+% basis that labels $g$ to that sequence. It follows that in order to evaluate
+% $g$ we need to suppose some order on the evaluations of the input gates. In
+% many cases this order is simply induced by an assumed order on the whole of
+% the circuit; an assumption common in most parts of complexity theory, where
+% the encoding of structures for computation induces such orders, but
+% problematic in finite model theory.
 
@@
 % for characterising the expressive power of logics. In particular, research has
-% focused on symmetric circuits defined over bases of symmetric Boolean functions
-% (see \cite{}). The fact that the basis consist of only symmetric functions is a
-% crucial requirement, ensuring that the evaluation of a gate does not depend on
-% an external order. However, in this paper we will need to consider circuits with
-% gates that compute rank, a function that is not symmetric.
+% focused on symmetric circuits defined over bases of symmetric Boolean
+% functions (see \cite{}). The fact that the basis consist of only symmetric
+% functions is a crucial requirement, ensuring that the evaluation of a gate
+% does not depend on an external order. However, in this paper we will need to
+% consider circuits with gates that compute rank, a function that is not
+% symmetric.
 
-% In this section we extend this circuit model so as to allow for the inclusion of
-% non-symmetric functions in the basis. We allow each gate $g$ to index its input
-% gate in accordance with the basis element labeling $g$. We introduce the notion
-% of a \emph{structured function}, a Boolean function whose input is indexed in
-% accordance with a many-sorted vocabulary $\tau$. The input vector to a
-% structured function can then be thought of as encoding a $\tau$-structure. In
-% particular, we consider structured functions that compute properties of
-% $\tau$-structures, which we call \emph{isomorphism-invariant} structured
-% functions. We then define what it means for a circuit over a basis of
-% isomorphism-invariant structured functions to be symmetric. This generalises the
-% notion of a symmetric circuit. We also show that there are limitations on the
-% power of symmetric circuits over bases of symmetric functions, justifying the
-% importance of this generalisation.
+% In this section we extend this circuit model so as to allow for the inclusion
+% of non-symmetric functions in the basis. We allow each gate $g$ to index its
+% input gate in accordance with the basis element labeling $g$. We introduce the
+% notion of a \emph{structured function}, a Boolean function whose input is
+% indexed in accordance with a many-sorted vocabulary $\tau$. The input vector
+% to a structured function can then be thought of as encoding a
+% $\tau$-structure. In particular, we consider structured functions that compute
+% properties of $\tau$-structures, which we call \emph{isomorphism-invariant}
+% structured functions. We then define what it means for a circuit over a basis
+% of isomorphism-invariant structured functions to be symmetric. This
+% generalises the notion of a symmetric circuit. We also show that there are
+% limitations on the power of symmetric circuits over bases of symmetric
+% functions, justifying the importance of this generalisation.
 
@@
 
-%AD - rewrote the paragraph to reduce the use of subscripts and superscripts.
+% AD - rewrote the paragraph to reduce the use of subscripts and superscripts.
 Let $\tau = (R, S, \nu)$ be a many-sorted signature.
-% with $R = \{R_1 \ldots,
-% R_t\}$, $S = \{s_1, \ldots , s_p\}$, and $\nu(R_i) = (a^i_1, \ldots ,
-% a^i_{r_i)})$, where $r_i = \arty(R_i)$ and $a^i_q \in S$ for all $q \in
-% [r_i]$.
-Let $D := \biguplus_{s \in S} D_{s} = \{(s,d) : d \in D_s\}$, be a
-disjoint union of non-empty sets, indexed by $S$, i.e.\ $D$ is
-potentially the universe of a $\tau$-structure. We call $D$ a \emph{$\tau$-sorted set}.
-For each $P \in R$, let $P^D$ denote the trivial relation over the
-many-sorted universe $D$, i.e.\ $P^D := D_{a_1} \times \ldots \times
-D_{a_{r}}$, where $\nu(P) = (a_1, \ldots , a_{r)})$.   Let the \emph{index defined by the pair $(\tau, D)$} be
-the set $\biguplus_{P\in R} P^{D}$.  We use this set to index the input to a Boolean
-function, as such we abuse notation and denote the index defined by
-$(\tau, D)$ by $\ind(\tau, D)$. We call $\tau$ the vocabulary and $D$ the universe of $\ind(\tau, D)$.
+% with $R = \{R_1 \ldots, R_t\}$, $S = \{s_1, \ldots , s_p\}$, and $\nu(R_i) =
+% (a^i_1, \ldots , a^i_{r_i)})$, where $r_i = \arty(R_i)$ and $a^i_q \in S$ for
+% all $q \in [r_i]$.
+Let $D := \biguplus_{s \in S} D_{s} = \{(s,d) : d \in D_s\}$, be a disjoint
+union of non-empty sets, indexed by $S$, i.e.\ $D$ is potentially the universe
+of a $\tau$-structure. We call $D$ a \emph{$\tau$-sorted set}. For each $P \in
+R$, let $P^D$ denote the trivial relation over the many-sorted universe $D$,
+i.e.\ $P^D := D_{a_1} \times \ldots \times D_{a_{r}}$, where $\nu(P) = (a_1,
+\ldots , a_{r)})$. Let the \emph{index defined by the pair $(\tau, D)$} be the
+set $\biguplus_{P\in R} P^{D}$. We use this set to index the input to a Boolean
+function, as such we abuse notation and denote the index defined by $(\tau, D)$
+by $\ind(\tau, D)$. We call $\tau$ the vocabulary and $D$ the universe of
+$\ind(\tau, D)$.
 
 For the remainder of this subsection we fix a vocabulary $\tau$ and a
-many-sorted set $D=\biguplus_{s \in S} D_{s}$
-and let $X := \ind (\tau, D)$. Let $G \leq \sym_{X}$, and let
-$\sortsym(D) := \prod_{s \in S} \sym_{D_{s}}$.  We call the elements of $\sortsym(D)$ \emph{sorted permutations}. Note that
-$\sortsym(D)$ can be identified with a subgroup of $\sym_X$. There is an
-obvious action of $G$ on $X$.  We can extend this to an action on the set of functions
-of the form $f: X \rightarrow X$, for any set $H$, defined by $\sigma \cdot f(x)
-= f(\sigma \cdot x)$ for all $x \in X$, $\sigma \in G$.
+many-sorted set $D=\biguplus_{s \in S} D_{s}$ and let $X := \ind (\tau, D)$. Let
+$G \leq \sym_{X}$, and let $\sortsym(D) := \prod_{s \in S} \sym_{D_{s}}$. We
+call the elements of $\sortsym(D)$ \emph{sorted permutations}. Note that
+$\sortsym(D)$ can be identified with a subgroup of $\sym_X$. There is an obvious
+action of $G$ on $X$. We can extend this to an action on the set of functions of
+the form $f: X \rightarrow X$, for any set $H$, defined by $\sigma \cdot f(x) =
+f(\sigma \cdot x)$ for all $x \in X$, $\sigma \in G$.
 
@@
 there exists $\sigma \in G$ such that $f = \sigma \cdot g$. We say $f$ and $g$
-are \emph{isomorphism-equivalent} if they are $\sortsym(D)$-equivalent.
-We are interested in the case where $H = \{0,1\}$, i.e.\ $f : X
-\rightarrow \{0,1\}$.
-In this case $f$ defines for each relation $R^D_i$ a subset of that relation, and thus determines a $\tau$-structure over the universe $D$.
-We note that two functions $f, g: X \rightarrow
-\{0,1\}$ are isomorphism-equivalent if, and only if, the two $\tau$-structures
-they determine are isomorphic.
+are \emph{isomorphism-equivalent} if they are $\sortsym(D)$-equivalent. We are
+interested in the case where $H = \{0,1\}$, i.e.\ $f : X \rightarrow \{0,1\}$.
+In this case $f$ defines for each relation $R^D_i$ a subset of that relation,
+and thus determines a $\tau$-structure over the universe $D$. We note that two
+functions $f, g: X \rightarrow \{0,1\}$ are isomorphism-equivalent if, and only
+if, the two $\tau$-structures they determine are isomorphic.
 
@@
 when there is no need to emphasise the particular vocabulary. We note that
-$\ind(F) = \ind(\tau, D)$, justifying our choice of notation.  We let
-\emph{the vocabulary of $F$} and \emph{the universe of $F$} denote
-$\tau$ and $D$ respectively.
+$\ind(F) = \ind(\tau, D)$, justifying our choice of notation. We let \emph{the
+  vocabulary of $F$} and \emph{the universe of $F$} denote $\tau$ and $D$
+respectively.
 
@@
 
-Structured functions give us a general framework for indexing the input sequence to a Boolean function and associating with that function an appropriate symmetry condition. Let $F$ be a
-$(\tau, D)$-structured function. We say $F$ is \emph{$G$-invariant} if it is
-constant on $G$-equivalent input vectors, i.e.\ for all $G$-equivalent $\vec{x},
-\vec{y} \in \{0,1\}^{X}$, $F(\vec{x}) = F(\vec{y})$. We say $F$ is
-\emph{isomorphism-invariant} if it is $\sortsym (D)$-invariant. Note that
-a structured function with vocabulary $\tau$ is isomorphism-invariant if, and
-only if, it decides a property of $\tau$-structures.
+Structured functions give us a general framework for indexing the input sequence
+to a Boolean function and associating with that function an appropriate symmetry
+condition. Let $F$ be a $(\tau, D)$-structured function. We say $F$ is
+\emph{$G$-invariant} if it is constant on $G$-equivalent input vectors, i.e.\
+for all $G$-equivalent $\vec{x}, \vec{y} \in \{0,1\}^{X}$, $F(\vec{x}) =
+F(\vec{y})$. We say $F$ is \emph{isomorphism-invariant} if it is $\sortsym
+(D)$-invariant. Note that a structured function with vocabulary $\tau$ is
+isomorphism-invariant if, and only if, it decides a property of
+$\tau$-structures.
 
@@
 From the above observations, we may think of symmetric functions as
-isomorphism-invariant structured functions over the single-sorted vocabulary with
-a single unary relation. We can similarly think of matrix-invariant functions as
-isomorphism-invariant structured functions over the appropriate vocabulary. More
-formally, if the vocabulary of $F$ consists of $p$ sort symbols $s_1, \ldots ,
-s_p$ and only one relation symbol with type $(s_1, \ldots, s_p)$ and $F$ is
-isomorphism-invariant, then we say $F$ is \emph{sort-invariant}. If $p = 2$ and
-$F$ is sort-invariant then we say that $F$ is \emph{matrix-invariant}.
+isomorphism-invariant structured functions over the single-sorted vocabulary
+with a single unary relation. We can similarly think of matrix-invariant
+functions as isomorphism-invariant structured functions over the appropriate
+vocabulary. More formally, if the vocabulary of $F$ consists of $p$ sort symbols
+$s_1, \ldots , s_p$ and only one relation symbol with type $(s_1, \ldots, s_p)$
+and $F$ is isomorphism-invariant, then we say $F$ is \emph{sort-invariant}. If
+$p = 2$ and $F$ is sort-invariant then we say that $F$ is
+\emph{matrix-invariant}.
 
@@
 without a loss of generality, we assume that the universe of any structured
-function is always a disjoint union of initial segments of the natural
-numbers, i.e.\ if $F$ is structured function with universe $D_{s_1} \uplus \ldots
-\uplus D_{s_p}$, then for all $s \in \{s_1 , \ldots , s_p\}$ there exists $d_s \in \mathbb{N}$ such
-that $D_{s} = [d_s]$. We also assume that every $(\tau, D)$-structured function has the property that every $a \in D$ appears in at least one element of $\ind(\tau, D)$.
+function is always a disjoint union of initial segments of the natural numbers,
+i.e.\ if $F$ is structured function with universe $D_{s_1} \uplus \ldots \uplus
+D_{s_p}$, then for all $s \in \{s_1 , \ldots , s_p\}$ there exists $d_s \in
+\mathbb{N}$ such that $D_{s} = [d_s]$. We also assume that every $(\tau,
+D)$-structured function has the property that every $a \in D$ appears in at
+least one element of $\ind(\tau, D)$.
 
@@
 vocabularies.
+
 \begin{definition}[Circuits on Structures]
@@
 Let $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
-\tau)$-circuit. The $n$ here denotes that $C_n$ accepts structures of size $n$.
-For a gate $g \in C_n$, we define the \emph{index} of $g$, denoted by $\ind(g)$,
-as $\ind(\Sigma(g))$ and we let $H_g$ denote the set of all gates in the image
-of $L(g)$. We also refer to the vocabulary and universe of $g$ to abbreviate
-referring to the vocabulary and universe of $\Sigma(g)$.
+\tau)$-circuit. The $n$ is used to indicates that $C_n$ accepts structures of
+size $n$. For a gate $g \in C_n$, we define the \emph{index} of $g$, denoted by
+$\ind(g)$, as $\ind(\Sigma(g))$. We define the relation $W \subseteq G^2$ by
+$W(h,g)$ if, and only if, $h \in \range(L(g))$. For each $g \in G$ we let
+$W(\cdot, g) := \{h \in G : W(h,g)\}$, and let $W(g, \cdot) := \{h \in G :
+W(g,h)\}$. We call $W(\cdot, g)$ the \emph{children} of $g$ and $W(g, \cdot)$
+the \emph{parents} of $g$. We also abbreviate $W(g, \cdot)$ by $H_g$. We let the
+vocabulary and universe of $g$ be the vocabulary and universe of $\Sigma(g)$,
+respectively.
 
@@
 
-Let $\tau$ be a relational vocabulary, % = (R_1, \ldots , R_t)$
-$\mathcal{A}$ a $\tau$-structure over an $n$-element universe $U$ and $\gamma
-\in [n]^{\underline{U}}$.
-% AD - need to define the notation [n]^{\underline{U}} in the background section
-% -- DONE
-
-Let $\gamma \mathcal{A}$ be the structure on universe $[n]$ formed by mapping
-$U$ in accordance with $\gamma$. The evaluation of a $(\mathbb{B},
-\tau)$-circuit $C_n$ computing a $q$-ary query $Q$ proceeds by recursively
-evaluating the gates in the circuit. The evaluation of the gate $g$ for the
-bijection $\gamma$ and input $\mathcal{A}$ is denoted by $C[\gamma
-\mathcal{A}](g)$, and is given as follows:
+Let $\tau$ be a relational vocabulary, $\mathcal{A}$ a $\tau$-structure over an
+$n$-element universe $U$ and $\gamma \in [n]^{\underline{U}}$. Let $\gamma
+\mathcal{A}$ be the structure on universe $[n]$ formed by mapping $U$ in
+accordance with $\gamma$. The evaluation of a $(\mathbb{B}, \tau)$-circuit $C_n$
+computing a $q$-ary query $Q$ proceeds by recursively evaluating the gates in
+the circuit. The evaluation of the gate $g$ for the bijection $\gamma$ and input
+$\mathcal{A}$ is denoted by $C[\gamma \mathcal{A}](g)$, and is given as follows
 \begin{enumerate}
@@
 We say that $C_n$ defines the $q$-ary query $Q \subseteq U^q$ under $\gamma$
-where $\vec{a} \in Q$ iff $C_n[\gamma \mathcal{A}](\Omega (\gamma \vec{a})) =
-1$.
+where $\vec{a} \in Q$ if, and only if, $C_n[\gamma \mathcal{A}](\Omega (\gamma
+\vec{a})) = 1$.
 
@@
   Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit. The function computed by $C_n$ is
-  $\tau$-invariant iff $C_n$ is an invariant circuit.
+  $\tau$-invariant if, and only if, $C_n$ is an invariant circuit.
 \end{lem}
-% AD - does this require a few lines of proof? To be added
+% AD - does this require a few lines of proof? GW - To be added. I have not done
+% this yet.
 
@@
 
+% It can be shown that $P$-uniform families of invariant circuits over the
+% standard basis can decide exactly those languages in $\PT$\cite{}. In this
+% paper, we are instead interested in circuits with broader symmetry properties.
+% We first define the notion of automorphism for circuits.
+
+We now define the notion of an automorphism of circuit.
+
 \begin{definition}[Automorphism]
@@
 
+We are particularly interested in circuits that have the property that every
+permutation in $\sym_n$ extends to an automorphism of the circuit.
+
 \begin{definition}[Symmetry]
@@
 It follows that for any symmetric circuit $C_n$ there is a homomorphism $h$ that
-maps $\sym_n$ to $\aut(C)$, taking any $\sigma \in \sym_n$ to an automorphism
-that extends it. Such a homomorphism is injective so long as some element of
-$[n]$ appears in a label of some input gate of $C$ (as then all elements appear
-by symmetry)~\cite{AndersonD17} and therefore no two distinct elements of
-$\sym_n$ agree on all input gates. In this paper we always assume that this is
-the case, as otherwise all inputs are constant, and so the circuit just computes
-a constant function. In order to develop a great many technical tools needed in
-this paper we should like to be able to, without a loss of generality, assume
-that that this homomorphism is in fact an isomorphism as well. In order to do so
-we make use of the rigidity condition.
+maps $\sym_n$ to $\aut(C_n)$, taking any $\sigma \in \sym_n$ to an automorphism
+that extends it. Suppose $C_n$ contains no relational gates of non-zero arity.
+In that case $C_n$ computes a constant function. As such, in this paper we
+always assume a circuit contains at least one relational gate with non-zero
+arity. There there exists a relational gate in $C_n$ with some element of $[n]$
+appearing in the tuple labelling that gate. By symmetry it follows that all
+elements of $[n]$ appear in tuples labelling relational gates in $C_n$. Thus no
+two distinct elements of $\sym_n$ agree on all input gates, and so the
+homomorphism $h$ is injective.
 
-We define rigidity in terms of an equivalence relation on the gates of a
-circuit. This recursively defined equivalence relation holds between two gates
-if the circuit underneath these two gates are in some sense the same. Before we
-define this relation we need to introduce some notation.
+If this homomorphism is also surjective then we have that each element of
+$\sigma$ extends uniquely to an automorphism of the circuit. Since many of the
+technical tools developed in this paper require that circuits have this
+property, we restrict our attention to classes of circuits that have
+\emph{unique extensions}.
+
+\begin{definition}
+  We say that a circuit $C_n$ has \emph{unique extensions} if for every $\sigma
+  \in \sym_n$ there is at most one $\pi_{\sigma} \in \aut(C_n)$ such that
+  $\pi_{\sigma}$ extends $\sigma$.
+\end{definition}
+
+Anderson and Dawar~\cite{AndersonD17} introduce the notion of a \emph{rigid}
+circuit, and show that, for circuits defined over a basis of symmetric functions
+there is a polynomial-time algorithm that takes as input a symmetric circuit and
+outputs an equivalent rigid symmetric circuit. They also show that rigid
+circuits have unique extensions, allowing them to conclude that $P$-uniform
+families of symmetric circuits over bases of symmetric functions may be assumed
+to be rigid (and hence have unique extensions) without a loss of generality.
+
+While we establish an approximately analogous argument, unfortunately, for the
+general $(\mathbb{B}, \tau)$-circuit, establishing an exactly analogous
+condition is a non-trivial problem. We discuss this problem in more detail in
+Section \label{sec:transparency-and-unique-extensions}.
+
+We now introduce the notion of a circuit with \emph{unique labels}, and show
+that if a circuit has unique labels then it has has unique extensions. Before we
+do so, we define the \emph{syntactic equivalence} relation on the gates of a
+circuit.
+
+% In order to prove this result, Anderson and Dawar introduce the notion of a
+% \emph{rigid} circuit, proving that symmetric circuits may be
+
+% However, it is not obvious that it is possible to generalise this result. We
+% show in Proposition \ref{}, that for the general $(\mathbb{B}, \tau)$-circuit,
+% the problem of deciding if a given circuit has unique extensions is at least
+% as hard as the graph isomorphism problem. As such, we instead define a the
+% notion of a circuit having \emph{unique labels} and show that if a circuit has
+% unique labels then we may assume it has unique extensions. We then explicitly
+% restrict ourselves to circuits with unique labels.
 
@@
 
-We have already required that for each gate $g$ in a circuit must have an
-injective labelling function. The following condition ensures that $L(g)/{\sim}$
-is also an injection.
+It is easy to show that determining if two gates in a given circuit compute the
+same function is $NP$-complete. The syntactic-equivalence relation defines a
+weaker relation between gates, instead identifying gates that have `hereditary
+similar' circuits defining them. It is easy to show that, for a circuit $C_n$,
+if $\sigma \in \sym_n$ and $\pi, \pi' \in \aut(C_n)$ extend $\sigma$, then for
+every gate $g$ in $C_n$, $\pi (g)$ and $\pi'(g)$ are syntactically equivalent.
+
+We now introduce the \emph{unique labels} condition.
 
 \begin{definition}
-  Let $C_n$ be a circuit and $g$ be a gate in $C_n$. We say $g$ has \emph{unique
-    labels} if $\vert H_g \vert = \vert H_g \setminus \equiv \vert $. We say
-  that the circuit $C_n$ has \emph{unique labels} if every gate in $C_n$ has
-  unique labels.
+  Let $C_n$ be a circuit and $g$ be a gate in $C_n$. We say $g$ has
+  \emph{injective labels} if $L(g)$ is an injection. We say $g$ has \emph{unique
+    labels} if $L(g)$ has injective labels and no two gates in $\range(L(g))$
+  are syntactically equivalent. We say $C_n$ has \emph{injective labels} (resp.
+  \emph{unique labels}) if every gate in $C_n$ has injective labels (resp.
+  unique labels). We say $C_n$ is \emph{transparent} if every non-symmetric gate
+  in $C_n$ has unique labels.
 \end{definition}
 
-We are also ready to define what it means for a circuit to be rigid.
+Let $C_n$ be a circuit and $W_t$ be the transitive closure of the $W$ relation
+on $C_n$. We note that a circuit $C_n$ may have an internal gate $g$ such that
+for every output gate $g'$, $\neg W_t(g, g')$ (i.e. there is no path from $g$ to
+any output gate). We call such a gate \emph{redundant}, as their inclusion in
+the circuit can not possibly have any bearing on the function computed by the
+circuit. It can be shown that given a circuit $C_n$ with redundant gates we may
+construct a new circuit $C_n'$ by simply removing the redundant gates. Moreover,
+this process preserves important circuit properties and can be done efficiently.
+We state and prove this formally in Lemma \ref{lem:redudant-gates}.
 
-\begin{definition}
-  We say that a circuit $C_n$ is \emph{rigid} if every equivalence class of
-  gates under the syntactic equivalence relation is a singleton.
-\end{definition}
+% \begin{definition}
+%   Let $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a circuit
+%   computing a $q$-ary query. We say a gate $g \in G$ is \emph{redundant} if
+%   there is no $\vec{a} \in [n]^q$ such that $W_t(g, \Omega (\vec{a}))$.
+% \end{definition}
 
-We prove in Proposition~\ref{} that there is a polynomial time algorithm that
-takes in a symmetric circuit with unique labels and outputs an equivalent rigid
-circuit. It is worth noting that the requirement that the circuit have unique
-labels is very important (see Section \ref{} for a detailed discussion of this
-point). Since we are interested in $P$-uniform families of circuits, this result
-allows us to assume the rigidity of a circuit without a loss of generality.
-Moreover, as we will show in Proposition \ref{}, if a circuit is rigid then
-every $\sigma \in \sym_n$ has exactly one an extension to an automorphism of
-$C_n$, and so the above defined homomorphism mapping $\sym_n$ to $\aut(C_n)$ is
-an isomorphism. Since we may assume rigidity without a loss of generality this
-property may also be assumed without a loss of generality. As such we abuse
-notation and let $\sigma \in \sym_n$ also denote the induced automorphism of the
-circuit.
+% We note that the definition of a circuit allows for the inclusion of gates
+% that are never used when evaluating the circuit. That is, for a circuit $C_n$
+% let $W_t$ be the transitive closure of $W$. It may be the case that there
+% exists a gate $h$ in $C_n$ such that there is no output gate $g$ with $W_t(h,
+% g)$.
+
+\begin{lem}
+  There exists an algorithm that takes as input a $(\mathbb{B}, \tau)$-circuit
+  $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ computing a $q$-ary
+  query and outputs a $(\mathbb{B}, \tau)$-circuit $C_n'$ such that (i) every
+  gate in $C_n$ is in $C_n'$, (ii) $C_n$ and $C_n'$ compute the same query,
+  (iii) no gate in $C_n'$ is redundant, (iv) if $C_n$ is symmetric then $C_n'$
+  is symmetric, (v) if $C_n$ has unique labels then $C_n'$ has unique labels,
+  and (vi) if $C_n$ is transparent then $C_n'$ is transparent. This algorithm
+  runs in time polynomial in the size of the input circuit.
+  \label{lem:redudant-gates}
+\end{lem}
+\begin{proof}
+  We construct the sub-circuit $C_n'$ of $C_n$ by removing all redundant gates
+  in $C_n$. Since $W_t$, the transitive closure of $W$, can be computed in time
+  polynomial in the size of the circuit, this construction can be completed in
+  time polynomial in the size of $C_n$.
+
+  Conditions (i), (ii), (iii), (v) and (vi) follow obviously for $C_n'$. Suppose
+  $C_n$ is symmetric and let $\sigma \in \sym_n$. Let $\pi$ be an automorphism
+  of $C_n$ extending $\sigma$. Let $g$ be a gate in $C_n'$. Then there exists
+  $\vec{a} \in [n]^q$ such that $W_t(g, \Omega(\vec{a}))$ in $C_n$. It can be
+  shown that $W_t (\pi(g), \Omega(\sigma(\vec{a})))$. Thus $\pi (g)$ is in
+  $C_n'$, and so restricting $\pi$ to the gates of $C_n'$ is an automorphism of
+  $C_n'$ extending $\sigma$. It follows that $C_n'$ is symmetric.
+\end{proof}
+
+Given Lemma \ref{lem:redudant-gates}, we may assume, without a loss of
+generality, that a circuit has no redundant gates. In this paper we make this
+assumption of every circuit unless stated otherwise.
+
+We now show that unique labels are sufficient for unique extensions.
+
+\begin{prop}
+  Let $C_n := \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a $\mathbb{B},
+  \tau)$-circuit. If $C_n$ has unique labels then $C_n$ has unique extensions.
+  \label{prop:unique-labels-unique-extensions}
+\end{prop}
+% \begin{prop}
+%   Let $C_n := \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be an injective
+%   $(\mathbb{B}, \tau)$-circuit. Then $C_n$ has unique labels if, and only if,
+%   $C_n$ has unique extensions.
+% \end{prop}
+\begin{proof}
+  Suppose $C_n$ has unique labels. Let $\pi_{\sigma}, \pi_{\sigma}' \in
+  \aut(C_n)$ be automorphisms extending $\sigma \in \sym_n$. We now prove that
+  $\pi_\sigma = \pi_{\sigma}'$. It is sufficient to show that $\pi :=
+  \pi_{\sigma}'\pi^{-1}_\sigma$ is the trivial automorphism on the circuit. It
+  is easy to see that $\pi$ extends the trivial permutation $e \in \sym_n$. Thus
+  $\pi$ acts trivially on input gates and output gates in the circuit, as $\pi$
+  acts as $e$ on relational gates and for any output gate $g$ there exists
+  $\vec{a} \in [n]^q$ such that $\pi (g) = \pi (\Omega(\vec{a})) = \Omega(e \dot
+  \vec{a}) = \Omega(\vec{a}) = g$.
+
+  It can be shown by induction that, since $\pi$ extends the trivial
+  permutation, for all gates $g \in G$, $\pi(g)$ is syntactically equivalent to
+  $g$. Let $W_t$ be the transitive closure of the relation $W$ on $C_n$. Let $g
+  \in G$ and suppose $\pi (g) = g$. Then $\pi H_{g} = H_g$ and, since $g$ has
+  unique labels, it follows that $\pi$ acts trivially on $H_g$ (i.e. for all $h
+  \in H_{g}$, $\pi(h) = h$). It follows by induction that for all $h \in G$ if
+  $W_t(h, g)$ then $\pi (h) = h$. Since the circuit contains no redundant gates,
+  it follows that $G = \bigcup_{\vec{a} \in [n]^q} \{g \in G : W_t (g,
+  \Omega(\vec{a}))\}$. Thus, since $\pi$ acts trivially on output gates, we have
+  that for all $g \in G$, $\pi (g) = g$. The result follows.
+
+  % Suppose $C_n$ does have not have unique labels. For every such gate $g \in
+  % G$ let $D(g)$ be the distance from $g$ to the set of output gates. From the
+  % hypothesis there exists $g \in G$ such that $h, h' \in H_g$ and $h \equiv
+  % h'$. Let $g$ the gate in the circuit without unique labels and with minimal
+  % $D(g)$. Then
+
+  % to the set of output gates Order the set of all such gates by their distance
+  % to the set of output gates, and let $g$ be the minimal gate in this set.
+
+  % such that it is of minimal distance to the set of output gates. Let $e \in
+  % \sym_n$ be the trivial permutation and $\pi \in \aut(C_n)$ be the unique
+  % extension of $e$. We have that $\pi (g) = g$, as if $\pi (g) \neq g$
+\end{proof}
+
+We also show that a transparent circuit can be converted into an equivalent
+circuit with unique labels in time polynomial in the size of the circuit. Since
+we are working with $P$-uniform families of transparent circuits, this fact
+allows us to assume, without a loss of generality, that transparent circuits
+have unique labels. We prove this formally in Proposition
+\ref{prop:transparent-unique}.
+
+% \begin{definition}
+%   We say that a circuit $C_n$ is \emph{rigid} if every equivalence class of
+%   gates under the syntactic equivalence relation is a singleton.
+% \end{definition}
+% \
+
+% We prove in Proposition~\ref{} that there is a polynomial time algorithm that
+% takes in a symmetric circuit with unique labels and outputs an equivalent
+% rigid circuit. It is worth noting that the requirement that the circuit have
+% unique labels is very important (see Section \ref{} for a detailed discussion
+% of this point). Since we are interested in $P$-uniform families of circuits,
+% this result allows us to assume the rigidity of a circuit without a loss of
+% generality. Moreover, as we will show in Proposition \ref{}, if a circuit is
+% rigid then every $\sigma \in \sym_n$ has exactly one an extension to an
+% automorphism of $C_n$, and so the above defined homomorphism mapping $\sym_n$
+% to $\aut(C_n)$ is an isomorphism. Since we may assume rigidity without a loss
+% of generality this property may also be assumed without a loss of generality.
+% As such we abuse notation and let $\sigma \in \sym_n$ also denote the induced
+% automorphism of the circuit.
 
@@
 
-Let $\MB$ be the set of all structured functions that are symmetric or
-matrix-invariant. Let $r, p \in \nats$, with $p$ prime, and let $D_1$ and $D_2$
-be initial segments of the natural numbers. Then there is a matrix-invariant
-structured function $F^{\rank}_{p,r}: \{0,1\}^{D_1 \times D_2}$, with universe
-$D_1 \uplus D_2$, such that $F^{\rank}_{p,r}(M) = 1$ if, and only if, the matrix
-$M \in \{0,1\}^{D_1 \times D_2}$ has rank at most $r$ when its entries are
-understood as elements of the finite field $\mathbb{F}_p$. Let
-$\mathbb{B}_\rank$ be the union of the set of all such functions with
-$\mathbb{B}_{\maj}$.
+% Let $\MB$ be the set of all structured functions that are symmetric or
+% matrix-invariant.
 
-\begin{definition}
-  Let $\mathbb{B} \subseteq \MB$. We call a symmetric $(\mathbb{B},
-  \tau)$-circuit with unique labels a \emph{symmetric matrix-circuit}.
-\end{definition}
+In many contexts, circuits are defined over a basis of symbols, usually the
+usual logical symbols $\land, \neg, \lor$ and perhaps $\maj$ (for majority).
+When evaluating a circuit, a gate labelled by a particular symbol is evaluated
+using a Boolean function appropriate to the particular symbol. We have instead
+defined a basis to be a set of Boolean functions. However, when reasoning about
+circuits or dealing with them as inputs to algorithms we often want to identify
+a function in the basis with a particular symbol. We now formally define a few
+natural bases used in this paper, assigning to each function in these bases an
+appropriate symbol.
 
-\begin{definition}
-  Let $\mathbb{B} \subseteq \MB$. We call a symmetric $(\mathbb{B}_\rank,
-  \tau)$-circuit with unique labels a \emph{symmetric rank-circuit}.
-\end{definition}
+Let $a \in \nats$, let $\land[a] : \{0,1\}^{[a]} \rightarrow \{0,1\}$ be the
+structured function computing the $\AND$ operation on $a$ inputs. Let $\lor[a] :
+\{0,1\}^{[a]} \rightarrow \{0,1\}$ be the structured function computing the
+$\OR$ operation on $a$ inputs. Let $\maj [a] : \{0,1\}^{[a]} \rightarrow
+\{0,1\}$ be the structured function computing the the majority function on $a$
+inputs. We abuse notation and let $\neg : \{0,1\} \rightarrow \{0,1\}$ also
+denote the structured function computing negation on a single input. In each
+case we use the name of the function above as a symbol denoting that function.
+
+Let the \emph{standard basis} $\BS$ be the basis containing $\neg$ and all
+functions $\land[a]$ and $\lor[a]$ for every $a \in \nats$. Let the
+\emph{majority basis }$\BM := \BS \cup \{\maj[a] : a \in \nats\}$. We say a
+basis $\BB$ is \emph{symmetric} if every function in $\mathbb{B}$ is a symmetric
+Boolean function.
+
+Let $a, b, r, p \in \nats$, with $p$ prime. Let $\rank^r_p[a,b] : \{0,1\}^{[a]
+  \times [b]} \rightarrow \{0,1\}$ be a matrix-invariant structured with
+universe $[a] \uplus [b]$, such that $\rank^r_p[a,b](M) = 1$ if, and only if,
+the matrix $M \in \{0,1\}^{[a] \times [b]}$ has rank at most $r$ when its
+entries are understood as elements of the finite field $\mathbb{F}_p$. We again
+identify the function $\rank^{r}_p[a,b]$ with the symbol $\rank^{r}_p[a,b]$.
+
+Let the \emph{\rank basis} $\RB := \BM \cup \{\rank^{r}_p[a,b] : a, b, r, p \in
+\nats, \text{ $p$ prime}\}$. We say a basis $\BB$ is \emph{matrix-symmetric} if
+every function in $\BB$ is symmetric or matrix-symmetric.
+
+% Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit and let $g$ be a gate in $C_n$. We
+% say $g$ is an \emph{\AND-gate} if $g$ is an internal gate labelled a function
+% of the . We say $g$ is a a \emph{majority gate}
+
+Let $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
+\tau)$-circuit and let $g \in G$. We say a gate $g \in G$ is a \emph{symmetric
+  gate} if $\Sigma(g)$ is a symmetric function. We say a gate $g \in G$ is a
+\emph{matrix-symmetric gate} if $\Sigma(g)$ is a matrix-symmetric structured
+function. We say that $g$ is an \emph{$\AND$ gate} if $\Sigma(g) := \land [a]$
+for some $a \in \nats$. Similarly we define \emph{$\OR$- gates}, \emph{$\NOT$
+  gates}, \emph{$MAJ$ gates} and \emph{$\rank$ gates}.
+
+We say $C_n$ is a \emph{circuit with symmetric gates} if every gate in $C_n$ is
+symmetric. We say $C_n$ is a \emph{matrix-circuit} if every gate in $C_n$ is
+matrix-symmetric or symmetric. We say $C_n$ is a \emph{rank-circuit} if $C_n$ is a
+matrix-circuit and every non-symmetric gate is a $\rank$ gate.
+
+% \begin{definition}
+%   Let $C_n = \langle G, \Omega, \Simga, \Lambda, L \rangle$ be a $(\mathbb{B},
+%   \tau)$-circuit. Let $g \in $ Let $\mathbb{B} \subseteq \MB$. We call a
+%   symmetric $(\mathbb{B}, \tau)$-circuit with unique labels a \emph{symmetric
+%   matrix-circuit}.
+% \end{definition}
+
+% \begin{definition}
+%   Let $\mathbb{B} \subseteq \MB$. We call a symmetric $(\mathbb{B}_\rank,
+%   \tau)$-circuit with unique labels a \emph{symmetric rank-circuit}.
+% \end{definition}
 
@@
 \begin{thm}[Main Theorem]
-  A graph property is decidable by a $P$-uniform family of symmetric
+  A graph property is decidable by a $P$-uniform family of transparent symmetric
   rank-circuits if, and only if, it is definable by an $\FPR$ sentence.
@@
 In this section we show that any family of symmetric circuits over an arbitrary
-basis of symmetric functions can be transformed in polynomial time into a family of
-symmetric circuits that decide the same language but are defined over the basis
-$\mathbb{B}_\maj$.  In other words, it makes no difference to the
-expressive power of such circuits whether we include \emph{all}
-symmetric functions in the basis or just $\mathbb{B}_\maj$.
-It follows that in order to construct $P$-uniform families of
-symmetric circuits that define queires not in $\FPC$, we need to
-consider bases with non-symmetric functions.
+basis of symmetric functions can be transformed in polynomial time into a family
+of symmetric circuits that decide the same language but are defined over the
+basis $\mathbb{B}_\maj$. In other words, it makes no difference to the
+expressive power of such circuits whether we include \emph{all} symmetric
+functions in the basis or just $\mathbb{B}_\maj$. It follows that in order to
+construct $P$-uniform families of symmetric circuits that define queires not in
+$\FPC$, we need to consider bases with non-symmetric functions.
 
@@
 that the output of $F$ is entirely determined by the number of $1$s in its
-input. Let $c_{F} \subseteq [n]$ be the set of all $m \leq n$ such that for
-all $\vec{x} \in \{ 0,1 \}^n$ with $m$ $1$s we have $F (\vec{x}) = 1$. Clearly
-any symmetric function $F$ is entirely determined by $c_{F}$. As such, $F$
-may be encoded by a tuple $f \in \{0,1\}^{n}$, where $f (i) = 1 $ iff $i
-\in c_{F}$. We assume this encoding below.
+input. Let $c_{F} \subseteq [n]$ be the set of all $m \leq n$ such that for all
+$\vec{x} \in \{ 0,1 \}^n$ with $m$ $1$s we have $F (\vec{x}) = 1$. Clearly any
+symmetric function $F$ is entirely determined by $c_{F}$. As such, $F$ may be
+encoded by a tuple $f \in \{0,1\}^{n}$, where $f (i) = 1 $ iff $i \in c_{F}$. We
+assume this encoding below.
 
@@
   There is a deterministic algorithm that outputs for each symmetric function
-  $F: \{0,1\}^n \rightarrow \{0,1\}$ (encoded as a binary $n$-tuple as above) a symmetric circuit $C$ defined over
-  the basis $\mathbb{B}_\maj$ that computes $F$. Moreover, this function is
-  computable in time polynomial in $n$ and the circuit $C$ has depth at most
-  $5$, width at most $2n+2$ and size at most $5n + 3$.
+  $F: \{0,1\}^n \rightarrow \{0,1\}$ (encoded as a binary $n$-tuple as above) a
+  symmetric circuit $C$ defined over the basis $\mathbb{B}_\maj$ that computes
+  $F$. Moreover, this function is computable in time polynomial in $n$ and the
+  circuit $C$ has depth at most $5$, width at most $2n+2$ and size at most $5n +
+  3$.
 \end{prop}
@@
 \begin{proof}
-  We have $c_{F}$ from the input. We now define $C$. We define the set of
-  gates and wires of $C$ layer by layer as follows. The first layer consists
-  of just the $n$ input gates labelled by the variables $x_1, \ldots , x_n$. The
-  second layer consists of two `majority' gates for each $a \in c_{F}$, which
-  we denote by $\maj_a$ and $\maj^{\neg}_a$. For each $a \in c_{F}$ there is
-  one wire from each of $x_1, \ldots , x_n$ to $\maj_a$ and $\maj^{\neg}_a$. For
-  all $a \geq \frac{n}{2}$, there are $2a - n$ wires from $0$ to $\maj_a$ and
-  $2a - n + 2$ wires from $0$ to $\maj^{\neg}_a$. For all $a < \frac{n}{2}$
-  there are $n - 2a$ wires from $1$ to $\maj_a$ and $n - 2a - 2$ wires from $1$
-  to $maj^{\neg}_a$. The third layer consists of one `not' gate for each $a \in
-  c_{F}$, which we denote by $\neg_a$. For each $a \in c_{F}$ there is a
-  wire from $\maj^\neg_a$ to $\neg_a$. The fourth layer consists of one `and'
-  gate for each $a \in c_{F}$, which we denote by $\countgate_a$. For each $a
-  \in c_{F}$ there is a wire from each of $\maj_a$ and $\neg_a$ to
-  $\countgate_a$. The fifth layer consists of just a single `or' gate,
-  designated as the output gate, and for each $a \in c_{F}$ there is a wire
-  from $\countgate_a$ to the output gate.
+  We have $c_{F}$ from the input. We now define $C$. We define the set of gates
+  and wires of $C$ layer by layer as follows. The first layer consists of just
+  the $n$ input gates labelled by the variables $x_1, \ldots , x_n$. The second
+  layer consists of two `majority' gates for each $a \in c_{F}$, which we denote
+  by $\maj_a$ and $\maj^{\neg}_a$. For each $a \in c_{F}$ there is one wire from
+  each of $x_1, \ldots , x_n$ to $\maj_a$ and $\maj^{\neg}_a$. For all $a \geq
+  \frac{n}{2}$, there are $2a - n$ wires from $0$ to $\maj_a$ and $2a - n + 2$
+  wires from $0$ to $\maj^{\neg}_a$. For all $a < \frac{n}{2}$ there are $n -
+  2a$ wires from $1$ to $\maj_a$ and $n - 2a - 2$ wires from $1$ to
+  $maj^{\neg}_a$. The third layer consists of one `not' gate for each $a \in
+  c_{F}$, which we denote by $\neg_a$. For each $a \in c_{F}$ there is a wire
+  from $\maj^\neg_a$ to $\neg_a$. The fourth layer consists of one `and' gate
+  for each $a \in c_{F}$, which we denote by $\countgate_a$. For each $a \in
+  c_{F}$ there is a wire from each of $\maj_a$ and $\neg_a$ to $\countgate_a$.
+  The fifth layer consists of just a single `or' gate, designated as the output
+  gate, and for each $a \in c_{F}$ there is a wire from $\countgate_a$ to the
+  output gate.
 
@@
   runs in time polynomial in $n$.
-%AD - perhaps include a brief argument for why C is symmetric?
+  % AD - perhaps include a brief argument for why C is symmetric?
 
@@
   layer contains at most $2 \vert c_{F} \vert \leq 2n$ gates. The third and
-  fourth layer each contain at most $n$ gates. As such $C$ has size at most $n
-  + 2n + 2n + 1 + 2 = 5n +3$ (the additional 2 is for the constant gates). The
+  fourth layer each contain at most $n$ gates. As such $C$ has size at most $n +
+  2n + 2n + 1 + 2 = 5n +3$ (the additional 2 is for the constant gates). The
   width of $C$ is at most $2n + 2$, and the depth is at most $5$.
@@
   Let $\mathbb{B}$ be a basis of symmetric functions and let $(C_n)_{n \in
-    \mathbb{N}}$ be a family of symmetric circuits defined over the basis $\mathbb{B}$. Then there exists a family
-  of symmetric circuits $(C_n')_{n \in \mathbb{N}}$ defined over
-  $\mathbb{B}_\maj$ that decides the same language. Moreover, the map $C_n
-  \mapsto C_n'$ is polynomial-time computable and for each $n \in \nats$, $\vert
-  C_n' \vert \leq (5 \cdot \vert C_n \vert + 3) \cdot \vert C_n \vert$.
+    \mathbb{N}}$ be a family of symmetric circuits defined over the basis
+  $\mathbb{B}$. Then there exists a family of symmetric circuits $(C_n')_{n \in
+    \mathbb{N}}$ defined over $\mathbb{B}_\maj$ that decides the same language.
+  Moreover, the map $C_n \mapsto C_n'$ is polynomial-time computable and for
+  each $n \in \nats$, $\vert C_n' \vert \leq (5 \cdot \vert C_n \vert + 3) \cdot
+  \vert C_n \vert$.
 \end{thm}
@@
 \begin{proof}
-  From $C_n$ we construct $C_n'$ as follows. For each gate $g \in C_n$ 
-  labelled by a member of $\mathbb{B}$ we have a symmetric circuit $C_g$ from
+  From $C_n$ we construct $C_n'$ as follows. For each gate $g \in C_n$ labelled
+  by a member of $\mathbb{B}$ we have a symmetric circuit $C_g$ from
   Proposition~\ref{prop:function-maj} that computes the same function as $g$.
@@
 This result gives us that for any family of circuits over an arbitrary basis of
-symmetric functions we can construct another symmetric circuit family
-computing the same function over the majority basis without a blowup in size.
-Moreover, we also have that if the first family was uniform the second family
-will be as well. As such, we cannot extend the power of the $P$-uniform
-symmetric circuits families studied by Anderson and Dawar \cite{AndersonD17} by
-simply considering alternative bases of symmetric functions, thus motivating the
-generalisation developed in the previous subsection to non-symmetric functions.
+symmetric functions we can construct another symmetric circuit family computing
+the same function over the majority basis without a blowup in size. Moreover, we
+also have that if the first family was uniform the second family will be as
+well. As such, we cannot extend the power of the $P$-uniform symmetric circuits
+families studied by Anderson and Dawar \cite{AndersonD17} by simply considering
+alternative bases of symmetric functions, thus motivating the generalisation
+developed in the previous subsection to non-symmetric functions.
 \end{document}

### 2017-11-28 sections/translating-formulas-to-cicuits.tex
28 Nov 2017

@@
 
-\subsection{Circuit Manipulation}
-In this section and the next we develop a number of results that reference
-$P$-uniform families of circuits. In order to prove these results we often need
-to define polynomial-time algorithms for generating or manipulating circuits. In
-this subsection we define a number of algorithms that perform commonly invoked
-operations on circuits.
-
-We often include quotes around the names of these algorithm in order to avoid
-any confusion. We assume a reasonable encoding of the circuit.
+\subsection{Algorithms for Circuits}
+In order to translate between $P$-uniform families of circuits and formulas of
+$\FPR$ we will require that certain important circuit transformations can be
+completed in polynomial time. In this subsection we define a number of
+operations that perform commonly invoked operations on circuits, and which can
+easily be shown to be implementable as algorithms that run in polynomial time.
+In each case we assume a reasonable encoding of the circuit.
 
@@
   \Omega, \Sigma , \Lambda, L \rangle$ and a set of syntactically equivalent
-  gates $H = \{h_1, \ldots , h_p\}$ and outputs the circuit $C' = \langle G',
+  gates $H := \{h_1, \ldots , h_p\}$ and outputs the circuit $C' = \langle G',
   \Omega', \Sigma', \Lambda', L' \rangle$, where
@@
 output circuits compute the same function. Moreover, if the input circuit is
-symmetric (resp. has unique labels) then the output circuit will also be
-symmetric (resp. have unique labels).
+symmetric (resp. has unique labels, is transparent) then the output circuit will
+also be symmetric (resp. have unique labels, is transparent).
 
@@
   The operation $\op{merge-all}(C, H)$ takes as input an ordered circuit $C$ and
-  a set of gates $H$ with unique labels and outputs another circuit $C'$. Let
-  $H_1, \ldots, H_p$ be the equivalence classes of $H$ linearly ordered using
-  the order on the circuit but such that for all $i, j \in [p]$ if $i \leq j$
-  then the height of the gates in $H_i$ is less than or equal to the height of
-  the gates in $H_j$. Let $C'$ be the result of successively executing
-  $\op{merge}$ on each partition.
+  a set of gates $H$ and outputs another circuit $C'$. Let $H_1, \ldots, H_p$ be
+  the syntactic equivalence classes of $H$ linearly ordered using the order on
+  the circuit but such that for all $i, j \in [p]$ if $i \leq j$ then the height
+  of the gates in $H_i$ is less than or equal to the height of the gates in
+  $H_j$. Let $C'$ be the result of successively executing $\op{merge}$ on each
+  equivalence class.
 \end{definition}
 
-For an input tuple $(C, H)$ it follows from Lemma \cite{} that the syntactic
-equivalence relation on $H$ can be computed in time polynomial in the size of
-$C$. Thus it can be shown that the operation $\op{merge-all}$ can be computed in
+For an input tuple $(C, H)$ if $H$ is a set of gates with unique labels it
+follows from Lemma \cite{} that the syntactic equivalence relation on $H$ can be
+computed in time polynomial in the size of $C$. Thus, if the set $H$ has unique
+labels it can be shown that the operation $\op{merge-all}$ can be computed in
 time polynomial in the size of the input circuit. As in the case of
@@
 $C$ is an ordered circuit and $H$ is a set of gates with unique labels, then if
-$g$ is a gate in both $C$ and $C' := \op{merge-all}(C, H)$, then if all of the input
-gates of $g$ in $C$ are in $H$ then no two distinct input gates of $g$ in $C'$
-are syntactically equivalent (but $g$ does not have unique labels in $C'$ as
-$L'(g)$ may not be injective).
+$g$ is a gate in both $C$ and $C' := \op{merge-all}(C, H)$, then if all of the
+input gates of $g$ in $C$ are in $H$ then no two distinct input gates of $g$ in
+$C'$ are syntactically equivalent (but $g$ does not have unique labels in $C'$
+as $L'(g)$ may not be injective).
 
@@
   \item $\Omega'$ is an function from the domain of $\Omega$ to $G'$ such that
-    for each $\vec{a} \in \dom(Omega)$ if $\Omega(\vec{a}) = g_1$ then
+    for each $\vec{a} \in \dom(\Omega)$ if $\Omega(\vec{a}) = g_1$ then
     $\Omega'(\vec{a}) = g_2$ and if then $\Omega'(\vec{a}) = \Omega(\vec{a})$.
@@
   $L'(h)(\vec{b}) = L(h)(\vec{b})$.
-
 \end{definition}
@@
   query of arity $\arty(R_i)$, and $R$ is a relation symbol in $(\tau \setminus
-  \tau_R) \cup (\bigcup_{1 \leq i \leq t}\tau_i))$. The operation outputs a
+  \tau_R) \cup (\bigcup_{1 \leq i \leq t},\tau_i))$. The operation outputs a
   circuit $C' = \langle G', \Omega', \Sigma', \Lambda', L' \rangle$ defined from
@@
 It can be shown that $\op(concatenate)$ can be computed in time polynomial in
-the combined size of the input circuits. Moreover, if the input circuits are all
-symmetric (resp. have unique labels) then the output circuit will be symmetric
-(resp. have unique labels). We sometimes refer to $\op(concatenate)$ $(C^1,
-\ldots, C^t)$ into $C^0$ along $(R_1 , \ldots , R_t)$ when invoking
-`glue-circuit' on the input $(C^0, \ldots , C^t)$ and $\tau_R = \{R_1, \ldots ,
-R_t\}$.
-
-\subsection{Unique Labels and Rigidity}
-In contrast with the work of Anderson and Dawar~\cite{}, the circuit families we
-use to establish our main result are additionally required to have unique
-labels. In this subsection we briefly discuss this inclusion, and present
-results suggesting its importance.
-
-It is important to note that our analysis of circuits depends crucially on the
-fact that a circuit may be transformed (in polynomial time) into an equivalent
-circuit with the property that each element of $\sym_n$ induces a unique
-automorphism on the circuit $C_n$. This fact ensures a canonical action of
-$\sym_n$ on the circuit $C_n$ and is a crucial requirement for defining needed
-theoretical tools, such as supports, and computing various facts about the
-circuit in polynomial time, such as the coarsest supporting partition or the
-orbit of a gate.
-
-Anderson and Dawar~\cite{AndersonD17} define a condition analogous to the one
-define above and prove that it's a sufficient condition for establishing the
-uniqueness of the induced automorphism on the circuit and that a circuit can be
-transformed into an equivalent rigid circuit in polynomial time.
-
-Although the rigidity condition we present in this paper is similarly defined,
-the existence of a polynomial-time computable transformation of a circuit into
-an equivalent rigid circuit is not as straight forward. Indeed, it is possible
-to show that the problem of determining if a given $(\mathbb{B}, \tau)$-circuit
-is rigid is as least as hard as the graph isomorphism problem. This is a direct
-consequence of the following result.
+the sum of the sizes of the input circuits. Moreover, if the input circuits are
+all symmetric then the output circuit will be symmetric. Furthermore, if the
+input sequences of circuits and relations have just a single element, then if
+the input circuits have unique labels then the output circuit will have unique
+labels.
+
+\subsection{Transparency and Unique Extensions}
+\label{sec:transparency-and-unique-extensions}
+% In contrast with the work of Anderson and Dawar~\cite{AndersonD17}, the
+% circuit families we use to establish the main result of this paper are
+% additionally required to be transparent. In this subsection we briefly discuss
+% this condition, and present results suggesting its necessity.
+
+As mentioned earlier, the unique extensions condition plays a crucial role in
+the definition of needed theoretical tools, such as supports, and for proving
+the existence of polynomial-time algorithms computing important functions, such
+as the coarsest supporting partition or the orbit of a gate (see Proposition
+\ref{lem:computing support}).
+
+In this subsection we show that if a circuit is transparent then it may be
+transformed in polynomial time into an equivalent circuit with unique labels.
+Since we already have that circuits with unique labels have unique extensions
+(see Proposition \ref{prop:unique-labels-unique-extensions}), it follows that we
+may assume, without a loss of generality, that $P$-uniform families of
+transparent circuits have unique labels, and hence unique extensions. We also
+discuss relevant special cases and the motivate the explicit requirement that
+the $P$-uniform families of circuit referenced in the main result of this paper
+consist of transparent circuits.
+
+% Anderson and Dawar~\cite{AndersonD17} introduce the notion of a `rigid'
+% circuit, a condition analogous to the rigidity condition defined in this
+% paper. The following
+
+% \begin{definition}
+%   We say a circuit $C_n$ is que labels it has unique extensions. We finally
+%   discuss th\emph{rigid} if it has injective labels and for every pair of
+%   gates $(g, g')$ in $C_n$ such that $H_g = H_{g'}$ and $g \equiv g'$.
+% \end{definition}
+
+We first show that the syntactic equivalence relation can be efficiently
+computed for transparent circuits.
+
+\begin{remark}
+  I have introduced the notion of a syntactically transparent class. The reason
+  I did this seems to have dissipated, I will probably remove this definition
+  and simply the statement of the below proposition.
+\end{remark}
+
+\begin{definition}
+  We say a class of circuits $\mathcal{C}$ is \emph{syntactically transparent}
+  if there is an algorithm that takes in a circuit $C \in \mathcal{C}$ and
+  outputs the syntactic equivalence relation on the gates of $C$ and runs in
+  time polynomial in the size of the input circuit.
+\end{definition}
 
 \begin{prop}
-  There is a a polynomial time reduction from the graph isomorphism problem to
-  the problem of deciding if a specified gate in a matrix-circuit is syntacticly
-  equivalent to any other gate in the circuit.
-  \label{prop:syntactic-graph-iso}
-\end{prop}
-\begin{proof}
-\end{proof}
-
-Another obvious consequence of this result is that if the syntactic equivalence
-relation for an input $(\mathbb{B}, \tau)$-circuit can be computed in polynomial
-time then the graph isomorphism problem is in $\PT$. It is worth noting that if
-we restrict the input to a class of circuits defined over symmetric bases then
-we can decide the syntactic equivalence relation in polynomial time.
-
-\begin{prop}
-  Let $C_n$ be a circuit with symmetric gates. There is an algorithm that takes
-  in such a circuit, runs in time polynomial in the size of the circuit, and
-  outputs the syntactic equivalence relation on the gates of $C_n$.
-  \label{prop:symmetric-syntactic}
-\end{prop}
-\begin{proof}
-\end{proof}
-
-Moreover, it turns out that being able to compute the syntactic equivalence
-relation in polynomial time for some class of circuits $\mathcal{C}$ implies
-that the existence of a polynomial-time algorithm for converting circuits in $C$
-into equivalent rigid circuit.
-
-\begin{prop}
-  Let $\mathcal{C}$ be a set of circuits. Suppose the syntactic equivalence
-  relation can be computed in polynomial time for circuits in $\mathcal{C}$. It
-  follows that there is an algorithm that runs in polynomial time that takes in
-  a circuit $C \in \mathcal{C}$ and outputs a rigid circuit $C'$ such that if
-  $C$ is symmetric then $C'$ is symmetric.
-  \label{prop:syntactic-equivilence-rigid}
-\end{prop}
-\begin{proof}
-\end{proof}
-
-The following result gives us that the unique labels condition is sufficient.
-
-\begin{prop}
-  Let $C_n := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
-  \tau)$-circuit with unique labels. There is a deterministic algorithm that
-  takes in such a circuit and outputs the syntactic equivalence relation on $G$.
-  Moreover, this algorithm runs in time polynomial in the size of the circuit.
+  Any class of transparent circuits is syntactically transparent.
+  % Let $C_n := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a
+  % $(\mathbb{B},
+  % \tau)$-circuit with unique labels. There is a deterministic algorithm that
+  % takes in such a circuit and outputs the syntactic equivalence relation on
+  % $G$.
+  % Moreover, this algorithm runs in time polynomial in the size of the circuit.
   \label{prop:unique-labels-syntactic-equiv}
 \end{prop}
-\begin{proof}
-  We proceed to define a relation $\sim$ by induction on height (i.e. distance
-  from an input gate). This relation will be the syntactic equivalence relation
-  on $G$. It is easy to check the conditions for syntactic equivalence for gates
-  of height 0 as all such gates are input gates and so are either constant gates
-  or relational gates. Suppose $g$ and $h$ are gates of height greater than
-  zero. We only need to check conditions (i), (iv) and (v) of syntactic
-  equivalence. It is easy to check (i) and (v). If either condition is false
-  then $g$ and $h$ are not syntacticly equivalent. So suppose $g$ and $h$ are
-  two internal gates such that $\Sigma (g) = \Sigma(h)$ and if they are both
-  output gates then $\Omega^{-1}(g) = \Omega^{-1}(h)$. It remains to check if
-  $L(g)/{\sim}$ and $L(h)/{\sim}$ are isomorphism equivalent. First check if
-  $H_h /{\sim} = H_g /{\sim}$. If not, $g$ and $h$ are not syntactically
-  equivalent. So suppose $H_h /{\sim} = H_g /{\sim}$. We know that $C_n$ has
-  unique labels, and so $L(g)/{\sim}$ and $L(h)/{\sim}$ are injections so are
-  isomorphism equivalent if, and only if, $L(g)^{-1}L(h)$ acts like an
-  isomorphism. This can be checked by first checking that the function induces a
-  sorted permutation on the universe of $g$ (which can be done by iterating over
-  the index of $g$). This is sufficient as $L(g)(L(g)^{-1}L(h)) = L(h)$.
+\begin{proof} Let $C_n := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a
+  transparent $(\mathbb{B}, \tau)$-circuit. We define a relation $\sim$ by
+  induction on height (i.e. distance from an input gate). This relation will be
+  the syntactic equivalence relation on $G$. It is easy to check the conditions
+  for syntactic equivalence for gates of height 0 as all such gates are input
+  gates and so are either constant gates or relational gates. Suppose $g$ and
+  $h$ are gates of height greater than zero. We only need to check conditions
+  (i), (iv) and (v) of syntactic equivalence. It is easy to check (i) and (v).
+  If either condition is false then $g$ and $h$ are not syntacticly equivalent.
+  So suppose $g$ and $h$ are two internal gates such that $\Sigma (g) =
+  \Sigma(h)$ and suppose that if they are both output gates then $\Omega^{-1}(g)
+  = \Omega^{-1}(h)$. It remains to check if $L(g)/{\sim}$ and $L(h)/{\sim}$ are
+  isomorphism equivalent. First check if $H_h /{\sim} = H_g /{\sim}$. If not,
+  $g$ and $h$ are not syntactically equivalent. So suppose $H_h /{\sim} = H_g
+  /{\sim}$. If $g$ and $h$ are symmetric gates then $H_h /{\sim} = H_g/{\sim}$
+  if, and only if, $L(g)/{\sim}$ and $L(h)/{\sim}$ are isomorphism equivalent,
+  so let $g \sim h$. If $g$ and $h$ are not symmetric gates then, since $C_n$ is
+  transparent, $g$ and $h$ have unique labels. We thus have that $L(g)/{\sim}$
+  and $L(h)/{\sim}$ are isomorphism equivalent if, and only if, $L(g)^{-1}L(h)$
+  acts like an isomorphism. This can be checked by first checking that the
+  function induces a sorted permutation on the universe of $g$ (which can be
+  checked efficiently). This is sufficient as $L(g)(L(g)^{-1}L(h)) = L(h)$.
 
@@
 
+\begin{prop}
+  Let $C_n \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a transparent
+  $(\mathbb{B}, \tau)$-circuit. There is an algorithm that that takes in such a
+  circuit and outputs a $(\mathbb{B} \cup \mathbb{B}_{\std}, \tau)$-circuit $C'$
+  such that $C$ and $C'$ compute the same function, $C'$ has unique labels, and
+  if $C$ is symmetric then $C'$ is symmetric. Moreover, this algorithm runs in
+  time polynomial in the size of the input circuit.
+  \label{prop:transparent-unique}
+\end{prop}
+\begin{proof}
+  Let $C' := \op{make-injective-all}(\op{merge-all} (C, G))$. We have that $C'$
+  is symmetric if $C$ is symmetric. Since the syntactic equivalence relation can
+  be computed in polynomial time for circuits in $\mathcal{C}$ it follows that
+  this operation can be implemented so as to run in time polynomial in the size
+  of $C$. Clearly every gate $g$ in $C'$ belongs to a singleton syntactic
+  equivalence class.
+\end{proof}
+
+Anderson and Dawar~\cite{AndersonD17}, in their study of circuits with symmetric
+gates, show that such circuits may be transformed in polynomial time into
+equivalent circuits with unique extensions. They do this by showing that a
+circuit with symmetric gates may be transformed into an equivalent \emph{rigid}
+circuit in polynomial time and that all rigid circuits have unique extensions.
+We have similarly shown that transparent circuits can be translated into
+equivalent circuits with unique labels in polynomial time and that circuits with
+unique labels have unique extensions. Since all circuits with symmetric gates
+are transparent, this is a generalisation of their result.
+
+It is natural to ask if the requirement in the main theorem of this paper that
+the circuits be transparent is strictly necessary. It may be that, just as for
+the case of circuits with symmetric gates, a circuit (not necessarily
+transparent) can be transformed in polynomial time into an equivalent
+transparent circuit. While we do not address this question exactly, we do show
+that the problem of computing the syntactic equivalence relation for a circuit
+is at least as hard as the graph isomorphism problem. We also show that that the
+related problems of checking if given gate in a circuit has unique labels or has
+unique extensions (in a sense we define below) are all also at least as hard as
+the graph isomorphism problem. We move on to show that computing other basic
+facts about the circuit, such as the orbit of a gate, is also at least as hard
+as the graph isomorphism problem.
+
+% ,; address two related decision problems in Proposition \ref{} and Corollaries
+% \ref{} and \ref{}. In partic
+
+% As we will show in Proposition \ref{}, formulas of $\FPR$ can be translated
+% into. For this transparent circuits. However, the transformation is
+% complicated by the requirement that the resultant circuit be transparent.
+% However, it is worth asking if the transparency condition is required, i.e. if
+% it can be shown that
+
+% \emph{rigid} circuit. They show that all circuits such circuits can be
+% transformed into equivalent rigid circuits . They show that if a circuit is
+% rigid then it has unique extensions and that every circuit with injective
+% labels and symmetric gates can be transformed into an equivalent rigid circuit
+% in polynomial time. We have similarly shown that a transparent circuit can be
+% transformed into an equivalent one with unique labels in polynomial time, and
+% that circuits with unique labels have unique extensions. Moreover, since all
+% circuits with symmetric gates and injective labels are transparent, this is a
+% strict generalisation of their result.
+
+% and they show that a symmetric gate
+
+% Using the language developed in this paper, a circuit $C_n$ is \emph{rigid} if
+% it has injective labels and there are no two gates $g$ and $h$ in $C_n$ such
+% that $g$ and $h$ are syntactically equivalent. Since their discussion is
+% limited to circuits with symmetric gates and injective labels this is equ
+
+% circuit, a condition analogous to the rigidity condition defined in this
+% paper. The following
+
+% It is worth noting that all symmetric circuits are transparent, and
+
+% prove that it's a sufficient condition for establishing the uniqueness of the
+% induced automorphism on the circuit. Moreover, they prove that any circuit
+% (noting that they limit themselves to a discussion of circuits over a
+% symmetric basis) may be transformed into an equivalent rigid circuit in
+% polynomial time. As such, they may assume $P$-uniform symmetric circuit
+% families are rigid without a loss of generality, and hence be may assume
+% without a loss of generality that each permutation in $\sym_n$ uniquely
+% extends to an automorphism of the circuit.
+
+% However, in this subsection we show that deciding the rigidity of circuits
+% over bases which may include non-symmetric functions is at least as hard as
+% the graph isomorphism problem. However, we shoudl that on classes
+
+% Although the rigidity condition we present in this paper is similarly defined,
+% the existence of a polynomial-time computable transformation of a circuit into
+% an equivalent rigid circuit is not as straight forward. Indeed, it is possible
+% to show that the problem of determining if a given $(\mathbb{B},
+% \tau)$-circuit is rigid is as least as hard as the graph isomorphism problem.
+% This is a direct consequence of the following result.
+
+% \begin{definition}
+%   The \emph{syntactic equivalence class problem} is the decision problem for
+%   the set of all triples $(C, g_1, g_2)$, where $C$ is a $(\mathbb{B},
+%   \tau)$-circuit, and $g_1$ and $g_2$ are two syntactically equivalent gates
+%   in $C$.
+% \end{definition}
+
+% \begin{definition}
+%   The \emph{rigidity problem} is the decision problem for the set of all
+%   circuits $C$ where $C$ is a rigid circuit.
+% \end{definition}
+
+% \begin{definition}
+%   The \emph{unique labels problem} is the decision problem for the set of all
+%   circuits $C$ where $C$ has unique labels.
+% \end{definition}
+
 % \begin{prop}
-%   There is an algorithm that takes in a $(\mathbb{B}, \tau)$-circuit $C$ with
-%   unique labels and outputs the syntactic equivalence relation on its gates.
-%   This algorithm runs in time polynomial in the size of $C$.
+%   Let $\tau$ be any non-empty relational vocabulary and let $n, r, p \in
+%   \nats$ with $p$ prime. There is a a polynomial time reduction from the graph
+%   isomorphism problem to the problem of deciding if a given pair of gates in a
+%   given symmetric rank-circuit for structures of size $n$ that (i) has
+%   injective labels, (ii) contains no constant gates, and (iii) contains at
+%   most two rank gates with bound $r$ and prime $p$, are syntactically
+%   equivalent.
+%   \label{prop:syntactic-graph-iso}
+% \end{prop}
+% \begin{proof}
+%   We have from \cite{} that there is a polynomial time reduction from the
+%   graph isomorphism problem to the bipartite isomorphism problem. The
+%   bipartite isomorphism problem is the decision problem for the set of all
+%   pairs of partitioned bipartite graphs $B_1 := (U_1, V_1, E_1)$ and $B_2 :=
+%   (U_2, V_2, E_2)$ such that there exists a graph isomorphism $\pi : B_1
+%   \rightarrow B_2$ with $\restr{\pi}{U_1} = U_2$ and $\restr{\pi}{V_1} = V_2$.
+
+%   Suppose we are given two partitioned bipartite graphs $B_1 := (U_1, V_1,
+%   E_1)$ and $B_2 := (U_2, V_2, E_2)$. We assume, without a loss of generality,
+%   that there exists $a, b \in \nats$ such that $U_1 = U_2 = [a]$ and $V_1 =
+%   V_2 = [b]$.
+
+%   Let $R$ be a relation symbol in $\tau$ and let $k := \arty{R}$. Let $G_{R}
+%   := \{g_{R, \vec{c}} : \vec{c} \in [n]^k\}$, $G_{\text{mid}} := \{\land_0,
+%   \land_1, \neg_0, \land_{\text{out}} \}$, $G_{\rank} : = \{ g_{\rank, 1},
+%   g_{\rank, 2}\}$, and $G_{\land} := \{g_{i, (u,v)} : i \in [2] \, (u,v) \in
+%   E_i \}$. Let $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a
+%   $(\{\rank^{1}_2\}, \tau)$-circuit defined as follows. Let $G = G_R \cup
+%   G_{\text{mid}} \cup G_{\rank} \cup G_{\land}$ and $\Omega$ be the $0$-ary
+%   function $\land_{\text{out}}$. For each $\vec{c} \in [n]^{\arty{R}}$ let
+%   $\Lambda(\vec{c}) = g_{R, \vec{c}}$. Define $\Sigma$ as follows. For each $g
+%   \in G$,
+%   \begin{itemize}
+%     \setlength\itemsep{0mm}
+%   \item if $g \in G_R$ then $\Sigma(g) = R$,
+%   \item if $g$ equals $\land_0$ or $\land_1$ then $\Sigma(g) = \land[n^k]$
+%   \item if $g$ equals $\land_{\text{out}}$ then $\Sigma(g) = \land[2]$,
+%   \item if $g \in G_\rank$ let $\Sigma(g) = \rank^r_p [a,b]$, and
+%   \item if $g \in G_{\text{in}}$ and $g$ then $\Sigma(g) = \land[1]$.
+%   \end{itemize}
+%   Define $L$ as follows. For each $g \in G$,
+%   \begin{itemize}
+%     \setlength\itemsep{0mm}
+%   \item if $g \in G$ and $g = g_{\text{out}}$ then for each $i \in [2]$,
+%     $L(g)(i) := g_{\rank, i}$,
+%   \item if $g \in G_\rank$ and $g = g_{\rank, i}$ then $L(g)(p,q) = g_{i,
+%     (p,q)}$,
+%   \item if $g \in G_{\land}$ and $g = g_{i, (p,q)}$ then $L(g)(1) = \land_1$
+%     if $(p,q) \in E_i$ and $L(g)(1) = \neg_0$ otherwise,
+%   \item if $g = \neg_0$ then $L(g)(1) = \land_0$, and
+%   \item if $g = \land_0$ or $g = \land_1$ then for all $p \in [n^k]$ we have
+%     that $L(g)(p)$ equals $\Lambda^{-1}(\vec{c}_p)$, where $\vec{c}_p$ is the
+%     $p$th element of $[n]^k$ in the lexicographical ordering on $[n]^k$.
+%   \end{itemize}
+
+%   We note that for $i \in [2]$, $L(g_{\rank, i})(p,q) = \land_1$ if $(p,q)$ is
+%   an edge in in $B_i$ and $L(g_\rank, i)(p,q) = \neg_0$ if $(p,q)$ is not an
+%   edge in $B_i$. We thus have that $B_1$ and $B_2$ are bipartite isomorphic
+%   (in the sense defined above) if, and only if, $g_{\rank, 1}$ is
+%   syntactically equivalent to $g_{\rank, 2}$.
+
+%   Since the construction of $C_n$ can be implemented in time polynomial in the
+%   combined sizes of the input graphs, the mapping of $(B_1, B_2)$ to the tuple
+%   $(C_n, (g_{\rank, 1}, g_{\rank, 2}))$ witnesses the reduction. The result
+%   follows.
+% \end{proof}
+\begin{prop}
+  Let $\tau$ be any non-empty relational vocabulary and let $n, r, p \in \nats$,
+  with $p$ prime. There is a a polynomial time reduction from the graph
+  isomorphism problem to the problem of deciding if a given pair of gates in a
+  given symmetric rank-circuit for structures of size $n$ that (i) has injective
+  labels, (ii) contains no constant gates, and (iii) contains at most two rank
+  gates with bound $r$ and prime $p$, are syntactically equivalent.
+  \label{prop:syntactic-graph-iso}
+\end{prop}
+\begin{proof}
+  We have from \cite{} that there is a polynomial time reduction from the graph
+  isomorphism problem to the bipartite isomorphism problem. The bipartite
+  isomorphism problem is the decision problem for the set of all pairs of
+  partitioned bipartite graphs $B_1 := (U_1, V_1, E_1)$ and $B_2 := (U_2, V_2,
+  E_2)$ such that there exists a graph isomorphism $\pi : B_1 \rightarrow B_2$
+  with $\restr{\pi}{U_1} = U_2$ and $\restr{\pi}{V_1} = V_2$.
+
+  Suppose we are given two partitioned bipartite graphs $B_1 := (U_1, V_1, E_1)$
+  and $B_2 := (U_2, V_2, E_2)$. We assume, without a loss of generality, that
+  there exists $a, b \in \nats$ such that $U_1 = U_2 = [a]$ and $V_1 = V_2 =
+  [b]$.
+
+  Let $R$ be a relation symbol in $\tau$ and let $k := \arty{R}$. Let $G_{R} :=
+  \{g_{R, \vec{c}} : \vec{c} \in [n]^k\}$, $G_{\text{mid}} := \{\land_0,
+  \land_1, \neg_0, \land_{\text{out}} \}$, $G_{\rank} : = \{ g_{\rank, 1},
+  g_{\rank, 2}\}$, and $G_{\land} := \{g_{i, (u,v)} : i \in [2] \, (u,v) \in E_i
+  \}$. Let $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a
+  $(\{\rank^{1}_2\}, \tau)$-circuit defined as follows. Let $G = G_R \cup
+  G_{\text{mid}} \cup G_{\rank} \cup G_{\land}$ and $\Omega$ be the $0$-ary
+  function $\land_{\text{out}}$. For each $\vec{c} \in [n]^{\arty{R}}$ let
+  $\Lambda(\vec{c}) = g_{R, \vec{c}}$. Define $\Sigma$ as follows. For each $g
+  \in G$,
+  \begin{itemize}
+    \setlength\itemsep{0mm}
+  \item if $g \in G_R$ then $\Sigma(g) = R$,
+  \item if $g$ equals $\land_0$ or $\land_1$ then $\Sigma(g) = \land[n^k]$
+  \item if $g$ equals $\land_{\text{out}}$ then $\Sigma(g) = \land[2]$,
+  \item if $g \in G_\rank$ let $\Sigma(g) = \rank^r_p [a,b]$, and
+  \item if $g \in G_{\text{in}}$ and $g$ then $\Sigma(g) = \land[1]$.
+  \end{itemize}
+  Define $L$ as follows. For each $g \in G$,
+  \begin{itemize}
+    \setlength\itemsep{0mm}
+  \item if $g \in G$ and $g = g_{\text{out}}$ then for each $i \in [2]$,
+    $L(g)(i) := g_{\rank, i}$,
+  \item if $g \in G_\rank$ and $g = g_{\rank, i}$ then $L(g)(p,q) = g_{i,
+      (p,q)}$,
+  \item if $g \in G_{\land}$ and $g = g_{i, (p,q)}$ then $L(g)(1) = \land_1$ if
+    $(p,q) \in E_i$ and $L(g)(1) = \neg_0$ otherwise,
+  \item if $g = \neg_0$ then $L(g)(1) = \land_0$, and
+  \item if $g = \land_0$ or $g = \land_1$ then for all $p \in [n^k]$ we have
+    that $L(g)(p)$ equals $\Lambda^{-1}(\vec{c}_p)$, where $\vec{c}_p$ is the
+    $p$th element of $[n]^k$ in the lexicographical ordering on $[n]^k$.
+  \end{itemize}
+
+  We note that for $i \in [2]$, $L(g_{\rank, i})(p,q) = \land_1$ if $(p,q)$ is
+  an edge in in $B_i$ and $L(g_\rank, i)(p,q) = \neg_0$ if $(p,q)$ is not an
+  edge in $B_i$. We thus have that $B_1$ and $B_2$ are bipartite isomorphic (in
+  the sense defined above) if, and only if, $g_{\rank, 1}$ is syntactically
+  equivalent to $g_{\rank, 2}$.
+
+  Since the construction of $C_n$ can be implemented in time polynomial in the
+  combined sizes of the input graphs, the mapping of $(B_1, B_2)$ to the tuple
+  $(C_n, (g_{\rank, 1}, g_{\rank, 2}))$ witnesses the reduction. The result
+  follows.
+\end{proof}
+
+We have from Proposition \ref{prop:syntactic-graph-iso} that the problem of
+computing the syntactic equivalence relation, even if we restrict the input
+circuit to have very particular properties, as least as hard as the graph
+isomorphism problem. Since there is a trivial reduction from the problem of
+computing the syntactic equivalence relation over a restricted class of circuits
+to the general problem we have the following corollary.
+
+\begin{cor}
+  There is a polynomial-time reduction from the graph isomorphism problem to the
+  problem of determining if a given pair of gates in a given $(\mathbb{B},
+  \tau)$-circuit are syntactically equivalent.
+  \label{lem:syntactically-equivilent-general-hard}
+\end{cor}
+
+We also have a reduction from the problem of computing the syntactic equivalence
+relation to the problem of deciding if a given gate has unique labels.
+
+\begin{lem}
+  There are a polynomial-time reduction from the problem of determining if a
+  given pair of gates in a given $(\mathbb{B}, \tau)$-circuit are syntactically
+  equivalent to the problems of determining if a given gate in a given circuit
+  has unique labels.
+  \label{lem:syntactically-equivalent-unique-labels}
+\end{lem}
+
+\begin{proof}
+  Let $C_n := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a circuit and
+  let $g_1, g_2 \in G$. Let $D_n$ be the circuit formed from $C_n$ by removing
+  every gate $g \in G \setminus\{g_1, g_2\}$ such that $\neg W_t(g, g_1) \land
+  \neg W_t(g, g_2)$ (i.e. all those gates in the circuit such that there is no
+  path from them to either of the two gates). Let $C_n'$ be the circuit formed
+  from $D_n$ by adding in a single two-input $\AND$ gate $g'$ and connect both
+  $g_1$ and $g_2$ as inputs to $g'$ Moreover, we let this $g'$ be the single
+  output gate of $C_n'$.
+
+  It follows that $g_1 \equiv g_2$ in $C_n$ if, and only if, $g'$ has unique
+  labels in $C_n'$. Since the construction of $C_n'$ from $C_n$ can be completed
+  in polynomial time, the mapping of $(C_n, (g_1, g_2))$ to $(C_n', g')$
+  witnesses the reduction.
+\end{proof}
+
+We can construct a similar argument reducing the problem of deciding if two
+gates are syntactically equivalent to the problem of deciding if a given gate
+$g$ in a circuit $C_n$ has the property that there exists a permutation and two
+automorphisms extending that permutation that disagree with each other on $g$.
+
+\begin{lem}
+  There is a polynomial-time reduction to the problem from the problem of
+  determining if a given pair of gates gates in a given $(\mathbb{B},
+  \tau)$-circuit are syntactically equivalent to the problem of determining if
+  for a given triple $(C_n, g)$, where $C_n$ is a circuit, $g$ is a gate in
+  $C_n$, that there exists $\sigma \in \sym_n$ and automorphisms $\pi, \pi' \in
+  \aut(C_n)$ extending $\sigma$ such that $\pi (g) \neq \pi' (g)$.
+  \label{lem:syntactically-equivilent-unique-extensions}
+\end{lem}
+\begin{proof}
+  Let $C_n$ be a circuit and let $g_1$ and $g_2$ be two gates in $C_n$. Note
+  that for any gate $g$ in $\sigma \in sym_n$, if $\pi, \pi' \in \aut(C_n)$
+  extend $\sigma$ and $\pi_e := \pi'\pi{-1}$ then $\pi(g) \neq \pi'(g)$ if, and
+  only if, $\pi_e (g) \neq g$. It follows that there exists $\sigma \in sym_n$
+  such that there are automorphisms $\pi, \pi' \in \aut(C_n)$ extending $\sigma$
+  such that $\pi (g) \neq \pi'(g)$ if, and only if, there exists $\pi_e$
+  extending the trivial permutation such that $\pi (g) \neq g$.
+
+  Let $C_n'$ be the circuit constructed in the proof of Lemma
+  \ref{lem:syntactically-equivalent}. Let $\pi_e$ be a function from the gates
+  of $C_n$ to the gates of $C_n$ that swaps $g_1$ and $g_2$ and fixes all other
+  gates. Then if $g_1 \equiv g_2$ then $\pi_e$ is an automorphism extending the
+  trivial permutation. Moreover, if there exists an automorphism $\pi_e$
+  extending the trivial permutation such that $\pi_e(g_1) \neq g_1$ then it must
+  be that $\pi_e (g_1) = g_2$ and $\pi_e(g_2) = \pi(g_1)$, and so $g_1 \equiv
+  g_2$.
+
+  It follows that the mapping $(C_n, (g_1, g_2))$ to $(C_n', g_1)$ witnesses the
+  reduction and the result follows.
+\end{proof}
+
+We have shown in Proposition \ref{prop:syntactic-graph-iso}, Lemma
+\ref{lem:syntactically-equivalent-unique-labels} and Lemma
+\ref{lem:syntactically-equivilent-unique-extensions}, that various problems
+perhaps related to the problem of translating a circuit into an equivalent
+transparent circuit are at least as hard as the graph isomorphism problem. We
+now show that additionally recognising if a circuit has unique extensions is at
+least as hard as the graph isomorphism problem.
+
+\begin{lem}
+  There is a polynomial-time reduction from the graph isomorphism problem to the
+  problem of determining if a given circuit does not have unique extensions.
+  \label{lem:unique-extensions-hard}
+\end{lem}
+\begin{proof}
+  We use a similar argument as for Proposition \ref{prop:syntactic-graph-iso}.
+  We again argue using a reduction from thee bipartite isomorphism problem. Let
+  $B_1 := (U_1, V_1, E_1)$ and $B_2 := (U_2, V_2, E_2)$ and let $C_n$ be the
+  associated circuit defined in the proof of Proposition
+  \ref{prop:syntactic-graph-iso}. Let $C_n' = \op{merge-all} (C_n, G_{\land})$.
+  Notice that $B_1$ and $B_2$ are isomorphic if, and only if, $g_{\rank, 1}$ and
+  $g_{\rank, 2}$ are syntactically equivalent, which holds if, and only if,
+  there exists $\pi \in \aut(C_n')$ extending the trivial permutation such that
+  $\pi (g_{\rank, 1}) = g_{\rank, 2}$, which is true if, and only if, $C_n'$
+  does not have unique extensions. The mapping $(B_1, B_2)$ to $C_n'$ thus
+  witnesses the reduction.
+\end{proof}
+
+\begin{remark}
+  It's interesting to note that the circuit used in the reduction does not have
+  injective labels. If we instead ask about a reduction from GI to the problem
+  of deciding if a circuit has unique extensions and injective labels, then I
+  can reduce from to the problem of deciding if two rigid graphs are isomorphic.
+  It is unknown if this decision problem is as hard as the full graph
+  isomorphism problem. After looking around a bit I discovered that it's a very
+  important open problem in quantum computation. Is this worth mentioning?
+\end{remark}
+
+We have that if a circuit is transparent then we may compute in polynomial time
+the syntactic equivalence relation on the gates of that circuit, and hence
+compute an equivalent circuit that has unique extensions. However, we've shown
+that absent the transparency condition, computing the the syntactic equivalence
+relation is at least as hard as the graph isomorphism problem. Moreover, other
+properties that can be computed in polynomial time for transparent circuits,
+e.g. deciding if particular gates have unique labels or might act as
+counterexamples to the unique extensions, have also been shown to be at least as
+the graph isomorphism problem.
+
+While we have not shown that there is no polynomial time algorithm that
+translates an arbitrary circuit into an equivalent transparent circuit, we have
+provided evidence in favour of the conjecture that such an algorithm might not
+exist.
+
+\begin{remark}
+  I really don't like the slightly vague language here. I would prefer to say
+  this differently. How does one provide `evidence' that a functional problem is
+  hard, when one has proved results about a few related decision problems?
+\end{remark}
+
+However, we must then address another question: If we must include an explicit
+requirement on circuits, why not simply require that the circuit have unique
+extensions? But we have from Lemma \ref{lem:unique-extensions-hard} that at the
+least verifying that a circuit have unique extensions is at least as hard as the
+graph isomorphism problem. We show that, in contrast, deciding if a circuit is
+transparent is in $\PT$.
+
+\begin{prop}
+  There is an algorithm that takes as input a circuit, decides if that circuit
+  is transitive and runs in time polynomial in the size of the circuit.
+  \label{prop:tansitive-polynomial-time}
+\end{prop}
+\begin{proof}
+  Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
+  \tau)$-circuit. We first check that, for each non-symmetric gate $g \in G$,
+  $L(g)$ is an injection. If not, we return that $C$ is not transitive.
+
+  The height of a gate $g$ in the circuit is the distance from $g$ to the set of
+  input gates. For each $p \in nats$ let $G^p \subseteq G$ be the set of all
+  gates of height $p$ and let $G^{\leq p} = \bigcup_{0 \leq i \leq p}G^i$. Note
+  that each $g \in G^1$, $g$ has unique labels. Thus, from Lemma \ref{}, we can
+  compute the syntactic equivalence relation between gates in $G^{\leq 1}$
+  efficiently. We construct a loop as follows. Let $p$ be initialised to $1$. We
+  have that every non-symmetric gate $g \in G^{\leq p}$ has unique gates. We
+  compute the syntactic equivalence relation on $G^{\leq p}$ and check if each
+  non-symmetric gate in $g \in G^{i + 1}$ has unique labels. If not, halt and
+  output that the circuit is not transitive. If $p = \depth(C) -1$ then halt and
+  output that the circuit is transitive. If neither halt state is reached, then
+  increment $p$ by one and continue to the next iteration of the loop.
+
+  We note that in every iteration of the loop we have that every non-symmetric
+  gate in $G^{\leq p}$ has unique labels. Thus, from Proposition
+  \ref{prop:unique-labels-syntactic-equiv}, we may compute the syntactic
+  equvilence relation on this set of gates efficiently. Thus it is easy to see
+  that the above algorithm can be implemented so as to run in polynomial time.
+\end{proof}
+
+A similar result for circuits with unique labels.
+
+\begin{cor}
+  There is an algorithm that takes in a circuit and decides if that circuit has
+  unique labels and runs in time polynomial in the size of the circuit.
+\end{cor}
+\begin{proof}
+  Let $C$ be the input circuit. From Proposition
+  \ref{prop:transitive-polynomial-time} we may check if $C$ is transitive in
+  polynomial time. If $C$ is not transitive halt and output that $C$ does not
+  have unique labels. If $C$ is transitive then from Lemma \ref{} we may compute
+  the syntactic equivalence relation on the gates of $C$ efficiently. This then
+  allows us to check if each gate in $C$ has unique labels.
+\end{proof}
+
+We thus have that we can verify in polynomial time that a family of circuits
+indeed is transparent or has unique labels. The same cannot be said for the
+unique extensions property.
+
+It is also possible to show that we may compute orbits and supports on circuits
+with unique labels in polynomial-time (recall that we may assume, without a loss
+of generality, that transparent circuits have unique labels). The proof
+technique used here is analogous to the one used by Anderson and
+Dawar~\cite{AndersonD17}.
+
+\begin{lem}
+  Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit with unique labels of size $n$ and
+  $\sigma \in \sym_n$. There is an algorithm takes as input a circuit $C_n$ and
+  $\sigma \in \sym_n$ and outputs for each gate $g$ its image under the unique
+  automorphism extending $\sigma$ (if it exists). This algorithm runs in time
+  polynomial in the combined size of the input circuit and the encoding of the
+  permutation.
+  \label{lem:compute-automorphisms}
+\end{lem}
+\begin{proof}
+  Suppose $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$. We build up the
+  mapping $\pi$ extending $\sigma$ recursively. If at some point in the
+  recursive construction we arrive at a point where no mapping for $g$ can be
+  found we halt at that point and return that no automorphism exists.
+
+  Let $h$ be any gate in the circuit. Suppose $h$ is an input gate. If $h$ is a
+  constant gate then let $\pi (h) = h'$. If $h$ is a relational gate such that
+  $R := \Sigma(h)$ and check if there exists $h'$ such that $\Sigma (h') = R$
+  and $\sigma \Lambda_R(h) = \Lambda_R(h')$ and, if $h$ is an output gate then
+  $h'$ is an output gate such that $\sigma Omega^{-1}(h) = \Omega^{-1}(h')$. If
+  such a $h'$ does not exist halt and output that there is no automorphism
+  extending $\sigma$. We have from Lemma \ref{} that if such an $h'$ exists it
+  must be unique, and we set $\pi(h) = h'$.
+
+  Let $h$ be an internal gate in the circuit and assume we have defined $\pi
+  (g)$ for every gate $g$ of height less than $h$. Let $h'$ be a gate in the
+  circuit such that $\Sigma(h) = \Sigma (h')$, $\pi L(h)$ is isomorphism
+  equivalent to $L(h')$ and, if $h$ is an output gate then $h'$ is an output
+  gate such that $\sigma \Omega^{-1}(h) = \Omega^{-1}(h')$. Since $C_n$ has
+  unique labels we have that $\pi L(h)$ is isomorphism equivalent to $L(h')$ if,
+  and only if, $L(h')^{-1}\pi L(h)$ acts like an isomorphism. This can be
+  determined easily. If no such $h'$ exists halt and output that there is no
+  automorphism extending $\sigma$. We have from Lemma \ref{} that if $C_n$ has
+  unique labels then there is at most one such $h'$.
+
+  This recursive approach can be implemented as an algorithm that runs in time
+  polynomial in the combined size of the inputs and outputs the required
+  automorphism if it exists.
+\end{proof}
+
+This result uses a proof very similar to the one for a similar result proved by
+Anderson and Dawar~\cite{Anderson17D}.
+
+\begin{lem}
+  There is an algorithm that takes as input a circuit $C_n$ with unique labels
+  and decides if $C_n$ is symmetric. If $C_n$ is symmetric outputs the orbits
+  and coarsest supporting partitions of every gate. Moreover, this algorithm
+  runs in time polynomial in the size of the input circuit.
+  \label{lem:computing support}
+\end{lem}
+
+\begin{proof}
+  Suppose $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$. Let $(u, v) \in
+  \sym_n$ be a transposition. We may use Lemma \ref{lem:compute-automorphisms}
+  to determine the unique automorphism $\pi_{(u,v)}$ extending $(u, v)$. It is
+  easy to see that, since the set of transpositions generate $\sym_n$, for all
+  $(u,v) \in \sym_n$ $\pi_{(u,v)}$ the automorphism $\pi_{(u,v)}$ exists if, and
+  only if, $C_n$ is symmetric. We note that there are ${n}\choose{2}$
+  transpositions. It follows that we may check in polynomial time if $C_n$ is
+  symmetric. If $C_n$ is not symmetric we output that it is not symmetric and
+  halt.
+
+  Suppose then that $C_n$ is symmetric. For transposition $(u, v) \in \sym_n$,
+  let $\mathcal{P}_{(u,v)} := \{\{u,v\}\}\bigcup_{w \in [n] \setminus
+    \{u,v\}}\{\{w\}\}$ be a partition of $[n]$. We have that $\pi_{(u,v)}$ fixes
+  $g$ if, and only if, $\mathcal{P}_{(u,v)}$ supports $g$. Since we can
+  efficiently check if $\pi_{(u,v)}$ fixes $g$ it follows that we can
+  effeciently check if $\mathcal{P}_{(u,v)}$ supports $g$. Let $\mathcal{P}$ be
+  the result of combining the set consisting of those partitions
+  $\mathcal{P}_{(u,v)}$ that support $g$ using $\mathcal{E}$. From Proposition
+  \ref{prop:combining-supporting-patitions} we have that $\mathcal{P}$ supports
+  $g$. Suppose that $\mathcal{P}$ is not the coarsest supporting partition of
+  $g$. Then there exists a partition $\mathcal{P}'$ supporting $g$ such
+  $\mathcal{P}' \preceq P$ and $\mathcal{P}' \neq \mathcal{P}$. But then there
+  exists $P \in \mathcal{P}$ and $P' \in \mathcal{P}'$ such that $P \subsetneq
+  P'$. But then there exists $a , b \in P'$ such that $a \not\in P$. It follows
+  that the transposition $(a,b)$ fixes $\mathcal{P}'$ and so $\pi_{(a,b)}$ fixes
+  $g$, but then, $\mathcal{P}_{(a,b)}$ supports $g$ and so, from the
+  construction of $\mathcal{P}$, $\mathcal{P}$ is fixed by $(a,b)$. But
+  $\mathcal{P}$ is not fixed by $(a,b)$, so we have a contradiction. We thus
+  have that $\mathcal{P}$ is the coarsest supporting partition of $g$.
+
+  It remains to compute the orbit of a gate $g$. Let $S_0 := \{g\}$ and for each
+  $i \geq 0$ let $S_{i+1} := S_i \bigcup_{(u,v) \in \sym_n} \pi_{(u,v)}S_i$. Let
+  $S$ be the least fixed point. It is easy to see that $S \subseteq \orb(g)$ as
+  every gate in $S$ is equal to the action of some sequence of automorphisms
+  (extending transpositions) acting on $g$. Moreover, since the set of all
+  transpositions generates $\sym_n$, it follows that $\orb(g) \subseteq S$ and
+  so $\orb(g) = S$.
+
+  Given the polynomial bound on the number of transpositions, and the
+  polynomial-time bound on the algorithm from Proposition
+  \ref{prop:combining-supporting-partitions}, it is easy to see that the
+  procedures described above can be implemented so as to run in time polynomial
+  in the size of the input circuit.
+\end{proof}
+
+\begin{remark}
+  The above result shouldn't be here. They are about group theory, or rather
+  group action, I don't think they actually has anything to do with circuits.
+\end{remark}
+
+Once again we note that computing the orbit of a gate for a general circuit is
+as hard as the graph isomorphism problem. We make use of the ability to compute
+the orbit of a gate in polynomial time in sub-section
+\ref{sec:translating-formulas-to-FPR} when translating families of circuits into
+equivalent formulas. As such the approach in this paper would fail for the
+general circuit.
+
+\begin{prop}
+  There is a polynomial-time reduction from the graph isomorphism problem to the
+  problem of computing if two gates in a given circuit are in the same orbit.
+\end{prop}
+\begin{proof}
+  This is a really simple circuit similar to the one from an earlier
+  proposition. I will fill this result in later.
+\end{proof}
+
+% \begin{lem}
+%   There is a polynomial-time Turing reduction from the problem of determining
+%   if a given pair of gates in a given circuit are syntactically equivalent to
+%   the problem of deciding if a circuit is transparent.
+%   %   If the problem of deciding if a given circuit is transparent can be
+%   %   decided
+%   %   in
+%   %   polynomial time then the graph isomorphism problem is in polynomial
+%   %   time.
+% \end{lem}
+% \begin{proof}
+%   Suppose there is an algorithm that takes as input, runs in time polynomial
+%   in the size of the circuit, and decides whether or not the circuit is
+%   transparent.
+
+%   From Corollary \ref{} it is sufficient to show that there is a
+%   polynomial-time algorithm for the problem of deciding if a pair of gates in
+%   a given circuit are syntactically equivalent. Let $C_n$ be a circuit and
+%   $g_1$ and $g_2$ be two gates in the circuit.
+
+%   %   We simply need a polynomial-time reduction from the problem of computing
+%   %   t
+%   %   to the problem
+%   %   of checking if a given circuit is transparent. Let $C_n =\langle G,
+%   %   \Omega,
+%   %   \Sigma, \Lambda, L\rangle$ be a circuit and let $g_1$ and $g_2$ be two
+%   %   gates
+%   %   in $G$. We now construct a circuit $C_n'$. If $g_1 = g_2$ then let
+%   %   $C_n'$ be
+%   %   any transparent circuit. If $g_1$ and $g_2$ do not satisfy any of
+%   %   conditions
+%   %   (i), (ii), (iii) or (v) of syntactic equivalence then let $C_n'$ be any
+%   %   non-transparent circuit. So suppose all these conditions are met and
+%   %   $g_1
+%   %   \neq
+%   %   g_2$, then let $D_n$ be the sub-circuit of $C_n$ consisting of exactly
+%   %   those
+%   %   gates $g$ in $C_n$ such that $W_t(g, g_1)$ or $W_t(g, g_2)$. Then let
+%   %   $C_n'$
+%   %   be $D_n'$ with an additional gate $g_\rank$, such that $g_\rank $ is
+%   %   labelled
+%   %   by the function $\rank^1_2[2,1]$ and $g_\rank$
+% \end{proof}
+
+% \begin{corollary}
+% \end{corollary}
+
+% We have from this proposition that even many nice properties Since there is a
+% polynomial-time reduction from this problem reduces the general problem of
+% deciding the syntatic equivilence relation for an arbitary
+
+% \begin{corollary}
+%   There is a polynomial-time reduction from the graph isomorphism problem to
+%   the problem of determining if a given $(\mathbb{B}, \tau)$-circuit is rigid.
+% \end{corollary}
+
+% \begin{corollary}
+%   There is a polynomial-time reduction from the graph isomorphism problem to
+%   the problem of determining if a given gate in a given $(\mathbb{B},
+%   \tau)$-circuit has unique labels.
+% \end{corollary}
+
+% reduction from the graph isomorphism from to the problem of of computing the
+% the syntactic equivalence relation on the gates of an arbitrary $(\mathbb{B},
+% \tau)$-circuit.
+
+% It is worth noting that if we restrict the input to a class of circuits
+% defined over symmetric bases then we can decide the syntactic equivalence
+% relation in polynomial time.
+
+% % \begin{prop}
+% %   Let $C_n$ be a circuit with symmetric gates. There is an algorithm that
+% %   takes in such a circuit, runs in time polynomial in the size of the circuit,
+% %   and outputs the syntactic equivalence relation on the gates of $C_n$.
+% %   \label{prop:symmetric-syntactic}
+% % \end{prop}
+% % \begin{proof}
+% % \end{proof}
+
+% Moreover, it turns out that being able to compute the syntactic equivalence
+% relation in polynomial time for some class of circuits $\mathcal{C}$ implies
+% that the existence of a polynomial-time algorithm for converting circuits in
+% $C$ into equivalent rigid circuit.
+
+% % \begin{prop}
+% %   Let $\mathcal{C}$ be a set of circuits. Suppose the syntactic equivalence
+% %   relation can be computed in polynomial time for circuits in $\mathcal{C}$.
+% %   It follows that there is an algorithm that runs in polynomial time that
+% %   takes in a circuit $C \in \mathcal{C}$ and outputs a rigid circuit $C''$
+% %   such that if $C$ is symmetric then $C'$ is symmetric.
+% %   \label{prop:syntactic-equivilence-rigid}
+% % \end{prop}
+% % \begin{proof}
+% % \end{proof}
+
+% The following result gives us that the unique labels condition is sufficient.
+
+% % \begin{prop}
+% %   Let $\mathcal{C}$ be syntactically transparent class of circuits. It follows
+% %   that there exists an algorithm that takes in a $(\mathbb{B}, \tau)$-circuit
+% %   $C \in \mathcal{C}$ and outputs a $(\mathbb{B} \cup \mathbb{B}_{\std},
+% %   \tau)$-circuit $C'$ such that $C$ and $C'$ compute the same function, $C'$
+% %   is rigid, and if $C$ is symmetric then $C'$ is symmetric. Moreover, this
+% %   algorithm runs in time polynomial in the size of the input circuit.
+% % \end{prop}
+% % \begin{proof}
+% %   Let $C' = \make-injective-all(\op{merge-all} (C, G)($). We have that $C'$ is
+% %   symmetric if $C$ is symmetric. Since the syntactic equivalence relation can
+% %   be computed in polynomial time for circuits in $\mathcal{C}$ it follows that
+% %   this operation can be implemented so as to run in time polynomial in the
+% %   size of $C$. Clearly every gate $g$ in $C'$ belongs to a singleton syntactic
+% %   equivalence class.
+% % \end{proof}
+
+% \begin{lem}
+%   Let $\mathbb{B}$ be a basis of symmetric functions. Then for any class of
+%   circuits $\mathcal{C}$ defined over the basis $\mathbb{B}$, $\mathcal{C}$ is
+%   a syntactically transparent class of circuits.
+% \end{lem}
+% In contrast to
+% \begin{lem}
+%   If the class of all circuits is syntactically transparent then then graph
+%   isomorphism problem is in $\PT$.
+% \end{lem}
+
+% \begin{lem}
+%   Let $\mathcal{C}$ be a syntactically transparent class of circuits. There is
+%   an algorithm that takes as input a $(\mathbb{B}, \tau)$-circuit $C \in
+%   \mathcal{C}$ and decides if $C$
+% \end{lem}
+
+% Since the class of The following result, also proved by Anderson and Dawar
+% \cite{AndersonD17}, follows as a corollary.
+
+% \begin{lem}
+%   Let $\mathcal{C}$
+% \end{lem}
+
+% \begin{lem}
+%   Let $C_n = \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a $(\mathbb{B},
+%   \tau)$-circuit computing a $q$-ary query. If $C_n$ has unique labels then it
+%   is $C_n$ rigid
+%   \label{lem:unique-implies-rigid}
+% \end{lem}
+% \begin{proof}
+
+%   %   Suppose there exists a gate $g'$ such that $W_t (g, g')$ and $W_t
+%   %   (\pi(g),
+%   %   g')$ and $\pi (g') = g'$, then $\pi H_{g'} = H_{g'}$, and since $g'$ has
+%   %   unique labels it follows that $\pi$ acts trivially on $H_{g'}$ (i.e. for
+%   %   all
+%   %   $h \in H_{g'}$, $\pi(h) = h$). Moreover, for any pair of gates $h,h' \in
+%   %   G$
+%   %   such that $W(h, h')$ and $W_t(h', g')$, if $\pi$ acts on trivially on
+%   %   the
+%   %   children of $h'$ then $\pi (h) = h$ and so $\pi$ must act trivially
+
+%   %   $\pi$ acts trivially on the children of $h$.
+
+%   %   If $\Omega_g \cap \Omega_{\pi(g)} = \emptyset$ then, since
+%   %   $\Omega_{\pi(g)}
+%   %   =
+%   %   \pi \Omega_g$, there exists $g' \in \Omega_g$ such that $\pi g' \neq
+%   %   g'$.
+%   %   But
+%   %   $\pi$ must act trivially on output gates, so this is a contradiction. So
+%   %   there
+%   %   exists $g' \in \Omega_g \cap \Omega_{\pi(g)}$. But then $W_t (g, g')$
+%   %   and
+%   %   $W_t
+%   %   (\pi (g), g')$.
+
+%   %   We have that $g$ must be a non-output internal gate. So $g$ is
+%   %   syntactically
+%   %   equivalent to $\pi (g)$.
+
+%   %   and let $h$ be a gate such that $W_t (g, h)$.
+% \end{proof}
+
+% \begin{prop}
+%   Let $C_n$ be a circuit with unique labels. If
+% \end{prop}
+
+% \begin{prop}
+
+% \end{prop}
+% \begin{proof}
+% \end{proof}
+
+% \begin{prop}
+%   Let $\mathcal{C}$ be a class on which the Let $C_n := \langle G, \Omega,
+%   \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B}, \tau)$-circuit with unique
+%   labels. There is a deterministic algorithm that takes in such a circuit and
+%   outputs the syntactic equivalence relation on $G$. Moreover, this algorithm
+%   runs in time polynomial in the size of the circuit.
 %   \label{prop:unique-labels-syntactic-equiv}
 % \end{prop}
-% \begin{proof}
-%   We build of the relation by induction. Let $g$
-% \end{proof}
-
-Putting together Propositions \ref{prop:symmetric-syntactic},
-\ref{prop:syntactic-equivilence-rigid}, and
-\ref{prop:unique-labels-syntactic-equiv}, we have that there is a
-polynomial-time algorithm that takes as input a circuit with unique labels and
-outputs an equivalent rigid circuit. In fact, there is an equivalence of sorts
-between the unique labels condition and the rigidity condition.
-
-\begin{prop}
-  Let $\mathcal{C}$ be a family of circuits. There is an algorithm that runs in
-  polynomial-time and takes in a circuit $C \in \mathcal{C}$ and outputs a rigid
-  circuit $C'$ such that if $C$ is symmetric then $C'$ is symmetric if, and only
-  if, there is an algorithm that runs in polynomial-time and takes in a circuit
-  $C \in \mathcal{C}$ and outputs a circuit $C'$ with unique labels such that if
-  $C$ is symmetric then $C'$ is symmetric.
-\end{prop}
-
-It follows then that for the symmetric circuits defined over bases of symmetric
-functions discussed by Anderson and Dawar~\cite{} we may assume the circuits are
-rigid and/or have unique labels without a loss of generality. For the more
-general circuit discussed in this paper we cannot make such an assumption as
-deciding rigidity is harder then graph isomorphism. However, if we restrict
-ourselves to families of circuits with unique labels then again we may assume
-rigidity without a loss of generality.
-
-Of course, this restriction to circuits with unique labels is only useful if we
-can show that formulas in rank logic can be translated into $P$-uniform families
-circuits with unique labels. In the next subsection we prove that this is indeed
-the case.
+
+% % \begin{prop}
+% %   There is an algorithm that takes in a $(\mathbb{B}, \tau)$-circuit $C$ with
+% %   unique labels and outputs the syntactic equivalence relation on its gates.
+% %   This algorithm runs in time polynomial in the size of $C$.
+% %   \label{prop:unique-labels-syntactic-equiv}
+% % \end{prop}
+% % \begin{proof}
+% %   We build of the relation by induction. Let $g$
+% % \end{proof}
+
+% Putting together Propositions \ref{prop:symmetric-syntactic},
+% \ref{prop:syntactic-equivilence-rigid}, and
+% \ref{prop:unique-labels-syntactic-equiv}, we have that there is a
+% polynomial-time algorithm that takes as input a circuit with unique labels and
+% outputs an equivalent rigid circuit. In fact, there is an equivalence of sorts
+% between the unique labels condition and the rigidity condition.
+
+% \begin{prop}
+%   Let $\mathcal{C}$ be a family of circuits. There is an algorithm that runs
+%   in polynomial-time that takes in a circuit $C \in \mathcal{C}$ and outputs a
+%   rigid circuit $C'$ such that if $C$ is symmetric then $C'$ is symmetric if,
+%   and only if, there is an algorithm that runs in polynomial-time and takes in
+%   a circuit $C \in \mathcal{C}$ and outputs a circuit $C'$ with unique labels
+%   such that if $C$ is symmetric then $C'$ is symmetric.
+% \end{prop}
+
+% It follows then that for the symmetric circuits defined over bases of
+% symmetric functions discussed by Anderson and Dawar~\cite{} we may assume the
+% circuits are rigid and/or have unique labels without a loss of generality. For
+% the more general circuit discussed in this paper we cannot make such an
+% assumption as deciding rigidity is harder then graph isomorphism. However, if
+% we restrict ourselves to families of circuits with unique labels then again we
+% may assume rigidity without a loss of generality.
+
+% Of course, this restriction to circuits with unique labels is only useful if
+% we can show that formulas in rank logic can be translated into $P$-uniform
+% families circuits with unique labels. In the next subsection we prove that
+% this is indeed the case.
 
 \subsection{Translating FPR to Symmetric Matrix Circuits}
-Anderson and Dawar~\cite{} define a translation from formulas of $\FPC$ into
-equivalent $P$-uniform families of symmetric majority-circuits. More formally,
-they show that for $\theta(\vec{x}) \in \FPC[\tau]$ there exists a $P$-uniform
+In this subsection we translate formulas of $\FPR$ into circuits. In particular,
+we show that for $\theta(\vec{x}) \in \FPR[\tau]$ there exists a $P$-uniform
 family of symmetric majority-circuits $(C_n)_{n \in \nats}$ such that the query
@@
 \begin{proof}
-  We say a formula $\psi(\vec{x}) \in \FPR[tau]$ is
-  \emph{matrix-circuit-translatable} if there is a $P$-uniform family of
-  symmetric matrix-circuits with unique labels that compute the same query as
-  $\psi(\vec{x})$. If a formula $\psi(\vec{x}) \in \FPR[tau]$ is
-  matrix-circuit-translatable we let $(C^\psi_n)_{n \in \nats}$ denote the
-  corresponding $P$-uniform family of symmetric matrix-circuits with unique
-  labels.
-
-  We prove that $\theta(\vec{x}) \in \FPR[\tau]$ is matrix-circuit-translatable
-  by structural induction. That is, we first prove that if every sub-formula of
+  We say a formula $\psi(\vec{x}) \in \FPR[tau]$ is \emph{circuit-translatable}
+  if there is a $P$-uniform family of transparent symmetric matrix-circuits that
+  compute the same query as $\psi(\vec{x})$. If a formula $\psi(\vec{x}) \in
+  \FPR[tau]$ is circuit-translatable we let $(C^\psi_n)_{n \in \nats}$ denote
+  the corresponding $P$-uniform family of transparent symmetric matrix-circuits.
+
+  We prove that $\theta(\vec{x}) \in \FPR[\tau]$ is circuit-translatable by
+  structural induction. That is, we first prove that if every sub-formula of
   $\theta(\vec{x})$ is circuit-translatable then $\theta(\vec{x})$ is
@@
   and in fact we may assume, without a loss of generality, that this translation
-  yields a family of rigid circuits.
-
-  % It is sufficient to prove that if $\theta(\vec{x})$ has the property that
-  % all
-  % of its subformulas have are matrix-circuit-translatable then there is an
-  % algorithm that takes in a natural number $n$ and outputs a symmetric
-  % matrix-circuit $C^\theta_n$ with unique labels that is equivalent to
-  % $\theta(\vec{x})$ on structures of size $n$.
+  yields a family of transparent circuits with unique extensions.
 
   We first consider the case where $\theta(\vec{x})$ is a conjunction of
-  matrix-circuit-translatable formulas. Suppose $\phi_1, \phi_2 \in \FPR[\tau]$
-  are matrix-circuit-translatable and $\theta (\vec{x}) = \phi_1(\vec{x}) \land
+  circuit-translatable formulas. Suppose $\phi_1, \phi_2 \in \FPR[\tau]$ are
+  circuit-translatable and $\theta (\vec{x}) = \phi_1(\vec{x}) \land
   \phi_2(\vec{x})$. Let $R_{\phi_1}$ and $R_{\phi_2}$ be two $\vert \vec{x}
@@
   inductive hypothesis, for each $i \in \{1,2\}$ we may efficiently compute the
-  circuit $C^{\phi_i}_n = \langle G_i, \Omega_i, \Sigma_i Lambda_i, L_i
+  circuit $C^{\phi_i}_n = \langle G_i, \Omega_i, \Sigma_i \Lambda_i, L_i
   \rangle$. Let $R \in \tau$ and let $D^{\theta}_n :=
@@
   computes the same relation as defined by $\theta(\vec{x})$ for structures of
-  size $n$. Furthermore, since $C^{\phi_1}_n$, $C^{\phi_2}_n$ and $C^{theta'}_n$
+  size $n$. Furthermore, since $C^{\phi_1}_n$, $C^{\phi_2}_n$ and $C^{\theta'}_n$
   are symmetric so is $C^{\theta}_n$. Lastly, notice that all non-output gates
   in $D^{\theta}_n$ have unique labels. After the $\op{merge-all}$ and
-  $\op{make-injective-all}$ operation the output gates have unique labels, and thus
-  $C^{\theta}_n$ has unique labels. This construction takes in a natural number
-  $n$ and produces the required circuit $C^{\theta}_n$. This construction can be
-  computed by an algorithm in time polynomial in $n$. Thus $\theta(\vec{x})$ is
-  matrix-circuit-translatable.
-
-  % We construct the circuit $C'_n = \langle G', \Omega', \Sigma',
-  % \Lambda', L' \rangle$ by `inserting' $C^{\phi_1}_n$ and $C^{\phi_2}_n$
-  % into
-  % $C^{\theta'}_n$. We now construct $C^{\theta}_n$ from $C'_n$ as follows:
-  % \begin{itemize}
-  % \item For each $i \in \{1,2\}$ and each relational gate $g$ in $C_n$ such
-  %   that $\Sigma'(g) = R_{\phi_i}$ `replace' $g$ with
-  %   $\Omega_i(\Lambda_i(g))$,
-  % \item then, for each syntactic equivalence class $H \subseteq
-  %   \range(\Omega_1) \uplus \range(Omega_2)$, `merge' $H$, and finally
-  % \item run `separate-labels' on the circuit.
-  % \end{itemize}
-
-  % We note that, since $C^{\phi_1}_n$, $C^{\phi_2}_n$ and $C^{\theta'}_n$ have
-  % unique labels, the only gates that might not have unique labels in
-  % $C^{\theta}_n$ are those whose input gates include gates in the range of
-  % $\Omega_1$ or $\Omega_2$. However, all such gates are symmetric and steps
-  % (2)
-  % and (3) above guarantee that these gates have unique labels. Finally, we
-  % note
-  % that this algorithm can implemented such that the computation of
-  % $C^{\theta}_n$ from $n$ runs in time polynomial in $n$.
+  $\op{make-injective-all}$ operation the output gates have unique labels, and
+  thus $C^{\theta}_n$ has unique labels. This construction takes in a natural
+  number $n$ and produces the required circuit $C^{\theta}_n$. This construction
+  can be computed by an algorithm in time polynomial in $n$. Thus
+  $\theta(\vec{x})$ is circuit-translatable.
 
@@
   This same approach can be used for to handle many other cases. For
-  matrix-circuit-translatable $\phi, \phi_1, \phi_2 \in \FPR[\tau]$ similar
+  circuit-translatable $\phi, \phi_1, \phi_2 \in \FPR[\tau]$ similar
   constructions can be used to prove that if $\theta(\vec{x}) \in FPR[\tau]$ is
@@
   $\forall y. \phi (\vec{x}, y)$ or $\exists y. \phi (\vec{x}, y)$ then
-  $\theta(\vec{x})$ is matrix-circuit-translatable.
-
-  Suppose $\theta(\vec{x}) = [\lfp_{V, \vec{y}} \phi(\vec{y}, V)](\vec{x})$ for
-  some matrix-circuit-translatable formula $\phi(\vec{x}, \vec{y}) \in FPR[\tau
-  \uplus \{V\}]$ and $k$-ary relation symbol $V$. We now describe an algorithm
-  that takes in a natural number $n$ and outputs $C^{\theta}_n$. We have that we
+  $\theta(\vec{x})$ is circuit-translatable.
+
+  Suppose $\theta(\vec{x}) = \lfp{V, \vec{y}}{\phi(\vec{x}, \vec{y},
+    V)}(\vec{x})$ for some circuit-translatable formula $\phi(\vec{x},
+  \vec{y}) \in FPR[\tau \uplus \{V\}]$ and $k$-ary relation symbol $V$. Let $n$
+  be a natural number. We construct $C^{\theta}_n$ as follows. We have that we
   may efficiently compute $C^{\phi}_n$. For each $i \in [n^k]$ we construct a
   circuit $C^i = \langle G^i, \Omega^i, \Sigma^i, \Lambda^i, L \rangle $ as
-  follows. Let $C^1$ be $C^{\phi}_n$ but with all relational gates labelled by
-  the symbol $V$ replaced with a $0$. For each $i>1$ we construct $C^{i}$ by
-  `gluing' $C^{i-1}$ into $C^\phi_n$, producing $C^i$. Set $C^{\theta}_n :=
-  C^{n^k}$. Since $C^1$ and $C^\phi_n$ are symmetric and have unique labels, by
-  induction for each $i > 1$ $C^i$ is symmetric and has unique labels. It
-  follows that $C^{\theta}_n$ is symmetric and has unique labels. Moreover,
-  since the least-fixed-point operator must converge in at most $n^k$ steps,
-  this algorithm runs in time polynomial in $n$ and the family
-  $(C^{\theta}_n)_{n \in \nats}$ computes the same query as $\theta(\vec{x})$.
+  follows. Let $C^0$ be a circuit consisting of exactly $n^k$ gates, such that
+  each gate is a constant $0$ gate and each gate is an output gate. Let $R$ be a
+  relation symbol in $\tau$. For each $i > 0$ let $C^i :=
+  \op{concatinate}(C^{\phi}_n, (C^{i-1}_n), (V), R)$ be $C^{\phi}_n$ but with
+  all relational gates labelled by the symbol $V$ replaced with the constant
+  $0$. Since $C^1$ and $C^\phi_n$ are symmetric and have unique labels, and the
+  operation $\op{concatinate}$ preserves the properties of symmetric and unique
+  labels, it follows by induction that for each $i \geq 1$, $C^i$ is a symmetric
+  rank-circuit with unique labels. It follows that $C^{\theta}_n := C^{n^k}$ is
+  a symmetric rank-circuit and has unique labels. Moreover, since the
+  least-fixed-point operator must converge in at most $n^k$ steps, this
+  construction can be implemented so as to run in time polynomial in $n$. The
+  construction also guarantees that $(C^{\theta}_n)_{n \in \nats}$ computes the
+  same query as $\theta(\vec{x})$.
 
@@
 
-  % gives for each $\theta (\vec{x}) \in FPC[\tau]$ a $P$-uniform family of
-  % formulas $(\theta_n)_{n \in \nats}$ such that $\theta_n(\vec{x})$ is in the
-  % extension of fixed-point logic with counting quantifiers and is equivalent
-  % to
-  % $\theta(\vec{x})$ on structures of size $n$. Similarly, it can be shown that
-  % for $\theta (\vec{x}) \in FPR[\tau]$ there exists an algorithm that takes as
-  % input a natural number $n$ and outputs a formula $\theta_n(\vec{x})$ with
-  % counting quantifiers and no number terms which is equivalent to
-  % $\theta(\vec{x})$ for structures of size $n$ and does not contain any number
-  % terms. Moreover, this algorithm runs in time polynomial in $n$.
-
   Thus, in order to handle the number-term case, it is sufficient to show that
   if $\phi(\vec{x}) \in \FPR[\tau]$ is circuit-translatable then
-  $\theta(\vec{x}) := C^{k}y. \phi(\vec{x}, y)$ is matrix-circuit-translatable.
+  $\theta(\vec{x}) := C^{k}y. \phi(\vec{x}, y)$ is circuit-translatable.
   A similar construction as for the universal and existential quantifier gives
@@
   $\theta_n(\vec{x})$ are equivalent on structures of size $n$. It is thus
-  sufficient to prove that, for matrix-circuit-translatable $\phi(\vec{z},
+  sufficient to prove that, for circuit-translatable $\phi(\vec{z},
   \vec{y}, \vec{x}) \in \FPR[\tau]$ is, a prime $p$, and a natural number $r$,
@@
 
-  \item $\Sigma^{\theta'} (g) := rk^r_p$ if $g \in G_1$ and $\Sigma^{\theta'}(g)
-    = R_\phi$ if $g \in G_2$,
+  \item $\Sigma^{\theta'} (g) := rank^r_p$ if $g \in G_1$ and
+    $\Sigma^{\theta'}(g) = R_\phi$ if $g \in G_2$,
   \item For each $(\vec{a}, \vec{b}, \vec{c}) \in [n]^{k_1 +k_2 + k}$ let
@@
 
-  Since $C^{\theta'}_n$ and $C^{\phi}_n$ are symmetric and have unique labels it
-  follows that $D^{\theta}_n$ is a symmetric rank-circuit with unique labels. It
-  can be shown that the construction of $C^{\theta}_n$ given the number $n$ can
-  be implemented as an algorithm running in time polynomial in $n$. The
+  Since $C^{\theta'}_n$ and $C^{\phi}_n$ are symmetric, have unique labels, and
+  the input tuples of relations and circuits are singletons, it follows that
+  $D^{\theta}_n$ is a symmetric rank-circuit with unique labels. It can be shown
+  that the construction of $C^{\theta}_n$ from the natural number $n$ can be
+  implemented as an algorithm running in time polynomial in $n$. The
   construction ensures that the circuit family $(C^{\theta}_n)_{n \in \nats}$
@@
 \end{proof}
+
+% \begin{proof}
+%   We say a formula $\psi(\vec{x}) \in \FPR[tau]$ is
+%   \emph{circuit-translatable} if there is a $P$-uniform family of symmetric
+%   matrix-circuits with unique labels that compute the same query as
+%   $\psi(\vec{x})$. If a formula $\psi(\vec{x}) \in \FPR[tau]$ is
+%   matrix-circuit-translatable we let $(C^\psi_n)_{n \in \nats}$ denote the
+%   corresponding $P$-uniform family of symmetric matrix-circuits with unique
+%   labels.
+
+%   We prove that $\theta(\vec{x}) \in \FPR[\tau]$ is circuit-translatable by
+%   structural induction. That is, we first prove that if every sub-formula of
+%   $\theta(\vec{x})$ is circuit-translatable then $\theta(\vec{x})$ is
+%   circuit-translatable and, second, we note that every atomic formula in
+%   $\FPR[\tau]$ is circuit-translatable. We have already that formulas of
+%   $\FPC[\tau]$ are circuit translatable (Anderson and
+%   Dawar~\cite{AndersonD17}), and in fact we may assume, without a loss of
+%   generality, that this translation yields a family of rigid circuits.
+
+%   %   It is sufficient to prove that if $\theta(\vec{x})$ has the property
+%   %   that
+%   %   all
+%   %   of its subformulas have are matrix-circuit-translatable then there is an
+%   %   algorithm that takes in a natural number $n$ and outputs a symmetric
+%   %   matrix-circuit $C^\theta_n$ with unique labels that is equivalent to
+%   %   $\theta(\vec{x})$ on structures of size $n$.
+
+%   We first consider the case where $\theta(\vec{x})$ is a conjunction of
+%   matrix-circuit-translatable formulas. Suppose $\phi_1, \phi_2 \in
+%   \FPR[\tau]$ are matrix-circuit-translatable and $\theta (\vec{x}) =
+%   \phi_1(\vec{x}) \land \phi_2(\vec{x})$. Let $R_{\phi_1}$ and $R_{\phi_2}$ be
+%   two $\vert \vec{x} \vert$-ary relation symbols not in $\tau$. Let $\theta'
+%   (\vec{x}) := R_{\phi_1}(\vec{x}) \land R_{\phi_2}(\vec{x})$. Let $n \in
+%   \nats$. Since $\theta'(\vec{x})$ is a formula of $\FPC$, we may efficiently
+%   compute $C^{\theta'}_n$ using the construction in \cite{AndersonD17}. From
+%   the inductive hypothesis, for each $i \in \{1,2\}$ we may efficiently
+%   compute the circuit $C^{\phi_i}_n = \langle G_i, \Omega_i, \Sigma_i
+%   Lambda_i, L_i \rangle$. Let $R \in \tau$ and let $D^{\theta}_n :=
+%   \op{compose}(C^{\theta'}_n, (C^{\phi_1}_n, C^{\phi_2}_n), (R_1, R_2), R)$.
+%   Let $H$ consist of all non-output gates in $D^{\theta}_n$. From the
+%   inductive hypothesis all gates in $H$ have unique labels. Let $C^{\theta}_n
+%   := \op{make-injective-all}(\op{merge-all}(D^{\theta}_n, H))$.
+
+%   Notice that $D^{\theta}_n$ computes the same relation as defined by
+%   $\theta(\vec{x})$ for structures of size $n$. Moreover, since the remaining
+%   two operations preserve the function computed, it follows $C^{\theta}_n$
+%   computes the same relation as defined by $\theta(\vec{x})$ for structures of
+%   size $n$. Furthermore, since $C^{\phi_1}_n$, $C^{\phi_2}_n$ and
+%   $C^{theta'}_n$ are symmetric so is $C^{\theta}_n$. Lastly, notice that all
+%   non-output gates in $D^{\theta}_n$ have unique labels. After the
+%   $\op{merge-all}$ and $\op{make-injective-all}$ operation the output gates
+%   have unique labels, and thus $C^{\theta}_n$ has unique labels. This
+%   construction takes in a natural number $n$ and produces the required circuit
+%   $C^{\theta}_n$. This construction can be computed by an algorithm in time
+%   polynomial in $n$. Thus $\theta(\vec{x})$ is matrix-circuit-translatable.
+
+%   %   We construct the circuit $C'_n = \langle G', \Omega', \Sigma',
+%   %   \Lambda', L' \rangle$ by `inserting' $C^{\phi_1}_n$ and $C^{\phi_2}_n$
+%   %   into
+%   %   $C^{\theta'}_n$. We now construct $C^{\theta}_n$ from $C'_n$ as follows:
+%   %   \begin{itemize}
+%   %   \item For each $i \in \{1,2\}$ and each relational gate $g$ in $C_n$
+%   %     such
+%   %     that $\Sigma'(g) = R_{\phi_i}$ `replace' $g$ with
+%   %     $\Omega_i(\Lambda_i(g))$,
+%   %   \item then, for each syntactic equivalence class $H \subseteq
+%   %     \range(\Omega_1) \uplus \range(Omega_2)$, `merge' $H$, and finally
+%   %   \item run `separate-labels' on the circuit.
+%   %   \end{itemize}
+
+%   %   We note that, since $C^{\phi_1}_n$, $C^{\phi_2}_n$ and $C^{\theta'}_n$
+%   %   have
+%   %   unique labels, the only gates that might not have unique labels in
+%   %   $C^{\theta}_n$ are those whose input gates include gates in the range of
+%   %   $\Omega_1$ or $\Omega_2$. However, all such gates are symmetric and
+%   %   steps
+%   %   (2)
+%   %   and (3) above guarantee that these gates have unique labels. Finally, we
+%   %   note
+%   %   that this algorithm can implemented such that the computation of
+%   %   $C^{\theta}_n$ from $n$ runs in time polynomial in $n$.
+
+%   The approach used above for resolving the conjunctive case can be thought of
+%   as having three steps. First, replacing each sub-formula with a relation
+%   symbol, resulting in a formula of $\FPC$. Second, using the algorithms from
+%   the inductive hypothesis' on sub-formulas, producing appropriate families of
+%   circuits computing each sub-formula, and the known circuit-translation for
+%   formulas of $\FPC$, in order to to produce an appropriate family of circuits
+%   computing the operation on these sub-formulas. Third, using the
+%   concatenation operation to combine these circuit families and two final
+%   operations in order to ensure the family has the required properties.
+
+%   This same approach can be used for to handle many other cases. For
+%   matrix-circuit-translatable $\phi, \phi_1, \phi_2 \in \FPR[\tau]$ similar
+%   constructions can be used to prove that if $\theta(\vec{x}) \in FPR[\tau]$
+%   is equal to $\phi_1(\vec{x}) \lor \phi_2(\vec{x})$, $\neg \phi(\vec{x})$,
+%   $\forall y. \phi (\vec{x}, y)$ or $\exists y. \phi (\vec{x}, y)$ then
+%   $\theta(\vec{x})$ is matrix-circuit-translatable.
+
+%   Suppose $\theta(\vec{x}) = \lfp{V, \vec{y}}{\phi(\vec{x}, \vec{y},
+%   V)}(\vec{x})$ for some matrix-circuit-translatable formula $\phi(\vec{x},
+%   \vec{y}) \in FPR[\tau \uplus \{V\}]$ and $k$-ary relation symbol $V$. Let
+%   $n$ be a natural number. We construct $C^{\theta}_n$ as follows. We have
+%   that we may efficiently compute $C^{\phi}_n$. For each $i \in [n^k]$ we
+%   construct a circuit $C^i = \langle G^i, \Omega^i, \Sigma^i, \Lambda^i, L
+%   \rangle $ as follows. Let $C^0$ be a circuit consisting of exactly $n^k$
+%   gates, such that each gate is a constant $0$ gate and each gate is an output
+%   gate. Let $R$ be a relation symbol in $\tau$. For each $i > 0$ let $C^i :=
+%   \op{concatinate}(C^{\phi}_n, (C^{i-1}_n), (V), R)$ be $C^{\phi}_n$ but with
+%   all relational gates labelled by the symbol $V$ replaced with the constant
+%   $0$. Since $C^1$ and $C^\phi_n$ are symmetric and have unique labels, and
+%   the operation $\op{concatinate}$ preserves the properties of symmetric and
+%   unique labels, it follows by induction that for each $i \geq 1$, $C^i$ is a
+%   symmetric rank-circuit with unique labels. It follows that $C^{\theta}_n :=
+%   C^{n^k}$ is a symmetric rank-circuit and has unique labels. Moreover, since
+%   the least-fixed-point operator must converge in at most $n^k$ steps, this
+%   construction can be implemented so as to run in time polynomial in $n$. The
+%   construction also guarantees that $(C^{\theta}_n)_{n \in \nats}$ computes
+%   the same query as $\theta(\vec{x})$.
+
+%   The result in \cite{} establishes that for every formula $\theta(\vec{x})$
+%   containing number-terms there is a $P$-uniform family of formulas
+%   $(\theta_n(\vec{x}))_{n \in \nats}$ containing counting quantifiers and no
+%   number-terms, and such that for all $n \in \nats$, $\theta(\vec{x})$ and
+%   $\theta_n(\vec{x})$ are equivalent on structures of size $n$.
+
+%   %   Suppose $\theta(\vec{x}) = \lfp{V, \vec{y}}{\phi(\vec{x}, \vec{y},
+%   %   V)}(\vec{x})$ for some matrix-circuit-translatable formula
+%   %   $\phi(\vec{x},
+%   %   \vec{y}) \in FPR[\tau \uplus \{V\}]$ and $\vert y \vert$-ary relation
+%   %   symbol
+%   %   $V$. Let $n$ be a natural number. We now construct $C^{\theta}_n$. We
+%   %   have
+%   %   that we may efficiently compute $C^{\phi}_n$. For each $i \in [n^k]$ we
+%   %   construct a circuit $C^i = \langle G^i, \Omega^i, \Sigma^i, \Lambda^i, L
+%   %   \rangle $ as follows. Let $C^1$ be $C^{\phi}_n$ but with all relational
+%   %   gates
+%   %   labelled by the symbol $V$ replaced with the constant $0$. For each
+%   %   $i>1$ we
+%   %   construct $C^{i}$ by `gluing' $C^{i-1}$ into $C^\phi_n$, producing
+%   %   $C^i$.
+%   %   Set
+%   %   $C^{\theta}_n := C^{n^k}$. Since $C^1$ and $C^\phi_n$ are symmetric and
+%   %   have
+%   %   unique labels, by induction for each $i > 1$ $C^i$ is symmetric and has
+%   %   unique
+%   %   labels. It follows that $C^{\theta}_n$ is symmetric and has unique
+%   %   labels.
+%   %   Moreover, since the least-fixed-point operator must converge in at most
+%   %   $n^k$
+%   %   steps, this algorithm runs in time polynomial in $n$ and the family
+%   %   $(C^{\theta}_n)_{n \in \nats}$ computes the same query as
+%   %   $\theta(\vec{x})$.
+
+%   %   The result in \cite{} establishes that for every formula
+%   %   $\theta(\vec{x})$
+%   %   containing number-terms there is a $P$-uniform family of formulas
+%   %   $(\theta_n(\vec{x}))_{n \in \nats}$ containing counting quantifiers and
+%   %   no
+%   %   number-terms, and such that for all $n \in \nats$, $\theta(\vec{x})$ and
+%   %   $\theta_n(\vec{x})$ are equivalent on structures of size $n$.
+
+%   %   gives for each $\theta (\vec{x}) \in FPC[\tau]$ a $P$-uniform family of
+%   %   formulas $(\theta_n)_{n \in \nats}$ such that $\theta_n(\vec{x})$ is in
+%   %   the
+%   %   extension of fixed-point logic with counting quantifiers and is
+%   %   equivalent
+%   %   to
+%   %   $\theta(\vec{x})$ on structures of size $n$. Similarly, it can be shown
+%   %   that
+%   %   for $\theta (\vec{x}) \in FPR[\tau]$ there exists an algorithm that
+%   %   takes as
+%   %   input a natural number $n$ and outputs a formula $\theta_n(\vec{x})$
+%   %   with
+%   %   counting quantifiers and no number terms which is equivalent to
+%   %   $\theta(\vec{x})$ for structures of size $n$ and does not contain any
+%   %   number
+%   %   terms. Moreover, this algorithm runs in time polynomial in $n$.
+
+%   Thus, in order to handle the number-term case, it is sufficient to show that
+%   if $\phi(\vec{x}) \in \FPR[\tau]$ is circuit-translatable then
+%   $\theta(\vec{x}) := C^{k}y. \phi(\vec{x}, y)$ is
+%   matrix-circuit-translatable. A similar construction as for the universal and
+%   existential quantifier gives the required algorithm.
+
+%   The result in \cite{} establishes that for every formula $\theta(\vec{x})
+%   \in \FPR[\tau]$ containing rank operators, there exists an algorithm that
+%   takes as input a natural number $n$ and outputs a formula
+%   $\theta_n(\vec{x})$ with rank quantifiers and no rank operators such that
+%   $\theta(\vec{x})$ and $\theta_n(\vec{x})$ are equivalent on structures of
+%   size $n$. It is thus sufficient to prove that, for
+%   matrix-circuit-translatable $\phi(\vec{z}, \vec{y}, \vec{x}) \in \FPR[\tau]$
+%   is, a prime $p$, and a natural number $r$, $\theta(\vec{x}) := \rank^{\leq
+%   r}_p \vec{z} \vec{y}. \phi(\vec{z}, \vec{y}, \vec{x})$ is
+%   circuit-translatable. We define an algorithm that takes as input a natural
+%   number $n$ outputs the required circuit $C^{\theta}_n$.
+
+%   From the inductive hypothesis we may efficiently compute $C^{\phi}_n =
+%   \langle G^{\phi}, \Omega^{\phi}, \Sigma^{\phi}, \Lambda^{\phi}, L^{\phi}
+%   \rangle$. Let $k:= \vert \vec{x} \vert$, $k_1 : = \vert \vec{z} \vert$ and
+%   $k_2 := \vert \vec{y} \vert$. Let $R_\phi$ be a $(k_1 + k_2 + k)$-ary
+%   relation symbol not in $\tau$. Let $\theta'(\vec{x}) = \rank^{\leq r}_r :=
+%   \vec{z}, \vec{y}. \phi (\vec{z}, \vec{y}, \vec{x})$. We now define a
+%   $(\mathbb{B}_{\rank}, \{ R_{\phi} \})$-circuit $C^{\theta'}_n:= \langle
+%   G^{\theta'}, \Omega^{\theta'}, \Sigma^{\theta'}, \Lambda^{\theta'},
+%   L^{\theta'}\rangle$ as follows. Let $G_1 := \{g_{\rank, \vec{c}} : \vec{c}
+%   \in [n]^k\}$ and $G_2 : = \{ g_{R_{\phi}, \vec{a}, \vec{b}, \vec{c}} :
+%   \vec{a} \in [n]^{k_1}, \vec{b} \in [n]^{k_2}, \vec{c} \in [n]^{k}\}$.
+
+%   \begin{itemize}
+%     \setlength\itemsep{0mm}
+%   \item Let $G^{\theta'} := G_1 \uplus G_2$,
+%   \item $\Omega^{\theta'}$ be an injection from $[n]^k$ to $G'$ defined by
+%     $\Omega^{\theta'}(\vec{c}) = g_{\rank, \vec{c}}$,
+
+%   \item $\Sigma^{\theta'} (g) := rank^r_p$ if $g \in G_1$ and
+%     $\Sigma^{\theta'}(g) = R_\phi$ if $g \in G_2$,
+%   \item For each $(\vec{a}, \vec{b}, \vec{c}) \in [n]^{k_1 +k_2 + k}$ let
+%     $\Lambda^{\theta'} (\vec{a}, \vec{b}, \vec{c}) := g_{R_{\phi}, \vec{a},
+%     \vec{b}, \vec{c}}$, and
+
+%   \item For each gate $g_{\rank, \vec{a}} \in G_1$ let $L(g_{\rank, \vec{a}}):
+%     [n]^{k_1} \times [n]^{k_2} \rightarrow G^{\theta'}$ be defined by
+%     $L(g_{\rank, \vec{c}})(\vec{a}, \vec{b}) := g_{R_\phi, \vec{a}, \vec{b},
+%     \vec{c}}$ for each $\vec{a} \in [n]^{k_1}$ and $\vec{b} \in [n]^{k_2}$.
+%   \end{itemize}
+
+%   It is easy to see that both $C^{\theta'}_n$ (and $C^{\phi}_n$) are symmetric
+%   rank-circuits with unique labels. Let $R$ be a relation symbol in $\tau$.
+%   Let $D^{\theta}_n := \op{compose}(C^{\theta'}_n, (C^{\phi}_n), (R_\phi),
+%   R)$. Let $H$ consist of all non-output gates in $D^{\theta}_n$. From the
+%   inductive hypothesis all gates in $H$ have unique labels. Let $C^{\theta}_n
+%   := \op{make-injective-all}(\op{merge-all}(D^{\theta}_n, H))$.
+
+%   Since $C^{\theta'}_n$ and $C^{\phi}_n$ are symmetric, have unique labels,
+%   and the input tuples of relations and circuits are singletons, it follows
+%   that $D^{\theta}_n$ is a symmetric rank-circuit with unique labels. It can
+%   be shown that the construction of $C^{\theta}_n$ from the natural number $n$
+%   can be implemented as an algorithm running in time polynomial in $n$. The
+%   construction ensures that the circuit family $(C^{\theta}_n)_{n \in \nats}$
+%   computes the same query as the one defined by $\theta(\vec{x})$.
+
+%   It remains only to note that any atomic formula of $\FPR[\tau]$ is trivially
+%   matrix-circuit-translatable. The result thus follows.
+% \end{proof}
 
@@
 
-% \item $\Sigma' (g) := rk^r_p$ if $g \in G_1'$ and $\Sigma'(g) = R$ if $g \in
+% \item $\Sigma' (g) := rank^r_p$ if $g \in G_1'$ and $\Sigma'(g) = R$ if $g \in
 %   G_2'$,
 % \item For each $(\vec{a}, \vec{b}, \vec{c}) \in [n]^{k_1 +k_2 + k}$ let
-%   $\Lambda' (\vec{a}, \vec{b}, \vec{c}) := g_{R, \vec{a}, \vec{b},
-%   \vec{c}}$,
+%   $\Lambda' (\vec{a}, \vec{b}, \vec{c}) := g_{R, \vec{a}, \vec{b}, \vec{c}}$,
 %   and
@@
 % It remains to show that for any $k \in \nats$ and formula $\phi \in
-% \FPR[\tau]$ such that $\phi$ formula of the form $\theta (\vec{z}): = [rk
+% \FPR[\tau]$ such that $\phi$ formula of the form $\theta (\vec{z}): = [rank
 % (\vec{x}, \vec {\nu} \leq \vec{t}, \vec{y}\vec{\mu} \leq \vec{s}, \pi \leq r).
@@
 %   Let $\tau$ be a relational vocabulary and let $\phi(\vec{x})$ be a formula
-%   of $\FPR[\tau]$. There is an algorithm that takes as input a natural
-%   number $n$ and outputs a formula $\phi_n$ such that $\phi_n$ contains no
-%   rank operators or counting terms and for any $\tau$-structure
-%   $\mathcal{A}$ of size $n$ and $\vert \vec{x} \vert$-tuple of elements
-%   $\vec{a}$ from the universe of $\mathcal{A}$, $\mathcal{A}\models
-%   \phi[\vec{a}]$ if, and only if, $\mathcal{A}\models \phi_n[\vec{a}]$.
-%   Moreover, this algorithm runs in time polynomial in $n$.
+%   of $\FPR[\tau]$. There is an algorithm that takes as input a natural number
+%   $n$ and outputs a formula $\phi_n$ such that $\phi_n$ contains no rank
+%   operators or counting terms and for any $\tau$-structure $\mathcal{A}$ of
+%   size $n$ and $\vert \vec{x} \vert$-tuple of elements $\vec{a}$ from the
+%   universe of $\mathcal{A}$, $\mathcal{A}\models \phi[\vec{a}]$ if, and only
+%   if, $\mathcal{A}\models \phi_n[\vec{a}]$. Moreover, this algorithm runs in
+%   time polynomial in $n$.
 % \end{lem}
@@
 %   Let $\tau$ be a relational vocabulary and let $\phi$ be a formula of
-%   $\FPR[\tau]$. There is an algorithm that takes as input a natural number
-%   $n$ and outputs a symmetric matrix-circuit $C_n$. This algorithm runs in
-%   time polynomial in $n$. Moreover, the query computed by the circuit family
-%   $(C_n)_{n \in \nats}$ and the query defined by the formula $\phi$ are
-%   equal.
+%   $\FPR[\tau]$. There is an algorithm that takes as input a natural number $n$
+%   and outputs a symmetric matrix-circuit $C_n$. This algorithm runs in time
+%   polynomial in $n$. Moreover, the query computed by the circuit family
+%   $(C_n)_{n \in \nats}$ and the query defined by the formula $\phi$ are equal.
 % \end{thm}

### 2017-12-07 sections/symmetric-circuits.tex
dec 7

@@
 its $m$ inputs. This unstated assumption is pervasive in circuit complexity. In
-particular, the standard Boolean basis of AND, OR and NOT gates as well as bases
+particular, the standard Boolean basis of $\AND$, $\OR$ and $\NOT$ gates as well as bases
 with majority or threshold gates only contain symmetric functions.
@@
 % AD - rewrote the paragraph to reduce the use of subscripts and superscripts.
-Let $\tau = (R, S, \nu)$ be a many-sorted signature.
+Let $\tau = (R, S, \nu)$ be a many-sorted vocabulary.
 % with $R = \{R_1 \ldots, R_t\}$, $S = \{s_1, \ldots , s_p\}$, and $\nu(R_i) =
@@
 Let $D := \biguplus_{s \in S} D_{s} = \{(s,d) : d \in D_s\}$, be a disjoint
-union of non-empty sets, indexed by $S$, i.e.\ $D$ is potentially the universe
-of a $\tau$-structure. We call $D$ a \emph{$\tau$-sorted set}. For each $P \in
-R$, let $P^D$ denote the trivial relation over the many-sorted universe $D$,
-i.e.\ $P^D := D_{a_1} \times \ldots \times D_{a_{r}}$, where $\nu(P) = (a_1,
-\ldots , a_{r)})$. Let the \emph{index defined by the pair $(\tau, D)$} be the
-set $\biguplus_{P\in R} P^{D}$. We use this set to index the input to a Boolean
-function, as such we abuse notation and denote the index defined by $(\tau, D)$
-by $\ind(\tau, D)$. We call $\tau$ the vocabulary and $D$ the universe of
-$\ind(\tau, D)$.
-
+union of non-empty sets, indexed by $S$. We call $D$ a \emph{$\tau$-universe}.
+For each $P \in R$, let $P^D$ denote the trivial relation over the many-sorted
+universe $D$, i.e.\ $P^D := D_{a_1} \times \ldots \times D_{a_{r}}$, where
+$\nu(P) = (a_1, \ldots , a_{r)})$. Let the \emph{index defined by the pair
+  $(\tau, D)$} be the set $\biguplus_{P\in R} P^{D}$. We use this set to index
+the input to a Boolean function, as such we abuse notation and denote the index
+defined by $(\tau, D)$ by $\ind(\tau, D)$. We call $\tau$ the vocabulary and $D$
+the universe of $\ind(\tau, D)$.
+
+% GW: move sorted permutations into the background section
 For the remainder of this subsection we fix a vocabulary $\tau$ and a
 many-sorted set $D=\biguplus_{s \in S} D_{s}$ and let $X := \ind (\tau, D)$. Let
-$G \leq \sym_{X}$, and let $\sortsym(D) := \prod_{s \in S} \sym_{D_{s}}$. We
-call the elements of $\sortsym(D)$ \emph{sorted permutations}. Note that
+$G \leq \sym_{X}$, and let $\sortsym_D := \prod_{s \in S} \sym_{D_{s}}$. We
+call the elements of $\sortsym_D$ \emph{sorted permutations}. Note that
 $\sortsym(D)$ can be identified with a subgroup of $\sym_X$. There is an obvious
@@
 are \emph{isomorphism-equivalent} if they are $\sortsym(D)$-equivalent. We are
-interested in the case where $H = \{0,1\}$, i.e.\ $f : X \rightarrow \{0,1\}$.
-In this case $f$ defines for each relation $R^D_i$ a subset of that relation,
-and thus determines a $\tau$-structure over the universe $D$. We note that two
-functions $f, g: X \rightarrow \{0,1\}$ are isomorphism-equivalent if, and only
-if, the two $\tau$-structures they determine are isomorphic.
+often interested in the case where $H = \{0,1\}$, i.e.\ $f : X \rightarrow
+\{0,1\}$. In this case $f$ defines for each relation $R^D_i$ a subset of that
+relation, and thus determines a $\tau$-structure over the universe $D$. We note
+that two functions $f, g: X \rightarrow \{0,1\}$ are isomorphism-equivalent if,
+and only if, the two $\tau$-structures they determine are isomorphic.
 
@@
 condition. Let $F$ be a $(\tau, D)$-structured function. We say $F$ is
-\emph{$G$-invariant} if it is constant on $G$-equivalent input vectors, i.e.\
-for all $G$-equivalent $\vec{x}, \vec{y} \in \{0,1\}^{X}$, $F(\vec{x}) =
+\emph{$G$-invariant} if it is constant on $G$-equivalent input vectors, i.e. for
+all $G$-equivalent $\vec{x}, \vec{y} \in \{0,1\}^{X}$, $F(\vec{x}) =
 F(\vec{y})$. We say $F$ is \emph{isomorphism-invariant} if it is $\sortsym

### 2017-12-16 sections/translating-formulas-to-cicuits.tex
editing process

@@
   \ref{prop:unique-labels-syntactic-equiv}, we may compute the syntactic
-  equvilence relation on this set of gates efficiently. Thus it is easy to see
+  equivalence relation on this set of gates efficiently. Thus it is easy to see
   that the above algorithm can be implemented so as to run in polynomial time.
@@
 \begin{lem}
+  If $G \subseteq \sym_n$
   Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit with unique labels of size $n$ and
@@
 
+% \begin{lem}
+%   Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit with unique labels of size $n$ and
+%   $\sigma \in \sym_n$. There is an algorithm takes as input a circuit $C_n$ and
+%   $\sigma \in \sym_n$ and outputs for each gate $g$ its image under the unique
+%   automorphism extending $\sigma$ (if it exists). This algorithm runs in time
+%   polynomial in the combined size of the input circuit and the encoding of the
+%   permutation.
+%   \label{lem:compute-automorphisms}
+% \end{lem}
+% \begin{proof}
+%   Suppose $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$. We build up the
+%   mapping $\pi$ extending $\sigma$ recursively. If at some point in the
+%   recursive construction we arrive at a point where no mapping for $g$ can be
+%   found we halt at that point and return that no automorphism exists.
+
+%   Let $h$ be any gate in the circuit. Suppose $h$ is an input gate. If $h$ is a
+%   constant gate then let $\pi (h) = h'$. If $h$ is a relational gate such that
+%   $R := \Sigma(h)$ and check if there exists $h'$ such that $\Sigma (h') = R$
+%   and $\sigma \Lambda_R(h) = \Lambda_R(h')$ and, if $h$ is an output gate then
+%   $h'$ is an output gate such that $\sigma Omega^{-1}(h) = \Omega^{-1}(h')$. If
+%   such a $h'$ does not exist halt and output that there is no automorphism
+%   extending $\sigma$. We have from Lemma \ref{} that if such an $h'$ exists it
+%   must be unique, and we set $\pi(h) = h'$.
+
+%   Let $h$ be an internal gate in the circuit and assume we have defined $\pi
+%   (g)$ for every gate $g$ of height less than $h$. Let $h'$ be a gate in the
+%   circuit such that $\Sigma(h) = \Sigma (h')$, $\pi L(h)$ is isomorphism
+%   equivalent to $L(h')$ and, if $h$ is an output gate then $h'$ is an output
+%   gate such that $\sigma \Omega^{-1}(h) = \Omega^{-1}(h')$. Since $C_n$ has
+%   unique labels we have that $\pi L(h)$ is isomorphism equivalent to $L(h')$ if,
+%   and only if, $L(h')^{-1}\pi L(h)$ acts like an isomorphism. This can be
+%   determined easily. If no such $h'$ exists halt and output that there is no
+%   automorphism extending $\sigma$. We have from Lemma \ref{} that if $C_n$ has
+%   unique labels then there is at most one such $h'$.
+
+%   This recursive approach can be implemented as an algorithm that runs in time
+%   polynomial in the combined size of the inputs and outputs the required
+%   automorphism if it exists.
+% \end{proof}
+
 This result uses a proof very similar to the one for a similar result proved by
-Anderson and Dawar~\cite{Anderson17D}.
+Anderson and Dawar~\cite{AndersonD17}.
 
 \begin{lem}
-  There is an algorithm that takes as input a circuit $C_n$ with unique labels
-  and decides if $C_n$ is symmetric. If $C_n$ is symmetric outputs the orbits
-  and coarsest supporting partitions of every gate. Moreover, this algorithm
-  runs in time polynomial in the size of the input circuit.
-  \label{lem:computing support}
+\label{lem:computing-support}
+  Let $G \leq \sym_n$ be a subgroup and be $X$ a finite set.
+Suppose there there is an algorithm that $(g, x) \mapsto g \cdot x$ is computable in time polynomial in $\vert X \vert + n$.
+Suppose  $s \subset [n]$ be a support of $g$ There is an algorithm that takes in $x \in X$ and outputs $\orb_G (x)$ and $\SP_G(x)$.
+This algorithm runs in time polynomial in $\vert X \vert + n$.
 \end{lem}
-
 \begin{proof}
-  Suppose $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$. Let $(u, v) \in
-  \sym_n$ be a transposition. We may use Lemma \ref{lem:compute-automorphisms}
-  to determine the unique automorphism $\pi_{(u,v)}$ extending $(u, v)$. It is
-  easy to see that, since the set of transpositions generate $\sym_n$, for all
-  $(u,v) \in \sym_n$ $\pi_{(u,v)}$ the automorphism $\pi_{(u,v)}$ exists if, and
-  only if, $C_n$ is symmetric. We note that there are ${n}\choose{2}$
-  transpositions. It follows that we may check in polynomial time if $C_n$ is
-  symmetric. If $C_n$ is not symmetric we output that it is not symmetric and
-  halt.
-
-  Suppose then that $C_n$ is symmetric. For transposition $(u, v) \in \sym_n$,
-  let $\mathcal{P}_{(u,v)} := \{\{u,v\}\}\bigcup_{w \in [n] \setminus
-    \{u,v\}}\{\{w\}\}$ be a partition of $[n]$. We have that $\pi_{(u,v)}$ fixes
-  $g$ if, and only if, $\mathcal{P}_{(u,v)}$ supports $g$. Since we can
-  efficiently check if $\pi_{(u,v)}$ fixes $g$ it follows that we can
-  effeciently check if $\mathcal{P}_{(u,v)}$ supports $g$. Let $\mathcal{P}$ be
-  the result of combining the set consisting of those partitions
-  $\mathcal{P}_{(u,v)}$ that support $g$ using $\mathcal{E}$. From Proposition
-  \ref{prop:combining-supporting-patitions} we have that $\mathcal{P}$ supports
-  $g$. Suppose that $\mathcal{P}$ is not the coarsest supporting partition of
-  $g$. Then there exists a partition $\mathcal{P}'$ supporting $g$ such
-  $\mathcal{P}' \preceq P$ and $\mathcal{P}' \neq \mathcal{P}$. But then there
-  exists $P \in \mathcal{P}$ and $P' \in \mathcal{P}'$ such that $P \subsetneq
-  P'$. But then there exists $a , b \in P'$ such that $a \not\in P$. It follows
-  that the transposition $(a,b)$ fixes $\mathcal{P}'$ and so $\pi_{(a,b)}$ fixes
-  $g$, but then, $\mathcal{P}_{(a,b)}$ supports $g$ and so, from the
-  construction of $\mathcal{P}$, $\mathcal{P}$ is fixed by $(a,b)$. But
-  $\mathcal{P}$ is not fixed by $(a,b)$, so we have a contradiction. We thus
-  have that $\mathcal{P}$ is the coarsest supporting partition of $g$.
-
-  It remains to compute the orbit of a gate $g$. Let $S_0 := \{g\}$ and for each
-  $i \geq 0$ let $S_{i+1} := S_i \bigcup_{(u,v) \in \sym_n} \pi_{(u,v)}S_i$. Let
-  $S$ be the least fixed point. It is easy to see that $S \subseteq \orb(g)$ as
-  every gate in $S$ is equal to the action of some sequence of automorphisms
-  (extending transpositions) acting on $g$. Moreover, since the set of all
-  transpositions generates $\sym_n$, it follows that $\orb(g) \subseteq S$ and
-  so $\orb(g) = S$.
+  Let $(u, v) \in \sym([n] \setminus \consp(G))$ be a transposition.
+We note that $(u,v) \in \stab(\consp(G))$ and there are ${n - \vert \consp(G) \vert}\choose{2}$ (and so polynomially) many such transpositions.
+For a transposition $(u, v) \in \sym ([n] \setminus \consp(G))$, let
+  \begin{align*}
+  \mathcal{P}_{(u,v)} := \{ \{u,v\}\} \bigcup_{w \in [n] \setminus \{ u,v \}} \{ \{ w \} \}
+  \end{align*}
+   be a partition of $[n]$.
+Then $\mathcal{P}_{(u,v)}$ supports $\stab_{\consp(G)}(x)$ if, and only if, $(u,v) \cdot x = x$.
+Then let $\mathcal{P}$ be the partition formed by applying $\mathcal{E}$ to all $\mathcal{P}_{(u,v)}$ such that $(u,v) \cdot x = x$ (which can be checked in polynomial time).
+From Proposition~\ref{prop:combining-supporting-patitions} we have that $\mathcal{P}$ supports $\stab_{\consp(G)}(x)$.
+Suppose that $\mathcal{P}$ is not the coarsest supporting partition of $\stab_{\consp(G)}(x)$.
+Then there exists a partition $\mathcal{P}'$ supporting $\stab_{\consp(G)}(x)$ such that $\mathcal{P}' \preceq P$ and $\mathcal{P}' \neq \mathcal{P}$.
+And so there exists $P \in \mathcal{P}$ and $P' \in \mathcal{P}'$ such that $P \subsetneq P'$.
+But then there exists $a , b \in P'$ such that $a \not\in P$.
+Note that It follows that the transposition $(a,b)$ fixes $\mathcal{P}'$ and so $(a,b) \in \stab_{\consp(G)}(x)$ (and so $a, b \not\in [n] \setminus \consp(G)$).
+But then $\mathcal{P}_{(a,b)}$ supports $\stab_{\consp(G)}(x)$ and so, from the construction of $\mathcal{P}$, $\mathcal{P}$ is fixed by $(a,b)$.
+But we selected $a$ and $b$ such that $\mathcal{P}$ is not fixed by $(a,b)$, and so we have a contradiction.
+We thus have that $\mathcal{P}$ is the coarsest supporting partition of $\stab_{\consp(G)}(x)$.
+
+  It remains to compute $\orb_{\consp(G)}(x)$. Let $S_0 := \{g\}$ and for each
+  $i \geq 0$ let $S_{i+1} := S_i \bigcup_{(u,v) \in \sym_{[n] \setminus \consp(G)}} (u,v)\cdot S_i$.
+Let  $S$ be the least fixed point.
+It is easy to see that $S \subseteq \orb_{\consp(G)}(x)$ as every gate in $S$ is equal to the action of some sequence of automorphisms (extending transpositions) acting on $g$.
+Moreover, since the set of all transpositions generates $\sym_n$, it follows that $\orb_{\consp(G)}(x) \subseteq S$ and so $\orb_{\consp(G)}(x) = S$.
 
@@
   in the size of the input circuit.
+\end{proof}
+
+\begin{lem}
+  There is an algorithm that takes in a symmetric circuit $C$ of order $n$ with unique labels and outputs for each gate $g$ in $C$ and $a \in \universe{g}$, $\orb_g (a)$ and $\SP_g (a)$.
+\end{lem}
+\begin{proof}
+  Let $(u,v) \in \sym_n$ be a transposition.
+We can check if $(u,v) \in \stab(g)$ using Lemma~\ref{lem:compute-automorphisms}.
+Then $(u,v)$ acts like an isomorphism at $g$, and hence $(u,v) \cdot a = L(g)^{-1}((\sigma L(g)(\vec{x}))) (i)$, where $\vec{x} \in \ind(g)$ such that $\vec{x} (i) = a$ for some $i \in [\vert \vec{x} \vert]$.
+Thus, since Lemma~\ref{lem:compute-automorphisms} gives us that that we can compute $\sigma L(g)(\vec{x})$ in polynomial time, we can compute $(u,v) \cdot a$ in polynomial-time.
+
+  We note that
+
+  and hence we can compute $\sigma \cdot a$ effeciently.  and hence compute $\orb_g(a) = \{ \sigma \cdot a : \sigma \in \stab(g)\}$.
+
 \end{proof}

### 2018-01-15 sections/background.tex
dec 7
January 15 Update

@@
 
+\subsection{Group Theory}
+--Include details on how to define a groupa action. Particularly a group action
+as a homomorphism from $G$ to $\sym_X$
+
+Let $X$ be a set and $G$ be a group acting on $X$. We let the stabiliser of $S
+\subseteq X$ for $G$ be defined as $\stab_G(S) := \{ \sigma \in G : \forall x
+\in S \, \sigma \cdot x = x \}$ and the orbit of $S$ for $G$ to be defined as
+$\orb_G (S) := \{ T \subseteq X : \exists \sigma \in G \, \sigma \cdot S = T
+\}$. If $S = \{x\}$, for some $x \in X$, we write $\stab_G (x)$ and $\orb_G(x)$
+in order to abbreviate $\stab_G(\{x\})$ and $\orb_G(\{x\})$, respectively. In
+the event that the choice of $G$ is obvious from context we omit the subscript.
+
+We are often interested in the case where $G$ is the symmetric group $\sym_n$ on
+$n$ elements. In this case we write $\stab_n(x)$ and $\orb_n(x)$ in order to
+abbreviate $\stab_{\sym_n}(x)$ and $\orb_{\sym_n}(x)$, respectively.
+
+We are also often interested in the case where $G$ is the stabiliser group for
+set of elements, or single element, from $X$. For $S, T \subseteq X$, we write
+$\stab_{S}(T)$ and $\orb_{S}(T)$ in order to abbreviate $\stab_{\stab(S)}(T)$
+and $\orb_{\stab(S)}(T)$.
+
 \subsection{Circuits}
@@
 
-Let $f : X \rightarrow Y$ be a function and $\sim$ be an equivalence relation on Y.
-We define $f/{\sim} : X \rightarrow Y/{\sim}$ by $f(x) = [f(x)]_{\sim}$.
-We call this the quotient of the function by $\sim$.
-For any two sets $X, Y$ we let $X^{\underline{Y}}$ denote the set of all injective functions from $Y$ to $X$.
+Let $f : X \rightarrow Y$ be a function and $\sim$ be an equivalence relation on
+Y. We define $f/{\sim} : X \rightarrow Y/{\sim}$ by $f(x) = [f(x)]_{\sim}$. We
+call this the quotient of the function by $\sim$. For any two sets $X, Y$ we let
+$X^{\underline{Y}}$ denote the set of all injective functions from $Y$ to $X$.
 

### 2018-01-15 sections/symmetric-circuits.tex
January 15 Update

@@
 % AD - rewrote the paragraph to reduce the use of subscripts and superscripts.
-Let $\tau = (R, S, \nu)$ be a many-sorted vocabulary.
-% with $R = \{R_1 \ldots, R_t\}$, $S = \{s_1, \ldots , s_p\}$, and $\nu(R_i) =
-% (a^i_1, \ldots , a^i_{r_i)})$, where $r_i = \arty(R_i)$ and $a^i_q \in S$ for
-% all $q \in [r_i]$.
-Let $D := \biguplus_{s \in S} D_{s} = \{(s,d) : d \in D_s\}$, be a disjoint
-union of non-empty sets, indexed by $S$. We call $D$ a \emph{$\tau$-universe}.
-For each $P \in R$, let $P^D$ denote the trivial relation over the many-sorted
-universe $D$, i.e.\ $P^D := D_{a_1} \times \ldots \times D_{a_{r}}$, where
-$\nu(P) = (a_1, \ldots , a_{r)})$. Let the \emph{index defined by the pair
-  $(\tau, D)$} be the set $\biguplus_{P\in R} P^{D}$. We use this set to index
-the input to a Boolean function, as such we abuse notation and denote the index
-defined by $(\tau, D)$ by $\ind(\tau, D)$. We call $\tau$ the vocabulary and $D$
-the universe of $\ind(\tau, D)$.
+Let $\tau = (R, S, \nu)$ be a many-sorted vocabulary. Let $D := \biguplus_{s \in
+  S} D_{s} = \{(s,d) : d \in D_s\}$, be a disjoint union of non-empty sets,
+indexed by $S$. For $R_i \in R$ let $R^D_i$ denote the trivial relation over the
+many-sorted universe $D$, i.e.\ $R^D_i := D_{a_1} \times \ldots \times
+D_{a_{r}}$, where $\nu(R_i) = (a_1, \ldots , a_{r)})$. There is an obvious
+interpretation of $\tau$ over $D$ given by assigning each sort symbol in $\tau$
+in the obvious manner and each relation symbol in $\tau$ to the trivial relation
+over $D$. We call this \emph{the structure defined by $(\tau, D)$}, and denote
+it by $\str(\tau, D)$.
+
+The idea is to use the tuples in the relations of this structure as an index
+set, and with the automorphisms of this structure defining a group action. Let
+the \emph{index defined by the pair $(\tau, D)$} be the set $\biguplus_{R_i\in
+  R} R^{D}_i$. We often use this set to index the input to a Boolean function,
+as such we abuse notation and denote the index defined by $(\tau, D)$ by
+$\ind(\tau, D)$, and call $\tau$ the vocabulary and $D$ the universe of
+$\ind(\tau, D)$.
 
@@
 For the remainder of this subsection we fix a vocabulary $\tau$ and a
-many-sorted set $D=\biguplus_{s \in S} D_{s}$ and let $X := \ind (\tau, D)$. Let
-$G \leq \sym_{X}$, and let $\sortsym_D := \prod_{s \in S} \sym_{D_{s}}$. We
-call the elements of $\sortsym_D$ \emph{sorted permutations}. Note that
-$\sortsym(D)$ can be identified with a subgroup of $\sym_X$. There is an obvious
-action of $G$ on $X$. We can extend this to an action on the set of functions of
-the form $f: X \rightarrow X$, for any set $H$, defined by $\sigma \cdot f(x) =
+many-sorted set $D := \biguplus_{s \in S} D_{s}$, and let $X := \ind (\tau, D)$
+and $G \leq \sym_{X}$. There is an obvious action of $G$ on $X$. There is also
+an obvious action of the automorphism group $\str(\tau, D)$ on $X$ (with
+permutations in $\str(\tau, D)$ acting element-wise on tuples in $X$). We denote
+this group by $\aut(\tau, D)$, and identify it with the subgroup of $\sym_X$
+that acts equivalently on $X$.
+
+We can extend the action of $G$ on $X$ to an action on the set of functions of
+the form $f: X \rightarrow H$, for any set $H$, defined by $\sigma \cdot f(x) :=
 f(\sigma \cdot x)$ for all $x \in X$, $\sigma \in G$.
+
+% and let $\sortsym_D := \prod_{s \in S} \sym_{D_{s}}$. We call the elements of
+% $\sortsym_D$ \emph{sorted permutations}. Note that $\sortsym(D)$ can be
+% identified with a subgroup of $\sym_X$.
 
@@
 % indexes $H$ by $\mathcal{D}$}.
-We say that two functions $f, g : X \rightarrow H$ are \emph{$G$-equivalent} if
-there exists $\sigma \in G$ such that $f = \sigma \cdot g$. We say $f$ and $g$
-are \emph{isomorphism-equivalent} if they are $\sortsym(D)$-equivalent. We are
-often interested in the case where $H = \{0,1\}$, i.e.\ $f : X \rightarrow
-\{0,1\}$. In this case $f$ defines for each relation $R^D_i$ a subset of that
-relation, and thus determines a $\tau$-structure over the universe $D$. We note
-that two functions $f, g: X \rightarrow \{0,1\}$ are isomorphism-equivalent if,
-and only if, the two $\tau$-structures they determine are isomorphic.
+
+We say that two functions $f: \ind(\tau, D) \rightarrow H$ and $g: \ind(\tau',
+D') \rightarrow H$ are \emph{isomorphism-equivalent} if there exists an
+isomorphism $\pi :\str(\tau, D) \rightarrow \str(\tau', D')$ such that $f (x) =
+g (\pi (x))$ for all $x \in \str(\tau, D)$. It is easy to see that
+isomorphism-equivalence is an equivalence relation.
+
+We are often interested in the case where $X = \ind(\tau, D) = \ind(\tau', D')$.
+We say that $f, g X \rightarrow H$ are \emph{$G$-equivalent} if there exists
+$\sigma \in G$ such that $f = \sigma \cdot g$. We note that in this case $f$ and
+$g$ are \emph{isomorphism-equivalent} if, and only if, they are $\aut(\tau,
+G)$-equivalent.
+
+In this paper we will often let the co-domain $H$ be the binary symbols
+$\{0,1\}$, and so consider functions of the form $f : X \rightarrow \{0,1\}$. In
+this case we may think of $f$ as defining for each relation $R^D_i$ a subset of
+that relation, and thus determining a $\tau$-structure over the universe $D$. We
+note that two functions $f, g: X \rightarrow \{0,1\}$ are isomorphism-equivalent
+if, and only if, the two $\tau$-structures they determine are isomorphic.
 
@@
 to a Boolean function and associating with that function an appropriate symmetry
-condition. Let $F$ be a $(\tau, D)$-structured function. We say $F$ is
-\emph{$G$-invariant} if it is constant on $G$-equivalent input vectors, i.e. for
-all $G$-equivalent $\vec{x}, \vec{y} \in \{0,1\}^{X}$, $F(\vec{x}) =
-F(\vec{y})$. We say $F$ is \emph{isomorphism-invariant} if it is $\sortsym
-(D)$-invariant. Note that a structured function with vocabulary $\tau$ is
-isomorphism-invariant if, and only if, it decides a property of
+condition, or notion of equivalence. Let $F$ be a $(\tau, D)$-structured
+function. We say $F$ is \emph{$G$-invariant} if it is constant on $G$-equivalent
+input vectors, i.e. for all $G$-equivalent $\vec{x}, \vec{y} \in \{0,1\}^{X}$,
+$F(\vec{x}) = F(\vec{y})$. We say $F$ is \emph{isomorphism-invariant} if it is
+$\aut(\tau, D)$-invariant. Note that a structured function with vocabulary
+$\tau$ is isomorphism-invariant if, and only if, it decides a property of
 $\tau$-structures.
@@
 Let $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
-\tau)$-circuit. The $n$ is used to indicates that $C_n$ accepts structures of
+\rho)$-circuit. The $n$ is used to indicates that $C_n$ accepts structures of
 size $n$. For a gate $g \in C_n$, we define the \emph{index} of $g$, denoted by
@@
 $W(h,g)$ if, and only if, $h \in \range(L(g))$. For each $g \in G$ we let
-$W(\cdot, g) := \{h \in G : W(h,g)\}$, and let $W(g, \cdot) := \{h \in G :
-W(g,h)\}$. We call $W(\cdot, g)$ the \emph{children} of $g$ and $W(g, \cdot)$
-the \emph{parents} of $g$. We also abbreviate $W(g, \cdot)$ by $H_g$. We let the
-vocabulary and universe of $g$ be the vocabulary and universe of $\Sigma(g)$,
-respectively.
+$W(\cdot, g) := \{h \in G : W(h,g)\}$ and $W(g, \cdot) := \{h \in G : W(g,h)\}$.
+We call the elements of $W(\cdot, g)$ the \emph{children} of $g$ and the
+elements of $W(g, \cdot)$ the \emph{parents} of $g$. We also abbreviate $W(g,
+\cdot)$ by $H_g$.
+
+We let the vocabulary and universe of $g$ be the vocabulary and universe of
+$\Sigma(g)$, respectively, and denote the vocabulary of $g$ by $\vocab{g}$ and
+the universe by $\universe{g}$. We also let $\aut(g) := \aut(\tau, D)$ and
+$\str(g) := \str(\tau, D)$.
 
@@
 symmetric. We say $C_n$ is a \emph{matrix-circuit} if every gate in $C_n$ is
-matrix-symmetric or symmetric. We say $C_n$ is a \emph{rank-circuit} if $C_n$ is a
-matrix-circuit and every non-symmetric gate is a $\rank$ gate.
+matrix-symmetric or symmetric. We say $C_n$ is a \emph{rank-circuit} if $C_n$ is
+a matrix-circuit and every non-symmetric gate is a $\rank$ gate.
 

### 2018-01-15 sections/translating-formulas-to-cicuits.tex
January 15 Update

--- 2017-11-28 sections/translating-formulas-to-cicuits.tex
@@
 \begin{lem}
-  Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit with unique labels of size $n$ and
-  $\sigma \in \sym_n$. There is an algorithm takes as input a circuit $C_n$ and
-  $\sigma \in \sym_n$ and outputs for each gate $g$ its image under the unique
-  automorphism extending $\sigma$ (if it exists). This algorithm runs in time
-  polynomial in the combined size of the input circuit and the encoding of the
-  permutation.
+  There is an algorithm takes as input a $(\mathbb{B}, \tau)$-circuit $C$ of
+  order $n$ with unique labels and $\sigma \in \sym_n$ and outputs for each gate
+  $g$ its image under the unique automorphism extending $\sigma$ (if it exists).
+  This algorithm runs in time polynomial in the combined size of the input
+  circuit and the encoding of the permutation.
   \label{lem:compute-automorphisms}
@@
 \begin{proof}
-  Suppose $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$. We build up the
+  Suppose $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$. We build up the
   mapping $\pi$ extending $\sigma$ recursively. If at some point in the
@@
   equivalent to $L(h')$ and, if $h$ is an output gate then $h'$ is an output
-  gate such that $\sigma \Omega^{-1}(h) = \Omega^{-1}(h')$. Since $C_n$ has
-  unique labels we have that $\pi L(h)$ is isomorphism equivalent to $L(h')$ if,
-  and only if, $L(h')^{-1}\pi L(h)$ acts like an isomorphism. This can be
-  determined easily. If no such $h'$ exists halt and output that there is no
-  automorphism extending $\sigma$. We have from Lemma \ref{} that if $C_n$ has
-  unique labels then there is at most one such $h'$.
+  gate such that $\sigma \Omega^{-1}(h) = \Omega^{-1}(h')$. Since $C$ has unique
+  labels we have that $\pi L(h)$ is isomorphism equivalent to $L(h')$ if, and
+  only if, $L(h')^{-1}\pi L(h)$ acts like an isomorphism. This can be determined
+  easily. If no such $h'$ exists halt and output that there is no automorphism
+  extending $\sigma$. We have from Lemma \ref{} that if $C$ has unique labels
+  then there is at most one such $h'$.
 
@@
 
+\begin{cor}
+  There is an algorithm takes as input a $(\mathbb{B}, \tau)$-circuit $C$ of
+  order $n$, $\sigma \in \sym_n$, $g$ a gate in $C$, and $a \in \universe{g}$
+  and, if there exists an automorphism of $C$ extending $\sigma$ such that
+  $\sigma in \stab(g)$, outputs image of $a$ under $\sigma$.
+  \label{cor:compute-automorphisms-labels}
+\end{cor}
+\begin{proof}
+  Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$. Use the algorithm
+  from Lemma \ref{lem:compute-automorphisms} to check if $\sigma$ extends to an
+  automorphism on $C$ and $\sigma \in \stab(g)$. If not, return that no such
+  automorphism exists. We thus have that $C$ is symmetric. Let $h \in H_g$ and
+  $\vec{a} := L(g)^{-1}(h)$ be such that $a \in \vec{a}$, and let $i$ be the
+  index of $a$ in $\vec{a}$. Output $\sigma \cdot a := L(g)^{-1}(\sigma h)(i)$.
+\end{proof}
+
+% \begin{lem}
+%   Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit with unique labels of size $n$
+%   and $\sigma \in \sym_n$. There is an algorithm takes as input a circuit
+%   $C_n$ and $\sigma \in \sym_n$ and outputs for each gate $g$ its image under
+%   the unique automorphism extending $\sigma$ (if it exists). This algorithm
+%   runs in time polynomial in the combined size of the input circuit and the
+%   encoding of the permutation.
+%   \label{lem:compute-automorphisms}
+% \end{lem}
+% \begin{proof}
+%   Suppose $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$. We build up
+%   the mapping $\pi$ extending $\sigma$ recursively. If at some point in the
+%   recursive construction we arrive at a point where no mapping for $g$ can be
+%   found we halt at that point and return that no automorphism exists.
+
+%   Let $h$ be any gate in the circuit. Suppose $h$ is an input gate. If $h$ is
+%   a constant gate then let $\pi (h) = h'$. If $h$ is a relational gate such
+%   that $R := \Sigma(h)$ and check if there exists $h'$ such that $\Sigma (h')
+%   = R$ and $\sigma \Lambda_R(h) = \Lambda_R(h')$ and, if $h$ is an output gate
+%   then $h'$ is an output gate such that $\sigma Omega^{-1}(h) =
+%   \Omega^{-1}(h')$. If such a $h'$ does not exist halt and output that there
+%   is no automorphism extending $\sigma$. We have from Lemma \ref{} that if
+%   such an $h'$ exists it must be unique, and we set $\pi(h) = h'$.
+
+%   Let $h$ be an internal gate in the circuit and assume we have defined $\pi
+%   (g)$ for every gate $g$ of height less than $h$. Let $h'$ be a gate in the
+%   circuit such that $\Sigma(h) = \Sigma (h')$, $\pi L(h)$ is isomorphism
+%   equivalent to $L(h')$ and, if $h$ is an output gate then $h'$ is an output
+%   gate such that $\sigma \Omega^{-1}(h) = \Omega^{-1}(h')$. Since $C_n$ has
+%   unique labels we have that $\pi L(h)$ is isomorphism equivalent to $L(h')$
+%   if, and only if, $L(h')^{-1}\pi L(h)$ acts like an isomorphism. This can be
+%   determined easily. If no such $h'$ exists halt and output that there is no
+%   automorphism extending $\sigma$. We have from Lemma \ref{} that if $C_n$ has
+%   unique labels then there is at most one such $h'$.
+
+%   This recursive approach can be implemented as an algorithm that runs in time
+%   polynomial in the combined size of the inputs and outputs the required
+%   automorphism if it exists.
+% \end{proof}
+
 This result uses a proof very similar to the one for a similar result proved by
-Anderson and Dawar~\cite{Anderson17D}.
+Anderson and Dawar~\cite{AndersonD17}.
 
 \begin{lem}
-  There is an algorithm that takes as input a circuit $C_n$ with unique labels
-  and decides if $C_n$ is symmetric. If $C_n$ is symmetric outputs the orbits
-  and coarsest supporting partitions of every gate. Moreover, this algorithm
-  runs in time polynomial in the size of the input circuit.
-  \label{lem:computing support}
+  \label{lem:computing-support-orbit}
+  There is an algorithm that takes in a subset $S \subseteq [n]$ and $x \in X$,
+  where $X$ is some finite set such that there is a group action of $\stab(S)$
+  on $X$ computable in time polynomial in $n$ and $\vert X \vert$ and outputs
+  $\orb_{\stab(S)} (x)$ and $\SP_{\stab(S)}(x)$. This algorithm runs in time
+  polynomial in $\vert X \vert$ and $n$.
 \end{lem}
-
 \begin{proof}
-  Suppose $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$. Let $(u, v) \in
-  \sym_n$ be a transposition. We may use Lemma \ref{lem:compute-automorphisms}
-  to determine the unique automorphism $\pi_{(u,v)}$ extending $(u, v)$. It is
-  easy to see that, since the set of transpositions generate $\sym_n$, for all
-  $(u,v) \in \sym_n$ $\pi_{(u,v)}$ the automorphism $\pi_{(u,v)}$ exists if, and
-  only if, $C_n$ is symmetric. We note that there are ${n}\choose{2}$
-  transpositions. It follows that we may check in polynomial time if $C_n$ is
-  symmetric. If $C_n$ is not symmetric we output that it is not symmetric and
-  halt.
-
-  Suppose then that $C_n$ is symmetric. For transposition $(u, v) \in \sym_n$,
-  let $\mathcal{P}_{(u,v)} := \{\{u,v\}\}\bigcup_{w \in [n] \setminus
-    \{u,v\}}\{\{w\}\}$ be a partition of $[n]$. We have that $\pi_{(u,v)}$ fixes
-  $g$ if, and only if, $\mathcal{P}_{(u,v)}$ supports $g$. Since we can
-  efficiently check if $\pi_{(u,v)}$ fixes $g$ it follows that we can
-  effeciently check if $\mathcal{P}_{(u,v)}$ supports $g$. Let $\mathcal{P}$ be
-  the result of combining the set consisting of those partitions
-  $\mathcal{P}_{(u,v)}$ that support $g$ using $\mathcal{E}$. From Proposition
-  \ref{prop:combining-supporting-patitions} we have that $\mathcal{P}$ supports
-  $g$. Suppose that $\mathcal{P}$ is not the coarsest supporting partition of
-  $g$. Then there exists a partition $\mathcal{P}'$ supporting $g$ such
-  $\mathcal{P}' \preceq P$ and $\mathcal{P}' \neq \mathcal{P}$. But then there
+  Let $(u, v) \in \sym_{[n] \setminus S}$ be a transposition. We note that
+  $(u,v) \in \stab(S)$ and there are ${n - \vert S \vert}\choose{2}$ many such
+  transpositions. For a transposition $(u, v) \in \sym_{[n] \setminus S}$, let
+  \begin{align*}
+    \mathcal{P}_{(u,v)} := \{ \{u,v\}\} \bigcup_{w \in [n] \setminus \{ u,v \}} \{ \{ w \} \}
+  \end{align*}
+  be a partition of $[n]$. Then $\mathcal{P}_{(u,v)}$ supports
+  $\stab_{\stab(S)}(x)$ if, and only if, $(u,v) \cdot x = x$.
+
+  Let $\mathcal{P}$ be the partition formed by applying $\mathcal{E}$ to all
+  $\mathcal{P}_{(u,v)}$ such that $(u,v) \cdot x = x$ (which can be checked in
+  time polynomial in $\vert X \vert + n$). From
+  Proposition~\ref{prop:combining-supporting-patitions} we have that
+  $\mathcal{P}$ supports $\stab_{\stab(S)}(x)$. Suppose that $\mathcal{P}$ is
+  not the coarsest supporting partition of $\stab_{\stab(S)}(x)$. Then there
+  exists a partition $\mathcal{P}'$ supporting $\stab_{\stab(S)}(x)$ such that
+  $\mathcal{P}' \preceq P$ and $\mathcal{P}' \neq \mathcal{P}$. And so there
   exists $P \in \mathcal{P}$ and $P' \in \mathcal{P}'$ such that $P \subsetneq
-  P'$. But then there exists $a , b \in P'$ such that $a \not\in P$. It follows
-  that the transposition $(a,b)$ fixes $\mathcal{P}'$ and so $\pi_{(a,b)}$ fixes
-  $g$, but then, $\mathcal{P}_{(a,b)}$ supports $g$ and so, from the
-  construction of $\mathcal{P}$, $\mathcal{P}$ is fixed by $(a,b)$. But
-  $\mathcal{P}$ is not fixed by $(a,b)$, so we have a contradiction. We thus
-  have that $\mathcal{P}$ is the coarsest supporting partition of $g$.
-
-  It remains to compute the orbit of a gate $g$. Let $S_0 := \{g\}$ and for each
-  $i \geq 0$ let $S_{i+1} := S_i \bigcup_{(u,v) \in \sym_n} \pi_{(u,v)}S_i$. Let
-  $S$ be the least fixed point. It is easy to see that $S \subseteq \orb(g)$ as
-  every gate in $S$ is equal to the action of some sequence of automorphisms
-  (extending transpositions) acting on $g$. Moreover, since the set of all
-  transpositions generates $\sym_n$, it follows that $\orb(g) \subseteq S$ and
-  so $\orb(g) = S$.
-
-  Given the polynomial bound on the number of transpositions, and the
-  polynomial-time bound on the algorithm from Proposition
-  \ref{prop:combining-supporting-partitions}, it is easy to see that the
-  procedures described above can be implemented so as to run in time polynomial
-  in the size of the input circuit.
+  P'$. But then there exists $a , b \in P'$ such that $a \not\in P$. Note that
+  $(a,b)$ fixes $\mathcal{P}'$ and, since $\mathcal{P}'$ supports
+  $\stab_{\stab(S)}(x)$, it follows that $(a,b) \in \stab_{\stab(S)}(x)$ and $a
+  \not\in S$ and $b \not\in S$. But then we have that $(a,b) \cdot x = x$, and
+  so $\mathcal{P}_{(a,b)}$ supports $\stab_{\stab(S))}(x)$ and thus, from the
+  construction of $\mathcal{P}$, $\mathcal{P}$ is fixed by $(a,b)$. But we
+  selected $a$ and $b$ such that $\mathcal{P}$ is not fixed by $(a,b)$, and so
+  we have a contradiction. We thus have that $\mathcal{P}$ is the coarsest
+  supporting partition of $\stab_{\stab(S)}(x)$.
+
+  It remains to compute $\orb_{\stab(S)}(x)$. Let $M_0 := \{x\}$ and for each $i
+  \geq 0$ let $M_{i+1} := M_i \bigcup_{(u,v) \in \sym_{[n] \setminus S}} (u,v)
+  \cdot M_i$. Let $M$ be the least fixed point. It is easy to see that $M
+  \subseteq \orb_{\stab(S)}(x)$ as every element of $M$ is equal to the action
+  of some finite sequence of transpositions acting on $x$. Moreover, if $y \in
+  \orb_{\stab(S)}(x)$, then there exists $\pi \in \stab(S)$ such that $y = \pi
+  \cdot x$. But then, since $\sym_{[n] \setminus S}$, is generated by the set of
+  all transpositions in $\sym_{[n] \setminus S}$, it follows that $\pi$ can be
+  written as a sequence of $t$ transpositions (for some $t \in nats$). Thus $y
+  \in M_t \subseteq M$, and hence $\orb_{\stab(S)}(x) \subseteq M$ and so
+  $\orb_{\consp(G)}(x) = $.
+
+  Note that the set of all transpositions in $\sym_{[n] \setminus S}$ can be
+  computed in time $\mathcal{O}(n^{2})$ and whether such a transposition fixes
+  $x$ can be computed in time polynomial in $\vert X \vert + n$. Moreover, since
+  it is easy to show that $\mathcal{E}$ can be computed in time polynomial in
+  $n$, it follows that $\mathcal{P}$ (defined above) can be computed in
+  $\mathcal{O} (n^{2} q(\vert X \vert + n))$, for some polynomial $q$.
+
+  Furthermore, since, when computing the orbit, the least fixed point must be
+  reached in fewer than $\vert X \vert$ iterations, and each iteration requires
+  at most $\mathcal{O} (n^{2})$ applications of the group action, it follows
+  that the procedure terminates in time $\mathcal{O}(\vert X \vert n^{2} q'
+  (\vert X \vert + n))$, for some polynomial $q'$. The result follows.
 \end{proof}
+
+\begin{lem}
+  There is an algorithm that takes in a circuit $C$ of order $n$ with unique
+  labels and outputs if the circuit is symmetric. If it is symmetric then it
+  outputs the orbit and coarsest supporting partition of every gate. This
+  algorithm runs in time polynomial in the size of the circuit.
+  \label{lem:computing-support-orbit-gate}
+\end{lem}
+
+\begin{proof}
+  For each transposition $(u,v) \in \sym_n$ and each gate $g$ in $C$ use
+  Lemma~\ref{lem:compute-automorphisms} to check if the image of $g$ under
+  $(u,v)$ exists. If for any transposition and gate the algorithm returns that
+  no image exists then output that the circuit is not symmetric.
+
+  We note that if all gates have an image under all transpositions then, since
+  $\sym_n$ is generated by the set of transpositions, we have that $C$ is
+  symmetric.
+
+  We have from Lemma~\ref{lem:compute-automorphisms} that computing the action
+  of $\sym_n$ on the gates of $C$ can be done in time polynomial in the size of
+  the circuit. For each $g$ in $C$ use the algorithm from
+  Lemma~\ref{lem:computing-support-orbit} with $S := \emptyset$, $X := G$, and
+  $x := g$, and output the results.
+
+  Since there are ${{n}\choose{2}} \leq n^2$ transpositions in $\sym_n$, the
+  initial symmetry check can be completed in time polynomial in the size of the
+  circuit. Moreover, from Lemmas~\ref{lem:compute-automorphisms} and
+  \ref{lem:computing-support-orbit}, and the fact that $\vert C \vert \geq n$
+  and $\vert C \vert \geq \vert \universe{g} \vert$, we have that the rest of
+  the algorithm also runs in time polynomial in the size of the circuit.
+\end{proof}
+
+\begin{lem}
+  There is an algorithm that takes in a circuit $C$ of order $n$ with unique
+  labels, a gate $g$ in $C$ with small support, and $a \in \universe{g}$, and
+  outputs if the circuit is symmetric. If it is symmetric it outputs the orbit
+  $\orb_{\vec{\consp(g)}} (a)$ and coarsest supporting partition
+  $\SP_{\vec{\consp(g)}} (a)$. This algorithm runs in time polynomial in the
+  size of the circuit.
+  \label{lem:computing-support-orbit-index}
+\end{lem}
+\begin{proof}
+  Use the algorithm from Lemma~\ref{lem:computing-support-orbit-gate} in order
+  to compute the canonical support of $g$. If the algorithm returns that $C$ is
+  not symmetric, output that $C$ is not symmetric.
+
+  Use the algorithm from Lemma~\ref{lem:computing-support-orbit}, with $S :=
+  \consp(g)$, $X := \universe{g}$ and $x:= a$, and output the results.
+
+  Notice that, since $\vert \universe{g} \vert \leq \vert C \vert$ and $n \leq
+  \vert C \vert$, this algorithm runs in polynomial time.
+\end{proof}
+
+% \begin{lem}
+%   There is an algorithm that takes in a symmetric circuit $C$ of order $n$
+%   with unique labels, a gate $g$ in $C$ and $a \in \universe{g}$, the orbit
+%   $\orb_g (a)$ and coarsest supporting partition $\SP_g (a)$.
+% \end{lem}
+% \begin{proof}
+%   Let $(u,v) \in \sym_n$ be a transposition. We can check if $(u,v) \in
+%   \stab(g)$ using Lemma~\ref{lem:compute-automorphisms}. Then $(u,v)$ acts
+%   like an isomorphism at $g$, and hence $(u,v) \cdot a = L(g)^{-1}((\sigma
+%   L(g)(\vec{x}))) (i)$, where $\vec{x} \in \ind(g)$ such that $\vec{x} (i) =
+%   a$ for some $i \in [\vert \vec{x} \vert]$. Thus, since
+%   Lemma~\ref{lem:compute-automorphisms} gives us that that we can compute
+%   $\sigma L(g)(\vec{x})$ in polynomial time, we can compute $(u,v) \cdot a$ in
+%   polynomial-time.
+
+%   We note that
+
+%   and hence we can compute $\sigma \cdot a$ effeciently. and hence compute
+%   $\orb_g(a) = \{ \sigma \cdot a : \sigma \in \stab(g)\}$.
+
+% \end{proof}
 

### 2018-01-24 sections/translating-formulas-to-cicuits.tex
24th January 2018

--- 2017-11-28 sections/translating-formulas-to-cicuits.tex
@@
 \begin{document}
+In this section we first introduce a number of useful polynomial-time computable
+functions which define transformations on circuits. In the second subsection we
+use these these functions to define a transformation of $\FPR$-formulas into
+equivalent families of transparent rank-circuits.
 
 \subsection{Algorithms for Circuits}
-In order to translate between $P$-uniform families of circuits and formulas of
-$\FPR$ we will require that certain important circuit transformations can be
-completed in polynomial time. In this subsection we define a number of
-operations that perform commonly invoked operations on circuits, and which can
-easily be shown to be implementable as algorithms that run in polynomial time.
-In each case we assume a reasonable encoding of the circuit.
-
-We first define the operation $\op{merge}$ that takes in a circuit and a set of
-syntactically equivalent gates and produces a new circuit by combining those
-gates into a single gate.
+In order to simplify the presentation of the translation between $P$-uniform
+families of circuits and formulas of $\FPR$, as well as the proofs of other
+results (see Lemma~\ref{lem:transparent-unique}), we define a number of
+often-used polynomial-time computable circuit transformations.
+
+We first define the function $\op{merge}$, which maps a circuit and a set of
+syntactically-equivalent gates to a circuit formed by combining those gates into
+a single gate.
 
 \begin{definition}
-  The operation $\op{merge}(C, H)$ takes as input a circuit $C = \langle G,
-  \Omega, \Sigma , \Lambda, L \rangle$ and a set of syntactically equivalent
-  gates $H := \{h_1, \ldots , h_p\}$ and outputs the circuit $C' = \langle G',
-  \Omega', \Sigma', \Lambda', L' \rangle$, where
+  Let $C := \langle G, \Omega, \Sigma , \Lambda, L \rangle$ be a circuit and $H
+  := \{h_1, \ldots, h_p\}$ be a set of syntactically equivalent gates. We let
+  $\op{merge}(C, H) := C' := \langle G', \Omega', \Sigma', \Lambda', L'
+  \rangle$, where
   \begin{itemize}
@@
 
-It can be shown that $\op{merge}$ can be computed by an algorithm running in
-time polynomial in the size of the input circuit. We note that the input and
-output circuits compute the same function. Moreover, if the input circuit is
-symmetric (resp. has unique labels, is transparent) then the output circuit will
-also be symmetric (resp. have unique labels, is transparent).
-
-The the operation $\op{merge-all}$ simply applies $\op{merge}$ to the syntactic
-equivalence classes of some input set of gates.
+It can be shown that $\op{merge}$ can be computed in time polynomial in the size
+of the input circuit. We note that the input and output circuits compute the
+same function. Moreover, if the input circuit is symmetric (resp. has unique
+labels, is transparent) then the output circuit will also be symmetric (resp.
+have unique labels, is transparent).
+
+We now define the function $\op{merge-all}$ which maps a circuit and a set of
+gates to a new circuit formed by applying $\op{merge}$ to the
+syntactic-equivalence classes of the set of gates.
 
 \begin{definition}
-  The operation $\op{merge-all}(C, H)$ takes as input an ordered circuit $C$ and
-  a set of gates $H$ and outputs another circuit $C'$. Let $H_1, \ldots, H_p$ be
-  the syntactic equivalence classes of $H$ linearly ordered using the order on
-  the circuit but such that for all $i, j \in [p]$ if $i \leq j$ then the height
-  of the gates in $H_i$ is less than or equal to the height of the gates in
-  $H_j$. Let $C'$ be the result of successively executing $\op{merge}$ on each
-  equivalence class.
+  \label{def:merge-all}
+  The function $\op{merge-all}$ maps a circuit $C$ and a set of gates $H$ to a
+  circuit $\op{merge-all}(C, H) := C'$, where $C'$ is defined as follows. Let
+  $H_1, \ldots, H_p$ be the syntactic equivalence classes of $H$, and let $C'$
+  be defined from $C$ by successively applying $\op{merge}$ to each of these
+  equivalence classes.
 \end{definition}
 
-For an input tuple $(C, H)$ if $H$ is a set of gates with unique labels it
-follows from Lemma \cite{} that the syntactic equivalence relation on $H$ can be
-computed in time polynomial in the size of $C$. Thus, if the set $H$ has unique
-labels it can be shown that the operation $\op{merge-all}$ can be computed in
-time polynomial in the size of the input circuit. As in the case of
-$\op{merge}$, the operation $\op{merge-all}$ preserves symmetry, unique labels
-and the ensures that the input and output circuits compute the same function. If
-$C$ is an ordered circuit and $H$ is a set of gates with unique labels, then if
-$g$ is a gate in both $C$ and $C' := \op{merge-all}(C, H)$, then if all of the
-input gates of $g$ in $C$ are in $H$ then no two distinct input gates of $g$ in
-$C'$ are syntactically equivalent (but $g$ does not have unique labels in $C'$
-as $L'(g)$ may not be injective).
+We can compute $\op{merge-all}$ using the following algorithm. Let $(C, H)$ be a
+tuple in the domain of $\op{merge-all}$. We assume a reasonable encoding of the
+circuit, and note that any such encoding induces a linear order on the
+structure. Let $H_1, \ldots, H_p$ be the syntactic equivalence classes of $H$
+linearly ordered such that for all $i, j \in [p]$ if $i \leq j$ the height of
+the gates in $H_i$ is less than or equal to the height of the gates in $H_j$.
+Let $C'$ be the result of successively executing the algorithm for $\op{merge}$
+on each such equivalence class in order.
+
+It is worth noting that for an input tuple $(C, H)$, if follows from
+Lemma~\cite{lem:unique-labels-syntactic-equiv} that if $H$ has unique labels
+then the syntactic equivalence relation on $H$ can be computed in time
+polynomial in the size of $C$. Thus, if the set $H$ has unique labels, it can be
+shown that the operation $\op{merge-all}$ can be computed in time polynomial in
+the size of the input circuit.
+
+As in the case of $\op{merge}$, the function $\op{merge-all}$ preserves
+symmetry, unique labels and the ensures that the input and output circuits
+compute the same function. Let be a circuit $C$ a circuit and $H$ a set of gates
+in $C$ with unique labels. Then if $g$ is a gate in both $C$ and $C' :=
+\op{merge-all}(C, H)$, and all of the children of $g$ in $C$ are in $H$, then no
+two distinct children of $g$ in $C'$ are syntactically-equivalent. We note we
+have no guarantee that $g$ will have unique labels in $C'$ as $L'(g)$ may not be
+injective.
 
@@
 
-The operation $\op{make-injective}$ takes in a circuit and a symmetric gate and
-outputs an equivalent circuit but such that the selected gate now has injective
-labels.
+The now define the function $\op{make-injective}$ that maps a circuit and a
+symmetric gate to an equivalent circuit containing all the same gates as the
+input circuit but such that the specified gate now has injective labels.
 
 \begin{definition}
-  The operation $\op{make-injective}(C, h)$ takes as input an ordered
-  $(\mathbb{B}, \tau)$-circuit $C := \langle G, \Omega, \Sigma , \Lambda, L
-  \rangle$ and a gate $h \in G$ and outputs the circuit $C' := \langle G',
-  \Omega', \Sigma', \Lambda', L' \rangle$. Let $c = \max \{\vert
-  L(g)^{-1}(h)\vert : g \in W(h, \cdot)\}$. If $c = 1$ then $C' := C$. If $c >
-  1$ then $C'$ is defined such that
+  \label{def:make-injective}
+  The function $\op{make-injective}$ maps a circuit $C := \langle G, \Omega,
+  \Sigma , \Lambda, L \rangle$ and a gate $h \in G$ to the circuit
+  $\op{make-injective}(C, h) := C' := \langle G', \Omega', \Sigma', \Lambda', L'
+  \rangle$, defined as follows. Let $c = \max \{\vert L(g)^{-1}(h)\vert : g \in
+  W(h, \cdot)\}$. If $c = 1$ then $C' := C$. If $c > 1$ then $C'$ is defined
+  such that
   \begin{itemize}
@@
 
-The operation $\op{make-injective-all}$ takes in a circuit and outputs an
-equivalent circuit such that every symmetric-gate in that circuit has injective
-labels.
+We now define the function $\op{make-injective-all}$ that maps a circuit to an
+equivalent circuit such that every symmetric gate now has injective labels.
 
 \begin{definition}
-  The operation $\op{make-injective-all}(C)$ takes as input an ordered
-  $(\mathbb{B}, \tau)$-circuit $C := \langle G, \Omega, \Sigma , \Lambda, L
-  \rangle$ and outputs the circuit $C' := \langle G', \Omega', \Sigma',
-  \Lambda', L' \rangle$ defined as follows. Let $F(C*) = \op{make-injective}(C*,
-  h)$, where $h$ is the first gate in $C*$ such that there exists a gate $g$ in
-  $C*$ where $\vert L*(g)^{-1}(h)\vert > 1$. Let $(C^0, C^1, \ldots)$ be a
-  sequence of circuits where $C^0 := C$ and for $i > 1$, $C^i = F(C^{i-1})$. It
-  can be shown that this sequence converges after at most $\vert C \vert$ many
-  steps. Let $C'$ be this limit.
+  The function $\op{make-injective-all}$ maps a circuit $C := \langle G, \Omega,
+  \Sigma , \Lambda, L \rangle$ to a circuit $\op{make-injective}(C) := C' :=
+  \langle G', \Omega', \Sigma', \Lambda', L' \rangle$ defined as follows.
+
+  Let $F$ be a function that maps an ordered circuit $C*$ to the circuit
+  $\op{make-injective}(C*, h)$, where $h$ is the topologically first gate such
+  that there exists a gate $g$ in $C*$ where $h$ is a child of $g$ and $\vert
+  L*(g)^{-1}(h) \vert > 1$. Let $(C^0, C^1, \ldots)$ be a sequence of circuits
+  where $C^0 := C$ and for $i > 1$, $C^i := F(C^{i-1})$. It can be shown that
+  this sequence converges after at most $\vert C \vert$ many steps. Let $C'$ be
+  the limit of this sequence.
 \end{definition}
@@
 Since $\op{make-injective}$ can be computed in polynomial time, and the number
-of iterations required in order to reach is a fixed-point in the definition of
-$\op{make-injective-all}$ is bounded by the size of the input circuit, it
-follows that $\op{make-injective-all}$ can be computed in time polynomial in the
-size of the input circuit. Moreover, $\op{make-injective-all}$ preserves
+of iterations required to converge to the limit in the above definition is
+bounded by the size of the circuit, it can be shown that
+$\op{make-injective-all}$ can be computed in time polynomial in the size of the
+input circuit. Furthermore, we note that $\op{make-injective-all}$ preserves
 symmetry, rigidity and unique labels. Moreover, the input and output circuits
@@
 
-The operation $\op{insert}$ takes as input two circuits and outputs a circuit
+We now define the function $\op{insert}$ that maps two circuits to a circuit
 formed by inserting the gates of the first circuit into the second circuit.
@@
 \begin{definition}
-  The operation $\op{insert}(C^1, C^2)$ takes as input a $(\mathbb{B}_1,
-  \tau_1)$-circuit $C^1 := \langle G_1, \Omega_1, \Sigma_1 , \Lambda_1, L_1
-  \rangle$ and a $(\mathbb{B}_2, \tau_2)$-circuit $C^2 := \langle G_2, \Omega_2,
-  \Sigma_2 , \Lambda_2, L_2 \rangle$ and outputs a $(\mathbb{B}_1 \cup
-  \mathbb{B}_2, \tau_1 \uplus \tau_2)$-circuit $C = \langle G, \Omega, \Sigma ,
-  \Lambda, L \rangle$ where
+  The function $\op{insert}$ maps a $(\mathbb{B}_1, \tau_1)$-circuit $C^1 :=
+  \langle G_1, \Omega_1, \Sigma_1 , \Lambda_1, L_1 \rangle$ and a
+  $(\mathbb{B}_2, \tau_2)$-circuit $C^2 := \langle G_2, \Omega_2, \Sigma_2 ,
+  \Lambda_2, L_2 \rangle$ to a $(\mathbb{B}_1 \cup \mathbb{B}_2, \tau_1 \uplus
+  \tau_2)$-circuit $\op{insert}(C^1, C^2) := C := \langle G, \Omega, \Sigma ,
+  \Lambda, L \rangle$, where
   \begin{itemize}
@@
 
-It can be shown that $\op{insert}$ can be be computed in polynomial time. If the
-input circuits are symmetric then the output circuit will be symmetric.
-
-The operation $\op{replace}$ removes a gate from a circuit and replaces it with
-another gate.
+It can be shown that $\op{insert}$ can be be computed in time polynomial in the
+size of the input circuits. Moreover, if the input circuits are symmetric then
+the output circuit will be symmetric.
+
+We now define the function $\op{replace}$ that maps a circuit $C$ and a pair of
+gates $(g_1, g_2)$ in $C$ to a circuit $C'$ formed by replacing $g_1$ with $g_2$
+in $C$.
 
 \begin{definition}
-  The operation $\op{replace}(C, g_1, g_2)$ takes as input a circuit $C =
-  \langle G, \Omega, \Sigma, \Lambda, L\rangle$ and a pair of gates $(g_1, g_2)$
-  in $C$ and outputs a circuit $C' = \langle G', \Omega', \Sigma', \Lambda', L'
-  \rangle$ such that
+  The function $\op{replace}$ maps a circuit $C = \langle G, \Omega, \Sigma,
+  \Lambda, L\rangle$ and a pair of gates $(g_1, g_2)$ in $C$ to a circuit
+  $\op{replace}(C, g_1, g_2) := C' := \langle G', \Omega', \Sigma', \Lambda', L'
+  \rangle$, where
   \begin{itemize}
@@
     for each $\vec{a} \in \dom(\Omega)$ if $\Omega(\vec{a}) = g_1$ then
-    $\Omega'(\vec{a}) = g_2$ and if then $\Omega'(\vec{a}) = \Omega(\vec{a})$.
+    $\Omega'(\vec{a}) = g_2$ and otherwise $\Omega'(\vec{a}) = \Omega(\vec{a})$.
   \item $\Sigma' = \restr{\Sigma}{G'}$
@@
 
-It can be shown that the operation $\op{replace}$ can be computed in time
+It can be shown that the function $\op{replace}$ can be computed in time
 polynomial in the size of the input circuit.
 
-The operation $\op{tag}$ takes in a circuit, a gate in that circuit, a relation
-symbol and a tuple and outputs a circuit computing the same function but with an
-additional gadget, constructed using the gates labelled by the given relation
-symbol and tuple, marking the designated gate. The idea is that marking a gate
-can be used as a step to ensure unique labels in a circuit.
+We now define the function $\op{tag}$ that maps a circuit, a relation symbol, a
+gate in that circuit, and a tuple to a circuit computing the same function as
+the input circuit but with an additional gadget, constructed using the gates
+labelled by the given relation symbol and tuple, marking the designated gate.
+The intuition is that this marking helps to distinguish a gate, and is used as a
+step to ensure that a circuit has unique labels.
 
 \begin{definition}
-  The operation $\op{tag}(C, R, g, \vec{a})$ takes in a $(\mathbb{B},
-  \tau)$-circuit $C_n := \langle G, \Omega, \Sigma, \Lambda, L \rangle$, a
-  relation symbol $R \in \tau$, a gate $g \in G$ and a tuple $\vec{a} \in [n]^k$
-  for some $k$ and outputs the circuit $C_n' = \langle G', \Omega', \Sigma',
-  \Lambda', L'\rangle$ defined by the following algorithm. Let $G' = G \uplus
-  \{\land_g, \land_{g'}, \land_1, \ldots , \land_k\}$, $\Omega' = \Omega$, and
-  $\Lambda' = \Lambda$. Define $L'$ and $\Sigma'$ as follows. For each $g \in G$
-  $\Sigma'(g) = \Sigma(g)$. For each $g \in \{\land_0, \land_1, \ldots , \land_k
-  \}$, $\Sigma(g)$ is an $\AND$-gate that takes in two inputs. $\Sigma(\land_g)$
-  is an $\AND$-gate that takes in a single input. Set $g$ to be the lone input
-  to $\land_g$. Set the two inputs to $\land_0$ to be $\land_g$ and $\land_1$.
-  For each $i \in [k-1]$ set the inputs of $\land_i$ to be $\land_{i+1}$ and the
-  gate $g_i \in G'$ such that $\Sigma(g_i) = R$ and $\Lambda^{-1}(g_i) =
-  \vec{a}_i$, where $\vec{a}_i$ is the $k$-tuple $(\vec{a}(i), \ldots,
-  \vec{a}(i))$. Set the inputs of $\land_k$ to be the constant gate $1$ and the
-  gate $g_k$ such that $\Sigma(g) = R$ and $\Lambda^{-1}(g_k) = \vec{a}_k$.
-
-  For each gate $h \in G \setminus \{g\}$ and $\vec{b} \in \ind(h)$, if
-  $L(h)(\vec{b}) = g$ then let $L'(h)(\vec{b}) = \land_0$, otherwise let
+  The function $\op{tag}$ maps a $(\mathbb{B}, \tau)$-circuit $C := \langle G,
+  \Omega, \Sigma, \Lambda, L \rangle$ of order $n$, a relation symbol $R \in
+  \tau$, a gate $g \in G$, and a tuple $\vec{a} \in [n]^k$ for some $k$ to a
+  circuit $\op{tag}(C, R, g, \vec{a}) := C' := \langle G', \Omega', \Sigma',
+  \Lambda', L'\rangle$ of order $n$, such that $G' = G \uplus \{\land_g,
+  \land_{g'}, \land_1, \ldots , \land_k\}$, $\Omega' = \Omega$, and $\Lambda' =
+  \Lambda$. For each $g \in G$ $\Sigma'(g) = \Sigma(g)$. For each $g \in
+  \{\land_0, \land_1, \ldots , \land_k \}$, $\Sigma(g)$ is an $\AND$-gate that
+  takes in two inputs. $\Sigma(\land_g)$ is an $\AND$-gate that takes in a
+  single input, $g$ is the lone input to $\land_g$, and $\land_0$ has as input
+  $\land_g$ and $\land_1$. For each $i \in [k-1]$ the inputs of $\land_i$ are
+  $\land_{i+1}$ and the gate $g_i \in G'$ such that $\Sigma(g_i) = R$ and
+  $\Lambda^{-1}(g_i) = \vec{a}_i$, where $\vec{a}_i$ is the $k$-tuple
+  $(\vec{a}(i), \ldots, \vec{a}(i))$. The inputs of $\land_k$ are the constant
+  gate $1$ and the gate $g_k$ such that $\Sigma(g) = R$ and $\Lambda^{-1}(g_k) =
+  \vec{a}_k$. For each gate $h \in G \setminus \{g\}$ and $\vec{b} \in \ind(h)$,
+  if $L(h)(\vec{b}) = g$ then $L'(h)(\vec{b}) = \land_0$, otherwise
   $L'(h)(\vec{b}) = L(h)(\vec{b})$.
@@
 
-It can be shown that $\op{concatenate}$ can be implemented so as to run in time
-polynomial in the size of the input. The input and output circuits compute the
-same function. Moreover, if the input circuit had unique labels then the output
-circuit will have unique labels. In the event that the input relation symbol is
-obvious from the context we omit it when invoking this algorithm.
-
-The operation $\op{concatenate}$ takes in a circuit and a set of appropriate
-circuits and forms a new circuit by replacing the relational gates of the
-designated circuit with the output gates of the circuits in the given set of
+It can be shown that $\op{tag}$ can be computed in time polynomial in the size
+of its input. The input and output circuits compute the same function. Moreover,
+if the input circuit has unique labels then the output circuit will have unique
+labels. If the input relation symbol is obvious from the context we omit it when
+invoking $\op{tag}$.
+
+\begin{definition}
+  The function $\op{tag-all}$ maps a $(\mathbb{B}, \tau)$-circuit $C := \langle
+  G, \Omega, \Sigma, \Lambda, L \rangle$ of order $n$, a relation symbol $R \in
+  \tau$, a set of gates $H \subseteq G$, and $T := (\vec{a}_h)_{h \in H}
+  \subseteq [n]^{k}$ a sequence of tuples indexed by $H$ for some fixed $k$, to
+  a circuit $\op{tag-all}(C, R, H, T) := C' := \langle G', \Omega', \Sigma',
+  \Lambda', L'\rangle$ of order $n$ defined as follows.
+
+  Suppose there is a linear order on $H$, and write $H = \{h_1, \ldots, h_t\}$.
+  Let $C_0 := C$ and for all $i \in [t]$ let $C_i := \op{tag}(C_{i-1}, R, h_i,
+  T(h_i))$. Then $C' = C_{t}$.
+
+  % such that $G' = G \uplus \{\land_g, \land_{g'}, \land_1, \ldots ,
+  % \land_k\}$,
+  % $\Omega' = \Omega$, and $\Lambda' = \Lambda$. For each $g \in G$ $\Sigma'(g)
+  % =
+  % \Sigma(g)$. For each $g \in \{\land_0, \land_1, \ldots , \land_k \}$,
+  % $\Sigma(g)$ is an $\AND$-gate that takes in two inputs. $\Sigma(\land_g)$ is
+  % an $\AND$-gate that takes in a single input, $g$ is the lone input to
+  % $\land_g$, and $\land_0$ has as input $\land_g$ and $\land_1$. For each $i
+  % \in
+  % [k-1]$ the inputs of $\land_i$ are $\land_{i+1}$ and the gate $g_i \in G'$
+  % such that $\Sigma(g_i) = R$ and $\Lambda^{-1}(g_i) = \vec{a}_i$, where
+  % $\vec{a}_i$ is the $k$-tuple $(\vec{a}(i), \ldots, \vec{a}(i))$. The inputs
+  % of
+  % $\land_k$ are the constant gate $1$ and the gate $g_k$ such that $\Sigma(g)
+  % =
+  % R$ and $\Lambda^{-1}(g_k) = \vec{a}_k$. For each gate $h \in G \setminus
+  % \{g\}$ and $\vec{b} \in \ind(h)$, if $L(h)(\vec{b}) = g$ then
+  % $L'(h)(\vec{b})
+  % = \land_0$, otherwise $L'(h)(\vec{b}) = L(h)(\vec{b})$.
+\end{definition}
+
+It is easy to see that, since $\op{tag}$ can be computed in time polynomial in
+the combined size of its inputs, $\op{tag-all}$ can also be computed in time
+polynomial in the combined size of its inputs.
+
+We now define the function $\op{compose}$ that maps a circuit and a sequence of
+appropriate circuits and to a circuit formed by replacing the input gates of the
+designated circuit with the output gates of the circuits in the sequence of
 circuits.
@@
 \begin{definition}
-  The operation $\op{concatenate}(C, \mathcal{C}, \tau_R, R)$, where $C :=
-  \langle G, \Omega, \Sigma, \Lambda, L \rangle$ is a $(\mathbb{B},
-  \tau)$-circuit, $\tau_R := (R_1, \ldots, R_t)$ is a sequence of relation
-  symbols such that $\tau_R \subseteq \tau$, $\mathcal{C} := ( C^1, \ldots,
-  C^t)$ is a finite sequence of circuits, where for each $i \in [t]$, $C^i =
-  \langle G_i, \Omega_i, \Sigma_i, \Lambda_i, L_i \rangle$ is a $(\mathbb{B}_i,
-  \tau_i)$-circuit such that $\tau_i \not\subset \tau_R$ and $C^i$ computes a
-  query of arity $\arty(R_i)$, and $R$ is a relation symbol in $(\tau \setminus
-  \tau_R) \cup (\bigcup_{1 \leq i \leq t},\tau_i))$. The operation outputs a
-  circuit $C' = \langle G', \Omega', \Sigma', \Lambda', L' \rangle$ defined from
-  the input as follows. Note that all circuits take in structures of size $n$.
-
-  Let ${C^0}' := \langle G^0, \Omega^0, \Sigma^0, \Lambda^0, L^0 \rangle := C$.
-  For each $i \in [t]$ fix a relation symbol $V_i \in \tau_i \setminus \tau_R$.
-  For each $i \in [t]$ construct the circuit ${C^{i}}' = \langle G_i',
-  \Omega_i', \Sigma_i', \Lambda_i', L_i' \rangle $ by $\op{inserting}$ $C^i$
-  into ${C^{i-1}}'$, and call the resultant circuit ${D^{i-1}}'$. For each
-  relational gate $g$ in $D^{i-1}$ labelled by the symbol $R_i$, $\op{replace}$
-  $g$ with the gate $\Omega_{i}(\Lambda_{i-1}'(g))$ in $D^{i-1}$ and $\op{tag}$
-  the gate $\Omega_i(\Lambda_{i-1}'(g))$ in $D^{i-1}$ using the tuple
-  $\Lambda_{i-1}'(g)$ and the relation symbol $R$. Output the circuit $C' :=
-  {C^t}'$.
+  The function $\op{compose}$ maps a $(\mathbb{B}, \tau)$-circuit $C := \langle
+  G, \Omega, \Sigma, \Lambda, L \rangle$, a sequence of relation sybmols $\tau_R
+  := (R_1, \ldots, R_t)$ such that $\tau_R \subseteq \tau$, a sequence of
+  circuits $\mathcal{C} := ( C^1, \ldots, C^t)$, where for each $i \in [t]$,
+  $C^i = \langle G_i, \Omega_i, \Sigma_i, \Lambda_i, L_i \rangle$ is a
+  $(\mathbb{B}_i, \tau_i)$-circuit, and $\tau_i \not\subset \tau_R$ and $C^i$
+  computes a query of arity $\arty(R_i)$ to a circuit $\op{compose}(C,
+  \mathcal{C}, \tau_R) := C' := \langle G', \Omega', \Sigma', \Lambda', L'
+  \rangle$. Note that all circuits take in structures of size $n$. The circuit
+  $C'$ is defined as follows.
+
+  Let ${C^0}' := \langle G_0', \Omega_0', \Sigma_0', \Lambda_0', L_0' \rangle :=
+  C$, and let $i \in [t]$. Let $D^{i-1}:= \op{insert} (C^i, {C^{i-1}}')$ and
+  $G^{i-1}_{R_i}$ be the set of all relational gates in $D^{i-1}$ labelled by
+  the relational symbol in $R_i$. Let ${C^{i-1}}' := \langle G_i', \Omega_i',
+  \Sigma_i', \Lambda_i', L_i' \rangle$ be the circuit formed from $D^{i-1}$ by
+  replacing each gate in $g \in G^{i-1}_{R_i}$ with the gate
+  $\Omega_{i}(\Lambda_{i-1}'(g))$ in $D^{i-1}$ (by repeated calls to the
+  $op{replace}$ function). Let $C' = {C^{t}}'$.
 \end{definition}
+
+% \begin{definition}
+%   The function $\op{concatenate}$ maps a $(\mathbb{B}, \tau)$-circuit $C :=
+%   \langle G, \Omega, \Sigma, \Lambda, L \rangle$, a sequence of relation
+%   sybmols $\tau_R := (R_1, \ldots, R_t)$ such that $\tau_R \subseteq \tau$, a
+%   sequence of circuits $\mathcal{C} := ( C^1, \ldots, C^t)$, where for each $i
+%   \in [t]$, $C^i = \langle G_i, \Omega_i, \Sigma_i, \Lambda_i, L_i \rangle$ is
+%   a $(\mathbb{B}_i, \tau_i)$-circuit, $\tau_i \not\subset \tau_R$ and $C^i$
+%   computes a query of arity $\arty(R_i)$, and $R$ is a relation symbol in
+%   $(\tau \setminus \tau_R) \cup (\bigcup_{1 \leq i \leq t},\tau_i))$ to a
+%   circuit $\op{concatenate}(C, \mathcal{C}, \tau_R, R) := C' := \langle G',
+%   \Omega', \Sigma', \Lambda', L' \rangle$. Note that all circuits take in
+%   structures of size $n$. The circuit $C'$ is defined as follows.
+
+%   Let ${C^0}' := \langle G^0, \Omega^0, \Sigma^0, \Lambda^0, L^0 \rangle :=
+%   C$. For each $i \in [t]$ fix a relation symbol $V_i \in \tau_i \setminus
+%   \tau_R$. For each $i \in [t]$ let ${C^{i}}' := \langle G_i', \Omega_i',
+%   \Sigma_i', \Lambda_i', L_i' \rangle := \op{insert} (C^i, {C^{i-1}}')$ be
+%   defined as follows. Let $D^{i-1}:= \op{insert} (C^i, {C^{i-1}}')$. Let
+%   $G_{R_i}$ be the set of all relational gates in $D^{i-1}$ labelled by the
+%   relational symbol in $R_i$. Let ${C^{i}}'$ be the circuit formed by
+%   replacing each gate in $g \in G_{R_i}$ with the gate
+%   $\Omega_{i}(\Lambda_{i-1}'(g))$ in $D^{i-1}$ (by repeated calls to the
+%   $op{replace}$ function) and using the $\op{tag}$ function on each gate
+%   $\Omega_i (\Lambda_{i-1}'(g))$ in $D^{i-1}$ using the tuple
+%   $\Lambda_{i-1}'(g)$ and the relation symbol $V_i$. We then let $C' :=
+%   {C^{t}}'$.
+
+%   %   For each relational gate $g$ in $D^{i-1}$ labelled by the symbol
+%   %   $R_i$,
+%   %   $\op{replace}$ $g$ with the gate $\Omega_{i}(\Lambda_{i-1}'(g))$ in
+%   %   $D^{i-1}$
+%   %   and $\op{tag}$ the gate $\Omega_i(\Lambda_{i-1}'(g))$ in $D^{i-1}$
+%   %   using
+%   %   the
+%   %   tuple $\Lambda_{i-1}'(g)$ and the relation symbol $R$. Output the
+%   %   circuit
+%   %   $C'
+%   %   := {C^t}'$.
+% \end{definition}
+% GW: do this tomorrow.
 
@@
 
-It can be shown that $\op(concatenate)$ can be computed in time polynomial in
-the sum of the sizes of the input circuits. Moreover, if the input circuits are
-all symmetric then the output circuit will be symmetric. Furthermore, if the
-input sequences of circuits and relations have just a single element, then if
-the input circuits have unique labels then the output circuit will have unique
-labels.
-
-\subsection{Transparency and Unique Extensions}
-\label{sec:transparency-and-unique-extensions}
-% In contrast with the work of Anderson and Dawar~\cite{AndersonD17}, the
-% circuit families we use to establish the main result of this paper are
-% additionally required to be transparent. In this subsection we briefly discuss
-% this condition, and present results suggesting its necessity.
-
-As mentioned earlier, the unique extensions condition plays a crucial role in
-the definition of needed theoretical tools, such as supports, and for proving
-the existence of polynomial-time algorithms computing important functions, such
-as the coarsest supporting partition or the orbit of a gate (see Proposition
-\ref{lem:computing support}).
-
-In this subsection we show that if a circuit is transparent then it may be
-transformed in polynomial time into an equivalent circuit with unique labels.
-Since we already have that circuits with unique labels have unique extensions
-(see Proposition \ref{prop:unique-labels-unique-extensions}), it follows that we
-may assume, without a loss of generality, that $P$-uniform families of
-transparent circuits have unique labels, and hence unique extensions. We also
-discuss relevant special cases and the motivate the explicit requirement that
-the $P$-uniform families of circuit referenced in the main result of this paper
-consist of transparent circuits.
-
-% Anderson and Dawar~\cite{AndersonD17} introduce the notion of a `rigid'
-% circuit, a condition analogous to the rigidity condition defined in this
-% paper. The following
-
-% \begin{definition}
-%   We say a circuit $C_n$ is que labels it has unique extensions. We finally
-%   discuss th\emph{rigid} if it has injective labels and for every pair of
-%   gates $(g, g')$ in $C_n$ such that $H_g = H_{g'}$ and $g \equiv g'$.
-% \end{definition}
-
-We first show that the syntactic equivalence relation can be efficiently
-computed for transparent circuits.
-
-\begin{remark}
-  I have introduced the notion of a syntactically transparent class. The reason
-  I did this seems to have dissipated, I will probably remove this definition
-  and simply the statement of the below proposition.
-\end{remark}
+It can be shown that $\op{compose}$ can be computed in time polynomial in the
+sum of the sizes of the input circuits. Moreover, if the input circuits are all
+symmetric then the output circuit will be symmetric. Also, for an input tuple
+$(C, \mathcal{C}, \tau_R)$, we have that if $C$ has symmetric gates and
+transparent, and all the circuits in $\mathcal{C}$ are transparent, then $C' :=
+\op{compose}(C, \mathcal{C}, \tau_R)$ is transparent. If $C$ does not have
+symmetric gates then, as the output gates of the circuits in $\mathcal{C}$ are
+no longer labelled as output gates in $C'$, it may be that some of these gates
+are syntactically-equivalent in $C'$, resulting in $C'$ not being transparent.
+
+In certain contexts we are interested composing gates such that if the input circuits are
+transparent (resp. have unique labels) then the output circuits will be
+transparent (resp. have unique labels). In this case, while composing the
+circuits we could apply the $\op{tag}$ function to the output gates of the
+circuits in the input sequence. We now define the function
+$\op{compose-and-tag}$ that implements this mapping.
 
 \begin{definition}
-  We say a class of circuits $\mathcal{C}$ is \emph{syntactically transparent}
-  if there is an algorithm that takes in a circuit $C \in \mathcal{C}$ and
-  outputs the syntactic equivalence relation on the gates of $C$ and runs in
-  time polynomial in the size of the input circuit.
+  The function $\op{compose-and-tag}$ maps a $(\mathbb{B}, \tau)$-circuit $C :=
+  \langle G, \Omega, \Sigma, \Lambda, L \rangle$, a sequence of relation symbols
+  $\tau_R := (R_1, \ldots, R_t)$ such that $\tau_R \subseteq \tau$, a sequence
+  of circuits $\mathcal{C} := ( C^1, \ldots, C^t)$, where for each $i \in [t]$,
+  $C^i = \langle G_i, \Omega_i, \Sigma_i, \Lambda_i, L_i \rangle$ is a
+  $(\mathbb{B}_i, \tau_i)$-circuit, and $\tau_i \not\subset \tau_R$ and $C^i$
+  computes a query of arity $\arty(R_i)$ to a circuit $\op{compose-and-tag}(C,
+  \mathcal{C}, \tau_R, R) := C'$. The circuit $C'$ is defined as follows. Note
+  that all circuits take in structures of size $n$.
+
+  Let $D^0 := \op{compose}(C, \mathcal{C}, \tau_R)$. For each $i \in [t]$, let
+  $D^{i} := \op{tag-all}(D^{i-1}, R, \img(\Omega^{-1}_i), \Omega^{-1}_i)$. Let
+  $C' := D^t$.
 \end{definition}
 
-\begin{prop}
-  Any class of transparent circuits is syntactically transparent.
-  % Let $C_n := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a
-  % $(\mathbb{B},
-  % \tau)$-circuit with unique labels. There is a deterministic algorithm that
-  % takes in such a circuit and outputs the syntactic equivalence relation on
-  % $G$.
-  % Moreover, this algorithm runs in time polynomial in the size of the circuit.
-  \label{prop:unique-labels-syntactic-equiv}
-\end{prop}
-\begin{proof} Let $C_n := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a
-  transparent $(\mathbb{B}, \tau)$-circuit. We define a relation $\sim$ by
-  induction on height (i.e. distance from an input gate). This relation will be
-  the syntactic equivalence relation on $G$. It is easy to check the conditions
-  for syntactic equivalence for gates of height 0 as all such gates are input
-  gates and so are either constant gates or relational gates. Suppose $g$ and
-  $h$ are gates of height greater than zero. We only need to check conditions
-  (i), (iv) and (v) of syntactic equivalence. It is easy to check (i) and (v).
-  If either condition is false then $g$ and $h$ are not syntacticly equivalent.
-  So suppose $g$ and $h$ are two internal gates such that $\Sigma (g) =
-  \Sigma(h)$ and suppose that if they are both output gates then $\Omega^{-1}(g)
-  = \Omega^{-1}(h)$. It remains to check if $L(g)/{\sim}$ and $L(h)/{\sim}$ are
-  isomorphism equivalent. First check if $H_h /{\sim} = H_g /{\sim}$. If not,
-  $g$ and $h$ are not syntactically equivalent. So suppose $H_h /{\sim} = H_g
-  /{\sim}$. If $g$ and $h$ are symmetric gates then $H_h /{\sim} = H_g/{\sim}$
-  if, and only if, $L(g)/{\sim}$ and $L(h)/{\sim}$ are isomorphism equivalent,
-  so let $g \sim h$. If $g$ and $h$ are not symmetric gates then, since $C_n$ is
-  transparent, $g$ and $h$ have unique labels. We thus have that $L(g)/{\sim}$
-  and $L(h)/{\sim}$ are isomorphism equivalent if, and only if, $L(g)^{-1}L(h)$
-  acts like an isomorphism. This can be checked by first checking that the
-  function induces a sorted permutation on the universe of $g$ (which can be
-  checked efficiently). This is sufficient as $L(g)(L(g)^{-1}L(h)) = L(h)$.
-
-  It is easy to see that, given a reasonable binary encoding of a circuit, the
-  above procedure can be implemented so as to run in polynomial time, and that
-  the relation $\sim$ is the syntactic equivalence relation on $C_n$.
-\end{proof}
-
-\begin{prop}
-  Let $C_n \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a transparent
-  $(\mathbb{B}, \tau)$-circuit. There is an algorithm that that takes in such a
-  circuit and outputs a $(\mathbb{B} \cup \mathbb{B}_{\std}, \tau)$-circuit $C'$
-  such that $C$ and $C'$ compute the same function, $C'$ has unique labels, and
-  if $C$ is symmetric then $C'$ is symmetric. Moreover, this algorithm runs in
-  time polynomial in the size of the input circuit.
-  \label{prop:transparent-unique}
-\end{prop}
-\begin{proof}
-  Let $C' := \op{make-injective-all}(\op{merge-all} (C, G))$. We have that $C'$
-  is symmetric if $C$ is symmetric. Since the syntactic equivalence relation can
-  be computed in polynomial time for circuits in $\mathcal{C}$ it follows that
-  this operation can be implemented so as to run in time polynomial in the size
-  of $C$. Clearly every gate $g$ in $C'$ belongs to a singleton syntactic
-  equivalence class.
-\end{proof}
-
-Anderson and Dawar~\cite{AndersonD17}, in their study of circuits with symmetric
-gates, show that such circuits may be transformed in polynomial time into
-equivalent circuits with unique extensions. They do this by showing that a
-circuit with symmetric gates may be transformed into an equivalent \emph{rigid}
-circuit in polynomial time and that all rigid circuits have unique extensions.
-We have similarly shown that transparent circuits can be translated into
-equivalent circuits with unique labels in polynomial time and that circuits with
-unique labels have unique extensions. Since all circuits with symmetric gates
-are transparent, this is a generalisation of their result.
-
-It is natural to ask if the requirement in the main theorem of this paper that
-the circuits be transparent is strictly necessary. It may be that, just as for
-the case of circuits with symmetric gates, a circuit (not necessarily
-transparent) can be transformed in polynomial time into an equivalent
-transparent circuit. While we do not address this question exactly, we do show
-that the problem of computing the syntactic equivalence relation for a circuit
-is at least as hard as the graph isomorphism problem. We also show that that the
-related problems of checking if given gate in a circuit has unique labels or has
-unique extensions (in a sense we define below) are all also at least as hard as
-the graph isomorphism problem. We move on to show that computing other basic
-facts about the circuit, such as the orbit of a gate, is also at least as hard
-as the graph isomorphism problem.
-
-% ,; address two related decision problems in Proposition \ref{} and Corollaries
-% \ref{} and \ref{}. In partic
-
-% As we will show in Proposition \ref{}, formulas of $\FPR$ can be translated
-% into. For this transparent circuits. However, the transformation is
-% complicated by the requirement that the resultant circuit be transparent.
-% However, it is worth asking if the transparency condition is required, i.e. if
-% it can be shown that
-
-% \emph{rigid} circuit. They show that all circuits such circuits can be
-% transformed into equivalent rigid circuits . They show that if a circuit is
-% rigid then it has unique extensions and that every circuit with injective
-% labels and symmetric gates can be transformed into an equivalent rigid circuit
-% in polynomial time. We have similarly shown that a transparent circuit can be
-% transformed into an equivalent one with unique labels in polynomial time, and
-% that circuits with unique labels have unique extensions. Moreover, since all
-% circuits with symmetric gates and injective labels are transparent, this is a
-% strict generalisation of their result.
-
-% and they show that a symmetric gate
-
-% Using the language developed in this paper, a circuit $C_n$ is \emph{rigid} if
-% it has injective labels and there are no two gates $g$ and $h$ in $C_n$ such
-% that $g$ and $h$ are syntactically equivalent. Since their discussion is
-% limited to circuits with symmetric gates and injective labels this is equ
-
-% circuit, a condition analogous to the rigidity condition defined in this
-% paper. The following
-
-% It is worth noting that all symmetric circuits are transparent, and
-
-% prove that it's a sufficient condition for establishing the uniqueness of the
-% induced automorphism on the circuit. Moreover, they prove that any circuit
-% (noting that they limit themselves to a discussion of circuits over a
-% symmetric basis) may be transformed into an equivalent rigid circuit in
-% polynomial time. As such, they may assume $P$-uniform symmetric circuit
-% families are rigid without a loss of generality, and hence be may assume
-% without a loss of generality that each permutation in $\sym_n$ uniquely
-% extends to an automorphism of the circuit.
-
-% However, in this subsection we show that deciding the rigidity of circuits
-% over bases which may include non-symmetric functions is at least as hard as
-% the graph isomorphism problem. However, we shoudl that on classes
-
-% Although the rigidity condition we present in this paper is similarly defined,
-% the existence of a polynomial-time computable transformation of a circuit into
-% an equivalent rigid circuit is not as straight forward. Indeed, it is possible
-% to show that the problem of determining if a given $(\mathbb{B},
-% \tau)$-circuit is rigid is as least as hard as the graph isomorphism problem.
-% This is a direct consequence of the following result.
-
-% \begin{definition}
-%   The \emph{syntactic equivalence class problem} is the decision problem for
-%   the set of all triples $(C, g_1, g_2)$, where $C$ is a $(\mathbb{B},
-%   \tau)$-circuit, and $g_1$ and $g_2$ are two syntactically equivalent gates
-%   in $C$.
-% \end{definition}
-
-% \begin{definition}
-%   The \emph{rigidity problem} is the decision problem for the set of all
-%   circuits $C$ where $C$ is a rigid circuit.
-% \end{definition}
-
-% \begin{definition}
-%   The \emph{unique labels problem} is the decision problem for the set of all
-%   circuits $C$ where $C$ has unique labels.
-% \end{definition}
-
-% \begin{prop}
-%   Let $\tau$ be any non-empty relational vocabulary and let $n, r, p \in
-%   \nats$ with $p$ prime. There is a a polynomial time reduction from the graph
-%   isomorphism problem to the problem of deciding if a given pair of gates in a
-%   given symmetric rank-circuit for structures of size $n$ that (i) has
-%   injective labels, (ii) contains no constant gates, and (iii) contains at
-%   most two rank gates with bound $r$ and prime $p$, are syntactically
-%   equivalent.
-%   \label{prop:syntactic-graph-iso}
-% \end{prop}
-% \begin{proof}
-%   We have from \cite{} that there is a polynomial time reduction from the
-%   graph isomorphism problem to the bipartite isomorphism problem. The
-%   bipartite isomorphism problem is the decision problem for the set of all
-%   pairs of partitioned bipartite graphs $B_1 := (U_1, V_1, E_1)$ and $B_2 :=
-%   (U_2, V_2, E_2)$ such that there exists a graph isomorphism $\pi : B_1
-%   \rightarrow B_2$ with $\restr{\pi}{U_1} = U_2$ and $\restr{\pi}{V_1} = V_2$.
-
-%   Suppose we are given two partitioned bipartite graphs $B_1 := (U_1, V_1,
-%   E_1)$ and $B_2 := (U_2, V_2, E_2)$. We assume, without a loss of generality,
-%   that there exists $a, b \in \nats$ such that $U_1 = U_2 = [a]$ and $V_1 =
-%   V_2 = [b]$.
-
-%   Let $R$ be a relation symbol in $\tau$ and let $k := \arty{R}$. Let $G_{R}
-%   := \{g_{R, \vec{c}} : \vec{c} \in [n]^k\}$, $G_{\text{mid}} := \{\land_0,
-%   \land_1, \neg_0, \land_{\text{out}} \}$, $G_{\rank} : = \{ g_{\rank, 1},
-%   g_{\rank, 2}\}$, and $G_{\land} := \{g_{i, (u,v)} : i \in [2] \, (u,v) \in
-%   E_i \}$. Let $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a
-%   $(\{\rank^{1}_2\}, \tau)$-circuit defined as follows. Let $G = G_R \cup
-%   G_{\text{mid}} \cup G_{\rank} \cup G_{\land}$ and $\Omega$ be the $0$-ary
-%   function $\land_{\text{out}}$. For each $\vec{c} \in [n]^{\arty{R}}$ let
-%   $\Lambda(\vec{c}) = g_{R, \vec{c}}$. Define $\Sigma$ as follows. For each $g
-%   \in G$,
-%   \begin{itemize}
-%     \setlength\itemsep{0mm}
-%   \item if $g \in G_R$ then $\Sigma(g) = R$,
-%   \item if $g$ equals $\land_0$ or $\land_1$ then $\Sigma(g) = \land[n^k]$
-%   \item if $g$ equals $\land_{\text{out}}$ then $\Sigma(g) = \land[2]$,
-%   \item if $g \in G_\rank$ let $\Sigma(g) = \rank^r_p [a,b]$, and
-%   \item if $g \in G_{\text{in}}$ and $g$ then $\Sigma(g) = \land[1]$.
-%   \end{itemize}
-%   Define $L$ as follows. For each $g \in G$,
-%   \begin{itemize}
-%     \setlength\itemsep{0mm}
-%   \item if $g \in G$ and $g = g_{\text{out}}$ then for each $i \in [2]$,
-%     $L(g)(i) := g_{\rank, i}$,
-%   \item if $g \in G_\rank$ and $g = g_{\rank, i}$ then $L(g)(p,q) = g_{i,
-%     (p,q)}$,
-%   \item if $g \in G_{\land}$ and $g = g_{i, (p,q)}$ then $L(g)(1) = \land_1$
-%     if $(p,q) \in E_i$ and $L(g)(1) = \neg_0$ otherwise,
-%   \item if $g = \neg_0$ then $L(g)(1) = \land_0$, and
-%   \item if $g = \land_0$ or $g = \land_1$ then for all $p \in [n^k]$ we have
-%     that $L(g)(p)$ equals $\Lambda^{-1}(\vec{c}_p)$, where $\vec{c}_p$ is the
-%     $p$th element of $[n]^k$ in the lexicographical ordering on $[n]^k$.
-%   \end{itemize}
-
-%   We note that for $i \in [2]$, $L(g_{\rank, i})(p,q) = \land_1$ if $(p,q)$ is
-%   an edge in in $B_i$ and $L(g_\rank, i)(p,q) = \neg_0$ if $(p,q)$ is not an
-%   edge in $B_i$. We thus have that $B_1$ and $B_2$ are bipartite isomorphic
-%   (in the sense defined above) if, and only if, $g_{\rank, 1}$ is
-%   syntactically equivalent to $g_{\rank, 2}$.
-
-%   Since the construction of $C_n$ can be implemented in time polynomial in the
-%   combined sizes of the input graphs, the mapping of $(B_1, B_2)$ to the tuple
-%   $(C_n, (g_{\rank, 1}, g_{\rank, 2}))$ witnesses the reduction. The result
-%   follows.
-% \end{proof}
-\begin{prop}
-  Let $\tau$ be any non-empty relational vocabulary and let $n, r, p \in \nats$,
-  with $p$ prime. There is a a polynomial time reduction from the graph
-  isomorphism problem to the problem of deciding if a given pair of gates in a
-  given symmetric rank-circuit for structures of size $n$ that (i) has injective
-  labels, (ii) contains no constant gates, and (iii) contains at most two rank
-  gates with bound $r$ and prime $p$, are syntactically equivalent.
-  \label{prop:syntactic-graph-iso}
-\end{prop}
-\begin{proof}
-  We have from \cite{} that there is a polynomial time reduction from the graph
-  isomorphism problem to the bipartite isomorphism problem. The bipartite
-  isomorphism problem is the decision problem for the set of all pairs of
-  partitioned bipartite graphs $B_1 := (U_1, V_1, E_1)$ and $B_2 := (U_2, V_2,
-  E_2)$ such that there exists a graph isomorphism $\pi : B_1 \rightarrow B_2$
-  with $\restr{\pi}{U_1} = U_2$ and $\restr{\pi}{V_1} = V_2$.
-
-  Suppose we are given two partitioned bipartite graphs $B_1 := (U_1, V_1, E_1)$
-  and $B_2 := (U_2, V_2, E_2)$. We assume, without a loss of generality, that
-  there exists $a, b \in \nats$ such that $U_1 = U_2 = [a]$ and $V_1 = V_2 =
-  [b]$.
-
-  Let $R$ be a relation symbol in $\tau$ and let $k := \arty{R}$. Let $G_{R} :=
-  \{g_{R, \vec{c}} : \vec{c} \in [n]^k\}$, $G_{\text{mid}} := \{\land_0,
-  \land_1, \neg_0, \land_{\text{out}} \}$, $G_{\rank} : = \{ g_{\rank, 1},
-  g_{\rank, 2}\}$, and $G_{\land} := \{g_{i, (u,v)} : i \in [2] \, (u,v) \in E_i
-  \}$. Let $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a
-  $(\{\rank^{1}_2\}, \tau)$-circuit defined as follows. Let $G = G_R \cup
-  G_{\text{mid}} \cup G_{\rank} \cup G_{\land}$ and $\Omega$ be the $0$-ary
-  function $\land_{\text{out}}$. For each $\vec{c} \in [n]^{\arty{R}}$ let
-  $\Lambda(\vec{c}) = g_{R, \vec{c}}$. Define $\Sigma$ as follows. For each $g
-  \in G$,
-  \begin{itemize}
-    \setlength\itemsep{0mm}
-  \item if $g \in G_R$ then $\Sigma(g) = R$,
-  \item if $g$ equals $\land_0$ or $\land_1$ then $\Sigma(g) = \land[n^k]$
-  \item if $g$ equals $\land_{\text{out}}$ then $\Sigma(g) = \land[2]$,
-  \item if $g \in G_\rank$ let $\Sigma(g) = \rank^r_p [a,b]$, and
-  \item if $g \in G_{\text{in}}$ and $g$ then $\Sigma(g) = \land[1]$.
-  \end{itemize}
-  Define $L$ as follows. For each $g \in G$,
-  \begin{itemize}
-    \setlength\itemsep{0mm}
-  \item if $g \in G$ and $g = g_{\text{out}}$ then for each $i \in [2]$,
-    $L(g)(i) := g_{\rank, i}$,
-  \item if $g \in G_\rank$ and $g = g_{\rank, i}$ then $L(g)(p,q) = g_{i,
-      (p,q)}$,
-  \item if $g \in G_{\land}$ and $g = g_{i, (p,q)}$ then $L(g)(1) = \land_1$ if
-    $(p,q) \in E_i$ and $L(g)(1) = \neg_0$ otherwise,
-  \item if $g = \neg_0$ then $L(g)(1) = \land_0$, and
-  \item if $g = \land_0$ or $g = \land_1$ then for all $p \in [n^k]$ we have
-    that $L(g)(p)$ equals $\Lambda^{-1}(\vec{c}_p)$, where $\vec{c}_p$ is the
-    $p$th element of $[n]^k$ in the lexicographical ordering on $[n]^k$.
-  \end{itemize}
-
-  We note that for $i \in [2]$, $L(g_{\rank, i})(p,q) = \land_1$ if $(p,q)$ is
-  an edge in in $B_i$ and $L(g_\rank, i)(p,q) = \neg_0$ if $(p,q)$ is not an
-  edge in $B_i$. We thus have that $B_1$ and $B_2$ are bipartite isomorphic (in
-  the sense defined above) if, and only if, $g_{\rank, 1}$ is syntactically
-  equivalent to $g_{\rank, 2}$.
-
-  Since the construction of $C_n$ can be implemented in time polynomial in the
-  combined sizes of the input graphs, the mapping of $(B_1, B_2)$ to the tuple
-  $(C_n, (g_{\rank, 1}, g_{\rank, 2}))$ witnesses the reduction. The result
-  follows.
-\end{proof}
-
-We have from Proposition \ref{prop:syntactic-graph-iso} that the problem of
-computing the syntactic equivalence relation, even if we restrict the input
-circuit to have very particular properties, as least as hard as the graph
-isomorphism problem. Since there is a trivial reduction from the problem of
-computing the syntactic equivalence relation over a restricted class of circuits
-to the general problem we have the following corollary.
-
-\begin{cor}
-  There is a polynomial-time reduction from the graph isomorphism problem to the
-  problem of determining if a given pair of gates in a given $(\mathbb{B},
-  \tau)$-circuit are syntactically equivalent.
-  \label{lem:syntactically-equivilent-general-hard}
-\end{cor}
-
-We also have a reduction from the problem of computing the syntactic equivalence
-relation to the problem of deciding if a given gate has unique labels.
-
-\begin{lem}
-  There are a polynomial-time reduction from the problem of determining if a
-  given pair of gates in a given $(\mathbb{B}, \tau)$-circuit are syntactically
-  equivalent to the problems of determining if a given gate in a given circuit
-  has unique labels.
-  \label{lem:syntactically-equivalent-unique-labels}
-\end{lem}
-
-\begin{proof}
-  Let $C_n := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a circuit and
-  let $g_1, g_2 \in G$. Let $D_n$ be the circuit formed from $C_n$ by removing
-  every gate $g \in G \setminus\{g_1, g_2\}$ such that $\neg W_t(g, g_1) \land
-  \neg W_t(g, g_2)$ (i.e. all those gates in the circuit such that there is no
-  path from them to either of the two gates). Let $C_n'$ be the circuit formed
-  from $D_n$ by adding in a single two-input $\AND$ gate $g'$ and connect both
-  $g_1$ and $g_2$ as inputs to $g'$ Moreover, we let this $g'$ be the single
-  output gate of $C_n'$.
-
-  It follows that $g_1 \equiv g_2$ in $C_n$ if, and only if, $g'$ has unique
-  labels in $C_n'$. Since the construction of $C_n'$ from $C_n$ can be completed
-  in polynomial time, the mapping of $(C_n, (g_1, g_2))$ to $(C_n', g')$
-  witnesses the reduction.
-\end{proof}
-
-We can construct a similar argument reducing the problem of deciding if two
-gates are syntactically equivalent to the problem of deciding if a given gate
-$g$ in a circuit $C_n$ has the property that there exists a permutation and two
-automorphisms extending that permutation that disagree with each other on $g$.
-
-\begin{lem}
-  There is a polynomial-time reduction to the problem from the problem of
-  determining if a given pair of gates gates in a given $(\mathbb{B},
-  \tau)$-circuit are syntactically equivalent to the problem of determining if
-  for a given triple $(C_n, g)$, where $C_n$ is a circuit, $g$ is a gate in
-  $C_n$, that there exists $\sigma \in \sym_n$ and automorphisms $\pi, \pi' \in
-  \aut(C_n)$ extending $\sigma$ such that $\pi (g) \neq \pi' (g)$.
-  \label{lem:syntactically-equivilent-unique-extensions}
-\end{lem}
-\begin{proof}
-  Let $C_n$ be a circuit and let $g_1$ and $g_2$ be two gates in $C_n$. Note
-  that for any gate $g$ in $\sigma \in sym_n$, if $\pi, \pi' \in \aut(C_n)$
-  extend $\sigma$ and $\pi_e := \pi'\pi{-1}$ then $\pi(g) \neq \pi'(g)$ if, and
-  only if, $\pi_e (g) \neq g$. It follows that there exists $\sigma \in sym_n$
-  such that there are automorphisms $\pi, \pi' \in \aut(C_n)$ extending $\sigma$
-  such that $\pi (g) \neq \pi'(g)$ if, and only if, there exists $\pi_e$
-  extending the trivial permutation such that $\pi (g) \neq g$.
-
-  Let $C_n'$ be the circuit constructed in the proof of Lemma
-  \ref{lem:syntactically-equivalent}. Let $\pi_e$ be a function from the gates
-  of $C_n$ to the gates of $C_n$ that swaps $g_1$ and $g_2$ and fixes all other
-  gates. Then if $g_1 \equiv g_2$ then $\pi_e$ is an automorphism extending the
-  trivial permutation. Moreover, if there exists an automorphism $\pi_e$
-  extending the trivial permutation such that $\pi_e(g_1) \neq g_1$ then it must
-  be that $\pi_e (g_1) = g_2$ and $\pi_e(g_2) = \pi(g_1)$, and so $g_1 \equiv
-  g_2$.
-
-  It follows that the mapping $(C_n, (g_1, g_2))$ to $(C_n', g_1)$ witnesses the
-  reduction and the result follows.
-\end{proof}
-
-We have shown in Proposition \ref{prop:syntactic-graph-iso}, Lemma
-\ref{lem:syntactically-equivalent-unique-labels} and Lemma
-\ref{lem:syntactically-equivilent-unique-extensions}, that various problems
-perhaps related to the problem of translating a circuit into an equivalent
-transparent circuit are at least as hard as the graph isomorphism problem. We
-now show that additionally recognising if a circuit has unique extensions is at
-least as hard as the graph isomorphism problem.
-
-\begin{lem}
-  There is a polynomial-time reduction from the graph isomorphism problem to the
-  problem of determining if a given circuit does not have unique extensions.
-  \label{lem:unique-extensions-hard}
-\end{lem}
-\begin{proof}
-  We use a similar argument as for Proposition \ref{prop:syntactic-graph-iso}.
-  We again argue using a reduction from thee bipartite isomorphism problem. Let
-  $B_1 := (U_1, V_1, E_1)$ and $B_2 := (U_2, V_2, E_2)$ and let $C_n$ be the
-  associated circuit defined in the proof of Proposition
-  \ref{prop:syntactic-graph-iso}. Let $C_n' = \op{merge-all} (C_n, G_{\land})$.
-  Notice that $B_1$ and $B_2$ are isomorphic if, and only if, $g_{\rank, 1}$ and
-  $g_{\rank, 2}$ are syntactically equivalent, which holds if, and only if,
-  there exists $\pi \in \aut(C_n')$ extending the trivial permutation such that
-  $\pi (g_{\rank, 1}) = g_{\rank, 2}$, which is true if, and only if, $C_n'$
-  does not have unique extensions. The mapping $(B_1, B_2)$ to $C_n'$ thus
-  witnesses the reduction.
-\end{proof}
-
-\begin{remark}
-  It's interesting to note that the circuit used in the reduction does not have
-  injective labels. If we instead ask about a reduction from GI to the problem
-  of deciding if a circuit has unique extensions and injective labels, then I
-  can reduce from to the problem of deciding if two rigid graphs are isomorphic.
-  It is unknown if this decision problem is as hard as the full graph
-  isomorphism problem. After looking around a bit I discovered that it's a very
-  important open problem in quantum computation. Is this worth mentioning?
-\end{remark}
-
-We have that if a circuit is transparent then we may compute in polynomial time
-the syntactic equivalence relation on the gates of that circuit, and hence
-compute an equivalent circuit that has unique extensions. However, we've shown
-that absent the transparency condition, computing the the syntactic equivalence
-relation is at least as hard as the graph isomorphism problem. Moreover, other
-properties that can be computed in polynomial time for transparent circuits,
-e.g. deciding if particular gates have unique labels or might act as
-counterexamples to the unique extensions, have also been shown to be at least as
-the graph isomorphism problem.
-
-While we have not shown that there is no polynomial time algorithm that
-translates an arbitrary circuit into an equivalent transparent circuit, we have
-provided evidence in favour of the conjecture that such an algorithm might not
-exist.
-
-\begin{remark}
-  I really don't like the slightly vague language here. I would prefer to say
-  this differently. How does one provide `evidence' that a functional problem is
-  hard, when one has proved results about a few related decision problems?
-\end{remark}
-
-However, we must then address another question: If we must include an explicit
-requirement on circuits, why not simply require that the circuit have unique
-extensions? But we have from Lemma \ref{lem:unique-extensions-hard} that at the
-least verifying that a circuit have unique extensions is at least as hard as the
-graph isomorphism problem. We show that, in contrast, deciding if a circuit is
-transparent is in $\PT$.
-
-\begin{prop}
-  There is an algorithm that takes as input a circuit, decides if that circuit
-  is transitive and runs in time polynomial in the size of the circuit.
-  \label{prop:tansitive-polynomial-time}
-\end{prop}
-\begin{proof}
-  Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
-  \tau)$-circuit. We first check that, for each non-symmetric gate $g \in G$,
-  $L(g)$ is an injection. If not, we return that $C$ is not transitive.
-
-  The height of a gate $g$ in the circuit is the distance from $g$ to the set of
-  input gates. For each $p \in nats$ let $G^p \subseteq G$ be the set of all
-  gates of height $p$ and let $G^{\leq p} = \bigcup_{0 \leq i \leq p}G^i$. Note
-  that each $g \in G^1$, $g$ has unique labels. Thus, from Lemma \ref{}, we can
-  compute the syntactic equivalence relation between gates in $G^{\leq 1}$
-  efficiently. We construct a loop as follows. Let $p$ be initialised to $1$. We
-  have that every non-symmetric gate $g \in G^{\leq p}$ has unique gates. We
-  compute the syntactic equivalence relation on $G^{\leq p}$ and check if each
-  non-symmetric gate in $g \in G^{i + 1}$ has unique labels. If not, halt and
-  output that the circuit is not transitive. If $p = \depth(C) -1$ then halt and
-  output that the circuit is transitive. If neither halt state is reached, then
-  increment $p$ by one and continue to the next iteration of the loop.
-
-  We note that in every iteration of the loop we have that every non-symmetric
-  gate in $G^{\leq p}$ has unique labels. Thus, from Proposition
-  \ref{prop:unique-labels-syntactic-equiv}, we may compute the syntactic
-  equvilence relation on this set of gates efficiently. Thus it is easy to see
-  that the above algorithm can be implemented so as to run in polynomial time.
-\end{proof}
-
-A similar result for circuits with unique labels.
-
-\begin{cor}
-  There is an algorithm that takes in a circuit and decides if that circuit has
-  unique labels and runs in time polynomial in the size of the circuit.
-\end{cor}
-\begin{proof}
-  Let $C$ be the input circuit. From Proposition
-  \ref{prop:transitive-polynomial-time} we may check if $C$ is transitive in
-  polynomial time. If $C$ is not transitive halt and output that $C$ does not
-  have unique labels. If $C$ is transitive then from Lemma \ref{} we may compute
-  the syntactic equivalence relation on the gates of $C$ efficiently. This then
-  allows us to check if each gate in $C$ has unique labels.
-\end{proof}
-
-We thus have that we can verify in polynomial time that a family of circuits
-indeed is transparent or has unique labels. The same cannot be said for the
-unique extensions property.
-
-It is also possible to show that we may compute orbits and supports on circuits
-with unique labels in polynomial-time (recall that we may assume, without a loss
-of generality, that transparent circuits have unique labels). The proof
-technique used here is analogous to the one used by Anderson and
-Dawar~\cite{AndersonD17}.
-
-\begin{lem}
-  Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit with unique labels of size $n$ and
-  $\sigma \in \sym_n$. There is an algorithm takes as input a circuit $C_n$ and
-  $\sigma \in \sym_n$ and outputs for each gate $g$ its image under the unique
-  automorphism extending $\sigma$ (if it exists). This algorithm runs in time
-  polynomial in the combined size of the input circuit and the encoding of the
-  permutation.
-  \label{lem:compute-automorphisms}
-\end{lem}
-\begin{proof}
-  Suppose $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$. We build up the
-  mapping $\pi$ extending $\sigma$ recursively. If at some point in the
-  recursive construction we arrive at a point where no mapping for $g$ can be
-  found we halt at that point and return that no automorphism exists.
-
-  Let $h$ be any gate in the circuit. Suppose $h$ is an input gate. If $h$ is a
-  constant gate then let $\pi (h) = h'$. If $h$ is a relational gate such that
-  $R := \Sigma(h)$ and check if there exists $h'$ such that $\Sigma (h') = R$
-  and $\sigma \Lambda_R(h) = \Lambda_R(h')$ and, if $h$ is an output gate then
-  $h'$ is an output gate such that $\sigma Omega^{-1}(h) = \Omega^{-1}(h')$. If
-  such a $h'$ does not exist halt and output that there is no automorphism
-  extending $\sigma$. We have from Lemma \ref{} that if such an $h'$ exists it
-  must be unique, and we set $\pi(h) = h'$.
-
-  Let $h$ be an internal gate in the circuit and assume we have defined $\pi
-  (g)$ for every gate $g$ of height less than $h$. Let $h'$ be a gate in the
-  circuit such that $\Sigma(h) = \Sigma (h')$, $\pi L(h)$ is isomorphism
-  equivalent to $L(h')$ and, if $h$ is an output gate then $h'$ is an output
-  gate such that $\sigma \Omega^{-1}(h) = \Omega^{-1}(h')$. Since $C_n$ has
-  unique labels we have that $\pi L(h)$ is isomorphism equivalent to $L(h')$ if,
-  and only if, $L(h')^{-1}\pi L(h)$ acts like an isomorphism. This can be
-  determined easily. If no such $h'$ exists halt and output that there is no
-  automorphism extending $\sigma$. We have from Lemma \ref{} that if $C_n$ has
-  unique labels then there is at most one such $h'$.
-
-  This recursive approach can be implemented as an algorithm that runs in time
-  polynomial in the combined size of the inputs and outputs the required
-  automorphism if it exists.
-\end{proof}
-
-This result uses a proof very similar to the one for a similar result proved by
-Anderson and Dawar~\cite{Anderson17D}.
-
-\begin{lem}
-  There is an algorithm that takes as input a circuit $C_n$ with unique labels
-  and decides if $C_n$ is symmetric. If $C_n$ is symmetric outputs the orbits
-  and coarsest supporting partitions of every gate. Moreover, this algorithm
-  runs in time polynomial in the size of the input circuit.
-  \label{lem:computing support}
-\end{lem}
-
-\begin{proof}
-  Suppose $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$. Let $(u, v) \in
-  \sym_n$ be a transposition. We may use Lemma \ref{lem:compute-automorphisms}
-  to determine the unique automorphism $\pi_{(u,v)}$ extending $(u, v)$. It is
-  easy to see that, since the set of transpositions generate $\sym_n$, for all
-  $(u,v) \in \sym_n$ $\pi_{(u,v)}$ the automorphism $\pi_{(u,v)}$ exists if, and
-  only if, $C_n$ is symmetric. We note that there are ${n}\choose{2}$
-  transpositions. It follows that we may check in polynomial time if $C_n$ is
-  symmetric. If $C_n$ is not symmetric we output that it is not symmetric and
-  halt.
-
-  Suppose then that $C_n$ is symmetric. For transposition $(u, v) \in \sym_n$,
-  let $\mathcal{P}_{(u,v)} := \{\{u,v\}\}\bigcup_{w \in [n] \setminus
-    \{u,v\}}\{\{w\}\}$ be a partition of $[n]$. We have that $\pi_{(u,v)}$ fixes
-  $g$ if, and only if, $\mathcal{P}_{(u,v)}$ supports $g$. Since we can
-  efficiently check if $\pi_{(u,v)}$ fixes $g$ it follows that we can
-  effeciently check if $\mathcal{P}_{(u,v)}$ supports $g$. Let $\mathcal{P}$ be
-  the result of combining the set consisting of those partitions
-  $\mathcal{P}_{(u,v)}$ that support $g$ using $\mathcal{E}$. From Proposition
-  \ref{prop:combining-supporting-patitions} we have that $\mathcal{P}$ supports
-  $g$. Suppose that $\mathcal{P}$ is not the coarsest supporting partition of
-  $g$. Then there exists a partition $\mathcal{P}'$ supporting $g$ such
-  $\mathcal{P}' \preceq P$ and $\mathcal{P}' \neq \mathcal{P}$. But then there
-  exists $P \in \mathcal{P}$ and $P' \in \mathcal{P}'$ such that $P \subsetneq
-  P'$. But then there exists $a , b \in P'$ such that $a \not\in P$. It follows
-  that the transposition $(a,b)$ fixes $\mathcal{P}'$ and so $\pi_{(a,b)}$ fixes
-  $g$, but then, $\mathcal{P}_{(a,b)}$ supports $g$ and so, from the
-  construction of $\mathcal{P}$, $\mathcal{P}$ is fixed by $(a,b)$. But
-  $\mathcal{P}$ is not fixed by $(a,b)$, so we have a contradiction. We thus
-  have that $\mathcal{P}$ is the coarsest supporting partition of $g$.
-
-  It remains to compute the orbit of a gate $g$. Let $S_0 := \{g\}$ and for each
-  $i \geq 0$ let $S_{i+1} := S_i \bigcup_{(u,v) \in \sym_n} \pi_{(u,v)}S_i$. Let
-  $S$ be the least fixed point. It is easy to see that $S \subseteq \orb(g)$ as
-  every gate in $S$ is equal to the action of some sequence of automorphisms
-  (extending transpositions) acting on $g$. Moreover, since the set of all
-  transpositions generates $\sym_n$, it follows that $\orb(g) \subseteq S$ and
-  so $\orb(g) = S$.
-
-  Given the polynomial bound on the number of transpositions, and the
-  polynomial-time bound on the algorithm from Proposition
-  \ref{prop:combining-supporting-partitions}, it is easy to see that the
-  procedures described above can be implemented so as to run in time polynomial
-  in the size of the input circuit.
-\end{proof}
-
-\begin{remark}
-  The above result shouldn't be here. They are about group theory, or rather
-  group action, I don't think they actually has anything to do with circuits.
-\end{remark}
-
-Once again we note that computing the orbit of a gate for a general circuit is
-as hard as the graph isomorphism problem. We make use of the ability to compute
-the orbit of a gate in polynomial time in sub-section
-\ref{sec:translating-formulas-to-FPR} when translating families of circuits into
-equivalent formulas. As such the approach in this paper would fail for the
-general circuit.
-
-\begin{prop}
-  There is a polynomial-time reduction from the graph isomorphism problem to the
-  problem of computing if two gates in a given circuit are in the same orbit.
-\end{prop}
-\begin{proof}
-  This is a really simple circuit similar to the one from an earlier
-  proposition. I will fill this result in later.
-\end{proof}
-
-% \begin{lem}
-%   There is a polynomial-time Turing reduction from the problem of determining
-%   if a given pair of gates in a given circuit are syntactically equivalent to
-%   the problem of deciding if a circuit is transparent.
-%   %   If the problem of deciding if a given circuit is transparent can be
-%   %   decided
-%   %   in
-%   %   polynomial time then the graph isomorphism problem is in polynomial
-%   %   time.
-% \end{lem}
-% \begin{proof}
-%   Suppose there is an algorithm that takes as input, runs in time polynomial
-%   in the size of the circuit, and decides whether or not the circuit is
-%   transparent.
-
-%   From Corollary \ref{} it is sufficient to show that there is a
-%   polynomial-time algorithm for the problem of deciding if a pair of gates in
-%   a given circuit are syntactically equivalent. Let $C_n$ be a circuit and
-%   $g_1$ and $g_2$ be two gates in the circuit.
-
-%   %   We simply need a polynomial-time reduction from the problem of computing
-%   %   t
-%   %   to the problem
-%   %   of checking if a given circuit is transparent. Let $C_n =\langle G,
-%   %   \Omega,
-%   %   \Sigma, \Lambda, L\rangle$ be a circuit and let $g_1$ and $g_2$ be two
-%   %   gates
-%   %   in $G$. We now construct a circuit $C_n'$. If $g_1 = g_2$ then let
-%   %   $C_n'$ be
-%   %   any transparent circuit. If $g_1$ and $g_2$ do not satisfy any of
-%   %   conditions
-%   %   (i), (ii), (iii) or (v) of syntactic equivalence then let $C_n'$ be any
-%   %   non-transparent circuit. So suppose all these conditions are met and
-%   %   $g_1
-%   %   \neq
-%   %   g_2$, then let $D_n$ be the sub-circuit of $C_n$ consisting of exactly
-%   %   those
-%   %   gates $g$ in $C_n$ such that $W_t(g, g_1)$ or $W_t(g, g_2)$. Then let
-%   %   $C_n'$
-%   %   be $D_n'$ with an additional gate $g_\rank$, such that $g_\rank $ is
-%   %   labelled
-%   %   by the function $\rank^1_2[2,1]$ and $g_\rank$
-% \end{proof}
-
-% \begin{corollary}
-% \end{corollary}
-
-% We have from this proposition that even many nice properties Since there is a
-% polynomial-time reduction from this problem reduces the general problem of
-% deciding the syntatic equivilence relation for an arbitary
-
-% \begin{corollary}
-%   There is a polynomial-time reduction from the graph isomorphism problem to
-%   the problem of determining if a given $(\mathbb{B}, \tau)$-circuit is rigid.
-% \end{corollary}
-
-% \begin{corollary}
-%   There is a polynomial-time reduction from the graph isomorphism problem to
-%   the problem of determining if a given gate in a given $(\mathbb{B},
-%   \tau)$-circuit has unique labels.
-% \end{corollary}
-
-% reduction from the graph isomorphism from to the problem of of computing the
-% the syntactic equivalence relation on the gates of an arbitrary $(\mathbb{B},
-% \tau)$-circuit.
-
-% It is worth noting that if we restrict the input to a class of circuits
-% defined over symmetric bases then we can decide the syntactic equivalence
-% relation in polynomial time.
-
-% % \begin{prop}
-% %   Let $C_n$ be a circuit with symmetric gates. There is an algorithm that
-% %   takes in such a circuit, runs in time polynomial in the size of the circuit,
-% %   and outputs the syntactic equivalence relation on the gates of $C_n$.
-% %   \label{prop:symmetric-syntactic}
-% % \end{prop}
-% % \begin{proof}
-% % \end{proof}
-
-% Moreover, it turns out that being able to compute the syntactic equivalence
-% relation in polynomial time for some class of circuits $\mathcal{C}$ implies
-% that the existence of a polynomial-time algorithm for converting circuits in
-% $C$ into equivalent rigid circuit.
-
-% % \begin{prop}
-% %   Let $\mathcal{C}$ be a set of circuits. Suppose the syntactic equivalence
-% %   relation can be computed in polynomial time for circuits in $\mathcal{C}$.
-% %   It follows that there is an algorithm that runs in polynomial time that
-% %   takes in a circuit $C \in \mathcal{C}$ and outputs a rigid circuit $C''$
-% %   such that if $C$ is symmetric then $C'$ is symmetric.
-% %   \label{prop:syntactic-equivilence-rigid}
-% % \end{prop}
-% % \begin{proof}
-% % \end{proof}
-
-% The following result gives us that the unique labels condition is sufficient.
-
-% % \begin{prop}
-% %   Let $\mathcal{C}$ be syntactically transparent class of circuits. It follows
-% %   that there exists an algorithm that takes in a $(\mathbb{B}, \tau)$-circuit
-% %   $C \in \mathcal{C}$ and outputs a $(\mathbb{B} \cup \mathbb{B}_{\std},
-% %   \tau)$-circuit $C'$ such that $C$ and $C'$ compute the same function, $C'$
-% %   is rigid, and if $C$ is symmetric then $C'$ is symmetric. Moreover, this
-% %   algorithm runs in time polynomial in the size of the input circuit.
-% % \end{prop}
-% % \begin{proof}
-% %   Let $C' = \make-injective-all(\op{merge-all} (C, G)($). We have that $C'$ is
-% %   symmetric if $C$ is symmetric. Since the syntactic equivalence relation can
-% %   be computed in polynomial time for circuits in $\mathcal{C}$ it follows that
-% %   this operation can be implemented so as to run in time polynomial in the
-% %   size of $C$. Clearly every gate $g$ in $C'$ belongs to a singleton syntactic
-% %   equivalence class.
-% % \end{proof}
-
-% \begin{lem}
-%   Let $\mathbb{B}$ be a basis of symmetric functions. Then for any class of
-%   circuits $\mathcal{C}$ defined over the basis $\mathbb{B}$, $\mathcal{C}$ is
-%   a syntactically transparent class of circuits.
-% \end{lem}
-% In contrast to
-% \begin{lem}
-%   If the class of all circuits is syntactically transparent then then graph
-%   isomorphism problem is in $\PT$.
-% \end{lem}
-
-% \begin{lem}
-%   Let $\mathcal{C}$ be a syntactically transparent class of circuits. There is
-%   an algorithm that takes as input a $(\mathbb{B}, \tau)$-circuit $C \in
-%   \mathcal{C}$ and decides if $C$
-% \end{lem}
-
-% Since the class of The following result, also proved by Anderson and Dawar
-% \cite{AndersonD17}, follows as a corollary.
-
-% \begin{lem}
-%   Let $\mathcal{C}$
-% \end{lem}
-
-% \begin{lem}
-%   Let $C_n = \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a $(\mathbb{B},
-%   \tau)$-circuit computing a $q$-ary query. If $C_n$ has unique labels then it
-%   is $C_n$ rigid
-%   \label{lem:unique-implies-rigid}
-% \end{lem}
-% \begin{proof}
-
-%   %   Suppose there exists a gate $g'$ such that $W_t (g, g')$ and $W_t
-%   %   (\pi(g),
-%   %   g')$ and $\pi (g') = g'$, then $\pi H_{g'} = H_{g'}$, and since $g'$ has
-%   %   unique labels it follows that $\pi$ acts trivially on $H_{g'}$ (i.e. for
-%   %   all
-%   %   $h \in H_{g'}$, $\pi(h) = h$). Moreover, for any pair of gates $h,h' \in
-%   %   G$
-%   %   such that $W(h, h')$ and $W_t(h', g')$, if $\pi$ acts on trivially on
-%   %   the
-%   %   children of $h'$ then $\pi (h) = h$ and so $\pi$ must act trivially
-
-%   %   $\pi$ acts trivially on the children of $h$.
-
-%   %   If $\Omega_g \cap \Omega_{\pi(g)} = \emptyset$ then, since
-%   %   $\Omega_{\pi(g)}
-%   %   =
-%   %   \pi \Omega_g$, there exists $g' \in \Omega_g$ such that $\pi g' \neq
-%   %   g'$.
-%   %   But
-%   %   $\pi$ must act trivially on output gates, so this is a contradiction. So
-%   %   there
-%   %   exists $g' \in \Omega_g \cap \Omega_{\pi(g)}$. But then $W_t (g, g')$
-%   %   and
-%   %   $W_t
-%   %   (\pi (g), g')$.
-
-%   %   We have that $g$ must be a non-output internal gate. So $g$ is
-%   %   syntactically
-%   %   equivalent to $\pi (g)$.
-
-%   %   and let $h$ be a gate such that $W_t (g, h)$.
-% \end{proof}
-
-% \begin{prop}
-%   Let $C_n$ be a circuit with unique labels. If
-% \end{prop}
-
-% \begin{prop}
-
-% \end{prop}
-% \begin{proof}
-% \end{proof}
-
-% \begin{prop}
-%   Let $\mathcal{C}$ be a class on which the Let $C_n := \langle G, \Omega,
-%   \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B}, \tau)$-circuit with unique
-%   labels. There is a deterministic algorithm that takes in such a circuit and
-%   outputs the syntactic equivalence relation on $G$. Moreover, this algorithm
-%   runs in time polynomial in the size of the circuit.
-%   \label{prop:unique-labels-syntactic-equiv}
-% \end{prop}
-
-% % \begin{prop}
-% %   There is an algorithm that takes in a $(\mathbb{B}, \tau)$-circuit $C$ with
-% %   unique labels and outputs the syntactic equivalence relation on its gates.
-% %   This algorithm runs in time polynomial in the size of $C$.
-% %   \label{prop:unique-labels-syntactic-equiv}
-% % \end{prop}
-% % \begin{proof}
-% %   We build of the relation by induction. Let $g$
-% % \end{proof}
-
-% Putting together Propositions \ref{prop:symmetric-syntactic},
-% \ref{prop:syntactic-equivilence-rigid}, and
-% \ref{prop:unique-labels-syntactic-equiv}, we have that there is a
-% polynomial-time algorithm that takes as input a circuit with unique labels and
-% outputs an equivalent rigid circuit. In fact, there is an equivalence of sorts
-% between the unique labels condition and the rigidity condition.
-
-% \begin{prop}
-%   Let $\mathcal{C}$ be a family of circuits. There is an algorithm that runs
-%   in polynomial-time that takes in a circuit $C \in \mathcal{C}$ and outputs a
-%   rigid circuit $C'$ such that if $C$ is symmetric then $C'$ is symmetric if,
-%   and only if, there is an algorithm that runs in polynomial-time and takes in
-%   a circuit $C \in \mathcal{C}$ and outputs a circuit $C'$ with unique labels
-%   such that if $C$ is symmetric then $C'$ is symmetric.
-% \end{prop}
-
-% It follows then that for the symmetric circuits defined over bases of
-% symmetric functions discussed by Anderson and Dawar~\cite{} we may assume the
-% circuits are rigid and/or have unique labels without a loss of generality. For
-% the more general circuit discussed in this paper we cannot make such an
-% assumption as deciding rigidity is harder then graph isomorphism. However, if
-% we restrict ourselves to families of circuits with unique labels then again we
-% may assume rigidity without a loss of generality.
-
-% Of course, this restriction to circuits with unique labels is only useful if
-% we can show that formulas in rank logic can be translated into $P$-uniform
-% families circuits with unique labels. In the next subsection we prove that
-% this is indeed the case.
+It is easy to see that $\op{compose-and-tag}$ can be computed in time polynomial
+in the sizes of the input circuits. Furthermore, if the input sequences of
+circuits and relations are both singletons, then if the input circuits are all
+transparent (resp. have unique labels) then the output circuit is transparent
+(resp. have unique labels).
 
 \subsection{Translating FPR to Symmetric Matrix Circuits}
-In this subsection we translate formulas of $\FPR$ into circuits. In particular,
-we show that for $\theta(\vec{x}) \in \FPR[\tau]$ there exists a $P$-uniform
-family of symmetric majority-circuits $(C_n)_{n \in \nats}$ such that the query
-computed by $(C_n)_{n \in \nats}$ is equal to the query defined by $\theta
-(\vec{x})$. In this subsection we develop a similar translation from formulas of
-$\FPR$ into $P$-uniform families of symmetric matrix-circuits.
+In this subsection we translate $\FPR$-formulas into families of transparent
+rank-circuits. In particular, we now show that for $\theta(\vec{x}) \in
+\FPR[\tau]$ there exists a $P$-uniform family of symmetric rank-circuits
+$(C_n)_{n \in \nats}$ such that the query computed by $(C_n)_{n \in \nats}$ is
+equal to the query defined by $\theta (\vec{x})$.
 
@@
 
-We are now ready to prove the main theorem of this section.
-
 \begin{thm}
   For any relational vocabulary $\tau$ and each $\theta(\vec{x}) \in \FPR[\tau]$
-  there is an algorithm that takes as input a natural number $n$ and outputs a
-  symmetric matrix-circuit $C_n$ with unique labels. This algorithm runs in time
-  polynomial in $n$ and the family of circuits produced by this algorithm
-  $(C_n)_{n \in \nats}$ computes the same query as the one defined by
-  $\theta(\vec{x})$.
+  there is a map $n \mapsto C_n$, where $C_n$ is a transparent symmetric
+  rank-circuit, and is computable in time polynomial in $n$. The family of
+  circuits $(C_n)_{n \in \nats}$ defined by this mapping computes the same query
+  as the one defined by $\theta(\vec{x})$.
+  \label{thm:translating-formulas-to-circuits}
 \end{thm}
@@
 \begin{proof}
-  We say a formula $\psi(\vec{x}) \in \FPR[tau]$ is \emph{circuit-translatable}
-  if there is a $P$-uniform family of transparent symmetric matrix-circuits that
-  compute the same query as $\psi(\vec{x})$. If a formula $\psi(\vec{x}) \in
-  \FPR[tau]$ is circuit-translatable we let $(C^\psi_n)_{n \in \nats}$ denote
-  the corresponding $P$-uniform family of transparent symmetric matrix-circuits.
-
-  We prove that $\theta(\vec{x}) \in \FPR[\tau]$ is circuit-translatable by
-  structural induction. That is, we first prove that if every sub-formula of
-  $\theta(\vec{x})$ is circuit-translatable then $\theta(\vec{x})$ is
-  circuit-translatable and, second, we note that every atomic formula in
-  $\FPR[\tau]$ is circuit-translatable. We have already that formulas of
-  $\FPC[\tau]$ are circuit translatable (Anderson and Dawar~\cite{AndersonD17}),
-  and in fact we may assume, without a loss of generality, that this translation
-  yields a family of transparent circuits with unique extensions.
-
-  We first consider the case where $\theta(\vec{x})$ is a conjunction of
-  circuit-translatable formulas. Suppose $\phi_1, \phi_2 \in \FPR[\tau]$ are
+  We say a formula $\psi(\vec{x})$ is \emph{circuit-translatable} if there is a
+  $P$-uniform family of transparent symmetric rank-circuits computing the query
+  as the one defined by $\psi(\vec{x})$. If a formula $\psi(\vec{x})$ is
+  circuit-translatable we let $(C^\psi_n)_{n \in \nats}$ denote a $P$-uniform
+  family of transparent symmetric rank-circuits computing the same query as
+  defined by $\psi(\vec{x})$.
+
+  Let $\theta(\vec{x}) \in \FPR[\tau]$. We prove that $\theta(\vec{x})$ is
+  circuit-translatable by structural induction. That is, we prove that if every
+  sub-formula of $\theta(\vec{x})$ is circuit-translatable then
+  $\theta(\vec{x})$ is circuit-translatable. Since it is obvious that every
+  atomic formula in $\FPR[\tau]$ is circuit-translatable, the result thus
+  follows. We already have that the formulas of $\FPC[\tau]$ are
+  circuit-translatable (Anderson and Dawar~\cite{AndersonD17}), and in fact we
+  may assume, without a loss of generality, that this translation yields a
+  family of transparent circuits with unique labels (and unique extensions).
+
+  We begin by showing that for any $\theta(\vec{x}) \in \FPR[\tau]$, there
+  exists a $P$-uniform family of formulas $(\theta(\vec{x}))_{n \in \nats}$ such
+  that for each $n \in \nats$, $\theta_n(\vec{x})$ is a first order formula with
+  counting and rank quantifiers and is equivalent to $\theta(\vec{x})$ on
+  structures of size $n$. This fact follows immediately from three observations.
+  First, we note that for any $\phi \in FPR[\tau]$ of the form $\lfp{V,
+    \vec{y}}{\psi(\vec{x}, \vec{y}, V)}(\vec{x})$ , there is a mapping $n
+  \mapsto \phi_n$, computable in time polynomial in $n$, such that for all $n
+  \in \nats$, both $\phi_n$ and $\phi$ are equivalent on structures of size $n$,
+  and $\phi_n$ contains no least-fixed-point operator. The formula $\phi_n$ is
+  define from $\phi$ by `unfurling' the least-fixed-point operator, producing,
+  for a given $n \in \nats$, a formula that explicitly implements the definition
+  of the operator in the obvious manner (for details on this implementation see
+  \ref{}). This construction of $\phi_n$ involves adding a constant number of
+  terms to $\phi$ for each iteration involved in computing the
+  least-fixed-point. Since there are at most $n^k$ such iterations, where $k$ is
+  the width of the formula $\psi$, the construction of $\phi_n$ can be completed
+  in time polynomial in $n$.
+
+  Similar arguments holds for number terms and rank operators. We have
+  from~\cite{} that for any formula $\phi$ containing number-terms there is a
+  $P$-uniform family of formulas $(\phi_n)_{n \in \nats}$ containing counting
+  quantifiers and no number-terms, and such that for all $n \in \nats$, $\phi$
+  and $\phi_n$ are equivalent on structures of size $n$. We have from Dawar et
+  al.~\cite{Dawar09logicswith} that for every formula $\phi \in \FPR[\tau]$
+  containing rank operators, there exists a $P$-uniform family that takes as
+  input a natural number $n$ and outputs a formula $\phi_n$ with rank
+  quantifiers and no rank operators, and such that for all $n \in \nats$, $\phi$
+  and $\phi_n$ are equivalent on structures of size $n$.
+
+  The algorithm given by executing each of the above three algorithms in
+  succession computes the required mapping $n \mapsto \theta_n(\vec{x})$ in time
+  polynomial in $n$, thus giving us the required $P$-uniform family
+  $(\theta_n(\vec{x}))_{n \in \nats}$.
+
+  It follows that the number of sub-formulas of $\theta_n$
+
+  It follows that in order to prove that $\theta(\vec{x})$ is
+  circuit-translatable it is sufficient to prove that there exists a function
+  that maps $\theta_n$ (for any $n \in \nats$) to $C^{\theta}_n$, a transparent
+  symmetric rank-circuit that computes the same query as defined by
+  $\theta_n(\vec{x})$ (and so $\theta(\vec{x})$) for structures of size $n$, and
+  is computable in time polynomial in in both $n$ and the number of sub-formulas
+  in $\theta_n$. This is sufficient as the number of sub-formulas in $\theta_n$
+  is bounded by some polynomial in $n$, and so composing functions, we can
+  compute the map that takes $n$ to $\theta_n$ to $C^{\theta}_n$ in time
+  polynomial in $n$.
+
+  We define an algorithm for constructing $C^{\theta}_n$ given
+  $\theta_n(\vec{x})$ by recursion on the structure of the input formula. The
+  first note that if $\theta_n(\vec{x})$ an atomic formula then there is a
+  trivial construction of $C^{\theta}_n$.
+
+  We consider the conjunctive case. Suppose $\phi_1, \phi_2 \in \FPR[\tau]$ are
   circuit-translatable and $\theta (\vec{x}) = \phi_1(\vec{x}) \land
@@
   R_{\phi_1}(\vec{x}) \land R_{\phi_2}(\vec{x})$. Let $n \in \nats$. Since
-  $\theta'(\vec{x})$ is a formula of $\FPC$, we may efficiently compute
-  $C^{\theta'}_n$ using the construction in \cite{AndersonD17}. From the
-  inductive hypothesis, for each $i \in \{1,2\}$ we may efficiently compute the
-  circuit $C^{\phi_i}_n = \langle G_i, \Omega_i, \Sigma_i \Lambda_i, L_i
-  \rangle$. Let $R \in \tau$ and let $D^{\theta}_n :=
-  \op{compose}(C^{\theta'}_n, (C^{\phi_1}_n, C^{\phi_2}_n), (R_1, R_2), R)$. Let
-  $H$ consist of all non-output gates in $D^{\theta}_n$. From the inductive
-  hypothesis all gates in $H$ have unique labels. Let $C^{\theta}_n :=
-  \op{make-injective-all}(\op{merge-all}(D^{\theta}_n, H))$.
-
-  Notice that $D^{\theta}_n$ computes the same relation as defined by
-  $\theta(\vec{x})$ for structures of size $n$. Moreover, since the remaining
-  two operations preserve the function computed, it follows $C^{\theta}_n$
-  computes the same relation as defined by $\theta(\vec{x})$ for structures of
-  size $n$. Furthermore, since $C^{\phi_1}_n$, $C^{\phi_2}_n$ and $C^{\theta'}_n$
-  are symmetric so is $C^{\theta}_n$. Lastly, notice that all non-output gates
-  in $D^{\theta}_n$ have unique labels. After the $\op{merge-all}$ and
-  $\op{make-injective-all}$ operation the output gates have unique labels, and
-  thus $C^{\theta}_n$ has unique labels. This construction takes in a natural
-  number $n$ and produces the required circuit $C^{\theta}_n$. This construction
-  can be computed by an algorithm in time polynomial in $n$. Thus
-  $\theta(\vec{x})$ is circuit-translatable.
-
-  The approach used above for resolving the conjunctive case can be thought of
-  as having three steps. First, replacing each sub-formula with a relation
-  symbol, resulting in a formula of $\FPC$. Second, using the algorithms from
-  the inductive hypothesis' on sub-formulas, producing appropriate families of
-  circuits computing each sub-formula, and the known circuit-translation for
-  formulas of $\FPC$, in order to to produce an appropriate family of circuits
-  computing the operation on these sub-formulas. Third, using the concatenation
-  operation to combine these circuit families and two final operations in order
-  to ensure the family has the required properties.
-
-  This same approach can be used for to handle many other cases. For
-  circuit-translatable $\phi, \phi_1, \phi_2 \in \FPR[\tau]$ similar
-  constructions can be used to prove that if $\theta(\vec{x}) \in FPR[\tau]$ is
-  equal to $\phi_1(\vec{x}) \lor \phi_2(\vec{x})$, $\neg \phi(\vec{x})$,
-  $\forall y. \phi (\vec{x}, y)$ or $\exists y. \phi (\vec{x}, y)$ then
-  $\theta(\vec{x})$ is circuit-translatable.
-
-  Suppose $\theta(\vec{x}) = \lfp{V, \vec{y}}{\phi(\vec{x}, \vec{y},
-    V)}(\vec{x})$ for some circuit-translatable formula $\phi(\vec{x},
-  \vec{y}) \in FPR[\tau \uplus \{V\}]$ and $k$-ary relation symbol $V$. Let $n$
-  be a natural number. We construct $C^{\theta}_n$ as follows. We have that we
-  may efficiently compute $C^{\phi}_n$. For each $i \in [n^k]$ we construct a
-  circuit $C^i = \langle G^i, \Omega^i, \Sigma^i, \Lambda^i, L \rangle $ as
-  follows. Let $C^0$ be a circuit consisting of exactly $n^k$ gates, such that
-  each gate is a constant $0$ gate and each gate is an output gate. Let $R$ be a
-  relation symbol in $\tau$. For each $i > 0$ let $C^i :=
-  \op{concatinate}(C^{\phi}_n, (C^{i-1}_n), (V), R)$ be $C^{\phi}_n$ but with
-  all relational gates labelled by the symbol $V$ replaced with the constant
-  $0$. Since $C^1$ and $C^\phi_n$ are symmetric and have unique labels, and the
-  operation $\op{concatinate}$ preserves the properties of symmetric and unique
-  labels, it follows by induction that for each $i \geq 1$, $C^i$ is a symmetric
-  rank-circuit with unique labels. It follows that $C^{\theta}_n := C^{n^k}$ is
-  a symmetric rank-circuit and has unique labels. Moreover, since the
-  least-fixed-point operator must converge in at most $n^k$ steps, this
-  construction can be implemented so as to run in time polynomial in $n$. The
-  construction also guarantees that $(C^{\theta}_n)_{n \in \nats}$ computes the
-  same query as $\theta(\vec{x})$.
-
-  The result in \cite{} establishes that for every formula $\theta(\vec{x})$
-  containing number-terms there is a $P$-uniform family of formulas
-  $(\theta_n(\vec{x}))_{n \in \nats}$ containing counting quantifiers and no
-  number-terms, and such that for all $n \in \nats$, $\theta(\vec{x})$ and
-  $\theta_n(\vec{x})$ are equivalent on structures of size $n$.
-
-  Thus, in order to handle the number-term case, it is sufficient to show that
-  if $\phi(\vec{x}) \in \FPR[\tau]$ is circuit-translatable then
-  $\theta(\vec{x}) := C^{k}y. \phi(\vec{x}, y)$ is circuit-translatable.
-  A similar construction as for the universal and existential quantifier gives
-  the required algorithm.
-
-  The result in \cite{} establishes that for every formula $\theta(\vec{x}) \in
-  \FPR[\tau]$ containing rank operators, there exists an algorithm that takes as
-  input a natural number $n$ and outputs a formula $\theta_n(\vec{x})$ with rank
-  quantifiers and no rank operators such that $\theta(\vec{x})$ and
-  $\theta_n(\vec{x})$ are equivalent on structures of size $n$. It is thus
-  sufficient to prove that, for circuit-translatable $\phi(\vec{z},
-  \vec{y}, \vec{x}) \in \FPR[\tau]$ is, a prime $p$, and a natural number $r$,
+  $\theta'(\vec{x})$ is a formula of $\FPC[\tau]$, we have from Anderson and
+  Dawar~\cite{AndersonD17} that $\theta'(\vec{x})$ is circuit-translatable. We
+  let $C^{\theta}_n := \op{compose}(C^{\theta'}, (C^{\phi_1}, C^{\phi_2}),
+  (R_{\phi_1}, R_{\phi_2}))$.
+
+  Since all internal gates in $C^{\theta'}$ are symmetric, and both $C^{\phi_1}$
+  and $C^{\phi_2}$ are transparent, it follows that $C^{\theta}_n$ is
+  transparent. Moreover, it is easy to see that the construction of
+  $C^{\theta}_n$ can be carried implemented so as to run in time polynomial in
+  $n$, and that $(C^{\theta}_n)_{n \in \nats}$ computes the same query defined
+  by $\theta(\vec{x})$. It follows that $\theta(\vec{x})$ is
+  circuit-translatable.
+
+  % Notice that $D^{\theta}_n$ computes the same relation as defined by
+  % $\theta(\vec{x})$ for structures of size $n$. Moreover, since the remaining
+  % two operations preserve the function computed, it follows $C^{\theta}_n$
+  % computes the same relation as defined by $\theta(\vec{x})$ for structures of
+  % size $n$. Furthermore, since $C^{\phi_1}_n$, $C^{\phi_2}_n$ and
+  % $C^{\theta'}_n$ are symmetric so is $C^{\theta}_n$. Lastly, notice that all
+  % non-output gates in $D^{\theta}_n$ have unique labels. After the
+  % $\op{merge-all}$ and $\op{make-injective-all}$ operation the output gates
+  % have
+  % unique labels, and thus $C^{\theta}_n$ has unique labels. This construction
+  % takes in a natural number $n$ and produces the required circuit
+  % $C^{\theta}_n$. Moreover, it is easy to see that this construction can be
+  % implement as an algorithm running in time polynomial in $n$. It follows that
+  % $\theta(\vec{x})$ is circuit-translatable.
+
+  The approach used for resolving the conjunctive case can be thought of as
+  having three steps. First, replacing each sub-formula in $\theta$ with a
+  relation symbol, resulting in a formula $\theta'$ of $\FPC$. Second, using the
+  algorithms from the inductive hypothesis' (and the results of Anderson and
+  Dawar) on $\theta'$ and the sub-formulas, producing appropriate families for
+  $\theta'$ and each sub-formula of $\theta$. Third, for each $n \in \nats$
+  composing the circuit $C^{\theta'}_n$ with the circuits for each sub-formula,
+  producing the the circuit $C^{\theta}_n$. Since this process can be executed
+  in time polynomial in $n$, we conclude that $\theta$ is circuit-translatable.
+
+  This same approach can be used to handle many other cases. For
+  circuit-translatable $\phi, \phi_1, \phi_2 \in \FPR[\tau]$, and $k \in \nats$,
+  similar constructions can be used to prove that if $\theta(\vec{x}) \in
+  \FPR[\tau]$ is of the form $\phi_1(\vec{x}) \lor \phi_2(\vec{x})$, $\neg
+  \phi(\vec{x})$, $\forall y. \phi (\vec{x}, y)$, $\exists y. \phi (\vec{x}, y)$
+  or $C^k y. \phi(\vec{x}, y)$ then $\theta(\vec{x})$ is circuit-translatable.
+
+  % Suppose $\phi(\vec{x},y) \in \FPR[\tau]$ is circuit-translatable and
+  % $\theta(\vec{x}) := C^{k}y. \phi(\vec{x}, y)$. Let $k := \vert \vec{x}
+  % \vert$
+  % and $R$ be a $(k+1)-$-ary relational symbol. Let $D_n$ be a $(\MB,
+  % \{R\})$-circuit computing the $k$-ary query such that for each $\vec{a} \in
+  % [n]^k$, the output gate labelled by $\vec{a}$ computes the Boolean function
+  % \begin{align*}
+  %   \countgate_{\vec{a}} &(x_{(\vec{a}, 1)}, \ldots, x_{({\vec{a}, n})}) 
+  %                          := \\ & \begin{cases} \land ( \maj ( x_{(\vec{a}, 1)}, \ldots, x_{(\vec{a}, n)},
+  %                            \underbrace {0, \ldots, 0}_{2k - n} ), \neg ( \maj ( x_{(\vec{a}, 1)},
+  %                            \ldots, x_{(\vec{a}, n)}, \underbrace{0, \ldots,
+  %                              0}_{2k - n + 2} ) )) &  k \geq \frac{n}{2} \\
+  %                            \land ( \maj ( x_{(\vec{a}, 1)}, \ldots, x_{(\vec{a}, n)}, \underbrace {1,
+  %                              \ldots, 1}_{n - 2k} ), \neg ( \maj ( x_{(\vec{a}, 1)}, \ldots,
+  %                            x_{(\vec{a}, n)}, \underbrace{1, \ldots, 1}_{n - 2k -2} ) )) & k <
+  %                            \frac{n}{2},
+  %                          \end{cases}
+  % \end{align*}
+  % using the obvious circuit (for a more detailed construction see the proof of
+  % Proposition~\ref{prop:fuctions-maj}), and where for each $i \in [n]$, the
+  % variable $x_{(\vec{a}, i)}$ is replaced by the relational gate in the
+  % circuit
+  % labelled by $(\vec{a}, i)$. Then $C^{\theta}_n := \op{compose}(D_n,
+  % {C^\phi_n}, \{R\})$. It is easy to see that this construction can be carried
+  % out in time polynomial in $n$.
+
+  % GW: include here the result of inserting the circuit
+
+  Suppose $\phi(\vec{z}, \vec{y}, \vec{x}) \in \FPR[\tau]$ is
+  circuit-translatable, $p$ is a prime, $r$ is a natural number, and
   $\theta(\vec{x}) := \rank^{\leq r}_p \vec{z} \vec{y}. \phi(\vec{z}, \vec{y},
-  \vec{x})$ is circuit-translatable. We define an algorithm that takes as input
-  a natural number $n$ outputs the required circuit $C^{\theta}_n$.
+  \vec{x})$. We define an algorithm that takes as input a natural number $n$
+  outputs the required circuit $C^{\theta}_n$.
 
@@
   \vec{y} \vert$. Let $R_\phi$ be a $(k_1 + k_2 + k)$-ary relation symbol not in
-  $\tau$. Let $\theta'(\vec{x}) = \rank^{\leq r}_r := \vec{z}, \vec{y}. \phi
-  (\vec{z}, \vec{y}, \vec{x})$. We now define a $(\mathbb{B}_{\rank}, \{
-  R_{\phi} \})$-circuit $C^{\theta'}_n:= \langle G^{\theta'}, \Omega^{\theta'},
-  \Sigma^{\theta'}, \Lambda^{\theta'}, L^{\theta'}\rangle$ as follows. Let $G_1
-  := \{g_{\rank, \vec{c}} : \vec{c} \in [n]^k\}$ and $G_2 : = \{ g_{R_{\phi},
-    \vec{a}, \vec{b}, \vec{c}} : \vec{a} \in [n]^{k_1}, \vec{b} \in [n]^{k_2},
-  \vec{c} \in [n]^{k}\}$.
+  $\tau$.
+
+  Let $\theta'(\vec{x}) = \rank^{\leq r}_r := \vec{z}, \vec{y}. R_{\phi}
+  (\vec{z}, \vec{y}, \vec{x})$. We define the $(\mathbb{B}_{\rank}, \{ R_{\phi}
+  \})$-circuit $C^{\theta'}_n:= \langle G^{\theta'}, \Omega^{\theta'},
+  \Sigma^{\theta'}, \Lambda^{\theta'}, L^{\theta'}\rangle$ as follows. Let
+  $G_{\text{out}} := \{g_{\vec{c}} : \vec{c} \in [n]^k\}$ and $G_{\text{in}} : =
+  \{ g_{\vec{a}, \vec{b}, \vec{c}} : \vec{a} \in [n]^{k_1}, \vec{b} \in
+  [n]^{k_2}, \vec{c} \in [n]^{k}\}$.
 
@@
     \setlength\itemsep{0mm}
-  \item Let $G^{\theta'} := G_1 \uplus G_2$,
-  \item $\Omega^{\theta'}$ be an injection from $[n]^k$ to $G'$ defined by
-    $\Omega^{\theta'}(\vec{c}) = g_{\rank, \vec{c}}$,
-
-  \item $\Sigma^{\theta'} (g) := rank^r_p$ if $g \in G_1$ and
-    $\Sigma^{\theta'}(g) = R_\phi$ if $g \in G_2$,
+  \item Let $G^{\theta'} = G_{\text{out}} \uplus G_{\text{in}}$,
+  \item $\Omega^{\theta'}$ be an injection from $[n]^k$ to $G^{\theta'}$ defined
+    by $\Omega^{\theta'}(\vec{c}) = g_{\vec{c}}$ for all $\vec{c} \in [n]^k$,
+  \item $\Sigma^{\theta'} (g) = \rank^r_p$ if $g \in G_{\text{out}}$ and
+    $\Sigma^{\theta'}(g) = R_\phi$ if $g \in G_{\text{in}}$,
   \item For each $(\vec{a}, \vec{b}, \vec{c}) \in [n]^{k_1 +k_2 + k}$ let
-    $\Lambda^{\theta'} (\vec{a}, \vec{b}, \vec{c}) := g_{R_{\phi}, \vec{a},
-      \vec{b}, \vec{c}}$, and
-
-  \item For each gate $g_{\rank, \vec{a}} \in G_1$ let $L(g_{\rank, \vec{a}}):
+    $\Lambda^{\theta'} (\vec{a}, \vec{b}, \vec{c}) := g_{\vec{a}, \vec{b},
+      \vec{c}}$, and
+  \item For each gate $g_{\vec{c}} \in G_{\text{out}}$ let $L(g_{\vec{c}}):
     [n]^{k_1} \times [n]^{k_2} \rightarrow G^{\theta'}$ be defined by
-    $L(g_{\rank, \vec{c}})(\vec{a}, \vec{b}) := g_{R_\phi, \vec{a}, \vec{b},
-      \vec{c}}$ for each $\vec{a} \in [n]^{k_1}$ and $\vec{b} \in [n]^{k_2}$.
+    $L(g_{\vec{c}})(\vec{a}, \vec{b}) := g_{\vec{a}, \vec{b}, \vec{c}}$ for each
+    $\vec{a} \in [n]^{k_1}$ and $\vec{b} \in [n]^{k_2}$.
   \end{itemize}
 
-  It is easy to see that both $C^{\theta'}_n$ (and $C^{\phi}_n$) are symmetric
-  rank-circuits with unique labels. Let $R$ be a relation symbol in $\tau$. Let
-  $D^{\theta}_n := \op{compose}(C^{\theta'}_n, (C^{\phi}_n), (R_\phi), R)$. Let
-  $H$ consist of all non-output gates in $D^{\theta}_n$. From the inductive
-  hypothesis all gates in $H$ have unique labels. Let $C^{\theta}_n :=
-  \op{make-injective-all}(\op{merge-all}(D^{\theta}_n, H))$.
-
-  Since $C^{\theta'}_n$ and $C^{\phi}_n$ are symmetric, have unique labels, and
-  the input tuples of relations and circuits are singletons, it follows that
-  $D^{\theta}_n$ is a symmetric rank-circuit with unique labels. It can be shown
-  that the construction of $C^{\theta}_n$ from the natural number $n$ can be
-  implemented as an algorithm running in time polynomial in $n$. The
-  construction ensures that the circuit family $(C^{\theta}_n)_{n \in \nats}$
-  computes the same query as the one defined by $\theta(\vec{x})$.
+  % It is easy to see that both $C^{\theta'}_n$ (and $C^{\phi}_n$) are symmetric
+  % rank-circuits with unique labels.
+
+  % It is easy to see that every gate in $$
+
+  % be the result of calling $\op{tag}$ on
+
+  % Let $C^{\theta}_n := \op{make-injective-all}(\op{merge-all}(D_n, H))$.
+  Let $R$ be a relation symbol in $\tau$. Let $C^{\theta}_n :=
+  \op{compose-and-tag}(C^{\theta'}_n, (C^{\phi}_n), (R_\phi), R)$. It is easy to
+  see that for all $n \in \nats$, $C^{\theta}_n$ computes the same query as
+  defined by $\theta(\vec{x})$ for structures of size $n$. Moreover, since
+  $C^{\theta'}_n$ and $C^{\phi}_n$ are symmetric, transparent, and the input
+  sequences of relations and circuits are singletons, it follows that
+  $C^{\theta}_n$ is a transparent symmetric rank-circuit. W have thus defined a
+  mapping from $n \mapsto C^{\theta}_n$, that, and that mapping can be computed
+  in time polynomial in $n$.
 

### 2018-01-24 sections/transparency-and-unique-extensions.tex
24th January 2018

\documentclass[../paper.tex]{subfiles}
\begin{document}
% In contrast with the work of Anderson and Dawar~\cite{AndersonD17}, the
% circuit families we use to establish the main result of this paper are
% additionally required to be transparent. In this subsection we briefly discuss
% this condition, and present results suggesting its necessity.

In the statement of the main theorem of this paper, rather than working with
general symmetric rank-circuits, we instead restrict ourselves to families of
\emph{transparent} circuits. In this section we justify this restriction,
showing first that the a great number of very useful circuit properties (e.g.
syntactic-equivalence) are polynomial-time decidable for transparent circuits
and, second, that deciding most of these circuit properties for general circuits
(with non-symmetric gates) is at least as hard as the graph-isomorphism
problem. Since the proof of the main theorem makes use of the polynomial-time
decidability of many of these properties, these results together justify the
inclusion of the transparency restriction.
% We note additionally that the circuit properties that we show

% In this section we discuss the transparency condition on circuits. It is worth
% noting that, since the symmetric circuits of Anderson and
% Dawar~\cite{AndersonD17} have no non-symmetric internal gates, these circuits
% are transparent. We have from the first part of this subsection that a great
% number of useful properties (and transformations) are polynomial-time
% computable on transparent circuits. However, it is still reasonable to ask if
% the explicit inclusion of the transparency restriction is strictly necessary
% for proving these results, or indeed proving the main result of this paper. We
% provide evidence for necessity of the transparency condition, presenting
% reductions from the graph-isomorphism problem to the problem of deciding some
% of this important properties (e.g. symmetry, syntactic-equivalence, computing
% the orbit of a gate, etc.) over general, not necessarily transparent,
% circuits. We note that in all of these cases the decision problem restricted
% to transparent circuits is polynomial-time decidable.

% We further argue that, since most natural algorithms for transforming an
% arbitrary symmetric circuit into an equivalent transparent circuit make use of
% the polynomial-time decidability of these properties, we should consider these
% hardness results evidence that computing this transformation may be as hard as
% the graph-isomorphism problem
% We also prove that a number of related decision problems (e.g. synatcatic)
% important decision problems are reducible to the graph-isomorphism
% xthat the problem of deciding the orbit of a gate is reduca
% why (or whether) the transparency condition is strictly required when
% considering circuits that contain non-symmetric gates. In the second
% subsection we address this question, proving

% when considering circuits

% It is worth noting that the analogous results of Anderson and Dawar~\ref{}
% make no explicit restriction to transparent circuits,

% mentio It is worth asking if this additional transparency requirement is
% structing It is worth noting that Anderson and Dawar~\ref{} when developing
% their analogous translation, define a polynomial-time algorithm that
% transforms symmetric circuits into equivalent circuits with unique extensions
% -- making no mention of any transparency condition. Of course, the circuits
% they consider contain only symmetric internal gates, and as such are
% transparent already, but we may still ask if the transparency restriction is
% strictly necessary for proving the useful results mentioned above.

% It is worth noting that the translation defined by Anderson and Dawar~\cite{}
% between $P$-uniform families of symmetric circuits (with symmetric gates) and
% formulas of $\FPC$ makes no

% In the second subsection we discuss the necessity of the transparency
% requirement. Anderson and Dawar~\cite{AndersonD17} importance of this trans

% into In the main result of this paper we restrict ourselves to transparent
% circuits, a restriction not found in the analogous result of Anderson and
% Dawar~\cite{}. In this section we develop a number of technical that are
% important for defining and developing the basic technical tools used in this
% paper.

% Anderson and Dawar~\cite{} develop an correspondence between symmetric
% circuits (with symmetric gates) and formulas of fixed point with counting. In
% contrast, in the main theorem of this paper we explicitly require that the
% circuits under discussion be \emph{transparent}. This section we develop a
% number of results about transparent circuits. In the first subsection we
% discuss

% In this section we present a number of useful results for transparent circuits
% that together enable our analysis

% This condition does not appear explicitly in the analogous result of Anderson
% and Dawar~\cite{}, and in this section we discuss the importance of this
% requirement on circuits with non-symmetric gates.

% In the first subsection we demonstrate the usefulness of transparency. We
% begin by showing that we may transform transparent circuits into circuits with
% unique extensions in polynomial-time, allowing us assume, without a loss of
% generality, that $P$-uniform families of transparent circuits also have unique
% labels, and hence (from Proposition~\ref{}) unique extensions. We are also
% able to show that if a circuit has unique labels, which transparency allows us
% to assume, then many natural circuit properties, including the action of a
% permutation on the circuit, as well as the orbit and coarsest supporting
% partition of a gate, are polynomial-time computable.

% These results suggest the importance fundamental to our analysis of circuits.
% The ability to assume that the circuits under discussion have unique
% extensions (and unique labels) allows us to define many important theoretical
% tools, such as a canonical action of $\sym_n$ on the circuit and hence the
% notions of support and supporting partition. Moreover, the polynomial-time
% algorithms for computing the orbit and support of a gate play an important
% role (through the Immerman-Vardi Theorem~\cite{}) in our translation of
% circuits into formulas (see Section \ref{})

% we also show that if a circuit has unique labels (which transparency allows us
% to assume) then there exists polynomial-time algorithms for computing the
% action of $\sym_n$ on the circuit, and the canonical supporting partition and
% the orbit a gate (or elements of a universe of a gate). These algorithms play
% (along with the

% polynomial-time algorithms are thus crucial for developing our translation
% from circuits to formulas.

% and prove the existence of polynomial-time algorithms computing important
% functions, such as the coarsest supporting partition or the orbit of a gate
% (see Proposition~\ref{prop:c} and Lemma~\ref{}).

% Thus the transparency condition enables our analysis of circuits by allowing
% us to assume the circuits also have unique extensions. However, Anderson and
% Dawar~\cite{AndersonD17} prove that symmetric circuit can be transformed into
% circuits with unique extensions,without making any mention of any condition
% analogous to transparency. Of course, our result generalises theirs as they
% only consider circuits with symmetric gates, which are transparent, but it is
% reasonable to ask if the transparency requirement on circuits is strictly
% necessary.

% We address this question in this subsection, presenting reductions
% graph-isomorphism problem to the many related and important problems. We show,
% for example, that there is a polynomial-time many-one reduction from
% graph-isomorphism problem to the problem of deciding the orbit of a gate in an
% arbitrary symmetric circuit, and contrast this result with the known
% polynomial-time algorithm computing orbits of gates in transparent circuits.
% We also present reductions from the graph-isomorphism problem to many related
% problems (e.g. checking syntactic-equivalence or unique label for gates).
% Since most natural algorithms for transforming any an arbitrary symmetric
% circuit into an equivalent family of transparent circuits entail solving these
% related problems, we consider this evidence that computing this transformation
% may be as hard as the graph isomorphism problem.

% Moreover, we show that non-transparent circuits

% an ay be as hard as the graph isomorphism problem. However, we

% show that that being able to transform a circuit into an equivalent
% transparent circuit in polynomial-time would

% make no mention In contrast, Anderson and Dawar~\ref{} do not include any
% specific condition on the circuit families they consider

% consider only symmetric circuits with symmetric gates, which are transparent,
% and as such include no such condition.

% make use of an explicit condition on circuits we call \emph{transparency}. In
% this section we show that transparency is a sufficient condition in that it
% allows us to assume, without a loss of generality, that $P$-uniform families
% of In this subsection we show that if a circuit is transparent then it may be
% transformed in polynomial time into an equivalent circuit with unique labels.
% It follows from Proposition~\ref{prop:unique-labels-unique-extensions}) that
% we may assume, without a loss of generality, that $P$-uniform families of
% transparent circuits have unique labels, and hence unique extensions.

% We also discuss the importance of the transparency condition on circuits
% introduced in this paper. Indeed, while Anderson and Dawar~\cite{AndersonD17},
% place no similar requirement on the symmetric circuits in their paper, in our
% generalisation of their result, transparency is required.

% We also discuss relevant special cases and motivate the explicit requirement
% that the $P$-uniform families of circuit referenced in the main result of this
% paper consist of transparent circuits.

% Anderson and Dawar~\cite{AndersonD17} introduce the notion of a `rigid'
% circuit, a condition analogous to the rigidity condition defined in this
% paper. The following

% \begin{definition}
%   We say a circuit $C_n$ is que labels it has unique extensions. We finally
%   discuss th\emph{rigid} if it has injective labels and for every pair of
%   gates $(g, g')$ in $C_n$ such that $H_g = H_{g'}$ and $g \equiv g'$.
% \end{definition}
\subsection{The Usefulness of Transparency}
In the this subsection we show that a number of important circuit properties are
polynomial-time decidable for transparent circuits (e.g. symmetry, the
syntactic-equivalence relation, etc.). We also provide polynomial-time
algorithms for computing the action of a permutation on a symmetric circuit, as
well as for computing the orbits and supports of gates, and elements of
universes of gates, in a circuit.

We use the polynomial-time decidability of many of these properties throughout
this paper, and particularly for our translation of circuits into formulas. For
example, the polynomial-time decidability of the syntactic-equivalence relation
enables us to transform transparent circuits into circuits with unique labels
(and so unique extensions) in polynomial-time. This result allows us, when
working with $\PT$-uniform families of transparent circuits, to assume without a
loss of generality that these circuits have unique labels and unique extensions.
This is a crucial step in the proof of our main result, as the unique labels
requirement is needed to apply the support theorem, and the unique extensions
property is necessary for applying (and even defining) a great many technical tools (e.g. supports
and supporting partitions) used extensively throughout this paper.

We now show that the syntactic-equivalence relation can be computed in
polynomial time for transparent circuits.

% \begin{definition}
%   We say a class of circuits $\mathcal{C}$ is \emph{syntactically transparent}
%   if there is an algorithm that takes in a circuit $C \in \mathcal{C}$ and
%   outputs the syntactic equivalence relation on the gates of $C$ and runs in
%   time polynomial in the size of the input circuit.
% \end{definition}

\begin{lem}
  There is an algorithm that takes as input a transparent circuit $C$ and
  outputs the syntactic-equivalence relation on the gates of $C$. The algorithm
  runs in time polynomial in the size of $C$.
  \label{lem:unique-labels-syntactic-equiv}
\end{lem}
\begin{proof}
  Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a transparent
  $(\mathbb{B}, \rho)$-circuit of order $n$. We define a relation $\sim$ by
  induction on height (i.e. distance from an input gate). This relation will be
  the syntactic-equivalence relation on $G$. It is easy to check the conditions
  for syntactic-equivalence for gates of height 0 as all such gates are input
  gates and so are either constant gates or relational gates. Suppose $g$ and
  $h$ are gates of height greater than zero. We only need to check conditions
  (i), (iv) and (v) of syntactic-equivalence. It is easy to check (i) and (v).
  If either condition is false then $g$ and $h$ are not syntacticly equivalent.
  So suppose $g$ and $h$ are two internal gates such that $\Sigma (g) =
  \Sigma(h)$ and suppose that if they are both output gates then $\Omega^{-1}(g)
  = \Omega^{-1}(h)$. It remains to check if $L(g)/{\sim}$ and $L(h)/{\sim}$ are
  isomorphism equivalent. First check if $H_h /{\sim} = H_g /{\sim}$. If not,
  $g$ and $h$ are not syntactically equivalent. So suppose $H_h /{\sim} = H_g
  /{\sim}$. If $g$ and $h$ are symmetric gates then $H_h /{\sim} = H_g/{\sim}$
  if, and only if, $L(g)/{\sim}$ and $L(h)/{\sim}$ are isomorphism equivalent,
  so let $g \sim h$. If $g$ and $h$ are not symmetric gates then, since $C$ is
  transparent, $g$ and $h$ have unique labels. We thus have that $L(g)/{\sim}$
  and $L(h)/{\sim}$ are isomorphism equivalent if, and only if, $L(g)^{-1}L(h)$
  acts like an isomorphism. This can be checked by first checking that the
  function induces a sorted permutation on the universe of $g$ (which can be
  checked efficiently). This is sufficient as $L(g)(L(g)^{-1}L(h)) = L(h)$.

  It is easy to see that, given a reasonable binary encoding of a circuit, the
  above procedure can be implemented so as to run in polynomial time, and that
  the relation $\sim$ is the syntactic-equivalence relation on the gates of $C$.

\end{proof}

We now prove that transparent circuits can be transformed in polynomial time
into equivalent circuits with unique extensions, and that this transformation
preserves important properties of the circuit.

\begin{lem}
  Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a transparent
  $(\mathbb{B}, \rho)$-circuit. There is an algorithm that that takes in such a
  circuit and outputs a $(\mathbb{B} \cup \mathbb{B}_{\std}, \rho)$-circuit $C'$
  such that $C$ and $C'$ compute the same function, $C'$ has unique labels, and
  if $C$ is symmetric then $C'$ is symmetric. Moreover, this algorithm runs in
  time polynomial in the size of the input circuit.
  \label{lem:transparent-unique}
\end{lem}
\begin{proof}
  Let $C' := \op{make-injective-all}(\op{merge-all} (C, G))$ (see
  Definition~\ref{def:make-injective} and~\ref{def:merge-all} for the
  definitions of these functions). It follows that if $C$ is symmetric then $C'$
  is symmetric. We have from Lemma~\ref{lem:unique-labels-syntactic-equiv} that
  the syntactic-equivalence relation can be computed in polynomial time for
  transparent circuits. It follows that the construction of $C'$ from $C$ can be
  implemented so as to run in time polynomial in the size of $C$. Clearly every
  gate $g$ in $C'$ belongs to a singleton syntactic-equivalence equivalence
  class, and as such $C'$ has unique labels.
\end{proof}
% GW: read this when fresh

We now show that it is possible to compute the action of $\sym_n$ on the gates
of a circuit of order $n$ with unique labels in polynomial time. Recall that
from Proposition~\ref{prop:transparent-unique} we may, without a loss of
generality, restrict of attention from transparent circuits to circuits with
unique labels. The proof technique used here is similar to the one used by
Anderson and Dawar~\cite{AndersonD17}.

\begin{lem}
  There is an algorithm takes as input a $(\mathbb{B}, \rho)$-circuit $C$ of
  order $n$ with unique labels and $\sigma \in \sym_n$ and outputs for each gate
  $g$ its image under the unique automorphism extending $\sigma$ (if it exists).
  This algorithm runs in time polynomial in the combined size of the input
  circuit and the encoding of the permutation.
  \label{lem:compute-automorphisms}
\end{lem}
\begin{proof}
  Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$. We recursively build
  up the mapping $\pi$ extending $\sigma$. If at some point in the recursive
  construction we arrive at a point where no mapping for $g$ can be found we
  halt at that point and return that no automorphism exists.

  Let $h$ be any gate in the circuit. Suppose $h$ is an input gate. If $h$ is a
  constant gate then let $\pi (h) = h'$. If $h$ is a relational gate such that
  $R := \Sigma(h)$, then check if there exists $h'$ such that $\Sigma (h') = R$,
  $\sigma \Lambda_R(h) = \Lambda_R(h')$, and either both $h$ and $h'$ are output
  gates or neither are. If no such $h'$ exists then halt and output that no
  automorphism exists. If both $h$ and $h'$ are not output gates then set $\pi
  (h) = h'$. If both are output gates then check if $\sigma \Omega^{-1}(h) =
  \Omega^{-1}(h')$. If equality holds set $\pi(h) = h'$, otherwise halt and
  output that no automorphism exists. We have from Lemma~\ref{} that there is at
  most one gate $h'$ that meets the above criteria, and so $\pi(h)$ is well
  defined.

  Let $h$ be an internal gate in the circuit and assume we have defined $\pi
  (g)$ for every gate $g$ of height less than $h$. Let $h'$ be a gate in the
  circuit such that $\Sigma(h) = \Sigma (h')$, $\pi L(h)$ is
  isomorphism-equivalent to $L(h')$ and, if $h$ is an output gate then $h'$ is
  an output gate such that $\sigma \Omega^{-1}(h) = \Omega^{-1}(h')$. Since $C$
  has unique labels (and so unique extensions) we have that $\pi L(h)$ is
  isomorphism-equivalent to $L(h')$ if, and only if, $L(h')^{-1}\pi L(h)$ acts
  on $\ind(h)$ like an automorphism of $\str{h}$. This can be determined easily.
  If no such $h'$ exists halt and output that there is no automorphism extending
  $\sigma$. Again, we have that if $C$ has unique labels then there is at most
  one such $h'$.

  This recursive approach can be implemented as an algorithm that runs in time
  polynomial in the combined size of the inputs and outputs the required
  automorphism if it exists.
\end{proof}

We now that, using the algorithm from Lemma~\ref{lem:compute-automorphisms}, we
can similarly compute the action of $\sym_n$ on the elements of the universes of
the gates of a circuit of order $n$ in polynomial time.

\begin{lem}
  There is an algorithm takes as input a $(\mathbb{B}, \rho)$-circuit $C$ of
  order $n$, $\sigma \in \sym_n$, $g$ a gate in $C$, and $a \in \universe{g}$
  and, if there exists an automorphism of $C$ extending $\sigma$ such that
  $\sigma in \stab(g)$, outputs image of $a$ under $\sigma$. The algorithm runs
  in time polynomial in the size of $C$ and the encoding of $\sigma$.
  \label{lem:compute-automorphisms-labels}
\end{lem}
\begin{proof}
  Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$. Use the algorithm
  from Lemma \ref{lem:compute-automorphisms} to check if $\sigma$ extends to an
  automorphism on $C$ and $\sigma \in \stab(g)$. If not, return that no such
  automorphism exists. We thus have that $C$ is symmetric. Let $h \in H_g$ and
  $\vec{a} := L(g)^{-1}(h)$ be such that $a \in \vec{a}$, and let $i$ be the
  index of $a$ in $\vec{a}$. Output $\sigma \cdot a := L(g)^{-1}(\sigma h)(i)$.
\end{proof}

We now show that it is possible to compute the orbits and canonical supporting
partitions of gates in circuits with unique labels in polynomial-time. We also
show that it is possible to compute the orbits and canonical supporting
partitions of elements on the universes of gates in circuits with unique labels
in polynomial-time. In order to prove both of these results we first prove a
more general result for group actions.

\begin{lem}
  \label{lem:computing-support-orbit}
  There is an algorithm that takes in a subset $S \subseteq [n]$ and $x \in X$,
  where $X$ is some finite set such that there is a group action of $\stab(S)$
  on $X$ computable in time polynomial in both $n$ and $\vert X \vert$ and
  outputs $\orb_{\stab(S)} (x)$ and $\SP_{\stab(S)}(x)$. This algorithm runs in
  time polynomial in both $\vert X \vert$ and $n$.
\end{lem}
\begin{proof}
  Let $(u, v) \in \sym_{[n] \setminus S}$ be a transposition. We note that
  $(u,v) \in \stab(S)$ and there are ${n - \vert S \vert}\choose{2}$ many such
  transpositions. For a transposition $(u, v) \in \sym_{[n] \setminus S}$, let
  \begin{align*}
    \mathcal{P}_{(u,v)} := \{ \{u,v\}\} \bigcup_{w \in [n] \setminus \{ u,v \}} \{ \{ w \} \}
  \end{align*}
  be a partition of $[n]$. Then $\mathcal{P}_{(u,v)}$ supports
  $\stab_{\stab(S)}(x)$ if, and only if, $(u,v) \cdot x = x$.

  Let $\mathcal{P}$ be the partition formed by applying $\mathcal{E}$ to all
  $\mathcal{P}_{(u,v)}$ such that $(u,v) \cdot x = x$ (which can be checked in
  time polynomial in $\vert X \vert$ and $n$). From
  Proposition~\ref{prop:combining-supporting-patitions} we have that
  $\mathcal{P}$ supports $\stab_{\stab(S)}(x)$. Suppose that $\mathcal{P}$ is
  not the coarsest supporting partition of $\stab_{\stab(S)}(x)$. Then there
  exists a partition $\mathcal{P}'$ supporting $\stab_{\stab(S)}(x)$ such that
  $\mathcal{P}' \preceq P$ and $\mathcal{P}' \neq \mathcal{P}$. And so there
  exists $P \in \mathcal{P}$ and $P' \in \mathcal{P}'$ such that $P \subsetneq
  P'$. But then there exists $a , b \in P'$ such that $a \not\in P$. Note that
  $(a,b)$ fixes $\mathcal{P}'$ and, since $\mathcal{P}'$ supports
  $\stab_{\stab(S)}(x)$, it follows that $(a,b) \in \stab_{\stab(S)}(x)$ and $a
  \not\in S$ and $b \not\in S$. But then we have that $(a,b) \cdot x = x$, and
  so $\mathcal{P}_{(a,b)}$ supports $\stab_{\stab(S))}(x)$ and thus, from the
  construction of $\mathcal{P}$, $\mathcal{P}$ is fixed by $(a,b)$. But we
  selected $a$ and $b$ such that $\mathcal{P}$ is not fixed by $(a,b)$, and so
  we have a contradiction. We thus have that $\mathcal{P}$ is the coarsest
  supporting partition of $\stab_{\stab(S)}(x)$.

  It remains to compute $\orb_{\stab(S)}(x)$. Let $M_0 := \{x\}$ and for each $i
  \geq 0$ let $M_{i+1} := M_i\cup \bigcup_{(u,v) \in \sym_{[n] \setminus S}}
  ((u,v) \cdot M_i)$. Let $M$ be the least fixed point of this sequence. It is
  easy to see that $M \subseteq \orb_{\stab(S)}(x)$ as every element of $M$ is
  equal to the action of some finite sequence of transpositions acting on $x$.
  Moreover, if $y \in \orb_{\stab(S)}(x)$, then there exists $\pi \in \stab(S)$
  such that $y = \pi \cdot x$. But then, since $\sym_{[n] \setminus S}$, is
  generated by the set of all transpositions in $\sym_{[n] \setminus S}$, it
  follows that $\pi$ can be written as a sequence of $t$ transpositions (for
  some $t \in \nats$). Thus $y \in M_t \subseteq M$, and hence
  $\orb_{\stab(S)}(x) \subseteq M$, and so $\orb_{\stab(S)}(x) = M$.

  Note that the set of all transpositions in $\sym_{[n] \setminus S}$ can be
  computed in time $\mathcal{O}(n^{2})$ and whether a transposition fixes $x$
  can be computed in time polynomial in both $\vert X \vert$ and $n$. Moreover,
  since it is easy to show that $\mathcal{E}$ can be computed in time polynomial
  in $n$, it follows that $\mathcal{P}$ (defined above) can be computed in
  $\mathcal{O} (n^{2} q(\vert X \vert, n))$, for some polynomial $q$.

  Furthermore, since, when computing the orbit, the least fixed point must be
  reached in fewer than $\vert X \vert$ iterations, and each iteration requires
  at most $\mathcal{O} (n^{2})$ applications of the group action, it follows
  that the procedure terminates in time $\mathcal{O}(\vert X \vert n^{2} q'
  (\vert X \vert, n))$, for some polynomial $q'$. The result follows.
\end{proof}

We now use Lemma~\ref{lem:computing-support-orbit} to prove the result for the
orbits and canonical supporting partitions of gates in the circuit.

\begin{lem}
  There is an algorithm that takes in a circuit $C$ of order $n$ with unique
  labels and outputs if the circuit is symmetric. If it is symmetric then it
  outputs the orbit and coarsest supporting partition of every gate. This
  algorithm runs in time polynomial in the size of the circuit.
  \label{lem:computing-support-orbit-gate}
\end{lem}

\begin{proof}
  For each transposition $(u,v) \in \sym_n$ and each gate $g$ in $C$ use
  Lemma~\ref{lem:compute-automorphisms} to check if the image of $g$ under
  $(u,v)$ exists. If for any transposition and gate the algorithm returns that
  no image exists then output that the circuit is not symmetric.

  We note that if all gates have an image under all transpositions then, since
  $\sym_n$ is generated by the set of transpositions, we have that $C$ is
  symmetric.

  We have from Lemma~\ref{lem:compute-automorphisms} that computing the action
  of $\sym_n$ on the gates of $C$ can be done in time polynomial in the size of
  the circuit. For each gate $g$ in $C$ we run the algorithm from
  Lemma~\ref{lem:computing-support-orbit} with $S := \emptyset$, $X := G$ (the
  set of gates in C), and $x := g$, and output the results.

  Since there are ${{n}\choose{2}} \leq n^2$ transpositions in $\sym_n$, the
  initial symmetry check can be completed in time polynomial in the size of the
  circuit. Moreover, from Lemmas~\ref{lem:compute-automorphisms} and
  \ref{lem:computing-support-orbit}, and the fact that $\vert C \vert \geq n$
  and $\vert C \vert \geq \vert \universe{g} \vert$, we have that the rest of
  the algorithm also runs in time polynomial in the size of the circuit.
\end{proof}

We now use Lemma~\ref{lem:computing-support-orbit} to prove the result for the
orbits and canonical supporting partitions of elements of the universes of gates
in the circuit.

\begin{lem}
  There is an algorithm that takes in a circuit $C$ of order $n$ with unique
  labels, a gate $g$ in $C$ with small support, and $a \in \universe{g}$, and
  outputs if the circuit is symmetric. If $C$ is symmetric it outputs the orbit
  $\orb_{\consp(g)} (a)$ and coarsest supporting partition $\SP_{\consp(g)}(a)$.
  This algorithm runs in time polynomial in the size of the circuit.
  \label{lem:computing-support-orbit-index}
\end{lem}
\begin{proof}
  Use the algorithm from Lemma~\ref{lem:computing-support-orbit-gate} in order
  to compute the canonical support of $g$. If the algorithm returns that $C$ is
  not symmetric, output that $C$ is not symmetric.

  Use the algorithm from Lemma~\ref{lem:computing-support-orbit}, with $S :=
  \consp(g)$, $X := \universe{g}$ and $x:= a$, and output the results.

  Notice that, since $\vert \universe{g} \vert \leq \vert C \vert$ and $n \leq
  \vert C \vert$, this algorithm runs in polynomial time.
\end{proof}

Anderson and Dawar~\cite{AndersonD17}, in their study of circuits with symmetric
gates, show that such circuits may be transformed in polynomial time into
equivalent circuits with unique extensions. They do this by showing that a
circuit with symmetric gates may be transformed into an equivalent \emph{rigid}
circuit in polynomial time, and that all rigid circuits have unique extensions.
Moreover, they also prove the existence of polynomial-time algorithms computing
the action of a permutation on a rigid circuit, and the orbits and coarsest
supporting partitions of gates in a rigid circuits. We have shown that
transparent circuits can be translated into equivalent circuits with unique
labels in polynomial time, and that circuits with unique labels have unique
extensions (see Proposition~\ref{}). Moreover, we have similarly shown that, for
transparent circuits, the action of a permutation, as well as the coarsest
supporting partition and orbit of a gate (or element of the universe of a gate),
can be computed in polynomial-time. Since all circuits with symmetric gates are
transparent, this is direct generalisation of the results of Anderson an Dawar.

\subsection{The Necessity of Transparency}
% The reader will notice that while we have included a specific requirement that
% each non-symmetric internal gate in a circuit have unique labels (i.e. that
% the circuit be transparent) no similar condition In this section we discuss
% the transparency condition on circuits. It is worth noting that, since the
% symmetric circuits of Anderson and Dawar~\cite{AndersonD17} have no
% non-symmetric internal gates, these circuits are transparent.

% we provide evidence f (which from lemma~\ref{} may be assumed to have unique
% extensions)or necessity of the transparency condition, presenting reductions
% from the graph-isomorphism problem to the problem of deciding some of this
% important properties (e.g. symmetry, syntactic-equivalence, computing the
% orbit of a gate, etc.) over general, not necessarily transparent, circuits. we
% note that in all of these cases the decision problem restricted to transparent
% circuits is polynomial-time decidable.

% we further argue that, since most natural algorithms for transforming an
% arbitrary symmetric circuit into an equivalent transparent circuit make use of
% the polynomial-time decidability of these properties, we should consider these
% hardness results evidence that computing this transformation may be as hard as
% the graph-isomorphism problem.
We have from the first subsection that a great number of useful properties are
polynomial-time computable on transparent circuits. However, it is still
reasonable to ask if the explicit inclusion of the transparency restriction is
strictly necessary for proving these results. In this subsection we present a
number of results suggesting the importance of the transparency requirement. In
particular, we present reductions from the graph-isomorphism problem to many
important decision problems addressed in the first subsection (e.g. deciding if
a circuit is symmetric, if a gate has unique labels, if two gates are
syntactically-equivalent, of if two gates are in the same orbit).

These results together strongly suggest the necessity of the transparency
condition for enabling the polynomial-time decidability of many basic properties
of circuits with non-symmetric gates. Moreover, while we do not show that there
is no polynomial-time computable transformation from a general circuit to an
equivalent transparent circuit, the difficulty associated with computing basic
circuit properties that seem essential for defining such a transformation
provide evidence in favour of this conjecture. (Indeed, the translation defined
by Anderson and Dawar~\cite{AndersonD17} from circuits with symmetric gates to
equivalent circuits with unique extensions makes explicit use of the
polynomial-time computability of syntactic-equivalence on such circuits).

As a final point, we note that while we present evidence against the ability to
transform arbitrary circuits into transparent circuits in polynomial-time, we do
show that the class of transparent circuits is polynomial-time decidable. In contrast, we show
that deciding the class of circuits with unique extensions is at least as hard
as the graph-isomorphism problem.

% We particularly note the hardness results for syntactic-equivalence note The
% difficulty of computing the orbit for non-transparent circuits is particularly
% important to note, as we make use of the existence of the polynomial-time
% decidability of the orbit in the proof of our main result.

% In particular, we show that the graph-isomorphism problem reduces to the
% problem of computing the syntactic-equivalence relation for general circuits.

% As we noted, Anderson and Dawar~\cite{AndersonD17} show that circuits (with
% symmetric gates) can be transformed in polynomial time into equivalent rigid
% circuits (in fact, their algorithm transforms these circuits into equivalent
% circuits with unique labels, a stronger condition than rigidity). Their proof
% of this result makes explicit use of the fact that the syntactic-equivalence
% relation on the gates of these circuits can be computed in polynomial-time

% These results together suggest that the a polynomial-time definable

% use of to compute the orbit is a particularly important limitation, as we make
% use of a polynomial-time algorithm for deciding the orbit of a gate (or
% element of a universe of a gate) in our proof of the main result.

% Moreover, we also show that

% However, if we allow gates that compute non-symmetric functions, it is not
% clear that the syntactic-equivalence relation remains polynomial-time
% decidable.

% . prove results analogous to Lemma~\cite{} The reader will notice that, while
% we require that the circuit families in our main result consist of transparent
% circuits, no similar explicit condition is introduced in Anderson and
% Dawar~\cite{}.

% When Anderson and Dawar~\cite{} prove these results for symmetric circuits
% (with symmetric gates) they explicitly use the fact that the syntactic
% equivalence relation can be computed in polynomial time.

% The proofs of these results by Anderson and Dawar~\cite{} can prove all of
% these results

% We now turn to the question of the importance of the transparency condition.
% It could be that, just as for the case of circuits with symmetric gates, a
% general circuit (not necessarily transparent) can be transformed in polynomial
% time into an equivalent transparent circuit. If so, from the argument above,
% we could assume without a loss of generality that $P$-uniform families of
% symmetric circuit have unique extensions, eliminating the need for the
% explicit transparency requirement present in the main theorem.

% While we do not show that no such transformation exists, we do show that many
% related problems are as hard as the graph isomorphism problem for a general,
% not-necessarily transparent, circuit). In particular, we show that the related
% problems of computing the syntactic equivalence relation for a circuit, or
% whether a gate in the circuit has unique labels, or unique extensions (in the
% sense defined below), are all also at least as hard as the graph isomorphism
% problem. We also show that computing other basic properties of a symmetric
% circuit, such as the orbit of a gate, is also at least as hard as the graph
% isomorphism problem. This is a particularly important limitation, as we make
% use of a polynomial-time algorithm for deciding the orbit of a gate (or
% element of a universe of a gate) in our proof of the main result.

% ,; address two related decision problems in Proposition \ref{} and Corollaries
% \ref{} and \ref{}. In partic

% As we will show in Proposition \ref{}, formulas of $\FPR$ can be translated
% into. For this transparent circuits. However, the transformation is
% complicated by the requirement that the resultant circuit be transparent.
% However, it is worth asking if the transparency condition is required, i.e. if
% it can be shown that

% \emph{rigid} circuit. They show that all circuits such circuits can be
% transformed into equivalent rigid circuits . They show that if a circuit is
% rigid then it has unique extensions and that every circuit with injective
% labels and symmetric gates can be transformed into an equivalent rigid circuit
% in polynomial time. We have similarly shown that a transparent circuit can be
% transformed into an equivalent one with unique labels in polynomial time, and
% that circuits with unique labels have unique extensions. Moreover, since all
% circuits with symmetric gates and injective labels are transparent, this is a
% strict generalisation of their result.

% and they show that a symmetric gate

% Using the language developed in this paper, a circuit $C_n$ is \emph{rigid} if
% it has injective labels and there are no two gates $g$ and $h$ in $C_n$ such
% that $g$ and $h$ are syntactically equivalent. Since their discussion is
% limited to circuits with symmetric gates and injective labels this is equ

% circuit, a condition analogous to the rigidity condition defined in this
% paper. The following

% It is worth noting that all symmetric circuits are transparent, and

% prove that it's a sufficient condition for establishing the uniqueness of the
% induced automorphism on the circuit. Moreover, they prove that any circuit
% (noting that they limit themselves to a discussion of circuits over a
% symmetric basis) may be transformed into an equivalent rigid circuit in
% polynomial time. As such, they may assume $P$-uniform symmetric circuit
% families are rigid without a loss of generality, and hence be may assume
% without a loss of generality that each permutation in $\sym_n$ uniquely
% extends to an automorphism of the circuit.

% However, in this subsection we show that deciding the rigidity of circuits
% over bases which may include non-symmetric functions is at least as hard as
% the graph isomorphism problem. However, we shoudl that on classes

% Although the rigidity condition we present in this paper is similarly defined,
% the existence of a polynomial-time computable transformation of a circuit into
% an equivalent rigid circuit is not as straight forward. Indeed, it is possible
% to show that the problem of determining if a given $(\mathbb{B},
% \tau)$-circuit is rigid is as least as hard as the graph isomorphism problem.
% This is a direct consequence of the following result.

% \begin{definition}
%   The \emph{syntactic equivalence class problem} is the decision problem for
%   the set of all triples $(C, g_1, g_2)$, where $C$ is a $(\mathbb{B},
%   \tau)$-circuit, and $g_1$ and $g_2$ are two syntactically equivalent gates
%   in $C$.
% \end{definition}

% \begin{definition}
%   The \emph{rigidity problem} is the decision problem for the set of all
%   circuits $C$ where $C$ is a rigid circuit.
% \end{definition}

% \begin{definition}
%   The \emph{unique labels problem} is the decision problem for the set of all
%   circuits $C$ where $C$ has unique labels.
% \end{definition}

% \begin{prop}
%   Let $\tau$ be any non-empty relational vocabulary and let $n, r, p \in
%   \nats$ with $p$ prime. There is a a polynomial time reduction from the graph
%   isomorphism problem to the problem of deciding if a given pair of gates in a
%   given symmetric rank-circuit for structures of size $n$ that (i) has
%   injective labels, (ii) contains no constant gates, and (iii) contains at
%   most two rank gates with bound $r$ and prime $p$, are syntactically
%   equivalent.
%   \label{prop:syntactic-graph-iso}
% \end{prop}
% \begin{proof}
%   We have from \cite{} that there is a polynomial time reduction from the
%   graph isomorphism problem to the bipartite isomorphism problem. The
%   bipartite isomorphism problem is the decision problem for the set of all
%   pairs of partitioned bipartite graphs $B_1 := (U_1, V_1, E_1)$ and $B_2 :=
%   (U_2, V_2, E_2)$ such that there exists a graph isomorphism $\pi : B_1
%   \rightarrow B_2$ with $\restr{\pi}{U_1} = U_2$ and $\restr{\pi}{V_1} = V_2$.

%   Suppose we are given two partitioned bipartite graphs $B_1 := (U_1, V_1,
%   E_1)$ and $B_2 := (U_2, V_2, E_2)$. We assume, without a loss of generality,
%   that there exists $a, b \in \nats$ such that $U_1 = U_2 = [a]$ and $V_1 =
%   V_2 = [b]$.

%   Let $R$ be a relation symbol in $\tau$ and let $k := \arty{R}$. Let $G_{R}
%   := \{g_{R, \vec{c}} : \vec{c} \in [n]^k\}$, $G_{\text{mid}} := \{\land_0,
%   \land_1, \neg_0, \land_{\text{out}} \}$, $G_{\rank} : = \{ g_{\rank, 1},
%   g_{\rank, 2}\}$, and $G_{\land} := \{g_{i, (u,v)} : i \in [2] \, (u,v) \in
%   E_i \}$. Let $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a
%   $(\{\rank^{1}_2\}, \tau)$-circuit defined as follows. Let $G = G_R \cup
%   G_{\text{mid}} \cup G_{\rank} \cup G_{\land}$ and $\Omega$ be the $0$-ary
%   function $\land_{\text{out}}$. For each $\vec{c} \in [n]^{\arty{R}}$ let
%   $\Lambda(\vec{c}) = g_{R, \vec{c}}$. Define $\Sigma$ as follows. For each $g
%   \in G$,
%   \begin{itemize}
%     \setlength\itemsep{0mm}
%   \item if $g \in G_R$ then $\Sigma(g) = R$,
%   \item if $g$ equals $\land_0$ or $\land_1$ then $\Sigma(g) = \land[n^k]$
%   \item if $g$ equals $\land_{\text{out}}$ then $\Sigma(g) = \land[2]$,
%   \item if $g \in G_\rank$ let $\Sigma(g) = \rank^r_p [a,b]$, and
%   \item if $g \in G_{\text{in}}$ and $g$ then $\Sigma(g) = \land[1]$.
%   \end{itemize}
%   Define $L$ as follows. For each $g \in G$,
%   \begin{itemize}
%     \setlength\itemsep{0mm}
%   \item if $g \in G$ and $g = g_{\text{out}}$ then for each $i \in [2]$,
%     $L(g)(i) := g_{\rank, i}$,
%   \item if $g \in G_\rank$ and $g = g_{\rank, i}$ then $L(g)(p,q) = g_{i,
%     (p,q)}$,
%   \item if $g \in G_{\land}$ and $g = g_{i, (p,q)}$ then $L(g)(1) = \land_1$
%     if $(p,q) \in E_i$ and $L(g)(1) = \neg_0$ otherwise,
%   \item if $g = \neg_0$ then $L(g)(1) = \land_0$, and
%   \item if $g = \land_0$ or $g = \land_1$ then for all $p \in [n^k]$ we have
%     that $L(g)(p)$ equals $\Lambda^{-1}(\vec{c}_p)$, where $\vec{c}_p$ is the
%     $p$th element of $[n]^k$ in the lexicographical ordering on $[n]^k$.
%   \end{itemize}

%   We note that for $i \in [2]$, $L(g_{\rank, i})(p,q) = \land_1$ if $(p,q)$ is
%   an edge in in $B_i$ and $L(g_\rank, i)(p,q) = \neg_0$ if $(p,q)$ is not an
%   edge in $B_i$. We thus have that $B_1$ and $B_2$ are bipartite isomorphic
%   (in the sense defined above) if, and only if, $g_{\rank, 1}$ is
%   syntactically equivalent to $g_{\rank, 2}$.

%   Since the construction of $C_n$ can be implemented in time polynomial in the
%   combined sizes of the input graphs, the mapping of $(B_1, B_2)$ to the tuple
%   $(C_n, (g_{\rank, 1}, g_{\rank, 2}))$ witnesses the reduction. The result
%   follows.
% \end{proof}

We now present a reduction from the graph-isomorphism problem to the problem of
deciding if two gates in a circuit are syntactically-equivalent. In fact, we
prove a stronger result, presenting a reduction from the graph-isomorphism
problem to the problem of computing the syntactic-equivalence relation over an
ostensibly simpler class of circuits.

\begin{prop}
  Let $\rho$ be any non-empty relational vocabulary and let $n, r, p \in \nats$,
  with $p$ prime. There is a a polynomial time reduction from the
  graph-isomorphism problem to the problem of deciding if a given pair of gates
  in a given symmetric rank-circuit for structures of size $n$ that (i) has
  injective labels, (ii) contains no constant gates, and (iii) contains at most
  two rank gates with bound $r$ and prime $p$, are syntactically equivalent.
  \label{prop:syntactic-graph-iso}
\end{prop}
\begin{proof}
  We have from \cite{} that there is a polynomial time reduction from the graph
  isomorphism problem to the bipartite isomorphism problem. The bipartite
  isomorphism problem is the decision problem for the set of all pairs of
  partitioned bipartite graphs $B_1 := (U_1, V_1, E_1)$ and $B_2 := (U_2, V_2,
  E_2)$ such that there exists a graph isomorphism $\pi : B_1 \rightarrow B_2$
  with $\restr{\pi}{U_1} = U_2$ and $\restr{\pi}{V_1} = V_2$.

  Suppose we are given two partitioned bipartite graphs $B_1 := (U_1, V_1, E_1)$
  and $B_2 := (U_2, V_2, E_2)$. We assume, without a loss of generality, that
  there exists $a, b \in \nats$ such that $U_1 = U_2 = [a]$ and $V_1 = V_2 =
  [b]$.

  Let $R$ be a relation symbol in $\rho$ and let $k := \arty(R) > 0$. Let $G_{R}
  := \{g_{R, \vec{c}} : \vec{c} \in [n]^k\}$, $G_{\text{mid}} := \{\land_0,
  \land_1, \neg_0, \land_{\text{out}} \}$, $G_{\rank} : = \{ g_{\rank, 1},
  g_{\rank, 2}\}$, and $G_{\text{nodes}} := \{g_{i, (u,v)} : i \in [2] \, (u,v)
  \in E_i \}$. Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a
  $(\{\rank^{1}_2\}, \rho)$-circuit of order $n$ defined as follows. Let $G =
  G_R \cup G_{\text{mid}} \cup G_{\rank} \cup G_{\text{nodes}}$ and $\Omega$ be
  the $0$-ary function $\land_{\text{out}}$. For each $\vec{c} \in
  [n]^{\arty(R)}$ let $\Lambda(\vec{c}) = g_{R, \vec{c}}$. Define $\Sigma$ as
  follows. For each $g \in G$,
  \begin{itemize}
    \setlength\itemsep{0mm}
  \item if $g = \land_{\text{out}}$ then $\Sigma(g) = \land[2]$,
  \item if $g \in G_\rank$ then $\Sigma(g) = \rank^r_p [a,b]$,
  \item if $g \in G_{\text{nodes}}$ then $\Sigma(g) = \land[1]$,
  \item if $g= \neg_0$ then $\Sigma(g) = \neg$,
  \item if $g$ equals $\land_0$ or $\land_1$ then $\Sigma(g) = \land[n^k]$, and
  \item if $g \in G_R$ then $\Sigma(g) = R$.
  \end{itemize}
  Define $L$ as follows. For each $g \in G$,
  \begin{itemize}
    \setlength\itemsep{0mm}
  \item if $g = \land_{\text{out}}$ then for each $i \in [2]$, $L(g)(i) :=
    g_{\rank, i}$,
  \item if $g \in G_\rank$ and $g = g_{\rank, i}$ then $L(g)(p,q) = g_{i,
      (p,q)}$,
  \item if $g \in G_{\text{nodes}}$ and $g = g_{i, (p,q)}$ then if $(p, q \in
    E_i)$ then $L(g)(1) = \land_1$, otherwise $L(g)(1) = \neg_0$,
  \item if $g = \neg_0$ then $L(g)(1) = \land_0$, and
  \item if $g = \land_0$ or $g = \land_1$ then for all $p \in [n^k]$ we have
    that $L(g)(p)$ equals $\Lambda^{-1}(\vec{c}_p)$, where $\vec{c}_p$ is the
    $p$th element of $[n]^k$ in the lexicographical ordering on $[n]^k$.
  \end{itemize}

  We note that for $i \in [2]$, $L(g_{\rank, i})(p,q) = \land_1$ if, and only
  if, $(p,q)$ is an edge in in $B_i$ and $L(g_\rank, i)(p,q) = \neg_0$ if, and
  only if, $(p,q)$ is not an edge in $B_i$. We thus have that $B_1$ and $B_2$
  are bipartite-isomorphic (in the sense defined above) if, and only if,
  $g_{\rank, 1}$ is syntactically equivalent to $g_{\rank, 2}$.

  Since the construction of $C$ can be implemented in time polynomial in the
  combined sizes of the input graphs, the mapping of $(B_1, B_2)$ to the tuple
  $(C, (g_{\rank, 1}, g_{\rank, 2}))$ is a reduction, and the result follows.
\end{proof}

Since there is a trivial reduction from the problem of computing the
syntactic-equivalence relation over a restricted class of circuits to the
problem over the general class of circuits, we have the following corollary.

\begin{cor}
  There is a polynomial-time reduction from the graph isomorphism problem to the
  problem of determining if a given pair of gates in a given circuit are
  syntactically-equivalent.
  \label{lem:syntactically-equivilent-general-hard}
\end{cor}

We also have a reduction from the problem of computing the syntactic-equivalence
relation to the problem of deciding if a given gate in a circuit has unique
labels. From then transitivity of polynomial-time many-one reductions, this gives
us a reduction from the graph-isomorphism problem to the problem of deciding if
a gate has unique labels.

\begin{lem}
  There are a polynomial-time reduction from the problem of determining if a
  given pair of gates in a given circuit are syntactically equivalent to the
  problems of determining if a given gate in a given circuit has unique labels.
  \label{lem:syntactically-equivalent-unique-labels}
\end{lem}

\begin{proof}
  Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a circuit of order
  $n$ and let $g_1, g_2 \in G$. Let $D$ be the circuit formed from $C$ by
  removing every gate $g \in G \setminus\{g_1, g_2\}$ such that $\neg W_t(g,
  g_1) \land \neg W_t(g, g_2)$ (i.e. all those gates in the circuit such that
  there is no path from them to either $g_1$ or $g_2$). Here $W_t$ is the
  relation defined in the proof of Lemma~\ref{}. Let $C'$ be the circuit formed
  from $D$ by adding in a single two-input $\AND$ gate $g'$ and connecting the
  outputs of $g_1$ and $g_2$ to the inputs of $g'$. Moreover, we let this $g'$
  be the single output gate of $C'$.

  It follows that $g_1$ and $g_2$ are syntactically equivalent in $C$ if, and
  only if, $g'$ has unique labels in $C'$. Since the construction of $C'$ from
  $C$ can be completed in polynomial time, the mapping of $(C, (g_1, g_2))$ to
  $(C', g')$ is a reduction.
\end{proof}

We can construct a similar argument for reducing the problem of deciding if two
gates are syntactically equivalent to the problem of deciding if a given gate
$g$ in a circuit $C$ does not have \emph{unique extensions}. We say a gate $g$
has unique extensions if there is no permutation such that two automorphisms of
the circuit extend the permutation and disagree with each other on $g$ (i.e. $g$
is not a counterexample to $C$ having unique extensions).

\begin{lem}
  There is a polynomial-time reduction from the problem of determining if a
  given pair of gates gates in a given $(\mathbb{B}, \rho)$-circuit are
  syntactically-equivalent to the problem of determining if for a given triple
  $(C, g)$, where $C$ is a circuit of order $n$, $g$ is a gate in $C$, that
  there exists $\sigma \in \sym_n$ and automorphisms $\pi, \pi' \in \aut(C)$
  extending $\sigma$ such that $\pi (g) \neq \pi' (g)$.
  \label{lem:syntactically-equivilent-unique-extensions}
\end{lem}
\begin{proof}
  Let $C$ be a circuit of order $n$ and let $g_1$ and $g_2$ be two gates in $C$.
  Note that for any gate $g$ in $\sigma \in sym_n$, if $\pi, \pi' \in \aut(C)$
  extend $\sigma$ and $\pi_e := \pi'\pi{-1}$ then $\pi(g) \neq \pi'(g)$ if, and
  only if, $\pi_e (g) \neq g$. It follows that there exists $\sigma \in sym_n$
  such that there are automorphisms $\pi, \pi' \in \aut(C)$ extending $\sigma$
  such that $\pi (g) \neq \pi'(g)$ if, and only if, there exists $\pi_e$
  extending the trivial permutation such that $\pi (g) \neq g$.

  Let $C'$ be the circuit constructed from $C$ as in the proof of
  Lemma~\ref{lem:syntactically-equivalent-unique-labels}. We now prove that the
  mapping $(C, (g_1, g_2))$ to $(C', g_1)$ is a reduction. Let $\pi_e$ be a
  function from the gates of $C'$ to the gates of $C'$ that swaps $g_1$ and
  $g_2$ and fixes all other gates. It follows that if $g_1$ and $g_2$ are
  syntactically-equivalent in $C$, then they are syntactically-equivalent in
  $C'$, and so $\pi_e$ is a non-trivial automorphism extending the trivial
  permutation, and $g_1$ does not have unique extensions in $C'$. In the other
  direction, suppose $g_1$ does not have unique extensions in $C'$. Then there
  exists an automorphism $\pi_e \in \aut(C')$ extending the trivial permutation
  and such that $\pi_e(g_1) \neq g_1$. But $g_1$ is a child of the single output
  gate $g'$ (which must be fixed by any automorphism), and the only other child
  of $g'$ is $g_2$. It follows $\pi_e$ swaps $g_1$ and $g_2$, and so $g_1$ and
  $g_2$ are syntactically-equivalent in $C'$. The result follows.
\end{proof}

We now show that there is a reduction from the graph-isomorphism problem to the
problem of deciding if a given circuit is symmetric.

\begin{prop}
  The graph-isomorphism problem is polynomial-time reducible to the problem of
  determining if a circuit is symmetric.
  \label{prop:graph-iso-symmetric}
\end{prop}

\begin{proof}
  We use a similar approach as in Proposition~\ref{prop:syntactic-graph-iso},
  and so proving a reduction from the bipartite-graph-isomorphism to the problem
  of deciding if a circuit is symmetric.

  Suppose we are given two partitioned bipartite graphs $B_1 := (U_1, V_1, E_1)$
  and $B_2 := (U_2, V_2, E_2)$. We assume, without a loss of generality, that
  there exists $a, b \in \nats$ such that $U_1 = U_2 = [a]$ and $V_1 = V_2 =
  [b]$.

  Let $\rho:= \{R\}$ be a relational vocabulary, where $R$ is a unary relational
  symbol. Fix any number $r$ and $p$ prime. We define a $(\rho, \RB)$-circuit $C
  := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ of order two as follows. Let
  $G_{R} := \{g_{R, 1}, g_{R_2}\}$ and $G_{\text{ands}} := \{\land^1_0,
  \land^2_0, \land^1_1, \land^2_1 , \land_{\text{out}}\}$, $G_{\text{negs}} :=
  \{,neg^1_0, \neg^2_0\}$, $G_{\rank} : = \{ g_{\rank, 1}, g_{\rank, 2}\}$, and
  $G_{\text{nodes}} := \{g_{i, (u,v)} : i \in [2] \, (u,v) \in E_i \}$. Let $G =
  G_R \cup G_{\text{ands}} \cup G_{\text{negs}} \cup G_{\rank} \cup
  G_{\text{nodes}}$ and $\Omega$ be the $0$-ary function $\land_{\text{out}}$.
  Let $\Lambda(1) := g_{R, 1}$ and $\Lambda(2) := g_{R,2}$. Define $\Sigma$ as
  follows. For each $g \in G$,
  \begin{itemize}
    \setlength\itemsep{0mm}
  \item if $g$ equals $\land_{\text{out}}$ then $\Sigma(g) = \land[2]$,
  \item if $g \in G_\rank$ let $\Sigma(g) = \rank^r_p [a,b]$,
  \item if $g \in G_{\text{nodes}}$ then $\Sigma(g) = \land[1]$,
  \item if $g \in G_{\text{ands}}$ then $\Sigma(g) = \land[1]$ and if $g \in
    G_{\text{negs}}$ then $\Sigma(g) = \neg$, and
  \item if $g \in G_R$ then $\Sigma(g) = R$.
  \end{itemize}
  Define $L$ as follows. For each $g \in G$,
  \begin{itemize}
    \setlength\itemsep{0mm}
  \item if $g = g_{\text{out}}$ then for each $i \in [2]$, $L(g)(i) := g_{\rank,
      i}$,
  \item if $g \in G_\rank$ and $g = g_{\rank, i}$ then $L(g)(p,q) = g_{i,
      (p,q)}$,
  \item if $g \in G_{\text{nodes}}$ and $g = g_{i, (p,q)}$ for some $i \in [2]$,
    then $L(g)(1) = \land^i_1$ if $(p,q) \in E_i$ and $L(g)(1) = \neg^i_0$
    otherwise ,
  \item if $g = \neg^i_0$ for some $i \in [2]$, then $L(g)(1) = \land^i_0$, and
  \item if $g = \land^i_0$ or $g = \land^i_1$ for some $i \in [2]$, then
    $L(g)(p) = \Lambda^{-1}(i)$.
  \end{itemize}

  We note that for $i \in [2]$, $L(g_{\rank, i})(p,q) = \land^i_1$ if, and only
  if, $(p,q)$ is an edge in $B_i$ and $L(g_\rank, i)(p,q) = \neg^i_0$ if, and
  only if, $(p,q)$ is not an edge in $B_i$. It can be shown that $C$ is
  symmetric if, and only if, there exists an extension of the transposition
  $(1,2)$ to an automorphism of the circuit, which holds if, and only if, there
  exists an extension of $(1,2)$ to an automorphism of the circuit such that
  $(1,2) (L(g_{\rank, 1}))$ is isomorphism-equivilent to $L(g_{\rank, 2})$,
  which holds if, and only if, $B_1$ and $B_2$ are biparetite-isomorphic.

  % Suppose $C$ is not symmetric. If $\vert L(g_{\rank,1})^{-1}(\land^1_1) \vert
  % \neq L_(g_{\rank,2})^{-1}(\land^2_1) \vert$ then clear $B_1$ and $B_2$ are
  % not biparetite-isomorphic as they have different numbers of edges. Suppose
  % $\vert L(g_{\rank,1})^{-1}(\land^1_1) \vert =
  % L_(g_{\rank,2})^{-1}(\land^2_1) \vert$. Then the only reason $C$ would not
  % be symmetric is that there is no extension of $\sigma$ to the circuit t

  % If $B_1$ and $B_2$ are

  % We thus have that if $B_1$ and $B_2$ are bipartite-isomorphic

  % (in the sense defined in the proof of
  % Proposition~\ref{prop:syntactic-graph-iso}) if, and only if, $g_{\rank, 1}$
  % is syntactically-equivalent to $g_{\rank, 2}$.

  Since the construction of $C$ can be implemented in time polynomial in the
  combined sizes of the input graphs, the mapping of $(B_1, B_2)$ to $C$ is a
  reduction, and the result follows.
\end{proof}

We now show that computing the orbit of a gate for a general circuit is as hard
as the graph isomorphism problem. We make use of the ability to compute the
orbit of a gate in polynomial-time in
Section~\ref{sec:translating-formulas-to-FPR}, when translating families of
circuits into equivalent formulas.

\begin{lem}
  There is a polynomial-time reduction from the graph isomorphism problem to the
  problem of computing if two gates in a given circuit are in the same orbit.
  \label{lem:graph-iso-to-orbit}
\end{lem}
\begin{proof}
  Let $C$ be a circuit. Let $g_1$ and $g_2$ be two gates in $C$ such that
  $H_{g_1} = H_{g_2}$. Then there exists $\pi \in \aut(C)$ such that $\pi (g_1)
  = g_2$ if, and only if, $g_1$ is syntactically-equivalent to $g_2$. As such,
  we may use the same construction as in
  Proposition~\ref{prop:syntactic-graph-iso} to prove this result.
\end{proof}
We have from Propositions~\ref{prop:syntactic-graph-iso}
and~\ref{prop:graph-iso-symmetric}, and
Lemmas~\ref{lem:syntactically-equivalent-unique-labels},
\ref{lem:graph-iso-to-orbit}
and~\ref{lem:syntactically-equivilent-unique-extensions}, that a number of basic
circuit properties are at least as hard for general circuits as the
graph-isomorphism problem. In contrast, all of these properties are known to be
polynomial-time computable for transparent circuits (as follows from
Lemmas~\ref{lem:unique-labels-syntactic-equiv}
and~\ref{lem:computing-support-orbit-gate}).

The hardness results for the problems of computing syntactic-equivalence
relation and deciding if a gate has unique labels are particularly worth noting
as many natural algorithms for translating a circuit into an equivalent
transparent circuit (or one with unique labels) make use of polynomial-time
decidability of these properties. Indeed, the translation defined by Anderson
and Dawar~\cite{AndersonD17} from circuits with symmetric gates to equivalent
circuits with unique extensions makes explicit use of the polynomial-time
computability of the syntactic-equivalence relation on such circuits. As such,
these results, along with the hardness results for many other basic circuit
properties (e.g. symmetry, unique extensions, or the orbits of a gate) provides
evidence against the existence of an easily-definable polynomial-time
translation from circuits to transparent circuits, or circuits with unique
labels.

% We note that in all of the above casesgive us that many circuit properties of
% interest are harder to compute than the graph-isomorphism problem. In
% particular, determining

% We have shown that basic properties of a circuit, including the ability to
% compute the syntactic equivalence relation or whether a gate has unique
% labels, are as hard to decide as the graph-isomorphism problem. Moreover,

% incluidng that various properties of the circuit that seem necessary for
% defining a translation of a circuit into an equivalent transparent circuit are
% as hard to compute as the graph-isomorphism problem. We note that all of these
% properties are polynomial-time computable for transparent circuits (as follows
% from Lemma~\ref{} and Lemma~\ref{}).

While we have provided evidence against the ability to efficiently transform a
circuit into an equivalent transparent circuit, we now show that, in contrast,
there is a polynomial-time algorithm for checking if a circuit is transparent.
This has a certain significance, as we now have transparency is not some
unverifiable condition on circuits, further motivating the usefulness of this
definition.

\begin{prop}
  There is an algorithm that takes as input a circuit, decides if that circuit
  is transparent and runs in time polynomial in the size of the circuit.
  \label{prop:transparent-polynomial-time}
\end{prop}
\begin{proof}
  Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
  \rho)$-circuit. We first check that, for each non-symmetric gate $g \in G$,
  $L(g)$ is an injection. If not, we return that $C$ is not transparent.

  The height of a gate $g$ in the circuit is the distance from $g$ to the set of
  input gates. For each $p \in \nats$ let $G^p \subseteq G$ be the set of all
  gates of height $p$ and let $G^{\leq p} = \bigcup_{0 \leq i \leq p}G^i$. Note
  that each $g \in G^1$, $g$ has unique labels. Thus, from
  Lemma~\ref{lem:unique-labels-syntactic-equiv}, we can compute the syntactic
  equivalence relation between gates in $G^{\leq 1}$ efficiently. We construct a
  loop as follows. Let $p$ be initialised to $1$. We have that every
  non-symmetric gate $g \in G^{\leq p}$ has unique gates. We compute the
  syntactic-equivalence relation on $G^{\leq p}$ and check if each non-symmetric
  gate in $g \in G^{i + 1}$ has unique labels. If not, halt and output that the
  circuit is not transparent. If $p = \depth(C) -1$ then halt and output that
  the circuit is transparent. If neither halt state is reached, then increment
  $p$ by one and continue to the next iteration of the loop.

  We note that in every iteration of the loop we have that every non-symmetric
  gate in $G^{\leq p}$ has unique labels. Thus, from Proposition
  \ref{prop:unique-labels-syntactic-equiv}, we may compute the
  syntactic-equivalence relation on this set of gates efficiently. It follows
  that the above algorithm can be implemented so as to run in polynomial time.
\end{proof}

We similarly have that the unique labels property on circuits can be decided in
time polynomial in the number of gates in the circuit.

\begin{cor}
  There is an algorithm that takes in a circuit and decides if that circuit has
  unique labels and runs in time polynomial in the size of the circuit.
\end{cor}
\begin{proof}
  Let $C$ be the input circuit. From Proposition
  \ref{prop:transparent-polynomial-time} we may check if $C$ is transparent in
  polynomial time. If $C$ is not transparent halt and output that $C$ does not
  have unique labels. If $C$ is transparent then from Lemma \ref{} we may
  compute the syntactice-equivalence relation on the gates of $C$ efficiently.
  This then allows us to check if each gate in $C$ has unique labels.
\end{proof}

% perhaps related to the problem of translating a circuit into an equivalent
% transparent circuit are at least as hard as the graph isomorphism problem. We
% now show that additionally recognising if a circuit has unique extensions is
% at least as hard as the graph isomorphism problem.

We have restricted ourselves to transparent circuits in large part because they
can be transformed in polynomial-time into circuits with unique extensions and
because the transparency property is polynomial-time verifiable. It may be asked
why we do not just include an explicit restriction to circuits with unique
extensions. We now show that, in contrast with transparency, the problem of
deciding if a circuit has unique-extensions is at least as hard as the
graph-isomorphism problem.

\begin{lem}
  There is a polynomial-time reduction from the graph isomorphism problem to the
  problem of determining if a given circuit does not have unique extensions.
  \label{lem:unique-extensions-hard}
\end{lem}
\begin{proof}
  We use a similar argument as for Proposition \ref{prop:syntactic-graph-iso}.
  We again argue using a reduction from thee bipartite isomorphism problem. Let
  $B_1 := (U_1, V_1, E_1)$ and $B_2 := (U_2, V_2, E_2)$ and let $C$ be the
  associated circuit defined in the proof of Proposition
  \ref{prop:syntactic-graph-iso}. Let $C' = \op{merge-all} (C, G_{\land})$.
  Notice that $B_1$ and $B_2$ are isomorphic if, and only if, $g_{\rank, 1}$ and
  $g_{\rank, 2}$ are syntactically equivalent, which holds if, and only if,
  there exists $\pi \in \aut(C')$ extending the trivial permutation such that
  $\pi (g_{\rank, 1}) = g_{\rank, 2}$, which is true if, and only if, $C'$ does
  not have unique extensions. it follows that the mapping of $(B_1, B_2)$ to
  $C'$ defines a reduction.
\end{proof}

\begin{remark}
  It's interesting to note that the circuit used in the reduction does not have
  injective labels. If we instead ask about a reduction from GI to the problem
  of deciding if a circuit has unique extensions and injective labels, then I
  can reduce from to the problem of deciding if two rigid graphs are isomorphic.
  It is unknown if this decision problem is as hard as the full graph
  isomorphism problem. After looking around a bit I discovered that it's a very
  important open problem in quantum computation. Is this worth mentioning?
\end{remark}

% We have that if a circuit is transparent then we may compute in polynomial
% time the syntactic equivalence relation on the gates of that circuit, and
% hence compute an equivalent circuit that has unique extensions. However, we've
% shown that absent the transparency condition, computing the the syntactic
% equivalence relation is at least as hard as the graph isomorphism problem.
% Moreover, other properties that can be computed in polynomial time for
% transparent circuits, e.g. deciding if particular gates have unique labels or
% might act as counterexamples to the unique extensions, have also been shown to
% be at least as the graph isomorphism problem.

% While we have not shown that there is no polynomial time algorithm that
% translates an arbitrary circuit into an equivalent transparent circuit, we
% have provided evidence in favour of the conjecture that such an algorithm
% might not exist.

% \begin{remark}
%   I really don't like the slightly vague language here. I would prefer to say
%   this differently. How does one provide `evidence' that a functional problem
%   is hard, when one has proved results about a few related decision problems?
% \end{remark}

% However, we must then address another question: If we must include an explicit
% requirement on circuits, why not simply require that the circuit have unique
% extensions? But we have from Lemma \ref{lem:unique-extensions-hard} that at
% the least verifying that a circuit have unique extensions is at least as hard
% as the graph isomorphism problem. We show that, in contrast, deciding if a
% circuit is transparent is in $\PT$.

% \begin{prop}
%   There is an algorithm that takes as input a circuit, decides if that circuit
%   is transitive and runs in time polynomial in the size of the circuit.
%   \label{prop:tansitive-polynomial-time}
% \end{prop}
% \begin{proof}
%   Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
%   \tau)$-circuit. We first check that, for each non-symmetric gate $g \in G$,
%   $L(g)$ is an injection. If not, we return that $C$ is not transitive.

%   The height of a gate $g$ in the circuit is the distance from $g$ to the set
%   of input gates. For each $p \in nats$ let $G^p \subseteq G$ be the set of
%   all gates of height $p$ and let $G^{\leq p} = \bigcup_{0 \leq i \leq p}G^i$.
%   Note that each $g \in G^1$, $g$ has unique labels. Thus, from Lemma \ref{},
%   we can compute the syntactic equivalence relation between gates in $G^{\leq
%   1}$ efficiently. We construct a loop as follows. Let $p$ be initialised to
%   $1$. We have that every non-symmetric gate $g \in G^{\leq p}$ has unique
%   gates. We compute the syntactic equivalence relation on $G^{\leq p}$ and
%   check if each non-symmetric gate in $g \in G^{i + 1}$ has unique labels. If
%   not, halt and output that the circuit is not transitive. If $p = \depth(C)
%   -1$ then halt and output that the circuit is transitive. If neither halt
%   state is reached, then increment $p$ by one and continue to the next
%   iteration of the loop.

%   We note that in every iteration of the loop we have that every non-symmetric
%   gate in $G^{\leq p}$ has unique labels. Thus, from Proposition
%   \ref{prop:unique-labels-syntactic-equiv}, we may compute the syntactic
%   equivalence relation on this set of gates efficiently. Thus it is easy to
%   see that the above algorithm can be implemented so as to run in polynomial
%   time.
% \end{proof}

% A similar result for circuits with unique labels.

% \begin{cor}
%   There is an algorithm that takes in a circuit and decides if that circuit
%   has unique labels and runs in time polynomial in the size of the circuit.
% \end{cor}
% \begin{proof}
%   Let $C$ be the input circuit. From Proposition
%   \ref{prop:transitive-polynomial-time} we may check if $C$ is transitive in
%   polynomial time. If $C$ is not transitive halt and output that $C$ does not
%   have unique labels. If $C$ is transitive then from Lemma \ref{} we may
%   compute the syntactic equivalence relation on the gates of $C$ efficiently.
%   This then allows us to check if each gate in $C$ has unique labels.
% \end{proof}

% We thus have that we can verify in polynomial time that a family of circuits
% indeed is transparent or has unique labels. The same cannot be said for the
% unique extensions property.

% \begin{lem}
%   There is an algorithm that takes in a symmetric circuit $C$ of order $n$
%   with unique labels, a gate $g$ in $C$ and $a \in \universe{g}$, the orbit
%   $\orb_g (a)$ and coarsest supporting partition $\SP_g (a)$.
% \end{lem}
% \begin{proof}
%   Let $(u,v) \in \sym_n$ be a transposition. We can check if $(u,v) \in
%   \stab(g)$ using Lemma~\ref{lem:compute-automorphisms}. Then $(u,v)$ acts
%   like an isomorphism at $g$, and hence $(u,v) \cdot a = L(g)^{-1}((\sigma
%   L(g)(\vec{x}))) (i)$, where $\vec{x} \in \ind(g)$ such that $\vec{x} (i) =
%   a$ for some $i \in [\vert \vec{x} \vert]$. Thus, since
%   Lemma~\ref{lem:compute-automorphisms} gives us that that we can compute
%   $\sigma L(g)(\vec{x})$ in polynomial time, we can compute $(u,v) \cdot a$ in
%   polynomial-time.

%   We note that

%   and hence we can compute $\sigma \cdot a$ effeciently. and hence compute
%   $\orb_g(a) = \{ \sigma \cdot a : \sigma \in \stab(g)\}$.

% \end{proof}

% Once again we note that computing the orbit of a gate for a general circuit is
% as hard as the graph isomorphism problem. We make use of the ability to
% compute the orbit of a gate in polynomial time in sub-section
% \ref{sec:translating-formulas-to-FPR} when translating families of circuits
% into equivalent formulas. As such the approach in this paper would fail for
% the general circuit.

% \begin{prop}
%   There is a polynomial-time reduction from the graph isomorphism problem to
%   the problem of computing if two gates in a given circuit are in the same
%   orbit.
%   \label{prop:graph-iso-to-orbit}
% \end{prop}
% \begin{proof}
%   Let $C$ be a circuit. Let $g_1$ and $g_2$ be two gates in $C$ such that
%   $H_{g_1} = H_{g_2}$. Then there exists $\pi \in \aut(C)$ such that $\pi
%   (g_1) = g_2$ if, and only if, $g_1$ is syntactically equivalent to $g_2$. As
%   such, we may use the same construction as in
%   Proposition~\ref{prop:syntactic-graph-iso} to prove this result.
% \end{proof}

% \begin{lem}
%   There is a polynomial-time Turing reduction from the problem of determining
%   if a given pair of gates in a given circuit are syntactically equivalent to
%   the problem of deciding if a circuit is transparent.
%   %   If the problem of deciding if a given circuit is transparent can be
%   %   decided
%   %   in
%   %   polynomial time then the graph isomorphism problem is in polynomial
%   %   time.
% \end{lem}
% \begin{proof}
%   Suppose there is an algorithm that takes as input, runs in time polynomial
%   in the size of the circuit, and decides whether or not the circuit is
%   transparent.

%   From Corollary \ref{} it is sufficient to show that there is a
%   polynomial-time algorithm for the problem of deciding if a pair of gates in
%   a given circuit are syntactically equivalent. Let $C_n$ be a circuit and
%   $g_1$ and $g_2$ be two gates in the circuit.

%   %   We simply need a polynomial-time reduction from the problem of computing
%   %   t
%   %   to the problem
%   %   of checking if a given circuit is transparent. Let $C_n =\langle G,
%   %   \Omega,
%   %   \Sigma, \Lambda, L\rangle$ be a circuit and let $g_1$ and $g_2$ be two
%   %   gates
%   %   in $G$. We now construct a circuit $C_n'$. If $g_1 = g_2$ then let
%   %   $C_n'$ be
%   %   any transparent circuit. If $g_1$ and $g_2$ do not satisfy any of
%   %   conditions
%   %   (i), (ii), (iii) or (v) of syntactic equivalence then let $C_n'$ be any
%   %   non-transparent circuit. So suppose all these conditions are met and
%   %   $g_1
%   %   \neq
%   %   g_2$, then let $D_n$ be the sub-circuit of $C_n$ consisting of exactly
%   %   those
%   %   gates $g$ in $C_n$ such that $W_t(g, g_1)$ or $W_t(g, g_2)$. Then let
%   %   $C_n'$
%   %   be $D_n'$ with an additional gate $g_\rank$, such that $g_\rank $ is
%   %   labelled
%   %   by the function $\rank^1_2[2,1]$ and $g_\rank$
% \end{proof}

% \begin{corollary}
% \end{corollary}

% We have from this proposition that even many nice properties Since there is a
% polynomial-time reduction from this problem reduces the general problem of
% deciding the syntatic equivilence relation for an arbitary

% \begin{corollary}
%   There is a polynomial-time reduction from the graph isomorphism problem to
%   the problem of determining if a given $(\mathbb{B}, \tau)$-circuit is rigid.
% \end{corollary}

% \begin{corollary}
%   There is a polynomial-time reduction from the graph isomorphism problem to
%   the problem of determining if a given gate in a given $(\mathbb{B},
%   \tau)$-circuit has unique labels.
% \end{corollary}

% reduction from the graph isomorphism from to the problem of of computing the
% the syntactic equivalence relation on the gates of an arbitrary $(\mathbb{B},
% \tau)$-circuit.

% It is worth noting that if we restrict the input to a class of circuits
% defined over symmetric bases then we can decide the syntactic equivalence
% relation in polynomial time.

% % \begin{prop}
% %   Let $C_n$ be a circuit with symmetric gates. There is an algorithm that
% %   takes in such a circuit, runs in time polynomial in the size of the circuit,
% %   and outputs the syntactic equivalence relation on the gates of $C_n$.
% %   \label{prop:symmetric-syntactic}
% % \end{prop}
% % \begin{proof}
% % \end{proof}

% Moreover, it turns out that being able to compute the syntactic equivalence
% relation in polynomial time for some class of circuits $\mathcal{C}$ implies
% that the existence of a polynomial-time algorithm for converting circuits in
% $C$ into equivalent rigid circuit.

% % \begin{prop}
% %   Let $\mathcal{C}$ be a set of circuits. Suppose the syntactic equivalence
% %   relation can be computed in polynomial time for circuits in $\mathcal{C}$.
% %   It follows that there is an algorithm that runs in polynomial time that
% %   takes in a circuit $C \in \mathcal{C}$ and outputs a rigid circuit $C''$
% %   such that if $C$ is symmetric then $C'$ is symmetric.
% %   \label{prop:syntactic-equivilence-rigid}
% % \end{prop}
% % \begin{proof}
% % \end{proof}

% The following result gives us that the unique labels condition is sufficient.

% % \begin{prop}
% %   Let $\mathcal{C}$ be syntactically transparent class of circuits. It follows
% %   that there exists an algorithm that takes in a $(\mathbb{B}, \tau)$-circuit
% %   $C \in \mathcal{C}$ and outputs a $(\mathbb{B} \cup \mathbb{B}_{\std},
% %   \tau)$-circuit $C'$ such that $C$ and $C'$ compute the same function, $C'$
% %   is rigid, and if $C$ is symmetric then $C'$ is symmetric. Moreover, this
% %   algorithm runs in time polynomial in the size of the input circuit.
% % \end{prop}
% % \begin{proof}
% %   Let $C' = \make-injective-all(\op{merge-all} (C, G)($). We have that $C'$ is
% %   symmetric if $C$ is symmetric. Since the syntactic equivalence relation can
% %   be computed in polynomial time for circuits in $\mathcal{C}$ it follows that
% %   this operation can be implemented so as to run in time polynomial in the
% %   size of $C$. Clearly every gate $g$ in $C'$ belongs to a singleton syntactic
% %   equivalence class.
% % \end{proof}

% \begin{lem}
%   Let $\mathbb{B}$ be a basis of symmetric functions. Then for any class of
%   circuits $\mathcal{C}$ defined over the basis $\mathbb{B}$, $\mathcal{C}$ is
%   a syntactically transparent class of circuits.
% \end{lem}
% In contrast to
% \begin{lem}
%   If the class of all circuits is syntactically transparent then then graph
%   isomorphism problem is in $\PT$.
% \end{lem}

% \begin{lem}
%   Let $\mathcal{C}$ be a syntactically transparent class of circuits. There is
%   an algorithm that takes as input a $(\mathbb{B}, \tau)$-circuit $C \in
%   \mathcal{C}$ and decides if $C$
% \end{lem}

% Since the class of The following result, also proved by Anderson and Dawar
% \cite{AndersonD17}, follows as a corollary.

% \begin{lem}
%   Let $\mathcal{C}$
% \end{lem}

% \begin{lem}
%   Let $C_n = \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a $(\mathbb{B},
%   \tau)$-circuit computing a $q$-ary query. If $C_n$ has unique labels then it
%   is $C_n$ rigid
%   \label{lem:unique-implies-rigid}
% \end{lem}
% \begin{proof}

%   %   Suppose there exists a gate $g'$ such that $W_t (g, g')$ and $W_t
%   %   (\pi(g),
%   %   g')$ and $\pi (g') = g'$, then $\pi H_{g'} = H_{g'}$, and since $g'$ has
%   %   unique labels it follows that $\pi$ acts trivially on $H_{g'}$ (i.e. for
%   %   all
%   %   $h \in H_{g'}$, $\pi(h) = h$). Moreover, for any pair of gates $h,h' \in
%   %   G$
%   %   such that $W(h, h')$ and $W_t(h', g')$, if $\pi$ acts on trivially on
%   %   the
%   %   children of $h'$ then $\pi (h) = h$ and so $\pi$ must act trivially

%   %   $\pi$ acts trivially on the children of $h$.

%   %   If $\Omega_g \cap \Omega_{\pi(g)} = \emptyset$ then, since
%   %   $\Omega_{\pi(g)}
%   %   =
%   %   \pi \Omega_g$, there exists $g' \in \Omega_g$ such that $\pi g' \neq
%   %   g'$.
%   %   But
%   %   $\pi$ must act trivially on output gates, so this is a contradiction. So
%   %   there
%   %   exists $g' \in \Omega_g \cap \Omega_{\pi(g)}$. But then $W_t (g, g')$
%   %   and
%   %   $W_t
%   %   (\pi (g), g')$.

%   %   We have that $g$ must be a non-output internal gate. So $g$ is
%   %   syntactically
%   %   equivalent to $\pi (g)$.

%   %   and let $h$ be a gate such that $W_t (g, h)$.
% \end{proof}

% \begin{prop}
%   Let $C_n$ be a circuit with unique labels. If
% \end{prop}

% \begin{prop}

% \end{prop}
% \begin{proof}
% \end{proof}

% \begin{prop}
%   Let $\mathcal{C}$ be a class on which the Let $C_n := \langle G, \Omega,
%   \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B}, \tau)$-circuit with unique
%   labels. There is a deterministic algorithm that takes in such a circuit and
%   outputs the syntactic equivalence relation on $G$. Moreover, this algorithm
%   runs in time polynomial in the size of the circuit.
%   \label{prop:unique-labels-syntactic-equiv}
% \end{prop}

% % \begin{prop}
% %   There is an algorithm that takes in a $(\mathbb{B}, \tau)$-circuit $C$ with
% %   unique labels and outputs the syntactic equivalence relation on its gates.
% %   This algorithm runs in time polynomial in the size of $C$.
% %   \label{prop:unique-labels-syntactic-equiv}
% % \end{prop}
% % \begin{proof}
% %   We build of the relation by induction. Let $g$
% % \end{proof}

% Putting together Propositions \ref{prop:symmetric-syntactic},
% \ref{prop:syntactic-equivilence-rigid}, and
% \ref{prop:unique-labels-syntactic-equiv}, we have that there is a
% polynomial-time algorithm that takes as input a circuit with unique labels and
% outputs an equivalent rigid circuit. In fact, there is an equivalence of sorts
% between the unique labels condition and the rigidity condition.

% \begin{prop}
%   Let $\mathcal{C}$ be a family of circuits. There is an algorithm that runs
%   in polynomial-time that takes in a circuit $C \in \mathcal{C}$ and outputs a
%   rigid circuit $C'$ such that if $C$ is symmetric then $C'$ is symmetric if,
%   and only if, there is an algorithm that runs in polynomial-time and takes in
%   a circuit $C \in \mathcal{C}$ and outputs a circuit $C'$ with unique labels
%   such that if $C$ is symmetric then $C'$ is symmetric.
% \end{prop}

% It follows then that for the symmetric circuits defined over bases of
% symmetric functions discussed by Anderson and Dawar~\cite{} we may assume the
% circuits are rigid and/or have unique labels without a loss of generality. For
% the more general circuit discussed in this paper we cannot make such an
% assumption as deciding rigidity is harder then graph isomorphism. However, if
% we restrict ourselves to families of circuits with unique labels then again we
% may assume rigidity without a loss of generality.

% Of course, this restriction to circuits with unique labels is only useful if
% we can show that formulas in rank logic can be translated into $P$-uniform
% families circuits with unique labels. In the next subsection we prove that
% this is indeed the case.

\end{document}

### 2018-01-30 sections/symmetric-circuits.tex
24th January 2018
30 Jan

@@
 structured Boolean functions. These are functions whose inputs naturally encode
-$\tau$-structures and where the output is invariant under the natural symmetries
+$\rho$-structures and where the output is invariant under the natural symmetries
 of such structures. The\emph{matrix-invariant} functions are a natural
@@
 % AD - rewrote the paragraph to reduce the use of subscripts and superscripts.
-Let $\tau = (R, S, \nu)$ be a many-sorted vocabulary. Let $D := \biguplus_{s \in
+Let $\tau := (R, S, \nu)$ be a many-sorted vocabulary. Let $D := \biguplus_{s \in
   S} D_{s} = \{(s,d) : d \in D_s\}$, be a disjoint union of non-empty sets,
@@
 over $D$. We call this \emph{the structure defined by $(\tau, D)$}, and denote
-it by $\str(\tau, D)$.
+it by $\str{\tau, D}$.
 
@@
 the \emph{index defined by the pair $(\tau, D)$} be the set $\biguplus_{R_i\in
-  R} R^{D}_i$. We often use this set to index the input to a Boolean function,
-as such we abuse notation and denote the index defined by $(\tau, D)$ by
-$\ind(\tau, D)$, and call $\tau$ the vocabulary and $D$ the universe of
-$\ind(\tau, D)$.
+  R} R^{D}_i := \{ (\vec{a}, R) : \vec{a} \in R^{D}, \, R \in \tau \} $. We
+often use this set to index the input to a Boolean function, and as such we
+denote the index defined by $(\tau, D)$ by $\ind(\tau, D)$, and call $\tau$ the
+vocabulary and $D$ the universe of $\ind(\tau, D)$.
+
+We abbreviate $(\vec{a}, R) \in \ind(\tau, D)$ by $\vec{a}_R$, and refer
+to $R$ as \emph{the type} of $\vec{a}_R$. We often abuse notation and treat
+$\vec{a}_R$ as the tuple $\vec{a}$ in $R^D$. In the event that there is only one
+relational symbol in $\tau$ we identify $\vec{a}_R$ with $\vec{a}$.
+
+% Although we often use the convention of identifying the elements of the
+% disjoint union with the elements of the sets from which the union was formed
+% (i.e. identify the elements of $\ind(\tau, D)$ with the tuples that appear in
+% a some relation in $\str(\tau, D)$), it is important to note that $\ind(\tau,
+% D)$ is formally a disjoint union, and as such each tuple in this set is
+% associated with an identifiable relation symbol. We refer to $R$ as the type
 
@@
 For the remainder of this subsection we fix a vocabulary $\tau$ and a
-many-sorted set $D := \biguplus_{s \in S} D_{s}$, and let $X := \ind (\tau, D)$
-and $G \leq \sym_{X}$. There is an obvious action of $G$ on $X$. There is also
-an obvious action of the automorphism group $\str(\tau, D)$ on $X$ (with
-permutations in $\str(\tau, D)$ acting element-wise on tuples in $X$). We denote
-this group by $\aut(\tau, D)$, and identify it with the subgroup of $\sym_X$
-that acts equivalently on $X$.
+many-sorted set $D := \biguplus_{s \in S} D_{s}$, let $X := \ind (\tau, D)$ and $G \leq \sym_{X}$.
+There is an obvious action of $G$ on $X$. There is also an action of the
+automorphism group $\str{\tau, D}$ on $X$ defined for the automorphism $\sigma$
+by $\sigma \cdot \vec{a}_R := (\sigma \vec{a})_R$. We denote the group of
+automorphisms of $\str{\tau, D}$ by $\aut(\tau, D)$, and identify it with the
+subgroup of $\sym_X$ that acts equivalently on $X$.
 
@@
 
-We say that two functions $f: \ind(\tau, D) \rightarrow H$ and $g: \ind(\tau',
+We say that two functions $f: \ind(\tau, D) \rightarrow H$ and $g: \ind(\tau,
 D') \rightarrow H$ are \emph{isomorphism-equivalent} if there exists an
-isomorphism $\pi :\str(\tau, D) \rightarrow \str(\tau', D')$ such that $f (x) =
-g (\pi (x))$ for all $x \in \str(\tau, D)$. It is easy to see that
+isomorphism $\pi :\str{\tau, D} \rightarrow \str{\tau, D'}$ such that $f (\vec{a}_R) =
+g (\pi \vec{a}_R)$ for all $\vec{a}_R \in \ind(\tau, D)$. It is easy to see that
 isomorphism-equivalence is an equivalence relation.
 
-We are often interested in the case where $X = \ind(\tau, D) = \ind(\tau', D')$.
-We say that $f, g X \rightarrow H$ are \emph{$G$-equivalent} if there exists
+We are often interested in the case where $X = \ind(\tau, D) = \ind(\tau, D')$.
+We say that $f, g: X \rightarrow H$ are \emph{$G$-equivalent} if there exists
 $\sigma \in G$ such that $f = \sigma \cdot g$. We note that in this case $f$ and
-$g$ are \emph{isomorphism-equivalent} if, and only if, they are $\aut(\tau,
-G)$-equivalent.
-
-In this paper we will often let the co-domain $H$ be the binary symbols
-$\{0,1\}$, and so consider functions of the form $f : X \rightarrow \{0,1\}$. In
-this case we may think of $f$ as defining for each relation $R^D_i$ a subset of
-that relation, and thus determining a $\tau$-structure over the universe $D$. We
-note that two functions $f, g: X \rightarrow \{0,1\}$ are isomorphism-equivalent
-if, and only if, the two $\tau$-structures they determine are isomorphic.
+$g$ are isomorphism-equivalent if, and only if, they are $\aut(\tau,
+D)$-equivalent.
+
+In this paper we will often take the co-domain $H$ to be $\{0,1\}$, and so $f :
+X \rightarrow \{0,1\}$. In this case we may think of $f$ as defining for each
+relation $R^D_i$ a subset of that relation, and so determining a
+$\tau$-structure over the universe $D$. We note that two functions $f, g: X
+\rightarrow \{0,1\}$ are isomorphism-equivalent if, and only if, the two
+$\tau$-structures they determine are isomorphic.
 
@@
 function. We say $F$ is \emph{$G$-invariant} if it is constant on $G$-equivalent
-input vectors, i.e. for all $G$-equivalent $\vec{x}, \vec{y} \in \{0,1\}^{X}$,
-$F(\vec{x}) = F(\vec{y})$. We say $F$ is \emph{isomorphism-invariant} if it is
-$\aut(\tau, D)$-invariant. Note that a structured function with vocabulary
-$\tau$ is isomorphism-invariant if, and only if, it decides a property of
+input vectors, i.e. for all $G$-equivalent $f, g \in \{0,1\}^{X}$, $F(f) =
+F(g)$. We say $F$ is \emph{isomorphism-invariant} if it is $\aut(\tau,
+D)$-invariant. Note that a structured function with vocabulary $\tau$ is
+isomorphism-invariant if, and only if, it decides a property of
 $\tau$-structures.
@@
 symmetry conditions we discussed are naturally reproduced. Suppose $\tau$ is
-single-sorted and consists of a single unary relation. Then any structured
+single-sorted and consists of a single unary relation symbol. Then any structured
 function $F$ with vocabulary $\tau$ is isomorphism-invariant if, and only if, it
@@
 
-In each case a natural choice of the structure indexes the input to the
+In each case a natural choice of $\tau$ (and $D$) indexes the input to the
 structured function appropriately and produces the appropriate symmetry
 condition. It is worth mentioning that the graph-invariant case is not strictly
-reproduced above, as the structured functions are rather defined over directed
-graphs.
+reproduced using structured functions. This is because structured functions
+index the input string using the elements of the relations of the complete
+$\tau$-structure (in this case, edges in the complete graph). As such, the input
+string is indexed by ordered pairs of elements, rather than two-element
+subsets, and as such the symmetry condition on the relation is not enforced. As
+such, in the structured function case the function decides properties of
+directed graphs, rather than ordinary graphs. We should note, however, that the symmetry
+of the edge relation is a property of directed-graph, and as such can be decided
+by an isomorphism-invariant structured function over the graph vocabulary.
+
+% , and any
+% input sequence encodes a sub-relation of that complete relation. As such, the
+% function  This is because in the event that $\tau := {E}$ (where $E$ is
+% a binary relation, thought of as the edge relation) there is no assurance that
+% the function $f : \ind
+% (\tau, D) \rightarrow \{0,1\}$ is encoding
+
+% as the structured functions are rather defined over directed
+% graphs.
 
@@
 D_{s_p}$, then for all $s \in \{s_1 , \ldots , s_p\}$ there exists $d_s \in
-\mathbb{N}$ such that $D_{s} = [d_s]$. We also assume that every $(\tau,
+\nats{N}$ such that $D_{s} = [d_s]$. We also assume that every $(\tau,
 D)$-structured function has the property that every $a \in D$ appears in at
@@
 
-We now define a \emph{$(\mathbb{B}, \tau)$-circuit} . This is a circuit that
-computes a function on structures in the relational vocabulary $\tau$ and where
-the gates are labelled by elements of the basis $\mathbb{B}$. Each element of
-the basis is a $(\tau,D)$-structured function for some $\tau$ and $D$. Note
-that, in the interests of keeping our definitions from getting excessively
-complicated, we do not consider circuits computing functions over multi-sorted
-vocabularies.
+We now define a \emph{$(\mathbb{B}, \rho)$-circuit} . This is a circuit that
+computes a function on structures in the relational vocabulary $\rho$ and where
+the gates are labelled by elements of the basis $\mathbb{B}$ consisting of
+structured functions. Note that, in the interests of keeping our definitions
+from getting excessively complicated, we do not consider circuits computing
+functions over multi-sorted vocabularies.
 
 \begin{definition}[Circuits on Structures]
-  Let $\mathbb{B}$ be a basis and $\tau$ be a relational vocabulary, we define a
-  \emph{$(\mathbb{B}, \tau)$-circuit} $C_n$ computing a $q$-ary query $Q$ as a
-  structure $\langle G, \Omega, \Sigma, \Lambda, L \rangle$.
+  Let $\mathbb{B}$ be a basis and $\rho$ be a relational vocabulary, we define a
+  \emph{$(\mathbb{B}, \rho)$-circuit} $C$ of order $n$ computing a $q$-ary query
+  $Q$ as a structure $\langle G, \Omega, \Sigma, \Lambda, L \rangle$.
   \begin{itemize}
     \setlength\itemsep{0mm}
-  \item $G$ is called the set of gates of $C_n$ and $\vert C_n \vert := \vert G
+  \item $G$ is called the set of gates of $C$ and $\vert C \vert := \vert G
     \vert$.
@@
     constant function mapping to a single output gate.
-  \item $\Sigma$ is a function from $G$ to $\mathbb{B} \uplus \tau \uplus
+  \item $\Sigma$ is a function from $G$ to $\mathbb{B} \uplus \rho \uplus
     \{0,1\} $ such that $\vert \Sigma^{-1} (0) \vert \leq 1$ and $\vert
-    \Sigma^{-1} (1) \vert \leq 1$. Those gates mapped to $\tau \uplus \{0,1\}$
-    are called input gates, with those mapped to $\tau$ called relational gates
+    \Sigma^{-1} (1) \vert \leq 1$. Those gates mapped to $\rho \uplus \{0,1\}$
+    are called input gates, with those mapped to $\rho$ called relational gates
     and those mapped $\{0,1\}$ called constant gates. Those gates mapped to
@@
 
-Let $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
-\rho)$-circuit. The $n$ is used to indicates that $C_n$ accepts structures of
-size $n$. For a gate $g \in C_n$, we define the \emph{index} of $g$, denoted by
-$\ind(g)$, as $\ind(\Sigma(g))$. We define the relation $W \subseteq G^2$ by
+Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
+\rho)$-circuit of order $n$. The order of a circuit denotes the fact that it
+takes as input structures of size $n$. We often consider families of circuits of
+the form $(C_n)_{n \in \nats}$, and here we assume that each $C_n$ is a circuit
+of order $n$. For a gate $g \in C$, we define the \emph{index} of $g$, denoted
+by $\ind(g)$, as $\ind(\Sigma(g))$. We define the relation $W \subseteq G^2$ by
 $W(h,g)$ if, and only if, $h \in \range(L(g))$. For each $g \in G$ we let
@@
 $\Sigma(g)$, respectively, and denote the vocabulary of $g$ by $\vocab{g}$ and
-the universe by $\universe{g}$. We also let $\aut(g) := \aut(\tau, D)$ and
-$\str(g) := \str(\tau, D)$.
+the universe by $\universe{g}$. We also let $\aut(g) := \aut(\vocab{g}, \universe{g})$ and
+$\str{g} := \str{\vocab{g}, \universe{g}}$.
 
@@
 
-Let $\tau$ be a relational vocabulary, $\mathcal{A}$ a $\tau$-structure over an
+Let $\rho$ be a relational vocabulary, $\mathcal{A}$ a $\rho$-structure over an
 $n$-element universe $U$ and $\gamma \in [n]^{\underline{U}}$. Let $\gamma
 \mathcal{A}$ be the structure on universe $[n]$ formed by mapping $U$ in
-accordance with $\gamma$. The evaluation of a $(\mathbb{B}, \tau)$-circuit $C_n$
-computing a $q$-ary query $Q$ proceeds by recursively evaluating the gates in
-the circuit. The evaluation of the gate $g$ for the bijection $\gamma$ and input
-$\mathcal{A}$ is denoted by $C[\gamma \mathcal{A}](g)$, and is given as follows
+accordance with $\gamma$. The evaluation of a $(\mathbb{B}, \rho)$-circuit $C$
+of order $n$ computing a $q$-ary query $Q$ proceeds by recursively evaluating
+the gates in the circuit. The evaluation of the gate $g$ for the bijection
+$\gamma$ and input $\mathcal{A}$ is denoted by $C[\gamma \mathcal{A}](g)$, and
+is given as follows
 \begin{enumerate}
@@
 \item If $g$ is a constant gate then it evaluates to the bit given by
-  $\Sigma(g)$.
-\item If $g$ is a relational gate then $g$ evaluates to true iff $\gamma
-  \mathcal{A} \models \Sigma(g)(\Lambda (g))$.
-\item If $g$ is an internal gate such that $\Sigma (g)$ let $L^{\gamma}_g:
+  $\Sigma(g)$,
+\item if $g$ is a relational gate then $g$ evaluates to true iff $\gamma
+  \mathcal{A} \models \Sigma(g)(\Lambda (g))$, and
+\item if $g$ is an internal gate such that $\Sigma (g)$ let $L^{\gamma}_g:
   \ind(g) \rightarrow \{0,1\}$ be defined by $L^{\gamma}_g(x) = C[\gamma
   \mathcal{A}](L(g)(x))$, for all $x \in \ind(g)$. Then $g$ evaluates to true
-  iff $\Sigma(g) (L^{\gamma}_g) = 1$.
+  if, and only if, $\Sigma(g) (L^{\gamma}_g) = 1$.
 \end{enumerate}
-We say that $C_n$ defines the $q$-ary query $Q \subseteq U^q$ under $\gamma$
-where $\vec{a} \in Q$ if, and only if, $C_n[\gamma \mathcal{A}](\Omega (\gamma
-\vec{a})) = 1$.
+We say that $C$ defines the $q$-ary query $Q \subseteq U^q$ under $\gamma$ where
+$\vec{a} \in Q$ if, and only if, $C[\gamma \mathcal{A}](\Omega (\gamma \vec{a}))
+= 1$.
 
@@
 \begin{definition}[Invariant Circuit]
-  Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit, computing some $q$-ary query. We
-  say $C_n$ is \emph{invariant} if for every $\tau$-structure $\mathcal{A}$ of
-  size $n$, $\vec{a} \in U^{q}$, and $\gamma_1, \gamma_2: [n]^{\underline{U}}$
-  we have that $C[\gamma_1 \mathcal{A}](\Omega (\gamma_1 \vec{a})) = C[\gamma_2
-  \mathcal{A}](\Omega (\gamma_2 \vec{a}))$.
+  Let $C$ be a $(\mathbb{B}, \rho)$-circuit of order $n$, computing some $q$-ary
+  query. We say $C$ is \emph{invariant} if for every $\rho$-structure
+  $\mathcal{A}$ of size $n$, $\vec{a} \in U^{q}$, and $\gamma_1, \gamma_2:
+  [n]^{\underline{U}}$ we have that $C[\gamma_1 \mathcal{A}](\Omega (\gamma_1
+  \vec{a})) = C[\gamma_2 \mathcal{A}](\Omega (\gamma_2 \vec{a}))$.
 \end{definition}
 
-In other words $C_n$ is invariant if the evaluation of the circuit on any
-$n$-element structure $\mathcal{A}$ does not depend on the particular map
-$\gamma$ that takes the universe of the structure to $[n]$. In general, the
-evaluation of a circuit depends on the presentation of the structure (i.e.\ the
-bijection $\gamma$). If a family of $(\mathcal{B}, \tau)$-circuits $\mathcal{C}$
-is invariant it follows that the query computed is a $q$-query on
-$\tau$-structures. Thus if $q = 0$ then $\mathcal{C}$ computes a property of
-$\tau$-structures. The following lemma allows us to recast this notion in terms
-of the language developed in this paper.
+It follows that the circuit $C$ of order $n$ is invariant if, and only if, the
+evaluation of the circuit for any input $n$-element structure $\mathcal{A}$ does
+not depend on the bijection $\gamma$. In general, the evaluation of a circuit
+depends on the presentation of the structure (i.e.\ the bijection $\gamma$). If
+a family of $(\mathcal{B}, \rho)$-circuits $\mathcal{C}$ is invariant it follows
+that the query computed is a $q$-query on $\rho$-structures. Thus if $q = 0$
+then $\mathcal{C}$ computes a property of $\rho$-structures. The following lemma
+allows us to recast this notion in terms of the language developed in this
+paper.
 
 \begin{lem}
-  Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit. The function computed by $C_n$ is
-  $\tau$-invariant if, and only if, $C_n$ is an invariant circuit.
+  Let $C$ be a $(\mathbb{B}, \rho)$-circuit of order $n$ computing a $0$-ary
+  query. The function computed by $C$ is isomorphism-invariant if, and only if,
+  $C$ is an invariant circuit.
 \end{lem}
+\begin{proof}
+  We first note that, since $C$ computes a $0$-ary query, there is exactly one
+  output gate. We call this gate $g_o$. We can associate with each relational
+  gate $g$ in $C$ a unique pair $(\vec{a}, R)$, where $R := \Sigma (g)$ is a
+  relational symbol in $\tau$ and $\vec{a} := \Lambda_R(g)$ is an an element of
+  $R^{[n]}$. Thus we can think of the function $F_C$ computed by the circuit as
+  having it's input string indexed by the elements of $\ind(\rho, [n])$, and so
+  think of $F_C$ as a $(\rho, [n])$-structured function.
+
+  % The value of $F_C (f)$, for some element $f \in
+  % \{0,1\}^{\ind(\rho, [n])}$, is computed by assigning to each relational gate
+  % $(\vec{a}, R)$ the value $f(\vec{a}, R)$, recursively evaluating the
+  % circuit,
+  % and letting $F_C (f)$ be the result of evaluating $g_{\text{out}}$.
+
+  We now present a number of observations, and then combine these observations
+  to prove both directions of the hypothesis. Let $\mathcal{B}$ be a
+  $\rho$-structure of size $n$ over the universe $[n]$. We can define a function
+  $f_{\mathcal{B}} : \ind(\rho, [n]) \rightarrow {0,1}$ such that
+  $f_{\mathcal{B}} (\vec{a}_R) = 1$ if, and only if, $\vec{a} \in
+  R^{\mathcal{B}}$. Let $f : \ind(\rho, [n]) \rightarrow \{0,1\}$. We can define
+  the $\rho$-structure $\mathcal{B}_f$ over the universe $[n]$ such that for all
+  $R \in \rho$, we have $\vec{a} \in R^{\mathcal{B}_f}$ if, and only if,
+  $f(\vec{a}_R) = 1$. It is easy to see that the functions $\mathcal{B} \mapsto
+  f_{\mathcal{B}}$ and $f \mapsto \mathcal{B}_f$ are inverse to one another, and
+  so define a bijection. Moreover, we notice that for all $\sigma \in \sym_n$ we
+  have that $f_{\sigma \mathcal{B}}(\vec{a}_R) = 1$ if, and only if, $\vec{a}
+  \in R^{\sigma \mathcal{B}}$ if, and only if, $\sigma^{-1} \vec{a} \in
+  R^{\mathcal{B}}$ if, and only if, $\sigma ^{-1} f_{\mathcal{B}}(\vec{a}_R) =
+  f_{\mathcal{B}}(\sigma^{-1} \vec{a}_R)= 1$.
+
+  Let $\mathcal{A}$ be a $\rho$-structure of size $n$ over the universe $U$, and
+  let $\gamma_1, \gamma_2 \in [n]^{\underline{U}}$. From the definition of $F_C$
+  it follows that for $\gamma \in \sym_n$ we have that $F_C (f_{\gamma
+    \mathcal{A}})$ if, and only if, $C[\gamma \mathcal{A}](g_{\text{o}}) = 1$.
+
+  Let $\gamma_1, \gamma_2 \in [n]^{\underline{U}}$ and let $\sigma \in \sym_n$
+  be such that $\gamma_1 = \sigma \gamma_2$. We have that
+  \begin{align*}
+    C[\gamma_1 \mathcal{A}](g_{\text{o}}) = C[\gamma_2 \mathcal{A}](g_{\text{o}}) & \Leftrightarrow  F_C(f_{\gamma_1 \mathcal{A}}) = F_C (f_{\gamma_2 \mathcal{A}}) \\
+                                                                                  & \Leftrightarrow F_C(f_{\gamma_1 \mathcal{A}}) = F_C (f_{\sigma^{-1}\gamma_1 \mathcal{A}}) \\
+                                                                                  & \Leftrightarrow F_C(f_{\gamma_1 \mathcal{A}}) = F_C (\sigma f_{\gamma_1 \mathcal{A}}).
+  \end{align*}
+
+  We now combine the above observations to prove the result. Suppose $F_C$ is
+  isomorphism-invariant. Let $\gamma_1, \gamma_2 \in [n]^{\underline{U}}$ and
+  let $\sigma \in \sym_n$ be such that $\gamma_1 = \sigma \gamma_2$. Then, from
+  isomorphism-invariance, we have $F_C(f_{\gamma_1 \mathcal{A}}) = F_C (\sigma
+  f_{\gamma_1 \mathcal{A}})$, and so $C[\gamma_1 \mathcal{A}](g_{\text{o}}) =
+  C[\gamma_2 \mathcal{A}](g_{\text{o}})$.
+
+  Suppose $C$ is invariant. Fix the bijection $\gamma_1 \in
+  [n]^{\underline{U}}$. Let $\sigma \in \sym_n$ and $f: \ind(\rho, [n])
+  \rightarrow \{0,1\}$. Let $\mathcal{A} = \gamma^{-1}_1 \mathcal{B}_f$ and
+  $\gamma_2 := \sigma^{-1}\gamma_1 $. Since $C$ is invariant we have $C[\gamma_1
+  \mathcal{A}](g_{\text{o}}) = C[\gamma_2\mathcal{A}](g_{\text{o}})$, and so
+  $F_C (\sigma f_{\gamma_1 \mathcal{A}}) = F_C(f_{\gamma_1 \mathcal{A}})$. But
+  $f_{\gamma_1 \mathcal{A}} = f_{\mathcal{B}_f} = f$, and so $F_C (\sigma f) =
+  F_C (f)$. It follows that $F_C$ is isomorphism-invariant.
+
+  % Let $f_{\gamma \mathcal{A}} : \ind(\rho, [n]) \rightarrow {0,1}$ be defined
+  % by
+  % $f (\vec{a}_R) = 1$ if, and only if, $\vec{a} \in R^{\gamma \mathcal{A}}$.
+  % So
+  % $C[\gamma_1 \mathcal{A}](g_{\text{out}}) = F_C (f_{\gamma_1 \mathcal{A}}) =
+  % F_C(f_{\sigma \gamma_2 \mathcal{A}}) = F_C (\sigma f_{\gamma_2 \mathcal{A}})
+  % =
+  % F_C (f_{\gamma_2 \mathcal{A}}) = C[\gamma_2 \mathcal{A}](g_{\text{out}})$.
+
+  % are labelled by relational symbols from $\tau$ and elements of the
+  % complete-re
+
+  % Let $X := \ind(\rho, [n])$. We can define an injection $f_R$ that maps the
+  % relational gate $g$ to $\vec{a}_R \in X$, where $R:= \Sigma(g)$ and $\vec{a}
+  % := \Lamda_R(g)$. function computed by $C$ $F_C : \{0,1\}^{X} \rightarrow
+  % \{0,1\}$.
+\end{proof}
 % AD - does this require a few lines of proof? GW - To be added. I have not done
@@
 
-% \begin{definition}[Automorphism]
-%   let $C = \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a
-%   $(\mathbb{B},\tau)$-circuit computing a $q$-ary query on structures of size
-%   $n$, and where $\mathbb{B}$ is a basis of isomorphism-invariant structured
-%   functions. Let $\sigma \in \sym_n$ and $\pi: G \rightarrow G$ be a bijection
-%   such that
+% \begin{definition}[Automorphism]1 let $C = \langle G, \Omega, \Sigma, \Lambda,
+%   L\rangle$ be a $(\mathbb{B},\tau)$-circuit computing a $q$-ary query on
+%   structures of size $n$, and where $\mathbb{B}$ is a basis of
+%   isomorphism-invariant structured functions. Let $\sigma \in \sym_n$ and
+%   $\pi: G \rightarrow G$ be a bijection such that
 %   \begin{itemize}
@@
   let $C = \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a
-  $(\mathbb{B},\tau)$-circuit computing a $q$-ary query on structures of size
-  $n$, and where $\mathbb{B}$ is a basis of isomorphism-invariant structured
-  functions. Let $\sigma \in \sym_n$ and $\pi: G \rightarrow G$ be a bijection
-  such that
+  $(\mathbb{B},\tau)$-circuit of order $n$ computing a $q$-ary, and where
+  $\mathbb{B}$ is a basis of isomorphism-invariant structured functions. Let
+  $\sigma \in \sym_n$ and $\pi: G \rightarrow G$ be a bijection such that
   \begin{itemize}
@@
     x)$,
-  \item for all gates $g \in G$, let $\Sigma (g) = \Sigma (\pi g)$,
+  \item for all gates $g \in G$, $\Sigma (g) = \Sigma (\pi g)$,
   \item for each relational gate $g \in G$, $\sigma \Lambda (g) = \Lambda (\pi
@@
 
-It follows that for any symmetric circuit $C_n$ there is a homomorphism $h$ that
-maps $\sym_n$ to $\aut(C_n)$, taking any $\sigma \in \sym_n$ to an automorphism
-that extends it. Suppose $C_n$ contains no relational gates of non-zero arity.
-In that case $C_n$ computes a constant function. As such, in this paper we
-always assume a circuit contains at least one relational gate with non-zero
-arity. There there exists a relational gate in $C_n$ with some element of $[n]$
-appearing in the tuple labelling that gate. By symmetry it follows that all
-elements of $[n]$ appear in tuples labelling relational gates in $C_n$. Thus no
-two distinct elements of $\sym_n$ agree on all input gates, and so the
+It follows that for any symmetric circuit $C$ of order $n$ there is a
+homomorphism $h$ that maps $\sym_n$ to $\aut(C)$, taking any $\sigma \in \sym_n$
+to an automorphism that extends it. Suppose $C$ contains no relational gates of
+non-zero arity. In that case $C$ computes a constant function. As such, in this
+paper we always assume a circuit contains at least one relational gate with
+non-zero arity. There there exists a relational gate in $C$ with some element of
+$[n]$ appearing in the tuple labelling that gate. By symmetry it follows that
+all elements of $[n]$ appear in tuples labelling relational gates in $C$. Thus
+no two distinct elements of $\sym_n$ agree on all input gates, and so the
 homomorphism $h$ is injective.
@@
 \begin{definition}
-  We say that a circuit $C_n$ has \emph{unique extensions} if for every $\sigma
-  \in \sym_n$ there is at most one $\pi_{\sigma} \in \aut(C_n)$ such that
+  We say that a circuit $C$ has \emph{unique extensions} if for every $\sigma
+  \in \sym_n$ there is at most one $\pi_{\sigma} \in \aut(C)$ such that
   $\pi_{\sigma}$ extends $\sigma$.
@@
 
-While we establish an approximately analogous argument, unfortunately, for the
-general $(\mathbb{B}, \tau)$-circuit, establishing an exactly analogous
-condition is a non-trivial problem. We discuss this problem in more detail in
-Section \label{sec:transparency-and-unique-extensions}.
+% It turns out that establishing an exactly analogous argument for general
+% circuits is a non-trivial problem.
+
+% In this paper we establish an approximately analogous argument
+
+Anderson and Dawar's argument makes use of the fact that many important circuit
+properties are polynomial-time decidable for circuits defined over a symmetric
+bases. We show in Section~\label{sec:transparency-and-unique-extension} that for
+circuits that include gates computing non-symmetric functions most of these
+properties are at least as hard to decide as the graph-isomorphism problem. As
+such, constructing an analogous translation, as well as establishing the many
+other results that rely on certain properties being polynomial-time decidable,
+would be highly non-trivial.
+
+In order to deal with this problem we limit the ways in which gates computing
+non-symmetric functions can be wired into the circuit and we show in
+Section~\label{sec:transparency-and-unique-extensions} that this limitation is
+sufficient for our purposes.
+
+% ourselves to circuits in which those gates that compute non-symmetric
+% functions
+
+% While we should like to establish an analogous polynomial-time computable
+% translation from a general circuit to a equivalent circuit with unique
+% extensions, it turns out that the inclusion of gates that compute
+% non-symmetric functions greatly complicates the analysis of the circuit. We
+% show in Section~\label{sec:transparency-and-unique-extensions} that most of
+% the polynomial-time decidable properties used by Anderson and Dawar in order
+% to define this translation are at least as hard to decide for general circuits
+% as the graph-isomorphism problem.
+
+% Since the proof of our main result requires that many circuit properties are
+% polynomial-time decidable, we introduce restrictions on how gates computing
+% non-symmetric functions can be wired into the circuit.
+
+% The inclusion of gates that inclusion greatly complicates the analysis of a
+% general circuit, resulting in many circuit polynomial-time decidable circuit
+% properties
+
+% It turns out that allowing non-symmetric functions greatly complicates the the
+% structure of a circuit, and makes certain many circuit properties difficult to
+% decide (in a technical sense).
+
+% inclusion of non-symmetric functions in the basis makes deciding certain
+% circuits properties non-trivial,
+
+% determining certain properties
+
+% in the basis greatly complicates the argument, unfortunately, for the general
+% $(\mathbb{B}, \rho)$-circuit, establishing an exactly analogous condition is a
+% non-trivial problem. We discuss this problem in more detail in
+% Section \label{sec:transparency-and-unique-extensions}
+.
 
 We now introduce the notion of a circuit with \emph{unique labels}, and show
-that if a circuit has unique labels then it has has unique extensions. Before we
-do so, we define the \emph{syntactic equivalence} relation on the gates of a
+that if a circuit has unique labels then it has unique extensions. Before we do
+so, we define the \emph{syntactic equivalence} relation on the gates of a
 circuit.
@@
 \begin{definition}
-  Let $\tau$ be a many-sorted vocabulary and $D$ be a $\tau$-sorted set. Let X
-  be a set and $\sim$ be an equivalence relation defined on $X$. Let $Y, Z
-  \subset X$. We say two functions $f : \ind(\tau,D) \rightarrow X$ and $g :
-  \ind(\tau, D) \rightarrow Y$ are \emph{isomorphism-equivalent up to $\sim$} if
-  $Y/{\sim} = X/{\sim}$ and $f/{\sim}$ is isomorphism-equivalent to $g/{\sim}$.
+  Let $\tau$ be a many-sorted vocabulary and $D$ and $D'$ be $\tau$-sorted sets.
+  Let $X$ be a set and $\sim$ be an equivalence relation defined on $X$. Let $Y,
+  Z \subset X$. We say two functions $f : \ind(\tau,D) \rightarrow X$ and $g :
+  \ind(\tau, D') \rightarrow Y$ are \emph{isomorphism-equivalent up to $\sim$}
+  if there exists an isomorphism $\pi : \str{\tau, D} \rightarrow \str{\tau,
+    D'}$ such that $f (\vec{x}_R) \sim g (\pi \vec{x}_R)$ for all $\vec{x}_R \in
+  \ind(\tau, D)$ .
 \end{definition}
 
+% \begin{definition}
+%   Let $C := \langle G, W, \Omega, \Sigma, \Lambda, L \rangle$ be a
+%   $(\mathbb{B}, \rho)$-circuit of order $n$. We recursively define the
+%   equivalence relation \emph{syntactic equivalence}, which we denote using the
+%   symbol `$\equiv$', on $G$ as follows. We say $g \equiv h$ if (i) $\Sigma(g)
+%   = \Sigma(h)$, (ii) if $g$ and $h$ are constant gates then they are equal,
+%   (iii) if $g$ and $h$ are relational gates then $\Lambda(g) = \Lambda(h)$,
+%   (iv) if $g$ and $h$ are internal gates then the functions $L(g)$ and $L(h)$
+%   are isomorphism-equivalent up to syntactic equivalence, and (v) if $g$ and
+%   $h$ are output gates then $\Omega^{-1}(g) = \Omega^{-1}(h)$.
+% \end{definition}
+
 \begin{definition}
-  Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit such that $C_n = \langle G, W,
-  \Omega, \Sigma, \Lambda, L\rangle$. We recursively define the equivalence
-  relation \emph{syntactic equivalence}, which we denote using the symbol
-  `$\equiv$', on $G$ as follows. We say $g \equiv h$ if (i) $\Sigma(g) =
-  \Sigma(h)$, (ii) if $g$ and $h$ are constant gates then they are equal, (iii)
-  if $g$ and $h$ are relational gates then $\Lambda(g) = \Lambda(h)$, (iv) if
-  $g$ and $h$ are internal gates then the functions $L(g)$ and $L(h)$ are
-  isomorphism-equivalent up to syntactic equivalence, and (v) if $g$ and $h$ are
-  output gates then $\Omega^{-1}(g) = \Omega^{-1}(h)$.
+  Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
+  \rho)$-circuit of order $n$. We recursively define the equivalence relation
+  \emph{syntactic-equivalence}, which we denote using the symbol `$\equiv$', on
+  $G$ as follows. Suppose $g$ and $h$ are gates in $C$ such that $\Sigma (g) =
+  \Sigma(h)$ and either both $g$ and $h$ are output gates and $\Omega^{-1}(g) =
+  \Omega^{-1}(h)$ or neither are output gates. Suppose $g$ and $h$ are input
+  gates, then $g \equiv h$ if, and only if, both $g$ and $h$ are constant gates
+  or both are relational gates and $\Lambda(g) = \Lambda (h)$. Suppose $g$ and
+  $h$ are internal gates and and suppose we have defined the
+  syntactic-equivalence relation for all gates of height less than the height of
+  either $g$ or $h$. Then $g \equiv h$ if, and only if, $L(g)$ and $L(h)$ are
+  isomorphism equivalent up to $\equiv$.
 \end{definition}
 
-It is easy to show that determining if two gates in a given circuit compute the
-same function is $NP$-complete. The syntactic-equivalence relation defines a
-weaker relation between gates, instead identifying gates that have `hereditary
-similar' circuits defining them. It is easy to show that, for a circuit $C_n$,
-if $\sigma \in \sym_n$ and $\pi, \pi' \in \aut(C_n)$ extend $\sigma$, then for
-every gate $g$ in $C_n$, $\pi (g)$ and $\pi'(g)$ are syntactically equivalent.
-
-We now introduce the \emph{unique labels} condition.
-
-\begin{definition}
-  Let $C_n$ be a circuit and $g$ be a gate in $C_n$. We say $g$ has
-  \emph{injective labels} if $L(g)$ is an injection. We say $g$ has \emph{unique
-    labels} if $L(g)$ has injective labels and no two gates in $\range(L(g))$
-  are syntactically equivalent. We say $C_n$ has \emph{injective labels} (resp.
-  \emph{unique labels}) if every gate in $C_n$ has injective labels (resp.
-  unique labels). We say $C_n$ is \emph{transparent} if every non-symmetric gate
-  in $C_n$ has unique labels.
-\end{definition}
-
-Let $C_n$ be a circuit and $W_t$ be the transitive closure of the $W$ relation
-on $C_n$. We note that a circuit $C_n$ may have an internal gate $g$ such that
-for every output gate $g'$, $\neg W_t(g, g')$ (i.e. there is no path from $g$ to
-any output gate). We call such a gate \emph{redundant}, as their inclusion in
-the circuit can not possibly have any bearing on the function computed by the
-circuit. It can be shown that given a circuit $C_n$ with redundant gates we may
-construct a new circuit $C_n'$ by simply removing the redundant gates. Moreover,
-this process preserves important circuit properties and can be done efficiently.
-We state and prove this formally in Lemma \ref{lem:redudant-gates}.
-
-% \begin{definition}
-%   Let $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a circuit
-%   computing a $q$-ary query. We say a gate $g \in G$ is \emph{redundant} if
-%   there is no $\vec{a} \in [n]^q$ such that $W_t(g, \Omega (\vec{a}))$.
-% \end{definition}
-
-% We note that the definition of a circuit allows for the inclusion of gates
-% that are never used when evaluating the circuit. That is, for a circuit $C_n$
-% let $W_t$ be the transitive closure of $W$. It may be the case that there
-% exists a gate $h$ in $C_n$ such that there is no output gate $g$ with $W_t(h,
-% g)$.
+\begin{remark}
+  Should I prove these are actually equivalence relations? I use that fact, but
+  it's very easy to prove.
+\end{remark}
+
+We could define an equivalence relation on gates that identifies a pair of gates
+if, and only if, they compute the same function in the circuit. However, it is
+not hard to show that deciding this equivalence relation is $\NP$-hard. The
+syntactic-equivalence relation instead identifies gates that have `hereditary
+similar' circuits underneath them. Since it can be shown that two
+syntactically-equivalent gates must compute the same function in the circuit, it
+follows that the syntactic-equivalence relation refines the above-referenced
+equivalence relation.
+
+We may also define an equivalence relation between gates identifying a pair of
+gates $(h, h')$ in a circuit $C$ of order $n$ if, and only if, there exists
+$\sigma \in \sym_n$, $\pi, \pi' \in \aut(C)$ both extending $\sigma$, and $g$ a
+gate in $C$, such that $h = \pi (g)$ and $h' = \pi' (g)$. We now show this
+relation is a refinement of syntactic-equivalence.
+
+\begin{remark}
+  It's interesting to note that if $C$ has unique extensions then this relation
+  collapses to equality, syntactic-equivalence does not. Note to self: should I
+  mention this? Also, the following result is equivalent to checking for just
+  $\pi $
+\end{remark}
 
 \begin{lem}
-  There exists an algorithm that takes as input a $(\mathbb{B}, \tau)$-circuit
-  $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ computing a $q$-ary
-  query and outputs a $(\mathbb{B}, \tau)$-circuit $C_n'$ such that (i) every
-  gate in $C_n$ is in $C_n'$, (ii) $C_n$ and $C_n'$ compute the same query,
-  (iii) no gate in $C_n'$ is redundant, (iv) if $C_n$ is symmetric then $C_n'$
-  is symmetric, (v) if $C_n$ has unique labels then $C_n'$ has unique labels,
-  and (vi) if $C_n$ is transparent then $C_n'$ is transparent. This algorithm
-  runs in time polynomial in the size of the input circuit.
-  \label{lem:redudant-gates}
+  Let $C$ be a circuit of order $n$, $\sigma \in \sym_n$ and $\pi, \pi' \in
+  \aut(C)$ both extend $\sigma$, then for every gate $g$ in the circuit we have
+  that $\pi (g)$ and $\pi'(g)$ are syntactically-equivalent.
+  \label{lem:permutation-extending-syntactic-equivalence}
 \end{lem}
 \begin{proof}
-  We construct the sub-circuit $C_n'$ of $C_n$ by removing all redundant gates
-  in $C_n$. Since $W_t$, the transitive closure of $W$, can be computed in time
-  polynomial in the size of the circuit, this construction can be completed in
-  time polynomial in the size of $C_n$.
-
-  Conditions (i), (ii), (iii), (v) and (vi) follow obviously for $C_n'$. Suppose
-  $C_n$ is symmetric and let $\sigma \in \sym_n$. Let $\pi$ be an automorphism
-  of $C_n$ extending $\sigma$. Let $g$ be a gate in $C_n'$. Then there exists
-  $\vec{a} \in [n]^q$ such that $W_t(g, \Omega(\vec{a}))$ in $C_n$. It can be
-  shown that $W_t (\pi(g), \Omega(\sigma(\vec{a})))$. Thus $\pi (g)$ is in
-  $C_n'$, and so restricting $\pi$ to the gates of $C_n'$ is an automorphism of
-  $C_n'$ extending $\sigma$. It follows that $C_n'$ is symmetric.
+  We first note that, from the definition of an automorphism, for any gate $g$
+  in $C$, $\Sigma (g) = \Sigma (\pi (g)) = \Sigma (\pi' (g))$, and either all of
+  $g$, $\pi (g)$ and $\pi (g')$ are output gates and $\pi \Omega
+  (\Omega^{-1}(g)) = \Omega (\sigma \Omega^{-1}(g)) = \pi' \Omega
+  (\Omega^{-1})$, or none of $g$, $\pi(g)$ or $\pi' (g)$ are output gates.
+
+  We now prove the result by induction on height. Suppose $g$ is a gate of
+  height $0$. Then $g$ is either a relational or constant gate. In either case
+  $\pi (g) = \pi' (g)$, and so $\pi(g)$ and $\pi'(g)$ are
+  syntactically-equivalent.
+
+  Suppose $g$ is an internal gate and suppose that for every gate $h$ of height
+  less than $g$, $\pi (h)$ is syntactically-equivalent to $\pi'(h)$. We have
+  that there exists $\lambda, \lambda' \in \aut(g)$ such that $\pi
+  L(g)(\vec{a}_R) = L(\pi g) (\lambda \vec{a}_R)$ and $\pi' L(g)(\vec{a}_R) =
+  L(\pi' g)(\lambda' \vec{a}_R)$, for all $\vec{a}_R \in ind(g)$. Then, from the
+  inductive hypothesis, we have that $\pi L(g)(\vec{a}_R) \equiv \pi
+  'L(g)(\vec{a}_R)$ and so $L(\pi g)(\lambda \vec{a}_R) \equiv L(\pi' g)
+  (\lambda' \vec{a}_R)$, for all $\vec{a}_R \in \ind(g)$. Thus we have that
+  $L(\pi g) (\vec{a}_R) = L (\pi g) (\lambda \lambda^{-1}\vec{a}_R) \equiv
+  L(\pi' g) (\lambda' \lambda^{-1}\vec{a}_R)$, for all $\vec{a}_R \in \ind(g)$,
+  and so $L(\pi g)$ is isomorphism equivalent to $L(\pi'g)$ up to
+  syntactic-equivalence. We thus have that $\pi (g) $ and $\pi' (g)$ are
+  syntactically-equivalent, and the result follows.
+
+  % We prove the result by induction on height. Let $g$ be a gate of height $0$.
+  % Then $g$ is either a relational or constant gate. In either case $\pi (g) =
+  % \pi (g')$, and so $\pi(g)$ and $g$ are syntactically-equivalent.
+  % Let $g$ be a
+  % gate of height $0$ and suppose we have that for every gate $h$ of height
+  % less
+  % than $g$, $\pi (h)$ is syntactically-equivalent to $h$. We have that there
+  % exists $\sigma \in \aut(g)$ such that $\pi L(g)(\vec{a}_R) = L(\pi (g))
+  % (\sigma \vec{a}_R)$, for all $\vec{a}_R \in ind(g)$. But from the inductive
+  % hypothesis we have for all $\vec{a}_R \in \ind(g)$ that $\pi L(g)(\vec{a}_R)
+  % \equiv L(g)(\vec{a}_R)$ and so $L(g)(\vec{a}_R) \equiv L(\pi (g)) (\sigma
+  % \vec{a}_R)$. The definition of an automorphism ensures that the other
+  % conditions sufficient for syntactic-equivalence hold, and the result
+  % follows.
 \end{proof}
 
-Given Lemma \ref{lem:redudant-gates}, we may assume, without a loss of
-generality, that a circuit has no redundant gates. In this paper we make this
-assumption of every circuit unless stated otherwise.
-
-We now show that unique labels are sufficient for unique extensions.
+It is easy to show that, for a circuit $C$ of order $n$, if $\sigma \in \sym_n$
+and both $\pi, \pi' \in \aut(C)$ extend $\sigma$, then for every gate $g$ in
+$C$, $\pi (g)$ and $\pi'(g)$ are syntactically-equivalent.
+
+We now introduce the \emph{unique labels} and \emph{transparency} conditions on
+circuits.
+
+\begin{definition}
+  Let $C$ be a circuit and $g$ be a gate in $C$. We say $g$ has \emph{injective
+    labels} if $L(g)$ is an injection. We say $g$ has \emph{unique labels} if
+  $g$ has injective labels and no two gates in $\img(L(g))$ are
+  syntactically-equivalent. We say $C$ has \emph{injective labels} (resp.
+  \emph{unique labels}) if every gate in $C$ has injective labels (resp. unique
+  labels). We say $C$ is \emph{transparent} if every gate $g$ in $C$ such that
+  $\Sigma(g)$ is not a symmetric function has unique labels.
+\end{definition}
+
+There is a small technical point that needs some discussion before we continue.
+The definition of a circuit allows for the inclusion of gates whose outputs need
+not lead to any output gate. In other words, we can be sure, not matter the rest
+of the circuit, that these gates cannot have any effect the function computed by
+the circuit. We say these gates are \emph{redundant}.
+
+\begin{definition}
+  Let $C$ be a circuit and $W_t$ be the transitive closure of the $W$ relation
+  on the gates of $C$. We say that an internal gate $g$ in $C$ is
+  \emph{redundant} if for all output gates $g'$ in $C$, we have $\neg W_t (g,
+  g')$.
+\end{definition}
+
+It is easy to see that we can simply remove the redundant gates from a circuit,
+and so construct from a given circuit an equivalent circuit without redundant
+gates. Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a circuit of
+order $n$ and let $g$ be a redundant circuit in $C$. It is easy to see that $g$
+is not the child of a non-redundant gate, nor is it a relational or output gate.
+Thus we can define $C' := \langle G', \Omega, \restr{\Sigma}{G'}, \Lambda,
+\restr{L}{G'} \rangle$, where $G' \subseteq G$ is the set of all non-redundant
+gates in $C$.
+
+It is easy to see that $C'$ computes the same query as $C$, and that each $g \in
+G'$ has unique labels in $C$ if, and only if, $g$ has unique labels in $C'$.
+Moreover, it can be shown that if $C$ is symmetric and $g'$ is in the orbit of
+$g$ in $C$ then $g' \in G'$. As such, if $C$ is symmetric then so is $C'$. We
+thus have the following Lemma.
+
+\begin{lem}
+  Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a circuit of order
+  $n$. Let $G'$ be the set of non-redundant gates in $C$. Let $C' := \langle G',
+  \Omega, \restr{\Sigma}{G'}, \Lambda, \restr{L}{G'} \rangle$. Then (i) $C$ and
+  $C'$ compute the same query, (ii) no gate in $C'$ is redundant, (iii) if $C$
+  is symmetric then $C'$ is symmetric, (iv) if $C$ has unique labels then $C'$
+  has unique labels, and (v) if $C$ is transparent then $C'$ is transparent
+\end{lem}
+
+We note that the construction of $C'$ from $C$ in Lemma~\ref{lem:redudant-gates}
+can be implemented so as to run in time polynomial in the size of $C$. As such,
+for the remainder of this paper we assume every circuit has no redundant gates.
+With this assumption stated we now show that every circuit with unique labels
+has unique extensions.
+
+% \begin{lem}
+%   Let $C$ be a circuit and suppose there is an automorphism $\pi \in \aut(C)$
+%   extending the trivial permutation. Then for every gate $g$ in $C$ we have
+%   that $g$ is syntactically-equivalent to $\pi (g)$.
+%   \label{lem:trivial-permutation-syntactic-equivalence}
+% \end{lem}
+% \begin{proof}
+%   We prove the result by induction on height. Let $g$ be a gate of height $0$.
+%   Then $\pi(g) = g$, and so $\pi(g)$ and $g$ are syntactically-equivalent. Let
+%   $g$ be a gate of height $0$ and suppose we have that for every gate $h$ of
+%   height less than $g$, $\pi (h)$ is syntactically-equivalent to $h$. We have
+%   that there exists $\sigma \in \aut(g)$ such that $\pi L(g)(\vec{a}_R) =
+%   L(\pi (g)) (\sigma \vec{a}_R)$, for all $\vec{a}_R \in ind(g)$. But from the
+%   inductive hypothesis we have for all $\vec{a}_R \in \ind(g)$ that $\pi
+%   L(g)(\vec{a}_R) \equiv L(g)(\vec{a}_R)$ and so $L(g)(\vec{a}_R) \equiv L(\pi
+%   (g)) (\sigma \vec{a}_R)$. The definition of an automorphism ensures that the
+%   other conditions sufficient for syntactic-equivalence hold, and the result
+%   follows.
+% \end{proof}
 
 \begin{prop}
-  Let $C_n := \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a $\mathbb{B},
-  \tau)$-circuit. If $C_n$ has unique labels then $C_n$ has unique extensions.
+  Let $C := \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a $(\mathbb{B},
+  \rho)$-circuit of order $n$. If $C$ has unique labels then $C$ has unique
+  extensions.
   \label{prop:unique-labels-unique-extensions}
@@
 \begin{proof}
-  Suppose $C_n$ has unique labels. Let $\pi_{\sigma}, \pi_{\sigma}' \in
-  \aut(C_n)$ be automorphisms extending $\sigma \in \sym_n$. We now prove that
-  $\pi_\sigma = \pi_{\sigma}'$. It is sufficient to show that $\pi :=
-  \pi_{\sigma}'\pi^{-1}_\sigma$ is the trivial automorphism on the circuit. It
-  is easy to see that $\pi$ extends the trivial permutation $e \in \sym_n$. Thus
-  $\pi$ acts trivially on input gates and output gates in the circuit, as $\pi$
-  acts as $e$ on relational gates and for any output gate $g$ there exists
-  $\vec{a} \in [n]^q$ such that $\pi (g) = \pi (\Omega(\vec{a})) = \Omega(e \dot
-  \vec{a}) = \Omega(\vec{a}) = g$.
-
-  It can be shown by induction that, since $\pi$ extends the trivial
-  permutation, for all gates $g \in G$, $\pi(g)$ is syntactically equivalent to
-  $g$. Let $W_t$ be the transitive closure of the relation $W$ on $C_n$. Let $g
-  \in G$ and suppose $\pi (g) = g$. Then $\pi H_{g} = H_g$ and, since $g$ has
-  unique labels, it follows that $\pi$ acts trivially on $H_g$ (i.e. for all $h
-  \in H_{g}$, $\pi(h) = h$). It follows by induction that for all $h \in G$ if
-  $W_t(h, g)$ then $\pi (h) = h$. Since the circuit contains no redundant gates,
-  it follows that $G = \bigcup_{\vec{a} \in [n]^q} \{g \in G : W_t (g,
-  \Omega(\vec{a}))\}$. Thus, since $\pi$ acts trivially on output gates, we have
-  that for all $g \in G$, $\pi (g) = g$. The result follows.
-
-  % Suppose $C_n$ does have not have unique labels. For every such gate $g \in
-  % G$ let $D(g)$ be the distance from $g$ to the set of output gates. From the
-  % hypothesis there exists $g \in G$ such that $h, h' \in H_g$ and $h \equiv
-  % h'$. Let $g$ the gate in the circuit without unique labels and with minimal
-  % $D(g)$. Then
-
-  % to the set of output gates Order the set of all such gates by their distance
-  % to the set of output gates, and let $g$ be the minimal gate in this set.
-
-  % such that it is of minimal distance to the set of output gates. Let $e \in
-  % \sym_n$ be the trivial permutation and $\pi \in \aut(C_n)$ be the unique
-  % extension of $e$. We have that $\pi (g) = g$, as if $\pi (g) \neq g$
+  Suppose $C$ has unique labels. Let $\pi_{\sigma}, \pi_{\sigma}' \in \aut(C_n)$
+  be automorphisms extending $\sigma \in \sym_n$. We now prove that $\pi_\sigma
+  = \pi_{\sigma}'$. Let $\pi := \pi_{\sigma}'\pi^{-1}_\sigma$. We have that
+  $\pi$ is an automorphism of the circuit and that $\pi$ extends
+  $\sigma^{-1}\sigma = e$, the identity permutation. It follows that $\pi$ fixes
+  all input gates and, since for any output gate $g$, $\pi (g) = \pi
+  (\Omega(\vec{a})) = \Omega(e \vec{a}) = \Omega(\vec{a}) = g$ for all $\vec{a}
+  \in [n]^q$, $\pi$ fixes all output gates.
+
+  We now prove the result by structural induction on the circuit starting from
+  the output gates. Let $g$ be an output gate then $\pi (g) = g$ from the above
+  argument. Let $g$ be an internal, non-output gate. We now show that if $\pi
+  (g) = g$ then for all $h \in H_g$ we have $\pi (h) = h$. Suppose $\pi (g) = g$
+  and let $h \in H_g$. Since $\pi (g) = g$ we have that $\pi H_{g} = H_g$, and
+  so $\pi (h) \in H_g$. We have from
+  Lemma~\ref{lem:permutation-extending-syntactic-equivalence} that $h$ is
+  syntactically-equivalent to $\pi (h)$ and, since $g$ has unique labels, $h$ is
+  the only gate in $H_g$ syntactically-equivalent to $h$. It follows that $\pi
+  (h) = h$.
+
+  Let $W_t$ be the transitive closure of the relation $W$ on $C$. The inductive
+  argument gives us that for all $h \in G$ if there exists an output gate $g$
+  such that $W_t(h, g)$, then $\pi (h) = h$. Since the circuit contains no
+  redundant gates, we have that $G = \bigcup_{\vec{a} \in [n]^q} \{g \in G : W_t
+  (g, \Omega(\vec{a}))\}$, and the result follows.
 \end{proof}
@@
 
-Let the \emph{\rank basis} $\RB := \BM \cup \{\rank^{r}_p[a,b] : a, b, r, p \in
+Let the \emph{rank basis} $\RB := \BM \cup \{\rank^{r}_p[a,b] : a, b, r, p \in
 \nats, \text{ $p$ prime}\}$. We say a basis $\BB$ is \emph{matrix-symmetric} if
@@
 Let $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
-\tau)$-circuit and let $g \in G$. We say a gate $g \in G$ is a \emph{symmetric
+\rho)$-circuit and let $g \in G$. We say a gate $g \in G$ is a \emph{symmetric
   gate} if $\Sigma(g)$ is a symmetric function. We say a gate $g \in G$ is a

### 2018-01-30 sections/transparency-and-unique-extensions.tex
30 Jan

@@
 requirement is needed to apply the support theorem, and the unique extensions
-property is necessary for applying (and even defining) a great many technical tools (e.g. supports
-and supporting partitions) used extensively throughout this paper.
+property is necessary for applying (and even defining) a great many technical
+tools (e.g. supports and supporting partitions) used extensively throughout this
+paper.
 
@@
 
+  % Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a transparent
+  % $(\mathbb{B}, \rho)$-circuit of order $n$. We define a relation $\sim$ by
+  % induction on height (i.e. distance from an input gate). This relation will be
+  % the syntactic-equivalence relation on $G$. It is easy to check the conditions
+  % for syntactic-equivalence for gates of height 0 as all such gates are input
+  % gates and so are either constant gates or relational gates. Suppose $g$ and
+  % $h$ are gates of height greater than zero. We only need to check conditions
+  % (i), (iv) and (v) of syntactic-equivalence. It is easy to check (i) and (v).
+  % If either condition is false then $g$ and $h$ are not syntacticly equivalent.
+  % So suppose $g$ and $h$ are two internal gates such that $\Sigma (g) =
+  % \Sigma(h)$ and suppose that if they are both output gates then $\Omega^{-1}(g)
+  % = \Omega^{-1}(h)$. It remains to check if $L(g)/{\sim}$ and $L(h)/{\sim}$ are
+  % isomorphism equivalent. First check if $H_h /{\sim} = H_g /{\sim}$. If not,
+  % $g$ and $h$ are not syntactically equivalent. So suppose $H_h /{\sim} = H_g
+  % /{\sim}$. If $g$ and $h$ are symmetric gates then $H_h /{\sim} = H_g/{\sim}$
+  % if, and only if, $L(g)/{\sim}$ and $L(h)/{\sim}$ are isomorphism equivalent,
+  % so let $g \sim h$. If $g$ and $h$ are not symmetric gates then, since $C$ is
+  % transparent, $g$ and $h$ have unique labels. We thus have that $L(g)/{\sim}$
+  % and $L(h)/{\sim}$ are isomorphism equivalent if, and only if, $L(g)^{-1}L(h)$
+  % acts like an isomorphism. This can be checked by first checking that the
+  % function induces a sorted permutation on the universe of $g$ (which can be
+  % checked efficiently). This is sufficient as $L(g)(L(g)^{-1}L(h)) = L(h)$.
+
+  % It is easy to see that, given a reasonable binary encoding of a circuit, the
+  % above procedure can be implemented so as to run in polynomial time, and that
+  % the relation $\sim$ is the syntactic-equivalence relation on the gates of $C$.
+
 \end{proof}
@@
 transform arbitrary circuits into transparent circuits in polynomial-time, we do
-show that the class of transparent circuits is polynomial-time decidable. In contrast, we show
-that deciding the class of circuits with unique extensions is at least as hard
-as the graph-isomorphism problem.
+show that the class of transparent circuits is polynomial-time decidable. In
+contrast, we show that deciding the class of circuits with unique extensions is
+at least as hard as the graph-isomorphism problem.
 
@@
 relation to the problem of deciding if a given gate in a circuit has unique
-labels. From then transitivity of polynomial-time many-one reductions, this gives
-us a reduction from the graph-isomorphism problem to the problem of deciding if
-a gate has unique labels.
+labels. From then transitivity of polynomial-time many-one reductions, this
+gives us a reduction from the graph-isomorphism problem to the problem of
+deciding if a gate has unique labels.
 
@@
   removing every gate $g \in G \setminus\{g_1, g_2\}$ such that $\neg W_t(g,
-  g_1) \land \neg W_t(g, g_2)$ (i.e. all those gates in the circuit such that
-  there is no path from them to either $g_1$ or $g_2$). Here $W_t$ is the
-  relation defined in the proof of Lemma~\ref{}. Let $C'$ be the circuit formed
-  from $D$ by adding in a single two-input $\AND$ gate $g'$ and connecting the
-  outputs of $g_1$ and $g_2$ to the inputs of $g'$. Moreover, we let this $g'$
-  be the single output gate of $C'$.
-
-  It follows that $g_1$ and $g_2$ are syntactically equivalent in $C$ if, and
+  g_1) \land \neg W_t(g, g_2)$, where $W_t$ is the transitive closure of the $W$
+  relation (i.e. we move all those gates in the circuit such that there is no
+  path from the gate to either $g_1$ or $g_2$). Let $C'$ be the circuit formed from $D$ by adding in a
+  single two-input $\AND$ gate $g'$ and connecting the outputs of $g_1$ and
+  $g_2$ to the inputs of $g'$. Moreover, we let this $g'$ be the single output
+  gate of $C'$.
+
+  It follows that $g_1$ and $g_2$ are syntactically-equivalent in $C$ if, and
   only if, $g'$ has unique labels in $C'$. Since the construction of $C'$ from
@@
   given pair of gates gates in a given $(\mathbb{B}, \rho)$-circuit are
-  syntactically-equivalent to the problem of determining if for a given triple
+  syntactically-equivalent to the problem of determining if for a given pair
   $(C, g)$, where $C$ is a circuit of order $n$, $g$ is a gate in $C$, that
@@
   Lemma~\ref{lem:syntactically-equivalent-unique-labels}. We now prove that the
-  mapping $(C, (g_1, g_2))$ to $(C', g_1)$ is a reduction. Let $\pi_e$ be a
-  function from the gates of $C'$ to the gates of $C'$ that swaps $g_1$ and
+  mapping $(C, g_1, g_2)$ to $(C', g_1)$ is a reduction. Let $\pi_e$ be
+  bijection from the gates of $C'$ to the gates of $C'$ that swaps $g_1$ and
   $g_2$ and fixes all other gates. It follows that if $g_1$ and $g_2$ are

### 2018-02-05 sections/symmetric-circuits.tex
February 5 2018

@@
 % AD - rewrote the paragraph to reduce the use of subscripts and superscripts.
-Let $\tau := (R, S, \nu)$ be a many-sorted vocabulary. Let $D := \biguplus_{s \in
-  S} D_{s} = \{(s,d) : d \in D_s\}$, be a disjoint union of non-empty sets,
+Let $\tau := (R, S, \nu)$ be a many-sorted vocabulary. Let $D := \biguplus_{s
+  \in S} D_{s} = \{(s,d) : d \in D_s\}$, be a disjoint union of non-empty sets,
 indexed by $S$. For $R_i \in R$ let $R^D_i$ denote the trivial relation over the
@@
 D_{a_{r}}$, where $\nu(R_i) = (a_1, \ldots , a_{r)})$. There is an obvious
-interpretation of $\tau$ over $D$ given by assigning each sort symbol in $\tau$
-in the obvious manner and each relation symbol in $\tau$ to the trivial relation
-over $D$. We call this \emph{the structure defined by $(\tau, D)$}, and denote
-it by $\str{\tau, D}$.
+interpretation of $\tau$ over $D$ given by assigning each sort symbol $s$ in
+$\tau$ to the set $D_s$ and each relation symbol in $\tau$ to the trivial
+relation over $D$. We call this \emph{the structure defined by $(\tau, D)$}, and
+denote it by $\str{\tau, D}$.
 
@@
 
-We abbreviate $(\vec{a}, R) \in \ind(\tau, D)$ by $\vec{a}_R$, and refer
-to $R$ as \emph{the type} of $\vec{a}_R$. We often abuse notation and treat
-$\vec{a}_R$ as the tuple $\vec{a}$ in $R^D$. In the event that there is only one
-relational symbol in $\tau$ we identify $\vec{a}_R$ with $\vec{a}$.
+We abbreviate $(\vec{a}, R) \in \ind(\tau, D)$ by $\vec{a}_R$, and refer to $R$
+as the \emph{tag} of $\vec{a}_R$. We often abuse notation and treat $\vec{a}_R$
+as the tuple $\vec{a}$ in $R^D$. In the event that there is only one relational
+symbol in $\tau$ we identify $\vec{a}_R$ with $\vec{a}$.
 
@@
 For the remainder of this subsection we fix a vocabulary $\tau$ and a
-many-sorted set $D := \biguplus_{s \in S} D_{s}$, let $X := \ind (\tau, D)$ and $G \leq \sym_{X}$.
-There is an obvious action of $G$ on $X$. There is also an action of the
-automorphism group $\str{\tau, D}$ on $X$ defined for the automorphism $\sigma$
-by $\sigma \cdot \vec{a}_R := (\sigma \vec{a})_R$. We denote the group of
-automorphisms of $\str{\tau, D}$ by $\aut(\tau, D)$, and identify it with the
-subgroup of $\sym_X$ that acts equivalently on $X$.
-
-We can extend the action of $G$ on $X$ to an action on the set of functions of
-the form $f: X \rightarrow H$, for any set $H$, defined by $\sigma \cdot f(x) :=
-f(\sigma \cdot x)$ for all $x \in X$, $\sigma \in G$.
+many-sorted set $D := \biguplus_{s \in S} D_{s}$. Let $X := \ind (\tau, D)$ and
+$G \leq \sym_{X}$. We note that $G$ there is an obvious group action of $G$ on
+$X$. Let $\aut (\tau, D)$ be the automorphism group of $\str{\tau, D}$. We
+define a group action of $\aut (\tau, D)$ on $X$ for $\sigma \in \aut(\tau, D)$
+by $\sigma \cdot \vec{a}_R := (\sigma \vec{a})_R$, for all $\vec{a}_R \in X$. We
+identify $\aut(\tau, D)$ with the subgroup of $\sym_X$ that acts equivalently on
+$X$.
+
+We can extend the action of $G$ on $X$ to a right group action on the set of
+functions of the form $f: X \rightarrow H$, for any set $H$, defined by $(f \cdot
+\sigma)(x) := f(\sigma x)$ for all $x \in X$, $\sigma \in G$.
 
@@
 D') \rightarrow H$ are \emph{isomorphism-equivalent} if there exists an
-isomorphism $\pi :\str{\tau, D} \rightarrow \str{\tau, D'}$ such that $f (\vec{a}_R) =
-g (\pi \vec{a}_R)$ for all $\vec{a}_R \in \ind(\tau, D)$. It is easy to see that
-isomorphism-equivalence is an equivalence relation.
+isomorphism $\pi :\str{\tau, D} \rightarrow \str{\tau, D'}$ such that
+$f(\vec{a}_R) = g(\pi \vec{a}_R)$ for all $\vec{a}_R \in \ind(\tau, D)$. It is
+easy to see that isomorphism-equivalence is an equivalence relation.
 
@@
 We say that $f, g: X \rightarrow H$ are \emph{$G$-equivalent} if there exists
-$\sigma \in G$ such that $f = \sigma \cdot g$. We note that in this case $f$ and
-$g$ are isomorphism-equivalent if, and only if, they are $\aut(\tau,
-D)$-equivalent.
-
-In this paper we will often take the co-domain $H$ to be $\{0,1\}$, and so $f :
-X \rightarrow \{0,1\}$. In this case we may think of $f$ as defining for each
-relation $R^D_i$ a subset of that relation, and so determining a
-$\tau$-structure over the universe $D$. We note that two functions $f, g: X
-\rightarrow \{0,1\}$ are isomorphism-equivalent if, and only if, the two
-$\tau$-structures they determine are isomorphic.
+$\sigma \in G$ such that $f = g \sigma$. We note that in this case $f$ and $g$
+are isomorphism-equivalent if, and only if, they are $\aut(\tau, D)$-equivalent.
+
+In this paper we will often take the co-domain to be $\{0,1\}$, and so have a
+function of the form $f : X \rightarrow \{0,1\}$. In this case we may think of
+$f$ as defining for each relation $R^D_i$ a subset of that relation, and thus
+determining a $\tau$-structure over the universe $D$. We note that two functions
+$f, g: X \rightarrow \{0,1\}$ are isomorphism-equivalent if, and only if, the
+two $\tau$-structures they determine are isomorphic.
 
@@
 symmetry conditions we discussed are naturally reproduced. Suppose $\tau$ is
-single-sorted and consists of a single unary relation symbol. Then any structured
-function $F$ with vocabulary $\tau$ is isomorphism-invariant if, and only if, it
-is symmetric. If instead the vocabulary of $F$ is the graph vocabulary, then $F$
-is isomorphism-invariant if, and only if, $F$ decides a property of directed
-graphs. Lastly, if the vocabulary of $F$ has just two sorts $(s_1, s_2)$ and one
-binary relation with type $(s_1, s_2)$, then $F$ is isomorphism-invariant if,
-and only if, it is matrix-invariant.
+single-sorted and consists of a single unary relation symbol. Then any
+structured function $F$ with vocabulary $\tau$ is isomorphism-invariant if, and
+only if, it is symmetric. If instead the vocabulary of $F$ is the graph
+vocabulary, then $F$ is isomorphism-invariant if, and only if, $F$ decides a
+property of directed graphs. Lastly, if the vocabulary of $F$ has just two sorts
+$(s_1, s_2)$ and one binary relation with type $(s_1, s_2)$, then $F$ is
+isomorphism-invariant if, and only if, it is matrix-invariant.
 
@@
 condition. It is worth mentioning that the graph-invariant case is not strictly
-reproduced using structured functions. This is because structured functions
-index the input string using the elements of the relations of the complete
-$\tau$-structure (in this case, edges in the complete graph). As such, the input
-string is indexed by ordered pairs of elements, rather than two-element
-subsets, and as such the symmetry condition on the relation is not enforced. As
-such, in the structured function case the function decides properties of
-directed graphs, rather than ordinary graphs. We should note, however, that the symmetry
-of the edge relation is a property of directed-graph, and as such can be decided
-by an isomorphism-invariant structured function over the graph vocabulary.
-
-% , and any
-% input sequence encodes a sub-relation of that complete relation. As such, the
-% function  This is because in the event that $\tau := {E}$ (where $E$ is
-% a binary relation, thought of as the edge relation) there is no assurance that
-% the function $f : \ind
-% (\tau, D) \rightarrow \{0,1\}$ is encoding
-
-% as the structured functions are rather defined over directed
-% graphs.
+reproduced using structured functions. This is because in the structured
+function case the input string is indexed by all possible elements of the binary
+relation (i.e. all ordered pairs over the universe). As such, the input string
+of the structured function may encode any structure over the universe with a
+single binary relation, i.e. a directed graph. In contrast, the graph-invariant
+function discussed at the beginning of this subsection indexes the input string
+using two element subsets of the universe, rather pairs of elements, an encoding
+that naturally enforces the symmetry and irreflexivity properties the edge
+relation. We should note, however, that symmetry and irreflexivity are
+properties of directed-graph, and as such can be decided by an
+isomorphism-invariant structured function over the graph vocabulary.
+
+% , and any input sequence encodes a sub-relation of that complete relation. As
+% such, the function This is because in the event that $\tau := {E}$ (where $E$
+% is a binary relation, thought of as the edge relation) there is no assurance
+% that the function $f : \ind (\tau, D) \rightarrow \{0,1\}$ is encoding
+
+% as the structured functions are rather defined over directed graphs.
 
@@
 D_{s_p}$, then for all $s \in \{s_1 , \ldots , s_p\}$ there exists $d_s \in
-\nats{N}$ such that $D_{s} = [d_s]$. We also assume that every $(\tau,
+\nats$ such that $D_{s} = [d_s]$. We also assume that every $(\tau,
 D)$-structured function has the property that every $a \in D$ appears in at
@@
 
-We now define a \emph{$(\mathbb{B}, \rho)$-circuit} . This is a circuit that
+We now define a \emph{$(\mathbb{B}, \rho)$-circuit}. This is a circuit that
 computes a function on structures in the relational vocabulary $\rho$ and where
@@
 \rho)$-circuit of order $n$. The order of a circuit denotes the fact that it
-takes as input structures of size $n$. We often consider families of circuits of
-the form $(C_n)_{n \in \nats}$, and here we assume that each $C_n$ is a circuit
-of order $n$. For a gate $g \in C$, we define the \emph{index} of $g$, denoted
-by $\ind(g)$, as $\ind(\Sigma(g))$. We define the relation $W \subseteq G^2$ by
-$W(h,g)$ if, and only if, $h \in \range(L(g))$. For each $g \in G$ we let
-$W(\cdot, g) := \{h \in G : W(h,g)\}$ and $W(g, \cdot) := \{h \in G : W(g,h)\}$.
-We call the elements of $W(\cdot, g)$ the \emph{children} of $g$ and the
-elements of $W(g, \cdot)$ the \emph{parents} of $g$. We also abbreviate $W(g,
-\cdot)$ by $H_g$.
+takes as input structures of size $n$. If $(C_n)_{n \in \nats}$ is a family of
+circuits we assume that each $C_n$ is a circuit of order $n$.
+
+For a gate $g \in C$, we let the \emph{index} of $g$, denoted by $\ind(g)$, be
+$\ind(\Sigma(g))$. We define the relation $W \subseteq G^2$ by $W(h,g)$ if, and
+only if, $h \in \img(L(g))$. For each $g \in G$ we let $W(\cdot, g) := \{h \in G
+: W(h,g)\}$ and $W(g, \cdot) := \{h \in G : W(g,h)\}$. We call the elements of
+$W(\cdot, g)$ the \emph{children} of $g$ and the elements of $W(g, \cdot)$ the
+\emph{parents} of $g$. We also abbreviate $W(g, \cdot)$ by $H_g$.
 
@@
 $\Sigma(g)$, respectively, and denote the vocabulary of $g$ by $\vocab{g}$ and
-the universe by $\universe{g}$. We also let $\aut(g) := \aut(\vocab{g}, \universe{g})$ and
-$\str{g} := \str{\vocab{g}, \universe{g}}$.
+the universe by $\universe{g}$. We also let $\aut(g) := \aut(\vocab{g},
+\universe{g})$ and $\str{g} := \str{\vocab{g}, \universe{g}}$.
 
@@
   \in R^{\sigma \mathcal{B}}$ if, and only if, $\sigma^{-1} \vec{a} \in
-  R^{\mathcal{B}}$ if, and only if, $\sigma ^{-1} f_{\mathcal{B}}(\vec{a}_R) =
-  f_{\mathcal{B}}(\sigma^{-1} \vec{a}_R)= 1$.
+  R^{\mathcal{B}}$ if, and only if, $(f_{\mathcal{B}} \sigma^{-1})(\vec{a}_R) =
+  f_{\mathcal{B}}(\sigma^{-1} \vec{a}_R)= 1$. It follows $f_{\sigma \mathcal{B}}
+  = f_{\mathcal{B}} \sigma^{-1}$.
 
@@
                                                                                   & \Leftrightarrow F_C(f_{\gamma_1 \mathcal{A}}) = F_C (f_{\sigma^{-1}\gamma_1 \mathcal{A}}) \\
-                                                                                  & \Leftrightarrow F_C(f_{\gamma_1 \mathcal{A}}) = F_C (\sigma f_{\gamma_1 \mathcal{A}}).
+                                                                                  & \Leftrightarrow F_C(f_{\gamma_1 \mathcal{A}}) = F_C ( f_{\gamma_1 \mathcal{A}} \sigma).
   \end{align*}
@@
   let $\sigma \in \sym_n$ be such that $\gamma_1 = \sigma \gamma_2$. Then, from
-  isomorphism-invariance, we have $F_C(f_{\gamma_1 \mathcal{A}}) = F_C (\sigma
-  f_{\gamma_1 \mathcal{A}})$, and so $C[\gamma_1 \mathcal{A}](g_{\text{o}}) =
-  C[\gamma_2 \mathcal{A}](g_{\text{o}})$.
-
-  Suppose $C$ is invariant. Fix the bijection $\gamma_1 \in
-  [n]^{\underline{U}}$. Let $\sigma \in \sym_n$ and $f: \ind(\rho, [n])
-  \rightarrow \{0,1\}$. Let $\mathcal{A} = \gamma^{-1}_1 \mathcal{B}_f$ and
-  $\gamma_2 := \sigma^{-1}\gamma_1 $. Since $C$ is invariant we have $C[\gamma_1
+  isomorphism-invariance, we have $F_C(f_{\gamma_1 \mathcal{A}}) = F_C (
+  f_{\gamma_1 \mathcal{A}}\sigma)$, and so $C[\gamma_1
+  \mathcal{A}](g_{\text{o}}) = C[\gamma_2 \mathcal{A}](g_{\text{o}})$.
+
+  Suppose $C$ is invariant. Fix a bijection $\gamma_1 \in [n]^{\underline{U}}$.
+  Let $\sigma \in \sym_n$ and $f: \ind(\rho, [n]) \rightarrow \{0,1\}$. Let
+  $\mathcal{A} = \gamma^{-1}_1 \mathcal{B}_f$ and $\gamma_2 :=
+  \sigma^{-1}\gamma_1 $. Since $C$ is invariant we have $C[\gamma_1
   \mathcal{A}](g_{\text{o}}) = C[\gamma_2\mathcal{A}](g_{\text{o}})$, and so
-  $F_C (\sigma f_{\gamma_1 \mathcal{A}}) = F_C(f_{\gamma_1 \mathcal{A}})$. But
-  $f_{\gamma_1 \mathcal{A}} = f_{\mathcal{B}_f} = f$, and so $F_C (\sigma f) =
+  $F_C (f_{\gamma_1 \mathcal{A}} \sigma) = F_C(f_{\gamma_1 \mathcal{A}})$. But
+  $f_{\gamma_1 \mathcal{A}} = f_{\mathcal{B}_f} = f$, and so $F_C (f \sigma) =
   F_C (f)$. It follows that $F_C$ is isomorphism-invariant.
@@
 It follows that for any symmetric circuit $C$ of order $n$ there is a
-homomorphism $h$ that maps $\sym_n$ to $\aut(C)$, taking any $\sigma \in \sym_n$
+homomorphism $h$ that maps $\sym_n$ to $\aut(C)$ that takes $\sigma \in \sym_n$
 to an automorphism that extends it. Suppose $C$ contains no relational gates of
@@
 Anderson and Dawar's argument makes use of the fact that many important circuit
-properties are polynomial-time decidable for circuits defined over a symmetric
-bases. We show in Section~\label{sec:transparency-and-unique-extension} that for
-circuits that include gates computing non-symmetric functions most of these
+properties are polynomial-time decidable for circuits defined over symmetric
+bases. While we should like to construct an analogous argument, we show in
+Section~\ref{sec:transparency-and-unique-extension} that for circuits that
+include gates computing non-symmetric functions most of these important circuit
 properties are at least as hard to decide as the graph-isomorphism problem. As
-such, constructing an analogous translation, as well as establishing the many
-other results that rely on certain properties being polynomial-time decidable,
-would be highly non-trivial.
-
-In order to deal with this problem we limit the ways in which gates computing
-non-symmetric functions can be wired into the circuit and we show in
-Section~\label{sec:transparency-and-unique-extensions} that this limitation is
-sufficient for our purposes.
-
-% ourselves to circuits in which those gates that compute non-symmetric
-% functions
-
-% While we should like to establish an analogous polynomial-time computable
-% translation from a general circuit to a equivalent circuit with unique
-% extensions, it turns out that the inclusion of gates that compute
-% non-symmetric functions greatly complicates the analysis of the circuit. We
-% show in Section~\label{sec:transparency-and-unique-extensions} that most of
-% the polynomial-time decidable properties used by Anderson and Dawar in order
-% to define this translation are at least as hard to decide for general circuits
-% as the graph-isomorphism problem.
-
-% Since the proof of our main result requires that many circuit properties are
-% polynomial-time decidable, we introduce restrictions on how gates computing
-% non-symmetric functions can be wired into the circuit.
-
-% The inclusion of gates that inclusion greatly complicates the analysis of a
-% general circuit, resulting in many circuit polynomial-time decidable circuit
-% properties
-
-% It turns out that allowing non-symmetric functions greatly complicates the the
-% structure of a circuit, and makes certain many circuit properties difficult to
-% decide (in a technical sense).
-
-% inclusion of non-symmetric functions in the basis makes deciding certain
-% circuits properties non-trivial,
-
-% determining certain properties
-
-% in the basis greatly complicates the argument, unfortunately, for the general
-% $(\mathbb{B}, \rho)$-circuit, establishing an exactly analogous condition is a
-% non-trivial problem. We discuss this problem in more detail in
-% Section \label{sec:transparency-and-unique-extensions}
-.
-
-We now introduce the notion of a circuit with \emph{unique labels}, and show
-that if a circuit has unique labels then it has unique extensions. Before we do
-so, we define the \emph{syntactic equivalence} relation on the gates of a
-circuit.
+such, constructing an analogous translation, as well as establishing the
+numerous other needed results whose proofs rely on certain properties being
+polynomial-time decidable, would be non-trivial.
+
+In order to proceed we will restrict ourselves to circuits with certain
+constraints on how those gates computing non-symmetric functions can be wired
+into the circuit. We call these circuits \emph{transparent} circuits. We show in
+Sections~\ref{sec:transparency-and-unique-extensions} and~\ref{} that
+transparency is sufficient to allow for the polynomial-time decidability of many
+important circuit properties, while still keeping the circuit model powerful
+enough for us to establish a translation from formulas to families of circuits.
+
+Before we can formally define \emph{transparency} we need to define the
+\emph{syntactic-equivalence} relation on the gates of a circuit. The intuition
+is that two gates in a circuit are syntactically-equivalent if the circuits
+underneath them are `hereditary similar'.
 
@@
 
-We could define an equivalence relation on gates that identifies a pair of gates
-if, and only if, they compute the same function in the circuit. However, it is
-not hard to show that deciding this equivalence relation is $\NP$-hard. The
-syntactic-equivalence relation instead identifies gates that have `hereditary
-similar' circuits underneath them. Since it can be shown that two
-syntactically-equivalent gates must compute the same function in the circuit, it
-follows that the syntactic-equivalence relation refines the above-referenced
-equivalence relation.
-
-We may also define an equivalence relation between gates identifying a pair of
-gates $(h, h')$ in a circuit $C$ of order $n$ if, and only if, there exists
-$\sigma \in \sym_n$, $\pi, \pi' \in \aut(C)$ both extending $\sigma$, and $g$ a
-gate in $C$, such that $h = \pi (g)$ and $h' = \pi' (g)$. We now show this
-relation is a refinement of syntactic-equivalence.
+We could think of any gate $g$ in the circuit as computing a function that maps
+a given assignment to the input gates to the evaluation of the circuit at $g$
+for the given assignment. While we would like to be able to identify gates that
+compute the same function in this sense, it is not hard to show that deciding
+this property is $\NP$-hard. The syntactic-equivalence relation is an
+easier-to-compute refinement of this relation, instead identifying pairs of
+gates if the circuits underneath them are hereditary similar.
+
+We could also define a similar equivalence relation using the automorphisms of a
+circuit. In this case we identify a pair of gates $(h, h')$ in a circuit $C$ of
+order $n$ if, and only if, there exists $\sigma \in \sym_n$, $\pi, \pi' \in
+\aut(C)$ both extending $\sigma$, and $g$ a gate in $C$, such that $h = \pi (g)$
+and $h' = \pi' (g)$. We now show this relation is a refinement of
+syntactic-equivalence.
 
@@
 
-It is easy to show that, for a circuit $C$ of order $n$, if $\sigma \in \sym_n$
-and both $\pi, \pi' \in \aut(C)$ extend $\sigma$, then for every gate $g$ in
-$C$, $\pi (g)$ and $\pi'(g)$ are syntactically-equivalent.
-
-We now introduce the \emph{unique labels} and \emph{transparency} conditions on
+We now define the \emph{unique labels} and \emph{transparency} conditions on
 circuits.
@@
 There is a small technical point that needs some discussion before we continue.
-The definition of a circuit allows for the inclusion of gates whose outputs need
-not lead to any output gate. In other words, we can be sure, not matter the rest
-of the circuit, that these gates cannot have any effect the function computed by
-the circuit. We say these gates are \emph{redundant}.
+The definition of a circuit allows for the inclusion of a gate such that there
+is no path from this gate to any of the output gates. In other words, we can be
+sure, not matter the rest of the circuit, that any such gate cannot have any
+effect the function computed by the circuit. We say these gates are
+\emph{redundant}.
 
@@
 
-It is easy to see that we can simply remove the redundant gates from a circuit,
-and so construct from a given circuit an equivalent circuit without redundant
-gates. Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a circuit of
-order $n$ and let $g$ be a redundant circuit in $C$. It is easy to see that $g$
-is not the child of a non-redundant gate, nor is it a relational or output gate.
-Thus we can define $C' := \langle G', \Omega, \restr{\Sigma}{G'}, \Lambda,
-\restr{L}{G'} \rangle$, where $G' \subseteq G$ is the set of all non-redundant
-gates in $C$.
+It is easy to see that we can construct from a given circuit an equivalent
+circuit without redundant gates by simply removing all of the redundant gates.
+Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a circuit of order
+$n$ and let $g$ be a redundant circuit in $C$. It is easy to see that $g$ is not
+the child of a non-redundant gate, nor is it a relational or output gate. Thus
+we can define the circuit $C' := \langle G', \Omega, \restr{\Sigma}{G'},
+\Lambda, \restr{L}{G'} \rangle$, where $G' \subseteq G$ is the set of all
+non-redundant gates in $C$.
 
@@
 G'$ has unique labels in $C$ if, and only if, $g$ has unique labels in $C'$.
-Moreover, it can be shown that if $C$ is symmetric and $g'$ is in the orbit of
-$g$ in $C$ then $g' \in G'$. As such, if $C$ is symmetric then so is $C'$. We
-thus have the following Lemma.
+Moreover, it can be shown that if $C$ is symmetric and $g, g' \in G$ then if $g$
+and $g'$ are in the same orbit then either both $g$ and $g'$ are in $G'$ or
+neither are in $G'$. As such, if $C$ is symmetric then so is $C'$. We thus have
+the following Lemma.
 
 \begin{lem}
+  \label{lem:redundant-gates}
   Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a circuit of order
@@
 
-We note that the construction of $C'$ from $C$ in Lemma~\ref{lem:redudant-gates}
-can be implemented so as to run in time polynomial in the size of $C$. As such,
-for the remainder of this paper we assume every circuit has no redundant gates.
-With this assumption stated we now show that every circuit with unique labels
-has unique extensions.
+We note that the construction of $C'$ from $C$ in
+Lemma~\ref{lem:redundant-gates} can be implemented so as to run in time
+polynomial in the size of $C$. As such, for the remainder of this paper we
+assume, unless stated otherwise, every circuit has no redundant gates. With this
+assumption in mind we now show that every circuit with unique labels has unique
+extensions.
 
@@
 \end{prop}
-% \begin{prop}
-%   Let $C_n := \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be an injective
-%   $(\mathbb{B}, \tau)$-circuit. Then $C_n$ has unique labels if, and only if,
-%   $C_n$ has unique extensions.
-% \end{prop}
 \begin{proof}
-  Suppose $C$ has unique labels. Let $\pi_{\sigma}, \pi_{\sigma}' \in \aut(C_n)$
+  Suppose $C$ has unique labels. Let $\pi_{\sigma}, \pi_{\sigma}' \in \aut(C)$
   be automorphisms extending $\sigma \in \sym_n$. We now prove that $\pi_\sigma
@@
 
-We also show that a transparent circuit can be converted into an equivalent
-circuit with unique labels in time polynomial in the size of the circuit. Since
-we are working with $P$-uniform families of transparent circuits, this fact
-allows us to assume, without a loss of generality, that transparent circuits
-have unique labels. We prove this formally in Proposition
-\ref{prop:transparent-unique}.
+We show in Proposition~\ref{prop:transparent-unique} that a transparent circuit
+can be converted into an equivalent circuit with unique labels in time
+polynomial in the size of the circuit. Since we are
+working with $P$-uniform families of transparent circuits, this fact allows us
+to assume, without a loss of generality, that transparent circuits have unique
+labels (and so unique extensions).
 
@@
 In many contexts, circuits are defined over a basis of symbols, usually the
-usual logical symbols $\land, \neg, \lor$ and perhaps $\maj$ (for majority).
+standard logical symbols $\land, \neg, \lor$, and perhaps $\maj$ (for majority).
 When evaluating a circuit, a gate labelled by a particular symbol is evaluated
@@
 
-Let $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
-\rho)$-circuit and let $g \in G$. We say a gate $g \in G$ is a \emph{symmetric
-  gate} if $\Sigma(g)$ is a symmetric function. We say a gate $g \in G$ is a
-\emph{matrix-symmetric gate} if $\Sigma(g)$ is a matrix-symmetric structured
-function. We say that $g$ is an \emph{$\AND$ gate} if $\Sigma(g) := \land [a]$
-for some $a \in \nats$. Similarly we define \emph{$\OR$- gates}, \emph{$\NOT$
-  gates}, \emph{$MAJ$ gates} and \emph{$\rank$ gates}.
-
-We say $C_n$ is a \emph{circuit with symmetric gates} if every gate in $C_n$ is
-symmetric. We say $C_n$ is a \emph{matrix-circuit} if every gate in $C_n$ is
-matrix-symmetric or symmetric. We say $C_n$ is a \emph{rank-circuit} if $C_n$ is
-a matrix-circuit and every non-symmetric gate is a $\rank$ gate.
+Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
+\rho)$-circuit of order $n$ and let $g \in G$. We say a gate $g \in G$ is a
+\emph{symmetric gate} if $\Sigma(g)$ is a symmetric function. We say a gate $g
+\in G$ is a \emph{matrix-symmetric gate} if $\Sigma(g)$ is a matrix-symmetric
+structured function. We say that $g$ is an \emph{$\AND$ gate} if $\Sigma(g) :=
+\land [a]$ for some $a \in \nats$. Similarly we define \emph{$\OR$- gates},
+\emph{$\NOT$ gates}, \emph{$MAJ$ gates} and \emph{$\rank$ gates}.
+
+We say $C$ is a \emph{circuit with symmetric gates} if every gate in $C$ is
+symmetric. We say $C$ is a \emph{matrix-circuit} if every gate in $C$ is
+matrix-symmetric or symmetric. We say $C$ is a \emph{rank-circuit} if $C$ is a
+matrix-circuit and every non-symmetric gate is a $\rank$ gate.
 

### 2018-02-05 sections/translating-formulas-to-cicuits.tex
February 5 2018

@@
     \setlength\itemsep{0mm}
-  \item $G' = G \setminus \{h_2, \ldots, h_q\}$,
+  \item $G' = G \setminus \{h_2, \ldots, h_p\}$,
   \item $\Omega' = \Omega$,
@@
 
-% Moreover, if we run merge on a circuit $C$ and a set $H$ then if $C$ has
-% unique labels and $H$ has the property that there is no gate $g$ in $C$ such
-% that two elements of $H$ are in $H_g$ then if $C$ has unique labels then so
-% does $C'$. Moreover, if $C$ is symmetric then so is $C'$.
-
 The now define the function $\op{make-injective}$ that maps a circuit and a
@@
   such that
-  \begin{itemize}
-    \setlength\itemsep{0mm}
+  \begin{itemizens}
   \item $G' = G \uplus \{h_2, \ldots, h_{c-1}\}$,
@@
     L(g)^{-1}(h)$ then let $L'(g)(\vec{a}) = h_i$.
-  \end{itemize}
+  \end{itemizens}
 \end{definition}
@@
 and output circuits of this operation compute the same function.
-
-% Furthermore, $\op{make-injective}(C, h) = C'$ and there exists a symmetric
-% gate $g \in C$ such that $\vert L(g)^{-1}(h) \vert > 1$ then the number of
-% non-injective symmetric gates in $C'$ is strictly less than the number of
-% non-injective symmetric gates in $C'$.
 
@@
 compute the same function.
-
-% $ $g$ in $C$ such that $W(h,g)$, let $g_{h_1}$ be the first gate in the
-% circuit such that for all $g' \in S_j$, $\vert L(g_{h_1})^{-1}(h_1) \vert \geq
-% L(g')^{-1}(h_1)$
-
-% We define $C'$ as follows. Let $F$ be a function that takes in an ordered
-% circuit $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ and outputs a
-% circuit $C* := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ defined as
-% follows. If for all $g \in G$, $L(g)$ is an injection then $F(C) = C$ and if
-% not then $F(C)$ is defined as follows.
-
-% Let $j \in [\depth(C)]$, and let ${G_0}' = G$, ${\Sigma_0}' = \Sigma$ and
-% ${L}_0' = L$.
-
-% Let $S_j$ be the set of all gates of height $j$ that are symmetric-gates. For
-% each $h_1 \in \bigcup_{g \in S_j} H_g$ let $g_{h_1} \in S_j$ be the first gate
-% in the circuit such that for all $g' \in S_j$, $\vert L(g_{h_1})^{-1}(h_1)
-% \vert \geq L(g')^{-1}(h_1)$. Let $(a_1, \ldots, a_p) := L(g_{h_1})^{-1}(h_1)$
-% (ordered according the to order on the circuit). We add to $G'$ the gates
-% $\{h_2, \ldots, h_p\}$ and for each $i \in \{2, \ldots, p\}$ we set
-% $\Sigma'(h_i)$ such that $h_i$ is a $\land$ gate with a single output and
-% $L'(h_i)$ such that $h_i$ takes only $h_{i-1}$ as an input. For each $g' \in
-% S$ such that $h_1 \in H_g$ let $\{ b_1, \ldots, b_q \} := L(g)^{-1}(h_1)$. For
-% each $i \in [q]$ let $L'(g')(b_i) = h_i$. Iterate $k$ and repeat this
-% procedure until $k$ exceeds the depth of the circuit.
-
-% \begin{definition}
-%   The operation \emph{separate-labels} takes as input an ordered $(\mathbb{B},
-%   \tau)$-circuit $C := \langle G, \Omega, \Sigma , \Lambda, L \rangle$ and
-%   outputs the circuit $C' = \langle G', \Omega', \Sigma', \Lambda', L'
-%   \rangle$. We define $C'$ as follows. Let $j \in [\depth(C)]$, and let
-%   ${G_0}' = G$, ${\Sigma_0}' = \Sigma$ and ${L}_0' = L$. Let $S_j$ be the set
-%   of all gates of height $j$ that are symmetric-gates. For each $h_1 \in
-%   \bigcup_{g \in S_j} H_g$ let $g_{h_1} \in S_j$ be the first gate in the
-%   circuit such that for all $g' \in S_j$, $\vert L(g_{h_1})^{-1}(h_1) \vert
-%   \geq L(g')^{-1}(h_1)$. Let $(a_1, \ldots, a_p) := L(g_{h_1})^{-1}(h_1)$
-%   (ordered according the to order on the circuit). We add to $G'$ the gates
-%   $\{h_2, \ldots, h_p\}$ and for each $i \in \{2, \ldots, p\}$ we set
-%   $\Sigma'(h_i)$ such that $h_i$ is a $\land$ gate with a single output and
-%   $L'(h_i)$ such that $h_i$ takes only $h_{i-1}$ as an input. For each $g' \in
-%   S$ such that $h_1 \in H_g$ let $\{ b_1, \ldots, b_q \} := L(g)^{-1}(h_1)$.
-%   For each $i \in [q]$ let $L'(g')(b_i) = h_i$. Iterate $k$ and repeat this
-%   procedure until $k$ exceeds the depth of the circuit.
-% \end{definition}
-
-% Notice that for a given circuit $C$ and a symmetric-gate $g$ in $C$, running
-% `merge' on each equivalence class of syntactically equivalent gates input to
-% $g$ and then running `separate-labels' on the resultant circuit produces
-% circuit $C'$ computing the same function as $C$ but the gate $g$ in $C$ has
-% unique labels.
 
@@
 
-% \begin{definition}
-%   The algorithm \emph{tag} takes in a $(\mathbb{B}, \tau)$-circuit $C_n :=
-%   \langle G, \Omega, \Sigma, \Lambda, L \rangle$, a relation symbol $R \in
-%   \tau$, a gate $g \in G$ and a tuple $\vec{a} \in [n]^k$ for some $k$ and
-%   outputs the circuit $C_n' = \langle G', \Omega', \Sigma', \Lambda',
-%   L'\rangle$ defined by the following algorithm. Let $G' = G \uplus \{\land_g,
-%   \land_{g'}, \land_1, \ldots , \land_k\}$, $\Omega' = \Omega$, and $\Lambda'
-%   = \Lambda$. Define $L'$ and $\Sigma'$ as follows. For each $g \in G$
-%   $\Sigma'(g) = \Sigma(g)$. For each $g \in \{\land_0, \land_1, \ldots ,
-%   \land_k \}$, $\Sigma(g)$ is an $\AND$-gate that takes in two inputs.
-%   $\Sigma(\land_g)$ is an $\AND$-gate that takes in a single input. Set $g$ to
-%   be the lone input to $\land_g$. Set the two inputs to $\land_0$ to be
-%   $\land_g$ and $\land_1$. For each $i \in [k-1]$ set the inputs of $\land_i$
-%   to be $\land_{i+1}$ and the gate $g_i \in G'$ such that $\Sigma(g_i) = R$
-%   and $\Lambda^{-1}(g_i) = \vec{a}_i$, where $\vec{a}_i$ is the $k$-tuple
-%   $(\vec{a}(i), \ldots, \vec{a}(i))$. Set the inputs of $\land_k$ to be the
-%   constant gate $1$ and the gate $g_k$ such that $\Sigma(g) = R$ and
-%   $\Lambda^{-1}(g_k) = \vec{a}_k$.
-
-%   For each gate $h \in G \setminus \{g\}$ and $\vec{b} \in \ind(h)$, if
-%   $L(h)(\vec{b}) = g$ then let $L'(h)(\vec{b}) = \land_0$, otherwise let
-%   $L'(h)(\vec{b}) = L(h)(\vec{b})$.
-
-% \end{definition}
-
 It can be shown that $\op{tag}$ can be computed in time polynomial in the size
@@
   T(h_i))$. Then $C' = C_{t}$.
-
-  % such that $G' = G \uplus \{\land_g, \land_{g'}, \land_1, \ldots ,
-  % \land_k\}$,
-  % $\Omega' = \Omega$, and $\Lambda' = \Lambda$. For each $g \in G$ $\Sigma'(g)
-  % =
-  % \Sigma(g)$. For each $g \in \{\land_0, \land_1, \ldots , \land_k \}$,
-  % $\Sigma(g)$ is an $\AND$-gate that takes in two inputs. $\Sigma(\land_g)$ is
-  % an $\AND$-gate that takes in a single input, $g$ is the lone input to
-  % $\land_g$, and $\land_0$ has as input $\land_g$ and $\land_1$. For each $i
-  % \in
-  % [k-1]$ the inputs of $\land_i$ are $\land_{i+1}$ and the gate $g_i \in G'$
-  % such that $\Sigma(g_i) = R$ and $\Lambda^{-1}(g_i) = \vec{a}_i$, where
-  % $\vec{a}_i$ is the $k$-tuple $(\vec{a}(i), \ldots, \vec{a}(i))$. The inputs
-  % of
-  % $\land_k$ are the constant gate $1$ and the gate $g_k$ such that $\Sigma(g)
-  % =
-  % R$ and $\Lambda^{-1}(g_k) = \vec{a}_k$. For each gate $h \in G \setminus
-  % \{g\}$ and $\vec{b} \in \ind(h)$, if $L(h)(\vec{b}) = g$ then
-  % $L'(h)(\vec{b})
-  % = \land_0$, otherwise $L'(h)(\vec{b}) = L(h)(\vec{b})$.
 \end{definition}
@@
 
-% \begin{definition}
-%   The function $\op{concatenate}$ maps a $(\mathbb{B}, \tau)$-circuit $C :=
-%   \langle G, \Omega, \Sigma, \Lambda, L \rangle$, a sequence of relation
-%   sybmols $\tau_R := (R_1, \ldots, R_t)$ such that $\tau_R \subseteq \tau$, a
-%   sequence of circuits $\mathcal{C} := ( C^1, \ldots, C^t)$, where for each $i
-%   \in [t]$, $C^i = \langle G_i, \Omega_i, \Sigma_i, \Lambda_i, L_i \rangle$ is
-%   a $(\mathbb{B}_i, \tau_i)$-circuit, $\tau_i \not\subset \tau_R$ and $C^i$
-%   computes a query of arity $\arty(R_i)$, and $R$ is a relation symbol in
-%   $(\tau \setminus \tau_R) \cup (\bigcup_{1 \leq i \leq t},\tau_i))$ to a
-%   circuit $\op{concatenate}(C, \mathcal{C}, \tau_R, R) := C' := \langle G',
-%   \Omega', \Sigma', \Lambda', L' \rangle$. Note that all circuits take in
-%   structures of size $n$. The circuit $C'$ is defined as follows.
-
-%   Let ${C^0}' := \langle G^0, \Omega^0, \Sigma^0, \Lambda^0, L^0 \rangle :=
-%   C$. For each $i \in [t]$ fix a relation symbol $V_i \in \tau_i \setminus
-%   \tau_R$. For each $i \in [t]$ let ${C^{i}}' := \langle G_i', \Omega_i',
-%   \Sigma_i', \Lambda_i', L_i' \rangle := \op{insert} (C^i, {C^{i-1}}')$ be
-%   defined as follows. Let $D^{i-1}:= \op{insert} (C^i, {C^{i-1}}')$. Let
-%   $G_{R_i}$ be the set of all relational gates in $D^{i-1}$ labelled by the
-%   relational symbol in $R_i$. Let ${C^{i}}'$ be the circuit formed by
-%   replacing each gate in $g \in G_{R_i}$ with the gate
-%   $\Omega_{i}(\Lambda_{i-1}'(g))$ in $D^{i-1}$ (by repeated calls to the
-%   $op{replace}$ function) and using the $\op{tag}$ function on each gate
-%   $\Omega_i (\Lambda_{i-1}'(g))$ in $D^{i-1}$ using the tuple
-%   $\Lambda_{i-1}'(g)$ and the relation symbol $V_i$. We then let $C' :=
-%   {C^{t}}'$.
-
-%   %   For each relational gate $g$ in $D^{i-1}$ labelled by the symbol
-%   %   $R_i$,
-%   %   $\op{replace}$ $g$ with the gate $\Omega_{i}(\Lambda_{i-1}'(g))$ in
-%   %   $D^{i-1}$
-%   %   and $\op{tag}$ the gate $\Omega_i(\Lambda_{i-1}'(g))$ in $D^{i-1}$
-%   %   using
-%   %   the
-%   %   tuple $\Lambda_{i-1}'(g)$ and the relation symbol $R$. Output the
-%   %   circuit
-%   %   $C'
-%   %   := {C^t}'$.
-% \end{definition}
-% GW: do this tomorrow.
-
-% \begin{definition}
-%   The operation $\op{concatenate-circuits}(C, \mathcal{C}, \tau_R) = C'$,
-%   where $C := \langle G, \Omega, \Sigma, \Lambda_0, L_0 \rangle$ is a
-%   $(\mathbb{B}, \tau)$-circuit, $\mathcal{C}$ is a finite set of circuits
-%   takes as input a set of relation symbols $\tau_R := \{R_1, \ldots, R_t\}$
-%   and $t+1$ circuits $\{C^0, \ldots, C^{t}\}$, where $C^0 = \langle G_0,
-%   \Omega_0, \Sigma_0, \Lambda_0, L_0 \rangle$ is a $(\mathbb{B},
-%   \tau)$-circuit with $\tau_R \subseteq \tau$ and for each $i \in [t]$, $C^i =
-%   \langle G_i, \Omega_i, \Sigma_i, \Lambda_i, L_i \rangle$ is a
-%   $(\mathbb{B}_i, \tau_i)$-circuit computing a query of arity $\arty(R_i)$.
-%   The algorithm outputs, for a given input, a circuit $C = \langle G, \Omega,
-%   \Sigma, \Lambda, L\rangle$ constructed as follows. Let ${C^0}' := C^0$. For
-%   each $i \in [t]$ fix a relation symbol $V_i \in \tau_i \setminus \tau_R$.
-%   For each $i \in [t]$ construct the circuit ${C^{i}}' = \langle G_i',
-%   \Omega_i', \Sigma_i', \Lambda_i', L_i' \rangle $ by `inserting' $C^i$ into
-%   ${C^{i-1}}'$, and call the resultant circuit ${D^{i-1}}'$. For each
-%   relational gate $g$ in $D^{i-1}$ labelled by the symbol $R_i$, `replace' $g$
-%   with the gate $\Omega_{i}(\Lambda_{i-1}'(g))$ in $D^{i-1}$ and `tag' the
-%   gate $\Omega_i(\Lambda_{i-1}'(g))$ in $D^{i-1}$ using the tuple
-%   $\Lambda_{i-1}'(g)$ and the relation symbol $V_i$. Output the circuit $C :=
-%   {C^t}'$.
-% \end{definition}
-
 It can be shown that $\op{compose}$ can be computed in time polynomial in the
@@
 
-In certain contexts we are interested composing gates such that if the input circuits are
-transparent (resp. have unique labels) then the output circuits will be
-transparent (resp. have unique labels). In this case, while composing the
-circuits we could apply the $\op{tag}$ function to the output gates of the
+In certain contexts we are interested composing gates such that if the input
+circuits are transparent (resp. have unique labels) then the output circuits
+will be transparent (resp. have unique labels). In this case, while composing
+the circuits we could apply the $\op{tag}$ function to the output gates of the
 circuits in the input sequence. We now define the function
@@
 It is easy to see that $\op{compose-and-tag}$ can be computed in time polynomial
-in the sizes of the input circuits. Furthermore, if the input sequences of
-circuits and relations are both singletons, then if the input circuits are all
-transparent (resp. have unique labels) then the output circuit is transparent
-(resp. have unique labels).
+in the sun of the sizes of the input circuits. We also have that if the input
+circuits are symmetric then the output circuits are symmetric. Furthermore, if
+the input sequences of circuits and relations are both singletons, then if the
+input circuits are all transparent (resp. have unique labels) then the output
+circuit is transparent (resp. have unique labels).
 
@@
 equal to the query defined by $\theta (\vec{x})$.
-
-% From Lemma \cite{} we may assume, without a loss of generality, that $(C_n)_{n
-% \in nats}$ is a family of rigid circuits (and hence has unique labels).
 
@@
 \begin{proof}
-  We say a formula $\psi(\vec{x})$ is \emph{circuit-translatable} if there is a
-  $P$-uniform family of transparent symmetric rank-circuits computing the query
-  as the one defined by $\psi(\vec{x})$. If a formula $\psi(\vec{x})$ is
-  circuit-translatable we let $(C^\psi_n)_{n \in \nats}$ denote a $P$-uniform
-  family of transparent symmetric rank-circuits computing the same query as
-  defined by $\psi(\vec{x})$.
-
-  Let $\theta(\vec{x}) \in \FPR[\tau]$. We prove that $\theta(\vec{x})$ is
-  circuit-translatable by structural induction. That is, we prove that if every
-  sub-formula of $\theta(\vec{x})$ is circuit-translatable then
-  $\theta(\vec{x})$ is circuit-translatable. Since it is obvious that every
-  atomic formula in $\FPR[\tau]$ is circuit-translatable, the result thus
-  follows. We already have that the formulas of $\FPC[\tau]$ are
-  circuit-translatable (Anderson and Dawar~\cite{AndersonD17}), and in fact we
-  may assume, without a loss of generality, that this translation yields a
-  family of transparent circuits with unique labels (and unique extensions).
-
-  We begin by showing that for any $\theta(\vec{x}) \in \FPR[\tau]$, there
-  exists a $P$-uniform family of formulas $(\theta(\vec{x}))_{n \in \nats}$ such
-  that for each $n \in \nats$, $\theta_n(\vec{x})$ is a first order formula with
-  counting and rank quantifiers and is equivalent to $\theta(\vec{x})$ on
-  structures of size $n$. This fact follows immediately from three observations.
-  First, we note that for any $\phi \in FPR[\tau]$ of the form $\lfp{V,
-    \vec{y}}{\psi(\vec{x}, \vec{y}, V)}(\vec{x})$ , there is a mapping $n
-  \mapsto \phi_n$, computable in time polynomial in $n$, such that for all $n
-  \in \nats$, both $\phi_n$ and $\phi$ are equivalent on structures of size $n$,
-  and $\phi_n$ contains no least-fixed-point operator. The formula $\phi_n$ is
-  define from $\phi$ by `unfurling' the least-fixed-point operator, producing,
-  for a given $n \in \nats$, a formula that explicitly implements the definition
-  of the operator in the obvious manner (for details on this implementation see
-  \ref{}). This construction of $\phi_n$ involves adding a constant number of
-  terms to $\phi$ for each iteration involved in computing the
-  least-fixed-point. Since there are at most $n^k$ such iterations, where $k$ is
-  the width of the formula $\psi$, the construction of $\phi_n$ can be completed
-  in time polynomial in $n$.
-
-  Similar arguments holds for number terms and rank operators. We have
-  from~\cite{} that for any formula $\phi$ containing number-terms there is a
-  $P$-uniform family of formulas $(\phi_n)_{n \in \nats}$ containing counting
-  quantifiers and no number-terms, and such that for all $n \in \nats$, $\phi$
-  and $\phi_n$ are equivalent on structures of size $n$. We have from Dawar et
-  al.~\cite{Dawar09logicswith} that for every formula $\phi \in \FPR[\tau]$
-  containing rank operators, there exists a $P$-uniform family that takes as
-  input a natural number $n$ and outputs a formula $\phi_n$ with rank
-  quantifiers and no rank operators, and such that for all $n \in \nats$, $\phi$
-  and $\phi_n$ are equivalent on structures of size $n$.
-
-  The algorithm given by executing each of the above three algorithms in
-  succession computes the required mapping $n \mapsto \theta_n(\vec{x})$ in time
-  polynomial in $n$, thus giving us the required $P$-uniform family
-  $(\theta_n(\vec{x}))_{n \in \nats}$.
-
-  It follows that the number of sub-formulas of $\theta_n$
-
-  It follows that in order to prove that $\theta(\vec{x})$ is
-  circuit-translatable it is sufficient to prove that there exists a function
-  that maps $\theta_n$ (for any $n \in \nats$) to $C^{\theta}_n$, a transparent
-  symmetric rank-circuit that computes the same query as defined by
-  $\theta_n(\vec{x})$ (and so $\theta(\vec{x})$) for structures of size $n$, and
-  is computable in time polynomial in in both $n$ and the number of sub-formulas
-  in $\theta_n$. This is sufficient as the number of sub-formulas in $\theta_n$
-  is bounded by some polynomial in $n$, and so composing functions, we can
-  compute the map that takes $n$ to $\theta_n$ to $C^{\theta}_n$ in time
-  polynomial in $n$.
-
-  We define an algorithm for constructing $C^{\theta}_n$ given
-  $\theta_n(\vec{x})$ by recursion on the structure of the input formula. The
-  first note that if $\theta_n(\vec{x})$ an atomic formula then there is a
-  trivial construction of $C^{\theta}_n$.
-
-  We consider the conjunctive case. Suppose $\phi_1, \phi_2 \in \FPR[\tau]$ are
-  circuit-translatable and $\theta (\vec{x}) = \phi_1(\vec{x}) \land
-  \phi_2(\vec{x})$. Let $R_{\phi_1}$ and $R_{\phi_2}$ be two $\vert \vec{x}
-  \vert$-ary relation symbols not in $\tau$. Let $\theta' (\vec{x}) :=
-  R_{\phi_1}(\vec{x}) \land R_{\phi_2}(\vec{x})$. Let $n \in \nats$. Since
-  $\theta'(\vec{x})$ is a formula of $\FPC[\tau]$, we have from Anderson and
-  Dawar~\cite{AndersonD17} that $\theta'(\vec{x})$ is circuit-translatable. We
-  let $C^{\theta}_n := \op{compose}(C^{\theta'}, (C^{\phi_1}, C^{\phi_2}),
-  (R_{\phi_1}, R_{\phi_2}))$.
-
-  Since all internal gates in $C^{\theta'}$ are symmetric, and both $C^{\phi_1}$
-  and $C^{\phi_2}$ are transparent, it follows that $C^{\theta}_n$ is
-  transparent. Moreover, it is easy to see that the construction of
-  $C^{\theta}_n$ can be carried implemented so as to run in time polynomial in
-  $n$, and that $(C^{\theta}_n)_{n \in \nats}$ computes the same query defined
-  by $\theta(\vec{x})$. It follows that $\theta(\vec{x})$ is
-  circuit-translatable.
-
-  % Notice that $D^{\theta}_n$ computes the same relation as defined by
-  % $\theta(\vec{x})$ for structures of size $n$. Moreover, since the remaining
-  % two operations preserve the function computed, it follows $C^{\theta}_n$
-  % computes the same relation as defined by $\theta(\vec{x})$ for structures of
-  % size $n$. Furthermore, since $C^{\phi_1}_n$, $C^{\phi_2}_n$ and
-  % $C^{\theta'}_n$ are symmetric so is $C^{\theta}_n$. Lastly, notice that all
-  % non-output gates in $D^{\theta}_n$ have unique labels. After the
-  % $\op{merge-all}$ and $\op{make-injective-all}$ operation the output gates
-  % have
-  % unique labels, and thus $C^{\theta}_n$ has unique labels. This construction
-  % takes in a natural number $n$ and produces the required circuit
-  % $C^{\theta}_n$. Moreover, it is easy to see that this construction can be
-  % implement as an algorithm running in time polynomial in $n$. It follows that
-  % $\theta(\vec{x})$ is circuit-translatable.
-
-  The approach used for resolving the conjunctive case can be thought of as
-  having three steps. First, replacing each sub-formula in $\theta$ with a
-  relation symbol, resulting in a formula $\theta'$ of $\FPC$. Second, using the
-  algorithms from the inductive hypothesis' (and the results of Anderson and
-  Dawar) on $\theta'$ and the sub-formulas, producing appropriate families for
-  $\theta'$ and each sub-formula of $\theta$. Third, for each $n \in \nats$
-  composing the circuit $C^{\theta'}_n$ with the circuits for each sub-formula,
-  producing the the circuit $C^{\theta}_n$. Since this process can be executed
-  in time polynomial in $n$, we conclude that $\theta$ is circuit-translatable.
-
-  This same approach can be used to handle many other cases. For
-  circuit-translatable $\phi, \phi_1, \phi_2 \in \FPR[\tau]$, and $k \in \nats$,
-  similar constructions can be used to prove that if $\theta(\vec{x}) \in
-  \FPR[\tau]$ is of the form $\phi_1(\vec{x}) \lor \phi_2(\vec{x})$, $\neg
-  \phi(\vec{x})$, $\forall y. \phi (\vec{x}, y)$, $\exists y. \phi (\vec{x}, y)$
-  or $C^k y. \phi(\vec{x}, y)$ then $\theta(\vec{x})$ is circuit-translatable.
-
-  % Suppose $\phi(\vec{x},y) \in \FPR[\tau]$ is circuit-translatable and
-  % $\theta(\vec{x}) := C^{k}y. \phi(\vec{x}, y)$. Let $k := \vert \vec{x}
-  % \vert$
-  % and $R$ be a $(k+1)-$-ary relational symbol. Let $D_n$ be a $(\MB,
-  % \{R\})$-circuit computing the $k$-ary query such that for each $\vec{a} \in
-  % [n]^k$, the output gate labelled by $\vec{a}$ computes the Boolean function
-  % \begin{align*}
-  %   \countgate_{\vec{a}} &(x_{(\vec{a}, 1)}, \ldots, x_{({\vec{a}, n})}) 
-  %                          := \\ & \begin{cases} \land ( \maj ( x_{(\vec{a}, 1)}, \ldots, x_{(\vec{a}, n)},
-  %                            \underbrace {0, \ldots, 0}_{2k - n} ), \neg ( \maj ( x_{(\vec{a}, 1)},
-  %                            \ldots, x_{(\vec{a}, n)}, \underbrace{0, \ldots,
-  %                              0}_{2k - n + 2} ) )) &  k \geq \frac{n}{2} \\
-  %                            \land ( \maj ( x_{(\vec{a}, 1)}, \ldots, x_{(\vec{a}, n)}, \underbrace {1,
-  %                              \ldots, 1}_{n - 2k} ), \neg ( \maj ( x_{(\vec{a}, 1)}, \ldots,
-  %                            x_{(\vec{a}, n)}, \underbrace{1, \ldots, 1}_{n - 2k -2} ) )) & k <
-  %                            \frac{n}{2},
-  %                          \end{cases}
-  % \end{align*}
-  % using the obvious circuit (for a more detailed construction see the proof of
-  % Proposition~\ref{prop:fuctions-maj}), and where for each $i \in [n]$, the
-  % variable $x_{(\vec{a}, i)}$ is replaced by the relational gate in the
-  % circuit
-  % labelled by $(\vec{a}, i)$. Then $C^{\theta}_n := \op{compose}(D_n,
-  % {C^\phi_n}, \{R\})$. It is easy to see that this construction can be carried
-  % out in time polynomial in $n$.
-
-  % GW: include here the result of inserting the circuit
-
-  Suppose $\phi(\vec{z}, \vec{y}, \vec{x}) \in \FPR[\tau]$ is
-  circuit-translatable, $p$ is a prime, $r$ is a natural number, and
-  $\theta(\vec{x}) := \rank^{\leq r}_p \vec{z} \vec{y}. \phi(\vec{z}, \vec{y},
-  \vec{x})$. We define an algorithm that takes as input a natural number $n$
-  outputs the required circuit $C^{\theta}_n$.
-
-  From the inductive hypothesis we may efficiently compute $C^{\phi}_n = \langle
-  G^{\phi}, \Omega^{\phi}, \Sigma^{\phi}, \Lambda^{\phi}, L^{\phi} \rangle$. Let
-  $k:= \vert \vec{x} \vert$, $k_1 : = \vert \vec{z} \vert$ and $k_2 := \vert
-  \vec{y} \vert$. Let $R_\phi$ be a $(k_1 + k_2 + k)$-ary relation symbol not in
-  $\tau$.
-
-  Let $\theta'(\vec{x}) = \rank^{\leq r}_r := \vec{z}, \vec{y}. R_{\phi}
-  (\vec{z}, \vec{y}, \vec{x})$. We define the $(\mathbb{B}_{\rank}, \{ R_{\phi}
-  \})$-circuit $C^{\theta'}_n:= \langle G^{\theta'}, \Omega^{\theta'},
-  \Sigma^{\theta'}, \Lambda^{\theta'}, L^{\theta'}\rangle$ as follows. Let
-  $G_{\text{out}} := \{g_{\vec{c}} : \vec{c} \in [n]^k\}$ and $G_{\text{in}} : =
-  \{ g_{\vec{a}, \vec{b}, \vec{c}} : \vec{a} \in [n]^{k_1}, \vec{b} \in
-  [n]^{k_2}, \vec{c} \in [n]^{k}\}$.
-
-  \begin{itemize}
-    \setlength\itemsep{0mm}
-  \item Let $G^{\theta'} = G_{\text{out}} \uplus G_{\text{in}}$,
-  \item $\Omega^{\theta'}$ be an injection from $[n]^k$ to $G^{\theta'}$ defined
-    by $\Omega^{\theta'}(\vec{c}) = g_{\vec{c}}$ for all $\vec{c} \in [n]^k$,
-  \item $\Sigma^{\theta'} (g) = \rank^r_p$ if $g \in G_{\text{out}}$ and
-    $\Sigma^{\theta'}(g) = R_\phi$ if $g \in G_{\text{in}}$,
-  \item For each $(\vec{a}, \vec{b}, \vec{c}) \in [n]^{k_1 +k_2 + k}$ let
-    $\Lambda^{\theta'} (\vec{a}, \vec{b}, \vec{c}) := g_{\vec{a}, \vec{b},
+  We say that a circuit $C$ \emph{translates} a formula $\psi(\vec{x})$ for $n
+  \in \nats$ if $C$ is a transparent symmetric rank-circuit of order $n$ and $C$
+  computes the query defined by $\psi(\vec{x})$ on structures of size $n$. We
+  say a family of circuits $(C_n)_{n \in \nats}$ \emph{translates} a formula
+  $\psi (\vec{x})$ if $(C_n)_{n \in \nats}$ is $\PT$-uniform and for all $n \in
+  \nats$, $C_n$ translates $\psi(\vec{x})$ for $n$.
+
+  We have from Anderson and Dawar~\cite{AndersonD17} that for every formula
+  $\phi(\vec{x}) \in \FPC[\tau]$ there is a $\PT$-uniform family of symmetric
+  circuits $(C^{\phi}_n)_{n \in \nats}$ with unique labels and symmetric gates
+  that translates $\phi(\vec{x})$.
+
+  Let $\theta(\vec{x}) \in \FPR[\tau]$ and $t := \width (\theta)$. We begin by
+  showing that there exists a $P$-uniform family of formulas
+  $(\theta(\vec{x}))_{n \in \nats}$ such that for each $n \in \nats$, we have
+  $\theta_n(\vec{x}) \in \FOrk[\tau]$, $\width(\theta_n) \leq 4 t$, and
+  $\theta_n(\vec{x})$ is equivalent to $\theta(\vec{x})$ on structures of size
+  $n$. This result follows from two observations.
+
+  First, using the translation in~\cite{Dawar09logicswith}, we have that for any
+  $\phi(\vec{x}) \in \FPR[\tau]$ of the form $\lfp{V, \vec{y}}{\psi(\vec{x},
+    \vec{y}, V)}(\vec{x})$ , there is a mapping $n \mapsto \phi_n$, computable
+  in time polynomial in both $n$ and the size of $\phi(\vec{x})$ such that for
+  all $n \in \nats$, we have $\phi_n(\vec{x}) \in \FOR[\tau]$, $\width (\phi_n)
+  \leq 2 \cdot \width (\phi)$, and $\phi_n(\vec{x})$ and $\phi(\vec{x})$ are
+  equivalent on structures of size $n$.
+
+  Second, using the translation in~\cite{libkin2004elements}, we have that if
+  $\phi (\vec{x}) \in \FOR[\tau]$ is of the form $\rank (\vec{y}\vec{\mu} \leq
+  \vec{t}, \vec{z}\vec{\nu} \leq \vec{s}, \pi \leq r) . \psi (\vec{y}\vec{\mu},
+  \vec{z} \vec{\nu})$, then there is a mapping $n \mapsto \phi_n$ computable in
+  time polynomial in both $n$ and the size of $\phi(\vec{x})$ such that for all
+  $n \in \nats$, $\phi_n(\vec{x}) \in \FOrk[\tau]$, $\width(\phi_n) \leq 2 \cdot
+  \width(\phi)$, and $\phi_n(\vec{x})$ and $\phi(\vec{x})$ are equivalent on
+  structures of size $n$.
+
+  We thus derive the required $\PT$-uniform family $(\theta_n(\vec{x}))_{n \in
+    \nats}$ by applying the first translation and then the second.
+
+  Fix $n \in \nats$. We recursively define a function $T_n$ that maps $\psi
+  (\vec{y})$, a sub-formula of $\theta_n(\vec{x})$, to a circuit $C^{\psi}_n$,
+  where $C^{\psi}_n$ translates $\psi(\vec{y})$ at $n$. We then have that for
+  all $n \in \nats$, $T_n(\theta_n(\vec{x}))$ translates $\theta_n$ (and hence
+  $\theta$) at $n$.
+
+  We first consider the base case. Suppose $\psi(\vec{y})$ is an atomic formula.
+  Then $\psi(\vec{y}) \in \FPC[\tau]$, and so, using the translation defined by
+  Anderson and Dawar~\cite{AndersonD17}, there exists a family of circuits
+  $(C^{\psi}_n)_{n \in \nats}$ that translates $\psi(\vec{y})$. Let
+  $T_n(\psi(\vec{y})) := C^{\psi}_n$.
+
+  We now consider the conjunctive case. Suppose $\psi(\vec{y})$ is a sub-formula
+  of $\theta_n(\vec{x})$ such that $\psi (\vec{y}) = \phi_1(\vec{y}) \land
+  \phi_2(\vec{y})$. Let $R_{\phi_1}$ and $R_{\phi_2}$ be two $\vert \vec{y}
+  \vert$-ary relation symbols not in $\tau$ and let $\psi' (\vec{y}) :=
+  R_{\phi_1}(\vec{y}) \land R_{\phi_2}(\vec{y})$. Then $\psi'(\vec{y}) \in
+  \FPC[\tau]$ and so, using the translation defined by Anderson and Dawar, there
+  exists a circuit family $(C^{\psi'}_n)_{n \in \nats}$ that translates
+  $\psi'(\vec{y})$. Let $T_n(\psi (\vec{y})) := \op{compose}(C^{\psi'}_n, (
+  T_n(\phi_1(\vec{y})), T_n(\phi_2(\vec{y}))), (R_{\phi_1}, R_{\phi_2}))$. We
+  note that $T_n(\psi(\vec{y}))$ translates $\psi (\vec{y})$ at $n$ if
+  $T_n(\phi_1 (\vec{y}))$ and $T_n(\phi_2(\vec{y}))$ translate $\phi_1(\vec{y})$
+  and $\phi_2(\vec{y})$ at $n$, respectively.
+
+  % We also note that this construction gives us that, if we exclude the cost of
+  % the recrive calls, then $n \mapsto T_n(\psi(\vec{y}))$ is computable in time
+  % polynomial in $n$. Notice, though, that this polynomial does depend on
+  % $\psi'(\vec{y})$, i.e. the form of $\psi (\vec{y})$.
+
+  The approach used in the conjunctive case can be summarised as follows. Given
+  a sub-formula $\psi (\vec{y})$, we construct an auxiliary formula
+  $\psi'(\vec{y})$ in which all the sub-formulas of $\psi(\vec{y})$ are replaced
+  with relation symbols. We then construct a circuit $C^{\psi'}$ that translates
+  $\psi'(\vec{y})$ at $n$ using the translation defined by Anderson and Dawar.
+  Finally, we recursively construct circuits that translate the sub-formulas of
+  $\psi(\vec{y})$, and compose these circuits with $C^{\psi'}$.
+
+  This approach can be used in order to handle every case with the exception of
+  rank. In other words, we can use a similar approach to define
+  $T_n(\psi(\vec{y}))$ where $\psi(\vec{y})$ is a sub-formula of
+  $\theta_n(\vec{x})$ of the form $\phi_1(\vec{y}) \lor \phi_2(\vec{y})$, $\neg
+  \phi(\vec{y})$, $\forall z. \phi (\vec{y}, z)$, or $\exists z. \phi (\vec{y},
+  z)$.
+
+  We now handle the rank case. The approach is quite similar, except in this
+  case we cannot use the translation defined by Anderson and Dawar in order to
+  translate the auxiliary formula, and so must define this translation
+  explicitly. Moreover, rather than just composing the circuits, we also add a
+  small gadget in order to ensure the resultant circuit is transparent.
+
+  Suppose $\psi(\vec{z}, \vec{w}, \vec{y})$ is a sub-formula of
+  $\theta_n(\vec{x})$ such that $\psi (\vec{y}) = \rank^{\leq r}_p \vec{z},
+  \vec{w} .\phi(\vec{z}, \vec{w}, \vec{y})$, for some $p, r \in \nats$ and $p$
+  prime. Let $k:= \vert \vec{y} \vert$, $k_1 : = \vert \vec{z} \vert$ and $k_2
+  := \vert \vec{w} \vert$. Let $R_\phi$ be a $(k_1 + k_2 + k)$-ary relation
+  symbol not in $\tau$. Let $\psi'(\vec{y}) := \rank^{\leq r}_p\vec{z}, \vec{w}.
+  R_{\phi} (\vec{z}, \vec{w}, \vec{y})$. Let $G_{\text{out}} := \{g_{\vec{c}} :
+  \vec{c} \in [n]^k\}$ and $G_{\text{in}} : = \{ g_{\vec{a}, \vec{b}, \vec{c}} :
+  \vec{a} \in [n]^{k_1}, \vec{b} \in [n]^{k_2}, \vec{c} \in [n]^{k}\}$. Let
+  $C^{\psi'}_n:= \langle G^{\psi'}, \Omega^{psi'}, \Sigma^{\psi'},
+  \Lambda^{\psi'}, L^{\psi'}\rangle$ be a $(\mathbb{B}_{\rank}, \{ R_{\phi}
+  \})$-circuit such that
+  \begin{itemizens}
+  \item $G^{\psi'} = G_{\text{out}} \cup G_{\text{in}}$,
+  \item $\Omega^{\psi'}$ be an injection from $[n]^k$ to $G^{\psi'}$ defined by
+    $\Omega^{\psi'}(\vec{c}) = g_{\vec{c}}$ for all $\vec{c} \in [n]^k$,
+  \item $\Sigma^{\psi'} (g) = \rank^r_p$ if $g \in G_{\text{out}}$ and
+    $\Sigma^{\psi'}(g) = R_\phi$ if $g \in G_{\text{in}}$,
+  \item for each $(\vec{a}, \vec{b}, \vec{c}) \in [n]^{k_1 +k_2 + k}$,
+    $\Lambda^{\psi'} (\vec{a}, \vec{b}, \vec{c}) = g_{\vec{a}, \vec{b},
       \vec{c}}$, and
-  \item For each gate $g_{\vec{c}} \in G_{\text{out}}$ let $L(g_{\vec{c}}):
-    [n]^{k_1} \times [n]^{k_2} \rightarrow G^{\theta'}$ be defined by
+  \item for each gate $g_{\vec{c}} \in G_{\text{out}}$, $L(g_{\vec{c}}):
+    [n]^{k_1} \times [n]^{k_2} \rightarrow G^{\psi'}$ is defined by
     $L(g_{\vec{c}})(\vec{a}, \vec{b}) := g_{\vec{a}, \vec{b}, \vec{c}}$ for each
     $\vec{a} \in [n]^{k_1}$ and $\vec{b} \in [n]^{k_2}$.
-  \end{itemize}
-
-  % It is easy to see that both $C^{\theta'}_n$ (and $C^{\phi}_n$) are symmetric
-  % rank-circuits with unique labels.
-
-  % It is easy to see that every gate in $$
-
-  % be the result of calling $\op{tag}$ on
-
-  % Let $C^{\theta}_n := \op{make-injective-all}(\op{merge-all}(D_n, H))$.
-  Let $R$ be a relation symbol in $\tau$. Let $C^{\theta}_n :=
-  \op{compose-and-tag}(C^{\theta'}_n, (C^{\phi}_n), (R_\phi), R)$. It is easy to
-  see that for all $n \in \nats$, $C^{\theta}_n$ computes the same query as
-  defined by $\theta(\vec{x})$ for structures of size $n$. Moreover, since
-  $C^{\theta'}_n$ and $C^{\phi}_n$ are symmetric, transparent, and the input
-  sequences of relations and circuits are singletons, it follows that
-  $C^{\theta}_n$ is a transparent symmetric rank-circuit. W have thus defined a
-  mapping from $n \mapsto C^{\theta}_n$, that, and that mapping can be computed
-  in time polynomial in $n$.
-
-  It remains only to note that any atomic formula of $\FPR[\tau]$ is trivially
-  circuit-translatable. The result thus follows.
+  \end{itemizens}
+
+  We note that $C^{\psi'}_n$ translates $\psi (\vec{y})$ at $n$. Let $R$ be a
+  relation symbol in $\tau$. Let
+  \begin{align*} T_n(\psi(\vec{y})) := \op{compose-and-tag}(C^{\psi'}_n,
+    (T_n(\phi(\vec{z}, \vec{w}, \vec{y}))), (R_\phi), R).
+  \end{align*}
+
+  We recall that $\op{compose-and-tag}$ combines circuits in a similar way to
+  $\op{compose}$ except that it also adds a set of gadgets to the circuit
+  ensuring that no two child gates of an output gate are
+  syntactically-equivalent. We thus have that $T_n(\psi (\vec{y}))$ is
+  transparent if $T_n(\phi (\vec{z}, \vec{w},\vec{y}))$ is transparent, and
+  $T_n(\psi(\vec{y}))$ translates $\psi (\vec{y})$ at $n$ if $T_n(\phi (\vec{z},
+  \vec{w},\vec{y}))$ translates $\phi(\vec{z}, \vec{w}, \vec{y})$ at $n$.
+
+  We have completed our definition of $T_n$ and shown, by induction on the
+  structure of $\theta_n(\vec{x})$, that for each $\psi (\vec{y})$ a sub-formula
+  of $\theta_n(\vec{x})$, $T_n(\psi(\vec{y}))$ translates $\psi(\vec{y})$ at
+  $n$.
+
+  The above definition can be used to define a recursive algorithm computing the
+  function $n \mapsto T_n (\theta_n(\vec{x}))$. We note that, since
+  $\width(\theta_n) \leq 4 t$ for all $n \in \nats$, there are only a finite
+  number of cases that need to be considered at each recursive step in this
+  algorithm. This fact can be used to show that there exists a polynomial bound
+  on the running time of the algorithm that depends only on $n$ and the
+  structure of $\theta(\vec{x})$. As such, we have that $(T_n (\theta_n))_{n \in
+    \nats}$ translates $\theta(\vec{x})$, and the result follows.
+
+  % We first construct an auxiliary formula $\psi'(\vec{y}$ in which all the
+  % sub-formulas of $\psi(\vec{y})$ are replaced with a relation symbol. We then
+  % construct a circuit $C^{\psi'}$ translating $\psi'(\vec{y})$ at $n$ (either
+  % explicitly, as in the rank case, or using the translation defined by
+  % Anderson and Dawar~\cite{}). Finally, we compose the circuit $C^{\psi'}$
+  % with the recursively defined circuits translating the sub-formulas of
+  % $\psi(\vec{y})$ (when composing in the rank case case we add an additional
+  % gadget, but the computation cost of this function is similar).
+
+  % The total computation cost of computing $T_n(\psi(\vec{y}))$ is then the
+  % cost of constructing $\psi'(\vec{y})$ + the cost of constructing
+  % $C^{\psi'}_n$ + the cost of the recursive calls + the cost of composition.
+  % We notice that, since there are only a finite number of cases, there are
+  % only a finite number of possible formulas $\psi'(\vec{y})$. Let
+  % $q_{\psi}(n)$ be a polynomial bounding time required to compute $n \mapsto
+  % C^{\psi'}_n$ for the case of $\psi(\vec{y})$. There are only a finite number
+  % of cases, so we can define $q_M(n)$ such that $q_M(n) \geq q_\psi(n)$ for
+  % all $n \in \nats$ and all cases $\psi(\vec{y})$. Let $q_c(x)$ be a
+  % polynomial larger than the polynomials bounding the run time of
+  % $\op{compose}$ and $\op{\compose-and-tag}$. Let $p(n)$ be the polynomial
+  % bounding witnessing the $P$-uniformity of $(\theta_n)_{n \in \nats}$. We
+  % then have that
+  % \begin{align*}
+  %   \time {T_n(\psi(\vec{y}))} := q_c(\vert C^{\psi'}_n \vert + \vert
+  %   %   T_n(\phi_1(\vec{y})) \vert + \vert (\phi_2(\vec{y}))) + \time {T_n
+  %   %   (\phi_1(\vec{y}))} + \time {T_n (\phi_2(\vec{y}} + q_M(n)
+  % \end{align*}
+
+  % For $i \in [2]$, it can be shown that
+  % \begin{align*}
+  %   \vert T_n(\phi_i) \vert  =  
+  % \end{align*}
+  % Let $p(n)$
+
+  % there exists a polynomial $q(n)$ such that $n \maps T_n (\psi(\vec{y}))$ is
+  % computable in time
+
+  % . Let $p(n)$ be the polynomial witnessing the $P$-uniformity of
+  % $(\theta_n)_{n
+  % \in \nats}$. We begin with the bases cases. We notice that in each case
+
+  % We now show that $T_n$ can be computed in time polynomial in $n$, thus
+  % giving
+  % us that $n \mapsto T_n (\theta_n(\vec{x}))$ can be computed computed in time
+  % polynomial in $n$, hence proving the result.
+
+  % It is easy to see that for $\psi (\vec{y})$ a subformula of $\theta_n$, the
+  % number of recursive calls needed to define $T_n(\psi(\vec{y}))$ is bounded
+  % by
+  % the number of sub-formulas in $\theta_n(\vec{x})$, which in turn is bounded
+  % by
+  % the size of $\theta_n(\vec{x})$, and hence by $p(n)$, where $p$ is the
+  % polynomial witnessing the $P$-uniformity of $(\theta_n)_{n \in \nats}$.
+
+  % We note that, up to renaming of variables, there are a constant number of
+  % cases to consider (i.e. possible forms of $\psi (\vec{y})$) at each
+  % recursive
+  % call (this follows from the fact that $\width(\theta_n) \leq 4\width
+  % (\theta)$
+  % for all $n \in \nats$).
+
+  % A the polynomial is dependent on the form being considered. Since there are
+  % only a finite number of such forms, we can sum up these polynomial bounds
+  % and
+  % arrive at a polynomial bound
+
+  % can appear as sub-formulas of $\theta_n$.
+
+  % It is easy to see that our definition of $T_n$ requires at most recursive
+  % steps
+
+  % We have now completed our definition of $T_n$. In each recursive step of our
+  % definition we used the translation of Anderson and Dawar~\ref{}
+
+  % We note that $C^{\psi'}_n$ is a transparent symmetric circuit with the
+  % property
+
+  % It is easy to see that for all $n \in \nats$, computes the same query as
+  % defined by $\theta(\vec{x})$ for structures of size $n$. Moreover, since
+  % $C^{\psi'}_n$ and $C^{\phi}_n$ are symmetric, transparent, and the input
+  % sequences of relations and circuits are singletons, it follows that
+  % $C^{\theta}_n$ is a transparent symmetric rank-circuit. W have thus defined
+  % a
+  % mapping from $n \mapsto C^{\theta}_n$, that, and that mapping can be
+  % computed
+  % in time polynomial in $n$.
+
+  % It remains only to note that any atomic formula of $\FPR[\tau]$ is trivially
+  % circuit-translatable. The result thus follows.
+
+  % $p$ is a prime, $r$ is a natural number, and $\theta(\vec{x}) := \rank^{\leq
+  % r}_p \vec{z} \vec{y}. \phi(\vec{z}, \vec{y}, \vec{x})$. We define an
+  % algorithm that takes as input a natural number $n$ outputs the required
+  % circuit $C^{\theta}_n$.
+
+  % The approach used for resolving the conjunctive case can be thought of as
+  % having three steps. First, replacing each sub-formula in $\psi$ with a
+  % relation symbol, resulting in a formula $\psi'$ of $\FPC[\tau]$. Second,
+  % using
+  % the translation of Anderson and Dawar to define the corresponding
+  % transparent
+  % symmetric circuit $C^{\psi'}_n$. Third, recursively computing the circuits
+  % for
+  % the sub-formulas, and then composing the circuits in order to construct
+  % $T(\psi(\vec{y}))$.
+
+  % Notice that if the sub-formulas are circuit-translatable then
+
+  % (and the results of Anderson and Dawar) on $\theta'$ and the sub-formulas,
+  % producing appropriate families for $\theta'$ and each sub-formula of
+  % $\theta$.
+  % Third, for each $n \in \nats$ composing the circuit $C^{\theta'}_n$ with the
+  % circuits for each sub-formula, producing the the circuit $C^{\theta}_n$.
+  % Since
+  % this process can be executed in time polynomial in $n$, we conclude that
+  % $\theta$ is circuit-translatable.
+
+  % This same approach can be used to handle many other cases. For
+  % circuit-translatable $\phi, \phi_1, \phi_2 \in \FPR[\tau]$, and $k \in
+  % \nats$,
+  % similar constructions can be used to prove that if $\theta(\vec{x}) \in
+  % \FPR[\tau]$ is of the form $\phi_1(\vec{x}) \lor \phi_2(\vec{x})$, $\neg
+  % \phi(\vec{x})$, $\forall y. \phi (\vec{x}, y)$, $\exists y. \phi (\vec{x},
+  % y)$
+  % or $C^k y. \phi(\vec{x}, y)$ then $\theta(\vec{x})$ is circuit-translatable.
+
+  % It follows that the number of sub-formulas of $\theta_n$
+
+  % It follows that in order to prove that $\theta(\vec{x})$ is
+  % circuit-translatable it is sufficient to prove that there exists a function
+  % that maps $\theta_n$ (for any $n \in \nats$) to $C^{\theta}_n$, a
+  % transparent
+  % symmetric rank-circuit that computes the same query as defined by
+  % $\theta_n(\vec{x})$ (and so $\theta(\vec{x})$) for structures of size $n$,
+  % and
+  % is computable in time polynomial in in both $n$ and the number of
+  % sub-formulas
+  % in $\theta_n$. This is sufficient as the number of sub-formulas in
+  % $\theta_n$
+  % is bounded by some polynomial in $n$, and so composing functions, we can
+  % compute the map that takes $n$ to $\theta_n$ to $C^{\theta}_n$ in time
+  % polynomial in $n$.
+
+  % We define an algorithm for constructing $C^{\theta}_n$ given
+  % $\theta_n(\vec{x})$ by recursion on the structure of the input formula. The
+  % first note that if $\theta_n(\vec{x})$ an atomic formula then there is a
+  % trivial construction of $C^{\theta}_n$.
+
+  % We consider the conjunctive case. Suppose $\phi_1, \phi_2 \in \FPR[\tau]$
+  % are
+  % circuit-translatable and $\theta (\vec{x}) = \phi_1(\vec{x}) \land
+  % \phi_2(\vec{x})$. Let $R_{\phi_1}$ and $R_{\phi_2}$ be two $\vert \vec{x}
+  % \vert$-ary relation symbols not in $\tau$. Let $\theta' (\vec{x}) :=
+  % R_{\phi_1}(\vec{x}) \land R_{\phi_2}(\vec{x})$. Let $n \in \nats$. Since
+  % $\theta'(\vec{x})$ is a formula of $\FPC[\tau]$, we have from Anderson and
+  % Dawar~\cite{AndersonD17} that $\theta'(\vec{x})$ is circuit-translatable. We
+  % let $C^{\theta}_n := \op{compose}(C^{\theta'}, (C^{\phi_1}, C^{\phi_2}),
+  % (R_{\phi_1}, R_{\phi_2}))$.
+
+  % Since all internal gates in $C^{\theta'}$ are symmetric, and both
+  % $C^{\phi_1}$
+  % and $C^{\phi_2}$ are transparent, it follows that $C^{\theta}_n$ is
+  % transparent. Moreover, it is easy to see that the construction of
+  % $C^{\theta}_n$ can be carried implemented so as to run in time polynomial in
+  % $n$, and that $(C^{\theta}_n)_{n \in \nats}$ computes the same query defined
+  % by $\theta(\vec{x})$. It follows that $\theta(\vec{x})$ is
+  % circuit-translatable.
+
+  % The approach used for resolving the conjunctive case can be thought of as
+  % having three steps. First, replacing each sub-formula in $\theta$ with a
+  % relation symbol, resulting in a formula $\theta'$ of $\FPC$. Second, using
+  % the
+  % algorithms from the inductive hypothesis' (and the results of Anderson and
+  % Dawar) on $\theta'$ and the sub-formulas, producing appropriate families for
+  % $\theta'$ and each sub-formula of $\theta$. Third, for each $n \in \nats$
+  % composing the circuit $C^{\theta'}_n$ with the circuits for each
+  % sub-formula,
+  % producing the the circuit $C^{\theta}_n$. Since this process can be executed
+  % in time polynomial in $n$, we conclude that $\theta$ is
+  % circuit-translatable.
+
+  % This same approach can be used to handle many other cases. For
+  % circuit-translatable $\phi, \phi_1, \phi_2 \in \FPR[\tau]$, and $k \in
+  % \nats$,
+  % similar constructions can be used to prove that if $\theta(\vec{x}) \in
+  % \FPR[\tau]$ is of the form $\phi_1(\vec{x}) \lor \phi_2(\vec{x})$, $\neg
+  % \phi(\vec{x})$, $\forall y. \phi (\vec{x}, y)$, $\exists y. \phi (\vec{x},
+  % y)$
+  % or $C^k y. \phi(\vec{x}, y)$ then $\theta(\vec{x})$ is circuit-translatable.
+
+  % Suppose $\phi(\vec{z}, \vec{y}, \vec{x}) \in \FPR[\tau]$ is
+  % circuit-translatable, $p$ is a prime, $r$ is a natural number, and
+  % $\theta(\vec{x}) := \rank^{\leq r}_p \vec{z} \vec{y}. \phi(\vec{z}, \vec{y},
+  % \vec{x})$. We define an algorithm that takes as input a natural number $n$
+  % outputs the required circuit $C^{\theta}_n$.
+
+  % From the inductive hypothesis we may efficiently compute $C^{\phi}_n =
+  % \langle
+  % G^{\phi}, \Omega^{\phi}, \Sigma^{\phi}, \Lambda^{\phi}, L^{\phi} \rangle$.
+  % Let
+  % $k:= \vert \vec{x} \vert$, $k_1 : = \vert \vec{z} \vert$ and $k_2 := \vert
+  % \vec{y} \vert$. Let $R_\phi$ be a $(k_1 + k_2 + k)$-ary relation symbol not
+  % in
+  % $\tau$.
+
+  % Let $\theta'(\vec{x}) = \rank^{\leq r}_r := \vec{z}, \vec{y}. R_{\phi}
+  % (\vec{z}, \vec{y}, \vec{x})$. We define the $(\mathbb{B}_{\rank}, \{
+  % R_{\phi}
+  % \})$-circuit $C^{\theta'}_n:= \langle G^{\theta'}, \Omega^{\theta'},
+  % \Sigma^{\theta'}, \Lambda^{\theta'}, L^{\theta'}\rangle$ as follows. Let
+  % $G_{\text{out}} := \{g_{\vec{c}} : \vec{c} \in [n]^k\}$ and $G_{\text{in}} :
+  % =
+  % \{ g_{\vec{a}, \vec{b}, \vec{c}} : \vec{a} \in [n]^{k_1}, \vec{b} \in
+  % [n]^{k_2}, \vec{c} \in [n]^{k}\}$.
+
+  % \begin{itemize}
+  %   \setlength\itemsep{0mm}
+  % \item Let $G^{\theta'} = G_{\text{out}} \uplus G_{\text{in}}$,
+  % \item $\Omega^{\theta'}$ be an injection from $[n]^k$ to $G^{\theta'}$
+  %   defined
+  %   by $\Omega^{\theta'}(\vec{c}) = g_{\vec{c}}$ for all $\vec{c} \in [n]^k$,
+  % \item $\Sigma^{\theta'} (g) = \rank^r_p$ if $g \in G_{\text{out}}$ and
+  %   $\Sigma^{\theta'}(g) = R_\phi$ if $g \in G_{\text{in}}$,
+  % \item For each $(\vec{a}, \vec{b}, \vec{c}) \in [n]^{k_1 +k_2 + k}$ let
+  %   $\Lambda^{\theta'} (\vec{a}, \vec{b}, \vec{c}) := g_{\vec{a}, \vec{b},
+  %   \vec{c}}$, and
+  % \item For each gate $g_{\vec{c}} \in G_{\text{out}}$ let $L(g_{\vec{c}}):
+  %   [n]^{k_1} \times [n]^{k_2} \rightarrow G^{\theta'}$ be defined by
+  %   $L(g_{\vec{c}})(\vec{a}, \vec{b}) := g_{\vec{a}, \vec{b}, \vec{c}}$ for
+  %   each
+  %   $\vec{a} \in [n]^{k_1}$ and $\vec{b} \in [n]^{k_2}$.
+  % \end{itemize}
+
+  % % It is easy to see that both $C^{\theta'}_n$ (and $C^{\phi}_n$) are
+  % % symmetric
+  % % rank-circuits with unique labels.
+
+  % % It is easy to see that every gate in $$
+
+  % % be the result of calling $\op{tag}$ on
+
+  % % Let $C^{\theta}_n := \op{make-injective-all}(\op{merge-all}(D_n, H))$.
+  % Let $R$ be a relation symbol in $\tau$. Let $C^{\theta}_n :=
+  % \op{compose-and-tag}(C^{\theta'}_n, (C^{\phi}_n), (R_\phi), R)$. It is easy
+  % to
+  % see that for all $n \in \nats$, $C^{\theta}_n$ computes the same query as
+  % defined by $\theta(\vec{x})$ for structures of size $n$. Moreover, since
+  % $C^{\theta'}_n$ and $C^{\phi}_n$ are symmetric, transparent, and the input
+  % sequences of relations and circuits are singletons, it follows that
+  % $C^{\theta}_n$ is a transparent symmetric rank-circuit. W have thus defined
+  % a
+  % mapping from $n \mapsto C^{\theta}_n$, that, and that mapping can be
+  % computed
+  % in time polynomial in $n$.
+
+  % It remains only to note that any atomic formula of $\FPR[\tau]$ is trivially
+  % circuit-translatable. The result thus follows.
+
 \end{proof}
+\bibliography{../references.bib}
+% \ifcsdef{mainfile}{}{\bibliography{../references.bib}}
+\end{document}
 
@@
 % \end{proof}
- \end{document}

### 2018-02-05 sections/transparency-and-unique-extensions.tex
February 5 2018

@@
 % consider only symmetric circuits with symmetric gates, which are transparent,
-% and as such include no such condition.
+% and as such include no such condition
 
@@
 % \end{definition}
+
 \subsection{The Usefulness of Transparency}
@@
   Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a transparent
-  $(\mathbb{B}, \rho)$-circuit of order $n$. We define a relation $\sim$ by
-  induction on height (i.e. distance from an input gate). This relation will be
-  the syntactic-equivalence relation on $G$. It is easy to check the conditions
-  for syntactic-equivalence for gates of height 0 as all such gates are input
-  gates and so are either constant gates or relational gates. Suppose $g$ and
-  $h$ are gates of height greater than zero. We only need to check conditions
-  (i), (iv) and (v) of syntactic-equivalence. It is easy to check (i) and (v).
-  If either condition is false then $g$ and $h$ are not syntacticly equivalent.
-  So suppose $g$ and $h$ are two internal gates such that $\Sigma (g) =
-  \Sigma(h)$ and suppose that if they are both output gates then $\Omega^{-1}(g)
-  = \Omega^{-1}(h)$. It remains to check if $L(g)/{\sim}$ and $L(h)/{\sim}$ are
-  isomorphism equivalent. First check if $H_h /{\sim} = H_g /{\sim}$. If not,
-  $g$ and $h$ are not syntactically equivalent. So suppose $H_h /{\sim} = H_g
-  /{\sim}$. If $g$ and $h$ are symmetric gates then $H_h /{\sim} = H_g/{\sim}$
-  if, and only if, $L(g)/{\sim}$ and $L(h)/{\sim}$ are isomorphism equivalent,
-  so let $g \sim h$. If $g$ and $h$ are not symmetric gates then, since $C$ is
-  transparent, $g$ and $h$ have unique labels. We thus have that $L(g)/{\sim}$
-  and $L(h)/{\sim}$ are isomorphism equivalent if, and only if, $L(g)^{-1}L(h)$
-  acts like an isomorphism. This can be checked by first checking that the
-  function induces a sorted permutation on the universe of $g$ (which can be
-  checked efficiently). This is sufficient as $L(g)(L(g)^{-1}L(h)) = L(h)$.
-
-  It is easy to see that, given a reasonable binary encoding of a circuit, the
-  above procedure can be implemented so as to run in polynomial time, and that
-  the relation $\sim$ is the syntactic-equivalence relation on the gates of $C$.
+  $(\mathbb{B}, \rho)$-circuit of order $n$. We define the syntactic-equivalence
+  relation on $G$ by induction on the height of a gate We note that this
+  definition can be implemented by a dynamic program.
+
+  Suppose $g$ and $h$ are gates in $C$ such that $\Sigma (g) = \Sigma(h)$ and
+  either both $g$ and $h$ are output gates and $\Omega^{-1}(g) = \Omega^{-1}(h)$
+  or neither are output gates. Let $g$ and $h$ be input gates, then set $g
+  \equiv h$ if, and only if, both $g$ and $h$ are constant gates or both are
+  relational gates and $\Lambda(g) = \Lambda (h)$. Let $g$ and $h$ be internal
+  gates and suppose we have defined the syntactic-equivalence relation for all
+  gates of height less than the height of either $g$ or $h$. Then $g \equiv h$
+  if, and only if, $L(g)$ and $L(h)$ are isomorphism equivalent up to $\equiv$.
+
+  % Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a transparent
+  % $(\mathbb{B}, \rho)$-circuit of order $n$. We define the
+  % syntactic-equivalence
+  % relation on $G$ by induction on the height of a gate. We note that this
+  % definition can be implemented as a recursive algorithm.
+
+  % Suppose $g$ and $h$ are gates in $C$, and check if $\Sigma (g) = \Sigma(h)$
+  % and either both $g$ and $h$ are output gates and $\Omega^{-1}(g) =
+  % \Omega^{-1}(h)$ or neither are output gates. If this check fails, return
+  % that
+  % $g \not\equiv h$. Otherwise, check if $g$ and $h$ are input gates and, if
+  % so,
+  % set $g \equiv h$ if, and only if, both $g$ and $h$ are constant gates or
+  % both
+  % are relational gates and $\Lambda(g) = \Lambda (h)$. Check if $g$ and $h$
+  % are
+  % internal gates and, if so, set $g \equiv h$ if, and only if, $L(g)$ and
+  % $L(h)$
+  % are isomorphism equivalent up to $\equiv$. ()
+
+  The above algorithm can be implemented by a dynamic program with the number of
+  iterations bounded by the number of pairs of gates in $C$, i.e. $\vert C
+  \vert$ choose $2$. It remains to show that each iterative step can be
+  implemented so as to run in time polynomial in the size of $C$. The only
+  condition that is not obviously polynomial-time decidable is checking if
+  $L(g)$ is isomorphism-equivalent to $L(h)$ up to $\equiv$. We sketch an
+  algorithm that decides this condition in time polynomial in the size of the
+  circuit.
+
+  Let $g$ and $h$ be two internal gates in $C$ and suppose we have defined the
+  syntactic-equivalence relation for all gates of height less than the height of
+  either $g$ or $h$. We test if for each gate in $g' \in H_g$, there exists
+  $h_{g'} \in H_h$ such that $g' \equiv h_{g'}$ and $\vert \{g'' \in H_g : g''
+  \equiv g'\} \vert = \vert \{h'' \in H_h : h'' \equiv h'\}$. If this test
+  fails, we set $g \not\equiv h$.
+
+  We then check if both $g$ and $h$ are symmetric gates or if both are
+  non-symmetric gates. Suppose both $g$ and $h$ are symmetric gates. We have
+  that $L(g)$ is isomorphism-equivalent to $L(h)$ up to $\equiv$ if, and only
+  if, there exists a bijection $f : H_g \rightarrow H_h$ such that $f(g') \equiv
+  g'$, for all $g' \in H_g$ if, and only if, for each gate in $g' \in H_g$,
+  there exists $h' \in H_h$ such that $g' \equiv h'$ and $\vert \{g'' \in H_g :
+  g'' \equiv g'\} \vert = \vert \{h'' \in H_h : h'' \equiv h'\}$. Since we have
+  already checked this condition we set $g \equiv h$.
+
+  Suppose $g$ and $h$ are non-symmetric gates. Then, since $C$ is transparent,
+  both $g$ and $h$ have unique labels. We thus have that for each $g' \in H_g$
+  there is exactly one $h_{g'} \in H_h$ such that $g' \equiv h_{g'}$, and so we
+  can define the bijection $f : H_g \rightarrow H_h$ by $f(g') := h_{g'}$ for
+  all $g' \in H_g$. It can be shown that $L(g)$ is isomorphism-equivalent to
+  $L(h)$ up to $\equiv$ if, and only if, $f \circ L(g)$ is
+  isomorphism-equivalent to $L(h)$ if, and only if, $L(h)^{-1} f L(g)$ acts on
+  $\ind (g)$ like an element of $\aut(g)$. We have from
+  Lemma~\ref{lem:aut-partial} that $\sigma := L(h)^{-1} f L(g)$ acts like an
+  element of $\aut(g)$ if, and only if, for all $\vec{a}_R, \vec{b}_{R'} \in \ind(g)$,
+  $\sigma$ acts like a partial automorphism on $(\vec{a}_R, \vec{b}_{R'})$. We
+  thus conduct the test by iterating through every pair $(\vec{a}_R,
+  \vec{b}_{R'}) \in \ind(g)$, and set $g \equiv h$ if, and only if, $\sigma$
+  acts like a partial automorphism on every such pair.
+
+  % for all $\vec{a}_R \in \ind(g)$, $\sigma \vec{a}_R$ has type $R$, and for all
+  % $\vec{b}_{R'}$, $i \in [\arty(R)]$, and $j \in [\arty(R')]$ we have that
+  % $\vec{a}(i) = \vec{b}(j)$ if, and only if, $(\sigma \vec{a}_R)(i) = (\sigma
+  % \vec{b}_R)(j)$. Since $\vert \ind(g) \vert \leq \vert C \vert$, we can check
+  % if $\sigma$ acts like an element of $\aut(g)$ by iterating through $\ind(g)$
+  % and checking each tuple satisfies the above conditions. We set $g \equiv h$
+  % if, and only if, $\sigma$ acts like an element of $\aut(g)$.
+
+  % This relation will be the syntactic-equivalence relation on $G$.
+
+  % Let $g, h \in G$. Suppose $g$ and $h$ are input gates, then $g \sim h$ if,
+  % and only if, $\Sigma (g) = \Sigma (h)$,
+  % \item if $g$ and $h$ are relational gates then $\Lambda (g) = \Lambda (h)$,
+  % \item either both or neither of $g$ and $h$ are output gates, and
+  % \item if both $g$ and $h$ are output gates then $\Omega^{-1}(g) =
+  %   \Omega^{-1}(h)$.
+  % \end{itemize}
+  % \setlength\itemsep{0mm} Suppose $g$ and $h$ are internal gates, and suppose
+  % we have defined $\sim$ for all gates of height less than either $g$ or $h$.
+  % Then $g \sim h$ if, and only if,
+  % \begin{itemize}
+  % \item $\Sigma (g) = \Sigma (h)$,
+  % \item either both or neither of $g$ and $h$ are output gates,
+  % \item if both $g$ and $h$ are output gates then $\Omega^{-1}(g) =
+  %   \Omega^{-1}(h)$, and
+  % \item $L (g)$ is isomorphism-equivalent to $L(h)$ up to $\sim$.
+  % \end{itemize}
+
+  % The above inductive definition can be implemented as a recursive algorithm
+  % with the number of recursive steps bounded by the number of pairs of gates
+  % in
+  % $C$, i.e. $\vert C \vert$ choose $2$. It remains to show that each recursive
+  % call can be implemented so as to run in time polynomial in the size of $C$.
+  % It
+  % is easy to see that we can check if a pair of input gates are
+  % syntactically-equivalent in time polynomial in the size of $C$. The only
+  % condition that is not obviously polynomial-time decidable is checking if
+  % $L(g)$ is isomorphism-equivalent to $L(h)$ up to $\sim$. We sketch an
+  % algorithm for deciding this condition for two internal gates.
+
+  % Let $g$ and $h$ be two internal gates in $C$. We first check if both $g$ and
+  % $h$ are symmetric gates or non-symmetric gates. Suppose both $g$ and $h$ are
+  % symmetric gates. It can be shown that $L(g)$ is isomorphism-equivalent to
+  % $L(h)$ up to $\sim$ if, and only if, there exists a bijection $f : H_g
+  % \rightarrow H_h$ such that $f(g') \sim g'$, for all $g' \in H_g$ if, and
+  % only
+  % if, for each gate in $g' \in H_g$, there exists $h' \in H_h$ such that $g'
+  % \sim h'$ and $\vert [g']_{\sim}\cap H_g \vert = \vert [h']_{\sim} \cap H_h$.
+  % It is easy to see that this last condition can be checked in polynomial
+  % time,
+  % and so we can check if $g \sim h$ in polynomial-time.
+
+  % Suppose $g$ and $h$ are non-symmetric gates. Then, since $C$ is transparent,
+  % $g$ and $h$ have unique labels. First check if there exists for each $g' \in
+  % H_g$ a gate $h_{g'} \in H_h$ such that $g' \sim h_{g'}$. If there exists
+  % $g'$
+  % such that no corresponding $h_{g'}$ exists, then we return that $g \not\sim
+  % h$. Since $g$ and $h$ have unique labels for each $g' \in H_g$ there is at
+  % most one $h_{g'} \in H_h$, and so we can define $f : H_g \rightarrow H_h$ by
+  % $f(g') := h_{g'}$ for all $g' \in H_g$. We note that there exists $\sigma
+  % \in
+  % aut(g)$ such that $f(L(g)(\vec{a}_R)) \sim L(h)(\sigma \vec{a}_R)$ for all
+  % $\vec{a}$, if and only if, $L(h)^{-1} f L(g)$ is compatible with every pair
+  % $(h', h'') \in H^2_h$.
+
+  % If this algorthm terminates and $f$ is constructed then we have that $L(g)$
+  % is
+  % isomorphism-equivalent to $L(h)$ up to $\sim$ and if this Suppose both $g$
+  % and
+  % $h$ are non-symmetric gates. Then both have unique labels, and so there is
+  % exactly
+
+  % Suppose $g$ is a symmetric gate. We then have that $L(g)$ is
+  % isomorphism-equivalent to $L(h)$
+
+  % It easy to see that for any pair of input gates we can check $g \sim h$ in
+  % polynomial time. If $\Sigma (g) \neq \Sigma (h)$ then set $g \not\sim h$. If
+  % exactly one of the two gates is an output gate then set $g \not\sim h$. If
+  % both $g$ and $h$ are output gates and $\Omega^{-1}(g) \neq \Omega^{-1}(h)$,
+  % then set $g \not\sim h$. If $g$ and $h$ are both relational gates and
+  % $\Lambda
+  % (g) \neq \Lambda (h)$ then set $g \not\sim h$.
+
+  % We have thus far handled the base case.
+
+  % If $g$ and $h$ are not both internal gates or both not input gates then set
+  % $g
+  % \not\sim h$. If $g$ and $h$ are both
+
+  % is easy to check the conditions for syntactic-equivalence for gates of
+  % height
+  % 0 as all such gates are input gates and so are either constant gates or
+  % relational gates. Suppose $g$ and $h$ are gates of height greater than zero.
+  % We only need to check conditions (i), (iv) and (v) of syntactic-equivalence.
+  % It is easy to check (i) and (v). If either condition is false then $g$ and
+  % $h$
+  % are not syntacticly equivalent. So suppose $g$ and $h$ are two internal
+  % gates
+  % such that $\Sigma (g) = \Sigma(h)$ and suppose that if they are both output
+  % gates then $\Omega^{-1}(g) = \Omega^{-1}(h)$. It remains to check if
+  % $L(g)/{\sim}$ and $L(h)/{\sim}$ are isomorphism equivalent. First check if
+  % $H_h /{\sim} = H_g /{\sim}$. If not, $g$ and $h$ are not syntactically
+  % equivalent. So suppose $H_h /{\sim} = H_g /{\sim}$. If $g$ and $h$ are
+  % symmetric gates then $H_h /{\sim} = H_g/{\sim}$ if, and only if,
+  % $L(g)/{\sim}$
+  % and $L(h)/{\sim}$ are isomorphism equivalent, so let $g \sim h$. If $g$ and
+  % $h$ are not symmetric gates then, since $C$ is transparent, $g$ and $h$ have
+  % unique labels. We thus have that $L(g)/{\sim}$ and $L(h)/{\sim}$ are
+  % isomorphism equivalent if, and only if, $L(g)^{-1}L(h)$ acts like an
+  % isomorphism. This can be checked by first checking that the function induces
+  % a
+  % sorted permutation on the universe of $g$ (which can be checked
+  % efficiently).
+  % This is sufficient as $L(g)(L(g)^{-1}L(h)) = L(h)$.
+
+  % It is easy to see that, given a reasonable binary encoding of a circuit, the
+  % above procedure can be implemented so as to run in polynomial time, and that
+  % the relation $\sim$ is the syntactic-equivalence relation on the gates of
+  % $C$.
 
@@
   % $(\mathbb{B}, \rho)$-circuit of order $n$. We define a relation $\sim$ by
-  % induction on height (i.e. distance from an input gate). This relation will be
-  % the syntactic-equivalence relation on $G$. It is easy to check the conditions
-  % for syntactic-equivalence for gates of height 0 as all such gates are input
-  % gates and so are either constant gates or relational gates. Suppose $g$ and
-  % $h$ are gates of height greater than zero. We only need to check conditions
-  % (i), (iv) and (v) of syntactic-equivalence. It is easy to check (i) and (v).
-  % If either condition is false then $g$ and $h$ are not syntacticly equivalent.
-  % So suppose $g$ and $h$ are two internal gates such that $\Sigma (g) =
-  % \Sigma(h)$ and suppose that if they are both output gates then $\Omega^{-1}(g)
-  % = \Omega^{-1}(h)$. It remains to check if $L(g)/{\sim}$ and $L(h)/{\sim}$ are
-  % isomorphism equivalent. First check if $H_h /{\sim} = H_g /{\sim}$. If not,
-  % $g$ and $h$ are not syntactically equivalent. So suppose $H_h /{\sim} = H_g
-  % /{\sim}$. If $g$ and $h$ are symmetric gates then $H_h /{\sim} = H_g/{\sim}$
-  % if, and only if, $L(g)/{\sim}$ and $L(h)/{\sim}$ are isomorphism equivalent,
-  % so let $g \sim h$. If $g$ and $h$ are not symmetric gates then, since $C$ is
-  % transparent, $g$ and $h$ have unique labels. We thus have that $L(g)/{\sim}$
-  % and $L(h)/{\sim}$ are isomorphism equivalent if, and only if, $L(g)^{-1}L(h)$
-  % acts like an isomorphism. This can be checked by first checking that the
-  % function induces a sorted permutation on the universe of $g$ (which can be
-  % checked efficiently). This is sufficient as $L(g)(L(g)^{-1}L(h)) = L(h)$.
+  % induction on height (i.e. distance from an input gate). This relation will
+  % be the syntactic-equivalence relation on $G$. It is easy to check the
+  % conditions for syntactic-equivalence for gates of height 0 as all such gates
+  % are input gates and so are either constant gates or relational gates.
+  % Suppose $g$ and $h$ are gates of height greater than zero. We only need to
+  % check conditions (i), (iv) and (v) of syntactic-equivalence. It is easy to
+  % check (i) and (v). If either condition is false then $g$ and $h$ are not
+  % syntacticly equivalent. So suppose $g$ and $h$ are two internal gates such
+  % that $\Sigma (g) = \Sigma(h)$ and suppose that if they are both output gates
+  % then $\Omega^{-1}(g) = \Omega^{-1}(h)$. It remains to check if $L(g)/{\sim}$
+  % and $L(h)/{\sim}$ are isomorphism equivalent. First check if $H_h /{\sim} =
+  % H_g /{\sim}$. If not, $g$ and $h$ are not syntactically equivalent. So
+  % suppose $H_h /{\sim} = H_g /{\sim}$. If $g$ and $h$ are symmetric gates then
+  % $H_h /{\sim} = H_g/{\sim}$ if, and only if, $L(g)/{\sim}$ and $L(h)/{\sim}$
+  % are isomorphism equivalent, so let $g \sim h$. If $g$ and $h$ are not
+  % symmetric gates then, since $C$ is transparent, $g$ and $h$ have unique
+  % labels. We thus have that $L(g)/{\sim}$ and $L(h)/{\sim}$ are isomorphism
+  % equivalent if, and only if, $L(g)^{-1}L(h)$ acts like an isomorphism. This
+  % can be checked by first checking that the function induces a sorted
+  % permutation on the universe of $g$ (which can be checked efficiently). This
+  % is sufficient as $L(g)(L(g)^{-1}L(h)) = L(h)$.
 
@@
   % above procedure can be implemented so as to run in polynomial time, and that
-  % the relation $\sim$ is the syntactic-equivalence relation on the gates of $C$.
+  % the relation $\sim$ is the syntactic-equivalence relation on the gates of
+  % $C$.
 
@@
   relation (i.e. we move all those gates in the circuit such that there is no
-  path from the gate to either $g_1$ or $g_2$). Let $C'$ be the circuit formed from $D$ by adding in a
-  single two-input $\AND$ gate $g'$ and connecting the outputs of $g_1$ and
-  $g_2$ to the inputs of $g'$. Moreover, we let this $g'$ be the single output
-  gate of $C'$.
+  path from the gate to either $g_1$ or $g_2$). Let $C'$ be the circuit formed
+  from $D$ by adding in a single two-input $\AND$ gate $g'$ and connecting the
+  outputs of $g_1$ and $g_2$ to the inputs of $g'$. Moreover, we let this $g'$
+  be the single output gate of $C'$.
 

### 2018-02-05 sections/symmetric-circuits.tex
Feb 5

@@
 \in G$ is a \emph{matrix-symmetric gate} if $\Sigma(g)$ is a matrix-symmetric
-structured function. We say that $g$ is an \emph{$\AND$ gate} if $\Sigma(g) :=
-\land [a]$ for some $a \in \nats$. Similarly we define \emph{$\OR$- gates},
-\emph{$\NOT$ gates}, \emph{$MAJ$ gates} and \emph{$\rank$ gates}.
+structured function. We say that $g$ is an \emph{$\AND$-gate} if $\Sigma(g) :=
+\land [a]$ for some $a \in \nats$. Similarly we define \emph{$\OR$-gates},
+\emph{$\NOT$-gates}, \emph{$\MAJ$-gates} and \emph{$\rank$-gates}.
 
@@
 matrix-symmetric or symmetric. We say $C$ is a \emph{rank-circuit} if $C$ is a
-matrix-circuit and every non-symmetric gate is a $\rank$ gate.
+matrix-circuit and every non-symmetric gate is a $\rank$-gate.
 

### 2018-02-05 sections/translating-formulas-to-cicuits.tex
Feb 5

@@
 functions which define transformations on circuits. In the second subsection we
-use these these functions to define a transformation of $\FPR$-formulas into
-equivalent families of transparent rank-circuits.
+use these functions to define a transformation that takes $\FPR$-formulas to
+equivalent families of transparent symmetric rank-circuits.
 
@@
   \item $\Lambda' = \Lambda$, and
-  \item For all $g \in G'$ and $\vec{a} \in Ind(g)$ if $L(g) (\vec{a}) \in H$
-    then $L'(g)(\vec{a}) = h_1$ and if $L(g)(\vec{a}) \notin H$ then
-    $L'(g)(\vec{a}) = L(g)(\vec{a})$.
+  \item For all $g \in G'$ and $x \in Ind(g)$ if $L(g) (x) \in H$ then $L'(g)(x)
+    = h_1$ and if $L(g)(x) \notin H$ then $L'(g)(x) = L(g)(x)$.
   \end{itemize}
@@
 labels, is transparent) then the output circuit will also be symmetric (resp.
-have unique labels, is transparent).
+have unique labels, transparent).
 
@@
 circuit, and note that any such encoding induces a linear order on the
-structure. Let $H_1, \ldots, H_p$ be the syntactic equivalence classes of $H$
+structure. Let $H_1, \ldots, H_p$ be the syntactic-equivalence classes of $H$
 linearly ordered such that for all $i, j \in [p]$ if $i \leq j$ the height of
@@
 Lemma~\cite{lem:unique-labels-syntactic-equiv} that if $H$ has unique labels
-then the syntactic equivalence relation on $H$ can be computed in time
-polynomial in the size of $C$. Thus, if the set $H$ has unique labels, it can be
-shown that the operation $\op{merge-all}$ can be computed in time polynomial in
-the size of the input circuit.
+then the syntactic-equivalence relation on $H$ can be computed in time
+polynomial in the size of $C$. Thus, if each gate in $H$ has unique labels, it
+can be shown that $\op{merge-all}$ can be computed in time polynomial in the
+size of the input circuit.
 
@@
 \op{merge-all}(C, H)$, and all of the children of $g$ in $C$ are in $H$, then no
-two distinct children of $g$ in $C'$ are syntactically-equivalent. We note we
-have no guarantee that $g$ will have unique labels in $C'$ as $L'(g)$ may not be
-injective.
+two distinct children of $g$ in $C'$ are syntactically-equivalent. However, we
+have no guarantee that $g$ will have unique labels in $C'$ as we have no
+guarantee that $L'(g)$ is injective.
 
@@
   \item For each $g \in G'$ if $g \in G \setminus W(h, \cdot)$ then $L'(g) =
-    L(g)$. If $g \in W(h, \cdot)$ let $\{\vec{a}_1, \ldots, \vec{a}_k\} :=
-    L(g)^{-1}(h)$ and for each $\vec{a} \in \ind(g)$ if $L(g)(\vec{a}) \neq h$
-    then $L'(g)(\vec{a}) = L(g)(\vec{a})$ and if $\vec{a} = \vec{a_i} \in
-    L(g)^{-1}(h)$ then let $L'(g)(\vec{a}) = h_i$.
+    L(g)$. If $g \in W(h, \cdot)$ let $\{x_1, \ldots, x_k\} := L(g)^{-1}(h)$ and
+    for each $x \in \ind(g)$ if $L(g)(x) \neq h$ then $L'(g)(x) = L(g)(x)$ else
+    if $x = x_i \in L(g)^{-1}(h)$ then let $L'(g)(x) = h_i$.
   \end{itemizens}
@@
 size of the input circuits. Moreover, if the input circuits are symmetric then
-the output circuit will be symmetric.
+the output circuit is symmetric.
 
@@
   \item $\Lambda' = \restr{\Lambda}{G'}$
-  \item For each $g \in G'$ and each $\vec{a} \in \ind(g)$ if $L(g)(\vec{a}) =
-    g_1$ then $L'(g)(\vec{a}) = g_2$ and if not then $L'(g)(\vec{a}) =
-    L(g)(\vec{a})$.
+  \item For each $g \in G'$ and each $x \in \ind(g)$ if $L(g)(x) = g_1$ then
+    $L'(g)(x) = g_2$ and if not then $L'(g)(x) = L(g)(x)$.
   \end{itemize}
@@
   gate $1$ and the gate $g_k$ such that $\Sigma(g) = R$ and $\Lambda^{-1}(g_k) =
-  \vec{a}_k$. For each gate $h \in G \setminus \{g\}$ and $\vec{b} \in \ind(h)$,
-  if $L(h)(\vec{b}) = g$ then $L'(h)(\vec{b}) = \land_0$, otherwise
-  $L'(h)(\vec{b}) = L(h)(\vec{b})$.
+  \vec{a}_k$. For each gate $h \in G \setminus \{g\}$ and $x \in \ind(h)$, if
+  $L(h)(x) = g$ then $L'(h)(x) = \land_0$, otherwise $L'(h)(x) = L(h)(x)$.
 \end{definition}
@@
 We now define the function $\op{compose}$ that maps a circuit and a sequence of
-appropriate circuits and to a circuit formed by replacing the input gates of the
-designated circuit with the output gates of the circuits in the sequence of
-circuits.
+circuits and to a circuit formed by replacing the input gates of the designated
+circuit with the output gates of the circuits in the sequence.
 
@@
   $\Omega_{i}(\Lambda_{i-1}'(g))$ in $D^{i-1}$ (by repeated calls to the
-  $op{replace}$ function). Let $C' = {C^{t}}'$.
+  $\op{replace}$ function). Let $C' = {C^{t}}'$.
 \end{definition}
@@
 It can be shown that $\op{compose}$ can be computed in time polynomial in the
-sum of the sizes of the input circuits. Moreover, if the input circuits are all
-symmetric then the output circuit will be symmetric. Also, for an input tuple
-$(C, \mathcal{C}, \tau_R)$, we have that if $C$ has symmetric gates and
-transparent, and all the circuits in $\mathcal{C}$ are transparent, then $C' :=
-\op{compose}(C, \mathcal{C}, \tau_R)$ is transparent. If $C$ does not have
-symmetric gates then, as the output gates of the circuits in $\mathcal{C}$ are
-no longer labelled as output gates in $C'$, it may be that some of these gates
-are syntactically-equivalent in $C'$, resulting in $C'$ not being transparent.
+sum of the sizes of the input circuits. We also note that the size of $C'$ is
+less than or equal to the sum of the sizes of the input circuits. Moreover, if
+the input circuits are all symmetric then the output circuit will be symmetric.
+Also, for an input tuple $(C, \mathcal{C}, \tau_R)$, we have that if $C$ has
+symmetric gates and transparent, and all the circuits in $\mathcal{C}$ are
+transparent, then $C' := \op{compose}(C, \mathcal{C}, \tau_R)$ is transparent.
+If $C$ contains a non-symmetric gates then, as the output gates of the circuits
+in $\mathcal{C}$ are no longer labelled as output gates in $C'$, it may be that
+some of these gates are syntactically-equivalent in $C'$, resulting in $C'$ not
+being transparent.
 
@@
 will be transparent (resp. have unique labels). In this case, while composing
-the circuits we could apply the $\op{tag}$ function to the output gates of the
-circuits in the input sequence. We now define the function
-$\op{compose-and-tag}$ that implements this mapping.
+the circuits we apply the $\op{tag}$ function to the output gates of the
+circuits in the input sequence of circuits. We now define the function
+$\op{compose-and-tag}$ that implements this operation.
 
@@
 input circuits are all transparent (resp. have unique labels) then the output
-circuit is transparent (resp. have unique labels).
+circuit is transparent (resp. have unique labels). We also note that the output
+circuit
 
@@
 
-  % We also note that this construction gives us that, if we exclude the cost of
-  % the recrive calls, then $n \mapsto T_n(\psi(\vec{y}))$ is computable in time
-  % polynomial in $n$. Notice, though, that this polynomial does depend on
-  % $\psi'(\vec{y})$, i.e. the form of $\psi (\vec{y})$.
-
   The approach used in the conjunctive case can be summarised as follows. Given
@@
     \nats}$ translates $\theta(\vec{x})$, and the result follows.
+\end{proof}
 
-  % We first construct an auxiliary formula $\psi'(\vec{y}$ in which all the
-  % sub-formulas of $\psi(\vec{y})$ are replaced with a relation symbol. We then
-  % construct a circuit $C^{\psi'}$ translating $\psi'(\vec{y})$ at $n$ (either
-  % explicitly, as in the rank case, or using the translation defined by
-  % Anderson and Dawar~\cite{}). Finally, we compose the circuit $C^{\psi'}$
-  % with the recursively defined circuits translating the sub-formulas of
-  % $\psi(\vec{y})$ (when composing in the rank case case we add an additional
-  % gadget, but the computation cost of this function is similar).
-
-  % The total computation cost of computing $T_n(\psi(\vec{y}))$ is then the
-  % cost of constructing $\psi'(\vec{y})$ + the cost of constructing
-  % $C^{\psi'}_n$ + the cost of the recursive calls + the cost of composition.
-  % We notice that, since there are only a finite number of cases, there are
-  % only a finite number of possible formulas $\psi'(\vec{y})$. Let
-  % $q_{\psi}(n)$ be a polynomial bounding time required to compute $n \mapsto
-  % C^{\psi'}_n$ for the case of $\psi(\vec{y})$. There are only a finite number
-  % of cases, so we can define $q_M(n)$ such that $q_M(n) \geq q_\psi(n)$ for
-  % all $n \in \nats$ and all cases $\psi(\vec{y})$. Let $q_c(x)$ be a
-  % polynomial larger than the polynomials bounding the run time of
-  % $\op{compose}$ and $\op{\compose-and-tag}$. Let $p(n)$ be the polynomial
-  % bounding witnessing the $P$-uniformity of $(\theta_n)_{n \in \nats}$. We
-  % then have that
-  % \begin{align*}
-  %   \time {T_n(\psi(\vec{y}))} := q_c(\vert C^{\psi'}_n \vert + \vert
-  %   %   T_n(\phi_1(\vec{y})) \vert + \vert (\phi_2(\vec{y}))) + \time {T_n
-  %   %   (\phi_1(\vec{y}))} + \time {T_n (\phi_2(\vec{y}} + q_M(n)
-  % \end{align*}
-
-  % For $i \in [2]$, it can be shown that
-  % \begin{align*}
-  %   \vert T_n(\phi_i) \vert  =  
-  % \end{align*}
-  % Let $p(n)$
-
-  % there exists a polynomial $q(n)$ such that $n \maps T_n (\psi(\vec{y}))$ is
-  % computable in time
-
-  % . Let $p(n)$ be the polynomial witnessing the $P$-uniformity of
-  % $(\theta_n)_{n
-  % \in \nats}$. We begin with the bases cases. We notice that in each case
-
-  % We now show that $T_n$ can be computed in time polynomial in $n$, thus
-  % giving
-  % us that $n \mapsto T_n (\theta_n(\vec{x}))$ can be computed computed in time
-  % polynomial in $n$, hence proving the result.
-
-  % It is easy to see that for $\psi (\vec{y})$ a subformula of $\theta_n$, the
-  % number of recursive calls needed to define $T_n(\psi(\vec{y}))$ is bounded
-  % by
-  % the number of sub-formulas in $\theta_n(\vec{x})$, which in turn is bounded
-  % by
-  % the size of $\theta_n(\vec{x})$, and hence by $p(n)$, where $p$ is the
-  % polynomial witnessing the $P$-uniformity of $(\theta_n)_{n \in \nats}$.
-
-  % We note that, up to renaming of variables, there are a constant number of
-  % cases to consider (i.e. possible forms of $\psi (\vec{y})$) at each
-  % recursive
-  % call (this follows from the fact that $\width(\theta_n) \leq 4\width
-  % (\theta)$
-  % for all $n \in \nats$).
-
-  % A the polynomial is dependent on the form being considered. Since there are
-  % only a finite number of such forms, we can sum up these polynomial bounds
-  % and
-  % arrive at a polynomial bound
-
-  % can appear as sub-formulas of $\theta_n$.
-
-  % It is easy to see that our definition of $T_n$ requires at most recursive
-  % steps
-
-  % We have now completed our definition of $T_n$. In each recursive step of our
-  % definition we used the translation of Anderson and Dawar~\ref{}
-
-  % We note that $C^{\psi'}_n$ is a transparent symmetric circuit with the
-  % property
-
-  % It is easy to see that for all $n \in \nats$, computes the same query as
-  % defined by $\theta(\vec{x})$ for structures of size $n$. Moreover, since
-  % $C^{\psi'}_n$ and $C^{\phi}_n$ are symmetric, transparent, and the input
-  % sequences of relations and circuits are singletons, it follows that
-  % $C^{\theta}_n$ is a transparent symmetric rank-circuit. W have thus defined
-  % a
-  % mapping from $n \mapsto C^{\theta}_n$, that, and that mapping can be
-  % computed
-  % in time polynomial in $n$.
-
-  % It remains only to note that any atomic formula of $\FPR[\tau]$ is trivially
-  % circuit-translatable. The result thus follows.
-
-  % $p$ is a prime, $r$ is a natural number, and $\theta(\vec{x}) := \rank^{\leq
-  % r}_p \vec{z} \vec{y}. \phi(\vec{z}, \vec{y}, \vec{x})$. We define an
-  % algorithm that takes as input a natural number $n$ outputs the required
-  % circuit $C^{\theta}_n$.
-
-  % The approach used for resolving the conjunctive case can be thought of as
-  % having three steps. First, replacing each sub-formula in $\psi$ with a
-  % relation symbol, resulting in a formula $\psi'$ of $\FPC[\tau]$. Second,
-  % using
-  % the translation of Anderson and Dawar to define the corresponding
-  % transparent
-  % symmetric circuit $C^{\psi'}_n$. Third, recursively computing the circuits
-  % for
-  % the sub-formulas, and then composing the circuits in order to construct
-  % $T(\psi(\vec{y}))$.
-
-  % Notice that if the sub-formulas are circuit-translatable then
-
-  % (and the results of Anderson and Dawar) on $\theta'$ and the sub-formulas,
-  % producing appropriate families for $\theta'$ and each sub-formula of
-  % $\theta$.
-  % Third, for each $n \in \nats$ composing the circuit $C^{\theta'}_n$ with the
-  % circuits for each sub-formula, producing the the circuit $C^{\theta}_n$.
-  % Since
-  % this process can be executed in time polynomial in $n$, we conclude that
-  % $\theta$ is circuit-translatable.
-
-  % This same approach can be used to handle many other cases. For
-  % circuit-translatable $\phi, \phi_1, \phi_2 \in \FPR[\tau]$, and $k \in
-  % \nats$,
-  % similar constructions can be used to prove that if $\theta(\vec{x}) \in
-  % \FPR[\tau]$ is of the form $\phi_1(\vec{x}) \lor \phi_2(\vec{x})$, $\neg
-  % \phi(\vec{x})$, $\forall y. \phi (\vec{x}, y)$, $\exists y. \phi (\vec{x},
-  % y)$
-  % or $C^k y. \phi(\vec{x}, y)$ then $\theta(\vec{x})$ is circuit-translatable.
-
-  % It follows that the number of sub-formulas of $\theta_n$
-
-  % It follows that in order to prove that $\theta(\vec{x})$ is
-  % circuit-translatable it is sufficient to prove that there exists a function
-  % that maps $\theta_n$ (for any $n \in \nats$) to $C^{\theta}_n$, a
-  % transparent
-  % symmetric rank-circuit that computes the same query as defined by
-  % $\theta_n(\vec{x})$ (and so $\theta(\vec{x})$) for structures of size $n$,
-  % and
-  % is computable in time polynomial in in both $n$ and the number of
-  % sub-formulas
-  % in $\theta_n$. This is sufficient as the number of sub-formulas in
-  % $\theta_n$
-  % is bounded by some polynomial in $n$, and so composing functions, we can
-  % compute the map that takes $n$ to $\theta_n$ to $C^{\theta}_n$ in time
-  % polynomial in $n$.
-
-  % We define an algorithm for constructing $C^{\theta}_n$ given
-  % $\theta_n(\vec{x})$ by recursion on the structure of the input formula. The
-  % first note that if $\theta_n(\vec{x})$ an atomic formula then there is a
-  % trivial construction of $C^{\theta}_n$.
-
-  % We consider the conjunctive case. Suppose $\phi_1, \phi_2 \in \FPR[\tau]$
-  % are
-  % circuit-translatable and $\theta (\vec{x}) = \phi_1(\vec{x}) \land
-  % \phi_2(\vec{x})$. Let $R_{\phi_1}$ and $R_{\phi_2}$ be two $\vert \vec{x}
-  % \vert$-ary relation symbols not in $\tau$. Let $\theta' (\vec{x}) :=
-  % R_{\phi_1}(\vec{x}) \land R_{\phi_2}(\vec{x})$. Let $n \in \nats$. Since
-  % $\theta'(\vec{x})$ is a formula of $\FPC[\tau]$, we have from Anderson and
-  % Dawar~\cite{AndersonD17} that $\theta'(\vec{x})$ is circuit-translatable. We
-  % let $C^{\theta}_n := \op{compose}(C^{\theta'}, (C^{\phi_1}, C^{\phi_2}),
-  % (R_{\phi_1}, R_{\phi_2}))$.
-
-  % Since all internal gates in $C^{\theta'}$ are symmetric, and both
-  % $C^{\phi_1}$
-  % and $C^{\phi_2}$ are transparent, it follows that $C^{\theta}_n$ is
-  % transparent. Moreover, it is easy to see that the construction of
-  % $C^{\theta}_n$ can be carried implemented so as to run in time polynomial in
-  % $n$, and that $(C^{\theta}_n)_{n \in \nats}$ computes the same query defined
-  % by $\theta(\vec{x})$. It follows that $\theta(\vec{x})$ is
-  % circuit-translatable.
-
-  % The approach used for resolving the conjunctive case can be thought of as
-  % having three steps. First, replacing each sub-formula in $\theta$ with a
-  % relation symbol, resulting in a formula $\theta'$ of $\FPC$. Second, using
-  % the
-  % algorithms from the inductive hypothesis' (and the results of Anderson and
-  % Dawar) on $\theta'$ and the sub-formulas, producing appropriate families for
-  % $\theta'$ and each sub-formula of $\theta$. Third, for each $n \in \nats$
-  % composing the circuit $C^{\theta'}_n$ with the circuits for each
-  % sub-formula,
-  % producing the the circuit $C^{\theta}_n$. Since this process can be executed
-  % in time polynomial in $n$, we conclude that $\theta$ is
-  % circuit-translatable.
-
-  % This same approach can be used to handle many other cases. For
-  % circuit-translatable $\phi, \phi_1, \phi_2 \in \FPR[\tau]$, and $k \in
-  % \nats$,
-  % similar constructions can be used to prove that if $\theta(\vec{x}) \in
-  % \FPR[\tau]$ is of the form $\phi_1(\vec{x}) \lor \phi_2(\vec{x})$, $\neg
-  % \phi(\vec{x})$, $\forall y. \phi (\vec{x}, y)$, $\exists y. \phi (\vec{x},
-  % y)$
-  % or $C^k y. \phi(\vec{x}, y)$ then $\theta(\vec{x})$ is circuit-translatable.
-
-  % Suppose $\phi(\vec{z}, \vec{y}, \vec{x}) \in \FPR[\tau]$ is
-  % circuit-translatable, $p$ is a prime, $r$ is a natural number, and
-  % $\theta(\vec{x}) := \rank^{\leq r}_p \vec{z} \vec{y}. \phi(\vec{z}, \vec{y},
-  % \vec{x})$. We define an algorithm that takes as input a natural number $n$
-  % outputs the required circuit $C^{\theta}_n$.
-
-  % From the inductive hypothesis we may efficiently compute $C^{\phi}_n =
-  % \langle
-  % G^{\phi}, \Omega^{\phi}, \Sigma^{\phi}, \Lambda^{\phi}, L^{\phi} \rangle$.
-  % Let
-  % $k:= \vert \vec{x} \vert$, $k_1 : = \vert \vec{z} \vert$ and $k_2 := \vert
-  % \vec{y} \vert$. Let $R_\phi$ be a $(k_1 + k_2 + k)$-ary relation symbol not
-  % in
-  % $\tau$.
-
-  % Let $\theta'(\vec{x}) = \rank^{\leq r}_r := \vec{z}, \vec{y}. R_{\phi}
-  % (\vec{z}, \vec{y}, \vec{x})$. We define the $(\mathbb{B}_{\rank}, \{
-  % R_{\phi}
-  % \})$-circuit $C^{\theta'}_n:= \langle G^{\theta'}, \Omega^{\theta'},
-  % \Sigma^{\theta'}, \Lambda^{\theta'}, L^{\theta'}\rangle$ as follows. Let
-  % $G_{\text{out}} := \{g_{\vec{c}} : \vec{c} \in [n]^k\}$ and $G_{\text{in}} :
-  % =
-  % \{ g_{\vec{a}, \vec{b}, \vec{c}} : \vec{a} \in [n]^{k_1}, \vec{b} \in
-  % [n]^{k_2}, \vec{c} \in [n]^{k}\}$.
-
-  % \begin{itemize}
-  %   \setlength\itemsep{0mm}
-  % \item Let $G^{\theta'} = G_{\text{out}} \uplus G_{\text{in}}$,
-  % \item $\Omega^{\theta'}$ be an injection from $[n]^k$ to $G^{\theta'}$
-  %   defined
-  %   by $\Omega^{\theta'}(\vec{c}) = g_{\vec{c}}$ for all $\vec{c} \in [n]^k$,
-  % \item $\Sigma^{\theta'} (g) = \rank^r_p$ if $g \in G_{\text{out}}$ and
-  %   $\Sigma^{\theta'}(g) = R_\phi$ if $g \in G_{\text{in}}$,
-  % \item For each $(\vec{a}, \vec{b}, \vec{c}) \in [n]^{k_1 +k_2 + k}$ let
-  %   $\Lambda^{\theta'} (\vec{a}, \vec{b}, \vec{c}) := g_{\vec{a}, \vec{b},
-  %   \vec{c}}$, and
-  % \item For each gate $g_{\vec{c}} \in G_{\text{out}}$ let $L(g_{\vec{c}}):
-  %   [n]^{k_1} \times [n]^{k_2} \rightarrow G^{\theta'}$ be defined by
-  %   $L(g_{\vec{c}})(\vec{a}, \vec{b}) := g_{\vec{a}, \vec{b}, \vec{c}}$ for
-  %   each
-  %   $\vec{a} \in [n]^{k_1}$ and $\vec{b} \in [n]^{k_2}$.
-  % \end{itemize}
-
-  % % It is easy to see that both $C^{\theta'}_n$ (and $C^{\phi}_n$) are
-  % % symmetric
-  % % rank-circuits with unique labels.
-
-  % % It is easy to see that every gate in $$
-
-  % % be the result of calling $\op{tag}$ on
-
-  % % Let $C^{\theta}_n := \op{make-injective-all}(\op{merge-all}(D_n, H))$.
-  % Let $R$ be a relation symbol in $\tau$. Let $C^{\theta}_n :=
-  % \op{compose-and-tag}(C^{\theta'}_n, (C^{\phi}_n), (R_\phi), R)$. It is easy
-  % to
-  % see that for all $n \in \nats$, $C^{\theta}_n$ computes the same query as
-  % defined by $\theta(\vec{x})$ for structures of size $n$. Moreover, since
-  % $C^{\theta'}_n$ and $C^{\phi}_n$ are symmetric, transparent, and the input
-  % sequences of relations and circuits are singletons, it follows that
-  % $C^{\theta}_n$ is a transparent symmetric rank-circuit. W have thus defined
-  % a
-  % mapping from $n \mapsto C^{\theta}_n$, that, and that mapping can be
-  % computed
-  % in time polynomial in $n$.
-
-  % It remains only to note that any atomic formula of $\FPR[\tau]$ is trivially
-  % circuit-translatable. The result thus follows.
-
-\end{proof}
 \bibliography{../references.bib}
@@
 \end{document}
-
-% \begin{proof}
-%   We say a formula $\psi(\vec{x}) \in \FPR[tau]$ is
-%   \emph{circuit-translatable} if there is a $P$-uniform family of symmetric
-%   matrix-circuits with unique labels that compute the same query as
-%   $\psi(\vec{x})$. If a formula $\psi(\vec{x}) \in \FPR[tau]$ is
-%   matrix-circuit-translatable we let $(C^\psi_n)_{n \in \nats}$ denote the
-%   corresponding $P$-uniform family of symmetric matrix-circuits with unique
-%   labels.
-
-%   We prove that $\theta(\vec{x}) \in \FPR[\tau]$ is circuit-translatable by
-%   structural induction. That is, we first prove that if every sub-formula of
-%   $\theta(\vec{x})$ is circuit-translatable then $\theta(\vec{x})$ is
-%   circuit-translatable and, second, we note that every atomic formula in
-%   $\FPR[\tau]$ is circuit-translatable. We have already that formulas of
-%   $\FPC[\tau]$ are circuit translatable (Anderson and
-%   Dawar~\cite{AndersonD17}), and in fact we may assume, without a loss of
-%   generality, that this translation yields a family of rigid circuits.
-
-%   %   It is sufficient to prove that if $\theta(\vec{x})$ has the property
-%   %   that
-%   %   all
-%   %   of its subformulas have are matrix-circuit-translatable then there is an
-%   %   algorithm that takes in a natural number $n$ and outputs a symmetric
-%   %   matrix-circuit $C^\theta_n$ with unique labels that is equivalent to
-%   %   $\theta(\vec{x})$ on structures of size $n$.
-
-%   We first consider the case where $\theta(\vec{x})$ is a conjunction of
-%   matrix-circuit-translatable formulas. Suppose $\phi_1, \phi_2 \in
-%   \FPR[\tau]$ are matrix-circuit-translatable and $\theta (\vec{x}) =
-%   \phi_1(\vec{x}) \land \phi_2(\vec{x})$. Let $R_{\phi_1}$ and $R_{\phi_2}$ be
-%   two $\vert \vec{x} \vert$-ary relation symbols not in $\tau$. Let $\theta'
-%   (\vec{x}) := R_{\phi_1}(\vec{x}) \land R_{\phi_2}(\vec{x})$. Let $n \in
-%   \nats$. Since $\theta'(\vec{x})$ is a formula of $\FPC$, we may efficiently
-%   compute $C^{\theta'}_n$ using the construction in \cite{AndersonD17}. From
-%   the inductive hypothesis, for each $i \in \{1,2\}$ we may efficiently
-%   compute the circuit $C^{\phi_i}_n = \langle G_i, \Omega_i, \Sigma_i
-%   Lambda_i, L_i \rangle$. Let $R \in \tau$ and let $D^{\theta}_n :=
-%   \op{compose}(C^{\theta'}_n, (C^{\phi_1}_n, C^{\phi_2}_n), (R_1, R_2), R)$.
-%   Let $H$ consist of all non-output gates in $D^{\theta}_n$. From the
-%   inductive hypothesis all gates in $H$ have unique labels. Let $C^{\theta}_n
-%   := \op{make-injective-all}(\op{merge-all}(D^{\theta}_n, H))$.
-
-%   Notice that $D^{\theta}_n$ computes the same relation as defined by
-%   $\theta(\vec{x})$ for structures of size $n$. Moreover, since the remaining
-%   two operations preserve the function computed, it follows $C^{\theta}_n$
-%   computes the same relation as defined by $\theta(\vec{x})$ for structures of
-%   size $n$. Furthermore, since $C^{\phi_1}_n$, $C^{\phi_2}_n$ and
-%   $C^{theta'}_n$ are symmetric so is $C^{\theta}_n$. Lastly, notice that all
-%   non-output gates in $D^{\theta}_n$ have unique labels. After the
-%   $\op{merge-all}$ and $\op{make-injective-all}$ operation the output gates
-%   have unique labels, and thus $C^{\theta}_n$ has unique labels. This
-%   construction takes in a natural number $n$ and produces the required circuit
-%   $C^{\theta}_n$. This construction can be computed by an algorithm in time
-%   polynomial in $n$. Thus $\theta(\vec{x})$ is matrix-circuit-translatable.
-
-%   %   We construct the circuit $C'_n = \langle G', \Omega', \Sigma',
-%   %   \Lambda', L' \rangle$ by `inserting' $C^{\phi_1}_n$ and $C^{\phi_2}_n$
-%   %   into
-%   %   $C^{\theta'}_n$. We now construct $C^{\theta}_n$ from $C'_n$ as follows:
-%   %   \begin{itemize}
-%   %   \item For each $i \in \{1,2\}$ and each relational gate $g$ in $C_n$
-%   %     such
-%   %     that $\Sigma'(g) = R_{\phi_i}$ `replace' $g$ with
-%   %     $\Omega_i(\Lambda_i(g))$,
-%   %   \item then, for each syntactic equivalence class $H \subseteq
-%   %     \range(\Omega_1) \uplus \range(Omega_2)$, `merge' $H$, and finally
-%   %   \item run `separate-labels' on the circuit.
-%   %   \end{itemize}
-
-%   %   We note that, since $C^{\phi_1}_n$, $C^{\phi_2}_n$ and $C^{\theta'}_n$
-%   %   have
-%   %   unique labels, the only gates that might not have unique labels in
-%   %   $C^{\theta}_n$ are those whose input gates include gates in the range of
-%   %   $\Omega_1$ or $\Omega_2$. However, all such gates are symmetric and
-%   %   steps
-%   %   (2)
-%   %   and (3) above guarantee that these gates have unique labels. Finally, we
-%   %   note
-%   %   that this algorithm can implemented such that the computation of
-%   %   $C^{\theta}_n$ from $n$ runs in time polynomial in $n$.
-
-%   The approach used above for resolving the conjunctive case can be thought of
-%   as having three steps. First, replacing each sub-formula with a relation
-%   symbol, resulting in a formula of $\FPC$. Second, using the algorithms from
-%   the inductive hypothesis' on sub-formulas, producing appropriate families of
-%   circuits computing each sub-formula, and the known circuit-translation for
-%   formulas of $\FPC$, in order to to produce an appropriate family of circuits
-%   computing the operation on these sub-formulas. Third, using the
-%   concatenation operation to combine these circuit families and two final
-%   operations in order to ensure the family has the required properties.
-
-%   This same approach can be used for to handle many other cases. For
-%   matrix-circuit-translatable $\phi, \phi_1, \phi_2 \in \FPR[\tau]$ similar
-%   constructions can be used to prove that if $\theta(\vec{x}) \in FPR[\tau]$
-%   is equal to $\phi_1(\vec{x}) \lor \phi_2(\vec{x})$, $\neg \phi(\vec{x})$,
-%   $\forall y. \phi (\vec{x}, y)$ or $\exists y. \phi (\vec{x}, y)$ then
-%   $\theta(\vec{x})$ is matrix-circuit-translatable.
-
-%   Suppose $\theta(\vec{x}) = \lfp{V, \vec{y}}{\phi(\vec{x}, \vec{y},
-%   V)}(\vec{x})$ for some matrix-circuit-translatable formula $\phi(\vec{x},
-%   \vec{y}) \in FPR[\tau \uplus \{V\}]$ and $k$-ary relation symbol $V$. Let
-%   $n$ be a natural number. We construct $C^{\theta}_n$ as follows. We have
-%   that we may efficiently compute $C^{\phi}_n$. For each $i \in [n^k]$ we
-%   construct a circuit $C^i = \langle G^i, \Omega^i, \Sigma^i, \Lambda^i, L
-%   \rangle $ as follows. Let $C^0$ be a circuit consisting of exactly $n^k$
-%   gates, such that each gate is a constant $0$ gate and each gate is an output
-%   gate. Let $R$ be a relation symbol in $\tau$. For each $i > 0$ let $C^i :=
-%   \op{concatinate}(C^{\phi}_n, (C^{i-1}_n), (V), R)$ be $C^{\phi}_n$ but with
-%   all relational gates labelled by the symbol $V$ replaced with the constant
-%   $0$. Since $C^1$ and $C^\phi_n$ are symmetric and have unique labels, and
-%   the operation $\op{concatinate}$ preserves the properties of symmetric and
-%   unique labels, it follows by induction that for each $i \geq 1$, $C^i$ is a
-%   symmetric rank-circuit with unique labels. It follows that $C^{\theta}_n :=
-%   C^{n^k}$ is a symmetric rank-circuit and has unique labels. Moreover, since
-%   the least-fixed-point operator must converge in at most $n^k$ steps, this
-%   construction can be implemented so as to run in time polynomial in $n$. The
-%   construction also guarantees that $(C^{\theta}_n)_{n \in \nats}$ computes
-%   the same query as $\theta(\vec{x})$.
-
-%   The result in \cite{} establishes that for every formula $\theta(\vec{x})$
-%   containing number-terms there is a $P$-uniform family of formulas
-%   $(\theta_n(\vec{x}))_{n \in \nats}$ containing counting quantifiers and no
-%   number-terms, and such that for all $n \in \nats$, $\theta(\vec{x})$ and
-%   $\theta_n(\vec{x})$ are equivalent on structures of size $n$.
-
-%   %   Suppose $\theta(\vec{x}) = \lfp{V, \vec{y}}{\phi(\vec{x}, \vec{y},
-%   %   V)}(\vec{x})$ for some matrix-circuit-translatable formula
-%   %   $\phi(\vec{x},
-%   %   \vec{y}) \in FPR[\tau \uplus \{V\}]$ and $\vert y \vert$-ary relation
-%   %   symbol
-%   %   $V$. Let $n$ be a natural number. We now construct $C^{\theta}_n$. We
-%   %   have
-%   %   that we may efficiently compute $C^{\phi}_n$. For each $i \in [n^k]$ we
-%   %   construct a circuit $C^i = \langle G^i, \Omega^i, \Sigma^i, \Lambda^i, L
-%   %   \rangle $ as follows. Let $C^1$ be $C^{\phi}_n$ but with all relational
-%   %   gates
-%   %   labelled by the symbol $V$ replaced with the constant $0$. For each
-%   %   $i>1$ we
-%   %   construct $C^{i}$ by `gluing' $C^{i-1}$ into $C^\phi_n$, producing
-%   %   $C^i$.
-%   %   Set
-%   %   $C^{\theta}_n := C^{n^k}$. Since $C^1$ and $C^\phi_n$ are symmetric and
-%   %   have
-%   %   unique labels, by induction for each $i > 1$ $C^i$ is symmetric and has
-%   %   unique
-%   %   labels. It follows that $C^{\theta}_n$ is symmetric and has unique
-%   %   labels.
-%   %   Moreover, since the least-fixed-point operator must converge in at most
-%   %   $n^k$
-%   %   steps, this algorithm runs in time polynomial in $n$ and the family
-%   %   $(C^{\theta}_n)_{n \in \nats}$ computes the same query as
-%   %   $\theta(\vec{x})$.
-
-%   %   The result in \cite{} establishes that for every formula
-%   %   $\theta(\vec{x})$
-%   %   containing number-terms there is a $P$-uniform family of formulas
-%   %   $(\theta_n(\vec{x}))_{n \in \nats}$ containing counting quantifiers and
-%   %   no
-%   %   number-terms, and such that for all $n \in \nats$, $\theta(\vec{x})$ and
-%   %   $\theta_n(\vec{x})$ are equivalent on structures of size $n$.
-
-%   %   gives for each $\theta (\vec{x}) \in FPC[\tau]$ a $P$-uniform family of
-%   %   formulas $(\theta_n)_{n \in \nats}$ such that $\theta_n(\vec{x})$ is in
-%   %   the
-%   %   extension of fixed-point logic with counting quantifiers and is
-%   %   equivalent
-%   %   to
-%   %   $\theta(\vec{x})$ on structures of size $n$. Similarly, it can be shown
-%   %   that
-%   %   for $\theta (\vec{x}) \in FPR[\tau]$ there exists an algorithm that
-%   %   takes as
-%   %   input a natural number $n$ and outputs a formula $\theta_n(\vec{x})$
-%   %   with
-%   %   counting quantifiers and no number terms which is equivalent to
-%   %   $\theta(\vec{x})$ for structures of size $n$ and does not contain any
-%   %   number
-%   %   terms. Moreover, this algorithm runs in time polynomial in $n$.
-
-%   Thus, in order to handle the number-term case, it is sufficient to show that
-%   if $\phi(\vec{x}) \in \FPR[\tau]$ is circuit-translatable then
-%   $\theta(\vec{x}) := C^{k}y. \phi(\vec{x}, y)$ is
-%   matrix-circuit-translatable. A similar construction as for the universal and
-%   existential quantifier gives the required algorithm.
-
-%   The result in \cite{} establishes that for every formula $\theta(\vec{x})
-%   \in \FPR[\tau]$ containing rank operators, there exists an algorithm that
-%   takes as input a natural number $n$ and outputs a formula
-%   $\theta_n(\vec{x})$ with rank quantifiers and no rank operators such that
-%   $\theta(\vec{x})$ and $\theta_n(\vec{x})$ are equivalent on structures of
-%   size $n$. It is thus sufficient to prove that, for
-%   matrix-circuit-translatable $\phi(\vec{z}, \vec{y}, \vec{x}) \in \FPR[\tau]$
-%   is, a prime $p$, and a natural number $r$, $\theta(\vec{x}) := \rank^{\leq
-%   r}_p \vec{z} \vec{y}. \phi(\vec{z}, \vec{y}, \vec{x})$ is
-%   circuit-translatable. We define an algorithm that takes as input a natural
-%   number $n$ outputs the required circuit $C^{\theta}_n$.
-
-%   From the inductive hypothesis we may efficiently compute $C^{\phi}_n =
-%   \langle G^{\phi}, \Omega^{\phi}, \Sigma^{\phi}, \Lambda^{\phi}, L^{\phi}
-%   \rangle$. Let $k:= \vert \vec{x} \vert$, $k_1 : = \vert \vec{z} \vert$ and
-%   $k_2 := \vert \vec{y} \vert$. Let $R_\phi$ be a $(k_1 + k_2 + k)$-ary
-%   relation symbol not in $\tau$. Let $\theta'(\vec{x}) = \rank^{\leq r}_r :=
-%   \vec{z}, \vec{y}. \phi (\vec{z}, \vec{y}, \vec{x})$. We now define a
-%   $(\mathbb{B}_{\rank}, \{ R_{\phi} \})$-circuit $C^{\theta'}_n:= \langle
-%   G^{\theta'}, \Omega^{\theta'}, \Sigma^{\theta'}, \Lambda^{\theta'},
-%   L^{\theta'}\rangle$ as follows. Let $G_1 := \{g_{\rank, \vec{c}} : \vec{c}
-%   \in [n]^k\}$ and $G_2 : = \{ g_{R_{\phi}, \vec{a}, \vec{b}, \vec{c}} :
-%   \vec{a} \in [n]^{k_1}, \vec{b} \in [n]^{k_2}, \vec{c} \in [n]^{k}\}$.
-
-%   \begin{itemize}
-%     \setlength\itemsep{0mm}
-%   \item Let $G^{\theta'} := G_1 \uplus G_2$,
-%   \item $\Omega^{\theta'}$ be an injection from $[n]^k$ to $G'$ defined by
-%     $\Omega^{\theta'}(\vec{c}) = g_{\rank, \vec{c}}$,
-
-%   \item $\Sigma^{\theta'} (g) := rank^r_p$ if $g \in G_1$ and
-%     $\Sigma^{\theta'}(g) = R_\phi$ if $g \in G_2$,
-%   \item For each $(\vec{a}, \vec{b}, \vec{c}) \in [n]^{k_1 +k_2 + k}$ let
-%     $\Lambda^{\theta'} (\vec{a}, \vec{b}, \vec{c}) := g_{R_{\phi}, \vec{a},
-%     \vec{b}, \vec{c}}$, and
-
-%   \item For each gate $g_{\rank, \vec{a}} \in G_1$ let $L(g_{\rank, \vec{a}}):
-%     [n]^{k_1} \times [n]^{k_2} \rightarrow G^{\theta'}$ be defined by
-%     $L(g_{\rank, \vec{c}})(\vec{a}, \vec{b}) := g_{R_\phi, \vec{a}, \vec{b},
-%     \vec{c}}$ for each $\vec{a} \in [n]^{k_1}$ and $\vec{b} \in [n]^{k_2}$.
-%   \end{itemize}
-
-%   It is easy to see that both $C^{\theta'}_n$ (and $C^{\phi}_n$) are symmetric
-%   rank-circuits with unique labels. Let $R$ be a relation symbol in $\tau$.
-%   Let $D^{\theta}_n := \op{compose}(C^{\theta'}_n, (C^{\phi}_n), (R_\phi),
-%   R)$. Let $H$ consist of all non-output gates in $D^{\theta}_n$. From the
-%   inductive hypothesis all gates in $H$ have unique labels. Let $C^{\theta}_n
-%   := \op{make-injective-all}(\op{merge-all}(D^{\theta}_n, H))$.
-
-%   Since $C^{\theta'}_n$ and $C^{\phi}_n$ are symmetric, have unique labels,
-%   and the input tuples of relations and circuits are singletons, it follows
-%   that $D^{\theta}_n$ is a symmetric rank-circuit with unique labels. It can
-%   be shown that the construction of $C^{\theta}_n$ from the natural number $n$
-%   can be implemented as an algorithm running in time polynomial in $n$. The
-%   construction ensures that the circuit family $(C^{\theta}_n)_{n \in \nats}$
-%   computes the same query as the one defined by $\theta(\vec{x})$.
-
-%   It remains only to note that any atomic formula of $\FPR[\tau]$ is trivially
-%   matrix-circuit-translatable. The result thus follows.
-% \end{proof}
-
-% \langle G', \Omega', \Sigma', \Lambda', L'\rangle$, where $R$ is a $(k_1 + k_2
-% +k)$-arity relation symbol. Let $G_1' := \{g_{\rank, \vec{c}} : \vec{c} \in
-% [n]^k\}$ and $G_2' : = \{ g_{R, \vec{a}, \vec{b}, \vec{c}} : \vec{a} \in
-% [n]^{k_1}, \vec{b} \in [n]^{k_2}, \vec{c} \in [n]^{k}\}$.
-
-% \begin{itemize}
-%   \setlength\itemsep{0mm}
-% \item Let $G' := G_1' \uplus G_2'$,
-% \item $\Omega'$ be an injection from $[n]^k$ to $G'$ defined by
-%   $\Omega'(\vec{c}) = g_{\rank, \vec{c}}$,
-
-% \item $\Sigma' (g) := rank^r_p$ if $g \in G_1'$ and $\Sigma'(g) = R$ if $g \in
-%   G_2'$,
-% \item For each $(\vec{a}, \vec{b}, \vec{c}) \in [n]^{k_1 +k_2 + k}$ let
-%   $\Lambda' (\vec{a}, \vec{b}, \vec{c}) := g_{R, \vec{a}, \vec{b}, \vec{c}}$,
-%   and
-
-% \item For each gate $g_{\rank, \vec{a}} \in G_1'$ let $L(g_{\rank, \vec{a}}):
-%   [n]^{k_1} \times [n]^{k_2} \rightarrow G'$ be defined by $L(g_{\rank,
-%   \vec{c}})(\vec{a}, \vec{b}) := g_{R, \vec{a}, \vec{b}, \vec{c}}$ for each
-%   $\vec{a} \in [n]^{k_1}$ and $\vec{b} \in [n]^{k_2}$.
-
-% \end{itemize}
-% Let $C^{\theta}_n$ be the result of `gluing' $C^{\phi}_n$ into $C'$.
-
-% It is easy to see that both $C'$ and $C^{\phi}_n$ are symmetric rank-circuits
-% with unique labels. Thus $C^{\theta}_n$ is a symmetric rank-circuit with
-% unique labels. The construction of $C'$, and hence $C^{\theta}_n$, can be
-% implemented so as to run in time polynomial in $n$. The construction ensures
-% that the circuit family $(C^{\theta}_n)_{n \in \nats}$ computes the same query
-% as the one defined by $\theta(\vec{x})$.
-
-% It remains only to note that any atomic formula of $\FPR[\tau]$ is trivially
-% circuit-translatable. The result thus follows.
-% \end{proof}
-
-% such that for any structure $\mathcal{A}$ of size $n$ and an assignment $$ to
-% the tuple of variables $\vec{x}$
-
-% is symmetric and has unique labels.
-
-% an equality between two numerical terms or an application of the
-% least-fixed-point operator,
-
-% it follows from Lemma \ref{}, that the syntactic equivalence relation on $G_1
-% \uplus G_2$ can be efficiently computed.
-
-% Note that the construction guarantees that $C^{\theta}_n$ is symmetric.
-% Moreover, since the only gates in $C^{\theta}_n$ are either output gates or
-% gates
-
-% Suppose $\theta(\vec{x})$ is of the form $\phi_1(\vec{x}) \land
-% \phi_2(\vec{x})$, $\phi_1(\vec{x})\lor \phi_2(\vec{x})$, $\neg \phi(\vec{x})$,
-% $\thr_k(y).\phi(\vec{x}, y)$, $\forall y. \phi (\vec{x}, y)$, $\exists y. \phi
-% (\vec{x}, y)$, an equality between two numerical terms or an application of
-% the least-fixed-point operator, and each of these sub-formulas is
-% $(\mathbb{B}, \tau)$-circuit-translatable} then $\theta(\vec{x})$ is
-% $(\mathbb{B}, \tau)$-circuit-translatable}. This follows from the following
-% construction. Let $n \in \nats$. We take derive the formula $\theta'(\vec{x})$
-% from $\theta(\vec{x})$ by replacing each sub-formula $\phi(\vec{z})$ with the
-% formula $R_\phi(\vec{z})$ (adding in some new relational symbol $R_\phi$). We
-% may then translate $\theta'(\vec{x})$ into a $P$-uniform family of symmetric
-% circuits with threshold and unique labels $(C^{\theta'}_n)_{n \in \nats}$. For
-% each $n$ we then replace the relational gates in $C^{\theta'}_n$ labelled by
-% $R_\phi$ with the circuit $C^{\phi}_n$ (that is, we add in the entire circuit
-% $C^\phi_n$ and replace each relational gate $g$ labelled by $R_\phi$ such that
-% $\vec{a}:= \Lambda(\vec{a})$ with with the output gates of $C^{\phi}_n$ such
-% that if $g$ is a relational gate computing $R_\phi(\vec{a})$ then $g$ is
-% replaced by the gate $\Omega^{-1}(\vec{a})$ in $C^{\phi}_n$). We call this new
-% circuit $C^\theta_n$. It is easy to see that this circuit is symmetric. To see
-% that it has unique labels, notice that we need only check
-
-% , if $L;$ $L'(g) := L(g)$ for all $g \in G' \cap G$ and for all $g \in H$
-% $L'(H) := L(g)$ if $g \in H$
-
-% \begin{lem}
-%   We say a
-% \end{lem}
-
-% We should like to argue that for any $\theta(\vec{x}) \in \FPR[\tau]$ if every
-% sub-formula of $\theta(\vec{x})$ is $(\mathbb_{\mat}, \tau)$-circuit
-% translatable then $\theta(\vec{x})$ is $(\mathbb_{\mat}, \tau)$-circuit
-% translatable. The existence of the desired translation then follows by
-% induction on the structure of the formula.
-
-% It is easy to see that if $\theta(\vec{x})$ is of the form $\phi_1(\vec{x})
-% \land \phi_2(\vec{x})$, $\phi_1(\vec{x})\lor \phi_2(\vec{x})$, $\neg
-% \phi(\vec{x})$, $\thr_k(y).\phi(\vec{x}, y)$, $\forall y. \phi (\vec{x}, y)$,
-% $\exists y. \phi (\vec{x}, y)$, an equality between two numerical terms or an
-% application of the least-fixed-point operator, and each of these sub-formulas
-% is $(\mathbb{B}, \tau)$-circuit-translatable} then $\theta(\vec{x})$ is
-% $(\mathbb{B}, \tau)$-circuit-translatable}. This follows from the following
-% construction. Let $n \in \nats$. We take derive the formula $\theta'(\vec{x})$
-% from $\theta(\vec{x})$ by replacing each sub-formula $\phi(\vec{z})$ with the
-% formula $R_\phi(\vec{z})$ (adding in some new relational symbol $R_\phi$). We
-% may then translate $\theta'(\vec{x})$ into a $P$-uniform family of symmetric
-% circuits with threshold and unique labels $(C^{\theta'}_n)_{n \in \nats}$. For
-% each $n$ we then replace the relational gates in $C^{\theta'}_n$ labelled by
-% $R_\phi$ with the circuit $C^{\phi}_n$ (that is, we add in the entire circuit
-% $C^\phi_n$ and replace each relational gate $g$ labelled by $R_\phi$ such that
-% $\vec{a}:= \Lambda(\vec{a})$ with with the output gates of $C^{\phi}_n$ such
-% that if $g$ is a relational gate computing $R_\phi(\vec{a})$ then $g$ is
-% replaced by the gate $\Omega^{-1}(\vec{a})$ in $C^{\phi}_n$). We call this new
-% circuit $C^\theta_n$. It is easy to see that this circuit is symmetric. To see
-% that it has unique labels, notice that we need only check
-
-% We solve this problem completely for one case and argue that the other cases
-% follow similarly. Suppose $\theta (\vec{x}) = \phi_1(\vec{x}) \land
-% \phi_2(\vec{x})$. We now describe an algorithm that takes in $n\in \nats$ and
-% outputs a formula $C^\theta_n$ with the required properties. We first
-% introduce two relation symbols $R_{\phi_1}$ and $R_{\phi_2}$ not in $\tau$ and
-% with arity $\vert\vec{x}\vert$. We define $\theta' (\vec{x}) =
-% R_{\phi_1}(\vec{x}) \land R_{\phi_2}(\vec{x})$ and compute the associated
-% symmetric threshold circuit with unique labels $C^{\theta'}_n$. Similarly, for
-% each $i\ \in \{1,2\}$ we may compute the symmetric $(\mathbb{B},
-% \tau)$-circuit with unique labels corresponding to $\phi_i$ that takes in
-% inputs of size $n$, $C^{\phi_i}_n = \langle G_i, \Omega_i, \Sigma_i Lambda_i,
-% L_i \rangle$ algorithms given by the inductive hypothesis. We then construct
-% $C^{\theta}_n$ by inserting into $C^{\theta'}_n$ the circuits $C^{\phi_1}_n$
-% and $C^{\phi_2}_n$ (that is, taking a disjoint union of the sets of gates and
-% the functions that define each circuit -- with the exception of $\Omega$ which
-% is specified by $C^{\theta'}_n$ alone). Then for all $i \in \{1,2\}$ and each
-% relational gate $g$ in $C^{\theta}_n$ such that $\Sigma(g) = R_{\phi_i}$ we
-% replace $g$ with $\Omega_i(\Lambda_i(g))$. Since $C^{\phi_1}_n$ and
-% $C^{\phi_2}_n$ have unique labels, it follows from Lemma \ref{} that we can
-% efficiently decide if any two gates $g_1, g_2 \in G_1 \uplus G_2$ are
-% syntactical equivalent. For each pair of gates $g_1, g_2$ in the range of
-% $\Omega_1 \uplus \Omega_2$ we check if $g_1 \equiv g_2$, and if so we merge
-% them.
-
-% The resultant circuit $C^{\theta}_n$ is clearly a symmetric $(\mathbb{B},
-% \tau)-circuit$-circuit. Moreover, it is easy to see that if all pairs of gates
-% in the range of $\Omega_1 \uplus Omega_2$ are not syntactical equivalent $g$
-% is a gate such that $h_1, h_2 \in H_g$ are syntactically equivalent then . it
-% has unique labels (as the only point where two input gates could be equivalent
-
-% we can from Lemma \ref{} that we can efficiently decide if two any two gates
-% from the union of these circuits are syntactical equivalent. If any of their
-% output gates are syntactically equivalent, merge these gates. This new circuit
-% has disjoint
-
-% we replace the relational gate $g$ in $C^{\theta'}_n$ such that $\Sigma(g) =
-% R_\phi$ and $\Lambda(g) = \vec{a}$ with the circuit $C^\phi_n$ $\vec{a}$, an
-% $\arty(R_\pi)$ each relational gate $R_\phi(\vec{a})$ in the circuit
-% $C^{\theta'}_n$
-
-% It remains to show that for any $k \in \nats$ and formula $\phi \in
-% \FPR[\tau]$ such that $\phi$ formula of the form $\theta (\vec{z}): = [rank
-% (\vec{x}, \vec {\nu} \leq \vec{t}, \vec{y}\vec{\mu} \leq \vec{s}, \pi \leq r).
-% \phi(\vec{x}, \vec{nu}, \vec{y}, \vec(mu), \vec{s}, \vec{z})] \leq k$ there is
-% an equivalent $P$-uniform family of symmetric rank-circuits with unique labels
-% $(C_n)_{n \in \nats}$ that compute the same query as $\theta$.
-
-% \begin{lem}
-%   Let $\tau$ be a relational vocabulary and let $\phi(\vec{x})$ be a formula
-%   of $\FPR[\tau]$. There is an algorithm that takes as input a natural number
-%   $n$ and outputs a formula $\phi_n$ such that $\phi_n$ contains no rank
-%   operators or counting terms and for any $\tau$-structure $\mathcal{A}$ of
-%   size $n$ and $\vert \vec{x} \vert$-tuple of elements $\vec{a}$ from the
-%   universe of $\mathcal{A}$, $\mathcal{A}\models \phi[\vec{a}]$ if, and only
-%   if, $\mathcal{A}\models \phi_n[\vec{a}]$. Moreover, this algorithm runs in
-%   time polynomial in $n$.
-% \end{lem}
-
-% \begin{thm}
-%   Let $\tau$ be a relational vocabulary and let $\phi$ be a formula of
-%   $\FPR[\tau]$. There is an algorithm that takes as input a natural number $n$
-%   and outputs a symmetric matrix-circuit $C_n$. This algorithm runs in time
-%   polynomial in $n$. Moreover, the query computed by the circuit family
-%   $(C_n)_{n \in \nats}$ and the query defined by the formula $\phi$ are equal.
-% \end{thm}
-% \begin{proof}
-%   We describe a transformation inductively on the structure of the formula.
-%   This procedure can then be implemented algorithmically using recursion.
-
-%   If $\phi(\vec{a})$ is an atomic formula
-
-% \end{proof}
-
-% We define this transformation by recursion on the structure of the formula and
-% note that and note that such a transformation can be implemented so as to run
-% in time polynomial in $n$.
-
-% Let $\phi$ be a formula
-
-% \begin{thm}
-%   Formulas of $\FPR$ can be translated into symmetric matrix-circuits
-% \end{thm}
-% \begin{proof}
-%   The idea here is to do exactly the same thing as for FPC formulas except
-%   when we arrive at a rank quantifier we `tag' each formula with
-% \end{proof}

### 2018-02-10 sections/background.tex
February 5 2018
Feb 10

--- 2017-08-03 sections/background.tex
@@
 \subsection{Logic and Structures}
-A \emph{relational vocabulary} (usually denoted by $\tau$) is a finite sequence
-of relation symbols $(R_1, \ldots, R_k)$, such that for all $i \in [k]$, $R_i$
-has arity of $r_i \in \nats$. All vocabularies discussed in this paper are
-relational vocabularies. A \emph{many-sorted vocabulary} is a tuple of the form
-$(R, S, \nu)$, where $R$ is a relational vocabulary, $S$ is a finite sequence of
-\emph{sort} symbols $(s_1, \ldots s_p)$, and $\nu$ is a function that assigns to
-each $R_i \in R$ a tuple $\nu(R_i) := (s^i_1, \ldots, s^i_{r_i})$, where for
-each $j \in [r_i]$, $s^i_j \in S$. We call $\nu$ the \emph{\type function} and
-$\nu(R_i)$ the \emph(type) of $R_i$.
+A \emph{relational vocabulary} (otherwise just called a \emph{vocabulary} or
+\emph{signature}) is a finite sequence of relation symbols $(R_1, \ldots, R_k)$,
+each of which has a fixed \emph{arity}, denoted by $\arty(R_i) \in \nats$. We
+often let $r_i \in \nats$ denote the arity of the relation symbol $R_i$. A
+\emph{many-sorted vocabulary} is a tuple of the form $(R, S, \nu)$, where $R$ is
+a relational vocabulary, $S$ is a finite sequence of \emph{sort} symbols $(s_1,
+\ldots s_p)$, and $\nu$ is a function that assigns to each $R_i \in R$ a tuple
+$\nu(R_i) := (s^i_1, \ldots, s^i_{r_i})$, where for each $j \in [r_i]$, $s^i_j
+\in S$. We call $\nu$ the \emph{\type function} and $\nu(R_i)$ the \emph{type}
+of $R_i$. We notice that a relational vocabulary can be thought of as a
+single-sorted vocabulary, i.e. a many-sorted vocabulary where the set of sorts
+is a singleton. As such, if $\tau := (R, S, \nu)$ is single-sorted we identify
+$\tau$ with $R$.
 
-Let $\tau$ be a many-sorted vocabulary. A \emph{$\tau$-structure} $\mathcal{A}$
-is a tuple $(U , R^{\mathcal{A}}_1 , \ldots , R^{\mathcal{A}}_k )$, where $U$,
-the \emph{universe} of $\mathcal{A}$, is a disjoint union of non-empty sets
-$U_{s_j}$, one for each sort symbol $s_j \in S$. For each $i \in [k]$, where
-$\nu(R_i) = (s^i_1 , \ldots , s^i_{r_i})$, $R^{\mathcal{A}}_i \subseteq
-U_{s^i_1} \times \ldots \times U_{s^i_{r_i}}$. The elements of $U$ are called
-the elements of $\mathcal{A}$. If $tau$ is a relational vocabulary, a
-$\tau$-structure is a structure over $(\tau, S, \nu)$, where $S$ is a singleton
-and $\nu$ is the only allowable type function. The size of a structure
-$\mathcal{A}$, denoted by $\vert \mathcal{A} \vert$, is the cardinality of its
-universe. The sorted-size of a structure is a vector $\vec{n} := (n_{s_1},
-\ldots , n_{s_p}) \in \mathbb{N}^{S}$ such that $\vert U_{s} \vert = n_{s}$ for
-all $s \in S$. If $a \in U_{s_j}$ for some sort $s_j \in S$, we say that $a$ has
-sort $s_j$. We often use $A$ to denote the universe of a structure
-$\mathcal{A}$. All structures in this paper are finite unless stated otherwise.
+Let $\tau := (R, S, \nu)$ be a many-sorted vocabulary, where $R = (R_1, \ldots,
+R_k)$ and $S = (s_1, \ldots , s_p)$ A \emph{$\tau$-structure} $\mathcal{A}$ is a
+tuple $(U , R^{\mathcal{A}}_1 , \ldots , R^{\mathcal{A}}_k)$ where $U =
+\uplus_{s \in S } U_{s}$ a disjoint union of non-empty sets, and is called the
+\emph{universe} of $\mathcal{A}$, and for all $i \in [k]$, $R^{\mathcal{A}}_i
+\subseteq R^{\mathcal{A}}_i \subseteq U_{s^i_1} \times \ldots \times
+U_{s^i_{r_i}}$, where $(s^i_1 , \ldots , s^i_{r_i}) = \nu (R_i)$. The size of
+$\mathcal{A}$, denoted by $\vert \mathcal{A} \vert$ is the cardinality of its
+universe. The \emph{sorted-size} of $\mathcal{A}$ is a vector $\vec{n} :=
+(n_{s_1}, \ldots , n_{s_p}) \in \mathbb{N}^{p}$ such that $\vert U_{s_i} \vert =
+n_{s_i}$ for all $i \in [p]$. We say $a \in U$ has \emph{sort} $s \in S$ if $a
+\in U_s$.
 
-\begin{definition}
-  Let $S = \{s_1, \ldots , s_p\}$ be a set of sort symbols and $A = A_{s_1}
-  \sqcup \ldots \sqcup A_{s_p}$ and $B = B_{s_1}\dotcup \ldots \dotcup
-  B_{s_p}$ be disjoint unions of non-empty sets. A \emph{sorted bijection}
-  between $A$ and $B$ is a bijection $f: A \rightarrow B$ such that $f (A_s) =
-  B_s$ for all $s \in S$.
-\end{definition}
+All structures in this paper are assumed to have finite size unless stated
+otherwise. For more details on these basic definitions please
+see~\cite{Gradel:2005}, \cite{immerman1999descriptive},
+or~\cite{grohe2017descriptive}.
 
-If $\tau = (R, S, \nu)$ is a single-sorted vocabulary then we abuse notation and
-identify $\tau$ with $R$.
+% \begin{definition}
+%   Let $S = \{s_1, \ldots , s_p\}$ be a set of sort symbols and $A = A_{s_1}
+%   \uplus \ldots \uplus A_{s_p}$ and $B = B_{s_1}\uplus \ldots \uplus B_{s_p}$
+%   be disjoint unions of non-empty sets. A \emph{sorted bijection} between $A$
+%   and $B$ is a bijection $f: A \rightarrow B$ such that $f (A_s) = B_s$ for
+%   all $s \in S$.
+% \end{definition}
 
-\subsection{First Order, Fixed-Point and Counting}
-Let $\FO(\tau)$ denote \emph{first order logic} with respect to the vocabulary
-$\tau$. \emph{Fixed-Point Logic} is the extension of $\FO(\tau)$ with an
-inflationary fixed-point operator (see \cite{} for details). For logic
-$\mathcal{L}$, a formula $\phi \in \mathcal{L}(\tau)$, $x$ a $k$-tuple of
-variables, $\mathcal{A}$ a (finite) structure, and $a \in U^k$, we write the
-formulas $phi (x)$ to denote that the free variables of $\phi$ are among and we
-write $\mathcal{A} \models_{\mathcal{L}} \phi[a]$ iff the the formula $\phi$ is
-true in $\mathcal{A}$ with respect to $\mathcal{L}$ with the variables $x$
-assigned to $a$. The context often makes the logic obvious, and in that case we
-usually omit the subscript.
+\subsection{First Order and Fixed-Point Logic}
+Let $L$ be a logic and $\tau$ be a vocabulary, we let $L[\tau]$ denote the set
+of all $\tau$-formulas of $L$ (i.e. the set of all $L$-formulas with respect to
+$\tau$). Let $\FO[\tau]$ denote \emph{first-order logic} with respect to the
+vocabulary $\tau$. A formula in $\FO[\tau]$ is formed from atomic formulas, each
+formed using variables from some countable sequence of (first-order) variable
+symbols $(x, y, \ldots)$, the relation symbols in $\tau$, and the equality
+symbol $=$, and then closing the set of atomic formulas under the Boolean
+connectives, negation, and universal and existential quantification (i.e.
+$\land$, $\lor$, $\neg$, $\forall$, and $\exists$).
 
-We also recall the definition of \emph{fixed-point logic with counting} $\FPC$,
-an extension $\FP$ with counting terms (see \cite{grohe2017descriptive} for
-details). Variables and terms in $\FPC$ must be of one of two sorts, vertex or
-numeric, where vertex variables are assigned to elements of the universe the
-structure and numeric variables to the elements of $\mathbb{N}$. All atomic
-formula as in $\FP$ are formulas of $\FPC$ (using only vertex sort variables).
-Let $\phi(x)$ be a formula of $\FPC$ with free variables $x$, then $\# x \phi$
-is a numeric, with the term's semantics being the number of elements satisfying
-$\phi$. All numeric variables as well as the symbols 0 and 1 are numeric terms
-with the expected semantics. If $\mu_1 and \mu_2$ are numeric terms, then $\mu_1
-+ \mu_2$ and $\mu_1 * \mu_2$ are numeric terms with the expected semantics.
-Moreover, if $\mu_1$ and $\mu_2$ are numeric terms, then $\mu_1 < \mu_2$ and
-$\mu_1 = \mu_2$ are formulas with the expected semantics. If $\vec{x}$ is a
-$k$-tuple of numeric variables and $\vec{\mu}$ is a $k$-tuple of closed numeric
-term (i.e. ones without any free variables) then $\exists \vec{x} \leq \vec{\mu}
-\phi(\vec{x})$ and $\forall \vec{x} \leq \vec{mu} \phi(\vec{x})$ are formulas.
-In the existential case, for a $\tau$-structure $\mathcal{A}$, we say
-$\mathcal{A} \models \exists \vec{x} \leq \vec{\mu} \phi(\vec{x})$ iff there
-exists $\vec{n} \in [\mu^{\mathcal{A}}_1] \times \ldots \times
-[\mu^{\mathcal{A}}_2]$, such that $phi^{\mathcal{A}}$ holds for the assignment
-$\vec{x} \mapsto \vec{n}$. The semantics of the universal case follows
-similarly. The application of the fixed-point operator (but now with the
-relation variables possibly being of mixed type), and Boolean connectives
-similarly define formulas as in $\FP$. The semantics of these formulas is also
-similarly defined.
+Let $\FP[\tau]$ denote \emph{fixed-point logic} with respect to $\tau$. The
+logic $\FP$ is an extension of $\FO$ by an inflationary fixed-point operator. In
+other words, $\FP[\tau]$ includes all formulas in $\FO[\tau]$, along with all
+formulas of the form $[\ifp_{V, \vec{x}}. \phi]$, where $V$ is a relation symbol
+not in $\tau$, $\phi \in \FO[\tau \cup \{V\}]$, and $\vec{x}$ is a sequence of
+variables of length $\arty(V)$. We assume the standard syntax and semantics for
+$\FO[\tau]$ and $\FP[\tau]$. For more detail on the syntax and semantics of
+these logics please see~\cite{grohe2017descriptive} and~\cite{GradelP15a}.
+
+Let $L$ be a logic and $\tau$ a vocabulary. For $\phi \in L[\tau]$ and a
+sequence of variables $\vec{x}$, we write $\phi(vec{x})$ if the free variables
+in $\phi$ are among those in $\vec{x}$. Suppose $\vec{x} = (x_1, \ldots , x_k)$,
+and let $\mathcal{A}$ be a $\tau$-structure with universe $U$, and let $\vec{a}
+\in U^k$. We write $\mathcal{A} \models_L \phi[\vec{a}]$ if, and only if, $\phi$
+is true in $\mathcal{A}$ with respect to $L$ where for all $i \in [k]$ each
+variable $x_i$ is assigned to $a_i$. If the logic is obvious from context we
+omit the subscript and just write $\mathcal{A} \models \phi[\vec{a}]$.
+
+\subsection{Fixed-Point with Counting}
+Let $\FPC[\tau]$ denote \emph{fixed-point logic with counting} with respect to
+the vocabulary $\tau$. The logic $\FPC$ is an extension of $\FP$ that includes a
+counting operator that allows the logic to determine the size of a definable
+set, as well as other mechanisms for reasoning about quantities. We now briefly
+describe the structure of a formula of $\FPC[\tau]$. In order to facilitate
+counting we define terms which are assigned to natural numbers. Every
+first-order variable is assigned a type, and so each variable is either a
+\emph{vertex} or \emph{number} variable. Vertex variables are assigned to
+elements of the universe of the structure, and play a similar role to the
+variables that appear in formulas in $\FO[\tau]$ or $\FP[\tau]$. Number
+variables are assigned to elements of $\nats$. We usually use Latin letters
+(e.g. $x, y, z, \ldots$) to denote vertex variables and Greek letters (e.g.
+$\mu, \nu, \epsilon, \ldots$) to denote number variables. All atomic formulas in
+$\FP[\tau]$ are atomic formulas in $\FPC[\tau]$. We say that $t$ is a
+\emph{number term} if $t$ a number variable or if $t$ is an application of the
+\emph{counting operator}, i.e. $t = \#x. \phi(x)$, where $\phi \in \FPC[\tau]$
+and $x$ is a vertex variable free in $\phi$. If $t_1$ and $t_2$ are number terms
+then $t_1 \leq t_2$ and $t_1 = t_2$ are atomic formulas. The formulas of $\FPC$
+are then formed by closing the set of atomic formulas under the usual Boolean
+connectives, the first-order quantifiers (for vertex variables), and the
+inflationary fixed-point operator. The second-order variables, such as those
+that appear in an application of the fixed-point operator, are allowed to have
+mixed-type, i.e. we associate with a second-order variable $R$ a type $(k, l)
+\in \nats^2$ intended to mean that $R$ is assigned to a subset of $U^k \times
+\nats^l$.
+
+In order to ensure that the data complexity of $\FPC$ is in polynomial time, we
+only allow bounded quantification when using number variables. In other words,
+if $Q \in \{\forall, \exists \}$, $\phi \in \FPC[\tau]$, $\mu$ is a number
+variable free in $\phi$, and $t$ is a number term, then $Q \mu \leq t . \phi$ is
+a formula of $\FPC[\tau]$. Similarly, if $\phi$ is a number term then $\# \mu
+\leq t .\phi$ is a number term in $\FPC[\tau]$.
+
+If $\mathcal{A}$ is a $\tau$-structure with universe $U$, the counting term
+$\#x. \phi(x)$ evaluates to $\vert \{a \in U : \mathcal{A} \models \phi[a]\}
+\vert$ in $\mathcal{A}$, assuming a fixed assignment to the other free variables
+in $\phi$. The intended semantics for bounded quantification is that the
+variable may only be assigned to a value at most equal to the the evaluation of
+the number term bounding the variable. The semantics of the $=$ and $\leq$
+symbols are defined for number terms in the obvious manner. For a more detailed
+description of the syntax and semantics of $\FPC$ please
+see~\cite{grohe2017descriptive} or the introduction of~\cite{GradelP15a}.
+
+It is possible to define the usual arithmetic operations on number terms using
+the constructs thus far introduced. We do not show how to explicitly define
+these operations in $\FPC$, but we do make use of them in this paper. Please
+see~\cite{grohe2017descriptive} for the explicit constructions.
+
+Let $\FOC[\tau]$ denote \emph{first-order logic with counting} with respect to
+the vocabulary $\tau$, and be the set of all formulas in $\FPC[\tau]$ that do
+not contain the an application of the fixed-point operator.
+
+% We also recall the definition of \emph{fixed-point logic with counting}
+% $\FPC$, an extension $\FP$ with counting terms (see
+% \cite{grohe2017descriptive} for details). Variables and terms in $\FPC$ must
+% be of one of two sorts, vertex or numeric, where vertex variables are assigned
+% to elements of the universe the structure and numeric variables to the
+% elements of $\mathbb{N}$. All atomic formula as in $\FP$ are formulas of
+% $\FPC$ (using only vertex sort variables). Let $\phi(x)$ be a formula of
+% $\FPC$ with free variables $x$, then $\# x \phi$ is a numeric, with the term's
+% semantics being the number of elements satisfying $\phi$. All numeric
+% variables as well as the symbols 0 and 1 are numeric terms with the expected
+% semantics. If $\mu_1 and \mu_2$ are numeric terms, then $\mu_1 + \mu_2$ and
+% $\mu_1 * \mu_2$ are numeric terms with the expected semantics. Moreover, if
+% $\mu_1$ and $\mu_2$ are numeric terms, then $\mu_1 < \mu_2$ and $\mu_1 =
+% \mu_2$ are formulas with the expected semantics. If $\vec{x}$ is a $k$-tuple
+% of numeric variables and $\vec{\mu}$ is a $k$-tuple of closed numeric term
+% (i.e. ones without any free variables) then $\exists \vec{x} \leq \vec{\mu}
+% \phi(\vec{x})$ and $\forall \vec{x} \leq \vec{mu} \phi(\vec{x})$ are formulas.
+% In the existential case, for a $\tau$-structure $\mathcal{A}$, we say
+% $\mathcal{A} \models \exists \vec{x} \leq \vec{\mu} \phi(\vec{x})$ iff there
+% exists $\vec{n} \in [\mu^{\mathcal{A}}_1] \times \ldots \times
+% [\mu^{\mathcal{A}}_2]$, such that $phi^{\mathcal{A}}$ holds for the assignment
+% $\vec{x} \mapsto \vec{n}$. The semantics of the universal case follows
+% similarly. The application of the fixed-point operator (but now with the
+% relation variables possibly being of mixed type), and Boolean connectives
+% similarly define formulas as in $\FP$. The semantics of these formulas is also
+% similarly defined.
 
@@
 \subsection{Rank Logic}
-In this paper we use the definition of $\FPR$ given by Grad\"{e}l and Pakusa
-\cite{Gradel2015}, an strictly more expressive extension of the rank logic
-introduced by Dawar et. al. cite{Dawar09logicswith}. We briefly define this
-logic here. For more detail please see \cite{Gradel2015}. $\FPR$ is an extension
-of $\FPC$ with rank operators, which we now define.
+Let $\FPR[\tau]$ denote \emph{fixed-point logic with rank} (or just \emph{rank
+  logic}) with respect to the vocabulary $\tau$. The logic $\FPR$ is an
+extension of $\FP$ to include an operator that decides the rank of a definable
+matrix over a finite field, as well as other mechanisms for reasoning about
+quantity. In this way we can think of the structure of a formula of $\FPR$ as
+being similar to that of $\FPC$, with rank operators replacing counting
+operators.
 
-Let $\phi (\vec{x}, \vec {\nu} \leq \vec{t}, \vec{y}\vec{\mu} \leq \vec{s})$ be
-a numeric term, where $\vec{x}$ and $\vec{y}$ are tuples of variables ranging
-over the universe of the structure, $\vec{\nu}$ and $\vec{\mu}$ are tuples of
-numeric variables , and $\vec{s}$ and $\vec{t}$ are tuples of closed numeric
-terms that bound the range of $\vec{\nu}$ and $\vec{\mu}$ respectively. Then let
-$\mathcal{A}$ be a structure and let $\mathbb{N}^{\leq\vec{t}} := \{\vec{n} \in
+We now briefly describe the structure of a formula in $\FPR[\tau]$. For more
+detail on the syntax and semantics of $\FPR$ please see~\cite{GradelP15a}
+and~\cite{Dawar09logicswith}. As in the case of $\FPC$, we suppose the
+first-order variable are assigned one of two types. We call the first type
+\emph{vertex variables} and the second \emph{number variables} variables. Vertex
+variables are assigned to elements of the universe and number variables are
+assigned to natural numbers. All atomic formulas in $\FP[\tau]$ are atomic
+formulas in $\FPC[\tau]$. We say that $t$ is a \emph{number term} if $t$ is a
+number variable or if $t$ is an application of the \emph{rank operator}, i.e. $t
+= [\rank (\vec{x}, \vec {\nu} \leq \vec{t}, \vec{y}\vec{\mu} \leq \vec{s}, \pi
+\leq \eta). \phi]$, where $\phi$ is a number term, $\vec{t}$ and $\vec{s}$ are
+tuples of number terms bounding the sequences of number variables $\vec{\mu}$
+and $\vec{\nu}$, and $\eta$ is a number term bounding the number variable $\pi$.
+If $t_1$ and $t_2$ are number terms then $t_1 \leq t_2$ and $t_1 = t_2$ are
+atomic formulas. The formulas of $\FPR$ are then formed by closing the set of
+atomic formulas under the usual Boolean connectives, the first-order
+quantifiers, and the inflationary fixed-point operator. As in the case of
+$\FPC$, the second-order variables may have mixed-type and we only allow bounded
+quantification for number variables. We note additionally that formulas can be
+treated as number terms that evaluate to zero or one.
+
+We now briefly explain the intended semantics of the rank operator. Let $\phi
+(\vec{x}, \vec {\nu}, \vec{y}\vec{\mu})$ be a number term, where $\vec{x}$ and
+$\vec{y}$ are tuples of vertex variables, $\vec{\nu}$ and $\vec{\mu}$ are tuples
+of number variables. Let and $\vec{s}$ and $\vec{t}$ be tuples of number terms
+that bound the ranges of $\vec{\nu}$ and $\vec{\mu}$, respectively. Let $\pi$ be
+a number variable and $r$ be a number term bounding the range of $\pi$. Let
+$\mathcal{A}$ be a structure with universe $A$, and suppose we have a given
+assignment to the all of the free variables appearing in $r$ and in the terms in
+$\vec{t}$ and $\vec{s}$. Let $\mathbb{N}^{\leq\vec{t}} := \{\vec{n} \in
 \mathbb{N}^{\vert \vec{v} \vert}: n_i \leq t^{\mathcal{A}}_i\}$, and let
@@
   \vert} \times \mathbb{N}^{\leq \vec{t}}$ and $J := A^{\vert \vec{y} \vert}
-\times \mathbb{N}^{\leq \vec{s}}$ Then let $M^{\mathcal{A}}_\phi : I \times J
+\times \mathbb{N}^{\leq \vec{s}}$. Let $M^{\mathcal{A}}_\phi : I \times J
 \rightarrow \mathbb{N}$ be defined by $M^{\mathcal{A}}_\phi (\vec{a}\vec{n},
-\vec{b}\vec{m}):= \phi^{\mathcal{A}}(\vec{a}\vec{n},\vec{b}\vec{m})$.
+\vec{b}\vec{m}):= \phi^{\mathcal{A}}(\vec{a}\vec{n},\vec{b}\vec{m})$. For the
+structure $\mathcal{A}$ and assignment $\pi \mapsto p$, for $p \leq r^{A}$ prime,
+$[\rank (\vec{x}, \vec {\nu} \leq \vec{t}, \vec{y}\vec{\mu} \leq \vec{s}, \pi
+\leq r). \phi]$ evaluates to the rank of $M^{\mathcal{A}}_\phi$ mod $p$, where
+the matrix is understood to have entries in $\mathbb{F}_p$.
 
-The rank operator is then defined as $[rk (\vec{x}, \vec {\nu} \leq \vec{t},
-\vec{y}\vec{\mu} \leq \vec{s}, \pi \leq r). \phi]$, where $\pi$ is a numeric
-variable and $r$ is a closed numeric term that bounds $\pi$. The value of the
-rank term for a structure $\mathcal{A}$ and an assignment $\pi \mapsto p$, where
-$p$ is prime, is given by the rank  of $M^{\mathcal{A}}_\phi$ mod $p$, where the
-matrix is understood to have entries in $\mathbb{F}_p$.
+We should note that there are two different of rank logics defined in the
+literature. The first, introduced by Dawar et al.~\cite{Dawar09logicswith},
+differs from the one defined above in that it does not take the characteristic
+of the field as a parameter, instead including a different operator for every
+prime field over which compute rank. It was shown by Grad{\"e}l and
+Pakusa~\cite{GradelP15a} that this rank logic does not capture $\PT$. Grad{\"e}l
+and Pakusa introduced the rank logic we have presented above and showed that
+this logic, with the uniform rank operator, is strictly more expressive then the
+rank logic introduced by Dawar et al. For this reason when we refer to rank
+logic we are always referring to the rank logic introduced by Grad{\"e}l and
+Pakusa~\cite{GradelP15a}.
 
-\subsection{Circuits}
-A \emph{Boolean circuit} $C$ defined over some basis $\mathbb{B}$ is a directed
-acyclic graph (DAG) with designated input gates $x_1, \ldots, x_n$, each with
-in-degree $0$, internal gates labelled by elements of $\mathbb{B}$, and a single
-designated output gate with out-degree 0. A Boolean basis consists either of a
-set of Boolean functions or a set of symbols which implicitly define a family of
-Boolean functions.
+We may also define an extension of first order logic by rank operators. Let
+$\FOR[\tau]$ denote \emph{first-order with rank} with respect to the vocabulary
+$\tau$, and be the set of formulas in $\FPR[\tau]$ that do not contain an
+application of the fixed-point operator.
 
-Let $C$ be a circuit with input gates $x_1, \ldots, x_n$ and output gate $g_o$.
-The evaluation of $C$ for an input $\vec{x}\in \{0,1\}^n$ proceeds inductively
-from the assignment of $\vec{x}$ to the input gates. with the internal and
-output gates evaluated in accordance with the element of the basis labelling
-that gate. We denote the evaluation of a gate $g$ in by $C[\vec{x}](g)$, with
-the out of the circuit then given by $C[\vec{x}](g_o)$. In this way $C$ computes
-a Boolean function of the form $f:\{0,1\}^n \rightarrow \{0,1\}$. It is easy to
-see that for any complete Basis and any Boolean function there is a circuit over
-that basis that computes the function.
+Let $\FPrk[\tau]$ denote \emph{fixed-point logic with rank quantifiers} with
+respect to the vocabulary $\tau$. This logic, first introduced by Dawar et
+al~\cite{Dawar09logicswith}, is an extension of fixed-point logic by \emph{rank
+  quantifiers}. For a prime $p$ and $r$ a natural number, a rank quantifier
+$\rank^r_p$ is defined such that $\rank^r_p\vec{x}\vec{y}. \phi$ is interpreted
+as $[\rank (\vec{x}, \vec{y}, \pi) . \phi] \leq t$, where $\pi$ is assigned to
+$p$ and $t$ evaluates to $r$. The arity of this quantifier is $\vert \vec{x}
+\vert + \vert \vert{y} \vert$. We thus have a rank quantifier for every prime
+$p$, natural number $r$ and arity $k$. Let $\mathcal{R}$ be the set of all such
+quantifiers. Let $\FPrk[\tau]$ be the closure of $\FP[\tau]$ under the
+quantifiers in $\mathcal{R}$.
 
-% It is worth noting that the input to a gate is an unstructured set, and as
-% such it is implicitly required that the label associated with that gate define
-% a \emph{symmetric function} (a function whose output depends on the number of
-% 1's in its input).
+We may also define an extension of first-order logic with rank quantifiers. Let
+$\FOrk[\tau]$ denote \emph{first-order with rank quantifiers} with respect to
+the vocabulary $\tau$, and be the set of all formulas in $\FPR[\tau]$ that do
+not contain an application of the fixed-point operator.
 
-There are many natural properties of a circuit.The \emph{size} of a circuit $C$,
-denoted by $\vert C \vert$ is the number of gates in the circuit. The
-\emph{depth} of a circuit is the length of the longest path from an input gate
-to the output gate. The \emph{width} of a circuit is the maximum size of a set
-of gates all the same distance from the input gates.
+For more detail on the syntax and semantics of these logics with rank
+quantifiers please see~\cite{Dawar09logicswith}. It is easy to see that $\FPrk
+\leq \FPR$ and $\FOrk \leq FOR$. In fact, Dawar et al.~\cite{Dawar09logicswith}
+shows that these inclusions are strict. Moreover, we note that $[\rank(\vec{x},
+\vec{y}). (\vec{x} = \vec{y}, \pi \leq r) \land \phi(\vec{x})]$ evaluates, for a
+structure $\mathcal{A}$ and any assignment $\pi \mapsto p$, to the number of
+assignments to $\vec{x}$ for which $\phi$ holds (i.e.\ $\vert \{\vec{a} \in
+U^{\vert \vec{x} \vert} : \mathcal{A} \models \phi[\vec{a}]\} \vert$). It
+follows that $\FPC \leq \FPR$ and $\FOC \leq \FOR$. Dawar et
+al.\cite{Dawar09logicswith} show that these inclusions are strict.
 
-We say a family of circuits $(C_n)_{\mathbb{N}}$ \emph{decides} a language $L
-\{0,1\}^{*} \rightarrow \{0,1\}$ if $C_n$ computes the same function as $L$
-restricted to inputs of size $n$. It is common to ask about the class of
-languages that a can be decided by circuit families with certain restrictions.
-The following restriction is of importance in this paper.
+\subsection{Group Theory}
+Let $X$ be a set, we write $\sym_X$ to denote the symmetric group on the set
+$X$. For $n \in \nats$ we write $\sym_n$ to abbreviate $\sym_{[n]}$. We assume
+the reader is familiar with the basic theory of group actions.
 
-Two Boolean bases often considered in this paper are $\mathbb{B}_{\std} = \{
-\neg , \wedge , \lor \}$ and $\mathbb{B}_\maj = \{ \maj \} \cup \mathbb{B}$,
-where $\neg, \wedge and \lor$ are the usual logical connectives and $\maj$ is
-the majority gate, where for a Boolean sequence $\vec{x}$, $\maj(\vec{x}) = 1$
-iff the number of $1$'s in $\vec{x}$ is greater than or equal to
-$\frac{\vert\vec{x}\vert}{2}$.
+Let $G$ be a group and let $H \leq G$. Let $X$ be a set on which a group action
+of $G$ is defined. This group action defines a natural action on
+$\mathcal{P}(X)$ (and hence $\mathcal{P}(\ldots(\mathcal{P}(X)))$) defined by
+$\sigma \cdot S := \{\sigma x : x \in S\}$ for $\sigma \in G$, $S \subseteq X$.
+Let $S \subseteq X$. We call $\stab_G(S) = \{\sigma in G : \forall x \in S \,
+\sigma x = x\}$ the \emph{stabiliser} of $S$ with respect to $G$. We call
+$\setstab_G(S) = \stab_G(\{S\}) = \{\sigma \in G : \sigma S = S\}$ the
+\emph{set-wise stabiliser} of $S$ with respect to $G$. We call $\orb_G(S) :=
+\{\sigma S : \sigma \in G\}$ the \emph{orbit} of $S$ with respect to $G$. If $S$
+is a singleton we omit the set bracers, e.g.\ we write $\orb_G(x)$ for
+$\orb_G(\{x\})$. If $G = \sym_n$ for some $n \in \nats$ we replace the subscript
+with the number $n$, e.g.\ we write $\orb_n(x)$ for $\orb_{\sym_n}(x)$. If the
+group $G$ is obvious from context we omit the subscript, e.g.\ we write
+$\orb(x)$ for $\orb_G(x)$.
+
+\subsection{Boolean Functions, Bases, and Circuits}
+A (finite) \emph{Boolean function} is a function of the form $f: \{0,1\}^X
+\rightarrow \{0,1\}$, for some finite index set $X$. We often take $X = [n]$,
+and think of $f$ as taking $n$-length strings as inputs. We call a Boolean
+function $f: \{0,1\}^X \rightarrow \{0,1\}$ \emph{symmetric} if for all $\sigma
+\in \sym_X$ and $\vec{a} \in \{0,1\}^X$, $f (\vec{a} \sigma) = f(\vec{a})$. It
+follows that a Boolean function is symmetric if, and only if, the output of the
+function is entirely determined by the number of ones in the input. We say a
+function $f : \{0,1\}^{*} \rightarrow \{0,1\}$ is \emph{symmetric} if its
+restriction to inputs of size $n$ is symmetric for all $n$.
+
+A \emph{Boolean basis} (or \emph{basis}) is a set of Boolean functions. We
+always denote a basis by $\BB$. It is common in the literature to define a basis
+using a finite sequence of functions $f_1, \ldots , f_k:\{0,1\}^* \rightarrow
+\{0,1\}$. We write $\BB = \{f_1, \ldots, f_k\}$ to denote the basis consisting
+of all Boolean functions $f^n_i : \{0,1\}^n \rightarrow \{0,1\}$ where $n \in
+\nats$, $i \in [k]$, and $f^n_i$ is the restriction of $f_i$ to strings of
+length $n$. We have $\AND, \OR, \NAND, \MAJ : \{0,1\}^* \rightarrow \{0,1\}$,
+where $\AND, \OR, \NAND$ are the usual (unbounded fan-in) logical operators, amd
+$\MAJ$ is the majority function. We write $\BS := \{\AND, \OR, \NOT\}$ to denote
+the \emph{standard basis} and $\BS := \BS \cup \{\MAJ\}$ to denote the
+\emph{majority basis}.
+
+Let $\BB$ be a basis. A \emph{Boolean circuit} $C$ defined over $\BB$ is a
+labelled directed acyclic graph (DAG) with designated input gates $x_1, \ldots,
+x_n$, each with in-degree $0$, internal gates labelled by elements of $\BB$, and
+a single internal gate with out-degree $0$ designated as the output gate. We say
+a circuit with $n$ input gates has \emph{order $n$}. Let $C$ be a Boolean
+circuit of order $n$ and let $\vec{a} := (a_1, \ldots, a_n) \in \{0,1\}^n$. The
+evaluation of $C$ for the input $\vec{a}$ is denoted by $C[\vec{a}]$ and is
+defined by induction on the structure of the circuit. We denote the evaluation
+of a gate $g$ in $C$ for the input $\vec{a}$ by $C[\vec{a}](g)$. If $g$ is an
+input gate, then $g = x_i$ and $C[\vec{a}](g) = a_i$. If $g$ is an internal gate
+then $g$ is labelled by a symbol denoting a Boolean operation, and
+$C[\vec{a}](g)$ is the result of applying that operation the string formed from
+the evaluations of those gates input to $g$. If $g$ is the output gate, let
+$C[\vec{a}] = C[\vec{a}](g)$.
+
+The \emph{size} of a circuit $C$, denoted by $\vert C \vert$ is the number of
+gates in the circuit. The \emph{depth} of a gate is the longest path from an
+input gate to that gate, and the \emph{depth} if the circuit is the depth of the
+output gate. The \emph{width} of a circuit is the maximum size of a set of gates
+with the same depth.
+
+If $C$ is a circuit of order $n$, then $C$ computes a Boolean function $f_C :
+\{0,1\}^n \rightarrow \{0,1\}$ defined by $f_C(\vec{a}) = C[\vec{a}]$. Let
+$(C_n)_{n \in \nats}$ be a family of circuits, where $C_n$ has order $n$. We say
+$(C_n)_{n \in \nats}$ \emph{decides} a language $L : \{0,1\}^{*} \rightarrow
+\{0,1\}$ if for all $\vec{a} \in \{0,1\}^{*}$, $C_{\vert \vec{a} \vert}
+[\vec{a}] = L(\vec{a})$.
 
@@
 
-Let $C$ be a circuit with the sets of gates $G$ and edge relation $W$. Let $g
-\in G$, we denote the \emph{children} or \emph{input gates} of $g$ by the set
-$H_g := \{h \in G : W(h,g)\}$.
+\subsection{Circuits for Structures}
+Anderson and Dawar~\cite{AndersonD17} define a circuit that takes as input an
+encoding of a finite relational structure. Let $\tau$ be a vocabulary, $\BB$ be
+a basis of symmetric functions and $q, n \in \nats$. A \emph{circuit for
+  structures} (or \emph{circuit}) $C$ is a DAG with a designated set of input
+gates each labelled by a relation symbol $R \in \tau$ and a tuple $\vec{a} \in
+[n]^{\arty(R)}$, internal gates each labelled by an element of $\BB$, and a
+designated set of output gates, each labelled by a unique element of $[n]^q$.
 
-\subsection{Symmetric Circuits}
-A circuit for structures, as given by Anderson and Dawar, is defined for a fixed
-relational vocabulary $\tau$, a Boolean basis of $\mathbb{B}$ \emph{symmetric
-  functions} (function's whose output depends only on the number of 1's in the
-input) and some fixed universe of size $n$. The input gates are taken to be the
-formal graph of the relational symbols over the universe $[n]$, i.e. gates
-labelled by $R(\vec{x})$ where $\vec{x} \in [n]^{\arty(R)}$. The input to the
-circuit is a finite $\tau$-structure $\mathcal{A}$ of cardinality $n$.
+Let $\mathcal{A}$ be a $\tau$-structure of size $n$ and fix a bijection $\gamma$
+from the universe of $\mathcal{A}$ to $[n]$. This bijection defines an encoding
+of $\mathcal{A}$ as a $\tau$-structure with universe $[n]$. This encoding
+defines an assignment to the input gates of the circuit, assigning the gate
+labelled by the relation symbol $R$ and tuple $\vec{a})$ to one if, and only if,
+$\vec{a}$ is an element of the interpretation of $R$ in the encoding of
+$\mathcal{A}$. The circuit may then be recursively evaluated, with the
+evaluation of the output gates taken as the output of the circuit. We note that
+an evaluation of the output gates (and hence the output of the circuit) is an
+element of $\{0,1\}^{[n]^q}$. The circuit then associates with every
+$\tau$-structure and bijection $\gamma$ a set of $q$-tuples in $\mathcal{A}$.
 
-Evaluation of the circuit proceeds by first choosing a bijection $\gamma$ from
-the universe of $\mathcal{A}$ to $[n]$ and then, for each input gate, using the
-interpretation of the relevant relational symbol in $\mathcal{A}$ and the
-bijection $\gamma$ to evaluate the gate. Recursing through the circuit and
-evaluating the internal gates using the given semantics for the symbols in the
-Boolean basis allows each gate in the circuit to be evaluated.
+A circuit is called \emph{invariant} if its output does not depend on the choice
+of $\gamma$. In this case the circuit defines a $q$-ary query of
+$\tau$-structures. If $C$ is an invariant circuit with $q = 0$, and the circuit
+has a single output gate and decides a property of $\tau$-structures. A circuit
+is called \emph{symmetric} if every permutation on the universe $[n]$, each of
+which induces a permutation on the input gates, extends to an automorphism of
+the circuit. A symmetric circuit is necessarily invariant.
 
-A circuit is \emph{invariant} if its output does not depend on the choice of
-$\gamma$. A \emph{symmetric} circuit is a circuit such that every permutation on
-the universe $[n]$, each of which induces a permutation on the input gates,
-extends to an automorphism of the circuit. A symmetric circuit is necessarily
-invariant.
+Anderson and Dawar use families of symmetric circuits to characterise $\FPC$.
 
-It is important to note that the word `symmetric' is used in two different ways
-here. When applied to a circuit the above definition is used, but when applied
-to a Boolean function it denotes a function whose output depends only on the
-number of 1's in its input.
-
-The main result of~\cite{AndersonD17} is the following characterisation theorem.
-
-\begin{thm}
-  For any relational vocabulary $\tau$, a property of finite $\tau$-structures
-  is decided by a P-uniform family of symmetric circuits with majority gates if,
-  and only if, it is expressible in FPC.
+\begin{thm}[Anderson and Dawar~\cite{AndersonD17}]
+  For a relational vocabulary $\tau$, a property of finite $\tau$-structures is
+  decided by a P-uniform family of symmetric circuits defined over the basis
+  $\BS$ if, and only if, it is expressible in $\FPC[\tau]$.
 \end{thm}
 
+% \subsection{Basic Notation}
+
+% Let $f : X \rightarrow Y$ be a function and $\sim$ be an equivalence relation
+% on Y. We define $f/{\sim} : X \rightarrow Y/{\sim}$ by $f(x) = [f(x)]_{\sim}$.
+% We call this the quotient of the function by $\sim$. For any two sets $X, Y$
+% we let $X^{\underline{Y}}$ denote the set of all injective functions from $Y$
+% to $X$.
+
+% INCLUDE STUFF ON SUPPORTS SET-WISE SUPPORTS
+
 \end{document}

### 2018-02-10 sections/conclusion.tex
Feb 10

@@
 \begin{document}
+In the quest for a logic that captures polynomial time
+
+At the time of writing there are two candidate logics which 
+Recent work on the problem of capturing $\PT$ has produced two `candidate'
+logics for capturing polynomial-time.
+In this paper we extend Anderson and Dawar's symmetric circuit characterisation
+of $\FPC$, showing that $P$-uniform families of transparent symmetric circuits
+with rank gates have the same expressive power as $\FPR$. Since $\FPR$ remains
+one of the two c
+the candidate logics for capturing $\PT$, along with choiceless polynomial time, 
 \end{document}

### 2018-02-10 sections/transparency-and-unique-extensions.tex
Feb 10

--- 2018-01-30 sections/transparency-and-unique-extensions.tex
@@
 \begin{document}
-% In contrast with the work of Anderson and Dawar~\cite{AndersonD17}, the
-% circuit families we use to establish the main result of this paper are
-% additionally required to be transparent. In this subsection we briefly discuss
-% this condition, and present results suggesting its necessity.
 
@@
 inclusion of the transparency restriction.
-% We note additionally that the circuit properties that we show
-
-% In this section we discuss the transparency condition on circuits. It is worth
-% noting that, since the symmetric circuits of Anderson and
-% Dawar~\cite{AndersonD17} have no non-symmetric internal gates, these circuits
-% are transparent. We have from the first part of this subsection that a great
-% number of useful properties (and transformations) are polynomial-time
-% computable on transparent circuits. However, it is still reasonable to ask if
-% the explicit inclusion of the transparency restriction is strictly necessary
-% for proving these results, or indeed proving the main result of this paper. We
-% provide evidence for necessity of the transparency condition, presenting
-% reductions from the graph-isomorphism problem to the problem of deciding some
-% of this important properties (e.g. symmetry, syntactic-equivalence, computing
-% the orbit of a gate, etc.) over general, not necessarily transparent,
-% circuits. We note that in all of these cases the decision problem restricted
-% to transparent circuits is polynomial-time decidable.
-
-% We further argue that, since most natural algorithms for transforming an
-% arbitrary symmetric circuit into an equivalent transparent circuit make use of
-% the polynomial-time decidability of these properties, we should consider these
-% hardness results evidence that computing this transformation may be as hard as
-% the graph-isomorphism problem
-% We also prove that a number of related decision problems (e.g. synatcatic)
-% important decision problems are reducible to the graph-isomorphism
-% xthat the problem of deciding the orbit of a gate is reduca
-% why (or whether) the transparency condition is strictly required when
-% considering circuits that contain non-symmetric gates. In the second
-% subsection we address this question, proving
-
-% when considering circuits
-
-% It is worth noting that the analogous results of Anderson and Dawar~\ref{}
-% make no explicit restriction to transparent circuits,
-
-% mentio It is worth asking if this additional transparency requirement is
-% structing It is worth noting that Anderson and Dawar~\ref{} when developing
-% their analogous translation, define a polynomial-time algorithm that
-% transforms symmetric circuits into equivalent circuits with unique extensions
-% -- making no mention of any transparency condition. Of course, the circuits
-% they consider contain only symmetric internal gates, and as such are
-% transparent already, but we may still ask if the transparency restriction is
-% strictly necessary for proving the useful results mentioned above.
-
-% It is worth noting that the translation defined by Anderson and Dawar~\cite{}
-% between $P$-uniform families of symmetric circuits (with symmetric gates) and
-% formulas of $\FPC$ makes no
-
-% In the second subsection we discuss the necessity of the transparency
-% requirement. Anderson and Dawar~\cite{AndersonD17} importance of this trans
-
-% into In the main result of this paper we restrict ourselves to transparent
-% circuits, a restriction not found in the analogous result of Anderson and
-% Dawar~\cite{}. In this section we develop a number of technical that are
-% important for defining and developing the basic technical tools used in this
-% paper.
-
-% Anderson and Dawar~\cite{} develop an correspondence between symmetric
-% circuits (with symmetric gates) and formulas of fixed point with counting. In
-% contrast, in the main theorem of this paper we explicitly require that the
-% circuits under discussion be \emph{transparent}. This section we develop a
-% number of results about transparent circuits. In the first subsection we
-% discuss
-
-% In this section we present a number of useful results for transparent circuits
-% that together enable our analysis
-
-% This condition does not appear explicitly in the analogous result of Anderson
-% and Dawar~\cite{}, and in this section we discuss the importance of this
-% requirement on circuits with non-symmetric gates.
-
-% In the first subsection we demonstrate the usefulness of transparency. We
-% begin by showing that we may transform transparent circuits into circuits with
-% unique extensions in polynomial-time, allowing us assume, without a loss of
-% generality, that $P$-uniform families of transparent circuits also have unique
-% labels, and hence (from Proposition~\ref{}) unique extensions. We are also
-% able to show that if a circuit has unique labels, which transparency allows us
-% to assume, then many natural circuit properties, including the action of a
-% permutation on the circuit, as well as the orbit and coarsest supporting
-% partition of a gate, are polynomial-time computable.
-
-% These results suggest the importance fundamental to our analysis of circuits.
-% The ability to assume that the circuits under discussion have unique
-% extensions (and unique labels) allows us to define many important theoretical
-% tools, such as a canonical action of $\sym_n$ on the circuit and hence the
-% notions of support and supporting partition. Moreover, the polynomial-time
-% algorithms for computing the orbit and support of a gate play an important
-% role (through the Immerman-Vardi Theorem~\cite{}) in our translation of
-% circuits into formulas (see Section \ref{})
-
-% we also show that if a circuit has unique labels (which transparency allows us
-% to assume) then there exists polynomial-time algorithms for computing the
-% action of $\sym_n$ on the circuit, and the canonical supporting partition and
-% the orbit a gate (or elements of a universe of a gate). These algorithms play
-% (along with the
-
-% polynomial-time algorithms are thus crucial for developing our translation
-% from circuits to formulas.
-
-% and prove the existence of polynomial-time algorithms computing important
-% functions, such as the coarsest supporting partition or the orbit of a gate
-% (see Proposition~\ref{prop:c} and Lemma~\ref{}).
-
-% Thus the transparency condition enables our analysis of circuits by allowing
-% us to assume the circuits also have unique extensions. However, Anderson and
-% Dawar~\cite{AndersonD17} prove that symmetric circuit can be transformed into
-% circuits with unique extensions,without making any mention of any condition
-% analogous to transparency. Of course, our result generalises theirs as they
-% only consider circuits with symmetric gates, which are transparent, but it is
-% reasonable to ask if the transparency requirement on circuits is strictly
-% necessary.
-
-% We address this question in this subsection, presenting reductions
-% graph-isomorphism problem to the many related and important problems. We show,
-% for example, that there is a polynomial-time many-one reduction from
-% graph-isomorphism problem to the problem of deciding the orbit of a gate in an
-% arbitrary symmetric circuit, and contrast this result with the known
-% polynomial-time algorithm computing orbits of gates in transparent circuits.
-% We also present reductions from the graph-isomorphism problem to many related
-% problems (e.g. checking syntactic-equivalence or unique label for gates).
-% Since most natural algorithms for transforming any an arbitrary symmetric
-% circuit into an equivalent family of transparent circuits entail solving these
-% related problems, we consider this evidence that computing this transformation
-% may be as hard as the graph isomorphism problem.
-
-% Moreover, we show that non-transparent circuits
-
-% an ay be as hard as the graph isomorphism problem. However, we
-
-% show that that being able to transform a circuit into an equivalent
-% transparent circuit in polynomial-time would
-
-% make no mention In contrast, Anderson and Dawar~\ref{} do not include any
-% specific condition on the circuit families they consider
-
-% consider only symmetric circuits with symmetric gates, which are transparent,
-% and as such include no such condition.
-
-% make use of an explicit condition on circuits we call \emph{transparency}. In
-% this section we show that transparency is a sufficient condition in that it
-% allows us to assume, without a loss of generality, that $P$-uniform families
-% of In this subsection we show that if a circuit is transparent then it may be
-% transformed in polynomial time into an equivalent circuit with unique labels.
-% It follows from Proposition~\ref{prop:unique-labels-unique-extensions}) that
-% we may assume, without a loss of generality, that $P$-uniform families of
-% transparent circuits have unique labels, and hence unique extensions.
-
-% We also discuss the importance of the transparency condition on circuits
-% introduced in this paper. Indeed, while Anderson and Dawar~\cite{AndersonD17},
-% place no similar requirement on the symmetric circuits in their paper, in our
-% generalisation of their result, transparency is required.
-
-% We also discuss relevant special cases and motivate the explicit requirement
-% that the $P$-uniform families of circuit referenced in the main result of this
-% paper consist of transparent circuits.
-
-% Anderson and Dawar~\cite{AndersonD17} introduce the notion of a `rigid'
-% circuit, a condition analogous to the rigidity condition defined in this
-% paper. The following
-
-% \begin{definition}
-%   We say a circuit $C_n$ is que labels it has unique extensions. We finally
-%   discuss th\emph{rigid} if it has injective labels and for every pair of
-%   gates $(g, g')$ in $C_n$ such that $H_g = H_{g'}$ and $g \equiv g'$.
-% \end{definition}
+
 \subsection{The Usefulness of Transparency}
@@
 
-% \begin{definition}
-%   We say a class of circuits $\mathcal{C}$ is \emph{syntactically transparent}
-%   if there is an algorithm that takes in a circuit $C \in \mathcal{C}$ and
-%   outputs the syntactic equivalence relation on the gates of $C$ and runs in
-%   time polynomial in the size of the input circuit.
-% \end{definition}
-
 \begin{lem}
@@
   Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a transparent
-  $(\mathbb{B}, \rho)$-circuit of order $n$. We define a relation $\sim$ by
-  induction on height (i.e. distance from an input gate). This relation will be
-  the syntactic-equivalence relation on $G$. It is easy to check the conditions
-  for syntactic-equivalence for gates of height 0 as all such gates are input
-  gates and so are either constant gates or relational gates. Suppose $g$ and
-  $h$ are gates of height greater than zero. We only need to check conditions
-  (i), (iv) and (v) of syntactic-equivalence. It is easy to check (i) and (v).
-  If either condition is false then $g$ and $h$ are not syntacticly equivalent.
-  So suppose $g$ and $h$ are two internal gates such that $\Sigma (g) =
-  \Sigma(h)$ and suppose that if they are both output gates then $\Omega^{-1}(g)
-  = \Omega^{-1}(h)$. It remains to check if $L(g)/{\sim}$ and $L(h)/{\sim}$ are
-  isomorphism equivalent. First check if $H_h /{\sim} = H_g /{\sim}$. If not,
-  $g$ and $h$ are not syntactically equivalent. So suppose $H_h /{\sim} = H_g
-  /{\sim}$. If $g$ and $h$ are symmetric gates then $H_h /{\sim} = H_g/{\sim}$
-  if, and only if, $L(g)/{\sim}$ and $L(h)/{\sim}$ are isomorphism equivalent,
-  so let $g \sim h$. If $g$ and $h$ are not symmetric gates then, since $C$ is
-  transparent, $g$ and $h$ have unique labels. We thus have that $L(g)/{\sim}$
-  and $L(h)/{\sim}$ are isomorphism equivalent if, and only if, $L(g)^{-1}L(h)$
-  acts like an isomorphism. This can be checked by first checking that the
-  function induces a sorted permutation on the universe of $g$ (which can be
-  checked efficiently). This is sufficient as $L(g)(L(g)^{-1}L(h)) = L(h)$.
-
-  It is easy to see that, given a reasonable binary encoding of a circuit, the
-  above procedure can be implemented so as to run in polynomial time, and that
-  the relation $\sim$ is the syntactic-equivalence relation on the gates of $C$.
-
-  % Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a transparent
-  % $(\mathbb{B}, \rho)$-circuit of order $n$. We define a relation $\sim$ by
-  % induction on height (i.e. distance from an input gate). This relation will be
-  % the syntactic-equivalence relation on $G$. It is easy to check the conditions
-  % for syntactic-equivalence for gates of height 0 as all such gates are input
-  % gates and so are either constant gates or relational gates. Suppose $g$ and
-  % $h$ are gates of height greater than zero. We only need to check conditions
-  % (i), (iv) and (v) of syntactic-equivalence. It is easy to check (i) and (v).
-  % If either condition is false then $g$ and $h$ are not syntacticly equivalent.
-  % So suppose $g$ and $h$ are two internal gates such that $\Sigma (g) =
-  % \Sigma(h)$ and suppose that if they are both output gates then $\Omega^{-1}(g)
-  % = \Omega^{-1}(h)$. It remains to check if $L(g)/{\sim}$ and $L(h)/{\sim}$ are
-  % isomorphism equivalent. First check if $H_h /{\sim} = H_g /{\sim}$. If not,
-  % $g$ and $h$ are not syntactically equivalent. So suppose $H_h /{\sim} = H_g
-  % /{\sim}$. If $g$ and $h$ are symmetric gates then $H_h /{\sim} = H_g/{\sim}$
-  % if, and only if, $L(g)/{\sim}$ and $L(h)/{\sim}$ are isomorphism equivalent,
-  % so let $g \sim h$. If $g$ and $h$ are not symmetric gates then, since $C$ is
-  % transparent, $g$ and $h$ have unique labels. We thus have that $L(g)/{\sim}$
-  % and $L(h)/{\sim}$ are isomorphism equivalent if, and only if, $L(g)^{-1}L(h)$
-  % acts like an isomorphism. This can be checked by first checking that the
-  % function induces a sorted permutation on the universe of $g$ (which can be
-  % checked efficiently). This is sufficient as $L(g)(L(g)^{-1}L(h)) = L(h)$.
-
-  % It is easy to see that, given a reasonable binary encoding of a circuit, the
-  % above procedure can be implemented so as to run in polynomial time, and that
-  % the relation $\sim$ is the syntactic-equivalence relation on the gates of $C$.
-
+  $(\mathbb{B}, \rho)$-circuit of order $n$. We define the syntactic-equivalence
+  relation on $G$ by induction on the height of a gate We note that this
+  definition can be implemented by a dynamic program.
+
+  Suppose $g$ and $h$ are gates in $C$ such that $\Sigma (g) = \Sigma(h)$ and
+  either both $g$ and $h$ are output gates and $\Omega^{-1}(g) = \Omega^{-1}(h)$
+  or neither are output gates. Let $g$ and $h$ be input gates, then set $g
+  \equiv h$ if, and only if, both $g$ and $h$ are constant gates or both are
+  relational gates and $\Lambda(g) = \Lambda (h)$. Let $g$ and $h$ be internal
+  gates and suppose we have defined the syntactic-equivalence relation for all
+  gates of height less than the height of either $g$ or $h$. Then $g \equiv h$
+  if, and only if, $L(g)$ and $L(h)$ are isomorphism equivalent up to $\equiv$.
+
+  The above algorithm can be implemented by a dynamic program with the number of
+  iterations bounded by the number of pairs of gates in $C$, i.e. $\vert C
+  \vert$ choose $2$. It remains to show that each iterative step can be
+  implemented so as to run in time polynomial in the size of $C$. The only
+  condition that is not obviously polynomial-time decidable is checking if
+  $L(g)$ is isomorphism-equivalent to $L(h)$ up to $\equiv$. We sketch an
+  algorithm that decides this condition in time polynomial in the size of the
+  circuit.
+
+  Let $g$ and $h$ be two internal gates in $C$ and suppose we have defined the
+  syntactic-equivalence relation for all gates of height less than the height of
+  either $g$ or $h$. We test if for each gate in $g' \in H_g$, there exists
+  $h_{g'} \in H_h$ such that $g' \equiv h_{g'}$ and $\vert \{g'' \in H_g : g''
+  \equiv g'\} \vert = \vert \{h'' \in H_h : h'' \equiv h'\}$. If this test
+  fails, we set $g \not\equiv h$.
+
+  We then check if both $g$ and $h$ are symmetric gates or if both are
+  non-symmetric gates. Suppose both $g$ and $h$ are symmetric gates. We have
+  that $L(g)$ is isomorphism-equivalent to $L(h)$ up to $\equiv$ if, and only
+  if, there exists a bijection $f : H_g \rightarrow H_h$ such that $f(g') \equiv
+  g'$, for all $g' \in H_g$ if, and only if, for each gate in $g' \in H_g$,
+  there exists $h' \in H_h$ such that $g' \equiv h'$ and $\vert \{g'' \in H_g :
+  g'' \equiv g'\} \vert = \vert \{h'' \in H_h : h'' \equiv h'\}$. Since we have
+  already checked this condition we set $g \equiv h$.
+
+  Suppose $g$ and $h$ are non-symmetric gates. Then, since $C$ is transparent,
+  both $g$ and $h$ have unique labels. We thus have that for each $g' \in H_g$
+  there is exactly one $h_{g'} \in H_h$ such that $g' \equiv h_{g'}$, and so we
+  can define the bijection $f : H_g \rightarrow H_h$ by $f(g') := h_{g'}$ for
+  all $g' \in H_g$. It can be shown that $L(g)$ is isomorphism-equivalent to
+  $L(h)$ up to $\equiv$ if, and only if, $f \circ L(g)$ is
+  isomorphism-equivalent to $L(h)$ if, and only if, $L(h)^{-1} f L(g)$ acts on
+  $\ind (g)$ like an element of $\aut(g)$. We have from
+  Lemma~\ref{lem:aut-partial} that $\sigma := L(h)^{-1} f L(g)$ acts like an
+  element of $\aut(g)$ if, and only if, for all $\vec{a}_R, \vec{b}_{R'} \in \ind(g)$,
+  $\sigma$ acts like a partial automorphism on $(\vec{a}_R, \vec{b}_{R'})$. We
+  thus conduct the test by iterating through every pair $(\vec{a}_R,
+  \vec{b}_{R'}) \in \ind(g)$, and set $g \equiv h$ if, and only if, $\sigma$
+  acts like a partial automorphism on every such pair.
 \end{proof}

### 2018-02-11 sections/translating-formulas-to-cicuits.tex
Feb 10
feb 11

@@
 
+\begin{definition}
+  The function $\op{tag-inputs}$ maps a circuit $C := \langle G, \Omega, \Sigma,
+  \Lambda, L \rangle$, a relation symbol $R \in \tau$, and $H \subseteq G$
+\end{definition}
+
 \subsection{Translating FPR to Symmetric Matrix Circuits}
@@
 equal to the query defined by $\theta (\vec{x})$.
+
+We say that a circuit $C$ \emph{translates} a formula $\psi(\vec{x})$ for $n \in
+\nats$ if $C$ is a transparent symmetric rank-circuit of order $n$, $C$ is
+defined over the same vocabulary as $\psi (\vec{x})$, and $C$ computes the query
+defined by $\psi(\vec{x})$ on structures of size $n$. We say a family of
+circuits $(C_n)_{n \in \nats}$ \emph{translates} a formula $\psi (\vec{x})$ if
+$(C_n)_{n \in \nats}$ is $\PT$-uniform and for all $n \in \nats$, $C_n$
+translates $\psi(\vec{x})$ for $n$.
+
+\begin{definition}
+	Let $\alpha : X \rightarrow Y$ and $\beta : W \rightarrow Z$. We say that $f$
+  is \emph{compatible} with $g$, and we write $f \sim g$, if for all $a \in X
+  \cap W$, $f(a) = g(a)$ and for all $a \in X \setminus W$ and $b \in W
+  \setminus X$, $f(a) \neq g(b)$.
+\end{definition}
+
+We now prove that for every $\FOrk$-formula $\theta(\vec{x})$ and $n \in \nats$
+there exists a circuit $C$ that translates $\theta(\vec{x})$ for $n$. The gates
+of $C$ are of the form $g_{\psi, \alpha}$, where $\psi(\vec{y})$, a sub-formula
+of $\theta(\vec{x})$, and $\alpha$ is an assignment to the free variables of
+$\psi$. We then wire up the gates such that $g_{\psi, \alpha}$ is associated
+with an appropriate function from the basis, and the children of $g_{\psi,
+  \alpha} $ are those gates $g_{\phi, \beta}$, where $\phi$ is an immediate
+sub-formula of $\psi$ and $\beta$ is an assignment to the free variables in
+$\phi$ that agrees with the assignment $\alpha$. The resultant circuit is
+symmetric and has the property that $g_{\psi, \alpha}$ evaluates to one for a
+given input structure if, and only if, $\psi$ holds for that structure given the
+assignment $\alpha$. However, as stated this construction does not result in a
+transparent circuit. In order to ensure that $C$ is also transparent we first
+alter $\theta$ by appending to each application of the rank operator a gadget
+that ensures that no two children of a rank gate are syntactically-equivalent.
+We now formally define this construction and, moreover, provide a bound on the
+running time of the algorithm constructing this circuit.
+
+\begin{lem}
+  There is an algorithm that takes in a $\FOrk$-formula $\theta(\vec{x})$ and $n
+  \in \nats$ and outputs a rank-circuit $C$ that translates $\theta(\vec{x})$
+  for $n$. Moreover, there is a polynomial in $p$ such that for an input
+  $(\theta(\vec{x}), n)$ the algorithm terminates in at most
+  $p(n^{\width(\theta)}\vert \cl{\theta} \vert)$ many steps.
+\end{lem}
+\begin{proof}
+  Let $\tau$ be the vocabulary of $\theta(\vec{x})$. Let $k := \width(\theta)$.
+  Suppose $\tau$ is empty. In this case we can evaluate $\theta$ for each
+  assignment $\vec{a}$ in a number of steps polynomial in $n^k \vert \cl{\theta}
+  \vert$. Let $f : [n]^k \rightarrow \{0,1\}$ be defined such that $f (\vec{a})
+  = 1$ if, and only if, $[n] \models \theta[\vec{a}]$. Let $C = \langle G,
+  \Sigma, \Omega, \Lambda, L \rangle$, where
+  \begin{itemizens}
+  \item $G = \{g_0, g_1\} \cup \{g_{\vec{a}} : \vec{a} \in [n]^{k}\}$,
+  \item $\Sigma (g_0) = 0$, $\Sigma (g_1) = 1$ and $\Sigma (g_{\vec{a}}) =
+    \land[1]$,
+  \item $\Omega : [n]^k \rightarrow G$ is defined by $\Omega(\vec{a}) =
+    g_{\vec{a}}$ for all $\vec{a} \in [n]^k$,
+  \item $\Lambda = \emptyset$,
+  \item for $\vec{a} \in [n]^k$, $L(g_{\vec{a}}) : [1] \rightarrow G$ is defined
+    by $L(g_{\vec{a}})(1) = g_{f(\vec{a})}$.
+  \end{itemizens}
+
+  Since $C$ has symmetric gates, $C$ is transparent. Notice that, since
+  $\theta(\vec{x})$ defines a query on structures over the empty vocabulary, we
+  have for all $\sigma \in \sym_n$, $f(\sigma \vec{a}) = f(\vec{a})$ for all
+  $\vec{a} \in [n]^k$. For $\sigma \in \sym_n$, let $\pi_\sigma : G \rightarrow
+  G$ be a bijection that fixes the constant gates and such that $\pi_{\sigma}
+  (g_{\vec{a}}) = g_{\sigma \vec{a}}$ for all $\vec{a} \in [n]^k$. Then
+  $\pi_\sigma \Omega (\vec{a}) = \pi_\sigma g_{\vec{a}} = g_{\sigma \vec{a}} =
+  \Omega (\sigma \vec{a})$. It follows that $\pi_\sigma$ is an automorphism of
+  the circuit extending $\sigma$. It follows that $C$ is symmetric, and so $C$
+  translates $\theta(\vec{x})$ for $n$.
+
+  Suppose $\tau$ is not empty. Let $R \in \tau$. We now construct a $C$ that
+  translates $\theta(\vec{x})$ at $n$. We first pre-proccess the formula $\theta(\vec{x})$
+
+  Let $\op{no-op}(y) := (R(y, y) \land (\neg R(y, y)))$. Let $\vec{y} := (y_1,
+  \ldots, y_k)$ be a vector of variables and $\op{add-tag} (\vec{y}) :=
+  \op{no-op}(y_1) \land (\op{no-op}(y_2) \land ( \op{no-op}(y_2) \land ( \ldots
+  \land (\op{no-op}(y_k)) \ldots)))$. From $\theta (\vec{x})$ we construct a new
+  formula $\theta' (\vec{x})$ by replacing each sub-formula $\phi(\vec{y})$ of
+  the form $\rank^r_p \vec{w} \vec{z} . \psi$ by the sub-formula $\rank^r_p
+  \vec{w}\vec{z} . ((\forall u . u = u) \land \phi) \land \op{add-tag}(\vec{w}
+  \cup \vec{z})$.
+
+  Fix $n \in \nats$. For each $\psi \in \cl{\theta'}$ let $G_\psi := \{g_{\psi,
+    \alpha} : \alpha \in [n]^{\free{\psi}} \}$. Let $G_c := \{g_0, g_1\}$. Let
+  $G := G_c \cup (\bigcup_{\psi \in \cl{\theta'}} G_{\psi})$. We define
+  $\Sigma$, $\Lambda$ and $L$ as follows. Let $\Sigma (g_1) = 1$ and $\Sigma
+  (g_0) = 0$. If $g_{\psi, \alpha} \in G \setminus G_c$.
+
+  \begin{itemizens}
+  \item If $\psi$ is of the form $T(\vec{y})$ for some $T \in \tau$, then
+    $\Sigma (g_{\psi, \alpha}) = T$ and $\Lambda_T (g_{\psi, \alpha}) = \alpha
+    \vec{y}$.
+  \item If $\psi$ is of the form $(y_1 = y_2)$, then $\Sigma (g_{\psi, \alpha})
+    = \land[1]$ and $L(g) : [1] \rightarrow G$ by $L(g)(1) = g_1$ if $\alpha
+    (y_1) = \alpha (y_2)$ and $L(g)(1) = g_0$ otherwise.
+  \item If $\psi$ is of the form $\rank^r_p \vec{w} \vec{z}. \phi$, let $a =
+    n^{\vert \vec{w}\vert}$ and $b = n^{\vert \vec{z}\vert}$, and $\Sigma
+    (g_{\psi, \alpha}) = \rank[a, b]$. Let $L(g) : [a] \times [b] \rightarrow G$
+    be defined by $L(g)(i,j) = g_{\phi, \beta}$, where $\beta : \vec{w} \cup
+    \vec{z} \cup \vec{y} \rightarrow [n]$ is such that $\alpha \subseteq \beta$
+    and such $\beta \vec{y}$ and $\beta \vec{z}$ are the $i$th and $j$th
+    elements of $[n]^{\vert \vec{w} \vert}$ and $[n]^{\vert \vec{z} \vert}$ in
+    the lexicographical ordering.
+  \item If $\psi$ is of the form $Q z . \phi(\vec{y}, z)$, for $Q \in \{\forall,
+    \exists\}$, then if $Q = \forall$ we have $\Sigma (g_{\psi, \alpha}) = \land
+    [n]$, otherwise $\Sigma (g_{\psi, \alpha}) = \lor [n]$. Let $L(g) : [n]
+    \rightarrow G$ be defined by $L(g)(i) = g_{\phi, \beta_i}$, where $\beta_i
+    \in [n]^{\vec{y} \cup \{z\}}$ and $\alpha \subseteq \beta_i$ and $\beta_i
+    (z) = i$.
+  \item If $\psi$ has free variables $\vec{y}$ and is of the form $\phi_1
+    (\vec{y}_1) \land \phi_2(\vec{y}_2)$, where $\vec{y_1}, \vec{y_2} \subseteq
+    \vec{y}$, then $\Sigma(g_{\psi, \alpha}) = \land[2]$ and $L(g) : [2]
+    \rightarrow G$ is defined by $L(g)(i) = g_{\phi_i, \beta_i}$ where $\beta_i
+    \in [n]^{\vec{y}_i}$ and $\beta_i \subseteq \alpha$ for $i \in [2]$. The
+    same approach is used in the disjunctive case.
+  \item if $\psi$ is of the form $\neg \phi$ then $\Sigma (g_{\psi, \alpha}) =
+    \neg$ and $L(g): [1] \rightarrow G$, where $L(g)(1) = g_{\phi, \alpha}$.
+  \end{itemizens}
+
+  We let $\Omega : [n]^k \rightarrow G$ be defined by $\Omega (\vec{a}) =
+  g_{\theta', \alpha}$, where $\alpha \vec{x} = \vec{a}$, for all $\vec{a} \in
+  [n]^k$. Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$. We notice
+  that $\vert C \vert \leq n^{\width(\theta')} \vert \cl{\theta} \vert$. It can
+  be shown that $C$ can be constructed in time bounded by a polynomial in the
+  size of $C$.
+
+  We now show that $C$ translates $\theta(\vec{x})$ for $n$. It is obvious that
+  $C$ has order $n$. Let $\sigma \in \sym_n$. Let $\pi_\sigma : G \rightarrow G$
+  be a defined such that $\pi (g) = g$ if $g \in G_c$ and $\pi_\sigma(g_{\psi,
+    \alpha}) = g_{\psi, \sigma \alpha}$ for all $\psi \in \cl{\theta}$ and
+  $\alpha \in n^{\free(\psi)}$. It is easy to see that $\pi_\sigma$ is an
+  automorphism of $C$ extending $\sigma$. It follows that $C$ is symmetric. Let
+  $g := g_{\psi, \alpha} \in G$ be a rank gate and let $h, h' \in H_g$. Suppose
+  $\psi (\vec{y}) := \rank^r_p \vec{w} \vec{z}. \phi$ and $h := g_{\phi, \beta}$
+  and $h' := g_{\phi, \beta'}$ are syntactically-equivalent. From the
+  construction of $\theta'$ we have that $\phi$ must be of a particular form.
+  Suppose $\phi = \eta \land \op{add-tag}(\vec{w} \cup \vec{z})$. Let $\gamma$
+  and $\gamma'$ be the restrictions of $\beta$ and $\beta'$ to $\vec{w} \cup
+  \vec{z}$, respectively, and let $\zeta(\vec{w}\cup\vec{z}) :=
+  \op{add-tag}(\vec{w} \cup \vec{z})$. The $\op{add-tag} (\vec{w} \cup \vec{z})$
+
+  The structure of this formula gives us that $h$ is syntactically-equivalent to
+  $h'$ if, and only if, $g_{\zeta , \beta'}$
+
+  We also note that $C$ has order $n$.
+
+\end{proof}
 
@@
 
-  We have from Anderson and Dawar~\cite{AndersonD17} that for every formula
-  $\phi(\vec{x}) \in \FPC[\tau]$ there is a $\PT$-uniform family of symmetric
-  circuits $(C^{\phi}_n)_{n \in \nats}$ with unique labels and symmetric gates
-  that translates $\phi(\vec{x})$.
+  % We have from Anderson and Dawar~\cite{AndersonD17} that for every formula
+  % $\phi(\vec{x}) \in \FPC[\tau]$ there is a $\PT$-uniform family of symmetric
+  % circuits $(C^{\phi}_n)_{n \in \nats}$ with unique labels and symmetric gates
+  % that translates $\phi(\vec{x})$.
 
@@
   We thus derive the required $\PT$-uniform family $(\theta_n(\vec{x}))_{n \in
-    \nats}$ by applying the first translation and then the second.
+    \nats}$ by applying the first translation and then the second. Let $x$ be a
+  variable and $R \in \tau$. Let $\op{no-op}(x) := R(x, x) \land (\neg R(x,
+  x))$. Let $\vec{x} := (x_1, \ldots, x_k)$ and $\op{add-tag} (\vec{x}) :=
+  \op{no-op}(x_1) \land (\op{no-op}(x_2) \land ( \ldots \land (\op{no-op}(x_k))
+  \ldots)$. For each $\theta_n (\vec{x})$ we construct a new formula $\theta_n'
+  (\vec{x})$ by replacing each sub-formula $\phi(\vec{y})$ of
+  $\theta_n(\vec{x})$ of the form $\rank^r_p \vec{w} \vec{z} . \psi$ by
+  $\rank^r_p \vec{w}\vec{z} . (\psi \land \op{add-tag}(\vec{w} \cup \vec{z}))$.
+  It is easy to see that we can construct $\theta_n'$ from $\theta_n$ in time
+  polynomial in $\theta_n$. Moreover, $\theta_n'$ and $\theta_n$ are equivalent
+  and have the same width.
 
-  Fix $n \in \nats$. We recursively define a function $T_n$ that maps $\psi
-  (\vec{y})$, a sub-formula of $\theta_n(\vec{x})$, to a circuit $C^{\psi}_n$,
-  where $C^{\psi}_n$ translates $\psi(\vec{y})$ at $n$. We then have that for
-  all $n \in \nats$, $T_n(\theta_n(\vec{x}))$ translates $\theta_n$ (and hence
-  $\theta$) at $n$.
+  Fix $n \in \nats$. We now construct a circuit $C_n$ that translates
+  $\theta_n'$ (and hence $\theta_n$ and $\theta$) at $n$. For each $\psi \in
+  \cl{\theta_n}$ let $G_\psi := \{g_{\psi, \alpha} : \alpha \in
+  [n]^{\free{\psi}} \}$. Let $G := \bigcup_{\psi \in \cl{\theta_n}} G_{\psi}$.
+  Let $g_{\psi, \alpha} \in G$. We define $\Sigma$, $\Lambda$ and $L$ as
+  follows.
+  \begin{itemizens}
+  \item If $\psi (\vec{y}) = R(\vec{y})$, for some $R \in \tau$, then $\Sigma
+    (g_{\psi, \alpha}) = R$ and $\Lambda_R (g_{\psi, \alpha}) = \alpha
+    \vec{y})$.
+  \item If $\psi (y_1, y_2) = (y_1 = y_2)$, then if $\alpha (y_1) = \alpha
+    (y_2)$, $\Sigma (g_{\psi, \alpha}) = 1$, else $\Sigma (g_{\psi, \alpha}) =
+    0$.
+  \item if $\psi (\vec{y}) = \rank^r_p \vec{w} \vec{z}. \phi$, then $\Sigma ()$
+  \end{itemizens}
 
@@
   \vec{a} \in [n]^{k_1}, \vec{b} \in [n]^{k_2}, \vec{c} \in [n]^{k}\}$. Let
-  $C^{\psi'}_n:= \langle G^{\psi'}, \Omega^{psi'}, \Sigma^{\psi'},
+  $C^{\psi'}_n:= \langle G^{\psi'}, \Omega^{\psi'}, \Sigma^{\psi'},
   \Lambda^{\psi'}, L^{\psi'}\rangle$ be a $(\mathbb{B}_{\rank}, \{ R_{\phi}

### 2018-02-11 sections/background.tex
feb 11

@@
 \subsection{First Order and Fixed-Point Logic}
-Let $L$ be a logic and $\tau$ be a vocabulary, we let $L[\tau]$ denote the set
-of all $\tau$-formulas of $L$ (i.e. the set of all $L$-formulas with respect to
-$\tau$). Let $\FO[\tau]$ denote \emph{first-order logic} with respect to the
-vocabulary $\tau$. A formula in $\FO[\tau]$ is formed from atomic formulas, each
-formed using variables from some countable sequence of (first-order) variable
-symbols $(x, y, \ldots)$, the relation symbols in $\tau$, and the equality
-symbol $=$, and then closing the set of atomic formulas under the Boolean
-connectives, negation, and universal and existential quantification (i.e.
-$\land$, $\lor$, $\neg$, $\forall$, and $\exists$).
+Let $\FO[\tau]$ denote \emph{first-order logic} with respect to the vocabulary
+$\tau$. A formula in $\FO[\tau]$ is formed from atomic formulas, each formed
+using variables from some countable sequence of (first-order) variable symbols
+$(x, y, \ldots)$, the relation symbols in $\tau$, and the equality symbol $=$,
+and then closing the set of atomic formulas under the Boolean connectives,
+negation, and universal and existential quantification (i.e. $\land$, $\lor$,
+$\neg$, $\forall$, and $\exists$).
 
@@
 Let $L$ be a logic and $\tau$ a vocabulary. For $\phi \in L[\tau]$ and a
-sequence of variables $\vec{x}$, we write $\phi(vec{x})$ if the free variables
+sequence of variables $\vec{x}$, we write $\phi(\vec{x})$ if the free variables
 in $\phi$ are among those in $\vec{x}$. Suppose $\vec{x} = (x_1, \ldots , x_k)$,
@@
 set, as well as other mechanisms for reasoning about quantities. We now briefly
-describe the structure of a formula of $\FPC[\tau]$. In order to facilitate
-counting we define terms which are assigned to natural numbers. Every
-first-order variable is assigned a type, and so each variable is either a
-\emph{vertex} or \emph{number} variable. Vertex variables are assigned to
-elements of the universe of the structure, and play a similar role to the
-variables that appear in formulas in $\FO[\tau]$ or $\FP[\tau]$. Number
-variables are assigned to elements of $\nats$. We usually use Latin letters
-(e.g. $x, y, z, \ldots$) to denote vertex variables and Greek letters (e.g.
-$\mu, \nu, \epsilon, \ldots$) to denote number variables. All atomic formulas in
-$\FP[\tau]$ are atomic formulas in $\FPC[\tau]$. We say that $t$ is a
-\emph{number term} if $t$ a number variable or if $t$ is an application of the
-\emph{counting operator}, i.e. $t = \#x. \phi(x)$, where $\phi \in \FPC[\tau]$
-and $x$ is a vertex variable free in $\phi$. If $t_1$ and $t_2$ are number terms
-then $t_1 \leq t_2$ and $t_1 = t_2$ are atomic formulas. The formulas of $\FPC$
-are then formed by closing the set of atomic formulas under the usual Boolean
-connectives, the first-order quantifiers (for vertex variables), and the
-inflationary fixed-point operator. The second-order variables, such as those
-that appear in an application of the fixed-point operator, are allowed to have
-mixed-type, i.e. we associate with a second-order variable $R$ a type $(k, l)
-\in \nats^2$ intended to mean that $R$ is assigned to a subset of $U^k \times
-\nats^l$.
+describe the structure of a formula of $\FPC[\tau]$. Every first-order variable
+is assigned a type, and so each variable is either a \emph{vertex} or
+\emph{number} variable. Vertex variables are assigned to elements of the
+universe of the structure, and play a similar role to the variables that appear
+in formulas in $\FO[\tau]$ or $\FP[\tau]$. Number variables are assigned to
+elements of $\nats$. We usually use Latin letters (e.g. $x, y, z, \ldots$) to
+denote vertex variables and Greek letters (e.g. $\mu, \nu, \epsilon, \ldots$) to
+denote number variables. All atomic formulas in $\FP[\tau]$ are atomic formulas
+in $\FPC[\tau]$. We say that $t$ is a \emph{number term} if $t$ a number
+variable or if $t$ is an application of the \emph{counting operator}, i.e. $t =
+\#x. \phi(x)$, where $\phi \in \FPC[\tau]$ and $x$ is a vertex variable free in
+$\phi$. If $t_1$ and $t_2$ are number terms then $t_1 \leq t_2$ and $t_1 = t_2$
+are atomic formulas. $\FPC[\tau]$ includes all formulas formed by closing the
+set of atomic formulas under the usual Boolean connectives, the first-order
+quantifiers (for vertex variables), and the inflationary fixed-point operator.
+The second-order variables, such as those that appear in an application of the
+fixed-point operator, are allowed to have mixed-type, i.e. we associate with a
+second-order variable $R$ a type $(k, l) \in \nats^2$ intended to mean that $R$
+is assigned to a subset of $U^k \times \nats^l$.
 
-In order to ensure that the data complexity of $\FPC$ is in polynomial time, we
-only allow bounded quantification when using number variables. In other words,
-if $Q \in \{\forall, \exists \}$, $\phi \in \FPC[\tau]$, $\mu$ is a number
-variable free in $\phi$, and $t$ is a number term, then $Q \mu \leq t . \phi$ is
-a formula of $\FPC[\tau]$. Similarly, if $\phi$ is a number term then $\# \mu
-\leq t .\phi$ is a number term in $\FPC[\tau]$.
+We also allow quantification over the number sort, but in order to ensure that
+the data complexity of $\FPC$ is in polynomial time we only allow bounded
+quantification. In other words, if $Q \in \{\forall, \exists \}$, $\phi \in
+\FPC[\tau]$, $\mu$ is a number variable free in $\phi$, and $t$ is a number
+term, then $Q \mu \leq t . \phi$ is a formula of $\FPC[\tau]$. Similarly, if
+$\phi$ is a number term then $\# \mu \leq t .\phi$ is a number term in
+$\FPC[\tau]$.
 
@@
 variable may only be assigned to a value at most equal to the the evaluation of
-the number term bounding the variable. The semantics of the $=$ and $\leq$
+the number term bounding the variable. The semantics of the `$=$' and `$\leq$'
 symbols are defined for number terms in the obvious manner. For a more detailed
@@
 detail on the syntax and semantics of $\FPR$ please see~\cite{GradelP15a}
-and~\cite{Dawar09logicswith}. As in the case of $\FPC$, we suppose the
-first-order variable are assigned one of two types. We call the first type
-\emph{vertex variables} and the second \emph{number variables} variables. Vertex
-variables are assigned to elements of the universe and number variables are
-assigned to natural numbers. All atomic formulas in $\FP[\tau]$ are atomic
-formulas in $\FPC[\tau]$. We say that $t$ is a \emph{number term} if $t$ is a
-number variable or if $t$ is an application of the \emph{rank operator}, i.e. $t
-= [\rank (\vec{x}, \vec {\nu} \leq \vec{t}, \vec{y}\vec{\mu} \leq \vec{s}, \pi
-\leq \eta). \phi]$, where $\phi$ is a number term, $\vec{t}$ and $\vec{s}$ are
-tuples of number terms bounding the sequences of number variables $\vec{\mu}$
-and $\vec{\nu}$, and $\eta$ is a number term bounding the number variable $\pi$.
-If $t_1$ and $t_2$ are number terms then $t_1 \leq t_2$ and $t_1 = t_2$ are
-atomic formulas. The formulas of $\FPR$ are then formed by closing the set of
-atomic formulas under the usual Boolean connectives, the first-order
-quantifiers, and the inflationary fixed-point operator. As in the case of
-$\FPC$, the second-order variables may have mixed-type and we only allow bounded
-quantification for number variables. We note additionally that formulas can be
-treated as number terms that evaluate to zero or one.
+and~\cite{Dawar09logicswith}. As in the case of $\FPC$, each variable is either
+a number or vertex variable, with vertex variables being assigned to elements of
+the universe and number variables assigned to natural numbers. All atomic
+formulas in $\FP[\tau]$ are atomic formulas in $\FPR[\tau]$. We say that $t$ is
+a \emph{number term} if $t$ is a number variable or if $t$ is an application of
+the \emph{rank operator}, i.e. $t = [\rank (\vec{x}, \vec {\nu} \leq \vec{t},
+\vec{y}\vec{\mu} \leq \vec{s}, \pi \leq \eta). \phi]$, where $\phi$ is a number
+term, $\vec{t}$ and $\vec{s}$ are tuples of number terms bounding the sequences
+of number variables $\vec{\mu}$ and $\vec{\nu}$, and $\eta$ is a number term
+bounding the number variable $\pi$. If $t_1$ and $t_2$ are number terms then
+$t_1 \leq t_2$ and $t_1 = t_2$ are atomic formulas. The formulas of $\FPR$ are
+then formed by closing the set of atomic formulas under the usual Boolean
+connectives, the first-order quantifiers, and the fixed-point operator. As in
+the case of $\FPC$, the second-order variables may have mixed-type and we only
+allow bounded quantification for number variables. We note additionally that
+formulas may be treated as number terms that evaluate to zero or one.
 
@@
 \vec{b}\vec{m}):= \phi^{\mathcal{A}}(\vec{a}\vec{n},\vec{b}\vec{m})$. For the
-structure $\mathcal{A}$ and assignment $\pi \mapsto p$, for $p \leq r^{A}$ prime,
-$[\rank (\vec{x}, \vec {\nu} \leq \vec{t}, \vec{y}\vec{\mu} \leq \vec{s}, \pi
-\leq r). \phi]$ evaluates to the rank of $M^{\mathcal{A}}_\phi$ mod $p$, where
-the matrix is understood to have entries in $\mathbb{F}_p$.
+structure $\mathcal{A}$ and assignment $\pi \mapsto p$, for $p \leq r^{A}$
+prime, $[\rank (\vec{x}, \vec {\nu} \leq \vec{t}, \vec{y}\vec{\mu} \leq \vec{s},
+\pi \leq r). \phi]$ evaluates to the rank of $M^{\mathcal{A}}_\phi$ mod $p$,
+where the entries in $M^{\mathcal{A}}$ are interpreted as elements of
+$\mathbb{F}_p$.
 
@@
 respect to the vocabulary $\tau$. This logic, first introduced by Dawar et
-al~\cite{Dawar09logicswith}, is an extension of fixed-point logic by \emph{rank
-  quantifiers}. For a prime $p$ and $r$ a natural number, a rank quantifier
-$\rank^r_p$ is defined such that $\rank^r_p\vec{x}\vec{y}. \phi$ is interpreted
-as $[\rank (\vec{x}, \vec{y}, \pi) . \phi] \leq t$, where $\pi$ is assigned to
-$p$ and $t$ evaluates to $r$. The arity of this quantifier is $\vert \vec{x}
-\vert + \vert \vert{y} \vert$. We thus have a rank quantifier for every prime
-$p$, natural number $r$ and arity $k$. Let $\mathcal{R}$ be the set of all such
-quantifiers. Let $\FPrk[\tau]$ be the closure of $\FP[\tau]$ under the
-quantifiers in $\mathcal{R}$.
+al~\cite{Dawar09logicswith}, is similar to $\FPR$, except that it extends $\FP$
+by \emph{rank quantifiers}, rather than a rank operator, that can decide if a
+definable matrix has a rank bounded by some constant. We define for each prime
+$p$, and natural number $r$, a rank quantifier $\rank^r_p$, such that
+$\rank^r_p\vec{x}\vec{y}. \phi$ is interpreted as $[\rank (\vec{x}, \vec{y},
+\pi) . \phi] \leq t_r$, where $\pi$ is assigned to $p$ and $t_r$ is a number
+term that evaluates to $r$. The arity of this quantifier is $\vert \vec{x} \vert
++ \vert \vec{y} \vert$. Let $\mathcal{R}$ be the set of all such quantifiers and
+$\FPrk[\tau]$ be the closure of $\FP[\tau]$ under $\mathcal{R}$.
 
@@
 
-For more detail on the syntax and semantics of these logics with rank
-quantifiers please see~\cite{Dawar09logicswith}. It is easy to see that $\FPrk
-\leq \FPR$ and $\FOrk \leq FOR$. In fact, Dawar et al.~\cite{Dawar09logicswith}
-shows that these inclusions are strict. Moreover, we note that $[\rank(\vec{x},
-\vec{y}). (\vec{x} = \vec{y}, \pi \leq r) \land \phi(\vec{x})]$ evaluates, for a
-structure $\mathcal{A}$ and any assignment $\pi \mapsto p$, to the number of
-assignments to $\vec{x}$ for which $\phi$ holds (i.e.\ $\vert \{\vec{a} \in
-U^{\vert \vec{x} \vert} : \mathcal{A} \models \phi[\vec{a}]\} \vert$). It
-follows that $\FPC \leq \FPR$ and $\FOC \leq \FOR$. Dawar et
-al.\cite{Dawar09logicswith} show that these inclusions are strict.
+For more detail on the syntax and semantics of logics rank quantifiers please
+see~\cite{Dawar09logicswith}. It is easy to see that $\FPrk \leq \FPR$ and
+$\FOrk \leq \FOR$. Moreover, we note that $[\rank(\vec{x}, \vec{y}).
+(\vec{x} = \vec{y}, \pi \leq r) \land \phi(\vec{x})]$ evaluates, for a structure
+$\mathcal{A}$ and any assignment $\pi \mapsto p$, to the number of assignments
+to $\vec{x}$ for which $\phi$ holds (i.e.\ $\vert \{\vec{a} \in U^{\vert \vec{x}
+  \vert} : \mathcal{A} \models \phi[\vec{a}]\} \vert$). It follows that $\FPC
+\leq \FPR$ and $\FOC \leq \FOR$. Dawar et al.\cite{Dawar09logicswith} show that
+all of these inclusions are strict.
 
@@
 Let $X$ be a set, we write $\sym_X$ to denote the symmetric group on the set
-$X$. For $n \in \nats$ we write $\sym_n$ to abbreviate $\sym_{[n]}$. We assume
-the reader is familiar with the basic theory of group actions.
+$X$. For $n \in \nats$ we write $\sym_n$ for $\sym_{[n]}$.
 
 Let $G$ be a group and let $H \leq G$. Let $X$ be a set on which a group action
-of $G$ is defined. This group action defines a natural action on
-$\mathcal{P}(X)$ (and hence $\mathcal{P}(\ldots(\mathcal{P}(X)))$) defined by
-$\sigma \cdot S := \{\sigma x : x \in S\}$ for $\sigma \in G$, $S \subseteq X$.
-Let $S \subseteq X$. We call $\stab_G(S) = \{\sigma in G : \forall x \in S \,
-\sigma x = x\}$ the \emph{stabiliser} of $S$ with respect to $G$. We call
-$\setstab_G(S) = \stab_G(\{S\}) = \{\sigma \in G : \sigma S = S\}$ the
-\emph{set-wise stabiliser} of $S$ with respect to $G$. We call $\orb_G(S) :=
-\{\sigma S : \sigma \in G\}$ the \emph{orbit} of $S$ with respect to $G$. If $S$
-is a singleton we omit the set bracers, e.g.\ we write $\orb_G(x)$ for
+of $G$ is defined. This group action can be lifted to a group action on
+$\mathcal{P}(X)$ (and hence $\mathcal{P}(\ldots(\mathcal{P}(X))\ldots)$) defined
+by $\sigma \cdot S := \{\sigma x : x \in S\}$ for $\sigma \in G$, $S \subseteq
+X$. Let $S \subseteq X$. We let $\stab_G(S) := \{\sigma \in G : \forall x \in S
+\,, \sigma x = x\}$ be the \emph{stabiliser} of $S$ with respect to $G$. We let
+$\setstab_G(S) := \stab_G(\{S\}) = \{\sigma \in G : \sigma S = S\}$ be the
+\emph{set-wise stabiliser} of $S$ with respect to $G$. We let $\orb_G(S) :=
+\{\sigma S : \sigma \in G\}$ be the \emph{orbit} of $S$ with respect to $G$. If
+$S$ is a singleton we omit the set bracers, e.g.\ we write $\orb_G(x)$ for
 $\orb_G(\{x\})$. If $G = \sym_n$ for some $n \in \nats$ we replace the subscript
-with the number $n$, e.g.\ we write $\orb_n(x)$ for $\orb_{\sym_n}(x)$. If the
-group $G$ is obvious from context we omit the subscript, e.g.\ we write
-$\orb(x)$ for $\orb_G(x)$.
+with the number $n$, e.g.\ we write $\orb_n(x)$ for $\orb_{\sym_n}(x)$, and if
+the group $G$ is obvious from context we omit the subscript entirely.
 
 \subsection{Boolean Functions, Bases, and Circuits}
-A (finite) \emph{Boolean function} is a function of the form $f: \{0,1\}^X
-\rightarrow \{0,1\}$, for some finite index set $X$. We often take $X = [n]$,
-and think of $f$ as taking $n$-length strings as inputs. We call a Boolean
-function $f: \{0,1\}^X \rightarrow \{0,1\}$ \emph{symmetric} if for all $\sigma
-\in \sym_X$ and $\vec{a} \in \{0,1\}^X$, $f (\vec{a} \sigma) = f(\vec{a})$. It
-follows that a Boolean function is symmetric if, and only if, the output of the
-function is entirely determined by the number of ones in the input. We say a
-function $f : \{0,1\}^{*} \rightarrow \{0,1\}$ is \emph{symmetric} if its
-restriction to inputs of size $n$ is symmetric for all $n$.
+A \emph{Boolean function} is a function of the form $f: \{0,1\}^X \rightarrow
+\{0,1\}$, for some finite index set $X$. We call a Boolean function $f:
+\{0,1\}^X \rightarrow \{0,1\}$ \emph{symmetric} if for all $\sigma \in \sym_X$
+and $\vec{a} \in \{0,1\}^X$, $f (\vec{a} \sigma) = f(\vec{a})$. It follows that
+a Boolean function is symmetric if, and only if, the output of the function is
+entirely determined by the number of ones in the input. We say a function $f :
+\{0,1\}^{*} \rightarrow \{0,1\}$ is \emph{symmetric} if its restriction to
+inputs of size $n$ is symmetric for all $n$.
 
@@
 a single internal gate with out-degree $0$ designated as the output gate. We say
-a circuit with $n$ input gates has \emph{order $n$}. Let $C$ be a Boolean
-circuit of order $n$ and let $\vec{a} := (a_1, \ldots, a_n) \in \{0,1\}^n$. The
-evaluation of $C$ for the input $\vec{a}$ is denoted by $C[\vec{a}]$ and is
-defined by induction on the structure of the circuit. We denote the evaluation
-of a gate $g$ in $C$ for the input $\vec{a}$ by $C[\vec{a}](g)$. If $g$ is an
-input gate, then $g = x_i$ and $C[\vec{a}](g) = a_i$. If $g$ is an internal gate
-then $g$ is labelled by a symbol denoting a Boolean operation, and
-$C[\vec{a}](g)$ is the result of applying that operation the string formed from
-the evaluations of those gates input to $g$. If $g$ is the output gate, let
-$C[\vec{a}] = C[\vec{a}](g)$.
+a circuit with $n$ input gates has \emph{order $n$}. The evaluation of circuit
+$C$ of order $n$ for the input $\vec{a} \in \{0,1\}^n$ is denoted by
+$C[\vec{a}]$ and computed by recursively evaluation the gates in the circuit. We
+denote the evaluation of a gate $g$ in $C$ for the input $\vec{a}$ by
+$C[\vec{a}](g)$. If $g$ is an input gate, then $g = x_i$ for some $i \in [n]$,
+and $C[\vec{a}](g) = a_i$. If $g$ is an internal gate then $g$ is labelled by a
+symbol denoting a Boolean operation, and $C[\vec{a}](g)$ is the result of
+applying that operation the string formed from the evaluations of those gates
+input to $g$. If $g$ is the output gate, let $C[\vec{a}] = C[\vec{a}](g)$.
 
-The \emph{size} of a circuit $C$, denoted by $\vert C \vert$ is the number of
-gates in the circuit. The \emph{depth} of a gate is the longest path from an
-input gate to that gate, and the \emph{depth} if the circuit is the depth of the
+The \emph{size} of a circuit $C$, denoted by $\vert C \vert$, is the number of
+gates in the circuit. The \emph{depth} of a gate $g$ is the longest path from an
+input gate to $g$, and the \emph{depth} if the circuit is the depth of the
 output gate. The \emph{width} of a circuit is the maximum size of a set of gates
@@
 \subsection{Circuits for Structures}
-Anderson and Dawar~\cite{AndersonD17} define a circuit that takes as input an
-encoding of a finite relational structure. Let $\tau$ be a vocabulary, $\BB$ be
-a basis of symmetric functions and $q, n \in \nats$. A \emph{circuit for
-  structures} (or \emph{circuit}) $C$ is a DAG with a designated set of input
-gates each labelled by a relation symbol $R \in \tau$ and a tuple $\vec{a} \in
-[n]^{\arty(R)}$, internal gates each labelled by an element of $\BB$, and a
-designated set of output gates, each labelled by a unique element of $[n]^q$.
+A \emph{circuit for structures} (or just \emph{circuit}), defined by Anderson
+and Dawar~\cite{AndersonD17}, takes as input an encoding of a $\tau$-structure
+and outputs a set of tuples from that structure. More formally, for a vocabulary
+$\tau$, a basis $\BB$ of symmetric functions, and $q, n \in \nats$, a
+\emph{circuit for structures} is a DAG with (i) a designated set of input gates,
+each labelled by a relation symbol $R \in \tau$ and a tuple $\vec{a} \in
+[n]^{\arty(R)}$, (ii) a set of internal gates, each labelled by an element of
+$\BB$, and (iii) a designated set of output gates, each labelled by a unique
+element of $[n]^q$.
 
-Let $\mathcal{A}$ be a $\tau$-structure of size $n$ and fix a bijection $\gamma$
-from the universe of $\mathcal{A}$ to $[n]$. This bijection defines an encoding
-of $\mathcal{A}$ as a $\tau$-structure with universe $[n]$. This encoding
-defines an assignment to the input gates of the circuit, assigning the gate
-labelled by the relation symbol $R$ and tuple $\vec{a})$ to one if, and only if,
-$\vec{a}$ is an element of the interpretation of $R$ in the encoding of
-$\mathcal{A}$. The circuit may then be recursively evaluated, with the
-evaluation of the output gates taken as the output of the circuit. We note that
-an evaluation of the output gates (and hence the output of the circuit) is an
-element of $\{0,1\}^{[n]^q}$. The circuit then associates with every
-$\tau$-structure and bijection $\gamma$ a set of $q$-tuples in $\mathcal{A}$.
+Let $\mathcal{A}$ be a $\tau$-structure of size $n$ and $\gamma$ be a bijection
+from the universe of $\mathcal{A}$ to $[n]$. The bijection $\gamma$ defines an
+encoding of $\mathcal{A}$ as a $\tau$-structure with universe $[n]$. The input
+gate labelled by the relation symbol $R$ and tuple $\vec{a}$ is assigned to one
+if, and only if, $\vec{a}$ is an element of the interpretation of $R$ in the
+encoding of $\mathcal{A}$. The circuit may then be recursively evaluated, and
+the evaluation of the output gates is taken as the output of the circuit. Since
+each output gate is labelled by an element of $[n]^q$, the output of the circuit
+is an element of $\{0,1\}^{[n]^q}$. In other words, a circuit maps a
+$\tau$-structure $\mathcal{A}$ and bijection $\gamma$ to a set of $q$-tuples in
+$\mathcal{A}$.
 
 A circuit is called \emph{invariant} if its output does not depend on the choice
-of $\gamma$. In this case the circuit defines a $q$-ary query of
+of $\gamma$. In this case the circuit defines a $q$-ary query on
 $\tau$-structures. If $C$ is an invariant circuit with $q = 0$, and the circuit
-has a single output gate and decides a property of $\tau$-structures. A circuit
+has a single output gate, then $C$ decides a property of $\tau$-structures. A circuit
 is called \emph{symmetric} if every permutation on the universe $[n]$, each of

### 2018-02-11 sections/translating-formulas-to-cicuits.tex
feb 11

@@
 
-  Suppose $\tau$ is not empty. Let $R \in \tau$. We now construct a $C$ that
-  translates $\theta(\vec{x})$ at $n$. We first pre-proccess the formula $\theta(\vec{x})$
+  Suppose $\tau$ is not empty. Let $R \in \tau$. We now construct a $C'$ that,
+  but for transparency, translates $\theta(\vec{x})$ at $n$.
 
-  Let $\op{no-op}(y) := (R(y, y) \land (\neg R(y, y)))$. Let $\vec{y} := (y_1,
-  \ldots, y_k)$ be a vector of variables and $\op{add-tag} (\vec{y}) :=
-  \op{no-op}(y_1) \land (\op{no-op}(y_2) \land ( \op{no-op}(y_2) \land ( \ldots
-  \land (\op{no-op}(y_k)) \ldots)))$. From $\theta (\vec{x})$ we construct a new
-  formula $\theta' (\vec{x})$ by replacing each sub-formula $\phi(\vec{y})$ of
-  the form $\rank^r_p \vec{w} \vec{z} . \psi$ by the sub-formula $\rank^r_p
-  \vec{w}\vec{z} . ((\forall u . u = u) \land \phi) \land \op{add-tag}(\vec{w}
-  \cup \vec{z})$.
+  % We first
+  % pre-proccess the formula $\theta(\vec{x})$
+
+  % Let $\op{no-op}(y) := (R(y, y) \land (\neg R(y, y)))$. Let $\vec{y} := (y_1,
+  % \ldots, y_k)$ be a vector of variables and $\op{add-tag} (\vec{y}) :=
+  % \op{no-op}(y_1) \land (\op{no-op}(y_2) \land ( \op{no-op}(y_2) \land (
+  % \ldots
+  % \land (\op{no-op}(y_k)) \ldots)))$. From $\theta (\vec{x})$ we construct a
+  % new
+  % formula $\theta' (\vec{x})$ by replacing each sub-formula $\phi(\vec{y})$ of
+  % the form $\rank^r_p \vec{w} \vec{z} . \psi$ by the sub-formula $\rank^r_p
+  % \vec{w}\vec{z} . ((\forall u . u = u) \land \phi) \land \op{add-tag}(\vec{w}
+  % \cup \vec{z})$.
 
   Fix $n \in \nats$. For each $\psi \in \cl{\theta'}$ let $G_\psi := \{g_{\psi,
-    \alpha} : \alpha \in [n]^{\free{\psi}} \}$. Let $G_c := \{g_0, g_1\}$. Let
-  $G := G_c \cup (\bigcup_{\psi \in \cl{\theta'}} G_{\psi})$. We define
-  $\Sigma$, $\Lambda$ and $L$ as follows. Let $\Sigma (g_1) = 1$ and $\Sigma
-  (g_0) = 0$. If $g_{\psi, \alpha} \in G \setminus G_c$.
+    \alpha} : \alpha \in [n]^{\free{\psi}} \}$. Let $G_{\text{sub}} :=
+  \bigcup_{\psi \in \cl{\theta}} G_{\psi}$ and $G_c := \{g_0, g_1\}$. Let $G' := G_c \cup
+    G_{\text{sub}}$. We define $\Sigma'$, $\Lambda'$ and $L'$ as follows. Let
+    $\Sigma' (g_1) = 1$ and $\Sigma' (g_0) = 0$. If $g_{\psi, \alpha} \in G'
+    \setminus G_c$.
 
@@
     \item If $\psi$ is of the form $T(\vec{y})$ for some $T \in \tau$, then
-    $\Sigma (g_{\psi, \alpha}) = T$ and $\Lambda_T (g_{\psi, \alpha}) = \alpha
-    \vec{y}$.
-  \item If $\psi$ is of the form $(y_1 = y_2)$, then $\Sigma (g_{\psi, \alpha})
-    = \land[1]$ and $L(g) : [1] \rightarrow G$ by $L(g)(1) = g_1$ if $\alpha
-    (y_1) = \alpha (y_2)$ and $L(g)(1) = g_0$ otherwise.
+      $\Sigma' (g_{\psi, \alpha}) = T$ and $\Lambda_T' (g_{\psi, \alpha}) =
+      \alpha \vec{y}$.
+    \item If $\psi$ is of the form $(y_1 = y_2)$, then $\Sigma' (g_{\psi,
+        \alpha}) = \land[1]$ and $L'(g) : [1] \rightarrow G$ by $L(g)(1) = g_1$
+      if $\alpha (y_1) = \alpha (y_2)$ and $L'(g)(1) = g_0$ otherwise.
     \item If $\psi$ is of the form $\rank^r_p \vec{w} \vec{z}. \phi$, let $a =
-    n^{\vert \vec{w}\vert}$ and $b = n^{\vert \vec{z}\vert}$, and $\Sigma
-    (g_{\psi, \alpha}) = \rank[a, b]$. Let $L(g) : [a] \times [b] \rightarrow G$
-    be defined by $L(g)(i,j) = g_{\phi, \beta}$, where $\beta : \vec{w} \cup
-    \vec{z} \cup \vec{y} \rightarrow [n]$ is such that $\alpha \subseteq \beta$
-    and such $\beta \vec{y}$ and $\beta \vec{z}$ are the $i$th and $j$th
-    elements of $[n]^{\vert \vec{w} \vert}$ and $[n]^{\vert \vec{z} \vert}$ in
-    the lexicographical ordering.
-  \item If $\psi$ is of the form $Q z . \phi(\vec{y}, z)$, for $Q \in \{\forall,
-    \exists\}$, then if $Q = \forall$ we have $\Sigma (g_{\psi, \alpha}) = \land
-    [n]$, otherwise $\Sigma (g_{\psi, \alpha}) = \lor [n]$. Let $L(g) : [n]
-    \rightarrow G$ be defined by $L(g)(i) = g_{\phi, \beta_i}$, where $\beta_i
-    \in [n]^{\vec{y} \cup \{z\}}$ and $\alpha \subseteq \beta_i$ and $\beta_i
-    (z) = i$.
+      n^{\vert \vec{w}\vert}$ and $b = n^{\vert \vec{z}\vert}$, and $\Sigma'
+      (g_{\psi, \alpha}) = \rank[a, b]$. Let $L'(g) : [a] \times [b] \rightarrow
+      G$ be defined by $L'(g)(i,j) = g_{\phi, \beta}$, where $\beta : \vec{w}
+      \cup \vec{z} \cup \vec{y} \rightarrow [n]$ is such that $\alpha \subseteq
+      \beta$ and such $\beta \vec{y}$ and $\beta \vec{z}$ are the $i$th and
+      $j$th elements of $[n]^{\vert \vec{w} \vert}$ and $[n]^{\vert \vec{z}
+        \vert}$ in the lexicographical ordering.
+    \item If $\psi$ is of the form $Q z . \phi(\vec{y}, z)$, for $Q \in
+      \{\forall, \exists\}$, then if $Q = \forall$ we have $\Sigma' (g_{\psi,
+        \alpha}) = \land [n]$, otherwise $\Sigma' (g_{\psi, \alpha}) = \lor
+      [n]$. Let $L'(g) : [n] \rightarrow G$ be defined by $L'(g)(i) = g_{\phi,
+        \beta_i}$, where $\beta_i \in [n]^{\vec{y} \cup \{z\}}$ and $\alpha
+      \subseteq \beta_i$ and $\beta_i (z) = i$.
     \item If $\psi$ has free variables $\vec{y}$ and is of the form $\phi_1
-    (\vec{y}_1) \land \phi_2(\vec{y}_2)$, where $\vec{y_1}, \vec{y_2} \subseteq
-    \vec{y}$, then $\Sigma(g_{\psi, \alpha}) = \land[2]$ and $L(g) : [2]
-    \rightarrow G$ is defined by $L(g)(i) = g_{\phi_i, \beta_i}$ where $\beta_i
-    \in [n]^{\vec{y}_i}$ and $\beta_i \subseteq \alpha$ for $i \in [2]$. The
-    same approach is used in the disjunctive case.
-  \item if $\psi$ is of the form $\neg \phi$ then $\Sigma (g_{\psi, \alpha}) =
-    \neg$ and $L(g): [1] \rightarrow G$, where $L(g)(1) = g_{\phi, \alpha}$.
+      (\vec{y}_1) \land \phi_2(\vec{y}_2)$, where $\vec{y_1}, \vec{y_2}
+      \subseteq \vec{y}$, then $\Sigma'(g_{\psi, \alpha}) = \land[2]$ and $L'(g)
+      : [2] \rightarrow G$ is defined by $L'(g)(i) = g_{\phi_i, \beta_i}$ where
+      $\beta_i \in [n]^{\vec{y}_i}$ and $\beta_i \subseteq \alpha$ for $i \in
+      [2]$. The same approach is used in the disjunctive case.
+    \item if $\psi$ is of the form $\neg \phi$ then $\Sigma' (g_{\psi, \alpha})
+      = \neg$ and $L'(g): [1] \rightarrow G$, where $L'(g)(1) = g_{\phi,
+        \alpha}$.
     \end{itemizens}
 
-  We let $\Omega : [n]^k \rightarrow G$ be defined by $\Omega (\vec{a}) =
-  g_{\theta', \alpha}$, where $\alpha \vec{x} = \vec{a}$, for all $\vec{a} \in
-  [n]^k$. Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$. We notice
-  that $\vert C \vert \leq n^{\width(\theta')} \vert \cl{\theta} \vert$. It can
-  be shown that $C$ can be constructed in time bounded by a polynomial in the
-  size of $C$.
+    We let $\Omega' : [n]^k \rightarrow G$ be defined by $\Omega' (\vec{a}) =
+    g_{\theta, \alpha}$, where $\alpha \vec{x} = \vec{a}$, for all $\vec{a} \in
+    [n]^k$. Let $C' := \langle G', \Omega', \Sigma', \Lambda', L' \rangle$. We
+    notice that $\vert C' \vert \leq n^{\width(\theta)} \vert \cl{\theta}
+    \vert$. It can be shown that $C'$ can be constructed in time bounded by a
+    polynomial in the size of $C'$.
 
-  We now show that $C$ translates $\theta(\vec{x})$ for $n$. It is obvious that
-  $C$ has order $n$. Let $\sigma \in \sym_n$. Let $\pi_\sigma : G \rightarrow G$
-  be a defined such that $\pi (g) = g$ if $g \in G_c$ and $\pi_\sigma(g_{\psi,
-    \alpha}) = g_{\psi, \sigma \alpha}$ for all $\psi \in \cl{\theta}$ and
-  $\alpha \in n^{\free(\psi)}$. It is easy to see that $\pi_\sigma$ is an
-  automorphism of $C$ extending $\sigma$. It follows that $C$ is symmetric. Let
-  $g := g_{\psi, \alpha} \in G$ be a rank gate and let $h, h' \in H_g$. Suppose
-  $\psi (\vec{y}) := \rank^r_p \vec{w} \vec{z}. \phi$ and $h := g_{\phi, \beta}$
-  and $h' := g_{\phi, \beta'}$ are syntactically-equivalent. From the
-  construction of $\theta'$ we have that $\phi$ must be of a particular form.
-  Suppose $\phi = \eta \land \op{add-tag}(\vec{w} \cup \vec{z})$. Let $\gamma$
-  and $\gamma'$ be the restrictions of $\beta$ and $\beta'$ to $\vec{w} \cup
-  \vec{z}$, respectively, and let $\zeta(\vec{w}\cup\vec{z}) :=
-  \op{add-tag}(\vec{w} \cup \vec{z})$. The $\op{add-tag} (\vec{w} \cup \vec{z})$
+    It is obvious that $C'$ has order $n$. Let $\sigma \in \sym_n$. Let
+    $\pi_\sigma' : G' \rightarrow G'$ be a defined such that $\pi_{\sigma}' (g)
+    = g$ if $g \in G_c$ and $\pi_\sigma'(g_{\psi, \alpha}) = g_{\psi, \sigma
+      \alpha}$ for all $\psi \in \cl{\theta}$ and $\alpha \in n^{\free(\psi)}$.
+    It can be seen that $\pi_\sigma$ is an automorphism of $C'$ extending
+    $\sigma$. It follows that $C'$ is symmetric.
 
-  The structure of this formula gives us that $h$ is syntactically-equivalent to
-  $h'$ if, and only if, $g_{\zeta , \beta'}$
+    If $C'$ contains no rank gates then output $C := C'$. Suppose $C'$ contains
+    at least one rank-gate. Let $\psi \in \cl{\theta}$, and suppose $\psi
+    (\vec{y}) := \rank^r_p \vec{w} \vec{z}. \phi$. Let $T_{\psi} : G_{\psi}
+    \rightarrow [n]^{\vert \vec{w} \vert + \vert \vec{z} \vert}$ be defined by
+    $T_{\psi} (g_{\psi, \alpha}) = \alpha \vec{y}$ for all $g_{\psi, \alpha} \in
+    G_{\psi}$. Let $T$ be the union of all $T_{\psi}$ and $H$ the union of all
+    $G_{\psi}$ for all $\psi \in \cl{\theta}$ an application of the rank
+    operator. Let $C := \op{tag-all}(C', R, H, T)$. We note that $\op{tag-all}$
+    may be computed in time polynomial in the size of the input circuit.
+
+    Let $a \in [n]$ and let $\op{no-op} (a) := R(a, a) \lor (\neg (R(a, a))$.
+    For $\psi (\vec{y})$
+
+    Let $(b_1, \ldots, b_m) := \beta (\vec{w} \cup \vec{z})$. The $\op{tag-all}
+    function replaces each input $g_{\phi, \beta}$ of the rank gate $g_{\psi,
+      \alpha}$ with the circuit $g_{\phi, \beta} \land \op{no-op}(b_1) \land
+    (\op{no-op}(b_2) \land ( \op{no-op}(b_2) \land (\ldots \land
+    (\op{no-op}(b_m)) \ldots)))$. This construction does not effect the
+    evaluation of any rank gate in the cirucit and ensures that no two to
+    $g_{\psi,\alpha}$ in $C$ are syntactically-equivilent.
+
+    $of the form $$R(a, a) \lor (\neg R(a, a))$ that encode the assignment to
+    $\vec{w}\cup \vec{z}$.
+
+    We have that $C$ is transparent, has order $n$, and $C$ and $C'$ decide the
+    same query. It remains to show that $C$ is still symmetric.
+
+    However, the $\op{tag-all}$ operation adds a tower of tautologies of the
+    form $R(a, \ldots, a) \lor (\neg R (a, \ldots, a))$
+
+    Let $g := g_{\psi, \alpha} \in G$ be a rank gate and let $h, h' \in H_g$.
+    Suppose $\psi (\vec{y}) := \rank^r_p \vec{w} \vec{z}. \phi$ and $h :=
+    g_{\phi, \beta}$ and $h' := g_{\phi, \beta'}$ are syntactically-equivalent.
+    From the construction of $\theta'$ we have that $\phi$ must be of a
+    particular form. Suppose $\phi = \eta \land \op{add-tag}(\vec{w} \cup
+    \vec{z})$. Let $\gamma$ and $\gamma'$ be the restrictions of $\beta$ and
+    $\beta'$ to $\vec{w} \cup \vec{z}$, respectively, and let
+    $\zeta(\vec{w}\cup\vec{z}) := \op{add-tag}(\vec{w} \cup \vec{z})$. The
+    $\op{add-tag} (\vec{w} \cup \vec{z})$
+
+    The structure of this formula gives us that $h$ is syntactically-equivalent
+    to $h'$ if, and only if, $g_{\zeta , \beta'}$
 

### 2018-02-13 sections/background.tex
FEB 13

@@
 in $\phi$ are among those in $\vec{x}$. Suppose $\vec{x} = (x_1, \ldots , x_k)$,
-and let $\mathcal{A}$ be a $\tau$-structure with universe $U$, and let $\vec{a}
-\in U^k$. We write $\mathcal{A} \models_L \phi[\vec{a}]$ if, and only if, $\phi$
-is true in $\mathcal{A}$ with respect to $L$ where for all $i \in [k]$ each
-variable $x_i$ is assigned to $a_i$. If the logic is obvious from context we
-omit the subscript and just write $\mathcal{A} \models \phi[\vec{a}]$.
+and let $\mathcal{A}$ be a $\tau$-structure with universe $U$. We call a
+function $\alpha : {x_1, \ldots, x_k} \rightarrow U$ an \emph{assignment}. If
+$\vec{a}\in U^k$, we write $\alpha^{\vec{x}}_{\vec{a}}$ to denote the assignment
+that maps the variable $x_i$ to $a_i$ for $i \in [k]$. We say that two
+assignments $\alpha$ and $\beta$ are \emph{compatible} if $\alpha$ and $\beta$
+agree on the intersection of their domain. We write $\mathcal{A} \models_L
+\phi[\alpha]$ if, and only if, $\phi$ is true in $\mathcal{A}$ with respect to
+$L$ where for all $i \in [k]$ each variable $x_i$ is assigned to $\alpha(x_i)$.
+If the logic is obvious from context we omit the subscript and just write
+$\mathcal{A} \models \phi[\vec{a}]$.
 

### 2018-02-13 sections/translating-formulas-to-cicuits.tex
FEB 13

--- 2018-02-05 sections/translating-formulas-to-cicuits.tex
@@
 
+\begin{definition}
+  The function $\op{tag-inputs}$ maps a circuit $C := \langle G, \Omega, \Sigma,
+  \Lambda, L \rangle$, a relation symbol $R \in \tau$, and $H \subseteq G$
+\end{definition}
+
 \subsection{Translating FPR to Symmetric Matrix Circuits}
-In this subsection we translate $\FPR$-formulas into families of transparent
-rank-circuits. In particular, we now show that for $\theta(\vec{x}) \in
-\FPR[\tau]$ there exists a $P$-uniform family of symmetric rank-circuits
-$(C_n)_{n \in \nats}$ such that the query computed by $(C_n)_{n \in \nats}$ is
-equal to the query defined by $\theta (\vec{x})$.
+% In this subsection we translate $\FPR$-formulas into families of transparent
+% rank-circuits. In particular, we now show that for $\theta(\vec{x}) \in
+% \FPR[\tau]$ there exists a $P$-uniform family of symmetric rank-circuits
+% $(C_n)_{n \in \nats}$ such that the query computed by $(C_n)_{n \in \nats}$ is
+% equal to the query defined by $\theta (\vec{x})$.
+
+We say that a circuit $C$ \emph{translates} a formula $\psi(\vec{x})$ for $n \in
+\nats$ if $C$ is a transparent symmetric rank-circuit of order $n$, $C$ is
+defined over the same vocabulary as $\psi$, and $C$ computes the query defined
+by $\psi(\vec{x})$ on structures of size $n$. We say a family of circuits
+$(C_n)_{n \in \nats}$ \emph{translates} a formula $\psi (\vec{x})$ if $(C_n)_{n
+  \in \nats}$ is $\PT$-uniform and for all $n \in \nats$, $C_n$ translates
+$\psi(\vec{x})$ for $n$.
+
+We now prove that for every $\FOrk$-formula $\theta(\vec{x})$ and $n \in \nats$
+there exists a circuit $C$ that translates $\theta(\vec{x})$ for $n$. We
+construct $C$ by including for each sub-formula $\psi \in \cl{\theta}$ and
+assignment $\alpha \in [n]^{\free{\psi}}$ a gate $g_{\psi[\alpha]}$. The
+children of $g_{\psi[\alpha]}$ are the gates of the form $g_{\phi[\beta]}$,
+where $\phi$ is an immediate sub-formula of $\psi$ and $\beta$ is an assignment
+to the free variables of $\psi$ that is compatible with the assignment $\alpha$.
+The gate $g_{\psi[\alpha]}$ for an input structure over the universe $[n]$
+evaluates to one if, and only if, $\psi$ holds for the input structure with the
+assignment $\alpha$. We now construct the translation of $\theta$ for $n$, and
+prove that the construction can be completed in a time bound that depends on $n$
+and certain properties of the formula $\theta$.
+
+\begin{lem}
+  There is an algorithm that takes in a $\FOrk$-formula $\theta(\vec{x})$ and $n
+  \in \nats$ and outputs a rank-circuit $C$ that translates $\theta(\vec{x})$
+  for $n$. Moreover, there is a polynomial in $p$ such that for an input
+  $(\theta(\vec{x}), n)$ the algorithm terminates in at most
+  $p(n^{\width(\theta)}\vert \cl{\theta} \vert)$ many steps.
+  \label{lem:translating-FOrk}
+\end{lem}
+\begin{proof}
+  Let $\tau$ be the vocabulary of $\theta(\vec{x})$. Let $k := \width(\theta)$.
+  Suppose $\tau$ is empty. Since the vocabulary of $\tau$ is empty, all of the
+  atomic formula in $\theta(\vec{x})$ are of the form $y_1 = y_2$, where $y_1$
+  and $y_2$ are variables. It can be shown that, for an assignment $\vec{a}$ to
+  $\vec{x}$, we can evaluate $[n] \models \theta[\vec{a}]$ in time polynomial in
+  $n^{k} \vert \cl{\theta} \vert$. Let $f : [n]^k \rightarrow \{0,1\}$ be
+  defined such that $f (\vec{a}) = 1$ if, and only if, $[n] \models
+  \theta[\vec{a}]$. Let $C := \langle G, \Sigma, \Omega, \Lambda, L \rangle$,
+  where
+  \begin{itemizens}
+  \item $G = \{g_0, g_1\} \cup \{g_{\vec{a}} : \vec{a} \in [n]^{k}\}$,
+  \item $\Sigma (g_0) = 0$, $\Sigma (g_1) = 1$ and $\Sigma (g_{\vec{a}}) =
+    \land[1]$,
+  \item $\Omega : [n]^k \rightarrow G$ is defined by $\Omega(\vec{a}) =
+    g_{\vec{a}}$ for all $\vec{a} \in [n]^k$,
+  \item $\Lambda = \emptyset$, and
+  \item for $\vec{a} \in [n]^k$, $L(g_{\vec{a}}) : [1] \rightarrow G$ is defined
+    by $L(g_{\vec{a}})(1) = g_{f(\vec{a})}$.
+  \end{itemizens}
+
+  Since $C$ has symmetric gates, $C$ is transparent. Notice that, since
+  $\theta(\vec{x})$ defines a query on structures over the empty vocabulary, we
+  have for all $\vec{a} \in [n]^k$, $\sigma \in \sym_n$, $f(\sigma \vec{a}) =
+  f(\vec{a})$. For $\sigma \in \sym_n$, let $\pi_\sigma : G \rightarrow G$ be a
+  bijection that fixes the constant gates and such that $\pi_{\sigma}
+  g_{\vec{a}} = g_{\sigma \vec{a}}$ for all $\vec{a} \in [n]^k$. Then
+  $\pi_\sigma \Omega (\vec{a}) = \pi_\sigma g_{\vec{a}} = g_{\sigma \vec{a}} =
+  \Omega (\sigma \vec{a})$. It follows that $\pi_\sigma$ is an automorphism of
+  the circuit extending $\sigma$, and $C$ is symmetric. We thus have that $C$
+  translates $\theta(\vec{x})$ for $n$.
+
+  Suppose $\tau$ is not empty. Let $R \in \tau$. We first define two helper
+  formulas. For a variable $y$ let $\op{no-op}(y) := (R(y, y) \land (\neg R(y,
+  y)))$. For a sequence of variables $\vec{y} = (y_1, \ldots, y_m)$ let
+  $\op{tag} (\vec{y}) := \op{no-op}(y_1) \land (\op{no-op}(y_2) \land (
+  \op{no-op}(y_2) \land ( \ldots \land (\op{no-op}(y_m)) \ldots)))$. Let
+  $\lambda (\vec{x})$ be constructed from $\theta(\vec{x})$ by replacing each
+  sub-formula $\psi(\vec{y})$ of the form $\rank^r_p \vec{w} \vec{z} . \phi$
+  with the formula $\rank^r_p \vec{w}\vec{z} . ((\forall u . u = u) \land \phi)
+  \land \op{tag}(\vec{w} \cup \vec{z})$. Since the sub-formulas added are
+  tautologies, the matrix defined at this point remains unchanged, and so
+  $\lambda (\vec{x})$ and $\theta (\vec{x})$ are equivalent. The idea is that
+  $\op{tag}$ adds a tower of conjunctions of tautologies each referencing
+  exactly one variable from $\vec{w} \cup \vec{z}$, and so encoding the order of
+  the sequence of variables $\vec{w} \cup \vec{z}$ in the syntax of the formula.
+  When we define a circuit from this formula, each input to the rank gate will
+  be `tagged' with a unique assignment to $\vec{w} \cup \vec{z}$, preventing two
+  inputs from being syntactically-equivalent, and so ensuring the circuit is
+  transparent.
+
+  % We also relabel the bound variables in $\lambda(\vec{x})$ such that there
+  % are
+  % no two sub-formulas $\psi$ and $\psi'$ such that $\psi$ and $\psi'$ are
+  % equal
+  % up to a renaming of those variables that are bound in $\psi$ or $\psi'$.
+
+  % Let $\psi (\vec{y}) \in \FOrk$ and $\alpha \in [n]^{\vec{y}}$. Let
+  % $\psi[\alpha]$ be the result of substituting $\vec{y}$ for $\alpha(y)$ in
+  % $\psi(\vec{y})$. If $\psi$ is of the form $y_1 = y_2$. Then $\psi [\alpha] =
+  % 1$ if $\alpha(y_1) = \alpha (y_2)$ and $\psi[\alpha] = 0$ otherwise.
+
+  We note that $\lambda(\vec{x})$ has the same width as $\theta(\vec{x})$, and
+  that the number of sub-formulas in $\lambda(\vec{x})$ is at most $\vert
+  \cl{\theta} \vert (5 + 4\width(\theta))$. We now construct a circuit $C$ and
+  show that $C$ translates $\lambda(\vec{x})$ (and hence $\theta(\vec{x})$) at
+  $n$.
+
+  % We first
+  % pre-proccess the formula $\theta(\vec{x})$
+
+  % Let $\op{no-op}(y) := (R(y, y) \land (\neg R(y, y)))$. Let $\vec{y} := (y_1,
+  % \ldots, y_k)$ be a vector of variables and $\op{add-tag} (\vec{y}) :=
+  % \op{no-op}(y_1) \land (\op{no-op}(y_2) \land ( \op{no-op}(y_2) \land (
+  % \ldots
+  % \land (\op{no-op}(y_k)) \ldots)))$. From $\theta (\vec{x})$ we construct a
+  % new
+  % formula $\theta' (\vec{x})$ by replacing each sub-formula $\phi(\vec{y})$ of
+  % the form $\rank^r_p \vec{w} \vec{z} . \psi$ by the sub-formula $\rank^r_p
+  % \vec{w}\vec{z} . ((\forall u . u = u) \land \phi) \land \op{add-tag}(\vec{w}
+  % \cup \vec{z})$.
+
+  Let $\vec{y}$ be a sequence of variables. We abuse notation and write $\alpha
+  :\vec{y} \rightarrow A$ to indicate that $\alpha$ maps the variables in the
+  sequence $\vec{y}$ to elements of the set $A$.
+
+  Fix $n \in \nats$. Let $\psi \in \FOrk$ and $\alpha \in [n]^{\free {\psi}}$.
+  We let $\psi[\alpha]$ be the result of substituting each occurrence of the
+  free variable $y \in \free{\psi}$ in $\psi$ with $\alpha(y)$. If $\psi$ is of
+  the form $y_1 = y_2$. Then $\psi [\alpha] = 1$ if $\alpha(y_1) = \alpha (y_2)$
+  and $\psi[\alpha] = 0$ otherwise. We call $\psi[\alpha]$ a \emph{ground
+    formula}. For each $\psi \in \cl{\theta}$ let $G_\psi := \{g_{\phi[\alpha]}
+  : \alpha \in [n]^{\free{\psi}} \}$. Let $G := \bigcup_{\psi \in \cl{\lambda}}
+  G_{\psi}$. We define $\Sigma$, $\Lambda$ and $L$ as follows. Let $\Sigma (g_1)
+  = 1$ and $\Sigma (g_0) = 0$. Let $g := g_{\psi[\alpha]} \in G$.
+
+  \begin{itemizens}
+  \item If $\psi[\alpha] = T(\vec{a})$ for some $T \in \tau$ and $\vec{a} \in
+    \arty(T)$, then $\Sigma (g) = T$ and $\Lambda_T (g) = \vec{a}$.
+  \item If $\psi[\alpha]$ is $0$ or $1$, then $\Sigma (g) = \psi[\alpha]$.
+  \item If $\psi$ is of the form $\rank^r_p \vec{w} \vec{z}. \phi$, let $A =
+    [n]^{\vert \vec{w}\vert}$ and $B = [n]^{\vert \vec{z}\vert}$, and $\Sigma
+    (g_{\psi, \alpha}) = \rank[A, B]$. Let $L(g) : A \times B \rightarrow G$ be
+    defined by $L(g)(\vec{a},\vec{b}) = g_{\phi[\beta]}$, where $\beta \in
+    [n]^{\free{\phi}}$, and where $\alpha$, and the assignments
+    $\alpha^{\vec{w}}_{\vec{a}}$ and $\alpha^{\vec{z}}_{\vec{b}}$, are
+    compatible with $\beta$.
+  \item If $\psi$ is of the form $Q z . \phi(\vec{y}, z)$, for $Q \in \{\forall,
+    \exists\}$, then if $Q = \forall$ we have $\Sigma (g) = \land [n]$,
+    otherwise $\Sigma (g) = \lor [n]$. Let $L(g) : [n] \rightarrow G$ be defined
+    for $i \in [n]$ by $L(g)(i) = g_{\phi[\beta_i]}$, where $\beta_i \in
+    [n]^{\free{\psi}}$, and where both $\alpha$ and $\alpha^{z}_{i}$ are
+    compatible with $\beta_i$.
+  \item If $\psi$ is of the form $\phi_1 \land \phi_2$, then $\Sigma(g) =
+    \land[2]$ and $L(g) : [2] \rightarrow G$ is defined for $i \in [2]$ by
+    $L(g)(i) = g_{\phi_i[\beta_i]}$, where $\beta_i \in [n]^{\free{\psi}}$ and
+    $\beta_i$ is compatible with $\alpha$. The same approach is used in the
+    disjunctive case.
+  \item if $\psi$ is of the form $\neg \phi$ then $\Sigma (g) = \neg$ and $L(g):
+    [1] \rightarrow G$, where $L(g)(1) = g_{\phi[\alpha]}$.
+  \end{itemizens}
+
+  We let $\Omega : [n]^k \rightarrow G$ be defined by $\Omega (\vec{a}) =
+  g_{\lambda [\alpha]}$, where $\alpha := \alpha^{\vec{x}}_{\vec{a}}$, for all
+  $\vec{a} \in [n]^k$. Suppose $\Omega (\vec{a}) = g_c$, where $ c \in {0,1}$.
+  Then $\lambda$ (and $\theta$) is of the form $(y_1 = y_2)$. But then the
+  vocabulary of $\theta$ is empty, contradicting our assumption. Suppose $\Omega
+  (\vec{a}) = \Omega(\vec{b})$ for $\vec{a}, \vec{b} \in [n]^k$. Then
+  $g_{\lambda[\alpha^{\vec{x}}_{\vec{a}}]} =
+  g_{\lambda[\alpha^{\vec{x}}_{\vec{b}}]}$, and so $\alpha^{\vec{x}}_{\vec{a}} =
+  \alpha^{\vec{x}}_{\vec{b}}$, and $\vec{a} = \vec{b}$. It follows that $\Omega$
+  is injective. Let $T \in \tau$, and let $g_{\psi[\alpha]}, g_{\phi[\beta]} \in
+  G$ be such that $\Lambda_T (g_{\psi[\alpha]}) = \Lambda_T (g_{\phi[\beta]})$.
+  Then $\psi[\alpha] = \Lambda_T (g_{\psi[\alpha]}) = \Lambda_T
+  (g_{\phi[\beta]}) = \phi[\beta]$, and so $g_{\psi[\alpha]} = g_{\phi[\beta]}$.
+  It follows that $\Lambda_T$ is injective. We thus have that $C := \langle G,
+  \Omega, \Sigma, \Lambda, L \rangle$ is a circuit of order $n$.
+
+\begin{claim}
+  The circuit $C$ is symmetric.
+\end{claim}
+\begin{proof}
+  Let $\pi_\sigma : G \rightarrow G$ be a function that fixes constant gates for
+  such that for all non-constant gates $g_{\psi[\alpha]} \in G$, $\pi_{\sigma}
+  g_{\psi [\alpha]} = g_{\psi[\sigma \alpha]}$. It is easy to see that
+  $\pi_\sigma$ is a bijection. We now show that $\pi_{\sigma}$ is an
+  automorphism of the circuit extending $\sigma$. Let $g_{\psi[\alpha]} := g \in
+  G$. Since the formula is unchanged by $\pi_\sigma$, we have $\Sigma(g) =
+  \Sigma (\pi_{\sigma} g)$. Suppose $g$ is an input gate. If $g$ is a constant
+  gate then $\pi_\sigma g = g$. If $g$ is a relational gate, then $\psi$ is of
+  the form $T(\vec{y})$ for some relation symbol $T$ and $\Lambda_T
+  (g_{\psi[\alpha]}) = \alpha \vec{y}$, and $\Lambda (\pi_{\sigma}
+  g_{\psi[\alpha]}) = \Lambda g_{\psi[\sigma \alpha]} = \sigma \alpha \vec{y} =
+  \sigma \Lambda_T (g_{\psi[\alpha]})$. Suppose $g$ is an internal gate. From
+  the construction of the circuit we have that if $g_{\phi[\beta]} \in H_g$ then
+  $\phi$ must be an immediate sub-formula of $\psi$ and so $g_{\phi[\sigma
+    \beta]}$ is a child of $g_{\psi[\sigma \alpha]} = \pi_{\sigma} g$. It
+  follows that $H_{\pi_\sigma g} = \pi_\sigma H_g$. If $g$ is a symmetric gate,
+  this is sufficient to conclude that $\pi_{\sigma} L(g)$ is
+  isomorphism-equivalent to $L(\pi_{\sigma} g)$. If $g$ not a symmetric gate
+  then it is a rank gate, and so $\psi$ is of the form $\rank^r_p \vec{w}
+  \vec{z} \phi$. Let $\vec{a} \in A$ and $\vec{b} \in B$, and note that
+  $\pi_\sigma L(g) (\vec{a}, \vec{b}) = \pi_{\sigma} g_{\phi[\beta]}$, where
+  $\beta \in [n]^{\free {\phi}}$ is compatible with $\alpha$,
+  $\alpha^{\vec{w}}_{\vec{a}}$ and $\alpha^{\vec{z}}_{\vec{b}}$. It follows that
+  $\sigma \beta$ is compatible with $\sigma \alpha$, $\sigma
+  \alpha^{\vec{w}}_{\vec{a}} = \alpha^{\vec{w}}_{\sigma \vec{a}}$ and
+  $\alpha^{\vec{z}}_{\vec{b}} = \alpha^{\vec{z}}_{\sigma \vec{b}}$. We thus have
+  that $L(\pi_{\sigma} g)(\sigma \vec{a}, \sigma \vec{b}) = g_{\phi[\sigma
+    \beta]} = \pi_{\sigma} g_{\phi[\beta]} = \pi_{\sigma} L(g)(\vec{a},
+  \vec{b})$. Suppose $g$ is an output gate, and let $\vec{a} \in [n]^k$ and
+  $\alpha := \alpha^{\vec{x}}_{\vec{a}}$. We have that $\pi_{\sigma} \Omega
+  (\vec{a}) = \pi_\sigma g_{\lambda[\alpha]} = g_{\lambda[\sigma \alpha]} =
+  \Omega (\sigma \alpha \vec{x}) = \Omega (\sigma \vec{a})$. This concludes the
+  proof of the claim.
+\end{proof}
+
+Let $\mathcal{A}$ be a $\tau$-structure with universe $U$ of size $n$ and let
+$\gamma \in [n]^{\underline{U}}$. It can be shown that for all $\psi \in
+\cl{\lambda}$ and $\alpha \in U^{\free{\psi}}$, $\mathcal{A} \models
+\psi[\alpha]$ if, and only if, $C[\gamma \mathcal{A}](g_{\psi[\gamma\alpha]}) =
+1$. It follows that $\vec{a} \in U^k$ is an element of $Q(\theta(\vec{x}))$ if,
+and only if, $\mathcal{A} \models \lambda[\alpha^{\vec{x}}_{\vec{a}}]$ if, and
+only if, $C[\gamma \mathcal{A}](g_{\lambda[\alpha^{\vec{x}}_{\gamma \vec{a}}]})
+= 1$. Since $g_{\lambda [\alpha^{\vec{x}}_{\gamma \vec{a}}]} = \Omega (\gamma
+\vec{a})$, we have that $C$ computes the query defined by $\theta(\vec{x})$ on
+structures of size $n$.
+
+\begin{claim}
+  The circuit $C$ is transparent.
+\end{claim}
+\begin{proof}
+  If $C$ has symmetric gates then $C$ is transparent. Suppose $C$ contains a
+  non-symmetric gate. Let $g_{\phi[\alpha]}:= g \in G$ be a rank gate and
+  suppose $\psi$ is of the form $\rank^r_p \vec{w} \vec{z}. \zeta$, where $\zeta
+  = \zeta_1 \land \zeta_2$ and where, $\zeta_1 = ((\forall u. u = u) \land
+  \phi)$, and $\zeta_2 = \land (\op{tag}(\vec{w} \cup \vec{z}))$. Let $\beta_1 ,
+  \beta_2 \in [n]^{\free{\zeta}}$ both compatible with $\alpha$, and let $h_1 =
+  g_{\zeta[\beta_1]}$ and $h_2 = g_{\zeta[\beta_2]}$. For $i \in [2]$ we have
+  that $H_{h_i} = \{g_{\zeta_1[\beta_i]}, g_{\zeta_2[\beta_i]}\}$. Since
+  $\zeta_1$ contains a sub-formula of the form $(u = u)$, while $\zeta_2$
+  contains no sub-formula with equality, we have that a child of a child of
+  $g_{\zeta_1[\beta_1]}$ is a constant gate while none of the children of the
+  children of $g_{\zeta_2[\beta_2]}$ are constant gates, and thus $g_{\zeta_1
+    [\beta_1]} \not\equiv g_{\zeta_2[\beta_2]}$. It follows that $h_1 \equiv
+  h_2$ if, and only if, both $g_{\zeta_1 [\beta_1]} \equiv g_{\zeta_1
+    [\beta_2]}$ and $g_{\zeta_2[\beta_1]} \equiv g_{\zeta_2[\beta_2]}$.
+  Moreover, the fact that $\zeta_2$ contains an ordered sequence of conjunctions
+  of tautologies, with each tautology referencing a different variable,
+  guarantees that $g_{\zeta_2[\beta_1]} \equiv g_{\zeta_2[\beta_2]}$ if, and
+  only if, $\beta_1$ and $\beta_2$ agree on $\free{\zeta_2}$. But we already
+  have that $\beta_1$ and $\beta_2$ are compatible with $\alpha$, and so agree
+  on $\free{\zeta_1}$. It follows that $g_{\zeta_2[\beta_1]} \equiv
+  g_{\zeta_2[\beta_2]}$ if, and only if, $\beta_1 = \beta_2$. This allows us to
+  conclude that $g_{\zeta[\beta_1]} \equiv g_{\zeta[\beta_2]}$ if, and only if,
+  $\beta_1 = \beta_2$ if, and only if, $g_{\zeta[\beta_1]} =
+  g_{\zeta[\beta_2]}$. It follows that $L(g)$ is injective, and no two $h_1, h_2
+  \in H_g$ are syntactically-equivalent. We conclude that $g$ has unique labels,
+  and so $C$ is transparent.
+\end{proof}
+
+We notice that $\vert C \vert \leq n^{\width(\lambda)} \vert \cl{\lambda} \vert
+\leq n^{\width(\theta)} \vert \cl{\theta} \vert (5 + \width(\theta))$. It is not
+hard to see that $C$ (and $\lambda(\vec{x})$) can be constructed in a number of
+steps bounded by a polynomial in the size of $C$. This completes the proof of
+the result.
+
+% = C[\gamma \mathcal{A}](\Omega(\gamma \vec{a}))$
+
+% Since $h_{}$Since $\pi_\sigma$ is a bijection, we have that $f$ is a
+% bijection. Moreover, we have that $\pi L(g) (a) = L(g) $
+
+% We also have that $\mathcal{A} \models \psi[\gamma \alpha]$ if, and only if,
+% $T^{\mathcal{A}} (\gamma \alpha \vec{y})$ if, and only if, $C[\gamma
+% \mathcal{A}](g) = 1$
+
+% Suppose $g$ is an internal gate, and we have both the results are true for all
+% gates that come before $g$ in the topological ordering of the circuit. Suppose
+% $\psi$ is an application of is an application of a logical connective ($land$
+% or $\lor$) or negation ($\neg$). We then have that $g$ is a symmetric gate,
+% and $f : H_{g} \rightarrow H_{\pi_\sigma g}$ defined by $f(h) = \pi_\sigma h$
+% is a bijection.
+
+% $\pi_\sigma g_{\psi[\alpha]} = \Lambda_T ()$, for some formula $\psi$
+% containing the relation symbol $T$ and assignment $\alpha$, where $\alpha$
+% assigns the free variables in $\psi$ to $\vec{a}$. Then $\pi_\sigma g =
+% \Lambda^{-1}_T (\sigma \Lambda_T (g)) = g_{\psi[\sigma \alpha]}$. Suppose $g$
+% is an internal gate. If $g = g_{psi[\alpha]}$ is an application of a logical
+% connective ( $land$ or $\lor$) or negation ($\neg$) then $\pi_{\sigma}g =
+% g_{\psi[\sigma \alpha]}$. If $g$
+
+% It can be shown by induction on the structure of the circuit that all
+% $g_{\psi[\alpha]} \in G$
+
+% We should note that $C'$ is not, in general, a circuit. This is because it has
+% (potentially) more than three constant gates, and perhaps more than one
+% relational gate for each assignment and relation symbol. Let $C$ be formed
+% from $C'$ by identifying all gates $g$ and $g'$ such that (i) $g$ and $g'$ are
+% constant gates and $\Sigma' (g) = \Sigma'(g')$, or (ii) $g$ and $g'$ are
+% relational gates, $T := \Sigma' (g) = \Sigma' (g') $, and $\Lambda_T' (g) =
+% \Lambda_T'(g')$. We now have $C := \langle G, \Omega, \Sigma, \Lambda, L
+% \rangle$. If the domain of $\Omega'$ includes a constant gate, then
+% $\theta(\vec{x}) = \Lambda (\vec{x}) = (x_1 = x_2)$
+
+% Notice that, formally, $C'$ is not a circuit, in that it contains too many
+% relational gates.
+
+% We now show that $C$ translates $\theta(\vec{x})$ at $n$. It is obvious that
+% $C$ has order $n$. For $\sigma \in \sym_n$ let $\pi_\sigma : G \rightarrow G$
+% be a defined such that $\pi_{\sigma} (g) = g$ if $g \in G_c$ and
+% $\pi_\sigma(g_{\psi, \alpha}) = g_{\psi, \sigma \alpha}$ for all $\psi \in
+% \cl{\lambda}$ and $\alpha \in n^{\free{\psi}}$. It can be shown that
+% $\pi_\sigma$ is an automorphism of $C$ extending $\sigma$. It follows that $C$
+% is symmetric.
+
+% Let $\mathcal{A}$ be a $\tau$-structure with a universe $U$ of size $n$ and
+% let $\gamma U^{\underline{[n]}}$. Let $\psi (\vec{y}) \in \cl{\lambda}$ and
+% let $\alpha \in [n]^{\vec{y}}$. It can be shown by induction on the structure
+% of the circuit that for all $\psi (\vec{y})$ and $\alpha \in [n]^{\vec{y}}$,
+% $C[\gamma \mathcal{A}](g_{\psi, \alpha}) = 1$ if, and only if, $\mathcal{A}
+% \models \psi [\gamma (\alpha \vec{y})]$. It follows that
+
+% Let $\vec{a} \in [n]^k$, and $\alpha \in [n]^{\vec{x}}$ be defined such that
+% $\alpha (x_i) = a_i$ for all $i \in [k]$. Then $C[\Omega]$
+
+% It is obvious that $C$ has order $n$. Let $\sigma \in \sym_n$. Let $\pi_\sigma
+% : G \rightarrow G$ be a defined such that $\pi_{\sigma} (g) = g$ if $g \in
+% G_c$ and $\pi_\sigma(g_{\psi, \alpha}) = g_{\psi, \sigma \alpha}$ for all
+% $\psi \in \cl{\lambda}$ and $\alpha \in n^{\free{\psi}}$. It can be shown that
+% $\pi_\sigma$ is an automorphism of $C$ extending $\sigma$. It follows that $C$
+% is symmetric.
+
+% Moreover, let $\alpha \in [n]^{\free{\theta}}$ be an assignment that maps the
+% sequence of variables $\vec{x}$ to the tuple $\vec{a} \in [n]^k$. It follows
+% that $\Omega (\vec{a}) = g_{\lambda, \alpha}$ evaluates to $1$ If $C$ does not
+% contain a rank gate then it is transparent. Suppose $C$ does contain a rank
+% gate. Let $g := g_{\psi, \alpha} \in G$ be a rank gate and suppose $\psi
+% (\vec{y}) := \rank^r_p \vec{w} \vec{z}. \zeta$, where $\zeta = \zeta_1 \land
+% \zeta_2$ and $\zeta_1 = ((\forall u. u = u) \land \phi)$ and $\zeta_2 = \land
+% (\op{tag}(\vec{w} \cup \vec{z}))$. Suppose $h_1, h_2 \in H_g$ are
+% syntactically-equivalent. It follows that there exist assignments $\beta_1,
+% \beta_2 \in [n]^{\vec{w} \cup \vec{z} \cup {y}}$ such that $\alpha \subseteq
+% \beta_1$ and $\alpha \subseteq \beta_2$ and $h_1 = g_{\zeta, \beta_1}$ and
+% $h_2 = g_{\zeta, \beta_2}$. Then $H_{h_i} = \{g_{\zeta_1, \beta_i},
+% g_{\zeta_2, \beta_i}\}$ for $i \in [2]$. Note that a child of a child of
+% $g_{\zeta_1, \beta_1}$ is a constant gate while none of the children of the
+% children of $g_{\zeta_2, \beta_2}$ are constant gates, and thus $g_{\zeta_1,
+% \beta_1} \not\equiv g_{\zeta_2, \beta_2}$ are not syntactically-equivalent. It
+% follows that $h_1 \equiv h_2$ if, and only if, both $g_{\zeta_1, \beta_1}
+% \equiv g_{\zeta_1, \beta_2}$ and $g_{\zeta_2, \beta_1} \equiv g_{\zeta_2,
+% \beta_2}$. However, the construction of $\zeta_2$ (and the fact that $\beta_1$
+% and $\beta_2$ agree on the variables in $\vec{y}$) guarantees that
+% $g_{\zeta_2, \beta_1} \equiv g_{\zeta_2, \beta_2}$ if, and only if, $\beta_1 =
+% \beta_2$ are equal. It follows that $h_1 = g_{\zeta, \beta_1} = g_{\zeta,
+% \beta_2} = h_2$. The construction of the circuit guarantees that $g$ has
+% injective labels. It follows that $g$ has unique labels, and the circuit $C$
+% is transparent.
+
+% and $h := g_{\phi, \beta}$ and $h' := g_{\phi, \beta'}$ are
+% syntactically-equivalent. From the construction of $\theta'$ we have that
+% $\phi$ must be of a particular form. Suppose $\phi = \eta \land
+% \op{add-tag}(\vec{w} \cup \vec{z})$. Let $\gamma$ and $\gamma'$ be the
+% restrictions of $\beta$ and $\beta'$ to $\vec{w} \cup \vec{z}$, respectively,
+% and let $\zeta(\vec{w}\cup\vec{z}) := \op{add-tag}(\vec{w} \cup \vec{z})$. The
+% $\op{add-tag} (\vec{w} \cup \vec{z})$
+
+% We notice that $\vert C \vert \leq n^{\width(\lambda)} \vert \cl{\lambda}
+% \vert \leq n^{\width(\theta)} \vert \cl{theta} \vert (5 + \width(\theta))$. It
+% can be shown that $C$ (and $\lambda(\vec{x})$ can be constructed in a number
+% of steps bounded by a polynomial in the size of $C$.
+
+% If $C'$ contains no rank gates then output $C := C'$. Suppose $C'$ contains at
+% least one rank-gate. We note add to $C'$ a gadget that ensures that no two
+% input gates to a rank gate can be syntactically-equivalent. Let $\psi \in
+% \cl{\theta}$, and suppose $\psi (\vec{y}) = \rank^r_p \vec{w} \vec{z}. \phi$.
+% We may think of the assignments to the variables $\vec{w}$ and $\vec{z}$ as
+% being the row and column indexes of the matrix. We
+
+% Then for $\alpha \in [n]^{\free (\psi)}$, $H_{g_{\psi, \alpha}}$ consists of
+% gates of the form $g_{\phi, \beta}$, where $\beta \in [n]^{\vec{w} \cup
+% \vec{z} \cup \vec{y}}$ and $\alpha subseteq \beta$.
+
+% Let $T_{\psi, \alpha} : H_{g_{\psi, \alpha}} \rightarrow [n]^{\vert \vec{w}
+% \vert + \vert \vec{z} \vert}$ be defined by $T_{\psi, \alpha} (g_{\phi,
+% \beta}) = \beta (\vec{z} \cup \vec{w})$ for all $g_{\phi, \beta} \in H_g$.
+% What $T_{\psi, \alpha}$ does is assign to each child of $g_{\psi, \alpha}$ an
+% ordered sequence formed Let $T$ be the union of all $T_{\psi}$ and $H$ the
+% union of all $G_{\psi}$ for all $\psi \in \cl{\theta}$ an application of the
+% rank operator. Let $C := \op{tag-all}(C', R, H, T)$. We note that
+% $\op{tag-all}$ may be computed in time polynomial in the size of the input
+% circuit.
+
+% Let $a \in [n]$ and let $\op{no-op} (a) := R(a, a) \lor (\neg (R(a, a))$. For
+% $\psi (\vec{y})$
+
+% % Let $(b_1, \ldots, b_m) := \beta (\vec{w} \cup \vec{z})$. The $\op{tag-all}
+% % function replaces each input $g_{\phi, \beta}$ of the rank gate $g_{\psi,
+% % \alpha}$ with the circuit $g_{\phi, \beta} \land \op{no-op}(b_1) \land
+% % (\op{no-op}(b_2) \land ( \op{no-op}(b_2) \land (\ldots \land
+% % (\op{no-op}(b_m))
+% % \ldots)))$. This construction does not effect the evaluation of any rank
+% % gate
+% % in the cirucit and ensures that no two to $g_{\psi,\alpha}$ in $C$ are
+% % syntactically-equivilent.
+
+% $of the form $$R(a, a) \lor (\neg R(a, a))$ that encode the assignment to
+% $\vec{w}\cup \vec{z}$.
+
+% We have that $C$ is transparent, has order $n$, and $C$ and $C'$ decide the
+% same query. It remains to show that $C$ is still symmetric.
+
+% However, the $\op{tag-all}$ operation adds a tower of tautologies of the form
+% $R(a, \ldots, a) \lor (\neg R (a, \ldots, a))$
+
+% Let $g := g_{\psi, \alpha} \in G$ be a rank gate and let $h, h' \in H_g$.
+% Suppose $\psi (\vec{y}) := \rank^r_p \vec{w} \vec{z}. \phi$ and $h := g_{\phi,
+% \beta}$ and $h' := g_{\phi, \beta'}$ are syntactically-equivalent. From the
+% construction of $\theta'$ we have that $\phi$ must be of a particular form.
+% Suppose $\phi = \eta \land \op{add-tag}(\vec{w} \cup \vec{z})$. Let $\gamma$
+% and $\gamma'$ be the restrictions of $\beta$ and $\beta'$ to $\vec{w} \cup
+% \vec{z}$, respectively, and let $\zeta(\vec{w}\cup\vec{z}) :=
+% \op{add-tag}(\vec{w} \cup \vec{z})$. The $\op{add-tag} (\vec{w} \cup \vec{z})$
+
+% The structure of this formula gives us that $h$ is syntactically-equivalent to
+% $h'$ if, and only if, $g_{\zeta , \beta'}$
+
+% We also note that $C$ has order $n$.
+\end{proof}
+
+We now use Lemma~\cite{lem:translating-FOrk} to prove that for every $\FPR$
+formula there is a corresponding $\PT$-uniform family of transparent symmetric
+rank-circuits that decides the same query.
 
 \begin{thm}
-  For any relational vocabulary $\tau$ and each $\theta(\vec{x}) \in \FPR[\tau]$
-  there is a map $n \mapsto C_n$, where $C_n$ is a transparent symmetric
-  rank-circuit, and is computable in time polynomial in $n$. The family of
-  circuits $(C_n)_{n \in \nats}$ defined by this mapping computes the same query
-  as the one defined by $\theta(\vec{x})$.
+  For each $\FPR$-formula $\theta(\vec{x})$ there exists a family of circuits
+  $(C_n)_{n \in \nats}$ that translates $\theta(\vec{x})$.
   \label{thm:translating-formulas-to-circuits}
 \end{thm}
-
 \begin{proof}
-  We say that a circuit $C$ \emph{translates} a formula $\psi(\vec{x})$ for $n
-  \in \nats$ if $C$ is a transparent symmetric rank-circuit of order $n$ and $C$
-  computes the query defined by $\psi(\vec{x})$ on structures of size $n$. We
-  say a family of circuits $(C_n)_{n \in \nats}$ \emph{translates} a formula
-  $\psi (\vec{x})$ if $(C_n)_{n \in \nats}$ is $\PT$-uniform and for all $n \in
-  \nats$, $C_n$ translates $\psi(\vec{x})$ for $n$.
-
-  We have from Anderson and Dawar~\cite{AndersonD17} that for every formula
-  $\phi(\vec{x}) \in \FPC[\tau]$ there is a $\PT$-uniform family of symmetric
-  circuits $(C^{\phi}_n)_{n \in \nats}$ with unique labels and symmetric gates
-  that translates $\phi(\vec{x})$.
-
   Let $\theta(\vec{x}) \in \FPR[\tau]$ and $t := \width (\theta)$. We begin by
@@
   We thus derive the required $\PT$-uniform family $(\theta_n(\vec{x}))_{n \in
-    \nats}$ by applying the first translation and then the second.
+    \nats}$ by applying the first translation and then the second. We have from
+  Lemma~\ref{} that there exists an algorithm that takes as input $n$ and
+  $\theta_n$, runs in time polynomial in $n^{\width(\theta_n)} \vert
+  \cl{\theta_n} \vert$, and outputs a circuit $C_n = T(\theta_n, n)$ that
+  translates $\theta_n$ for $n$. We note that $\width{\theta_n} \leq 4t$ and
+  $\cl{\theta_n}$ must be bounded by a polynomial in $n$ (since $\theta_n$ is a
+  member of a $P$-uniform family of circuits). It follows that the function $n
+  \mapsto C_n$ is computable in time polynomial in $n$, and so $(C_n)_{n \in
+    \nats}$ translates $\theta(\vec{x})$.
+\end{proof}
 
-  Fix $n \in \nats$. We recursively define a function $T_n$ that maps $\psi
-  (\vec{y})$, a sub-formula of $\theta_n(\vec{x})$, to a circuit $C^{\psi}_n$,
-  where $C^{\psi}_n$ translates $\psi(\vec{y})$ at $n$. We then have that for
-  all $n \in \nats$, $T_n(\theta_n(\vec{x}))$ translates $\theta_n$ (and hence
-  $\theta$) at $n$.
+% \begin{proof}
+%   We say that a circuit $C$ \emph{translates} a formula $\psi(\vec{x})$ for $n
+%   \in \nats$ if $C$ is a transparent symmetric rank-circuit of order $n$ and
+%   $C$ computes the query defined by $\psi(\vec{x})$ on structures of size $n$.
+%   We say a family of circuits $(C_n)_{n \in \nats}$ \emph{translates} a
+%   formula $\psi (\vec{x})$ if $(C_n)_{n \in \nats}$ is $\PT$-uniform and for
+%   all $n \in \nats$, $C_n$ translates $\psi(\vec{x})$ for $n$.
 
-  We first consider the base case. Suppose $\psi(\vec{y})$ is an atomic formula.
-  Then $\psi(\vec{y}) \in \FPC[\tau]$, and so, using the translation defined by
-  Anderson and Dawar~\cite{AndersonD17}, there exists a family of circuits
-  $(C^{\psi}_n)_{n \in \nats}$ that translates $\psi(\vec{y})$. Let
-  $T_n(\psi(\vec{y})) := C^{\psi}_n$.
+%   %   We have from Anderson and Dawar~\cite{AndersonD17} that for every
+%   %   formula
+%   %   $\phi(\vec{x}) \in \FPC[\tau]$ there is a $\PT$-uniform family of
+%   %   symmetric
+%   %   circuits $(C^{\phi}_n)_{n \in \nats}$ with unique labels and symmetric
+%   %   gates
+%   %   that translates $\phi(\vec{x})$.
 
-  We now consider the conjunctive case. Suppose $\psi(\vec{y})$ is a sub-formula
-  of $\theta_n(\vec{x})$ such that $\psi (\vec{y}) = \phi_1(\vec{y}) \land
-  \phi_2(\vec{y})$. Let $R_{\phi_1}$ and $R_{\phi_2}$ be two $\vert \vec{y}
-  \vert$-ary relation symbols not in $\tau$ and let $\psi' (\vec{y}) :=
-  R_{\phi_1}(\vec{y}) \land R_{\phi_2}(\vec{y})$. Then $\psi'(\vec{y}) \in
-  \FPC[\tau]$ and so, using the translation defined by Anderson and Dawar, there
-  exists a circuit family $(C^{\psi'}_n)_{n \in \nats}$ that translates
-  $\psi'(\vec{y})$. Let $T_n(\psi (\vec{y})) := \op{compose}(C^{\psi'}_n, (
-  T_n(\phi_1(\vec{y})), T_n(\phi_2(\vec{y}))), (R_{\phi_1}, R_{\phi_2}))$. We
-  note that $T_n(\psi(\vec{y}))$ translates $\psi (\vec{y})$ at $n$ if
-  $T_n(\phi_1 (\vec{y}))$ and $T_n(\phi_2(\vec{y}))$ translate $\phi_1(\vec{y})$
-  and $\phi_2(\vec{y})$ at $n$, respectively.
+%   Let $\theta(\vec{x}) \in \FPR[\tau]$ and $t := \width (\theta)$. We begin by
+%   showing that there exists a $P$-uniform family of formulas
+%   $(\theta(\vec{x}))_{n \in \nats}$ such that for each $n \in \nats$, we have
+%   $\theta_n(\vec{x}) \in \FOrk[\tau]$, $\width(\theta_n) \leq 4 t$, and
+%   $\theta_n(\vec{x})$ is equivalent to $\theta(\vec{x})$ on structures of size
+%   $n$. This result follows from two observations.
 
-  The approach used in the conjunctive case can be summarised as follows. Given
-  a sub-formula $\psi (\vec{y})$, we construct an auxiliary formula
-  $\psi'(\vec{y})$ in which all the sub-formulas of $\psi(\vec{y})$ are replaced
-  with relation symbols. We then construct a circuit $C^{\psi'}$ that translates
-  $\psi'(\vec{y})$ at $n$ using the translation defined by Anderson and Dawar.
-  Finally, we recursively construct circuits that translate the sub-formulas of
-  $\psi(\vec{y})$, and compose these circuits with $C^{\psi'}$.
+%   First, using the translation in~\cite{Dawar09logicswith}, we have that for
+%   any $\phi(\vec{x}) \in \FPR[\tau]$ of the form $\lfp{V,
+%   \vec{y}}{\psi(\vec{x}, \vec{y}, V)}(\vec{x})$ , there is a mapping $n
+%   \mapsto \phi_n$, computable in time polynomial in both $n$ and the size of
+%   $\phi(\vec{x})$ such that for all $n \in \nats$, we have $\phi_n(\vec{x})
+%   \in \FOR[\tau]$, $\width (\phi_n) \leq 2 \cdot \width (\phi)$, and
+%   $\phi_n(\vec{x})$ and $\phi(\vec{x})$ are equivalent on structures of size
+%   $n$.
 
-  This approach can be used in order to handle every case with the exception of
-  rank. In other words, we can use a similar approach to define
-  $T_n(\psi(\vec{y}))$ where $\psi(\vec{y})$ is a sub-formula of
-  $\theta_n(\vec{x})$ of the form $\phi_1(\vec{y}) \lor \phi_2(\vec{y})$, $\neg
-  \phi(\vec{y})$, $\forall z. \phi (\vec{y}, z)$, or $\exists z. \phi (\vec{y},
-  z)$.
+%   Second, using the translation in~\cite{libkin2004elements}, we have that if
+%   $\phi (\vec{x}) \in \FOR[\tau]$ is of the form $\rank (\vec{y}\vec{\mu} \leq
+%   \vec{t}, \vec{z}\vec{\nu} \leq \vec{s}, \pi \leq r) . \psi
+%   (\vec{y}\vec{\mu}, \vec{z} \vec{\nu})$, then there is a mapping $n \mapsto
+%   \phi_n$ computable in time polynomial in both $n$ and the size of
+%   $\phi(\vec{x})$ such that for all $n \in \nats$, $\phi_n(\vec{x}) \in
+%   \FOrk[\tau]$, $\width(\phi_n) \leq 2 \cdot \width(\phi)$, and
+%   $\phi_n(\vec{x})$ and $\phi(\vec{x})$ are equivalent on structures of size
+%   $n$.
 
-  We now handle the rank case. The approach is quite similar, except in this
-  case we cannot use the translation defined by Anderson and Dawar in order to
-  translate the auxiliary formula, and so must define this translation
-  explicitly. Moreover, rather than just composing the circuits, we also add a
-  small gadget in order to ensure the resultant circuit is transparent.
+%   We thus derive the required $\PT$-uniform family $(\theta_n(\vec{x}))_{n \in
+%   \nats}$ by applying the first translation and then the second. Let $x$ be a
+%   variable and $R \in \tau$. Let $\op{no-op}(x) := R(x, x) \land (\neg R(x,
+%   x))$. Let $\vec{x} := (x_1, \ldots, x_k)$ and $\op{add-tag} (\vec{x}) :=
+%   \op{no-op}(x_1) \land (\op{no-op}(x_2) \land ( \ldots \land
+%   (\op{no-op}(x_k)) \ldots)$. For each $\theta_n (\vec{x})$ we construct a new
+%   formula $\theta_n' (\vec{x})$ by replacing each sub-formula $\phi(\vec{y})$
+%   of $\theta_n(\vec{x})$ of the form $\rank^r_p \vec{w} \vec{z} . \psi$ by
+%   $\rank^r_p \vec{w}\vec{z} . (\psi \land \op{add-tag}(\vec{w} \cup
+%   \vec{z}))$. It is easy to see that we can construct $\theta_n'$ from
+%   $\theta_n$ in time polynomial in $\theta_n$. Moreover, $\theta_n'$ and
+%   $\theta_n$ are equivalent and have the same width.
 
-  Suppose $\psi(\vec{z}, \vec{w}, \vec{y})$ is a sub-formula of
-  $\theta_n(\vec{x})$ such that $\psi (\vec{y}) = \rank^{\leq r}_p \vec{z},
-  \vec{w} .\phi(\vec{z}, \vec{w}, \vec{y})$, for some $p, r \in \nats$ and $p$
-  prime. Let $k:= \vert \vec{y} \vert$, $k_1 : = \vert \vec{z} \vert$ and $k_2
-  := \vert \vec{w} \vert$. Let $R_\phi$ be a $(k_1 + k_2 + k)$-ary relation
-  symbol not in $\tau$. Let $\psi'(\vec{y}) := \rank^{\leq r}_p\vec{z}, \vec{w}.
-  R_{\phi} (\vec{z}, \vec{w}, \vec{y})$. Let $G_{\text{out}} := \{g_{\vec{c}} :
-  \vec{c} \in [n]^k\}$ and $G_{\text{in}} : = \{ g_{\vec{a}, \vec{b}, \vec{c}} :
-  \vec{a} \in [n]^{k_1}, \vec{b} \in [n]^{k_2}, \vec{c} \in [n]^{k}\}$. Let
-  $C^{\psi'}_n:= \langle G^{\psi'}, \Omega^{psi'}, \Sigma^{\psi'},
-  \Lambda^{\psi'}, L^{\psi'}\rangle$ be a $(\mathbb{B}_{\rank}, \{ R_{\phi}
-  \})$-circuit such that
-  \begin{itemizens}
-  \item $G^{\psi'} = G_{\text{out}} \cup G_{\text{in}}$,
-  \item $\Omega^{\psi'}$ be an injection from $[n]^k$ to $G^{\psi'}$ defined by
-    $\Omega^{\psi'}(\vec{c}) = g_{\vec{c}}$ for all $\vec{c} \in [n]^k$,
-  \item $\Sigma^{\psi'} (g) = \rank^r_p$ if $g \in G_{\text{out}}$ and
-    $\Sigma^{\psi'}(g) = R_\phi$ if $g \in G_{\text{in}}$,
-  \item for each $(\vec{a}, \vec{b}, \vec{c}) \in [n]^{k_1 +k_2 + k}$,
-    $\Lambda^{\psi'} (\vec{a}, \vec{b}, \vec{c}) = g_{\vec{a}, \vec{b},
-      \vec{c}}$, and
-  \item for each gate $g_{\vec{c}} \in G_{\text{out}}$, $L(g_{\vec{c}}):
-    [n]^{k_1} \times [n]^{k_2} \rightarrow G^{\psi'}$ is defined by
-    $L(g_{\vec{c}})(\vec{a}, \vec{b}) := g_{\vec{a}, \vec{b}, \vec{c}}$ for each
-    $\vec{a} \in [n]^{k_1}$ and $\vec{b} \in [n]^{k_2}$.
-  \end{itemizens}
+%   Fix $n \in \nats$. We now construct a circuit $C_n$ that translates
+%   $\theta_n'$ (and hence $\theta_n$ and $\theta$) at $n$. For each $\psi \in
+%   \cl{\theta_n}$ let $G_\psi := \{g_{\psi, \alpha} : \alpha \in
+%   [n]^{\free{\psi}} \}$. Let $G := \bigcup_{\psi \in \cl{\theta_n}} G_{\psi}$.
+%   Let $g_{\psi, \alpha} \in G$. We define $\Sigma$, $\Lambda$ and $L$ as
+%   follows.
+%   \begin{itemizens}
+%   \item If $\psi (\vec{y}) = R(\vec{y})$, for some $R \in \tau$, then $\Sigma
+%     (g_{\psi, \alpha}) = R$ and $\Lambda_R (g_{\psi, \alpha}) = \alpha
+%     \vec{y})$.
+%   \item If $\psi (y_1, y_2) = (y_1 = y_2)$, then if $\alpha (y_1) = \alpha
+%     (y_2)$, $\Sigma (g_{\psi, \alpha}) = 1$, else $\Sigma (g_{\psi, \alpha}) =
+%     0$.
+%   \item if $\psi (\vec{y}) = \rank^r_p \vec{w} \vec{z}. \phi$, then $\Sigma
+%     ()$
+%   \end{itemizens}
 
-  We note that $C^{\psi'}_n$ translates $\psi (\vec{y})$ at $n$. Let $R$ be a
-  relation symbol in $\tau$. Let
-  \begin{align*} T_n(\psi(\vec{y})) := \op{compose-and-tag}(C^{\psi'}_n,
-    (T_n(\phi(\vec{z}, \vec{w}, \vec{y}))), (R_\phi), R).
-  \end{align*}
+%   We first consider the base case. Suppose $\psi(\vec{y})$ is an atomic
+%   formula. Then $\psi(\vec{y}) \in \FPC[\tau]$, and so, using the translation
+%   defined by Anderson and Dawar~\cite{AndersonD17}, there exists a family of
+%   circuits $(C^{\psi}_n)_{n \in \nats}$ that translates $\psi(\vec{y})$. Let
+%   $T_n(\psi(\vec{y})) := C^{\psi}_n$.
 
-  We recall that $\op{compose-and-tag}$ combines circuits in a similar way to
-  $\op{compose}$ except that it also adds a set of gadgets to the circuit
-  ensuring that no two child gates of an output gate are
-  syntactically-equivalent. We thus have that $T_n(\psi (\vec{y}))$ is
-  transparent if $T_n(\phi (\vec{z}, \vec{w},\vec{y}))$ is transparent, and
-  $T_n(\psi(\vec{y}))$ translates $\psi (\vec{y})$ at $n$ if $T_n(\phi (\vec{z},
-  \vec{w},\vec{y}))$ translates $\phi(\vec{z}, \vec{w}, \vec{y})$ at $n$.
+%   We now consider the conjunctive case. Suppose $\psi(\vec{y})$ is a
+%   sub-formula of $\theta_n(\vec{x})$ such that $\psi (\vec{y}) =
+%   \phi_1(\vec{y}) \land \phi_2(\vec{y})$. Let $R_{\phi_1}$ and $R_{\phi_2}$ be
+%   two $\vert \vec{y} \vert$-ary relation symbols not in $\tau$ and let $\psi'
+%   (\vec{y}) := R_{\phi_1}(\vec{y}) \land R_{\phi_2}(\vec{y})$. Then
+%   $\psi'(\vec{y}) \in \FPC[\tau]$ and so, using the translation defined by
+%   Anderson and Dawar, there exists a circuit family $(C^{\psi'}_n)_{n \in
+%   \nats}$ that translates $\psi'(\vec{y})$. Let $T_n(\psi (\vec{y})) :=
+%   \op{compose}(C^{\psi'}_n, ( T_n(\phi_1(\vec{y})), T_n(\phi_2(\vec{y}))),
+%   (R_{\phi_1}, R_{\phi_2}))$. We note that $T_n(\psi(\vec{y}))$ translates
+%   $\psi (\vec{y})$ at $n$ if $T_n(\phi_1 (\vec{y}))$ and
+%   $T_n(\phi_2(\vec{y}))$ translate $\phi_1(\vec{y})$ and $\phi_2(\vec{y})$ at
+%   $n$, respectively.
 
-  We have completed our definition of $T_n$ and shown, by induction on the
-  structure of $\theta_n(\vec{x})$, that for each $\psi (\vec{y})$ a sub-formula
-  of $\theta_n(\vec{x})$, $T_n(\psi(\vec{y}))$ translates $\psi(\vec{y})$ at
-  $n$.
+%   The approach used in the conjunctive case can be summarised as follows.
+%   Given a sub-formula $\psi (\vec{y})$, we construct an auxiliary formula
+%   $\psi'(\vec{y})$ in which all the sub-formulas of $\psi(\vec{y})$ are
+%   replaced with relation symbols. We then construct a circuit $C^{\psi'}$ that
+%   translates $\psi'(\vec{y})$ at $n$ using the translation defined by Anderson
+%   and Dawar. Finally, we recursively construct circuits that translate the
+%   sub-formulas of $\psi(\vec{y})$, and compose these circuits with
+%   $C^{\psi'}$.
 
-  The above definition can be used to define a recursive algorithm computing the
-  function $n \mapsto T_n (\theta_n(\vec{x}))$. We note that, since
-  $\width(\theta_n) \leq 4 t$ for all $n \in \nats$, there are only a finite
-  number of cases that need to be considered at each recursive step in this
-  algorithm. This fact can be used to show that there exists a polynomial bound
-  on the running time of the algorithm that depends only on $n$ and the
-  structure of $\theta(\vec{x})$. As such, we have that $(T_n (\theta_n))_{n \in
-    \nats}$ translates $\theta(\vec{x})$, and the result follows.
-\end{proof}
+%   This approach can be used in order to handle every case with the exception
+%   of rank. In other words, we can use a similar approach to define
+%   $T_n(\psi(\vec{y}))$ where $\psi(\vec{y})$ is a sub-formula of
+%   $\theta_n(\vec{x})$ of the form $\phi_1(\vec{y}) \lor \phi_2(\vec{y})$,
+%   $\neg \phi(\vec{y})$, $\forall z. \phi (\vec{y}, z)$, or $\exists z. \phi
+%   (\vec{y}, z)$.
+
+%   We now handle the rank case. The approach is quite similar, except in this
+%   case we cannot use the translation defined by Anderson and Dawar in order to
+%   translate the auxiliary formula, and so must define this translation
+%   explicitly. Moreover, rather than just composing the circuits, we also add a
+%   small gadget in order to ensure the resultant circuit is transparent.
+
+%   Suppose $\psi(\vec{z}, \vec{w}, \vec{y})$ is a sub-formula of
+%   $\theta_n(\vec{x})$ such that $\psi (\vec{y}) = \rank^{\leq r}_p \vec{z},
+%   \vec{w} .\phi(\vec{z}, \vec{w}, \vec{y})$, for some $p, r \in \nats$ and $p$
+%   prime. Let $k:= \vert \vec{y} \vert$, $k_1 : = \vert \vec{z} \vert$ and $k_2
+%   := \vert \vec{w} \vert$. Let $R_\phi$ be a $(k_1 + k_2 + k)$-ary relation
+%   symbol not in $\tau$. Let $\psi'(\vec{y}) := \rank^{\leq r}_p\vec{z},
+%   \vec{w}. R_{\phi} (\vec{z}, \vec{w}, \vec{y})$. Let $G_{\text{out}} :=
+%   \{g_{\vec{c}} : \vec{c} \in [n]^k\}$ and $G_{\text{in}} : = \{ g_{\vec{a},
+%   \vec{b}, \vec{c}} : \vec{a} \in [n]^{k_1}, \vec{b} \in [n]^{k_2}, \vec{c}
+%   \in [n]^{k}\}$. Let $C^{\psi'}_n:= \langle G^{\psi'}, \Omega^{\psi'},
+%   \Sigma^{\psi'}, \Lambda^{\psi'}, L^{\psi'}\rangle$ be a
+%   $(\mathbb{B}_{\rank}, \{ R_{\phi} \})$-circuit such that
+%   \begin{itemizens}
+%   \item $G^{\psi'} = G_{\text{out}} \cup G_{\text{in}}$,
+%   \item $\Omega^{\psi'}$ be an injection from $[n]^k$ to $G^{\psi'}$ defined
+%     by $\Omega^{\psi'}(\vec{c}) = g_{\vec{c}}$ for all $\vec{c} \in [n]^k$,
+%   \item $\Sigma^{\psi'} (g) = \rank^r_p$ if $g \in G_{\text{out}}$ and
+%     $\Sigma^{\psi'}(g) = R_\phi$ if $g \in G_{\text{in}}$,
+%   \item for each $(\vec{a}, \vec{b}, \vec{c}) \in [n]^{k_1 +k_2 + k}$,
+%     $\Lambda^{\psi'} (\vec{a}, \vec{b}, \vec{c}) = g_{\vec{a}, \vec{b},
+%     \vec{c}}$, and
+%   \item for each gate $g_{\vec{c}} \in G_{\text{out}}$, $L(g_{\vec{c}}):
+%     [n]^{k_1} \times [n]^{k_2} \rightarrow G^{\psi'}$ is defined by
+%     $L(g_{\vec{c}})(\vec{a}, \vec{b}) := g_{\vec{a}, \vec{b}, \vec{c}}$ for
+%     each $\vec{a} \in [n]^{k_1}$ and $\vec{b} \in [n]^{k_2}$.
+%   \end{itemizens}
+
+%   We note that $C^{\psi'}_n$ translates $\psi (\vec{y})$ at $n$. Let $R$ be a
+%   relation symbol in $\tau$. Let
+%   \begin{align*} T_n(\psi(\vec{y})) := \op{compose-and-tag}(C^{\psi'}_n,
+%     (T_n(\phi(\vec{z}, \vec{w}, \vec{y}))), (R_\phi), R).
+%   \end{align*}
+
+%   We recall that $\op{compose-and-tag}$ combines circuits in a similar way to
+%   $\op{compose}$ except that it also adds a set of gadgets to the circuit
+%   ensuring that no two child gates of an output gate are
+%   syntactically-equivalent. We thus have that $T_n(\psi (\vec{y}))$ is
+%   transparent if $T_n(\phi (\vec{z}, \vec{w},\vec{y}))$ is transparent, and
+%   $T_n(\psi(\vec{y}))$ translates $\psi (\vec{y})$ at $n$ if $T_n(\phi
+%   (\vec{z}, \vec{w},\vec{y}))$ translates $\phi(\vec{z}, \vec{w}, \vec{y})$ at
+%   $n$.
+
+%   We have completed our definition of $T_n$ and shown, by induction on the
+%   structure of $\theta_n(\vec{x})$, that for each $\psi (\vec{y})$ a
+%   sub-formula of $\theta_n(\vec{x})$, $T_n(\psi(\vec{y}))$ translates
+%   $\psi(\vec{y})$ at $n$.
+
+%   The above definition can be used to define a recursive algorithm computing
+%   the function $n \mapsto T_n (\theta_n(\vec{x}))$. We note that, since
+%   $\width(\theta_n) \leq 4 t$ for all $n \in \nats$, there are only a finite
+%   number of cases that need to be considered at each recursive step in this
+%   algorithm. This fact can be used to show that there exists a polynomial
+%   bound on the running time of the algorithm that depends only on $n$ and the
+%   structure of $\theta(\vec{x})$. As such, we have that $(T_n (\theta_n))_{n
+%   \in \nats}$ translates $\theta(\vec{x})$, and the result follows.
+% \end{proof}
 

### 2018-02-16 paper.tex
Updated first four sections.
I have realised that my generalisation of symmetry is flawed and will need an overhaul. However, I want to keep a copy so I'm updating git.
This version is the told one where we are just speaking of $\mathcal{D}$-invarient functions.
13-Nov-2017
editing process
24th January 2018
February 5 2018
New introduction. Also changes to top-level file to put in Section labels. And a new reference.

@@
 % and command definitions. The preamble is everything between \documentclass
-% and \begin{document}.
+% and \begin{document}.asd
 
@@
 \usepackage{mymacros}
+\usepackage{anujmacros}
+\usepackage{amssymb}
+\usepackage{bm}
+\usepackage{etoolbox}
+
+\newenvironment{itemizens}
+{ \begin{itemize}
+    \setlength{\itemsep}{0pt}
+    \setlength{\parskip}{0pt}
+    \setlength{\parsep}{0pt}     }
+{ \end{itemize}                  }
 
@@
 
-\section{Background}
+\section{Background}\label{sec:background}
 \subfile{sections/background}
@@
 
-\section{Symmetric Circuits}
+\section{Symmetric Circuits}\label{sec:symm-circ}
 \subfile{sections/symmetric-circuits}
@@
 
-\section{Symmetry and Support}
+\section{Symmetry and Support}\label{sec:symm-support}
 \subfile{sections/symmetry-and-support}
@@
 
-\section{Translating Circuits into Formulas}
+\section{Transparent Circuits}\label{sec:transparent}
+\subfile{sections/transparency-and-unique-extensions.tex}
+
+\section{Translating Formulas into Circuits}\label{sec:formulas-to-circuits}
+\subfile{sections/translating-formulas-to-cicuits.tex}
+\newpage
+
+\section{Translating Circuits into Formulas}\label{sec:circuits-to-formulas}
 \subfile{sections/translating-circuits-into-formulas}
@@
 \newpage
-
 \bibliographystyle{plain} \bibliography{references}

### 2018-02-16 sections/introduction.tex
New introduction. Also changes to top-level file to put in Section labels. And a new reference.

@@
 \begin{document}
+
+The study of extensions of fixed-point logics plays an important role
+in the field of descriptive complexity theory.  In particular,
+fixed-point logic with counting ($\FPC$) has become a reference logic
+in the search for a logic for polynomial-time
+(see~\cite{Dawar-siglog}).  In this context, Anderson and
+Dawar~\cite{AndersonD17} provide an interesting characterization of
+the expressive power of $\FPC$ in terms of circuit complexity.  They
+show that the properties expressible in this logic are exactly those
+that can be decided by polynomially-uniform families of circuits (with
+threshold gates) satisfying a natural \emph{symmetry} condition.  Not
+only does this illustrate the robustness of $\FPC$ as a complexity
+class within $\PT$ by giving a distinct and natural characterization
+of it, it also demonstrates that the techniques for proving
+inexpressibility in the field of finite model theory can be understood
+as lower-bound methods against a natural circuit complexity class.
+This raises an obvious question (explicitly posed in the concluding
+section of~\cite{AndersonD17}) of how to obtain circuit
+characterizations of logics more expressive than $\FPC$, such as
+choiceless polynomial time (CPT) and fixed-point logic with rank
+($\FPR$).  It is this last question that we address in this paper.
+
+Fixed-point logic with rank extends the expressive power of $\FPC$ by
+means of operators that allow us to define the rank of a matrix over a
+finite field.  Such operators are natural extensions of
+counting---counting the dimension of a definable vector space
+rather than just the size of a definable set.  At the same time they
+make the logic rich enough to express many of the known examples that
+separate $\FPC$ from $\PT$.  Rank logics were first introduced
+in~\cite{Dawar09logicswith}.  The version $\FPR$ we consider here is that
+defined by Gr\"adel and Pakusa~\cite{GradelP15a} where the prime
+characteristic is a parameter to the rank operator, and we do not have
+a distinct operator for each prime number.  Formal definitions of
+these logics are given in Section~\ref{sec:background}.  We give a circuit
+characterization, in terms of symmetric circuits, of $\FPR$.  One
+might think, at first sight, that this is a simple matter of extending
+the circuit model with gates for computing the rank of a matrix.
+It turns out, however, that the matter is not so simple as the
+symmetry requirement interacts in surprising ways with such rank
+gates.  It requires a new framework for defining classes of such
+circuits, which yields remarkable new insights.
+
+It is important to clarify at the outset what is meant by symmetric
+circuits.  Indeed, there are different senses in which the word
+\emph{symmetry} is used in the context of circuits (and also in this
+paper).  We say that a Boolean function $f:\{0,1\}^n \ra \{0,1\}$ is
+symmetric if the value of the function on a string $s$ is determined
+by the number of $1$s in $s$.  In other words, $f$ is invariant under
+\emph{all} permutations of its input.  In contrast, when we consider
+the input to a Boolean function to be the adjacency matrix of an
+$n$-vertex graph, for example, and
+$f : \{0,1\}^{n \choose 2} \ra \{0,1\}$ decides a graph property, then
+$f$ is invariant under all permutations of its input induced by
+permutations of the $n$ vertices of the graph.  We call such a
+function \emph{graph-invariant}.  More generally, for a relational
+vocabulary $\tau$ and a standard encoding of $n$-element
+$\tau$-structures as strings over $\{0,1\}$, we can say that function
+taking such strings as input is $\tau$-invariant if it is invariant
+under permutations induced by the $n$ elements.
+A circuit $C$ computing such an invariant function is said to be \emph{symmetric} if every
+permutation of the $n$ elements extends to an automorphism of $C$.  It
+is families of symmetric circuits in this sense that characterize
+$\FPC$ in~\cite{AndersonD17}.  The restriction to symmetric circuits
+arises naturally in the study of logics and has appeared previously
+under the names of generic circuits in the work
+of~\cite{DENENBERG1986216} and explicitly order-invariant circuits in
+the work of Otto~\cite{Otto1997}.
+
+The main result of~\cite{AndersonD17} says that the properties of
+$\tau$-structures definable in $\FPC$ are exactly those that can be
+decided by $\PT$-uniform families of symmetric circuits using AND, OR,
+NOT and majority gates.  Note that each of these gates itself computes
+a Boolean function that is symmetric in the strong sense identified
+above.  On the other hand, a gate for computing a rank threshold
+function, e.g.\ one that takes as input a $n \times n$ matrix and
+outputs $1$ if the rank of the matrix is greater than a threshold $t$,
+is \emph{not} symmetric.  In our circuit characterization of $\FPR$ we
+necessarily have to consider such non-symmetric gates.  Indeed, we
+show in Section~\ref{sec:symm-circ} that  $\PT$-uniform families of
+symmetric circuits using gates for \emph{any} symmetric functions do
+not take us beyond the power of $\FPC$.  This is a further
+illustration of the robustness of $\FPC$.  In order to go beyond it,
+we need to introduce gates for Boolean functions that are not
+symmetric.  We construct a systematic framework for including
+functions computing $\tau$-invariant functions for arbitrary
+multi-sorted relational vocabularies $\tau$ in
+Section~\ref{sec:symm-circ}.  We also explore what it means for such
+circuits to be symmetric.
+
+The proof of the circuit characterization of $\FPC$ relies on the
+\emph{support theorem} proved in~\cite{AndersonD17}.  This establishes
+that for any $\PT$-uniform family of circuits using AND, OR, NOT and
+majority gates there is a constant $k$ such that every gate has a
+support of size at most $k$.  That is to say that we can associate
+with every gate $g$ in the circuit $C_n$ (the circuit in the family
+that works on $n$-element structures) a subset $X$ of $[n]$ of size at
+most $k$ such that any permutation of $[n]$ fixing $X$ pointwise
+extends to an automorphism of $C_n$ that fixes $g$.  This theorem is
+crucial to the translation of the family of circuits into a formula of
+$\FPC$, which is the difficult (and novel) direction of the
+equivalence.  In attempting to do the same with circuits that now use
+rank-threshold gates we are faced with the difficulty that the proof
+of the support theorem in~\cite{AndersonD17} relies in an essential
+way on the fact that the Boolean function computed at each gate is
+symmetric.  We are able to overcome this difficulty and prove a
+support theorem for circuits with rank gates but this requires
+substantial, novel technical machinery, which we develop in
+Section~\ref{sec:symm-support}.
+
+Another crucial ingredient in the proof of Anderson and Dawar is that
+we can eliminate redundancy in the circuit $C_n$ by making it
+\emph{rigid}.  That is, we can ensure that the \emph{only}
+automorphisms of $C_n$ are those that are induced by permutations of
+$[n]$.  Here we face the difficulty that identifying the symmetries
+and eliminating redundancy in a circuit that involves gates computing
+$\tau$-invariant functions requires us to solve the isomorphism
+problem for $\tau$-structures.  This is a hard problem (or, at least,
+one that we do not know how to solve efficiently) even when the
+$\tau$-structures are $0$-$1$-matrices.  We overcome this difficulty
+by placing a further restriction on circuits that we call
+\emph{transparency}.  Circuits satisfying this condition have the
+property that their lack of redundancy is transparent.  We explore
+this condition and its consequences in Section~\ref{sec:transparent}.
+
+In the characterization of $\FPC$, the translation from formulas into
+families of circuits is easy and, indeed, standard.  In our case, we
+have to show that formulas of $\FPR$ translate into uniform families of
+circuits using rank-threshold gates that are symmetric and
+transparent.  This is somewhat more involved technically and the
+details are presented in Section~\ref{sec:formulas-to-circuits}.
+Finally, with all the tools in place, the translation of such
+$\PT$-uniform families of circuits into formulas of $\FPR$ given in Section~\ref{sec:circuits-to-formulas} completes
+the characterization.
+
+\end{document}
+
 When we study algorithmic complexity we often study complexity classes defined

### 2018-02-16 sections/introduction.tex
Correction to introduction - commenting out previous version.

@@
 
-When we study algorithmic complexity we often study complexity classes defined
-in terms of some restricted class of machines. Circuit complexity, where one
-makes use of similarly restricted families of Boolean circuits rather than
-machines, has long served as an alternative approach. These circuits models have
-a natural attraction for researchers, as their simpler structure seems to make
-them more amendable to analysis and their connections with machine models
-provides an alternative avenue for better understanding fundamental problems in
-complexity theory, including the $\PT$ vs $\NP$ problem.
+% When we study algorithmic complexity we often study complexity classes defined
+% in terms of some restricted class of machines. Circuit complexity, where one
+% makes use of similarly restricted families of Boolean circuits rather than
+% machines, has long served as an alternative approach. These circuits models have
+% a natural attraction for researchers, as their simpler structure seems to make
+% them more amendable to analysis and their connections with machine models
+% provides an alternative avenue for better understanding fundamental problems in
+% complexity theory, including the $\PT$ vs $\NP$ problem.
 
-Descriptive complexity instead concerns the characterisation of complexity
-classes in terms of logics. The central open question in the field -- whether
-there is a logical characterisation of the polynomial-time decidable properties
-of finite relational structures -- essentially asks if there is a logic the
-sentences of which describe all (and only) polynomial-time decidable
-isomorphism-closed classes of graphs (i.e. every \emph{graph property} in
-$\PT$). As in the algorithmic complexity case, the use of circuits in
-descriptive complexity has proved useful, with Otto \cite{Otto1997} and
-Denenberg et al.~\cite{DENENBERG1986216} developing circuit-based
-characterisations for logics. These characterisation are given in terms of
-\emph{symmetric circuits}, circuits that take in finite structures over some
-universe and where permutations of the universe of the input structure are
-reflected by automorphisms of the circuit.
+% Descriptive complexity instead concerns the characterisation of complexity
+% classes in terms of logics. The central open question in the field -- whether
+% there is a logical characterisation of the polynomial-time decidable properties
+% of finite relational structures -- essentially asks if there is a logic the
+% sentences of which describe all (and only) polynomial-time decidable
+% isomorphism-closed classes of graphs (i.e. every \emph{graph property} in
+% $\PT$). As in the algorithmic complexity case, the use of circuits in
+% descriptive complexity has proved useful, with Otto \cite{Otto1997} and
+% Denenberg et al.~\cite{DENENBERG1986216} developing circuit-based
+% characterisations for logics. These characterisation are given in terms of
+% \emph{symmetric circuits}, circuits that take in finite structures over some
+% universe and where permutations of the universe of the input structure are
+% reflected by automorphisms of the circuit.
 
-% In this way symmetric circuits provide a natural class from which to develop
-% circuit characterisations for logics, taking in abstract structures and
-% ensuring that isomorphism (permutations) on the input structure are reflected
-% in the circuit structure, which consequently implies that the function
-% computed by the circuit is \emph{invariant} (i.e. computes a graph property)
-% makes symmetric circuits a natural class from which to develop circuit
-% characterisations of logics.
+% % In this way symmetric circuits provide a natural class from which to develop
+% % circuit characterisations for logics, taking in abstract structures and
+% % ensuring that isomorphism (permutations) on the input structure are reflected
+% % in the circuit structure, which consequently implies that the function
+% % computed by the circuit is \emph{invariant} (i.e. computes a graph property)
+% % makes symmetric circuits a natural class from which to develop circuit
+% % characterisations of logics.
 
-Anderson and Dawar \cite{AndersonD17} developed a similar
-circuit-characterisation for $\FPC$, proving that families of P-uniform families
-of symmetric circuits defined over a complete Boolean basis with majority gates
-completely characterises \emph{fixed-point logic with counting} ($\FPC$).
+% Anderson and Dawar \cite{AndersonD17} developed a similar
+% circuit-characterisation for $\FPC$, proving that families of P-uniform families
+% of symmetric circuits defined over a complete Boolean basis with majority gates
+% completely characterises \emph{fixed-point logic with counting} ($\FPC$).
 
-While it is known that $\FPC$ does not capture $\PT$ \cite{Cau1992}, $\FPC$ does
-capture $\PT$ over many classes of structures \cite{Grohe2010} and many natural
-$\PT$ problems are expressible in $\FPC$ (e.g.\ Maximum Matching
-\cite{Anderson2013}). While $\FPC$ is thus an important logic of interest for
-its own sake, it also plays a role as a logic from which other important logics
-of study are defined. The particular logic of interest in this paper is
-\emph{fixed-point logic with rank} ($\FPR$), introduced by Dawar et
-al.~\cite{Dawar09logicswith}, and is defined as an extension of $\FPC$ that
-includes operators that can define the rank of a definable matrix over a fixed
-finite field. This extension was prompted by the work of Atserias et
-al.~\cite{Atserias20091666}, who had shown that that some of the most difficult
-to express problems in $\PT$ (that are not expressible in $\FPC$) were reducible
-to the general problem of solving systems of linear equations over prime fields.
-Indeed, problems of this sort have remained the primary source of
-difficult-to-express problems in descriptive complexity, motivating the modern
-study of $\FPR$.
+% While it is known that $\FPC$ does not capture $\PT$ \cite{Cau1992}, $\FPC$ does
+% capture $\PT$ over many classes of structures \cite{Grohe2010} and many natural
+% $\PT$ problems are expressible in $\FPC$ (e.g.\ Maximum Matching
+% \cite{Anderson2013}). While $\FPC$ is thus an important logic of interest for
+% its own sake, it also plays a role as a logic from which other important logics
+% of study are defined. The particular logic of interest in this paper is
+% \emph{fixed-point logic with rank} ($\FPR$), introduced by Dawar et
+% al.~\cite{Dawar09logicswith}, and is defined as an extension of $\FPC$ that
+% includes operators that can define the rank of a definable matrix over a fixed
+% finite field. This extension was prompted by the work of Atserias et
+% al.~\cite{Atserias20091666}, who had shown that that some of the most difficult
+% to express problems in $\PT$ (that are not expressible in $\FPC$) were reducible
+% to the general problem of solving systems of linear equations over prime fields.
+% Indeed, problems of this sort have remained the primary source of
+% difficult-to-express problems in descriptive complexity, motivating the modern
+% study of $\FPR$.
 
-It is worth noting the logic defined by Dawar et al.\cite{} defines for each
-prime a separate operator that computes the rank of the matrix over that prime.
-It was shown by Gr\"{a}del and Pakusa \cite{GradelP15a} that this logic does not
-capture $\PT$. Instead, they present a strictly more expressive alternative rank
-logic which includes only a single rank operator that takes in both the matrix
-and a specific prime over which to compute the rank as input. In this paper when
-we refer to $\FPR$ we are referring to this more expressive version of
-Gra\"{a}del and Pakusa.
+% It is worth noting the logic defined by Dawar et al.\cite{} defines for each
+% prime a separate operator that computes the rank of the matrix over that prime.
+% It was shown by Gr\"{a}del and Pakusa \cite{GradelP15a} that this logic does not
+% capture $\PT$. Instead, they present a strictly more expressive alternative rank
+% logic which includes only a single rank operator that takes in both the matrix
+% and a specific prime over which to compute the rank as input. In this paper when
+% we refer to $\FPR$ we are referring to this more expressive version of
+% Gra\"{a}del and Pakusa.
 
-In this paper we develop a circuit characterisation of $\FPR$ in terms of
-symmetric circuits that have gates that compute rank. Concretely, a circuit
-$C_n$ for structures of size $n$ is a directed acyclic graph (DAG) whose
-internal gates are marked by elements of some basis. This basis consists of
-operations or, more concretely, Boolean functions such that a gate $g$ in $C_n$
-with $k$ input gates is labelled by a function $f: \{0,1\}^A \rightarrow
-\{0,1\}$, where $\vert A \vert = k$. When evaluating the circuit, $g$ is
-computed by evaluating $f$ with the input given by the binary string formed by
-evaluating the gates input to $g$, implicitly mapping $A$ to the input gates of
-$g$. However, the output of $f$ in general depends on the order (or structure)
-of the binary string taken as input, and as such the evaluation of $g$ depends
-on which gates are assigned to each element of $A$.
+% In this paper we develop a circuit characterisation of $\FPR$ in terms of
+% symmetric circuits that have gates that compute rank. Concretely, a circuit
+% $C_n$ for structures of size $n$ is a directed acyclic graph (DAG) whose
+% internal gates are marked by elements of some basis. This basis consists of
+% operations or, more concretely, Boolean functions such that a gate $g$ in $C_n$
+% with $k$ input gates is labelled by a function $f: \{0,1\}^A \rightarrow
+% \{0,1\}$, where $\vert A \vert = k$. When evaluating the circuit, $g$ is
+% computed by evaluating $f$ with the input given by the binary string formed by
+% evaluating the gates input to $g$, implicitly mapping $A$ to the input gates of
+% $g$. However, the output of $f$ in general depends on the order (or structure)
+% of the binary string taken as input, and as such the evaluation of $g$ depends
+% on which gates are assigned to each element of $A$.
 
-This point is often ignored in circuit complexity by ensuring that functions in
-the Boolean basis are \emph{symmetric}, i.e. depend only on the number of 1's in
-it's input, rendering the particular assignment from $A$ to the input gates
-irrelevant. This is the approach taken by Anderson and Dawar \cite{AndersonD17}.
-However, functions that compute an operation like rank, i.e. a function that
-takes in a matrix with Boolean entries and outputs 1 iff that matrix, when
-interpreted in $\mathbb{F}_p$, has rank at least $r$, certainly depend on how
-the input is formed into a matrix, and as such is not a symmetric function.
+% This point is often ignored in circuit complexity by ensuring that functions in
+% the Boolean basis are \emph{symmetric}, i.e. depend only on the number of 1's in
+% it's input, rendering the particular assignment from $A$ to the input gates
+% irrelevant. This is the approach taken by Anderson and Dawar \cite{AndersonD17}.
+% However, functions that compute an operation like rank, i.e. a function that
+% takes in a matrix with Boolean entries and outputs 1 iff that matrix, when
+% interpreted in $\mathbb{F}_p$, has rank at least $r$, certainly depend on how
+% the input is formed into a matrix, and as such is not a symmetric function.
 
-We introduce the notion of a \emph{structured function}, which allows us to both
-index inputs appropriately and introduce appropriate generalisations of symmetry
-depending on the structure of the input. Each such function $F$ is uses a many-sorted
-structure, with some signature $\tau_F$, in order to index the input. This
-definition allows us to generalise the notion of symmetry to a particular
-labelling, and so introduce the notion of a \emph{$\tau$-symmetric functions}.
+% We introduce the notion of a \emph{structured function}, which allows us to both
+% index inputs appropriately and introduce appropriate generalisations of symmetry
+% depending on the structure of the input. Each such function $F$ is uses a many-sorted
+% structure, with some signature $\tau_F$, in order to index the input. This
+% definition allows us to generalise the notion of symmetry to a particular
+% labelling, and so introduce the notion of a \emph{$\tau$-symmetric functions}.
 
-We also introduce a generalised symmetric circuit allows, which allows for
-$\tau$-symmetric functions in the Boolean basis, not just symmetric ones. The
-circuit also provides a function $L$ that maps to each internal gate $g$ to a
-labelling on its input corresponding the labelling on the input of the Boolean
-function that labels this gate.
+% We also introduce a generalised symmetric circuit allows, which allows for
+% $\tau$-symmetric functions in the Boolean basis, not just symmetric ones. The
+% circuit also provides a function $L$ that maps to each internal gate $g$ to a
+% labelling on its input corresponding the labelling on the input of the Boolean
+% function that labels this gate.
 
-\begin{remark}
-  I'm not sure how much detail to go into here, this could be a major
-  digression.
-\end{remark}
+% \begin{remark}
+%   I'm not sure how much detail to go into here, this could be a major
+%   digression.
+% \end{remark}
 
-% That is, eacFor example, if we should like The circuit $C_n$ associates with
-% each internal gate $g$ a structure $\dom (g)$, and each gate input a sequence of
-% elements from each sort $\dom(g)$ in accordance with the sorts of the
+% % That is, eacFor example, if we should like The circuit $C_n$ associates with
+% % each internal gate $g$ a structure $\dom (g)$, and each gate input a sequence of
+% % elements from each sort $\dom(g)$ in accordance with the sorts of the
 
-% of definition includes an additional function which assosiates for each gate $g$
-% a
+% % of definition includes an additional function which assosiates for each gate $g$
+% % a
 
-% require that the Basis over which the circuit is defined are symemtric.. We
-% begin by generalising the notion of a symmetric circuit. A symmetric circuit, as
-% presented in \cite{AndersonD17}, and in many parts of complexity theory,
-% supposes that the in Boolean function that labels in the gate is
-% \emph{symmetric} that labels a particular gate We first generalise the notion of
-% a symmetric circuit so as to allow for gate
+% % require that the Basis over which the circuit is defined are symemtric.. We
+% % begin by generalising the notion of a symmetric circuit. A symmetric circuit, as
+% % presented in \cite{AndersonD17}, and in many parts of complexity theory,
+% % supposes that the in Boolean function that labels in the gate is
+% % \emph{symmetric} that labels a particular gate We first generalise the notion of
+% % a symmetric circuit so as to allow for gate
 
-% In this general notion of a symmetric circuit, a Boolean basis consists not just
-% of a set of Boolean functions, but a set of \emph{structured functions} -- a
-% function indexed A symmetric $\tau$-circuits is defined for some universe size
-% $n$ and Boolean basis $\mathbb{B}$ of Boolean functions. Each Boolean function
-% in $\mathbb{B}$ is a \emph{structured Boolean function} in the sense that
+% % In this general notion of a symmetric circuit, a Boolean basis consists not just
+% % of a set of Boolean functions, but a set of \emph{structured functions} -- a
+% % function indexed A symmetric $\tau$-circuits is defined for some universe size
+% % $n$ and Boolean basis $\mathbb{B}$ of Boolean functions. Each Boolean function
+% % in $\mathbb{B}$ is a \emph{structured Boolean function} in the sense that
 
-% In this abstract we review the work of Anderson and Dawar on symmetric
-% circuits, and extend their analysis by broadening the basis of functions they
-% consider to include so-called `matrix-symmetric' functions. This class of
-% functions includes important non-symmetric functions, e.g.\ the rank of a
-% matrix, and this allows us to study symmetric circuits with gates that compute
-% rank. Our main result is a circuit characterisation for FPR. In particular, we
-% show that P-uniform families of symmetric circuits with rank gates
-% characterise FPR. This requires a significant advance on the methods
-% of~\cite{AndersonD17}.
-\end{document}
+% % In this abstract we review the work of Anderson and Dawar on symmetric
+% % circuits, and extend their analysis by broadening the basis of functions they
+% % consider to include so-called `matrix-symmetric' functions. This class of
+% % functions includes important non-symmetric functions, e.g.\ the rank of a
+% % matrix, and this allows us to study symmetric circuits with gates that compute
+% % rank. Our main result is a circuit characterisation for FPR. In particular, we
+% % show that P-uniform families of symmetric circuits with rank gates
+% % characterise FPR. This requires a significant advance on the methods
+% % of~\cite{AndersonD17}.
+% \end{document}

### 2018-02-28 sections/background.tex
Updates to the entire paper 28th Feb 2018

@@
 logic $\FP$ is an extension of $\FO$ by an inflationary fixed-point operator. In
-other words, $\FP[\tau]$ includes all formulas in $\FO[\tau]$, along with all
-formulas of the form $[\ifp_{V, \vec{x}}. \phi]$, where $V$ is a relation symbol
-not in $\tau$, $\phi \in \FO[\tau \cup \{V\}]$, and $\vec{x}$ is a sequence of
-variables of length $\arty(V)$. We assume the standard syntax and semantics for
-$\FO[\tau]$ and $\FP[\tau]$. For more detail on the syntax and semantics of
-these logics please see~\cite{grohe2017descriptive} and~\cite{GradelP15a}.
+other words, $\FP[\tau]$ includes all formulas in $\FO[\tau]$, and is closed
+under applications of the fixed-pint operator, i.e. if $\phi \in \FP[\tau]$, $V$
+is a second-order variable, and $\vec{x}$ is a tuple of variables of length
+$\arty(V)$, then $[\ifp_{V, \vec{x}}. \phi] \in FP[\tau]$. We assume the
+standard syntax and semantics for $\FO[\tau]$ and $\FP[\tau]$. For more detail
+on the syntax and semantics of these logics please
+see~\cite{grohe2017descriptive} and~\cite{GradelP15a}.
 
@@
 $L$ where for all $i \in [k]$ each variable $x_i$ is assigned to $\alpha(x_i)$.
-If the logic is obvious from context we omit the subscript and just write
-$\mathcal{A} \models \phi[\vec{a}]$.
+If the sequence of variables $\vec{x}$ that we are assigning to $\vec{a}$ is
+obvious from context we write $\mathcal{A} \models_L \phi[\vec{a}]$ instead. If
+the logic is obvious from context we omit the subscript and just write
+$\mathcal{A} \models \phi[\alpha]$.
 
@@
 the vocabulary $\tau$. The logic $\FPC$ is an extension of $\FP$ that includes a
-counting operator that allows the logic to determine the size of a definable
-set, as well as other mechanisms for reasoning about quantities. We now briefly
-describe the structure of a formula of $\FPC[\tau]$. Every first-order variable
-is assigned a type, and so each variable is either a \emph{vertex} or
-\emph{number} variable. Vertex variables are assigned to elements of the
-universe of the structure, and play a similar role to the variables that appear
-in formulas in $\FO[\tau]$ or $\FP[\tau]$. Number variables are assigned to
-elements of $\nats$. We usually use Latin letters (e.g. $x, y, z, \ldots$) to
-denote vertex variables and Greek letters (e.g. $\mu, \nu, \epsilon, \ldots$) to
-denote number variables. All atomic formulas in $\FP[\tau]$ are atomic formulas
-in $\FPC[\tau]$. We say that $t$ is a \emph{number term} if $t$ a number
-variable or if $t$ is an application of the \emph{counting operator}, i.e. $t =
-\#x. \phi(x)$, where $\phi \in \FPC[\tau]$ and $x$ is a vertex variable free in
-$\phi$. If $t_1$ and $t_2$ are number terms then $t_1 \leq t_2$ and $t_1 = t_2$
-are atomic formulas. $\FPC[\tau]$ includes all formulas formed by closing the
-set of atomic formulas under the usual Boolean connectives, the first-order
-quantifiers (for vertex variables), and the inflationary fixed-point operator.
-The second-order variables, such as those that appear in an application of the
-fixed-point operator, are allowed to have mixed-type, i.e. we associate with a
-second-order variable $R$ a type $(k, l) \in \nats^2$ intended to mean that $R$
-is assigned to a subset of $U^k \times \nats^l$.
+counting operator that allows us to define the size of a definable set, as well
+as other mechanisms for reasoning about quantities. We now briefly describe the
+structure of a formula of $\FPC[\tau]$. Every first-order variable is assigned a
+type, and so each variable is either a \emph{vertex} or \emph{number} variable.
+Vertex variables are assigned to elements of the universe of the structure, and
+play a similar role to the variables that appear in formulas in $\FO[\tau]$ or
+$\FP[\tau]$. Number variables are assigned to elements of $\nats$. We usually
+use Latin letters (e.g. $x, y, z, \ldots$) to denote vertex variables and Greek
+letters (e.g. $\mu, \nu, \epsilon, \ldots$) to denote number variables. All
+atomic formulas in $\FP[\tau]$ are atomic formulas in $\FPC[\tau]$. We say that
+$t$ is a \emph{number term} if $t$ is a number variable or if $t$ is an application
+of the \emph{counting operator}, i.e. $t = \#x. \phi(x)$, where $\phi \in
+\FPC[\tau]$ and $x$ is a vertex variable free in $\phi$. If $t_1$ and $t_2$ are
+number terms then $t_1 \leq t_2$ and $t_1 = t_2$ are atomic formulas.
+$\FPC[\tau]$ includes all formulas formed by closing the set of atomic formulas
+under the usual Boolean connectives, the first-order quantifiers (for vertex
+variables), and the inflationary fixed-point operator. The second-order
+variables, such as those that appear in an application of the fixed-point
+operator, are allowed to have mixed-type, i.e. we associate with a second-order
+variable $R$ a type $(k, l) \in \nats^2$ intended to mean that $R$ is assigned
+to a subset of $U^k \times \nats^l$.
 
@@
 \vert$ in $\mathcal{A}$, assuming a fixed assignment to the other free variables
-in $\phi$. The intended semantics for bounded quantification is that the
-variable may only be assigned to a value at most equal to the the evaluation of
-the number term bounding the variable. The semantics of the `$=$' and `$\leq$'
-symbols are defined for number terms in the obvious manner. For a more detailed
-description of the syntax and semantics of $\FPC$ please
-see~\cite{grohe2017descriptive} or the introduction of~\cite{GradelP15a}.
+in $\phi$. The intended semantics for bounded quantification is as for ordinary
+quantification but with the additional restriction that the assignment to the
+number variable be bounded by the evaluation of the bounding number term. The
+semantics of the `$=$' and `$\leq$' symbols are defined for number terms in the
+obvious manner. For a more detailed description of the syntax and semantics of
+$\FPC$ please see~\cite{grohe2017descriptive} or the introduction
+of~\cite{GradelP15a}.
 
@@
 Let $\FOC[\tau]$ denote \emph{first-order logic with counting} with respect to
-the vocabulary $\tau$, and be the set of all formulas in $\FPC[\tau]$ that do
-not contain the an application of the fixed-point operator.
+the vocabulary $\tau$, and let $\FOC[\tau]$ be set of all formulas in
+$\FPC[\tau]$ that do not contain an application of the fixed-point operator.
 
@@
   logic}) with respect to the vocabulary $\tau$. The logic $\FPR$ is an
-extension of $\FP$ to include an operator that decides the rank of a definable
+extension of $\FP$ to include an operator that denotes the rank of a definable
 matrix over a finite field, as well as other mechanisms for reasoning about
@@
 and~\cite{Dawar09logicswith}. As in the case of $\FPC$, each variable is either
-a number or vertex variable, with vertex variables being assigned to elements of
-the universe and number variables assigned to natural numbers. All atomic
-formulas in $\FP[\tau]$ are atomic formulas in $\FPR[\tau]$. We say that $t$ is
-a \emph{number term} if $t$ is a number variable or if $t$ is an application of
+a number or vertex variable, with vertex variables assigned to elements of the
+universe and number variables assigned to natural numbers. All atomic formulas
+in $\FP[\tau]$ are atomic formulas in $\FPR[\tau]$. We say that $t$ is a
+\emph{number term} if $t$ is a number variable or if $t$ is an application of
 the \emph{rank operator}, i.e. $t = [\rank (\vec{x}, \vec {\nu} \leq \vec{t},
@@
 We now briefly explain the intended semantics of the rank operator. Let $\phi
-(\vec{x}, \vec {\nu}, \vec{y}\vec{\mu})$ be a number term, where $\vec{x}$ and
+(\vec{x} \vec {\nu}, \vec{y}\vec{\mu})$ be a number term, where $\vec{x}$ and
 $\vec{y}$ are tuples of vertex variables, $\vec{\nu}$ and $\vec{\mu}$ are tuples
-of number variables. Let and $\vec{s}$ and $\vec{t}$ be tuples of number terms
-that bound the ranges of $\vec{\nu}$ and $\vec{\mu}$, respectively. Let $\pi$ be
-a number variable and $r$ be a number term bounding the range of $\pi$. Let
+of number variables. Let $\vec{s}$ and $\vec{t}$ be tuples of number terms such
+that $\vert \vec{s} \vert = \vert \vec{\nu} \vert$ $\vert \vec{t}\vert = \vert
+\vec{mu} \vert$. Let $\pi$ be a number variable and $r$ be a number term. Let
 $\mathcal{A}$ be a structure with universe $A$, and suppose we have a given
-assignment to the all of the free variables appearing in $r$ and in the terms in
+assignment to the those free variables appearing in $r$ or in the terms in
 $\vec{t}$ and $\vec{s}$. Let $\mathbb{N}^{\leq\vec{t}} := \{\vec{n} \in
-\mathbb{N}^{\vert \vec{v} \vert}: n_i \leq t^{\mathcal{A}}_i\}$, and let
+\mathbb{N}^{\vert \vec{\nu} \vert}: n_i \leq t^{\mathcal{A}}_i\}$, and let
 $\mathbb{N}^{\leq \vec{s}}$ be defined similarly. Let $I:= A^{\vert \vec{x}
@@
 \vec{b}\vec{m}):= \phi^{\mathcal{A}}(\vec{a}\vec{n},\vec{b}\vec{m})$. For the
-structure $\mathcal{A}$ and assignment $\pi \mapsto p$, for $p \leq r^{A}$
-prime, $[\rank (\vec{x}, \vec {\nu} \leq \vec{t}, \vec{y}\vec{\mu} \leq \vec{s},
-\pi \leq r). \phi]$ evaluates to the rank of $M^{\mathcal{A}}_\phi$ mod $p$,
-where the entries in $M^{\mathcal{A}}$ are interpreted as elements of
-$\mathbb{F}_p$.
+structure $\mathcal{A}$ and assignment $\pi \mapsto p$, where $p \leq
+r^{\mathcal{A}}$, if $p$ is prime then the rank term $[\rank (\vec{x}, \vec
+{\nu} \leq \vec{t}, \vec{y}\vec{\mu} \leq \vec{s}, \pi \leq r). \phi]$ is the
+rank of $M^{\mathcal{A}}_\phi$ mod $p$, where the entries in $M^{\mathcal{A}}$
+are interpreted as elements of $\mathbb{F}_p$. If $p$ is not prime then the rank
+term evaluates to zero.
 
-We should note that there are two different of rank logics defined in the
-literature. The first, introduced by Dawar et al.~\cite{Dawar09logicswith},
-differs from the one defined above in that it does not take the characteristic
-of the field as a parameter, instead including a different operator for every
-prime field over which compute rank. It was shown by Grad{\"e}l and
-Pakusa~\cite{GradelP15a} that this rank logic does not capture $\PT$. Grad{\"e}l
-and Pakusa introduced the rank logic we have presented above and showed that
-this logic, with the uniform rank operator, is strictly more expressive then the
-rank logic introduced by Dawar et al. For this reason when we refer to rank
-logic we are always referring to the rank logic introduced by Grad{\"e}l and
+We should note that there are two distinct rank logics defined in the
+literature. The first was introduced by Dawar et al.~\cite{Dawar09logicswith},
+and differs from the rank logic defined above in that it includes a sequence of
+rank operator, rather than a single uniform operator, one for each prime $p$
+expressing the rank over the field $\ff_p$. It was shown by Grad{\"e}l and
+Pakusa~\cite{GradelP15a} that this non-uniform rank logic does not capture
+$\PT$. After proving this result, Grad{\"e}l and Pakusa introduced the rank
+logic with a uniform rank operator that we have presented above, and showed that
+this rank logic is strictly more expressive then the rank logic introduced by
+Dawar et al. This uniform rank logic remains a candidate for capturing
+polynomial-time. For this reason when we refer to rank logic in this paper we
+are always referring to the rank logic introduced by Grad{\"e}l and
 Pakusa~\cite{GradelP15a}.
@@
 $\FOR[\tau]$ denote \emph{first-order with rank} with respect to the vocabulary
-$\tau$, and be the set of formulas in $\FPR[\tau]$ that do not contain an
-application of the fixed-point operator.
+$\tau$, and let $\FOR[\tau]$ be the set of formulas in $\FPR[\tau]$ that do not
+contain an application of the fixed-point operator.
 
@@
 al~\cite{Dawar09logicswith}, is similar to $\FPR$, except that it extends $\FP$
-by \emph{rank quantifiers}, rather than a rank operator, that can decide if a
-definable matrix has a rank bounded by some constant. We define for each prime
+by a set of \emph{rank quantifiers}, rather than a rank operator. We define for each prime
 $p$, and natural number $r$, a rank quantifier $\rank^r_p$, such that
@@
 $\FOrk[\tau]$ denote \emph{first-order with rank quantifiers} with respect to
-the vocabulary $\tau$, and be the set of all formulas in $\FPR[\tau]$ that do
-not contain an application of the fixed-point operator.
+the vocabulary $\tau$, and let $\FOrk[\tau]$ be the set of all formulas in
+$\FPR[\tau]$ that do not contain an application of the fixed-point operator.
 
-For more detail on the syntax and semantics of logics rank quantifiers please
+For more detail on the syntax and semantics of logics with rank quantifiers please
 see~\cite{Dawar09logicswith}. It is easy to see that $\FPrk \leq \FPR$ and
-$\FOrk \leq \FOR$. Moreover, we note that $[\rank(\vec{x}, \vec{y}).
-(\vec{x} = \vec{y}, \pi \leq r) \land \phi(\vec{x})]$ evaluates, for a structure
+$\FOrk \leq \FOR$. Moreover, we note that $[\rank(\vec{x}, \vec{y}). (\vec{x} =
+\vec{y}, \pi \leq r) \land \phi(\vec{x})]$ evaluates, for a structure
 $\mathcal{A}$ and any assignment $\pi \mapsto p$, to the number of assignments
@@
 length $n$. We have $\AND, \OR, \NAND, \MAJ : \{0,1\}^* \rightarrow \{0,1\}$,
-where $\AND, \OR, \NAND$ are the usual (unbounded fan-in) logical operators, amd
+where $\AND, \OR, \NAND$ are the usual (unbounded fan-in) logical operators, and
 $\MAJ$ is the majority function. We write $\BS := \{\AND, \OR, \NOT\}$ to denote
-the \emph{standard basis} and $\BS := \BS \cup \{\MAJ\}$ to denote the
+the \emph{standard basis} and $\BM := \BS \cup \{\MAJ\}$ to denote the
 \emph{majority basis}.
@@
 $C$ of order $n$ for the input $\vec{a} \in \{0,1\}^n$ is denoted by
-$C[\vec{a}]$ and computed by recursively evaluation the gates in the circuit. We
+$C[\vec{a}]$ and computed by recursively evaluating the gates in the circuit. We
 denote the evaluation of a gate $g$ in $C$ for the input $\vec{a}$ by
@@
 symbol denoting a Boolean operation, and $C[\vec{a}](g)$ is the result of
-applying that operation the string formed from the evaluations of those gates
+applying that operation to the string formed from the evaluations of those gates
 input to $g$. If $g$ is the output gate, let $C[\vec{a}] = C[\vec{a}](g)$.
@@
   decided by a P-uniform family of symmetric circuits defined over the basis
-  $\BS$ if, and only if, it is expressible in $\FPC[\tau]$.
+  $\BM$ if, and only if, it is expressible in $\FPC[\tau]$.
 \end{thm}
+
+\subsection{Equivalence Relations}
+Let $\sim$ be an equivalence relation on the set $X$. For $x \in X$ we write
+$[x]_\sim$ to denote the equivalence class of $x$ with respect to $\sim$. We
+omit the subscript if the equivalence relation is obvious from context. We write
+$X/_{\sim}$ to denote the set of equivalence classes of $X$. Let $A = \Pi_{i \in
+  I} A_i$ and let $J \subseteq I$ be such that for $i \in J$, $A_i \subseteq X$.
+Let $\sim_A$ be an equivalence relation on $A$ defined such that $\vec{a} \sim_A
+\vec{b}$ if, and only if, $\vec{a}(i) = \vec{b}(i)$ for all $i \in J$. We call
+$\sim_A$ the \emph{extension} of $\sim$ to $A$. We often abuse notation and
+write $\sim$ for the extension of the equivalence relation $\sim$. We notice
+that $(\Pi_{i \in I} A_i) /_{\sim} = \Pi_{i \in I} (A_i /_\sim)$.
+
+Let $Y$ and $Z$ be sets and let $f : Y \rightarrow Z$ be a function. We say $f$
+is \emph{invariant} under $\sim$ if for all $a, b \in Y$ if $a \sim_Y b$ then
+$f(a) \sim_Z f(b)$. If $f$ is an invariant under $\sim$ then $f /_{\sim}$ is a
+function mapping $Y /_{\sim_Y} $ to $ Z /_{\sim_Z}$ such that $f /_{\sim} ([a]) =
+[f(a)]$ for all $a \in Y$. We call $f_{\sim}$ the \emph{quotient} of $f$ with
+respect to $\sim$.
 

### 2018-02-28 sections/symmetric-circuits.tex
Updates to the entire paper 28th Feb 2018

@@
 function. We say $F$ is \emph{$G$-invariant} if it is constant on $G$-equivalent
-input vectors, i.e. for all $G$-equivalent $f, g \in \{0,1\}^{X}$, $F(f) =
+input vectors, i.e.\ for all $G$-equivalent $f, g \in \{0,1\}^{X}$, $F(f) =
 F(g)$. We say $F$ is \emph{isomorphism-invariant} if it is $\aut(\tau,
@@
 that naturally enforces the symmetry and irreflexivity properties the edge
-relation. We should note, however, that symmetry and irreflexivity are
-properties of directed-graph, and as such can be decided by an
-isomorphism-invariant structured function over the graph vocabulary.
+relation.
+
+% We should note, however, that symmetry and irreflexivity are
+% properties of directed-graph, and as such can be decided by an
+% isomorphism-invariant structured function over the graph vocabulary.
 
@@
 $W(\cdot, g)$ the \emph{children} of $g$ and the elements of $W(g, \cdot)$ the
-\emph{parents} of $g$. We also abbreviate $W(g, \cdot)$ by $H_g$.
+\emph{parents} of $g$. We also abbreviate $W(g, \cdot)$ by $H_g$. We write $W_T$
+for the transitive closure of $W$.
 
@@
   \mathcal{A} \models \Sigma(g)(\Lambda (g))$, and
-\item if $g$ is an internal gate such that $\Sigma (g)$ let $L^{\gamma}_g:
-  \ind(g) \rightarrow \{0,1\}$ be defined by $L^{\gamma}_g(x) = C[\gamma
-  \mathcal{A}](L(g)(x))$, for all $x \in \ind(g)$. Then $g$ evaluates to true
-  if, and only if, $\Sigma(g) (L^{\gamma}_g) = 1$.
+\item if $g$ is an internal gate such that $\Sigma (g)$ let $L^{\gamma
+    \mathcal{A}}(g): \ind(g) \rightarrow \{0,1\}$ be defined by
+  $L^{\gamma\mathcal{A}}(g)(x) = C[\gamma \mathcal{A}](L(g)(x))$, for all $x \in
+  \ind(g)$. Then $g$ evaluates to true if, and only if, $\Sigma(g)
+  (L^{\gamma}_g) = 1$.
 \end{enumerate}
@@
   $R^{[n]}$. Thus we can think of the function $F_C$ computed by the circuit as
-  having it's input string indexed by the elements of $\ind(\rho, [n])$, and so
+  having its input string indexed by the elements of $\ind(\rho, [n])$, and so
   think of $F_C$ as a $(\rho, [n])$-structured function.
@@
 into the circuit. We call these circuits \emph{transparent} circuits. We show in
-Sections~\ref{sec:transparency-and-unique-extensions} and~\ref{} that
-transparency is sufficient to allow for the polynomial-time decidability of many
-important circuit properties, while still keeping the circuit model powerful
-enough for us to establish a translation from formulas to families of circuits.
+Sections~\ref{sec:transparency-and-unique-extensions} that transparency is
+sufficient to allow for the polynomial-time decidability of many important
+circuit properties, while still keeping the circuit model powerful enough for us
+to establish a translation from formulas to families of circuits.
 
@@
 underneath them are `hereditary similar'.
-
 % In order to prove this result, Anderson and Dawar introduce the notion of a
@@
 
-\begin{definition}
-  Let $\tau$ be a many-sorted vocabulary and $D$ and $D'$ be $\tau$-sorted sets.
-  Let $X$ be a set and $\sim$ be an equivalence relation defined on $X$. Let $Y,
-  Z \subset X$. We say two functions $f : \ind(\tau,D) \rightarrow X$ and $g :
-  \ind(\tau, D') \rightarrow Y$ are \emph{isomorphism-equivalent up to $\sim$}
-  if there exists an isomorphism $\pi : \str{\tau, D} \rightarrow \str{\tau,
-    D'}$ such that $f (\vec{x}_R) \sim g (\pi \vec{x}_R)$ for all $\vec{x}_R \in
-  \ind(\tau, D)$ .
-\end{definition}
+% \begin{definition}
+%   Let $\tau$ be a many-sorted vocabulary and $D$ and $D'$ be $\tau$-sorted
+%   sets. Let $X$ be a set and $\sim$ be an equivalence relation defined on $X$.
+%   Let $Y, Z \subset X$. We say two functions $f : \ind(\tau,D) \rightarrow X$
+%   and $g : \ind(\tau, D') \rightarrow Y$ are \emph{isomorphism-equivalent up
+%   to $\sim$} if there exists an isomorphism $\pi : \str{\tau, D} \rightarrow
+%   \str{\tau, D'}$ such that $f (\vec{x}_R) \sim g (\pi \vec{x}_R)$ for all
+%   $\vec{x}_R \in \ind(\tau, D)$ .
+% \end{definition}
 
@@
   $h$ are internal gates and and suppose we have defined the
-  syntactic-equivalence relation for all gates of height less than the height of
-  either $g$ or $h$. Then $g \equiv h$ if, and only if, $L(g)$ and $L(h)$ are
-  isomorphism equivalent up to $\equiv$.
+  syntactic-equivalence relation for all gates of depth less than the depth of
+  either $g$ or $h$. Then $g \equiv h$ if, and only if, $L(g) /_\equiv$ and
+  $L(h) /_\equiv$ are isomorphism equivalent.
 \end{definition}
@@
 
-We could think of any gate $g$ in the circuit as computing a function that maps
-a given assignment to the input gates to the evaluation of the circuit at $g$
-for the given assignment. While we would like to be able to identify gates that
-compute the same function in this sense, it is not hard to show that deciding
-this property is $\NP$-hard. The syntactic-equivalence relation is an
-easier-to-compute refinement of this relation, instead identifying pairs of
-gates if the circuits underneath them are hereditary similar.
-
-We could also define a similar equivalence relation using the automorphisms of a
-circuit. In this case we identify a pair of gates $(h, h')$ in a circuit $C$ of
-order $n$ if, and only if, there exists $\sigma \in \sym_n$, $\pi, \pi' \in
-\aut(C)$ both extending $\sigma$, and $g$ a gate in $C$, such that $h = \pi (g)$
-and $h' = \pi' (g)$. We now show this relation is a refinement of
-syntactic-equivalence.
-
-\begin{remark}
-  It's interesting to note that if $C$ has unique extensions then this relation
-  collapses to equality, syntactic-equivalence does not. Note to self: should I
-  mention this? Also, the following result is equivalent to checking for just
-  $\pi $
-\end{remark}
+For a circuit $C$ of order $n$ and a gate $g$ we map think of $g$ as computing
+the function that maps an input structure $\mathcal{A}$ and a bijection $\gamma$
+from the universe of $\mathcal{A}$ to $[n]$ to the evaluation $C[\gamma
+\mathcal{A}(g)$. While we would like to be able to identify gates that compute
+the same function in this sense, it is not hard to show that deciding this
+equivalence relation for a given circuit is $\NP$-hard. We now show that if two
+gates are syntactically-equivalent then the functions computed at these two
+gates must be equal. We show later that the syntactic-equivalence relation is
+polynomial-time decidable for the class of circuits of interest to us in this
+paper.
+
+\begin{lem}
+  Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\BB,
+  \rho)$-circuit of order $n$. Let $\mathcal{A}$ be a $\rho$-structure of size
+  $n$ and let $\gamma$ be a bijection from the universe of $\mathcal{A}$ to
+  $[n]$. For all $g, g' \in G$ if $g \equiv g'$ then $C[\gamma \mathcal{A}](g) =
+  C[\gamma \mathcal{A}](g')$.
+  \label{lem:syntactic-equivalence-equal-function}
+\end{lem}
+\begin{proof}
+  We prove the result by induction on depth. Suppose $g$ and $g'$ have depth $0$
+  and $g \equiv g'$. Then they are both input gates and so $g = g'$. The result
+  for depth $0$ then follows trivially. Suppose $g$ and $g'$ are internal gates,
+  and suppose for all $h, h' \in G$ of depth less than $g$ or $g'$ we have that
+  if $h \equiv h'$ then $C[\gamma \mathcal{A}](h) = C[\gamma \mathcal{A}](h')$.
+  Suppose $g \equiv g'$. Then exists $\lambda \in \aut(g)$ such that $L(g) (x)
+  \equiv L(g') (\lambda x)$ for all $x \in \ind(g)$. It follows from the
+  inductive hypothesis that $L^{\gamma \mathcal{A}}(g)(x) = C[\gamma
+  \mathcal{A}](L(g)(x)) = C[\gamma \mathcal{A}](L(g')(\lambda x)) = (L^{\gamma
+    \mathcal{A}}(g) \lambda) (x)$ for all $x \in \ind(g)$. Since $\Sigma(g)$
+  (and so $\Sigma(g')$) is a structured function, it follows that $C[\gamma
+  \mathcal{A}](g) = \Sigma(g)(L^{\gamma \mathcal{A}} (g)) = \Sigma(g')
+  (L^{\gamma \mathcal{A}})(g') \lambda) = \Sigma(g') (L^{\gamma
+    \mathcal{A}}(g')) = C[\gamma \mathcal{A}](g')$. The result follows.
+\end{proof}
+
+The syntactic-equivalence relation identifies gates that have `equivalent'
+circuits underneath them. A similar intuition is captured by identifying gates
+that are mapped to one another by automorphisms of the circuit that extend the
+trivial permutation. We now show that if two automorphisms extend the same
+permutation then the two images of each gate must be syntactically-equivalent.
+
+% Stated slightly differently, we identify the gates $h$ and $h'$ in a circuit
+% $C$ of order $n$ if, and only if, there exists $\sigma \in \sym_n$, $\pi, \pi'
+% \in \aut(C)$ both extending $\sigma$, and $g$ a gate in $C$, such that $h =
+% \pi (g)$ and $h' = \pi' (g)$. We now show this relation is a refinement of
+% syntactic-equivalence.
+
+% \begin{remark}
+%   It's interesting to note that if $C$ has unique extensions then this
+%   relation collapses to equality, syntactic-equivalence does not. Note to
+%   self: should I mention this? Also, the following result is equivalent to
+%   checking for just $\pi $
+% \end{remark}
 
@@
 
-  We now prove the result by induction on height. Suppose $g$ is a gate of
-  height $0$. Then $g$ is either a relational or constant gate. In either case
-  $\pi (g) = \pi' (g)$, and so $\pi(g)$ and $\pi'(g)$ are
-  syntactically-equivalent.
-
-  Suppose $g$ is an internal gate and suppose that for every gate $h$ of height
+  We now prove the result by induction on depth. Suppose $g$ is a gate of depth
+  $0$. Then $g$ is either a relational or constant gate. In either case $\pi (g)
+  = \pi' (g)$, and so $\pi(g)$ and $\pi'(g)$ are syntactically-equivalent.
+
+  Suppose $g$ is an internal gate and suppose that for every gate $h$ of depth
   less than $g$, $\pi (h)$ is syntactically-equivalent to $\pi'(h)$. We have
@@
 
-We now define the \emph{unique labels} and \emph{transparency} conditions on
-circuits.
+It follows from Lemma~\ref{lem:permutation-extending-syntactic-equivalence} that
+the syntactic-equivalence relation of a circuit $C$ constrains the automorphism
+group of $C$, and so the orbits and stabiliser groups of the gates in $C$. We
+say that a circuit $C$ is \emph{syntactically simple} if $C$ has trivial
+syntactic-equivalence classes, i.e. for all gates $g$ and $h$ in $C$ if $g
+\equiv h$ then $g = h$. An immediate corollary of
+Lemma~\ref{lem:permutation-extending-syntactic-equivalence} is that if a circuit
+is syntactically simple then it has unique extensions. We now define a few
+properties of circuits in terms of the structure of their syntactic-equivalence
+classes.
 
@@
   Let $C$ be a circuit and $g$ be a gate in $C$. We say $g$ has \emph{injective
-    labels} if $L(g)$ is an injection. We say $g$ has \emph{unique labels} if
-  $g$ has injective labels and no two gates in $\img(L(g))$ are
-  syntactically-equivalent. We say $C$ has \emph{injective labels} (resp.
-  \emph{unique labels}) if every gate in $C$ has injective labels (resp. unique
-  labels). We say $C$ is \emph{transparent} if every gate $g$ in $C$ such that
-  $\Sigma(g)$ is not a symmetric function has unique labels.
+    labels} if $L(g)$ is an injection. We say $g$ has \emph{unique children} if
+  no two gates in $H_g$ are syntactically-equivalent. We say $g$ has
+  \emph{unique labels} if $g$ has injective labels and unique children. We say
+  $C$ has \emph{injective labels} (resp. \emph{unique labels}) if every gate in
+  $C$ has injective labels (resp. unique labels). We say $C$ is
+  \emph{transparent} if every gate $g$ in $C$ such that $\Sigma(g)$ is not a
+  symmetric function has unique labels.
 \end{definition}
+
+It is worth noting that if a circuit has injective labels and is syntactically
+simple then then it has unique labels. The converse is, in general, false.
 
@@
 assume, unless stated otherwise, every circuit has no redundant gates. With this
-assumption in mind we now show that every circuit with unique labels has unique
-extensions.
+assumption in mind we now show that every circuit with unique children (and so
+unique labels) has unique extensions.
 
@@
   Let $C := \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a $(\mathbb{B},
-  \rho)$-circuit of order $n$. If $C$ has unique labels then $C$ has unique
+  \rho)$-circuit of order $n$. If $C$ has unique children then $C$ has unique
   extensions.
-  \label{prop:unique-labels-unique-extensions}
+  \label{prop:unique-children-unique-extensions}
 \end{prop}
 \begin{proof}
-  Suppose $C$ has unique labels. Let $\pi_{\sigma}, \pi_{\sigma}' \in \aut(C)$
+  Suppose $C$ has unique children. Let $\pi_{\sigma}, \pi_{\sigma}' \in \aut(C)$
   be automorphisms extending $\sigma \in \sym_n$. We now prove that $\pi_\sigma
@@
   Lemma~\ref{lem:permutation-extending-syntactic-equivalence} that $h$ is
-  syntactically-equivalent to $\pi (h)$ and, since $g$ has unique labels, $h$ is
-  the only gate in $H_g$ syntactically-equivalent to $h$. It follows that $\pi
-  (h) = h$.
+  syntactically-equivalent to $\pi (h)$ and, since $g$ has unique children, $h$
+  is the only gate in $H_g$ syntactically-equivalent to $h$. It follows that
+  $\pi (h) = h$.
 
@@
 
-We show in Proposition~\ref{prop:transparent-unique} that a transparent circuit
-can be converted into an equivalent circuit with unique labels in time
-polynomial in the size of the circuit. Since we are
-working with $P$-uniform families of transparent circuits, this fact allows us
-to assume, without a loss of generality, that transparent circuits have unique
-labels (and so unique extensions).
+It follows from Proposition~\ref{prop:unique-children-unique-extensions} that if
+$C$ is of order $n$ then for each $\sigma \in \sym_n$ there exists at most one
+$\pi_\sigma \in \aut(C)$ extending $\sigma$. However, if $g$ is a gate in $C$
+and $\pi_{\sigma} g = g'$ there may no `canonical' $\lambda \in \aut(g)$
+witnessing the isomorphism-equivalence, i.e.\ such that $\pi L(g) = L(g')
+\lambda$. It is this lack of a `canonical' choice that allows us to prove in
+Section~\ref{sec:transparency-and-unique-extensions} that a great many important
+circuit properties (e.g. the orbit of a gate, symmetry of a circuit, etc.) for
+circuits with unique gates are at least as hard as the graph-isomorphism problem
+to decide.
+
+In contrast, it is easy to see that if $C$ has unique labels, and $g$ and $g'$
+are gates in the circuit, then $L(g)$ and $L(g')$ are isomorphism-equivalent if,
+and only if, $\lambda := L(g')^{-1}L(g)$ is in $\aut(g)$. We show in
+Section~\ref{sec:transparency-and-unique-extensions} all of the circuit
+properties of interest in this paper are polynomial-time decidable for circuits
+with unique labels. Moreover, we show in
+Proposition~\ref{prop:transparent-unique} that a transparent circuit can be
+converted into an equivalent circuit with unique labels in time polynomial in
+the size of the circuit. Since we are working with $P$-uniform families of
+transparent circuits, this fact allows us to assume, without a loss of
+generality, that transparent circuits have unique labels (and, from
+\ref{prop:unique-children-unique-extensions} so unique extensions).
 

### 2018-02-28 sections/translating-formulas-to-cicuits.tex
Updates to the entire paper 28th Feb 2018

@@
 \begin{document}
-In this section we first introduce a number of useful polynomial-time computable
-functions which define transformations on circuits. In the second subsection we
-use these functions to define a transformation that takes $\FPR$-formulas to
-equivalent families of transparent symmetric rank-circuits.
+% In this section we first introduce a number of useful polynomial-time
+% computable functions which define transformations on circuits. In the second
+% subsection we use these functions to define a transformation that takes
+% $\FPR$-formulas to equivalent families of transparent symmetric rank-circuits.
 
-\subsection{Algorithms for Circuits}
-In order to simplify the presentation of the translation between $P$-uniform
-families of circuits and formulas of $\FPR$, as well as the proofs of other
-results (see Lemma~\ref{lem:transparent-unique}), we define a number of
-often-used polynomial-time computable circuit transformations.
+% \subsection{Algorithms for Circuits}
+% In order to simplify the presentation of the translation between $P$-uniform
+% families of circuits and formulas of $\FPR$, as well as the proofs of other
+% results (see Lemma~\ref{lem:transparent-unique}), we define a number of
+% often-used polynomial-time computable circuit transformations.
 
-We first define the function $\op{merge}$, which maps a circuit and a set of
-syntactically-equivalent gates to a circuit formed by combining those gates into
-a single gate.
+% We first define the function $\op{merge}$, which maps a circuit and a set of
+% syntactically-equivalent gates to a circuit formed by combining those gates
+% into a single gate.
 
-\begin{definition}
-  Let $C := \langle G, \Omega, \Sigma , \Lambda, L \rangle$ be a circuit and $H
-  := \{h_1, \ldots, h_p\}$ be a set of syntactically equivalent gates. We let
-  $\op{merge}(C, H) := C' := \langle G', \Omega', \Sigma', \Lambda', L'
-  \rangle$, where
-  \begin{itemize}
-    \setlength\itemsep{0mm}
-  \item $G' = G \setminus \{h_2, \ldots, h_p\}$,
-  \item $\Omega' = \Omega$,
-  \item $\Sigma' = \restr{\Sigma}{G'}$,
-  \item $\Lambda' = \Lambda$, and
-  \item For all $g \in G'$ and $x \in Ind(g)$ if $L(g) (x) \in H$ then $L'(g)(x)
-    = h_1$ and if $L(g)(x) \notin H$ then $L'(g)(x) = L(g)(x)$.
-  \end{itemize}
-\end{definition}
+% \begin{definition}
+%   Let $C := \langle G, \Omega, \Sigma , \Lambda, L \rangle$ be a circuit and
+%   $H := \{h_1, \ldots, h_p\}$ be a set of syntactically equivalent gates. We
+%   let $\op{merge}(C, H) := C' := \langle G', \Omega', \Sigma', \Lambda', L'
+%   \rangle$, where
+%   \begin{itemize}
+%     \setlength\itemsep{0mm}
+%   \item $G' = G \setminus \{h_2, \ldots, h_p\}$,
+%   \item $\Omega' = \Omega$,
+%   \item $\Sigma' = \restr{\Sigma}{G'}$,
+%   \item $\Lambda' = \Lambda$, and
+%   \item For all $g \in G'$ and $x \in Ind(g)$ if $L(g) (x) \in H$ then
+%     $L'(g)(x) = h_1$ and if $L(g)(x) \notin H$ then $L'(g)(x) = L(g)(x)$.
+%   \end{itemize}
+% \end{definition}
 
-It can be shown that $\op{merge}$ can be computed in time polynomial in the size
-of the input circuit. We note that the input and output circuits compute the
-same function. Moreover, if the input circuit is symmetric (resp. has unique
-labels, is transparent) then the output circuit will also be symmetric (resp.
-have unique labels, transparent).
+% It can be shown that $\op{merge}$ can be computed in time polynomial in the
+% size of the input circuit. We note that the input and output circuits compute
+% the same function. Moreover, if the input circuit is symmetric (resp. has
+% unique labels, is transparent) then the output circuit will also be symmetric
+% (resp. have unique labels, transparent).
 
-We now define the function $\op{merge-all}$ which maps a circuit and a set of
-gates to a new circuit formed by applying $\op{merge}$ to the
-syntactic-equivalence classes of the set of gates.
+% We now define the function $\op{merge-all}$ which maps a circuit and a set of
+% gates to a new circuit formed by applying $\op{merge}$ to the
+% syntactic-equivalence classes of the set of gates.
 
-\begin{definition}
-  \label{def:merge-all}
-  The function $\op{merge-all}$ maps a circuit $C$ and a set of gates $H$ to a
-  circuit $\op{merge-all}(C, H) := C'$, where $C'$ is defined as follows. Let
-  $H_1, \ldots, H_p$ be the syntactic equivalence classes of $H$, and let $C'$
-  be defined from $C$ by successively applying $\op{merge}$ to each of these
-  equivalence classes.
-\end{definition}
+% \begin{definition}
+%   \label{def:merge-all}
+%   The function $\op{merge-all}$ maps a circuit $C$ and a set of gates $H$ to a
+%   circuit $\op{merge-all}(C, H) := C'$, where $C'$ is defined as follows. Let
+%   $H_1, \ldots, H_p$ be the syntactic equivalence classes of $H$, and let $C'$
+%   be defined from $C$ by successively applying $\op{merge}$ to each of these
+%   equivalence classes.
+% \end{definition}
 
-We can compute $\op{merge-all}$ using the following algorithm. Let $(C, H)$ be a
-tuple in the domain of $\op{merge-all}$. We assume a reasonable encoding of the
-circuit, and note that any such encoding induces a linear order on the
-structure. Let $H_1, \ldots, H_p$ be the syntactic-equivalence classes of $H$
-linearly ordered such that for all $i, j \in [p]$ if $i \leq j$ the height of
-the gates in $H_i$ is less than or equal to the height of the gates in $H_j$.
-Let $C'$ be the result of successively executing the algorithm for $\op{merge}$
-on each such equivalence class in order.
+% We can compute $\op{merge-all}$ using the following algorithm. Let $(C, H)$ be
+% a tuple in the domain of $\op{merge-all}$. We assume a reasonable encoding of
+% the circuit, and note that any such encoding induces a linear order on the
+% structure. Let $H_1, \ldots, H_p$ be the syntactic-equivalence classes of $H$
+% linearly ordered such that for all $i, j \in [p]$ if $i \leq j$ the height of
+% the gates in $H_i$ is less than or equal to the height of the gates in $H_j$.
+% Let $C'$ be the result of successively executing the algorithm for
+% $\op{merge}$ on each such equivalence class in order.
 
-It is worth noting that for an input tuple $(C, H)$, if follows from
-Lemma~\cite{lem:unique-labels-syntactic-equiv} that if $H$ has unique labels
-then the syntactic-equivalence relation on $H$ can be computed in time
-polynomial in the size of $C$. Thus, if each gate in $H$ has unique labels, it
-can be shown that $\op{merge-all}$ can be computed in time polynomial in the
-size of the input circuit.
+% It is worth noting that for an input tuple $(C, H)$, if follows from
+% Lemma~\cite{lem:unique-labels-syntactic-equiv} that if $H$ has unique labels
+% then the syntactic-equivalence relation on $H$ can be computed in time
+% polynomial in the size of $C$. Thus, if each gate in $H$ has unique labels, it
+% can be shown that $\op{merge-all}$ can be computed in time polynomial in the
+% size of the input circuit.
 
-As in the case of $\op{merge}$, the function $\op{merge-all}$ preserves
-symmetry, unique labels and the ensures that the input and output circuits
-compute the same function. Let be a circuit $C$ a circuit and $H$ a set of gates
-in $C$ with unique labels. Then if $g$ is a gate in both $C$ and $C' :=
-\op{merge-all}(C, H)$, and all of the children of $g$ in $C$ are in $H$, then no
-two distinct children of $g$ in $C'$ are syntactically-equivalent. However, we
-have no guarantee that $g$ will have unique labels in $C'$ as we have no
-guarantee that $L'(g)$ is injective.
+% As in the case of $\op{merge}$, the function $\op{merge-all}$ preserves
+% symmetry, unique labels and the ensures that the input and output circuits
+% compute the same function. Let be a circuit $C$ a circuit and $H$ a set of
+% gates in $C$ with unique labels. Then if $g$ is a gate in both $C$ and $C' :=
+% \op{merge-all}(C, H)$, and all of the children of $g$ in $C$ are in $H$, then
+% no two distinct children of $g$ in $C'$ are syntactically-equivalent. However,
+% we have no guarantee that $g$ will have unique labels in $C'$ as we have no
+% guarantee that $L'(g)$ is injective.
 
-The now define the function $\op{make-injective}$ that maps a circuit and a
-symmetric gate to an equivalent circuit containing all the same gates as the
-input circuit but such that the specified gate now has injective labels.
+% The now define the function $\op{make-injective}$ that maps a circuit and a
+% symmetric gate to an equivalent circuit containing all the same gates as the
+% input circuit but such that the specified gate now has injective labels.
 
-\begin{definition}
-  \label{def:make-injective}
-  The function $\op{make-injective}$ maps a circuit $C := \langle G, \Omega,
-  \Sigma , \Lambda, L \rangle$ and a gate $h \in G$ to the circuit
-  $\op{make-injective}(C, h) := C' := \langle G', \Omega', \Sigma', \Lambda', L'
-  \rangle$, defined as follows. Let $c = \max \{\vert L(g)^{-1}(h)\vert : g \in
-  W(h, \cdot)\}$. If $c = 1$ then $C' := C$. If $c > 1$ then $C'$ is defined
-  such that
-  \begin{itemizens}
-  \item $G' = G \uplus \{h_2, \ldots, h_{c-1}\}$,
-  \item $\Omega' = \Omega$,
-  \item For each $g \in G$ let $\Sigma' (g) = \Sigma(g)$, otherwise let
-    $\Sigma'(g)$ be a single-input $\AND$-gate.
-  \item $\Lambda'= \Lambda$
-  \item For each $g \in G'$ if $g \in G \setminus W(h, \cdot)$ then $L'(g) =
-    L(g)$. If $g \in W(h, \cdot)$ let $\{x_1, \ldots, x_k\} := L(g)^{-1}(h)$ and
-    for each $x \in \ind(g)$ if $L(g)(x) \neq h$ then $L'(g)(x) = L(g)(x)$ else
-    if $x = x_i \in L(g)^{-1}(h)$ then let $L'(g)(x) = h_i$.
-  \end{itemizens}
-\end{definition}
+% \begin{definition}
+%   \label{def:make-injective}
+%   The function $\op{make-injective}$ maps a circuit $C := \langle G, \Omega,
+%   \Sigma , \Lambda, L \rangle$ and a gate $h \in G$ to the circuit
+%   $\op{make-injective}(C, h) := C' := \langle G', \Omega', \Sigma', \Lambda',
+%   L' \rangle$, defined as follows. Let $c = \max \{\vert L(g)^{-1}(h)\vert : g
+%   \in W(h, \cdot)\}$. If $c = 1$ then $C' := C$. If $c > 1$ then $C'$ is
+%   defined such that
+%   \begin{itemizens}
+%   \item $G' = G \uplus \{h_2, \ldots, h_{c-1}\}$,
+%   \item $\Omega' = \Omega$,
+%   \item For each $g \in G$ let $\Sigma' (g) = \Sigma(g)$, otherwise let
+%     $\Sigma'(g)$ be a single-input $\AND$-gate.
+%   \item $\Lambda'= \Lambda$
+%   \item For each $g \in G'$ if $g \in G \setminus W(h, \cdot)$ then $L'(g) =
+%     L(g)$. If $g \in W(h, \cdot)$ let $\{x_1, \ldots, x_k\} := L(g)^{-1}(h)$
+%     and for each $x \in \ind(g)$ if $L(g)(x) \neq h$ then $L'(g)(x) = L(g)(x)$
+%     else if $x = x_i \in L(g)^{-1}(h)$ then let $L'(g)(x) = h_i$.
+%   \end{itemizens}
+% \end{definition}
 
-It can be shown that $\op{make-injective}$ can be computed by an algorithm
-running in time polynomial in the size of the input circuit. Moreover, the input
-and output circuits of this operation compute the same function.
+% It can be shown that $\op{make-injective}$ can be computed by an algorithm
+% running in time polynomial in the size of the input circuit. Moreover, the
+% input and output circuits of this operation compute the same function.
 
-We now define the function $\op{make-injective-all}$ that maps a circuit to an
-equivalent circuit such that every symmetric gate now has injective labels.
+% We now define the function $\op{make-injective-all}$ that maps a circuit to an
+% equivalent circuit such that every symmetric gate now has injective labels.
 
-\begin{definition}
-  The function $\op{make-injective-all}$ maps a circuit $C := \langle G, \Omega,
-  \Sigma , \Lambda, L \rangle$ to a circuit $\op{make-injective}(C) := C' :=
-  \langle G', \Omega', \Sigma', \Lambda', L' \rangle$ defined as follows.
+% \begin{definition}
+%   The function $\op{make-injective-all}$ maps a circuit $C := \langle G,
+%   \Omega, \Sigma , \Lambda, L \rangle$ to a circuit $\op{make-injective}(C) :=
+%   C' := \langle G', \Omega', \Sigma', \Lambda', L' \rangle$ defined as
+%   follows.
 
-  Let $F$ be a function that maps an ordered circuit $C*$ to the circuit
-  $\op{make-injective}(C*, h)$, where $h$ is the topologically first gate such
-  that there exists a gate $g$ in $C*$ where $h$ is a child of $g$ and $\vert
-  L*(g)^{-1}(h) \vert > 1$. Let $(C^0, C^1, \ldots)$ be a sequence of circuits
-  where $C^0 := C$ and for $i > 1$, $C^i := F(C^{i-1})$. It can be shown that
-  this sequence converges after at most $\vert C \vert$ many steps. Let $C'$ be
-  the limit of this sequence.
-\end{definition}
+%   Let $F$ be a function that maps an ordered circuit $C*$ to the circuit
+%   $\op{make-injective}(C*, h)$, where $h$ is the topologically first gate such
+%   that there exists a gate $g$ in $C*$ where $h$ is a child of $g$ and $\vert
+%   L*(g)^{-1}(h) \vert > 1$. Let $(C^0, C^1, \ldots)$ be a sequence of circuits
+%   where $C^0 := C$ and for $i > 1$, $C^i := F(C^{i-1})$. It can be shown that
+%   this sequence converges after at most $\vert C \vert$ many steps. Let $C'$
+%   be the limit of this sequence.
+% \end{definition}
 
-Since $\op{make-injective}$ can be computed in polynomial time, and the number
-of iterations required to converge to the limit in the above definition is
-bounded by the size of the circuit, it can be shown that
-$\op{make-injective-all}$ can be computed in time polynomial in the size of the
-input circuit. Furthermore, we note that $\op{make-injective-all}$ preserves
-symmetry, rigidity and unique labels. Moreover, the input and output circuits
-compute the same function.
+% Since $\op{make-injective}$ can be computed in polynomial time, and the number
+% of iterations required to converge to the limit in the above definition is
+% bounded by the size of the circuit, it can be shown that
+% $\op{make-injective-all}$ can be computed in time polynomial in the size of
+% the input circuit. Furthermore, we note that $\op{make-injective-all}$
+% preserves symmetry, rigidity and unique labels. Moreover, the input and output
+% circuits compute the same function.
 
-We now define the function $\op{insert}$ that maps two circuits to a circuit
-formed by inserting the gates of the first circuit into the second circuit.
+% We now define the function $\op{insert}$ that maps two circuits to a circuit
+% formed by inserting the gates of the first circuit into the second circuit.
 
-\begin{definition}
-  The function $\op{insert}$ maps a $(\mathbb{B}_1, \tau_1)$-circuit $C^1 :=
-  \langle G_1, \Omega_1, \Sigma_1 , \Lambda_1, L_1 \rangle$ and a
-  $(\mathbb{B}_2, \tau_2)$-circuit $C^2 := \langle G_2, \Omega_2, \Sigma_2 ,
-  \Lambda_2, L_2 \rangle$ to a $(\mathbb{B}_1 \cup \mathbb{B}_2, \tau_1 \uplus
-  \tau_2)$-circuit $\op{insert}(C^1, C^2) := C := \langle G, \Omega, \Sigma ,
-  \Lambda, L \rangle$, where
-  \begin{itemize}
-    \setlength\itemsep{0mm}
-  \item $G = G_1 \uplus G_2$,
-  \item $\Omega = \Omega_2$,
-  \item $\Sigma = \Sigma_1 \uplus \Sigma_2$,
-  \item $\Lambda = \Lambda_1 \uplus \Lambda_2$, and
-  \item $L = L_1 \uplus L_2$.
-  \end{itemize}
-\end{definition}
+% \begin{definition}
+%   The function $\op{insert}$ maps a $(\mathbb{B}_1, \tau_1)$-circuit $C^1 :=
+%   \langle G_1, \Omega_1, \Sigma_1 , \Lambda_1, L_1 \rangle$ and a
+%   $(\mathbb{B}_2, \tau_2)$-circuit $C^2 := \langle G_2, \Omega_2, \Sigma_2 ,
+%   \Lambda_2, L_2 \rangle$ to a $(\mathbb{B}_1 \cup \mathbb{B}_2, \tau_1 \uplus
+%   \tau_2)$-circuit $\op{insert}(C^1, C^2) := C := \langle G, \Omega, \Sigma ,
+%   \Lambda, L \rangle$, where
+%   \begin{itemize}
+%     \setlength\itemsep{0mm}
+%   \item $G = G_1 \uplus G_2$,
+%   \item $\Omega = \Omega_2$,
+%   \item $\Sigma = \Sigma_1 \uplus \Sigma_2$,
+%   \item $\Lambda = \Lambda_1 \uplus \Lambda_2$, and
+%   \item $L = L_1 \uplus L_2$.
+%   \end{itemize}
+% \end{definition}
 
-It can be shown that $\op{insert}$ can be be computed in time polynomial in the
-size of the input circuits. Moreover, if the input circuits are symmetric then
-the output circuit is symmetric.
+% It can be shown that $\op{insert}$ can be be computed in time polynomial in
+% the size of the input circuits. Moreover, if the input circuits are symmetric
+% then the output circuit is symmetric.
 
-We now define the function $\op{replace}$ that maps a circuit $C$ and a pair of
-gates $(g_1, g_2)$ in $C$ to a circuit $C'$ formed by replacing $g_1$ with $g_2$
-in $C$.
+% We now define the function $\op{replace}$ that maps a circuit $C$ and a pair
+% of gates $(g_1, g_2)$ in $C$ to a circuit $C'$ formed by replacing $g_1$ with
+% $g_2$ in $C$.
 
-\begin{definition}
-  The function $\op{replace}$ maps a circuit $C = \langle G, \Omega, \Sigma,
-  \Lambda, L\rangle$ and a pair of gates $(g_1, g_2)$ in $C$ to a circuit
-  $\op{replace}(C, g_1, g_2) := C' := \langle G', \Omega', \Sigma', \Lambda', L'
-  \rangle$, where
-  \begin{itemize}
-    \setlength\itemsep{0mm}
-  \item $G' = G \setminus \{g_1\}$,
-  \item $\Omega'$ is an function from the domain of $\Omega$ to $G'$ such that
-    for each $\vec{a} \in \dom(\Omega)$ if $\Omega(\vec{a}) = g_1$ then
-    $\Omega'(\vec{a}) = g_2$ and otherwise $\Omega'(\vec{a}) = \Omega(\vec{a})$.
-  \item $\Sigma' = \restr{\Sigma}{G'}$
-  \item $\Lambda' = \restr{\Lambda}{G'}$
-  \item For each $g \in G'$ and each $x \in \ind(g)$ if $L(g)(x) = g_1$ then
-    $L'(g)(x) = g_2$ and if not then $L'(g)(x) = L(g)(x)$.
-  \end{itemize}
-\end{definition}
+% \begin{definition}
+%   The function $\op{replace}$ maps a circuit $C = \langle G, \Omega, \Sigma,
+%   \Lambda, L\rangle$ and a pair of gates $(g_1, g_2)$ in $C$ to a circuit
+%   $\op{replace}(C, g_1, g_2) := C' := \langle G', \Omega', \Sigma', \Lambda',
+%   L' \rangle$, where
+%   \begin{itemize}
+%     \setlength\itemsep{0mm}
+%   \item $G' = G \setminus \{g_1\}$,
+%   \item $\Omega'$ is an function from the domain of $\Omega$ to $G'$ such that
+%     for each $\vec{a} \in \dom(\Omega)$ if $\Omega(\vec{a}) = g_1$ then
+%     $\Omega'(\vec{a}) = g_2$ and otherwise $\Omega'(\vec{a}) =
+%     \Omega(\vec{a})$.
+%   \item $\Sigma' = \restr{\Sigma}{G'}$
+%   \item $\Lambda' = \restr{\Lambda}{G'}$
+%   \item For each $g \in G'$ and each $x \in \ind(g)$ if $L(g)(x) = g_1$ then
+%     $L'(g)(x) = g_2$ and if not then $L'(g)(x) = L(g)(x)$.
+%   \end{itemize}
+% \end{definition}
 
-It can be shown that the function $\op{replace}$ can be computed in time
-polynomial in the size of the input circuit.
+% It can be shown that the function $\op{replace}$ can be computed in time
+% polynomial in the size of the input circuit.
 
-We now define the function $\op{tag}$ that maps a circuit, a relation symbol, a
-gate in that circuit, and a tuple to a circuit computing the same function as
-the input circuit but with an additional gadget, constructed using the gates
-labelled by the given relation symbol and tuple, marking the designated gate.
-The intuition is that this marking helps to distinguish a gate, and is used as a
-step to ensure that a circuit has unique labels.
+% We now define the function $\op{tag}$ that maps a circuit, a relation symbol,
+% a gate in that circuit, and a tuple to a circuit computing the same function
+% as the input circuit but with an additional gadget, constructed using the
+% gates labelled by the given relation symbol and tuple, marking the designated
+% gate. The intuition is that this marking helps to distinguish a gate, and is
+% used as a step to ensure that a circuit has unique labels.
 
-\begin{definition}
-  The function $\op{tag}$ maps a $(\mathbb{B}, \tau)$-circuit $C := \langle G,
-  \Omega, \Sigma, \Lambda, L \rangle$ of order $n$, a relation symbol $R \in
-  \tau$, a gate $g \in G$, and a tuple $\vec{a} \in [n]^k$ for some $k$ to a
-  circuit $\op{tag}(C, R, g, \vec{a}) := C' := \langle G', \Omega', \Sigma',
-  \Lambda', L'\rangle$ of order $n$, such that $G' = G \uplus \{\land_g,
-  \land_{g'}, \land_1, \ldots , \land_k\}$, $\Omega' = \Omega$, and $\Lambda' =
-  \Lambda$. For each $g \in G$ $\Sigma'(g) = \Sigma(g)$. For each $g \in
-  \{\land_0, \land_1, \ldots , \land_k \}$, $\Sigma(g)$ is an $\AND$-gate that
-  takes in two inputs. $\Sigma(\land_g)$ is an $\AND$-gate that takes in a
-  single input, $g$ is the lone input to $\land_g$, and $\land_0$ has as input
-  $\land_g$ and $\land_1$. For each $i \in [k-1]$ the inputs of $\land_i$ are
-  $\land_{i+1}$ and the gate $g_i \in G'$ such that $\Sigma(g_i) = R$ and
-  $\Lambda^{-1}(g_i) = \vec{a}_i$, where $\vec{a}_i$ is the $k$-tuple
-  $(\vec{a}(i), \ldots, \vec{a}(i))$. The inputs of $\land_k$ are the constant
-  gate $1$ and the gate $g_k$ such that $\Sigma(g) = R$ and $\Lambda^{-1}(g_k) =
-  \vec{a}_k$. For each gate $h \in G \setminus \{g\}$ and $x \in \ind(h)$, if
-  $L(h)(x) = g$ then $L'(h)(x) = \land_0$, otherwise $L'(h)(x) = L(h)(x)$.
-\end{definition}
+% \begin{definition}
+%   The function $\op{tag}$ maps a $(\mathbb{B}, \tau)$-circuit $C := \langle G,
+%   \Omega, \Sigma, \Lambda, L \rangle$ of order $n$, a relation symbol $R \in
+%   \tau$, a gate $g \in G$, and a tuple $\vec{a} \in [n]^k$ for some $k$ to a
+%   circuit $\op{tag}(C, R, g, \vec{a}) := C' := \langle G', \Omega', \Sigma',
+%   \Lambda', L'\rangle$ of order $n$, such that $G' = G \uplus \{\land_g,
+%   \land_{g'}, \land_1, \ldots , \land_k\}$, $\Omega' = \Omega$, and $\Lambda'
+%   = \Lambda$. For each $g \in G$ $\Sigma'(g) = \Sigma(g)$. For each $g \in
+%   \{\land_0, \land_1, \ldots , \land_k \}$, $\Sigma(g)$ is an $\AND$-gate that
+%   takes in two inputs. $\Sigma(\land_g)$ is an $\AND$-gate that takes in a
+%   single input, $g$ is the lone input to $\land_g$, and $\land_0$ has as input
+%   $\land_g$ and $\land_1$. For each $i \in [k-1]$ the inputs of $\land_i$ are
+%   $\land_{i+1}$ and the gate $g_i \in G'$ such that $\Sigma(g_i) = R$ and
+%   $\Lambda^{-1}(g_i) = \vec{a}_i$, where $\vec{a}_i$ is the $k$-tuple
+%   $(\vec{a}(i), \ldots, \vec{a}(i))$. The inputs of $\land_k$ are the constant
+%   gate $1$ and the gate $g_k$ such that $\Sigma(g) = R$ and $\Lambda^{-1}(g_k)
+%   = \vec{a}_k$. For each gate $h \in G \setminus \{g\}$ and $x \in \ind(h)$,
+%   if $L(h)(x) = g$ then $L'(h)(x) = \land_0$, otherwise $L'(h)(x) = L(h)(x)$.
+% \end{definition}
 
-It can be shown that $\op{tag}$ can be computed in time polynomial in the size
-of its input. The input and output circuits compute the same function. Moreover,
-if the input circuit has unique labels then the output circuit will have unique
-labels. If the input relation symbol is obvious from the context we omit it when
-invoking $\op{tag}$.
+% It can be shown that $\op{tag}$ can be computed in time polynomial in the size
+% of its input. The input and output circuits compute the same function.
+% Moreover, if the input circuit has unique labels then the output circuit will
+% have unique labels. If the input relation symbol is obvious from the context
+% we omit it when invoking $\op{tag}$.
 
-\begin{definition}
-  The function $\op{tag-all}$ maps a $(\mathbb{B}, \tau)$-circuit $C := \langle
-  G, \Omega, \Sigma, \Lambda, L \rangle$ of order $n$, a relation symbol $R \in
-  \tau$, a set of gates $H \subseteq G$, and $T := (\vec{a}_h)_{h \in H}
-  \subseteq [n]^{k}$ a sequence of tuples indexed by $H$ for some fixed $k$, to
-  a circuit $\op{tag-all}(C, R, H, T) := C' := \langle G', \Omega', \Sigma',
-  \Lambda', L'\rangle$ of order $n$ defined as follows.
+% \begin{definition}
+%   The function $\op{tag-all}$ maps a $(\mathbb{B}, \tau)$-circuit $C :=
+%   \langle G, \Omega, \Sigma, \Lambda, L \rangle$ of order $n$, a relation
+%   symbol $R \in \tau$, a set of gates $H \subseteq G$, and $T :=
+%   (\vec{a}_h)_{h \in H} \subseteq [n]^{k}$ a sequence of tuples indexed by $H$
+%   for some fixed $k$, to a circuit $\op{tag-all}(C, R, H, T) := C' := \langle
+%   G', \Omega', \Sigma', \Lambda', L'\rangle$ of order $n$ defined as follows.
 
-  Suppose there is a linear order on $H$, and write $H = \{h_1, \ldots, h_t\}$.
-  Let $C_0 := C$ and for all $i \in [t]$ let $C_i := \op{tag}(C_{i-1}, R, h_i,
-  T(h_i))$. Then $C' = C_{t}$.
-\end{definition}
+%   Suppose there is a linear order on $H$, and write $H = \{h_1, \ldots,
+%   h_t\}$. Let $C_0 := C$ and for all $i \in [t]$ let $C_i := \op{tag}(C_{i-1},
+%   R, h_i, T(h_i))$. Then $C' = C_{t}$.
+% \end{definition}
 
-It is easy to see that, since $\op{tag}$ can be computed in time polynomial in
-the combined size of its inputs, $\op{tag-all}$ can also be computed in time
-polynomial in the combined size of its inputs.
+% It is easy to see that, since $\op{tag}$ can be computed in time polynomial in
+% the combined size of its inputs, $\op{tag-all}$ can also be computed in time
+% polynomial in the combined size of its inputs.
 
-We now define the function $\op{compose}$ that maps a circuit and a sequence of
-circuits and to a circuit formed by replacing the input gates of the designated
-circuit with the output gates of the circuits in the sequence.
+% We now define the function $\op{compose}$ that maps a circuit and a sequence
+% of circuits and to a circuit formed by replacing the input gates of the
+% designated circuit with the output gates of the circuits in the sequence.
 
-\begin{definition}
-  The function $\op{compose}$ maps a $(\mathbb{B}, \tau)$-circuit $C := \langle
-  G, \Omega, \Sigma, \Lambda, L \rangle$, a sequence of relation sybmols $\tau_R
-  := (R_1, \ldots, R_t)$ such that $\tau_R \subseteq \tau$, a sequence of
-  circuits $\mathcal{C} := ( C^1, \ldots, C^t)$, where for each $i \in [t]$,
-  $C^i = \langle G_i, \Omega_i, \Sigma_i, \Lambda_i, L_i \rangle$ is a
-  $(\mathbb{B}_i, \tau_i)$-circuit, and $\tau_i \not\subset \tau_R$ and $C^i$
-  computes a query of arity $\arty(R_i)$ to a circuit $\op{compose}(C,
-  \mathcal{C}, \tau_R) := C' := \langle G', \Omega', \Sigma', \Lambda', L'
-  \rangle$. Note that all circuits take in structures of size $n$. The circuit
-  $C'$ is defined as follows.
+% \begin{definition}
+%   The function $\op{compose}$ maps a $(\mathbb{B}, \tau)$-circuit $C :=
+%   \langle G, \Omega, \Sigma, \Lambda, L \rangle$, a sequence of relation
+%   sybmols $\tau_R := (R_1, \ldots, R_t)$ such that $\tau_R \subseteq \tau$, a
+%   sequence of circuits $\mathcal{C} := ( C^1, \ldots, C^t)$, where for each $i
+%   \in [t]$, $C^i = \langle G_i, \Omega_i, \Sigma_i, \Lambda_i, L_i \rangle$ is
+%   a $(\mathbb{B}_i, \tau_i)$-circuit, and $\tau_i \not\subset \tau_R$ and
+%   $C^i$ computes a query of arity $\arty(R_i)$ to a circuit $\op{compose}(C,
+%   \mathcal{C}, \tau_R) := C' := \langle G', \Omega', \Sigma', \Lambda', L'
+%   \rangle$. Note that all circuits take in structures of size $n$. The circuit
+%   $C'$ is defined as follows.
 
-  Let ${C^0}' := \langle G_0', \Omega_0', \Sigma_0', \Lambda_0', L_0' \rangle :=
-  C$, and let $i \in [t]$. Let $D^{i-1}:= \op{insert} (C^i, {C^{i-1}}')$ and
-  $G^{i-1}_{R_i}$ be the set of all relational gates in $D^{i-1}$ labelled by
-  the relational symbol in $R_i$. Let ${C^{i-1}}' := \langle G_i', \Omega_i',
-  \Sigma_i', \Lambda_i', L_i' \rangle$ be the circuit formed from $D^{i-1}$ by
-  replacing each gate in $g \in G^{i-1}_{R_i}$ with the gate
-  $\Omega_{i}(\Lambda_{i-1}'(g))$ in $D^{i-1}$ (by repeated calls to the
-  $\op{replace}$ function). Let $C' = {C^{t}}'$.
-\end{definition}
+%   Let ${C^0}' := \langle G_0', \Omega_0', \Sigma_0', \Lambda_0', L_0' \rangle
+%   := C$, and let $i \in [t]$. Let $D^{i-1}:= \op{insert} (C^i, {C^{i-1}}')$
+%   and $G^{i-1}_{R_i}$ be the set of all relational gates in $D^{i-1}$ labelled
+%   by the relational symbol in $R_i$. Let ${C^{i-1}}' := \langle G_i',
+%   \Omega_i', \Sigma_i', \Lambda_i', L_i' \rangle$ be the circuit formed from
+%   $D^{i-1}$ by replacing each gate in $g \in G^{i-1}_{R_i}$ with the gate
+%   $\Omega_{i}(\Lambda_{i-1}'(g))$ in $D^{i-1}$ (by repeated calls to the
+%   $\op{replace}$ function). Let $C' = {C^{t}}'$.
+% \end{definition}
 
-It can be shown that $\op{compose}$ can be computed in time polynomial in the
-sum of the sizes of the input circuits. We also note that the size of $C'$ is
-less than or equal to the sum of the sizes of the input circuits. Moreover, if
-the input circuits are all symmetric then the output circuit will be symmetric.
-Also, for an input tuple $(C, \mathcal{C}, \tau_R)$, we have that if $C$ has
-symmetric gates and transparent, and all the circuits in $\mathcal{C}$ are
-transparent, then $C' := \op{compose}(C, \mathcal{C}, \tau_R)$ is transparent.
-If $C$ contains a non-symmetric gates then, as the output gates of the circuits
-in $\mathcal{C}$ are no longer labelled as output gates in $C'$, it may be that
-some of these gates are syntactically-equivalent in $C'$, resulting in $C'$ not
-being transparent.
+% It can be shown that $\op{compose}$ can be computed in time polynomial in the
+% sum of the sizes of the input circuits. We also note that the size of $C'$ is
+% less than or equal to the sum of the sizes of the input circuits. Moreover, if
+% the input circuits are all symmetric then the output circuit will be
+% symmetric. Also, for an input tuple $(C, \mathcal{C}, \tau_R)$, we have that
+% if $C$ has symmetric gates and transparent, and all the circuits in
+% $\mathcal{C}$ are transparent, then $C' := \op{compose}(C, \mathcal{C},
+% \tau_R)$ is transparent. If $C$ contains a non-symmetric gates then, as the
+% output gates of the circuits in $\mathcal{C}$ are no longer labelled as output
+% gates in $C'$, it may be that some of these gates are syntactically-equivalent
+% in $C'$, resulting in $C'$ not being transparent.
 
-In certain contexts we are interested composing gates such that if the input
-circuits are transparent (resp. have unique labels) then the output circuits
-will be transparent (resp. have unique labels). In this case, while composing
-the circuits we apply the $\op{tag}$ function to the output gates of the
-circuits in the input sequence of circuits. We now define the function
-$\op{compose-and-tag}$ that implements this operation.
+% In certain contexts we are interested composing gates such that if the input
+% circuits are transparent (resp. have unique labels) then the output circuits
+% will be transparent (resp. have unique labels). In this case, while composing
+% the circuits we apply the $\op{tag}$ function to the output gates of the
+% circuits in the input sequence of circuits. We now define the function
+% $\op{compose-and-tag}$ that implements this operation.
 
-\begin{definition}
-  The function $\op{compose-and-tag}$ maps a $(\mathbb{B}, \tau)$-circuit $C :=
-  \langle G, \Omega, \Sigma, \Lambda, L \rangle$, a sequence of relation symbols
-  $\tau_R := (R_1, \ldots, R_t)$ such that $\tau_R \subseteq \tau$, a sequence
-  of circuits $\mathcal{C} := ( C^1, \ldots, C^t)$, where for each $i \in [t]$,
-  $C^i = \langle G_i, \Omega_i, \Sigma_i, \Lambda_i, L_i \rangle$ is a
-  $(\mathbb{B}_i, \tau_i)$-circuit, and $\tau_i \not\subset \tau_R$ and $C^i$
-  computes a query of arity $\arty(R_i)$ to a circuit $\op{compose-and-tag}(C,
-  \mathcal{C}, \tau_R, R) := C'$. The circuit $C'$ is defined as follows. Note
-  that all circuits take in structures of size $n$.
+% \begin{definition}
+%   The function $\op{compose-and-tag}$ maps a $(\mathbb{B}, \tau)$-circuit $C
+%   := \langle G, \Omega, \Sigma, \Lambda, L \rangle$, a sequence of relation
+%   symbols $\tau_R := (R_1, \ldots, R_t)$ such that $\tau_R \subseteq \tau$, a
+%   sequence of circuits $\mathcal{C} := ( C^1, \ldots, C^t)$, where for each $i
+%   \in [t]$, $C^i = \langle G_i, \Omega_i, \Sigma_i, \Lambda_i, L_i \rangle$ is
+%   a $(\mathbb{B}_i, \tau_i)$-circuit, and $\tau_i \not\subset \tau_R$ and
+%   $C^i$ computes a query of arity $\arty(R_i)$ to a circuit
+%   $\op{compose-and-tag}(C, \mathcal{C}, \tau_R, R) := C'$. The circuit $C'$ is
+%   defined as follows. Note that all circuits take in structures of size $n$.
 
-  Let $D^0 := \op{compose}(C, \mathcal{C}, \tau_R)$. For each $i \in [t]$, let
-  $D^{i} := \op{tag-all}(D^{i-1}, R, \img(\Omega^{-1}_i), \Omega^{-1}_i)$. Let
-  $C' := D^t$.
-\end{definition}
+%   Let $D^0 := \op{compose}(C, \mathcal{C}, \tau_R)$. For each $i \in [t]$, let
+%   $D^{i} := \op{tag-all}(D^{i-1}, R, \img(\Omega^{-1}_i), \Omega^{-1}_i)$. Let
+%   $C' := D^t$.
+% \end{definition}
 
-It is easy to see that $\op{compose-and-tag}$ can be computed in time polynomial
-in the sun of the sizes of the input circuits. We also have that if the input
-circuits are symmetric then the output circuits are symmetric. Furthermore, if
-the input sequences of circuits and relations are both singletons, then if the
-input circuits are all transparent (resp. have unique labels) then the output
-circuit is transparent (resp. have unique labels). We also note that the output
-circuit
+% It is easy to see that $\op{compose-and-tag}$ can be computed in time
+% polynomial in the sun of the sizes of the input circuits. We also have that if
+% the input circuits are symmetric then the output circuits are symmetric.
+% Furthermore, if the input sequences of circuits and relations are both
+% singletons, then if the input circuits are all transparent (resp. have unique
+% labels) then the output circuit is transparent (resp. have unique labels). We
+% also note that the output circuit
 
-\begin{definition}
-  The function $\op{tag-inputs}$ maps a circuit $C := \langle G, \Omega, \Sigma,
-  \Lambda, L \rangle$, a relation symbol $R \in \tau$, and $H \subseteq G$
-\end{definition}
-
-\subsection{Translating FPR to Symmetric Matrix Circuits}
+% \subsection{Translating FPR to Symmetric Matrix Circuits}
 % In this subsection we translate $\FPR$-formulas into families of transparent
@@
 
-We say that a circuit $C$ \emph{translates} a formula $\psi(\vec{x})$ for $n \in
-\nats$ if $C$ is a transparent symmetric rank-circuit of order $n$, $C$ is
-defined over the same vocabulary as $\psi$, and $C$ computes the query defined
-by $\psi(\vec{x})$ on structures of size $n$. We say a family of circuits
-$(C_n)_{n \in \nats}$ \emph{translates} a formula $\psi (\vec{x})$ if $(C_n)_{n
-  \in \nats}$ is $\PT$-uniform and for all $n \in \nats$, $C_n$ translates
-$\psi(\vec{x})$ for $n$.
+In this section we construct for every formula of $\FPR$ an equivalent
+$\PT$-uniform family of transparent symmetric rank-circuits. We say that a
+circuit $C$ \emph{translates} a formula $\psi(\vec{x})$ for $n \in \nats$ if $C$
+is a transparent symmetric rank-circuit of order $n$, $C$ is defined over the
+same vocabulary as $\psi$, and $C$ computes the query defined by $\psi(\vec{x})$
+on structures of size $n$. We say a family of circuits $(C_n)_{n \in \nats}$
+\emph{translates} a formula $\psi (\vec{x})$ if $(C_n)_{n \in \nats}$ is
+$\PT$-uniform and for all $n \in \nats$, $C_n$ translates $\psi(\vec{x})$ for
+$n$.
 
-We now prove that for every $\FOrk$-formula $\theta(\vec{x})$ and $n \in \nats$
-there exists a circuit $C$ that translates $\theta(\vec{x})$ for $n$. We
-construct $C$ by including for each sub-formula $\psi \in \cl{\theta}$ and
-assignment $\alpha \in [n]^{\free{\psi}}$ a gate $g_{\psi[\alpha]}$. The
-children of $g_{\psi[\alpha]}$ are the gates of the form $g_{\phi[\beta]}$,
-where $\phi$ is an immediate sub-formula of $\psi$ and $\beta$ is an assignment
-to the free variables of $\psi$ that is compatible with the assignment $\alpha$.
-The gate $g_{\psi[\alpha]}$ for an input structure over the universe $[n]$
-evaluates to one if, and only if, $\psi$ holds for the input structure with the
-assignment $\alpha$. We now construct the translation of $\theta$ for $n$, and
-prove that the construction can be completed in a time bound that depends on $n$
-and certain properties of the formula $\theta$.
+We first show that for every $\FOrk$-formula $\theta(\vec{x})$ and $n \in \nats$
+there exists a circuit $C$ that translates $\theta(\vec{x})$ for $n$. The
+circuit $C$ contains a gate for each sub-formula $\psi$ of $\theta$ and each
+compatible assignment $\alpha$ to the free variables of $\psi$. We call this
+gate $g_{\psi[\alpha]}$. We label $g_{\psi[\alpha]}$ with an element of the
+basis appropriate to the operator at the head of the formula $\psi$ and wire up
+the circuit such that the children of $g_{\psi[\alpha]}$ are all those gates of
+the form $g_{\phi[\beta]}$, where $\phi$ is an immediate sub-formula of $\psi$
+and $\beta$ is an assignment to the free variables of $\psi$ compatible with the
+assignment $\alpha$. We show that for a given input structure $\mathcal{A}$ over
+the universe $[n]$, $g_{\psi[\alpha]}$ evaluates to one if, and only if,
+$\mathcal{A} \models \psi[\alpha]$.
+
+We now construct the circuit $C$ for $\theta(\vec{x})$ and $n$ and prove that
+the construction can be completed within a time bound that depends on $n$, the
+width of $\theta$ and number of sub-formulas of $\theta$.
 
 \begin{lem}
-  There is an algorithm that takes in a $\FOrk$-formula $\theta(\vec{x})$ and $n
-  \in \nats$ and outputs a rank-circuit $C$ that translates $\theta(\vec{x})$
-  for $n$. Moreover, there is a polynomial in $p$ such that for an input
-  $(\theta(\vec{x}), n)$ the algorithm terminates in at most
-  $p(n^{\width(\theta)}\vert \cl{\theta} \vert)$ many steps.
+  There is a function that takes as input a $\FOrk$-formula $\theta(\vec{x})$
+  and $n \in \nats$ and outputs a circuit $C$ that translates $\theta(\vec{x})$
+  for $n$. Moreover, this function is computable and there is a polynomial in
+  $p$ such that for an input $(\theta(\vec{x}), n)$ the algorithm computing this
+  function terminates in at most $p(n^{\width(\theta)}\vert \cl{\theta} \vert)$
+  many steps.
   \label{lem:translating-FOrk}
@@
   Let $\tau$ be the vocabulary of $\theta(\vec{x})$. Let $k := \width(\theta)$.
-  Suppose $\tau$ is empty. Since the vocabulary of $\tau$ is empty, all of the
-  atomic formula in $\theta(\vec{x})$ are of the form $y_1 = y_2$, where $y_1$
-  and $y_2$ are variables. It can be shown that, for an assignment $\vec{a}$ to
-  $\vec{x}$, we can evaluate $[n] \models \theta[\vec{a}]$ in time polynomial in
-  $n^{k} \vert \cl{\theta} \vert$. Let $f : [n]^k \rightarrow \{0,1\}$ be
-  defined such that $f (\vec{a}) = 1$ if, and only if, $[n] \models
-  \theta[\vec{a}]$. Let $C := \langle G, \Sigma, \Omega, \Lambda, L \rangle$,
-  where
+  Suppose $\tau$ is empty. Since $\tau$, the vocabulary of $\theta$, is empty,
+  all of the atomic formulas in $\theta(\vec{x})$ are of the form $y_1 = y_2$,
+  where $y_1$ and $y_2$ are variables. It can be shown that for $\vec{a} \in
+  n^k$, we can evaluate $[n] \models \theta[\alpha^{\vec{x}}_{\vec{a}}]$ in time
+  polynomial in $n^{k} \vert \cl{\theta} \vert$. Let $f : [n]^k \rightarrow
+  \{0,1\}$ be defined such that $f (\vec{a}) = 1$ if, and only if, $[n] \models
+  \theta[\alpha^{\vec{x}}_{\vec{a}}]$. Let $C := \langle G, \Sigma, \Omega,
+  \Lambda, L \rangle$, where
   \begin{itemizens}
@@
   \item $\Sigma (g_0) = 0$, $\Sigma (g_1) = 1$ and $\Sigma (g_{\vec{a}}) =
-    \land[1]$,
+    \land[1]$ for all $\vec{a} \in [n]^k$,
   \item $\Omega : [n]^k \rightarrow G$ is defined by $\Omega(\vec{a}) =
@@
   \Omega (\sigma \vec{a})$. It follows that $\pi_\sigma$ is an automorphism of
-  the circuit extending $\sigma$, and $C$ is symmetric. We thus have that $C$
-  translates $\theta(\vec{x})$ for $n$.
+  the circuit extending $\sigma$. We thus have that $C$ translates
+  $\theta(\vec{x})$ for $n$.
+
+  \begin{remark}
+    G: I have removed the section where I define equality between ground
+    formulas. Do you find this adds ambiguity? I have added a little bit
+    explaining what I mean by `the matrix at this point remains unchanged'. Does
+    this help?
+  \end{remark}
 
   Suppose $\tau$ is not empty. Let $R \in \tau$. We first define two helper
-  formulas. For a variable $y$ let $\op{no-op}(y) := (R(y, y) \land (\neg R(y,
+  formulas. For a variable $y$ let $\op{no-op}(y) := (R(y, y) \lor (\neg R(y,
   y)))$. For a sequence of variables $\vec{y} = (y_1, \ldots, y_m)$ let
-  $\op{tag} (\vec{y}) := \op{no-op}(y_1) \land (\op{no-op}(y_2) \land (
-  \op{no-op}(y_2) \land ( \ldots \land (\op{no-op}(y_m)) \ldots)))$. Let
-  $\lambda (\vec{x})$ be constructed from $\theta(\vec{x})$ by replacing each
-  sub-formula $\psi(\vec{y})$ of the form $\rank^r_p \vec{w} \vec{z} . \phi$
-  with the formula $\rank^r_p \vec{w}\vec{z} . ((\forall u . u = u) \land \phi)
-  \land \op{tag}(\vec{w} \cup \vec{z})$. Since the sub-formulas added are
-  tautologies, the matrix defined at this point remains unchanged, and so
-  $\lambda (\vec{x})$ and $\theta (\vec{x})$ are equivalent. The idea is that
-  $\op{tag}$ adds a tower of conjunctions of tautologies each referencing
-  exactly one variable from $\vec{w} \cup \vec{z}$, and so encoding the order of
-  the sequence of variables $\vec{w} \cup \vec{z}$ in the syntax of the formula.
-  When we define a circuit from this formula, each input to the rank gate will
-  be `tagged' with a unique assignment to $\vec{w} \cup \vec{z}$, preventing two
-  inputs from being syntactically-equivalent, and so ensuring the circuit is
+  $\op{tag} (\vec{y}) := (\op{no-op}(y_1) \land (\op{no-op}(y_2) \land (
+  \op{no-op}(y_2) \land ( \ldots \land (\op{no-op}(y_m)) \ldots))))$. Let
+  $\lambda (\vec{x})$ be a formula constructed from $\theta(\vec{x})$ by
+  replacing each sub-formula $\psi(\vec{y})$ of the form $\rank^r_p \vec{w}
+  \vec{z} . \phi$ with the formula $\rank^r_p \vec{w}\vec{z} . ((\forall u . u =
+  u) \land \phi) \land \op{tag}(\vec{w} \cup \vec{z})$. Since this process
+  involves inserting conjunctions of tautologies, the matrix defined at point
+  remains unchanged (i.e. $\phi \Leftrightarrow ((\forall u . u = u) \land \phi)
+  \land \op{tag}(\vec{w} \cup \vec{z})$ is a tautology), and so the evaluation
+  of $\psi(\vec{y})$ is unchanged by this replacement. It follows that $\lambda
+  (\vec{x})$ and $\theta (\vec{x})$ are equivalent. The intuition is that
+  $\op{tag}(\vec{w} \cup \vec{z})$ appends a tower of conjunctions of
+  tautologies, with each tautology referencing a unique variable from $\vec{w}
+  \cup \vec{z}$. When we construct the circuit, this tower of tautologies will
+  act to `tag' each input to the rank gate with a unique gadget. We then show
+  that the presence of these gadgets ensures that no two inputs to a rank gate
+  are syntactically-equivalent, and so the circuit is
   transparent.
 
-  % We also relabel the bound variables in $\lambda(\vec{x})$ such that there
+  %We also relabel the bound variables in $\lambda(\vec{x})$ such that there
   % are
@@
   % \cup \vec{z})$.
-
-  Let $\vec{y}$ be a sequence of variables. We abuse notation and write $\alpha
-  :\vec{y} \rightarrow A$ to indicate that $\alpha$ maps the variables in the
-  sequence $\vec{y}$ to elements of the set $A$.
-
-  Fix $n \in \nats$. Let $\psi \in \FOrk$ and $\alpha \in [n]^{\free {\psi}}$.
-  We let $\psi[\alpha]$ be the result of substituting each occurrence of the
-  free variable $y \in \free{\psi}$ in $\psi$ with $\alpha(y)$. If $\psi$ is of
-  the form $y_1 = y_2$. Then $\psi [\alpha] = 1$ if $\alpha(y_1) = \alpha (y_2)$
-  and $\psi[\alpha] = 0$ otherwise. We call $\psi[\alpha]$ a \emph{ground
-    formula}. For each $\psi \in \cl{\theta}$ let $G_\psi := \{g_{\phi[\alpha]}
-  : \alpha \in [n]^{\free{\psi}} \}$. Let $G := \bigcup_{\psi \in \cl{\lambda}}
-  G_{\psi}$. We define $\Sigma$, $\Lambda$ and $L$ as follows. Let $\Sigma (g_1)
-  = 1$ and $\Sigma (g_0) = 0$. Let $g := g_{\psi[\alpha]} \in G$.
+  Fix $n \in \nats$. Let $\psi \in \FOrk[\tau]$ and $\alpha \in [n]^{\free
+    {\psi}}$. We let $\psi[\alpha]$ be the result of substituting each
+  occurrence of the free variable $y \in \free{\psi}$ in $\psi$ with
+  $\alpha(y)$. If $\psi$ is of the form $y_1 = y_2$, then $\psi [\alpha] = 1$ if
+  $\alpha(y_1) = \alpha (y_2)$ and $\psi[\alpha] = 0$ otherwise. We call
+  $\psi[\alpha]$ a \emph{ground formula}. For each $\psi \in \cl{\theta}$ let
+  $G_\psi := \{g_{\phi[\alpha]} : \alpha \in [n]^{\free{\psi}} \}$. Let $G :=
+  \bigcup_{\psi \in \cl{\lambda}} G_{\psi}$. We define $\Sigma$, $\Lambda$ and
+  $L$ as follows. Let $\Sigma (g_1) = 1$ and $\Sigma (g_0) = 0$. Let $g :=
+  g_{\psi[\alpha]} \in G$.
 
@@
   \item if $\psi$ is of the form $\neg \phi$ then $\Sigma (g) = \neg$ and $L(g):
-    [1] \rightarrow G$, where $L(g)(1) = g_{\phi[\alpha]}$.
+    [1] \rightarrow G$ is defined by $L(g)(1) = g_{\phi[\alpha]}$.
   \end{itemizens}
 
-  We let $\Omega : [n]^k \rightarrow G$ be defined by $\Omega (\vec{a}) =
+  Let $\Omega : [n]^k \rightarrow G$ be defined by $\Omega (\vec{a}) =
   g_{\lambda [\alpha]}$, where $\alpha := \alpha^{\vec{x}}_{\vec{a}}$, for all
@@
 \begin{proof}
-  Let $\pi_\sigma : G \rightarrow G$ be a function that fixes constant gates for
-  such that for all non-constant gates $g_{\psi[\alpha]} \in G$, $\pi_{\sigma}
-  g_{\psi [\alpha]} = g_{\psi[\sigma \alpha]}$. It is easy to see that
-  $\pi_\sigma$ is a bijection. We now show that $\pi_{\sigma}$ is an
+  Let $\pi_\sigma : G \rightarrow G$ be a function that fixes constant gates and
+  such that if $g_{\psi[\alpha]} \in G$ is a non-constant gate then
+  $\pi_{\sigma} g_{\psi [\alpha]} = g_{\psi[\sigma \alpha]}$. It is easy to see
+  that $\pi_\sigma$ is a bijection. We now show that $\pi_{\sigma}$ is an
   automorphism of the circuit extending $\sigma$. Let $g_{\psi[\alpha]} := g \in
-  G$. Since the formula is unchanged by $\pi_\sigma$, we have $\Sigma(g) =
-  \Sigma (\pi_{\sigma} g)$. Suppose $g$ is an input gate. If $g$ is a constant
-  gate then $\pi_\sigma g = g$. If $g$ is a relational gate, then $\psi$ is of
-  the form $T(\vec{y})$ for some relation symbol $T$ and $\Lambda_T
-  (g_{\psi[\alpha]}) = \alpha \vec{y}$, and $\Lambda (\pi_{\sigma}
-  g_{\psi[\alpha]}) = \Lambda g_{\psi[\sigma \alpha]} = \sigma \alpha \vec{y} =
-  \sigma \Lambda_T (g_{\psi[\alpha]})$. Suppose $g$ is an internal gate. From
-  the construction of the circuit we have that if $g_{\phi[\beta]} \in H_g$ then
-  $\phi$ must be an immediate sub-formula of $\psi$ and so $g_{\phi[\sigma
-    \beta]}$ is a child of $g_{\psi[\sigma \alpha]} = \pi_{\sigma} g$. It
-  follows that $H_{\pi_\sigma g} = \pi_\sigma H_g$. If $g$ is a symmetric gate,
-  this is sufficient to conclude that $\pi_{\sigma} L(g)$ is
-  isomorphism-equivalent to $L(\pi_{\sigma} g)$. If $g$ not a symmetric gate
-  then it is a rank gate, and so $\psi$ is of the form $\rank^r_p \vec{w}
-  \vec{z} \phi$. Let $\vec{a} \in A$ and $\vec{b} \in B$, and note that
-  $\pi_\sigma L(g) (\vec{a}, \vec{b}) = \pi_{\sigma} g_{\phi[\beta]}$, where
-  $\beta \in [n]^{\free {\phi}}$ is compatible with $\alpha$,
-  $\alpha^{\vec{w}}_{\vec{a}}$ and $\alpha^{\vec{z}}_{\vec{b}}$. It follows that
-  $\sigma \beta$ is compatible with $\sigma \alpha$, $\sigma
-  \alpha^{\vec{w}}_{\vec{a}} = \alpha^{\vec{w}}_{\sigma \vec{a}}$ and
-  $\alpha^{\vec{z}}_{\vec{b}} = \alpha^{\vec{z}}_{\sigma \vec{b}}$. We thus have
-  that $L(\pi_{\sigma} g)(\sigma \vec{a}, \sigma \vec{b}) = g_{\phi[\sigma
-    \beta]} = \pi_{\sigma} g_{\phi[\beta]} = \pi_{\sigma} L(g)(\vec{a},
-  \vec{b})$. Suppose $g$ is an output gate, and let $\vec{a} \in [n]^k$ and
-  $\alpha := \alpha^{\vec{x}}_{\vec{a}}$. We have that $\pi_{\sigma} \Omega
-  (\vec{a}) = \pi_\sigma g_{\lambda[\alpha]} = g_{\lambda[\sigma \alpha]} =
-  \Omega (\sigma \alpha \vec{x}) = \Omega (\sigma \vec{a})$. This concludes the
-  proof of the claim.
+  G$. Since $\pi_{\sigma}$ acts on gates by permuting the associated assignment,
+  but has no effect on the associated sub-formula, we have $\Sigma(g) = \Sigma
+  (\pi_{\sigma} g)$. Suppose $g$ is an input gate. If $g$ is a constant gate
+  then $\pi_\sigma g = g$. If $g$ is a relational gate, then $\psi$ is of the
+  form $T(\vec{y})$ for some relation symbol $T$ and $\Lambda_T
+  (g_{\psi[\alpha]}) = \alpha \vec{y}$. It follows that $\Lambda_T (\pi_{\sigma}
+  g_{\psi[\alpha]}) = \Lambda_T( g_{\psi[\sigma \alpha]}) = \sigma \alpha
+  \vec{y} = \sigma \Lambda_T (g_{\psi[\alpha]})$. Suppose $g$ is an internal
+  gate. From the construction of the circuit we have that if $g_{\phi[\beta]}$
+  is a child of $g$ then $\phi$ must be an immediate sub-formula of $\psi$ and
+  so $g_{\phi[\sigma \beta]}$ is a child of $g_{\psi[\sigma \alpha]} =
+  \pi_{\sigma} g$. It follows that $H_{\pi_\sigma g} = \pi_\sigma H_g$. If $g$
+  is a symmetric gate, this is sufficient to conclude that $\pi_{\sigma} L(g)$
+  is isomorphism-equivalent to $L(\pi_{\sigma} g)$. If $g$ is not a symmetric
+  gate then it must be a rank gate, and so $\psi$ is of the form $\rank^r_p
+  \vec{w} \vec{z} \phi$. Let $A$ and $B$ be defined as in our definition of $C$,
+  and let $\vec{a} \in A$ and $\vec{b} \in B$. Note that $\pi_\sigma L(g)
+  (\vec{a}, \vec{b}) = \pi_{\sigma} g_{\phi[\beta]}$, where $\beta \in
+  [n]^{\free {\phi}}$ is compatible with $\alpha$, $\alpha^{\vec{w}}_{\vec{a}}$
+  and $\alpha^{\vec{z}}_{\vec{b}}$. It follows that $\sigma \beta$ is compatible
+  with $\sigma \alpha$, $\sigma \alpha^{\vec{w}}_{\vec{a}} =
+  \alpha^{\vec{w}}_{\sigma \vec{a}}$ and $\alpha^{\vec{z}}_{\vec{b}} =
+  \alpha^{\vec{z}}_{\sigma \vec{b}}$. We thus have that $L(\pi_{\sigma}
+  g)(\sigma \vec{a}, \sigma \vec{b}) = g_{\phi[\sigma \beta]} = \pi_{\sigma}
+  g_{\phi[\beta]} = \pi_{\sigma} L(g)(\vec{a}, \vec{b})$. Suppose $g$ is an
+  output gate, and let $\vec{a} \in [n]^k$ and $\alpha :=
+  \alpha^{\vec{x}}_{\vec{a}}$. We have that $\pi_{\sigma} \Omega (\vec{a}) =
+  \pi_\sigma g_{\lambda[\alpha]} = g_{\lambda[\sigma \alpha]} = \Omega (\sigma
+  \alpha \vec{x}) = \Omega (\sigma \vec{a})$. This concludes the proof of the
+  claim.
 \end{proof}
@@
   If $C$ has symmetric gates then $C$ is transparent. Suppose $C$ contains a
-  non-symmetric gate. Let $g_{\phi[\alpha]}:= g \in G$ be a rank gate and
-  suppose $\psi$ is of the form $\rank^r_p \vec{w} \vec{z}. \zeta$, where $\zeta
-  = \zeta_1 \land \zeta_2$ and where, $\zeta_1 = ((\forall u. u = u) \land
-  \phi)$, and $\zeta_2 = \land (\op{tag}(\vec{w} \cup \vec{z}))$. Let $\beta_1 ,
-  \beta_2 \in [n]^{\free{\zeta}}$ both compatible with $\alpha$, and let $h_1 =
+  non-symmetric gate. Let $g_{\psi[\alpha]}\in G$ be a rank gate and suppose
+  $\psi$ is of the form $\rank^r_p \vec{w} \vec{z}. \zeta$, where $\zeta =
+  \zeta_1 \land \zeta_2$ and where, $\zeta_1 = ((\forall u. u = u) \land \phi)$,
+  and $\zeta_2 = \op{tag}(\vec{w} \cup \vec{z})$. Let $\beta_1 , \beta_2 \in
+  [n]^{\free{\zeta}}$ both be compatible with $\alpha$, and let $h_1 =
   g_{\zeta[\beta_1]}$ and $h_2 = g_{\zeta[\beta_2]}$. For $i \in [2]$ we have
@@
   have that $\beta_1$ and $\beta_2$ are compatible with $\alpha$, and so agree
-  on $\free{\zeta_1}$. It follows that $g_{\zeta_2[\beta_1]} \equiv
+  on all other free variables. It follows that $g_{\zeta_2[\beta_1]} \equiv
   g_{\zeta_2[\beta_2]}$ if, and only if, $\beta_1 = \beta_2$. This allows us to
@@
   $\beta_1 = \beta_2$ if, and only if, $g_{\zeta[\beta_1]} =
-  g_{\zeta[\beta_2]}$. It follows that $L(g)$ is injective, and no two $h_1, h_2
-  \in H_g$ are syntactically-equivalent. We conclude that $g$ has unique labels,
-  and so $C$ is transparent.
+  g_{\zeta[\beta_2]}$. It follows that $L(g_{\psi[\alpha]})$ is injective, and
+  no two child gates of $g_{\psi[\alpha]}$ are syntactically-equivalent. We
+  conclude that $g_{\psi[\alpha]}$ has unique labels, and so $C$ is transparent.
 \end{proof}
@@
   Let $\theta(\vec{x}) \in \FPR[\tau]$ and $t := \width (\theta)$. We begin by
-  showing that there exists a $P$-uniform family of formulas
+  showing that there exists a $\PT$-uniform family of formulas
   $(\theta(\vec{x}))_{n \in \nats}$ such that for each $n \in \nats$, we have
@@
   First, using the translation in~\cite{Dawar09logicswith}, we have that for any
-  $\phi(\vec{x}) \in \FPR[\tau]$ of the form $\lfp{V, \vec{y}}{\psi(\vec{x},
-    \vec{y}, V)}(\vec{x})$ , there is a mapping $n \mapsto \phi_n$, computable
-  in time polynomial in both $n$ and the size of $\phi(\vec{x})$ such that for
-  all $n \in \nats$, we have $\phi_n(\vec{x}) \in \FOR[\tau]$, $\width (\phi_n)
-  \leq 2 \cdot \width (\phi)$, and $\phi_n(\vec{x})$ and $\phi(\vec{x})$ are
-  equivalent on structures of size $n$.
+  $\phi(\vec{x}) \in \FPR[\tau]$ there is a mapping $n \mapsto \phi_n(\vec{x})$
+  computable in time polynomial in both $n$ and the size of $\phi(\vec{x})$, and
+  such that for all $n \in \nats$, we have $\phi_n(\vec{x}) \in \FOR[\tau]$,
+  $\width (\phi_n) \leq 2 \cdot \width (\phi)$, and $\phi_n(\vec{x})$ and
+  $\phi(\vec{x})$ are equivalent on structures of size $n$.
 
   Second, using the translation in~\cite{libkin2004elements}, we have that if
-  $\phi (\vec{x}) \in \FOR[\tau]$ is of the form $\rank (\vec{y}\vec{\mu} \leq
-  \vec{t}, \vec{z}\vec{\nu} \leq \vec{s}, \pi \leq r) . \psi (\vec{y}\vec{\mu},
-  \vec{z} \vec{\nu})$, then there is a mapping $n \mapsto \phi_n$ computable in
-  time polynomial in both $n$ and the size of $\phi(\vec{x})$ such that for all
-  $n \in \nats$, $\phi_n(\vec{x}) \in \FOrk[\tau]$, $\width(\phi_n) \leq 2 \cdot
-  \width(\phi)$, and $\phi_n(\vec{x})$ and $\phi(\vec{x})$ are equivalent on
-  structures of size $n$.
+  $\phi (\vec{x}) \in \FOR[\tau]$, then there is a mapping $n \mapsto \phi_n$
+  computable in time polynomial in both $n$ and the size of $\phi(\vec{x})$, and
+  such that for all $n \in \nats$, $\phi_n(\vec{x}) \in \FOrk[\tau]$,
+  $\width(\phi_n) \leq 2 \cdot \width(\phi)$, and $\phi_n(\vec{x})$ and
+  $\phi(\vec{x})$ are equivalent on structures of size $n$.
 
   We thus derive the required $\PT$-uniform family $(\theta_n(\vec{x}))_{n \in
-    \nats}$ by applying the first translation and then the second. We have from
-  Lemma~\ref{} that there exists an algorithm that takes as input $n$ and
-  $\theta_n$, runs in time polynomial in $n^{\width(\theta_n)} \vert
-  \cl{\theta_n} \vert$, and outputs a circuit $C_n = T(\theta_n, n)$ that
-  translates $\theta_n$ for $n$. We note that $\width{\theta_n} \leq 4t$ and
+    \nats}$ by applying the first translation and then the second. For each $n
+  \in \nats$ let $C_n$ be the output of the function defined in
+  Lemma~\ref{lem:translating-FOrk} for the input $\theta_n(\vec{x})$ and $n$. We
+  have from Lemma~\ref{lem:translating-FOrk} that for all $n \in \nats$, $C_n$
+  translates $\theta_n(\vec{x})$, and hence $\theta(\vec{x})$, for $n$.
+  Moreover, we note that $\theta_n$ can be computed in time polynomial in $n$
+  and $C_n$ can be computed in time polynomial in $n^{\width(\theta_n)} \vert
+  \cl{\theta_n} \vert$. We note that $\width(\theta_n) \leq 4t$ and
   $\cl{\theta_n}$ must be bounded by a polynomial in $n$ (since $\theta_n$ is a

### 2018-02-28 sections/transparency-and-unique-extensions.tex
Updates to the entire paper 28th Feb 2018

@@
   runs in time polynomial in the size of $C$.
-  \label{lem:unique-labels-syntactic-equiv}
+  \label{lem:transparent-syntactic-equiv}
 \end{lem}
@@
   $(\mathbb{B}, \rho)$-circuit of order $n$. We define the syntactic-equivalence
-  relation on $G$ by induction on the height of a gate We note that this
-  definition can be implemented by a dynamic program.
+  relation on $G$ by induction on the depth of a gate We note that this
+  definition by induction can be implemented as a construction using a dynamic program.
 
@@
   gates and suppose we have defined the syntactic-equivalence relation for all
-  gates of height less than the height of either $g$ or $h$. Then $g \equiv h$
+  gates of depth less than the depth of either $g$ or $h$. Then $g \equiv h$
   if, and only if, $L(g)$ and $L(h)$ are isomorphism equivalent up to $\equiv$.
@@
   Let $g$ and $h$ be two internal gates in $C$ and suppose we have defined the
-  syntactic-equivalence relation for all gates of height less than the height of
+  syntactic-equivalence relation for all gates of depth less than the depth of
   either $g$ or $h$. We test if for each gate in $g' \in H_g$, there exists
@@
   Lemma~\ref{lem:aut-partial} that $\sigma := L(h)^{-1} f L(g)$ acts like an
-  element of $\aut(g)$ if, and only if, for all $\vec{a}_R, \vec{b}_{R'} \in \ind(g)$,
-  $\sigma$ acts like a partial automorphism on $(\vec{a}_R, \vec{b}_{R'})$. We
-  thus conduct the test by iterating through every pair $(\vec{a}_R,
-  \vec{b}_{R'}) \in \ind(g)$, and set $g \equiv h$ if, and only if, $\sigma$
-  acts like a partial automorphism on every such pair.
+  element of $\aut(g)$ if, and only if, for all $\vec{a}_R, \vec{b}_{R'} \in
+  \ind(g)$, $\sigma$ acts like a partial automorphism on $(\vec{a}_R,
+  \vec{b}_{R'})$. We thus conduct the test by iterating through every pair
+  $(\vec{a}_R, \vec{b}_{R'}) \in \ind(g)$, and set $g \equiv h$ if, and only if,
+  $\sigma$ acts like a partial automorphism on every such pair.
 \end{proof}
 
-We now prove that transparent circuits can be transformed in polynomial time
-into equivalent circuits with unique extensions, and that this transformation
-preserves important properties of the circuit.
+It is sometimes useful to define one circuit from another circuit by
+\emph{quotienting} a circuit by the syntactic equivalence relation. Intuitively,
+a quotient circuit is defined by `merging' each syntactic-equivalence class into
+a single gate and including a wire between two gates in the quotient circuit if,
+and only if, there is a wire between an element of each equivalence class.
+
+\begin{definition}
+  Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\BB,
+  \rho)$-circuit. A \emph{quotient of $C$} is a $(\BB, \rho)$-circuit $C_\equiv
+  := \langle G_\equiv , \Omega_\equiv, \Sigma_\equiv , \Lambda_\equiv, L_\equiv
+  \rangle$, where $G_\equiv = G /_\equiv$, $\Omega_\equiv = \Omega /_\equiv$,
+  $\Sigma = \Sigma /_\equiv$, $(\Lambda_\equiv)_R = \Lambda_R /_\equiv$ for all
+  $R \in \rho$, and for all $[g] \in G_\equiv$ there exists $g' \in [g]$ such
+  that, $L_\equiv$ associates with $[g]$ a function $L_\equiv([g]) : \ind(g')
+  \rightarrow G_\equiv$ where $L_\equiv([g]) = L(g')/_\equiv$.
+\end{definition}
+
+We now show that taking the quotient of a circuit preserves important
+properties, including the function computed by the circuit, whether the circuit
+is symmetric, and has unique unique labels. We also show that the quotient of a
+circuit has trivial syntactic-equivalence classes, and hence unique extensions.
+
+\begin{lem}
+  Let $C := \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a $(\BB,
+  \rho)$-circuit of order $n$ and $C_{\equiv} = \langle G_\equiv ,
+  \Omega_\equiv, \Sigma_\equiv , \Lambda_\equiv, L_\equiv \rangle$ be a quotient
+  of $C$. Then $C$ and $C_{\equiv}$ compute the same function and each
+  syntacitic-equivalence class in $C_\equiv$ is a singleton. Moreover, if $C$ is
+  symmetric then $C_{\equiv}$ is symmetric, and for all $g \in G$, $g$ has
+  unique labels in $C$ if, and only if, $[g]$ has unique labels in $C_{\equiv}$.
+  \label{lem:quotient-circuits-preserve}
+\end{lem}
+\begin{proof}
+  We first prove that $C_\equiv$ and $C$ compute the same function. Let
+  $\mathcal{A}$ be a $\rho$-structure of size $n$ and let $\gamma$ be a
+  bijection from $U$ to $[n]$. We now show that for all $g \in G$, $C_\equiv
+  [\gamma \mathcal{A}]([g]) = C[\gamma \mathcal{A}](g)$. We do this by induction
+  on the depth of a gate. Suppose $g \in G$ has depth $0$. In this case $g$ is
+  an input gate and the result follows trivially. Suppose $g$ is an internal
+  gate and suppose for all $h$ of depth less than $g$ we have that
+  $C_\equiv[\gamma \mathcal{A}]([h]) = C[\gamma \mathcal{A}](h)$. We have that
+  there exists $g' \in [g]$ such that $L_\equiv ([g]) = L(g') /_\equiv$ and
+  $\Sigma_\equiv([g]) = \Sigma (g) = \Sigma (g')$. We have from Lemma~\ref{} and
+  the inductive hypothesis that there exists $\lambda \in \aut(g)$ such that
+  $L_\equiv ([g]) = L(g') = L(g) \lambda$. It follows from the fact that
+  $\Sigma(g)$ is a structured function that $C_\equiv[\gamma \mathcal{A}]([g]) =
+  \Sigma_\equiv ([g])(L^{\gamma \mathcal{A}}_\equiv([g])) = \Sigma (g')
+  (L^{\gamma \mathcal{A}}(g')) = \Sigma (g)(L^{\gamma \mathcal{A}}(g) \lambda) =
+  \Sigma (g) (L^{\gamma \mathcal{A}}(g)) = C[\gamma \mathcal{A}](g)$.
+
+  We now show that each syntactic-equivalence class in $C_\equiv$ is a
+  singleton. Suppose $[g], [h] \in G_\equiv$ and suppose $[g] \equiv [h]$. If
+  $[g]$ and $[h]$ are both input or output gates then $[g] = [h]$. Suppose $[g]$
+  and $[h]$ are internal gates that are not output gates. Then $\Sigma (g) =
+  \Sigma_\equiv ([g]) = \Sigma_\equiv([h]) = \Sigma(h)$. There exists $g', h'
+  \in G$ such that $g' \equiv g$ and $h' \equiv h$, and $L_\equiv ([g]) = L(g')
+  /_\equiv$ and $L_\equiv ([h]) = L(h') /_\equiv$. It follows from $[g] \equiv
+  [h]$ that $L(g') /_\equiv$ is isomorphism-equivalent to $L(h') /_\equiv$. It
+  follows that $g' \equiv h'$, and so $[g] = [h]$.
+
+  We now show that if $C$ is symmetric then $C_\equiv$ is symmetric. Suppose $C$
+  is symmetric. Let $\sigma \in \sym_n$. Then there exists $\pi \in \aut(C)$
+  that extends $\sigma$. Let $\pi_\equiv = pi /_\equiv$. We now show that
+  $\pi_\equiv$ is an automorphism of $C_\equiv$ extending $\sigma$. It is easy
+  to see that $\pi_\equiv$ is a bijection from $G_\equiv$ to $G_\equiv$ that
+  preserves syntactic-equivalence, and is thus is a well-defined function. Let
+  $[g] \in G_\equiv$. We have that $\Sigma_\equiv (\pi_\equiv [g]) =
+  \Sigma_\equiv ([\pi g]) = \Sigma (\pi g) = \Sigma (g) = \Sigma_\equiv ([g])$.
+  It is easy to check the automorphism conditions for input gates. Suppose $[g]$
+  is an internal gate. Let $g' \in [g]$ be such that $L_\equiv([g]) = L(g')
+  /_\equiv$ and $h \in [g]$ be such that $L_\equiv(\pi_\equiv[g]) = L_\equiv
+  ([\pi h]) = L(\pi h) /_\equiv$. We have that $\pi L(g')$ is
+  isomorphism-equivalent to $L(\pi g')$, and it follows that $(\pi
+  L(g'))/_\equiv$ is isomorphism-equivalent to $L(\pi g') /_\equiv$. We then
+  have $(\pi L(g'))/_\equiv = \pi_\equiv (L(g') /_\equiv) = \pi_\equiv L_\equiv
+  ([g])$ and, since $g' \equiv h$ and so $\pi g' \equiv \pi h$, we have that
+  $L(\pi g')/_\equiv$ is isomorphism-equivalent to $L(\pi h) /_\equiv =
+  L_\equiv(\pi_\equiv[g])$. It follows that $\pi_\equiv L_\equiv ([g])$ is
+  isomorphism-equivalent to $L_\equiv(\pi_\equiv [g]) /_\equiv$. Suppose $[g]$
+  is an output gate. Then for $\vec{a} \in \dom (\Omega)$, $\pi_\equiv
+  \Omega_\equiv (\vec{a}) = [\pi \Omega (\vec{a})] = [\Omega (\sigma \vec{a})] =
+  \Omega_\equiv (\sigma \vec{a})$.
+
+  Let $g \in G$. Suppose $[g]$ has unique labels. There exists $h \in [g]$ such
+  that $L_\equiv([g]) = L(h) /_\equiv$. Since $L_\equiv([g])$ is injective,
+  $L(h) /_\equiv$ must be injective and so $L(h)$ must be injective and no two
+  child gates of $L(h)$ must be syntactically-equivalent. It follows that $h$
+  has unique labels. Since $h \equiv g$ and $h$ has unique labels, it follows
+  that $g$ has unique labels. Suppose $g$ has unique labels. Let $h \in [g]$ be
+  such that $L_\equiv([g]) = L(h) /_\equiv$. Since $h \equiv g$ and $g$ has
+  unique labels $h$ has unique labels and so $L_\equiv([g])$ has injective
+  labels. Since each equivilence class in $C_\equiv$ is a singlton it follows
+  that $[g]$ has unique labels.
+
+  % If $[g]$ is an input gate then $\pi_\equiv [g] = [\pi g]$, and
+
+  % Let $\mathcal{A}$ be a $\rho$-structure of size $n$ and let $\gamma$ be a
+  % bijection from $U$ to $[n]$. We have from Lemma~\ref{} that for all $g, g'
+  % \in
+  % G$, if $g \equiv g'$ then $C[\gamma \mathcal{A}](g) = C[\gamma
+  % \mathcal{A}](g')$. Moreover, we should note that for each internal gate
+
+  % We show that for all $g \in G$, $C_\equiv [\gamma \mathcal{A}]([g]) =
+  % C[\gamma
+  % \mathcal{A}](g)$ by induction on the structure of the circuit. Suppose $g
+  % \in
+  % G$ is an input gate then, since every input gate is part of a singleton
+  % equivalence class, we have that $C /_\equiv [\gamma \mathcal{A}]([g]) =
+  % C[\gamma \mathcal{A}](g)$. Suppose $g \in G$ is an internal gate. Let $h \in
+  % [g]$ such that $L /_\equiv ([g]) = L(h)/_\equiv$. Then $(L/_\equiv)^{\gamma
+  % \mathcal{A}}([g])(x) = C /_\equiv[\gamma \mathcal{A}](L /_\equiv ([g])(x)) =
+  % C [\gamma \mathcal{A}](L(h)(x)) = L^{\gamma \mathcal{A}}(h)(x) \equiv
+  % L^{\gamma \mathcal{A}}(g) \circ \lambda (x)$ for some $\lambda \in \aut(g)$.
+  % But then, since $\Sigma (g)$ is a structured function, we have that
+  % $\Sigma(g)((L^{\gamma \mathcal{A}}(g) \lambda)) = \Sigma(g)(\L^{\gamma
+  % \mathcal{A}})$. It follows that $C /_\equiv [\gamma\mathcal{A}]([g]) =
+  % \Sigma /_\equiv ((L/_\equiv)^{\gamma mathcal{A}}([g])) = \Sigma (L^{\gamma
+  % \mathcal{A}}(g)\lambda) = \Sigma (L^{\gamma \mathcal{A}}(g)) = C[\gamma
+  % \mathcal{A}](g)$. It follows that $C/_\equiv [\gamma \mathcal{A}]
+  % (\Omega/_\equiv (\vec{a})) = C [\gamma \mathcal{A}](\Omega (\vec{a}))$ for
+  % all
+  % $a \in [n]^q$. It follows that $C_{\equiv}$ and $C$ compute the same
+  % function.
+
+  % Suppose $C$ is symmetric. Suppose $C$ is symmetric. We have from For $\sigma
+  % \in \sym_n$ let $\pi \in \aut(C)$ be an extension of $\sigma$. It can be
+  % shown
+  % that $\pi$ is invariant under $\equiv$, and hence we have that $\pi
+  % /_{\equiv}$ is a function. Since each gate that is either an input or output
+  % gate is a member of a singleton equivalence class we only need to check the
+  % symmetry condition for internal gates. Suppose $g$ is an internal gate then
+  % $\pi /_{\equiv} L /_{\equiv}([g]) (x) = [\pi L(g) (x)] = [L(\pi g) (\lambda
+  % x)] = L([\pi g]) (\lambda x) = L(\pi /_{\equiv} [g]) (\lambda x)$ for some
+  % $\lambda \in \aut(g)$. It follows that $\pi /_{\equiv}$ is an automorphism
+  % of
+  % $C_{\equiv}$ extending $\sigma$, and so $C_{\equiv}$ is symmetric.
+
+  % Let $[g], [g'] \in G/_{\equiv}$. Suppose $[g] \equiv [g']$. If $g$ is an
+  % input
+  % or output gate we have that $g = g'$. Suppose $g$ is an internal gate. Then
+  % there exists $h \in [g]$ and $h' \in [g']$ such that $L /_\equiv ([g]) =
+  % L(h)
+  % /_\equiv$ and $L /_\equiv ([g']) = L(h') /_\equiv$. We have that
+  % $L_{\equiv}([g])$ is isomorphism-equivilent to $L_{\equiv}$
+
+  % Let $g \in G$. Since every gate in $G /_{\equiv}$ is part of a singleton
+  % equivalence class.
+
+  % Then for each gate $g,
+  % g' \in G$ such that $g \equiv g'$ we have that $C[\gamma\mathcal{A}](g) =
+  % C[\gamma \mathcal{A}](g')$. If $g$ is an input gate we have that
+  % $C[\gamma\mathcal{A}](g) = C /_\eqiv [\gamma \mathcal{A}]([g])$. Suppose
+  % $[g] \in G /_{\equiv}$ is an internal gate. Let $L^{\gamma}([g]) : \ind(g)
+  % \rightarrow \{0,1\}$ be defined by $L^{\gamma}([g]) (x) = C[\gamma
+  % \mathcal{A}]([g])$
+\end{proof}
+
+It is worth noting that if $C$ is a transparent circuit we can compute a
+quotient of $C$ in time polynomial in the size of $C$. Since the circuit is
+transparent we can compute the syntactic-equivalence classes of $C$ in
+polynomial time (see Lemma~\ref{lem:transparent-syntactic-equiv}). Picking a
+representative of each equivalence class and wiring up the circuit in the
+obvious way then yields the desired quotient circuit.
+
+We now show that transparent circuits can be transformed in polynomial time into
+equivalent circuit with unique labels, and hence unique extensions (see
+Lemma~\ref{}), and that this transformation preserves important properties of
+the circuit.
 
@@
 \begin{proof}
-  Let $C' := \op{make-injective-all}(\op{merge-all} (C, G))$ (see
-  Definition~\ref{def:make-injective} and~\ref{def:merge-all} for the
-  definitions of these functions). It follows that if $C$ is symmetric then $C'$
-  is symmetric. We have from Lemma~\ref{lem:unique-labels-syntactic-equiv} that
-  the syntactic-equivalence relation can be computed in polynomial time for
-  transparent circuits. It follows that the construction of $C'$ from $C$ can be
-  implemented so as to run in time polynomial in the size of $C$. Clearly every
-  gate $g$ in $C'$ belongs to a singleton syntactic-equivalence equivalence
-  class, and as such $C'$ has unique labels.
+  Let $C_0 := \langle G_0, \Omega_0, \Sigma_0, \Lambda_0, L_0 \rangle$ be the
+  quotient of $C$. If $C_0$ does not contain the constant gates $g_0$ and $g_1$
+  such that $\Sigma(g_0) = 0$ and $\Sigma (g_1) = 1$ we construct a new circuit
+  from $C_0$ by adding these gates. We abuse notation and also call this new
+  circuit $C_0$. The addition of these constant gates to the circuit does not
+  alter the function computed by the circuit, nor does it effect the symmetry of
+  the circuit or weather it has unique labels.
+
+  The proof proceeds by first defining a circuit $C_1$ from $C_0$ and then
+  defining $C'$ from $C_1$. We then show that each of these constructions
+  preserves the relevant circuit properties and that $C'$ has unique labels.
+
+  We will define $C_1$ from $C_0$ by adding a designated gate that always
+  evaluates to $1$ and which is part of a singleton syntactic-equivalence class,
+  and then adding a wire from that gate to each $\AND$-gate in the circuit. This
+  process ensures that each $\AND$-gates in $C_1$ has a fan-in of at least two.
+  The construction of $C'$ from $C_1$ involves adding in a number of
+  single-input $\AND$-gates, and so the construction of $C_1$ will allow us to
+  distinguish these new gates from those in $C_1$.
+
+  We now define the circuit $C_1$ formally. Let $C_1 := \langle G_1, \Omega_1,
+  \Sigma_1 , \Lambda_1, L_1 \rangle$ be defined as follows. Let $G_1 = G_0
+  \uplus \{ g_\lor\}$. Let $\Omega_1 = \Omega_0$ and $\Lambda_1 = \Lambda_0$.
+  Let $g \in G_1$. If $g = g_\lor$ then $\Sigma_1 (g) = \lor[2]$, $L_1(g)(1) =
+  g_0$, and $L_1(g)(2) = g_1$. If $g \in G_0$, $\Sigma(g) = \lor[2]$ and $H_g =
+  \{g_0, g_1\}$ then $\Sigma_1 (g) = \lor[3]$, $L_1(g)(1) = L_0(g)(1)$,
+  $L_1(g)(2) = L_0(g)(2)$, and $L_1(g)(3) = g_\lor$. If $g \in G_0$ and $g =
+  \land[k]$ for some $k \in \nats$ then $\Sigma_1(g) = \land[k+1]$ and
+  $L_1(g)(i) = L_0(g)(i)$ for all $i \in [k]$ and $L_1(g)(k+1) = g_\lor$.
+  Otherwise let $\Sigma_1(g) = \Sigma_0(g)$ and $L_1(g) = L_0(g)$.
+
+  More informally, we define $C_1$ from $C_0$ by adding in an $\OR$-gate
+  $g_\lor$ that always evaluates to one, and then adding a wire from that gate
+  to all $\AND$-gates in the circuit, and also a wire from $g_\lor$ to another
+  $\OR$-gate in order to ensure that $g_\lor$ is part of a singleton
+  syntactic-equivalence class in $C_1$. The important point to note is that each
+  $\AND$-gate in $C_1$ has fan-in at least two, a property we will use to
+  construct $C'$. We now show that the construction of $C_1$ preserves the
+  relevant circuit properties.
+
+  % We have defined $C_1$ from $C_0$ by in a gate $g_\lor$ that always evaluates
+  % to $1$ and then adding a wire from that gate to each $\AND$-gate in the
+  % circuit. This process ensures that each $\AND$-gates in $C_1$ has a fan-in
+  % of at least two. The construction of $C'$ from $C_1$ involves adding in a
+  % number of single-input $\AND$-gates, and so the construction of $C_1$ will
+  % allow us to distinguish these new gates from those in $C_1$.
+
+  % We have constructed $C_1$ from $C_0$ by adding in a gate $g_\lor$ and then
+  % adding a wire from $g_\lor$ to each $\AND$-gate in the circuit and each gate
+  % two-input $\OR$-gate with the same children as $g_\lor$. Since $g_\lor$
+  % always evaluates to $1$, adding as an input to each $\AND$-gate (or the
+  % $\OR$-gate) has no effect on the evaluation of the circuit.
+
+  It is easy to see that if $C$ has order $n$ then $C_0$ has order $n$ and so
+  $C_1$ has order $n$. Let $\mathcal{A}$ be a $\rho$-structure of size $n$ and
+  let $\gamma$ be a bijection from the universe of $\mathcal{A}$ to $[n]$. We
+  have that $C_1[\gamma \mathcal{A}](g_\lor) = 1$. We constructed $C_1$ from
+  $C_0$ by adding a single wire from $g_\lor$ to each $\AND$-gate and each
+  two-input $\OR$-gate with only the two constant gates as children. Notice that
+  if $g$ is a two-input $\OR$ gate in $C_0$ with the two constant gates as
+  children, then since $g$ has $g_1$ as a child and $g$ is an $\OR$-gate
+  $C_0[\gamma \mathcal{A}](g) = C_1[\gamma \mathcal{A}](g) = 1$. It can be shown
+  by induction that if $g \in G_1 \setminus \{g_\lor\}$ then $C_0 [\gamma
+  \mathcal{A}](g) = C_1[\gamma \mathcal{A}](g)$. Since $\Omega_1 = \Omega_0$, it
+  follows that $C_0$ and $C_1$ compute the same function. We thus have from
+  Lemma~\ref{lem:quotient-circuits-preserve} that $C$ and $C_1$ compute the same
+  function.
+
+  Suppose $C$ is symmetric. From Lemma~\ref{lem:quotient-circuits-preserve} it
+  follows that $C_0$ is symmetric. Let $\sigma \in sym_n$ and let $\pi_0 \in
+  \aut(C_0)$ be an extension of $\sigma$. We define a bijection $\pi_1 : G_1
+  \rightarrow G_1$ such that $\pi_1 (g) = \pi_0(g)$ for all $g \in G_0$ and
+  $\pi_1 (g_\lor) = g_\lor$. It is easy to see that $\pi_1$ is an automorphism
+  of $C_1$ extending $\sigma$. It follows that $C_1$ is symmetric.
+
+  We have from Lemma~\ref{lem:quotient-circuits-preserve} that $C_0$ has trivial
+  syntactic-equivalence classes. Since $g_\lor$ is the only two input $\OR$-gate
+  with exactly the two constant gates as children, it follows that $g_\lor$ is
+  contained in a singleton syntactic-equivalence class. It can be shown by
+  induction that if $g, g' \in G_0$ are syntactically equivalent in $C_1$ then
+  they must be syntactically-equivalent in $C_0$. It follows that if $g$ and
+  $g'$ are syntactically-equivalent in $C_1$ then $g = g'$. We thus have that
+  $C_1$ has trivial syntactic-equivalence classes.
+
+  Let $C' := \{G', \Omega', \Sigma' \Lambda' L'\}$ be defined as follows. For
+  each $h \in G_1$ let $c^h_g := \vert L_1(g)^{-1}(h) \vert$ if $h \in H_g$ and
+  $c^h_g := 0$ otherwise. For each $h \in G_1$ let $c^h$ be the maximum of
+  $c^h_g$ for $g \in G_1$. For each $h \in G_1$ if $c^h > 1$ let $G_h :=
+  \{g^{h}_{1}, ldots, g^h_{c_h-1}\}$ otherwise let $G_h := \emptyset$. Let
+  $G_{\land} := \biguplus_{h \in G_1} G_h$ and $G' = G_{\land} \uplus G_1$. Let
+  $\Omega' = \Omega_1$ and $\Lambda' = \Lambda_1$. For $g \in G'$ if $g \in G_1$
+  let $\Sigma'(g) = \Sigma_1(g)$ and otherwise let $\Sigma'(g) = \land[1]$. For
+  each $g \in G_1$ and $h \in H_g$ let $\{x^{h,g}_0, x^{h,g}_1 ,\ldots,
+  x^{h,g}_{c^h_g - 1}\} := L_1(g)^{-1}(h)$ be a fixed ordering of the set
+  $L_1(g)^{-1}(h)$. Let $g \in G'$. If $g \in G_1$ and $x \in \ind(g)$ then
+  there exists $h \in H_g$ and $i \in \{0, \ldots , c^h_g -1\}$ such that $x =
+  x^{h,g}_i$, and we let $L'(g)(x) = h$ if $i = 0$ and $L'(g)(x^{h,g}_i) =
+  g^h_i$ otherwise. If $g \in G_{\land}$ then $g = g^h_i$ for some $h \in G_1$
+  and $i \in [c^h_g]$, and we let $L'(g)(1) = h$ if $i = 1$ and $L'(g)(1) =
+  g^h_{i-1}$ otherwise.
+
+  The construction ensures that $C'$ has injective labels. Let $g \in G_1$. In
+  order to avoid confusion we let $H_g$ be the set of children of $g$ in $C_1$
+  and $H_g'$ be the set of children of $g$ in $C'$. If $g' \in G_1$ we let $g
+  \equiv g'$ denote syntactic-equivalence in $C_1$ and $g \equiv' g'$ denote
+  syntactic-equivalence in $C'$.
+
+  \begin{claim}
+    $C'$ has trivial syntactic-equivalence classes.
+  \end{claim}
+  \begin{proof}
+    We prove this result by induction on depth. Let $g \in G'$. If $g$ has depth
+    $0$ then $g$ is an input gate and so $[g] = \{g\}$. Let $g \in G'$ be an
+    internal gate in $C'$ and suppose for each gate $h$ of depth less than $g$
+    we have that $[h] = \{ h \}$. Let $g' \in G'$ and suppose $g \equiv' g'$. We
+    now show that $g = g'$, and so prove the claim. Since $g \equiv' g'$ it
+    follows that $\Sigma (g) = \Sigma(g')$ and both $g$ and $g'$ have the same
+    depth. Moreover, from the inductive hypothesis, we have that there exists
+    $\lambda \in \aut(g)$ such that for all $x \in \ind(g)$, $L'(g) (x) =
+    L'(g')(x)$. It follows that $H_{g}' = H_{g'}'$. Moreover, from the inductive
+    hypothesis the children of $g$ and $g'$ must be contained in singleton
+    syntactic-equivalence classes, and so , since $C'$ has injective labels, it
+    follows that $g$ and $g'$ have unique labels in $C'$.
+
+    % Suppose $g = g_\lor$. Then $H_g = H_g' = \{g_0, g_1\} = H_{g'}'$ and
+    % $\Sigma' (g) = \Sigma'(g') = \lor[2]$. But from the construction the only
+    % two-input $\OR$-gate in $C_1$, and so $C'$, with children $\{g_0 , g_1\}$
+    % is
+    % $g$. It follows that $g = g'$.
+
+    Suppose $g \in G_{\land}$. Then there exists $h \in G_1$ and $i \in [c^h -
+    1]$ such that $g = g^h_i$. Suppose $g' \in G_1$. Then $\Sigma'(g) =
+    \land[1]$. But, from the construction of $C_1$, there are no single-input
+    $\AND$-gates in $G_1$. It follows $\Sigma'(g') \neq \Sigma'(g)$ and so $g'
+    \not\equiv' g$, a contradiction, and so we must have $g' \in G_{\land}$. If
+    $i = 1$ then $\{ h \} = H_g' = H_{g'}'$. Since the only gate in $G_\land$
+    that has $h$ as a child gate is $g^h_1$, it follows that $g = g^h_1 = g'$.
+    If $i > 1$ then $\{g^{h}_{i-1}\} = H_g' = H_{g'}'$. Since $g^h_i$ is the
+    only gate in $G_\land$ that has $g^h_{i-1}$ as a child gate, we have $g =
+    g^h_i = g'$. It follows that if $g \in G_\land$ then $g = g'$.
+
+    Suppose $g \in G_1$. We have already shown that if $g' \in G_\land G_1$ then
+    $g \not\equiv' g'$, a contradiction, and so we must have $g' \in G_1$. Since
+    $g \equiv' g'$ there exists $\lambda \in \aut(g)$ such that for all $x \in
+    \ind(g)$, $L'(g)(\lambda x) = L'(g')(x)$. From the construction, we have
+    that for all $x \in \ind(g)$ and $h \in G_1$, $L'(g)(x) \in \{h, g^h_1 ,
+    \ldots, g^h_{c^h_g -1}\}$ if, and only if, $L_1(g)(x) = h$. Suppose $g$ is
+    not a symmetric gate. Since $C$ is transparent, $C_0$ is transparent and so
+    $C_1$ is transparent. It follows that for all $h \in H_g$, $H_g = H_{g'}$,
+    and $c^h_g = 1 = c^h_{g'}$. It follows that for all $x \in \ind(g)$, there
+    exists a unique $h \in G_1$ such that $L_1(g)(\lambda x) = L'(g)(\lambda x)
+    = L'(g')(x) = L_1 (g')(x) = h$. It follows that $g \equiv g'$ and so $g =
+    g'$. Suppose $g$ is a symmetric gate. Let $x \ind(g)$ and $h = L_1(g)(x)$.
+    If $L'(g)(\lambda x) = L'(g')(x)= h$ then $L_1(g)(\lambda x) = h$ if, and
+    only if, $L'(g)(\lambda x ) = h* = L'(g')(x)$, where $h* = h$ or $h* =
+    g^{h}_i$, for some $i \in [c^h_g -1]$, if, and only if, $L_1(g) (x) = h$. It
+    follows that for all $x \in \ind(g)$, $L_1 (g) (\lambda x) = L_1 (g)(x)$,
+    and so $g \equiv g'$ and so $g = g'$.
+
+    % It follows that for all $g \in G'$, $[g] = \{g\}$. The result follows.
+
+    % Suppose $g \in G_0$. If $g$ is a non-symmetric gate then $g$ has unique
+    % labels in $C_0$ and so has unique labels in $C_1$. It follows that for all
+    % $h \in H_g$, $c^h_g = 1$, $g$ has injective labels in $C'$ and so, using
+    % the
+    % inductive hypothesis, $g$ has unique labels. Since $g \equiv' g'$ we also
+    % have that $g'$ has unique labels.
+
+    % It is easy to show that for all $h, g \in G_1$, if $W_t(h,g)$ in $C_1$
+    % then
+    % $W_t(h,g)$ in $C'$. We prove this result by induction on depth. Suppose
+    % $g$
+    % and $g'$ have depth $0$ in $C'$ then $g$ and $g'$ are input gates, and so
+    % $g
+    % \equiv' g'$ if, and only if, $g = g'$ if, and only if, $g \equiv g'$.
+    % Suppose $g, g' \in G_1$ are internal symmetric gates and for all $h , h'
+    % \in
+    % G_1$ of depth less than $g$ or $g'$ in $C'$ $h \equiv h'$ if, and only if,
+    % $h \equiv' h'$. Suppose $g \equiv g'$. Then there exists $\lambda \in
+    % \aut(g)$ such that for all $x \in \ind(g)$, $L_1(g)(x) \equiv
+    % L_1(g')(\lambda x)$. If $H_g'\cup \H_{g'}' \subseteq G_1$ then the result
+    % follows obviously from the inductive hypothesis. For each $h \in H_g$ and
+    % $x
+    % \in L(g)^{-1}(h)$ if $c^h_g = 1$ then let $\lambda' x = x$ and if $c^h_g >
+    % 1$ and if $x = x^{h,g}_i$ for some $i \in [c^h_g - 1]$ then $\lambda' x =
+    % x^{h', g'}_i$ where $h' = L_1(g')(\lambda x)$. It can be shown that
+    % $\lambda'$ is a bijection on $\ind(g)$. Since $g$ and $g'$ are symmetric
+    % gates it follows that $\lambda' \in \aut(g)$...
+  \end{proof}
+
+  Since $C'$ has injective labels and trivial syntactic-equivalence classes it
+  follows $C'$ has unique labels.
+
+  We have already shown that if $C$ is symmetric then $C_1$ is symmetric. We now
+  show that if $C_1$ is symmetric then $C'$ is symmetric. Suppose $C_1$ is
+  symmetric. Let $\sigma \in \sym_n$ and let $\pi_1 \in \aut(C_1)$ be an
+  extension of $\sigma$. We define the function $\pi' : G' \rightarrow G'$ as
+  follows. Let $g \in G'$. If $g \in G_1$ then $\pi'(g) = \pi_1(g)$, otherwise
+  $g \in G_\land$, and so there exists $h \in G_1$ and $i \in [c^h - 1]$ such
+  that $g = g^h_i$, let $\pi'(g) = g^{\pi_1 h}_i$. It is easy to show that
+  $\pi'$ is an automorphism of $C'$ extending $\sigma$.
+
+  \begin{claim}
+    Let $g \in G_1$, $\mathcal{A}$ be a $\rho$-structure of size $n$, and
+    $\gamma$ be a bijection from the universe of $\mathcal{A}$ to $[n]$. Then
+    $C'[\gamma \mathcal{A}](g) = C_1[\gamma \mathcal{A}](g)$.
+  \end{claim}
+  \begin{proof}
+    It is easy to see that for all $h \in G_1$ and $i \in [c^h-1]$ we have that
+    $C'[\gamma \mathcal{A}](g^h_i) = C'[\gamma \mathcal{A}](h)$. Suppose $g \in
+    G_1$. We now prove the result by induction on the depth of a gate. Suppose
+    $g$ has depth $0$, then $g$ is an input gate, and the case follows
+    trivially. Suppose $g$ is an internal gate, and for all $h$ of depth less
+    than $g$ we have that if $h \in G_1$ then $C'[\gamma \mathcal{A}](h) =
+    C_1[\gamma \mathcal{A}](h)$. Let $x \in \ind(g)$. From the construction of
+    $C'$ we have that if $L'(g)(x) \in G_1$ then ${L'}^{\gamma
+      \mathcal{A}}(g)(x) = L^{\gamma \mathcal{A}}_1(g)(x)$. If $L'(g)(x) \not\in
+    G_1$ then $L'(g)(x) \in G_{\land}$ and so $L'(g)(x) = g^h_i$, where $h =
+    L_1(g)(x)$ and some $i \in [c^h_g -1]$. But then ${L'}^{\gamma
+      \mathcal{A}}(g)(x) = C'[\gamma \mathcal{A}](g^h_i) = C'[\gamma
+    \mathcal{A}](h) = C_1[\gamma \mathcal{A}](h) = L^{\gamma
+      \mathcal{A}}_1(g)(x)$. The penultimate equality follow from from the
+    inductive hypothesis. The final equality follows from the fact that $h = L_1
+    (g)(x)$. We thus have $C'[\gamma \mathcal{A}](g) = \Sigma'({L'}^{\gamma
+      \mathcal{A}}(g)) = \Sigma_1 (L^{\gamma \mathcal{A}}_1(g)) = C_1[\gamma
+    \mathcal{A}](g)$.
+  \end{proof}
+
+  Since $\Omega' = \Omega_1$, we have that $C'$ and $C_1$ compute the same
+  function. It follows that, since $C_1$ and $C$ compute the same function, $C$
+  and $C'$ compute the same function. Since $C$ is transparent, we may construct
+  the quotient circuit $C_0$ in time polynomial in $\vert C \vert$. Since $C_1$
+  is constructed by adding in a single gate and then adding at most $\vert C_0
+  \vert$ wires, we may construct $C_1$ from $C_0$ in time polynomial in $\vert C
+  \vert$. It is is easy to see that $C'$ can be constructed in time polynomial
+  in $\vert C_1 \vert$ and hence polynomial in $\vert C \vert$. The result
+  follows.
+  %
+  % It is easy to see that $C'$ has injective labels. Let $g$ be an internal
+  % gate
+  % in $C'$ and suppose each gate of depth less than $g$ has unique labels. Let
+  % $h, h' \in H_g$ such that $h \equiv h'$. If $h, h' \in G_1$ it follows $h =
+  % h'$. Suppose $h, h' \in G_{\land}$. Then there exists $d, d' \in G_1$ and
+  % $i,
+  % j$ such that $g^d_i \equiv g^{d'}_j$. If $j = i$ then $d \equiv d'$ and so
+  % $d
+  % = d'$ and $h = h'$. Suppose, without a loss of generality, that $i > j$. It
+  % follows that $g^d_{i-j} \equiv d'$. But then $d'$ is a single-input
+  % $\AND$-gate, which is impossible, as from the construction $d'$ must have at
+  % least two inputs. Suppose
+
+  % Thus $g \equiv g'$ if, and only if, $g = g'$
+  % Let $C'':= \langle G'', \Omega'', \Sigma'', \Lambda'', L'' \rangle$ be a
+  % quotient of $C$. We have from Lemma~\ref{lem:quotient-circuits-preserve}
+  % that
+  % $C''$ is transparent, i.e. all the non-symmetric gates have unique labels,
+  % and
+  % that no two input gates to any one gate are syntactically-equivalent. We now
+  % construct a circuit $C'$ from $C''$ that leaves the non-symmetric gates
+  % unchanged but such that each symmetric gate in $C'$ has unique labels. We
+  % construct $C'$ by taking each symmetric gate $g$ in $C''$ and each gate $h
+  % \in
+  % H_g$ and adding in a sequence of single-input $\AND$-gates, one for each
+  % wire
+  % from $h$ to $g$, such that the first $\AND$-gate in this sequence has $h$ as
+  % its input and each successive $\AND$-gate has the previous one as an input.
+  % We
+  % then remove all but one of the wires from $h$ to $g$ and add a wire from
+  % each
+  % $\AND$-gate in this sequence to $g$. We now construct $C'$ formally.
+
+  % Let $C_i = \langle G_i, \Omega_i, \Sigma_i, \Lambda_i, L_i \rangle$ be a
+  % transparent circuit of order $n$. We construct $C_{i+1} := \langle G_{i+1},
+  % \Omega_{i+1}, \Sigma_{i+1}, \Lambda_{i+1}, L_{i+1} \rangle$ as follows. For
+  % each $g \in G_i$ and $h \in H_g$ let $s^g_h = \{x \in \ind(g) : L(g)(x)
+  % \equiv
+  % h\}$ and let $c_h$ be the maximum $\vert c^g_h \vert$ for all $g \in G_i$.
+  % Let
+  % $G_{\land} := \{g^h_\land : h \in G_i, \, c_h > 1\}$. Let $G_{i}' := G_i
+  % \cup
+  % G_{\land}$. Let $\Omega_{i}' := \Omega_i$. For $g \in G_i$ let $\Sigma_{i}'
+  % (g) := \Sigma_i (g)$ if $g \in G_i$ and $\Sigma_{i}'(g) := \land[1]$
+  % otherwise. Let $\Lambda_{i}' := \Lambda_i$. We now define $L_{i}'(g)$ for
+  % each
+  % $g \in G_{i}'$. If $g \in G_{i}$ and $g$ is not a symmetric gate then
+  % $L_{i}'(g) = L_i(g)$. If $g \in G_{\land}$ and $g = g^h_\land$ for some $h
+  % \in
+  % G_i$ let $L(g)(1) = h$. Suppose $g \in G_{i}$ and $g$ is a symmetric gate.
+  % For
+  % each $h \in H_g$ select one $x_h \in \ind(g)$. For $x \in \ind(g)$ let
+  % $L_{i+1}(g) (x) = h$ if $x = x_h$ and $L_{i}'(g)(x) = g^h_\land$ otherwise.
+  % Let $F(C_i) := C_{i+1} := \langle G_{i+1}, \Omega_{i+1}, \Sigma_{i+1},
+  % \Lambda_{i+1}, L_{i+1} \rangle$ be a quotient of $C_i'$.
+
+  % Let $C_0' := C$ and $C_1$ be a quotient of $C_0$. For each natural number
+  % $i>
+  % 0$ we define a circuit $C_{i+1}$ from $C_{i} := \langle G_{i}, \Omega_{i},
+  % \Sigma_{i}, \Lambda_{i}, L_{i} \rangle$ as follows. We first define $C_i' =
+  % \langle G_i', \Omega_i', \Sigma_i', \Lambda_i', L_i' \rangle$ as follows.
+  % For
+  % each $g, h \in G_i$ let $c^g_h = \vert L_i(g)^{-1}(h) \vert$ and let $c_h$
+  % be
+  % the maximum $c^g_h$ for all $g \in G_i$. Let $G_{\land} := \{g^h_\land : h
+  % \in
+  % G_i, \, c_h > 1\}$. Let $G_{i}' := G_i \cup G_{\land}$. Let $\Omega_{i}' :=
+  % \Omega_i$. For $g \in G_i$ let $\Sigma_{i}' (g) := \Sigma_i (g)$ if $g \in
+  % G_i$ and $\Sigma_{i}'(g) := \land[1]$ otherwise. Let $\Lambda_{i}' :=
+  % \Lambda_i$. We now define $L_{i}'(g)$ for each $g \in G_{i}'$. If $g \in
+  % G_{i}$ and $g$ is not a symmetric gate then $L_{i}'(g) = L_i(g)$. If $g \in
+  % G_{\land}$ and $g = g^h_\land$ for some $h \in G_i$ let $L(g)(1) = h$.
+  % Suppose
+  % $g \in G_{i}$ and $g$ is a symmetric gate. For each $h \in H_g$ select one
+  % $x_h \in \ind(g)$. For $x \in \ind(g)$ let $L_{i}'(g) (x) = h$ if $x = x_h$
+  % and $L_{i}'(g)(x) = g^h_\land$ otherwise. Let $C_{i+1} = F(C_i) := C_{i+1}
+  % :=
+  % \langle G_{i+1}, \Omega_{i+1}, \Sigma_{i+1}, \Lambda_{i+1}, L_{i+1} \rangle$
+  % be a quotient of $C_i'$.
+
+  % Let $i \in \nats$. For $g \in G_i$, in order to avoid ambiguity we let $H_g$
+  % denote the set of children of $g$ in $C_i$ and $H_g'$ denote the set of
+  % children of $g$ in $C_i'$. We let $\equiv$ be the syntactic-equivalence
+  % relation in $C_i$ and $\equiv'$ be the syntactic-equivalence relation in
+  % $C_i'$.
+
+  % If $C_i$ has order $n$ then $C_i'$ is has order $n$ and so $C_{i+1}$ has
+  % order
+  % $n$. We first show that $C_{i+1}$ and $C_i$ compute the same function. Let
+  % $\mathcal{A}$ be a $\rho$-structure of size $n$ and let $\gamma$ be a
+  % bijection
+  % from the universe of $\mathcal{A}$ to $[n]$. The construction of $C_i'$ from
+  % $C_i$ by identifying those gates $h, g \in G_i$ such that $h \in H_g$ and
+  % $\vert L_i(g)^{-1}(h) \vert > 1$ and then replacing all but one of the wires
+  % from $h$ to $g$ with a wire from $g^h_\land$ to $g$. Since $g^h_\land$ is a
+  % single-input $\AND$-gate with input $h$, we have that $C_i[\gamma
+  % \mathcal{A}](h) = C_{i}'[\gamma \mathcal{A}](h) = C_i'[\gamma
+  % \mathcal{A}](g^h_\land)$. It follows that $C_i [\gamma \mathcal{A}](g) =
+  % C_i'
+  % [\gamma \mathcal{A}](g)$. We thus have that $C_i$ and $C_i'$ compute the
+  % same
+  % function and so, using Lemma~\ref{lem:quotient-circuits-preserve}, $C_{i+1}$
+  % computes the same function as $C_i$.
+
+  % Suppose $C_i$ is symmetric. Let $\sigma \in \sym_n$ and $\pi \in \aut(C)$ be
+  % an extension of $\sigma$. It can be shown that $c_h = c_{\pi h}$. As such,
+  % we
+  % can extend $\pi$ to $G_i'$, defining $\pi' : G_i' \rightarrow G_i'$ by $\pi'
+  % g
+  % = \pi g$ if $g \in G_i$ and letting $\pi' g^h_\land = g^{\pi h}_\land$ if
+  % $g^h_\land \in G_{\land}$. It can be shown that $\pi'$ is an automorphism of
+  % $G_i'$ extending $\sigma$, and so $C_i'$ is symmetric. It follows from
+  % Lemma~\ref{lem:quotient-circuits-preserve} that $C_{i+1}$ is symmetric.
+
+  % It can be shown that for all $g, g' \in G_i$, $g \equiv g'$ if, and only if,
+  % $g \equiv' g'$.
+
+  % % It follows that for $g^h_\land, g^{h'}_\land \in G_\land$ if
+  % % $g^h_\land \equiv' g^{h'}_\land$ then $h \equiv' h'$ and so $h \equiv h'$.
+
+  % Suppose $C_i$ has unique labels. It follows that $c_h = 1$ for all $h \in
+  % G_i$
+  % and so $C_i = C_{i}'$. We thus have, using
+  % Lemma~\ref{lem:quotient-circuits-preserve}, that $C_{i+1}$ has unique
+  % labels.
+  % Suppose $C_i$ does not have unique labels. For $g \in G_{i}$ and $h \in H_g$
+  % let $s^h_g := \vert \{x \in \ind(g): L_i(g)(x) \equiv h\} \vert$. In other
+  % words $s^h_g$ is the number of wires to $g$ from either $h$ or a gate
+  % syntactically-equivalent to $h$. For $g \in G_i$ let $d_g$ be the minimum
+  % depth of a gate $h \in H_g$ in $C_i$ such that $s^h_g > 1$ and let $d_g
+  % :=\infty$ if no such gate exists. In other words $d_g$ is the depth of the
+  % minimum-depth gate witnessing that $g$ does not have unique labels. For $g
+  % \in
+  % G_i'$ we define $d_g'$ similarly for $C_i'$. For $g \in G_i$ let $S^i_g :=
+  % \{h
+  % \in H_g : \depth(C_i, h) < d_g \}$ be a set of gates in $C_i$. For $g \in
+  % G_i'$ we define $S^i_g'$ similarly for $C_i'$.
+
+  % Since $C_i$ does not have unique labels, there exists $g \in G_i$ such that
+  % $d^i_g \neq \infty$. Let $H^d_g := \{h \in H_g : \depth (C_i, h) = d_g\}$ be
+  % a
+  % set of gates in $C_i$. We now prove that $H^d_g \cup S^i_g \subseteq
+  % S^i_g'$.
+  % It can be shown that for all $h, h' \in H_g$, if $\depth(C_i, h) <
+  % \depth(C_i,
+  % h')$ then $\depth(C_i', h) < \depth(C_i', h')$. Since the construction
+  % preserves the `child of' relation, we have for all $h \in H_g$ that
+  % $\depth(C_i, h) \leq \depth(C_i', h)$. Let $h \in S^i_g$. Since $s^h_g = c_h
+  % =
+  % 1$ we have that $\vert L_{i}'(g)^{-1}(g) \vert = 1$. From
+  % Lemma~\ref{lem:quotient-circuits-preserve} we have that $h \not\equiv h'$
+  % for
+  % all $h' \in H_g$. So suppose $h \equiv' g^{h'}_{\land}$ for some $g^h'_\land
+  % \in G_\land$. It follows that $h'$ must be syntactically-equivalent to the
+  % single child of $h$ in $C_i$ and so $\depth(C_i',h') < \depth(C_i', h)$
+
+  % It follows that $h' \in H_{h}'$ (since $C_i$ is a quotient) Suppose there
+  % exists a gate $h' \in G_i'$ such that $h \equiv h'$ in $C_i'$. Since $C_i$
+  % has
+  % trivial symmetric-equivalence classes, it follows that $h' = g^{h''}_\land$
+  % for
+
+  % Let $d$ be the maximum depth in $C_i'$ of a gate in $H^d_g \cup S^i_g$.
+  % Suppose $h \in G_i'$ such that $\depth (C_i', h) \leq d$ and $s^h_g' > 1$.
+
+  % We have from the construction that $\vert L_i'(g)^{-1}(h) \vert = 1$. It
+  % follows that there exists $h' \in H_g'$, $h' \neq h$ such that $h' \equiv' h
+  % $. Moreover, since $G_i$ has singleton-equivalence classes we have that $h'
+  % \not\in G_i$. So there exists $h'' \in H_g$ such that $c^g_{h''} > 1$ and
+  % $h'
+  % = g^{h''}_i \equiv' h'$. Since $C_i$ is a quotient we have that $h''$ is the
+  % only child of $h'$ in $C_i$, and so $\depth(C_i, h'') < \depth(C_i, h')$.
+  % Moreover, since $\depth(C_i, h') \leq \depth(C_i', h') \leq d \leq d_g$ We
+  % thus have that $d_g \leq \depth(C_i, h'') < \depth(C_i, h') \leq \depth(C_i,
+  % h) \leq d_g$
+
+  % If $d < d_g'$ we are done. Suppose $d \geq d_g'$. Then there exists $h \in
+  % H^d_g \cup S^i_g$ such that $d_g' \leq d(C_i', h) \leq d$
+
+  % and suppose there exists $h \in H_g'$ such that $\depth(C_i, h) < d$
+
+  % Since $C_i$ does not have unique labels there exists $g \in G_i$ and $h \in
+  % H_g$ such that $d(C_i, g) \neq \infty$. If $h \in s(C_i, g)$ and $c_h = 1$
+  % then $s(C_i', g)$.
+
+  % Let $H^{d}_g \subseteq H_g$ be the set of children of $g$ of depth
+  % $d(C_i,g)$.
+
+  % We have for each $h \in G_i$ such that $c_h > 1$ that $g^h_i$ has a depth in
+  % $C_i'$ strictly greater than $h$ ensures that $d_g \leq d_g'$
+
+  % For $g \in G_{i}$ and $h \in H_g$ let $s^h_g := \vert \{x \in \ind(g):
+  % L_i(g)(x) \equiv h\} \vert$. Let $d_g$ be the minimum depth of a gate $h \in
+  % H_g$ in $C_i$ such that $s^h_g > 1$ and let $d_g :=\infty$ if no such gate
+  % exists. It follows that $d_g = \infty$ for all $g \in G_i$ if, and only if,
+  % $C_i$ has unique labels.
+
+  % Suppose $C_i$ does not have unique labels. Let $g \in G_i$ such that $d_g
+  % \neq
+  % \infy$ and let $H^{d}_g \subseteq H_g$ be the set of children of $g$ of
+  % depth
+  % $d_g$. We notice that for all $h, h' \in H^d_g$, $h'$ and $g^h_\land$ have
+  % different depths in $C_i'$ and so $h' \no\equiv g^h_\land$ in $C_i'$.
+  % Moreover,
+
+  % For $g \in G_i$ let $s_g := s^h_g$ where $h$ is the minmimal-depth where $h
+  % \in H_g$ is the
+
+  % be the minimum depth the is minimum depth child such that $\vert H_g
+  % /_\equiv
+  % \vert > 1$, and $s_g = 0$ if no such gate exists. Let $S(C_i)$ be the
+  % maximum
+  % of $s_0$.
+
+  % Notice that $s_i = 0$ if, and only if, $C_i$ has unique labels. Suppose
+  % $S(C_i) \neq 0$. Let $H^s_g = \{ h \in H_g : c^h_g > 1\}i$. Let $h$ be the
+  % gate of minimal depth in $H^s_g$. Then $h$ is not syntactically-equivalent
+  % to
+  % $g^h_\land$
+
+  % Suppose $C_i$ does not have unique labels. Then
+
+  % Suppose $C_i$ is symmetric.
+
+  % % Let $H \subseteq G''$ be the set of all symmetric gates. For each $h \in
+  % % G''$
+  % % let $c_h$ be the maximum of $\vert L(g)^{-1}(h) \vert$ for $g \in H$ such
+  % % that
+  % % $h \in H_g$. For each $h \in G''$ let $G_{h, \land} := \{g^h_1, \ldots,
+  % % g^h_{c_h - 1}\}$. Let $G_\land := \bigcup_{h \in G''} G_{h, \land}$. Let
+  % % $G'
+  % % := G'' \cup G_{\land}$. Let $\Omega' := \Omega''$. For $g \in G''$ let
+  % % $\Sigma' (g) := \Sigma'' (g)$ if $g \in G$ and $\Sigma'(g) := \land[1]$
+  % % otherwise. Let $\Lambda' := \Lambda''$. We now define $L'(g)$ for each $g
+  % % \in
+  % % G'$. If $g \in G' \setminus (H \cup G_\land)$ let $L'(g) = L''(g)$. If $g
+  % % \in
+  % % G_\land$ and $g = g^h_i$ for some $h \in G''$ and $i \in [c_h]$, if $i =
+  % % 1$
+  % % let $L(g)(1) = h$ otherwise let $L(g)(1) = g^h_{i-1}$. Suppose $g \in H$.
+  % % For
+  % % each $h \in H_g$ let $\{x^h, x^h_1, \ldots, x^h_k\} := L(g)^{-1}(h)$, and
+  % % notice that $\vert L(g)^{-1}(h) \vert \leq c_h$. For each $x \in \ind(g)$
+  % % let
+  % % $h = L(g)(x)$ and let $L'(g) (x) = h$ if $x = x^h$ and $L'(g)(x) = g^h_i$
+  % % if
+  % % $x = x^h_i$ for some $i \in [\vert L(g)^{-1} \vert - 1]$.
+
+  % e have from Lemma~\ref{lem:quotient-circuits-preserve} that $C''$ has unique
+  % labels if $C$ has unique labels, $C''$ is symmetric if $C$ is symmetric and
+  % $C''$ and $C$ compute the same function. Since $C''$ is constructed from
+  % $C'$
+  % by replacing some of the wires from $h$ to the symmetric gate $g$ with
+  % $\AND$-gates that evaluate to the same value as $h$, it is not hard to see
+  % that $C'$ computes the same function as $C''$, and hence $C'$. Moreover, the
+  % construction also ensures that each symmetric gate (and so each internal
+  % gate)
+  % in $C'$ has injective labels. It is easy to see that for a fixed $h \in G''$
+  % no two gates in $G_{h,\land} \uplus \{h\}$ are syntactically-equivalent.
+  % Suppose $h, h' \in G''$ and $g^h_i \equiv g^{h'}_j$ for some $i \in [c_h -
+  % 1]
+  % $ and $j \in [c_{h'} -1]$. If $j = i$ then it can be shown that $h \equiv
+  % h'$
+  % and so $h = h'$. If $i > j$ then it can be shown that $g^h_{i-j} \equiv h'$,
+  % but then $W_T(h', h)$ in $C''$
+
+  % Let $C/_{\equiv} := \langle G /_{\equiv}, \Omega/_{\equiv},
+  % \Sigma/_{\equiv},
+  % \Lambda/_{\equiv}, L/_{\equiv}$ be the quotient of $C$ by
+  % syntactic-equivalence. Since each gate that is an input or output gates is a
+  % member of a singleton equivalence class, we have that $C/_{\equiv}$ is
+  % indeed
+  % a circuit.
+
+  % We have that no two gates in $G /_{\equiv}$ are syntactically-equivalent.
+  % Suppose $C$ is symmetric. We have from For $\sigma \in \sym_n$ let $\pi \in
+  % \aut(C)$ be an extension of $\sigma$. It can be shown that $\pi$ preserves
+  % $\equiv$, and hence we can define $\pi /_{\equiv}$. We note that each gate
+  % that is either an input or output gate is a member of a singleton
+  % equivalence
+  % class. Moreover, if $g$ is an internal gate then $\pi /_{\equiv} L
+  % /_{\equiv}([g]) (x) = [\pi L(g) (x)] = [L(\pi g) (\lambda x)] = L([\pi g])
+  % (\lambda x) = L(\pi /_{\equiv} [g]) (\lambda x)$ for some $\lambda \in
+  % \aut(g)$. It follows that $\pi /_{\equiv}$ is an automorphism of
+  % $C_{\equiv}$
+  % extending $\sigma$, and so $C_{\equiv}$ is symmetric.
+
+  % are each members of singleton equivalence classes $\pi /_{\equiv}$ is an
+  % automorphism of $C /_{\equiv}$ extending We first define a circuit $C''$ by
+  % quotienting $C$ by the syntactic-equivalence relation. Let $H_1, \ldots,
+  % H_q$
+  % be the syntactic-equivalence classes of $C$, and let $H_i = \{h^i_1, \ldots
+  % h^i_{\vert H_i \vert}\}$ for all $i \in [q]$. We now define a circuit $C''$.
+  % Let $G'' := G \setminus (\bigcup_{i \in [q]} (H_i \setminus \{h^i_1\}))$. We
+  % notice that each input and output gate in $C$ is in a singleton
+  % syntactic-equivalence class. Let $\Omega'' := \Omega$ and $\Lambda'' :=
+  % \Lambda$. Let $\Sigma'' (g) = \restr{\Sigma}{G''}$. For all $g \in G''$ and
+  % $x
+  % \in \ind(g)$, if $L(g)(x) \in H_i$ for some $i \in [q]$ then let $L''(g) =
+  % h^i_1$. Let $C'' := \langle G'', \Omega'', \Sigma'', \Lambda'', L''
+  % \rangle$.
+  % Notice that $C''$ is just the process
+
+  % Let $q : G \rightarrow G''$ be defined for $g \in G$ by $q(g) = g'$ if, and
+  % only if, $g'$ and $g$ are syntactical-equivalent in $C$.
+
+  % For $\sigma \in \sym_n$ let $\pi_\sigma\in \aut(C)$ be an extension of
+  % $\sigma$ and let $\pi_\sigma'': G'' \rightarrow G''$ be defined by
+  % $\pi_{\sigma}'' (g) = q(\pi_{\sigma}g))$. It can be shown that
+  % $\pi_{\sigma}''$ is an automorphism of $C''$ that extends
+
+  % Given a circuit $g$ Let $C' := \op{make-injective-all}(\op{merge-all} (C,
+  % G))$
+  % (see Definition~\ref{def:make-injective} and~\ref{def:merge-all} for the
+  % definitions of these functions). It follows that if $C$ is symmetric then
+  % $C'$
+  % is symmetric. We have from Lemma~\ref{lem:unique-labels-syntactic-equiv}
+  % that
+  % the syntactic-equivalence relation can be computed in polynomial time for
+  % transparent circuits. It follows that the construction of $C'$ from $C$ can
+  % be
+  % implemented so as to run in time polynomial in the size of $C$. Clearly
+  % every
+  % gate $g$ in $C'$ belongs to a singleton syntactic-equivalence equivalence
+  % class, and as such $C'$ has unique labels.
 \end{proof}
@@
 from Proposition~\ref{prop:transparent-unique} we may, without a loss of
-generality, restrict of attention from transparent circuits to circuits with
+generality, restrict our attention from transparent circuits to circuits with
 unique labels. The proof technique used here is similar to the one used by
@@
   Let $h$ be an internal gate in the circuit and assume we have defined $\pi
-  (g)$ for every gate $g$ of height less than $h$. Let $h'$ be a gate in the
+  (g)$ for every gate $g$ of depth less than $h$. Let $h'$ be a gate in the
   circuit such that $\Sigma(h) = \Sigma (h')$, $\pi L(h)$ is
@@
 % the graph-isomorphism problem.
+
 We have from the first subsection that a great number of useful properties are
@@
 strictly necessary for proving these results. In this subsection we present a
-number of results suggesting the importance of the transparency requirement. In
-particular, we present reductions from the graph-isomorphism problem to many
-important decision problems addressed in the first subsection (e.g. deciding if
-a circuit is symmetric, if a gate has unique labels, if two gates are
-syntactically-equivalent, of if two gates are in the same orbit).
+number of results suggesting the importance of the transparency, and unique
+labels, requirements. In particular, we present reductions from the
+graph-isomorphism problem to many important decision problems addressed in the
+first subsection (e.g. deciding if a circuit is symmetric, if a gate has unique
+labels, if two gates are syntactically-equivalent, of if two gates are in the
+same orbit).
 
@@
   Let $R$ be a relation symbol in $\rho$ and let $k := \arty(R) > 0$. Let $G_{R}
-  := \{g_{R, \vec{c}} : \vec{c} \in [n]^k\}$, $G_{\text{mid}} := \{\land_0,
-  \land_1, \neg_0, \land_{\text{out}} \}$, $G_{\rank} : = \{ g_{\rank, 1},
-  g_{\rank, 2}\}$, and $G_{\text{nodes}} := \{g_{i, (u,v)} : i \in [2] \, (u,v)
-  \in E_i \}$. Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a
+  := \{g_{R, \vec{c}} : \vec{c} \in [n]^k\}$, $G_{\text{mid}} := \{g_{\lor},
+  g_{\land}, g_{\text{out}} \}$, $G_{\rank} : = \{ g^1_{\rank}, g^2_{\rank}\}$,
+  and $G_{\text{nodes}} := \{g_{i, (u,v)} : i \in [2] \, (u,v) \in [a] \times
+  [b] \}$. Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a
   $(\{\rank^{1}_2\}, \rho)$-circuit of order $n$ defined as follows. Let $G =
@@
   the $0$-ary function $\land_{\text{out}}$. For each $\vec{c} \in
-  [n]^{\arty(R)}$ let $\Lambda(\vec{c}) = g_{R, \vec{c}}$. Define $\Sigma$ as
+  [n]^{\arty(R)}$ let $\Lambda_R(\vec{c}) = g_{R, \vec{c}}$. Define $\Sigma$ as
   follows. For each $g \in G$,
@@
   \item if $g \in G_{\text{nodes}}$ then $\Sigma(g) = \land[1]$,
-  \item if $g= \neg_0$ then $\Sigma(g) = \neg$,
-  \item if $g$ equals $\land_0$ or $\land_1$ then $\Sigma(g) = \land[n^k]$, and
+  \item if $g = \land[n^k]$, $\Sigma (g) = \land[n^k]$ and if $g = g_{\lor}$
+    then $\Sigma(g) = \lor[n^k]$, and
   \item if $g \in G_R$ then $\Sigma(g) = R$.
@@
   \item if $g = \land_{\text{out}}$ then for each $i \in [2]$, $L(g)(i) :=
-    g_{\rank, i}$,
-  \item if $g \in G_\rank$ and $g = g_{\rank, i}$ then $L(g)(p,q) = g_{i,
-      (p,q)}$,
+    g^i_{\rank}$,
+  \item if $g \in G_\rank$ and $g = g^i_{\rank}$ then for all $(p,q) \in
+    \ind(g)$, $L(g)(p,q) = g_{i, (p,q)}$,
   \item if $g \in G_{\text{nodes}}$ and $g = g_{i, (p,q)}$ then if $(p, q \in
-    E_i)$ then $L(g)(1) = \land_1$, otherwise $L(g)(1) = \neg_0$,
-  \item if $g = \neg_0$ then $L(g)(1) = \land_0$, and
-  \item if $g = \land_0$ or $g = \land_1$ then for all $p \in [n^k]$ we have
-    that $L(g)(p)$ equals $\Lambda^{-1}(\vec{c}_p)$, where $\vec{c}_p$ is the
-    $p$th element of $[n]^k$ in the lexicographical ordering on $[n]^k$.
+    E_i)$ then $L(g)(1) = g_{\land}$, otherwise $L(g)(1) = g_\lor$, and
+  \item if $g = g_\land$ or $g = g_\lor$ then for all $p \in [n^k]$ we have that
+    $L(g)(p)$ equals $\Lambda^{-1}(\vec{c}_p)$, where $\vec{c}_p$ is the $p$th
+    element of $[n]^k$ in the lexicographical ordering on $[n]^k$.
   \end{itemize}
 
-  We note that for $i \in [2]$, $L(g_{\rank, i})(p,q) = \land_1$ if, and only
-  if, $(p,q)$ is an edge in in $B_i$ and $L(g_\rank, i)(p,q) = \neg_0$ if, and
-  only if, $(p,q)$ is not an edge in $B_i$. We thus have that $B_1$ and $B_2$
-  are bipartite-isomorphic (in the sense defined above) if, and only if,
-  $g_{\rank, 1}$ is syntactically equivalent to $g_{\rank, 2}$.
+  We note that for $i \in [2]$, the child of $L(g^i_{\rank})(p,q)$ equals
+  $g_\land$ if, and only if, $(p,q)$ is an edge in in $B_i$ and the child of
+  $L(g^i_\rank)(p,q) $ equals $g_\lor$ if, and only if, $(p,q)$ is not an edge
+  in $B_i$. We thus have that $B_1$ and $B_2$ are bipartite-isomorphic (in the
+  sense defined above) if, and only if, there exists $\lambda \in \sym_{a}
+  \times \sym_{b} = \aut(g^1_{\rank}) = \aut(g^2_{\rank})$ such that for all
+  $(u,v) \in [a] \times [b] = \ind(g^1_{\rank})$, $L(g^1_{\rank})((u,v)) = g_{1,
+    (u,v)} \equiv g_{2, \lambda (u,v)} = L(g^2_{\rank})(\lambda (u,v))$. It
+  follows that $B_1$ and $B_2$ are bipartite-isomorphic if, and only if,
+  $g^1_{\rank} \equiv g^2_{\rank}$.
 
@@
   combined sizes of the input graphs, the mapping of $(B_1, B_2)$ to the tuple
-  $(C, (g_{\rank, 1}, g_{\rank, 2}))$ is a reduction, and the result follows.
+  $(C, (g^1_{\rank}, g^2_{\rank}))$ is a reduction, and the result follows.
 \end{proof}
@@
 
-We also have a reduction from the problem of computing the syntactic-equivalence
-relation to the problem of deciding if a given gate in a circuit has unique
-labels. From then transitivity of polynomial-time many-one reductions, this
-gives us a reduction from the graph-isomorphism problem to the problem of
-deciding if a gate has unique labels.
+Proposition~\ref{prop:syntactic-graph-iso} gives us that computing the the
+syntactic-equivalence for a given circuit remains hard even if we restrict
+ourselves to circuits with injective labels. In fact, every gate but the two
+rank gates (and, possibly, the output gate) have unique labels, indicating that
+even if we restrict ourselves to circuits with injective labels and such that
+each non-symmetric gates has the property that all of its input gates have
+unique labels, the syntactic-equivalence relation remains hard to compute.
+
+We now show that the syntactic-equivalence relation remains hard to compute if
+we restrict ourselves to class of circuits such that each non-symmetric gate has
+unique children.
+
+\begin{lem}
+  There is a polynomial-time reduction from the graph-isomorphism problem to the
+  problem of deciding if two gates in a given circuit with the property that
+  each non-symmetric gate has unique children are syntactically-equivalent.
+  \label{lem:syntactic-equivalence-unique-gates-hard}
+\end{lem}
+\begin{proof}
+  We use a similar approach as in Proposition~\ref{prop:syntactic-graph-iso},
+  again using the reduction from graph-isomorphism to the bipartite
+  graph-isomorphism problem.
+
+  Suppose we are given two partitioned bipartite graphs $B_1 := (U_1, V_1, E_1)$
+  and $B_2 := (U_2, V_2, E_2)$. We assume, without a loss of generality, that
+  there exists $a, b \in \nats$ such that $U_1 = U_2 = [a]$ and $V_1 = V_2 =
+  [b]$.
+
+  Let $C = \langle G, , \Omega, \Sigma, \Lambda, L \rangle$ be the circuit
+  defined in the proof of Proposition~\ref{prop:syntactic-graph-iso}. Let $C' =
+  \langle G', \Omega', \Sigma', \Lambda', L'\rangle$ be defined as follows. Let
+  $G' = G \setminus G_{\text{nodes}}$, $\Omega' = \Omega$, $\Lambda' = \Lambda$,
+  and $\Sigma' = \restr{\Sigma}{G'}$. For all $g \in G' \setminus G_{\rank}$,
+  $L'(g) = L(g)$. For $i \in [2]$ and $(p,q) \in [a] \times [b]$,
+  $L(g^i_{\rank})(p,q) = g_{\land}$ if $(p,q) \in E_i$ and $L(g^i_{\rank})(p,q)
+  = g_{\lor}$ otherwise.
+
+  We have defined $C'$ from $C$ by deleting the gates in $G_{\text{nodes}}$ and
+  for each $g \in G_{\text{nodes}}$ adding a wire directly from the child of $g$
+  in to the parent of $g$. Using an argument similar to that of
+  Proposition~\ref{prop:syntactic-graph-iso} we may then prove that $B_1$ and
+  $B_2$ are bipartite-isomorphic if, and only if, $g^1_{\rank} \equiv
+  g^2_{\rank}$. Since the construction of $C$, and so $C'$, can be implemented
+  in time polynomial in the combined sizes of the input graphs, the mapping of
+  $(B_1, B_2)$ to the tuple $(C', (g^1_{\rank}, g^2_{\rank}))$ is a reduction,
+  and the result follows.
+\end{proof}
+
+We recall that a circuit $C$ is transparent if, and only if, every non-symmetric
+gate in $C$ has injective labels and unique children. We have shown that
+computing the syntactic-equivalence relation is at least as hard as the
+graph-isomorphism problem if we restrict ourselves to either the class of
+circuits in which non-symmetric gates have injective labels
+(Proposition~\ref{prop:syntactic-graph-iso}) or the class of circuits in which
+each non-symmetric gate has unique children
+(Lemma~\ref{lem:syntactic-equivalence-equivalence-unique-gates-hard}).
+
+We now present a reduction from the problem of computing the
+syntactic-equivalence relation to the problem of deciding if a given gate in a
+circuit has unique labels. From then transitivity of polynomial-time many-one
+reductions and Proposition~\ref{prop:syntactic-graph-iso}, this gives us a
+reduction from the graph-isomorphism problem to the problem of deciding if a
+gate has unique labels.
 
@@
   g_1) \land \neg W_t(g, g_2)$, where $W_t$ is the transitive closure of the $W$
-  relation (i.e. we move all those gates in the circuit such that there is no
+  relation (i.e. we remove all those gates in the circuit such that there is no
   path from the gate to either $g_1$ or $g_2$). Let $C'$ be the circuit formed
-  from $D$ by adding in a single two-input $\AND$ gate $g'$ and connecting the
+  from $D$ by adding in a single two-input $\AND$-gate $g'$ and connecting the
   outputs of $g_1$ and $g_2$ to the inputs of $g'$. Moreover, we let this $g'$
@@
 We can construct a similar argument for reducing the problem of deciding if two
-gates are syntactically equivalent to the problem of deciding if a given gate
-$g$ in a circuit $C$ does not have \emph{unique extensions}. We say a gate $g$
-has unique extensions if there is no permutation such that two automorphisms of
-the circuit extend the permutation and disagree with each other on $g$ (i.e. $g$
-is not a counterexample to $C$ having unique extensions).
+gates are syntactically equivalent in a circuit with injective labels to the
+problem of deciding if a given gate $g$ in a circuit $C$ with injective labels
+does not have \emph{unique extensions}. We say a gate $g$ has unique extensions
+if there is no permutation such that two automorphisms of the circuit extend the
+permutation and disagree with each other on $g$ (i.e. $g$ is not a
+counterexample to $C$ having unique extensions). From then transitivity of
+polynomial-time many-one reductions and
+Proposition~\ref{prop:syntactic-graph-iso}, this gives us a reduction from the
+graph-isomorphism problem to the problem of deciding if a gate has unique
+extensions.
 
@@
   There is a polynomial-time reduction from the problem of determining if a
-  given pair of gates gates in a given $(\mathbb{B}, \rho)$-circuit are
-  syntactically-equivalent to the problem of determining if for a given pair
-  $(C, g)$, where $C$ is a circuit of order $n$, $g$ is a gate in $C$, that
-  there exists $\sigma \in \sym_n$ and automorphisms $\pi, \pi' \in \aut(C)$
-  extending $\sigma$ such that $\pi (g) \neq \pi' (g)$.
+  given pair of gates gates in a given $(\mathbb{B}, \rho)$-circuit with
+  injective labels are syntactically-equivalent to the problem of determining if
+  for a given pair $(C, g)$, where $C$ is a circuit of order $n$ with injective
+  labels, $g$ is a gate in $C$, that there exists $\sigma \in \sym_n$ and
+  automorphisms $\pi, \pi' \in \aut(C)$ extending $\sigma$ such that $\pi (g)
+  \neq \pi' (g)$.
   \label{lem:syntactically-equivilent-unique-extensions}
@@
 We now show that there is a reduction from the graph-isomorphism problem to the
-problem of deciding if a given circuit is symmetric.
+problem of deciding if a given circuit is symmetric. In fact, we prove a
+stronger result, showing that this reduction holds even if we restrict ourselves
+to the class of circuits with trivial syntactic-equivalence classes and in
+which, all but two gates in the circuit have unique labels.
 
@@
   The graph-isomorphism problem is polynomial-time reducible to the problem of
-  determining if a circuit is symmetric.
+  deciding if a circuit with trivial syntactic-equivalence classes and in which
+  all but two gates in the circuit have unique labels is symmetric.
   \label{prop:graph-iso-symmetric}
 \end{prop}
-
 \begin{proof}
@@
   Let $\rho:= \{R\}$ be a relational vocabulary, where $R$ is a unary relational
-  symbol. Fix any number $r$ and $p$ prime. We define a $(\rho, \RB)$-circuit $C
+  symbol. Fix any number $r$ and prime $p$. We define a $(\rho, \RB)$-circuit $C
   := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ of order two as follows. Let
-  $G_{R} := \{g_{R, 1}, g_{R_2}\}$ and $G_{\text{ands}} := \{\land^1_0,
-  \land^2_0, \land^1_1, \land^2_1 , \land_{\text{out}}\}$, $G_{\text{negs}} :=
-  \{,neg^1_0, \neg^2_0\}$, $G_{\rank} : = \{ g_{\rank, 1}, g_{\rank, 2}\}$, and
-  $G_{\text{nodes}} := \{g_{i, (u,v)} : i \in [2] \, (u,v) \in E_i \}$. Let $G =
-  G_R \cup G_{\text{ands}} \cup G_{\text{negs}} \cup G_{\rank} \cup
-  G_{\text{nodes}}$ and $\Omega$ be the $0$-ary function $\land_{\text{out}}$.
-  Let $\Lambda(1) := g_{R, 1}$ and $\Lambda(2) := g_{R,2}$. Define $\Sigma$ as
-  follows. For each $g \in G$,
-  \begin{itemize}
-    \setlength\itemsep{0mm}
+  $G_{R} := \{g^1_{R}, g^1_{R}\}$ and $G_{\text{mid}} := \{g^1_{\land},
+  g^2_\land, g^1_\lor, g^2_\lor , g_{\text{out}}\}$, and $G_{\rank} : = \{
+  g^1_{\rank}, g^2_{\rank}\}$. Let $G = G_R \cup G_{\text{mid}} \cup G_{\rank}$
+  and $\Omega$ be the $0$-ary function $g_{\text{out}}$. Let $\Lambda(1) :=
+  g^1_{R}$ and $\Lambda(2) := g^2_{R}$. Define $\Sigma$ as follows. For each $g
+  \in G$,
+  \begin{itemizens}
   \item if $g$ equals $\land_{\text{out}}$ then $\Sigma(g) = \land[2]$,
   \item if $g \in G_\rank$ let $\Sigma(g) = \rank^r_p [a,b]$,
-  \item if $g \in G_{\text{nodes}}$ then $\Sigma(g) = \land[1]$,
-  \item if $g \in G_{\text{ands}}$ then $\Sigma(g) = \land[1]$ and if $g \in
-    G_{\text{negs}}$ then $\Sigma(g) = \neg$, and
+  \item if $g \in G_{\text{mid}}$ and $g = g^i_s$ for $ \in [2]$ and symbol $s$
+    then $\Sigma(g) = s[1]$, and
   \item if $g \in G_R$ then $\Sigma(g) = R$.
-  \end{itemize}
+  \end{itemizens}
   Define $L$ as follows. For each $g \in G$,
-  \begin{itemize}
-    \setlength\itemsep{0mm}
-  \item if $g = g_{\text{out}}$ then for each $i \in [2]$, $L(g)(i) := g_{\rank,
-      i}$,
-  \item if $g \in G_\rank$ and $g = g_{\rank, i}$ then $L(g)(p,q) = g_{i,
-      (p,q)}$,
-  \item if $g \in G_{\text{nodes}}$ and $g = g_{i, (p,q)}$ for some $i \in [2]$,
-    then $L(g)(1) = \land^i_1$ if $(p,q) \in E_i$ and $L(g)(1) = \neg^i_0$
-    otherwise ,
-  \item if $g = \neg^i_0$ for some $i \in [2]$, then $L(g)(1) = \land^i_0$, and
-  \item if $g = \land^i_0$ or $g = \land^i_1$ for some $i \in [2]$, then
-    $L(g)(p) = \Lambda^{-1}(i)$.
-  \end{itemize}
-
-  We note that for $i \in [2]$, $L(g_{\rank, i})(p,q) = \land^i_1$ if, and only
-  if, $(p,q)$ is an edge in $B_i$ and $L(g_\rank, i)(p,q) = \neg^i_0$ if, and
-  only if, $(p,q)$ is not an edge in $B_i$. It can be shown that $C$ is
-  symmetric if, and only if, there exists an extension of the transposition
-  $(1,2)$ to an automorphism of the circuit, which holds if, and only if, there
-  exists an extension of $(1,2)$ to an automorphism of the circuit such that
-  $(1,2) (L(g_{\rank, 1}))$ is isomorphism-equivilent to $L(g_{\rank, 2})$,
-  which holds if, and only if, $B_1$ and $B_2$ are biparetite-isomorphic.
+  \begin{itemizens}
+  \item if $g = g_{\text{out}}$ then for each $i \in [2]$, $L(g)(i) :=
+    g^i_{\rank}$,
+  \item if $g \in G_\rank$ and $g = g^i_{\rank}$ for some $i \in [2]$ then for
+    $(p,q) \in [a]\times [b]$, $L(g)(p,q) = g^i_\land$ if $(p,q) \in E_i$ and
+    $L(g)(p,q) = g^i_\lor$ otherwise, and
+  \item if $g = g^i_\land$ or $g = g^i_{\lor}$ for some $i \in [2]$, then
+    $L(g)(1) = \Lambda^{-1}(i)$.
+  \end{itemizens}
+
+  We note that for $i \in [2]$, $L(g^i_{\rank})(p,q)= g^i_\land$ if, and only
+  if, $(p,q)$ is an edge in $B_i$ and $L(g^i_{\rank})(p,q) g^i_\lor$ if, and
+  only if, $(p,q)$ is not an edge in $B_i$. Let $\pi_{(1,2)} : G \rightarrow G$
+  that fixes the output gate, and swaps each gate $g^1_s$, for some symbol $s$,
+  with the gate $g^1_s$. It is easy to see that $\pi_{(1,2)}$ is a bijection.
+  Moreover, $C$ is symmetric if, and only if, $\pi_{(1,2)}$ is an automorphism
+  of the circuit extending the transposition $(1,2)$, if and only if, $(1,2)
+  (L(g^1_{\rank}))$ is isomorphism-equivalent to $L(g^2_{\rank})$ if, and only
+  if, $B_1$ and $B_2$ are bipartite-isomorphic.
+
+  % Let
+  % $G_{R} := \{g_{R, 1}, g_{R_2}\}$ and $G_{\text{mid}} := \{g^1_{\land},
+  % g^2_\land, g^1_\lor, g^2_\lor , \land_{\text{out}}\}$, $G_{\rank} : = \{
+  % g_{\rank, 1}, g_{\rank, 2}\}$, and $G_{\text{nodes}} := \{g_{i, (u,v)} : i
+  % \in
+  % [2] \, (u,v) \in [a] times [b] \}$. Let $G = G_R \cup G_{\text{mid}} \cup
+  % G_{\rank} \cup G_{\text{nodes}}$ and $\Omega$ be the $0$-ary function
+  % $\land_{\text{out}}$. Let $\Lambda(1) := g_{R, 1}$ and $\Lambda(2) :=
+  % g_{R,2}$. Define $\Sigma$ as follows. For each $g \in G$,
+  % \begin{itemize}
+  %   \setlength\itemsep{0mm}
+  % \item if $g$ equals $\land_{\text{out}}$ then $\Sigma(g) = \land[2]$,
+  % \item if $g \in G_\rank$ let $\Sigma(g) = \rank^r_p [a,b]$,
+  % \item if $g \in G_{\text{nodes}}$ then $\Sigma(g) = \land[1]$,
+  % \item if $g \in G_{\text{mid}}$ and $g = g^i_s$ for $ \in [2]$ and symbol
+  %   $s$
+  %   then $\Sigma(g) = s[1]$, and
+  % \item if $g \in G_R$ then $\Sigma(g) = R$.
+  % \end{itemize}
+  % Define $L$ as follows. For each $g \in G$,
+  % \begin{itemize}
+  %   \setlength\itemsep{0mm}
+  % \item if $g = g_{\text{out}}$ then for each $i \in [2]$, $L(g)(i) :=
+  %   g_{\rank,
+  %   i}$,
+  % \item if $g \in G_\rank$ and $g = g_{\rank, i}$ then $L(g)(p,q) = g_{i,
+  %   (p,q)}$,
+  % \item if $g \in G_{\text{nodes}}$ and $g = g_{i, (p,q)}$ for some $i \in
+  %   [2]$,
+  %   then $L(g)(1) = g^i_\land$ if $(p,q) \in E_i$ and $L(g)(1) = g^i_\lor$
+  %   otherwise , and
+  % \item if $g = g^i_\land$ or $g = g^i_{\lor}$ for some $i \in [2]$, then
+  %   $L(g)(1) = \Lambda^{-1}(i)$.
+  % \end{itemize}
+
+  % We note that for $i \in [2]$, the child of $L(g_{\rank, i})(p,q)$ equals
+  % $g^i_\land$ if, and only if, $(p,q)$ is an edge in $B_i$ and the child of
+  % $L(g_{\rank, i})(p,q)$ equals $g^i_\lor$ if, and only if, $(p,q)$ is not an
+  % edge in $B_i$. It can be shown that $C$ is symmetric if, and only if, there
+  % exists an extension of the transposition $(1,2)$ to an automorphism of the
+  % circuit, which holds if, and only if, there exists an extension of $(1,2)$
+  % to
+  % an automorphism of the circuit such that $(1,2) (L(g_{\rank, 1}))$ is
+  % isomorphism-equivalent to $L(g_{\rank, 2})$, which holds if, and only if,
+  % $B_1$ and $B_2$ are bipartite-isomorphic.
 
@@
   % is syntactically-equivalent to $g_{\rank, 2}$.
-
-  Since the construction of $C$ can be implemented in time polynomial in the
-  combined sizes of the input graphs, the mapping of $(B_1, B_2)$ to $C$ is a
-  reduction, and the result follows.
+  It is easy to see that all gates in the circuit are part of a singleton
+  syntactic-equivalence class and that all gates have unique labels except for
+  the two rank gates. Since the construction of $C$ can be implemented in time
+  polynomial in the combined sizes of the input graphs, the mapping of $(B_1,
+  B_2)$ to $C$ is a reduction, and the result follows.
 \end{proof}
+
+Note that, in Proposition~\ref{prop:graph-iso-symmetric} we again have a
+hardness result for deciding a basic circuit property even if we restrict
+ourselves to circuits with trivial syntactic-equivalence classes (and so ones
+where each gate has unique children). It is possible to alter this reduction,
+using a construction analogous to the one used in the proof of
+Proposition~\ref{prop:syntactic-graph-iso}, to prove that deciding symmetry is
+also hard for circuits with injective labels. In contrast, we have from
+Proposition~\ref{lem:computing-support-orbit-index} that we can decide symmetry
+for transparent circuits (i.e. circuits where every non-symmetric gate has
+unique children and injective labels) in polynomial-time. These observations
+again suggest both the robustness of this hardness result, and the importance of
+the transparency condition.
 
@@
 \begin{proof}
-  Let $C$ be a circuit. Let $g_1$ and $g_2$ be two gates in $C$ such that
-  $H_{g_1} = H_{g_2}$. Then there exists $\pi \in \aut(C)$ such that $\pi (g_1)
-  = g_2$ if, and only if, $g_1$ is syntactically-equivalent to $g_2$. As such,
-  we may use the same construction as in
-  Proposition~\ref{prop:syntactic-graph-iso} to prove this result.
+  Let $C$ be the circuit constructed in
+  Proposition~\ref{prop:syntactic-graph-iso}. We again make use of the reduction
+  from the graph isomorphism problem to the problem of deciding if two bipartite
+  graphs are bipartite-isomorphic. Let $B_1$ and $B_2$ be two bipartite graphs.
+  The mapping $(B_1, B_2)$ of to $(C, g^1_{\rank}, g^2_{\rank})$ is a reduction.
 \end{proof}
+
 We have from Propositions~\ref{prop:syntactic-graph-iso}
@@
 graph-isomorphism problem. In contrast, all of these properties are known to be
-polynomial-time computable for transparent circuits (as follows from
+polynomial-time decidable for transparent circuits (as follows from
 Lemmas~\ref{lem:unique-labels-syntactic-equiv}
@@
 
-  The height of a gate $g$ in the circuit is the distance from $g$ to the set of
-  input gates. For each $p \in \nats$ let $G^p \subseteq G$ be the set of all
-  gates of height $p$ and let $G^{\leq p} = \bigcup_{0 \leq i \leq p}G^i$. Note
+  For each $p \in \nats$ let $G^p \subseteq G$ be the set of all
+  gates of depth $p$ and let $G^{\leq p} = \bigcup_{0 \leq i \leq p}G^i$. Note
   that each $g \in G^1$, $g$ has unique labels. Thus, from
-  Lemma~\ref{lem:unique-labels-syntactic-equiv}, we can compute the syntactic
+  Lemma~\ref{lem:transparent-syntactic-equiv}, we can compute the syntactic
   equivalence relation between gates in $G^{\leq 1}$ efficiently. We construct a
@@
   gate in $G^{\leq p}$ has unique labels. Thus, from Proposition
-  \ref{prop:unique-labels-syntactic-equiv}, we may compute the
+  \ref{lem:transparent-syntactic-equiv}, we may compute the
   syntactic-equivalence relation on this set of gates efficiently. It follows
@@
 \begin{proof}
-  Let $C$ be the input circuit. From Proposition
-  \ref{prop:transparent-polynomial-time} we may check if $C$ is transparent in
-  polynomial time. If $C$ is not transparent halt and output that $C$ does not
-  have unique labels. If $C$ is transparent then from Lemma \ref{} we may
-  compute the syntactice-equivalence relation on the gates of $C$ efficiently.
-  This then allows us to check if each gate in $C$ has unique labels.
+  Let $C$ be the input circuit. From
+  Proposition~\ref{prop:transparent-polynomial-time} we may check if $C$ is
+  transparent in time polynomial in the size of $C$. If $C$ is not transparent
+  halt and output that $C$ does not have unique labels. If $C$ is transparent
+  then from Lemma~\ref{lem:transparent-syntactic-equiv} we may compute the
+  syntactic-equivalence relation on the gates of $C$ in time polynomial in the
+  size of $C$. Note that $C$ has unique labels if, and only if, for each gate
+  $g$ in $C$, $\vert \ind(g) \vert = \vert H_g /_\equiv \vert$. We may thus
+  check if $C$ has unique labels by iterating through the gates of $C$. This can
+  be done in time polynomial in the size of $C$.
 \end{proof}
@@
 \begin{proof}
-  We use a similar argument as for Proposition \ref{prop:syntactic-graph-iso}.
-  We again argue using a reduction from thee bipartite isomorphism problem. Let
-  $B_1 := (U_1, V_1, E_1)$ and $B_2 := (U_2, V_2, E_2)$ and let $C$ be the
-  associated circuit defined in the proof of Proposition
-  \ref{prop:syntactic-graph-iso}. Let $C' = \op{merge-all} (C, G_{\land})$.
-  Notice that $B_1$ and $B_2$ are isomorphic if, and only if, $g_{\rank, 1}$ and
-  $g_{\rank, 2}$ are syntactically equivalent, which holds if, and only if,
-  there exists $\pi \in \aut(C')$ extending the trivial permutation such that
-  $\pi (g_{\rank, 1}) = g_{\rank, 2}$, which is true if, and only if, $C'$ does
-  not have unique extensions. it follows that the mapping of $(B_1, B_2)$ to
-  $C'$ defines a reduction.
+  We use a similar approach as in Proposition~\ref{prop:syntactic-graph-iso},
+  again arguing using a reduction from the graph-isomorphism problem to
+  bipartite-graph isomorphism problem. Suppose we are given two partitioned
+  bipartite graphs $B_1 := (U_1, V_1, E_1)$ and $B_2 := (U_2, V_2, E_2)$. We
+  assume, without a loss of generality, that there exists $a, b \in \nats$ such
+  that $U_1 = U_2 = [a]$ and $V_1 = V_2 = [b]$.
+
+  Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\RB,
+  \{R\})$-circuit of order one defined as follows. Let $G_R := \{g_R\}$, $G_1 :=
+  \{ g_{\lor}, g_{\land} \}$, $G_{\rank} := \{ g^1_{\rank}, g^2_{\rank} \}$ and
+  $G = G_R \cup G_1 \cup G_1 \cup G_{\rank} \cup \{ g_{\text{out}} \}$. Let
+  $\Omega = g_{\text{out}}$ an $\Lambda_R (g_R) = 1$. Let $\Sigma (g_R) = R$,
+  $\Sigma (g_\lor) = \lor[1]$, $\Sigma (g_\land) = \land[1]$, $\Sigma
+  (g_{\text{out}}) = \land[2]$ and for all $g \in G_{\rank}$, $\Sigma (g) =
+  \land[a,b]$. Let $L(g_\lor)(1) L(g_\land)(1) = g_R$, for all $i \in [2]$,
+  $L(g_{\text{out}})(i) = g^i_{\rank}$ and for all $(u, v) \in \ind(g)$,
+  $L(g^i_{\rank})(u,v) = g_{\land}$ if $(u, v) \in E_i$ and $L(g^i_{\rank} (u,v)
+  = g_{\lor}$ otherwise.
+
+  Suppose $B_1$ and $B_2$ are bipartite-isomorphic. Then there exists $\lambda
+  \in [a] \times [b]$ such that $(u,v) \in E_1$ if, and only if, $\lambda (u,v)
+  \in E_2$. It follows that $L(g^1_{\rank})((u,v)) =
+  L(g^2_{\rank})(\lambda(u,v))$. Let $\pi_{\lambda}: G \rightarrow G$ be defined
+  such that if $g = g^i_{\rank}$ for $i \in [2]$, $\pi_{\lambda} g =
+  g^j_{\rank}$ where $j \in [2] \setminus \{i\}$ and otherwise $\pi_{\lambda} g
+  = g$. It is easy to see that $\pi_{\lambda}$ is a bijection. Moveover, for
+  $(u,v) \in \sym_a \times \sym_b$ $\pi_{\lambda} L(g^1_{\rank})((u,v)) =
+  L(g^2_{\rank})(\lambda (u,v)) = L(\pi_\lambda g^1_{\rank})(\lambda (u,v))$.
+  Similarly, $\pi_\lambda L(g^2_{\rank})((u,v)) =
+  L(\pi_{\lambda}g^2_{\rank})(\lambda^{-1}(u,v))$. It follows that $\pi_\lambda$
+  is a non-trivial automorphism of $C$ extending the trivial permutation, and so
+  $C$ does not have unique extensions.
+
+  Suppose $C$ does not have unique extensions. Then there exists an automorphism
+  $\pi$ of the circuit extending the trivial permutation such that $\pi
+  g^1_{\rank} = g^2_{\rank}$. But then there exists $\lambda \in \sym_a \times
+  \sym_b$ such that for all $(u,v) \in [a]\times [b]$, $\pi
+  L(g^1_{\rank})((u,v)) = L(g^1_{\rank})((u,v)) = L(g^2_{\rank})(\lambda
+  (u,v))$. But then $(u,v) \in E_1$ if, and only if, $L(g^1_{\rank})((u,v)) =
+  g_{\land}$, if and only if, $L(g^2_{\rank})(\lambda(u,v)) = g_{\land}$ if, and
+  only if, $\lambda (u,v) \in E_2$. It follows $B_1$ and $B_2$ are
+  bipartite-isomorphic.
 \end{proof}
+
+% \begin{proof}
+%   We use a similar argument as for Proposition~\ref{prop:syntactic-graph-iso}.
+%   We again argue using a reduction from the bipartite isomorphism problem. Let
+%   $B_1 := (U_1, V_1, E_1)$ and $B_2 := (U_2, V_2, E_2)$, and let $C = \langle
+%   G, \Omega, \Sigma, \Lambda, L\rangle$ be the associated circuit defined in
+%   the proof of Proposition~\ref{prop:syntactic-graph-iso}. We recall that we
+%   may assume, without a loss of generality, that there exists $a, b \in \nats$
+%   such that $[a] = U_1 = U_2$ and $[b] = V_1 = V_2$ and $B_1$ and $B_2$ are
+%   not identical. Recall that $B_1$ and $B_2$ are bipartite-isomorphic if, and
+%   only if, there exists $\lambda \in \sym_{a} \times \sym_{b} = \aut(g_{\rank,
+%   1}) = \aut(g_{\rank, 2})$ such that for all $(u,v) \in [a] \times [b] =
+%   \ind(g_{\rank, 1})$, $L(g_{\rank_,1})((u,v)) = g_{1, (u,v)} \equiv g_{2,
+%   \lambda (u,v)} = L(g_{\rank, 2})(\lambda (u,v))$.
+
+%   Suppose $B_1$ and $B_2$ are bipartite-isomorphic. Then there exists $\lambda
+%   \in \sym_{a} \times \sym_b$ be such that for all $(u,v) \in [a] \times [b]$,
+%   $L(g_{\rank_,1})((u,v)) \equiv L(g_{\rank, 2})(\lambda (u,v))$. Let
+%   $\pi_\lambda : G \rightarrow G$ be defined as follows. Let $g \in G$. If $g
+%   \not\in G_{\rank} \cup G_{nodes}$ let $\pi_\lambda g = g$. If $g \in
+%   G_{nodes}$ then $g = g_{i, (u,v)}$ for some $i \in [2]$ and $(u,v) \in [a]
+%   \times [b]$, and let $\pi_{\lambda} g = g_{j, \lambda (u,v)}$, where $\{i,
+%   j\} = [2]$. If $g \in G_{\rank}$ then $g = g_{\rank, i}$ for some $i \in
+%   [2]$, and let $\pi_\lambda g = g_{\rank, j}$, where $\{i, j\} = [2]$. It is
+%   easy to see that $\pi_\lambda$ is a bijection and $\pi_\lambda$ fixes the
+%   input gates. Moreover, for $i, j \in [2]$ distinct, $(u,v) \in
+%   \ind(g_{\rank, i})$, $\pi_\lambda L(g_{\rank, i}))((u,v)) = \pi_\lambda
+%   g_{i, (u,v)} = g_{j, \lambda (u,v)} = L( \pi_\lambda g_{\rank, i})(\lambda
+%   (u,v))$. It follows that $\pi_\lambda$ is an automorphism of $C$ extending
+%   the trivial permutation. Moreover, if $\lambda$ is not the identity
+%   automorphism then $\pi_\lambda$ is not the identity automorphism, and so $C$
+%   does not have unique extensions.
+
+%   It $C$ does not have unique extensions then there is no permutation that
+%   maps $g_{\rank, 1}$ to $g_{\rank, 2}$. In other words there exists
+
+%   there exists $\lambda \in \sym_{a} \times \sym_{b} = \aut(g_{\rank, 1})$
+%   such that for all $(u,v) \in \ind(g_{\rank, 1})$, $g_{1,
+%   (u,v)}L(g_{\rank_,1})(x) = L(g_{\rank, 2})(\lambda x) = g_{2, \lambda
+%   (u,v)}$.
+
+%   if, and only if, $g_{\rank, 1}$ and $g_{\rank, 2}$ are
+%   syntactically-equivalent. If $g_{\rank,1}$ and $g_{\rank, 2}$ are
+%   syntactically-equivalent then there exists $\lambda \in \aut(g_{\rank,1})$
+%   such that $L(g_{\rank, 1})(\lambda x) \equiv L(g_{\rank, 2})(x)$. We can
+%   define an automorphism $\pi : G \rightarrow G$ such that for $g \in G$, $\pi
+%   (g) = g$ if $g$ is an input gate, $\pi g_{\rank, 1} = g_{\rank, 2}$ and $\pi
+%   g_{\rank, 2} = g_{\rank, 1}$ and
+
+%   Since Both $g_{\rank, 1}$ and $g_{\rank, 2}$ have unique labels.
+
+%   Let $C'$ be a quotient of $C$.
+
+%   which holds if, and only if, there exists $\pi \in \aut(C')$ extending the
+%   trivial permutation such that $\pi (g_{\rank, 1}) = g_{\rank, 2}$, which is
+%   true if, and only if, $C'$ does not have unique extensions. it follows that
+%   the mapping of $(B_1, B_2)$ to $C'$ defines a reduction.
+% \end{proof}
 

### 2018-03-01 sections/introduction.tex
A complete draft minus the conclusion. Large changes made to a number of sections.

@@
 
-It is important to clarify at the outset what is meant by symmetric
-circuits.  Indeed, there are different senses in which the word
-\emph{symmetry} is used in the context of circuits (and also in this
-paper).  We say that a Boolean function $f:\{0,1\}^n \ra \{0,1\}$ is
-symmetric if the value of the function on a string $s$ is determined
-by the number of $1$s in $s$.  In other words, $f$ is invariant under
-\emph{all} permutations of its input.  In contrast, when we consider
-the input to a Boolean function to be the adjacency matrix of an
-$n$-vertex graph, for example, and
-$f : \{0,1\}^{n \choose 2} \ra \{0,1\}$ decides a graph property, then
-$f$ is invariant under all permutations of its input induced by
-permutations of the $n$ vertices of the graph.  We call such a
-function \emph{graph-invariant}.  More generally, for a relational
-vocabulary $\tau$ and a standard encoding of $n$-element
-$\tau$-structures as strings over $\{0,1\}$, we can say that function
-taking such strings as input is $\tau$-invariant if it is invariant
-under permutations induced by the $n$ elements.
-A circuit $C$ computing such an invariant function is said to be \emph{symmetric} if every
-permutation of the $n$ elements extends to an automorphism of $C$.  It
-is families of symmetric circuits in this sense that characterize
-$\FPC$ in~\cite{AndersonD17}.  The restriction to symmetric circuits
-arises naturally in the study of logics and has appeared previously
-under the names of generic circuits in the work
-of~\cite{DENENBERG1986216} and explicitly order-invariant circuits in
-the work of Otto~\cite{Otto1997}.
+It is important to clarify at the outset what is meant by symmetric circuits.
+Indeed, there are different senses in which the word \emph{symmetry} is used in
+the context of circuits (and also in this paper). We say that a Boolean function
+$f:\{0,1\}^n \ra \{0,1\}$ is symmetric if the value of the function on a string
+$s$ is determined by the number of $1$s in $s$. In other words, $f$ is invariant
+under \emph{all} permutations of its input. In contrast, when we consider the
+input to a Boolean function to be the adjacency matrix of an $n$-vertex graph,
+for example, and $f : \{0,1\}^{n \choose 2} \ra \{0,1\}$ decides a graph
+property, then $f$ is invariant under all permutations of its input induced by
+permutations of the $n$ vertices of the graph. We call such a function
+\emph{graph-invariant}. More generally, for a relational vocabulary $\tau$ and a
+standard encoding of $n$-element $\tau$-structures as strings over $\{0,1\}$, we
+can say that function taking such strings as input is $\tau$-invariant if it is
+invariant under permutations induced by the $n$ elements. A circuit $C$
+computing such an invariant function is said to be \emph{symmetric} if every
+permutation of the $n$ elements extends to an automorphism of $C$. It is
+families of symmetric circuits in this sense that characterize $\FPC$
+in~\cite{AndersonD17}. The restriction to symmetric circuits arises naturally in
+the study of logics and has appeared previously under the names of generic
+circuits in the work of~\cite{DENENBERG1986216} and explicitly order-invariant
+circuits in the work of Otto~\cite{Otto1997}.
 
@@
 the characterization.
+
+\begin{remark}
+G: Should we also talk about the fact that the work done in
+Section~\ref{sec:circuits-to-formulas} is also novel?
+\end{remark}
 

### 2018-03-01 sections/symmetric-circuits.tex
A complete draft minus the conclusion. Large changes made to a number of sections.

@@
 bases. While we should like to construct an analogous argument, we show in
-Section~\ref{sec:transparency-and-unique-extension} that for circuits that
-include gates computing non-symmetric functions most of these important circuit
-properties are at least as hard to decide as the graph-isomorphism problem. As
-such, constructing an analogous translation, as well as establishing the
-numerous other needed results whose proofs rely on certain properties being
-polynomial-time decidable, would be non-trivial.
+Section~\ref{sec:transparent} that for circuits that include gates computing
+non-symmetric functions most of these important circuit properties are at least
+as hard to decide as the graph-isomorphism problem. As such, constructing an
+analogous translation, as well as establishing the numerous other needed results
+whose proofs rely on certain properties being polynomial-time decidable, would
+be non-trivial.
 
@@
 into the circuit. We call these circuits \emph{transparent} circuits. We show in
-Sections~\ref{sec:transparency-and-unique-extensions} that transparency is
-sufficient to allow for the polynomial-time decidability of many important
-circuit properties, while still keeping the circuit model powerful enough for us
-to establish a translation from formulas to families of circuits.
+Sections~\ref{sec:transparent} that transparency is sufficient to allow for the
+polynomial-time decidability of many important circuit properties, while still
+keeping the circuit model powerful enough for us to establish a translation from
+formulas to families of circuits.
 
@@
 We note that the construction of $C'$ from $C$ in
-Lemma~\ref{lem:redundant-gates} can be implemented so as to run in time
-polynomial in the size of $C$. As such, for the remainder of this paper we
+Lemma~\ref{lem:redundant-gates} can be implemented by an algorithm that runs in
+time polynomial in the size of $C$. As such, for the remainder of this paper we
 assume, unless stated otherwise, every circuit has no redundant gates. With this
@@
 $C$ is of order $n$ then for each $\sigma \in \sym_n$ there exists at most one
-$\pi_\sigma \in \aut(C)$ extending $\sigma$. However, if $g$ is a gate in $C$
-and $\pi_{\sigma} g = g'$ there may no `canonical' $\lambda \in \aut(g)$
-witnessing the isomorphism-equivalence, i.e.\ such that $\pi L(g) = L(g')
-\lambda$. It is this lack of a `canonical' choice that allows us to prove in
-Section~\ref{sec:transparency-and-unique-extensions} that a great many important
-circuit properties (e.g. the orbit of a gate, symmetry of a circuit, etc.) for
-circuits with unique gates are at least as hard as the graph-isomorphism problem
-to decide.
+$\pi_\sigma \in \aut(C)$ extending $\sigma$. This means that if $C$ is symmetric
+for each $\sigma \in \sym_n$ there is always a canonical automorphism
+$\pi_\sigma$ extending $\sigma$. However, for a gate $g$ in $C$ there may no
+canonical $\lambda \in \aut(g)$ witnessing the validity of the mapping from $g$
+to $\pi_\sigma g$, i.e.\ such that $\pi L(g) = L(g') \lambda$. We prove in
+Section~\ref{sec:transparent} that in fact, for the class of circuits with
+unique children, deciding if there is an isomorphism-equivalence between two
+gates is as hard as the graph-isomorphism problem. It follows that a great many
+important circuit properties (e.g. the orbit of a gate, symmetry of a circuit,
+etc.) for circuits with unique gates are at the very least not obviously
+polynomial-time decidable.
 
 In contrast, it is easy to see that if $C$ has unique labels, and $g$ and $g'$
-are gates in the circuit, then $L(g)$ and $L(g')$ are isomorphism-equivalent if,
-and only if, $\lambda := L(g')^{-1}L(g)$ is in $\aut(g)$. We show in
-Section~\ref{sec:transparency-and-unique-extensions} all of the circuit
-properties of interest in this paper are polynomial-time decidable for circuits
-with unique labels. Moreover, we show in
-Proposition~\ref{prop:transparent-unique} that a transparent circuit can be
-converted into an equivalent circuit with unique labels in time polynomial in
-the size of the circuit. Since we are working with $P$-uniform families of
-transparent circuits, this fact allows us to assume, without a loss of
-generality, that transparent circuits have unique labels (and, from
-\ref{prop:unique-children-unique-extensions} so unique extensions).
+are gates in the circuit $C$, then $L(g)$ and $L(g')$ are isomorphism-equivalent
+if, and only if, $\lambda := L(g')^{-1}L(g)$ is in $\aut(g)$. In this case,
+rather than having to decide the isomorphism problem we simply need to check if a given
+candidate is in fact a valid isomorphism. We prove in
+Section~\ref{sec:transparent} that all of the circuit properties of interest in
+this paper are polynomial-time decidable for circuits with unique labels.
+Moreover, we show in Lemma~\ref{lem:transparent-unique} that a
+transparent circuit can be converted into an equivalent circuit with unique
+labels in time polynomial in the size of the circuit. Since we are working with
+$P$-uniform families of transparent circuits, this fact allows us to assume,
+without a loss of generality, that transparent circuits have unique labels (and,
+from \ref{prop:unique-children-unique-extensions} so unique extensions).
 
@@
   by a member of $\mathbb{B}$ we have a symmetric circuit $C_g$ from
-  Proposition~\ref{prop:function-maj} that computes the same function as $g$.
+  Proposition~\ref{prop:fuctions-maj} that computes the same function as $g$.
   Then let $C_n'$ be as $C_n$ but with each gate $g \in C_n$ replaced by $C_g$.
@@
 well. As such, we cannot extend the power of the $P$-uniform symmetric circuits
-families studied by Anderson and Dawar \cite{AndersonD17} by simply considering
+families studied by Anderson and Dawar~\cite{AndersonD17} by simply considering
 alternative bases of symmetric functions, thus motivating the generalisation

### 2018-03-01 sections/transparency-and-unique-extensions.tex
A complete draft minus the conclusion. Large changes made to a number of sections.

@@
   relation on $G$ by induction on the depth of a gate We note that this
-  definition by induction can be implemented as a construction using a dynamic program.
+  definition by induction can be implemented as a construction using a dynamic
+  program.
 
@@
   gates and suppose we have defined the syntactic-equivalence relation for all
-  gates of depth less than the depth of either $g$ or $h$. Then $g \equiv h$
-  if, and only if, $L(g)$ and $L(h)$ are isomorphism equivalent up to $\equiv$.
+  gates of depth less than the depth of either $g$ or $h$. Then $g \equiv h$ if,
+  and only if, $L(g)$ and $L(h)$ are isomorphism equivalent up to $\equiv$.
 
@@
   there exists $g' \in [g]$ such that $L_\equiv ([g]) = L(g') /_\equiv$ and
-  $\Sigma_\equiv([g]) = \Sigma (g) = \Sigma (g')$. We have from Lemma~\ref{} and
-  the inductive hypothesis that there exists $\lambda \in \aut(g)$ such that
-  $L_\equiv ([g]) = L(g') = L(g) \lambda$. It follows from the fact that
-  $\Sigma(g)$ is a structured function that $C_\equiv[\gamma \mathcal{A}]([g]) =
-  \Sigma_\equiv ([g])(L^{\gamma \mathcal{A}}_\equiv([g])) = \Sigma (g')
-  (L^{\gamma \mathcal{A}}(g')) = \Sigma (g)(L^{\gamma \mathcal{A}}(g) \lambda) =
-  \Sigma (g) (L^{\gamma \mathcal{A}}(g)) = C[\gamma \mathcal{A}](g)$.
+  $\Sigma_\equiv([g]) = \Sigma (g) = \Sigma (g')$. We have from
+  Lemma~\ref{lem:syntactic-equivalence-equal-function} and the inductive
+  hypothesis that there exists $\lambda \in \aut(g)$ such that $L_\equiv ([g]) =
+  L(g') = L(g) \lambda$. It follows from the fact that $\Sigma(g)$ is a
+  structured function that $C_\equiv[\gamma \mathcal{A}]([g]) = \Sigma_\equiv
+  ([g])(L^{\gamma \mathcal{A}}_\equiv([g])) = \Sigma (g') (L^{\gamma
+    \mathcal{A}}(g')) = \Sigma (g)(L^{\gamma \mathcal{A}}(g) \lambda) = \Sigma
+  (g) (L^{\gamma \mathcal{A}}(g)) = C[\gamma \mathcal{A}](g)$.
 
@@
 equivalent circuit with unique labels, and hence unique extensions (see
-Lemma~\ref{}), and that this transformation preserves important properties of
+Proposition~\ref{prop:unique-children-unique-extensions}), and that this transformation preserves important properties of
 the circuit.
@@
 of a circuit of order $n$ with unique labels in polynomial time. Recall that
-from Proposition~\ref{prop:transparent-unique} we may, without a loss of
+from Lemma~\ref{lem:transparent-unique} we may, without a loss of
 generality, restrict our attention from transparent circuits to circuits with
@@
   \Omega^{-1}(h')$. If equality holds set $\pi(h) = h'$, otherwise halt and
-  output that no automorphism exists. We have from Lemma~\ref{} that there is at
+  output that no automorphism exists. We have from
+  Proposition~\ref{prop:unique-children-unique-extensions} that there is at
   most one gate $h'$ that meets the above criteria, and so $\pi(h)$ is well
@@
 labels in polynomial time, and that circuits with unique labels have unique
-extensions (see Proposition~\ref{}). Moreover, we have similarly shown that, for
+extensions (see Proposition~\ref{prop:unique-children-unique-extensions}). Moreover, we have similarly shown that, for
 transparent circuits, the action of a permutation, as well as the coarsest
@@
   follows. For each $g \in G$,
-  \begin{itemize}
+  \begin{itemizens}
     \setlength\itemsep{0mm}
@@
   \item if $g \in G_R$ then $\Sigma(g) = R$.
-  \end{itemize}
+  \end{itemizens}
   Define $L$ as follows. For each $g \in G$,
-  \begin{itemize}
+  \begin{itemizens}
     \setlength\itemsep{0mm}
@@
     element of $[n]^k$ in the lexicographical ordering on $[n]^k$.
-  \end{itemize}
+  \end{itemizens}
 
@@
 each non-symmetric gate has unique children
-(Lemma~\ref{lem:syntactic-equivalence-equivalence-unique-gates-hard}).
+(Lemma~\ref{lem:syntactic-equivalence-unique-gates-hard}).
 
@@
 polynomial-time decidable for transparent circuits (as follows from
-Lemmas~\ref{lem:unique-labels-syntactic-equiv}
+Lemmas~\ref{lem:transparent-syntactic-equiv}
 and~\ref{lem:computing-support-orbit-gate}).

### 2018-03-04 sections/background.tex
I have made changes to the section "symmetric circuits" and updated every other section in line with changes made.

@@
 \subsection{Boolean Functions, Bases, and Circuits}
-A \emph{Boolean function} is a function of the form $f: \{0,1\}^X \rightarrow
-\{0,1\}$, for some finite index set $X$. We call a Boolean function $f:
-\{0,1\}^X \rightarrow \{0,1\}$ \emph{symmetric} if for all $\sigma \in \sym_X$
-and $\vec{a} \in \{0,1\}^X$, $f (\vec{a} \sigma) = f(\vec{a})$. It follows that
-a Boolean function is symmetric if, and only if, the output of the function is
-entirely determined by the number of ones in the input. We say a function $f :
-\{0,1\}^{*} \rightarrow \{0,1\}$ is \emph{symmetric} if its restriction to
-inputs of size $n$ is symmetric for all $n$.
+A (finite) \emph{Boolean function} is a function of the form $f: \{0,1\}^X
+\rightarrow \{0,1\}$, for some finite index set $X$. We call a Boolean function
+$f: \{0,1\}^X \rightarrow \{0,1\}$ \emph{symmetric} if for all $\sigma \in
+\sym_X$ and $\vec{a} \in \{0,1\}^X$, $f (\vec{a} \sigma) = f(\vec{a})$. It
+follows that a Boolean function is symmetric if, and only if, the output of the
+function is entirely determined by the number of ones in the input. We say a
+Boolean function $f : \{0,1\}^{*} \rightarrow \{0,1\}$ is \emph{symmetric} if
+its restriction to inputs of size $n$ is symmetric for all $n$.
 
-A \emph{Boolean basis} (or \emph{basis}) is a set of Boolean functions. We
-always denote a basis by $\BB$. It is common in the literature to define a basis
-using a finite sequence of functions $f_1, \ldots , f_k:\{0,1\}^* \rightarrow
-\{0,1\}$. We write $\BB = \{f_1, \ldots, f_k\}$ to denote the basis consisting
-of all Boolean functions $f^n_i : \{0,1\}^n \rightarrow \{0,1\}$ where $n \in
-\nats$, $i \in [k]$, and $f^n_i$ is the restriction of $f_i$ to strings of
-length $n$. We have $\AND, \OR, \NAND, \MAJ : \{0,1\}^* \rightarrow \{0,1\}$,
-where $\AND, \OR, \NAND$ are the usual (unbounded fan-in) logical operators, and
-$\MAJ$ is the majority function. We write $\BS := \{\AND, \OR, \NOT\}$ to denote
-the \emph{standard basis} and $\BM := \BS \cup \{\MAJ\}$ to denote the
-\emph{majority basis}.
+We depart slight from the conventional notion of a basis in this paper. We
+define a \emph{Boolean basis} (or \emph{basis}) to be a set of finite Boolean
+functions. We always denote a basis by $\BB$. It is common in the literature to
+define a basis as a finite sequence of functions $f_1, \ldots , f_k:\{0,1\}^*
+\rightarrow \{0,1\}$. In this paper we instead think of this sequence as
+\emph{generating} a basis, and write $\BB = \langle f_1, \ldots, f_k \rangle$ to
+denote the basis generated by these functions, i.e.\ $\BB$ consists of all the
+Boolean functions $f_i[n] : \{0,1\}^n \rightarrow \{0,1\}$ where $n \in \nats$,
+$i \in [k]$, and $f_i[n]$ is the restriction of $f_i$ to strings of length $n$.
+In other words $\langle f_1, \ldots , f_k \rangle$ is the union of $\{f_i[n] : n
+\in \nats\}$ for each $f_i$ in the generating sequence. We have $\AND, \OR,
+\NAND, \MAJ : \{0,1\}^* \rightarrow \{0,1\}$, where $\AND, \OR, \NAND$ are the
+usual (unbounded fan-in) logical operators, and $\MAJ$ is the majority function
+(i.e.\ the function that outputs one if more than half of bits in the inputs are
+one). We write $\BS := \langle \AND, \OR, \NAND\} \rangle$ to denote the
+\emph{standard basis} and $\BM := \langle \AND, \OR, \NAND , \MAJ \rangle$ to
+denote the \emph{majority basis}.
 

### 2018-03-04 sections/symmetric-circuits.tex
I have made changes to the section "symmetric circuits" and updated every other section in line with changes made.

@@
 structured Boolean functions. These are functions whose inputs naturally encode
-$\rho$-structures and where the output is invariant under the natural symmetries
+$\tau$-structures and where the output is invariant under the natural symmetries
 of such structures. The\emph{matrix-invariant} functions are a natural
@@
 address this difficulty in the next section.
+
+\begin{drem}
+  G: In fact, this difficulty is present throughout the paper.
+\end{drem}
 
@@
 invariant under the action of the symmetric group on their index. However, in
-many cases this symmetry condition may be too strong, or otherwise
-inappropriate. For example, suppose $X$ consists of all two element subsets of
-some set $V$. We may think of $X$ as containing all potential edges in a graph,
-and the input sequence $ \vec{x} \in \{0,1\}^X$ as encoding a graph. In this
-case we might require instead that $F$ be invariant under the action of $\sym_V$
-on $\vec{x}$. This condition guarantees that $F$ determines a graph property,
-and we call such a function \emph{graph-invariant}. Another example of interest,
-especially in this paper, is the case where $X := A \times B$, where $A$ and $B$
-are non-empty sets, and we think of $\vec{x} \in \{0,1\}^X$ as encoding an
-(unordered) matrix. It is natural then to consider the case where $F$ is
-invariant under the action of $\sym_A \times \sym_B$, and we say such a function
-is \emph{matrix-invariant}. In this subsection we develop a general framework
-for dealing with functions that take in structures.
+many contexts this symmetry condition is inappropriate. For example, suppose $X$
+consists of all the two element subsets of some set $V$. So $X$ contains all the
+potential edges of a graph with vertex set $V$ and the string $ \vec{x} \in
+\{0,1\}^X$ encodes a graph. In this context, it is more natural to require
+instead that $F$ be invariant under the action of $\sym_V$ on $\vec{x}$. This
+condition guarantees that $F$ is constant on isomorphism classes of graphs with
+vertex set $V$, in other words $F$ determines a graph property $F$. We call such
+a function \emph{graph-invariant}. Another example of interest, especially in
+this paper, is the case where $X := A \times B$, where $A$ and $B$ are non-empty
+sets, and we think of $\vec{x} \in \{0,1\}^X$ as encoding an (unordered) matrix.
+It is natural then to consider the case where $F$ is invariant under the action
+of $\sym_A \times \sym_B$, and we say such a function is
+\emph{matrix-invariant}. In this subsection we develop a general framework for
+dealing with Boolean functions that take in strings that encode
+$\tau$-structures.
 
@@
 We can extend the action of $G$ on $X$ to a right group action on the set of
-functions of the form $f: X \rightarrow H$, for any set $H$, defined by $(f \cdot
-\sigma)(x) := f(\sigma x)$ for all $x \in X$, $\sigma \in G$.
+functions of the form $f: X \rightarrow H$, for any set $H$, defined by $(f
+\cdot \sigma)(x) := f(\sigma x)$ for all $x \in X$, $\sigma \in G$.
 
@@
 
-% We should note, however, that symmetry and irreflexivity are
-% properties of directed-graph, and as such can be decided by an
-% isomorphism-invariant structured function over the graph vocabulary.
+% We should note, however, that symmetry and irreflexivity are properties of
+% directed-graph, and as such can be decided by an isomorphism-invariant
+% structured function over the graph vocabulary.
 
@@
 % $g$.
-In this section we extend the circuit definitions of Anderson and Dawar
-\cite{AndersonD17}, introducing a circuit for structures that incorporates an
-indexing for each gate in accordance with the Boolean function labelling that
-gate. This allows us to define (and evaluate) circuits with gates labelled by
-non-symmetric functions.
+We now generalise the circuit model of Anderson and Dawar~\cite{AndersonD17} so
+as to allow for circuits to be defined over bases that potentially include
+non-symmetric (structured) functions. In this model each gate $g$ is not only
+associated with an element of the basis, as in the conventional case, but also
+with a labelling function. This labelling function maps the input gates of $g$
+to an appropriate set of labels (i.e. the index of the structured function
+associated with $g$). In concord with this generalisation, we also update the
+circuit-related notions discussed by Anderson and Dawar~\cite{AndersonD17},
+e.g.\ circuit automorphisms, symmetry, etc. Moreover, we briefly discuss some of
+the important complications introduced by our generalisation, and introduce some
+of the important tools we will use in later sections to address these
+complications.
+
+% in those gates input to each each gate in a circuit is assosiated with both an
+% element of the basis \emph{and} a function that labels the input and and the
+% circuit also includes a labelling function for each gateThe important addition
+% of this generalisation is the inclusion of a labelling function $L$ that
+% associates with each gate
+
+% extend the assosiated notion a basis of structured functions. The important to
+% be labelled by introducing a circuit for structures that incorporates an
+% indexing for each gate in accordance with the Boolean function labelling that
+% gate. This allows us to define (and evaluate) circuits with gates labelled by
+% non-symmetric functions.
 
@@
 % \in \mathbb{N}$.
-
-We now define a \emph{$(\mathbb{B}, \rho)$-circuit}. This is a circuit that
-computes a function on structures in the relational vocabulary $\rho$ and where
-the gates are labelled by elements of the basis $\mathbb{B}$ consisting of
-structured functions. Note that, in the interests of keeping our definitions
-from getting excessively complicated, we do not consider circuits computing
-functions over multi-sorted vocabularies.
 
@@
 
-Let $\rho$ be a relational vocabulary, $\mathcal{A}$ a $\rho$-structure over an
-$n$-element universe $U$ and $\gamma \in [n]^{\underline{U}}$. Let $\gamma
-\mathcal{A}$ be the structure on universe $[n]$ formed by mapping $U$ in
-accordance with $\gamma$. The evaluation of a $(\mathbb{B}, \rho)$-circuit $C$
-of order $n$ computing a $q$-ary query $Q$ proceeds by recursively evaluating
-the gates in the circuit. The evaluation of the gate $g$ for the bijection
-$\gamma$ and input $\mathcal{A}$ is denoted by $C[\gamma \mathcal{A}](g)$, and
-is given as follows
-\begin{enumerate}
-  \setlength\itemsep{0mm}
+Let $\rho$ be a relational vocabulary, $\mathcal{A}$ be a $\rho$-structure with
+universe $U$ of size $n$, and $\gamma \in [n]^{\underline{U}}$. Let $\gamma
+\mathcal{A}$ be the structure with universe $[n]$ formed by mapping the elements
+of $U$ in accordance with $\gamma$. The evaluation of a $(\mathbb{B},
+\rho)$-circuit $C$ of order $n$ computing a $q$-ary query $Q$ proceeds by
+recursively evaluating the gates in the circuit. The evaluation of the gate $g$
+for the bijection $\gamma$ and input structure $\mathcal{A}$ is denoted by
+$C[\gamma \mathcal{A}](g)$, and is given as follows
+
+\begin{myenum}
 \item If $g$ is a constant gate then it evaluates to the bit given by
@@
   (L^{\gamma}_g) = 1$.
-\end{enumerate}
+\end{myenum}
 We say that $C$ defines the $q$-ary query $Q \subseteq U^q$ under $\gamma$ where
@@
 
-The following circuit condition is from Anderson and Dawar \cite{AndersonD17}.
+We notice that in general the output of a circuit $C$ may depend on the
+particular encoding of $\mathcal{A}$ as a structure with universe $[n]$, i.e.\
+on the chosen bijection $\gamma$. It is natural to consider circuits whose
+outputs do do not depend on this choice of encoding. Anderson and
+Dawar~\cite{AndersonD17} call such a circuit \emph{invariant}. We have
+reproduced their definition below.
 
@@
 
-It follows that the circuit $C$ of order $n$ is invariant if, and only if, the
-evaluation of the circuit for any input $n$-element structure $\mathcal{A}$ does
-not depend on the bijection $\gamma$. In general, the evaluation of a circuit
-depends on the presentation of the structure (i.e.\ the bijection $\gamma$). If
-a family of $(\mathcal{B}, \rho)$-circuits $\mathcal{C}$ is invariant it follows
-that the query computed is a $q$-query on $\rho$-structures. Thus if $q = 0$
-then $\mathcal{C}$ computes a property of $\rho$-structures. The following lemma
-allows us to recast this notion in terms of the language developed in this
+If a family of $(\mathcal{B}, \rho)$-circuits $\mathcal{C}$ is invariant it
+follows that the query computed is a $q$-query on $\rho$-structures. Thus if $q
+= 0$ then $\mathcal{C}$ computes a property of $\rho$-structures. The following
+lemma allows us to recast this notion in terms of the language developed in this
 paper.
@@
 
-We now define the notion of an automorphism of circuit.
+We now define an automorphism of a circuit, generalising the definition
+introduced by Anderson and Dawar. The definition is similar, but adds the
+requirement that if a gate $g$ is mapped to $g'$, then children of $g$ must be
+mapped to the children of $g'$ via some appropriate isomorphism of the structure
+associated with $g$.
 
@@
   $\sigma \in \sym_n$ and $\pi: G \rightarrow G$ be a bijection such that
-  \begin{itemize}
-    \setlength\itemsep{0mm}
+  \begin{myitemize}
   \item for all output tuples $x \in [n]^q$, $\pi \Omega (x) = \Omega (\sigma
@@
     \cdot L(g)$ are isomorphism-equivalent.
-  \end{itemize}
+  \end{myitemize}
   We call $\pi$ an \emph{automorphism} of $C$, and we say that $\sigma$
@@
 
-We are particularly interested in circuits that have the property that every
-permutation in $\sym_n$ extends to an automorphism of the circuit.
+We are particularly interested in circuits that have the property that
+\emph{every} permutation in $\sym_n$ extends to an automorphism of the circuit.
 
@@
 It follows that for any symmetric circuit $C$ of order $n$ there is a
-homomorphism $h$ that maps $\sym_n$ to $\aut(C)$ that takes $\sigma \in \sym_n$
-to an automorphism that extends it. Suppose $C$ contains no relational gates of
-non-zero arity. In that case $C$ computes a constant function. As such, in this
-paper we always assume a circuit contains at least one relational gate with
-non-zero arity. There there exists a relational gate in $C$ with some element of
-$[n]$ appearing in the tuple labelling that gate. By symmetry it follows that
-all elements of $[n]$ appear in tuples labelling relational gates in $C$. Thus
-no two distinct elements of $\sym_n$ agree on all input gates, and so the
-homomorphism $h$ is injective.
+homomorphism $h$ that maps $\sym_n$ to $\aut(C)$ such that if $\sigma \in
+\sym_n$ then $h(\sigma)$ is an an automorphism extending $\sigma$. Suppose $C$
+does not contain a relational gate labelled by a relation symbol with non-zero
+arity. In that case $C$ computes a constant function. As such, in this paper we
+always assume a circuit contains at least one relational gate with non-zero
+arity. As such by assumption there exists a relational gate in $C$ such that
+some element of $[n]$ appears in the tuple labelling that gate. By symmetry it
+follows that every elements of $[n]$ appears in a tuple labelling a relational
+gate in $C$. It follows that no two distinct elements of $\sym_n$ agree on all
+input gates, and so the homomorphism $h$ is injective.
 
 If this homomorphism is also surjective then we have that each element of
-$\sigma$ extends uniquely to an automorphism of the circuit. Since many of the
-technical tools developed in this paper require that circuits have this
-property, we restrict our attention to classes of circuits that have
-\emph{unique extensions}.
+$\sigma$ extends uniquely to an automorphism of the circuit. In this case we say
+that a circuit has \emph{unique extensions}.
 
@@
 
-Anderson and Dawar~\cite{AndersonD17} introduce the notion of a \emph{rigid}
-circuit, and show that, for circuits defined over a basis of symmetric functions
-there is a polynomial-time algorithm that takes as input a symmetric circuit and
-outputs an equivalent rigid symmetric circuit. They also show that rigid
-circuits have unique extensions, allowing them to conclude that $P$-uniform
-families of symmetric circuits over bases of symmetric functions may be assumed
-to be rigid (and hence have unique extensions) without a loss of generality.
-
-% It turns out that establishing an exactly analogous argument for general
-% circuits is a non-trivial problem.
-
-% In this paper we establish an approximately analogous argument
-
-Anderson and Dawar's argument makes use of the fact that many important circuit
-properties are polynomial-time decidable for circuits defined over symmetric
-bases. While we should like to construct an analogous argument, we show in
+It is worth noting that many of the important technical tools needed in this
+paper are only applicable if the circuit under consideration has unique
+extensions. In order to handle this technicality Anderson and
+Dawar~\cite{AndersonD17} introduce the notion of a \emph{rigid} circuit and show
+that, for circuits defined over a basis of symmetric functions there is a
+polynomial-time algorithm that takes as input a symmetric circuit and outputs an
+equivalent rigid symmetric circuit. They also show that a great many properties
+of rigid circuits can be decided in polynomial time, a necessary step in their
+argument, and, importantly, that that rigid circuits have unique extensions.
+This allows them to restrict their attention to $P$-uniform families of
+symmetric circuits (over bases of symmetric functions) \emph{with unique
+  extensions}, without a loss of generality.
+
+In order to make use of these technical tools, as well ensure the
+polynomial-time decidability of many important circuit properties, we should
+like to be able to construct a normal form analogous to rigidity and present a
+polynomial time algorithm that transforms a circuit into an equivalent circuit
+of this form. It is at this point that we arrive at the first complication
+introduced by our generalisation. Anderson and Dawar's polynomial-time
+translation makes indispensable of the polynomial-time decidability of many
+important circuit properties for circuits defined over symmetric bases. However,
+for the more general circuits discussed here, it is not known if even the most
+basic circuit properties are polynomial-time decidable. Indeed, we show in
 Section~\ref{sec:transparent} that for circuits that include gates computing
-non-symmetric functions most of these important circuit properties are at least
-as hard to decide as the graph-isomorphism problem. As such, constructing an
-analogous translation, as well as establishing the numerous other needed results
-whose proofs rely on certain properties being polynomial-time decidable, would
-be non-trivial.
-
-In order to proceed we will restrict ourselves to circuits with certain
-constraints on how those gates computing non-symmetric functions can be wired
-into the circuit. We call these circuits \emph{transparent} circuits. We show in
-Sections~\ref{sec:transparent} that transparency is sufficient to allow for the
-polynomial-time decidability of many important circuit properties, while still
-keeping the circuit model powerful enough for us to establish a translation from
-formulas to families of circuits.
+non-symmetric functions all of the relevant circuit properties of interest are
+at least as hard to decide as the graph-isomorphism problem. As such,
+constructing an analogous argument, as well as establishing the numerous other
+crucial results whose proofs rely on the polynomial-time decidability of various
+circuit properties, would be beyond the scope of this paper.
+
+In order to proceed we explicitly restrict our attention to a particular class
+of circuits characterised by a restriction on the children of gates labelled by
+non-symmetric functions. We say such circuits are \emph{transparent}. We show in
+Section~\ref{sec:transparent} that all of the circuit properties of interest are
+polynomial-time decidabile for transparent circuits, and we use these results to
+define a polynomial-time transformation from transparent circuits to equivalent
+circuits with unique extensions. Importantly, while the class of transparency
+condition is a constraint sufficient to enable our analysis, we show in
+Section~\ref{sec:formulas-to-circuits}, that the class of transparent circuits
+is still rich enough to capture $\FPR$.
 
@@
 is that two gates in a circuit are syntactically-equivalent if the circuits
-underneath them are `hereditary similar'.
+underneath them are `hereditary equivalent', i.e.\ the two circuits underneath
+these gates are really just copies of one another.
 % In order to prove this result, Anderson and Dawar introduce the notion of a
@@
   either $g$ or $h$. Then $g \equiv h$ if, and only if, $L(g) /_\equiv$ and
-  $L(h) /_\equiv$ are isomorphism equivalent.
+  $L(h) /_\equiv$ are isomorphism-equivalent.
 \end{definition}
 
-\begin{remark}
+\begin{drem}
   Should I prove these are actually equivalence relations? I use that fact, but
   it's very easy to prove.
-\end{remark}
+\end{drem}
 
@@
 polynomial-time decidable for the class of circuits of interest to us in this
-paper.
+paper. In this sense we shall treat syntactic-equivalence as a tractable
+refinement of the $\NP$-complete relation.
 
@@
 group of $C$, and so the orbits and stabiliser groups of the gates in $C$. We
-say that a circuit $C$ is \emph{syntactically simple} if $C$ has trivial
+say that a circuit $C$ is \emph{reduced} if $C$ has trivial
 syntactic-equivalence classes, i.e. for all gates $g$ and $h$ in $C$ if $g
 \equiv h$ then $g = h$. An immediate corollary of
-Lemma~\ref{lem:permutation-extending-syntactic-equivalence} is that if a circuit
-is syntactically simple then it has unique extensions. We now define a few
-properties of circuits in terms of the structure of their syntactic-equivalence
-classes.
+Lemma~\ref{lem:permutation-extending-syntactic-equivalence}, and en example of
+this intuitive understanding of the result, is that if a circuit is reduced then
+it has unique extensions. We now define \emph{transparency} and other properties
+of circuits in terms of the structure of their syntactic-equivalence classes.
 
@@
 
-It is worth noting that if a circuit has injective labels and is syntactically
-simple then then it has unique labels. The converse is, in general, false.
+It is worth noting that if a circuit has injective labels and is reduced then
+then it has unique labels. The converse is, in general, false.
 
@@
 
-It follows from Proposition~\ref{prop:unique-children-unique-extensions} that if
-$C$ is of order $n$ then for each $\sigma \in \sym_n$ there exists at most one
-$\pi_\sigma \in \aut(C)$ extending $\sigma$. This means that if $C$ is symmetric
-for each $\sigma \in \sym_n$ there is always a canonical automorphism
-$\pi_\sigma$ extending $\sigma$. However, for a gate $g$ in $C$ there may no
-canonical $\lambda \in \aut(g)$ witnessing the validity of the mapping from $g$
-to $\pi_\sigma g$, i.e.\ such that $\pi L(g) = L(g') \lambda$. We prove in
-Section~\ref{sec:transparent} that in fact, for the class of circuits with
-unique children, deciding if there is an isomorphism-equivalence between two
-gates is as hard as the graph-isomorphism problem. It follows that a great many
-important circuit properties (e.g. the orbit of a gate, symmetry of a circuit,
-etc.) for circuits with unique gates are at the very least not obviously
-polynomial-time decidable.
-
-In contrast, it is easy to see that if $C$ has unique labels, and $g$ and $g'$
-are gates in the circuit $C$, then $L(g)$ and $L(g')$ are isomorphism-equivalent
-if, and only if, $\lambda := L(g')^{-1}L(g)$ is in $\aut(g)$. In this case,
-rather than having to decide the isomorphism problem we simply need to check if a given
-candidate is in fact a valid isomorphism. We prove in
+We have from Proposition~\ref{prop:unique-children-unique-extensions} that
+circuits with unique gates have unique extensions, but, in order to prove many
+of the results we will need later, we not only need that each automorphism is
+uniquely defined by the permutation it extends, but also that the isomorphisms
+that witness the isomorphism-equivalences, and so witness the validity of the
+automorphism, are also uniquely defined (or, at least very least, well
+constrained) by the permutation $\sigma$. Without a sufficient constraint on the
+choice of isomorphism, testing if two gates have isomorphism-equivalent
+labellings (a requirement for computing the automorphism extending a
+permutation) requires solving some version of the isomorphism problem for
+$\tau$-structures, where $\tau$ is the vocabulary of the gates in question.
+Indeed, we prove in Section~\ref{sec:transparent}, that for the class of
+circuits with unique children deciding if there is an isomorphism-equivalence
+between two gates is as hard as the graph-isomorphism problem. It follows that a
+great many important circuit properties (e.g. the orbit of a gate, symmetry of a
+circuit, etc.) for circuits with unique gates are at the very least not
+obviously polynomial-time decidable. As such, circuits with unique children,
+although satisfying the requirement of having unique extensions, are
+insufficient for our purposes.
+
+\begin{drem}
+  G: I think the above paragraph may be getting a bit too far into the weeds.
+\end{drem}
+
+In order to ensure a canonical choice of isomorphism we instead consider
+circuits with unique labels. It is easy to see that if $C$ has unique labels
+then $L(g)$ and $L(g')$ are isomorphism-equivalent if, and only if, $\lambda :=
+L(g')^{-1}L(g)$ is an isomorphism. In this case, rather than having to decide
+the isomorphism problem, we can decide isomorphism-equivalences by checking if a
+given candidate function is a valid isomorphism. We prove in
 Section~\ref{sec:transparent} that all of the circuit properties of interest in
 this paper are polynomial-time decidable for circuits with unique labels.
-Moreover, we show in Lemma~\ref{lem:transparent-unique} that a
-transparent circuit can be converted into an equivalent circuit with unique
-labels in time polynomial in the size of the circuit. Since we are working with
-$P$-uniform families of transparent circuits, this fact allows us to assume,
-without a loss of generality, that transparent circuits have unique labels (and,
-from \ref{prop:unique-children-unique-extensions} so unique extensions).
+Moreover, we show in Lemma~\ref{lem:transparent-unique} that a transparent
+circuit can be transformed into an equivalent circuit with unique labels in time
+polynomial in the size of the circuit. Since we are working with $P$-uniform
+families of transparent circuits, this fact allows us to assume, without a loss
+of generality, that transparent circuits have unique labels and so , from
+\ref{prop:unique-children-unique-extensions}, unique extensions).
 
@@
 % matrix-invariant.
-
-In many contexts, circuits are defined over a basis of symbols, usually the
-standard logical symbols $\land, \neg, \lor$, and perhaps $\maj$ (for majority).
-When evaluating a circuit, a gate labelled by a particular symbol is evaluated
-using a Boolean function appropriate to the particular symbol. We have instead
-defined a basis to be a set of Boolean functions. However, when reasoning about
-circuits or dealing with them as inputs to algorithms we often want to identify
-a function in the basis with a particular symbol. We now formally define a few
-natural bases used in this paper, assigning to each function in these bases an
-appropriate symbol.
-
-Let $a \in \nats$, let $\land[a] : \{0,1\}^{[a]} \rightarrow \{0,1\}$ be the
-structured function computing the $\AND$ operation on $a$ inputs. Let $\lor[a] :
-\{0,1\}^{[a]} \rightarrow \{0,1\}$ be the structured function computing the
-$\OR$ operation on $a$ inputs. Let $\maj [a] : \{0,1\}^{[a]} \rightarrow
-\{0,1\}$ be the structured function computing the the majority function on $a$
-inputs. We abuse notation and let $\neg : \{0,1\} \rightarrow \{0,1\}$ also
-denote the structured function computing negation on a single input. In each
-case we use the name of the function above as a symbol denoting that function.
-
-Let the \emph{standard basis} $\BS$ be the basis containing $\neg$ and all
-functions $\land[a]$ and $\lor[a]$ for every $a \in \nats$. Let the
-\emph{majority basis }$\BM := \BS \cup \{\maj[a] : a \in \nats\}$. We say a
-basis $\BB$ is \emph{symmetric} if every function in $\mathbb{B}$ is a symmetric
-Boolean function.
-
-Let $a, b, r, p \in \nats$, with $p$ prime. Let $\rank^r_p[a,b] : \{0,1\}^{[a]
-  \times [b]} \rightarrow \{0,1\}$ be a matrix-invariant structured with
-universe $[a] \uplus [b]$, such that $\rank^r_p[a,b](M) = 1$ if, and only if,
-the matrix $M \in \{0,1\}^{[a] \times [b]}$ has rank at most $r$ when its
-entries are understood as elements of the finite field $\mathbb{F}_p$. We again
-identify the function $\rank^{r}_p[a,b]$ with the symbol $\rank^{r}_p[a,b]$.
-
-Let the \emph{rank basis} $\RB := \BM \cup \{\rank^{r}_p[a,b] : a, b, r, p \in
-\nats, \text{ $p$ prime}\}$. We say a basis $\BB$ is \emph{matrix-symmetric} if
-every function in $\BB$ is symmetric or matrix-symmetric.
+We now discuss a few Boolean basis of interest in this paper and state the main
+result. In most cases (e.g.\ \cite{}) a Boolean basis is taken to be a finite
+sequence of symmetric Boolean functions. A binary encoding of a circuit defined
+over such a basis is given by assigning to each element of the basis a unique
+symbol, and then encoding the circuit in the obvious manner. Since there are
+only a finite number of basis elements, it follows that if each basis element
+can be computed in polynomial time then the mapping that takes a symbol $s$ and
+a string $\vec{x}$ to the value of the function denoted by $s$ for input
+$\vec{x}$ can be decided in polynomial-time. We call this function the
+\emph{gate evaluation function}, and note that its polynomial-time decidability
+is required for proving the polynomial-time evaluation of the circuit. However,
+in order to allow for the inclusion of structured (possibly non-symmetric)
+functions in the basis, we have instead defined a basis to be a (possibly
+infinite) set of finite Boolean functions. In this case the gate evaluation
+function may not even be decidable, let alone polynomial-time decidable.
+
+\begin{definition}
+  Let $\BB$ be a basis. Let $S$ be a set of symbols and let $F : \BB \rightarrow
+  S$ be a bijection. We say $\BB$ is \emph{effective} if the function $E$ that
+  maps a symbol $s$ and an input $x \in \dom(F(s))$ to the value
+  $(F^{-1}(s))(x)$ is decidable. We say $\BB$ is \emph{$\PT$-effective} if $E$
+  is polynomial-time decidable.
+\end{definition}
+
+It is easy to see that if $\BB$ is a $\PT$-effective basis then we can evaluate
+a circuit over $\BB$ in time polynomial in the size of the circuit.
+
+Let $n \in \nats$, we have that $\AND[n] : \{0,1\}^{[n]} \rightarrow \{0,1\}$ is
+the restriction (as a structured function) of the $\AND$ function to inputs of
+size $n$. Similarly, we have that $\OR[n]$, $\NAND[n]$ and $\MAJ[n]$ are the
+restrictions of these respective functions to strings of length $n$. We let
+$\NOT: \{0,1\} \ra \{0,1\}$ be the not function, and we often identify $\NOT$
+with $\NAND[1]$. In each case we use the name of the function as the symbol
+denoting that function.
+
+As such, the standard basis $\BS$ consists of the functions $\NAND[n]$,
+$\AND[n]$, and $\OR[n]$ for every $n \in \nats$, and the majority basis is $\BM
+:= \BS \cup \{\MAJ[n] : n \in \nats\}$. We often use $\NAND[1]$ and $\NOT$
+interchangeably. We say a basis $\BB$ is \emph{symmetric} if every function in
+$\BB$ is a symmetric Boolean function.
+
+Let $a, b, r, p \in \nats$, with $p$ prime. Let $\RANK^r_p[a,b] : \{0,1\}^{[a]
+  \times [b]} \rightarrow \{0,1\}$ be a matrix-invariant structured function
+with universe $[a] \uplus [b]$, such that $\RANK^r_p[a,b](M) = 1$ if, and only
+if, the matrix $M \in \{0,1\}^{[a] \times [b]}$ has rank at most $r$ over $\ff_p$
+when the entries of $M$ are interpreted as elements of $\mathbb{F}_p$. We
+identify the function $\RANK^{r}_p[a,b]$ with the symbol $\RANK^{r}_p[a,b]$.
+
+Let $\RANK = \{\RANK^{r}_p[a,b] : a, b, r, p \in \nats, \text{ $p$ prime}\}$ and
+let the \emph{rank basis} be $\RB := \BM \cup \RANK$. We say a basis $\BB$ is
+\emph{matrix-symmetric} if every function in $\BB$ is symmetric or
+matrix-symmetric. It is easy to see that the standard basis, the majority basis,
+and the rank basis are all $\PT$-effective.
 
@@
 \rho)$-circuit of order $n$ and let $g \in G$. We say a gate $g \in G$ is a
-\emph{symmetric gate} if $\Sigma(g)$ is a symmetric function. We say a gate $g
-\in G$ is a \emph{matrix-symmetric gate} if $\Sigma(g)$ is a matrix-symmetric
-structured function. We say that $g$ is an \emph{$\AND$-gate} if $\Sigma(g) :=
-\land [a]$ for some $a \in \nats$. Similarly we define \emph{$\OR$-gates},
-\emph{$\NOT$-gates}, \emph{$\MAJ$-gates} and \emph{$\rank$-gates}.
+\emph{symmetric gate} if $\Sigma(g)$ is a symmetric function, and otherwise we
+say $g$ is a \emph{non-symmetric gate} We say a gate $g \in G$ is a
+\emph{matrix-symmetric gate} if $\Sigma(g)$ is a matrix-symmetric structured
+function. We say that $g$ is an \emph{$\AND$-gate} if $\Sigma(g) := \AND[a]$ for
+some $a \in \nats$. Similarly we define an \emph{$\OR$-gates},
+\emph{$\NAND$-gate} \emph{$\NOT$-gates}, \emph{$\MAJ$-gates}, and
+\emph{$\RANK$-gates}.
 
@@
 matrix-symmetric or symmetric. We say $C$ is a \emph{rank-circuit} if $C$ is a
-matrix-circuit and every non-symmetric gate is a $\rank$-gate.
+matrix-circuit and every non-symmetric gate is a $\RANK$-gate.
 
@@
 of symmetric circuits that decide the same language but are defined over the
-basis $\mathbb{B}_\maj$. In other words, it makes no difference to the
-expressive power of such circuits whether we include \emph{all} symmetric
-functions in the basis or just $\mathbb{B}_\maj$. It follows that in order to
-construct $P$-uniform families of symmetric circuits that define queires not in
-$\FPC$, we need to consider bases with non-symmetric functions.
+basis $\BM$. In other words, it makes no difference to the expressive power of
+such circuits whether we include \emph{all} symmetric functions in the basis or
+just $\BM$. It follows that in order to construct $P$-uniform families of
+symmetric circuits that define queires not in $\FPC$, we need to consider bases
+with non-symmetric functions.
 
@@
   $F: \{0,1\}^n \rightarrow \{0,1\}$ (encoded as a binary $n$-tuple as above) a
-  symmetric circuit $C$ defined over the basis $\mathbb{B}_\maj$ that computes
-  $F$. Moreover, this function is computable in time polynomial in $n$ and the
+  symmetric circuit $C$ defined over the basis $\BM$ that computes $F$.
+  Moreover, this function is computable in time polynomial in $n$ and the
   circuit $C$ has depth at most $5$, width at most $2n+2$ and size at most $5n +
@@
   the $n$ input gates labelled by the variables $x_1, \ldots , x_n$. The second
-  layer consists of two `majority' gates for each $a \in c_{F}$, which we denote
-  by $\maj_a$ and $\maj^{\neg}_a$. For each $a \in c_{F}$ there is one wire from
+  layer consists of two $\MAJ$ gates for each $a \in c_{F}$, which we denote by
+  $\maj_a$ and $\maj^{\neg}_a$. For each $a \in c_{F}$ there is one wire from
   each of $x_1, \ldots , x_n$ to $\maj_a$ and $\maj^{\neg}_a$. For all $a \geq
@@
   2a$ wires from $1$ to $\maj_a$ and $n - 2a - 2$ wires from $1$ to
-  $maj^{\neg}_a$. The third layer consists of one `not' gate for each $a \in
+  $maj^{\neg}_a$. The third layer consists of one $\NOT$ gate for each $a \in
   c_{F}$, which we denote by $\neg_a$. For each $a \in c_{F}$ there is a wire
-  from $\maj^\neg_a$ to $\neg_a$. The fourth layer consists of one `and' gate
+  from $\maj^\neg_a$ to $\neg_a$. The fourth layer consists of one $\AND$ gate
   for each $a \in c_{F}$, which we denote by $\countgate_a$. For each $a \in
   c_{F}$ there is a wire from each of $\maj_a$ and $\neg_a$ to $\countgate_a$.
-  The fifth layer consists of just a single `or' gate, designated as the output
+  The fifth layer consists of just a single $\OR$ gate, designated as the output
   gate, and for each $a \in c_{F}$ there is a wire from $\countgate_a$ to the
@@
   number of $1$'s in $\vec{x}$ equals $a$ if, and only if, $F (\vec{x}) = 1$.
-  Moreover, it is easy to see that $C$ is symmetric and the algorithm defined
-  runs in time polynomial in $n$.
+  Let $\sigma \in \sym_n$. We define the automorphism $\pi$ extending $\sigma$
+  as follows. If $x_i$ is an input gate then let $\pi x_i := x_{\sigma i}$. We
+  note that for each of the majority gate $g$ in the second layer there is
+  exactly one wire from each input gate to $g$. We note additionally that every
+  other gate in the circuit is connected to the (non-constant) input gates only
+  through a gate in the second layer. As such, if $g$ is an internal gate we let
+  $\pi g := g$, and note that $\pi$ is an automorphism extending $\sigma$. It
+  follows that $C$ is symmetric. It is easy to see that the construction of the
+  circuit $C$ can be implemented by an algorithm running in time polynomial in
+  $n$.
+
   % AD - perhaps include a brief argument for why C is symmetric?
+  % G - I've added a discussion of this
 
@@
 \begin{thm}
-  Let $\mathbb{B}$ be a basis of symmetric functions and let $(C_n)_{n \in
-    \mathbb{N}}$ be a family of symmetric circuits defined over the basis
-  $\mathbb{B}$. Then there exists a family of symmetric circuits $(C_n')_{n \in
-    \mathbb{N}}$ defined over $\mathbb{B}_\maj$ that decides the same language.
-  Moreover, the map $C_n \mapsto C_n'$ is polynomial-time computable and for
-  each $n \in \nats$, $\vert C_n' \vert \leq (5 \cdot \vert C_n \vert + 3) \cdot
-  \vert C_n \vert$.
+  Let $\BB$ be a basis of symmetric functions and let $(C_n)_{n \in \nats}$ be a
+  family of symmetric circuits defined over the basis $\BB$. Then there exists a
+  family of symmetric circuits $(C_n')_{n \in \nats}$ defined over $\BM$ that
+    decides the same language. Moreover, the map $C_n \mapsto C_n'$ is
+    polynomial-time computable and for each $n \in \nats$, $\vert C_n' \vert
+    \leq (5 \cdot \vert C_n \vert + 3) \cdot \vert C_n \vert$.
   \end{thm}
@@
   From $C_n$ we construct $C_n'$ as follows. For each gate $g \in C_n$ labelled
-  by a member of $\mathbb{B}$ we have a symmetric circuit $C_g$ from
+  by a member of $\BB$ we have a symmetric circuit $C_g$ from
   Proposition~\ref{prop:fuctions-maj} that computes the same function as $g$.
@@
 also have that if the first family was uniform the second family will be as
-well. As such, we cannot extend the power of the $P$-uniform symmetric circuits
-families studied by Anderson and Dawar~\cite{AndersonD17} by simply considering
-alternative bases of symmetric functions, thus motivating the generalisation
-developed in the previous subsection to non-symmetric functions.
+well. As such, we cannot extend the power of the $\PT$-uniform symmetric
+circuits families studied by Anderson and Dawar~\cite{AndersonD17} by simply
+considering alternative bases of symmetric functions, thus motivating the
+generalisation developed in the previous subsection to circuits over bases
+including non-symmetric functions.
 \end{document}

### 2018-03-04 sections/transparency-and-unique-extensions.tex
I have made changes to the section "symmetric circuits" and updated every other section in line with changes made.

@@
 is symmetric, and has unique unique labels. We also show that the quotient of a
-circuit has trivial syntactic-equivalence classes, and hence unique extensions.
+circuit is reduced, and hence has unique extensions.
 
@@
   \Omega_\equiv, \Sigma_\equiv , \Lambda_\equiv, L_\equiv \rangle$ be a quotient
-  of $C$. Then $C$ and $C_{\equiv}$ compute the same function and each
-  syntacitic-equivalence class in $C_\equiv$ is a singleton. Moreover, if $C$ is
-  symmetric then $C_{\equiv}$ is symmetric, and for all $g \in G$, $g$ has
-  unique labels in $C$ if, and only if, $[g]$ has unique labels in $C_{\equiv}$.
+  of $C$. Then $C_\equiv$ is reduced and $C$ and $C_{\equiv}$ compute the same
+  function. Moreover, if $C$ is symmetric then $C_{\equiv}$ is symmetric, and
+  for all $g \in G$, $g$ has unique labels in $C$ if, and only if, $[g]$ has
+  unique labels in $C_{\equiv}$.
   \label{lem:quotient-circuits-preserve}
@@
 
-  We now show that each syntactic-equivalence class in $C_\equiv$ is a
-  singleton. Suppose $[g], [h] \in G_\equiv$ and suppose $[g] \equiv [h]$. If
-  $[g]$ and $[h]$ are both input or output gates then $[g] = [h]$. Suppose $[g]$
-  and $[h]$ are internal gates that are not output gates. Then $\Sigma (g) =
-  \Sigma_\equiv ([g]) = \Sigma_\equiv([h]) = \Sigma(h)$. There exists $g', h'
-  \in G$ such that $g' \equiv g$ and $h' \equiv h$, and $L_\equiv ([g]) = L(g')
-  /_\equiv$ and $L_\equiv ([h]) = L(h') /_\equiv$. It follows from $[g] \equiv
-  [h]$ that $L(g') /_\equiv$ is isomorphism-equivalent to $L(h') /_\equiv$. It
-  follows that $g' \equiv h'$, and so $[g] = [h]$.
+  We now show that $C_\equiv$ is reduced. Suppose $[g], [h] \in G_\equiv$ and
+  suppose $[g] \equiv [h]$. If $[g]$ and $[h]$ are both input or output gates
+  then $[g] = [h]$. Suppose $[g]$ and $[h]$ are internal gates that are not
+  output gates. Then $\Sigma (g) = \Sigma_\equiv ([g]) = \Sigma_\equiv([h]) =
+  \Sigma(h)$. There exists $g', h' \in G$ such that $g' \equiv g$ and $h' \equiv
+  h$, and $L_\equiv ([g]) = L(g') /_\equiv$ and $L_\equiv ([h]) = L(h')
+  /_\equiv$. It follows from $[g] \equiv [h]$ that $L(g') /_\equiv$ is
+  isomorphism-equivalent to $L(h') /_\equiv$. It follows that $g' \equiv h'$,
+  and so $[g] = [h]$.
 
@@
 equivalent circuit with unique labels, and hence unique extensions (see
-Proposition~\ref{prop:unique-children-unique-extensions}), and that this transformation preserves important properties of
-the circuit.
+Proposition~\ref{prop:unique-children-unique-extensions}), and that this
+transformation preserves important properties of the circuit.
 
@@
   \uplus \{ g_\lor\}$. Let $\Omega_1 = \Omega_0$ and $\Lambda_1 = \Lambda_0$.
-  Let $g \in G_1$. If $g = g_\lor$ then $\Sigma_1 (g) = \lor[2]$, $L_1(g)(1) =
-  g_0$, and $L_1(g)(2) = g_1$. If $g \in G_0$, $\Sigma(g) = \lor[2]$ and $H_g =
-  \{g_0, g_1\}$ then $\Sigma_1 (g) = \lor[3]$, $L_1(g)(1) = L_0(g)(1)$,
+  Let $g \in G_1$. If $g = g_\lor$ then $\Sigma_1 (g) = \OR[2]$, $L_1(g)(1) =
+  g_0$, and $L_1(g)(2) = g_1$. If $g \in G_0$, $\Sigma(g) = \OR[2]$ and $H_g =
+  \{g_0, g_1\}$ then $\Sigma_1 (g) = \OR[3]$, $L_1(g)(1) = L_0(g)(1)$,
   $L_1(g)(2) = L_0(g)(2)$, and $L_1(g)(3) = g_\lor$. If $g \in G_0$ and $g =
-  \land[k]$ for some $k \in \nats$ then $\Sigma_1(g) = \land[k+1]$ and
-  $L_1(g)(i) = L_0(g)(i)$ for all $i \in [k]$ and $L_1(g)(k+1) = g_\lor$.
-  Otherwise let $\Sigma_1(g) = \Sigma_0(g)$ and $L_1(g) = L_0(g)$.
+  \AND[k]$ for some $k \in \nats$ then $\Sigma_1(g) = \AND[k+1]$ and $L_1(g)(i)
+  = L_0(g)(i)$ for all $i \in [k]$ and $L_1(g)(k+1) = g_\lor$. Otherwise let
+  $\Sigma_1(g) = \Sigma_0(g)$ and $L_1(g) = L_0(g)$.
 
@@
 
-  We have from Lemma~\ref{lem:quotient-circuits-preserve} that $C_0$ has trivial
-  syntactic-equivalence classes. Since $g_\lor$ is the only two input $\OR$-gate
-  with exactly the two constant gates as children, it follows that $g_\lor$ is
-  contained in a singleton syntactic-equivalence class. It can be shown by
-  induction that if $g, g' \in G_0$ are syntactically equivalent in $C_1$ then
-  they must be syntactically-equivalent in $C_0$. It follows that if $g$ and
-  $g'$ are syntactically-equivalent in $C_1$ then $g = g'$. We thus have that
-  $C_1$ has trivial syntactic-equivalence classes.
+  We have from Lemma~\ref{lem:quotient-circuits-preserve} that $C_0$ is reduced.
+  Since $g_\lor$ is the only two input $\OR$-gate with exactly the two constant
+  gates as children, it follows that $g_\lor$ is contained in a singleton
+  syntactic-equivalence class. It can be shown by induction that if $g, g' \in
+  G_0$ are syntactically equivalent in $C_1$ then they must be
+  syntactically-equivalent in $C_0$. It follows that if $g$ and $g'$ are
+  syntactically-equivalent in $C_1$ then $g = g'$. We thus have that $C_1$ is
+  reduced.
 
@@
   $\Omega' = \Omega_1$ and $\Lambda' = \Lambda_1$. For $g \in G'$ if $g \in G_1$
-  let $\Sigma'(g) = \Sigma_1(g)$ and otherwise let $\Sigma'(g) = \land[1]$. For
+  let $\Sigma'(g) = \Sigma_1(g)$ and otherwise let $\Sigma'(g) = \AND[1]$. For
   each $g \in G_1$ and $h \in H_g$ let $\{x^{h,g}_0, x^{h,g}_1 ,\ldots,
@@
   \begin{claim}
-    $C'$ has trivial syntactic-equivalence classes.
+    $C'$ is reduced
   \end{claim}
@@
     L'(g')(x)$. It follows that $H_{g}' = H_{g'}'$. Moreover, from the inductive
-    hypothesis the children of $g$ and $g'$ must be contained in singleton
-    syntactic-equivalence classes, and so , since $C'$ has injective labels, it
+    hypothesis the children of $g$ and $g'$ must be contained in a singleton
+    syntactic-equivalence classes, and so, since $C'$ has injective labels, it
     follows that $g$ and $g'$ have unique labels in $C'$.
@@
     1]$ such that $g = g^h_i$. Suppose $g' \in G_1$. Then $\Sigma'(g) =
-    \land[1]$. But, from the construction of $C_1$, there are no single-input
+    \AND[1]$. But, from the construction of $C_1$, there are no single-input
     $\AND$-gates in $G_1$. It follows $\Sigma'(g') \neq \Sigma'(g)$ and so $g'
@@
 
-    Suppose $g \in G_1$. We have already shown that if $g' \in G_\land G_1$ then
-    $g \not\equiv' g'$, a contradiction, and so we must have $g' \in G_1$. Since
-    $g \equiv' g'$ there exists $\lambda \in \aut(g)$ such that for all $x \in
+    Suppose $g \in G_1$. We have already shown that if $g' \in G_\land$ then $g
+    \not\equiv' g'$, a contradiction, and so we must have $g' \in G_1$. Since $g
+    \equiv' g'$ there exists $\lambda \in \aut(g)$ such that for all $x \in
     \ind(g)$, $L'(g)(\lambda x) = L'(g')(x)$. From the construction, we have
@@
 
-  Since $C'$ has injective labels and trivial syntactic-equivalence classes it
-  follows $C'$ has unique labels.
+  Since $C'$ has injective labels and is reduced it follows $C'$ has unique
+  labels.
 
@@
 of a circuit of order $n$ with unique labels in polynomial time. Recall that
-from Lemma~\ref{lem:transparent-unique} we may, without a loss of
-generality, restrict our attention from transparent circuits to circuits with
-unique labels. The proof technique used here is similar to the one used by
-Anderson and Dawar~\cite{AndersonD17}.
+from Lemma~\ref{lem:transparent-unique} we may, without a loss of generality,
+restrict our attention from transparent circuits to circuits with unique labels.
+The proof technique used here is similar to the one used by Anderson and
+Dawar~\cite{AndersonD17}.
 
 \begin{lem}
-  There is an algorithm takes as input a $(\mathbb{B}, \rho)$-circuit $C$ of
-  order $n$ with unique labels and $\sigma \in \sym_n$ and outputs for each gate
-  $g$ its image under the unique automorphism extending $\sigma$ (if it exists).
-  This algorithm runs in time polynomial in the combined size of the input
-  circuit and the encoding of the permutation.
+  There is an algorithm takes as input a $(\BB, \rho)$-circuit $C$ of order $n$
+  with unique labels and $\sigma \in \sym_n$ and outputs for each gate $g$ its
+  image under the unique automorphism extending $\sigma$ (if it exists). This
+  algorithm runs in time polynomial in the combined size of the input circuit
+  and the encoding of the permutation.
   \label{lem:compute-automorphisms}
@@
   output that no automorphism exists. We have from
-  Proposition~\ref{prop:unique-children-unique-extensions} that there is at
-  most one gate $h'$ that meets the above criteria, and so $\pi(h)$ is well
-  defined.
+  Proposition~\ref{prop:unique-children-unique-extensions} that there is at most
+  one gate $h'$ that meets the above criteria, and so $\pi(h)$ is well defined.
 
@@
 labels in polynomial time, and that circuits with unique labels have unique
-extensions (see Proposition~\ref{prop:unique-children-unique-extensions}). Moreover, we have similarly shown that, for
-transparent circuits, the action of a permutation, as well as the coarsest
-supporting partition and orbit of a gate (or element of the universe of a gate),
-can be computed in polynomial-time. Since all circuits with symmetric gates are
-transparent, this is direct generalisation of the results of Anderson an Dawar.
+extensions (see Proposition~\ref{prop:unique-children-unique-extensions}).
+Moreover, we have similarly shown that, for transparent circuits, the action of
+a permutation, as well as the coarsest supporting partition and orbit of a gate
+(or element of the universe of a gate), can be computed in polynomial-time.
+Since all circuits with symmetric gates are transparent, this is direct
+generalisation of the results of Anderson an Dawar.
 
@@
 prove a stronger result, presenting a reduction from the graph-isomorphism
-problem to the problem of computing the syntactic-equivalence relation over an
-ostensibly simpler class of circuits.
+problem to the problem of computing the syntactic-equivalence relation over a
+more constrained class of circuits.
 
@@
   injective labels, (ii) contains no constant gates, and (iii) contains at most
-  two rank gates with bound $r$ and prime $p$, are syntactically equivalent.
+  two rank gates with bound $r$ and prime $p$, are syntactically-equivalent.
   \label{prop:syntactic-graph-iso}
@@
   G_R \cup G_{\text{mid}} \cup G_{\rank} \cup G_{\text{nodes}}$ and $\Omega$ be
-  the $0$-ary function $\land_{\text{out}}$. For each $\vec{c} \in
+  the $0$-ary function $g_{\text{out}}$. For each $\vec{c} \in
   [n]^{\arty(R)}$ let $\Lambda_R(\vec{c}) = g_{R, \vec{c}}$. Define $\Sigma$ as
   follows. For each $g \in G$,
-  \begin{itemizens}
+  \begin{myitemize}
+  \item if $g = g_{\text{out}}$ then $\Sigma(g) = \AND[2]$,
+  \item if $g \in G_\rank$ then $\Sigma(g) = \RANK^r_p [a,b]$,
+  \item if $g \in G_{\text{nodes}}$ then $\Sigma(g) = \AND[1]$,
+  \item if $g = \AND[n^k]$, $\Sigma (g) = \AND[n^k]$ and if $g = g_{\lor}$
+    then $\Sigma(g) = \OR[n^k]$, and
+  \item if $g \in G_R$ then $\Sigma(g) = R$.
+  \end{myitemize}
+  Define $L$ as follows. For each $g \in G$,
+  \begin{myitemize}
     \setlength\itemsep{0mm}
-  \item if $g = \land_{\text{out}}$ then $\Sigma(g) = \land[2]$,
-  \item if $g \in G_\rank$ then $\Sigma(g) = \rank^r_p [a,b]$,
-  \item if $g \in G_{\text{nodes}}$ then $\Sigma(g) = \land[1]$,
-  \item if $g = \land[n^k]$, $\Sigma (g) = \land[n^k]$ and if $g = g_{\lor}$
-    then $\Sigma(g) = \lor[n^k]$, and
-  \item if $g \in G_R$ then $\Sigma(g) = R$.
-  \end{itemizens}
-  Define $L$ as follows. For each $g \in G$,
-  \begin{itemizens}
-    \setlength\itemsep{0mm}
-  \item if $g = \land_{\text{out}}$ then for each $i \in [2]$, $L(g)(i) :=
+  \item if $g = g_{\text{out}}$ then for each $i \in [2]$, $L(g)(i) :=
     g^i_{\rank}$,
@@
     element of $[n]^k$ in the lexicographical ordering on $[n]^k$.
-  \end{itemizens}
+  \end{myitemize}
 
@@
 stronger result, showing that this reduction holds even if we restrict ourselves
-to the class of circuits with trivial syntactic-equivalence classes and in
-which, all but two gates in the circuit have unique labels.
+to the class of reduced circuits in which all but two gates in the circuit have
+injective labels. In other words, the class of circuits that have unique
+children and \emph{almost} have unique labels but for two gates.
 
@@
   The graph-isomorphism problem is polynomial-time reducible to the problem of
-  deciding if a circuit with trivial syntactic-equivalence classes and in which
-  all but two gates in the circuit have unique labels is symmetric.
+  deciding if a reduced circuit in which all but two gates in the circuit have
+  unique labels is symmetric.
   \label{prop:graph-iso-symmetric}
@@
   \in G$,
-  \begin{itemizens}
-  \item if $g$ equals $\land_{\text{out}}$ then $\Sigma(g) = \land[2]$,
-  \item if $g \in G_\rank$ let $\Sigma(g) = \rank^r_p [a,b]$,
+  \begin{myitemize}
+  \item if $g$ equals $\land_{\text{out}}$ then $\Sigma(g) = \AND[2]$,
+  \item if $g \in G_\rank$ let $\Sigma(g) = \RANK^r_p [a,b]$,
   \item if $g \in G_{\text{mid}}$ and $g = g^i_s$ for $ \in [2]$ and symbol $s$
@@
   \item if $g \in G_R$ then $\Sigma(g) = R$.
-  \end{itemizens}
+  \end{myitemize}
   Define $L$ as follows. For each $g \in G$,
-  \begin{itemizens}
+  \begin{myitemize}
   \item if $g = g_{\text{out}}$ then for each $i \in [2]$, $L(g)(i) :=
@@
     $L(g)(1) = \Lambda^{-1}(i)$.
-  \end{itemizens}
+  \end{myitemize}
 
@@
 hardness result for deciding a basic circuit property even if we restrict
-ourselves to circuits with trivial syntactic-equivalence classes (and so ones
-where each gate has unique children). It is possible to alter this reduction,
-using a construction analogous to the one used in the proof of
-Proposition~\ref{prop:syntactic-graph-iso}, to prove that deciding symmetry is
-also hard for circuits with injective labels. In contrast, we have from
-Proposition~\ref{lem:computing-support-orbit-index} that we can decide symmetry
-for transparent circuits (i.e. circuits where every non-symmetric gate has
-unique children and injective labels) in polynomial-time. These observations
-again suggest both the robustness of this hardness result, and the importance of
-the transparency condition.
+ourselves to reduced circuits (and so ones where each gate has unique children).
+It is possible to alter this reduction, using a construction analogous to the
+one used in the proof of Proposition~\ref{prop:syntactic-graph-iso}, to prove
+that deciding symmetry is also hard for circuits with injective labels. In
+contrast, we have from Proposition~\ref{lem:computing-support-orbit-index} that
+we can decide symmetry for transparent circuits (i.e. circuits where every
+non-symmetric gate has unique children and injective labels) in polynomial-time.
+These observations again suggest both the robustness of this hardness result,
+and the importance of the transparency condition.
 
@@
 
-  For each $p \in \nats$ let $G^p \subseteq G$ be the set of all
-  gates of depth $p$ and let $G^{\leq p} = \bigcup_{0 \leq i \leq p}G^i$. Note
-  that each $g \in G^1$, $g$ has unique labels. Thus, from
+  For each $p \in \nats$ let $G^p \subseteq G$ be the set of all gates of depth
+  $p$ and let $G^{\leq p} = \bigcup_{0 \leq i \leq p}G^i$. Note that each $g \in
+  G^1$, $g$ has unique labels. Thus, from
   Lemma~\ref{lem:transparent-syntactic-equiv}, we can compute the syntactic
@@
   $\Omega = g_{\text{out}}$ an $\Lambda_R (g_R) = 1$. Let $\Sigma (g_R) = R$,
-  $\Sigma (g_\lor) = \lor[1]$, $\Sigma (g_\land) = \land[1]$, $\Sigma
-  (g_{\text{out}}) = \land[2]$ and for all $g \in G_{\rank}$, $\Sigma (g) =
-  \land[a,b]$. Let $L(g_\lor)(1) L(g_\land)(1) = g_R$, for all $i \in [2]$,
+  $\Sigma (g_\lor) = \OR[1]$, $\Sigma (g_\land) = \AND[1]$, $\Sigma
+  (g_{\text{out}}) = \AND[2]$ and for all $g \in G_{\rank}$, $\Sigma (g) =
+  \AND[a,b]$. Let $L(g_\lor)(1) L(g_\land)(1) = g_R$, for all $i \in [2]$,
   $L(g_{\text{out}})(i) = g^i_{\rank}$ and for all $(u, v) \in \ind(g)$,

### 2018-03-10 sections/background.tex
I have been trying to improve the presentation of the translation of circuits into formulas. To this end, I have changed the notation we use to talk about the usual logical operators (e.g. AND, OR, NOT, etc). I have also added tried to simplify the writing, and better explain the approach taken when translating circuits into formulas. I am in the process of writing the conclusion, but there is so much to think about.

@@
 Boolean function $f : \{0,1\}^{*} \rightarrow \{0,1\}$ is \emph{symmetric} if
-its restriction to inputs of size $n$ is symmetric for all $n$.
+its restriction to inputs of size $n$ is symmetric for all $n \in \nats$.
 
-We depart slight from the conventional notion of a basis in this paper. We
-define a \emph{Boolean basis} (or \emph{basis}) to be a set of finite Boolean
-functions. We always denote a basis by $\BB$. It is common in the literature to
-define a basis as a finite sequence of functions $f_1, \ldots , f_k:\{0,1\}^*
-\rightarrow \{0,1\}$. In this paper we instead think of this sequence as
-\emph{generating} a basis, and write $\BB = \langle f_1, \ldots, f_k \rangle$ to
-denote the basis generated by these functions, i.e.\ $\BB$ consists of all the
-Boolean functions $f_i[n] : \{0,1\}^n \rightarrow \{0,1\}$ where $n \in \nats$,
-$i \in [k]$, and $f_i[n]$ is the restriction of $f_i$ to strings of length $n$.
-In other words $\langle f_1, \ldots , f_k \rangle$ is the union of $\{f_i[n] : n
-\in \nats\}$ for each $f_i$ in the generating sequence. We have $\AND, \OR,
-\NAND, \MAJ : \{0,1\}^* \rightarrow \{0,1\}$, where $\AND, \OR, \NAND$ are the
-usual (unbounded fan-in) logical operators, and $\MAJ$ is the majority function
-(i.e.\ the function that outputs one if more than half of bits in the inputs are
-one). We write $\BS := \langle \AND, \OR, \NAND\} \rangle$ to denote the
-\emph{standard basis} and $\BM := \langle \AND, \OR, \NAND , \MAJ \rangle$ to
+It the literature a basis is usually taken to be a finite sequence of
+(symmetric) functions from $\{0,1\}^*$ to $\{0,1\}$. In this paper we depart
+slightly from this definition, and instead define a \emph{Boolean basis} (or
+\emph{basis}) to be a (potentially infinite) set of finite Boolean functions. We
+always denote a basis by $\BB$. We note that any function $f:\{0,1\}^* \ra
+{0,1}$ is uniquely defined by a set of functions $\{f[n] : n \in \nats\}$, where
+for all $n \in \nats$, $f[n]:\{0,1\}^n \ra \{0,1\}$ is the restriction of $f$ to
+input strings of length $n$. It follows that any finite sequence of such
+functions defines a basis given by taking the union of the associated sets of
+finite functions. We denote the basis \emph{generated} by a sequence of
+functions $f_1, \ldots, f_k : \{0,1\}^* \ra \{0,1\}$ by $\langle f_1, \ldots,
+f_k \rangle := \bigcup_{i \in [k]} \{f_i[n] : n \in \nats\}$.
+
+Given some of the generalisations used in this paper, we find it more convenient
+to work over infinite sets of finite functions rather than the (equivalent)
+unbounded fan-in functions. As such, we associate the usual logical operators
+with infinite families of functions rather than a single unbounded fan-in
+function. For each $n \in \nats$ we let $\AND[n], \OR[n], \NAND[n], \MAJ[n] :
+\{0,1\}^n \rightarrow \{0,1\}$ be the usual logical operators, and with
+$\MAJ[n]$ being the majority function for input strings of length $n$ (the
+majority function outputs a one if, and only if, more than half of bits in the
+inputs string are ones). We let $\AND := \{\AND[n] : n \in \nats\}$, and define
+$\OR$, $\NAND$ and $\MAJ$ similarly. We write $\BS := \AND \cup \OR \cup \NAND
+\cup \MAJ$ to denote the \emph{standard basis} and $\BM := \BS \cup \MAJ$ to
 denote the \emph{majority basis}.
@@
 \begin{definition}
-  Let $(C_n)_{n \in \mathbb{N}}$ be a family of Boolean circuits. We say that
-  $(C_n)_{n \in \mathbb{N}}$ is \emph{$\PT$-uniform} if the mapping $n \mapsto
-  C_n$ is polynomial-time computable in $n$.
+  Let $(C_n)_{n \in \nats}$ be a family of Boolean circuits. We say that
+  $(C_n)_{n \in \nats}$ is \emph{$\PT$-uniform} if the mapping $n \mapsto C_n$
+  is polynomial-time computable in $n$.
 \end{definition}

### 2018-03-10 sections/conclusion.tex
A complete draft minus the conclusion. Large changes made to a number of sections.
I have been trying to improve the presentation of the translation of circuits into formulas. To this end, I have changed the notation we use to talk about the usual logical operators (e.g. AND, OR, NOT, etc). I have also added tried to simplify the writing, and better explain the approach taken when translating circuits into formulas. I am in the process of writing the conclusion, but there is so much to think about.

--- 2017-07-26 sections/conclusion.tex
@@
 \begin{document}
+
+The main result of this paper establishes an equivalence between the expressive
+power of $\FPR$ and the computational power of $\PT$-uniform transparent
+symmetric rank-circuits, generalising a similar result by Anderson and
+Dawar~\cite{AndersonD17}. Our motivation for proving this characterisation  The hope is that this characterisation will
+contribute to our understanding of one of the two candidate logics for capturing
+$\PT$.
+
+% In the quest for a logic that captures polynomial time
+
+% At the time of writing there are two candidate logics which Recent work on the
+% problem of capturing $\PT$ has produced two `candidate' logics for capturing
+% polynomial-time. In this paper we extend Anderson and Dawar's symmetric
+% circuit characterisation of $\FPC$, showing that $P$-uniform families of
+% transparent symmetric circuits with rank gates have the same expressive power
+% as $\FPR$. Since $\FPR$ remains one of the two c the candidate logics for
+% capturing $\PT$, along with choiceless polynomial time,
 \end{document}

### 2018-03-10 sections/symmetric-circuits.tex
I have been trying to improve the presentation of the translation of circuits into formulas. To this end, I have changed the notation we use to talk about the usual logical operators (e.g. AND, OR, NOT, etc). I have also added tried to simplify the writing, and better explain the approach taken when translating circuits into formulas. I am in the process of writing the conclusion, but there is so much to think about.

@@
 % matrix-invariant.
-We now discuss a few Boolean basis of interest in this paper and state the main
-result. In most cases (e.g.\ \cite{}) a Boolean basis is taken to be a finite
-sequence of symmetric Boolean functions. A binary encoding of a circuit defined
-over such a basis is given by assigning to each element of the basis a unique
-symbol, and then encoding the circuit in the obvious manner. Since there are
-only a finite number of basis elements, it follows that if each basis element
-can be computed in polynomial time then the mapping that takes a symbol $s$ and
-a string $\vec{x}$ to the value of the function denoted by $s$ for input
-$\vec{x}$ can be decided in polynomial-time. We call this function the
-\emph{gate evaluation function}, and note that its polynomial-time decidability
-is required for proving the polynomial-time evaluation of the circuit. However,
-in order to allow for the inclusion of structured (possibly non-symmetric)
-functions in the basis, we have instead defined a basis to be a (possibly
-infinite) set of finite Boolean functions. In this case the gate evaluation
-function may not even be decidable, let alone polynomial-time decidable.
+
+Before we state the main result of this paper we need to discuss the Boolean
+bases of interest in this paper and introduce some useful terminology. In most
+other contexts a basis is taken to be a finite sequence of symmetric Boolean
+functions, and a binary encoding of a circuit may is given by assigning to each
+element of the basis a unique symbol, and then encoding the circuit as a
+labelled DAG. Moreover, since there are only a finite number of basis elements,
+it follows that if each function in the basis can be computed in polynomial time
+then the mapping that takes a symbol $s$ and a string $\vec{x}$ to the value of
+the function denoted by $s$ for input $\vec{x}$ can also be decided in
+polynomial-time. We call this function the \emph{gate evaluation function}. It
+is easy to see that the gate evaluation function is polynomial-time computable
+if, and only if, the a given circuit can be evaluated in polynomial-time. It is
+here our that our definition of a basis introduces a complication. In order to
+allow for the inclusion of structured (possibly non-symmetric) functions in the
+basis, we have instead defined a basis to be a (possibly infinite) set of finite
+Boolean functions. In this case the gate evaluation function may not even be
+decidable, let alone polynomial-time decidable.
 
@@
   Let $\BB$ be a basis. Let $S$ be a set of symbols and let $F : \BB \rightarrow
-  S$ be a bijection. We say $\BB$ is \emph{effective} if the function $E$ that
-  maps a symbol $s$ and an input $x \in \dom(F(s))$ to the value
-  $(F^{-1}(s))(x)$ is decidable. We say $\BB$ is \emph{$\PT$-effective} if $E$
-  is polynomial-time decidable.
+  S$. We say $\BB$ is \emph{effective} if the function $E$ that maps a symbol
+  $s$ and an input $x \in \dom(F(s))$ to the value $(F^{-1}(s))(x)$ is
+  decidable. We say $\BB$ is \emph{$\PT$-effective} if $E$ is polynomial-time
+  decidable.
 \end{definition}
@@
 
-Let $n \in \nats$, we have that $\AND[n] : \{0,1\}^{[n]} \rightarrow \{0,1\}$ is
-the restriction (as a structured function) of the $\AND$ function to inputs of
-size $n$. Similarly, we have that $\OR[n]$, $\NAND[n]$ and $\MAJ[n]$ are the
-restrictions of these respective functions to strings of length $n$. We let
-$\NOT: \{0,1\} \ra \{0,1\}$ be the not function, and we often identify $\NOT$
-with $\NAND[1]$. In each case we use the name of the function as the symbol
-denoting that function.
-
-As such, the standard basis $\BS$ consists of the functions $\NAND[n]$,
-$\AND[n]$, and $\OR[n]$ for every $n \in \nats$, and the majority basis is $\BM
-:= \BS \cup \{\MAJ[n] : n \in \nats\}$. We often use $\NAND[1]$ and $\NOT$
-interchangeably. We say a basis $\BB$ is \emph{symmetric} if every function in
-$\BB$ is a symmetric Boolean function.
+We recall from Section~\ref{sec:background} that the standard basis $\BS$
+consists of the functions $\NAND[n]$, $\AND[n]$, and $\OR[n]$ for every $n \in
+\nats$, and that the majority basis $\BM := \BS \cup \{\MAJ[n] : n \in \nats\}$.
+When encoding a circuit over either of these bases we abuse notation and use the
+name of the function as the symbol denoting that function (e.g.\ the function
+$\AND[n]$ is associated with the symbol $\AND[n]$).
 
@@
 with universe $[a] \uplus [b]$, such that $\RANK^r_p[a,b](M) = 1$ if, and only
-if, the matrix $M \in \{0,1\}^{[a] \times [b]}$ has rank at most $r$ over $\ff_p$
-when the entries of $M$ are interpreted as elements of $\mathbb{F}_p$. We
-identify the function $\RANK^{r}_p[a,b]$ with the symbol $\RANK^{r}_p[a,b]$.
-
+if, the matrix $M \in \{0,1\}^{[a] \times [b]}$ has rank at most $r$ over
+$\ff_p$ when the entries of $M$ are interpreted as elements of $\mathbb{F}_p$.
+We associate the function $\RANK^{r}_p[a,b]$ with the symbol $\RANK^{r}_p[a,b]$.
 Let $\RANK = \{\RANK^{r}_p[a,b] : a, b, r, p \in \nats, \text{ $p$ prime}\}$ and
-let the \emph{rank basis} be $\RB := \BM \cup \RANK$. We say a basis $\BB$ is
-\emph{matrix-symmetric} if every function in $\BB$ is symmetric or
-matrix-symmetric. It is easy to see that the standard basis, the majority basis,
-and the rank basis are all $\PT$-effective.
+let the \emph{rank basis} be $\RB := \BM \cup \RANK$. It is easy to see, given
+the encoding of the basis, that the standard, majority and rank basis are all
+$\PT$-effective.
+
+We say a basis $\BB$ is \emph{symmetric} if every function in $\BB$ is symmetric
+and we say $\BB$ is \emph{matrix-symmetric} if every function in $\BB$ is
+symmetric or matrix-symmetric. Let $T_{\rank} := \{\AND, \NAND, \OR, \MAJ,
+\RANK\}$. We say that $f \in \RB$ has \emph{type} $t \in T_{\rank}$ if $F \in
+t$.
 
@@
 \emph{matrix-symmetric gate} if $\Sigma(g)$ is a matrix-symmetric structured
-function. We say that $g$ is an \emph{$\AND$-gate} if $\Sigma(g) := \AND[a]$ for
-some $a \in \nats$. Similarly we define an \emph{$\OR$-gates},
-\emph{$\NAND$-gate} \emph{$\NOT$-gates}, \emph{$\MAJ$-gates}, and
-\emph{$\RANK$-gates}.
+function. We say that $g$ has \emph{type} $t \in T_{\rank} \uplus \rho \uplus$
+if $g$ is an input gate and $\Sigma (g) = t$ or $g$ is an internal gate and
+$\Sigma (g)$ has type $t$. If $g$ has type $t$ we say $g$ is a $t$-gate (e.g.\
+if $g$ has type $\AND$ we call it an $\AND$-gate). It is easy to see that the
+function that maps a circuit and a gate to (a symbol denoting) the type of the
+gate is polynomial-time computable.
 
@@
 \begin{thm}[Main Theorem]
-  A graph property is decidable by a $P$-uniform family of transparent symmetric
-  rank-circuits if, and only if, it is definable by an $\FPR$ sentence.
+  A graph property is decidable by a $\P$-uniform family of transparent
+  symmetric rank-circuits if, and only if, it is definable by an $\FPR$
+  sentence.
 \end{thm}
@@
 such circuits whether we include \emph{all} symmetric functions in the basis or
-just $\BM$. It follows that in order to construct $P$-uniform families of
+just $\BM$. It follows that in order to construct $\P$-uniform families of
 symmetric circuits that define queires not in $\FPC$, we need to consider bases
@@
   decides the same language. Moreover, the map $C_n \mapsto C_n'$ is
-    polynomial-time computable and for each $n \in \nats$, $\vert C_n' \vert
-    \leq (5 \cdot \vert C_n \vert + 3) \cdot \vert C_n \vert$.
+  polynomial-time computable and for each $n \in \nats$, $\vert C_n' \vert \leq
+  (5 \cdot \vert C_n \vert + 3) \cdot \vert C_n \vert$.
 \end{thm}

### 2018-03-23 sections/background.tex
Minor revisions to Sections 1 and 2.

@@
 \emph{many-sorted vocabulary} is a tuple of the form $(R, S, \nu)$, where $R$ is
-a relational vocabulary, $S$ is a finite sequence of \emph{sort} symbols $(s_1,
-\ldots s_p)$, and $\nu$ is a function that assigns to each $R_i \in R$ a tuple
-$\nu(R_i) := (s^i_1, \ldots, s^i_{r_i})$, where for each $j \in [r_i]$, $s^i_j
+a relational vocabulary, $S$ is a finite sequence of \emph{sort} symbols, and $\nu$ is a function that assigns to each $R_i \in R$ a tuple
+$\nu(R_i) := (s_1, \ldots, s_{r_i})$, where for each $j \in [r_i]$, $s_j
 \in S$.  We call $\nu$ the \emph{\type function} and $\nu(R_i)$ the \emph{type}
-of $R_i$. We notice that a relational vocabulary can be thought of as a
-single-sorted vocabulary, i.e. a many-sorted vocabulary where the set of sorts
+of $R_i$.  We note that a relational vocabulary can be thought of as a
+single-sorted vocabulary, i.e.\ a many-sorted vocabulary where the set of sorts
 is a singleton. As such, if $\tau := (R, S, \nu)$ is single-sorted we identify
@@
 Let $\tau := (R, S, \nu)$ be a many-sorted vocabulary, where $R = (R_1, \ldots,
-R_k)$ and $S = (s_1, \ldots , s_p)$ A \emph{$\tau$-structure} $\mathcal{A}$ is a
+R_k)$ and $S = (s_1, \ldots , s_p)$.  A \emph{$\tau$-structure} $\mathcal{A}$ is a
 tuple $(U , R^{\mathcal{A}}_1 , \ldots , R^{\mathcal{A}}_k)$ where $U =
@@
 \subseteq R^{\mathcal{A}}_i \subseteq U_{s^i_1} \times \ldots \times
-U_{s^i_{r_i}}$, where $(s^i_1 , \ldots , s^i_{r_i}) = \nu (R_i)$. The size of
+U_{s_{r_i}}$, where $(s_1 , \ldots , s_{r_i}) = \nu (R_i)$. The size of
 $\mathcal{A}$, denoted by $\vert \mathcal{A} \vert$ is the cardinality of its
 universe.  The \emph{sorted-size} of $\mathcal{A}$ is a vector $\vec{n} :=
-(n_{s_1}, \ldots , n_{s_p}) \in \mathbb{N}^{p}$ such that $\vert U_{s_i} \vert =
-n_{s_i}$ for all $i \in [p]$. We say $a \in U$ has \emph{sort} $s \in S$ if $a
+(n_{s})_{s \in S} \in \mathbb{N}^{S}$ such that $\vert U_{s} \vert =
+n_{s}$ for all $s \in S$. We say $a \in U$ has \emph{sort} $s \in S$ if $a
 \in U_s$.
@@
 and then closing the set of atomic formulas under the Boolean connectives,
-negation, and universal and existential quantification (i.e. $\land$, $\lor$,
+negation, and universal and existential quantification (i.e.\ $\land$, $\lor$,
 $\neg$, $\forall$, and $\exists$).
@@
 other words, $\FP[\tau]$ includes all formulas in $\FO[\tau]$, and is closed
-under applications of the fixed-pint operator, i.e. if $\phi \in \FP[\tau]$, $V$
+under applications of the fixed-pint operator, i.e.\ if $\phi \in \FP[\tau]$, $V$
 is a second-order variable, and $\vec{x}$ is a tuple of variables of length
@@
 assignments $\alpha$ and $\beta$ are \emph{compatible} if $\alpha$ and $\beta$
-agree on the intersection of their domain. We write $\mathcal{A} \models_L
+agree on the intersection of their domains.  We write $\mathcal{A} \models_L
 \phi[\alpha]$ if, and only if, $\phi$ is true in $\mathcal{A}$ with respect to
@@
 $\FP[\tau]$. Number variables are assigned to elements of $\nats$. We usually
-use Latin letters (e.g. $x, y, z, \ldots$) to denote vertex variables and Greek
-letters (e.g. $\mu, \nu, \epsilon, \ldots$) to denote number variables. All
+use Latin letters (e.g.\ $x, y, z, \ldots$) to denote vertex variables and Greek
+letters (e.g.\ $\mu, \nu, \epsilon, \ldots$) to denote number variables. All
 atomic formulas in $\FP[\tau]$ are atomic formulas in $\FPC[\tau]$. We say that
 $t$ is a \emph{number term} if $t$ is a number variable or if $t$ is an application
-of the \emph{counting operator}, i.e. $t = \#x. \phi(x)$, where $\phi \in
-\FPC[\tau]$ and $x$ is a vertex variable free in $\phi$. If $t_1$ and $t_2$ are
+of the \emph{counting operator}, i.e.\ $t = \#x. \phi(x)$, where $\phi \in
+\FPC[\tau]$ and $x$ is a vertex variable. If $t_1$ and $t_2$ are
 number terms then $t_1 \leq t_2$ and $t_1 = t_2$ are atomic formulas.
@@
 variables, such as those that appear in an application of the fixed-point
-operator, are allowed to have mixed-type, i.e. we associate with a second-order
+operator, are allowed to have mixed-type, i.e.\ we associate with a second-order
 variable $R$ a type $(k, l) \in \nats^2$ intended to mean that $R$ is assigned
@@
 quantification. In other words, if $Q \in \{\forall, \exists \}$, $\phi \in
-\FPC[\tau]$, $\mu$ is a number variable free in $\phi$, and $t$ is a number
+\FPC[\tau]$, $\mu$ is a number variable, and $t$ is a number
 term, then $Q \mu \leq t . \phi$ is a formula of $\FPC[\tau]$. Similarly, if
@@
 % of numeric variables and $\vec{\mu}$ is a $k$-tuple of closed numeric term
-% (i.e. ones without any free variables) then $\exists \vec{x} \leq \vec{\mu}
+% (i.e.\ ones without any free variables) then $\exists \vec{x} \leq \vec{\mu}
 % \phi(\vec{x})$ and $\forall \vec{x} \leq \vec{mu} \phi(\vec{x})$ are formulas.
@@
 \emph{number term} if $t$ is a number variable or if $t$ is an application of
-the \emph{rank operator}, i.e. $t = [\rank (\vec{x}, \vec {\nu} \leq \vec{t},
-\vec{y}\vec{\mu} \leq \vec{s}, \pi \leq \eta). \phi]$, where $\phi$ is a number
+the \emph{rank operator}, i.e.\ $t = [\rank (\vec{x}, \vec {\nu} \leq \vec{t},
+\vec{y},\vec{\mu} \leq \vec{s}, \pi \leq \eta). \phi]$, where $\phi$ is a number
 term, $\vec{t}$ and $\vec{s}$ are tuples of number terms bounding the sequences
@@
 the case of $\FPC$, the second-order variables may have mixed-type and we only
-allow bounded quantification for number variables. We note additionally that
-formulas may be treated as number terms that evaluate to zero or one.
+allow bounded quantification for number variables. 
+%AD (23/3/18): I didn't understand the following sentence, so I've taken it out,
+%as it does not seem to add anything
+%We note additionally that
+%formulas may be treated as number terms that evaluate to zero or one.
 
@@
 that $\vert \vec{s} \vert = \vert \vec{\nu} \vert$ $\vert \vec{t}\vert = \vert
-\vec{mu} \vert$. Let $\pi$ be a number variable and $r$ be a number term. Let
+\vec{mu} \vert$. Let $\pi$ be a number variable and $r$ be a number
+term.  Let
 $\mathcal{A}$ be a structure with universe $A$, and suppose we have a given
-assignment to the those free variables appearing in $r$ or in the terms in
+assignment to the variables appearing free in $r$ or in the terms in
 $\vec{t}$ and $\vec{s}$.  Let $\mathbb{N}^{\leq\vec{t}} := \{\vec{n} \in
@@
 r^{\mathcal{A}}$, if $p$ is prime then the rank term $[\rank (\vec{x}, \vec
-{\nu} \leq \vec{t}, \vec{y}\vec{\mu} \leq \vec{s}, \pi \leq r). \phi]$ is the
+{\nu} \leq \vec{t}, \vec{y},\vec{\mu} \leq \vec{s}, \pi \leq r). \phi]$ is the
 rank of $M^{\mathcal{A}}_\phi$ mod $p$, where the entries in $M^{\mathcal{A}}$
@@
 Pakusa~\cite{GradelP15a} that this non-uniform rank logic does not capture
-$\PT$. After proving this result, Grad{\"e}l and Pakusa introduced the rank
-logic with a uniform rank operator that we have presented above, and showed that
-this rank logic is strictly more expressive then the rank logic introduced by
-Dawar et al. This uniform rank logic remains a candidate for capturing
+$\PT$.  Instead they propose the rank
+logic with a uniform rank operator that we have presented above, and show that
+this rank logic is strictly more expressive then the version
+introduced in~\cite{Dawar09logicswith}.  This uniform rank logic remains a candidate for capturing
 polynomial-time. For this reason when we refer to rank logic in this paper we
@@
 [n]^{\arty(R)}$, (ii) a set of internal gates, each labelled by an element of
-$\BB$, and (iii) a designated set of output gates, each labelled by a unique
-element of $[n]^q$.
+$\BB$, and (iii) a designated set of output gates with an injective
+map to this set from $[n^q]$.
 
@@
 is an element of $\{0,1\}^{[n]^q}$. In other words, a circuit maps a
-$\tau$-structure $\mathcal{A}$ and bijection $\gamma$ to a set of $q$-tuples in
-$\mathcal{A}$.
+$\tau$-structure $\mathcal{A}$ and bijection $\gamma$ to a $q$-ary
+relation on $\mathcal{A}$.
 
 A circuit is called \emph{invariant} if its output does not depend on the choice
-of $\gamma$. In this case the circuit defines a $q$-ary query on
-$\tau$-structures. If $C$ is an invariant circuit with $q = 0$, and the circuit
+of $\gamma$.  In this case the circuit defines a $q$-ary query on $n$-element
+$\tau$-structures and a family $(C_n)_{n\in\nats}$ defines a $q$-ary
+query on finite $\tau$-structures. If $C$ is an invariant circuit with $q = 0$, and the circuit
 has a single output gate, then $C$ decides a property of $\tau$-structures. A circuit
@@
 \begin{thm}[Anderson and Dawar~\cite{AndersonD17}]
-  For a relational vocabulary $\tau$, a property of finite $\tau$-structures is
-  decided by a P-uniform family of symmetric circuits defined over the basis
+  For a relational vocabulary $\tau$, a query on finite $\tau$-structures is
+  defined by a P-uniform family of symmetric circuits defined over the basis
   $\BM$ if, and only if, it is expressible in $\FPC[\tau]$.
@@
 Let $\sim_A$ be an equivalence relation on $A$ defined such that $\vec{a} \sim_A
-\vec{b}$ if, and only if, $\vec{a}(i) = \vec{b}(i)$ for all $i \in J$. We call
+\vec{b}$ if, and only if, $\vec{a}(i) \sim \vec{b}(i)$ for all $i \in J$. We call
 $\sim_A$ the \emph{extension} of $\sim$ to $A$. We often abuse notation and
@@
 
-Let $Y$ and $Z$ be sets and let $f : Y \rightarrow Z$ be a function. We say $f$
+Let $Y$ and $Z$ be sets on which extensions $\sim_Y$ and $\sim_Z$ of
+$\sim$ have been defined and let $f : Y \rightarrow Z$ be a function.  We say $f$
 is \emph{invariant} under $\sim$ if for all $a, b \in Y$ if $a \sim_Y b$ then

### 2018-03-23 sections/introduction.tex
Minor revisions to Sections 1 and 2.

@@
 property that their lack of redundancy is transparent.  We explore
-this condition and its consequences in Section~\ref{sec:transparent}.
+this condition and its consequences in Section~\ref{sec:transparent},
+where we also demonstrate that something like this requrement is
+necessary.  Natural weakenings of this requirement yield circuits in
+which deciding symmetry seems hard.
 
@@
 details are presented in Section~\ref{sec:formulas-to-circuits}.
-Finally, with all the tools in place, the translation of such
+Finally, with all these tools in place, the translation of such
 $\PT$-uniform families of circuits into formulas of $\FPR$ given in Section~\ref{sec:circuits-to-formulas} completes
-the characterization.
-
-\begin{remark}
-G: Should we also talk about the fact that the work done in
-Section~\ref{sec:circuits-to-formulas} is also novel?
-\end{remark}
+the characterization.  This still requires substantial new
+techniques.  The translation of circuits to formulas
+in~\cite{AndersonD17} relies on the fact that in order to evaluate a
+gate computing a symmetric Boolean function, it suffices to count the number
+of inputs that evaluate to true and there is a bijection between the
+orbits of a gate and tuple assignments to its support.  When counting
+is no longer sufficient, this bijection has to preserve more structure
+and demonstrating this in the case of matrices requires new insight.
 

### 2018-03-26 sections/symmetric-circuits.tex
Minor revisions to Sections 3 and 4.

@@
 
-As our aim is a circuit characterisation of $\FPR$, whose expressive power is
+As our ultimate aim is a circuit characterisation of $\FPR$, whose expressive power is
 strictly greater than that of $\FPC$, we need to consider gates corresponding to
@@
 $\tau$-structures and where the output is invariant under the natural symmetries
-of such structures. The\emph{matrix-invariant} functions are a natural
-partiruclar case. We therefore define symmetric circuits in a general form where
+of such structures. The \emph{matrix-invariant} functions (defined
+formally below) are a natural
+particular case. We therefore define symmetric circuits in a general form where
 gates can be labelled by \emph{isomorphism-invariant} structured functions.
 
-Ultimately, our aim is replicate the results Anderson and
+Ultimately, our aim is to replicate the results Anderson and
 Dawar~\cite{AndersonD17} in this more general setting. A difficulty we face is
@@
   \in S} D_{s} = \{(s,d) : d \in D_s\}$, be a disjoint union of non-empty sets,
-indexed by $S$. For $R_i \in R$ let $R^D_i$ denote the trivial relation over the
+indexed by $S$. For $R_i \in R$ let $R^D_i$ denote the full relation over the
 many-sorted universe $D$, i.e.\ $R^D_i := D_{a_1} \times \ldots \times
@@
 interpretation of $\tau$ over $D$ given by assigning each sort symbol $s$ in
-$\tau$ to the set $D_s$ and each relation symbol in $\tau$ to the trivial
+$\tau$ to the set $D_s$ and each relation symbol in $\tau$ to the full
 relation over $D$. We call this \emph{the structure defined by $(\tau, D)$}, and
@@
 many-sorted set $D := \biguplus_{s \in S} D_{s}$. Let $X := \ind (\tau, D)$ and
-$G \leq \sym_{X}$. We note that $G$ there is an obvious group action of $G$ on
+$G \leq \sym_{X}$. We note that there is an obvious group action of $G$ on
 $X$. Let $\aut (\tau, D)$ be the automorphism group of $\str{\tau, D}$. We
@@
 D)$-invariant. Note that a structured function with vocabulary $\tau$ is
-isomorphism-invariant if, and only if, it decides a property of
+isomorphism-invariant if, and only if, it determines a property of
 $\tau$-structures.
@@
     \setlength\itemsep{0mm}
-  \item $G$ is called the set of gates of $C$ and $\vert C \vert := \vert G
-    \vert$.
+  \item $G$ is called the set of gates of $C$.% and $\vert C \vert := \vert G    \vert$.
   \item $\Omega$ is an injective function from $[n]^q$ to $G$. The gates in the
@@
     are called input gates, with those mapped to $\rho$ called relational gates
-    and those mapped $\{0,1\}$ called constant gates. Those gates mapped to
+    and those mapped to $\{0,1\}$ called constant gates. Those gates mapped to
     $\mathbb{B}$ are called internal gates.
@@
 \end{definition}
+
+The definition requires some explanation.  Each gate in $G$ computes a
+function of its inputs and the relation $W$ on $G$ is the set of
+``wires''.  That is, $W(h,g)$ indicates that the value computed at $h$
+is an input to $g$.  However, since the functions are structured, we
+need more information on the set of inputs to $g$ and this is provided
+by the labelling $L$.  $\Sigma(g)$ tells us what the function computed
+at $g$ is, and thus $\ind(\Sigma(g))$ tells us the structure on the
+inputs and $L(g)$ maps this to the set of gates that form the inputs
+to $g$.
 
@@
 Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
-\rho)$-circuit of order $n$. The order of a circuit denotes the fact that it
-takes as input structures of size $n$. If $(C_n)_{n \in \nats}$ is a family of
+\rho)$-circuit of order $n$.  Recall that the orde of a circuit refers
+to the size of the input structures it takes.  In contrast, we define
+the \emph{size} of $C$, denoted $\vert C \vert$ to be the number of
+elements in $G$. If $(C_n)_{n \in \nats}$ is a family of
 circuits we assume that each $C_n$ is a circuit of order $n$.
@@
   We now present a number of observations, and then combine these observations
-  to prove both directions of the hypothesis. Let $\mathcal{B}$ be a
+  to prove both directions of the lemma. Let $\mathcal{B}$ be a
   $\rho$-structure of size $n$ over the universe $[n]$. We can define a function
@@
   it follows that for $\gamma \in \sym_n$ we have that $F_C (f_{\gamma
-    \mathcal{A}})$ if, and only if, $C[\gamma \mathcal{A}](g_{\text{o}}) = 1$.
+    \mathcal{A}})=1$ if, and only if, $C[\gamma \mathcal{A}](g_{\text{o}}) = 1$.
 
@@
 
-\begin{definition}[Automorphism]
-  let $C = \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a
-  $(\mathbb{B},\tau)$-circuit of order $n$ computing a $q$-ary, and where
+\begin{definition}[Automorphism]\label{defn:automorphism}
+  Let $C = \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a
+  $(\mathbb{B},\tau)$-circuit of order $n$ computing a $q$-ary query, and where
   $\mathbb{B}$ is a basis of isomorphism-invariant structured functions. Let
@@
 does not contain a relational gate labelled by a relation symbol with non-zero
-arity. In that case $C$ computes a constant function. As such, in this paper we
+arity.  In that case $C$ computes a constant function.  For this reason, in this paper we
 always assume a circuit contains at least one relational gate with non-zero
-arity. As such by assumption there exists a relational gate in $C$ such that
+arity.  Now, by assumption there exists a relational gate in $C$ such that
 some element of $[n]$ appears in the tuple labelling that gate.  By symmetry it
@@
 of this form.  It is at this point that we arrive at the first complication
-introduced by our generalisation. Anderson and Dawar's polynomial-time
-translation makes indispensable of the polynomial-time decidability of many
-important circuit properties for circuits defined over symmetric bases. However,
+introduced by our generalisation. The polynomial-time
+translation in~\cite{AndersonD17} makes indispensable of the polynomial-time decidability of many
+important circuit properties for circuits defined over symmetric
+bases.  However,
 for the more general circuits discussed here, it is not known if even the most
-basic circuit properties are polynomial-time decidable. Indeed, we show in
+basic circuit properties are polynomial-time decidable.  This is
+essentially due to the requirement built in to
+Definition~\ref{defn:automorphism} that an automorphism that takes $g$
+to $g'$ must be an isomorphism between $L(g)$ and $L(g')$, which makes
+checking the condition as hard as isomorphism checking.
+Indeed, we show in
 Section~\ref{sec:transparent} that for circuits that include gates computing
@@
 at least as hard to decide as the graph-isomorphism problem. As such,
-constructing an analogous argument, as well as establishing the numerous other
+constructing an argument analogous to~\cite{AndersonD17}, as well as establishing the numerous other
 crucial results whose proofs rely on the polynomial-time decidability of various
@@
 is that two gates in a circuit are syntactically-equivalent if the circuits
-underneath them are `hereditary equivalent', i.e.\ the two circuits underneath
+underneath them are `hereditarily equivalent', i.e.\ the two circuits underneath
 these gates are really just copies of one another.
@@
   or both are relational gates and $\Lambda(g) = \Lambda (h)$.  Suppose $g$ and
-  $h$ are internal gates and and suppose we have defined the
+  $h$ are internal gates and suppose we have defined the
   syntactic-equivalence relation for all gates of depth less than the depth of
@@
 
-For a circuit $C$ of order $n$ and a gate $g$ we map think of $g$ as computing
+For a circuit $C$ of order $n$ and a gate $g$ we think of $g$ as computing
 the function that maps an input structure $\mathcal{A}$ and a bijection $\gamma$
 from the universe of $\mathcal{A}$ to $[n]$ to the evaluation $C[\gamma
-\mathcal{A}(g)$. While we would like to be able to identify gates that compute
+\mathcal{A}(g)]$. While we would like to be able to identify gates that compute
 the same function in this sense, it is not hard to show that deciding this
@@
   in $C$, $\Sigma (g) = \Sigma (\pi (g)) = \Sigma (\pi' (g))$, and either all of
-  $g$, $\pi (g)$ and $\pi (g')$ are output gates and $\pi \Omega
+  $g$, $\pi (g)$ and $\pi (g')$ are output gates and $\pi (g) = \pi \Omega
   (\Omega^{-1}(g)) = \Omega (\sigma \Omega^{-1}(g)) = \pi' \Omega
-  (\Omega^{-1})$, or none of $g$, $\pi(g)$ or $\pi' (g)$ are output gates.
+  (\Omega^{-1}(g)) = \pi'(g)$, or none of $g$, $\pi(g)$ or $\pi' (g)$ are output gates.
 
@@
   \emph{unique labels} if $g$ has injective labels and unique children. We say
-  $C$ has \emph{injective labels} (resp. \emph{unique labels}) if every gate in
-  $C$ has injective labels (resp. unique labels). We say $C$ is
+  $C$ has \emph{injective labels} (resp.\ \emph{unique labels}) if every gate in
+  $C$ has injective labels (resp.\ unique labels). We say $C$ is
   \emph{transparent} if every gate $g$ in $C$ such that $\Sigma(g)$ is not a
@@
 
-It is worth noting that if a circuit has injective labels and is reduced then
+It is worth noting that if a circuit has injective labels and is reduced 
 then it has unique labels. The converse is, in general, false.
@@
 is no path from this gate to any of the output gates. In other words, we can be
-sure, not matter the rest of the circuit, that any such gate cannot have any
+sure, no matter the rest of the circuit, that any such gate cannot have any
 effect the function computed by the circuit. We say these gates are
@@
 Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a circuit of order
-$n$ and let $g$ be a redundant circuit in $C$. It is easy to see that $g$ is not
+$n$ and let $g$ be a redundant gate in $C$.  It is easy to see that $g$ is not
 the child of a non-redundant gate, nor is it a relational or output gate. Thus
@@
 that witness the isomorphism-equivalences, and so witness the validity of the
-automorphism, are also uniquely defined (or, at least very least, well
+automorphism, are also uniquely defined ( or, at the very least, well
 constrained) by the permutation $\sigma$. Without a sufficient constraint on the
@@
 between two gates is as hard as the graph-isomorphism problem. It follows that a
-great many important circuit properties (e.g. the orbit of a gate, symmetry of a
+great many important circuit properties (e.g.\ the orbit of a gate, symmetry of a
 circuit, etc.) for circuits with unique gates are at the very least not
@@
   symmetric circuit $C$ defined over the basis $\BM$ that computes $F$.
-  Moreover, this function is computable in time polynomial in $n$ and the
+  Moreover, this algorithm runs in time polynomial in $n$ and the
   circuit $C$ has depth at most $5$, width at most $2n+2$ and size at most $5n +

### 2018-03-28 sections/translating-formulas-to-cicuits.tex
A complete draft minus the conclusion. Large changes made to a number of sections.
I have made changes to the section "symmetric circuits" and updated every other section in line with changes made.
minor revisions to Sections 6 and 7

@@
   Let $\tau$ be the vocabulary of $\theta(\vec{x})$. Let $k := \width(\theta)$.
-  Suppose $\tau$ is empty. Since $\tau$, the vocabulary of $\theta$, is empty,
+  Suppose first that $\tau$ is empty, so
   all of the atomic formulas in $\theta(\vec{x})$ are of the form $y_1 = y_2$,
@@
   \Lambda, L \rangle$, where
-  \begin{itemizens}
+  \begin{myitemize}
   \item $G = \{g_0, g_1\} \cup \{g_{\vec{a}} : \vec{a} \in [n]^{k}\}$,
   \item $\Sigma (g_0) = 0$, $\Sigma (g_1) = 1$ and $\Sigma (g_{\vec{a}}) =
-    \land[1]$ for all $\vec{a} \in [n]^k$,
+    \AND[1]$ for all $\vec{a} \in [n]^k$,
   \item $\Omega : [n]^k \rightarrow G$ is defined by $\Omega(\vec{a}) =
@@
     by $L(g_{\vec{a}})(1) = g_{f(\vec{a})}$.
-  \end{itemizens}
+  \end{myitemize}
 
@@
 
-  Suppose $\tau$ is not empty. Let $R \in \tau$. We first define two helper
+  Suppose now $\tau$ is not empty.  We first define a transformation
+  of the formula $\theta$ to an equivalent formula $\lambda$ which has
+  the property that the \emph{natural} translation of $\lambda$ to a
+  circuit (given later) is transparent.
+Let $R \in \tau$.  We first define two helper
   formulas. For a variable $y$ let $\op{no-op}(y) := (R(y, y) \lor (\neg R(y,
@@
   $\op{tag} (\vec{y}) := (\op{no-op}(y_1) \land (\op{no-op}(y_2) \land (
-  \op{no-op}(y_2) \land ( \ldots \land (\op{no-op}(y_m)) \ldots))))$. Let
-  $\lambda (\vec{x})$ be a formula constructed from $\theta(\vec{x})$ by
+  \op{no-op}(y_2) \land ( \ldots \land (\op{no-op}(y_m)) \ldots))))$.
+  Now, let  $\lambda (\vec{x})$ be the formula constructed from $\theta(\vec{x})$ by
   replacing each sub-formula $\psi(\vec{y})$ of the form $\rank^r_p \vec{w}
   \vec{z} . \phi$ with the formula $\rank^r_p \vec{w}\vec{z} . ((\forall u . u =
-  u) \land \phi) \land \op{tag}(\vec{w} \cup \vec{z})$. Since this process
-  involves inserting conjunctions of tautologies, the matrix defined at point
-  remains unchanged (i.e. $\phi \Leftrightarrow ((\forall u . u = u) \land \phi)
-  \land \op{tag}(\vec{w} \cup \vec{z})$ is a tautology), and so the evaluation
-  of $\psi(\vec{y})$ is unchanged by this replacement. It follows that $\lambda
+  u) \land \phi) \land \op{tag}(\vec{w} \cup \vec{z})$.  Since we
+  always replace a subformula $\phi$ with a logically equivalent
+  formula, it follows that $\lambda
   (\vec{x})$ and $\theta (\vec{x})$ are equivalent. The intuition is that
@@
 
-  \begin{itemizens}
+  \begin{myitemize}
   \item If $\psi[\alpha] = T(\vec{a})$ for some $T \in \tau$ and $\vec{a} \in
@@
   \item If $\psi$ is of the form $Q z . \phi(\vec{y}, z)$, for $Q \in \{\forall,
-    \exists\}$, then if $Q = \forall$ we have $\Sigma (g) = \land [n]$,
-    otherwise $\Sigma (g) = \lor [n]$. Let $L(g) : [n] \rightarrow G$ be defined
+    \exists\}$, then if $Q = \forall$ we have $\Sigma (g) = \AND[n]$,
+    otherwise $\Sigma (g) = \OR[n]$. Let $L(g) : [n] \rightarrow G$ be defined
     for $i \in [n]$ by $L(g)(i) = g_{\phi[\beta_i]}$, where $\beta_i \in
@@
   \item If $\psi$ is of the form $\phi_1 \land \phi_2$, then $\Sigma(g) =
-    \land[2]$ and $L(g) : [2] \rightarrow G$ is defined for $i \in [2]$ by
+    \AND[2]$ and $L(g) : [2] \rightarrow G$ is defined for $i \in [2]$ by
     $L(g)(i) = g_{\phi_i[\beta_i]}$, where $\beta_i \in [n]^{\free{\psi}}$ and
@@
     [1] \rightarrow G$ is defined by $L(g)(1) = g_{\phi[\alpha]}$.
-  \end{itemizens}
+  \end{myitemize}
 
@@
 
-We notice that $\vert C \vert \leq n^{\width(\lambda)} \vert \cl{\lambda} \vert
+We note that $\vert C \vert \leq n^{\width(\lambda)} \vert \cl{\lambda} \vert
 \leq n^{\width(\theta)} \vert \cl{\theta} \vert (5 + \width(\theta))$. It is not
@@
 
+  \begin{remark}
+    A: Need more specific references than the above.
+  \end{remark}
+
   We thus derive the required $\PT$-uniform family $(\theta_n(\vec{x}))_{n \in
@@
 
-\bibliography{../references.bib}
 % \ifcsdef{mainfile}{}{\bibliography{../references.bib}}

### 2018-03-30 sections/conclusion.tex
Major Updates to Section 5 (and a complete check of the first part of this section). Fixed a few typos in Section 3.

--- 2017-07-26 sections/conclusion.tex
@@
 \begin{document}
+
+The main result of this paper establishes an equivalence between the expressive
+power of $\FPR$ and the computational power of $\PT$-uniform families of
+transparent symmetric rank-circuits. This work generalises an analogous
+characterisation of the expressive power of $\FPC$ using $\PT$-uniform families
+of symmetric circuits (with symmetric gates) presented by Anderson and
+Dawar~\cite{AndersonD17}. Our initial intention in developing this
+characterisation was to provide an alternative approach for studying the
+expressive power of $\FPR$. Since $\FPR$ is one of the two candidate logics for
+capturing $\PT$, understanding its expressive power is a central question in the
+field. Our result establishes a correspondence between inexpressibly results for
+$\FPR$ and circuit lower bounds (for the specific circuit model discussed), and
+so enables the application of many of the well-developed tools for finding
+circuit lower bounds to the problem understanding the expressive power of
+$\FPR$.
+
+However, while this application is certainly promising, it is perhaps the
+developments required for the proof of the main result, rather than the result
+itself, that deserve the most attention. When we started to work on this problem
+we believed that a circuit characterisation for $\FPR$ would require little more
+than adding rank gates to Anderson and Dawar's symmetric circuits, and then
+modifying the support theorem and few other key results. However the definition
+of a circuit they use, and the definitions used in almost all of the literature,
+is incoherent if the basis over which the circuit is defined is allowed to
+include non-symmetric functions. Moreover, almost all of the key definitions
+introduced by Anderson and Dawar, as well as the proofs of all their major
+results, make implicit use this symmetry condition, and often in ways that make
+direct generalisation impossible.
+
+As such, in order to develop our characterisation we needed to begin at the
+bottom, generalising symmetric functions and a bases, defining a new kind of
+circuit that could be defined over such a basis, generalising key notions for
+this model, and then proving key results for the characterisation -- often from
+scratch. We introduced isomorphism-invariant structured functions as a
+generalisation of symmetric functions. While symmetric functions take in a
+string of bits and are invariant under permutations on this string,
+isomorphism-invariant structured functions take in (an encoding of) a structure
+and are invariant under the action of a permutation on the structure (i.e.\
+constant on isomorphism classes of structures). We developed a circuit model
+that can be defined over a basis of isomorphism-invariant structured functions,
+and generalised the necessary concepts (e.g.\ circuit automorphisms, symmetric,
+etc.) to these circuits. We used this frame work to define rank circuits, and so
+symmetric rank-circuits.
+
+It would be natural to take symmetric rank-circuits as the appropriate
+generalisation of Anderson and Dawar's symmetric circuits, and then hope to
+prove an equivalence between the expressive power of $\PT$-uniform families of
+such circuits and $\FPR$. However, this circuits pose a problem for our
+analysis. As we showed in Section~\ref{sec:transparent}, most of the properties
+of these rank-circuits are at least as hard to decide as the graph isomorphism
+problem. This poses a problem as the approach we take (and the approach Anderson
+and Dawar take) to proving this characterisation make repeated use of the
+polynomial-time decidability of these properties. Indeed, the two key results
+for translating $\PT$-uniform circuit families into equivalent formulas, the
+support theorem and the inductive evaluation of a gate (see
+Section~\ref{sec:circuits-to-formulas}), make use of polynomial-time algorithms
+for transforming a circuit into an equivalent circuit with unique labels, as
+well as for deciding if a circuit is symmetric, computing orbits, and deciding
+syntactic-equivalence.
+
+As such, we prove our characterisation in terms of $\PT$-uniform families of
+\emph{transparent} symmetric rank-circuits. Since all circuits with symmetric
+gates are transparent, transparent circuits provide us with an alternative,
+possibly more restrictive, generalisation of the circuits studied by Anderson
+and Dawar. Crucially, this generalisation preserves the polynomial-time
+decidability of the relevant circuit properties, and so allows us to define a
+translation from $\PT$-uniform families of transparent rank-circuits to
+equivalent formulas of $\FPR$. While the restriction to transparent circuits
+suffice for proving one direction of the proof, i.e.\ translating circuits into
+formulas, it complicates proving the other direction. It is not hard to see that
+the conventional approach for translating formulas of $\FO$ (or $\FPC$, or other
+extensions of $\FO$) into $\PT$-uniform families of circuits does not in general
+produce a family of transparent circuits. In order to address this we defined a
+novel translation from formulas of $\FPR$ to equivalent $\PT$-uniform families
+of transparent symmetric rank-circuits. This translation is defined in two
+steps, first we define a translation from $\FPR$ to $\PT$-uniform families of
+bounded-width formulas of $\FOrk$ and then we define a translation from these
+families of formulas into $\PT$-uniform families of transparent symmetric
+rank-circuits. This translation, along with the main result of the paper, gives
+us an equivalence between the expressive power of these three formalisms, which
+we summarise as follows:
+
+\begin{center}
+  \begin{tikzcd}
+    \FPR \ar[r, equal] \ar[dr, equal] & \text{$\PT$-uniform families of
+      bounded-width $\FOrk$-formulas}  \ar[d, equal]\\
+    & \text{$\PT$-uniform families of transparent symmetric rank-circuits}
+  \end{tikzcd}
+\end{center}
+
+We already have a very similar result from from Anderson and
+Dawar~\cite{AndersonD17} and Otto~\cite{}:
+
+\begin{center}
+  \begin{tikzcd}
+    \FPC \ar[r, equal] \ar[dr, equal] & \text{$\PT$-uniform families of
+      bounded-width $\FOc$-formulas}  \ar[d, equal]\\
+    & \text{$\PT$-uniform families of symmetric circuits with symmetric gates}
+  \end{tikzcd}
+\end{center}
+
+Notice that each of the formalisms used to characterise the expressive power of
+$\FPC$ can be extended by some mechanism for computing rank. In particular, we
+can extend $\FOc$ by rank quantifiers in a very natural way and define $\FOrk$,
+we can add rank gates to symmetric circuits with symmetric gates and define
+transparent symmetric rank-circuits, and we can extend $\FPC$ by a rank operator
+and define $\FPR$. Since each of these extensions is defined quite differently,
+we might expect these three extensions of $\FPC$ to have different expressive
+power. But from the above sets of equivalences we have that all of these models
+have equivalent expressive power. In particular, $\FPR$, an extension of $\FPC$,
+has the same expressive power as other natural extensions by rank of other
+models with the same expressive power as $\FPC$. This suggests that $\FPR$ is
+the natural extension of $\FPC$ by rank operators. In contrast the rank logic
+introduced by Dawar et al.~\cite{} was shown by Gr\"{a}del and Pakus~\cite{} to
+be strictly less expressive than $\FPR$, and hence less expressive than
+$\PT$-uniform families of bounded-width $\FOrk$ and $\PT$-uniform families of
+transparent symmetric rank-circuits. The results of this paper thus suggest that
+$\FPR$, rather than the rank logic of Dawar et al., should be considered the
+appropriate extension of $\FPC$ by rank.
+
+\subsection{Future Work}
+We have characterised $\FPR$ using $\PT$-uniform families of transparent
+symmetric rank-circuits. It is easy to see that $\PT$-uniform families of
+symmetric rank-circuits must be at least as powerful as $\PT$-uniform families
+of transparent symmetric rank-circuits, but we do not know if they have the same
+expressive power or are strictly more expressive. If the general circuit for a
+strictly more powerful model then the main result gives us that that $\FPR$ does
+not capture $\PT$. We have not proven it here, but we believe it is possible to
+show that if the graph isomorphism problem is in $\PT$ then these classes are
+equivalent. If this is shown, separating these circuit classes would imply graph
+isomorphism is not in $\PT$.
+
+There are also natural questions regarding generalisation. In this paper we have
+characterised the expressive power of $\FPR$, an extension of $\FP$ by a rank
+operators, in terms of $\PT$-uniform families of symmetric circuits over the
+rank basis, where the rank basis is the extension of the standard basis by the a
+set of functions, each of which computed the rank operator for some fixed
+threshold and characteristic. It would be natural to ask if there is a much
+broader class of logics, perhaps some class of extensions of $\FP$, such that we
+can define for each logic in this class a natural characterisation in terms of
+$\PT$-uniform transparent symmetric circuits over some appropriate basis. We
+should note that the support theorem and most of the tools developed in this
+paper have application to circuits defined over any basis. In fact, the first
+time we explicitly use the properties of the rank function is in the proof of
+Lemma~\ref{}, right towards the end of the paper.
+
+It would be natural to ask if there is a class of circuits, perhaps symmetric
+circuits defined over an extension of the majority basis, that would suffice to
+give a circuit characterisation of $\CPT$ or $\CPTC$ ($\CPT$ with counting). We
+recall that $\CPTC$ is one of the two candidate logics for capturing
+polynomial-time, and as such there is significant interest in understanding its
+expressive power. At present, very little is known about $\CPTC$, and there are
+no known promising techniques for proving lower bounds. Since circuits families
+seem easier to analysis then $\CPTC$ programs, a circuit characterisation of
+$\CPTC$ would provide us with a very promising for studying the expressive power
+of $\CPTC$, perhaps allowing us to apply techniques for finding circuit lower
+bounds to the problem of deriving inexpressibly results for $\CPTC$. As a
+starting point we might ask if there are any interesting extensions of the
+majority basis by non-symmetric functions such that $\PT$-uniform symmetric
+circuits over such a basis is comparable to $\CPT$ -- i.e.\ known to be at least
+or at most as expressive as $\CPT$. We know that any fragment of $\CPTC$ given
+by placing a constant bound on the rank of sets used in computation is at least
+as expressive as $\FPC$ (see~\cite{}), and hence at least as expressive as
+$\PT$-uniform symmetric circuits with symmetric gates. We may ask if for each
+fragment of $\CPTC$ with a bound $r$ on the rank of the sets used, there is a
+non-trivial class of circuits $\mathcal{C}_r$ (perhaps a family of symmetric
+circuits over some basis) such that the fragment of $\CPT$ with bound $r$ is at
+most as expressive as the $\PT$-uniform families of circuits from
+$\mathcal{C}_r$. It is worth noting that, since we now have a circuit
+characterisation for $\FPR$, finding a circuit characterisation for $\CPT$ or
+$\CPTC$ (or showing none exists) may help clarify the relationship between
+$\CPTC$ and $\FPR$.
+
+We have proposed a new circuit model, presented a characterisation of $\FPR$ in
+terms of $\PT$-uniform families of a particular class of circuits, and suggested
+how we might generalise these results in order to develop circuit-based
+characterisations of other logics -- hopefully even $\CPT$ or $\CPTC$. The
+natural next step would be to develop techniques for proving lower bounds for
+$\PT$-uniform circuit families. A general approach for finding lower bounds for
+families of symmetric circuits over some basis may be very powerful,
+particularly if it turns out to be possible to characterise a broad class of
+extensions of $\FP$ using $\PT$-uniform families of transparent symmetric
+circuits. The usual approach for establishing inexpressibly results for logics
+involves first defining a pebble game for the logic. Dawar~\cite{} has shown
+that the pebble game of Hella~\cite{} can be directly linked with symmetric
+circuits with symmetric gates via a circuit-based argument that makes no
+reference to logic. Dawar and Holm~\cite{} have defined a pebble game for
+$\FPR$, and it would be interesting to know if a similar link can be established
+between this pebble game and transparent symmetric rank-circuits. It may be
+possible to generalise these arguments and establish for each basis $\BB$ a
+corresponding pebble game for transparent symmetric circuits defined over $\BB$.
+
+The circuit model we have developed is novel, and as such there are many basic
+questions of interest. We do not know, for example, whether for each $a \in
+\nats$ there is a symmetric circuit with symmetric gates where each gate has
+fan-in less than $a$ that computes $\NAND[a+1]$. For a basis $\BB$ let $Q_\BB$
+be the set of all queries computed by $\PT$-uniform families of transparent
+symmetric circuits defined over $\BB$. We have that $Q_{\MB} \subsetneq
+Q_{\RB}$. It follows from Theorem~\ref{} that if $\BB$ is a symmetric basis then
+$Q_\BB \subseteq Q_\MB$. It follows that $Q_\MB$ is a basis including structured
+functions defined over a vocabulary with two sorts that defines a circuit model
+strictly more powerful than any defined by basis of that only include functions
+with one sort.s
+
+defines a strictly more powerful class of circuits than
+
+It is not hard to show that $Q_\BB \subseteq Q_\MB$ for any matrix-symmetric
+basis $Q_\BB$ consisting of polynomial-time computable functions if, and only
+if, $\FPR$ captures $\PT$.
+
+We know from Theorem~\ref{} that the majority basis is `complete' for symmetric
+bases in the sense that any query computed by a $\PT$-uniform family of
+symmetric circuits defined over a symmetric basis there is a $\PT$-uniform
+family of symmetric circuits over the majority basis that computes the same
+query. It is easy to see that if
+
+Similarly, we do not know if for $r, a, p \in \nats$, with $p$ prime, the
+function $\RANK^r_p [a][a]$ is computable by a symmetric circuit with symmetric
+gates.
+
 \end{document}

### 2018-03-30 sections/symmetric-circuits.tex
Major Updates to Section 5 (and a complete check of the first part of this section). Fixed a few typos in Section 3.

@@
 Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
-\rho)$-circuit of order $n$.  Recall that the orde of a circuit refers
+\rho)$-circuit of order $n$.  Recall that the order of a circuit refers
 to the size of the input structures it takes.  In contrast, we define
@@
 argument, and, importantly, that that rigid circuits have unique extensions.
-This allows them to restrict their attention to $P$-uniform families of
+This allows them to restrict their attention to $\PT$-uniform families of
 symmetric circuits (over bases of symmetric functions) \emph{with unique

### 2018-03-30 sections/transparency-and-unique-extensions.tex
Major Updates to Section 5 (and a complete check of the first part of this section). Fixed a few typos in Section 3.

@@
 
-In the statement of the main theorem of this paper, rather than working with
-general symmetric rank-circuits, we instead restrict ourselves to families of
-\emph{transparent} circuits. In this section we justify this restriction,
-showing first that the a great number of very useful circuit properties (e.g.
-syntactic-equivalence) are polynomial-time decidable for transparent circuits
-and, second, that deciding most of these circuit properties for general circuits
-(with non-symmetric gates) is at least as hard as the graph-isomorphism
-problem. Since the proof of the main theorem makes use of the polynomial-time
-decidability of many of these properties, these results together justify the
-inclusion of the transparency restriction.
-
-\subsection{The Usefulness of Transparency}
-In the this subsection we show that a number of important circuit properties are
-polynomial-time decidable for transparent circuits (e.g. symmetry, the
-syntactic-equivalence relation, etc.). We also provide polynomial-time
-algorithms for computing the action of a permutation on a symmetric circuit, as
-well as for computing the orbits and supports of gates, and elements of
-universes of gates, in a circuit.
-
-We use the polynomial-time decidability of many of these properties throughout
-this paper, and particularly for our translation of circuits into formulas. For
-example, the polynomial-time decidability of the syntactic-equivalence relation
-enables us to transform transparent circuits into circuits with unique labels
-(and so unique extensions) in polynomial-time. This result allows us, when
-working with $\PT$-uniform families of transparent circuits, to assume without a
-loss of generality that these circuits have unique labels and unique extensions.
-This is a crucial step in the proof of our main result, as the unique labels
-requirement is needed to apply the support theorem, and the unique extensions
-property is necessary for applying (and even defining) a great many technical
-tools (e.g. supports and supporting partitions) used extensively throughout this
-paper.
+Many of the properties of circuits central to work of this paper, and
+particularly those that reference circuit automorphisms or
+syntactic-equivalence, make references to the existence of a isomorphism between
+pairs of structures associated with the gates of the circuit. We recall that
+each gate in a circuit is associated with a structure with the elements of the
+relations of that structure labelled by the children of that gate. These
+properties usually depend on the existence of an isomorphism that agrees with a
+given permutation of the gates labelling the structure. This introduces a
+potential difficulty as there is no know polynomial-time algorithm for the
+general isomorphism problem, but we we require many of these circuit properties
+to be polynomial-time decidable in order to define our translation from circuits
+to formulas (see Section~\ref{sec:circuits-to-formulas}). This is not a problem
+if we restrict our attention to circuits with symmetric gates, as Anderson and
+Dawar~\cite{AndersonD17} do, as in this case the structures of interest are
+sets, and set equivalence is clearly decidable in polynomial-time, but when we
+allow for circuits to be defined over bases including non-symmetric functions it
+is not obvious that these properties can be decided in polynomial-time.
+
+This is the reason we introduced the notion of a transparent circuit. The idea
+is that for transparent circuits the structures associated with each
+non-symmetric gate have the property that each element of each relation is
+labelled by a `unique' gate (i.e.\ such that no elements are labelled by gates
+from the same syntactic-equivalence class). In this case a permutation of the
+gates in the circuit defines exactly one function between the elements of the
+relations of these structures, and so checking for the existence of an
+isomorphism that agrees with the permutation is reduced to the problem of
+determining if a given function is in fact an isomorphism. This problem is
+polynomial-time tractable.
+
+In the first part of this section we prove that the requisite circuit properties
+are indeed polynomial-time decidable for transparent circuits. We then use these
+results to define a polynomial-time computable translation from transparent
+circuits to equivalent circuits with unique labels. As discussed in
+Section~\ref{sec:symm-circ}, this translation allows us to restrict our
+attention from transparent circuits to circuits with unique labels when working
+with families of circuits without a loss of generality. This restriction is
+important for two reasons. First, circuits with unique labels have unique
+extensions, which enables us to apply the support theorem. Second, as we will
+show in this section, all relevant symmetry-related circuit properties are
+polynomial-time decidable for circuits with unique labels. We use all of these
+properties in order to define our translation from circuits to formulas in
+Section~\ref{sec:circuits-to-formulas}.
+
+In the second part of this section we discuss more formally the relationship
+between the problem of deciding many of these natural circuit properties and the
+graph-isomorphism problem. In particular, we present reductions from the
+graph-isomorphism problem to the problems of deciding each of these circuit
+properties for general circuits. It follows that deciding most of these circuit
+properties is hard as the graph isomorphism problem -- a problem not known to be
+in $\PT$. We also show that most of these hardness results are quite robust, in
+that even if we restrict our attention to other natural classes of circuits
+(e.g.\ circuits with unique children or circuits with injective labels) these
+decision problems remain at least as hard as the graph-isomorphism problem.
+In this sense, while the first part of this section provides evidence in favour of the
+sufficiency of the restriction to transparent circuits, the second part provides
+evidence in favour of its necessity.
+
+% In Section~\ref{sec:circuits-to-formulas} we use the polynomial-time
+% decidability of these properties, along with the Immerman Vardi theorem, in
+% order to define a translation from circuit families to formulas of $\FPR$. The
+% results in this section thus justify the restriction to trans
+
+% the results in this section are useful both are useful needed for proving the
+% main result and help explain why it is that we need to restrict ourselves to
+% transparent circuits, rather than working with general circuits.
+
+% Since the proof of the main result makes use of the polynomial-time
+% decidability of many of these properties, these results help explain both why
+% transparent circuits suffice for the proof of our main result and why general
+% circuits
+
+% The restriction to transparent circuits is not found in the analogous circuit
+% characterisation of $\FPR$ by Anderson and Dawar~\ref{AndersonD17}.
+
+% In the first part of this section we show that a number of natural, and
+% useful, circuit properties (e.g. symmetry, syntactic-equivalence) are
+% polynomial-time decidable for transparent circuits. In
+% Section~\ref{sec:circuits-to-formulas} we use the polynomial-time decidability
+% of these properties, along with the Immerman-Vardi theorem, in order to define
+% a translation from families of circuits to formulas. We show in
+% Section~\ref{sec:formulas-to-circuits} that we can translate formulas to
+% families of transparent circuits. It follows that $\PT$-uniform families of
+% circuits suffice for our purposes.
+
+% In the second part of this section we justify the necessity of this
+% restriction, showing that most of these circuit properties for general
+% circuits (with non-symmetric gates) are at least as hard as the
+% graph-isomorphism problem. Since the proof of the main theorem makes use of
+% the polynomial-time decidability of many of these properties, these results
+% together justify the inclusion of the transparency restriction.
+
+% The second part of this
+
+% used to translate circuit families
+
+% Importantly, our proof of the main result makes use of the polynomial-time
+% decidability of these properties.
+
+% many natural show that a great number of
+
+% justify this restriction to transparent circuits, first showing that In this
+% section we justify this restriction, showing first that the a great number of
+% very useful circuit properties (e.g. syntactic-equivalence) are
+% polynomial-time decidable for transparent circuits
+
+% The transparency condition is a restriction on how non-symmetric gates are
+% wired into the circuit, and so all circuits with symmetric gates are
+% transparent. The circuit we have introduced includes
+
+% We have thought of a gate $g$ with a vocabulary $\tau$ in a circuit $C$ as
+% labelling its children using elements of the $\ind(g)$ (i.e\ the elements of
+% the relations of the $\tau$-structure defined at $g$). We could invert this
+% thinking, and instead think of the children of $g$ as labelling the elements
+% of $ind(g)$, and so defining at $g$ a $\tau$-structure with a labelling on the
+% elements of its relations. In particular, if $g$ is a rank-gate then $g$
+% defines a complete bipartite graph labelled by the children of $g$.
+
+% The idea is that a gate $g$ with a vocabulary $\tau$ in a circuit $C$ defines
+% a labelled $\rho$-structure, where the labels are the syntactic-equivalence
+% classes of the children of $g$.
+
+% the restriction to transparency enables us to decide many natural circuit
+% properties in polynomial-time (e.g.\ the orbit of a gate, whether the circuit
+% is symmetric, etc.). important point is that in order to decide many
+% properties of the circuit that we need in order to prove the main result
+% (e.g.\ )
+
+% In this section we justify this restriction, showing first that the a great
+% number of very useful circuit properties (e.g. syntactic-equivalence) are
+% polynomial-time decidable for transparent circuits and, second, that deciding
+% most of these circuit properties for general circuits (with non-symmetric
+% gates) is at least as hard as the graph-isomorphism problem. Since the proof
+% of the main theorem makes use of the polynomial-time decidability of many of
+% these properties, these results together justify the inclusion of the
+% transparency restriction
+
+\subsection{Tractable Properties of Transparent Circuits}
+In the this subsection we show that many useful circuit properties are
+polynomial-time decidable for transparent circuits. First, we prove that the
+syntactic-equivalence relation is polynomial-time computable for transparent
+circuits. We use this result to show that transparent circuits can be
+transformed in polynomial-time into equivalent circuits with unique labels. We
+show that for circuits with unique labels we can compute in polynomial-time the
+action of a given automorphism on the circuit, the orbits and supporting
+partitions of each gate, as well as the orbits and supporting partitions of each
+element of the universe of each gate. We make use of all of these results in
+order to define a translation from circuit families to formulas of $\FPR$ in
+Section~\ref{sec:circuits-to-formulas}.
+
+% The purpose of this section in then to show that we may transform tranparent
+% circuits to circuits with unique labels, and since circuits with unique
+% extension
+
+% the function that computes circuits with unique labels
+
+% We show that the set of transparent circuits, the set of circuits with unique
+% labels, and the set of symmetric transparent circuits are all polynomial-time
+% decidable. Moreover, we show that for circuits with unique labels
+
+% and hence that the the action of a and the orbit and supporting partition of a
+% gate are polynomial-time computable, . We also present polynomial-time
+% algorithms for computing the action of a permutation on a symmetric circuit,
+% as well as for computing the orbits and supports of gates, and elements of
+% universes of gates, in a circuit.
+
+% We use the polynomial-time decidability of many of these properties throughout
+% this paper, and particularly for our translation of circuits into formulas.
+% For example, the polynomial-time decidability of the syntactic-equivalence
+% relation enables us to transform transparent circuits into circuits with
+% unique labels (and so unique extensions) in polynomial-time. This result
+% allows us, when working with $\PT$-uniform families of transparent circuits,
+% to assume without a loss of generality that these circuits have unique labels
+% and unique extensions. This is a crucial step in the proof of our main result,
+% as the unique labels requirement is needed to apply the support theorem, and
+% the unique extensions property is necessary for applying (and even defining) a
+% great many technical tools (e.g. supports and supporting partitions) used
+% extensively throughout this paper.
 
@@
   $(\mathbb{B}, \rho)$-circuit of order $n$. We define the syntactic-equivalence
-  relation on $G$ by induction on the depth of a gate We note that this
-  definition by induction can be implemented as a construction using a dynamic
-  program.
+  relation on $G$ by induction on the depth of a gate. We note that this
+  definition by induction can be implemented as a construction, with the
+  induction defining a dynamic program.
 
@@
   The above algorithm can be implemented by a dynamic program with the number of
-  iterations bounded by the number of pairs of gates in $C$, i.e. $\vert C
-  \vert$ choose $2$. It remains to show that each iterative step can be
-  implemented so as to run in time polynomial in the size of $C$. The only
-  condition that is not obviously polynomial-time decidable is checking if
-  $L(g)$ is isomorphism-equivalent to $L(h)$ up to $\equiv$. We sketch an
-  algorithm that decides this condition in time polynomial in the size of the
-  circuit.
+  iterations bounded by the number of pairs of gates in $C$, i.e.\ ${\vert C
+    \vert} \choose{2}$. It remains to show that there is an algorithm that runs
+  in time polynomial in the size of the circuit and takes as input two gates $g$
+  and $h$ in $C$ and the syntactic-equivalence relation for all gates of depth
+  less than either $g$ or $h$ and returns whether or not $g \equiv h$. We now
+  sketch a definition of this algorithm.
 
@@
   syntactic-equivalence relation for all gates of depth less than the depth of
-  either $g$ or $h$. We test if for each gate in $g' \in H_g$, there exists
-  $h_{g'} \in H_h$ such that $g' \equiv h_{g'}$ and $\vert \{g'' \in H_g : g''
-  \equiv g'\} \vert = \vert \{h'' \in H_h : h'' \equiv h'\}$. If this test
-  fails, we set $g \not\equiv h$.
-
-  We then check if both $g$ and $h$ are symmetric gates or if both are
-  non-symmetric gates. Suppose both $g$ and $h$ are symmetric gates. We have
-  that $L(g)$ is isomorphism-equivalent to $L(h)$ up to $\equiv$ if, and only
-  if, there exists a bijection $f : H_g \rightarrow H_h$ such that $f(g') \equiv
-  g'$, for all $g' \in H_g$ if, and only if, for each gate in $g' \in H_g$,
-  there exists $h' \in H_h$ such that $g' \equiv h'$ and $\vert \{g'' \in H_g :
-  g'' \equiv g'\} \vert = \vert \{h'' \in H_h : h'' \equiv h'\}$. Since we have
-  already checked this condition we set $g \equiv h$.
-
-  Suppose $g$ and $h$ are non-symmetric gates. Then, since $C$ is transparent,
-  both $g$ and $h$ have unique labels. We thus have that for each $g' \in H_g$
-  there is exactly one $h_{g'} \in H_h$ such that $g' \equiv h_{g'}$, and so we
-  can define the bijection $f : H_g \rightarrow H_h$ by $f(g') := h_{g'}$ for
-  all $g' \in H_g$. It can be shown that $L(g)$ is isomorphism-equivalent to
-  $L(h)$ up to $\equiv$ if, and only if, $f \circ L(g)$ is
-  isomorphism-equivalent to $L(h)$ if, and only if, $L(h)^{-1} f L(g)$ acts on
-  $\ind (g)$ like an element of $\aut(g)$. We have from
-  Lemma~\ref{lem:aut-partial} that $\sigma := L(h)^{-1} f L(g)$ acts like an
-  element of $\aut(g)$ if, and only if, for all $\vec{a}_R, \vec{b}_{R'} \in
-  \ind(g)$, $\sigma$ acts like a partial automorphism on $(\vec{a}_R,
-  \vec{b}_{R'})$. We thus conduct the test by iterating through every pair
-  $(\vec{a}_R, \vec{b}_{R'}) \in \ind(g)$, and set $g \equiv h$ if, and only if,
-  $\sigma$ acts like a partial automorphism on every such pair.
+  either $g$ or $h$. We check all of the conditions for syntactic-equivalence
+  with the exception of the isomorphism condition, and any of them fail to hold
+  we halt and output that $g \not\equiv h$.
+
+  We now define a function $f: \ind(g) \rightarrow \ind(h)$ as follows. Let
+  $\{x_1, \ldots, x_{\vert \ind(g)\vert}\}$ be an ordering of $\ind(g)$. For
+  each $i \in \vert \ind(g) \vert$ select $y_i \in \ind(h)$ such that $y_i \neq
+  y_j$ for all $j \in [i-1]$ and $L(g)(x_i) \equiv L(h)(y_i)$. If at any point
+  we cannot select an appropriate $y_i$, halt and output that $g \not\equiv h$.
+  For each $i \in \vert \ind(g) \vert$ let $f(x_i) = y_i$. From the definition
+  of the function $f$ is injective. Check if $f$ is surjective. If not, halt and
+  output that $g \not\equiv h$. We thus have that $f$ is a bijective function
+  and for all $x \in \ind(g)$, $L(g)(x) \equiv L(h)(f(x))$. Check if both $g$
+  and $h$ are both symmetric gates. If so, $f$ witnesses the required
+  isomorphism-equivalence and so we halt and output that $g \equiv h$.
+
+  We thus have that $g$ and $h$ are non-symmetric gates. Then, since $C$ is
+  transparent, both $g$ and $h$ have unique labels. In that case the function
+  $f$ is the only function such that for all $x \in \ind(g)$, $L(g)(x) \equiv
+  L(h)(f(x))$. It follows that $g \equiv h$ if, and only if, $f$ defines an
+  isomorphism from $\str{g}$ to $\str{h}$. This is easy to check.
 \end{proof}
 
-It is sometimes useful to define one circuit from another circuit by
-\emph{quotienting} a circuit by the syntactic equivalence relation. Intuitively,
-a quotient circuit is defined by `merging' each syntactic-equivalence class into
-a single gate and including a wire between two gates in the quotient circuit if,
-and only if, there is a wire between an element of each equivalence class.
+It is common approach to define a new structure by \emph{quotienting} a given
+structure by some equivalence relation. We now define what it means to take a
+quotient of a circuit by the syntactic-equivalence relation. Intuitively, we
+think of a quotient of a given circuit as being formed by `merging' each
+syntactic-equivalence class into a single gate and including a wire between two
+gates in the quotient circuit if, and only if, there is a wire between an
+element of each equivalence class.
 
@@
 
+We should note that the there is no obvious quotienting operation that
+associates with each circuit a unique quotient circuit. However, it is easy to
+see that if $C$ and $C'$ are distinct quotients of a given circuit then the only
+point where they differ is in the definition of their respective labelling
+functions. But it is not hard to see that for every gate $g$ in $C$, $L(g)$ and
+$L'(g)$ are isomorphism-equivalent. It follows that these two circuits are
+structurally identical in a very strong sense. Indeed, while we have not
+formally defined what it means for two circuits to be isomorphic, under any
+reasonable definition we would have that any two quotients of a given circuit
+are isomorphic.
+
 We now show that taking the quotient of a circuit preserves important
-properties, including the function computed by the circuit, whether the circuit
-is symmetric, and has unique unique labels. We also show that the quotient of a
-circuit is reduced, and hence has unique extensions.
+properties, including the function computed by the circuit, the symmetry of the
+circuit, and whether the circuit has unique labels. We also show that the
+quotient of a circuit is reduced, and hence has unique children (and so, from
+Proposition~\ref{prop:unique-children-unique-extensions}, unique extensions).
 
@@
   unique labels $h$ has unique labels and so $L_\equiv([g])$ has injective
-  labels. Since each equivilence class in $C_\equiv$ is a singlton it follows
+  labels. Since each equivalence class in $C_\equiv$ is a singlton it follows
   that $[g]$ has unique labels.
-
-  % If $[g]$ is an input gate then $\pi_\equiv [g] = [\pi g]$, and
-
-  % Let $\mathcal{A}$ be a $\rho$-structure of size $n$ and let $\gamma$ be a
-  % bijection from $U$ to $[n]$. We have from Lemma~\ref{} that for all $g, g'
-  % \in
-  % G$, if $g \equiv g'$ then $C[\gamma \mathcal{A}](g) = C[\gamma
-  % \mathcal{A}](g')$. Moreover, we should note that for each internal gate
-
-  % We show that for all $g \in G$, $C_\equiv [\gamma \mathcal{A}]([g]) =
-  % C[\gamma
-  % \mathcal{A}](g)$ by induction on the structure of the circuit. Suppose $g
-  % \in
-  % G$ is an input gate then, since every input gate is part of a singleton
-  % equivalence class, we have that $C /_\equiv [\gamma \mathcal{A}]([g]) =
-  % C[\gamma \mathcal{A}](g)$. Suppose $g \in G$ is an internal gate. Let $h \in
-  % [g]$ such that $L /_\equiv ([g]) = L(h)/_\equiv$. Then $(L/_\equiv)^{\gamma
-  % \mathcal{A}}([g])(x) = C /_\equiv[\gamma \mathcal{A}](L /_\equiv ([g])(x)) =
-  % C [\gamma \mathcal{A}](L(h)(x)) = L^{\gamma \mathcal{A}}(h)(x) \equiv
-  % L^{\gamma \mathcal{A}}(g) \circ \lambda (x)$ for some $\lambda \in \aut(g)$.
-  % But then, since $\Sigma (g)$ is a structured function, we have that
-  % $\Sigma(g)((L^{\gamma \mathcal{A}}(g) \lambda)) = \Sigma(g)(\L^{\gamma
-  % \mathcal{A}})$. It follows that $C /_\equiv [\gamma\mathcal{A}]([g]) =
-  % \Sigma /_\equiv ((L/_\equiv)^{\gamma mathcal{A}}([g])) = \Sigma (L^{\gamma
-  % \mathcal{A}}(g)\lambda) = \Sigma (L^{\gamma \mathcal{A}}(g)) = C[\gamma
-  % \mathcal{A}](g)$. It follows that $C/_\equiv [\gamma \mathcal{A}]
-  % (\Omega/_\equiv (\vec{a})) = C [\gamma \mathcal{A}](\Omega (\vec{a}))$ for
-  % all
-  % $a \in [n]^q$. It follows that $C_{\equiv}$ and $C$ compute the same
-  % function.
-
-  % Suppose $C$ is symmetric. Suppose $C$ is symmetric. We have from For $\sigma
-  % \in \sym_n$ let $\pi \in \aut(C)$ be an extension of $\sigma$. It can be
-  % shown
-  % that $\pi$ is invariant under $\equiv$, and hence we have that $\pi
-  % /_{\equiv}$ is a function. Since each gate that is either an input or output
-  % gate is a member of a singleton equivalence class we only need to check the
-  % symmetry condition for internal gates. Suppose $g$ is an internal gate then
-  % $\pi /_{\equiv} L /_{\equiv}([g]) (x) = [\pi L(g) (x)] = [L(\pi g) (\lambda
-  % x)] = L([\pi g]) (\lambda x) = L(\pi /_{\equiv} [g]) (\lambda x)$ for some
-  % $\lambda \in \aut(g)$. It follows that $\pi /_{\equiv}$ is an automorphism
-  % of
-  % $C_{\equiv}$ extending $\sigma$, and so $C_{\equiv}$ is symmetric.
-
-  % Let $[g], [g'] \in G/_{\equiv}$. Suppose $[g] \equiv [g']$. If $g$ is an
-  % input
-  % or output gate we have that $g = g'$. Suppose $g$ is an internal gate. Then
-  % there exists $h \in [g]$ and $h' \in [g']$ such that $L /_\equiv ([g]) =
-  % L(h)
-  % /_\equiv$ and $L /_\equiv ([g']) = L(h') /_\equiv$. We have that
-  % $L_{\equiv}([g])$ is isomorphism-equivilent to $L_{\equiv}$
-
-  % Let $g \in G$. Since every gate in $G /_{\equiv}$ is part of a singleton
-  % equivalence class.
-
-  % Then for each gate $g,
-  % g' \in G$ such that $g \equiv g'$ we have that $C[\gamma\mathcal{A}](g) =
-  % C[\gamma \mathcal{A}](g')$. If $g$ is an input gate we have that
-  % $C[\gamma\mathcal{A}](g) = C /_\eqiv [\gamma \mathcal{A}]([g])$. Suppose
-  % $[g] \in G /_{\equiv}$ is an internal gate. Let $L^{\gamma}([g]) : \ind(g)
-  % \rightarrow \{0,1\}$ be defined by $L^{\gamma}([g]) (x) = C[\gamma
-  % \mathcal{A}]([g])$
 \end{proof}
 
-It is worth noting that if $C$ is a transparent circuit we can compute a
-quotient of $C$ in time polynomial in the size of $C$. Since the circuit is
-transparent we can compute the syntactic-equivalence classes of $C$ in
-polynomial time (see Lemma~\ref{lem:transparent-syntactic-equiv}). Picking a
-representative of each equivalence class and wiring up the circuit in the
-obvious way then yields the desired quotient circuit.
+In is not hard to show that there is a polynomial-time computable function that
+maps a transparent circuit to a quotient of that circuit. To see this, recall
+that from Lemma~\ref{lem:transparent-syntactic-equiv} we can compute the
+syntactic-equivalence classes of a transparent circuit in polynomial-time. We
+can thus define a quotient circuit by picking representatives from each
+syntactic-equivalence class and then applying the definition of a quotient
+circuit in the obvious manner.
 
 We now show that transparent circuits can be transformed in polynomial time into
-equivalent circuit with unique labels, and hence unique extensions (see
-Proposition~\ref{prop:unique-children-unique-extensions}), and that this
-transformation preserves important properties of the circuit.
+equivalent circuit with unique labels, and hence unique extensions, and that
+this transformation preserves important properties.
 
@@
   such that $\Sigma(g_0) = 0$ and $\Sigma (g_1) = 1$ we construct a new circuit
-  from $C_0$ by adding these gates. We abuse notation and also call this new
-  circuit $C_0$. The addition of these constant gates to the circuit does not
-  alter the function computed by the circuit, nor does it effect the symmetry of
-  the circuit or weather it has unique labels.
+  from $C_0$ by adding gates. We abuse notation and also call this new circuit
+  $C_0$. The addition of these constant gates to the circuit does not alter the
+  function computed by the circuit, nor does it effect the symmetry of the
+  circuit or weather it has unique labels.
 
@@
 
-  We will define $C_1$ from $C_0$ by adding a designated gate that always
-  evaluates to $1$ and which is part of a singleton syntactic-equivalence class,
-  and then adding a wire from that gate to each $\AND$-gate in the circuit. This
-  process ensures that each $\AND$-gates in $C_1$ has a fan-in of at least two.
-  The construction of $C'$ from $C_1$ involves adding in a number of
-  single-input $\AND$-gates, and so the construction of $C_1$ will allow us to
-  distinguish these new gates from those in $C_1$.
-
-  We now define the circuit $C_1$ formally. Let $C_1 := \langle G_1, \Omega_1,
-  \Sigma_1 , \Lambda_1, L_1 \rangle$ be defined as follows. Let $G_1 = G_0
-  \uplus \{ g_\lor\}$. Let $\Omega_1 = \Omega_0$ and $\Lambda_1 = \Lambda_0$.
-  Let $g \in G_1$. If $g = g_\lor$ then $\Sigma_1 (g) = \OR[2]$, $L_1(g)(1) =
-  g_0$, and $L_1(g)(2) = g_1$. If $g \in G_0$, $\Sigma(g) = \OR[2]$ and $H_g =
-  \{g_0, g_1\}$ then $\Sigma_1 (g) = \OR[3]$, $L_1(g)(1) = L_0(g)(1)$,
-  $L_1(g)(2) = L_0(g)(2)$, and $L_1(g)(3) = g_\lor$. If $g \in G_0$ and $g =
-  \AND[k]$ for some $k \in \nats$ then $\Sigma_1(g) = \AND[k+1]$ and $L_1(g)(i)
-  = L_0(g)(i)$ for all $i \in [k]$ and $L_1(g)(k+1) = g_\lor$. Otherwise let
-  $\Sigma_1(g) = \Sigma_0(g)$ and $L_1(g) = L_0(g)$.
-
-  More informally, we define $C_1$ from $C_0$ by adding in an $\OR$-gate
+  We now define the circuit $C_1$. Let $C_1 := \langle G_1, \Omega_1, \Sigma_1 ,
+  \Lambda_1, L_1 \rangle$ be defined as follows. Let $G_1 = G_0 \uplus \{
+  g_\lor\}$. Let $\Omega_1 = \Omega_0$ and $\Lambda_1 = \Lambda_0$. Let $g \in
+  G_1$. If $g = g_\lor$ then $\Sigma_1 (g) = \OR[2]$ with $L_1(g)(1) = g_0$ and
+  $L_1(g)(2) = g_1$. If $g \in G_0$, $\Sigma(g) = \OR[2]$ and $H_g = \{g_0,
+  g_1\}$, then $\Sigma_1 (g) = \OR[3]$, $L_1(g)(1) = L_0(g)(1)$, $L_1(g)(2) =
+  L_0(g)(2)$, and $L_1(g)(3) = g_\lor$. If $g \in G_0$ and $g = \AND[k]$ for
+  some $k \in \nats$ then $\Sigma_1(g) = \AND[k+1]$ and $L_1(g)(i) = L_0(g)(i)$
+  for all $i \in [k]$ and $L_1(g)(k+1) = g_\lor$. Otherwise let $\Sigma_1(g) =
+  \Sigma_0(g)$ and $L_1(g) = L_0(g)$.
+
+  Stated more informally, we define $C_1$ from $C_0$ by adding in an $\OR$-gate
   $g_\lor$ that always evaluates to one, and then adding a wire from that gate
-  to all $\AND$-gates in the circuit, and also a wire from $g_\lor$ to another
-  $\OR$-gate in order to ensure that $g_\lor$ is part of a singleton
-  syntactic-equivalence class in $C_1$. The important point to note is that each
-  $\AND$-gate in $C_1$ has fan-in at least two, a property we will use to
-  construct $C'$. We now show that the construction of $C_1$ preserves the
-  relevant circuit properties.
+  to all $\AND$-gates in the circuit (and also a wire from $g_\lor$ to any
+  similar gate that may already exist in the circuit in order to ensure that
+  $g_\lor$ is part of a singleton syntactic-equivalence class in $C_1$). The
+  important point to note is that each $\AND$-gate in $C_1$ has fan-in at least
+  two. We will construct $C'$ from $C_1$ by adding in a number of $\AND$-gates
+  with fan-in one. Therefore, since all of the $\AND$-gates in $C_1$ have fan-in
+  two, it will follow that none of these new gates are syntactically-equivalent
+  to any gate in $C_1$. We now show that $C_1$ and $C_0$ compute the same
+  function and if $C_0$ is symmetric then $C_1$ is symmetric.
 
@@
   Suppose $C$ is symmetric. From Lemma~\ref{lem:quotient-circuits-preserve} it
-  follows that $C_0$ is symmetric. Let $\sigma \in sym_n$ and let $\pi_0 \in
-  \aut(C_0)$ be an extension of $\sigma$. We define a bijection $\pi_1 : G_1
-  \rightarrow G_1$ such that $\pi_1 (g) = \pi_0(g)$ for all $g \in G_0$ and
-  $\pi_1 (g_\lor) = g_\lor$. It is easy to see that $\pi_1$ is an automorphism
-  of $C_1$ extending $\sigma$. It follows that $C_1$ is symmetric.
-
-  We have from Lemma~\ref{lem:quotient-circuits-preserve} that $C_0$ is reduced.
-  Since $g_\lor$ is the only two input $\OR$-gate with exactly the two constant
-  gates as children, it follows that $g_\lor$ is contained in a singleton
-  syntactic-equivalence class. It can be shown by induction that if $g, g' \in
-  G_0$ are syntactically equivalent in $C_1$ then they must be
-  syntactically-equivalent in $C_0$. It follows that if $g$ and $g'$ are
-  syntactically-equivalent in $C_1$ then $g = g'$. We thus have that $C_1$ is
-  reduced.
+  follows that $C_0$ is symmetric. Let $\sigma \in \sym_n$ and let $\pi_0 \in
+  \aut(C_0)$ be an extension of $\sigma$. Let $\pi_1 : G_1 \rightarrow G_1$ such
+  that $\pi_1 (g) = \pi_0(g)$ for all $g \in G_0$ and $\pi_1 (g_\lor) = g_\lor$.
+  It is easy to see that $\pi_1$ is an automorphism of $C_1$ extending $\sigma$.
+  It follows that $C_1$ is symmetric.
+
+  We now show that $C_1$ is reduced. We have from
+  Lemma~\ref{lem:quotient-circuits-preserve} that $C_0$ is reduced. Since
+  $g_\lor$ is the only two input $\OR$-gate with exactly the two constant gates
+  as children, $g_\lor$ is contained in a singleton syntactic-equivalence class.
+  It can be shown by induction that if $g, g' \in G_0$ are syntactically
+  equivalent in $C_1$ then they must be syntactically-equivalent in $C_0$. It
+  follows from these two observations that if $g, g' \in G_1$ are
+  syntactically-equivalent in $C_1$ then $g = g'$. We thus have that each
+  syntactic-equivilence class in $C_1$ is a singleton, and so $C_1$ is reduced.
 
   Let $C' := \{G', \Omega', \Sigma' \Lambda' L'\}$ be defined as follows. For
-  each $h \in G_1$ let $c^h_g := \vert L_1(g)^{-1}(h) \vert$ if $h \in H_g$ and
-  $c^h_g := 0$ otherwise. For each $h \in G_1$ let $c^h$ be the maximum of
-  $c^h_g$ for $g \in G_1$. For each $h \in G_1$ if $c^h > 1$ let $G_h :=
-  \{g^{h}_{1}, ldots, g^h_{c_h-1}\}$ otherwise let $G_h := \emptyset$. Let
+  each $g, h \in G_1$ let $c^h_g := \vert L^{-1}(\{h\}) \vert$. For each $h \in
+  G_1$ let $c^h = \max_{g \in G_1} c^h_g$. For each $h \in G_1$ if $c^h > 1$ we
+  define for each $i \in [c_h-1]$ a distinct gate $g^h_i$ and let $G_h :=
+  \{g^{h}_{1}, \ldots, g^h_{c_h-1}\}$, and otherwise let $G_h := \emptyset$. Let
   $G_{\land} := \biguplus_{h \in G_1} G_h$ and $G' = G_{\land} \uplus G_1$. Let
@@
   let $\Sigma'(g) = \Sigma_1(g)$ and otherwise let $\Sigma'(g) = \AND[1]$. For
-  each $g \in G_1$ and $h \in H_g$ let $\{x^{h,g}_0, x^{h,g}_1 ,\ldots,
-  x^{h,g}_{c^h_g - 1}\} := L_1(g)^{-1}(h)$ be a fixed ordering of the set
-  $L_1(g)^{-1}(h)$. Let $g \in G'$. If $g \in G_1$ and $x \in \ind(g)$ then
-  there exists $h \in H_g$ and $i \in \{0, \ldots , c^h_g -1\}$ such that $x =
-  x^{h,g}_i$, and we let $L'(g)(x) = h$ if $i = 0$ and $L'(g)(x^{h,g}_i) =
-  g^h_i$ otherwise. If $g \in G_{\land}$ then $g = g^h_i$ for some $h \in G_1$
-  and $i \in [c^h_g]$, and we let $L'(g)(1) = h$ if $i = 1$ and $L'(g)(1) =
-  g^h_{i-1}$ otherwise.
+  each $g \in G_1$ and $h \in H_g$ let $x^{h,g}_0, \ldots, x^{h,g}_{c^g_h - 1}$
+  be a ($0$-based) ordering of $L_1(g)^{-1}(\{h\})$. For each $g \in G'$ and $x
+  \in \ind(g)$ we define $L'(g)(x)$ as follows. If $g \in G_1$ then there exists
+  unique $h \in H_g$ and $i \in \{0, \ldots, c^h_g - 1\}$ such that $x =
+  x^{h,g}_i$, and we let $L'(g)(x) = h$ if $i = 0$ and $L'(g) (x) = g^h_i$
+  otherwise. If $g \in G_{\land}$ then $g = g^h_i$ for some $h \in G_1$ and $i
+  \in [c^h-1]$, and we let $L'(g)(x) = h$ if $i = 1$ and $L'(g)(x) = g^h_{i-1}$
+  otherwise.
 
@@
   syntactic-equivalence in $C'$.
+
+  We now prove that $C'$ has all of the requisite properties.
 
@@
     we have that $[h] = \{ h \}$. Let $g' \in G'$ and suppose $g \equiv' g'$. We
-    now show that $g = g'$, and so prove the claim. Since $g \equiv' g'$ it
-    follows that $\Sigma (g) = \Sigma(g')$ and both $g$ and $g'$ have the same
-    depth. Moreover, from the inductive hypothesis, we have that there exists
-    $\lambda \in \aut(g)$ such that for all $x \in \ind(g)$, $L'(g) (x) =
-    L'(g')(x)$. It follows that $H_{g}' = H_{g'}'$. Moreover, from the inductive
-    hypothesis the children of $g$ and $g'$ must be contained in a singleton
-    syntactic-equivalence classes, and so, since $C'$ has injective labels, it
-    follows that $g$ and $g'$ have unique labels in $C'$.
+    now show that $g = g'$, and so $[g] = \{g\}$, breaking down the argument by
+    case. We first make a few useful observations. Note that, since $g \equiv'
+    g'$, it follows that $\Sigma (g) = \Sigma(g')$ and both $g$ and $g'$ have
+    the same depth. Moreover, from the inductive hypothesis and the fact that $g
+    \equiv' g'$, we have that there exists $\lambda \in \aut(g)$ such that for
+    all $x \in \ind(g)$, $L'(g) (\lambda x) = L'(g')(x)$. It follows that
+    $H_{g}' = H_{g'}'$. We also have from the inductive hypothesis that each
+    child of $g$ and $g'$ must be contained in a singleton equivalence class.
+    Since $C'$ has injective labels it follows that $g$ and $g'$ have unique
+    labels.
 
@@
     not a symmetric gate. Since $C$ is transparent, $C_0$ is transparent and so
-    $C_1$ is transparent. It follows that for all $h \in H_g$, $H_g = H_{g'}$,
-    and $c^h_g = 1 = c^h_{g'}$. It follows that for all $x \in \ind(g)$, there
-    exists a unique $h \in G_1$ such that $L_1(g)(\lambda x) = L'(g)(\lambda x)
-    = L'(g')(x) = L_1 (g')(x) = h$. It follows that $g \equiv g'$ and so $g =
-    g'$. Suppose $g$ is a symmetric gate. Let $x \ind(g)$ and $h = L_1(g)(x)$.
-    If $L'(g)(\lambda x) = L'(g')(x)= h$ then $L_1(g)(\lambda x) = h$ if, and
-    only if, $L'(g)(\lambda x ) = h* = L'(g')(x)$, where $h* = h$ or $h* =
-    g^{h}_i$, for some $i \in [c^h_g -1]$, if, and only if, $L_1(g) (x) = h$. It
-    follows that for all $x \in \ind(g)$, $L_1 (g) (\lambda x) = L_1 (g)(x)$,
-    and so $g \equiv g'$ and so $g = g'$.
-
-    % It follows that for all $g \in G'$, $[g] = \{g\}$. The result follows.
+    $C_1$ is transparent. We thus have that $g$ and $g'$ have unique labels in
+    $C_1$ and so $c^h_g = 1 = c^h_{g'}$ and so for all $x \in \ind(g)$,
+    $L_1(g)(x) = L'(g)(x)$ and $L_1(g')(x) = L'(g)(x)$. It follows that for all
+    $x \in \ind(g)$, $L_1(g')(x) = L'(g')(x) = L'(g)(\lambda x) = L_1(g)(\lambda
+    x)$. We thus have that $g \equiv g'$ and so $g = g'$. Suppose instead that
+    $g$ is a symmetric gate. Let $x \in \ind(g)$ and $h := L_1(g)(\lambda x)$.
+    Then $L' (g')(x) = L'(g)(\lambda x) \in \{h, g^h_1, \ldots , g^h_{c^h_g -
+      1}\}$. It follows that $L_1(g')(x) = h$. Putting this together we have
+    that for all $x \in \ind(x)$, $L_1(g) (\lambda x) = L_1(g')(x)$, and so $g
+    \equiv g'$ and thus $g = g'$.
 
@@
   Since $C'$ has injective labels and is reduced it follows $C'$ has unique
-  labels.
-
-  We have already shown that if $C$ is symmetric then $C_1$ is symmetric. We now
-  show that if $C_1$ is symmetric then $C'$ is symmetric. Suppose $C_1$ is
-  symmetric. Let $\sigma \in \sym_n$ and let $\pi_1 \in \aut(C_1)$ be an
-  extension of $\sigma$. We define the function $\pi' : G' \rightarrow G'$ as
-  follows. Let $g \in G'$. If $g \in G_1$ then $\pi'(g) = \pi_1(g)$, otherwise
-  $g \in G_\land$, and so there exists $h \in G_1$ and $i \in [c^h - 1]$ such
-  that $g = g^h_i$, let $\pi'(g) = g^{\pi_1 h}_i$. It is easy to show that
-  $\pi'$ is an automorphism of $C'$ extending $\sigma$.
+  labels. We have already shown that if $C$ is symmetric then $C_1$ is
+  symmetric. We now show that if $C_1$ is symmetric then $C'$ is symmetric.
+  Suppose $C_1$ is symmetric. Let $\sigma \in \sym_n$ and let $\pi_1 \in
+  \aut(C_1)$ be an extension of $\sigma$. We define the function $\pi' : G'
+  \rightarrow G'$ as follows. Let $g \in G'$. If $g \in G_1$ let $\pi'(g) :=
+  \pi_1(g)$. If $g \not\in G_1$ then $g \in G_\land$, and so there exists $h \in
+  G_1$ and $i \in [c^h - 1]$ such that $g = g^h_i$. Let $\pi'(g) := g^{\pi_1
+    h}_i$. It is easy to show that $\pi'$ is an automorphism of $C'$ extending
+  $\sigma$.
 
@@
     G_1$. We now prove the result by induction on the depth of a gate. Suppose
-    $g$ has depth $0$, then $g$ is an input gate, and the case follows
+    $g$ has depth $0$. In this case $g$ is an input gate, and the result follows
     trivially. Suppose $g$ is an internal gate, and for all $h$ of depth less
     than $g$ we have that if $h \in G_1$ then $C'[\gamma \mathcal{A}](h) =
-    C_1[\gamma \mathcal{A}](h)$. Let $x \in \ind(g)$. From the construction of
-    $C'$ we have that if $L'(g)(x) \in G_1$ then ${L'}^{\gamma
-      \mathcal{A}}(g)(x) = L^{\gamma \mathcal{A}}_1(g)(x)$. If $L'(g)(x) \not\in
-    G_1$ then $L'(g)(x) \in G_{\land}$ and so $L'(g)(x) = g^h_i$, where $h =
-    L_1(g)(x)$ and some $i \in [c^h_g -1]$. But then ${L'}^{\gamma
-      \mathcal{A}}(g)(x) = C'[\gamma \mathcal{A}](g^h_i) = C'[\gamma
-    \mathcal{A}](h) = C_1[\gamma \mathcal{A}](h) = L^{\gamma
-      \mathcal{A}}_1(g)(x)$. The penultimate equality follow from from the
-    inductive hypothesis. The final equality follows from the fact that $h = L_1
-    (g)(x)$. We thus have $C'[\gamma \mathcal{A}](g) = \Sigma'({L'}^{\gamma
+    C_1[\gamma \mathcal{A}](h)$. Let $x \in \ind(g)$. Recall that $C'$ is
+    constructed such that if $g \in G_1$ then for all $x \in \ind(g)$ and $h \in
+    H_g$, $L_1(g)(x) = h$ if, and only if, $L'(g)(x) \in \{h, g^h_1, \ldots ,
+    g^h_{c^h_g - 1}\}$. But, from the construction, we have that all of the
+    gates in $\{h, g^h_1, \ldots, g^h_{c^h_g -1}\}$ evaluate to the same value
+    for a given input to the circuit. Thus, from the inductive hypothesis, we
+    have that if $L'(g)(x) \in G_1$ then $ {L'}^{\gamma \mathcal{A}}(g)(x) =
+    C'[\gamma \mathcal{A}](L(g)(x)) = C_1[\gamma \mathcal{A}](L_1(g)(x)) =
+    L^{\gamma \mathcal{A}}_1(g)(x) $. If $L'(g)(x) \not\in G_1$ then $L'(g)(x)
+    \in G_{\land}$ and so $L'(g)(x) = g^h_i$, where $h = L_1(g)(x)$ and some $i
+    \in [c^h_g -1]$. But then ${L'}^{\gamma \mathcal{A}}(g)(x) = C'[\gamma
+    \mathcal{A}](g^h_i) = C'[\gamma \mathcal{A}](h) = C_1[\gamma \mathcal{A}](h)
+    = L^{\gamma \mathcal{A}}_1(g)(x)$. The penultimate equality follow from from
+    the inductive hypothesis. The final equality follows from the fact that $h =
+    L_1 (g)(x)$. We thus have $C'[\gamma \mathcal{A}](g) = \Sigma'({L'}^{\gamma
       \mathcal{A}}(g)) = \Sigma_1 (L^{\gamma \mathcal{A}}_1(g)) = C_1[\gamma
@@
 \end{proof}
-% GW: read this when fresh
-
-We now show that it is possible to compute the action of $\sym_n$ on the gates
-of a circuit of order $n$ with unique labels in polynomial time. Recall that
-from Lemma~\ref{lem:transparent-unique} we may, without a loss of generality,
-restrict our attention from transparent circuits to circuits with unique labels.
-The proof technique used here is similar to the one used by Anderson and
-Dawar~\cite{AndersonD17}.
+
+We now show that there is an algorithm that runs in polynomial time and takes as
+input a circuit with unique labels and an appropriate permutation and outputs
+the action of the automorphism extending the permutation (if its defined) on the
+gates of the circuit.
 
@@
   There is an algorithm takes as input a $(\BB, \rho)$-circuit $C$ of order $n$
-  with unique labels and $\sigma \in \sym_n$ and outputs for each gate $g$ its
-  image under the unique automorphism extending $\sigma$ (if it exists). This
-  algorithm runs in time polynomial in the combined size of the input circuit
-  and the encoding of the permutation.
+  with unique labels and $\sigma \in \sym_n$ and outputs for each gate $g$ the
+  image of $g$ under the action of the unique automorphism extending $\sigma$
+  (if it exists). This algorithm runs in time polynomial in the combined size of
+  the input circuit and the encoding of the permutation.
   \label{lem:compute-automorphisms}
@@
   gates or neither are. If no such $h'$ exists then halt and output that no
-  automorphism exists. If both $h$ and $h'$ are not output gates then set $\pi
-  (h) = h'$. If both are output gates then check if $\sigma \Omega^{-1}(h) =
-  \Omega^{-1}(h')$. If equality holds set $\pi(h) = h'$, otherwise halt and
-  output that no automorphism exists. We have from
+  automorphism exists. If neither $h$ nor $h'$ are output gates then set $\pi
+  (h) = h'$. If both $h$ and $h'$ are output gates then check if $\sigma
+  \Omega^{-1}(h) = \Omega^{-1}(h')$. If the equality holds set $\pi(h) = h'$,
+  otherwise halt and output that no automorphism exists. We have from
   Proposition~\ref{prop:unique-children-unique-extensions} that there is at most
@@
   If no such $h'$ exists halt and output that there is no automorphism extending
-  $\sigma$. Again, we have that if $C$ has unique labels then there is at most
-  one such $h'$.
+  $\sigma$. Since $C$ has unique labels it has unique extensions, and so there
+  is at most one such $h'$. We thus let $\pi (h) = h'$.
 
@@
 
-We now that, using the algorithm from Lemma~\ref{lem:compute-automorphisms}, we
-can similarly compute the action of $\sym_n$ on the elements of the universes of
-the gates of a circuit of order $n$ in polynomial time.
+We now define an algorithm analogous to the one defined in
+Lemma~\ref{lem:compute-automorphisms} that computes in polynomial-time the image
+of a given element of the universe of a gate under the action of a given
+permutation.
 
 \begin{lem}
-  There is an algorithm takes as input a $(\mathbb{B}, \rho)$-circuit $C$ of
-  order $n$, $\sigma \in \sym_n$, $g$ a gate in $C$, and $a \in \universe{g}$
-  and, if there exists an automorphism of $C$ extending $\sigma$ such that
-  $\sigma in \stab(g)$, outputs image of $a$ under $\sigma$. The algorithm runs
-  in time polynomial in the size of $C$ and the encoding of $\sigma$.
+  There is an algorithm takes as input a $(\mathbb{B}, \rho)$-circuit $C$ with
+  unique labels of order $n$, a gate $\sigma \in \sym_n$, $g$ a gate in $C$, and
+  $a \in \universe{g}$ and, if there exists an automorphism of $C$ extending
+  $\sigma$ such that $\sigma \in \stab(g)$, outputs image of $a$ under $\sigma$.
+  The algorithm runs in time polynomial in the size of $C$ and the encoding of
+  $\sigma$.
   \label{lem:compute-automorphisms-labels}
@@
 \begin{proof}
-  Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$. Use the algorithm
+  Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$. We use the algorithm
   from Lemma \ref{lem:compute-automorphisms} to check if $\sigma$ extends to an
-  automorphism on $C$ and $\sigma \in \stab(g)$. If not, return that no such
-  automorphism exists. We thus have that $C$ is symmetric. Let $h \in H_g$ and
-  $\vec{a} := L(g)^{-1}(h)$ be such that $a \in \vec{a}$, and let $i$ be the
-  index of $a$ in $\vec{a}$. Output $\sigma \cdot a := L(g)^{-1}(\sigma h)(i)$.
+  automorphism on $C$. We also check if $\sigma \in \stab(g)$. If either of
+  these checks fail, halt and return that no such automorphism exists. Let $h
+  \in H_g$ and $\vec{b}_R := L(g)^{-1}(h)$ be such that $a \in \vec{b}_R$, and
+  let $i$ be the index of $a$ in $\vec{b}_R$. Halt and output $\sigma a =
+  (L(g)^{-1}(\sigma h))(i)$.
 \end{proof}
 
-We now show that it is possible to compute the orbits and canonical supporting
-partitions of gates in circuits with unique labels in polynomial-time. We also
-show that it is possible to compute the orbits and canonical supporting
-partitions of elements on the universes of gates in circuits with unique labels
-in polynomial-time. In order to prove both of these results we first prove a
-more general result for group actions.
+We aim to show that it is possible to compute in polynomial-time the orbits and
+canonical supporting partitions of the gates, and elements of the universes of
+the gates, of a given circuit with unique labels. In order to prove this, we
+first prove a more general result which shows that there is a polynomial-time
+algorithm that takes as input a set $X$, an element $x \in X$, and a
+polynomial-time computable group action on $X$, and computes the orbit and
+canonical supporting partition of $x$.
 
@@
   \label{lem:computing-support-orbit}
-  There is an algorithm that takes in a subset $S \subseteq [n]$ and $x \in X$,
-  where $X$ is some finite set such that there is a group action of $\stab(S)$
-  on $X$ computable in time polynomial in both $n$ and $\vert X \vert$ and
-  outputs $\orb_{\stab(S)} (x)$ and $\SP_{\stab(S)}(x)$. This algorithm runs in
-  time polynomial in both $\vert X \vert$ and $n$.
+  Let $p$ be a polynomial. There is an algorithm that takes as input a set $S
+  \subseteq [n]$, a set $X$, an element $x \in X$, and a turning machine $T$
+  computing the action of $\stab(S)$ on $X$ that runs in time bounded by $p(n +
+  \vert X \vert)$, and outputs $\orb_{\stab(S)} (x)$ and $\SP_{\stab(S)}(x)$.
+  This algorithm runs in time polynomial in $n + \vert X \vert + \vert T \vert$.
 \end{lem}
@@
 
-  Let $\mathcal{P}$ be the partition formed by applying $\mathcal{E}$ to all
-  $\mathcal{P}_{(u,v)}$ such that $(u,v) \cdot x = x$ (which can be checked in
-  time polynomial in $\vert X \vert$ and $n$). From
+  Let $\mathcal{P}$ be the partition formed by applying $\mathcal{E}$ to every
+  $\mathcal{P}_{(u,v)}$ with $(u,v) \cdot x = x$ in succession. From
   Proposition~\ref{prop:combining-supporting-patitions} we have that
@@
   It remains to compute $\orb_{\stab(S)}(x)$. Let $M_0 := \{x\}$ and for each $i
-  \geq 0$ let $M_{i+1} := M_i\cup \bigcup_{(u,v) \in \sym_{[n] \setminus S}}
-  ((u,v) \cdot M_i)$. Let $M$ be the least fixed point of this sequence. It is
+  \geq 0$ let $M_{i+1} := M_i\cup (\bigcup_{(u,v) \in \sym_{[n] \setminus S}}
+  ((u,v) \cdot M_i))$. Let $M$ be the least fixed point of this sequence. It is
   easy to see that $M \subseteq \orb_{\stab(S)}(x)$ as every element of $M$ is
@@
   generated by the set of all transpositions in $\sym_{[n] \setminus S}$, it
-  follows that $\pi$ can be written as a sequence of $t$ transpositions (for
-  some $t \in \nats$). Thus $y \in M_t \subseteq M$, and hence
-  $\orb_{\stab(S)}(x) \subseteq M$, and so $\orb_{\stab(S)}(x) = M$.
+  follows that $\pi$ can be written as a sequence of $t$ transpositions for some
+  $t \in \nats$. Thus $y \in M_t \subseteq M$, and hence $\orb_{\stab(S)}(x)
+  \subseteq M$, and so $\orb_{\stab(S)}(x) = M$.
 
   Note that the set of all transpositions in $\sym_{[n] \setminus S}$ can be
-  computed in time $\mathcal{O}(n^{2})$ and whether a transposition fixes $x$
-  can be computed in time polynomial in both $\vert X \vert$ and $n$. Moreover,
-  since it is easy to show that $\mathcal{E}$ can be computed in time polynomial
-  in $n$, it follows that $\mathcal{P}$ (defined above) can be computed in
-  $\mathcal{O} (n^{2} q(\vert X \vert, n))$, for some polynomial $q$.
+  computed in time $\mathcal{O}(n^{2})$, and we can check if a given
+  transposition fixes $x$ by simulating $T$ with the given transposition and $x$
+  as inputs. Moreover, since it is easy to show that $\mathcal{E}$ can be
+  computed in time polynomial in $n$, it follows that $\mathcal{P}$ can be
+  computed in $\mathcal{O} (n^2 \vert T \vert p(\vert X \vert +n)^2 q(\vert X
+  \vert + n))$, for some polynomial $q$.
 
   Furthermore, since, when computing the orbit, the least fixed point must be
-  reached in fewer than $\vert X \vert$ iterations, and each iteration requires
-  at most $\mathcal{O} (n^{2})$ applications of the group action, it follows
-  that the procedure terminates in time $\mathcal{O}(\vert X \vert n^{2} q'
-  (\vert X \vert, n))$, for some polynomial $q'$. The result follows.
+  reached in at most $\vert X \vert$ iterations, and each iteration requires at
+  most $\mathcal{O} (n^{2})$ applications of the group action, it follows that
+  this part of the procedure runs time $\mathcal{O}(n^2\vert X \vert \vert T
+  \vert p (\vert X \vert + n)^2)$. We thus have that the entire algorithm runs
+  in polynomial-time, and the result follows.
 \end{proof}
 
-We now use Lemma~\ref{lem:computing-support-orbit} to prove the result for the
-orbits and canonical supporting partitions of gates in the circuit.
+We now apply Lemma~\ref{lem:computing-support-orbit} and show that there is a
+polynomial-time algorithm that takes as input a circuit with unique labels and
+decides if the circuit is symmetric and, if it is, outputs the orbit and
+canonical supporting partition of each gate in the circuit.
 
 \begin{lem}
-  There is an algorithm that takes in a circuit $C$ of order $n$ with unique
-  labels and outputs if the circuit is symmetric. If it is symmetric then it
-  outputs the orbit and coarsest supporting partition of every gate. This
-  algorithm runs in time polynomial in the size of the circuit.
+  There is an algorithm that takes in a circuit $C$ with unique labels and
+  outputs if the circuit is symmetric. If it is symmetric then it outputs the
+  orbit and coarsest supporting partition of each gate. This algorithm runs in
+  time polynomial in the size of the circuit.
   \label{lem:computing-support-orbit-gate}
@@
 \begin{proof}
-  For each transposition $(u,v) \in \sym_n$ and each gate $g$ in $C$ use
-  Lemma~\ref{lem:compute-automorphisms} to check if the image of $g$ under
-  $(u,v)$ exists. If for any transposition and gate the algorithm returns that
-  no image exists then output that the circuit is not symmetric.
-
-  We note that if all gates have an image under all transpositions then, since
-  $\sym_n$ is generated by the set of transpositions, we have that $C$ is
-  symmetric.
-
-  We have from Lemma~\ref{lem:compute-automorphisms} that computing the action
-  of $\sym_n$ on the gates of $C$ can be done in time polynomial in the size of
-  the circuit. For each gate $g$ in $C$ we run the algorithm from
-  Lemma~\ref{lem:computing-support-orbit} with $S := \emptyset$, $X := G$ (the
-  set of gates in C), and $x := g$, and output the results.
-
-  Since there are ${{n}\choose{2}} \leq n^2$ transpositions in $\sym_n$, the
-  initial symmetry check can be completed in time polynomial in the size of the
-  circuit. Moreover, from Lemmas~\ref{lem:compute-automorphisms} and
-  \ref{lem:computing-support-orbit}, and the fact that $\vert C \vert \geq n$
-  and $\vert C \vert \geq \vert \universe{g} \vert$, we have that the rest of
-  the algorithm also runs in time polynomial in the size of the circuit.
+  Let $n$ be the order of $C$. We have from
+  Lemma~\ref{lem:compute-automorphisms} that there is a Turing machine $T'$ that
+  takes as input a circuit with unique labels and a permutation and outputs the
+  image of each gate (if it exists) in polynomial-time. We define a Turing
+  machine $T$ that takes as input a permutation $\sigma \in \sym_n$ and a gate
+  $g$ in $C$, runs $T'$ with inputs $C$ and $\sigma$ and outputs the image of
+  $g$ under the action of $\sigma$ (if it exists).
+
+  For each transposition $(u,v) \in \sym_n$ and each gate $g$ in $C$ use the
+  Turing machine $T$ to check if the image of $g$ under the action of $(u,v)$
+  exists. If for any transposition and gate the algorithm returns that no image
+  exists then output that the circuit is not symmetric.
+
+  We note that if every gate has an image under the action of every
+  transpositions then, since $\sym_n$ is generated by the set of transpositions,
+  we have that $C$ is symmetric.
+
+  For each gate $g$ in $C$ we run the algorithm from
+  Lemma~\ref{lem:computing-support-orbit} with $S := \emptyset$, $X := G$ (where
+  $G$ is the set of gates in $C$), $x := g$, and Turing machine $T$n, and output
+  the result of this computation.
+
+  We note that there are ${{n}\choose{2}} \leq n^2$ transpositions in $\sym_n$
+  and so, since from Lemma~\ref{lem:compute-automorphisms} the action of a
+  transposition on the gates of the circuit can be computed in polynomial-time,
+  the initial symmetry check can be completed in polynomial-time. Moreover, from
+  the polynomial-time bounds in Lemmas~\ref{lem:compute-automorphisms}
+  and~\ref{lem:computing-support-orbit}, we have that the rest of the algorithm
+  also runs in time polynomial in the size of the circuit.
 \end{proof}
 
-We now use Lemma~\ref{lem:computing-support-orbit} to prove the result for the
-orbits and canonical supporting partitions of elements of the universes of gates
-in the circuit.
+We now extend Lemma~\ref{lem:computing-support-orbit-gate} and construct an
+polynomial-time algorithm that computes the orbit and canonical supporting
+partition of each elements of the universe of each gate in a circuit.
 
@@
 \begin{proof}
-  Use the algorithm from Lemma~\ref{lem:computing-support-orbit-gate} in order
+  We first use the algorithm from Lemma~\ref{lem:computing-support-orbit-gate}
   to compute the canonical support of $g$. If the algorithm returns that $C$ is
@@
 
-  Use the algorithm from Lemma~\ref{lem:computing-support-orbit}, with $S :=
-  \consp(g)$, $X := \universe{g}$ and $x:= a$, and output the results.
-
-  Notice that, since $\vert \universe{g} \vert \leq \vert C \vert$ and $n \leq
-  \vert C \vert$, this algorithm runs in polynomial time.
+  We have from Lemma~\ref{lem:compute-automorphisms-labels} that there is a
+  Turing machine $T'$ that takes as input a circuit with unique labels, a gate,
+  an element of the universe of that gate, and a permutation, and outputs the
+  image of the given element under the action of the given permutation (if it
+  exists). We define a Turing machine $T$ that takes as input an element $b \in
+  \consp(g)$ and a permutation $\sigma \in \spstab{g}$ outputs the result of
+  running $T'$ with inputs $C$, $\sigma$, $g$ and $b$.
+
+  We then use the algorithm from Lemma~\ref{lem:computing-support-orbit}, with
+  $S := \consp(g)$, $X := \universe{g}$ and $x:= a$, and the Turing machine $T$,
+  and output the results.
+
+  We have from the bounds in Lemmas~\ref{lem:compute-automorphisms-labels}
+  and~\ref{lem:computing-support-orbit} that this algorithm runs in time
+  polynomial in the size of the circuit.
 \end{proof}
 
-Anderson and Dawar~\cite{AndersonD17}, in their study of circuits with symmetric
-gates, show that such circuits may be transformed in polynomial time into
-equivalent circuits with unique extensions. They do this by showing that a
-circuit with symmetric gates may be transformed into an equivalent \emph{rigid}
-circuit in polynomial time, and that all rigid circuits have unique extensions.
-Moreover, they also prove the existence of polynomial-time algorithms computing
-the action of a permutation on a rigid circuit, and the orbits and coarsest
-supporting partitions of gates in a rigid circuits. We have shown that
-transparent circuits can be translated into equivalent circuits with unique
-labels in polynomial time, and that circuits with unique labels have unique
-extensions (see Proposition~\ref{prop:unique-children-unique-extensions}).
-Moreover, we have similarly shown that, for transparent circuits, the action of
-a permutation, as well as the coarsest supporting partition and orbit of a gate
-(or element of the universe of a gate), can be computed in polynomial-time.
-Since all circuits with symmetric gates are transparent, this is direct
-generalisation of the results of Anderson an Dawar.
+We have so far shown that transparent circuits, and circuits with unique labels,
+have all of the requisite algorithmic properties needed to prove our main
+result. However, since transparency is defined in terms of
+syntactic-equivalence, and testing syntactic-equivalence seems to require an
+isomorphism test, it is not at all obvious that transparency itself is a
+polynomial-time decidable property of circuits. Indeed, if transparency is not
+polynomial-time decidable, it would suggest this restriction to transparent
+circuits is quite unnatural, and it may undermine the usefulness of the
+characterisation presented in this paper. We now show that the class of
+transparent circuits is polynomial-time decidable.
+
+\begin{prop}
+  There is an algorithm that takes as input a circuit and decides if that
+  circuit is transparent. This algorithm runs in time polynomial in the size of
+  the circuit.
+  \label{prop:transparent-polynomial-time}
+\end{prop}
+\begin{proof}
+  Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
+  \rho)$-circuit. We first check that, for each non-symmetric gate $g \in G$,
+  $L(g)$ is an injection. If not, we return that $C$ is not transparent.
+
+  For each $p \in \nats$ let $G^p \subseteq G$ be the set of all gates of depth
+  $p$ and let $G^{\leq p} = \bigcup_{0 \leq i \leq p}G^i$. Since no two input
+  gates are syntactically-equivalent, a gate in $G^1$ has unique labels if, and
+  only if, it has injective labels. We thus check if any non-symmetric gate in
+  $G^1$ do not have injective labels, halt and output that the circuit is not
+  transparent if such a gate is found. We then run the following iterative
+  algorithm. We initialise a variable $i$ to $1$. We have that all of the
+  non-symmetric gates in $G^{\leq i}$ have unique labels. We can thus compute
+  the syntactic-equivilence classes of $G^{\leq i}$ using the algorithm given in
+  Lemma~\ref{lem:transparent-syntactic-equiv}. We test if every non-symmetric
+  gate in $G^{i+1}$ has has unique labels, i.e.\ if it has injective labels and
+  no two of its children are elements of the same syntactic-equivalence class.
+  If this test fails, we halt and output that the circuit is not transparent, if
+  it succeeds we increment the variable $i$ and continue as above. If $i$ is
+  ever set to the value $\depth(C)$, we halt and output that the circuit is
+  transparent.
+
+  It is easy to see that the above algorithm can be implemented so as to run in
+  polynomial time.
+\end{proof}
+
+We can similarly show that the class of circuits with unique labels is
+polynomial-time decidable.
+
+\begin{cor}
+  There is an algorithm that takes in a circuit and decides if that circuit has
+  unique labels and runs in time polynomial in the size of the circuit.
+\end{cor}
+\begin{proof}
+  Let $C$ be the input circuit. From
+  Proposition~\ref{prop:transparent-polynomial-time} we may check if $C$ is
+  transparent in time polynomial in the size of $C$. If $C$ is not transparent
+  halt and output that $C$ does not have unique labels. If $C$ is transparent
+  then from Lemma~\ref{lem:transparent-syntactic-equiv} we may compute the
+  syntactic-equivalence relation for the gates of $C$ in time polynomial in the
+  size of $C$. Note that $C$ has unique labels if, and only if, for each gate
+  $g$ in $C$, $\vert \ind(g) \vert = \vert H_g /_\equiv \vert$. We may thus
+  check if $C$ has unique labels by iterating through the gates of $C$. 
+\end{proof}
+
+% Anderson and Dawar~\cite{AndersonD17}, in their study of circuits with
+% symmetric gates, show that such circuits may be transformed in polynomial time
+% into equivalent circuits with unique extensions. They do this by showing that
+% a circuit with symmetric gates may be transformed into an equivalent
+% \emph{rigid} circuit in polynomial time, and that all rigid circuits have
+% unique extensions. Moreover, they also prove the existence of polynomial-time
+% algorithms computing the action of a permutation on a rigid circuit, and the
+% orbits and coarsest supporting partitions of gates in a rigid circuits. We
+% have shown that transparent circuits can be translated into equivalent
+% circuits with unique labels in polynomial time, and that circuits with unique
+% labels have unique extensions (see
+% Proposition~\ref{prop:unique-children-unique-extensions}). Moreover, we have
+% similarly shown that, for circuits with unique labels, the action of a
+% permutation, as well as the coarsest supporting partition and orbit of a gate
+% (or element of the universe of a gate), can be computed in polynomial-time.
+% Since all circuits with symmetric gates are transparent, this is direct
+% generalisation of the results of Anderson an Dawar.
 
@@
 
-We have from the first subsection that a great number of useful properties are
-polynomial-time computable on transparent circuits. However, it is still
-reasonable to ask if the explicit inclusion of the transparency restriction is
-strictly necessary for proving these results. In this subsection we present a
-number of results suggesting the importance of the transparency, and unique
-labels, requirements. In particular, we present reductions from the
-graph-isomorphism problem to many important decision problems addressed in the
-first subsection (e.g. deciding if a circuit is symmetric, if a gate has unique
-labels, if two gates are syntactically-equivalent, of if two gates are in the
-same orbit).
-
-These results together strongly suggest the necessity of the transparency
-condition for enabling the polynomial-time decidability of many basic properties
-of circuits with non-symmetric gates. Moreover, while we do not show that there
-is no polynomial-time computable transformation from a general circuit to an
-equivalent transparent circuit, the difficulty associated with computing basic
-circuit properties that seem essential for defining such a transformation
-provide evidence in favour of this conjecture. (Indeed, the translation defined
-by Anderson and Dawar~\cite{AndersonD17} from circuits with symmetric gates to
-equivalent circuits with unique extensions makes explicit use of the
-polynomial-time computability of syntactic-equivalence on such circuits).
-
-As a final point, we note that while we present evidence against the ability to
-transform arbitrary circuits into transparent circuits in polynomial-time, we do
-show that the class of transparent circuits is polynomial-time decidable. In
-contrast, we show that deciding the class of circuits with unique extensions is
-at least as hard as the graph-isomorphism problem.
-
-% We particularly note the hardness results for syntactic-equivalence note The
-% difficulty of computing the orbit for non-transparent circuits is particularly
-% important to note, as we make use of the existence of the polynomial-time
-% decidability of the orbit in the proof of our main result.
-
-% In particular, we show that the graph-isomorphism problem reduces to the
-% problem of computing the syntactic-equivalence relation for general circuits.
-
-% As we noted, Anderson and Dawar~\cite{AndersonD17} show that circuits (with
-% symmetric gates) can be transformed in polynomial time into equivalent rigid
-% circuits (in fact, their algorithm transforms these circuits into equivalent
-% circuits with unique labels, a stronger condition than rigidity). Their proof
-% of this result makes explicit use of the fact that the syntactic-equivalence
-% relation on the gates of these circuits can be computed in polynomial-time
-
-% These results together suggest that the a polynomial-time definable
-
-% use of to compute the orbit is a particularly important limitation, as we make
-% use of a polynomial-time algorithm for deciding the orbit of a gate (or
-% element of a universe of a gate) in our proof of the main result.
-
-% Moreover, we also show that
-
-% However, if we allow gates that compute non-symmetric functions, it is not
-% clear that the syntactic-equivalence relation remains polynomial-time
-% decidable.
-
-% . prove results analogous to Lemma~\cite{} The reader will notice that, while
-% we require that the circuit families in our main result consist of transparent
-% circuits, no similar explicit condition is introduced in Anderson and
-% Dawar~\cite{}.
-
-% When Anderson and Dawar~\cite{} prove these results for symmetric circuits
-% (with symmetric gates) they explicitly use the fact that the syntactic
-% equivalence relation can be computed in polynomial time.
-
-% The proofs of these results by Anderson and Dawar~\cite{} can prove all of
-% these results
-
-% We now turn to the question of the importance of the transparency condition.
-% It could be that, just as for the case of circuits with symmetric gates, a
-% general circuit (not necessarily transparent) can be transformed in polynomial
-% time into an equivalent transparent circuit. If so, from the argument above,
-% we could assume without a loss of generality that $P$-uniform families of
-% symmetric circuit have unique extensions, eliminating the need for the
-% explicit transparency requirement present in the main theorem.
-
-% While we do not show that no such transformation exists, we do show that many
-% related problems are as hard as the graph isomorphism problem for a general,
-% not-necessarily transparent, circuit). In particular, we show that the related
-% problems of computing the syntactic equivalence relation for a circuit, or
-% whether a gate in the circuit has unique labels, or unique extensions (in the
-% sense defined below), are all also at least as hard as the graph isomorphism
-% problem. We also show that computing other basic properties of a symmetric
-% circuit, such as the orbit of a gate, is also at least as hard as the graph
-% isomorphism problem. This is a particularly important limitation, as we make
-% use of a polynomial-time algorithm for deciding the orbit of a gate (or
-% element of a universe of a gate) in our proof of the main result.
-
-% ,; address two related decision problems in Proposition \ref{} and Corollaries
-% \ref{} and \ref{}. In partic
-
-% As we will show in Proposition \ref{}, formulas of $\FPR$ can be translated
-% into. For this transparent circuits. However, the transformation is
-% complicated by the requirement that the resultant circuit be transparent.
-% However, it is worth asking if the transparency condition is required, i.e. if
-% it can be shown that
-
-% \emph{rigid} circuit. They show that all circuits such circuits can be
-% transformed into equivalent rigid circuits . They show that if a circuit is
-% rigid then it has unique extensions and that every circuit with injective
-% labels and symmetric gates can be transformed into an equivalent rigid circuit
-% in polynomial time. We have similarly shown that a transparent circuit can be
-% transformed into an equivalent one with unique labels in polynomial time, and
-% that circuits with unique labels have unique extensions. Moreover, since all
-% circuits with symmetric gates and injective labels are transparent, this is a
-% strict generalisation of their result.
-
-% and they show that a symmetric gate
-
-% Using the language developed in this paper, a circuit $C_n$ is \emph{rigid} if
-% it has injective labels and there are no two gates $g$ and $h$ in $C_n$ such
-% that $g$ and $h$ are syntactically equivalent. Since their discussion is
-% limited to circuits with symmetric gates and injective labels this is equ
-
-% circuit, a condition analogous to the rigidity condition defined in this
-% paper. The following
-
-% It is worth noting that all symmetric circuits are transparent, and
-
-% prove that it's a sufficient condition for establishing the uniqueness of the
-% induced automorphism on the circuit. Moreover, they prove that any circuit
-% (noting that they limit themselves to a discussion of circuits over a
-% symmetric basis) may be transformed into an equivalent rigid circuit in
-% polynomial time. As such, they may assume $P$-uniform symmetric circuit
-% families are rigid without a loss of generality, and hence be may assume
-% without a loss of generality that each permutation in $\sym_n$ uniquely
-% extends to an automorphism of the circuit.
-
-% However, in this subsection we show that deciding the rigidity of circuits
-% over bases which may include non-symmetric functions is at least as hard as
-% the graph isomorphism problem. However, we shoudl that on classes
-
-% Although the rigidity condition we present in this paper is similarly defined,
-% the existence of a polynomial-time computable transformation of a circuit into
-% an equivalent rigid circuit is not as straight forward. Indeed, it is possible
-% to show that the problem of determining if a given $(\mathbb{B},
-% \tau)$-circuit is rigid is as least as hard as the graph isomorphism problem.
-% This is a direct consequence of the following result.
-
-% \begin{definition}
-%   The \emph{syntactic equivalence class problem} is the decision problem for
-%   the set of all triples $(C, g_1, g_2)$, where $C$ is a $(\mathbb{B},
-%   \tau)$-circuit, and $g_1$ and $g_2$ are two syntactically equivalent gates
-%   in $C$.
-% \end{definition}
-
-% \begin{definition}
-%   The \emph{rigidity problem} is the decision problem for the set of all
-%   circuits $C$ where $C$ is a rigid circuit.
-% \end{definition}
-
-% \begin{definition}
-%   The \emph{unique labels problem} is the decision problem for the set of all
-%   circuits $C$ where $C$ has unique labels.
-% \end{definition}
-
-% \begin{prop}
-%   Let $\tau$ be any non-empty relational vocabulary and let $n, r, p \in
-%   \nats$ with $p$ prime. There is a a polynomial time reduction from the graph
-%   isomorphism problem to the problem of deciding if a given pair of gates in a
-%   given symmetric rank-circuit for structures of size $n$ that (i) has
-%   injective labels, (ii) contains no constant gates, and (iii) contains at
-%   most two rank gates with bound $r$ and prime $p$, are syntactically
-%   equivalent.
-%   \label{prop:syntactic-graph-iso}
-% \end{prop}
-% \begin{proof}
-%   We have from \cite{} that there is a polynomial time reduction from the
-%   graph isomorphism problem to the bipartite isomorphism problem. The
-%   bipartite isomorphism problem is the decision problem for the set of all
-%   pairs of partitioned bipartite graphs $B_1 := (U_1, V_1, E_1)$ and $B_2 :=
-%   (U_2, V_2, E_2)$ such that there exists a graph isomorphism $\pi : B_1
-%   \rightarrow B_2$ with $\restr{\pi}{U_1} = U_2$ and $\restr{\pi}{V_1} = V_2$.
-
-%   Suppose we are given two partitioned bipartite graphs $B_1 := (U_1, V_1,
-%   E_1)$ and $B_2 := (U_2, V_2, E_2)$. We assume, without a loss of generality,
-%   that there exists $a, b \in \nats$ such that $U_1 = U_2 = [a]$ and $V_1 =
-%   V_2 = [b]$.
-
-%   Let $R$ be a relation symbol in $\tau$ and let $k := \arty{R}$. Let $G_{R}
-%   := \{g_{R, \vec{c}} : \vec{c} \in [n]^k\}$, $G_{\text{mid}} := \{\land_0,
-%   \land_1, \neg_0, \land_{\text{out}} \}$, $G_{\rank} : = \{ g_{\rank, 1},
-%   g_{\rank, 2}\}$, and $G_{\land} := \{g_{i, (u,v)} : i \in [2] \, (u,v) \in
-%   E_i \}$. Let $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a
-%   $(\{\rank^{1}_2\}, \tau)$-circuit defined as follows. Let $G = G_R \cup
-%   G_{\text{mid}} \cup G_{\rank} \cup G_{\land}$ and $\Omega$ be the $0$-ary
-%   function $\land_{\text{out}}$. For each $\vec{c} \in [n]^{\arty{R}}$ let
-%   $\Lambda(\vec{c}) = g_{R, \vec{c}}$. Define $\Sigma$ as follows. For each $g
-%   \in G$,
-%   \begin{itemize}
-%     \setlength\itemsep{0mm}
-%   \item if $g \in G_R$ then $\Sigma(g) = R$,
-%   \item if $g$ equals $\land_0$ or $\land_1$ then $\Sigma(g) = \land[n^k]$
-%   \item if $g$ equals $\land_{\text{out}}$ then $\Sigma(g) = \land[2]$,
-%   \item if $g \in G_\rank$ let $\Sigma(g) = \rank^r_p [a,b]$, and
-%   \item if $g \in G_{\text{in}}$ and $g$ then $\Sigma(g) = \land[1]$.
-%   \end{itemize}
-%   Define $L$ as follows. For each $g \in G$,
-%   \begin{itemize}
-%     \setlength\itemsep{0mm}
-%   \item if $g \in G$ and $g = g_{\text{out}}$ then for each $i \in [2]$,
-%     $L(g)(i) := g_{\rank, i}$,
-%   \item if $g \in G_\rank$ and $g = g_{\rank, i}$ then $L(g)(p,q) = g_{i,
-%     (p,q)}$,
-%   \item if $g \in G_{\land}$ and $g = g_{i, (p,q)}$ then $L(g)(1) = \land_1$
-%     if $(p,q) \in E_i$ and $L(g)(1) = \neg_0$ otherwise,
-%   \item if $g = \neg_0$ then $L(g)(1) = \land_0$, and
-%   \item if $g = \land_0$ or $g = \land_1$ then for all $p \in [n^k]$ we have
-%     that $L(g)(p)$ equals $\Lambda^{-1}(\vec{c}_p)$, where $\vec{c}_p$ is the
-%     $p$th element of $[n]^k$ in the lexicographical ordering on $[n]^k$.
-%   \end{itemize}
-
-%   We note that for $i \in [2]$, $L(g_{\rank, i})(p,q) = \land_1$ if $(p,q)$ is
-%   an edge in in $B_i$ and $L(g_\rank, i)(p,q) = \neg_0$ if $(p,q)$ is not an
-%   edge in $B_i$. We thus have that $B_1$ and $B_2$ are bipartite isomorphic
-%   (in the sense defined above) if, and only if, $g_{\rank, 1}$ is
-%   syntactically equivalent to $g_{\rank, 2}$.
-
-%   Since the construction of $C_n$ can be implemented in time polynomial in the
-%   combined sizes of the input graphs, the mapping of $(B_1, B_2)$ to the tuple
-%   $(C_n, (g_{\rank, 1}, g_{\rank, 2}))$ witnesses the reduction. The result
-%   follows.
-% \end{proof}
+% In this first part of this section we showed that a number of useful
+% properties of circuits are polynomial-time decidable for transparent circuits.
+% We used these results to define a polynomial-time translation from transparent
+% circuits to equivalent circuits with unique labels. Finally, we showed that
+% for a given circuit with unique labels we can compute in polynomial-time many
+% important symmetry related properties of the circuit (e.g.\ the orbits and
+% supports of elements of the circuits, whether a circuit is symmetric, etc.).
+
+We have shown then that key properties of transparent circuits are
+polynomial-time tractable and, using these results, we have shown that
+transparent circuits can be transformed in polynomial time into circuits with
+unique labels. We have also shown that circuits with unique labels have all of
+the requisite algorithmic properties we need in order to define our translation
+from circuits to formulas. In the remainder of this section we prove that most
+of these properties, and particularly those used to define this translation to
+circuits with unique labels, are all at least as hard to decide as the graph
+isomorphism problem. In particular, we present reductions from the
+graph-isomorphism problem to most of the important decision problems addressed
+in the first part of this section, including: deciding if a circuit is
+symmetric, deciding if a gate has unique labels, deciding if two gates are
+syntactically-equivalent, deciding if two gates are in the same orbit, etc.
+Moreover, we show that many of these hardness results still hold even if we
+restrict ourselves to other natural classes of circuits (e.g.\ the class of
+circuits with injective labels, the class of circuits with unique children).
+
+These results together suggest the necessity of the restriction to transparent
+circuits. Moreover, while we do not show that there is no polynomial-time
+computable transformation from a general circuit to an equivalent transparent
+circuit (or equivalent circuit with unique labels), the difficulty associated
+with computing these basic circuit properties that seem essential for defining
+such a transformation should be considered evidence that, at the very least, the
+definition of such a translation is not easy to define.
+
+% As a final point, while we present evidence against the ability to transform
+% arbitrary circuits into transparent circuits in polynomial-time, we also show
+% that the class of transparent circuits is polynomial-time decidable. In
+% contrast, we show that deciding the class of circuits with unique extensions
+% is at least as hard as the graph-isomorphism problem.
+
+\begin{remark}
+  In this section we present a number of polynomial-time reductions from the
+  graph-isomorphism problem to various circuit-related problems. In each case we
+  present a reduction from the bipartite-isomorphism problem to the
+  circuit-related problem. This suffices as, from~\cite{Zemlyachenko1985}, there
+  is a polynomial-time reduction from the graph-isomorphism problem to the
+  bipartite-isomorphism problem. We recall that the bipartite-isomorphism
+  problem is the problem of deciding if for a given pair of bipartite graphs
+  $B_1 := (U_1, V_1, E_1)$ and $B_2 := (U_2, V_2, E_2)$ there exists a (graph)
+  isomorphism $\pi : B_1 \rightarrow B_2$ such that $\restr{\pi}{U_1} = U_2$ and
+  $\restr{\pi}{V_1} = V_2$.
+
+  We usually assume, without a loss of generality, that the two input graphs
+  have the property that $[a] = U_1 = U_2$ and $[b] = V_1 = V_2$ for some $a,b
+  \in \nats$.
+\end{remark}
 
@@
 \begin{proof}
-  We have from \cite{} that there is a polynomial time reduction from the graph
-  isomorphism problem to the bipartite isomorphism problem. The bipartite
-  isomorphism problem is the decision problem for the set of all pairs of
-  partitioned bipartite graphs $B_1 := (U_1, V_1, E_1)$ and $B_2 := (U_2, V_2,
-  E_2)$ such that there exists a graph isomorphism $\pi : B_1 \rightarrow B_2$
-  with $\restr{\pi}{U_1} = U_2$ and $\restr{\pi}{V_1} = V_2$.
-
   Suppose we are given two partitioned bipartite graphs $B_1 := (U_1, V_1, E_1)$
@@
   [b]$.
+
+  The idea is to construct a circuit with $n$ inputs, and with two designated
+  gates used to encode the presence or absence of an edge, and two rank gates
+  wired up so as to encode the two graphs. We wire the circuit such that, for a
+  given rank gate, the child gate labelled by $(p,q)$ has exactly one of the two
+  designated gates as a child, with the choice of which one depending on whether
+  $(p,q)$ is an edge in the associated graph. In this sense the circuit encodes
+  the two bipartite graphs at the rank gates, and the two gates being
+  syntactic-equivalence corresponds to the presence of a bipartite-isomorphism
+  between the two graphs. We now present this construction formally.
 
@@
   G_R \cup G_{\text{mid}} \cup G_{\rank} \cup G_{\text{nodes}}$ and $\Omega$ be
-  the $0$-ary function $g_{\text{out}}$. For each $\vec{c} \in
-  [n]^{\arty(R)}$ let $\Lambda_R(\vec{c}) = g_{R, \vec{c}}$. Define $\Sigma$ as
-  follows. For each $g \in G$,
+  the $0$-ary function $g_{\text{out}}$. For each $\vec{c} \in [n]^{\arty(R)}$
+  let $\Lambda_R(\vec{c}) = g_{R, \vec{c}}$. Define $\Sigma$ as follows. For
+  each $g \in G$,
   \begin{myitemize}
@@
   \item if $g \in G_{\text{nodes}}$ then $\Sigma(g) = \AND[1]$,
-  \item if $g = \AND[n^k]$, $\Sigma (g) = \AND[n^k]$ and if $g = g_{\lor}$
-    then $\Sigma(g) = \OR[n^k]$, and
+  \item if $g = \AND[n^k]$, $\Sigma (g) = \AND[n^k]$ and if $g = g_{\lor}$ then
+    $\Sigma(g) = \OR[n^k]$, and
   \item if $g \in G_R$ then $\Sigma(g) = R$.
@@
   $L(g^i_\rank)(p,q) $ equals $g_\lor$ if, and only if, $(p,q)$ is not an edge
-  in $B_i$. We thus have that $B_1$ and $B_2$ are bipartite-isomorphic (in the
-  sense defined above) if, and only if, there exists $\lambda \in \sym_{a}
-  \times \sym_{b} = \aut(g^1_{\rank}) = \aut(g^2_{\rank})$ such that for all
-  $(u,v) \in [a] \times [b] = \ind(g^1_{\rank})$, $L(g^1_{\rank})((u,v)) = g_{1,
-    (u,v)} \equiv g_{2, \lambda (u,v)} = L(g^2_{\rank})(\lambda (u,v))$. It
-  follows that $B_1$ and $B_2$ are bipartite-isomorphic if, and only if,
-  $g^1_{\rank} \equiv g^2_{\rank}$.
+  in $B_i$. We thus have that $B_1$ and $B_2$ are bipartite-isomorphic if, and
+  only if, there exists $\lambda \in \sym_{a} \times \sym_{b} =
+  \aut(g^1_{\rank}) = \aut(g^2_{\rank})$ such that for all $(u,v) \in [a] \times
+  [b] = \ind(g^1_{\rank})$, $L(g^1_{\rank})((u,v)) = g_{1, (u,v)} \equiv g_{2,
+    \lambda (u,v)} = L(g^2_{\rank})(\lambda (u,v))$. It follows that $B_1$ and
+  $B_2$ are bipartite-isomorphic if, and only if, $g^1_{\rank} \equiv
+  g^2_{\rank}$.
 
@@
   syntactically-equivalent.
-  \label{lem:syntactically-equivilent-general-hard}
+  \label{cor:syntactically-equivilent-general-hard}
 \end{cor}
@@
 We now show that the syntactic-equivalence relation remains hard to compute if
-we restrict ourselves to class of circuits such that each non-symmetric gate has
-unique children.
+we restrict ourselves to the class of circuits such that each non-symmetric gate
+has unique children.
 
@@
 \begin{proof}
-  We use a similar approach as in Proposition~\ref{prop:syntactic-graph-iso},
-  again using the reduction from graph-isomorphism to the bipartite
-  graph-isomorphism problem.
+  We use a similar approach as in the proof of
+  Proposition~\ref{prop:syntactic-graph-iso}. All that is really required is to
+  delete the row of gates between the two designated gates that encode the
+  existence or absence of an edge and the two rank gates, and replacing this
+  gate with a wire. We now present this reduction formally.
 
@@
 each non-symmetric gate has unique children
-(Lemma~\ref{lem:syntactic-equivalence-unique-gates-hard}).
+(Lemma~\ref{lem:syntactic-equivalence-unique-gates-hard}). It would seem then
+that while the conjunction of these two properties is sufficient, they are not
+if taken individually.
 
@@
 injective labels. In other words, the class of circuits that have unique
-children and \emph{almost} have unique labels but for two gates.
+children and \emph{almost} have unique labels -- in that all but two gates have
+unique labels.
 
@@
   The graph-isomorphism problem is polynomial-time reducible to the problem of
-  deciding if a reduced circuit in which all but two gates in the circuit have
-  unique labels is symmetric.
+  deciding if a circuit is symmetric. In fact, the graph-isomorphism problem is
+  polynomial-time reducible to the problem of deciding if a reduced circuit in
+  which all but two gates in the circuit have unique labels is symmetric.
   \label{prop:graph-iso-symmetric}
@@
 \begin{proof}
-  We use a similar approach as in Proposition~\ref{prop:syntactic-graph-iso},
-  and so proving a reduction from the bipartite-graph-isomorphism to the problem
-  of deciding if a circuit is symmetric.
+  We use a similar approach as in the proof of
+  Proposition~\ref{prop:syntactic-graph-iso}. In this case we construct a
+  circuit with two inputs, and each input is connected to an approximate copy of
+  the circuit defined in the proof of
+  Lemma~\ref{lem:syntactic-equivalence-unique-gates-hard}. We now define this
+  reduction formally.
 
@@
   Let $\rho:= \{R\}$ be a relational vocabulary, where $R$ is a unary relational
-  symbol. Fix any number $r$ and prime $p$. We define a $(\rho, \RB)$-circuit $C
+  symbol. Fix any number $r$ and prime $p$. We define a $(\RB, \rho)$-circuit $C
   := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ of order two as follows. Let
@@
 
-  % Let
-  % $G_{R} := \{g_{R, 1}, g_{R_2}\}$ and $G_{\text{mid}} := \{g^1_{\land},
-  % g^2_\land, g^1_\lor, g^2_\lor , \land_{\text{out}}\}$, $G_{\rank} : = \{
-  % g_{\rank, 1}, g_{\rank, 2}\}$, and $G_{\text{nodes}} := \{g_{i, (u,v)} : i
-  % \in
-  % [2] \, (u,v) \in [a] times [b] \}$. Let $G = G_R \cup G_{\text{mid}} \cup
-  % G_{\rank} \cup G_{\text{nodes}}$ and $\Omega$ be the $0$-ary function
-  % $\land_{\text{out}}$. Let $\Lambda(1) := g_{R, 1}$ and $\Lambda(2) :=
-  % g_{R,2}$. Define $\Sigma$ as follows. For each $g \in G$,
-  % \begin{itemize}
-  %   \setlength\itemsep{0mm}
-  % \item if $g$ equals $\land_{\text{out}}$ then $\Sigma(g) = \land[2]$,
-  % \item if $g \in G_\rank$ let $\Sigma(g) = \rank^r_p [a,b]$,
-  % \item if $g \in G_{\text{nodes}}$ then $\Sigma(g) = \land[1]$,
-  % \item if $g \in G_{\text{mid}}$ and $g = g^i_s$ for $ \in [2]$ and symbol
-  %   $s$
-  %   then $\Sigma(g) = s[1]$, and
-  % \item if $g \in G_R$ then $\Sigma(g) = R$.
-  % \end{itemize}
-  % Define $L$ as follows. For each $g \in G$,
-  % \begin{itemize}
-  %   \setlength\itemsep{0mm}
-  % \item if $g = g_{\text{out}}$ then for each $i \in [2]$, $L(g)(i) :=
-  %   g_{\rank,
-  %   i}$,
-  % \item if $g \in G_\rank$ and $g = g_{\rank, i}$ then $L(g)(p,q) = g_{i,
-  %   (p,q)}$,
-  % \item if $g \in G_{\text{nodes}}$ and $g = g_{i, (p,q)}$ for some $i \in
-  %   [2]$,
-  %   then $L(g)(1) = g^i_\land$ if $(p,q) \in E_i$ and $L(g)(1) = g^i_\lor$
-  %   otherwise , and
-  % \item if $g = g^i_\land$ or $g = g^i_{\lor}$ for some $i \in [2]$, then
-  %   $L(g)(1) = \Lambda^{-1}(i)$.
-  % \end{itemize}
-
-  % We note that for $i \in [2]$, the child of $L(g_{\rank, i})(p,q)$ equals
-  % $g^i_\land$ if, and only if, $(p,q)$ is an edge in $B_i$ and the child of
-  % $L(g_{\rank, i})(p,q)$ equals $g^i_\lor$ if, and only if, $(p,q)$ is not an
-  % edge in $B_i$. It can be shown that $C$ is symmetric if, and only if, there
-  % exists an extension of the transposition $(1,2)$ to an automorphism of the
-  % circuit, which holds if, and only if, there exists an extension of $(1,2)$
-  % to
-  % an automorphism of the circuit such that $(1,2) (L(g_{\rank, 1}))$ is
-  % isomorphism-equivalent to $L(g_{\rank, 2})$, which holds if, and only if,
-  % $B_1$ and $B_2$ are bipartite-isomorphic.
-
-  % Suppose $C$ is not symmetric. If $\vert L(g_{\rank,1})^{-1}(\land^1_1) \vert
-  % \neq L_(g_{\rank,2})^{-1}(\land^2_1) \vert$ then clear $B_1$ and $B_2$ are
-  % not biparetite-isomorphic as they have different numbers of edges. Suppose
-  % $\vert L(g_{\rank,1})^{-1}(\land^1_1) \vert =
-  % L_(g_{\rank,2})^{-1}(\land^2_1) \vert$. Then the only reason $C$ would not
-  % be symmetric is that there is no extension of $\sigma$ to the circuit t
-
-  % If $B_1$ and $B_2$ are
-
-  % We thus have that if $B_1$ and $B_2$ are bipartite-isomorphic
-
-  % (in the sense defined in the proof of
-  % Proposition~\ref{prop:syntactic-graph-iso}) if, and only if, $g_{\rank, 1}$
-  % is syntactically-equivalent to $g_{\rank, 2}$.
   It is easy to see that all gates in the circuit are part of a singleton
@@
 
-Note that, in Proposition~\ref{prop:graph-iso-symmetric} we again have a
-hardness result for deciding a basic circuit property even if we restrict
-ourselves to reduced circuits (and so ones where each gate has unique children).
-It is possible to alter this reduction, using a construction analogous to the
-one used in the proof of Proposition~\ref{prop:syntactic-graph-iso}, to prove
-that deciding symmetry is also hard for circuits with injective labels. In
-contrast, we have from Proposition~\ref{lem:computing-support-orbit-index} that
-we can decide symmetry for transparent circuits (i.e. circuits where every
-non-symmetric gate has unique children and injective labels) in polynomial-time.
-These observations again suggest both the robustness of this hardness result,
-and the importance of the transparency condition.
-
-We now show that computing the orbit of a gate for a general circuit is as hard
-as the graph isomorphism problem. We make use of the ability to compute the
-orbit of a gate in polynomial-time in
-Section~\ref{sec:translating-formulas-to-FPR}, when translating families of
-circuits into equivalent formulas.
+We note that Proposition~\ref{prop:graph-iso-symmetric} gives us that deciding
+symmetry, even if we restrict ourselves to reduced circuits or circuits with
+unique children, is as hard as the graph isomorphism problem. Moreover, it is
+possible to alter this reduction, using a construction analogous to the one used
+in the proof of Proposition~\ref{prop:syntactic-graph-iso}, in order to
+reproduce this hardness result with an additional restriction to circuits with
+injective labels. In contrast, we have from
+Lemma~\ref{lem:computing-support-orbit-index} that we can decide symmetry for
+transparent circuits (i.e.\ circuits where every non-symmetric gate has unique
+children and injective labels) in polynomial-time. These observations again
+suggest both the robustness of this hardness result and the importance of the
+transparency condition.
+
+In Lemma~\ref{} we showed that for circuits with unique labels, we can compute
+in polynomial-time the action of an automorphism on the gates of a circuit. In
+Proposition~\ref{} we show that we can also compute the orbit and supports of
+gates in polynomial-time. These results play a very central role in our
+translation from families of circuits to formulas, and hence in the proof of our
+main result. We now show that deciding the orbit of a gate for a general circuit
+is at least as hard as the graph isomorphism problem. We show that this result
+holds even if we restrict our attention to circuits with unique extensions or
+circuits with injective labels.
 
 \begin{lem}
-  There is a polynomial-time reduction from the graph isomorphism problem to the
-  problem of computing if two gates in a given circuit are in the same orbit.
+  There are polynomial-time reductions from the graph-isomorphism problem to the
+  problem of deciding if two given gates in a given circuit are in the same
+  orbit. In fact, this reduction holds even if we restrict ourselves to circuits
+  with unique extensions, circuits with unique children, or to circuits with
+  injective labels.
   \label{lem:graph-iso-to-orbit}
@@
 \begin{proof}
-  Let $C$ be the circuit constructed in
-  Proposition~\ref{prop:syntactic-graph-iso}. We again make use of the reduction
-  from the graph isomorphism problem to the problem of deciding if two bipartite
-  graphs are bipartite-isomorphic. Let $B_1$ and $B_2$ be two bipartite graphs.
-  The mapping $(B_1, B_2)$ of to $(C, g^1_{\rank}, g^2_{\rank})$ is a reduction.
+  Let $B_1$ and $B_2$ be bipartite graphs. Let $C$ be the circuit constructed in
+  Lemma~\ref{lem:syntactic-equivalence-unique-gates-hard}. The mapping of $(B_1,
+  B_2)$ to $(C, g^1_{\rank}, g^2_{\rank})$ is a reduction from the graph
+  isomorphism problem to the problem of deciding if two gates in a circuit with
+  unique children (and so unique extensions) are in the same orbit. A similar
+  reduction using the circuit constructed in
+  Proposition~\ref{prop:syntactic-graph-iso} gives a reduction to the problem of
+  deciding if two gates in a given circuit with injective labels are in the same
+  orbit.
 \end{proof}
 
-We have from Propositions~\ref{prop:syntactic-graph-iso}
+We have from Propositions~\ref{prop:syntactic-graph-iso},
 and~\ref{prop:graph-iso-symmetric}, and
-Lemmas~\ref{lem:syntactically-equivalent-unique-labels},
-\ref{lem:graph-iso-to-orbit}
+Lemmas~\ref{lem:syntactically-equivalent-unique-labels},~\ref{lem:syntactic-equivalence-unique-gates-hard},~\ref{lem:graph-iso-to-orbit},
 and~\ref{lem:syntactically-equivilent-unique-extensions}, that a number of basic
-circuit properties are at least as hard for general circuits as the
-graph-isomorphism problem. In contrast, all of these properties are known to be
-polynomial-time decidable for transparent circuits (as follows from
-Lemmas~\ref{lem:transparent-syntactic-equiv}
-and~\ref{lem:computing-support-orbit-gate}).
-
-The hardness results for the problems of computing syntactic-equivalence
-relation and deciding if a gate has unique labels are particularly worth noting
-as many natural algorithms for translating a circuit into an equivalent
-transparent circuit (or one with unique labels) make use of polynomial-time
-decidability of these properties. Indeed, the translation defined by Anderson
-and Dawar~\cite{AndersonD17} from circuits with symmetric gates to equivalent
-circuits with unique extensions makes explicit use of the polynomial-time
-computability of the syntactic-equivalence relation on such circuits. As such,
-these results, along with the hardness results for many other basic circuit
-properties (e.g. symmetry, unique extensions, or the orbits of a gate) provides
-evidence against the existence of an easily-definable polynomial-time
-translation from circuits to transparent circuits, or circuits with unique
-labels.
-
-% We note that in all of the above casesgive us that many circuit properties of
-% interest are harder to compute than the graph-isomorphism problem. In
-% particular, determining
-
-% We have shown that basic properties of a circuit, including the ability to
-% compute the syntactic equivalence relation or whether a gate has unique
-% labels, are as hard to decide as the graph-isomorphism problem. Moreover,
-
-% incluidng that various properties of the circuit that seem necessary for
-% defining a translation of a circuit into an equivalent transparent circuit are
-% as hard to compute as the graph-isomorphism problem. We note that all of these
-% properties are polynomial-time computable for transparent circuits (as follows
-% from Lemma~\ref{} and Lemma~\ref{}).
-
-While we have provided evidence against the ability to efficiently transform a
-circuit into an equivalent transparent circuit, we now show that, in contrast,
-there is a polynomial-time algorithm for checking if a circuit is transparent.
-This has a certain significance, as we now have transparency is not some
-unverifiable condition on circuits, further motivating the usefulness of this
-definition.
-
-\begin{prop}
-  There is an algorithm that takes as input a circuit, decides if that circuit
-  is transparent and runs in time polynomial in the size of the circuit.
-  \label{prop:transparent-polynomial-time}
-\end{prop}
-\begin{proof}
-  Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
-  \rho)$-circuit. We first check that, for each non-symmetric gate $g \in G$,
-  $L(g)$ is an injection. If not, we return that $C$ is not transparent.
-
-  For each $p \in \nats$ let $G^p \subseteq G$ be the set of all gates of depth
-  $p$ and let $G^{\leq p} = \bigcup_{0 \leq i \leq p}G^i$. Note that each $g \in
-  G^1$, $g$ has unique labels. Thus, from
-  Lemma~\ref{lem:transparent-syntactic-equiv}, we can compute the syntactic
-  equivalence relation between gates in $G^{\leq 1}$ efficiently. We construct a
-  loop as follows. Let $p$ be initialised to $1$. We have that every
-  non-symmetric gate $g \in G^{\leq p}$ has unique gates. We compute the
-  syntactic-equivalence relation on $G^{\leq p}$ and check if each non-symmetric
-  gate in $g \in G^{i + 1}$ has unique labels. If not, halt and output that the
-  circuit is not transparent. If $p = \depth(C) -1$ then halt and output that
-  the circuit is transparent. If neither halt state is reached, then increment
-  $p$ by one and continue to the next iteration of the loop.
-
-  We note that in every iteration of the loop we have that every non-symmetric
-  gate in $G^{\leq p}$ has unique labels. Thus, from Proposition
-  \ref{lem:transparent-syntactic-equiv}, we may compute the
-  syntactic-equivalence relation on this set of gates efficiently. It follows
-  that the above algorithm can be implemented so as to run in polynomial time.
-\end{proof}
-
-We similarly have that the unique labels property on circuits can be decided in
-time polynomial in the number of gates in the circuit.
-
-\begin{cor}
-  There is an algorithm that takes in a circuit and decides if that circuit has
-  unique labels and runs in time polynomial in the size of the circuit.
-\end{cor}
-\begin{proof}
-  Let $C$ be the input circuit. From
-  Proposition~\ref{prop:transparent-polynomial-time} we may check if $C$ is
-  transparent in time polynomial in the size of $C$. If $C$ is not transparent
-  halt and output that $C$ does not have unique labels. If $C$ is transparent
-  then from Lemma~\ref{lem:transparent-syntactic-equiv} we may compute the
-  syntactic-equivalence relation on the gates of $C$ in time polynomial in the
-  size of $C$. Note that $C$ has unique labels if, and only if, for each gate
-  $g$ in $C$, $\vert \ind(g) \vert = \vert H_g /_\equiv \vert$. We may thus
-  check if $C$ has unique labels by iterating through the gates of $C$. This can
-  be done in time polynomial in the size of $C$.
-\end{proof}
-
-% perhaps related to the problem of translating a circuit into an equivalent
-% transparent circuit are at least as hard as the graph isomorphism problem. We
-% now show that additionally recognising if a circuit has unique extensions is
-% at least as hard as the graph isomorphism problem.
-
-We have restricted ourselves to transparent circuits in large part because they
-can be transformed in polynomial-time into circuits with unique extensions and
-because the transparency property is polynomial-time verifiable. It may be asked
-why we do not just include an explicit restriction to circuits with unique
-extensions. We now show that, in contrast with transparency, the problem of
-deciding if a circuit has unique-extensions is at least as hard as the
-graph-isomorphism problem.
+circuit properties are at least as hard for general circuits -- and circuits
+with unique extensions, rigid circuits, and circuits with injective labels -- as
+the graph-isomorphism problem. In contrast, as proved in the first part of this
+section, all of these properties are known to be polynomial-time decidable for
+transparent circuits.
+
+These hardness results for syntactic-equivalence and deciding if a gate has
+unique labels are particularly worth noting, as many natural algorithms for
+translating a circuit into an equivalent transparent circuit (or circuit with
+unique labels) make use of the polynomial-time decidability of these properties.
+Indeed, the translation defined by Anderson and Dawar~\cite{AndersonD17} from
+circuits with symmetric gates to equivalent circuits with unique labels, and the
+translation we define in Lemma~\ref{lem:transparent-unique} for transparent
+circuits, makes explicit use of the polynomial-time computability of the
+syntactic-equivalence relation for such circuits. As such, these hardness
+results, along with the hardness results for many other basic circuit
+properties, should be considered evidence against the existence of an
+easily-definable polynomial-time translation from general circuits to
+transparent circuits or to circuits with unique labels.
+
+% While we have provided evidence against the ability to efficiently transform a
+% circuit into an equivalent transparent circuit, we now show that, in contrast,
+% there is a polynomial-time algorithm for checking if a circuit is transparent.
+% This has a certain significance, as we now have transparency is not some
+% unverifiable condition on circuits, further motivating the usefulness of this
+% definition.
+
+% GW: This final result may be unnecessary.
+
+In Proposition~\ref{prop:transparent-polynomial-time} and
+Corollary~\ref{cor:unique-labels-polynomial-time} we showed that both the class
+of transparent circuits and the class of circuits with unique labels are
+polynomial-time decidable. These results suggest that, while it may be hard to
+transform a circuit into an equivalent transparent circuit or a circuit with
+unique labels, verifying these properties is at least tractable. We now show
+that many other seemingly natural classes of circuits are at least as hard to
+decide as the graph-isomorphism problem.
 
 \begin{lem}
-  There is a polynomial-time reduction from the graph isomorphism problem to the
-  problem of determining if a given circuit does not have unique extensions.
+  There are polynomial-time reductions from the graph isomorphism problems to
+  the problems of deciding if a circuit does not have unique extensions and the
+  problem of deciding if a circuit does not have unique children.
   \label{lem:unique-extensions-hard}
@@
 \begin{proof}
-  We use a similar approach as in Proposition~\ref{prop:syntactic-graph-iso},
-  again arguing using a reduction from the graph-isomorphism problem to
-  bipartite-graph isomorphism problem. Suppose we are given two partitioned
-  bipartite graphs $B_1 := (U_1, V_1, E_1)$ and $B_2 := (U_2, V_2, E_2)$. We
-  assume, without a loss of generality, that there exists $a, b \in \nats$ such
-  that $U_1 = U_2 = [a]$ and $V_1 = V_2 = [b]$.
-
-  Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\RB,
-  \{R\})$-circuit of order one defined as follows. Let $G_R := \{g_R\}$, $G_1 :=
-  \{ g_{\lor}, g_{\land} \}$, $G_{\rank} := \{ g^1_{\rank}, g^2_{\rank} \}$ and
-  $G = G_R \cup G_1 \cup G_1 \cup G_{\rank} \cup \{ g_{\text{out}} \}$. Let
-  $\Omega = g_{\text{out}}$ an $\Lambda_R (g_R) = 1$. Let $\Sigma (g_R) = R$,
-  $\Sigma (g_\lor) = \OR[1]$, $\Sigma (g_\land) = \AND[1]$, $\Sigma
-  (g_{\text{out}}) = \AND[2]$ and for all $g \in G_{\rank}$, $\Sigma (g) =
-  \AND[a,b]$. Let $L(g_\lor)(1) L(g_\land)(1) = g_R$, for all $i \in [2]$,
-  $L(g_{\text{out}})(i) = g^i_{\rank}$ and for all $(u, v) \in \ind(g)$,
-  $L(g^i_{\rank})(u,v) = g_{\land}$ if $(u, v) \in E_i$ and $L(g^i_{\rank} (u,v)
-  = g_{\lor}$ otherwise.
-
-  Suppose $B_1$ and $B_2$ are bipartite-isomorphic. Then there exists $\lambda
-  \in [a] \times [b]$ such that $(u,v) \in E_1$ if, and only if, $\lambda (u,v)
-  \in E_2$. It follows that $L(g^1_{\rank})((u,v)) =
-  L(g^2_{\rank})(\lambda(u,v))$. Let $\pi_{\lambda}: G \rightarrow G$ be defined
-  such that if $g = g^i_{\rank}$ for $i \in [2]$, $\pi_{\lambda} g =
-  g^j_{\rank}$ where $j \in [2] \setminus \{i\}$ and otherwise $\pi_{\lambda} g
-  = g$. It is easy to see that $\pi_{\lambda}$ is a bijection. Moveover, for
-  $(u,v) \in \sym_a \times \sym_b$ $\pi_{\lambda} L(g^1_{\rank})((u,v)) =
-  L(g^2_{\rank})(\lambda (u,v)) = L(\pi_\lambda g^1_{\rank})(\lambda (u,v))$.
-  Similarly, $\pi_\lambda L(g^2_{\rank})((u,v)) =
-  L(\pi_{\lambda}g^2_{\rank})(\lambda^{-1}(u,v))$. It follows that $\pi_\lambda$
-  is a non-trivial automorphism of $C$ extending the trivial permutation, and so
-  $C$ does not have unique extensions.
-
-  Suppose $C$ does not have unique extensions. Then there exists an automorphism
-  $\pi$ of the circuit extending the trivial permutation such that $\pi
-  g^1_{\rank} = g^2_{\rank}$. But then there exists $\lambda \in \sym_a \times
-  \sym_b$ such that for all $(u,v) \in [a]\times [b]$, $\pi
-  L(g^1_{\rank})((u,v)) = L(g^1_{\rank})((u,v)) = L(g^2_{\rank})(\lambda
-  (u,v))$. But then $(u,v) \in E_1$ if, and only if, $L(g^1_{\rank})((u,v)) =
-  g_{\land}$, if and only if, $L(g^2_{\rank})(\lambda(u,v)) = g_{\land}$ if, and
-  only if, $\lambda (u,v) \in E_2$. It follows $B_1$ and $B_2$ are
-  bipartite-isomorphic.
+  In both cases the circuit constructed in the proof of
+  Lemma~\ref{lem:syntactic-equivalence-unique-gates-hard} suffices for the
+  reduction.
 \end{proof}
+
+% \begin{proof}
+%   We use a similar approach as in Proposition~\ref{prop:syntactic-graph-iso},
+%   again arguing using a reduction from the graph-isomorphism problem to
+%   bipartite-graph isomorphism problem. Suppose we are given two partitioned
+%   bipartite graphs $B_1 := (U_1, V_1, E_1)$ and $B_2 := (U_2, V_2, E_2)$. We
+%   assume, without a loss of generality, that there exists $a, b \in \nats$
+%   such that $U_1 = U_2 = [a]$ and $V_1 = V_2 = [b]$.
+
+%   Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\RB,
+%   \{R\})$-circuit of order one defined as follows. Let $G_R := \{g_R\}$, $G_1
+%   := \{ g_{\lor}, g_{\land} \}$, $G_{\rank} := \{ g^1_{\rank}, g^2_{\rank}
+%   \}$, and $G = G_R \cup G_1 \cup G_1 \cup G_{\rank} \cup \{ g_{\text{out}}
+%   \}$. Let $\Omega = g_{\text{out}}$ and $\Lambda_R (g_R) = 1$. Let $\Sigma
+%   (g_R) = R$, $\Sigma (g_\lor) = \OR[1]$, $\Sigma (g_\land) = \AND[1]$,
+%   $\Sigma (g_{\text{out}}) = \AND[2]$ and for all $g \in G_{\rank}$, $\Sigma
+%   (g) = \RANK[a,b]$. Let $L(g_\lor)(1) = L(g_\land)(1) = g_R$, for all $i \in
+%   [2]$, $L(g_{\text{out}})(i) = g^i_{\rank}$ and for all $(u, v) \in \ind(g)$,
+%   $L(g^i_{\rank})(u,v) = g_{\land}$ if $(u, v) \in E_i$ and $L(g^i_{\rank}
+%   (u,v) = g_{\lor}$ otherwise.
+
+%   Suppose $B_1$ and $B_2$ are bipartite-isomorphic. Then there exists $\lambda
+%   \in [a] \times [b]$ such that $(u,v) \in E_1$ if, and only if, $\lambda
+%   (u,v) \in E_2$. It follows that $L(g^1_{\rank})((u,v)) =
+%   L(g^2_{\rank})(\lambda(u,v))$. Let $\pi_{\lambda}: G \rightarrow G$ be
+%   defined such that if $g = g^i_{\rank}$ for $i \in [2]$, $\pi_{\lambda} g =
+%   g^j_{\rank}$ where $j \in [2] \setminus \{i\}$ and otherwise $\pi_{\lambda}
+%   g = g$. It is easy to see that $\pi_{\lambda}$ is a bijection. Moveover, for
+%   $(u,v) \in \sym_a \times \sym_b$ $\pi_{\lambda} L(g^1_{\rank})((u,v)) =
+%   L(g^2_{\rank})(\lambda (u,v)) = L(\pi_\lambda g^1_{\rank})(\lambda (u,v))$.
+%   Similarly, $\pi_\lambda L(g^2_{\rank})((u,v)) =
+%   L(\pi_{\lambda}g^2_{\rank})(\lambda^{-1}(u,v))$. It follows that
+%   $\pi_\lambda$ is a non-trivial automorphism of $C$ extending the trivial
+%   permutation, and so $C$ does not have unique extensions.
+
+%   Suppose $C$ does not have unique extensions. Then there exists an
+%   automorphism $\pi$ of the circuit extending the trivial permutation such
+%   that $\pi g^1_{\rank} = g^2_{\rank}$. But then there exists $\lambda \in
+%   \sym_a \times \sym_b$ such that for all $(u,v) \in [a]\times [b]$, $\pi
+%   L(g^1_{\rank})((u,v)) = L(g^1_{\rank})((u,v)) = L(g^2_{\rank})(\lambda
+%   (u,v))$. But then $(u,v) \in E_1$ if, and only if, $L(g^1_{\rank})((u,v)) =
+%   g_{\land}$, if and only if, $L(g^2_{\rank})(\lambda(u,v)) = g_{\land}$ if,
+%   and only if, $\lambda (u,v) \in E_2$. It follows $B_1$ and $B_2$ are
+%   bipartite-isomorphic.
+% \end{proof}
+% \begin{proof}
+%   We use a similar approach as in Proposition~\ref{prop:syntactic-graph-iso},
+%   again arguing using a reduction from the graph-isomorphism problem to
+%   bipartite-graph isomorphism problem. Suppose we are given two partitioned
+%   bipartite graphs $B_1 := (U_1, V_1, E_1)$ and $B_2 := (U_2, V_2, E_2)$. We
+%   assume, without a loss of generality, that there exists $a, b \in \nats$
+%   such that $U_1 = U_2 = [a]$ and $V_1 = V_2 = [b]$.
+
+%   Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\RB,
+%   \{R\})$-circuit of order one defined as follows. Let $G_R := \{g_R\}$, $G_1
+%   := \{ g_{\lor}, g_{\land} \}$, $G_{\rank} := \{ g^1_{\rank}, g^2_{\rank}
+%   \}$, and $G = G_R \cup G_1 \cup G_1 \cup G_{\rank} \cup \{ g_{\text{out}}
+%   \}$. Let $\Omega = g_{\text{out}}$ and $\Lambda_R (g_R) = 1$. Let $\Sigma
+%   (g_R) = R$, $\Sigma (g_\lor) = \OR[1]$, $\Sigma (g_\land) = \AND[1]$,
+%   $\Sigma (g_{\text{out}}) = \AND[2]$ and for all $g \in G_{\rank}$, $\Sigma
+%   (g) = \RANK[a,b]$. Let $L(g_\lor)(1) = L(g_\land)(1) = g_R$, for all $i \in
+%   [2]$, $L(g_{\text{out}})(i) = g^i_{\rank}$ and for all $(u, v) \in \ind(g)$,
+%   $L(g^i_{\rank})(u,v) = g_{\land}$ if $(u, v) \in E_i$ and $L(g^i_{\rank}
+%   (u,v) = g_{\lor}$ otherwise.
+
+%   Suppose $B_1$ and $B_2$ are bipartite-isomorphic. Then there exists $\lambda
+%   \in [a] \times [b]$ such that $(u,v) \in E_1$ if, and only if, $\lambda
+%   (u,v) \in E_2$. It follows that $L(g^1_{\rank})((u,v)) =
+%   L(g^2_{\rank})(\lambda(u,v))$. Let $\pi_{\lambda}: G \rightarrow G$ be
+%   defined such that if $g = g^i_{\rank}$ for $i \in [2]$, $\pi_{\lambda} g =
+%   g^j_{\rank}$ where $j \in [2] \setminus \{i\}$ and otherwise $\pi_{\lambda}
+%   g = g$. It is easy to see that $\pi_{\lambda}$ is a bijection. Moveover, for
+%   $(u,v) \in \sym_a \times \sym_b$ $\pi_{\lambda} L(g^1_{\rank})((u,v)) =
+%   L(g^2_{\rank})(\lambda (u,v)) = L(\pi_\lambda g^1_{\rank})(\lambda (u,v))$.
+%   Similarly, $\pi_\lambda L(g^2_{\rank})((u,v)) =
+%   L(\pi_{\lambda}g^2_{\rank})(\lambda^{-1}(u,v))$. It follows that
+%   $\pi_\lambda$ is a non-trivial automorphism of $C$ extending the trivial
+%   permutation, and so $C$ does not have unique extensions.
+
+%   Suppose $C$ does not have unique extensions. Then there exists an
+%   automorphism $\pi$ of the circuit extending the trivial permutation such
+%   that $\pi g^1_{\rank} = g^2_{\rank}$. But then there exists $\lambda \in
+%   \sym_a \times \sym_b$ such that for all $(u,v) \in [a]\times [b]$, $\pi
+%   L(g^1_{\rank})((u,v)) = L(g^1_{\rank})((u,v)) = L(g^2_{\rank})(\lambda
+%   (u,v))$. But then $(u,v) \in E_1$ if, and only if, $L(g^1_{\rank})((u,v)) =
+%   g_{\land}$, if and only if, $L(g^2_{\rank})(\lambda(u,v)) = g_{\land}$ if,
+%   and only if, $\lambda (u,v) \in E_2$. It follows $B_1$ and $B_2$ are
+%   bipartite-isomorphic.
+% \end{proof}
+
+% \begin{remark}
+%   It's interesting to note that the circuit used in the reduction does not
+%   have injective labels. If we instead ask about a reduction from GI to the
+%   problem of deciding if a circuit has unique extensions and injective labels,
+%   then I can reduce from to the problem of deciding if two rigid graphs are
+%   isomorphic. It is unknown if this decision problem is as hard as the full
+%   graph isomorphism problem. After looking around a bit I discovered that it's
+%   a very important open problem in quantum computation. Is this worth
+%   mentioning?
+% \end{remark}
 
@@
 % \end{proof}
-
-\begin{remark}
-  It's interesting to note that the circuit used in the reduction does not have
-  injective labels. If we instead ask about a reduction from GI to the problem
-  of deciding if a circuit has unique extensions and injective labels, then I
-  can reduce from to the problem of deciding if two rigid graphs are isomorphic.
-  It is unknown if this decision problem is as hard as the full graph
-  isomorphism problem. After looking around a bit I discovered that it's a very
-  important open problem in quantum computation. Is this worth mentioning?
-\end{remark}
-
 % We have that if a circuit is transparent then we may compute in polynomial
@@
 % equivalence relation is at least as hard as the graph isomorphism problem.
+
 % Moreover, other properties that can be computed in polynomial time for

### 2018-04-02 sections/symmetric-circuits.tex
I made major changes to the transparency section. I fixed a few typos in the symmetric circuits section.

@@
     \setlength\itemsep{0mm}
-  \item $G$ is called the set of gates of $C$.% and $\vert C \vert := \vert G    \vert$.
+  \item $G$ is called the set of gates of
+    $C$.% and $\vert C \vert := \vert G \vert$.
   \item $\Omega$ is an injective function from $[n]^q$ to $G$. The gates in the
@@
 
-The definition requires some explanation.  Each gate in $G$ computes a
-function of its inputs and the relation $W$ on $G$ is the set of
-``wires''.  That is, $W(h,g)$ indicates that the value computed at $h$
-is an input to $g$.  However, since the functions are structured, we
-need more information on the set of inputs to $g$ and this is provided
-by the labelling $L$.  $\Sigma(g)$ tells us what the function computed
-at $g$ is, and thus $\ind(\Sigma(g))$ tells us the structure on the
-inputs and $L(g)$ maps this to the set of gates that form the inputs
-to $g$.
+The definition requires some explanation. Each gate in $G$ computes a function
+of its inputs and the relation $W$ on $G$ is the set of ``wires''. That is,
+$W(h,g)$ indicates that the value computed at $h$ is an input to $g$. However,
+since the functions are structured, we need more information on the set of
+inputs to $g$ and this is provided by the labelling $L$. $\Sigma(g)$ tells us
+what the function computed at $g$ is, and thus $\ind(\Sigma(g))$ tells us the
+structure on the inputs and $L(g)$ maps this to the set of gates that form the
+inputs to $g$.
 
@@
 Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
-\rho)$-circuit of order $n$.  Recall that the order of a circuit refers
-to the size of the input structures it takes.  In contrast, we define
-the \emph{size} of $C$, denoted $\vert C \vert$ to be the number of
-elements in $G$. If $(C_n)_{n \in \nats}$ is a family of
-circuits we assume that each $C_n$ is a circuit of order $n$.
+\rho)$-circuit of order $n$. Recall that the order of a circuit refers to the
+size of the input structures it takes. In contrast, we define the \emph{size} of
+$C$, denoted $\vert C \vert$ to be the number of elements in $G$. If $(C_n)_{n
+  \in \nats}$ is a family of circuits we assume that each $C_n$ is a circuit of
+order $n$.
 
@@
   We now present a number of observations, and then combine these observations
-  to prove both directions of the lemma. Let $\mathcal{B}$ be a
-  $\rho$-structure of size $n$ over the universe $[n]$. We can define a function
-  $f_{\mathcal{B}} : \ind(\rho, [n]) \rightarrow {0,1}$ such that
-  $f_{\mathcal{B}} (\vec{a}_R) = 1$ if, and only if, $\vec{a} \in
-  R^{\mathcal{B}}$. Let $f : \ind(\rho, [n]) \rightarrow \{0,1\}$. We can define
-  the $\rho$-structure $\mathcal{B}_f$ over the universe $[n]$ such that for all
-  $R \in \rho$, we have $\vec{a} \in R^{\mathcal{B}_f}$ if, and only if,
-  $f(\vec{a}_R) = 1$. It is easy to see that the functions $\mathcal{B} \mapsto
-  f_{\mathcal{B}}$ and $f \mapsto \mathcal{B}_f$ are inverse to one another, and
-  so define a bijection. Moreover, we notice that for all $\sigma \in \sym_n$ we
-  have that $f_{\sigma \mathcal{B}}(\vec{a}_R) = 1$ if, and only if, $\vec{a}
-  \in R^{\sigma \mathcal{B}}$ if, and only if, $\sigma^{-1} \vec{a} \in
-  R^{\mathcal{B}}$ if, and only if, $(f_{\mathcal{B}} \sigma^{-1})(\vec{a}_R) =
+  to prove both directions of the lemma. Let $\mathcal{B}$ be a $\rho$-structure
+  of size $n$ over the universe $[n]$. We can define a function $f_{\mathcal{B}}
+  : \ind(\rho, [n]) \rightarrow {0,1}$ such that $f_{\mathcal{B}} (\vec{a}_R) =
+  1$ if, and only if, $\vec{a} \in R^{\mathcal{B}}$. Let $f : \ind(\rho, [n])
+  \rightarrow \{0,1\}$. We can define the $\rho$-structure $\mathcal{B}_f$ over
+  the universe $[n]$ such that for all $R \in \rho$, we have $\vec{a} \in
+  R^{\mathcal{B}_f}$ if, and only if, $f(\vec{a}_R) = 1$. It is easy to see that
+  the functions $\mathcal{B} \mapsto f_{\mathcal{B}}$ and $f \mapsto
+  \mathcal{B}_f$ are inverse to one another, and so define a bijection.
+  Moreover, we notice that for all $\sigma \in \sym_n$ we have that $f_{\sigma
+    \mathcal{B}}(\vec{a}_R) = 1$ if, and only if, $\vec{a} \in R^{\sigma
+    \mathcal{B}}$ if, and only if, $\sigma^{-1} \vec{a} \in R^{\mathcal{B}}$ if,
+  and only if, $(f_{\mathcal{B}} \sigma^{-1})(\vec{a}_R) =
   f_{\mathcal{B}}(\sigma^{-1} \vec{a}_R)= 1$. It follows $f_{\sigma \mathcal{B}}
@@
 does not contain a relational gate labelled by a relation symbol with non-zero
-arity.  In that case $C$ computes a constant function.  For this reason, in this paper we
-always assume a circuit contains at least one relational gate with non-zero
-arity.  Now, by assumption there exists a relational gate in $C$ such that
-some element of $[n]$ appears in the tuple labelling that gate.  By symmetry it
-follows that every elements of $[n]$ appears in a tuple labelling a relational
-gate in $C$. It follows that no two distinct elements of $\sym_n$ agree on all
-input gates, and so the homomorphism $h$ is injective.
+arity. In that case $C$ computes a constant function. For this reason, in this
+paper we always assume a circuit contains at least one relational gate with
+non-zero arity. Now, by assumption there exists a relational gate in $C$ such
+that some element of $[n]$ appears in the tuple labelling that gate. By symmetry
+it follows that every elements of $[n]$ appears in a tuple labelling a
+relational gate in $C$. It follows that no two distinct elements of $\sym_n$
+agree on all input gates, and so the homomorphism $h$ is injective.
 
@@
 of this form. It is at this point that we arrive at the first complication
-introduced by our generalisation. The polynomial-time
-translation in~\cite{AndersonD17} makes indispensable of the polynomial-time decidability of many
-important circuit properties for circuits defined over symmetric
-bases.  However,
-for the more general circuits discussed here, it is not known if even the most
-basic circuit properties are polynomial-time decidable.  This is
+introduced by our generalisation. The polynomial-time translation
+in~\cite{AndersonD17} makes indispensable of the polynomial-time decidability of
+many important circuit properties for circuits defined over symmetric bases.
+However, for the more general circuits discussed here, it is not known if even
+the most basic circuit properties are polynomial-time decidable. This is
 essentially due to the requirement built in to
-Definition~\ref{defn:automorphism} that an automorphism that takes $g$
-to $g'$ must be an isomorphism between $L(g)$ and $L(g')$, which makes
-checking the condition as hard as isomorphism checking.
-Indeed, we show in
+Definition~\ref{defn:automorphism} that an automorphism that takes $g$ to $g'$
+must be an isomorphism between $L(g)$ and $L(g')$, which makes checking the
+condition as hard as isomorphism checking. Indeed, we show in
 Section~\ref{sec:transparent} that for circuits that include gates computing
@@
 at least as hard to decide as the graph-isomorphism problem. As such,
-constructing an argument analogous to~\cite{AndersonD17}, as well as establishing the numerous other
-crucial results whose proofs rely on the polynomial-time decidability of various
-circuit properties, would be beyond the scope of this paper.
+constructing an argument analogous to~\cite{AndersonD17}, as well as
+establishing the numerous other crucial results whose proofs rely on the
+polynomial-time decidability of various circuit properties, would be beyond the
+scope of this paper.
 
@@
   or both are relational gates and $\Lambda(g) = \Lambda (h)$. Suppose $g$ and
-  $h$ are internal gates and suppose we have defined the
-  syntactic-equivalence relation for all gates of depth less than the depth of
-  either $g$ or $h$. Then $g \equiv h$ if, and only if, $L(g) /_\equiv$ and
-  $L(h) /_\equiv$ are isomorphism-equivalent.
+  $h$ are internal gates and suppose we have defined the syntactic-equivalence
+  relation for all gates of depth less than the depth of either $g$ or $h$. Then
+  $g \equiv h$ if, and only if, $L(g) /_\equiv$ and $L(h) /_\equiv$ are
+  isomorphism-equivalent.
 \end{definition}
@@
 
-For a circuit $C$ of order $n$ and a gate $g$ we think of $g$ as computing
-the function that maps an input structure $\mathcal{A}$ and a bijection $\gamma$
+For a circuit $C$ of order $n$ and a gate $g$ we think of $g$ as computing the
+function that maps an input structure $\mathcal{A}$ and a bijection $\gamma$
 from the universe of $\mathcal{A}$ to $[n]$ to the evaluation $C[\gamma
@@
   (\Omega^{-1}(g)) = \Omega (\sigma \Omega^{-1}(g)) = \pi' \Omega
-  (\Omega^{-1}(g)) = \pi'(g)$, or none of $g$, $\pi(g)$ or $\pi' (g)$ are output gates.
+  (\Omega^{-1}(g)) = \pi'(g)$, or none of $g$, $\pi(g)$ or $\pi' (g)$ are output
+  gates.
 
@@
 
-It is worth noting that if a circuit has injective labels and is reduced 
-then it has unique labels. The converse is, in general, false.
+It is worth noting that if a circuit has injective labels and is reduced then it
+has unique labels. The converse is, in general, false.
 
@@
   argument gives us that for all $h \in G$ if there exists an output gate $g$
-  such that $W_t(h, g)$, then $\pi (h) = h$. Since the circuit contains no
-  redundant gates, we have that $G = \bigcup_{\vec{a} \in [n]^q} \{g \in G : W_t
-  (g, \Omega(\vec{a}))\}$, and the result follows.
+  such that $W_t(h, g)$ or $h = g$, then $\pi (h) = h$. Since the circuit
+  contains no redundant gates, we have that $G = \bigcup_{\vec{a} \in [n]^q} \{g
+  \in G : W_t (g, \Omega(\vec{a}))\}$, and the result follows.
 \end{proof}
@@
 between two gates is as hard as the graph-isomorphism problem. It follows that a
-great many important circuit properties (e.g.\ the orbit of a gate, symmetry of a
-circuit, etc.) for circuits with unique gates are at the very least not
+great many important circuit properties (e.g.\ the orbit of a gate, symmetry of
+a circuit, etc.) for circuits with unique gates are at the very least not
 obviously polynomial-time decidable. As such, circuits with unique children,

### 2018-04-02 sections/transparency-and-unique-extensions.tex
I made major changes to the transparency section. I fixed a few typos in the symmetric circuits section.

@@
   for all $g \in G$, $g$ has unique labels in $C$ if, and only if, $[g]$ has
-  unique labels in $C_{\equiv}$.
+  unique labels in $C_{\equiv}$. In fact, for all $\sigma \in \sym_n$ if there
+  exists $\pi \in \aut(C)$ extending $\sigma$ then $\pi /_\equiv$ is an
+  automorphism of $C_\equiv$ extending $\sigma$.
   \label{lem:quotient-circuits-preserve}
@@
 
-  We now show that if $C$ is symmetric then $C_\equiv$ is symmetric. Suppose $C$
-  is symmetric. Let $\sigma \in \sym_n$. Then there exists $\pi \in \aut(C)$
-  that extends $\sigma$. Let $\pi_\equiv = pi /_\equiv$. We now show that
-  $\pi_\equiv$ is an automorphism of $C_\equiv$ extending $\sigma$. It is easy
-  to see that $\pi_\equiv$ is a bijection from $G_\equiv$ to $G_\equiv$ that
-  preserves syntactic-equivalence, and is thus is a well-defined function. Let
-  $[g] \in G_\equiv$. We have that $\Sigma_\equiv (\pi_\equiv [g]) =
-  \Sigma_\equiv ([\pi g]) = \Sigma (\pi g) = \Sigma (g) = \Sigma_\equiv ([g])$.
-  It is easy to check the automorphism conditions for input gates. Suppose $[g]$
-  is an internal gate. Let $g' \in [g]$ be such that $L_\equiv([g]) = L(g')
-  /_\equiv$ and $h \in [g]$ be such that $L_\equiv(\pi_\equiv[g]) = L_\equiv
-  ([\pi h]) = L(\pi h) /_\equiv$. We have that $\pi L(g')$ is
-  isomorphism-equivalent to $L(\pi g')$, and it follows that $(\pi
-  L(g'))/_\equiv$ is isomorphism-equivalent to $L(\pi g') /_\equiv$. We then
-  have $(\pi L(g'))/_\equiv = \pi_\equiv (L(g') /_\equiv) = \pi_\equiv L_\equiv
-  ([g])$ and, since $g' \equiv h$ and so $\pi g' \equiv \pi h$, we have that
-  $L(\pi g')/_\equiv$ is isomorphism-equivalent to $L(\pi h) /_\equiv =
-  L_\equiv(\pi_\equiv[g])$. It follows that $\pi_\equiv L_\equiv ([g])$ is
-  isomorphism-equivalent to $L_\equiv(\pi_\equiv [g]) /_\equiv$. Suppose $[g]$
-  is an output gate. Then for $\vec{a} \in \dom (\Omega)$, $\pi_\equiv
-  \Omega_\equiv (\vec{a}) = [\pi \Omega (\vec{a})] = [\Omega (\sigma \vec{a})] =
-  \Omega_\equiv (\sigma \vec{a})$.
+  Let $\sigma \in \sym_n$ and suppose there exists $\pi \in \aut(C)$ extending
+  $\sigma$. Let $\pi_\equiv = pi /_\equiv$. We now show that $\pi_\equiv$ is an
+  automorphism of $C_\equiv$ extending $\sigma$. It is easy to see that
+  $\pi_\equiv$ is a bijection from $G_\equiv$ to $G_\equiv$ that preserves
+  syntactic-equivalence, and is thus is a well-defined function. Let $[g] \in
+  G_\equiv$. We have that $\Sigma_\equiv (\pi_\equiv [g]) = \Sigma_\equiv ([\pi
+  g]) = \Sigma (\pi g) = \Sigma (g) = \Sigma_\equiv ([g])$. It is easy to check
+  the automorphism conditions for input gates. Suppose $[g]$ is an internal
+  gate. Let $g' \in [g]$ be such that $L_\equiv([g]) = L(g') /_\equiv$ and $h
+  \in [g]$ be such that $L_\equiv(\pi_\equiv[g]) = L_\equiv ([\pi h]) = L(\pi h)
+  /_\equiv$. We have that $\pi L(g')$ is isomorphism-equivalent to $L(\pi g')$,
+  and it follows that $(\pi L(g'))/_\equiv$ is isomorphism-equivalent to $L(\pi
+  g') /_\equiv$. We then have $(\pi L(g'))/_\equiv = \pi_\equiv (L(g') /_\equiv)
+  = \pi_\equiv L_\equiv ([g])$ and, since $g' \equiv h$ and so $\pi g' \equiv
+  \pi h$, we have that $L(\pi g')/_\equiv$ is isomorphism-equivalent to $L(\pi
+  h) /_\equiv = L_\equiv(\pi_\equiv[g])$. It follows that $\pi_\equiv L_\equiv
+  ([g])$ is isomorphism-equivalent to $L_\equiv(\pi_\equiv [g]) /_\equiv$.
+  Suppose $[g]$ is an output gate. Then for $\vec{a} \in \dom (\Omega)$,
+  $\pi_\equiv \Omega_\equiv (\vec{a}) = [\pi \Omega (\vec{a})] = [\Omega (\sigma
+  \vec{a})] = \Omega_\equiv (\sigma \vec{a})$. It follows that if $C$ is
+  symmetric then $C_\equiv$ is symmetric.
 
@@
 
+% \begin{lem}
+%   There is an algorithm that takes as an input a circuit $C$ of order $n$
+% \end{lem}
+
+% \begin{lem}
+%   There is an algorithm takes as input a $(\BB, \rho)$-circuit $C$ of order
+%   $n$ with unique labels and $\sigma \in \sym_n$ and outputs for each gate $g$
+%   the image of $g$ under the action of the unique automorphism extending
+%   $\sigma$ (if it exists). This algorithm runs in time polynomial in the
+%   combined size of the input circuit and the encoding of the permutation.
+%   \label{lem:compute-automorphisms}
+% \end{lem}
+% \begin{proof}
+%   Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$. We first construct
+%   a circuit $C^\sigma$ from $C$ by adding in the image of each gate in $C$
+%   under the action of $\sigma$. We now define this circuit formally.
+
+%   Let $C^\sigma := \langle G^\sigma, \Omega^\sigma, \Sigma^\sigma,
+%   \Lambda^\sigma, L^\sigma \rangle$. For each internal gate $g$ in $G$ we
+%   define a new gate $g^\sigma$ and let $G'$ be the set of all of these new
+%   gates. Let $G^\sigma = G \ucup G'$. Let $\Lambda^\sigma = \Lambda$ and
+%   $\Omega^\sigma = \Omega$. Let $\Sigma^\sigma (g) = \Sigma(g)$ for all $g \in
+%   G$ and $\Sigma^\sigma (g^\sigma) = \Sigma (g)$ for all $g^\sigma \in G'$.
+%   For each $g \in G$ let $L^\sigma(g) = L(g)$. For each $g^\sigma \in G'$ and
+%   $x \in \ind(g^\sigma)$ let $h = L(g)(x)$. If $h$ is an input gate then there
+%   is an obvious action of $\sigma$ on $h$ and we let $L^\sigma(g^\sigma)(x) =
+%   \sigma h$. If $h$ is an internal gate there there exists $h^\sigma \in G'$
+%   and we let $L^\sigma(g^\sigma)(x) = h^\sigma$.
+
+%   We should note that $C^{\sigma}$ does have redundant gates. Let $E, E'
+%   \subseteq {G^{\sigma}}^2$ be an equivalence relation defined as follows. Let
+%   $(g, g') \in E'$ if, and only if, $g,g' \in G$ and $g \equiv g'$ or there
+%   exists $h, h' \in G$ such that $g = h^\sigma$ and $g' = {h'}^\sigma$, and $h
+%   \equiv h'$. Let $(g,g') \in E$ if, and only if, $(g, g') \in E'$ or
+
+%   Let $g, g' \in G^{\sigma}$. If $g, g' \in G$ then $g \equiv g'$ if, and only
+%   if,$E(g,g')$, and if $g, g' \in G'$ then $E(g, g')$ if
+
+%   It is easy to see that $C^\sigma$ has unique labels and $\vert C^\sigma
+%   \vert \leq \vert C \vert$. We may thus use the algorithm from Lemma~\ref{}
+%   to compute the syntactic-equivalence classes of $C^\sigma$. We now have the
+%   following claim.
+
+%   \begin{claim}
+%     Let $\pi \in \aut(C)$ extending $\sigma$. If $g$ and $g'$ are internal
+%     non-output gates in $C$ and $g' = \pi (g)$ then $g'$ and $g^\sigma$ are
+%     syntactically-equivalent in $C^\sigma$.
+%   \end{claim}
+%   \begin{proof}
+%     We prove this claim by induction on the depth of a gate in the circuit.
+%     Let $g$ and $g'$ be internal non-output gates in $C$ and $g' = \pi (g)$.
+%     Suppose $g$ and $g'$ have depth $1$ i n $C$. It is clear that both $g$ and
+%     $g'$ are non-output internal gates, that $\Sigma (g) = \Sigma (g')$, and
+%     that there exists $\lambda \in \aut(g)$ such that $\pi L(g) = L(g')
+%     \lambda$. But, since $g$ and $g'$ have depth $1$ and so all of their
+%     children are input gates, we have for all $x \in \ind(g)$, that
+%     $L^\sigma(g^\sigma)(x) = \pi L(g)(x) = L(g') \lambda = L^\sigma(g')
+%     \lambda$. It follows that $g^\sigma$ and $g'$ are syntactically-equivalent
+%     in $C^\sigma$.
+
+%     Suppose $g$ and $g'$ have depth $i > 1$ and the result holds for all pairs
+%     of gates of depth less than $i$. It follows that there exists $\lambda \in
+%     \aut(g)$ such that $\pi L(g) = L(g') \lambda$. Let $x \in \ind(g)$ and let
+%     $h = L(g)(x)$. If $h$ is an input gate then $L^\sigma(g^\sigma)(x) = \pi
+%     L(g)(x) = L(g')(\lambda x) = L^\sigma(g')(\lambda x)$. If $h$ is not an
+%     input gate then $L^\sigma (g^\sigma)(x) = h^\sigma$. We have that $\pi (h)
+%     = \pi L(g)(x) = L(g')(\lambda x)$ and, from the inductive hypothesis, we
+%     have that $\pi(h)$ is syntactically-equivalent to $h^\sigma$ in
+%     $C^\sigma$. But then $L^\sigma (g^\sigma)(x) = h^\sigma \equiv \pi(h) =
+%     L(g')(\lambda x) = L^\sigma(g')(\lambda x)$. The claim follows.
+%   \end{proof}
+
+%   each point in this construction, when extending the mapping by a single
+%   gate, we notice that in each case there is only one choice of possible
+%   gate.If at some point in the recursive construction we arrive at a point
+%   where no mapping for $h$ can be found we halt at that point and return that
+%   no automorphism exists.
+
+%   For each gate $h$ in $C$ let $Q(h)$ be the maximum length of a path from $h$
+%   to an output gate. Let $h$ be a gate in $C$. Suppose $Q(h) = 0$. Then $h$ is
+%   an output gate. We recall that $\Omega$ is an injection. Let $\vec{a} =
+%   \Omega^{-1}(g)$ and let $h' \in G$ be such that $h' = \Omega (\sigma
+%   \vec{a})$ and $\Sigma (h) = \Sigma (h')$. Let $\pi (h) = h'$. Note that
+%   there is no other partial-automorphism extending $\sigma$ on the output
+%   gates of $C$, so if at this point we have failed to construct $\pi$ then
+%   there is indeed no automorphism extending of $\sigma$.
+
+%   Suppose $h$ is a gate in the circuit with $Q(h) > 0$ and for all $g$ with
+%   $Q(g ) < Q(h)$ we have defined $\pi (g)$ and that $\pi$ is a partial
+%   automorphism extending $\sigma$. Let $H = \bigcap_{g \in W(h, \cdot)}
+%   H_{\pi(g)}$. Notice that if there is an automorphism extending $\sigma$ then
+%   the image of $h$ under the action of that automorphism is in $H$. As such,
+%   if $H$ is empty we halt and output that no extension exists. Suppose that
+%   $H$ is non-empty. If $h$ is an input gate then there is an obvious action of
+%   $\sigma$ on $h$, and we let $h' = \sigma h$. If $h$ is an output gate, let
+%   $\vec{a} = \Omega^{-1}(g)$ and let $h' \in G$ be such that $h' = \Omega
+%   (\sigma \vec{a})$ and $\Sigma (h) = \Sigma (h')$. If $h' \not\in H$ we halt
+%   and output that no extension exists, and otherwise we let $\pi (h) = h'$.
+%   Notice that in the case that $h$ is an output gate or an input gate there is
+%   at most one choice of $h'$. Suppose $h$ is an internal non-output gate. Let
+%   $h' \in H$ such that $h'$ is syntactically-equivalent to $h^\sigma$ in
+%   $C^\sigma$. If not such $h'$ exists then, from the claim, there is no
+%   extension of $\sigma$ to an automorphism of the circuit, and so we halt and
+%   output accordingly. Suppose that $h'$ does exist. We now show that $h'$ is
+%   unique. Let $h'' \in H$ such that $h''$ is syntactically-equivalent to
+%   $h^\sigma$ in $C^\sigma$. It follows that there exists $g \in W(h, \cdot)$
+%   such that $h', h'' \in H_g$ and $g$ has unique labels. Moreover, $h'$ and
+%   $h''$ are syntactically-equivalent in $C^\sigma$ and so, from the
+%   construction of $C^\sigma$, $h'$ and $h''$ are syntactically-equivalent in
+%   $C$. But then $h' \equiv h''$ and so, since $g$ has unique labels, $h' =
+%   h''$. Let $\pi (h) = h'$. Notice that in each case there is at most one
+%   possible extension of $\pi$ to $h$.
+
+%   \begin{claim}
+%     There is an automorphism extending $\sigma$ if, and only if, $\pi$ is an
+%     automorphism extending $\sigma$.
+%   \end{claim}
+%   \begin{proof}
+%     `$\Rightarrow$': trivial `$\Leftarrowrrow$' : Let $\pi'$ be an
+%     automorphism extending $\sigma$. We show by induction on the structure of
+%     the circuit that for all $h \in G$, $\pi'(h) = \pi(h)$. Let $h \in G$. If
+%     $Q(h) = 0$ then $h$ is an output gate. Let $\vec{a} = \Omega(h)$. We have
+%     from the definition of $\pi$ and the definition of an automorphism that
+%     $\pi(h) = \Omega(\sigma \vec{a}) = \pi'(\Omega(\vec{a})) = \pi' (h)$.
+
+%     Suppose $Q(h) > 0 $ and for all gates $g \in G$ with $Q(g) < Q(h)$, $\pi
+%     (g) = \pi'(g)$. If $h$ is an output gate then the above argument suffices
+%     to show that $\pi(h) = \pi'(h)$. If $h$ is is easy to see that $\pi (g) =
+%     \pi'(g)$. Suppose that $h$ is a non-output internal gate. We have from the
+%     previous claim that $\pi'(h)$ is syntactically-equivalent to $h^\sigma$ in
+%     $C^\sigma$. We already have that $\pi(h)$ is syntactically-equivalent to
+%     $h^\sigma$. It follows that $\pi (h)$ and $\pi'(h)$ are
+%     syntactically-equivalent. Let $g \in W(h, \cdot)$. We have that $\pi(h)
+%     \in H_{\pi(g)}$ and $\pi'(h) \in H_{\pi'(g)}$. From the inductive
+%     hypothesis $\pi (g) = \pi'(g)$, and so $\pi' (h) \in H_{\pi(g)}$. But
+%     $\pi(g)$ has unique labels and $\pi(h)$ and $\pi'(h)$ are
+%     syntactically-equivalent. It follows that $\pi (h) = \pi'(h)$.
+%   \end{proof}
+
+%   It remains to check that $\pi$ is an automorphism extending $\sigma$. It
+%   suffices to check that for each $g \in G$, there exists $\lambda \in
+%   \aut(C)$ such that $\pi L(g) = L(\pi g) \lambda$. But this is equivalent to
+%   testing if for each $g \in G$, $L(\pi g) \pi L(g)^{-1}$ acts like an
+%   automorphism. This is easy to check. We check if $\Sigma (h) = \Sigma (h')$
+%   and check that both
+
+%   If there is no such $h'$ then either $\bigcap_{g \in W(h, \cdot)}
+%   H_{\pi(g)}$ is empty or it is non-empty but th
+
+%   $g' \in W(\pi(h), \cdot)$
+
+%   (g)(x) = \$
+
+%   Then for all $x \in \ind(g)$, $L(g)(x)$
+
+%   We should note that $C^\pi$ has unique labels.
+
+%   Let $C_0 = C$. Let $i \in [\depth(g)]$. Let $C_i := \langle G_i, \Omega_i,
+%   \Sigma_i, \Lambda_i, L_i\rangle$ be defined from $C_{i-1} := \langle
+%   G_{i-1}, \Omega_{i-1}, \Sigma_{i-1}, \Lambda_{i-1}, L_{i-1} \rangle$ as
+%   follows. For each internal gate $h \in G$ such that $\depth(h) = i$ and
+%   either $W_T(h,g)$ or $h = g$ we define a new gate $h^\pi$. Let $G_i'$ be the
+%   set of all these new gates and let $G_i = G_{i-1} \uplus G_i'$. Let
+%   $\Omega_i = \Omega_{i-1}$ and $\Lambda_i = \Lambda_{i-1}$. Let $h' \in G_i$.
+%   If $h' \in G_{i-1}$ then $\Sigma_i(h') = \Sigma_{i-1}(h')$ and $L_i(h') =
+%   L_{i-1}(h')$. If $h' \not\in G_i$ then $h' \in G_i'$ and so $h' = h^\pi$ for
+%   some appropriate $h \in G$. Let $\Sigma_i(h') = \Sigma_{i-1} (h)$. Let $x
+%   \in \ind(h')$ and let $h_x := L(h)(x)$. If $h_x$ is an input gate let
+%   $L(h')(x) = \sigma L(h)(x)$. Otherwise, $h_x$ is an internal gate and,
+%   moreover, $W_T(h_x,g)$ and the depth of $h_x$ is less than $i$. We thus have
+%   that there exists $h^\pi_x \in G_i$ corresponding to $h^\pi_x$.
+
+%   \begin{claim}
+%     For each $g' \in W(\cdot, \pi(h))$, $g'$ is the image of $g$ under the
+%     action of $\sigma$ if, and only if, $g'$ is syntactically-equivalent to
+%     $g^\pi$ in $C_g$.
+%   \end{claim}
+%   \begin{proof}
+%   \end{proof}
+%   Let $L(h')(x) = h^{\pi}_x$.
+
+%   Let $C_g = C_{\depth(g)}$. Let
+
+%   otherwise let $L(h')(x) = h^\pi_x$.
+
+%   $L(h')(x) =.
+
+%   let $g_h' = L(h)^{-1}(g)$
+
+%   Let $h$ be any gate in the circuit. Suppose $h$ is an input gate. If $h$ is
+%   a constant gate then let $\pi (h) = h'$. If $h$ is a relational gate such
+%   that $R := \Sigma(h)$, then check if there exists $h'$ such that $\Sigma
+%   (h') = R$, $\sigma \Lambda_R(h) = \Lambda_R(h')$, and either both $h$ and
+%   $h'$ are output gates or neither are. If no such $h'$ exists then halt and
+%   output that no automorphism exists. If neither $h$ nor $h'$ are output gates
+%   then set $\pi (h) = h'$. If both $h$ and $h'$ are output gates then check if
+%   $\sigma \Omega^{-1}(h) = \Omega^{-1}(h')$. If the equality holds set $\pi(h)
+%   = h'$, otherwise halt and output that no automorphism exists. We have from
+%   Proposition~\ref{prop:unique-children-unique-extensions} that there is at
+%   most one gate $h'$ that meets the above criteria, and so $\pi(h)$ is well
+%   defined.
+
+%   Let $h$ be an internal gate in the circuit and assume we have defined $\pi
+%   (g)$ for every gate $g$ of depth less than $h$. Let $h'$ be a gate in the
+%   circuit such that $\Sigma(h) = \Sigma (h')$, $\pi L(h)$ is
+%   isomorphism-equivalent to $L(h')$ and, if $h$ is an output gate then $h'$ is
+%   an output gate such that $\sigma \Omega^{-1}(h) = \Omega^{-1}(h')$. Since
+%   $C$ has unique labels (and so unique extensions) we have that $\pi L(h)$ is
+%   isomorphism-equivalent to $L(h')$ if, and only if, $L(h')^{-1}\pi L(h)$ acts
+%   on $\ind(h)$ like an automorphism of $\str{h}$. This can be determined
+%   easily. If no such $h'$ exists halt and output that there is no automorphism
+%   extending $\sigma$. Since $C$ has unique labels it has unique extensions,
+%   and so there is at most one such $h'$. We thus let $\pi (h) = h'$.
+
+%   This recursive approach can be implemented as an algorithm that runs in time
+%   polynomial in the combined size of the inputs and outputs the required
+%   automorphism if it exists.
+% \end{proof}
+
 \begin{lem}
@@
 \begin{proof}
-  Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$. We recursively build
-  up the mapping $\pi$ extending $\sigma$. If at some point in the recursive
+  Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$. Let $C_\equiv =
+  \langle G_\equiv, \Omega_\equiv, \Sigma_\equiv, \Lambda_\equiv, L_\equiv
+  \rangle$ be a quotient of $C$. We recursively build up the mapping $\pi' \in
+  \aut(C_\equiv)$ extending $\sigma$. If at some point in the recursive
   construction we arrive at a point where no mapping for $g$ can be found we
@@
 
-  Let $h$ be any gate in the circuit. Suppose $h$ is an input gate. If $h$ is a
-  constant gate then let $\pi (h) = h'$. If $h$ is a relational gate such that
-  $R := \Sigma(h)$, then check if there exists $h'$ such that $\Sigma (h') = R$,
-  $\sigma \Lambda_R(h) = \Lambda_R(h')$, and either both $h$ and $h'$ are output
-  gates or neither are. If no such $h'$ exists then halt and output that no
-  automorphism exists. If neither $h$ nor $h'$ are output gates then set $\pi
-  (h) = h'$. If both $h$ and $h'$ are output gates then check if $\sigma
-  \Omega^{-1}(h) = \Omega^{-1}(h')$. If the equality holds set $\pi(h) = h'$,
-  otherwise halt and output that no automorphism exists. We have from
-  Proposition~\ref{prop:unique-children-unique-extensions} that there is at most
-  one gate $h'$ that meets the above criteria, and so $\pi(h)$ is well defined.
-
-  Let $h$ be an internal gate in the circuit and assume we have defined $\pi
-  (g)$ for every gate $g$ of depth less than $h$. Let $h'$ be a gate in the
-  circuit such that $\Sigma(h) = \Sigma (h')$, $\pi L(h)$ is
-  isomorphism-equivalent to $L(h')$ and, if $h$ is an output gate then $h'$ is
-  an output gate such that $\sigma \Omega^{-1}(h) = \Omega^{-1}(h')$. Since $C$
-  has unique labels (and so unique extensions) we have that $\pi L(h)$ is
-  isomorphism-equivalent to $L(h')$ if, and only if, $L(h')^{-1}\pi L(h)$ acts
-  on $\ind(h)$ like an automorphism of $\str{h}$. This can be determined easily.
-  If no such $h'$ exists halt and output that there is no automorphism extending
-  $\sigma$. Since $C$ has unique labels it has unique extensions, and so there
-  is at most one such $h'$. We thus let $\pi (h) = h'$.
-
-  This recursive approach can be implemented as an algorithm that runs in time
-  polynomial in the combined size of the inputs and outputs the required
-  automorphism if it exists.
+  Let $h$ be any gate in $C_\equiv$. Suppose $h$ is an input gate. If $h$ is a
+  constant gate then let $\pi' (h) = h$. If $h$ is a relational gate such that
+  $R := \Sigma_\equiv(h)$, then check if there exists $h'$ such that
+  $\Sigma_\equiv (h') = R$ and $\sigma \Lambda_\equiv(h) = \Lambda_\equiv(h')$,
+  and also check that either both $h$ and $h'$ are output gates or neither are
+  output gates. If no such $h'$ exists then halt and output that no automorphism
+  exists. If neither $h$ nor $h'$ are output gates then set $\pi'(h) = h'$. If
+  both $h$ and $h'$ are output gates then check if $\sigma \Omega^{-1}_\equiv(h)
+  = \Omega^{-1}_\equiv(h')$. If the equality holds set $\pi'(h) = h'$, otherwise
+  halt and output that no automorphism exists. We note that, from the definition
+  of an automorphism, there is at most once such $h'$ meeting this criteria, and
+  so $\pi'(h)$ is well-defined.
+
+  Let $h$ be an internal gate in the circuit and assume we have defined
+  $\pi'(g)$ for every gate $g$ of depth less than $h$. Let $h'$ be a gate in the
+  circuit such that $\Sigma_\equiv(h) = \Sigma_\equiv (h')$, $\pi' L(h)$ is
+  isomorphism-equivalent to $L_\equiv(h')$ and, if $h$ is an output gate then
+  $h'$ is an output gate such that $\sigma \Omega^{-1}_\equiv(h) =
+  \Omega^{-1}_\equiv(h')$. Suppose there is another gate $h''$ in the circuit
+  that meets all of those criteria as well. But then it follows that $h'' \equiv
+  h'$. Since $C_\equiv$ is reduced, we then have that $h'' = h'$. We thus have
+  that the choice of $h'$, if it exist, is unique. Note that, since $C$ has
+  unique labels $C_\equiv$ has unique labels, and so unique extensions, and so
+  we have that $\pi' L_\equiv(h)$ is isomorphism-equivalent to $L_\equiv(h')$
+  if, and only if, $L_\equiv(h')^{-1}\pi'L_\equiv(h)$ acts on $\ind(h)$ like an
+  automorphism of $\str{h}$. This is easy to determine. If no such $h'$ exists,
+  halt and output that there is no automorphism extending $\sigma$. Otherwise,
+  let $\pi'(h) = h'$.
+
+  It is easy to see that if there is an automorphism of $C_\equiv$ extending
+  $\sigma$ then this construction must have been successful and $\pi'$ is the
+  unique automorphism of $C_\equiv$ extending $\sigma$. Thus, if we have thus
+  far halted and returned that no automorphism exists, then indeed there is no
+  automorphism of $C_\equiv$ extending $\sigma$ and so, from
+  Lemma~\ref{lem:quotient-circuits-preserve}, no automorphism of $C$ extending
+  $\sigma$. We suppose the algorithm has not halted, and thus that $\pi'$ is an
+  automorphism of $C_\equiv$ extending $\sigma$.
+
+  We say that a function $\pi : G \rightarrow G$ is a \emph{pseudo-automorphism}
+  extending $\sigma$ if (i) $\pi$ acts like an automorphism extending $\sigma$
+  on the input and output gates, (ii) $\Sigma (\pi (h)) = \Sigma(h)$ for all $h
+  \in G$, (iii) $\pi(h) \in H_{\pi(g)}$ for all $h \in G$ and $g \in W(h,
+  \cdot)$, and (iv) $\pi (h) \in \pi'([h])$.
+
+\begin{claim}
+  If $\pi$ is an automorphism of $C$ extending $\sigma$ then $\pi$ is a
+  psudo-automorphism extending $\sigma$.
+\end{claim}
+\begin{proof}
+  Suppose $\pi$ is an automorphism of $C$ extending $\sigma$. It is easy to see
+  that conditions (i), (ii) and (iii) are satisfied. We now show that (iv) is
+  satisfied as well. Notice that, since $C_\equiv$ is reduced and so has unique
+  extensions, $\pi'$ is the unique automorphism of $C_\equiv$ extending
+  $\sigma$. We have from Lemma~\ref{lem:quotient-circuits-preserve} that there
+  exists $\pi_\equiv \in \aut(C_\equiv)$ extending $\sigma$ such that
+  $\pi_\equiv ([g]) = [\pi(g)]$. It follows that for all $h \in G$, $\pi(h) \in
+  \pi_\equiv([h]) = \pi'([h])$.
 \end{proof}
 
-We now define an algorithm analogous to the one defined in
-Lemma~\ref{lem:compute-automorphisms} that computes in polynomial-time the image
-of a given element of the universe of a gate under the action of a given
-permutation.
+We now recursively build up the pseudo-automorphism $\pi$ extending $\sigma$. If
+at any point in this construction we assert that an object exists when it does
+not, we halt and output that there is no automorphism extending $\sigma$.
+Importantly, this construction is defined such that $\pi$, if it exists, is the
+\emph{unique} pseudo-automorphism extending $\sigma$.
+
+For each gate $h$ in $C$ let $Q(h)$ be the maximum length of a path from $h$ to
+an output gate. Let $h$ be a gate in $C$. Suppose $Q(h) = 0$. Then $h$ is an
+output gate. Let $h' \in G$ be such that $h' = \Omega (\sigma \Omega^{-1}(h))$
+and $\Sigma (h) = \Sigma (h')$. From the definition of an automorphism if $h'$
+exists it is the unique gate satisfying these criteria. We let $\pi (h) = h'$.
+
+Suppose $h$ is a gate in the circuit with $Q(h) > 0$ and for all $g$ such that
+$Q(g ) < Q(h)$ we have defined $\pi (g)$. Let $H = \bigcap_{g \in W(h, \cdot)}
+H_{\pi(g)}$. If $H$ is empty then we cannot satisfy condition (iii) in the
+definition of a pseudo-automorphism, and so we halt and output that no extension
+exists. Suppose that $H$ is non-empty. If $h$ is an input gate then there is an
+obvious action of $\sigma$ on $h$, and we let $h' = \sigma h$. If $h$ is an
+output gate, let $h' \in G$ be such that $h' = \Omega (\sigma \Omega^{-1} (h))$
+and $\Sigma (h) = \Sigma (h')$. If $h' \not\in H$ we halt and output that no
+extension exists, and otherwise we let $\pi (h) = h'$. Notice that in the case
+that $h$ is an output gate or an input gate then from the definition of an
+automorphism $h'$ is the unique gate satisfying these criteria. Suppose $h$ is
+an internal non-output gate. Let $h_\equiv \in G_\equiv$ be such that $h_\equiv
+= [h]$. Let $h' \in \pi_\equiv (h_\equiv)$ be such that $h' \in H$. We now show
+that $h'$, if it exists, is the unique gate satisfying these criteria. Let $h''
+\in \pi_\equiv (h_\equiv)$ and $h'' \in H$. Then $h'' \equiv h'$ and for all $g
+\in W(h, \cdot)$, $h' \in H_g$ and $h'' \in H_g$. But then, since every $g \in
+W(h, \cdot)$ has unique labels, $h'' = h'$. Let $\pi (h) = h'$.
+
+It is easy to see that if there is a pseudo-automorphism of $C$ extending
+$\sigma$ then this construction must have been successful, and $\pi$ is the
+unique pseudo-automorphism extending $\sigma$. It follows that if the algorithm
+has halted, then there is no pseudo-automorphism extending $\sigma$ and so, from
+the claim, there is indeed no automorphism extending $\sigma$. We suppose then
+that the algorithm has not halted and we have constructed $\pi$ successfully. It
+follows from the claim and the uniqueness of $\pi$ that if there is an
+automorphism extending $\sigma$ than it must be equal to $\pi$, and so $\pi$ is
+an automorphism. We thus have that there is an automorphism extending $\sigma$
+if, and only if, $\pi$ is an automorphism. It remains to check that $\pi$ is an
+automorphism. It suffices to check that $\pi$ is a bijection and that for each
+$h \in G$, $\pi L(h)$ is isomorphism-equivalent to $L(h')$. It is easy to check
+that $\pi$ is a bijection. Notice that $\pi L(h)$ is isomorphism-equivalent to
+$\L(\pi(h))$ if, and only if, $L(\pi(h))^{-1}\pi L(h)$ is an automorphism. This
+condition is also easy to check. If either of these checks fail, halt and output
+that there is no automorphism extending $\sigma$. Otherwise, output $\pi (g)$
+for all $g \in G$.
+
+We note that, since $C$ has unique labels, we can compute $C_\equiv$ in
+polynomial-time. Moreover, it is easy to see that the construction of $\pi'$ and
+$\pi$ can be completed in polynomial-time. We thus have that the algorithm
+described may be implemented so as to run in polynomial-time.
+\end{proof}
+
+% \begin{lem}
+%   There is an algorithm takes as input a $(\BB, \rho)$-circuit $C$ of order
+%   $n$ with unique labels and $\sigma \in \sym_n$ and outputs for each gate $g$
+%   the image of $g$ under the action of the unique automorphism extending
+%   $\sigma$ (if it exists). This algorithm runs in time polynomial in the
+%   combined size of the input circuit and the encoding of the permutation.
+%   \label{lem:compute-automorphisms}
+% \end{lem}
+% \begin{proof}
+%   Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$. We recursively
+%   build up the mapping $\pi$ extending $\sigma$. If at some point in the
+%   recursive construction we arrive at a point where no mapping for $g$ can be
+%   found we halt at that point and return that no automorphism exists.
+
+%   Let $h$ be any gate in the circuit. Suppose $h$ is an input gate. If $h$ is
+%   a constant gate then let $\pi (h) = h'$. If $h$ is a relational gate such
+%   that $R := \Sigma(h)$, then check if there exists $h'$ such that $\Sigma
+%   (h') = R$, $\sigma \Lambda_R(h) = \Lambda_R(h')$, and either both $h$ and
+%   $h'$ are output gates or neither are. If no such $h'$ exists then halt and
+%   output that no automorphism exists. If neither $h$ nor $h'$ are output gates
+%   then set $\pi (h) = h'$. If both $h$ and $h'$ are output gates then check if
+%   $\sigma \Omega^{-1}(h) = \Omega^{-1}(h')$. If the equality holds set $\pi(h)
+%   = h'$, otherwise halt and output that no automorphism exists. We have from
+%   Proposition~\ref{prop:unique-children-unique-extensions} that there is at
+%   most one gate $h'$ that meets the above criteria, and so $\pi(h)$ is well
+%   defined.
+
+%   Let $h$ be an internal gate in the circuit and assume we have defined $\pi
+%   (g)$ for every gate $g$ of depth less than $h$. Let $h'$ be a gate in the
+%   circuit such that $\Sigma(h) = \Sigma (h')$, $\pi L(h)$ is
+%   isomorphism-equivalent to $L(h')$ and, if $h$ is an output gate then $h'$ is
+%   an output gate such that $\sigma \Omega^{-1}(h) = \Omega^{-1}(h')$. Since
+%   $C$ has unique labels (and so unique extensions) we have that $\pi L(h)$ is
+%   isomorphism-equivalent to $L(h')$ if, and only if, $L(h')^{-1}\pi L(h)$ acts
+%   on $\ind(h)$ like an automorphism of $\str{h}$. This can be determined
+%   easily. If no such $h'$ exists halt and output that there is no automorphism
+%   extending $\sigma$. Since $C$ has unique labels it has unique extensions,
+%   and so there is at most one such $h'$. We thus let $\pi (h) = h'$.
+
+%   This recursive approach can be implemented as an algorithm that runs in time
+%   polynomial in the combined size of the inputs and outputs the required
+%   automorphism if it exists.
+% \end{proof}
+
+We now use Lemma~\ref{lem:compute-automorphisms} to define an algorithm that
+computes in polynomial-time the image of a given element of the universe of a
+gate under the action of a given permutation.
 
@@
 
-  For each transposition $(u,v) \in \sym_n$ and each gate $g$ in $C$ use the
-  Turing machine $T$ to check if the image of $g$ under the action of $(u,v)$
-  exists. If for any transposition and gate the algorithm returns that no image
-  exists then output that the circuit is not symmetric.
+  For each transposition $(u,v) \in \sym_n$ and each gate $g$ in $C$ we use $T$
+  to check if the image of $g$ under the action of $(u,v)$ exists. If for any
+  transposition and gate $T$ returns that no image exists then we halt and
+  output that the circuit is not symmetric.
 
@@
   Lemma~\ref{lem:computing-support-orbit} with $S := \emptyset$, $X := G$ (where
-  $G$ is the set of gates in $C$), $x := g$, and Turing machine $T$n, and output
+  $G$ is the set of gates in $C$), $x := g$, and Turing machine $T$, and output
   the result of this computation.
@@
   We then use the algorithm from Lemma~\ref{lem:computing-support-orbit}, with
-  $S := \consp(g)$, $X := \universe{g}$ and $x:= a$, and the Turing machine $T$,
-  and output the results.
+  inputs $S := \consp(g)$, $X := \universe{g}$ and $x:= a$, and the Turing
+  machine $T$, and output the results.
 
@@
   gates are syntactically-equivalent, a gate in $G^1$ has unique labels if, and
-  only if, it has injective labels. We thus check if any non-symmetric gate in
-  $G^1$ do not have injective labels, halt and output that the circuit is not
-  transparent if such a gate is found. We then run the following iterative
-  algorithm. We initialise a variable $i$ to $1$. We have that all of the
-  non-symmetric gates in $G^{\leq i}$ have unique labels. We can thus compute
-  the syntactic-equivilence classes of $G^{\leq i}$ using the algorithm given in
-  Lemma~\ref{lem:transparent-syntactic-equiv}. We test if every non-symmetric
-  gate in $G^{i+1}$ has has unique labels, i.e.\ if it has injective labels and
-  no two of its children are elements of the same syntactic-equivalence class.
-  If this test fails, we halt and output that the circuit is not transparent, if
-  it succeeds we increment the variable $i$ and continue as above. If $i$ is
-  ever set to the value $\depth(C)$, we halt and output that the circuit is
-  transparent.
+  only if, it has injective labels. We thus check if there exists a
+  non-symmetric gate in $G^1$ that does not have injective labels, and if we
+  find such a gate we halt and output that the circuit is not transparent. We
+  then run the following iterative algorithm. We initialise a variable $i$ to
+  $1$. We have that all of the non-symmetric gates in $G^{\leq i}$ have unique
+  labels. We can thus compute the syntactic-equivilence classes of $G^{\leq i}$
+  using the algorithm given in Lemma~\ref{lem:transparent-syntactic-equiv}. We
+  test if every non-symmetric gate in $G^{i+1}$ has unique labels, i.e.\ if
+  it has injective labels and no two of its children are elements of the same
+  syntactic-equivalence class. If this test fails, we halt and output that the
+  circuit is not transparent, and if it succeeds we increment the variable $i$ and
+  continue as above. If $i$ is ever set to the value $\depth(C)$, we halt and
+  output that the circuit is transparent.
 
@@
   unique labels and runs in time polynomial in the size of the circuit.
+  \label{cor:unique-labels-polynomial-time}
 \end{cor}
@@
 unique labels. We have also shown that circuits with unique labels have all of
-the requisite algorithmic properties we need in order to define our translation
+the requisite algorithmic properties needed in order to define our translation
 from circuits to formulas. In the remainder of this section we prove that most
@@
 with computing these basic circuit properties that seem essential for defining
-such a transformation should be considered evidence that, at the very least, the
-definition of such a translation is not easy to define.
+such a transformation should be considered evidence that, at the very least, it
+is not easy to define an algorithm computing such a translation.
 
@@
   graph-isomorphism problem to various circuit-related problems. In each case we
-  present a reduction from the bipartite-isomorphism problem to the
+  present a reduction from the bipartite-isomorphism problem to a
   circuit-related problem. This suffices as, from~\cite{Zemlyachenko1985}, there
@@
   isomorphism $\pi : B_1 \rightarrow B_2$ such that $\restr{\pi}{U_1} = U_2$ and
-  $\restr{\pi}{V_1} = V_2$.
-
-  We usually assume, without a loss of generality, that the two input graphs
-  have the property that $[a] = U_1 = U_2$ and $[b] = V_1 = V_2$ for some $a,b
-  \in \nats$.
+  $\restr{\pi}{V_1} = V_2$. We usually assume, without a loss of generality,
+  that the two input graphs have the property that $[a] = U_1 = U_2$ and $[b] =
+  V_1 = V_2$ for some $a,b \in \nats$.
 \end{remark}
@@
   wired up so as to encode the two graphs. We wire the circuit such that, for a
-  given rank gate, the child gate labelled by $(p,q)$ has exactly one of the two
-  designated gates as a child, with the choice of which one depending on whether
-  $(p,q)$ is an edge in the associated graph. In this sense the circuit encodes
-  the two bipartite graphs at the rank gates, and the two gates being
-  syntactic-equivalence corresponds to the presence of a bipartite-isomorphism
-  between the two graphs. We now present this construction formally.
+  given rank gate $g_\rank$, the child of $g_\rank$ labelled by $(p,q)$ has
+  exactly one of the two designated gates as a child, with the choice of which
+  one depending on whether $(p,q)$ is an edge in the associated graph. In this
+  sense the circuit encodes the two bipartite graphs at the rank gates, and the
+  two rank gates are syntactically-equivalent if, and only if, the two graphs
+  are bipartite-isomorphic. We now present this construction formally.
 
@@
   g_{\land}, g_{\text{out}} \}$, $G_{\rank} : = \{ g^1_{\rank}, g^2_{\rank}\}$,
-  and $G_{\text{nodes}} := \{g_{i, (u,v)} : i \in [2] \, (u,v) \in [a] \times
+  and $G_{\text{nodes}} := \{g_{i, (u,v)} : i \in [2] ,\, (u,v) \in [a] \times
   [b] \}$. Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a
-  $(\{\rank^{1}_2\}, \rho)$-circuit of order $n$ defined as follows. Let $G =
-  G_R \cup G_{\text{mid}} \cup G_{\rank} \cup G_{\text{nodes}}$ and $\Omega$ be
-  the $0$-ary function $g_{\text{out}}$. For each $\vec{c} \in [n]^{\arty(R)}$
-  let $\Lambda_R(\vec{c}) = g_{R, \vec{c}}$. Define $\Sigma$ as follows. For
-  each $g \in G$,
+  $(\{\RANK^{r}_p\} \cup \BS, \rho)$-circuit of order $n$ defined as follows.
+  Let $G = G_R \cup G_{\text{mid}} \cup G_{\rank} \cup G_{\text{nodes}}$ and
+  $\Omega$ be the $0$-ary function $g_{\text{out}}$. For each $\vec{c} \in
+  [n]^{\arty(R)}$ let $\Lambda_R(\vec{c}) = g_{R, \vec{c}}$. Define $\Sigma$ as
+  follows. For each $g \in G$,
   \begin{myitemize}
@@
     \ind(g)$, $L(g)(p,q) = g_{i, (p,q)}$,
-  \item if $g \in G_{\text{nodes}}$ and $g = g_{i, (p,q)}$ then if $(p, q \in
-    E_i)$ then $L(g)(1) = g_{\land}$, otherwise $L(g)(1) = g_\lor$, and
-  \item if $g = g_\land$ or $g = g_\lor$ then for all $p \in [n^k]$ we have that
-    $L(g)(p)$ equals $\Lambda^{-1}(\vec{c}_p)$, where $\vec{c}_p$ is the $p$th
-    element of $[n]^k$ in the lexicographical ordering on $[n]^k$.
+  \item if $g \in G_{\text{nodes}}$ and $g = g_{i, (p,q)}$ then if $(p, q) \in
+    E_i$ then $L(g)(1) = g_{\land}$, otherwise $L(g)(1) = g_\lor$, and
+  \item if $g = g_\land$ or $g = g_\lor$ then for all $q \in [n^k]$ we have that
+    $L(g)(q) =\Lambda^{-1}(\vec{c}_q)$, where $\vec{c}_q$ is the $q$th element
+    of $[n]^k$ in the lexicographical ordering on $[n]^k$.
   \end{myitemize}
 
-  We note that for $i \in [2]$, the child of $L(g^i_{\rank})(p,q)$ equals
-  $g_\land$ if, and only if, $(p,q)$ is an edge in in $B_i$ and the child of
-  $L(g^i_\rank)(p,q) $ equals $g_\lor$ if, and only if, $(p,q)$ is not an edge
-  in $B_i$. We thus have that $B_1$ and $B_2$ are bipartite-isomorphic if, and
-  only if, there exists $\lambda \in \sym_{a} \times \sym_{b} =
-  \aut(g^1_{\rank}) = \aut(g^2_{\rank})$ such that for all $(u,v) \in [a] \times
-  [b] = \ind(g^1_{\rank})$, $L(g^1_{\rank})((u,v)) = g_{1, (u,v)} \equiv g_{2,
+  We note that for $i \in [2]$, the child of $L(g^i_{\rank})(p,q)$ is $g_\land$
+  if, and only if, $(p,q)$ is an edge in in $B_i$ and the child of
+  $L(g^i_\rank)(p,q) $ is $g_\lor$ if, and only if, $(p,q)$ is not an edge in
+  $B_i$. We thus have that $B_1$ and $B_2$ are bipartite-isomorphic if, and only
+  if, there exists $\lambda \in \sym_{a} \times \sym_{b}$ such that for all
+  $(u,v) \in [a] \times [b]$, $L(g^1_{\rank})((u,v)) = g_{1, (u,v)} \equiv g_{2,
     \lambda (u,v)} = L(g^2_{\rank})(\lambda (u,v))$. It follows that $B_1$ and
@@
 
-Proposition~\ref{prop:syntactic-graph-iso} gives us that computing the the
-syntactic-equivalence for a given circuit remains hard even if we restrict
-ourselves to circuits with injective labels. In fact, every gate but the two
-rank gates (and, possibly, the output gate) have unique labels, indicating that
-even if we restrict ourselves to circuits with injective labels and such that
-each non-symmetric gates has the property that all of its input gates have
-unique labels, the syntactic-equivalence relation remains hard to compute.
+Proposition~\ref{prop:syntactic-graph-iso} gives us that computing the
+syntactic-equivalence relation for a given circuit remains hard even if we
+restrict ourselves to circuits with injective labels. In fact, every gate but
+the two rank gates (and, possibly, the output gate) have unique labels,
+indicating that even if we restrict ourselves to circuits with injective labels
+and such that each non-symmetric gates has the property that all of its input
+gates have unique labels, the syntactic-equivalence relation remains hard to
+compute.
 
@@
   We use a similar approach as in the proof of
-  Proposition~\ref{prop:syntactic-graph-iso}. All that is really required is to
-  delete the row of gates between the two designated gates that encode the
-  existence or absence of an edge and the two rank gates, and replacing this
-  gate with a wire. We now present this reduction formally.
+  Proposition~\ref{prop:syntactic-graph-iso}. The idea is to use the circuit
+  constructed in Proposition~\ref{prop:syntactic-graph-iso} but with the row of
+  gates between the two designated gates that encode the existence or absence of
+  an edge and the two rank gates deleted and replaced with direct wires. We now
+  present this reduction formally.
 
@@
   $G' = G \setminus G_{\text{nodes}}$, $\Omega' = \Omega$, $\Lambda' = \Lambda$,
-  and $\Sigma' = \restr{\Sigma}{G'}$. For all $g \in G' \setminus G_{\rank}$,
-  $L'(g) = L(g)$. For $i \in [2]$ and $(p,q) \in [a] \times [b]$,
+  and $\Sigma' = \restr{\Sigma}{G'}$. For all $g \in G' \setminus G_{\rank}$ let
+  $L'(g) = L(g)$. For $i \in [2]$ and $(p,q) \in [a] \times [b]$, let
   $L(g^i_{\rank})(p,q) = g_{\land}$ if $(p,q) \in E_i$ and $L(g^i_{\rank})(p,q)
@@
   in to the parent of $g$. Using an argument similar to that of
-  Proposition~\ref{prop:syntactic-graph-iso} we may then prove that $B_1$ and
-  $B_2$ are bipartite-isomorphic if, and only if, $g^1_{\rank} \equiv
-  g^2_{\rank}$. Since the construction of $C$, and so $C'$, can be implemented
-  in time polynomial in the combined sizes of the input graphs, the mapping of
-  $(B_1, B_2)$ to the tuple $(C', (g^1_{\rank}, g^2_{\rank}))$ is a reduction,
-  and the result follows.
+  Proposition~\ref{prop:syntactic-graph-iso} we have that $B_1$ and $B_2$ are
+  bipartite-isomorphic if, and only if, $g^1_{\rank} \equiv g^2_{\rank}$. Since
+  the construction of $C$, and so $C'$, can be implemented in time polynomial in
+  the combined sizes of the input graphs, the mapping of $(B_1, B_2)$ to the
+  tuple $(C', (g^1_{\rank}, g^2_{\rank}))$ is a reduction, and the result
+  follows.
 \end{proof}
@@
 (Lemma~\ref{lem:syntactic-equivalence-unique-gates-hard}). It would seem then
-that while the conjunction of these two properties is sufficient, they are not
-if taken individually.
+that, while the conjunction of these two properties is sufficient, each of these
+properties is insufficient alone.
 
@@
 syntactic-equivalence relation to the problem of deciding if a given gate in a
-circuit has unique labels. From then transitivity of polynomial-time many-one
+circuit has unique labels. From the transitivity of polynomial-time many-one
 reductions and Proposition~\ref{prop:syntactic-graph-iso}, this gives us a
@@
 We can construct a similar argument for reducing the problem of deciding if two
-gates are syntactically equivalent in a circuit with injective labels to the
+gates are syntactically-equivalent in a circuit with injective labels to the
 problem of deciding if a given gate $g$ in a circuit $C$ with injective labels
@@
 if there is no permutation such that two automorphisms of the circuit extend the
-permutation and disagree with each other on $g$ (i.e. $g$ is not a
+permutation and disagree with each other on $g$ (i.e.\ $g$ is not a
 counterexample to $C$ having unique extensions). From then transitivity of
@@
   Let $C$ be a circuit of order $n$ and let $g_1$ and $g_2$ be two gates in $C$.
-  Note that for any gate $g$ in $\sigma \in sym_n$, if $\pi, \pi' \in \aut(C)$
-  extend $\sigma$ and $\pi_e := \pi'\pi{-1}$ then $\pi(g) \neq \pi'(g)$ if, and
-  only if, $\pi_e (g) \neq g$. It follows that there exists $\sigma \in sym_n$
-  such that there are automorphisms $\pi, \pi' \in \aut(C)$ extending $\sigma$
-  such that $\pi (g) \neq \pi'(g)$ if, and only if, there exists $\pi_e$
-  extending the trivial permutation such that $\pi (g) \neq g$.
+  Note that for any gate $g$ in $\sigma \in \sym_n$, if $\pi, \pi' \in \aut(C)$
+  both extend $\sigma$ and $\pi_e := \pi'\pi^{-1}$ then $\pi(g) \neq \pi'(g)$
+  if, and only if, $\pi_e (g) \neq g$. We thus have that there exists $\sigma
+  \in \sym_n$ and $\pi, \pi' \in \aut(C)$ extending $\sigma$ such that $\pi (g)
+  \neq \pi'(g)$ if, and only if, there exists $\pi_e \in \aut(C)$ extending the
+  trivial permutation such that $\pi (g) \neq g$.
 
@@
   $C'$, and so $\pi_e$ is a non-trivial automorphism extending the trivial
-  permutation, and $g_1$ does not have unique extensions in $C'$. In the other
-  direction, suppose $g_1$ does not have unique extensions in $C'$. Then there
-  exists an automorphism $\pi_e \in \aut(C')$ extending the trivial permutation
-  and such that $\pi_e(g_1) \neq g_1$. But $g_1$ is a child of the single output
-  gate $g'$ (which must be fixed by any automorphism), and the only other child
-  of $g'$ is $g_2$. It follows $\pi_e$ swaps $g_1$ and $g_2$, and so $g_1$ and
-  $g_2$ are syntactically-equivalent in $C'$. The result follows.
+  permutation, and thus $g_1$ does not have unique extensions in $C'$. We now
+  prove the other direction. Suppose $g_1$ does not have unique extensions in
+  $C'$. Then there exists an automorphism $\pi_e \in \aut(C')$ extending the
+  trivial permutation and such that $\pi_e(g_1) \neq g_1$. But $g_1$ is a child
+  of the single output gate $g'$ (which must be fixed by any automorphism), and
+  the only other child of $g'$ is $g_2$. It follows $\pi_e$ swaps $g_1$ and
+  $g_2$, and so $g_1$ and $g_2$ are syntactically-equivalent in $C'$. The result
+  follows.
 \end{proof}
@@
 to the class of reduced circuits in which all but two gates in the circuit have
-injective labels. In other words, the class of circuits that have unique
-children and \emph{almost} have unique labels -- in that all but two gates have
-unique labels.
+injective labels. We might think of this as the class of circuits that
+\emph{almost} have unique labels -- in that all but two gates have unique labels
+and the remaining two have unique children.
 
@@
   := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ of order two as follows. Let
-  $G_{R} := \{g^1_{R}, g^1_{R}\}$ and $G_{\text{mid}} := \{g^1_{\land},
+  $G_{R} := \{g^1_{R}, g^2_{R}\}$ and $G_{\text{mid}} := \{g^1_{\land},
   g^2_\land, g^1_\lor, g^2_\lor , g_{\text{out}}\}$, and $G_{\rank} : = \{
@@
   only if, $(p,q)$ is not an edge in $B_i$. Let $\pi_{(1,2)} : G \rightarrow G$
-  that fixes the output gate, and swaps each gate $g^1_s$, for some symbol $s$,
-  with the gate $g^1_s$. It is easy to see that $\pi_{(1,2)}$ is a bijection.
-  Moreover, $C$ is symmetric if, and only if, $\pi_{(1,2)}$ is an automorphism
-  of the circuit extending the transposition $(1,2)$, if and only if, $(1,2)
-  (L(g^1_{\rank}))$ is isomorphism-equivalent to $L(g^2_{\rank})$ if, and only
-  if, $B_1$ and $B_2$ are bipartite-isomorphic.
+  be the function that fixes the output gate, and for each symbol $s$ swaps the
+  gate $g^1_s$ with the gate $g^2_s$. It is easy to see that $\pi_{(1,2)}$ is a
+  bijection. Moreover, $C$ is symmetric if, and only if, $\pi_{(1,2)}$ is an
+  automorphism of the circuit extending the transposition $(1,2)$, if and only
+  if, $(1,2) (L(g^1_{\rank}))$ is isomorphism-equivalent to $L(g^2_{\rank})$ if,
+  and only if, $B_1$ and $B_2$ are bipartite-isomorphic.
 
   It is easy to see that all gates in the circuit are part of a singleton
-  syntactic-equivalence class and that all gates have unique labels except for
-  the two rank gates. Since the construction of $C$ can be implemented in time
-  polynomial in the combined sizes of the input graphs, the mapping of $(B_1,
-  B_2)$ to $C$ is a reduction, and the result follows.
+  syntactic-equivalence class and that all of the gates in the circuit but the
+  two rank gates have have unique labels. Since the construction of $C$ can be
+  implemented in time polynomial in the combined sizes of the input graphs, the
+  mapping of $(B_1, B_2)$ to $C$ is a reduction, and the result follows.
 \end{proof}
@@
 We note that Proposition~\ref{prop:graph-iso-symmetric} gives us that deciding
-symmetry, even if we restrict ourselves to reduced circuits or circuits with
-unique children, is as hard as the graph isomorphism problem. Moreover, it is
-possible to alter this reduction, using a construction analogous to the one used
-in the proof of Proposition~\ref{prop:syntactic-graph-iso}, in order to
-reproduce this hardness result with an additional restriction to circuits with
-injective labels. In contrast, we have from
-Lemma~\ref{lem:computing-support-orbit-index} that we can decide symmetry for
-transparent circuits (i.e.\ circuits where every non-symmetric gate has unique
-children and injective labels) in polynomial-time. These observations again
+if a circuit is symmetric, even if we restrict ourselves to reduced circuits or
+circuits with unique children, is as hard as the graph-isomorphism problem.
+Moreover, it is possible to alter this reduction, using a construction analogous
+to the one used in the proof of Proposition~\ref{prop:syntactic-graph-iso}, in
+order to reproduce this hardness result with an additional restriction to
+circuits with injective labels. In contrast, we have from
+Lemma~\ref{lem:computing-support-orbit-index} that we can decide is a
+transparent circuit is symmetric in polynomial-time. These observations again
 suggest both the robustness of this hardness result and the importance of the
@@
 
-In Lemma~\ref{} we showed that for circuits with unique labels, we can compute
-in polynomial-time the action of an automorphism on the gates of a circuit. In
-Proposition~\ref{} we show that we can also compute the orbit and supports of
-gates in polynomial-time. These results play a very central role in our
-translation from families of circuits to formulas, and hence in the proof of our
-main result. We now show that deciding the orbit of a gate for a general circuit
-is at least as hard as the graph isomorphism problem. We show that this result
-holds even if we restrict our attention to circuits with unique extensions or
-circuits with injective labels.
+In Lemma~\ref{lem:compute-automorphisms} we showed that for circuits with unique
+labels, we can compute in polynomial-time the action of an automorphism on the
+gates of a circuit. In Proposition~\ref{lem:computing-support-orbit-gate} we
+show that we can also compute the orbit and supports of gates in
+polynomial-time. These results play a very central role in our translation from
+families of circuits to formulas, and hence in the proof of our main result. We
+now show that deciding the orbit of a gate in a general circuit is at least as
+hard as the graph isomorphism problem. We show that this result holds even if we
+restrict our attention to circuits with unique extensions or circuits with
+injective labels.
 
@@
 
-These hardness results for syntactic-equivalence and deciding if a gate has
-unique labels are particularly worth noting, as many natural algorithms for
+The hardness results for computing syntactic-equivalence and deciding if a gate
+has unique labels are particularly worth noting, as many natural algorithms for
 translating a circuit into an equivalent transparent circuit (or circuit with
@@
 translation we define in Lemma~\ref{lem:transparent-unique} for transparent
-circuits, makes explicit use of the polynomial-time computability of the
-syntactic-equivalence relation for such circuits. As such, these hardness
-results, along with the hardness results for many other basic circuit
+circuits, make explicit use of the polynomial-time computability of the
+syntactic-equivalence relation for circuits from this class. As such, these
+hardness results, along with the hardness results for many other basic circuit
 properties, should be considered evidence against the existence of an
 easily-definable polynomial-time translation from general circuits to
-transparent circuits or to circuits with unique labels.
+transparent circuits, or to circuits with unique labels.
 
@@
 
-In Proposition~\ref{prop:transparent-polynomial-time} and
-Corollary~\ref{cor:unique-labels-polynomial-time} we showed that both the class
-of transparent circuits and the class of circuits with unique labels are
+From Proposition~\ref{prop:transparent-polynomial-time} and
+Corollary~\ref{cor:unique-labels-polynomial-time} we have that both the class of
+transparent circuits and the class of circuits with unique labels are
 polynomial-time decidable. These results suggest that, while it may be hard to
 transform a circuit into an equivalent transparent circuit or a circuit with
-unique labels, verifying these properties is at least tractable. We now show
-that many other seemingly natural classes of circuits are at least as hard to
-decide as the graph-isomorphism problem.
+unique labels, verifying that a circuit has these properties is at least
+tractable. We now show that many other seemingly natural classes of circuits are
+at least as hard to decide as the graph-isomorphism problem.
 
 \begin{lem}
-  There are polynomial-time reductions from the graph isomorphism problems to
-  the problems of deciding if a circuit does not have unique extensions and the
+  There are polynomial-time reductions from the graph isomorphism problem to
+  the problem of deciding if a circuit does not have unique extensions and the
   problem of deciding if a circuit does not have unique children.

### 2018-04-02 sections/conclusion.tex
Fixed a few typos in the symmetric-circuits section and in the conclusion.

@@
 be the set of all queries computed by $\PT$-uniform families of transparent
-symmetric circuits defined over $\BB$. We have that $Q_{\MB} \subsetneq
+symmetric circuits defined over $\BB$. We have that $Q_{\BM} \subsetneq
 Q_{\RB}$. It follows from Theorem~\ref{} that if $\BB$ is a symmetric basis then
-$Q_\BB \subseteq Q_\MB$. It follows that $Q_\MB$ is a basis including structured
+$Q_\BB \subseteq Q_{\BM}$. It follows that $Q_{\BM}$ is a basis including structured
 functions defined over a vocabulary with two sorts that defines a circuit model
@@
 
-It is not hard to show that $Q_\BB \subseteq Q_\MB$ for any matrix-symmetric
+It is not hard to show that $Q_\BB \subseteq Q_{\BM}$ for any matrix-symmetric
 basis $Q_\BB$ consisting of polynomial-time computable functions if, and only

### 2018-04-02 sections/symmetric-circuits.tex
Fixed a few typos in the symmetric-circuits section and in the conclusion.

@@
   $Q$ as a structure $\langle G, \Omega, \Sigma, \Lambda, L \rangle$.
-  \begin{itemize}
+  \begin{myitemize}
     \setlength\itemsep{0mm}
@@
     in the image of $L(h_2)$, then $(G, W)$ is a directed acyclic graph.
-  \end{itemize}
+  \end{myitemize}
 \end{definition}
@@
   (\Omega^{-1}(g)) = \Omega (\sigma \Omega^{-1}(g)) = \pi' \Omega
-  (\Omega^{-1}(g)) = \pi'(g)$, or none of $g$, $\pi(g)$ or $\pi' (g)$ are output
+  (\Omega^{-1}(g)) = \pi'(g)$, or none of $g$, $\pi(g)$ and $\pi' (g)$ are output
   gates.

### 2018-04-04 sections/transparency-and-unique-extensions.tex
minor revisions to Section 5.  Also inserted (informal) definition of circuit isomorphism in Sec 3 for backward reference.

@@
 \begin{document}
-
-Many of the properties of circuits central to work of this paper, and
-particularly those that reference circuit automorphisms or
-syntactic-equivalence, make references to the existence of a isomorphism between
-pairs of structures associated with the gates of the circuit. We recall that
-each gate in a circuit is associated with a structure with the elements of the
-relations of that structure labelled by the children of that gate. These
-properties usually depend on the existence of an isomorphism that agrees with a
+Recall that each gate $g$ in a cricuit  is associated with a structure
+$D$ with the elements of the relations in $D$, i.e.\ $\ind(\Sigma(g))$
+labelled by the children of $g$.  Many of the properties of circuits
+that are central to our construction, and we wish to be able to decide
+efficiently, particularly those that reference circuit automorphisms or
+syntactic-equivalence, depend on the existence of isomorphisms that agrees with a
 given permutation of the gates labelling the structure.  This introduces a
-potential difficulty as there is no know polynomial-time algorithm for the
+potential difficulty as there is no known polynomial-time algorithm for the
 general isomorphism problem, but we we require many of these circuit properties
@@
 to formulas (see Section~\ref{sec:circuits-to-formulas}).  This is not a problem
-if we restrict our attention to circuits with symmetric gates, as Anderson and
-Dawar~\cite{AndersonD17} do, as in this case the structures of interest are
-sets, and set equivalence is clearly decidable in polynomial-time, but when we
+if we restrict our attention to circuits with symmetric gates, as
+in~\cite{AndersonD17}, as in this case the structures of interest are
+sets, and set equivalence is clearly decidable in polynomial-time.  When we
 allow for circuits to be defined over bases including non-symmetric functions it
@@
 important for two reasons. First, circuits with unique labels have unique
-extensions, which enables us to apply the support theorem. Second, as we will
+extensions, which enables us to apply the support theorem. Second, as we
 show in this section, all relevant symmetry-related circuit properties are
@@
 
-In the second part of this section we discuss more formally the relationship
+In Section~\ref{sec:necessity} we discuss more formally the relationship
 between the problem of deciding many of these natural circuit properties and the
@@
 properties for general circuits. It follows that deciding most of these circuit
-properties is hard as the graph isomorphism problem -- a problem not known to be
-in $\PT$. We also show that most of these hardness results are quite robust, in
+properties is as hard as the graph isomorphism problem---a problem not known to be
+in $\PT$, showing that some condition like transparency is necessary.  We also show that most of these hardness results are quite robust, in
 that even if we restrict our attention to other natural classes of circuits
@@
 \subsection{Tractable Properties of Transparent Circuits}
-In the this subsection we show that many useful circuit properties are
+In this subsection we show that many useful circuit properties are
 polynomial-time decidable for transparent circuits. First, we prove that the
@@
   gates of depth less than the depth of either $g$ or $h$. Then $g \equiv h$ if,
-  and only if, $L(g)$ and $L(h)$ are isomorphism equivalent up to $\equiv$.
+  and only if, $L(g)$ and $L(h)$ are isomorphic up to $\equiv$.
 
@@
   output that $g \not\equiv h$. We thus have that $f$ is a bijective function
-  and for all $x \in \ind(g)$, $L(g)(x) \equiv L(h)(f(x))$. Check if both $g$
+  and for all $x \in \ind(g)$, $L(g)(x) \equiv L(h)(f(x))$. Check if $g$
   and $h$ are both symmetric gates. If so, $f$ witnesses the required
@@
 
-It is common approach to define a new structure by \emph{quotienting} a given
-structure by some equivalence relation. We now define what it means to take a
+ We now define what it means to take a
 quotient of a circuit by the syntactic-equivalence relation. Intuitively, we
@@
 functions. But it is not hard to see that for every gate $g$ in $C$, $L(g)$ and
-$L'(g)$ are isomorphism-equivalent. It follows that these two circuits are
-structurally identical in a very strong sense. Indeed, while we have not
-formally defined what it means for two circuits to be isomorphic, under any
-reasonable definition we would have that any two quotients of a given circuit
-are isomorphic.
+$L'(g)$ are isomorphic.  It follows that these two circuits are
+isomorphic in the precise sense alluded to right after Definition~\ref{defn:automorphism}.
 
@@
   for all $g \in G$, $g$ has unique labels in $C$ if, and only if, $[g]$ has
-  unique labels in $C_{\equiv}$. In fact, for all $\sigma \in \sym_n$ if there
+  unique labels in $C_{\equiv}$.  Indeed, for all $\sigma \in \sym_n$ if there
   exists $\pi \in \aut(C)$ extending $\sigma$ then $\pi /_\equiv$ is an
@@
   Let $\sigma \in \sym_n$ and suppose there exists $\pi \in \aut(C)$ extending
-  $\sigma$. Let $\pi_\equiv = pi /_\equiv$. We now show that $\pi_\equiv$ is an
+  $\sigma$. Let $\pi_\equiv = \pi /_\equiv$. We now show that $\pi_\equiv$ is an
   automorphism of $C_\equiv$ extending $\sigma$. It is easy to see that
@@
   unique labels $h$ has unique labels and so $L_\equiv([g])$ has injective
-  labels. Since each equivalence class in $C_\equiv$ is a singlton it follows
+  labels. Since each equivalence class in $C_\equiv$ is a singleton it follows
   that $[g]$ has unique labels.
@@
 We now show that transparent circuits can be transformed in polynomial time into
-equivalent circuit with unique labels, and hence unique extensions, and that
+equivalent circuits with unique labels, and hence unique extensions, and that
 this transformation preserves important properties.
@@
   Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a transparent
-  $(\mathbb{B}, \rho)$-circuit. There is an algorithm that that takes in such a
+  $(\mathbb{B}, \rho)$-circuit. There is an algorithm that takes in such a
   circuit and outputs a $(\mathbb{B} \cup \mathbb{B}_{\std}, \rho)$-circuit $C'$
@@
   important point to note is that each $\AND$-gate in $C_1$ has fan-in at least
-  two. We will construct $C'$ from $C_1$ by adding in a number of $\AND$-gates
+  two. We construct $C'$ from $C_1$ by adding in a number of $\AND$-gates
   with fan-in one. Therefore, since all of the $\AND$-gates in $C_1$ have fan-in
-  two, it will follow that none of these new gates are syntactically-equivalent
+  two, it follows that none of these new gates are syntactically-equivalent
   to any gate in $C_1$. We now show that $C_1$ and $C_0$ compute the same
@@
     $i = 1$ then $\{ h \} = H_g' = H_{g'}'$.  Since the only gate in $G_\land$
-    that has $h$ as a child gate is $g^h_1$, it follows that $g = g^h_1 = g'$.
+    that has $h$ as a child is $g^h_1$, it follows that $g = g^h_1 = g'$.
     If $i > 1$ then $\{g^{h}_{i-1}\} = H_g' = H_{g'}'$. Since $g^h_i$ is the
-    only gate in $G_\land$ that has $g^h_{i-1}$ as a child gate, we have $g =
+    only gate in $G_\land$ that has $g^h_{i-1}$ as a child, we have $g =
     g^h_i = g'$. It follows that if $g \in G_\land$ then $g = g'$.
@@
     \mathcal{A}](g^h_i) = C'[\gamma \mathcal{A}](h) = C_1[\gamma \mathcal{A}](h)
-    = L^{\gamma \mathcal{A}}_1(g)(x)$. The penultimate equality follow from from
+    = L^{\gamma \mathcal{A}}_1(g)(x)$. The penultimate equality follow from 
     the inductive hypothesis. The final equality follows from the fact that $h =
@@
   \vert$ wires, we may construct $C_1$ from $C_0$ in time polynomial in $\vert C
-  \vert$. It is is easy to see that $C'$ can be constructed in time polynomial
+  \vert$. It is easy to see that $C'$ can be constructed in time polynomial
   in $\vert C_1 \vert$ and hence polynomial in $\vert C \vert$. The result
@@
 input a circuit with unique labels and an appropriate permutation and outputs
-the action of the automorphism extending the permutation (if its defined) on the
+the action of the automorphism extending the permutation (if it is defined) on the
 gates of the circuit.
@@
   h'$. Since $C_\equiv$ is reduced, we then have that $h'' = h'$.  We thus have
-  that the choice of $h'$, if it exist, is unique. Note that, since $C$ has
+  that the choice of $h'$, if it exists, is unique. Note that, since $C$ has
   unique labels $C_\equiv$ has unique labels, and so unique extensions, and so
@@
 automorphism.  It suffices to check that $\pi$ is a bijection and that for each
-$h \in G$, $\pi L(h)$ is isomorphism-equivalent to $L(h')$. It is easy to check
-that $\pi$ is a bijection. Notice that $\pi L(h)$ is isomorphism-equivalent to
-$\L(\pi(h))$ if, and only if, $L(\pi(h))^{-1}\pi L(h)$ is an automorphism. This
+$h \in G$, $\pi L(h)$ is isomorphic to $L(h')$. It is easy to check
+that $\pi$ is a bijection.  Notice that $\pi L(h)$ is isomorphic to
+$L(\pi(h))$ if, and only if, $L(\pi(h))^{-1}\pi L(h)$ is an automorphism. This
 condition is also easy to check.  If either of these checks fail, halt and output
@@
 \begin{lem}
-  There is an algorithm takes as input a $(\mathbb{B}, \rho)$-circuit $C$ with
+  There is an algorithm that takes as input a $(\mathbb{B}, \rho)$-circuit $C$ with
   unique labels of order $n$, a gate $\sigma \in \sym_n$, $g$ a gate in $C$, and
   $a \in \universe{g}$ and, if there exists an automorphism of $C$ extending
-  $\sigma$ such that $\sigma \in \stab(g)$, outputs image of $a$ under $\sigma$.
+  $\sigma$ such that $\sigma \in \stab(g)$, outputs $\sigma a$.
   The algorithm runs in time polynomial in the size of $C$ and the encoding of
@@
   Let $p$ be a polynomial. There is an algorithm that takes as input a set $S
-  \subseteq [n]$, a set $X$, an element $x \in X$, and a turning machine $T$
+  \subseteq [n]$, a set $X$, an element $x \in X$, and a Turing machine $T$
   computing the action of $\stab(S)$ on $X$ that runs in time bounded by $p(n +
@@
   \begin{align*}
-    \mathcal{P}_{(u,v)} := \{ \{u,v\}\} \bigcup_{w \in [n] \setminus \{ u,v \}} \{ \{ w \} \}
+    \mathcal{P}_{(u,v)} := \{ \{u,v\}\} \cup \bigcup_{w \in [n] \setminus \{ u,v \}} \{ \{ w \} \}
   \end{align*}
@@
 
-  Let $\mathcal{P}$ be the partition formed by applying $\mathcal{E}$ to every
-  $\mathcal{P}_{(u,v)}$ with $(u,v) \cdot x = x$ in succession. From
+%  Let $\mathcal{P}$ be the partition formed by applying $\mathcal{E}$ to every
+%  $\mathcal{P}_{(u,v)}$ with $(u,v) \cdot x = x$ in succession.
+
+Let  $\mathcal{P}$ be the partition that is the coarsest common
+refinement of the partitions $\mathcal{P}_{(u,v)}$, for all $u,v$ with $(u,v) \cdot x = x$.
+From
   Proposition~\ref{prop:combining-supporting-patitions} we have that
@@
   exists a partition $\mathcal{P}'$ supporting $\stab_{\stab(S)}(x)$ such that
-  $\mathcal{P}' \preceq P$ and $\mathcal{P}' \neq \mathcal{P}$. And so there
+  $\mathcal{P}' \preceq \mathcal{P}$ and $\mathcal{P}' \neq \mathcal{P}$. And so there
   exists $P \in \mathcal{P}$ and $P' \in \mathcal{P}'$ such that $P \subsetneq
@@
   \geq 0$ let $M_{i+1} := M_i\cup (\bigcup_{(u,v) \in \sym_{[n] \setminus S}}
-  ((u,v) \cdot M_i))$. Let $M$ be the least fixed point of this sequence. It is
+  ((u,v) \cdot M_i))$. Let $M \subseteq X$ be the union of this sequence. It is
   easy to see that $M \subseteq \orb_{\stab(S)}(x)$ as every element of $M$ is
@@
 
-  Furthermore, since, when computing the orbit, the least fixed point must be
-  reached in at most $\vert X \vert$ iterations, and each iteration requires at
+  Furthermore, when computing the orbit, we construct $M_i$
+  iteratively and obtain the orbit after at most $\vert X \vert$
+  iterations. Since each iteration requires at
   most $\mathcal{O} (n^{2})$ applications of the group action, it follows that
@@
   We note that if every gate has an image under the action of every
-  transpositions then, since $\sym_n$ is generated by the set of transpositions,
+  transposition then, since $\sym_n$ is generated by the set of transpositions,
   we have that $C$ is symmetric.
@@
 
-We now extend Lemma~\ref{lem:computing-support-orbit-gate} and construct an
+We now extend Lemma~\ref{lem:computing-support-orbit-gate} and construct a
 polynomial-time algorithm that computes the orbit and canonical supporting
-partition of each elements of the universe of each gate in a circuit.
+partition of each element of the universe of each gate in a circuit.
 
@@
   $1$. We have that all of the non-symmetric gates in $G^{\leq i}$ have unique
-  labels. We can thus compute the syntactic-equivilence classes of $G^{\leq i}$
+  labels. We can thus compute the syntactic-equivalence classes of $G^{\leq i}$
   using the algorithm given in Lemma~\ref{lem:transparent-syntactic-equiv}. We
@@
 
-\subsection{The Necessity of Transparency}
+\subsection{The Necessity of Transparency}\label{sec:necessity}
 % The reader will notice that while we have included a specific requirement that
@@
 We have shown then that key properties of transparent circuits are
-polynomial-time tractable and, using these results, we have shown that
+tractable and, using these results, we have shown that
 transparent circuits can be transformed in polynomial time into circuits with
@@
 \begin{prop}
-  Let $\rho$ be any non-empty relational vocabulary and let $n, r, p \in \nats$,
-  with $p$ prime. There is a a polynomial time reduction from the
-  graph-isomorphism problem to the problem of deciding if a given pair of gates
-  in a given symmetric rank-circuit for structures of size $n$ that (i) has
-  injective labels, (ii) contains no constant gates, and (iii) contains at most
-  two rank gates with bound $r$ and prime $p$, are syntactically-equivalent.
+   There is a polynomial-time reduction from the graph isomorphism problem to the
+  problem of determining if a given pair of gates in a given circuit are
+  syntactically-equivalent.
   \label{prop:syntactic-graph-iso}
@@
 \begin{proof}
+ Let $\rho$ be any non-empty relational vocabulary and let $r, p \in \nats$,
+  with $p$ prime.  We reduce the bipartite-isomorphism problem to the
+  problem of deciding whether two given gates are syntactically
+  equivalent in a symmetric rank-circuit taking $\rho$-structures as
+  input where the circuit (i) has
+  injective labels, (ii) contains no constant gates, and (iii) contains at most
+  two rank gates with bound $r$ and prime $p$.
+
   Suppose we are given two partitioned bipartite graphs $B_1 := (U_1, V_1, E_1)$
@@
 
-Since there is a trivial reduction from the problem of computing the
-syntactic-equivalence relation over a restricted class of circuits to the
-problem over the general class of circuits, we have the following corollary.
-
-\begin{cor}
-  There is a polynomial-time reduction from the graph isomorphism problem to the
-  problem of determining if a given pair of gates in a given circuit are
-  syntactically-equivalent.
-  \label{cor:syntactically-equivilent-general-hard}
-\end{cor}
-
 Proposition~\ref{prop:syntactic-graph-iso} gives us that computing the
@@
 permutation and disagree with each other on $g$ (i.e.\ $g$ is not a
-counterexample to $C$ having unique extensions). From then transitivity of
+counterexample to $C$ having unique extensions). From the transitivity of
 polynomial-time many-one reductions and
@@
   Lemma~\ref{lem:syntactically-equivalent-unique-labels}. We now prove that the
-  mapping $(C, g_1, g_2)$ to $(C', g_1)$ is a reduction. Let $\pi_e$ be
+  mapping $(C, g_1, g_2)$ to $(C', g_1)$ is a reduction. Let $\pi_e$
+  be a
   bijection from the gates of $C'$ to the gates of $C'$ that swaps $g_1$ and
@@
   The graph-isomorphism problem is polynomial-time reducible to the problem of
-  deciding if a circuit is symmetric. In fact, the graph-isomorphism problem is
-  polynomial-time reducible to the problem of deciding if a reduced circuit in
-  which all but two gates in the circuit have unique labels is symmetric.
+  deciding if a circuit is symmetric. 
   \label{prop:graph-iso-symmetric}
@@
 \begin{proof}
-  We use a similar approach as in the proof of
+In fact, we reduce the graph-isomorphism problem is to the problem of
+deciding symmetry of a reduced circuit in
+  which all but two gates have unique labels.
+
+  We use an approach similar to that in the proof of
   Proposition~\ref{prop:syntactic-graph-iso}. In this case we construct a
@@
 circuits with injective labels.  In contrast, we have from
-Lemma~\ref{lem:computing-support-orbit-index} that we can decide is a
+Lemma~\ref{lem:computing-support-orbit-index} that we can decide if a
 transparent circuit is symmetric in polynomial-time. These observations again
@@
 \begin{lem}
-  There are polynomial-time reductions from the graph-isomorphism problem to the
+  There is a polynomial-time reductions from the graph-isomorphism problem to the
   problem of deciding if two given gates in a given circuit are in the same
-  orbit. In fact, this reduction holds even if we restrict ourselves to circuits
-  with unique extensions, circuits with unique children, or to circuits with
-  injective labels.
+  orbit.
   \label{lem:graph-iso-to-orbit}
@@
 \begin{proof}
+ In fact, we construct the reduction to circuits
+  with unique extensions, circuits with unique children, or to circuits with
+  injective labels.
+
   Let $B_1$ and $B_2$ be bipartite graphs. Let $C$ be the circuit constructed in

### 2018-04-06 sections/conclusion.tex
Most recent changes to the conclusion, with edits all around the paper.

--- 2018-03-10 sections/conclusion.tex
@@
 
-The main result of this paper establishes an equivalence between the expressive
-power of $\FPR$ and the computational power of $\PT$-uniform transparent
-symmetric rank-circuits, generalising a similar result by Anderson and
-Dawar~\cite{AndersonD17}. Our motivation for proving this characterisation  The hope is that this characterisation will
-contribute to our understanding of one of the two candidate logics for capturing
-$\PT$.
+$\FPR$ is one of the two candidate logics for capturing $\PT$ an so
+understanding its expressive power is an absolutely central problem in the
+field. The main result of this paper establishes an equivalence between the
+expressive power of $\FPR$ and the computational power of $\PT$-uniform families
+of transparent symmetric rank-circuits. Not only does this result establish an
+interesting characterisation of a little-understood and crucially important
+logic, but it also further develops our understanding of the connection between
+logic and circuit complexity, allowing our understanding of $\FPR$ (and
+circuits) to benefit from ideas in both of these quite disparate fields.
 
-% In the quest for a logic that captures polynomial time
+This alternative view of the logic also helps emphasise certain characteristics
+of the logic that may be much less obvious when working with the conventional
+definition. To choose one notable example, the circuit characterisations (both
+of $\FPR$ and $\FPC$) help bring to the fore the importance of the symmetry
+properties inherent in the the syntactic structure of the logic. Indeed, we
+recall that $\PT$-uniform families of transparent invariant (rather than
+symmetric) rank-circuits and $\PT$-uniform families of invariant circuits with
+symmetric gates decide exactly those queries that are in $\PT$. In this way the
+restriction from families of invariant circuits to families of symmetric
+circuits corresponds to the restriction from $\PT$ to $\FPR$ or $\FPC$. In this
+sense, we might say that it is this underlying symmetry property of the logic,
+brought into focus by the circuit characterisation, that separates $\FPC$ from
+$\PT$, and which determines the relationship between $\FPR$ and $\PT$. In fact,
+we have that $\FPR$ captures $\PT$ if, and only if, $\PT$-uniform families of
+symmetric rank-circuits have the same computational power as $\PT$-uniform
+families of invariant rank-circuits. In this way the circuit-characterisation
+brings out this underlying symmetry property of the logic, demonstrates how
+crucial this symmetry property for understanding the logic, and then provides us
+with a framework for studying symmetry.
 
-% At the time of writing there are two candidate logics which Recent work on the
-% problem of capturing $\PT$ has produced two `candidate' logics for capturing
-% polynomial-time. In this paper we extend Anderson and Dawar's symmetric
-% circuit characterisation of $\FPC$, showing that $P$-uniform families of
-% transparent symmetric circuits with rank gates have the same expressive power
-% as $\FPR$. Since $\FPR$ remains one of the two c the candidate logics for
-% capturing $\PT$, along with choiceless polynomial time,
+% This illustrates just one important way in which this circuit characterisation
+% aids in our understanding of $\FPR$, and perhaps in our understanding of
+% logics more generally.
+
+% In this way the circuit-characterisation allows us to under would seem then
+% that understanding these symmetry properties of the circuit (and logic) is
+% central to understanding the relationship between $\FPR$ (or perhaps any
+% logic) and $\PT$. As such, we might thus rephrase the question of whether
+% $\FPR$ captures $\PT$ in a slightly informal way as, `Does symmetry matter for
+% rank-circuits?'.
+
+However, much of the contribution of this paper is not in the main result
+itself, but rather in the entirely novel framework for circuits and the numerous
+new results that we needed to develop in order to prove the main result of this
+paper. As such, we shall briefly review some of these contributions, placing an
+emphasis both on the nature of these contributions and on the necessity of their
+introduction. Indeed, it would seem at first glance that generalising Anderson
+and Dawar's circuit characterisation of $\FPC$ to $\FPR$ should be a simple
+matter of extending the model so as to allow circuits to be defined over bases
+that includes rank-threshold functions -- and perhaps extending a few key
+results and definitions as needed. We showed in
+Theorem~\ref{thm:symmetric-circuits-bound} that, in fact, we cannot increase the
+expressive power of the model by adding symmetric functions to the basis, and so
+the addition of non-symmetric functions to the basis seems almost unavoidable.
+However, while the inclusion of rank-threshold functions in the basis may seem
+benign, it in fact violates a near-ubiquitous assumption in circuit complexity,
+namely that the basis over which the circuit is defined must consist of
+symmetric functions. While this assumption is usually not stated, the fact that
+the circuit is taken to be a directed acyclic graph means that there is no order
+(or any structure at all) on the inputs of each gate, an assumption which only
+makes sense if it is assumed that the evaluation of each gate is invariant under
+any ordering of its inputs -- which is to say the basis must be symmetric.
+However, we found that in Anderson and Dawar's case this assumption pervades not
+just their definition of a circuit, but also the central ideas of their paper,
+including their definition of a circuit automorphism and of a symmetric circuit,
+as well as almost all of the key results and techniques they use to establish
+their characterisation.
+
+As such, in order to include rank-threshold functions in the basis we needed to
+construct a new framework for circuits as well as develop novel approaches and
+techniques in order to work with these circuits. We began by generalising the
+notion of a symmetric function, introducing isomorphism-invariant structured
+functions. These functions take in structures encoded and strings and are
+invariant under isomorphism, rather than under arbitrary permutations of the
+string. It is easy to see that rank-threshold functions are
+isomorphism-invariant. We defined a basis to be a set of isomorphism-invariant
+functions, and extended the circuit model, adding to each gate in the circuit a
+structure on its input gates in accord with the isomorphism-invariant structured
+function labelling that gate. Rather than a gate being invariant under arbitrary
+permutations of its input gates, a gate in this circuit should be invariant
+under permutations of its input gate that form a (labelled) isomorphism. We
+extended the notion of an automorphism to reflect this and defined what it means
+for a circuit to be symmetric.
+
+While we have generalised a few results for this framework, including the
+support theorem, it is important to note that a number of crucial counting
+techniques and polynomial-time algorithms for circuits are either not easy to
+generalise or otherwise resist generalisation entirely. This follows from the
+fact that a circuit automorphism needs to preserve more structure when acting on
+non-symmetric gates than when acting on symmetric gates. As a result, while many
+symmetry-related circuit properties are polynomial-time decidable for circuits
+with symmetric gates, we have shown that these same properties are at least as
+hard as the graph-isomorphism for circuits with non-symmetric gates. This is a
+problem as the polynomial-time decidability of these properties is essential for
+our translation from circuits into formulas.
+
+% used throughout this paper, and is needed in order to apply the support
+% theorem or reason about orbits, we need to
+
+% for are we have shown that many natural circuit properties which are known to
+% be polynomial-time decidable for circuits over symmetric bases are at least as
+% hard to decide for circuits over non-symmetric bases as the graph isomorphism
+% problem.
+
+% This follows from in a rather subtle way from the fact that
+% syntactic-equivalence for symmetric gates requires nothing more than checking
+% if two quotiented sets are equal, while syntactic-equivalence between
+% non-symmetric gates involves checking if two quotiented structures are equal.
+% As such, while determining many
+
+% While for circuits with functions into the basis. In Anderson and Dawar's case
+% establishing the image of a gate under the action of an automorphism is
+% entirely determined by the
+
+% In particular, in order to define the translation from families of circuits to
+% formulas we need that a number However, in order to prove this result we need
+% to be able to compute in polynomial-time many basic symmetry-related
+% properties of the circuit, and most of these properties reference the
+% existence of an isomorphism between the structures associated with each gate.
+% We show in Section~\ref{sec:transparent} that, in fact, deciding many of these
+% properties for (general) rank-circuits is at least as hard as the
+% graph-isomorphism problem. Importantly, the circuits studied by Anderson and
+% Dawar have all of the relevant algorithmic, as in this case the isomorphism
+% problems that arises reduces to set-equivalence, which is obviously
+% polynomial-time decidable.
+
+% In partoTo be more procides This is a problem, as these algorithmic properties
+% are needed throughout the paper
+
+% In particular, while almost all of the relevant properties are polynomial-time
+% decidable for circuits with symmetric gates, enabling a in polynomial-time
+% transformed into a normal form with unique extensions. Moreover, this normal
+% form also many other crucial algorithmic properties needed to prove the main
+% result, particularly the ability to compute the action of a permutation on a
+% circuit, in polynomial-time. We showed in Section~\ref{} that these useful
+% algorithmic properties are not (necessarily) preserved by the generalisation.
+% In particular, we showed that none of these properties are polynomial-time
+% decidable for rank-circuits (or any class of circuits over a non-symmetric
+% basis) unless the graph isomorphism is in $\PT$.
+
+% In order to prove our main result we $\PT$-uniform families of symmetric
+% rank-circuits into equivalent formulas of $\FPR$ and visa
+
+% Dawar. However, However, It would be natural to take symmetric rank-circuits
+% as the natural generalisation of Anderson and Dawar's symmetric circuits and
+% aim to prove an equivalence between the expressive power $\FPR$ and the
+% computational power of $\PT$-uniform families symmetric rank-circuits.
+% However, in order to prove this result we need to be able to compute in
+% polynomial-time many basic symmetry-related properties of the circuit, and
+% most of these properties reference the existence of an isomorphism between the
+% structures associated with each gate. We show in Section~\ref{sec:transparent}
+% that, in fact, deciding many of these properties for (general) rank-circuits
+% is at least as hard as the graph-isomorphism problem. Importantly, the
+% circuits studied by Anderson and Dawar have all of the relevant algorithmic,
+% as in this case the isomorphism problems that arises reduces to
+% set-equivalence, which is obviously polynomial-time decidable.
+
+% In order to ensure
+
+% when we introduce rank-gates this isomorphism problem that computing the
+% action of an automorphism, or showing that a circuit is symmetric, or
+% computing a great number of important properties is at least as hard for
+% rank-circuits as the graph-isomorphism problem.
+
+% to be able to apply the support theorem to circuits, and so needed a normal
+% form for circuits with unique extensions, and we also needed to ensure that a
+% number of basic circuit properties, and particularly those relating to
+% symmetry, are polynomial-time decidable to circuits as well as compute a
+% number of basic circuit properties in polynomial-time. This is not a problem
+% for Anderson and Dawar, as all of the relevant circuit properties are
+% polynomial-time decidable for symmetric-circuits with symmetric gates.
+% Moreover, can be easily transformed into a normal form that has unique
+% extensions (allowing for the application of the support theorem) and all of
+% the nessasary circuit-properties are
+
+% apply the support theorem, a crucial step in out proof, and in order to
+
+% the introduction of structured functions complicates the analysis of such
+% circuits. As we showed in Section~\ref{sec:transparent}, most of the
+% properties of these rank-circuits are at least as hard to decide as the graph
+% isomorphism problem. This poses a problem as the approach we take (and the
+% approach Anderson and Dawar take) to proving this characterisation make
+% repeated use of the polynomial-time decidability of these properties. Indeed,
+% the two key results for translating $\PT$-uniform circuit families into
+% equivalent formulas, the support theorem and the inductive evaluation of a
+% gate (see Section~\ref{sec:circuits-to-formulas}), make use of polynomial-time
+% algorithms for transforming a circuit into an equivalent circuit with unique
+% labels, as well as for deciding if a circuit is symmetric, computing orbits,
+% and deciding syntactic-equivalence.
+
+As such, instead of working with general rank-circuits we have restricted our
+attention to \emph{transparent} circuits, and proved our characterisation in
+terms of $\PT$-uniform families of transparent symmetric rank-circuits. As we
+have shown in Section~\ref{sec:transparent}, all of the relevant properties are
+polynomial-time decidable for transparent circuits. Since all circuits with
+symmetric gates are transparent, we might think of transparent circuits as an
+alternative, more `algorithmically accessible', generalisation of the circuits
+studied by Anderson and Dawar. However, while this restriction to transparent
+circuits aids in our translation from circuits to formulas, it complicates our
+translation in the other direction. Indeed, it is not hard to see that the
+conventional approach for translating formulas of $\FO$ (or $\FPC$, or other
+extensions of $\FO$) into $\PT$-uniform families of circuits does not, in
+general, produce a family of transparent circuits. In order to address this we
+defined a novel translation from formulas of $\FPR$ into equivalent
+$\PT$-uniform families of transparent symmetric rank-circuits. This translation
+is defined in two steps. First, we defined a translation from $\FPR$ to
+$\PT$-uniform families of bounded-width formulas of $\FOrk$ and, second, we
+defined a translation from these families of formulas into $\PT$-uniform
+families of transparent symmetric rank-circuits. This translation, along with
+the main result of the paper, gives us an equivalence between the expressive
+power of three formalisms, which we summarise as follows:
+
+% \begin{center}
+%   \begin{tikzcd}
+%     \FPR \ar[r, equal] \ar[dr, equal] & \text{$\PT$-uniform families of
+%     bounded-width $\FOrk$-formulas}  \ar[d, equal]\\
+%     & \text{$\PT$-uniform families of transparent symmetric rank-circuits}
+%   \end{tikzcd}
+% \end{center}
+
+\begin{center}
+  \begin{tikzcd}
+    \FPR \ar[r, equal] \ar[dr, equal] & \parbox{0.35\textwidth}{$\PT$-uniform
+      families of
+      bounded-width $\FOrk$-formulas}  \ar[d, equal]\\
+    & \parbox{0.38\textwidth}{$\PT$-uniform families of transparent symmetric
+      rank-circuits}
+  \end{tikzcd}
+\end{center}
+
+We already have a very similar result from from Anderson and
+Dawar~\cite{AndersonD17} and Otto~\cite{Otto1996}:
+
+\begin{center}
+  \begin{tikzcd}
+    \FPC \ar[r, equal] \ar[dr, equal] & \parbox{0.35\textwidth}{$\PT$-uniform
+      families of
+      bounded-width $\FOc$-formulas}  \ar[d, equal]\\
+    & \parbox{0.35\textwidth}{$\PT$-uniform families of symmetric circuits with
+      symmetric gates}
+  \end{tikzcd}
+\end{center}
+
+These two sets of equivalences each give us three distinct formalisms equivalent
+to $\FPR$ and $\FPC$, respectively. Importantly, each of these three formalisms
+for $\FPC$ may be extended by a rank in quite distinct ways. We can extend
+$\FOc$ by rank quantifiers and define $\FOrk$, we can add rank gates to
+symmetric circuits with symmetric gates and define transparent symmetric
+rank-circuits, and we can extend $\FPC$ by a rank operator and define $\FPR$. We
+might expect these three quite different extensions to result in three
+formalisms with quite different expressive power. However, the main result of
+this paper along with the translation we discussed above, gives us that these
+three extensions are indeed all equivalent. This provides evidence in favour of
+the proposition that $\FPR$ is indeed the canonical, and most natural, extension
+of $\FPC$. This is in contrast with the other rank logic in the literature, the
+one introduced by Dawar et al.~\cite{Dawar09logicswith}, which was shown by
+Gr\"{a}del and Pakusa~\cite{GradelP15a} to be strictly less expressive than
+$\FPR$, and hence less expressive than $\PT$-uniform families of bounded-width
+$\FOrk$ and $\PT$-uniform families of transparent symmetric rank-circuits.
+
+% the cononical nature of the extension from $\FPC$ to $\FPR$. This suggests
+% that the definition of $\FPR$ is indeed natural.
+
+% 'This has quite interesting implications for the robustness of the definition
+% of $\FPR$. We recall that there are really two rank logics in the literature,
+% $\FPR$ and another, strictly less expressive rank logic introduced by Dawar et
+% al. However, Gr\"{a}del and Pakusa~\cite{} to be strictly less expressive than
+% $\FPR$
+
+% But from these equivalences we have that these three seemingly distinct
+% extensions each result in a formalism equivalent to $\FPR$. In contrast if we
+% were to extend $\FPC$ by the family of rank non-uniform operators introduced
+% by Dawar et al.~\cite{}, rather than the non-uniform rank operator we use
+% instead, as was shown by Gr\"{a}del and Pakusa~\cite{} this logic would be
+% strictly less expressive than $\FPR$, and hence less expressive than
+% $\PT$-uniform families of bounded-width $\FOrk$ and $\PT$-uniform families of
+% transparent symmetric rank-circuits. What is perhaps most striking is that
+% extending each of these three quite different formalisms equivalent to $\FPC$
+% using quite different mechanisms for rank results in a formalism equivalent to
+% $\FPR$. of these formalisms by rank Since each of these extensions is defined
+% quite differently, we might expect these three extensions of $\FPC$ to have
+% different expressive power.
+
+% But from the above sets of equivalences we have that all of these models have
+% equivalent expressive power. In particular, $\FPR$, an extension of $\FPC$,
+% has the same expressive power as other natural extensions by rank of other
+% models with the same expressive power as $\FPC$. This suggests that $\FPR$ is
+% the natural extension of $\FPC$ by rank operators. In contrast the rank logic
+% introduced by Dawar et al.~\cite{} was shown by Gr\"{a}del and Pakusa~\cite{}
+% to be strictly less expressive than $\FPR$, and hence less expressive than
+% $\PT$-uniform families of bounded-width $\FOrk$ and $\PT$-uniform families of
+% transparent symmetric rank-circuits. The results of this paper thus suggest
+% that $\FPR$, rather than the rank logic of Dawar et al., should be considered
+% the appropriate extension of $\FPC$ by rank.
+
+% Since each of these extensions is defined quite differently, we might expect
+% these three extensions of $\FPC$ to have different expressive power. But from
+% the above sets of equivalences we have that all of these models have
+% equivalent expressive power. In particular, $\FPR$, an extension of $\FPC$,
+% has the same expressive power as other natural extensions by rank of other
+% models with the same expressive power as $\FPC$. This suggests that $\FPR$ is
+% the natural extension of $\FPC$ by rank operators. In contrast the rank logic
+% introduced by Dawar et al.~\cite{} was shown by Gr\"{a}del and Pakusa~\cite{}
+% to be strictly less expressive than $\FPR$, and hence less expressive than
+% $\PT$-uniform families of bounded-width $\FOrk$ and $\PT$-uniform families of
+% transparent symmetric rank-circuits. The results of this paper thus suggest
+% that $\FPR$, rather than the rank logic of Dawar et al., should be considered
+% the appropriate extension of $\FPC$ by rank.
+
+\subsection{Future Work}
+We have shown that $\FPR$ has the same expressive power as $\PT$-uniform
+families of transparent symmetric rank-circuits. It is easy to see that
+$\PT$-uniform families of symmetric rank-circuits must be at least as powerful
+as $\PT$-uniform families of transparent symmetric rank-circuits. It is natural
+to ask if these two formalisms actually have the same expressive power or
+whether the transparency restriction does indeed restrict the expressive power
+of the model. It is worth noting that if families of symmetric rank-circuits and
+families of transparent symmetric-rank circuits do not have the same expressive
+power then $\FPR$ does not capture $\PT$.
+
+In this paper we have developed a framework for working with circuits over
+non-symmetric bases. In fact, the first time we explicitly use make any
+reference to linear algebra is in the proof of
+Lemma~\ref{lem:rank-triple-equivilence}, right towards the end of the paper. It
+would be natural to ask if our circuit characterisation of $\FPR$ can be
+generalised in order to develop similar characterisations of other logics. It
+might be good idea to start with some other extension of $\FP$ by some operator
+and try to develop a similar circuit characterisation in terms $\PT$-uniform
+transparent symmetric circuits over an appropriate basis. There are numerous
+logics that are similar in definition to $\FPR$ but which are not known to have
+the same expressive power as $\FPR$, for example $\FP$ extended by an operator
+that expresses the solubility of systems of equations over rings (rather than
+fields). A first step might be to develop a circuit characterisation of one of
+these logics.
+
+% If the general circuit for a strictly more powerful model then the main result
+% gives us that that $\FPR$ does not capture $\PT$. We have not proven it here,
+% but we believe it is possible to show that if the graph isomorphism problem is
+% in $\PT$ then these classes are equivalent. If this is shown, separating these
+% circuit classes would imply graph isomorphism is not in $\PT$.
+
+% There are also natural questions regarding generalisation. In this paper we
+% have characterised the expressive power of $\FPR$, an extension of $\FP$ by a
+% rank operators, in terms of $\PT$-uniform families of symmetric circuits over
+% the rank basis, where the rank basis is the extension of the standard basis by
+% the a set of functions, each of which computed the rank operator for some
+% fixed threshold and characteristic. It would be natural to ask if there is a
+% much broader class of logics, perhaps some class of extensions of $\FP$, such
+% that we can define for each logic in this class a natural characterisation in
+% terms of $\PT$-uniform transparent symmetric circuits over some appropriate
+% basis. We should note that the support theorem and most of the tools developed
+% in this paper have application to circuits defined over any basis. In fact,
+% the first time we explicitly use the properties of the rank function is in the
+% proof of Lemma~\ref{}, right towards the end of the paper.
+
+While we have developed a new and much more general circuit framework we have
+not developed any approaches for proving lower bounds. As a first step out might
+try to prove lower bounds for symmetric circuits with gates with bounded fan-in.
+We might ask if it is possible to compute $\AND[3]$ using a symmetric circuit
+with gates that have fan-in two.
+
+An alternative, and perhaps more sophisticated, approach would be to try and use
+pebble games, a standard tool for proving inexpressibility results in logic, to
+directly prove lower bounds on circuits. Dawar~\cite{Dawar2016} has shown, via a
+circuit-based argument, that the pebble games of Hella~\cite{Hella19961} can
+played directly on symmetric circuits with symmetric gates without any need to
+reference the logic. Dawar and Holm~\cite{DawarH2012} have defined a similar
+pebble game for $\FPR$, and it would be interesting to know if an analogous
+result can be established, allowing us play this pebble game directly on
+symmetric rank-circuits and use it to prove lower bounds for these circuits.
+
+We have shown that the $\PT$-uniform families of transparent symmetric
+rank-circuits (resp. circuits with symmetric gates) have the same expressive
+power as $\FPR$ (resp. $\FPC$), but we recall that if we remove the symmetry
+restriction these circuit models express exactly those queries in $\PT$. A
+natural next step, also suggested by Anderson and Dawar, would be try and weaken
+the symmetry condition. One way this might be done would be to require that only
+permutations from a particular subgroup of the symmetric group extend to
+automorphisms of the circuit. It is easy to see that if we take this subgroup to
+be the trivial subgroup then this nullifies the the symmetry requirement, and
+the circuit model has the same expressive power as $\PT$, while if we take this
+subgroup to be the entire symmetric group then we get back the full symmetry
+requirement and hence our model has the same expressive power as the logic. As
+such, this approach can be used to interpolate between the logic and $\PT$.
+
+There is a rather easy way to develop a circuit characterisation for any logic
+or complexity class with complete problems under first-order reductions. All
+that is required is to extend the basis with the family of functions that decide
+a complete problem and consider $\PT$-uniform families of transparent symmetric
+circuits over this basis. We did not take this approach in our characterisation
+of $\FPR$, preferring to use a more `natural' basis that more closely resembles
+the actual definition of the logic. We should like to ask if there is a similar
+circuit characterisation of $\CPTC$. One might start with bounded-rank fragments
+of $\CPTC$ and see if these programs can be translated into circuits. We should
+note that it does seem as though the symmetry inherent in $\CPTC$ programs is in
+some sense different from the symmetry of symmetric circuits. It might be more
+natural then to ask if $\CPTC$ can be characterised using families of circuits
+with a weakened symmetry requirement.
+
+% The most obvious next step would be to try and develop a (natural) circuit
+% characterisation of $\CPTC$. There are a number of trivial approaches that can
+% be used to define a circuit characterisation for $\CPTC$. For example, if $Q$
+% is a decision problem in $\CPTC$ that is complete under first-order
+% reductions, and introduce define a circuit over a basis that includes
+% functions computing that decide that decide this problem. However, if a more
+% nau
+
+% It would be natural to ask if there is a class of circuits, perhaps symmetric
+% circuits defined over an extension of the majority basis, that would suffice
+% to give a circuit characterisation of $\CPT$ or $\CPTC$ ($\CPT$ with
+% counting). We recall that $\CPTC$ is one of the two candidate logics for
+% capturing polynomial-time, and as such there is significant interest in
+% understanding its expressive power. At present, very little is known about
+% $\CPTC$, and there are no known promising techniques for proving lower bounds.
+% Since circuits families seem easier to analysis then $\CPTC$ programs, a
+% circuit characterisation of $\CPTC$ would provide us with a very promising for
+% studying the expressive power of $\CPTC$, perhaps allowing us to apply
+% techniques for finding circuit lower bounds to the problem of deriving
+% inexpressibly results for $\CPTC$. As a starting point we might ask if there
+% are any interesting extensions of the majority basis by non-symmetric
+% functions such that $\PT$-uniform symmetric circuits over such a basis is
+% comparable to $\CPT$ -- i.e.\ known to be at least or at most as expressive as
+% $\CPT$. We know that any fragment of $\CPTC$ given by placing a constant bound
+% on the rank of sets used in computation is at least as expressive as $\FPC$
+% (see~\cite{}), and hence at least as expressive as $\PT$-uniform symmetric
+% circuits with symmetric gates. We may ask if for each fragment of $\CPTC$ with
+% a bound $r$ on the rank of the sets used, there is a non-trivial class of
+% circuits $\mathcal{C}_r$ (perhaps a family of symmetric circuits over some
+% basis) such that the fragment of $\CPT$ with bound $r$ is at most as
+% expressive as the $\PT$-uniform families of circuits from $\mathcal{C}_r$. It
+% is worth noting that, since we now have a circuit characterisation for $\FPR$,
+% finding a circuit characterisation for $\CPT$ or $\CPTC$ (or showing none
+% exists) may help clarify the relationship between $\CPTC$ and $\FPR$.
+
+% We have proposed a new circuit model, presented a characterisation of $\FPR$
+% in terms of $\PT$-uniform families of a particular class of circuits, and
+% suggested how we might generalise these results in order to develop
+% circuit-based characterisations of other logics -- hopefully even $\CPT$ or
+% $\CPTC$. The natural next step would be to develop techniques for proving
+% lower bounds for $\PT$-uniform circuit families. A general approach for
+% finding lower bounds for families of symmetric circuits over some basis may be
+% very powerful, particularly if it turns out to be possible to characterise a
+% broad class of extensions of $\FP$ using $\PT$-uniform families of transparent
+% symmetric circuits. The usual approach for establishing inexpressibly results
+% for logics involves first defining a pebble game for the logic. Dawar~\cite{}
+% has shown that the pebble game of Hella~\cite{} can be directly linked with
+% symmetric circuits with symmetric gates via a circuit-based argument that
+% makes no reference to logic. Dawar and Holm~\cite{} have defined a pebble game
+% for $\FPR$, and it would be interesting to know if a similar link can be
+% established between this pebble game and transparent symmetric rank-circuits.
+% It may be possible to generalise these arguments and establish for each basis
+% $\BB$ a corresponding pebble game for transparent symmetric circuits defined
+% over $\BB$.
+
+% The circuit model we have developed is novel, and as such there are many basic
+% questions of interest. We do not know, for example, whether for each $a \in
+% \nats$ there is a symmetric circuit with symmetric gates where each gate has
+% fan-in less than $a$ that computes $\NAND[a+1]$. For a basis $\BB$ let $Q_\BB$
+% be the set of all queries computed by $\PT$-uniform families of transparent
+% symmetric circuits defined over $\BB$. We have that $Q_{\BM} \subsetneq
+% Q_{\RB}$. It follows from Theorem~\ref{} that if $\BB$ is a symmetric basis
+% then $Q_\BB \subseteq Q_{\BM}$. It follows that $Q_{\BM}$ is a basis including
+% structured functions defined over a vocabulary with two sorts that defines a
+% circuit model strictly more powerful than any defined by basis of that only
+% include functions with one sort.s
+
+% defines a strictly more powerful class of circuits than
+
+% It is not hard to show that $Q_\BB \subseteq Q_{\BM}$ for any matrix-symmetric
+% basis $Q_\BB$ consisting of polynomial-time computable functions if, and only
+% if, $\FPR$ captures $\PT$.
+
+% We know from Theorem~\ref{} that the majority basis is `complete' for
+% symmetric bases in the sense that any query computed by a $\PT$-uniform family
+% of symmetric circuits defined over a symmetric basis there is a $\PT$-uniform
+% family of symmetric circuits over the majority basis that computes the same
+% query. It is easy to see that if
+
+% Similarly, we do not know if for $r, a, p \in \nats$, with $p$ prime, the
+% function $\RANK^r_p [a][a]$ is computable by a symmetric circuit with
+% symmetric gates.
+
 \end{document}

### 2018-04-06 sections/introduction.tex
Most recent changes to the conclusion, with edits all around the paper.

@@
 (see~\cite{Dawar-siglog}).  In this context, Anderson and
-Dawar~\cite{AndersonD17} provide an interesting characterization of
+Dawar~\cite{AndersonD17} provide an interesting characterisation of
 the expressive power of $\FPC$ in terms of circuit complexity.  They
@@
 $[n]$.  Here we face the difficulty that identifying the symmetries
-and eliminating redundancy in a circuit that involves gates computing
+and eliminting redundancy in a circuit that involves gates computing
 $\tau$-invariant functions requires us to solve the isomorphism

### 2018-04-06 sections/translating-formulas-to-cicuits.tex
Most recent changes to the conclusion, with edits all around the paper.

@@
   Let $\tau$ be the vocabulary of $\theta(\vec{x})$. Let $k := \width(\theta)$.
-  Suppose first that $\tau$ is empty, so
-  all of the atomic formulas in $\theta(\vec{x})$ are of the form $y_1 = y_2$,
-  where $y_1$ and $y_2$ are variables.  It can be shown that for $\vec{a} \in
-  n^k$, we can evaluate $[n] \models \theta[\alpha^{\vec{x}}_{\vec{a}}]$ in time
-  polynomial in $n^{k} \vert \cl{\theta} \vert$. Let $f : [n]^k \rightarrow
-  \{0,1\}$ be defined such that $f (\vec{a}) = 1$ if, and only if, $[n] \models
+  Suppose first that $\tau$ is empty, so all of the atomic formulas in
+  $\theta(\vec{x})$ are of the form $y_1 = y_2$, where $y_1$ and $y_2$ are
+  variables. It can be shown that for $\vec{a} \in n^k$, we can evaluate $[n]
+  \models \theta[\alpha^{\vec{x}}_{\vec{a}}]$ in time polynomial in $n^{k} \vert
+  \cl{\theta} \vert$. Let $f : [n]^k \rightarrow \{0,1\}$ be defined such that
+  $f (\vec{a}) = 1$ if, and only if, $[n] \models
   \theta[\alpha^{\vec{x}}_{\vec{a}}]$. Let $C := \langle G, \Sigma, \Omega,
@@
 
-  \begin{remark}
-    G: I have removed the section where I define equality between ground
-    formulas. Do you find this adds ambiguity? I have added a little bit
-    explaining what I mean by `the matrix at this point remains unchanged'. Does
-    this help?
-  \end{remark}
+  % \begin{remark}
+  %   G: I have removed the section where I define equality between ground
+  %   formulas. Do you find this adds ambiguity? I have added a little bit
+  %   explaining what I mean by `the matrix at this point remains unchanged'.
+  %   Does
+  %   this help?
+  % \end{remark}
 
-  Suppose now $\tau$ is not empty.  We first define a transformation
-  of the formula $\theta$ to an equivalent formula $\lambda$ which has
-  the property that the \emph{natural} translation of $\lambda$ to a
-  circuit (given later) is transparent.
-Let $R \in \tau$.  We first define two helper
-  formulas. For a variable $y$ let $\op{no-op}(y) := (R(y, y) \lor (\neg R(y,
-  y)))$. For a sequence of variables $\vec{y} = (y_1, \ldots, y_m)$ let
-  $\op{tag} (\vec{y}) := (\op{no-op}(y_1) \land (\op{no-op}(y_2) \land (
-  \op{no-op}(y_2) \land ( \ldots \land (\op{no-op}(y_m)) \ldots))))$.
-  Now, let  $\lambda (\vec{x})$ be the formula constructed from $\theta(\vec{x})$ by
-  replacing each sub-formula $\psi(\vec{y})$ of the form $\rank^r_p \vec{w}
-  \vec{z} . \phi$ with the formula $\rank^r_p \vec{w}\vec{z} . ((\forall u . u =
-  u) \land \phi) \land \op{tag}(\vec{w} \cup \vec{z})$.  Since we
-  always replace a subformula $\phi$ with a logically equivalent
-  formula, it follows that $\lambda
-  (\vec{x})$ and $\theta (\vec{x})$ are equivalent. The intuition is that
-  $\op{tag}(\vec{w} \cup \vec{z})$ appends a tower of conjunctions of
-  tautologies, with each tautology referencing a unique variable from $\vec{w}
-  \cup \vec{z}$. When we construct the circuit, this tower of tautologies will
-  act to `tag' each input to the rank gate with a unique gadget. We then show
-  that the presence of these gadgets ensures that no two inputs to a rank gate
-  are syntactically-equivalent, and so the circuit is
-  transparent.
+  Suppose now $\tau$ is not empty. We first define a transformation of the
+  formula $\theta$ to an equivalent formula $\lambda$ which has the property
+  that the \emph{natural} translation of $\lambda$ to a circuit (given later) is
+  transparent. Let $R \in \tau$. We first define two helper formulas. For a
+  variable $y$ let $\op{no-op}(y) := (R(y, y) \lor (\neg R(y, y)))$. For a
+  sequence of variables $\vec{y} = (y_1, \ldots, y_m)$ let $\op{tag} (\vec{y})
+  := (\op{no-op}(y_1) \land (\op{no-op}(y_2) \land ( \op{no-op}(y_2) \land (
+  \ldots \land (\op{no-op}(y_m)) \ldots))))$. Now, let $\lambda (\vec{x})$ be
+  the formula constructed from $\theta(\vec{x})$ by replacing each sub-formula
+  $\psi(\vec{y})$ of the form $\rank^r_p \vec{w} \vec{z} . \phi$ with the
+  formula $\rank^r_p \vec{w}\vec{z} . ((\forall u . u = u) \land \phi) \land
+  \op{tag}(\vec{w} \cup \vec{z})$. Since we always replace a subformula $\phi$
+  with a logically equivalent formula, it follows that $\lambda (\vec{x})$ and
+  $\theta (\vec{x})$ are equivalent. The intuition is that $\op{tag}(\vec{w}
+  \cup \vec{z})$ appends a tower of conjunctions of tautologies, with each
+  tautology referencing a unique variable from $\vec{w} \cup \vec{z}$. When we
+  construct the circuit, this tower of tautologies will act to `tag' each input
+  to the rank gate with a unique gadget. We then show that the presence of these
+  gadgets ensures that no two inputs to a rank gate are
+  syntactically-equivalent, and so the circuit is transparent.
 
-  %We also relabel the bound variables in $\lambda(\vec{x})$ such that there
+  % We also relabel the bound variables in $\lambda(\vec{x})$ such that there
   % are
@@
   \item If $\psi$ is of the form $Q z . \phi(\vec{y}, z)$, for $Q \in \{\forall,
-    \exists\}$, then if $Q = \forall$ we have $\Sigma (g) = \AND[n]$,
-    otherwise $\Sigma (g) = \OR[n]$. Let $L(g) : [n] \rightarrow G$ be defined
-    for $i \in [n]$ by $L(g)(i) = g_{\phi[\beta_i]}$, where $\beta_i \in
+    \exists\}$, then if $Q = \forall$ we have $\Sigma (g) = \AND[n]$, otherwise
+    $\Sigma (g) = \OR[n]$. Let $L(g) : [n] \rightarrow G$ be defined for $i \in
+    [n]$ by $L(g)(i) = g_{\phi[\beta_i]}$, where $\beta_i \in
     [n]^{\free{\psi}}$, and where both $\alpha$ and $\alpha^{z}_{i}$ are
@@
 
-We now use Lemma~\cite{lem:translating-FOrk} to prove that for every $\FPR$
+We now use Lemma~\ref{lem:translating-FOrk} to prove that for every $\FPR$
 formula there is a corresponding $\PT$-uniform family of transparent symmetric
@@
 
-  \begin{remark}
-    A: Need more specific references than the above.
-  \end{remark}
+  % \begin{remark}
+  %   A: Need more specific references than the above.
+  % \end{remark}
 

### 2018-04-06 sections/symmetric-circuits.tex
minor revisions to Section 5.  Also inserted (informal) definition of circuit isomorphism in Sec 3 for backward reference.
Most recent changes to the conclusion, with edits all around the paper.

@@
 
-\begin{drem}
-  G: In fact, this difficulty is present throughout the paper.
-\end{drem}
+% \begin{drem}
+%   G: In fact, this difficulty is present throughout the paper.
+% \end{drem}
 
@@
 \end{definition}
+We can equally define an isomorphism between a pair of circuits $C =
+\langle G, \Omega, \Sigma, \Lambda, L\rangle$ and  $C' = \langle G',
+\Omega', \Sigma', \Lambda', L'\rangle$ as a bijection $\pi: G
+\rightarrow G'$ satisfying conditions as above.  We do not usually
+need to consider distinct, isomorphic circuits and for this reason we
+only formally define automorphsims.
 
@@
 
-\begin{drem}
-  Should I prove these are actually equivalence relations? I use that fact, but
-  it's very easy to prove.
-\end{drem}
+% \begin{drem}
+%   Should I prove these are actually equivalence relations? I use that fact, but
+%   it's very easy to prove.
+% \end{drem}
 
@@
 
-\begin{drem}
-  G: I think the above paragraph may be getting a bit too far into the weeds.
-\end{drem}
+% \begin{drem}
+%   G: I think the above paragraph may be getting a bit too far into the weeds.
+% \end{drem}
 
@@
   (5 \cdot \vert C_n \vert + 3) \cdot \vert C_n \vert$.
+  \label{thm:symmetric-circuits-bound}
 \end{thm}

### 2018-04-06 sections/symmetric-circuits.tex
Another general edit. I have changed isomorphism-equivilent to isomorphic. I have also changed the "symmetric circuit" section in order to justify this choice of notation.

@@
 its $m$ inputs. This unstated assumption is pervasive in circuit complexity. In
-particular, the standard Boolean basis of $\AND$, $\OR$ and $\NOT$ gates as well as bases
-with majority or threshold gates only contain symmetric functions.
+particular, the standard Boolean basis of $\AND$, $\OR$ and $\NOT$ gates as well
+as bases with majority or threshold gates only contain symmetric functions.
 
@@
 
-As our ultimate aim is a circuit characterisation of $\FPR$, whose expressive power is
-strictly greater than that of $\FPC$, we need to consider gates corresponding to
-non-symmetric Boolean functions. In particular, we consider \emph{rank} gates
-whose inputs are a matrix and whose result is invariant under row and column
-permutations. To lead up to this, we first develop a general framework of
-structured Boolean functions. These are functions whose inputs naturally encode
-$\tau$-structures and where the output is invariant under the natural symmetries
-of such structures. The \emph{matrix-invariant} functions (defined
-formally below) are a natural
-particular case. We therefore define symmetric circuits in a general form where
-gates can be labelled by \emph{isomorphism-invariant} structured functions.
+As our ultimate aim is a circuit characterisation of $\FPR$, whose expressive
+power is strictly greater than that of $\FPC$, we need to consider gates
+corresponding to non-symmetric Boolean functions. In particular, we consider
+\emph{rank} gates whose inputs are a matrix and whose result is invariant under
+row and column permutations. To lead up to this, we first develop a general
+framework of structured Boolean functions. These are functions whose inputs
+naturally encode $\tau$-structures and where the output is invariant under the
+natural symmetries of such structures. The \emph{matrix-invariant} functions
+(defined formally below) are a natural particular case. We therefore define
+symmetric circuits in a general form where gates can be labelled by
+\emph{isomorphism-invariant} structured functions.
 
@@
 
-% AD - rewrote the paragraph to reduce the use of subscripts and superscripts.
 Let $\tau := (R, S, \nu)$ be a many-sorted vocabulary. Let $D := \biguplus_{s
@@
 interpretation of $\tau$ over $D$ given by assigning each sort symbol $s$ in
-$\tau$ to the set $D_s$ and each relation symbol in $\tau$ to the full
-relation over $D$. We call this \emph{the structure defined by $(\tau, D)$}, and
-denote it by $\str{\tau, D}$.
+$\tau$ to the set $D_s$ and each relation symbol in $\tau$ to the full relation
+over $D$. We call this \emph{the structure defined by $(\tau, D)$}, and denote
+it by $\str{\tau, D}$.
 
@@
 often use this set to index the input to a Boolean function, and as such we
-denote the index defined by $(\tau, D)$ by $\ind(\tau, D)$, and call $\tau$ the
+denote the index defined by $(\tau, D)$ by $\ind(\tau, D)$. We call $\tau$ the
 vocabulary and $D$ the universe of $\ind(\tau, D)$.
@@
 
-% GW: move sorted permutations into the background section
 For the remainder of this subsection we fix a vocabulary $\tau$ and a
-many-sorted set $D := \biguplus_{s \in S} D_{s}$. Let $X := \ind (\tau, D)$ and
-$G \leq \sym_{X}$. We note that there is an obvious group action of $G$ on
-$X$. Let $\aut (\tau, D)$ be the automorphism group of $\str{\tau, D}$. We
-define a group action of $\aut (\tau, D)$ on $X$ for $\sigma \in \aut(\tau, D)$
-by $\sigma \cdot \vec{a}_R := (\sigma \vec{a})_R$, for all $\vec{a}_R \in X$. We
-identify $\aut(\tau, D)$ with the subgroup of $\sym_X$ that acts equivalently on
-$X$.
-
-We can extend the action of $G$ on $X$ to a right group action on the set of
-functions of the form $f: X \rightarrow H$, for any set $H$, defined by $(f
-\cdot \sigma)(x) := f(\sigma x)$ for all $x \in X$, $\sigma \in G$.
+many-sorted set $D := \biguplus_{s \in S} D_{s}$, and let $X := \ind (\tau, D)$
+and $G \leq \sym_{X}$. There is an obvious group action of $G$ on $X$. Let $\aut
+(\tau, D)$ be the automorphism group of $\str{\tau, D}$. We define a group
+action of $\aut (\tau, D)$ on $X$ for $\sigma \in \aut(\tau, D)$ by $\sigma
+\cdot \vec{a}_R := (\sigma \vec{a})_R$ for all $\vec{a}_R \in X$. We identify
+$\aut(\tau, D)$ with the subgroup of $\sym_X$ that acts equivalently on $X$.
+
+Let $H$ be a set. We think of a function $f : X \rightarrow H$ as defining a
+labelling of $\str{\tau,D}$ by $H$, and we identify $f$ with this labelled
+instance of $\str{\tau, D}$. Let $f: \ind(\tau, D) \ra H$ and $g : \ind (\tau,
+D') \ra H$. We say that $f$ and $g$ are \emph{isomorphic} if there is an
+isomorphism $\pi : \str{\tau, D} \ra \str{\tau, D'}$ such that $f(\vec{a}_R) =
+g(\pi(\vec{a}_R))$ for all $\vec{a}_R \in \ind(\tau, D)$. In other words, $f$
+and $g$ are isomorphic if, and only if, they are isomorphic as (labelled)
+structures. We will often take the co-domain $H$ to be $\{0,1\}$. In this case
+$f$ and $g$ can be thought of as each defining a sub-structure of
+$\str{\tau,D}$. It is easy to see that $f$ and $g$ are isomorphic
+if, and only if, the $\tau$ structures they define are isomorphic.
 
@@
 
-We say that two functions $f: \ind(\tau, D) \rightarrow H$ and $g: \ind(\tau,
-D') \rightarrow H$ are \emph{isomorphism-equivalent} if there exists an
-isomorphism $\pi :\str{\tau, D} \rightarrow \str{\tau, D'}$ such that
-$f(\vec{a}_R) = g(\pi \vec{a}_R)$ for all $\vec{a}_R \in \ind(\tau, D)$. It is
-easy to see that isomorphism-equivalence is an equivalence relation.
-
-We are often interested in the case where $X = \ind(\tau, D) = \ind(\tau, D')$.
+% We say that two functions $f: \ind(\tau, D) \rightarrow H$ and $g: \ind(\tau,
+% D') \rightarrow H$ are \emph{isomorphism-equivalent} if there exists an
+% isomorphism $\pi :\str{\tau, D} \rightarrow \str{\tau, D'}$ such that
+% $f(\vec{a}_R) = g(\pi \vec{a}_R)$ for all $\vec{a}_R \in \ind(\tau, D)$. It is
+% easy to see that isomorphism-equivalence is an equivalence relation.
+
+% We are often interested in the case where $X = \ind(\tau, D) = \ind(\tau,
+% D')$. We say that $f, g: X \rightarrow H$ are \emph{$G$-equivalent} if there
+% exists $\sigma \in G$ such that $f = g \sigma$. We note that in this case $f$
+% and $g$ are isomorphism-equivalent if, and only if, they are $\aut(\tau,
+% D)$-equivalent.
+
+% In this paper we will often take the co-domain to be $\{0,1\}$, and so have a
+% function of the form $f : X \rightarrow \{0,1\}$. In this case we may think of
+% $f$ as defining for each relation $R^D_i$ a subset of that relation, and thus
+% determining a $\tau$-structure over the universe $D$. We note that two
+% functions $f, g: X \rightarrow \{0,1\}$ are isomorphism-equivalent if, and
+% only if, the two $\tau$-structures they determine are isomorphic.
+
 We say that $f, g: X \rightarrow H$ are \emph{$G$-equivalent} if there exists
-$\sigma \in G$ such that $f = g \sigma$. We note that in this case $f$ and $g$
-are isomorphism-equivalent if, and only if, they are $\aut(\tau, D)$-equivalent.
-
-In this paper we will often take the co-domain to be $\{0,1\}$, and so have a
-function of the form $f : X \rightarrow \{0,1\}$. In this case we may think of
-$f$ as defining for each relation $R^D_i$ a subset of that relation, and thus
-determining a $\tau$-structure over the universe $D$. We note that two functions
-$f, g: X \rightarrow \{0,1\}$ are isomorphism-equivalent if, and only if, the
-two $\tau$-structures they determine are isomorphic.
+$\sigma \in G$ such that $f = g \sigma$. We note that $f$ and $g$ are isomorphic
+if, and only if, they are $\aut(\tau, D)$-equivalent.
 
 We call a function of the form $F:\{0,1\}^{X} \rightarrow \{0,1\}$ a
-\emph{$(\tau, D)$-structured function}, or just a \emph{structured function}
-when there is no need to emphasise the particular vocabulary. We note that
+\emph{$(\tau, D)$-structured function}, or just a \emph{structured function}. We note that
 $\ind(F) = \ind(\tau, D)$, justifying our choice of notation. We let \emph{the
-  vocabulary of $F$} and \emph{the universe of $F$} denote $\tau$ and $D$
+  vocabulary of $F$} and \emph{the universe of $F$} be $\tau$ and $D$,
 respectively.
@@
 
-Structured functions give us a general framework for indexing the input sequence
-to a Boolean function and associating with that function an appropriate symmetry
-condition, or notion of equivalence. Let $F$ be a $(\tau, D)$-structured
-function. We say $F$ is \emph{$G$-invariant} if it is constant on $G$-equivalent
-input vectors, i.e.\ for all $G$-equivalent $f, g \in \{0,1\}^{X}$, $F(f) =
-F(g)$. We say $F$ is \emph{isomorphism-invariant} if it is $\aut(\tau,
-D)$-invariant. Note that a structured function with vocabulary $\tau$ is
-isomorphism-invariant if, and only if, it determines a property of
-$\tau$-structures.
+It is important to note that structured functions not only provide us with way
+of talking about Boolean functions that take as input (encodings of) structures,
+but their definition also suggests a natural notion of symmetry. Let $F$ be a
+$(\tau, D)$-structured function. We say $F$ is \emph{$G$-invariant} if for all
+$G$-equivalent $f, g : X \ra \{0,1\}$, $F(f) = F(g)$. We say $F$ is
+\emph{isomorphism-invariant} if $F$ is $\aut(\tau, D)$-invariant. Note that a
+structured function with vocabulary $\tau$ is isomorphism-invariant if, and only
+if, it decides a property of $\tau$-structures.
 
@@
 
-From the above observations, we may think of symmetric functions as
-isomorphism-invariant structured functions over the single-sorted vocabulary
-with a single unary relation. We can similarly think of matrix-invariant
-functions as isomorphism-invariant structured functions over the appropriate
-vocabulary. More formally, if the vocabulary of $F$ consists of $p$ sort symbols
-$s_1, \ldots , s_p$ and only one relation symbol with type $(s_1, \ldots, s_p)$
-and $F$ is isomorphism-invariant, then we say $F$ is \emph{sort-invariant}. If
-$p = 2$ and $F$ is sort-invariant then we say that $F$ is
-\emph{matrix-invariant}.
-
-In keeping with convention for Boolean functions, and for introducing simplicity
-without a loss of generality, we assume that the universe of any structured
-function is always a disjoint union of initial segments of the natural numbers,
-i.e.\ if $F$ is structured function with universe $D_{s_1} \uplus \ldots \uplus
-D_{s_p}$, then for all $s \in \{s_1 , \ldots , s_p\}$ there exists $d_s \in
-\nats$ such that $D_{s} = [d_s]$. We also assume that every $(\tau,
-D)$-structured function has the property that every $a \in D$ appears in at
-least one element of $\ind(\tau, D)$.
+We may think of symmetric functions as isomorphism-invariant structured
+functions over the single-sorted vocabulary with a single unary relation. We can
+similarly think of matrix-invariant functions as isomorphism-invariant
+structured functions over an appropriate vocabulary. More formally, if the
+vocabulary of $F$ consists of $p$ sort symbols $s_1, \ldots , s_p$ and only one
+relation symbol with type $(s_1, \ldots, s_p)$ and $F$ is isomorphism-invariant,
+then we say $F$ is \emph{sort-invariant}. If $p = 2$ and $F$ is sort-invariant
+then we say that $F$ is \emph{matrix-invariant}.
+
+In keeping with the conventions for Boolean functions we usually assume, without
+a loss of generality, that the universe of a structured function is a disjoint
+union of initial segments of the natural numbers, i.e.\ if $F$ is structured
+function with universe $D_{s_1} \uplus \ldots \uplus D_{s_p}$ then for all $s
+\in \{s_1 , \ldots , s_p\}$ there exists $d_s \in \nats$ such that $D_{s} =
+[d_s]$. We also assume that every $(\tau, D)$-structured function has the
+property that every $a \in D$ appears in at least one element of $\ind(\tau,
+D)$.
 
@@
     \pi g)$ and for each internal gate $g$ we have that $L(\pi g)$ and $ \pi
-    \cdot L(g)$ are isomorphism-equivalent.
+    \cdot L(g)$ are isomorphic.
   \end{myitemize}
@@
 \end{definition}
-We can equally define an isomorphism between a pair of circuits $C =
-\langle G, \Omega, \Sigma, \Lambda, L\rangle$ and  $C' = \langle G',
-\Omega', \Sigma', \Lambda', L'\rangle$ as a bijection $\pi: G
-\rightarrow G'$ satisfying conditions as above.  We do not usually
-need to consider distinct, isomorphic circuits and for this reason we
-only formally define automorphsims.
+We can equally define an isomorphism between a pair of circuits $C = \langle G,
+\Omega, \Sigma, \Lambda, L\rangle$ and $C' = \langle G', \Omega', \Sigma',
+\Lambda', L'\rangle$ as a bijection $\pi: G \rightarrow G'$ satisfying
+conditions as above. We do not usually need to consider distinct, isomorphic
+circuits and for this reason we only formally define automorphsims.
 
@@
   $g \equiv h$ if, and only if, $L(g) /_\equiv$ and $L(h) /_\equiv$ are
-  isomorphism-equivalent.
+  isomorphic.
 \end{definition}
@@
 % \begin{drem}
-%   Should I prove these are actually equivalence relations? I use that fact, but
-%   it's very easy to prove.
+%   Should I prove these are actually equivalence relations? I use that fact,
+%   but it's very easy to prove.
 % \end{drem}
@@
   (\Omega^{-1}(g)) = \Omega (\sigma \Omega^{-1}(g)) = \pi' \Omega
-  (\Omega^{-1}(g)) = \pi'(g)$, or none of $g$, $\pi(g)$ and $\pi' (g)$ are output
-  gates.
+  (\Omega^{-1}(g)) = \pi'(g)$, or none of $g$, $\pi(g)$ and $\pi' (g)$ are
+  output gates.
 
@@
   L(\pi' g) (\lambda' \lambda^{-1}\vec{a}_R)$, for all $\vec{a}_R \in \ind(g)$,
-  and so $L(\pi g)$ is isomorphism equivalent to $L(\pi'g)$ up to
-  syntactic-equivalence. We thus have that $\pi (g) $ and $\pi' (g)$ are
-  syntactically-equivalent, and the result follows.
+  and so $L(\pi g)/_\equiv$ is isomorphic to $L(\pi'g) /_\equiv$. We thus have
+  that $\pi (g) $ and $\pi' (g)$ are syntactically-equivalent, and the result
+  follows.
 
@@
 We have from Proposition~\ref{prop:unique-children-unique-extensions} that
-circuits with unique gates have unique extensions, but, in order to prove many
-of the results we will need later, we not only need that each automorphism is
-uniquely defined by the permutation it extends, but also that the isomorphisms
-that witness the isomorphism-equivalences, and so witness the validity of the
-automorphism, are also uniquely defined ( or, at the very least, well
-constrained) by the permutation $\sigma$. Without a sufficient constraint on the
-choice of isomorphism, testing if two gates have isomorphism-equivalent
-labellings (a requirement for computing the automorphism extending a
-permutation) requires solving some version of the isomorphism problem for
+circuits with unique gates have unique extensions. However, in order to prove
+many of the results we will need later we not only need that each automorphism
+is uniquely determined by the permutation it extends, but also that the
+isomorphisms between the labellings of each gate that witness 
+this automorphism are also uniquely determined by the permutation -- or, at the
+very least, well constrained. Without this constraint, computing many properties
+of the circuit would involve solving some version of the isomorphism problem for
 $\tau$-structures, where $\tau$ is the vocabulary of the gates in question.
 Indeed, we prove in Section~\ref{sec:transparent}, that for the class of
-circuits with unique children deciding if there is an isomorphism-equivalence
-between two gates is as hard as the graph-isomorphism problem. It follows that a
-great many important circuit properties (e.g.\ the orbit of a gate, symmetry of
-a circuit, etc.) for circuits with unique gates are at the very least not
-obviously polynomial-time decidable. As such, circuits with unique children,
-although satisfying the requirement of having unique extensions, are
-insufficient for our purposes.
+circuits with unique children deciding if a a given a given function is in fact
+a valid circuit automorphism is at least as hard as hard as the
+graph-isomorphism problem. Moreover, we go on to show that a great many
+important circuit 
+properties (e.g.\ the orbit of a gate, symmetry of a circuit, etc.) are also at
+least as hard to decide for circuits with unique gates as the graph isomorphism
+-- and so these properties 
+are, at the very least, not obviously polynomial-time decidable. As such,
+circuits with unique children, although satisfying the requirement of having
+unique extensions, are insufficient for our purposes.
 
@@
 circuits with unique labels. It is easy to see that if $C$ has unique labels
-then $L(g)$ and $L(g')$ are isomorphism-equivalent if, and only if, $\lambda :=
-L(g')^{-1}L(g)$ is an isomorphism. In this case, rather than having to decide
-the isomorphism problem, we can decide isomorphism-equivalences by checking if a
-given candidate function is a valid isomorphism. We prove in
-Section~\ref{sec:transparent} that all of the circuit properties of interest in
-this paper are polynomial-time decidable for circuits with unique labels.
-Moreover, we show in Lemma~\ref{lem:transparent-unique} that a transparent
-circuit can be transformed into an equivalent circuit with unique labels in time
-polynomial in the size of the circuit. Since we are working with $P$-uniform
-families of transparent circuits, this fact allows us to assume, without a loss
-of generality, that transparent circuits have unique labels and so , from
-\ref{prop:unique-children-unique-extensions}, unique extensions).
+then $L(g)$ and $L(g')$ are isomorphic if, and only if, $\lambda :=
+L(g')^{-1}L(g)$ is an automorphism of $\str{g'}$ . We see that in this case the problem of
+deciding if $L(g)$ and $L(g')$ are isomorphic reduces to the problem of deciding if a given
+candidate function is a valid automorphism, a much easier problem. Indeed, we
+prove in Section~\ref{sec:transparent} that all of the circuit properties of
+interest in this paper are polynomial-time decidable for circuits with unique
+labels. Moreover, we show in Lemma~\ref{lem:transparent-unique} that a
+transparent circuit can be transformed into an equivalent circuit with unique
+labels in time polynomial in the size of the circuit. Since we are working with
+$\PT$-uniform families of transparent circuits, this fact allows us to assume,
+without a loss of generality, that transparent circuits have unique labels and
+so, from Proposition~\ref{prop:unique-children-unique-extensions}, unique extensions.
 
@@
 
-Before we state the main result of this paper we need to discuss the Boolean
-bases of interest in this paper and introduce some useful terminology. In most
+Before we state the main result of this paper we need to discuss some of the Boolean
+bases that will be of interest to us and introduce some useful terminology. In most
 other contexts a basis is taken to be a finite sequence of symmetric Boolean
@@
 \begin{thm}[Main Theorem]
-  A graph property is decidable by a $\P$-uniform family of transparent
+  A graph property is decidable by a $\PT$-uniform family of transparent
   symmetric rank-circuits if, and only if, it is definable by an $\FPR$
@@
   symmetric circuit $C$ defined over the basis $\BM$ that computes $F$.
-  Moreover, this algorithm runs in time polynomial in $n$ and the
-  circuit $C$ has depth at most $5$, width at most $2n+2$ and size at most $5n +
-  3$.
+  Moreover, this algorithm runs in time polynomial in $n$ and the circuit $C$
+  has depth at most $5$, width at most $2n+2$ and size at most $5n + 3$.
 \end{prop}

### 2018-04-06 sections/transparency-and-unique-extensions.tex
Another general edit. I have changed isomorphism-equivilent to isomorphic. I have also changed the "symmetric circuit" section in order to justify this choice of notation.

@@
 \begin{document}
-Recall that each gate $g$ in a cricuit  is associated with a structure
-$D$ with the elements of the relations in $D$, i.e.\ $\ind(\Sigma(g))$
-labelled by the children of $g$.  Many of the properties of circuits
-that are central to our construction, and we wish to be able to decide
-efficiently, particularly those that reference circuit automorphisms or
-syntactic-equivalence, depend on the existence of isomorphisms that agrees with a
-given permutation of the gates labelling the structure.  This introduces a
-potential difficulty as there is no known polynomial-time algorithm for the
-general isomorphism problem, but we we require many of these circuit properties
-to be polynomial-time decidable in order to define our translation from circuits
-to formulas (see Section~\ref{sec:circuits-to-formulas}).  This is not a problem
-if we restrict our attention to circuits with symmetric gates, as
-in~\cite{AndersonD17}, as in this case the structures of interest are
-sets, and set equivalence is clearly decidable in polynomial-time.  When we
-allow for circuits to be defined over bases including non-symmetric functions it
-is not obvious that these properties can be decided in polynomial-time.
+Recall that each gate $g$ in a cricuit is associated with a structure $D$ with
+the elements of the relations in $D$, i.e.\ $\ind(\Sigma(g))$ labelled by the
+children of $g$. Many of the properties of circuits that are central to our
+construction, and we wish to be able to decide efficiently, particularly those
+that reference circuit automorphisms or syntactic-equivalence, depend on the
+existence of isomorphism of structures that agrees with a given permutation of
+the gates labelling the structure. This introduces a potential difficulty as
+there is no known polynomial-time algorithm for the general isomorphism problem,
+but we we require many of these circuit properties to be polynomial-time
+decidable in order to define our translation from circuits to formulas (see
+Section~\ref{sec:circuits-to-formulas}). This is not a problem if we restrict
+our attention to circuits with symmetric gates, as in~\cite{AndersonD17}, as in
+this case the structures of interest are sets, and set equivalence is clearly
+decidable in polynomial-time. When we allow for circuits to be defined over
+bases including non-symmetric functions it is not obvious that these properties
+can be decided in polynomial-time.
 
@@
 important for two reasons. First, circuits with unique labels have unique
-extensions, which enables us to apply the support theorem. Second, as we
-show in this section, all relevant symmetry-related circuit properties are
+extensions, which enables us to apply the support theorem. Second, as we show in
+this section, all relevant symmetry-related circuit properties are
 polynomial-time decidable for circuits with unique labels. We use all of these
@@
 
-In Section~\ref{sec:necessity} we discuss more formally the relationship
-between the problem of deciding many of these natural circuit properties and the
+In Section~\ref{sec:necessity} we discuss more formally the relationship between
+the problem of deciding many of these natural circuit properties and the
 graph-isomorphism problem. In particular, we present reductions from the
@@
 properties for general circuits. It follows that deciding most of these circuit
-properties is as hard as the graph isomorphism problem---a problem not known to be
-in $\PT$, showing that some condition like transparency is necessary.  We also show that most of these hardness results are quite robust, in
-that even if we restrict our attention to other natural classes of circuits
-(e.g.\ circuits with unique children or circuits with injective labels) these
-decision problems remain at least as hard as the graph-isomorphism problem.
-In this sense, while the first part of this section provides evidence in favour of the
-sufficiency of the restriction to transparent circuits, the second part provides
-evidence in favour of its necessity.
+properties is as hard as the graph isomorphism problem---a problem not known to
+be in $\PT$, showing that some condition like transparency is necessary. We also
+show that most of these hardness results are quite robust, in that even if we
+restrict our attention to other natural classes of circuits (e.g.\ circuits with
+unique children or circuits with injective labels) these decision problems
+remain at least as hard as the graph-isomorphism problem. In this sense, while
+the first part of this section provides evidence in favour of the sufficiency of
+the restriction to transparent circuits, the second part provides evidence in
+favour of its necessity.
 
@@
   output that $g \not\equiv h$. We thus have that $f$ is a bijective function
-  and for all $x \in \ind(g)$, $L(g)(x) \equiv L(h)(f(x))$. Check if $g$
-  and $h$ are both symmetric gates. If so, $f$ witnesses the required
-  isomorphism-equivalence and so we halt and output that $g \equiv h$.
+  and for all $x \in \ind(g)$, $L(g)(x) \equiv L(h)(f(x))$. Check if $g$ and $h$
+  are both symmetric gates. If so, $f$ is an isomorphism from $L(g)$ to $L(h)$,
+  and so we halt and output that $g \equiv h$.
 
@@
 
- We now define what it means to take a
-quotient of a circuit by the syntactic-equivalence relation. Intuitively, we
-think of a quotient of a given circuit as being formed by `merging' each
-syntactic-equivalence class into a single gate and including a wire between two
-gates in the quotient circuit if, and only if, there is a wire between an
-element of each equivalence class.
+We now define what it means to take a quotient of a circuit by the
+syntactic-equivalence relation. Intuitively, we think of a quotient of a given
+circuit as being formed by `merging' each syntactic-equivalence class into a
+single gate and including a wire between two gates in the quotient circuit if,
+and only if, there is a wire between an element of each equivalence class.
 
@@
 functions. But it is not hard to see that for every gate $g$ in $C$, $L(g)$ and
-$L'(g)$ are isomorphic.  It follows that these two circuits are
-isomorphic in the precise sense alluded to right after Definition~\ref{defn:automorphism}.
+$L'(g)$ are isomorphic. It follows that these two circuits are isomorphic in the
+precise sense alluded to right after Definition~\ref{defn:automorphism}.
 
@@
   /_\equiv$. It follows from $[g] \equiv [h]$ that $L(g') /_\equiv$ is
-  isomorphism-equivalent to $L(h') /_\equiv$. It follows that $g' \equiv h'$,
-  and so $[g] = [h]$.
+  isomorphic to $L(h') /_\equiv$. From this it follows that $g' \equiv h'$, and
+  so $[g] = [h]$.
 
@@
   \in [g]$ be such that $L_\equiv(\pi_\equiv[g]) = L_\equiv ([\pi h]) = L(\pi h)
-  /_\equiv$. We have that $\pi L(g')$ is isomorphism-equivalent to $L(\pi g')$,
-  and it follows that $(\pi L(g'))/_\equiv$ is isomorphism-equivalent to $L(\pi
-  g') /_\equiv$. We then have $(\pi L(g'))/_\equiv = \pi_\equiv (L(g') /_\equiv)
-  = \pi_\equiv L_\equiv ([g])$ and, since $g' \equiv h$ and so $\pi g' \equiv
-  \pi h$, we have that $L(\pi g')/_\equiv$ is isomorphism-equivalent to $L(\pi
-  h) /_\equiv = L_\equiv(\pi_\equiv[g])$. It follows that $\pi_\equiv L_\equiv
-  ([g])$ is isomorphism-equivalent to $L_\equiv(\pi_\equiv [g]) /_\equiv$.
-  Suppose $[g]$ is an output gate. Then for $\vec{a} \in \dom (\Omega)$,
-  $\pi_\equiv \Omega_\equiv (\vec{a}) = [\pi \Omega (\vec{a})] = [\Omega (\sigma
-  \vec{a})] = \Omega_\equiv (\sigma \vec{a})$. It follows that if $C$ is
-  symmetric then $C_\equiv$ is symmetric.
+  /_\equiv$. We have that $\pi L(g')$ is isomorphic to $L(\pi g')$, and it
+  follows that $(\pi L(g'))/_\equiv$ is isomorphic to $L(\pi g') /_\equiv$. We
+  then have $(\pi L(g'))/_\equiv = \pi_\equiv (L(g') /_\equiv) = \pi_\equiv
+  L_\equiv ([g])$ and, since $g' \equiv h$ and so $\pi g' \equiv \pi h$, we have
+  that $L(\pi g')/_\equiv$ is isomorphic to $L(\pi h) /_\equiv =
+  L_\equiv(\pi_\equiv[g])$. It follows that $\pi_\equiv L_\equiv ([g])$ is
+  isomorphic to $L_\equiv(\pi_\equiv [g]) /_\equiv$. Suppose $[g]$ is an output
+  gate. Then for $\vec{a} \in \dom (\Omega)$, $\pi_\equiv \Omega_\equiv
+  (\vec{a}) = [\pi \Omega (\vec{a})] = [\Omega (\sigma \vec{a})] = \Omega_\equiv
+  (\sigma \vec{a})$. It follows that if $C$ is symmetric then $C_\equiv$ is
+  symmetric.
 
@@
   important point to note is that each $\AND$-gate in $C_1$ has fan-in at least
-  two. We construct $C'$ from $C_1$ by adding in a number of $\AND$-gates
-  with fan-in one. Therefore, since all of the $\AND$-gates in $C_1$ have fan-in
-  two, it follows that none of these new gates are syntactically-equivalent
-  to any gate in $C_1$. We now show that $C_1$ and $C_0$ compute the same
-  function and if $C_0$ is symmetric then $C_1$ is symmetric.
+  two. We construct $C'$ from $C_1$ by adding in a number of $\AND$-gates with
+  fan-in one. Therefore, since all of the $\AND$-gates in $C_1$ have fan-in two,
+  it follows that none of these new gates are syntactically-equivalent to any
+  gate in $C_1$. We now show that $C_1$ and $C_0$ compute the same function and
+  if $C_0$ is symmetric then $C_1$ is symmetric.
 
@@
     $i = 1$ then $\{ h \} = H_g' = H_{g'}'$. Since the only gate in $G_\land$
-    that has $h$ as a child is $g^h_1$, it follows that $g = g^h_1 = g'$.
-    If $i > 1$ then $\{g^{h}_{i-1}\} = H_g' = H_{g'}'$. Since $g^h_i$ is the
-    only gate in $G_\land$ that has $g^h_{i-1}$ as a child, we have $g =
-    g^h_i = g'$. It follows that if $g \in G_\land$ then $g = g'$.
+    that has $h$ as a child is $g^h_1$, it follows that $g = g^h_1 = g'$. If $i
+    > 1$ then $\{g^{h}_{i-1}\} = H_g' = H_{g'}'$. Since $g^h_i$ is the only gate
+    in $G_\land$ that has $g^h_{i-1}$ as a child, we have $g = g^h_i = g'$. It
+    follows that if $g \in G_\land$ then $g = g'$.
 
@@
     \mathcal{A}](g^h_i) = C'[\gamma \mathcal{A}](h) = C_1[\gamma \mathcal{A}](h)
-    = L^{\gamma \mathcal{A}}_1(g)(x)$. The penultimate equality follow from 
-    the inductive hypothesis. The final equality follows from the fact that $h =
-    L_1 (g)(x)$. We thus have $C'[\gamma \mathcal{A}](g) = \Sigma'({L'}^{\gamma
+    = L^{\gamma \mathcal{A}}_1(g)(x)$. The penultimate equality follow from the
+    inductive hypothesis. The final equality follows from the fact that $h = L_1
+    (g)(x)$. We thus have $C'[\gamma \mathcal{A}](g) = \Sigma'({L'}^{\gamma
       \mathcal{A}}(g)) = \Sigma_1 (L^{\gamma \mathcal{A}}_1(g)) = C_1[\gamma
@@
   \vert$ wires, we may construct $C_1$ from $C_0$ in time polynomial in $\vert C
-  \vert$. It is easy to see that $C'$ can be constructed in time polynomial
-  in $\vert C_1 \vert$ and hence polynomial in $\vert C \vert$. The result
-  follows.
+  \vert$. It is easy to see that $C'$ can be constructed in time polynomial in
+  $\vert C_1 \vert$ and hence polynomial in $\vert C \vert$. The result follows.
   %
@@
 input a circuit with unique labels and an appropriate permutation and outputs
-the action of the automorphism extending the permutation (if it is defined) on the
-gates of the circuit.
+the action of the automorphism extending the permutation (if it is defined) on
+the gates of the circuit.
 
@@
   circuit such that $\Sigma_\equiv(h) = \Sigma_\equiv (h')$, $\pi' L(h)$ is
-  isomorphism-equivalent to $L_\equiv(h')$ and, if $h$ is an output gate then
-  $h'$ is an output gate such that $\sigma \Omega^{-1}_\equiv(h) =
-  \Omega^{-1}_\equiv(h')$. Suppose there is another gate $h''$ in the circuit
-  that meets all of those criteria as well. But then it follows that $h'' \equiv
-  h'$. Since $C_\equiv$ is reduced, we then have that $h'' = h'$.  We thus have
-  that the choice of $h'$, if it exists, is unique. Note that, since $C$ has
-  unique labels $C_\equiv$ has unique labels, and so unique extensions, and so
-  we have that $\pi' L_\equiv(h)$ is isomorphism-equivalent to $L_\equiv(h')$
-  if, and only if, $L_\equiv(h')^{-1}\pi'L_\equiv(h)$ acts on $\ind(h)$ like an
-  automorphism of $\str{h}$. This is easy to determine. If no such $h'$ exists,
-  halt and output that there is no automorphism extending $\sigma$. Otherwise,
-  let $\pi'(h) = h'$.
+  isomorphic to $L_\equiv(h')$ and, if $h$ is an output gate then $h'$ is an
+  output gate such that $\sigma \Omega^{-1}_\equiv(h) = \Omega^{-1}_\equiv(h')$.
+  Suppose there is another gate $h''$ in the circuit that meets all of those
+  criteria as well. But then it follows that $h'' \equiv h'$. Since $C_\equiv$
+  is reduced, we then have that $h'' = h'$. We thus have that the choice of
+  $h'$, if it exists, is unique. Note that, since $C$ has unique labels
+  $C_\equiv$ has unique labels, and so unique extensions, and so we have that
+  $\pi' L_\equiv(h)$ is isomorphic to $L_\equiv(h')$ if, and only if,
+  $L_\equiv(h')^{-1}\pi'L_\equiv(h)$ acts on $\ind(h)$ like an automorphism of
+  $\str{h}$. This is easy to determine. If no such $h'$ exists, halt and output
+  that there is no automorphism extending $\sigma$. Otherwise, let $\pi'(h) =
+  h'$.
 
@@
 automorphism. It suffices to check that $\pi$ is a bijection and that for each
-$h \in G$, $\pi L(h)$ is isomorphic to $L(h')$. It is easy to check
-that $\pi$ is a bijection.  Notice that $\pi L(h)$ is isomorphic to
-$L(\pi(h))$ if, and only if, $L(\pi(h))^{-1}\pi L(h)$ is an automorphism. This
-condition is also easy to check.  If either of these checks fail, halt and output
-that there is no automorphism extending $\sigma$.  Otherwise, output $\pi (g)$
-for all $g \in G$.
+$h \in G$, $\pi L(h)$ is isomorphic to $L(h')$. It is easy to check that $\pi$
+is a bijection. Notice that $\pi L(h)$ is isomorphic to $L(\pi(h))$ if, and only
+if, $L(\pi(h))^{-1}\pi L(h)$ is an automorphism. This condition is also easy to
+check. If either of these checks fail, halt and output that there is no
+automorphism extending $\sigma$. Otherwise, output $\pi (g)$ for all $g \in G$.
 
@@
 \begin{lem}
-  There is an algorithm that takes as input a $(\mathbb{B}, \rho)$-circuit $C$ with
-  unique labels of order $n$, a gate $\sigma \in \sym_n$, $g$ a gate in $C$, and
-  $a \in \universe{g}$ and, if there exists an automorphism of $C$ extending
-  $\sigma$ such that $\sigma \in \stab(g)$, outputs $\sigma a$.
-  The algorithm runs in time polynomial in the size of $C$ and the encoding of
+  There is an algorithm that takes as input a $(\mathbb{B}, \rho)$-circuit $C$
+  with unique labels of order $n$, a gate $\sigma \in \sym_n$, $g$ a gate in
+  $C$, and $a \in \universe{g}$ and, if there exists an automorphism of $C$
+  extending $\sigma$ such that $\sigma \in \stab(g)$, outputs $\sigma a$. The
+  algorithm runs in time polynomial in the size of $C$ and the encoding of
   $\sigma$.
@@
 
-Let  $\mathcal{P}$ be the partition that is the coarsest common
-refinement of the partitions $\mathcal{P}_{(u,v)}$, for all $u,v$ with $(u,v) \cdot x = x$.
-From
-  Proposition~\ref{prop:combining-supporting-patitions} we have that
+  Let $\mathcal{P}$ be the partition that is the coarsest common refinement of
+  the partitions $\mathcal{P}_{(u,v)}$, for all $u,v$ with $(u,v) \cdot x = x$.
+  From Proposition~\ref{prop:combining-supporting-patitions} we have that
   $\mathcal{P}$ supports $\stab_{\stab(S)}(x)$. Suppose that $\mathcal{P}$ is
@@
   exists a partition $\mathcal{P}'$ supporting $\stab_{\stab(S)}(x)$ such that
-  $\mathcal{P}' \preceq \mathcal{P}$ and $\mathcal{P}' \neq \mathcal{P}$. And so there
-  exists $P \in \mathcal{P}$ and $P' \in \mathcal{P}'$ such that $P \subsetneq
-  P'$. But then there exists $a , b \in P'$ such that $a \not\in P$. Note that
-  $(a,b)$ fixes $\mathcal{P}'$ and, since $\mathcal{P}'$ supports
+  $\mathcal{P}' \preceq \mathcal{P}$ and $\mathcal{P}' \neq \mathcal{P}$. And so
+  there exists $P \in \mathcal{P}$ and $P' \in \mathcal{P}'$ such that $P
+  \subsetneq P'$. But then there exists $a , b \in P'$ such that $a \not\in P$.
+  Note that $(a,b)$ fixes $\mathcal{P}'$ and, since $\mathcal{P}'$ supports
   $\stab_{\stab(S)}(x)$, it follows that $(a,b) \in \stab_{\stab(S)}(x)$ and $a
@@
 
-  Furthermore, when computing the orbit, we construct $M_i$
-  iteratively and obtain the orbit after at most $\vert X \vert$
-  iterations. Since each iteration requires at
-  most $\mathcal{O} (n^{2})$ applications of the group action, it follows that
-  this part of the procedure runs time $\mathcal{O}(n^2\vert X \vert \vert T
-  \vert p (\vert X \vert + n)^2)$. We thus have that the entire algorithm runs
-  in polynomial-time, and the result follows.
+  Furthermore, when computing the orbit, we construct $M_i$ iteratively and
+  obtain the orbit after at most $\vert X \vert$ iterations. Since each
+  iteration requires at most $\mathcal{O} (n^{2})$ applications of the group
+  action, it follows that this part of the procedure runs time
+  $\mathcal{O}(n^2\vert X \vert \vert T \vert p (\vert X \vert + n)^2)$. We thus
+  have that the entire algorithm runs in polynomial-time, and the result
+  follows.
 \end{proof}
@@
   using the algorithm given in Lemma~\ref{lem:transparent-syntactic-equiv}. We
-  test if every non-symmetric gate in $G^{i+1}$ has unique labels, i.e.\ if
-  it has injective labels and no two of its children are elements of the same
+  test if every non-symmetric gate in $G^{i+1}$ has unique labels, i.e.\ if it
+  has injective labels and no two of its children are elements of the same
   syntactic-equivalence class. If this test fails, we halt and output that the
-  circuit is not transparent, and if it succeeds we increment the variable $i$ and
-  continue as above. If $i$ is ever set to the value $\depth(C)$, we halt and
-  output that the circuit is transparent.
+  circuit is not transparent, and if it succeeds we increment the variable $i$
+  and continue as above. If $i$ is ever set to the value $\depth(C)$, we halt
+  and output that the circuit is transparent.
 
@@
 
-We have shown then that key properties of transparent circuits are
-tractable and, using these results, we have shown that
-transparent circuits can be transformed in polynomial time into circuits with
-unique labels. We have also shown that circuits with unique labels have all of
-the requisite algorithmic properties needed in order to define our translation
-from circuits to formulas. In the remainder of this section we prove that most
-of these properties, and particularly those used to define this translation to
-circuits with unique labels, are all at least as hard to decide as the graph
-isomorphism problem. In particular, we present reductions from the
-graph-isomorphism problem to most of the important decision problems addressed
-in the first part of this section, including: deciding if a circuit is
-symmetric, deciding if a gate has unique labels, deciding if two gates are
-syntactically-equivalent, deciding if two gates are in the same orbit, etc.
-Moreover, we show that many of these hardness results still hold even if we
-restrict ourselves to other natural classes of circuits (e.g.\ the class of
-circuits with injective labels, the class of circuits with unique children).
+We have shown then that key properties of transparent circuits are tractable
+and, using these results, we have shown that transparent circuits can be
+transformed in polynomial time into circuits with unique labels. We have also
+shown that circuits with unique labels have all of the requisite algorithmic
+properties needed in order to define our translation from circuits to formulas.
+In the remainder of this section we prove that most of these properties, and
+particularly those used to define this translation to circuits with unique
+labels, are all at least as hard to decide as the graph isomorphism problem. In
+particular, we present reductions from the graph-isomorphism problem to most of
+the important decision problems addressed in the first part of this section,
+including: deciding if a circuit is symmetric, deciding if a gate has unique
+labels, deciding if two gates are syntactically-equivalent, deciding if two
+gates are in the same orbit, etc. Moreover, we show that many of these hardness
+results still hold even if we restrict ourselves to other natural classes of
+circuits (e.g.\ the class of circuits with injective labels, the class of
+circuits with unique children).
 
@@
   Let $\rho$ be any non-empty relational vocabulary and let $r, p \in \nats$,
-  with $p$ prime.  We reduce the bipartite-isomorphism problem to the
-  problem of deciding whether two given gates are syntactically
-  equivalent in a symmetric rank-circuit taking $\rho$-structures as
-  input where the circuit (i) has
+  with $p$ prime. We reduce the bipartite-isomorphism problem to the problem of
+  deciding whether two given gates are syntactically equivalent in a symmetric
+  rank-circuit taking $\rho$-structures as input where the circuit (i) has
   injective labels, (ii) contains no constant gates, and (iii) contains at most
@@
   Lemma~\ref{lem:syntactically-equivalent-unique-labels}. We now prove that the
-  mapping $(C, g_1, g_2)$ to $(C', g_1)$ is a reduction. Let $\pi_e$
-  be a
+  mapping $(C, g_1, g_2)$ to $(C', g_1)$ is a reduction. Let $\pi_e$ be a
   bijection from the gates of $C'$ to the gates of $C'$ that swaps $g_1$ and
@@
 \begin{proof}
-In fact, we reduce the graph-isomorphism problem is to the problem of
-deciding symmetry of a reduced circuit in
-  which all but two gates have unique labels.
+  In fact, we reduce the graph-isomorphism problem is to the problem of deciding
+  symmetry of a reduced circuit in which all but two gates have unique labels.
 
@@
   automorphism of the circuit extending the transposition $(1,2)$, if and only
-  if, $(1,2) (L(g^1_{\rank}))$ is isomorphism-equivalent to $L(g^2_{\rank})$ if,
-  and only if, $B_1$ and $B_2$ are bipartite-isomorphic.
+  if, $(1,2) (L(g^1_{\rank}))$ is isomorphic to $L(g^2_{\rank})$ if, and only
+  if, $B_1$ and $B_2$ are bipartite-isomorphic.
 
@@
 \begin{lem}
-  There is a polynomial-time reductions from the graph-isomorphism problem to the
-  problem of deciding if two given gates in a given circuit are in the same
+  There is a polynomial-time reductions from the graph-isomorphism problem to
+  the problem of deciding if two given gates in a given circuit are in the same
   orbit.
@@
 \begin{proof}
- In fact, we construct the reduction to circuits
-  with unique extensions, circuits with unique children, or to circuits with
-  injective labels.
+  In fact, we construct the reduction to circuits with unique extensions,
+  circuits with unique children, or to circuits with injective labels.
 
@@
 \begin{lem}
-  There are polynomial-time reductions from the graph isomorphism problem to
-  the problem of deciding if a circuit does not have unique extensions and the
+  There are polynomial-time reductions from the graph isomorphism problem to the
+  problem of deciding if a circuit does not have unique extensions and the
   problem of deciding if a circuit does not have unique children.

### 2018-04-08 sections/conclusion.tex
re-worked conclusions

@@
 \begin{document}
+$\FPR$ is one of the most expressive logics we know that is still
+contained in $\PT$ and understanding its expressive power is an
+important question.  The main result of this paper establishes an equivalence between the
+expressive power of $\FPR$ and the computational power of uniform families
+of transparent symmetric rank-circuits.  Not only does this result establish an
+interesting characterisation of an important
+logic, but it also deepens our understanding of the connection between
+logic and circuit complexity in general and casts new light on
+foundational aspects of the circuit model.
 
-$\FPR$ is one of the two candidate logics for capturing $\PT$ an so
-understanding its expressive power is an absolutely central problem in the
-field. The main result of this paper establishes an equivalence between the
-expressive power of $\FPR$ and the computational power of $\PT$-uniform families
-of transparent symmetric rank-circuits. Not only does this result establish an
-interesting characterisation of a little-understood and crucially important
-logic, but it also further develops our understanding of the connection between
-logic and circuit complexity, allowing our understanding of $\FPR$ (and
-circuits) to benefit from ideas in both of these quite disparate fields.
+The circuit characterisation also helps emphasise certain important
+aspects of the logic.  Given that $\PT$-uniform families of invariant
+circuits (without the restriction to symmetry) express all properties
+on $\PT$, we can understand  the inability of $\FPC$ (and,
+conjecturally, $\FPR$) to express all such properties as essentially
+down to symmetry.  As with other (machine) models of computation, the
+translation to circuits exposes the inherent combinatorial structure
+of an algorithm.  In the case of logics, we find that a key property
+of this structure is its symmetry and the translation to circuits
+provides us with the tools to study it.
 
-This alternative view of the logic also helps emphasise certain characteristics
-of the logic that may be much less obvious when working with the conventional
-definition. To choose one notable example, the circuit characterisations (both
-of $\FPR$ and $\FPC$) help bring to the fore the importance of the symmetry
-properties inherent in the the syntactic structure of the logic. Indeed, we
-recall that $\PT$-uniform families of transparent invariant (rather than
-symmetric) rank-circuits and $\PT$-uniform families of invariant circuits with
-symmetric gates decide exactly those queries that are in $\PT$. In this way the
-restriction from families of invariant circuits to families of symmetric
-circuits corresponds to the restriction from $\PT$ to $\FPR$ or $\FPC$. In this
-sense, we might say that it is this underlying symmetry property of the logic,
-brought into focus by the circuit characterisation, that separates $\FPC$ from
-$\PT$, and which determines the relationship between $\FPR$ and $\PT$. In fact,
-we have that $\FPR$ captures $\PT$ if, and only if, $\PT$-uniform families of
-symmetric rank-circuits have the same computational power as $\PT$-uniform
-families of invariant rank-circuits. In this way the circuit-characterisation
-brings out this underlying symmetry property of the logic, demonstrates how
-crucial this symmetry property for understanding the logic, and then provides us
-with a framework for studying symmetry.
+% This alternative view of the logic also helps emphasise certain characteristics
+% of the logic that may be much less obvious when working with the conventional
+% definition. To choose one notable example, the circuit characterisations (both
+% of $\FPR$ and $\FPC$) help bring to the fore the importance of the symmetry
+% properties inherent in the the syntactic structure of the logic. Indeed, we
+% recall that $\PT$-uniform families of transparent invariant (rather than
+% symmetric) rank-circuits and $\PT$-uniform families of invariant circuits with
+% symmetric gates decide exactly those queries that are in $\PT$. In this way the
+% restriction from families of invariant circuits to families of symmetric
+% circuits corresponds to the restriction from $\PT$ to $\FPR$ or $\FPC$. In this
+% sense, we might say that it is this underlying symmetry property of the logic,
+% brought into focus by the circuit characterisation, that separates $\FPC$ from
+% $\PT$, and which determines the relationship between $\FPR$ and $\PT$. In fact,
+% we have that $\FPR$ captures $\PT$ if, and only if, $\PT$-uniform families of
+% symmetric rank-circuits have the same computational power as $\PT$-uniform
+% families of invariant rank-circuits. In this way the circuit-characterisation
+% brings out this underlying symmetry property of the logic, demonstrates how
+% crucial this symmetry property for understanding the logic, and then provides us
+% with a framework for studying symmetry.
 
@@
 
-However, much of the contribution of this paper is not in the main result
-itself, but rather in the entirely novel framework for circuits and the numerous
-new results that we needed to develop in order to prove the main result of this
-paper. As such, we shall briefly review some of these contributions, placing an
-emphasis both on the nature of these contributions and on the necessity of their
-introduction. Indeed, it would seem at first glance that generalising Anderson
-and Dawar's circuit characterisation of $\FPC$ to $\FPR$ should be a simple
-matter of extending the model so as to allow circuits to be defined over bases
-that includes rank-threshold functions -- and perhaps extending a few key
-results and definitions as needed. We showed in
-Theorem~\ref{thm:symmetric-circuits-bound} that, in fact, we cannot increase the
-expressive power of the model by adding symmetric functions to the basis, and so
-the addition of non-symmetric functions to the basis seems almost unavoidable.
-However, while the inclusion of rank-threshold functions in the basis may seem
-benign, it in fact violates a near-ubiquitous assumption in circuit complexity,
-namely that the basis over which the circuit is defined must consist of
-symmetric functions. While this assumption is usually not stated, the fact that
-the circuit is taken to be a directed acyclic graph means that there is no order
-(or any structure at all) on the inputs of each gate, an assumption which only
-makes sense if it is assumed that the evaluation of each gate is invariant under
-any ordering of its inputs -- which is to say the basis must be symmetric.
-However, we found that in Anderson and Dawar's case this assumption pervades not
-just their definition of a circuit, but also the central ideas of their paper,
-including their definition of a circuit automorphism and of a symmetric circuit,
-as well as almost all of the key results and techniques they use to establish
-their characterisation.
+Still, the most significant contribution of this paper is not in the main result
+but in the techniques that are developed to establish it, and we
+highlight some of these now.  The
+conclusion of~\cite{AndersonD17} says that the support theorem is
+``largely agnostic to the particular [\ldots] basis'', suggesting that
+it could be easily adapted to include other gates.  This turns out to
+have been a misjudgment.  Attempting to prove the support theorem for
+a basis that includes rank threshold gates showed us the extent to
+which both the proof of the theorem and, more broadly, the definitions
+of circuit classes, rest heavily on the assumption that all functions
+computed by gates are symmetric.  Thus, in order to define what the
+``symmetry'' condition might mean for circuits that include rank
+threshold gates, we radically generalise the circuit framework to allow
+for gates that take structured inputs (rather than sets of $0$s
+and $1$s) and are invariant under isomorphisms.  This leads to a
+refined notion of circuit automorphism, which allows us to formulate a
+notion of symmetry and prove a version of the support theorem.  Again,
+in that proof, substantial new methods are required.
 
-As such, in order to include rank-threshold functions in the basis we needed to
-construct a new framework for circuits as well as develop novel approaches and
-techniques in order to work with these circuits. We began by generalising the
-notion of a symmetric function, introducing isomorphism-invariant structured
-functions. These functions take in structures encoded and strings and are
-invariant under isomorphism, rather than under arbitrary permutations of the
-string. It is easy to see that rank-threshold functions are
-isomorphism-invariant. We defined a basis to be a set of isomorphism-invariant
-functions, and extended the circuit model, adding to each gate in the circuit a
-structure on its input gates in accord with the isomorphism-invariant structured
-function labelling that gate. Rather than a gate being invariant under arbitrary
-permutations of its input gates, a gate in this circuit should be invariant
-under permutations of its input gate that form a (labelled) isomorphism. We
-extended the notion of an automorphism to reflect this and defined what it means
-for a circuit to be symmetric.
+% itself, but rather in the entirely novel framework for circuits and the numerous
+% new results that we needed to develop in order to prove the main result of this
+% paper. As such, we shall briefly review some of these contributions, placing an
+% emphasis both on the nature of these contributions and on the necessity of their
+% introduction. Indeed, it would seem at first glance that generalising Anderson
+% and Dawar's circuit characterisation of $\FPC$ to $\FPR$ should be a simple
+% matter of extending the model so as to allow circuits to be defined over bases
+% that includes rank-threshold functions -- and perhaps extending a few key
+% results and definitions as needed. We showed in
+% Theorem~\ref{thm:symmetric-circuits-bound} that, in fact, we cannot increase the
+% expressive power of the model by adding symmetric functions to the basis, and so
+% the addition of non-symmetric functions to the basis seems almost unavoidable.
+% However, while the inclusion of rank-threshold functions in the basis may seem
+% benign, it in fact violates a near-ubiquitous assumption in circuit complexity,
+% namely that the basis over which the circuit is defined must consist of
+% symmetric functions. While this assumption is usually not stated, the fact that
+% the circuit is taken to be a directed acyclic graph means that there is no order
+% (or any structure at all) on the inputs of each gate, an assumption which only
+% makes sense if it is assumed that the evaluation of each gate is invariant under
+% any ordering of its inputs -- which is to say the basis must be symmetric.
+% However, we found that in Anderson and Dawar's case this assumption pervades not
+% just their definition of a circuit, but also the central ideas of their paper,
+% including their definition of a circuit automorphism and of a symmetric circuit,
+% as well as almost all of the key results and techniques they use to establish
+% their characterisation.
 
-While we have generalised a few results for this framework, including the
-support theorem, it is important to note that a number of crucial counting
-techniques and polynomial-time algorithms for circuits are either not easy to
-generalise or otherwise resist generalisation entirely. This follows from the
-fact that a circuit automorphism needs to preserve more structure when acting on
-non-symmetric gates than when acting on symmetric gates. As a result, while many
-symmetry-related circuit properties are polynomial-time decidable for circuits
-with symmetric gates, we have shown that these same properties are at least as
-hard as the graph-isomorphism for circuits with non-symmetric gates. This is a
-problem as the polynomial-time decidability of these properties is essential for
-our translation from circuits into formulas.
+% As such, in order to include rank-threshold functions in the basis we needed to
+% construct a new framework for circuits as well as develop novel approaches and
+% techniques in order to work with these circuits. We began by generalising the
+% notion of a symmetric function, introducing isomorphism-invariant structured
+% functions. These functions take in structures encoded and strings and are
+% invariant under isomorphism, rather than under arbitrary permutations of the
+% string. It is easy to see that rank-threshold functions are
+% isomorphism-invariant. We defined a basis to be a set of isomorphism-invariant
+% functions, and extended the circuit model, adding to each gate in the circuit a
+% structure on its input gates in accord with the isomorphism-invariant structured
+% function labelling that gate. Rather than a gate being invariant under arbitrary
+% permutations of its input gates, a gate in this circuit should be invariant
+% under permutations of its input gate that form a (labelled) isomorphism. We
+% extended the notion of an automorphism to reflect this and defined what it means
+% for a circuit to be symmetric.
 
-% used throughout this paper, and is needed in order to apply the support
-% theorem or reason about orbits, we need to
+While the new framework allows us to reproduce some results such as
+the support theorem, something is lost in the generalisation.  When
+our basis contains only symmetric functions, important properties of
+a circuit, including the symmetry of the circuit itself, are easily
+decidable.  In the new framework, checking circuit automorphism
+requires checking isomorphism of structured inputs to gates and codes
+hard problems.  For this reason, we imposed a further restriction to
+the circuits in the form of \emph{transparency}.  But, it should be
+clear that this is a restriction only in the broader framework.  All
+symmetric circuits with only symmetric gates are transparent.  Thus,
+transparent, symmetric circuits are still a generalisation of those
+considered in~\cite{AndersonD17}.
 
-% for are we have shown that many natural circuit properties which are known to
-% be polynomial-time decidable for circuits over symmetric bases are at least as
-% hard to decide for circuits over non-symmetric bases as the graph isomorphism
-% problem.
+The condition of transparency makes the translation of uniform circuit
+families into formulas of logic (which is the difficult direction of
+our characterisation) possible, but it complicates the other direction.
+Indeed, the natural translation of formulas of $\FPR$ into uniform
+circuit families yields circuits which are symmetric, but not
+transparent.  This problem is addressed by introducing gadgets in the
+translation---which for ease of exposition, we did in formulas of
+$\FOrk$ which are then translated into circuits in the natural way.
+Thus, the restriction to transparent circuits is sufficient to get
+both directions of the characterisation.  Moreover, we argue that
+something like it is necessary in order to avoid having to solve hard
+isomorphism problems in the translation.
 
-% This follows from in a rather subtle way from the fact that
-% syntactic-equivalence for symmetric gates requires nothing more than checking
-% if two quotiented sets are equal, while syntactic-equivalence between
-% non-symmetric gates involves checking if two quotiented structures are equal.
-% As such, while determining many
+% While we have generalised a few results for this framework, including the
+% support theorem, it is important to note that a number of crucial counting
+% techniques and polynomial-time algorithms for circuits are either not easy to
+% generalise or otherwise resist generalisation entirely. This follows from the
+% fact that a circuit automorphism needs to preserve more structure when acting on
+% non-symmetric gates than when acting on symmetric gates. As a result, while many
+% symmetry-related circuit properties are polynomial-time decidable for circuits
+% with symmetric gates, we have shown that these same properties are at least as
+% hard as the graph-isomorphism for circuits with non-symmetric gates. This is a
+% problem as the polynomial-time decidability of these properties is essential for
+% our translation from circuits into formulas.
 
-% While for circuits with functions into the basis. In Anderson and Dawar's case
-% establishing the image of a gate under the action of an automorphism is
-% entirely determined by the
-
-% In particular, in order to define the translation from families of circuits to
-% formulas we need that a number However, in order to prove this result we need
-% to be able to compute in polynomial-time many basic symmetry-related
-% properties of the circuit, and most of these properties reference the
-% existence of an isomorphism between the structures associated with each gate.
-% We show in Section~\ref{sec:transparent} that, in fact, deciding many of these
-% properties for (general) rank-circuits is at least as hard as the
-% graph-isomorphism problem. Importantly, the circuits studied by Anderson and
-% Dawar have all of the relevant algorithmic, as in this case the isomorphism
-% problems that arises reduces to set-equivalence, which is obviously
-% polynomial-time decidable.
-
-% In partoTo be more procides This is a problem, as these algorithmic properties
-% are needed throughout the paper
-
-% In particular, while almost all of the relevant properties are polynomial-time
-% decidable for circuits with symmetric gates, enabling a in polynomial-time
-% transformed into a normal form with unique extensions. Moreover, this normal
-% form also many other crucial algorithmic properties needed to prove the main
-% result, particularly the ability to compute the action of a permutation on a
-% circuit, in polynomial-time. We showed in Section~\ref{} that these useful
-% algorithmic properties are not (necessarily) preserved by the generalisation.
-% In particular, we showed that none of these properties are polynomial-time
-% decidable for rank-circuits (or any class of circuits over a non-symmetric
-% basis) unless the graph isomorphism is in $\PT$.
-
-% In order to prove our main result we $\PT$-uniform families of symmetric
-% rank-circuits into equivalent formulas of $\FPR$ and visa
-
-% Dawar. However, However, It would be natural to take symmetric rank-circuits
-% as the natural generalisation of Anderson and Dawar's symmetric circuits and
-% aim to prove an equivalence between the expressive power $\FPR$ and the
-% computational power of $\PT$-uniform families symmetric rank-circuits.
-% However, in order to prove this result we need to be able to compute in
-% polynomial-time many basic symmetry-related properties of the circuit, and
-% most of these properties reference the existence of an isomorphism between the
-% structures associated with each gate. We show in Section~\ref{sec:transparent}
-% that, in fact, deciding many of these properties for (general) rank-circuits
-% is at least as hard as the graph-isomorphism problem. Importantly, the
-% circuits studied by Anderson and Dawar have all of the relevant algorithmic,
-% as in this case the isomorphism problems that arises reduces to
-% set-equivalence, which is obviously polynomial-time decidable.
-
-% In order to ensure
-
-% when we introduce rank-gates this isomorphism problem that computing the
-% action of an automorphism, or showing that a circuit is symmetric, or
-% computing a great number of important properties is at least as hard for
-% rank-circuits as the graph-isomorphism problem.
-
-% to be able to apply the support theorem to circuits, and so needed a normal
-% form for circuits with unique extensions, and we also needed to ensure that a
-% number of basic circuit properties, and particularly those relating to
-% symmetry, are polynomial-time decidable to circuits as well as compute a
-% number of basic circuit properties in polynomial-time. This is not a problem
-% for Anderson and Dawar, as all of the relevant circuit properties are
-% polynomial-time decidable for symmetric-circuits with symmetric gates.
-% Moreover, can be easily transformed into a normal form that has unique
-% extensions (allowing for the application of the support theorem) and all of
-% the nessasary circuit-properties are
-
-% apply the support theorem, a crucial step in out proof, and in order to
-
-% the introduction of structured functions complicates the analysis of such
-% circuits. As we showed in Section~\ref{sec:transparent}, most of the
-% properties of these rank-circuits are at least as hard to decide as the graph
-% isomorphism problem. This poses a problem as the approach we take (and the
-% approach Anderson and Dawar take) to proving this characterisation make
-% repeated use of the polynomial-time decidability of these properties. Indeed,
-% the two key results for translating $\PT$-uniform circuit families into
-% equivalent formulas, the support theorem and the inductive evaluation of a
-% gate (see Section~\ref{sec:circuits-to-formulas}), make use of polynomial-time
-% algorithms for transforming a circuit into an equivalent circuit with unique
-% labels, as well as for deciding if a circuit is symmetric, computing orbits,
-% and deciding syntactic-equivalence.
-
-As such, instead of working with general rank-circuits we have restricted our
-attention to \emph{transparent} circuits, and proved our characterisation in
-terms of $\PT$-uniform families of transparent symmetric rank-circuits. As we
-have shown in Section~\ref{sec:transparent}, all of the relevant properties are
-polynomial-time decidable for transparent circuits. Since all circuits with
-symmetric gates are transparent, we might think of transparent circuits as an
-alternative, more `algorithmically accessible', generalisation of the circuits
-studied by Anderson and Dawar. However, while this restriction to transparent
-circuits aids in our translation from circuits to formulas, it complicates our
-translation in the other direction. Indeed, it is not hard to see that the
-conventional approach for translating formulas of $\FO$ (or $\FPC$, or other
-extensions of $\FO$) into $\PT$-uniform families of circuits does not, in
-general, produce a family of transparent circuits. In order to address this we
-defined a novel translation from formulas of $\FPR$ into equivalent
-$\PT$-uniform families of transparent symmetric rank-circuits. This translation
-is defined in two steps. First, we defined a translation from $\FPR$ to
-$\PT$-uniform families of bounded-width formulas of $\FOrk$ and, second, we
-defined a translation from these families of formulas into $\PT$-uniform
-families of transparent symmetric rank-circuits. This translation, along with
-the main result of the paper, gives us an equivalence between the expressive
-power of three formalisms, which we summarise as follows:
+% As such, instead of working with general rank-circuits we have restricted our
+% attention to \emph{transparent} circuits, and proved our characterisation in
+% terms of $\PT$-uniform families of transparent symmetric rank-circuits. As we
+% have shown in Section~\ref{sec:transparent}, all of the relevant properties are
+% polynomial-time decidable for transparent circuits. Since all circuits with
+% symmetric gates are transparent, we might think of transparent circuits as an
+% alternative, more `algorithmically accessible', generalisation of the circuits
+% studied by Anderson and Dawar. However, while this restriction to transparent
+% circuits aids in our translation from circuits to formulas, it complicates our
+% translation in the other direction. Indeed, it is not hard to see that the
+% conventional approach for translating formulas of $\FO$ (or $\FPC$, or other
+% extensions of $\FO$) into $\PT$-uniform families of circuits does not, in
+% general, produce a family of transparent circuits. In order to address this we
+% defined a novel translation from formulas of $\FPR$ into equivalent
+% $\PT$-uniform families of transparent symmetric rank-circuits. This translation
+% is defined in two steps. First, we defined a translation from $\FPR$ to
+% $\PT$-uniform families of bounded-width formulas of $\FOrk$ and, second, we
+% defined a translation from these families of formulas into $\PT$-uniform
+% families of transparent symmetric rank-circuits. This translation, along with
+% the main result of the paper, gives us an equivalence between the expressive
+% power of three formalisms, which we summarise as follows:
 
@@
 
+In short, we can represent the proof of our characterisation through
+the three equivalences in this triangle.
+
 \begin{center}
   \begin{tikzcd}
-    \FPR \ar[r, equal] \ar[dr, equal] & \parbox{0.35\textwidth}{$\PT$-uniform
+    \FPR \ar[r, equal] \ar[dr, equal] & \parbox{0.35\textwidth}{Uniform
       families of
-      bounded-width $\FOrk$-formulas}  \ar[d, equal]\\
-    & \parbox{0.38\textwidth}{$\PT$-uniform families of transparent symmetric
+      bounded-width $\FOrk$ formulas}  \ar[d, equal]\\
+    & \parbox{0.38\textwidth}{Uniform families of transparent symmetric
       rank-circuits}
@@
 
-We already have a very similar result from from Anderson and
-Dawar~\cite{AndersonD17} and Otto~\cite{Otto1996}:
+This highlights another interesting aspect of our result.  The first
+translation, of $\FPR$ to uniform families of $\FOrk$ formulas was
+given in~\cite{Dawar09logicswith} and used there to establish arity
+lower bounds.  However, this was for a weaker version of the rank
+logic rather than the strictly more expressive one defined by
+Gr\"{a}del and Pakusa~\cite{GradelP15a}.  The fact that we can
+complete the cycle of equivalences with the more powerful logic
+demonstrates that the definition of Gr\"{a}del and Pakusa is the
+``right'' formulation of $\FPR$.
 
-\begin{center}
-  \begin{tikzcd}
-    \FPC \ar[r, equal] \ar[dr, equal] & \parbox{0.35\textwidth}{$\PT$-uniform
-      families of
-      bounded-width $\FOc$-formulas}  \ar[d, equal]\\
-    & \parbox{0.35\textwidth}{$\PT$-uniform families of symmetric circuits with
-      symmetric gates}
-  \end{tikzcd}
-\end{center}
+% We already have a very similar result from from Anderson and
+% Dawar~\cite{AndersonD17} and Otto~\cite{Otto1996}:
 
-These two sets of equivalences each give us three distinct formalisms equivalent
-to $\FPR$ and $\FPC$, respectively. Importantly, each of these three formalisms
-for $\FPC$ may be extended by a rank in quite distinct ways. We can extend
-$\FOc$ by rank quantifiers and define $\FOrk$, we can add rank gates to
-symmetric circuits with symmetric gates and define transparent symmetric
-rank-circuits, and we can extend $\FPC$ by a rank operator and define $\FPR$. We
-might expect these three quite different extensions to result in three
-formalisms with quite different expressive power. However, the main result of
-this paper along with the translation we discussed above, gives us that these
-three extensions are indeed all equivalent. This provides evidence in favour of
-the proposition that $\FPR$ is indeed the canonical, and most natural, extension
-of $\FPC$. This is in contrast with the other rank logic in the literature, the
-one introduced by Dawar et al.~\cite{Dawar09logicswith}, which was shown by
-Gr\"{a}del and Pakusa~\cite{GradelP15a} to be strictly less expressive than
-$\FPR$, and hence less expressive than $\PT$-uniform families of bounded-width
-$\FOrk$ and $\PT$-uniform families of transparent symmetric rank-circuits.
+% \begin{center}
+%   \begin{tikzcd}
+%     \FPC \ar[r, equal] \ar[dr, equal] & \parbox{0.35\textwidth}{$\PT$-uniform
+%       families of
+%       bounded-width $\FOc$-formulas}  \ar[d, equal]\\
+%     & \parbox{0.35\textwidth}{$\PT$-uniform families of symmetric circuits with
+%       symmetric gates}
+%   \end{tikzcd}
+% \end{center}
+
+% These two sets of equivalences each give us three distinct formalisms equivalent
+% to $\FPR$ and $\FPC$, respectively. Importantly, each of these three formalisms
+% for $\FPC$ may be extended by a rank in quite distinct ways. We can extend
+% $\FOc$ by rank quantifiers and define $\FOrk$, we can add rank gates to
+% symmetric circuits with symmetric gates and define transparent symmetric
+% rank-circuits, and we can extend $\FPC$ by a rank operator and define $\FPR$. We
+% might expect these three quite different extensions to result in three
+% formalisms with quite different expressive power. However, the main result of
+% this paper along with the translation we discussed above, gives us that these
+% three extensions are indeed all equivalent. This provides evidence in favour of
+% the proposition that $\FPR$ is indeed the canonical, and most natural, extension
+% of $\FPC$. This is in contrast with the other rank logic in the literature, the
+% one introduced by Dawar et al.~\cite{Dawar09logicswith}, which was shown by
+% Gr\"{a}del and Pakusa~\cite{GradelP15a} to be strictly less expressive than
+% $\FPR$, and hence less expressive than $\PT$-uniform families of bounded-width
+% $\FOrk$ and $\PT$-uniform families of transparent symmetric rank-circuits.
 
@@
 
-\subsection{Future Work}
-We have shown that $\FPR$ has the same expressive power as $\PT$-uniform
-families of transparent symmetric rank-circuits. It is easy to see that
-$\PT$-uniform families of symmetric rank-circuits must be at least as powerful
-as $\PT$-uniform families of transparent symmetric rank-circuits. It is natural
-to ask if these two formalisms actually have the same expressive power or
-whether the transparency restriction does indeed restrict the expressive power
-of the model. It is worth noting that if families of symmetric rank-circuits and
-families of transparent symmetric-rank circuits do not have the same expressive
-power then $\FPR$ does not capture $\PT$.
+\subsection*{Future Work}
+There are many directions of work suggested by the methods and results
+developed in this paper.  First of all, there is the question of
+transparency.  We introduce it as a technical device that enables our
+characterisation to go through.  Could it be dispensed with?  Or are $\PT$-uniform
+families of transparent symmetric rank-circuits strictly weaker than
+families without the restriction of transparency?  Of course a
+positive answer to the latter question would require separating $\FPR$
+from $\PT$.
 
-In this paper we have developed a framework for working with circuits over
-non-symmetric bases. In fact, the first time we explicitly use make any
-reference to linear algebra is in the proof of
-Lemma~\ref{lem:rank-triple-equivilence}, right towards the end of the paper. It
-would be natural to ask if our circuit characterisation of $\FPR$ can be
-generalised in order to develop similar characterisations of other logics. It
-might be good idea to start with some other extension of $\FP$ by some operator
-and try to develop a similar circuit characterisation in terms $\PT$-uniform
-transparent symmetric circuits over an appropriate basis. There are numerous
-logics that are similar in definition to $\FPR$ but which are not known to have
-the same expressive power as $\FPR$, for example $\FP$ extended by an operator
-that expresses the solubility of systems of equations over rings (rather than
-fields). A first step might be to develop a circuit characterisation of one of
-these logics.
+The framework we have developed for  working with circuits with
+structured inputs is very general and not specific to rank gates.
+Indeed, the first use we make of linear algebra is in the proof of
+Lemma~\ref{lem:rank-triple-equivilence}.  It would be interesting to
+apply this framework to other logics.  It appears to be as general a way of
+extending the power of circuits as Lindstr\"om quantifiers are in the
+context of logic.  We would like to develop this link
+further, perhaps for specific quantifiers such as $\FP$ extended by an operator
+that expresses the solubility of systems of equations over rings as in~\cite{DGHKP}
+
+% In this paper we have developed a framework for working with circuits over
+% non-symmetric bases. In fact, the first time we explicitly use make any
+% reference to linear algebra is in the proof of
+% Lemma~\ref{lem:rank-triple-equivilence}, right towards the end of the paper. It
+% would be natural to ask if our circuit characterisation of $\FPR$ can be
+% generalised in order to develop similar characterisations of other logics. It
+% might be good idea to start with some other extension of $\FP$ by some operator
+% and try to develop a similar circuit characterisation in terms $\PT$-uniform
+% transparent symmetric circuits over an appropriate basis. There are numerous
+% logics that are similar in definition to $\FPR$ but which are not known to have
+% the same expressive power as $\FPR$, for example $\FP$ extended by an operator
+% that expresses the solubility of systems of equations over rings (rather than
+% fields). A first step might be to develop a circuit characterisation of one of
+% these logics.
 
@@
 
-While we have developed a new and much more general circuit framework we have
-not developed any approaches for proving lower bounds. As a first step out might
-try to prove lower bounds for symmetric circuits with gates with bounded fan-in.
+At the moment, we have little by way of methods for proving
+inexpressibility results for $\FPR$, whether we look at it as a logic
+or in the circuit model.  The logical formulation lays emphasis
+on some parameters (the number of variables, the arity of the
+operators, etc.) which we can treat as resources against which to
+prove lower bounds.  On the other hand, the circuit model brings to
+the fore other, more combinatorial, parameters.  One such is the
+fan-in of gates and a promising and novel approach is to try and prove lower bounds for symmetric circuits with gates with bounded fan-in.
 We might ask if it is possible to compute $\AND[3]$ using a symmetric circuit
-with gates that have fan-in two.
+with gates that have fan-in two.  Perhaps we could also combine the
+circuit view with lower-bound methods from logic, such as pebble games.
+ Dawar~\cite{Dawar2016} has shownn how the bijection games of
+ Hella~\cite{Hella19961} can be used directly to prove lower
+ bounds for symmetric without reference to the logic.  We also have pebble
+ games for $\FPR$~\cite{DawarH2012}, and it would be interesting to
+ know if we can use these on circuits and how the combinatorial
+ parameters of the circuit interact with the game.
 
-An alternative, and perhaps more sophisticated, approach would be to try and use
-pebble games, a standard tool for proving inexpressibility results in logic, to
-directly prove lower bounds on circuits. Dawar~\cite{Dawar2016} has shown, via a
-circuit-based argument, that the pebble games of Hella~\cite{Hella19961} can
-played directly on symmetric circuits with symmetric gates without any need to
-reference the logic. Dawar and Holm~\cite{DawarH2012} have defined a similar
-pebble game for $\FPR$, and it would be interesting to know if an analogous
-result can be established, allowing us play this pebble game directly on
-symmetric rank-circuits and use it to prove lower bounds for these circuits.
+Finally, we note that some of the interesting directions on the
+interplay between logic and symmetric circuits raised
+in~\cite{AndersonD17} remain relevant.  Can we relax the symmetry
+condition to something in between requiring invariance of the circuit
+under the full symmetric group (the case of symmetric circuits) and
+requiring no invariance condition at all?  Can such restricted
+symmetries give rise to interesting logics in between $\FPR$ and
+$\PT$?  It also remains a challenge to find a circuit characterisation
+of  $\CPTC$.  Could the general framework for non-symmetric gates we
+have developed here help in this respect?
 
-We have shown that the $\PT$-uniform families of transparent symmetric
-rank-circuits (resp. circuits with symmetric gates) have the same expressive
-power as $\FPR$ (resp. $\FPC$), but we recall that if we remove the symmetry
-restriction these circuit models express exactly those queries in $\PT$. A
-natural next step, also suggested by Anderson and Dawar, would be try and weaken
-the symmetry condition. One way this might be done would be to require that only
-permutations from a particular subgroup of the symmetric group extend to
-automorphisms of the circuit. It is easy to see that if we take this subgroup to
-be the trivial subgroup then this nullifies the the symmetry requirement, and
-the circuit model has the same expressive power as $\PT$, while if we take this
-subgroup to be the entire symmetric group then we get back the full symmetry
-requirement and hence our model has the same expressive power as the logic. As
-such, this approach can be used to interpolate between the logic and $\PT$.
+% We have shown that the $\PT$-uniform families of transparent symmetric
+% rank-circuits (resp. circuits with symmetric gates) have the same expressive
+% power as $\FPR$ (resp. $\FPC$), but we recall that if we remove the symmetry
+% restriction these circuit models express exactly those queries in $\PT$. A
+% natural next step, also suggested by Anderson and Dawar, would be try and weaken
+% the symmetry condition. One way this might be done would be to require that only
+% permutations from a particular subgroup of the symmetric group extend to
+% automorphisms of the circuit. It is easy to see that if we take this subgroup to
+% be the trivial subgroup then this nullifies the the symmetry requirement, and
+% the circuit model has the same expressive power as $\PT$, while if we take this
+% subgroup to be the entire symmetric group then we get back the full symmetry
+% requirement and hence our model has the same expressive power as the logic. As
+% such, this approach can be used to interpolate between the logic and $\PT$.
 
-There is a rather easy way to develop a circuit characterisation for any logic
-or complexity class with complete problems under first-order reductions. All
-that is required is to extend the basis with the family of functions that decide
-a complete problem and consider $\PT$-uniform families of transparent symmetric
-circuits over this basis. We did not take this approach in our characterisation
-of $\FPR$, preferring to use a more `natural' basis that more closely resembles
-the actual definition of the logic. We should like to ask if there is a similar
-circuit characterisation of $\CPTC$. One might start with bounded-rank fragments
-of $\CPTC$ and see if these programs can be translated into circuits. We should
-note that it does seem as though the symmetry inherent in $\CPTC$ programs is in
-some sense different from the symmetry of symmetric circuits. It might be more
-natural then to ask if $\CPTC$ can be characterised using families of circuits
-with a weakened symmetry requirement.
+% There is a rather easy way to develop a circuit characterisation for any logic
+% or complexity class with complete problems under first-order reductions. All
+% that is required is to extend the basis with the family of functions that decide
+% a complete problem and consider $\PT$-uniform families of transparent symmetric
+% circuits over this basis. We did not take this approach in our characterisation
+% of $\FPR$, preferring to use a more `natural' basis that more closely resembles
+% the actual definition of the logic. We should like to ask if there is a similar
+% circuit characterisation of $\CPTC$. One might start with bounded-rank fragments
+% of $\CPTC$ and see if these programs can be translated into circuits. We should
+% note that it does seem as though the symmetry inherent in $\CPTC$ programs is in
+% some sense different from the symmetry of symmetric circuits. It might be more
+% natural then to ask if $\CPTC$ can be characterised using families of circuits
+% with a weakened symmetry requirement.
 
